### 2023-12-13 main.tex
:pencil: Add MIMO power problem

\documentclass[journal]{IEEEtran}
% \documentclass[journal,12pt,onecolumn,draftclsnofoot]{IEEEtran}

\usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[makeroom]{cancel}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}

% page limit hacks
% \usepackage{setspace}
% ! \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
% \abovedisplayskip=1mm
% \belowdisplayskip=1mm
% \abovedisplayshortskip=1mm
% \belowdisplayshortskip=1mm
% \setlength{\jot}{0.1mm}
% \setlength{\floatsep}{1mm}
% \setlength{\textfloatsep}{1mm}
% \setlength{\intextsep}{1mm}
% \setlength{\skip\footins}{2mm}

% amsthm
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}

% PGF/TikZ
\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,decorations.shapes,shapes.geometric}
\usepgfplotslibrary{groupplots,patchplots}
\pgfplotsset{compat=newest}

% tabularx, ragged2e
\newcolumntype{L}{>{\RaggedRight}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\renewcommand\tabularxcolumn[1]{m{#1}}

% algpseudocode
\makeatletter
\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
\newcommand\setalgorithmcaptionfont[1]{%
	\let\my@floatc@ruled\floatc@ruled          % save \floatc@ruled
	\def\floatc@ruled{%
		\global\let\floatc@ruled\my@floatc@ruled % restore \floatc@ruled
		#1\floatc@ruled}}
\makeatother

\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
\algrenewcommand{\algorithmicdo}{}

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
% \newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{bd}{BD}{Beyond-Diagonal}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}

\begin{document}
\title{Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		Hongyu~Li,~\IEEEmembership{Graduate Student Member,~IEEE,}\\
		Yijie~Mao,~\IEEEmembership{Member,~IEEE,}
		Shanpu~Shen,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	% \thanks{
	% 	The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	% 	B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
	% }
}
\maketitle

% \begin{abstract}
% \end{abstract}

% \begin{IEEEkeywords}
% \end{IEEEkeywords}

\glsresetall

\begin{section}{Assumption}
	All proposals in this paper based on assumption of \emph{asymmetric} passive \gls{bd} \gls{ris}, i.e., symmetry constraint $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T}$ is relaxed.
	This is feasible when asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} are available.
	This assumption was also made in Hongyu's papers \cite{Li2023b,Li2023c}.
	For quadratic problems, the proposed algorithms may be extended to symmetric \gls{bd} \gls{ris} by replacing singular value decomposition with Takagi factorization \cite{Horn2012}.
\end{section}

\begin{section}{Point-to-Point MIMO}
	\begin{subsection}{Channel Power Maximization}
		Consider a \gls{bd} \gls{ris} with $N_\mathrm{s}$ elements, which is divided into $G$ groups of equal $L$ elements.
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\left\lVert \mathbf{H}^\mathrm{D} + \sum_g\nolimits \mathbf{H}_g^\mathrm{B} \mathbf{\Theta}_g \mathbf{H}_g^\mathrm{F} \right\rVert _\mathrm{F}^2}{\label{op:channel_power}}{}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}_L, \quad \forall g \in \mathcal{G} \triangleq \{1,\ldots,G\}}{}{}
		\end{maxi!}
		For \emph{symmetric} BD-RIS, the problem has been solved in
		\begin{itemize}
			\item Matteo's paper \cite{Nerini2023}: SISO and equivalent\footnote{Single-stream MIMO with given precoder and combiner.};
			\item Ignacio's paper \cite{Santamaria2023}: SISO and directless MISO/SIMO.
		\end{itemize}

		\begin{remark}
			% The difficulty of \eqref{op:channel_power} is that the \gls{ris} needs to balance the (additive) direct-indirect eigenspace alignment and the (multiplicative) forward-backward eigenspace alignment.
			The difficulty of \eqref{op:channel_power} is that the \gls{ris} needs to balance the additive (direct-indirect) and multiplicative (backward-forward) eigenspace alignment.
			% align the direct and indirect eigenspaces while preserving the
			Interestingly, it has the same form as the \emph{weighted orthogonal Procrustes problem} \cite{Gower2004}:
			\begin{mini!}
				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{C} - \mathbf{A \Theta B} \rVert _\text{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I}}{}{}
			\end{mini!}
			There exists no trivial solution to \eqref{op:weighted_orthogonal_procrustes}.
			One lossy transformation, by moving $\mathbf{\Theta}$ to one side \cite{Bell2003}, formulates a standard orthogonal Procrustes problem:
			\begin{mini!}
				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{A}^\dagger \mathbf{C} - \mathbf{\Theta B} \rVert _\text{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I}}{}{}
			\end{mini!}
			\eqref{op:standard_orthogonal_procrustes} has a global optimal solution $\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}$, where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{\mathbf{A}^\dagger \mathbf{C} \mathbf{B}^\mathsf{H}}$ \cite{Golub2013}.
			This low-complexity solution will be compared with the one proposed later.
		\end{remark}

		Inspired by \cite{Nie2017}, we propose an iterative algorithm to solve \eqref{op:channel_power}.
		The idea is to successively approximate the quadratic objective with a sequence of affine functions and solve the resulting subproblems in closed form.

		\begin{proposition}
			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
			\begin{equation}
				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g \in \mathcal{G}
			\end{equation}
			converges to a stationary point of \eqref{op:channel_power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
			\begin{equation}
				\begin{split}
					\mathbf{M}_g^{(r)}
					& = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{H}^\mathrm{D} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H} + \sum_{g' < g} {\mathbf{H}_{g'}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{g'}^\mathrm{B} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{g'}^\mathrm{F} {\mathbf{H}_{g'}^\mathrm{F}}^\mathsf{H} \\
					& \quad + \sum_{g' \ge g} {\mathbf{H}_{g'}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{g'}^\mathrm{B} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{g'}^\mathrm{F} {\mathbf{H}_{g'}^\mathrm{F}}^\mathsf{H}.
				\end{split}
			\end{equation}
		\end{proposition}

		\begin{proof}
			TODO
		\end{proof}

		% For any $\mathbf{\Theta}$, define the coefficient matrix of group $g \in \mathcal{G}$ as
		% \begin{equation}
		% 	\mathbf{M}_g \triangleq
		% \end{equation}
		% \begin{
		% \begin{itemize}
		% 	\item It becomes orthogonal procrustes problem with {\color{blue}closed-form solution if $\mathbf{\Theta}$ can be moved to one side}
		% 	\item For example, if $\mathbf{A}$ is unitary, then $\arg \min_\mathbf{\Theta} \lVert \mathbf{C} - \mathbf{A \Theta B} \rVert_\text{F}^2 = \arg \min_\mathbf{\Theta} \lVert \mathbf{A}^\mathsf{H} \mathbf{C} - \mathbf{\Theta B} \rVert_\text{F}^2$
		% \end{itemize}
		% The problem is nontrivial because
		% \begin{itemize}
		% 	\item $\mathbf{H}_{\text{B},g} \triangleq \mathbf{H}_\text{B}[:, (g-1)Q+1:gQ]$, $\mathbf{H}_{\text{F},g} \triangleq \mathbf{H}_\text{F}[(g-1)Q+1:gQ, :]$
		% 	\item RIS needs to balance $\lVert \mathbf{H}_\text{B} \mathbf{\Theta} \mathbf{H}_\text{F} \rVert^2$ and $\langle \mathbf{H}_\text{D}, \mathbf{H}_\text{B} \mathbf{\Theta} \mathbf{H}_\text{F} \rangle$
		% 	\item Same form as \emph{the weighted orthogonal Procrustes problem}, no closed-form solution
		% \end{itemize}
	\end{subsection}
\end{section}

\bibliographystyle{IEEEtran}
\bibliography{library.bib}
\end{document}

### 2023-12-13 main.tex
:pencil: Finsh MIMO power problem

@@
 	\begin{subsection}{Channel Power Maximization}
-		Consider a \gls{bd} \gls{ris} with $N_\mathrm{s}$ elements, which is divided into $G$ groups of equal $L$ elements.
+		Consider a \gls{bd} \gls{ris} with $N_\mathrm{S}$ elements, which is divided into $G$ groups of equal $L$ elements.
 		\begin{maxi!}
@@
 			% The difficulty of \eqref{op:channel_power} is that the \gls{ris} needs to balance the (additive) direct-indirect eigenspace alignment and the (multiplicative) forward-backward eigenspace alignment.
-			The difficulty of \eqref{op:channel_power} is that the \gls{ris} needs to balance the additive (direct-indirect) and multiplicative (backward-forward) eigenspace alignment.
+			The difficulty of \eqref{op:channel_power} is that the \gls{ris} needs to balance the additive (direct-indirect) and multiplicative (forward-backward) eigenspace alignment.
 			% align the direct and indirect eigenspaces while preserving the
@@
 		\begin{proof}
-			TODO
+			To be added.
 		\end{proof}
 
-		% For any $\mathbf{\Theta}$, define the coefficient matrix of group $g \in \mathcal{G}$ as
-		% \begin{equation}
-		% 	\mathbf{M}_g \triangleq
-		% \end{equation}
-		% \begin{
-		% \begin{itemize}
-		% 	\item It becomes orthogonal procrustes problem with {\color{blue}closed-form solution if $\mathbf{\Theta}$ can be moved to one side}
-		% 	\item For example, if $\mathbf{A}$ is unitary, then $\arg \min_\mathbf{\Theta} \lVert \mathbf{C} - \mathbf{A \Theta B} \rVert_\text{F}^2 = \arg \min_\mathbf{\Theta} \lVert \mathbf{A}^\mathsf{H} \mathbf{C} - \mathbf{\Theta B} \rVert_\text{F}^2$
-		% \end{itemize}
-		% The problem is nontrivial because
-		% \begin{itemize}
-		% 	\item $\mathbf{H}_{\text{B},g} \triangleq \mathbf{H}_\text{B}[:, (g-1)Q+1:gQ]$, $\mathbf{H}_{\text{F},g} \triangleq \mathbf{H}_\text{F}[(g-1)Q+1:gQ, :]$
-		% 	\item RIS needs to balance $\lVert \mathbf{H}_\text{B} \mathbf{\Theta} \mathbf{H}_\text{F} \rVert^2$ and $\langle \mathbf{H}_\text{D}, \mathbf{H}_\text{B} \mathbf{\Theta} \mathbf{H}_\text{F} \rangle$
-		% 	\item Same form as \emph{the weighted orthogonal Procrustes problem}, no closed-form solution
-		% \end{itemize}
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/pc_power_sx.tex}
+			}
+			\caption{Average channel power versus \gls{ris} elements $N_\mathrm{S}$ and group size $L$ for $(N_\mathrm{T}, N_\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+			\label{sm:pc_power_sx}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Without Direct Link\label{sm:pc_power_bond_nd}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_power_bond_nd.tex}
+				}
+			}
+			\subfloat[With Direct Link\label{sm:pc_power_bond_hd}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_power_bond_hd.tex}
+				}
+			}
+			\caption{Average channel power versus \gls{ris} group size $L$ for $(N_\mathrm{T}, N_\mathrm{S}, N_\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+			\label{sm:pc_power_bond}
+		\end{figure}
+		% Fig.~\ref{sm:pc_power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
+		% Fig.~\ref{sm:pc_power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
+		Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N_\mathrm{S}$, increasing the group size $L$ also improves the channel power.
+		% The behavior is more obvious for a large \gls{ris}.
+		This behavior is more pronounced for a large \gls{ris}.
+		For example, the gain of pairwise connection is 2.8\% for $N_\mathrm{S} = 16$ and 28\% for $N_\mathrm{S} = 256$.
+		% \gls{bd} \gls{ris} provides a higher channel power than conventional \gls{ris}.
+		% As $L$ increases from 1 to 2,
+		It implies that the channel shaping capability of \gls{bd} \gls{ris} scales with group size $L$.
+
+		Fig.~\ref{sm:pc_power_bond_hd} and \ref{sm:pc_power_bond_nd} compare the average channel power without and with direct link.
+		% where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
+		% where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
+		% ``Cascaded'' means the maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
+		% maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
+		``Cascaded'' means the \emph{power product} of the forward and backward channels.
+		We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect eigenspace.
+		When the direct link is absent, only 2.6\% of available power is utilized by diagonal \gls{ris} while 100\% power is recycled by fully-connected \gls{ris}.
+		When the direct link is present, the proposed \gls{bd} \gls{ris} design can balance the direct-indirect and forward-backward eigenspace alignment for an optimal channel boost.
+		It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
+		This again emphasizes the advantage of in-group connection of \gls{bd} \gls{ris}.
+		% This is because the direct and indirect channels superpose
+		% the proposed \gls{bd} \gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
+		% When the direct link is present, a small $L$ cannot align the direct-indirect eigenspace.
+
+		% neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect eigenspace.
+		% We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect eigenspace.
+		% For conventional \gls{ris},
+		% align the direct-indirect eigenspace.
+		% When the direct link is present, a small $L$ can neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
+		% For a relatively large $N_\mathrm{S}$, conventional \gls{ris} cannot
+		% neither the direct-indirect nor the forward-backward eigenspace can be effectively aligned with a small $L$.
+
+		% When the direct link is present, a small $L$ can neither preserve the
+		% neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
+
+		% When the direct link is absent, a large $L$ can align the forward-backward eigenspace but cannot preserve the forward-backward power balance.
 	\end{subsection}

### 2023-12-13 src/pc_power_bond.m

@@ -3,7 +3,7 @@ clc; clear; close; setup;
 [transmit.antenna, reflect.antenna, receive.antenna] = deal(8, 256, 4);
 [channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2 .^ (0 : 2 : log2(reflect.antenna)));
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.bond, number.realization, flag.direct] = deal(length(reflect.bond), 1e1, true);
+[number.bond, number.realization, flag.direct] = deal(length(reflect.bond), 1e1, false);
 
 for r = 1 : number.realization
 	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
@@ -27,18 +27,22 @@ end
 
 figure('Name', 'Channel Power vs RIS Group Size', 'Position', [0, 0, 500, 400]);
 hold all;
-for b = 1 : number.bond
-	handle.power(b) = bar(b, channel.power.aggregate(b));
-end
-handle.power(b + 1) = refline(0, channel.power.direct);
-handle.power(b + 2) = refline(0, channel.power.cascaded);
-set(handle.power(b + 1), 'Color', 'k', 'Marker', 'none');
-set(handle.power(b + 2), 'Color', '#ED8198', 'Marker', 'none');
+handle.power(1) = bar(channel.power.aggregate, 'FaceColor', '#77AC30');
+handle.power(2) = refline(0, channel.power.direct);
+handle.power(3) = refline(0, channel.power.cascaded);
+hold off; grid on; box on;
+set(handle.power(2), 'Color', 'k', 'Marker', 'none');
+set(handle.power(3), 'Color', '#ED8198', 'Marker', 'none');
+xlim([0, number.bond + 1]);
+xticks(1 : number.bond);
+xticklabels(reflect.bond);
 xlabel('RIS Group Size');
 ylabel('Channel Power [W]');
-legend(['$L = ' + string(vec(reflect.bond)) + '$'; 'Direct'; 'Cascaded'], 'Location', 'nw');
+legend(handle.power, {'Composite'; 'Direct'; 'Cascaded'}, 'Location', 'nw');
 if flag.direct == true
 	savefig('plots/pc_power_bond_hd.fig');
[…]

### 2023-12-13 src/pc_power_sx.m

@@ -35,9 +35,10 @@ for a = 1 : number.antenna
 		handle.power(a) = plot(log2(reflect.bond), channel.power.aggregate(1 : number.bond, a));
 	end
 end
-hold off; grid on;
+hold off; grid on; box on;
 style_plot(handle.power); set(handle.power(find(reflect.antenna == 0)), 'Color', 'k', 'Marker', 'none');
 xlabel('RIS Group Size');
 ylabel('Channel Power [W]');
 legend('$N_s = ' + string(vec(reflect.antenna)) + '$', 'Location', 'nw');
 savefig('plots/pc_power_sx.fig');
+matlab2tikz('../assets/simulation/pc_power_sx.tex', 'width', '8cm', 'height', '6cm');

### 2023-12-14 main.tex
:pencil: Add RCG method

@@
 \setabbreviationstyle[acronym]{long-short}
-% \newacronym{af}{AF}{Amplify-and-Forward}
+\newacronym{ao}{AO}{Alternating Optimization}
 \newacronym{bd}{BD}{Beyond-Diagonal}
+\newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
 \newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
@@
 	\begin{subsection}{Channel Power Maximization}
-		Consider a \gls{bd} \gls{ris} with $N_\mathrm{S}$ elements, which is divided into $G$ groups of equal $L$ elements.
+		Consider a \gls{bd} \gls{ris} with $N^\mathrm{S}$ elements, which is divided into $G$ groups of equal $L$ elements.
 		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\left\lVert \mathbf{H}^\mathrm{D} + \sum_g\nolimits \mathbf{H}_g^\mathrm{B} \mathbf{\Theta}_g \mathbf{H}_g^\mathrm{F} \right\rVert _\mathrm{F}^2}{\label{op:channel_power}}{}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}_L, \quad \forall g \in \mathcal{G} \triangleq \{1,\ldots,G\}}{}{}
+			{\scriptstyle{\mathbf{\Theta}}}{\left\lVert \mathbf{H}^\mathrm{D} + \sum_g\nolimits \mathbf{H}_g^\mathrm{B} \mathbf{\Theta}_g \mathbf{H}_g^\mathrm{F} \right\rVert _\mathrm{F}^2}{\label{op:pc_power}}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g \in \mathcal{G} \triangleq \{1,\ldots,G\}.}{}{}
 		\end{maxi!}
@@
 		\begin{remark}
-			% The difficulty of \eqref{op:channel_power} is that the \gls{ris} needs to balance the (additive) direct-indirect eigenspace alignment and the (multiplicative) forward-backward eigenspace alignment.
-			The difficulty of \eqref{op:channel_power} is that the \gls{ris} needs to balance the additive (direct-indirect) and multiplicative (forward-backward) eigenspace alignment.
+			% The difficulty of \eqref{op:pc_power} is that the \gls{ris} needs to balance the (additive) direct-indirect eigenspace alignment and the (multiplicative) forward-backward eigenspace alignment.
+			The difficulty of \eqref{op:pc_power} is that the \gls{ris} needs to balance the additive (direct-indirect) and multiplicative (forward-backward) eigenspace alignment.
 			% align the direct and indirect eigenspaces while preserving the
@@
 			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{C} - \mathbf{A \Theta B} \rVert _\text{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I}}{}{}
+				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{C} - \mathbf{A \Theta B} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
+				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I}.}{}{}
 			\end{mini!}
@@
 			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{A}^\dagger \mathbf{C} - \mathbf{\Theta B} \rVert _\text{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I}}{}{}
+				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{A}^\dagger \mathbf{C} - \mathbf{\Theta B} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
+				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I}.}{}{}
 			\end{mini!}
@@
 
-		Inspired by \cite{Nie2017}, we propose an iterative algorithm to solve \eqref{op:channel_power}.
+		Inspired by \cite{Nie2017}, we propose an iterative algorithm to solve \eqref{op:pc_power}.
 		The idea is to successively approximate the quadratic objective with a sequence of affine functions and solve the resulting subproblems in closed form.
@@
 			\end{equation}
-			converges to a stationary point of \eqref{op:channel_power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
+			converges to a stationary point of \eqref{op:pc_power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
 			\begin{equation}
@@
 			}
-			\caption{Average channel power versus \gls{ris} elements $N_\mathrm{S}$ and group size $L$ for $(N_\mathrm{T}, N_\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+			\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
 			\label{sm:pc_power_sx}
@@
 			}
-			\caption{Average channel power versus \gls{ris} group size $L$ for $(N_\mathrm{T}, N_\mathrm{S}, N_\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+			\caption{Average channel power versus \gls{ris} group size $L$ for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
 			\label{sm:pc_power_bond}
@@
 		% Fig.~\ref{sm:pc_power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
-		Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N_\mathrm{S}$, increasing the group size $L$ also improves the channel power.
+		Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
 		% The behavior is more obvious for a large \gls{ris}.
 		This behavior is more pronounced for a large \gls{ris}.
-		For example, the gain of pairwise connection is 2.8\% for $N_\mathrm{S} = 16$ and 28\% for $N_\mathrm{S} = 256$.
+		For example, the gain of pairwise connection is 2.8\% for $N^\mathrm{S} = 16$ and 28\% for $N^\mathrm{S} = 256$.
 		% \gls{bd} \gls{ris} provides a higher channel power than conventional \gls{ris}.
@@
 		% When the direct link is present, a small $L$ can neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
-		% For a relatively large $N_\mathrm{S}$, conventional \gls{ris} cannot
+		% For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
 		% neither the direct-indirect nor the forward-backward eigenspace can be effectively aligned with a small $L$.
@@
 	\end{subsection}
+
+	\begin{subsection}{Rate Maximization}
+		The problem is formulated w.r.t. precoder (instead of transmit covariance matrix) for reference:
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{\log \det \Bigl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\sigma_n^2}\Bigr)}{\label{op:pc_rate}}{}
+			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{\label{cs:pc_rate_unitary}}
+		\end{maxi!}
+
+		\eqref{op:pc_rate} is jointly non-convex and solved by \gls{ao}.
+		For a given $\mathbf{\Theta}$, the optimal precoder is given by
+		\begin{equation}
+			\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
+		\end{equation}
+		where $\mathbf{V}$ is right singular matrix of $\mathbf{H}$ and $\mathbf{S}^\star$ is a diagonal matrix of the water-filling power allocation.
+		For a given $\mathbf{W}$, we update $\mathbf{\Theta}$ by \gls{rcg} method along the geodesics \cite{Abrudan2009}.
+		\begin{remark}
+			A geodesic refers to the shortest path between two points in a Riemannian manifold.
+			% For unitary constraint \eqref{cs:pc_rate_unitary}, the
+			Unitary constraint \eqref{cs:pc_rate_unitary} translates to a Stiefel manifold where the geodesics have simple expressions described by the exponential map \cite{Abrudan2008}.
+			% Geodesics are the locally shortest paths in a Riemannian manifold.
+			% A Geodesics are the locally shortest paths in a Riemannian manifold.
+			% on Riemannian manifold are the shortest path between two points.
+		\end{remark}
+		For optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below.
+		\begin{enumerate}
+			\item Compute the Euclidean gradient
+			\begin{equation}
+				\nabla_{\mathbf{\Theta}_g}^\mathrm{E} f^{(r)} = \frac{\partial f^{(r)}}{\partial \mathbf{\Theta}_g^*}
+			\end{equation}
+			\item Translate to the Riemannian gradient
+			\begin{equation}
+				\nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r)} = \nabla_{\mathbf{\Theta}_g}^\mathrm{E} f^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathbf{\Theta}_g}^\mathrm{E} f^{(r)}}^\mathsf{H}
+			\end{equation}
+			\item Determine the weight factor
+			\begin{equation}
+				% \gamma^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl(\mathbf{G}_\mathrm{R}^{(r)} - \mathbf{G}_\mathrm{R}^{(r-1)}\bigr) \mathbf{G}_\mathrm{R}^{(r)\mathsf{H}}\Bigr)}{\mathrm{tr}\Bigl(\mathbf{G}_\mathrm{R}^{(r-1)} \mathbf{G}_\mathrm{R}^{(r-1)\mathsf{H}}\Bigr)}
+				\gamma^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl(\nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r)} - \nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r-1)}\bigr) \nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r)\mathsf{H}}\Bigr)}{\mathrm{tr}\Bigl(\nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r-1)} \nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r-1)\mathsf{H}}\Bigr)}
+			\end{equation}
+			\item Compute the conjugate direction
+			\begin{equation}
+				% \mathbf{D}_\mathrm{R}^{(r)} = \mathbf{G}_\mathrm{R}^{(r)} + \gamma^{(r)} \mathbf{D}_\mathrm{R}^{(r-1)}
+				\mathbf{D}^{(r)} = \nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r)} + \gamma^{(r)} \mathbf{D}^{(r-1)}
+			\end{equation}
+			\item Determine the Armijo step size
+			\begin{equation}
+				\mu^{(r)} = \arg\max_\mu f^{(r)}\Bigl(\exp\bigl(-\mu \mathbf{D}^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr)
+			\end{equation}
+			\item Perform multiplicative (rotational) update
+			\begin{equation}
+				\mathbf{\Theta}^{(r+1)} = {\color{gray}\exp}\Bigl(-\mu^{(r)} \mathbf{D}^{(r)}\Bigr) \mathbf{\Theta}_g^{(r)}
+			\end{equation}
+		\end{enumerate}
+		The advantage over general manifold optimization \cite{Absil2009,Pan2022d} is trifold: 1) no retraction is required; 2) no projection is required; 3) no matrix inversion is required.
+	\end{subsection}
 \end{section}

### 2023-12-14 main.tex
:pencil: Update RCG method

@@
 \algrenewcommand{\algorithmicuntil}{\textbf{Until}}
+\algrenewcommand{\algorithmicfor}{\textbf{For}}
 \algrenewcommand{\algorithmicdo}{}
@@
 \newacronym{bd}{BD}{Beyond-Diagonal}
+\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
 \newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
 \newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
+\newacronym{pc}{PC}{Point-to-point Channel}
+\newacronym{ic}{IC}{Interference Channel}
 
@@
 \begin{section}{Assumption}
-	All proposals in this paper based on assumption of \emph{asymmetric} passive \gls{bd} \gls{ris}, i.e., symmetry constraint $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T}$ is relaxed.
+	We introduce \gls{bd} \gls{ris} in \gls{mimo} \gls{pc} and \gls{ic}.
+	% point-to-point and interference \gls{mimo} channels.
+	All proposals are based on assumption of \emph{asymmetric} passive \gls{bd} \gls{ris}, i.e., symmetry constraint $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T}$ is relaxed.
 	This is feasible when asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} are available.
@@
 
-\begin{section}{Point-to-Point MIMO}
+\begin{section}{\glsentryshort{mimo}-\glsentryshort{pc}}
 	\begin{subsection}{Channel Power Maximization}
@@
 			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g \in \mathcal{G}
+				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
 			\end{equation}
@@
 		\begin{maxi!}
-			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{\log \det \Bigl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\sigma_n^2}\Bigr)}{\label{op:pc_rate}}{}
+			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\sigma_n^2}\biggr)}{\label{op:pc_rate}}{\label{ob:pc_rate}}
 			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
@@
 		\end{remark}
-		For optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below.
+		For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f^{(r)}$ is evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'=1}^{g-1}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'=g}^{G} \bigr\}$.
 		\begin{enumerate}
@@
 			\begin{equation}
-				\nabla_{\mathbf{\Theta}_g}^\mathrm{E} f^{(r)} = \frac{\partial f^{(r)}}{\partial \mathbf{\Theta}_g^*}
+				\nabla_g^\mathrm{E} f^{(r)} = \frac{\partial f^{(r)}}{\partial \mathbf{\Theta}_g^*};
+				\label{eq:rcg_gradient_euclidean}
 			\end{equation}
@@
 			\begin{equation}
-				\nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r)} = \nabla_{\mathbf{\Theta}_g}^\mathrm{E} f^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathbf{\Theta}_g}^\mathrm{E} f^{(r)}}^\mathsf{H}
+				\nabla_g^\mathrm{R} f^{(r)} = \nabla_g^\mathrm{E} f^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_g^\mathrm{E} f^{(r)}}^\mathsf{H};
+				\label{eq:rcg_gradient_riemannian}
 			\end{equation}
@@
 			\begin{equation}
-				% \gamma^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl(\mathbf{G}_\mathrm{R}^{(r)} - \mathbf{G}_\mathrm{R}^{(r-1)}\bigr) \mathbf{G}_\mathrm{R}^{(r)\mathsf{H}}\Bigr)}{\mathrm{tr}\Bigl(\mathbf{G}_\mathrm{R}^{(r-1)} \mathbf{G}_\mathrm{R}^{(r-1)\mathsf{H}}\Bigr)}
-				\gamma^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl(\nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r)} - \nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r-1)}\bigr) \nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r)\mathsf{H}}\Bigr)}{\mathrm{tr}\Bigl(\nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r-1)} \nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r-1)\mathsf{H}}\Bigr)}
+				\gamma_g^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl(\nabla_g^\mathrm{R} f^{(r)} - \nabla_g^\mathrm{R} f^{(r-1)}\bigr) \nabla_g^\mathrm{R} {f^{(r)}}^\mathsf{H}\Bigr)}{\mathrm{tr}\Bigl(\nabla_g^\mathrm{R} f^{(r-1)} \nabla_g^\mathrm{R} {f^{(r-1)}}^\mathsf{H}\Bigr)};
+				\label{eq:rcg_weight}
 			\end{equation}
@@
 			\begin{equation}
-				% \mathbf{D}_\mathrm{R}^{(r)} = \mathbf{G}_\mathrm{R}^{(r)} + \gamma^{(r)} \mathbf{D}_\mathrm{R}^{(r-1)}
-				\mathbf{D}^{(r)} = \nabla_{\mathbf{\Theta}_g}^\mathrm{R} f^{(r)} + \gamma^{(r)} \mathbf{D}^{(r-1)}
+				\mathbf{D}_g^{(r)} = \nabla_g^\mathrm{R} f^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)};
+				\label{eq:rcg_direction}
 			\end{equation}
-			\item Determine the Armijo step size
+			\item Determine the Armijo step size\footnote{To double the step size, simply square the argument instead of recomputing the matrix exponential, i.e., $\exp(2 \mu_g \mathbf{D}_g) = \exp^2(\mu_g \mathbf{D}_g)$.}
 			\begin{equation}
-				\mu^{(r)} = \arg\max_\mu f^{(r)}\Bigl(\exp\bigl(-\mu \mathbf{D}^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr)
+				\mu_g^{(r)} = \arg\max_{\mu_g} f^{(r)}\Bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr);
+				\label{eq:rcg_step}
 			\end{equation}
-			\item Perform multiplicative (rotational) update
+			\item Perform rotational update along local geodesics
 			\begin{equation}
-				\mathbf{\Theta}^{(r+1)} = {\color{gray}\exp}\Bigl(-\mu^{(r)} \mathbf{D}^{(r)}\Bigr) \mathbf{\Theta}_g^{(r)}
+				\mathbf{\Theta}_g^{(r+1)} = \exp\Bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\Bigr) \mathbf{\Theta}_g^{(r)}.
+				\label{eq:rcg_update}
 			\end{equation}
 		\end{enumerate}
-		The advantage over general manifold optimization \cite{Absil2009,Pan2022d} is trifold: 1) no retraction is required; 2) no projection is required; 3) no matrix inversion is required.
+
+		\begin{remark}
+			The adapted \gls{rcg} method leverages the fact that block unitary matrices are closed under multiplication (but not necessarily under addition).
+			Its advantage over universal manifold optimization \cite{Absil2009,Pan2022d} is trifold:
+			\begin{itemize}
+				\item No retraction is involved;
+				\item Lower computational complexity per iteration \cite{Abrudan2008};
+				\item Faster convergence thanks appropriate operational space.
+			\end{itemize}
+		\end{remark}
+
+		The complex derivative of \eqref{ob:pc_rate} w.r.t. \gls{ris} block $g$ is
+		\begin{equation}
+			\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\sigma_n^2} {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{HW} \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\sigma_n^2}\biggr)^{-1} \mathbf{W}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H}.
+			\label{eq:pc_rate_gradient_ris}
+		\end{equation}
+		The adapted \gls{rcg} method for the \gls{ris} rate maximization subproblem is summarized in Algorithm~\ref{ag:pc_rate_ris}.
+
+		\setalgorithmcaptionfont{\small}
+		\begin{algorithm}[!t]
+			\small
+			\caption{\gls{rcg} Method for \gls{ris} \gls{mimo}-\gls{pc} Rate Maximization}
+			\label{ag:pc_rate_ris}
+			\begin{algorithmic}[1]
+				\Require $\mathbf{H}^\mathrm{D}$, $\mathbf{H}^\mathrm{F}$, $\mathbf{H}^\mathrm{B}$, $\mathbf{W}$, $L$, $\sigma_n^2$
+				\Ensure $\mathbf{\Theta}^\star$
+				% \State Initialize $r \gets 0$, $\mathbf{\Theta}^{(0)}$
+				\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
+				\Repeat
+					% \State Update $r \gets r+1$
+					\State $r \gets r+1$
+					\For {$g \gets 1$ to $G$}
+						% \State Get $\mathbf{\Theta}_g^{(r)}$ by \eqref{eq:pc_rate_gradient_ris}, \eqref{eq:rcg_gradient_riemannian} -- \eqref{eq:rcg_update}
+						\State $\mathbf{\Theta}_g^{(r)} \gets$ \eqref{eq:pc_rate_gradient_ris}, \eqref{eq:rcg_gradient_riemannian}--\eqref{eq:rcg_update}
+					\EndFor
+				\Until $\lvert R^{(r)} - R^{(r-1)} \rvert / R^{(r-1)} \le \epsilon$
+			\end{algorithmic}
+		\end{algorithm}
 	\end{subsection}

### 2023-12-14 main.tex
:pencil: Finsh MIMO PC rate problem

@@
 \newacronym{ic}{IC}{Interference Channel}
+\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
 
@@
 		This behavior is more pronounced for a large \gls{ris}.
-		For example, the gain of pairwise connection is 2.8\% for $N^\mathrm{S} = 16$ and 28\% for $N^\mathrm{S} = 256$.
+		For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
 		% \gls{bd} \gls{ris} provides a higher channel power than conventional \gls{ris}.
@@
 		We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect eigenspace.
-		When the direct link is absent, only 2.6\% of available power is utilized by diagonal \gls{ris} while 100\% power is recycled by fully-connected \gls{ris}.
+		When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
 		When the direct link is present, the proposed \gls{bd} \gls{ris} design can balance the direct-indirect and forward-backward eigenspace alignment for an optimal channel boost.
@@
 		\end{remark}
-		For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f^{(r)}$ is evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'=1}^{g-1}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'=g}^{G} \bigr\}$.
+		For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)$ is the objective function evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'<g}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'>g} \bigr\}$.
 		\begin{enumerate}
@@
 			\begin{equation}
-				\nabla_g^\mathrm{E} f^{(r)} = \frac{\partial f^{(r)}}{\partial \mathbf{\Theta}_g^*};
+				{\nabla_g^\mathrm{E}}^{(r)} = \frac{\partial f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)}{\partial \mathbf{\Theta}_g^*};
 				\label{eq:rcg_gradient_euclidean}
@@
 			\begin{equation}
-				\nabla_g^\mathrm{R} f^{(r)} = \nabla_g^\mathrm{E} f^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_g^\mathrm{E} f^{(r)}}^\mathsf{H};
+				{\nabla_g^\mathrm{R}}^{(r)} = {\nabla_g^\mathrm{E}}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {{\nabla_g^\mathrm{E}}^{(r)}}^\mathsf{H};
 				\label{eq:rcg_gradient_riemannian}
@@
 			\begin{equation}
-				\gamma_g^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl(\nabla_g^\mathrm{R} f^{(r)} - \nabla_g^\mathrm{R} f^{(r-1)}\bigr) \nabla_g^\mathrm{R} {f^{(r)}}^\mathsf{H}\Bigr)}{\mathrm{tr}\Bigl(\nabla_g^\mathrm{R} f^{(r-1)} \nabla_g^\mathrm{R} {f^{(r-1)}}^\mathsf{H}\Bigr)};
+				\gamma_g^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl({\nabla_g^\mathrm{R}}^{(r)} - {\nabla_g^\mathrm{R}}^{(r-1)}\bigr) {{\nabla_g^\mathrm{R}}^{(r)}}^\mathsf{H}\Bigr)}{\mathrm{tr}\Bigl({\nabla_g^\mathrm{R}}^{(r-1)} {{\nabla_g^\mathrm{R}}^{(r-1)}}^\mathsf{H}\Bigr)};
 				\label{eq:rcg_weight}
@@
 			\begin{equation}
-				\mathbf{D}_g^{(r)} = \nabla_g^\mathrm{R} f^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)};
+				\mathbf{D}_g^{(r)} = {\nabla_g^\mathrm{R}}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)};
 				\label{eq:rcg_direction}
@@
 			\begin{equation}
-				\mu_g^{(r)} = \arg\max_{\mu_g} f^{(r)}\Bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr);
+				\mu_g^{(r)} = \arg\max_{\mu_g} f\Bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr);
 				\label{eq:rcg_step}
@@
 		\end{equation}
-		The adapted \gls{rcg} method for the \gls{ris} rate maximization subproblem is summarized in Algorithm~\ref{ag:pc_rate_ris}.
+		Algorithm~\ref{ag:pc_rate_ris} summarizes the adapted \gls{rcg} method for the \gls{ris} rate maximization subproblem.
 
@@
 				\Ensure $\mathbf{\Theta}^\star$
-				% \State Initialize $r \gets 0$, $\mathbf{\Theta}^{(0)}$
 				\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
 				\Repeat
-					% \State Update $r \gets r+1$
 					\State $r \gets r+1$
 					\For {$g \gets 1$ to $G$}
-						% \State Get $\mathbf{\Theta}_g^{(r)}$ by \eqref{eq:pc_rate_gradient_ris}, \eqref{eq:rcg_gradient_riemannian} -- \eqref{eq:rcg_update}
 						\State $\mathbf{\Theta}_g^{(r)} \gets$ \eqref{eq:pc_rate_gradient_ris}, \eqref{eq:rcg_gradient_riemannian}--\eqref{eq:rcg_update}
@@
 		\end{algorithm}
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/pc_rate_sx.tex}
+			}
+			\caption{Average achievable rate versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+			\label{sm:pc_rate_sx}
+		\end{figure}
+
+		Fig.~\ref{sm:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
+		To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
+		This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
+		If tetrads can be formed in \gls{bd} \gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
+		Further increase in $L$ yields a marginal gain and incurs quadratic number of connections.
+		Thus, dyadic or tetradic \gls{bd} \gls{ris} usually strike a good balance between performance and complexity.
+
 	\end{subsection}

### 2023-12-14 src/pc_rate_sx.m

@@ -51,10 +51,11 @@ for a = 1 : number.antenna
 		end
 	end
 end
-hold off; grid on;
+hold off; grid on; box on;
 set(handle.rate(1, find(reflect.antenna == 0)), 'Color', 'k', 'Marker', 'none');
 style_plot(handle.rate(:, find(reflect.antenna ~= 0)), number.bond);
 xlabel('Direct SNR [dB]');
 ylabel('Achievable Rate [bit/s/Hz]');
 legend('Location', 'nw');
 savefig('plots/pc_rate_sx.fig');
+matlab2tikz('../assets/simulation/pc_rate_sx.tex', 'width', '8cm', 'height', '6cm');

### 2023-12-15 main.tex
:pencil: Add MIMO PC SV toy example

@@
 \usepackage{tikz}
+\usepackage{graphicx}
+\usepackage{epstopdf}
 
@@
 		\end{remark}
-		For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)$ is the objective function evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'<g}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'>g} \bigr\}$.
+		For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)$ is the objective function also evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'<g}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'>g} \bigr\}$.
 		\begin{enumerate}
@@
 		If tetrads can be formed in \gls{bd} \gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
-		Further increase in $L$ yields a marginal gain and incurs quadratic number of connections.
-		Thus, dyadic or tetradic \gls{bd} \gls{ris} usually strike a good balance between performance and complexity.
+		Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
+		We thus conclude dyadic or tetradic \gls{bd} \gls{ris} usually strike a good balance between performance and complexity.
+	\end{subsection}
 
+	\begin{subsection}{Channel Singular Value Redistribution}
+		In this subsection, we first show the channel shaping advantage of \gls{bd} \gls{ris} by a toy example, then analyzes this \emph{capability} under specific setups.
+		Finally, we characterize the \emph{Pareto front} of channel singular values via optimization approach.
+
+		\begin{figure}
+			\centering
+			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
+			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris} for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ without direct link.}
+			\label{sm:pc_singular_toy}
+		\end{figure}
+
+		Consider a toy example with $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
+		The diagonal \gls{ris} is $\mathbf{\Theta}^\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
+		\begin{equation}
+			% \mathbf{\Theta}^\mathrm{D} =
+			% \begin{bmatrix}
+			% 	e^{\jmath \theta_1} & 0              \\
+			% 	0              & e^{\jmath \theta_2}
+			% \end{bmatrix}, \quad
+			\mathbf{\Theta}^\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
+				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
+				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
+			\end{bmatrix}.
+		\end{equation}
+		When the direct link is absent, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
+		For a fair comparison, we enforce \emph{symmetry} with $\beta = \pi / 2$.
+		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
+		Clearly, \gls{bd} \gls{ris} provides a much wider dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}, despite using the same number of elements and parameters.
+		A larger gap is expected when the symmetry constraint can be relaxed.
+
+		\begin{subsubsection}{Rank-1 Indirect Channel}
+			% When the \gls{ris} is in the vicinity of the transmitter / receiver, the forward / backward channel is often rank-1 and so is the indirect channel.
+			% This is because
+			When the \gls{ris} is in the vicinity of the transmitter / receiver, the forward / backward channel is often rank-1.
+			The indirect channel is also rank-1 because
+			\begin{equation}
+				\mathrm{rank}( \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F} ) \le \min \bigl( \mathrm{rank}(\mathbf{H}^\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}), \mathrm{rank}(\mathbf{H}^\mathrm{F}) \bigr).
+			\end{equation}
+			% That is to say, \gls{bd} \gls{ris}
+		\end{subsubsection}
 	\end{subsection}

### 2023-12-15 src/pc_singular_toy.m

@@ -25,7 +25,7 @@ for s = 1 : 2
 	handle.mesh(1, s).DataTipTemplate.DataTipRows.Format = '%.3f';
 	hold on;
 end
-hold off; legend;
+hold off; legend('Location', 'northeast');
 xlabel('$\theta_1$');
 ylabel('$\theta_2$');
 zlabel({'Singular Value'});
@@ -42,7 +42,7 @@ for s = 1 : 2
 	handle.mesh(2, s).DataTipTemplate.DataTipRows.Format = '%.3f';
 	hold on;
 end
-hold off; legend;
+hold off;
 xlabel('$\alpha$');
 ylabel('$\psi$');
 zlabel({'Singular Value'});
@@ -50,6 +50,7 @@ set(gca, 'XTick', 0 : pi / 2 : 2 * pi, 'YTick', 0 : pi / 2 : 2 * pi, 'XTickLabel
 title('Symmetry Unitary RIS');
 linkaxes(handle.axis);
 savefig('plots/pc_singular_toy.fig');
+saveas(gcf, '../assets/simulation/pc_singular_toy', 'epsc');
 
 
 function [Theta] = scatter_2x2_diagonal(theta_1, theta_2)

### 2023-12-15 main.tex
:pencil: Add MIMO PC SV toy example

@@
 \newacronym{bd}{BD}{Beyond-Diagonal}
+\newacronym{dof}{DoF}{Degree of Freedom}
 \newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
@@
 	\begin{subsection}{Channel Singular Value Redistribution}
-		In this subsection, we first show the channel shaping advantage of \gls{bd} \gls{ris} by a toy example, then analyzes this \emph{capability} under specific setups.
-		Finally, we characterize the \emph{Pareto front} of channel singular values via optimization approach.
-
-		\begin{figure}
-			\centering
-			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
-			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris} for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ without direct link.}
-			\label{sm:pc_singular_toy}
-		\end{figure}
-
-		Consider a toy example with $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
+		We first show the channel shaping benefit of \gls{bd} \gls{ris} by a toy example.
+		Consider $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
 		The diagonal \gls{ris} is $\mathbf{\Theta}^\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
 		\begin{equation}
-			% \mathbf{\Theta}^\mathrm{D} =
-			% \begin{bmatrix}
-			% 	e^{\jmath \theta_1} & 0              \\
-			% 	0              & e^{\jmath \theta_2}
-			% \end{bmatrix}, \quad
 			\mathbf{\Theta}^\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
@@
 		For a fair comparison, we enforce \emph{symmetry} with $\beta = \pi / 2$.
+		\begin{figure}
+			\centering
+			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
+			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris} for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ without direct link.}
+			\label{sm:pc_singular_toy}
+		\end{figure}
 		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
-		Clearly, \gls{bd} \gls{ris} provides a much wider dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}, despite using the same number of elements and parameters.
-		A larger gap is expected when the symmetry constraint can be relaxed.
+		Despite using the same number of elements and parameters, \gls{bd} \gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
+		Larger gaps are expected when the symmetry constraint can be relaxed.
+
+		We then analyze the channel shaping \emph{capability} of \gls{bd} \gls{ris} under specific setups.
+		\begin{subsubsection}{Rank-Deficient Channel}
+			In rank-deficient channels, \gls{bd} \gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
+			This is because $\mathrm{sv}(\mathbf{\Theta}^\mathrm{B}) = \mathrm{sv}(\mathbf{\Theta}^\mathrm{D}) = \boldsymbol{1}$ and
+			\begin{equation}
+				\begin{split}
+					\mathrm{rank}(\mathbf{H})
+					& \le \mathrm{rank}(\mathbf{H}^\mathrm{D}) + \mathrm{rank}(\mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F}) \\
+					& \le \mathrm{rank}(\mathbf{H}^\mathrm{D}) + \min \bigl( \mathrm{rank}(\mathbf{H}^\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}), \mathrm{rank}(\mathbf{H}^\mathrm{F}) \bigr).
+				\end{split}
+			\end{equation}
+			% However, \gls{bd} \gls{ris} can still guarantee a higher rate at finite \gls{snr}.
+			Note \gls{bd} \gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
+		\end{subsubsection}
 
 		\begin{subsubsection}{Rank-1 Indirect Channel}
-			% When the \gls{ris} is in the vicinity of the transmitter / receiver, the forward / backward channel is often rank-1 and so is the indirect channel.
-			% This is because
-			When the \gls{ris} is in the vicinity of the transmitter / receiver, the forward / backward channel is often rank-1.
-			The indirect channel is also rank-1 because
+			The indirect channel is rank-1 iff the forward or backward channel is rank-1.
+			Let $\mathbf{H}^\mathrm{F} = \sigma^\mathrm{F} \mathbf{u}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}$ without loss of generality.
+			In this case, the channel Gram matrix can be written as Hermitian-plus-rank-1:
 			\begin{equation}
-				\mathrm{rank}( \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F} ) \le \min \bigl( \mathrm{rank}(\mathbf{H}^\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}), \mathrm{rank}(\mathbf{H}^\mathrm{F}) \bigr).
+				\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
 			\end{equation}
-			% That is to say, \gls{bd} \gls{ris}
+			where $\mathbf{Y} \triangleq \mathbf{H}^\mathrm{D} (\mathbf{I} - \mathbf{v}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}) \mathbf{H}^\mathrm{D} = \mathbf{F} \mathbf{F}^\mathsf{H}$ and $\mathbf{z} \triangleq \sigma^\mathrm{F} \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{u}^\mathrm{F} + \mathbf{H}^\mathrm{D} \mathbf{v}^\mathrm{F}$.
+			Regardless of \gls{ris} size and structure\footnote{Similar conclusion was made for diagonal \gls{ris} in \cite{Semmler2023}.}, its $n$-th ($n \ge 2$) eigenvalues are bounded by the Cauchy interlacing formula \cite{Golub2013}
+			\begin{equation}
+				\lambda_1(\mathbf{Y}) \ge {\color{blue}\lambda_2(\mathbf{G})} \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{n-1}(\mathbf{Y}) \ge {\color{blue}\lambda_n(\mathbf{G})} \ge \lambda_n(\mathbf{Y}).
+			\end{equation}
+			That is to say, [for sv]
+
+			% \begin{equation}
+			% 	\mathbf{G} = \underbrace{\mathbf{H}_\text{D} (\mathbf{I} - \mathbf{v}_{\text{F}} \mathbf{v}_{\text{F}}^\mathsf{H}) \mathbf{H}_\text{D}^\mathsf{H}}_{\mathbf{C}} +
+			% 	\underbrace{
+			% 		\begin{bsmallmatrix}
+			% 			\sigma_{\text{F}} \mathbf{H}_\text{B} & \mathbf{H}_\text{D} \mathbf{v}_{\text{F}}
+			% 		\end{bsmallmatrix}
+			% 		\begin{bsmallmatrix}
+			% 			\mathbf{\Theta} \mathbf{u}_{\text{F}} \\
+			% 			1
+			% 		\end{bsmallmatrix}
+			% 	}_{\mathbf{z} = \sigma_{\text{F}} \mathbf{H}_\text{B} \mathbf{\Theta} \mathbf{u}_{\text{F}} + \mathbf{H}_\text{D} \mathbf{v}_{\text{F}}}
+			% 	\begin{bsmallmatrix}
+			% 		\mathbf{\Theta} \mathbf{u}_{\text{F}} \\
+			% 		1
+			% 	\end{bsmallmatrix}^\mathsf{H}
+			% 	\begin{bsmallmatrix}
+			% 		\sigma_{\text{F}} \mathbf{H}_\text{B} & \mathbf{H}_\text{D} \mathbf{v}_{\text{F}}
+			% 	\end{bsmallmatrix}^\mathsf{H}
+			% \end{equation}
 		\end{subsubsection}
+
+		Finally, we characterize the \emph{Pareto front} of channel singular values via optimization approach.
 	\end{subsection}

### 2023-12-15 src/pc_power_bond.m

@@ -3,7 +3,7 @@ clc; clear; close; setup;
 [transmit.antenna, reflect.antenna, receive.antenna] = deal(8, 256, 4);
 [channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2 .^ (0 : 2 : log2(reflect.antenna)));
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.bond, number.realization, flag.direct] = deal(length(reflect.bond), 1e1, false);
+[number.bond, number.realization, flag.direct] = deal(length(reflect.bond), 1e1, true);
 
 for r = 1 : number.realization
 	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);

### 2023-12-16 main.tex
:pencil: Add MIMO PC SV analysis

@@
 		% maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-		``Cascaded'' means the \emph{power product} of the forward and backward channels.
+		% ? ``Cascaded'' means the \emph{power product} of the forward and backward channels.
+		% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues of the forward and backward channels.
+		``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
 		We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect eigenspace.
@@
 		When the direct link is absent, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		For a fair comparison, we enforce \emph{symmetry} with $\beta = \pi / 2$.
+		For a fair comparison, we enforce symmetry with $\beta = \pi / 2$.
 		\begin{figure}
@@
 			\end{equation}
-			where $\mathbf{Y} \triangleq \mathbf{H}^\mathrm{D} (\mathbf{I} - \mathbf{v}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}) \mathbf{H}^\mathrm{D} = \mathbf{F} \mathbf{F}^\mathsf{H}$ and $\mathbf{z} \triangleq \sigma^\mathrm{F} \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{u}^\mathrm{F} + \mathbf{H}^\mathrm{D} \mathbf{v}^\mathrm{F}$.
-			Regardless of \gls{ris} size and structure\footnote{Similar conclusion was made for diagonal \gls{ris} in \cite{Semmler2023}.}, its $n$-th ($n \ge 2$) eigenvalues are bounded by the Cauchy interlacing formula \cite{Golub2013}
+			where $\mathbf{Y} \triangleq \mathbf{H}^\mathrm{D} (\mathbf{I} - \mathbf{v}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}) \mathbf{H}^\mathrm{D} = \mathbf{T} \mathbf{T}^\mathsf{H}$ and $\mathbf{z} \triangleq \sigma^\mathrm{F} \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{u}^\mathrm{F} + \mathbf{H}^\mathrm{D} \mathbf{v}^\mathrm{F}$.
+			Regardless of \gls{ris} size and structure\footnote{A similar conclusion was made for diagonal \gls{ris} in \cite{Semmler2023}.}, its $n$-th ($n \ge 2$) eigenvalues are bounded by the Cauchy interlacing formula \cite{Golub2013}
 			\begin{equation}
-				\lambda_1(\mathbf{Y}) \ge {\color{blue}\lambda_2(\mathbf{G})} \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{n-1}(\mathbf{Y}) \ge {\color{blue}\lambda_n(\mathbf{G})} \ge \lambda_n(\mathbf{Y}).
+				\lambda_1(\mathbf{Y}) \ge {\color{blue}\lambda_2(\mathbf{G})} \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge {\color{blue}\lambda_N(\mathbf{G})} \ge \lambda_N(\mathbf{Y}).
 			\end{equation}
-			That is to say, [for sv]
+			The equivalent singular value inequality is
+			\begin{equation}
+				\sigma_1(\mathbf{T}) \ge {\color{blue}\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\color{blue}\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
+				\label{iq:singular_value_interlacing}
+			\end{equation}
+			\eqref{iq:singular_value_interlacing} implies that, if the indirect channel is rank-1, then the \gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$.
+			Note that the largest channel singular value is unbounded with a sufficiently large \gls{ris}.
+		\end{subsubsection}
 
-			% \begin{equation}
-			% 	\mathbf{G} = \underbrace{\mathbf{H}_\text{D} (\mathbf{I} - \mathbf{v}_{\text{F}} \mathbf{v}_{\text{F}}^\mathsf{H}) \mathbf{H}_\text{D}^\mathsf{H}}_{\mathbf{C}} +
-			% 	\underbrace{
-			% 		\begin{bsmallmatrix}
-			% 			\sigma_{\text{F}} \mathbf{H}_\text{B} & \mathbf{H}_\text{D} \mathbf{v}_{\text{F}}
-			% 		\end{bsmallmatrix}
-			% 		\begin{bsmallmatrix}
-			% 			\mathbf{\Theta} \mathbf{u}_{\text{F}} \\
-			% 			1
-			% 		\end{bsmallmatrix}
-			% 	}_{\mathbf{z} = \sigma_{\text{F}} \mathbf{H}_\text{B} \mathbf{\Theta} \mathbf{u}_{\text{F}} + \mathbf{H}_\text{D} \mathbf{v}_{\text{F}}}
-			% 	\begin{bsmallmatrix}
-			% 		\mathbf{\Theta} \mathbf{u}_{\text{F}} \\
-			% 		1
-			% 	\end{bsmallmatrix}^\mathsf{H}
-			% 	\begin{bsmallmatrix}
-			% 		\sigma_{\text{F}} \mathbf{H}_\text{B} & \mathbf{H}_\text{D} \mathbf{v}_{\text{F}}
-			% 	\end{bsmallmatrix}^\mathsf{H}
-			% \end{equation}
+		\begin{subsubsection}{Fully-Connected \glsentryshort{ris} Without Direct Link}
+			Denote the singular value decomposition of forward / backward channels as $\mathbf{H}^{\mathrm{B}/\mathrm{F}} = \mathbf{U}^{\mathrm{B}/\mathrm{F}} \mathbf{\Sigma}^{\mathrm{B}/\mathrm{F}} {\mathbf{V}^{\mathrm{B}/\mathrm{F}}}^\mathsf{H}$.
+			The composite channel is
+			\begin{equation}
+				\mathbf{H} = \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F} = \mathbf{U}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{X} \mathbf{\Sigma}^\mathrm{F} {\mathbf{V}^\mathrm{F}}^\mathsf{H},
+			\end{equation}
+			where $\mathbf{X} = {\mathbf{V}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta} \mathbf{U}^\mathrm{F}$.
+			% Since unitary matrices are closed under multiplication,
+			\begin{proposition}
+				In this case, the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with singular values $\mathbf{\Sigma}^\mathrm{B}$ and $\mathbf{\Sigma}^\mathrm{F}$.
+				% The only singular value bounds applied here are those apply to the singular value bound of $\mathbf{F}\mathbf{B}$
+			\end{proposition}
+			\begin{proof}
+				We first observe that singular value control problem can be solved w.r.t.
+unitary $\mathbf{X}$ and retrieved by $\mathbf{\Theta} = \mathbf{V}^\mathrm{B} \mathbf{X} {\mathbf{U}^\mathrm{F}}^\mathsf{H}$.
+				Also, $\mathrm{sv}(\mathbf{U}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{X} \mathbf{\Sigma}^\mathrm{F} {\mathbf{V}^\mathrm{F}}^\mathsf{H}) = \mathrm{sv}(\bar{\mathbf{U}}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{\bar{V}}{{}^\mathrm{B}}^\mathsf{H} \bar{\mathbf{U}}^\mathrm{F} \mathbf{\Sigma}^\mathrm{F} \mathbf{\bar{V}}{{}^\mathrm{F}}^\mathsf{H}) = \mathrm{sv}(\mathbf{BF})$ where $\bar{\mathbf{U}}^{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}^{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
+			\end{proof}
+			The problem now becomes, given $\mathbf{\Sigma}^\mathrm{B}$ and $\mathbf{\Sigma}^\mathrm{F}$, what can we say about the singular value of $\mathbf{BF}$.
+			One comprehensive answer is Horn's inequality \cite{Bhatia2001}: for all admissible triples $(I, J, K)$,
+			\begin{equation}
+				\prod_{k \in {K}} \sigma_k(\mathbf{BF}) \leq \prod_{i \in {I}} \sigma_i(\mathbf{B}) \prod_{j \in {J}} \sigma_j(\mathbf{F}).
+			\end{equation}
+			It gives upper bound on the largest singular value and lower bound on the smallest singular value:
+			\begin{align}
+				\sigma_1(\mathbf{BF}) \le \sigma_1(\mathbf{B}) \sigma_1(\mathbf{F}) \label{iq:singular_value_largest}\\
+				\sigma_N(\mathbf{BF}) \geq \sigma_N(\mathbf{B}) \sigma_N(\mathbf{F}) \label{iq:singular_value_smallest}.
+			\end{align}
+			Another useful result is introduced in \cite{Hogben2013}: for all $p>0$,
+			\begin{equation}
+				\sum_n \sigma_n^p(\mathbf{BF}) \leq \sum_n \sigma_n^p(\mathbf{B}) \sigma_n^p(\mathbf{F}) \label{iq:singular_value_power_sum}.
+			\end{equation}
+			When $p=2$, it implies the channel energy is upper bounded by the sum of element-wise power product of the forward and backward channels, as illustrated in Fig.~\subref*{sm:pc_power_bond_nd}.
+			Interestingly, \eqref{iq:singular_value_largest}--\eqref{iq:singular_value_power_sum} are simultaneously tight when $\mathbf{X} = \mathbf{I}$ and $\mathbf{\Theta} = \mathbf{V}^\mathrm{B} {\mathbf{U}^\mathrm{F}}^\mathsf{H}$.
+			This solution was claimed in \cite{Bartoli2023} to achieve channel capacity, but it is not true at moderate \gls{snr}.
+			% In \cite{Bartoli2023}, the authors claimed this solution also achieves channel capacity but it is
 		\end{subsubsection}

### 2023-12-16 main.tex
:pencil: Add MIMO IC

@@
 \newacronym{bd}{BD}{Beyond-Diagonal}
+\newacronym{bcd}{BCD}{Block Coordinate Descent}
 \newacronym{dof}{DoF}{Degree of Freedom}
@@
 \newacronym{snr}{SNR}{Signal-to-Noise Ratio}
+\newacronym{wsr}{WSR}{Weighted Sum-Rate}
+\newacronym{mmse}{MMSE}{Minimum Mean-Square Error}
+\newacronym{wmmse}{WMMSE}{Weighted \gls{mmse}}
+\newacronym{mse}{MSE}{Mean-Square Error}
 
@@
 		\begin{maxi!}
-			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\sigma_n^2}\biggr)}{\label{op:pc_rate}}{\label{ob:pc_rate}}
+			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:pc_rate}}{\label{ob:pc_rate}}
 			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
@@
 		\begin{subsubsection}{Rank-Deficient Channel}
+			\label{sc:pc_rank_deficient}
 			In rank-deficient channels, \gls{bd} \gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
@@
 			This solution was claimed in \cite{Bartoli2023} to achieve channel capacity, but it is not true at moderate \gls{snr}.
-			% In \cite{Bartoli2023}, the authors claimed this solution also achieves channel capacity but it is
 		\end{subsubsection}
@@
 		Finally, we characterize the \emph{Pareto front} of channel singular values via optimization approach.
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		\end{maxi!}
+		where $\rho_n$ is the weight of $n$-th singular value.
+		The complex derivative of \eqref{ob:pc_singular} w.r.t. \gls{ris} block $g$ is
+		\begin{equation}
+			\frac{\partial J_1}{\partial \mathbf{\Theta}_g^*} = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{U} \mathrm{diag}(\boldsymbol{\rho}) \mathbf{V}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H},
+			\label{eq:pc_singular_gradient_ris}
+		\end{equation}
+		where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{H}$.
+		\eqref{op:pc_singular} can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:pc_singular_gradient_ris}.
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Pareto Front\label{sm:pc_singular_pareto_bond}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_singular_pareto_bond.tex}
+				}
+			}
+			\subfloat[Evolving Trend\label{sm:pc_singular_trend_bond}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_singular_trend_bond.tex}
+				}
+			}
+			\caption{Singular value Pareto front and trend for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 16, 2)$.}
+			\label{sm:pc_singular_bond}
+		\end{figure}
+		The Pareto front and evolving trend of channel singular values are shown in Fig.~\subref*{sm:pc_singular_pareto_bond} and \subref*{sm:pc_singular_trend_bond}.
+		Clearly, \gls{bd} \gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
+	\end{subsection}
+\end{section}
+
+\begin{section}{\glsentryshort{mimo}-\glsentryshort{ic}}
+	\begin{subsection}{Leakage Interference Minimization}
+		\begin{mini!}
+			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}_{kj}^\mathrm{D} + \mathbf{H}_k^\mathrm{B} \mathbf{\Theta} \mathbf{H}_j^\mathrm{F}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+			\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad \mathbf{W}_k^\mathsf{H} \mathbf{W}_k=\mathbf{I}, \quad \forall k.}{}{}
+		\end{mini!}
+		The non-convex problem can be solved by \gls{bcd} method.
+		For a given $\mathbf{\Theta}$, it reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
+		At iteration $r$, the combiner at receiver $k$ is updated as
+		\begin{equation}
+			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
+		\end{equation}
+		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H}$.
+		The precoder at transmitter $j$ is updated as
+		\begin{equation}
+			\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
+		\end{equation}
+		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds to interference covariance matrix $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} \mathbf{H}_{kj}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} \mathbf{H}_{kj}$ in the reciprocal network.
+		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_k\}$ are determined, we define $\bar{\mathbf{H}}_{kj}^\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}_{kj}^\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}_k^\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}_k^\mathrm{B}$, and $\bar{\mathbf{H}}_j^\mathrm{F} \triangleq \mathbf{H}_j^\mathrm{F} \mathbf{W}_j$.
+		The \gls{bd} \gls{ris} subproblem reduces to
+		\begin{mini!}
+			{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}_{kj}^\mathrm{D} + \bar{\mathbf{H}}_k^\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}_j^\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
+		\end{mini!}
+
+		\begin{proposition}
+			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
+			\begin{equation}
+				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+			\end{equation}
+			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
+			\begin{equation}
+				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}_{j,g}^\mathrm{F} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{D}_{kj,g}^{(r)}\bigr) {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H},
+			\end{equation}
+			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - \mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}$ and
+			\begin{equation}
+				\mathbf{D}_{kj,g}^{(r)} = \mathbf{H}_{jk}^\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
+			\end{equation}
+		\end{proposition}
+		\begin{proof}
+			To be added.
+		\end{proof}
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/ic_interference_sx.tex}
+			}
+			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$.
+Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}.
+Reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB} and $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$.}
+			\label{sm:ic_interference_sx}
+		\end{figure}
+		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd} \gls{ris} helps to reduce the leakage interference.
+		In this case, a fully-connected $2^n$-element \gls{bd} \gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
+		Interestingly, the result suggests that \gls{bd} \gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
+	\end{subsection}
+
+	\begin{subsection}{Weighted Sum-Rate Maximization}
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{J_2 = \sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k \mathbf{H}_{kj}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kj} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+			\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
+		\end{maxi!}
+		where $\rho_k$ is the weight of user $k$ and $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix
+		\begin{equation}
+			\mathbf{Q}_k = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H} + \eta \mathbf{I}.
+		\end{equation}
+		For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution based on \gls{wsr}-\gls{wmmse} relationship is proposed in \cite{Negro2010}.
+		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
+		\begin{equation}
+			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H}\bigr)^{-1},
+		\end{equation}
+		the corresponding error matrix is
+		\begin{equation}
+			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{(r-1)} \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+		\end{equation}
+		the \gls{mse} weight is
+		\begin{equation}
+			\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
+		\end{equation}
+		the Lagrange multiplier is
+		% \begin{equation}
+		% 	\begin{split}
+		% 		\lambda_k^{(r)}
+		% 		& = \frac{\sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)}}^\mathsf{H}) - \sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)}}^\mathsf{H})}{P_k} \\
+		% 		& \quad + \frac{\mathrm{tr}(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H})}{P_k}
+		% 	\end{split}
+		% \end{equation}
+		\begin{equation}
+			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)}}^\mathsf{H} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
+		\end{equation}
+		where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} \mathbf{H}_{kj} \mathbf{W}_j^{(r)}$.
+		The precoder at transmitter $k$ is
+		\begin{equation}
+			\mathbf{W}_k^{(r)} = \Bigl(\sum_j \mathbf{H}_{jk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}_{jk} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \mathbf{H}_{kk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
+		\end{equation}
+		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} w.r.t. \gls{ris} block $g$ is
+		\begin{equation}
+			\begin{split}
+				\frac{\partial J_2}{\partial \mathbf{\Theta}_g^*}
+				& = \sum_k \rho_k {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kk} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
+				& \quad \times \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H}\bigr).
+			\end{split}
+			\label{eq:ic_rate_gradient_ris}
+		\end{equation}
+		The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:ic_rate_gradient_ris}.
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/ic_rate_sx.tex}
+			}
+			\caption{Average weighted sum-rate versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
+			\label{sm:ic_rate_sx}
+		\end{figure}
+		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd} \gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
 	\end{subsection}

### 2023-12-16 src/ic_interference_sx.m

@@ -64,5 +64,7 @@ hold off; grid on;
 style_plot(handle.interference); set(handle.interference(find(reflect.antenna == 0)), 'Color', 'k', 'Marker', 'none');
 xlabel('RIS Group Size');
 ylabel('Leakage Interference [W]');
-legend('$N_s = ' + string(vec(reflect.antenna)) + '$', 'Location', 'sw');
+legend('$N_s = ' + string(vec(reflect.antenna)) + '$', 'Location', 'ne');
 savefig('plots/ic_interference_sx.fig');
+matlab2tikz('../assets/simulation/ic_interference_sx.tex', 'width', '8cm', 'height', '6cm');
+

### 2023-12-16 src/ic_rate_sx.m

@@ -61,3 +61,4 @@ xlabel('Direct SNR [dB]');
 ylabel('Weighted Sum-Rate [bit/s/Hz]');
 legend('Location', 'nw');
 savefig('plots/ic_rate_sx.fig');
+matlab2tikz('../assets/simulation/ic_rate_sx.tex', 'width', '8cm', 'height', '6cm');

### 2023-12-22 assets/simulation/ic_rate_user.tex
:zap: Refactor code

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
%
\begin{tikzpicture}

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
xmin=2,
xmax=10,
xlabel style={font=\color{white!15!black}},
xlabel={User Pairs},
ymin=24.0366620568765,
ymax=62.9320178950178,
ylabel style={font=\color{white!15!black}},
ylabel={Weighted Sum-Rate [bit/s/Hz]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
2	24.0366620568765\\
4	34.2503871208668\\
6	41.622749643327\\
8	44.0380050877313\\
10	43.8795026226494\\
};
\addlegendentry{$N^\mathrm{S} = 0$}

\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
2	25.3990077780911\\
4	36.3182517013294\\
6	42.844297578367\\
8	46.9811600018883\\
10	47.4095039520004\\
};
\addlegendentry{$(N^\mathrm{S}, L) = (16, 1)$}

\addplot [color=mycolor1, dashed, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
2	26.1302675490509\\
4	37.2433314642391\\
6	43.8241685215847\\
8	48.7515778844427\\
10	50.0262345258606\\
};
\addlegendentry{$(N^\mathrm{S}, L) = (16, 4)$}

\addplot [color=mycolor1, dotted, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
2	26.5005433882963\\
4	37.8529809047498\\
6	44.5290585688344\\
8	50.1996330401944\\
10	51.8865599593385\\
};
\addlegendentry{$(N^\mathrm{S}, L) = (16, 16)$}

\addplot [color=mycolor2, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
2	29.0139251001163\\
4	39.8325157791058\\
6	47.087891457604\\
8	52.0445486861005\\
10	53.9856612942705\\
};
\addlegendentry{$(N^\mathrm{S}, L) = (64, 1)$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
2	31.3276950788263\\
4	42.7749665094192\\
6	50.0160405682383\\
8	56.5092293329805\\
10	59.5047215843355\\
};
\addlegendentry{$(N^\mathrm{S}, L) = (64, 4)$}

\addplot [color=mycolor2, dotted, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
2	32.6664816559571\\
4	44.5042904532228\\
6	51.6271886078106\\
8	58.8237458788222\\
10	62.9320178950178\\
};
\addlegendentry{$(N^\mathrm{S}, L) = (64, 64)$}

\end{axis}
\end{tikzpicture}%

### 2023-12-22 assets/simulation/pc_singular_bound.tex
:zap: Refactor code

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.58039,0.76863,0.96078}%
\definecolor{mycolor2}{rgb}{0.25882,0.37647,0.66667}%
\definecolor{mycolor3}{rgb}{0.94902,0.38039,0.38039}%
\definecolor{mycolor4}{rgb}{0.91765,0.03529,0.03529}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\begin{tikzpicture}

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1,2,3,4},
xticklabels={{$\sigma_1$},{$\sigma_2$},{$\sigma_3$},{$\sigma_4$}},
ymin=0,
ymax=4.5,
ylabel style={font=\color{white!15!black}},
ylabel={Amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
legend columns=5,
transpose legend,
legend style={/tikz/column 2/.style={column sep=5pt}}
]
\addplot[ybar, bar width=0.123, fill=black, draw=black, area legend] table[row sep=crcr] {%
1	3.11578483462081\\
2	2.33621539044729\\
3	1.33501504737837\\
4	0.346232804852115\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addlegendentry{Direct}

\addplot[ybar, bar width=0.123, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	2.74905207049567\\
2	1.83843449000086\\
3	0.952844790933556\\
4	0.022527302733258\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addlegendentry{Min, $L = 1$}

\addplot[ybar, bar width=0.123, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	2.71936092735902\\
2	1.81605826060481\\
3	0.906339746943746\\
4	0.00914697809349159\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addlegendentry{Min, $L = 32$}

\addplot[ybar, bar width=0.123, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	3.8960081771894\\
2	2.67136418131802\\
3	1.64221742934803\\
4	0.603919247269453\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addlegendentry{Max, $L = 1$}

\addplot[ybar, bar width=0.123, fill=mycolor4, draw=black, area legend] table[row sep=crcr] {%
1	4.03127940593837\\
2	2.67500105747776\\
3	1.67178857361767\\
4	0.628233917896107\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addlegendentry{Max, $L = 32$}

\addplot [color=mycolor5, line width=2.0pt]
  table[row sep=crcr]{%
0	2.68074858002325\\
5	2.68074858002325\\
};
\addlegendentry{$\sigma_1(\mathbf{T})$}

\addplot [color=mycolor5, dashed, line width=2.0pt]
  table[row sep=crcr]{%
0	1.7029380545254\\
5	1.7029380545254\\
};
\addlegendentry{$\sigma_2(\mathbf{T})$}

\addplot [color=mycolor5, dotted, line width=2.0pt]
  table[row sep=crcr]{%
0	0.745179150575099\\
5	0.745179150575099\\
};
\addlegendentry{$\sigma_3(\mathbf{T})$}

\addplot [color=mycolor5, dashdotted, line width=2.0pt]
  table[row sep=crcr]{%
0	1.47492426026826e-08\\
5	1.47492426026826e-08\\
};
\addlegendentry{$\sigma_4(\mathbf{T})$}

\end{axis}

\begin{axis}[%
width=12.27cm,
height=9.202cm,
at={(-1.595cm,-1.012cm)},
scale only axis,
xmin=0,
xmax=1,
ymin=0,
ymax=1,
axis line style={draw=none},
ticks=none,
axis x line*=bottom,
axis y line*=left,
legend columns=5,
transpose legend,
legend style={/tikz/column 2/.style={column sep=5pt}}
]
\end{axis}
\end{tikzpicture}%

### 2023-12-22 main.tex
:zap: Refactor code

@@
 \algrenewcommand{\algorithmicdo}{}
+
+% optidef
+\DeclareDocumentEnvironment{customopti}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
+	\ifthenelse{\equal{#3}{b}}{%
+		\ifthenelse{\equal{#1}{s}}%
+		% Short version problem
+		{\setFormatShort{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
+		% Long version problem
+		{\setFormatLong{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
+	}{%
+		\ifthenelse{\equal{#1}{s}}%
+		% Short version problem
+		{\setFormatShort{#4}{#5}\BaseMini{#2}{#5}{#6}{#7}{#8}{#4}}%
+		% Long version problem
+		{\setFormatLong{#4}{#5}\BaseMini{#2}{#5}{#6}{#7}{#8}{#4}}%
+	}%
+}%
+{\endBaseMini\toggletrue{bodyCon}}
+
+\DeclareDocumentEnvironment{customopti*}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
+	\ifthenelse{\equal{#1}{s}}%
+	% Short version problem
+	{\setFormatShort{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
+	% Long version problem
+	{\setFormatLong{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
+}{\endBaseMiniStar\toggletrue{bodyCon}}
+
+\DeclareDocumentEnvironment{customopti!}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
+	\ifthenelse{\equal{#1}{s}}%
+	% Short version problem
+	{\setFormatShort{#4}{#5}\BaseMiniExclam{#2}{#5}{#6}{#7}{#8}{#4}{#3}}%
+	% Long version problem
+	{\setFormatLong{#4}{#5}\BaseMiniExclam{#2}{#5}{#6}{#7}{#8}{#4}{#3}}%
+}{\endBaseMiniExclam\toggletrue{bodyCon}}
 
@@
 			}
-			\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+			\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
+$(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
 			\label{sm:pc_power_sx}
@@
 			}
-			\caption{Average channel power versus \gls{ris} group size $L$ for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+			\caption{Average channel power versus \gls{ris} group size $L$.
+$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
 			\label{sm:pc_power_bond}
@@
 		\begin{equation}
-			\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\sigma_n^2} {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{HW} \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\sigma_n^2}\biggr)^{-1} \mathbf{W}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H}.
+			\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{HW} \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)^{-1} \mathbf{W}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H}.
 			\label{eq:pc_rate_gradient_ris}
@@
 			\begin{algorithmic}[1]
-				\Require $\mathbf{H}^\mathrm{D}$, $\mathbf{H}^\mathrm{F}$, $\mathbf{H}^\mathrm{B}$, $\mathbf{W}$, $L$, $\sigma_n^2$
+				\Require $\mathbf{H}^\mathrm{D}$, $\mathbf{H}^\mathrm{F}$, $\mathbf{H}^\mathrm{B}$, $\mathbf{W}$, $L$, $\eta$
 				\Ensure $\mathbf{\Theta}^\star$
@@
 			\centering
-			\resizebox{0.65\columnwidth}{!}{
+			\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{sm:pc_rate_sx}]{
+				\resizebox{0.48\columnwidth}{!}{
 					\input{assets/simulation/pc_rate_sx.tex}
 				}
-			\caption{Average achievable rate versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-			\label{sm:pc_rate_sx}
+			}
+			\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{sm:pc_rate_tx}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_rate_tx.tex}
+				}
+			}
+			\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+			\label{sm:pc_rate}
 		\end{figure}
@@
 			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
-			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris} for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ without direct link.}
+			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris}. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$. Direct link is absent.}
 			\label{sm:pc_singular_toy}
@@
 		Finally, we characterize the \emph{Pareto front} of channel singular values via optimization approach.
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
+		% \begin{maxi!}
+		% 	{\scriptstyle{\mathbf{\Theta}}}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
+		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		% \end{maxi!}
+
+		\begin{customopti!}
+			{\underset{\scriptstyle{\mathbf{\Theta}}}{max / min}}{}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		\end{maxi!}
+		\end{customopti!}
+
 		where $\rho_n$ is the weight of $n$-th singular value.
@@
 			\centering
-			\subfloat[Pareto Front\label{sm:pc_singular_pareto_bond}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_singular_pareto_bond.tex}
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/pc_singular_pareto.tex}
 			}
+			\caption{Singular value Pareto front. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 64, 2)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
+			\label{sm:pc_singular_pareto}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/pc_singular_bound.tex}
 			}
-			\subfloat[Evolving Trend\label{sm:pc_singular_trend_bond}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_singular_trend_bond.tex}
-				}
-			}
-			\caption{Singular value Pareto front and trend for $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 16, 2)$.}
-			\label{sm:pc_singular_bond}
+			\caption{Singular value bounds for rank-1 indirect channel.
+$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
+			\label{sm:pc_singular_bound}
 		\end{figure}
-		The Pareto front and evolving trend of channel singular values are shown in Fig.~\subref*{sm:pc_singular_pareto_bond} and \subref*{sm:pc_singular_trend_bond}.
+
+		The Pareto front and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
 		Clearly, \gls{bd} \gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
@@
 			\end{equation}
-			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - \mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}$ and
+			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{k,g}^\mathrm{B}$ and
 			\begin{equation}
@@
 			}
-			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$.
+			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
 Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}.
-Reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB} and $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$.}
+$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$, and reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB}.}
 			\label{sm:ic_interference_sx}
@@
 			}
-			\caption{Average weighted sum-rate versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$ for $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
+			\caption{Average weighted sum-rate versus \gls{snr}, \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
+$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
 			\label{sm:ic_rate_sx}
 		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/ic_rate_user.tex}
+			}
+			\caption{Average weighted sum-rate versus user pairs $K$, \gls{ris} elements $N^\mathrm{S}$ and group size $L$ at $\mathrm{SNR} = \qty{15}{dB}$.
+$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}) = (4, 4, 3)$, $\rho_k = 1, \ \forall k$.}
+			\label{sm:ic_rate_user}
+		\end{figure}
+
 		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd} \gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}

### 2023-12-22 src/ic_interference_sx.m

@@ -1,70 +1,60 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream, network.pair, transmit.power, network.coverage] = deal(8, 2 .^ [-inf, 2 : 2 : 8], 4, 3, 5, db2pow(0), 50);
+[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream, network.pair, transmit.power, network.coverage] = deal(8, 2 .^ (2 : 2 : 8), 4, 3, 5, db2pow(0), 50);
 [channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(db2pow(-30), 3, 2.4, 2.4);
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = pathloss_disk(network.pair, network.coverage, channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward);
-[number.antenna, number.realization] = deal(length(reflect.antenna), 1e1);
+[number.bond, number.antenna, number.realization] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 2);
 
 for r = 1 : number.realization
+	% * No RIS
 	channel.direct = shiftdim(sqrt(channel.pathloss.direct), -2) .* fading_nlos(receive.antenna, transmit.antenna, network.pair, network.pair);
+	receive.beamformer = combiner_initial_ic(channel.direct, transmit.stream);
+	transmit.beamformer = precoder_initial_ic(channel.direct, transmit.stream, transmit.power);
+	[iter.converge, iter.tolerance, iter.counter, iter.interference] = deal(false, 1e-4, 0, interference_leakage(pagemtimes(pagemtimes(receive.beamformer, channel.direct), transmit.beamformer)));
+	while ~iter.converge
+		receive.beamformer = combiner_interference_ic(channel.direct, transmit.beamformer);
+		transmit.beamformer = precoder_interference_ic(channel.direct, receive.beamformer, transmit.power);
+		receive.interference.direct(r) = interference_leakage(pagemtimes(pagemtimes(receive.beamformer, channel.direct), transmit.beamformer));
+		iter.converge = (abs(receive.interference.direct(r) - iter.interference) / iter.interference <= iter.tolerance);
+		iter.interference = receive.interference.direct(r);
[…]

### 2023-12-22 src/ic_rate_sx.m

@@ -1,64 +1,57 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream, network.pair] = deal(8, 2 .^ [-inf, 5, 8], 4, 3, 5);
+[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream, network.pair] = deal(8, 2 .^ [5, 8], 4, 3, 5);
 [transmit.power, receive.noise, receive.weight] = deal(db2pow(-20), db2pow(-75 : -10 : -115), ones(network.pair, 1));
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
 transmit.snr = pow2db(transmit.power * channel.pathloss.direct ./ receive.noise);
-[number.bond, number.noise, number.antenna, number.realization] = deal(2, length(receive.noise), length(reflect.antenna), 1e1);
+[number.bond, number.noise, number.antenna, number.realization] = deal(3, length(receive.noise), length(reflect.antenna), 2);
 
 for r = 1 : number.realization
+	% * No RIS
 	channel.direct = sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair, network.pair);
+	transmit.beamformer = precoder_initial_ic(channel.direct, transmit.stream, transmit.power);
+	for n = 1 : number.noise
+		transmit.beamformer = precoder_rate_explicit_ic(channel.direct, transmit.beamformer, transmit.power, receive.noise(n), receive.weight);
+		receive.wsr.direct(n, r) = receive.weight' * rate_mimo(channel.direct, transmit.beamformer, receive.noise(n));
+	end
+	% * Have RIS
 	for a = 1 : number.antenna
-		if reflect.antenna(a) == 0
+		reflect.bond = [1, 4, reflect.antenna(a)];
+		channel.forward = sqrt(channel.pathloss.forward) .* fading_nlos(reflect.antenna(a), transmit.antenna, 1, network.pair);
+		channel.backward = sqrt(channel.pathloss.backward) .* fading_nlos(receive.antenna, reflect.antenna(a), network.pair, 1);
+		clear scatter_rate_ic;
+		for b = 1 : number.bond
[…]

### 2023-12-22 src/ic_rate_user.m

@@ -1,0 +1,59 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream, network.pair] = deal(4, 2 .^ [4, 6], 4, 3, 2 : 2 : 10);
+[transmit.power, receive.noise] = deal(db2pow(-20), db2pow(-100));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[number.bond, number.antenna, number.pair, number.realization] = deal(3, length(reflect.antenna), length(network.pair), 20);
+
+for r = 1 : number.realization
+	% * No RIS
+	for p = 1 : number.pair
+		receive.weight = ones(network.pair(p), 1);
+		channel.direct = sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair(p), network.pair(p));
+		transmit.beamformer = precoder_initial_ic(channel.direct, transmit.stream, transmit.power);
+		transmit.beamformer = precoder_rate_bisection_ic(channel.direct, transmit.beamformer, transmit.power, receive.noise, receive.weight);
+		receive.wsr.direct(p, r) = receive.weight' * rate_mimo(channel.direct, transmit.beamformer, receive.noise);
+	end
+	% * Have RIS
+	for a = 1 : number.antenna
+		reflect.bond = [1, 4, reflect.antenna(a)];
+		for p = 1 : number.pair
+			receive.weight = ones(network.pair(p), 1);
+			channel.direct = sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair(p), network.pair(p));
+			channel.forward = sqrt(channel.pathloss.forward) .* fading_nlos(reflect.antenna(a), transmit.antenna, 1, network.pair(p));
+			channel.backward = sqrt(channel.pathloss.backward) .* fading_nlos(receive.antenna, reflect.antenna(a), network.pair(p), 1);
+			transmit.beamformer = precoder_initial_ic(channel.direct, transmit.stream, transmit.power);
+			clear scatter_rate_ic;
+			for b = 1 : number.bond
[…]

### 2023-12-22 src/lib/precoder_rate_bisection_ic.m

@@ -1,6 +1,6 @@
-function [W] = precoder_rate_ic_bisection(H, W, P_t, P_n, rho)
+function [W] = precoder_rate_bisection_ic(H, W, P_t, P_n, rho)
 	[N_r, N_t, N_e, K] = deal(size(H, 1), size(H, 2), size(W, 2), size(W, 4));
-	[iter.converge, iter.tolerance, iter.counter] = deal(false, 1e-3, 0);
+	[iter.converge, iter.tolerance, iter.counter] = deal(false, 1e-4, 0);
 	iter.J = rho' * rate_mimo(H, W, P_n);
 	while ~iter.converge
 		T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');

### 2023-12-22 src/lib/rate_mimo.m

@@ -1,3 +1,16 @@
+function [R] = rate_mimo(H, W, P_n)
+	if size(H, 3) == 1
+		R = rate_mimo_pc(H, W, P_n);
+	else
+		R = rate_mimo_ic(H, W, P_n);
+	end
+end
+
+function [R] = rate_mimo_pc(H, W, P_n)
+	R = log(det(eye(size(W, 2)) + (H * W)' * (H * W) / P_n));
+	R = real(R);
+end
+
 function [R] = rate_mimo_ic(H, W, P_n)
 	[N_r, K] = deal(size(H, 1), size(H, 3));
 	T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');

### 2023-12-22 src/lib/scatter_interference_ic.m

@@ -1,8 +1,14 @@
-function [Theta, H] = scatter_interference_ic(H_d, H_f, H_b, Theta, L)
+function [Theta, H] = scatter_interference_ic(H_d, H_f, H_b, L)
+	persistent iter;
+	if isempty(iter)
+		Theta = eye(size(H_f, 1));
+	else
+		Theta = iter.Theta;
+	end
+
 	[K, G] = deal(size(H_d, 3), length(Theta) / L);
 	H = channel_aggregate(H_d, H_f, H_b, Theta);
-	[iter.converge, iter.tolerance, iter.counter] = deal(false, 1e-4, 0);
-	iter.I = interference_leakage(H);
+	[iter.converge, iter.tolerance, iter.counter, iter.I] = deal(false, 1e-4, 0, interference_leakage(H));
 	while ~iter.converge
 		for g = 1 : G
 			S = (g - 1) * L + 1 : g * L;
@@ -21,4 +27,5 @@ function [Theta, H] = scatter_interference_ic(H_d, H_f, H_b, Theta, L)
 		iter.I = I;
 		iter.counter = iter.counter + 1;
 	end
+	iter.Theta = Theta;
 end

### 2023-12-22 src/lib/scatter_power_max_pc.m

@@ -1,8 +1,14 @@
-function [Theta, H] = scatter_power_pc(H_d, H_f, H_b, Theta, L)
+function [Theta, H] = scatter_power_max_pc(H_d, H_f, H_b, L)
+	persistent iter;
+	if isempty(iter)
+		Theta = eye(size(H_f, 1));
+	else
+		Theta = iter.Theta;
+	end
+
 	G = length(Theta) / L;
 	H = channel_aggregate(H_d, H_f, H_b, Theta);
-	[iter.converge, iter.tolerance, iter.counter] = deal(false, 1e-4, 0);
-	iter.P = norm(H, 'fro') ^ 2;
+	[iter.converge, iter.tolerance, iter.counter, iter.P] = deal(false, 1e-4, 0, norm(H, 'fro') ^ 2);
 	while ~iter.converge
 		for g = 1 : G
 			S = (g - 1) * L + 1 : g * L;
@@ -16,4 +22,5 @@ function [Theta, H] = scatter_power_pc(H_d, H_f, H_b, Theta, L)
 		iter.P = P;
 		iter.counter = iter.counter + 1;
 	end
+	iter.Theta = Theta;
 end

### 2023-12-22 src/lib/scatter_power_min_pc.m

@@ -1,0 +1,30 @@
+function [Theta, H] = scatter_power_min_pc(H_d, H_f, H_b, L)
+	persistent iter;
+	if isempty(iter)
+		Theta = eye(size(H_f, 1));
+	else
+		Theta = iter.Theta;
+	end
+
+	G = length(Theta) / L;
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+	[iter.converge, iter.tolerance, iter.counter, iter.P] = deal(false, 1e-4, 0, norm(H, 'fro') ^ 2);
+	while ~iter.converge
+		for g = 1 : G
+			S = (g - 1) * L + 1 : g * L;
+			S_c = setdiff(1 : length(Theta), S);
+			D = H_d + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :);
+			T = H_b(:, S)' * H_b(:, S);
+			B = max(eig(T)) * eye(L) - T + eps;
+			M = (B * Theta(S, S) * H_f(S, :) - H_b(:, S)' * D) * H_f(S, :)';
+			[U, ~, V] = svd(M);
+			Theta(S, S) = U * V';
+		end
+		H = channel_aggregate(H_d, H_f, H_b, Theta);
+		P = norm(H, 'fro') ^ 2;
+		iter.converge = (abs(P - iter.P) / iter.P <= iter.tolerance);
+		iter.P = P;
+		iter.counter = iter.counter + 1;
+	end
+	iter.Theta = Theta;
+end

### 2023-12-22 src/lib/scatter_singular_min_pc.m

@@ -1,7 +1,8 @@
-function [Theta, H] = scatter_rate_pc(H_d, H_f, H_b, W, L, P_n)
+function [Theta, H] = scatter_singular_min_pc(H_d, H_f, H_b, rho, L)
 	persistent iter;
 	if isempty(iter)
-		Theta = eye(size(H_f, 1));
+		clear scatter_power_min_pc;
+		Theta = scatter_power_min_pc(H_d, H_f, H_b, L);
 	else
 		Theta = iter.Theta;
 	end
@@ -9,27 +10,29 @@ function [Theta, H] = scatter_rate_pc(H_d, H_f, H_b, W, L, P_n)
 	G = length(Theta) / L;
 	H = channel_aggregate(H_d, H_f, H_b, Theta);
 	[G_e, G_r, D] = deal(zeros(size(Theta)));
-	[iter.converge, iter.tolerance, iter.counter, iter.R] = deal(false, 1e-4, 0, rate_mimo(H, W, P_n));
+	[iter.converge, iter.tolerance, iter.counter, iter.J] = deal(false, 1e-4, 0, - rho' * svd(H));
 	while ~iter.converge
 		[iter.G_r, iter.D] = deal(G_r, D);
 		for g = 1 : G
 			S = (g - 1) * L + 1 : g * L;
 			S_c = setdiff(1 : length(Theta), S);
-			fun = @(Theta_g) rate_mimo(H_d + H_b(:, S) * Theta_g * H_f(S, :) + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :), W, P_n);
-			G_e(S, S) = gradient_euclidean(H, H_f(S, :), H_b(:, S), W, P_n);
+			fun = @(Theta_g) - rho' * svd(H_d + H_b(:, S) * Theta_g * H_f(S, :) + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :));
+			G_e(S, S) = gradient_euclidean(H, H_f(S, :), H_b(:, S), rho);
 			G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
 			D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
 			Theta(S, S) = step_armijo(fun, Theta(S, S), D(S, S));
 			H = channel_aggregate(H_d, H_f, H_b, Theta);
 		end
[…]

### 2023-12-22 src/pc_power_sx.m

@@ -1,44 +1,41 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(8, 2 .^ [-inf, 2 : 2 : 8], 4);
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(8, 2 .^ (2 : 2 : 8), 4);
 % [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.antenna, number.realization] = deal(length(reflect.antenna), 1e1);
+[number.bond, number.antenna, number.realization] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 2);
 
 for r = 1 : number.realization
+	% * No RIS
 	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	channel.power.direct(r) = norm(channel.direct, 'fro') ^ 2;
+	% * Have RIS
 	for a = 1 : number.antenna
-		if reflect.antenna(a) == 0
-			channel.power.aggregate(1, a, r) = norm(channel.direct, 'fro') ^ 2;
-		else
-			channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
-			channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
-			reflect.bond = 2 .^ (0 : log2(reflect.antenna(a))); number.bond = length(reflect.bond);
-			for b = 1 : number.bond
-				[reflect.beamformer, channel.aggregate] = scatter_power_pc(channel.direct, channel.forward, channel.backward, eye(reflect.antenna(a)), reflect.bond(b));
-				channel.power.aggregate(b, a, r) = norm(channel.aggregate, 'fro') ^ 2;
-			end
+		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
[…]

### 2023-12-22 src/pc_rate_sx.m

@@ -1,61 +1,56 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(8, 2 .^ [-inf, 5, 8], 4);
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(8, 2 .^ [5, 8], 4);
 [transmit.power, receive.noise] = deal(db2pow(-20), db2pow(-75 : -10 : -115));
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
 transmit.snr = pow2db(transmit.power * channel.pathloss.direct ./ receive.noise);
-[number.bond, number.noise, number.antenna, number.realization] = deal(3, length(receive.noise), length(reflect.antenna), 1e1);
+[number.bond, number.noise, number.antenna, number.realization] = deal(3, length(receive.noise), length(reflect.antenna), 2);
 
 for r = 1 : number.realization
+	% * No RIS
 	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	for n = 1 : number.noise
+		transmit.beamformer = precoder_rate_pc(channel.direct, transmit.power, receive.noise(n));
+		receive.rate.direct(n, r) = rate_mimo(channel.direct, transmit.beamformer, receive.noise(n));
+	end
+	% * Have RIS
 	for a = 1 : number.antenna
+		reflect.bond = [1, 4, reflect.antenna(a)];
 		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
 		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
-		for n = 1 : number.noise
-			if reflect.antenna(a) == 0
+		clear scatter_rate_pc;
+		for b = 1 : number.bond
+			for n = 1 : number.noise
 				transmit.beamformer = precoder_rate_pc(channel.direct, transmit.power, receive.noise(n));
-				receive.rate(1, n, a, r) = rate_mimo_pc(channel.direct, transmit.beamformer, receive.noise(n));
-			else
-				reflect.bond = [1, 4, reflect.antenna(a)];
-				for b = 1 : number.bond
-					reflect.beamformer = eye(reflect.antenna(a));
[…]

### 2023-12-22 src/pc_rate_tx.m

@@ -1,0 +1,46 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(2 .^ (0 : 2 : 4), 256, 4);
+[transmit.power, receive.noise] = deal(db2pow(-20), db2pow(-75 : -10 : -115));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[transmit.snr, reflect.bond] = deal(pow2db(transmit.power * channel.pathloss.direct ./ receive.noise), [1, reflect.antenna]);
+[number.bond, number.noise, number.antenna, number.realization] = deal(length(reflect.bond), length(receive.noise), length(transmit.antenna), 2);
+
+for r = 1 : number.realization
+	for a = 1 : number.antenna
+		channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna(a));
+		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna(a));
+		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
+		clear scatter_rate_pc;
+		for b = 1 : number.bond
+			for n = 1 : number.noise
+				transmit.beamformer = precoder_rate_pc(channel.direct, transmit.power, receive.noise(n));
+				[iter.converge, iter.tolerance, iter.counter, iter.rate] = deal(false, 1e-4, 0, rate_mimo(channel.direct, transmit.beamformer, receive.noise(n)));
+				while ~iter.converge
+					[reflect.beamformer, channel.aggregate] = scatter_rate_pc(channel.direct, channel.forward, channel.backward, transmit.beamformer, reflect.bond(b), receive.noise(n));
+					transmit.beamformer = precoder_rate_pc(channel.aggregate, transmit.power, receive.noise(n));
+					receive.rate(n, b, a, r) = rate_mimo(channel.aggregate, transmit.beamformer, receive.noise(n));
+					iter.converge = (abs(receive.rate(n, b, a, r) - iter.rate) / iter.rate <= iter.tolerance);
+					iter.rate = receive.rate(n, b, a, r);
+					iter.counter = iter.counter + 1;
+				end
+			end
+		end
[…]

### 2023-12-22 src/pc_singular_pareto.m

@@ -1,0 +1,43 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 64, 2);
+[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2 .^ (0 : 2 : log2(reflect.antenna)));
+assert(channel.rank == 2, 'The plot function is only for 2-sv case.');
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(1, db2pow(-17.5), db2pow(-17.5));
+channel.weight = simplex_standard(channel.rank, 0.1);
+[number.weight, number.bond, number.realization] = deal(size(channel.weight, 2), length(reflect.bond), 2);
+
+for r = 1 : number.realization
+	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna);
+	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
+	channel.singular.direct(:, r) = svd(channel.direct);
+	for b = 1 : number.bond
+		clear scatter_singular_min_pc scatter_singular_max_pc;
+		for w = 1 : number.weight
+			[reflect.beamformer.min, channel.aggregate.min] = scatter_singular_min_pc(channel.direct, channel.forward, channel.backward, channel.weight(:, w), reflect.bond(b));
+			[reflect.beamformer.max, channel.aggregate.max] = scatter_singular_max_pc(channel.direct, channel.forward, channel.backward, channel.weight(:, w), reflect.bond(b));
+			channel.singular.aggregate.min(:, w, b, r) = svd(channel.aggregate.min);
+			channel.singular.aggregate.max(:, w, b, r) = svd(channel.aggregate.max);
+		end
+	end
+end
+channel.singular.direct = mean(channel.singular.direct, ndims(channel.singular.direct));
+channel.singular.aggregate.min = mean(channel.singular.aggregate.min, ndims(channel.singular.aggregate.min));
+channel.singular.aggregate.max = mean(channel.singular.aggregate.max, ndims(channel.singular.aggregate.max));
+save('data/pc_singular_pareto.mat');
+
[…]

### 2024-01-03 abstract.tex
:pencil: Add abstract

--- 2023-12-22 main.tex
@@
 		Hongyu~Li,~\IEEEmembership{Graduate Student Member,~IEEE,}\\
-		Yijie~Mao,~\IEEEmembership{Member,~IEEE,}
-		Shanpu~Shen,~\IEEEmembership{Member,~IEEE,}
+		Massimo~Franceschetti,~\IEEEmembership{Fellow,~IEEE,}
 		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}

### 2024-01-04 main.tex
:pencil: Add background

@@
 
-% \begin{abstract}
-% \end{abstract}
+\begin{abstract}
+	\gls{ris} is a promising technology that recycles and redistributes ambient waves for improved wireless performance.
+	% \gls{ris} is a real-time programmable reflector that recycles and redistributes ambient waves for improved wireless performance.
+	This paper investigates the use of passive \gls{ris} for channel shaping in \gls{mimo} \gls{pc} and \gls{ic}.
+	We depart from the widely-adapted diagonal phase shift model and focus on a general asymmetric \gls{bd} architecture, which allows off-diagonal entries by in-group connections between elements.
+	For arbitrary group size, we propose a closed-form iterative algorithm for quadratic problems and a \gls{rcg} algorithm for general problems.
+	Various case studies are then conducted, including rate maximization and Pareto singular value characterization for \gls{pc}, and interference alignment and \gls{wsr} maximization for \gls{ic}.
+	To quantify channel shaping capability, we also derive analytical bounds under specific scenarios and validate those by aforementioned methods.
+	Simulation results suggest the advantage of \gls{bd} \gls{ris} scales with group size, while dyadic or tetradic architecture usually strikes a good balance between performance and complexity.
+	% Through theoretical analysis and numerical evaluation,
+	Our findings unlock unprecedented efficiency and adaptability, paving the way for smarter and greener wireless environments.
+	% truly programmable
+	% useful guidelines for prototype design.
+\end{abstract}
 
-% \begin{IEEEkeywords}
-% \end{IEEEkeywords}
+\begin{IEEEkeywords}
+	Reconfigurable intelligent surface, channel shaping, point-to-point channel, interference channel.
+\end{IEEEkeywords}
 
 \glsresetall
+
+\begin{section}{Introduction}
+	The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
+	Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
+	Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
+	This is made possible by the recent advances in \gls{ris}, a real-time programmable metasurface made of low-power reflecting elements.
+	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than conventional relays.
+	Using \gls{ris} for \emph{passive beamforming} has attracted significant interest in wireless communication, backscatter, sensing, and power transfer literature \cite{Wu2019,Wu2020c,Yang2020,Zheng2021,Jia2020,Liang2022,Liu2022a,Hua2023,Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
+	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as investigated \cite{Liu2019d,Karasik2020,Basar2020,Ma2020a,Zhang2021d,Hua2022,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
+	Although fruitful outcomes have been harvested by fancy optimization tools, one fundamental yet critical unanswered question is the \emph{channel shaping} capability of \gls{ris}: To what extent can \gls{ris} reshape the wireless channel?
+
+	% we aim to answer this question by a simple yet insightful approach: \emph{from diagonal to beyond}.
+	% The answer depends heavily on the phase shift model of \gls{ris}.
+	Before answering the question, we first need to revisit the \gls{ris} architecture.
+
+	% Despite the fruitful results, the existing literature on \gls{ris} is still limited to the diagonal phase shift model, where the phase shifters are constrained to be diagonal matrices.
+
+	% \gls{ris} also offers a new degree of freedom for \emph{channel shaping}, i.e., to reshape the wireless channel to a desired form.
+\end{section}
 

### 2024-01-07 main.tex
:pencil: Update background

@@
 	Using \gls{ris} for \emph{passive beamforming} has attracted significant interest in wireless communication, backscatter, sensing, and power transfer literature \cite{Wu2019,Wu2020c,Yang2020,Zheng2021,Jia2020,Liang2022,Liu2022a,Hua2023,Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
-	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as investigated \cite{Liu2019d,Karasik2020,Basar2020,Ma2020a,Zhang2021d,Hua2022,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
+	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Liu2019d,Karasik2020,Basar2020,Ma2020a,Zhang2021d,Hua2022,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
 	Although fruitful outcomes have been harvested by fancy optimization tools, one fundamental yet critical unanswered question is the \emph{channel shaping} capability of \gls{ris}: To what extent can \gls{ris} reshape the wireless channel?

### 2024-01-08 main.tex
:pencil: Update literature review

--- 2024-01-04 main.tex
@@
 \newacronym{dof}{DoF}{Degree of Freedom}
+\newacronym{siso}{SISO}{Single-Input Single-Output}
+\newacronym{miso}{MISO}{Multiple-Input Single-Output}
 \newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
@@
 \begin{abstract}
-	\gls{ris} is a promising technology that recycles and redistributes ambient waves for improved wireless performance.
+	\gls{ris} recycles and redistributes ambient waves for improved wireless performance.
+	% \gls{ris} is a promising technology that recycles and redistributes ambient waves for improved wireless performance.
 	% \gls{ris} is a real-time programmable reflector that recycles and redistributes ambient waves for improved wireless performance.
@@
 	For arbitrary group size, we propose a closed-form iterative algorithm for quadratic problems and a \gls{rcg} algorithm for general problems.
-	Various case studies are then conducted, including rate maximization and Pareto singular value characterization for \gls{pc}, and interference alignment and \gls{wsr} maximization for \gls{ic}.
+	Various case studies are then conducted, including Pareto singular value characterization and rate maximization for \gls{pc}, and interference alignment and \gls{wsr} maximization for \gls{ic}.
 	To quantify channel shaping capability, we also derive analytical bounds under specific scenarios and validate those by aforementioned methods.
@@
 \begin{section}{Introduction}
-	The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
-	Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
-	This is made possible by the recent advances in \gls{ris}, a real-time programmable metasurface made of low-power reflecting elements.
+	% The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
+	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
+	Today we are witnessing a paradigm shift from {connectivity} to {intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
+	This is made possible by the recent advances in \gls{ris}, a real-time programmable metasurface made of numerous non-resonant sub-wavelength scattering elements.
 	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than conventional relays.
-	Using \gls{ris} for \emph{passive beamforming} has attracted significant interest in wireless communication, backscatter, sensing, and power transfer literature \cite{Wu2019,Wu2020c,Yang2020,Zheng2021,Jia2020,Liang2022,Liu2022a,Hua2023,Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
-	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as investigated \cite{Liu2019d,Karasik2020,Basar2020,Ma2020a,Zhang2021d,Hua2022,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
-	Although fruitful outcomes have been harvested by fancy optimization tools, one fundamental yet critical unanswered question is the \emph{channel shaping} capability of \gls{ris}: To what extent can \gls{ris} reshape the wireless channel?
+	Using \gls{ris} for \emph{passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
+	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
+	Although fruitful outcomes have been harvested over optimization tools, one fundamental yet critical question is the \emph{channel shaping} capability: To what extent can a passive \gls{ris} reshape the wireless channel?
+	The answer indeed depends on the hardware architecture and scattering model.
+
+	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and functions as an \emph{individual} phase shifter \cite{Wu2020}.
+	% , accounting for a diagonal phase shift model with unit magnitude.
+	The idea is extended to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} featuring in-group connections between elements.
+	This allows \emph{cooperative} reflection --- wave impinging on one element can propagate within the circuit and depart partially from all elements.
+	\gls{bd} \gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
+	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Li2023c,Bartoli2023}.
+	The channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} issues have also been investigated.
+	Therefore, \gls{bd} \gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
+
+	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
+	Metrics of channel shaping can be classified into \emph{singular value centric} and \emph{power centric}.
+	For diagonal \gls{ris}, the former has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023} in \gls{pc}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023} in \gls{ic}.
+	The latter has been studied in terms of channel power \cite{Wu2019} in \gls{pc} and leakage interference \cite{Santamaria2023a} in \gls{ic}.
+	When it comes to \gls{bd} \gls{ris}, the only metric analyzed is the channel power \cite{Nerini2023,Santamaria2023} where the \gls{mimo} case is still unexplored.\footnote{Single-stream \gls{mimo} with given precoder and combiner was considered in \cite{Nerini2023}.
+It is equivalent \gls{siso} channel shaping.}
+	Although insightful, the answers are far from complete and the optimization techniques are limited to very specific scenarios.
+	In this paper, we aim to quantify the channel shaping capability of \gls{bd} \gls{ris} through theoretical analysis and numerical evaluation.
+	The contributions are summarized below.
 
@@
 	% The answer depends heavily on the phase shift model of \gls{ris}.
-	Before answering the question, we first need to revisit the \gls{ris} architecture.
-
-	% Despite the fruitful results, the existing literature on \gls{ris} is still limited to the diagonal phase shift model, where the phase shifters are constrained to be diagonal matrices.
 

### 2024-01-09 main.tex
:pencil: Add contributions

@@
 	\gls{bd} \gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
-	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Li2023c,Bartoli2023}.
+	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
 	The channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} issues have also been investigated.
@@
 	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
-	Metrics of channel shaping can be classified into \emph{singular value centric} and \emph{power centric}.
+	Channel shaping metrics can be classified into \emph{singular value centric} and \emph{power centric}.
 	For diagonal \gls{ris}, the former has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023} in \gls{pc}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023} in \gls{ic}.
 	The latter has been studied in terms of channel power \cite{Wu2019} in \gls{pc} and leakage interference \cite{Santamaria2023a} in \gls{ic}.
-	When it comes to \gls{bd} \gls{ris}, the only metric analyzed is the channel power \cite{Nerini2023,Santamaria2023} where the \gls{mimo} case is still unexplored.\footnote{Single-stream \gls{mimo} with given precoder and combiner was considered in \cite{Nerini2023}.
-It is equivalent \gls{siso} channel shaping.}
-	Although insightful, the answers are far from complete and the optimization techniques are limited to very specific scenarios.
-	In this paper, we aim to quantify the channel shaping capability of \gls{bd} \gls{ris} through theoretical analysis and numerical evaluation.
+	When it comes to \gls{bd} \gls{ris}, the only metric analyzed is the channel power \cite{Nerini2023,Santamaria2023} while the \gls{mimo} case is still unexplored.\footnote{Single-stream \gls{mimo} with given precoder and combiner was considered in \cite{Nerini2023}.
+In terms of channel shaping, it is equivalent to \gls{siso}.}
+	Although insightful, those attempts are far from complete and the methods are limited to specific scenarios.
+	% This paper aims to quantify the channel shaping capability of asymmetric \gls{bd} \gls{ris} through theoretical analysis and numerical evaluation.
+	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
+	% quantify the channel shaping capability of asymmetric \gls{bd} \gls{ris} through theoretical analysis and numerical evaluation.
 	The contributions are summarized below.
 
-	% we aim to answer this question by a simple yet insightful approach: \emph{from diagonal to beyond}.
-	% The answer depends heavily on the phase shift model of \gls{ris}.
+	First, we examine the capability of \gls{bd} \gls{ris} to redistribute the channel singular values in \gls{mimo} \gls{pc}.
+	The Pareto frontiers are characterized by optimizing the \emph{weighted sum of singular values}, where the weights can be positive, zero, or negative.
+	It generalizes all singular value metrics and provides a powerful design framework.
+	We then discuss analytical singular value bounds under rank-deficient and no-direct scenarios.
 
-	% \gls{ris} also offers a new degree of freedom for \emph{channel shaping}, i.e., to reshape the wireless channel to a desired form.
+	% and demonstrate the channel shaping advantage of \gls{bd} \gls{ris} over diagonal \gls{ris}.
+
+	Second, we tailor a \gls{rcg} algorithm for asymmetric\footnote{Although the constraint of symmetric scattering parameters is widely respected in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, it can be relaxed when the \gls{bd} \gls{ris} involves asymmetric passive components \cite{Ahn2006}, as previously assumed in \cite{Li2023b,Li2023c}.
+Symmetry can be enforced by projection if necessary.} \gls{bd} \gls{ris} optimization.
+	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold and concisely evaluated as matrix exponential.
+	The proposed method not only features lower complexity and faster convergence than universal manifold optimization \cite{Absil2009,Pan2022d}, but also applies to any \gls{bd} \gls{ris} problem where gradient exists.
+	% It is used to solve the Pareto singular problem, as well as rate maximization in \gls{mimo} \gls{pc} and \gls{wsr} maximization in \gls{mimo} \gls{ic}.
+	% It effectively solves the Pareto singular problem.
+
+	% , as well as rate maximization in \gls{mimo} \gls{pc} and \gls{wsr} maximization in \gls{mimo} \gls{ic}.
+
+	% It helps to solve the aforementioned Pareto singular value problem.
+	% We exploit it to solve the Pareto singular value problem and
+
+	% It is exploited for the Pareto singular value problem, as well as rate maximization in \gls{mimo} \gls{pc} and \gls{wsr} maximization in \gls{mimo} \gls{ic}.
+	% It is used to solve the Pareto singular value problem,
+
+	Third, we consider power centric design
+	% Second, we consider power centric design
+	% exploit \gls{bd} \gls{ris} to power centric
+	% maximize channel power in \gls{mimo} \gls{pc} and minimize leakage interference in \gls{mimo} \gls{ic}.
+
 \end{section}
@@
 \begin{section}{\glsentryshort{mimo}-\glsentryshort{pc}}
+
+	\begin{subsection}{Channel Singular Value Redistribution}
+		We first show the channel shaping benefit of \gls{bd} \gls{ris} by a toy example.
+		Consider $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
+		The diagonal \gls{ris} is $\mathbf{\Theta}^\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
+		\begin{equation}
+			\mathbf{\Theta}^\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
+				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
+				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
+			\end{bmatrix}.
+		\end{equation}
+		When the direct link is absent, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
+		For a fair comparison, we enforce symmetry with $\beta = \pi / 2$.
+		\begin{figure}
+			\centering
+			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
+			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris}. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$. Direct link is absent.}
+			\label{sm:pc_singular_toy}
+		\end{figure}
+		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
+		Despite using the same number of elements and parameters, \gls{bd} \gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
+		Larger gaps are expected when the symmetry constraint can be relaxed.
+
+		We then analyze the channel shaping \emph{capability} of \gls{bd} \gls{ris} under specific setups.
+		\begin{subsubsection}{Rank-Deficient Channel}
+			\label{sc:pc_rank_deficient}
+			In rank-deficient channels, \gls{bd} \gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
+			This is because $\mathrm{sv}(\mathbf{\Theta}^\mathrm{B}) = \mathrm{sv}(\mathbf{\Theta}^\mathrm{D}) = \boldsymbol{1}$ and
+			\begin{equation}
+				\begin{split}
+					\mathrm{rank}(\mathbf{H})
+					& \le \mathrm{rank}(\mathbf{H}^\mathrm{D}) + \mathrm{rank}(\mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F}) \\
+					& \le \mathrm{rank}(\mathbf{H}^\mathrm{D}) + \min \bigl( \mathrm{rank}(\mathbf{H}^\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}), \mathrm{rank}(\mathbf{H}^\mathrm{F}) \bigr).
+				\end{split}
+			\end{equation}
+			% However, \gls{bd} \gls{ris} can still guarantee a higher rate at finite \gls{snr}.
+			Note \gls{bd} \gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Rank-1 Indirect Channel}
+			The indirect channel is rank-1 iff the forward or backward channel is rank-1.
+			Let $\mathbf{H}^\mathrm{F} = \sigma^\mathrm{F} \mathbf{u}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}$ without loss of generality.
+			In this case, the channel Gram matrix can be written as Hermitian-plus-rank-1:
+			\begin{equation}
+				\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
+			\end{equation}
+			where $\mathbf{Y} \triangleq \mathbf{H}^\mathrm{D} (\mathbf{I} - \mathbf{v}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}) \mathbf{H}^\mathrm{D} = \mathbf{T} \mathbf{T}^\mathsf{H}$ and $\mathbf{z} \triangleq \sigma^\mathrm{F} \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{u}^\mathrm{F} + \mathbf{H}^\mathrm{D} \mathbf{v}^\mathrm{F}$.
+			Regardless of \gls{ris} size and structure\footnote{A similar conclusion was made for diagonal \gls{ris} in \cite{Semmler2023}.}, its $n$-th ($n \ge 2$) eigenvalues are bounded by the Cauchy interlacing formula \cite{Golub2013}
+			\begin{equation}
+				\lambda_1(\mathbf{Y}) \ge {\color{blue}\lambda_2(\mathbf{G})} \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge {\color{blue}\lambda_N(\mathbf{G})} \ge \lambda_N(\mathbf{Y}).
+			\end{equation}
+			The equivalent singular value inequality is
+			\begin{equation}
+				\sigma_1(\mathbf{T}) \ge {\color{blue}\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\color{blue}\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
+				\label{iq:singular_value_interlacing}
+			\end{equation}
+			\eqref{iq:singular_value_interlacing} implies that, if the indirect channel is rank-1, then the \gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$.
+			Note that the largest channel singular value is unbounded with a sufficiently large \gls{ris}.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Fully-Connected \glsentryshort{ris} Without Direct Link}
+			Denote the singular value decomposition of forward / backward channels as $\mathbf{H}^{\mathrm{B}/\mathrm{F}} = \mathbf{U}^{\mathrm{B}/\mathrm{F}} \mathbf{\Sigma}^{\mathrm{B}/\mathrm{F}} {\mathbf{V}^{\mathrm{B}/\mathrm{F}}}^\mathsf{H}$.
+			The composite channel is
+			\begin{equation}
+				\mathbf{H} = \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F} = \mathbf{U}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{X} \mathbf{\Sigma}^\mathrm{F} {\mathbf{V}^\mathrm{F}}^\mathsf{H},
+			\end{equation}
+			where $\mathbf{X} = {\mathbf{V}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta} \mathbf{U}^\mathrm{F}$.
+			% Since unitary matrices are closed under multiplication,
+			\begin{proposition}
+				In this case, the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with singular values $\mathbf{\Sigma}^\mathrm{B}$ and $\mathbf{\Sigma}^\mathrm{F}$.
+				% The only singular value bounds applied here are those apply to the singular value bound of $\mathbf{F}\mathbf{B}$
+			\end{proposition}
+			\begin{proof}
+				We first observe that singular value control problem can be solved w.r.t.
+unitary $\mathbf{X}$ and retrieved by $\mathbf{\Theta} = \mathbf{V}^\mathrm{B} \mathbf{X} {\mathbf{U}^\mathrm{F}}^\mathsf{H}$.
+				Also, $\mathrm{sv}(\mathbf{U}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{X} \mathbf{\Sigma}^\mathrm{F} {\mathbf{V}^\mathrm{F}}^\mathsf{H}) = \mathrm{sv}(\bar{\mathbf{U}}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{\bar{V}}{{}^\mathrm{B}}^\mathsf{H} \bar{\mathbf{U}}^\mathrm{F} \mathbf{\Sigma}^\mathrm{F} \mathbf{\bar{V}}{{}^\mathrm{F}}^\mathsf{H}) = \mathrm{sv}(\mathbf{BF})$ where $\bar{\mathbf{U}}^{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}^{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
+			\end{proof}
+			The problem now becomes, given $\mathbf{\Sigma}^\mathrm{B}$ and $\mathbf{\Sigma}^\mathrm{F}$, what can we say about the singular value of $\mathbf{BF}$.
+			One comprehensive answer is Horn's inequality \cite{Bhatia2001}: for all admissible triples $(I, J, K)$,
+			\begin{equation}
+				\prod_{k \in {K}} \sigma_k(\mathbf{BF}) \leq \prod_{i \in {I}} \sigma_i(\mathbf{B}) \prod_{j \in {J}} \sigma_j(\mathbf{F}).
+			\end{equation}
+			It gives upper bound on the largest singular value and lower bound on the smallest singular value:
+			\begin{align}
+				\sigma_1(\mathbf{BF}) \le \sigma_1(\mathbf{B}) \sigma_1(\mathbf{F}) \label{iq:singular_value_largest}\\
+				\sigma_N(\mathbf{BF}) \geq \sigma_N(\mathbf{B}) \sigma_N(\mathbf{F}) \label{iq:singular_value_smallest}.
+			\end{align}
+			Another useful result is introduced in \cite{Hogben2013}: for all $p>0$,
+			\begin{equation}
+				\sum_n \sigma_n^p(\mathbf{BF}) \leq \sum_n \sigma_n^p(\mathbf{B}) \sigma_n^p(\mathbf{F}) \label{iq:singular_value_power_sum}.
+			\end{equation}
+			When $p=2$, it implies the channel energy is upper bounded by the sum of element-wise power product of the forward and backward channels, as illustrated in Fig.~\subref*{sm:pc_power_bond_nd}.
+			Interestingly, \eqref{iq:singular_value_largest}--\eqref{iq:singular_value_power_sum} are simultaneously tight when $\mathbf{X} = \mathbf{I}$ and $\mathbf{\Theta} = \mathbf{V}^\mathrm{B} {\mathbf{U}^\mathrm{F}}^\mathsf{H}$.
+			This solution was claimed in \cite{Bartoli2023} to achieve channel capacity, but it is not true at moderate \gls{snr}.
+		\end{subsubsection}
+
+		Finally, we characterize the \emph{Pareto frontier} of channel singular values via optimization approach.
+		% \begin{maxi!}
+		% 	{\scriptstyle{\mathbf{\Theta}}}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
+		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		% \end{maxi!}
+
+		\begin{customopti!}
+			{\underset{\scriptstyle{\mathbf{\Theta}}}{max / min}}{}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		\end{customopti!}
+
+		where $\rho_n$ is the weight of $n$-th singular value.
+		The complex derivative of \eqref{ob:pc_singular} w.r.t. \gls{ris} block $g$ is
+		\begin{equation}
+			\frac{\partial J_1}{\partial \mathbf{\Theta}_g^*} = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{U} \mathrm{diag}(\boldsymbol{\rho}) \mathbf{V}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H},
+			\label{eq:pc_singular_gradient_ris}
+		\end{equation}
+		where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{H}$.
+		\eqref{op:pc_singular} can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:pc_singular_gradient_ris}.
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/pc_singular_pareto.tex}
+			}
+			\caption{Singular value Pareto frontier. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 64, 2)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
+			\label{sm:pc_singular_pareto}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/simulation/pc_singular_bound.tex}
+			}
+			\caption{Singular value bounds for rank-1 indirect channel.
+$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
+			\label{sm:pc_singular_bound}
+		\end{figure}
+
+		The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
+		Clearly, \gls{bd} \gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
+	\end{subsection}
 	\begin{subsection}{Channel Power Maximization}
@@
 
-	\begin{subsection}{Channel Singular Value Redistribution}
-		We first show the channel shaping benefit of \gls{bd} \gls{ris} by a toy example.
-		Consider $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
-		The diagonal \gls{ris} is $\mathbf{\Theta}^\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
-		\begin{equation}
-			\mathbf{\Theta}^\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
-				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
-				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
-			\end{bmatrix}.
-		\end{equation}
-		When the direct link is absent, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		For a fair comparison, we enforce symmetry with $\beta = \pi / 2$.
-		\begin{figure}
-			\centering
-			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
-			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris}. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$. Direct link is absent.}
-			\label{sm:pc_singular_toy}
-		\end{figure}
-		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
-		Despite using the same number of elements and parameters, \gls{bd} \gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
-		Larger gaps are expected when the symmetry constraint can be relaxed.
-
-		We then analyze the channel shaping \emph{capability} of \gls{bd} \gls{ris} under specific setups.
-		\begin{subsubsection}{Rank-Deficient Channel}
-			\label{sc:pc_rank_deficient}
-			In rank-deficient channels, \gls{bd} \gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
-			This is because $\mathrm{sv}(\mathbf{\Theta}^\mathrm{B}) = \mathrm{sv}(\mathbf{\Theta}^\mathrm{D}) = \boldsymbol{1}$ and
-			\begin{equation}
-				\begin{split}
-					\mathrm{rank}(\mathbf{H})
-					& \le \mathrm{rank}(\mathbf{H}^\mathrm{D}) + \mathrm{rank}(\mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F}) \\
-					& \le \mathrm{rank}(\mathbf{H}^\mathrm{D}) + \min \bigl( \mathrm{rank}(\mathbf{H}^\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}), \mathrm{rank}(\mathbf{H}^\mathrm{F}) \bigr).
-				\end{split}
-			\end{equation}
-			% However, \gls{bd} \gls{ris} can still guarantee a higher rate at finite \gls{snr}.
-			Note \gls{bd} \gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Rank-1 Indirect Channel}
-			The indirect channel is rank-1 iff the forward or backward channel is rank-1.
-			Let $\mathbf{H}^\mathrm{F} = \sigma^\mathrm{F} \mathbf{u}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}$ without loss of generality.
-			In this case, the channel Gram matrix can be written as Hermitian-plus-rank-1:
-			\begin{equation}
-				\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{Y} \triangleq \mathbf{H}^\mathrm{D} (\mathbf{I} - \mathbf{v}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}) \mathbf{H}^\mathrm{D} = \mathbf{T} \mathbf{T}^\mathsf{H}$ and $\mathbf{z} \triangleq \sigma^\mathrm{F} \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{u}^\mathrm{F} + \mathbf{H}^\mathrm{D} \mathbf{v}^\mathrm{F}$.
-			Regardless of \gls{ris} size and structure\footnote{A similar conclusion was made for diagonal \gls{ris} in \cite{Semmler2023}.}, its $n$-th ($n \ge 2$) eigenvalues are bounded by the Cauchy interlacing formula \cite{Golub2013}
-			\begin{equation}
-				\lambda_1(\mathbf{Y}) \ge {\color{blue}\lambda_2(\mathbf{G})} \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge {\color{blue}\lambda_N(\mathbf{G})} \ge \lambda_N(\mathbf{Y}).
-			\end{equation}
-			The equivalent singular value inequality is
-			\begin{equation}
-				\sigma_1(\mathbf{T}) \ge {\color{blue}\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\color{blue}\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
-				\label{iq:singular_value_interlacing}
-			\end{equation}
-			\eqref{iq:singular_value_interlacing} implies that, if the indirect channel is rank-1, then the \gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$.
-			Note that the largest channel singular value is unbounded with a sufficiently large \gls{ris}.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Fully-Connected \glsentryshort{ris} Without Direct Link}
-			Denote the singular value decomposition of forward / backward channels as $\mathbf{H}^{\mathrm{B}/\mathrm{F}} = \mathbf{U}^{\mathrm{B}/\mathrm{F}} \mathbf{\Sigma}^{\mathrm{B}/\mathrm{F}} {\mathbf{V}^{\mathrm{B}/\mathrm{F}}}^\mathsf{H}$.
-			The composite channel is
-			\begin{equation}
-				\mathbf{H} = \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F} = \mathbf{U}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{X} \mathbf{\Sigma}^\mathrm{F} {\mathbf{V}^\mathrm{F}}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{X} = {\mathbf{V}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta} \mathbf{U}^\mathrm{F}$.
-			% Since unitary matrices are closed under multiplication,
-			\begin{proposition}
-				In this case, the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with singular values $\mathbf{\Sigma}^\mathrm{B}$ and $\mathbf{\Sigma}^\mathrm{F}$.
-				% The only singular value bounds applied here are those apply to the singular value bound of $\mathbf{F}\mathbf{B}$
-			\end{proposition}
-			\begin{proof}
-				We first observe that singular value control problem can be solved w.r.t.
-unitary $\mathbf{X}$ and retrieved by $\mathbf{\Theta} = \mathbf{V}^\mathrm{B} \mathbf{X} {\mathbf{U}^\mathrm{F}}^\mathsf{H}$.
-				Also, $\mathrm{sv}(\mathbf{U}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{X} \mathbf{\Sigma}^\mathrm{F} {\mathbf{V}^\mathrm{F}}^\mathsf{H}) = \mathrm{sv}(\bar{\mathbf{U}}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{\bar{V}}{{}^\mathrm{B}}^\mathsf{H} \bar{\mathbf{U}}^\mathrm{F} \mathbf{\Sigma}^\mathrm{F} \mathbf{\bar{V}}{{}^\mathrm{F}}^\mathsf{H}) = \mathrm{sv}(\mathbf{BF})$ where $\bar{\mathbf{U}}^{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}^{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
-			\end{proof}
-			The problem now becomes, given $\mathbf{\Sigma}^\mathrm{B}$ and $\mathbf{\Sigma}^\mathrm{F}$, what can we say about the singular value of $\mathbf{BF}$.
-			One comprehensive answer is Horn's inequality \cite{Bhatia2001}: for all admissible triples $(I, J, K)$,
-			\begin{equation}
-				\prod_{k \in {K}} \sigma_k(\mathbf{BF}) \leq \prod_{i \in {I}} \sigma_i(\mathbf{B}) \prod_{j \in {J}} \sigma_j(\mathbf{F}).
-			\end{equation}
-			It gives upper bound on the largest singular value and lower bound on the smallest singular value:
-			\begin{align}
-				\sigma_1(\mathbf{BF}) \le \sigma_1(\mathbf{B}) \sigma_1(\mathbf{F}) \label{iq:singular_value_largest}\\
-				\sigma_N(\mathbf{BF}) \geq \sigma_N(\mathbf{B}) \sigma_N(\mathbf{F}) \label{iq:singular_value_smallest}.
-			\end{align}
-			Another useful result is introduced in \cite{Hogben2013}: for all $p>0$,
-			\begin{equation}
-				\sum_n \sigma_n^p(\mathbf{BF}) \leq \sum_n \sigma_n^p(\mathbf{B}) \sigma_n^p(\mathbf{F}) \label{iq:singular_value_power_sum}.
-			\end{equation}
-			When $p=2$, it implies the channel energy is upper bounded by the sum of element-wise power product of the forward and backward channels, as illustrated in Fig.~\subref*{sm:pc_power_bond_nd}.
-			Interestingly, \eqref{iq:singular_value_largest}--\eqref{iq:singular_value_power_sum} are simultaneously tight when $\mathbf{X} = \mathbf{I}$ and $\mathbf{\Theta} = \mathbf{V}^\mathrm{B} {\mathbf{U}^\mathrm{F}}^\mathsf{H}$.
-			This solution was claimed in \cite{Bartoli2023} to achieve channel capacity, but it is not true at moderate \gls{snr}.
-		\end{subsubsection}
-
-		Finally, we characterize the \emph{Pareto front} of channel singular values via optimization approach.
-		% \begin{maxi!}
-		% 	{\scriptstyle{\mathbf{\Theta}}}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
-		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		% \end{maxi!}
-
-		\begin{customopti!}
-			{\underset{\scriptstyle{\mathbf{\Theta}}}{max / min}}{}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		\end{customopti!}
-
-		where $\rho_n$ is the weight of $n$-th singular value.
-		The complex derivative of \eqref{ob:pc_singular} w.r.t. \gls{ris} block $g$ is
-		\begin{equation}
-			\frac{\partial J_1}{\partial \mathbf{\Theta}_g^*} = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{U} \mathrm{diag}(\boldsymbol{\rho}) \mathbf{V}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H},
-			\label{eq:pc_singular_gradient_ris}
-		\end{equation}
-		where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{H}$.
-		\eqref{op:pc_singular} can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:pc_singular_gradient_ris}.
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/pc_singular_pareto.tex}
-			}
-			\caption{Singular value Pareto front. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 64, 2)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-			\label{sm:pc_singular_pareto}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/pc_singular_bound.tex}
-			}
-			\caption{Singular value bounds for rank-1 indirect channel.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-			\label{sm:pc_singular_bound}
-		\end{figure}
-
-		The Pareto front and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
-		Clearly, \gls{bd} \gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
-	\end{subsection}
 \end{section}

### 2024-01-10 main.tex
:pencil: Update contributions

@@
 \newacronym{wsr}{WSR}{Weighted Sum-Rate}
+\newacronym{svd}{SVD}{Singular Value Decomposition}
 \newacronym{mmse}{MMSE}{Minimum Mean-Square Error}
@@
 	% , accounting for a diagonal phase shift model with unit magnitude.
-	The idea is extended to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} featuring in-group connections between elements.
+	The concept is generalized to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} featuring in-group connections between elements.
 	This allows \emph{cooperative} reflection --- wave impinging on one element can propagate within the circuit and depart partially from all elements.
@@
 	The latter has been studied in terms of channel power \cite{Wu2019} in \gls{pc} and leakage interference \cite{Santamaria2023a} in \gls{ic}.
-	When it comes to \gls{bd} \gls{ris}, the only metric analyzed is the channel power \cite{Nerini2023,Santamaria2023} while the \gls{mimo} case is still unexplored.\footnote{Single-stream \gls{mimo} with given precoder and combiner was considered in \cite{Nerini2023}.
+	For \gls{bd} \gls{ris}, the only metric analyzed is the channel power \cite{Nerini2023,Santamaria2023} while the \gls{mimo} case is still unexplored.\footnote{Single-stream \gls{mimo} with given precoder and combiner was considered in \cite{Nerini2023}.
 In terms of channel shaping, it is equivalent to \gls{siso}.}
-	Although insightful, those attempts are far from complete and the methods are limited to specific scenarios.
-	% This paper aims to quantify the channel shaping capability of asymmetric \gls{bd} \gls{ris} through theoretical analysis and numerical evaluation.
+	Although insightful, those attempts are far from complete and the techniques are limited to specific scenarios.
 	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
-	% quantify the channel shaping capability of asymmetric \gls{bd} \gls{ris} through theoretical analysis and numerical evaluation.
 	The contributions are summarized below.
@@
 	It generalizes all singular value metrics and provides a powerful design framework.
-	We then discuss analytical singular value bounds under rank-deficient and no-direct scenarios.
+	We then discuss some analytical singular value bounds under rank-deficient and no-direct scenarios.
 
@@
 
-	Second, we tailor a \gls{rcg} algorithm for asymmetric\footnote{Although the constraint of symmetric scattering parameters is widely respected in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, it can be relaxed when the \gls{bd} \gls{ris} involves asymmetric passive components \cite{Ahn2006}, as previously assumed in \cite{Li2023b,Li2023c}.
+	Second, we tailor a \gls{rcg} algorithm for asymmetric\footnote{Although the constraint of symmetric scattering parameters is widely respected in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, it can be relaxed when the \gls{bd} \gls{ris} involves asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, as previously assumed in \cite{Li2023b,Li2023c}.
 Symmetry can be enforced by projection if necessary.} \gls{bd} \gls{ris} optimization.
@@
 	The proposed method not only features lower complexity and faster convergence than universal manifold optimization \cite{Absil2009,Pan2022d}, but also applies to any \gls{bd} \gls{ris} problem where gradient exists.
-	% It is used to solve the Pareto singular problem, as well as rate maximization in \gls{mimo} \gls{pc} and \gls{wsr} maximization in \gls{mimo} \gls{ic}.
-	% It effectively solves the Pareto singular problem.
+	It effectively solves the Pareto singular problem.
 
-	% , as well as rate maximization in \gls{mimo} \gls{pc} and \gls{wsr} maximization in \gls{mimo} \gls{ic}.
+	Third, we propose a closed-form iterative algorithm for power centric channel shaping problems.
+	The idea is to successively approximate the quadratic objective by a sequence of affines and solve the local problems by \gls{svd}.
+	Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.
 
-	% It helps to solve the aforementioned Pareto singular value problem.
-	% We exploit it to solve the Pareto singular value problem and
-
-	% It is exploited for the Pareto singular value problem, as well as rate maximization in \gls{mimo} \gls{pc} and \gls{wsr} maximization in \gls{mimo} \gls{ic}.
-	% It is used to solve the Pareto singular value problem,
-
-	Third, we consider power centric design
-	% Second, we consider power centric design
-	% exploit \gls{bd} \gls{ris} to power centric
-	% maximize channel power in \gls{mimo} \gls{pc} and minimize leakage interference in \gls{mimo} \gls{ic}.
-
+	Fourth, we perform extensive simulations to validate and quantify the signal processing advantage of \gls{bd} \gls{ris}.
+	Besides channel shaping, we also consider typical joint active and passive beamforming problems, including rate maximization in \gls{pc} and \gls{wsr} maximization in \gls{ic}.
+	Results suggest that \gls{bd} \gls{ris} achieves a larger array gain in \gls{pc} and a higher \gls{dof} in \gls{ic}.
 \end{section}
 
-\begin{section}{Assumption}
-	We introduce \gls{bd} \gls{ris} in \gls{mimo} \gls{pc} and \gls{ic}.
-	% point-to-point and interference \gls{mimo} channels.
-	All proposals are based on assumption of \emph{asymmetric} passive \gls{bd} \gls{ris}, i.e., symmetry constraint $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T}$ is relaxed.
-	This is feasible when asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} are available.
-	This assumption was also made in Hongyu's papers \cite{Li2023b,Li2023c}.
-	For quadratic problems, the proposed algorithms may be extended to symmetric \gls{bd} \gls{ris} by replacing singular value decomposition with Takagi factorization \cite{Horn2012}.
-\end{section}
+% \begin{section}{Assumption}
+% 	We introduce \gls{bd} \gls{ris} in \gls{mimo} \gls{pc} and \gls{ic}.
+% 	% point-to-point and interference \gls{mimo} channels.
+% 	All proposals are based on assumption of \emph{asymmetric} passive \gls{bd} \gls{ris}, i.e., symmetry constraint $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T}$ is relaxed.
+% 	This is feasible when asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} are available.
+% 	This assumption was also made in Hongyu's papers \cite{Li2023b,Li2023c}.
+% 	For quadratic problems, the proposed algorithms may be extended to symmetric \gls{bd} \gls{ris} by replacing singular value decomposition with Takagi factorization \cite{Horn2012}.
+% \end{section}
 

### 2024-01-18 src/lib/precoder_rate_ic_bisection.m
:construction: Update Pareto singular front

@@ -1,52 +1,0 @@
-function [W] = precoder_rate_ic_bisection(H, W, P_t, P_n, rho)
-	[N_r, N_t, N_e, K] = deal(size(H, 1), size(H, 2), size(W, 2), size(W, 4));
-	[iter.converge, iter.tolerance, iter.counter] = deal(false, 1e-3, 0);
-	iter.J = rho' * rate_mimo(H, W, P_n);
-	while ~iter.converge
-		T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
-		Q = sum(T, 4) - T(:, :, logical(eye(K))) + P_n * eye(N_r);
-		F = pagemtimes(H(:, :, logical(eye(K))), pageswap(W));
-		G = pagemrdivide(pagectranspose(F), Q + T(:, :, logical(eye(K))));
-		V = shiftdim(rho, -2) .* pagehermitize(eye(N_e) + pagemtimes(pagemrdivide(pagectranspose(F), Q), F));
-		Y = pagemtimes(pagemtimes(pagemtimes(G, H), 'ctranspose', V, 'none'), pagemtimes(G, H));
-		for k = 1 : K
-			fun = @(lambda) norm(mldivide(sum(Y(:, :, :, k), 3) + lambda * eye(N_t), H(:, :, k, k)' * G(:, :, k)' * V(:, :, k)), 'fro') ^ 2 - P_t;
-			[lb, ub] = deal(0, 1e3);
-			if fun(lb) * fun(ub) < 0
-				lambda = bisection(fun, lb, ub);
-			else
-				lambda = 0;
-			end
-			W(:, :, :, k) = mldivide(sum(Y(:, :, :, k), 3) + lambda * eye(N_t), H(:, :, k, k)' * G(:, :, k)' * V(:, :, k));
-		end
-		J = rho' * rate_mimo(H, W, P_n);
-		iter.converge = (abs(J - iter.J) / iter.J <= iter.tolerance) && all(abs(pagenorm(W, 'fro') .^ 2 - P_t) ./ P_t < iter.tolerance | abs(pagenorm(W, 'fro') .^ 2) < iter.tolerance);
-		iter.J = J;
-		iter.counter = iter.counter + 1;
-	end
-end
-
-function [A] = pageswap(A)
-	A = permute(A, [1, 2, 4, 3]);
-end
-
-function [A] = pagehermitize(A)
[…]

### 2024-01-18 src/lib/scatter_singular_pc.m

@@ -1,8 +1,14 @@
-function [Theta, H] = scatter_singular_max_pc(H_d, H_f, H_b, rho, L)
+function [Theta, H] = scatter_singular_pc(H_d, H_f, H_b, rho, L)
 	persistent iter;
 	if isempty(iter)
-		clear scatter_power_max_pc;
-		Theta = scatter_power_max_pc(H_d, H_f, H_b, L);
+		clear scatter_power_max_pc scatter_power_min_pc;
+		if all(rho >= 0)
+			Theta = scatter_power_max_pc(H_d, H_f, H_b, L);
+		elseif all(rho <= 0)
+			Theta = scatter_power_min_pc(H_d, H_f, H_b, L);
+		else
+			Theta = eye(size(H_f, 1));
+		end
 	else
 		Theta = iter.Theta;
 	end
@@ -10,7 +16,7 @@ function [Theta, H] = scatter_singular_max_pc(H_d, H_f, H_b, rho, L)
 	G = length(Theta) / L;
 	H = channel_aggregate(H_d, H_f, H_b, Theta);
 	[G_e, G_r, D] = deal(zeros(size(Theta)));
-	[iter.converge, iter.tolerance, iter.counter, iter.J] = deal(false, 1e-4, 0, rho' * svd(H));
+	[iter.converge, iter.tolerance, iter.counter, iter.J] = deal(false, 1e-9, 0, rho' * svd(H));
 	while ~iter.converge
 		[iter.G_r, iter.D] = deal(G_r, D);
 		for g = 1 : G

### 2024-01-22 main.tex
:pencil: Add sidenote
:construction: Update Pareto singular front
:pencil: Update abstract

@@
 \newacronym{mse}{MSE}{Mean-Square Error}
+\newacronym{los}{LoS}{Line-of-Sight}
 
@@
 \begin{abstract}
-	\gls{ris} recycles and redistributes ambient waves for improved wireless performance.
-	% \gls{ris} is a promising technology that recycles and redistributes ambient waves for improved wireless performance.
-	% \gls{ris} is a real-time programmable reflector that recycles and redistributes ambient waves for improved wireless performance.
-	This paper investigates the use of passive \gls{ris} for channel shaping in \gls{mimo} \gls{pc} and \gls{ic}.
-	We depart from the widely-adapted diagonal phase shift model and focus on a general asymmetric \gls{bd} architecture, which allows off-diagonal entries by in-group connections between elements.
-	For arbitrary group size, we propose a closed-form iterative algorithm for quadratic problems and a \gls{rcg} algorithm for general problems.
-	Various case studies are then conducted, including Pareto singular value characterization and rate maximization for \gls{pc}, and interference alignment and \gls{wsr} maximization for \gls{ic}.
-	To quantify channel shaping capability, we also derive analytical bounds under specific scenarios and validate those by aforementioned methods.
-	Simulation results suggest the advantage of \gls{bd} \gls{ris} scales with group size, while dyadic or tetradic architecture usually strikes a good balance between performance and complexity.
-	% Through theoretical analysis and numerical evaluation,
-	Our findings unlock unprecedented efficiency and adaptability, paving the way for smarter and greener wireless environments.
-	% truly programmable
-	% useful guidelines for prototype design.
+	This paper investigates how a passive \gls{ris} can shape the \gls{mimo} point-to-point channel in terms of singular values.
+	We depart from the widely-adapted diagonal phase shift model to a general \gls{bd} architecture, which provides superior shaping capability thanks to in-group connections between elements.
+	An efficient \gls{rcg} algorithm is tailored for smooth optimization problems of asymmetric \gls{bd} \gls{ris} with arbitrary group size, then invoked for the Pareto frontier of channel singular values.
+	To understand the gain from off-diagonal entries, we also derive analytical singular value bounds in \gls{los} and fully-connected scenarios.
+	As a side product, we tackle \gls{mimo} rate maximization problem by alternating between active beamformer (eigenmode transmission) and passive beamformer (\gls{rcg} algorithm) until convergence.
+	A low-complexity suboptimal solution that decouples both blocks is also proposed, where the channel shaping subproblem is formulated as power maximization and solved iteratively in closed form.
+	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd} \gls{ris} increases with group size and stems from subchannel rearrangement and subspace alignment.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Reconfigurable intelligent surface, channel shaping, point-to-point channel, interference channel.
+	Reconfigurable intelligent surface, multi-input multi-output, manifold optimization, singular value control, rate maximization.
 \end{IEEEkeywords}
@@
 	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	Today we are witnessing a paradigm shift from {connectivity} to {intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
-	This is made possible by the recent advances in \gls{ris}, a real-time programmable metasurface made of numerous non-resonant sub-wavelength scattering elements.
-	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than conventional relays.
-	Using \gls{ris} for \emph{passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
-	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
-	Although fruitful outcomes have been harvested over optimization tools, one fundamental yet critical question is the \emph{channel shaping} capability: To what extent can a passive \gls{ris} reshape the wireless channel?
+	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
+	This is empowered by the recent advances in \gls{ris}, a real-time programmable metasurface of numerous non-resonant sub-wavelength scattering elements.
+	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than relays.
+	Using \gls{ris} for {passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
+	On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
+	Although fruitful outcomes have been harvested, one fundamental unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
+
 	The answer indeed depends on the hardware architecture and scattering model.
-
-	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and functions as an \emph{individual} phase shifter \cite{Wu2020}.
-	% , accounting for a diagonal phase shift model with unit magnitude.
-	The concept is generalized to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} featuring in-group connections between elements.
-	This allows \emph{cooperative} reflection --- wave impinging on one element can propagate within the circuit and depart partially from all elements.
+	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
+	% The concept is generalized to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} featuring in-group connections between elements.
+	The concept is generalized to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} that connects adjacent elements as a group using passive components.
+	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any elements in the same group.
 	\gls{bd} \gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
@@
 % \end{section}
+
+% ! Evaluate the rate performance of RIS that maximizes channel power (should coincide at low and high snr)
 

### 2024-01-23 main.tex
:pencil: Update background

@@
 \begin{abstract}
-	This paper investigates how a passive \gls{ris} can shape the \gls{mimo} point-to-point channel in terms of singular values.
+	This paper investigates how a passive \gls{ris} can reshape the \gls{mimo} point-to-point channel in terms of singular values.
 	We depart from the widely-adapted diagonal phase shift model to a general \gls{bd} architecture, which provides superior shaping capability thanks to in-group connections between elements.
@@
 	As a side product, we tackle \gls{mimo} rate maximization problem by alternating between active beamformer (eigenmode transmission) and passive beamformer (\gls{rcg} algorithm) until convergence.
-	A low-complexity suboptimal solution that decouples both blocks is also proposed, where the channel shaping subproblem is formulated as power maximization and solved iteratively in closed form.
-	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd} \gls{ris} increases with group size and stems from subchannel rearrangement and subspace alignment.
+	A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved iteratively in closed form.
+	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd} \gls{ris} increases with group size and stems from stronger subchannel rearrangement and subspace alignment capabilities.
 \end{abstract}
@@
 	On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
-	Although fruitful outcomes have been harvested, one fundamental unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
+	Despite fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
 
@@
 	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
-	% The concept is generalized to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} featuring in-group connections between elements.
-	The concept is generalized to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} that connects adjacent elements as a group using passive components.
-	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any elements in the same group.
+	The concept is generalized to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} which groups adjacent elements using passive components.
+	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
 	\gls{bd} \gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
 	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
-	The channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} issues have also been investigated.
+	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
 	Therefore, \gls{bd} \gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
@@
 	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
-	Channel shaping metrics can be classified into \emph{singular value centric} and \emph{power centric}.
-	For diagonal \gls{ris}, the former has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023} in \gls{pc}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023} in \gls{ic}.
-	The latter has been studied in terms of channel power \cite{Wu2019} in \gls{pc} and leakage interference \cite{Santamaria2023a} in \gls{ic}.
-	For \gls{bd} \gls{ris}, the only metric analyzed is the channel power \cite{Nerini2023,Santamaria2023} while the \gls{mimo} case is still unexplored.\footnote{Single-stream \gls{mimo} with given precoder and combiner was considered in \cite{Nerini2023}.
-In terms of channel shaping, it is equivalent to \gls{siso}.}
-	Although insightful, those attempts are far from complete and the techniques are limited to specific scenarios.
-	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
+	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
+	Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself.
+	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of channel manipulation.
+	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
+	On the other hand, \gls{bd} \gls{ris} can provide a higher channel power but the results are limited to \gls{siso} \cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
+	While these studies offer promising glimpses into the channel shaping potential of passive \gls{ris}, a comprehensive understanding of its capabilities and limitations is desired, and a universal design framework is still missing.
+	% \footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
+	% Although insightful, those attempts are far from complete and the techniques are limited to specific scenarios.
+	This paper aims to answer the channel shaping question through theoretical analysis and numerical optimization.
 	The contributions are summarized below.

### 2024-01-24 main.tex
:pencil: Update contribution 1-3

@@
 	We depart from the widely-adapted diagonal phase shift model to a general \gls{bd} architecture, which provides superior shaping capability thanks to in-group connections between elements.
-	An efficient \gls{rcg} algorithm is tailored for smooth optimization problems of asymmetric \gls{bd} \gls{ris} with arbitrary group size, then invoked for the Pareto frontier of channel singular values.
+	An efficient \gls{rcg} algorithm is tailored for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size, then invoked for the Pareto frontier of channel singular values.
 	To understand the gain from off-diagonal entries, we also derive analytical singular value bounds in \gls{los} and fully-connected scenarios.
 	As a side product, we tackle \gls{mimo} rate maximization problem by alternating between active beamformer (eigenmode transmission) and passive beamformer (\gls{rcg} algorithm) until convergence.
-	A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved iteratively in closed form.
-	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd} \gls{ris} increases with group size and stems from stronger subchannel rearrangement and subspace alignment capabilities.
+	A low-complexity suboptimal solution based on channel shaping is also proposed, where the decoupled problem is formulated as channel power maximization and solved iteratively in closed form.
+	% We then show how channel shaping decouples the design and amounts to a low-complexity suboptimal solution.
+	% A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved iteratively in closed form.
+	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and stems from stronger subchannel rearrangement and subspace alignment capabilities.
 \end{abstract}
@@
 	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
-	The concept is generalized to \gls{bd} \gls{ris} \cite{Shen2020a,Li2023b} which groups adjacent elements using passive components.
+	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which groups adjacent elements using passive components.
 	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
-	\gls{bd} \gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
+	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
 	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
 	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
-	Therefore, \gls{bd} \gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
+	Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
 
@@
 	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
-	On the other hand, \gls{bd} \gls{ris} can provide a higher channel power but the results are limited to \gls{siso} \cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
-	While these studies offer promising glimpses into the channel shaping potential of passive \gls{ris}, a comprehensive understanding of its capabilities and limitations is desired, and a universal design framework is still missing.
-	% \footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
-	% Although insightful, those attempts are far from complete and the techniques are limited to specific scenarios.
+	In contrast, \gls{bd}-\gls{ris} provides a higher channel power but the results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
+\cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
+	While these studies offer promising glimpses into the channel shaping potential of passive \gls{ris}, a comprehensive understanding of its capabilities and limitations is desired, and a universal design framework is missing.
 	This paper aims to answer the channel shaping question through theoretical analysis and numerical optimization.
@@
 
-	First, we examine the capability of \gls{bd} \gls{ris} to redistribute the channel singular values in \gls{mimo} \gls{pc}.
+	First, we quantify the capability of \gls{bd}-\gls{ris} to manipulate the channel singular values in \gls{mimo} point-to-point channel.
 	The Pareto frontiers are characterized by optimizing the \emph{weighted sum of singular values}, where the weights can be positive, zero, or negative.
-	It generalizes all singular value metrics and provides a powerful design framework.
-	We then discuss some analytical singular value bounds under rank-deficient and no-direct scenarios.
+	% This generalizes most singular value metrics and provides a powerful design framework.
+	The resulting region provides a comprehensive and intuitive channel shaping benchmark in terms of singular values.
+	We then discuss some analytical singular value bounds in \gls{los} and fully-connected scenarios.
+	This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
 
-	% and demonstrate the channel shaping advantage of \gls{bd} \gls{ris} over diagonal \gls{ris}.
+	% and the first to analytically characterize the singular value bounds of \gls{bd}-\gls{ris}.
+	% characterize the Pareto frontier of channel singular values in the presence of \gls{ris}.
 
-	Second, we tailor a \gls{rcg} algorithm for asymmetric\footnote{Although the constraint of symmetric scattering parameters is widely respected in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, it can be relaxed when the \gls{bd} \gls{ris} involves asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, as previously assumed in \cite{Li2023b,Li2023c}.
-Symmetry can be enforced by projection if necessary.} \gls{bd} \gls{ris} optimization.
-	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold and concisely evaluated as matrix exponential.
-	The proposed method not only features lower complexity and faster convergence than universal manifold optimization \cite{Absil2009,Pan2022d}, but also applies to any \gls{bd} \gls{ris} problem where gradient exists.
-	It effectively solves the Pareto singular problem.
+	Second, we propose a \gls{rcg} algorithm for smooth optimization problems of asymmetric\footnote{Although the constraint of symmetric scattering parameters is widely respected in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, it can be relaxed when the \gls{bd}-\gls{ris} involves asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.
+This assumption has been previously adopted in \cite{Li2023b,Li2023c} and symmetry can be enforced on solutions by projection if necessary.} \gls{bd}-\gls{ris} with arbitrary group size.
+	Specifically, blockwise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold and evaluated compactly as matrix exponential.
+	% The proposed method not only features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, but also applies to any \gls{bd}-\gls{ris} problem where gradient exists.
+	The proposed method features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, which effectively addresses the Pareto singular value problem.
+	This is the first paper to tailor an efficient optimization framework that unleashes the design potential of asymmetric \gls{bd}-\gls{ris}.
 
-	Third, we propose a closed-form iterative algorithm for power centric channel shaping problems.
-	The idea is to successively approximate the quadratic objective by a sequence of affines and solve the local problems by \gls{svd}.
-	Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.
+	Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: an optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
+	The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
+	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
+	We then highlight the corresponding channel singular values on the Pareto frontier and compare with analytical bounds.
 
-	Fourth, we perform extensive simulations to validate and quantify the signal processing advantage of \gls{bd} \gls{ris}.
+	% Third, we propose a closed-form iterative algorithm for power centric channel shaping problems.
+	% The idea is to successively approximate the quadratic objective by a sequence of affines and solve the local problems by \gls{svd}.
+	% Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.
+
+	Fourth, we perform extensive simulations to validate and quantify the signal processing advantage of \gls{bd}-\gls{ris}.
 	Besides channel shaping, we also consider typical joint active and passive beamforming problems, including rate maximization in \gls{pc} and \gls{wsr} maximization in \gls{ic}.
-	Results suggest that \gls{bd} \gls{ris} achieves a larger array gain in \gls{pc} and a higher \gls{dof} in \gls{ic}.
+	Results suggest that \gls{bd}-\gls{ris} achieves a larger array gain in \gls{pc} and a higher \gls{dof} in \gls{ic}.
+	We discover that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and stems from stronger subchannel rearrangement and subspace alignment capabilities.
 \end{section}
-
-% \begin{section}{Assumption}
-% 	We introduce \gls{bd} \gls{ris} in \gls{mimo} \gls{pc} and \gls{ic}.
-% 	% point-to-point and interference \gls{mimo} channels.
-% 	All proposals are based on assumption of \emph{asymmetric} passive \gls{bd} \gls{ris}, i.e., symmetry constraint $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T}$ is relaxed.
-% 	This is feasible when asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} are available.
-% 	This assumption was also made in Hongyu's papers \cite{Li2023b,Li2023c}.
-% 	For quadratic problems, the proposed algorithms may be extended to symmetric \gls{bd} \gls{ris} by replacing singular value decomposition with Takagi factorization \cite{Horn2012}.
-% \end{section}
 
@@
 	\begin{subsection}{Channel Singular Value Redistribution}
-		We first show the channel shaping benefit of \gls{bd} \gls{ris} by a toy example.
+		We first show the channel shaping benefit of \gls{bd}-\gls{ris} by a toy example.
 		Consider $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
@@
 		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
-		Despite using the same number of elements and parameters, \gls{bd} \gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
+		Despite using the same number of elements and parameters, \gls{bd}-\gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
 		Larger gaps are expected when the symmetry constraint can be relaxed.
 
-		We then analyze the channel shaping \emph{capability} of \gls{bd} \gls{ris} under specific setups.
+		We then analyze the channel shaping \emph{capability} of \gls{bd}-\gls{ris} under specific setups.
 		\begin{subsubsection}{Rank-Deficient Channel}
 			\label{sc:pc_rank_deficient}
-			In rank-deficient channels, \gls{bd} \gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
+			In rank-deficient channels, \gls{bd}-\gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
 			This is because $\mathrm{sv}(\mathbf{\Theta}^\mathrm{B}) = \mathrm{sv}(\mathbf{\Theta}^\mathrm{D}) = \boldsymbol{1}$ and
@@
 			\end{equation}
-			% However, \gls{bd} \gls{ris} can still guarantee a higher rate at finite \gls{snr}.
-			Note \gls{bd} \gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
+			% However, \gls{bd}-\gls{ris} can still guarantee a higher rate at finite \gls{snr}.
+			Note \gls{bd}-\gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
 		\end{subsubsection}
@@
 		The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
-		Clearly, \gls{bd} \gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
+		Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
 	\end{subsection}
 	\begin{subsection}{Channel Power Maximization}
-		Consider a \gls{bd} \gls{ris} with $N^\mathrm{S}$ elements, which is divided into $G$ groups of equal $L$ elements.
+		Consider a \gls{bd}-\gls{ris} with $N^\mathrm{S}$ elements, which is divided into $G$ groups of equal $L$ elements.
 		\begin{maxi!}
@@
 		For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
-		% \gls{bd} \gls{ris} provides a higher channel power than conventional \gls{ris}.
+		% \gls{bd}-\gls{ris} provides a higher channel power than conventional \gls{ris}.
 		% As $L$ increases from 1 to 2,
-		It implies that the channel shaping capability of \gls{bd} \gls{ris} scales with group size $L$.
+		It implies that the channel shaping capability of \gls{bd}-\gls{ris} scales with group size $L$.
 
@@
 		When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
-		When the direct link is present, the proposed \gls{bd} \gls{ris} design can balance the direct-indirect and forward-backward eigenspace alignment for an optimal channel boost.
+		When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward eigenspace alignment for an optimal channel boost.
 		It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
-		This again emphasizes the advantage of in-group connection of \gls{bd} \gls{ris}.
+		This again emphasizes the advantage of in-group connection of \gls{bd}-\gls{ris}.
 		% This is because the direct and indirect channels superpose
-		% the proposed \gls{bd} \gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
+		% the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
 		% When the direct link is present, a small $L$ cannot align the direct-indirect eigenspace.
@@
 		This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
-		If tetrads can be formed in \gls{bd} \gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
+		If tetrads can be formed in \gls{bd}-\gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
 		Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
-		We thus conclude dyadic or tetradic \gls{bd} \gls{ris} usually strike a good balance between performance and complexity.
+		We thus conclude dyadic or tetradic \gls{bd}-\gls{ris} usually strike a good balance between performance and complexity.
 	\end{subsection}
@@
 		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_k\}$ are determined, we define $\bar{\mathbf{H}}_{kj}^\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}_{kj}^\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}_k^\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}_k^\mathrm{B}$, and $\bar{\mathbf{H}}_j^\mathrm{F} \triangleq \mathbf{H}_j^\mathrm{F} \mathbf{W}_j$.
-		The \gls{bd} \gls{ris} subproblem reduces to
+		The \gls{bd}-\gls{ris} subproblem reduces to
 		\begin{mini!}
@@
 		\end{figure}
-		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd} \gls{ris} helps to reduce the leakage interference.
-		In this case, a fully-connected $2^n$-element \gls{bd} \gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
-		Interestingly, the result suggests that \gls{bd} \gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
+		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
+		In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
+		Interestingly, the result suggests that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
 	\end{subsection}
@@
 
-		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd} \gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
+		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd}-\gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
 	\end{subsection}

### 2024-01-25 main.tex
:pencil: Update contribution 4

@@
 	As a side product, we tackle \gls{mimo} rate maximization problem by alternating between active beamformer (eigenmode transmission) and passive beamformer (\gls{rcg} algorithm) until convergence.
-	A low-complexity suboptimal solution based on channel shaping is also proposed, where the decoupled problem is formulated as channel power maximization and solved iteratively in closed form.
+	A low-complexity suboptimal solution based on channel shaping is also proposed, where the decoupled problem is formulated as channel power maximization and solved in closed form iteratively.
 	% We then show how channel shaping decouples the design and amounts to a low-complexity suboptimal solution.
-	% A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved iteratively in closed form.
-	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and stems from stronger subchannel rearrangement and subspace alignment capabilities.
+	% A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved in closed form iteratively.
+	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size, stemming from stronger subchannel rearrangement and subspace alignment capabilities.
 \end{abstract}
@@
 	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
+	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that respects customization.
+	% serves on demand.
 	This is empowered by the recent advances in \gls{ris}, a real-time programmable metasurface of numerous non-resonant sub-wavelength scattering elements.
@@
 	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
-	In contrast, \gls{bd}-\gls{ris} provides a higher channel power but the results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
+	In contrast, \gls{bd}-\gls{ris} can provide a higher channel power but the results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
 \cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
@@
 
-	First, we quantify the capability of \gls{bd}-\gls{ris} to manipulate the channel singular values in \gls{mimo} point-to-point channel.
-	The Pareto frontiers are characterized by optimizing the \emph{weighted sum of singular values}, where the weights can be positive, zero, or negative.
+	First, we quantify the capability of a \gls{bd}-\gls{ris} to reshape the \gls{mimo} point-to-point channel in terms of singular values.
+	The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
 	% This generalizes most singular value metrics and provides a powerful design framework.
-	The resulting region provides a comprehensive and intuitive channel shaping benchmark in terms of singular values.
-	We then discuss some analytical singular value bounds in \gls{los} and fully-connected scenarios.
+	The resulting region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	We then discuss some analytical singular value bounds in \gls{los} and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
 	This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
-
-	% and the first to analytically characterize the singular value bounds of \gls{bd}-\gls{ris}.
-	% characterize the Pareto frontier of channel singular values in the presence of \gls{ris}.
 
@@
 	Specifically, blockwise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold and evaluated compactly as matrix exponential.
-	% The proposed method not only features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, but also applies to any \gls{bd}-\gls{ris} problem where gradient exists.
-	The proposed method features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, which effectively addresses the Pareto singular value problem.
+	The proposed method features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, which is used to solve the Pareto singular value problem.
 	This is the first paper to tailor an efficient optimization framework that unleashes the design potential of asymmetric \gls{bd}-\gls{ris}.
 
-	Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: an optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
+	Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
 	The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
-	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
-	We then highlight the corresponding channel singular values on the Pareto frontier and compare with analytical bounds.
+	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it in closed form iteratively.
+	Interestingly, the gap vanishes as \gls{bd}-\gls{ris} evolves from single-connected (diagonal) to fully-connected (unitary).
+	It suggests that channel shaping offers a crucial guideline for joint \gls{ris}-transceiver designs.
 
@@
 
-	Fourth, we perform extensive simulations to validate and quantify the signal processing advantage of \gls{bd}-\gls{ris}.
-	Besides channel shaping, we also consider typical joint active and passive beamforming problems, including rate maximization in \gls{pc} and \gls{wsr} maximization in \gls{ic}.
-	Results suggest that \gls{bd}-\gls{ris} achieves a larger array gain in \gls{pc} and a higher \gls{dof} in \gls{ic}.
-	We discover that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and stems from stronger subchannel rearrangement and subspace alignment capabilities.
+	Fourth, extensive simulations reveal that the advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} increases with group size and \gls{mimo} dimensions.
+	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\%, 312\%, 537\% in $1 \times 1$, $4 \times 4$, $16 \times 16$ configuration under Rayleigh fading.
+	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
 \end{section}
-
-% ! Evaluate the rate performance of RIS that maximizes channel power (should coincide at low and high snr)
 

### 2024-01-26 main.tex
:pencil: Update introduction

@@
 	% A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved in closed form iteratively.
-	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size, stemming from stronger subchannel rearrangement and subspace alignment capabilities.
+	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions, stemming from stronger subchannel rearrangement and subspace alignment capabilities.
 \end{abstract}
@@
 	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that respects customization.
-	% serves on demand.
+	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
 	This is empowered by the recent advances in \gls{ris}, a real-time programmable metasurface of numerous non-resonant sub-wavelength scattering elements.
@@
 	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
-	In contrast, \gls{bd}-\gls{ris} can provide a higher channel power but the results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
+	In contrast, \gls{bd}-\gls{ris} can provide a higher channel power but existing results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
 \cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
-	While these studies offer promising glimpses into the channel shaping potential of passive \gls{ris}, a comprehensive understanding of its capabilities and limitations is desired, and a universal design framework is missing.
+	While these studies offer promising glimpses into the channel shaping potential, a comprehensive understanding of the capabilities and limitations is desired, and a universal design framework is missing.
 	This paper aims to answer the channel shaping question through theoretical analysis and numerical optimization.
@@
 
-	Second, we propose a \gls{rcg} algorithm for smooth optimization problems of asymmetric\footnote{Although the constraint of symmetric scattering parameters is widely respected in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, it can be relaxed when the \gls{bd}-\gls{ris} involves asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.
-This assumption has been previously adopted in \cite{Li2023b,Li2023c} and symmetry can be enforced on solutions by projection if necessary.} \gls{bd}-\gls{ris} with arbitrary group size.
+	Second, we propose a \gls{rcg} algorithm for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
 	Specifically, blockwise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold and evaluated compactly as matrix exponential.
-	The proposed method features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, which is used to solve the Pareto singular value problem.
+	The proposed method features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and is used to solve the Pareto singular value problem.
 	This is the first paper to tailor an efficient optimization framework that unleashes the design potential of asymmetric \gls{bd}-\gls{ris}.
@@
 
-	Fourth, extensive simulations reveal that the advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} increases with group size and \gls{mimo} dimensions.
-	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\%, 312\%, 537\% in $1 \times 1$, $4 \times 4$, $16 \times 16$ configuration under Rayleigh fading.
+	Fourth, extensive simulations reveal that the advantage of \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
+	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\%, 312\%, 537\% over single-connected in $1 \times 1$, $4 \times 4$, $16 \times 16$ configuration under Rayleigh fading.
 	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
+	It emphasizes the importance of \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
 \end{section}
 
-\begin{section}{\glsentryshort{mimo}-\glsentryshort{pc}}
+\begin{section}{System Model}
+	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, receive antennas, respectively.
+	The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ independent groups.
+	Each group contains $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
+	To simplify the analysis, we assume the \gls{bd}-\gls{ris} features lossless asymmetric\footnote{While symmetric (impedance) network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
+Asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.
+Symmetry can be enforced by projection \cite{Fang2023} if necessary.} in-group connections without mutual coupling.
+	The overall scattering matrix is thus a block diagonal matrix $\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G)$, where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix corresponding to group $g \in \mathcal{G} \triangleq \{1,\ldots,G\}$.
 

### 2024-01-27 main.tex
:pencil: Add notation and model

@@
 \newacronym{los}{LoS}{Line-of-Sight}
+\newacronym{csi}{CSI}{Channel State Information}
+\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
 
@@
 	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it in closed form iteratively.
-	Interestingly, the gap vanishes as \gls{bd}-\gls{ris} evolves from single-connected (diagonal) to fully-connected (unitary).
+	Interestingly, the gap vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
 	It suggests that channel shaping offers a crucial guideline for joint \gls{ris}-transceiver designs.
@@
 	It emphasizes the importance of \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
+
+	\emph{Notation:}
+	Italic, bold lower-case, and bold upper-case letters indicate scalars, vectors and matrices, respectively.
+	$\jmath$ denotes the imaginary unit.
+	$\mathbb{C}$ represents the set of complex numbers.
+	% $\mathrm{U}(n)$ is the group of $n \times n$ unitary matrices.
+	$\mathbb{U}^{n \times n}$ denotes the set of $n \times n$ unitary matrices.
+	$\mathbf{0}$ and $\mathbf{I}$ are the all-zero and identity matrices with appropriate size, respectively.
+	$\mathrm{tr}(\cdot)$ and $\det(\cdot)$ evaluates the trace and determinant of a square matrix, respectively.
+	$\mathrm{diag}(\cdot)$ constructs a square matrix with arguments on the main diagonal and zeros elsewhere.
+	$\mathrm{sv}(\cdot)$ returns the singular value vector.
+	$\sigma_n(\cdot)$ and $\lambda_n(\cdot)$ is the $n$-th largest singular value and eigenvalue, respectively.
+	% $\boldsymbol{\sigma}(\cdot)$ and $\boldsymbol{\lambda}(\cdot)$ are the corresponding vectors.
+	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose, $r$-th iterated, and final results, respectively.
+	$\lvert \cdot \rvert$ denotes the absolute value.
+	$\lVert \cdot \rVert _p$ means the $p$-norm and $\lVert \cdot \rVert$ suggests $p = 2$.
+	$\lVert \cdot \rVert _\mathrm{F}$ represents the Frobenius norm.
+	% $(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and optimal results, respectively.
+	% The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
+	$\sim$ means ``distributed as''.
+	$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
+	% The \gls{cscg} distribution with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$.
 \end{section}
 
-\begin{section}{System Model}
-	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, receive antennas, respectively.
+\begin{section}{\gls{bd}-\gls{ris} Model}
+	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
+	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$.
 	The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ independent groups.
 	Each group contains $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume the \gls{bd}-\gls{ris} features lossless asymmetric\footnote{While symmetric (impedance) network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
-Asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.
-Symmetry can be enforced by projection \cite{Fang2023} if necessary.} in-group connections without mutual coupling.
-	The overall scattering matrix is thus a block diagonal matrix $\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G)$, where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix corresponding to group $g \in \mathcal{G} \triangleq \{1,\ldots,G\}$.
+	To simplify the analysis, we assume the \gls{bd}-\gls{ris} features lossless asymmetric\footnote{While symmetric (impedance) network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006} and asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.} in-group connections without mutual coupling.
+	The overall scattering matrix is thus block diagonal $\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix corresponding to group $g \in \mathcal{G} \triangleq \{1,\ldots,G\}$.
+	Consider a quasi-static block fading model where $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$ denote the direct (transmitter-receiver), forward (transmitter-\gls{ris}), and backward (\gls{ris}-receiver) channels, respectively.
+	The equivalent channel is
+	\begin{equation}
+		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
+		\label{eq:channel_equivalent}
+	\end{equation}
+	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels of \gls{ris} group $g$, respectively.
+	\begin{remark}
+		\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size 1 and $N_\mathrm{S}$, respectively.
+	\end{remark}
+	\begin{remark}
+		Individual forward and backward \gls{csi} are generally required for \gls{bd}-\gls{ris} designs.
+		This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
+	\end{remark}
+\end{section}
 
-	\begin{subsection}{Channel Singular Value Redistribution}
-		We first show the channel shaping benefit of \gls{bd}-\gls{ris} by a toy example.
-		Consider $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$ and assume the direct link is absent.
-		The diagonal \gls{ris} is $\mathbf{\Theta}^\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
+\begin{section}{Channel Singular Value Redistribution}
+	\begin{subsection}{A Toy Example}
+		% We first show the channel shaping advantage of \gls{bd}-\gls{ris} by a toy example.
+		We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
+		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
+		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
 		\begin{equation}
-			\mathbf{\Theta}^\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
+			\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
 				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
@@
 		\end{equation}
-		When the direct link is absent, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		For a fair comparison, we enforce symmetry with $\beta = \pi / 2$.
+		In particular, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
+		For a fair comparison, we also consider symmetric impedance network with $\beta = \pi / 2$.
+		% For a fair comparison, we also consider symmetric impedance network with $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
+		% also enforce symmetry with $\beta = \pi / 2$.
 		\begin{figure}
@@
 		\end{figure}
-		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
-		Despite using the same number of elements and parameters, \gls{bd}-\gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
-		Larger gaps are expected when the symmetry constraint can be relaxed.
+		Fig.~\ref{sm:pc_singular_toy} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
+		Interestingly, both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of angular parameters and scattering elements.
+		A larger performance gap is expected for asymmetric \gls{bd}-\gls{ris}.
+		This example emphasizes the importance of cooperative scattering and motivates further studies on channel shaping.
 

### 2024-01-29 main.tex
:pencil: Add Pareto frontier problem

@@
 	Second, we propose a \gls{rcg} algorithm for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-	Specifically, blockwise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold and evaluated compactly as matrix exponential.
+	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} and evaluated compactly by the exponential map.
 	The proposed method features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and is used to solve the Pareto singular value problem.
@@
 	Each group contains $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume the \gls{bd}-\gls{ris} features lossless asymmetric\footnote{While symmetric (impedance) network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006} and asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.} in-group connections without mutual coupling.
+	To simplify the analysis, we assume the \gls{bd}-\gls{ris} features lossless asymmetric\footnote{While symmetric impedance network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
+Asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.} in-group connections without mutual coupling.
 	The overall scattering matrix is thus block diagonal $\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix corresponding to group $g \in \mathcal{G} \triangleq \{1,\ldots,G\}$.
@@
 	\begin{remark}
-		Individual forward and backward \gls{csi} are generally required for \gls{bd}-\gls{ris} designs.
+		Individual forward and backward \gls{csi} are required for \gls{bd}-\gls{ris} designs.
 		This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
+		Later we will show the potential benefits from the \gls{csi} overhead.
 	\end{remark}
@@
 	\begin{subsection}{A Toy Example}
-		% We first show the channel shaping advantage of \gls{bd}-\gls{ris} by a toy example.
-		We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
+		We first illustrate the channel shaping capabilities of different \gls{ris} by a toy example.
+		% We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
 		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{ris} has 4 independent angular parameters
+		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{bd}-\gls{ris} has 4 independent angular parameters
 		\begin{equation}
@@
 		Interestingly, both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of angular parameters and scattering elements.
-		A larger performance gap is expected for asymmetric \gls{bd}-\gls{ris}.
-		This example emphasizes the importance of cooperative scattering and motivates further studies on channel shaping.
+		A larger performance gap is expected when asymmetric \gls{bd}-\gls{ris} is available.
+		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
+		It emphasizes the importance of cooperative scattering and motivates further studies on channel shaping.
+	\end{subsection}
 
+	\begin{subsection}{Pareto Frontier Characterization}
+		We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		\end{maxi!}
+		where $n \in \{1,\ldots,\min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
+		Varying $\{\rho_n\}$ allows us to explore the entire achievable singular value region.
+		Problem~\eqref{op:pc_singular} thus generalizes all relevant metrics and provides a powerful channel shaping framework.
+		For group $g$, the objective is smooth in $\mathbf{\Theta}_g$ and the feasible domain corresponds to the Stiefel manifold.
+		% Those properties motivate us to propose a \gls{rcg} algorithm for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
+		% Those motivate us to propose a general \gls{rcg} algorithm for asymmetric \gls{bd}-\gls{ris} with arbitrary group size, which will be detailed in Section~\ref{sc:rcg}.
+		Those properties motivate us to zoom out to general smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
+
+		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a block-wise \gls{rcg} update along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
+		The gradient
+
+		% It effectively solves general smooth asymmetric \gls{bd}-\gls{ris} problems with arbitrary group size.
+		% The steps are summarized in Algorithm~\ref{ag:rcg}, where line \ref{ln:gradient_euclidean} computes the gradient in the Euclidean space, line \ref{ln:gradient_riemannian} translates it to the Riemannian manifold,
+		% \footnote{The geodesics of the Stiefel manifold have compact expressions described by exponential map.}
+
+% \footnote{The geodesics of the Stiefel manifold have compact expressions described by exponential map.}
+		\setalgorithmcaptionfont{\small}
+		\begin{algorithm}[!t]
+			\small
+			\caption{Block-wise \gls{rcg} update for asymmetric \gls{bd}-\gls{ris}}
+			\label{ag:rcg}
+			\begin{algorithmic}[1]
+				\Require $f(\mathbf{\Theta})$, $G$
+				\Ensure $\mathbf{\Theta}^\star$
+				\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
+				\Repeat
+					\State $r \gets r+1$
+					\For {$g \gets 1$ to $G$}
+						\State $\nabla_{\mathrm{E},g}^{(r)} \gets {\partial f(\mathbf{\Theta}_g^{(r)})}/{\partial \mathbf{\Theta}_g^*}$\label{ln:gradient_euclidean}
+						\State $\nabla_{\mathrm{R},g}^{(r)} \gets \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}$\label{ln:gradient_riemannian}
+						\State $\gamma_g^{(r)} \gets {\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}/{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}$\label{ln:parameter_polak_approx}
+						\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}$\label{ln:direction_conjugate}
+						\State $\mu_g^{(r)} \gets \arg\max_{\mu_g} f\bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\bigr)$\label{ln:step_armijo}
+						\State $\mathbf{\Theta}_g^{(r+1)} \gets \exp\bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}$\label{ln:update_geodesic}
+					\EndFor
+				\Until $\lvert R^{(r)} - R^{(r-1)} \rvert / R^{(r-1)} \le \epsilon$
+			\end{algorithmic}
+		\end{algorithm}
+
+		% fun = @(Theta_g) rho' * svd(H_d + H_b(:, S) * Theta_g * H_f(S, :) + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :));
+		% G_e(S, S) = gradient_euclidean(H, H_f(S, :), H_b(:, S), rho);
+		% G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
+		% D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
+		% Theta(S, S) = step_armijo(fun, Theta(S, S), D(S, S));
+
+		% we update $\mathbf{\Theta}$ by \gls{rcg} method along the geodesics.
+		% \begin{remark}
+		% 	A geodesic refers to the shortest path between two points in a Riemannian manifold.
+		% 	% For unitary constraint \eqref{cs:pc_rate_unitary}, the
+		% 	Unitary constraint \eqref{cs:pc_rate_unitary} translates to a Stiefel manifold where the geodesics have simple expressions described by the exponential map \cite{Abrudan2008}.
+		% 	% Geodesics are the locally shortest paths in a Riemannian manifold.
+		% 	% A Geodesics are the locally shortest paths in a Riemannian manifold.
+		% 	% on Riemannian manifold are the shortest path between two points.
+		% \end{remark}
+		For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)$ is the objective function also evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'<g}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'>g} \bigr\}$.
+		\begin{enumerate}
+			\item Compute the Euclidean gradient
+			\begin{equation}
+				{\nabla_g^\mathrm{E}}^{(r)} = \frac{\partial f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)}{\partial \mathbf{\Theta}_g^*};
+				\label{eq:rcg_gradient_euclidean}
+			\end{equation}
+			\item Translate to the Riemannian gradient
+			\begin{equation}
+				{\nabla_g^\mathrm{R}}^{(r)} = {\nabla_g^\mathrm{E}}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {{\nabla_g^\mathrm{E}}^{(r)}}^\mathsf{H};
+				\label{eq:rcg_gradient_riemannian}
+			\end{equation}
+			\item Determine the weight factor
+			\begin{equation}
+				\gamma_g^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl({\nabla_g^\mathrm{R}}^{(r)} - {\nabla_g^\mathrm{R}}^{(r-1)}\bigr) {{\nabla_g^\mathrm{R}}^{(r)}}^\mathsf{H}\Bigr)}{\mathrm{tr}\Bigl({\nabla_g^\mathrm{R}}^{(r-1)} {{\nabla_g^\mathrm{R}}^{(r-1)}}^\mathsf{H}\Bigr)};
+				\label{eq:rcg_weight}
+			\end{equation}
+			\item Compute the conjugate direction
+			\begin{equation}
+				\mathbf{D}_g^{(r)} = {\nabla_g^\mathrm{R}}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)};
+				\label{eq:rcg_direction}
+			\end{equation}
+			\item Determine the Armijo step size\footnote{To double the step size, simply square the argument instead of recomputing the matrix exponential, i.e., $\exp(2 \mu_g \mathbf{D}_g) = \exp^2(\mu_g \mathbf{D}_g)$.}
+			\begin{equation}
+				\mu_g^{(r)} = \arg\max_{\mu_g} f\Bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr);
+				\label{eq:rcg_step}
+			\end{equation}
+			\item Perform rotational update along local geodesics
+			\begin{equation}
+				\mathbf{\Theta}_g^{(r+1)} = \exp\Bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\Bigr) \mathbf{\Theta}_g^{(r)}.
+				\label{eq:rcg_update}
+			\end{equation}
+		\end{enumerate}
+
+		\begin{remark}
+			The adapted \gls{rcg} method leverages the fact that block unitary matrices are closed under multiplication (but not necessarily under addition).
+			Its advantage over universal manifold optimization \cite{Absil2009,Pan2022d} is trifold:
+			\begin{itemize}
+				\item No retraction is involved;
+				\item Lower computational complexity per iteration \cite{Abrudan2008};
+				\item Faster convergence thanks appropriate operational space.
+			\end{itemize}
+		\end{remark}
+
+	\end{subsection}
+
+	\begin{subsection}{Analytical Bounds}
 		We then analyze the channel shaping \emph{capability} of \gls{bd}-\gls{ris} under specific setups.
@@
 			\begin{align}
-				\sigma_1(\mathbf{BF}) \le \sigma_1(\mathbf{B}) \sigma_1(\mathbf{F}) \label{iq:singular_value_largest}\\
-				\sigma_N(\mathbf{BF}) \geq \sigma_N(\mathbf{B}) \sigma_N(\mathbf{F}) \label{iq:singular_value_smallest}.
+				\sigma_1(\mathbf{BF}) \le \sigma_1(\mathbf{B}) \sigma_1(\mathbf{F})\label{iq:singular_value_largest}\\
+				\sigma_N(\mathbf{BF}) \geq \sigma_N(\mathbf{B}) \sigma_N(\mathbf{F})\label{iq:singular_value_smallest}.
 			\end{align}
@@
 			\begin{equation}
-				\sum_n \sigma_n^p(\mathbf{BF}) \leq \sum_n \sigma_n^p(\mathbf{B}) \sigma_n^p(\mathbf{F}) \label{iq:singular_value_power_sum}.
+				\sum_n \sigma_n^p(\mathbf{BF}) \leq \sum_n \sigma_n^p(\mathbf{B}) \sigma_n^p(\mathbf{F})\label{iq:singular_value_power_sum}.
 			\end{equation}
@@
 
-		\begin{customopti!}
-			{\underset{\scriptstyle{\mathbf{\Theta}}}{max / min}}{}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		\end{customopti!}
+		% \begin{customopti!}
+		% 	{\underset{\scriptstyle{\mathbf{\Theta}}}{max / min}}{}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
+		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		% \end{customopti!}
 
@@
 		where $\mathbf{V}$ is right singular matrix of $\mathbf{H}$ and $\mathbf{S}^\star$ is a diagonal matrix of the water-filling power allocation.
-		For a given $\mathbf{W}$, we update $\mathbf{\Theta}$ by \gls{rcg} method along the geodesics \cite{Abrudan2009}.
-		\begin{remark}
-			A geodesic refers to the shortest path between two points in a Riemannian manifold.
-			% For unitary constraint \eqref{cs:pc_rate_unitary}, the
-			Unitary constraint \eqref{cs:pc_rate_unitary} translates to a Stiefel manifold where the geodesics have simple expressions described by the exponential map \cite{Abrudan2008}.
-			% Geodesics are the locally shortest paths in a Riemannian manifold.
-			% A Geodesics are the locally shortest paths in a Riemannian manifold.
-			% on Riemannian manifold are the shortest path between two points.
-		\end{remark}
-		For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)$ is the objective function also evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'<g}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'>g} \bigr\}$.
-		\begin{enumerate}
-			\item Compute the Euclidean gradient
-			\begin{equation}
-				{\nabla_g^\mathrm{E}}^{(r)} = \frac{\partial f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)}{\partial \mathbf{\Theta}_g^*};
-				\label{eq:rcg_gradient_euclidean}
-			\end{equation}
-			\item Translate to the Riemannian gradient
-			\begin{equation}
-				{\nabla_g^\mathrm{R}}^{(r)} = {\nabla_g^\mathrm{E}}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {{\nabla_g^\mathrm{E}}^{(r)}}^\mathsf{H};
-				\label{eq:rcg_gradient_riemannian}
-			\end{equation}
-			\item Determine the weight factor
-			\begin{equation}
-				\gamma_g^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl({\nabla_g^\mathrm{R}}^{(r)} - {\nabla_g^\mathrm{R}}^{(r-1)}\bigr) {{\nabla_g^\mathrm{R}}^{(r)}}^\mathsf{H}\Bigr)}{\mathrm{tr}\Bigl({\nabla_g^\mathrm{R}}^{(r-1)} {{\nabla_g^\mathrm{R}}^{(r-1)}}^\mathsf{H}\Bigr)};
-				\label{eq:rcg_weight}
-			\end{equation}
-			\item Compute the conjugate direction
-			\begin{equation}
-				\mathbf{D}_g^{(r)} = {\nabla_g^\mathrm{R}}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)};
-				\label{eq:rcg_direction}
-			\end{equation}
-			\item Determine the Armijo step size\footnote{To double the step size, simply square the argument instead of recomputing the matrix exponential, i.e., $\exp(2 \mu_g \mathbf{D}_g) = \exp^2(\mu_g \mathbf{D}_g)$.}
-			\begin{equation}
-				\mu_g^{(r)} = \arg\max_{\mu_g} f\Bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr);
-				\label{eq:rcg_step}
-			\end{equation}
-			\item Perform rotational update along local geodesics
-			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \exp\Bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\Bigr) \mathbf{\Theta}_g^{(r)}.
-				\label{eq:rcg_update}
-			\end{equation}
-		\end{enumerate}
-
-		\begin{remark}
-			The adapted \gls{rcg} method leverages the fact that block unitary matrices are closed under multiplication (but not necessarily under addition).
-			Its advantage over universal manifold optimization \cite{Absil2009,Pan2022d} is trifold:
-			\begin{itemize}
-				\item No retraction is involved;
-				\item Lower computational complexity per iteration \cite{Abrudan2008};
-				\item Faster convergence thanks appropriate operational space.
-			\end{itemize}
-		\end{remark}
-
+		For a given $\mathbf{W}$,
 		The complex derivative of \eqref{ob:pc_rate} w.r.t. \gls{ris} block $g$ is

### 2024-01-31 main.tex
:pencil: Add RCG algorithm

@@
 \usepackage{epstopdf}
+% \usepackage{cleveref}
 
@@
 \algrenewcommand{\algorithmicfor}{\textbf{For}}
+\algrenewcommand{\algorithmicif}{\textbf{If}}
+\algrenewcommand{\algorithmicelse}{\textbf{Else}}
 \algrenewcommand{\algorithmicdo}{}
+\algrenewcommand{\algorithmicthen}{}
+\algnewcommand{\Initialize}[1]{%
+	\State \textbf{Initialize }{#1}
+}
 
@@
 	% This generalizes most singular value metrics and provides a powerful design framework.
-	The resulting region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
 	We then discuss some analytical singular value bounds in \gls{los} and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
@@
 
-	Second, we propose a \gls{rcg} algorithm for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} and evaluated compactly by the exponential map.
-	The proposed method features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and is used to solve the Pareto singular value problem.
-	This is the first paper to tailor an efficient optimization framework that unleashes the design potential of asymmetric \gls{bd}-\gls{ris}.
+	Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
+	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
+	It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
+	This is the first paper to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
 
@@
 	The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
-	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it in closed form iteratively.
-	Interestingly, the gap vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
-	It suggests that channel shaping offers a crucial guideline for joint \gls{ris}-transceiver designs.
+	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
+	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
+	It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.
 
@@
 
-	Fourth, extensive simulations reveal that the advantage of \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\%, 312\%, 537\% over single-connected in $1 \times 1$, $4 \times 4$, $16 \times 16$ configuration under Rayleigh fading.
+	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
+	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\%, 312\%, 537\% over single-connected in $1 \times 1$, $4 \times 4$, $16 \times 16$ \gls{mimo} under independent Rayleigh fading, respectively.
 	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
-	It emphasizes the importance of \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
+	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
 
@@
 	% $\boldsymbol{\sigma}(\cdot)$ and $\boldsymbol{\lambda}(\cdot)$ are the corresponding vectors.
-	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose, $r$-th iterated, and final results, respectively.
+	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), $r$-th iterated point, and final solution, respectively.
 	$\lvert \cdot \rvert$ denotes the absolute value.
@@
 	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$.
-	The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ independent groups.
+	The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ individual groups.
 	Each group contains $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume the \gls{bd}-\gls{ris} features lossless asymmetric\footnote{While symmetric impedance network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
+	% To simplify the analysis, we assume the \gls{bd}-\gls{ris} features lossless asymmetric\footnote{While symmetric impedance network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
 Asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.} in-group connections without mutual coupling.
+	To simplify the analysis, we assume there are no mutual coupling and the in-group connections can be lossless and asymmetric\footnote{While symmetric impedance network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
+Asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.}.
 	The overall scattering matrix is thus block diagonal $\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix corresponding to group $g \in \mathcal{G} \triangleq \{1,\ldots,G\}$.
-	Consider a quasi-static block fading model where $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$ denote the direct (transmitter-receiver), forward (transmitter-\gls{ris}), and backward (\gls{ris}-receiver) channels, respectively.
+	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$ denote the direct (transmitter-receiver), forward (transmitter-\gls{ris}), and backward (\gls{ris}-receiver) channels, respectively.
 	The equivalent channel is
@@
 		This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
-		Later we will show the potential benefits from the \gls{csi} overhead.
+		% Later we will show the potential benefits from the \gls{csi} overhead.
 	\end{remark}
@@
 		In particular, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		For a fair comparison, we also consider symmetric impedance network with $\beta = \pi / 2$.
-		% For a fair comparison, we also consider symmetric impedance network with $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
+		% For a fair comparison, we also consider symmetric impedance network with $\beta = \pi / 2$.
+		We also enforce symmetry by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
 		% also enforce symmetry with $\beta = \pi / 2$.
@@
 		Fig.~\ref{sm:pc_singular_toy} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
-		Interestingly, both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of angular parameters and scattering elements.
+		It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and design parameters.
 		A larger performance gap is expected when asymmetric \gls{bd}-\gls{ris} is available.
-		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
-		It emphasizes the importance of cooperative scattering and motivates further studies on channel shaping.
+		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
 	\end{subsection}
@@
 		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:pareto_unitary}}
 		\end{maxi!}
 		where $n \in \{1,\ldots,\min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
-		Varying $\{\rho_n\}$ allows us to explore the entire achievable singular value region.
-		Problem~\eqref{op:pc_singular} thus generalizes all relevant metrics and provides a powerful channel shaping framework.
-		For group $g$, the objective is smooth in $\mathbf{\Theta}_g$ and the feasible domain corresponds to the Stiefel manifold.
+		Varying $\{\rho_n\}$ unveils the entire achievable singular value region.
+		Thus, the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
+		% For group $g$, the objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}_g$ and the feasible domain \eqref{co:pareto.unitary} corresponds to the Stiefel manifold.
+		The objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} for group $g$ corresponds to the Stiefel manifold.
+		% Next, we zoom out to solve general smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
 		% Those properties motivate us to propose a \gls{rcg} algorithm for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
 		% Those motivate us to propose a general \gls{rcg} algorithm for asymmetric \gls{bd}-\gls{ris} with arbitrary group size, which will be detailed in Section~\ref{sc:rcg}.
-		Those properties motivate us to zoom out to general smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
+		% Those properties motivate us to zoom out to general smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
+		Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
 
-		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a block-wise \gls{rcg} update along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
-		The gradient
+		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a block-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
+		It leverages the fact that unitary matrices are closed under multiplication.
+		At iteration $r$, the gradient is computed in the Euclidean space and translated to the Riemannian manifold \cite{Absil2009}
+		\begin{gather}
+			\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
+			\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian}
+		\end{gather}
+		The Polak-Ribierre parameter \cite{Polak1969} is approximated as \cite{Abrudan2009}
+		\begin{equation}
+			\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)},
+			\label{eq:parameter_cg}
+		\end{equation}
+		and the conjugate direction is
+		\begin{equation}
+			\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}.
+			\label{eq:direction_cg}
+		\end{equation}
+		% In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu_g$ is described compactly by the exponential map \cite{Edelman1998}
+		% In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu_g^{(r)}$ is described compactly by the exponential map \cite{Edelman1998}
+		In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
+		\begin{equation}
+			\mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}.
+			\label{eq:geodesic}
+		\end{equation}
+		% \begin{gather}
+		% 	\mathbf{T}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}),\label{eq:exponential_map}\\
+		% 	\mathbf{G}_g^{(r)}(\mu) = \mathbf{T}_g^{(r)}(\mu) \mathbf{\Theta}_g^{(r)}.\label{eq:geodesic}
+		% \end{gather}
+		An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.\footnote{To double the step size, one only need to square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.}
+		Finally, the scattering matrix is updated along the geodesic as
+		\begin{equation}
+			\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
+			\label{eq:update_geodesic}
+		\end{equation}
+		% Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} update for asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
+		Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
+		Convergence to stationary points is guaranteed as updating each block iteratively does not reduce the objective function.
 
-		% It effectively solves general smooth asymmetric \gls{bd}-\gls{ris} problems with arbitrary group size.
-		% The steps are summarized in Algorithm~\ref{ag:rcg}, where line \ref{ln:gradient_euclidean} computes the gradient in the Euclidean space, line \ref{ln:gradient_riemannian} translates it to the Riemannian manifold,
-		% \footnote{The geodesics of the Stiefel manifold have compact expressions described by exponential map.}
+		\begin{remark}
+			Compared with universal manifold optimization \cite{Absil2009,Pan2022d}, Algorithm~\ref{ag:rcg} inherits a trifold benefit from \cite{Abrudan2008,Abrudan2009}:
+			% The advantage of the proposed block-wise \gls{rcg} algorithm over universal manifold optimization \cite{Absil2009,Pan2022d} is trifold:
+			\begin{enumerate}
+				\item No retraction thanks to rotational update;
+				\item Lower computational complexity per iteration;
+				\item Faster convergence thanks to proper parameter space.
+			\end{enumerate}
+		\end{remark}
 
-% \footnote{The geodesics of the Stiefel manifold have compact expressions described by exponential map.}
 		\setalgorithmcaptionfont{\small}
@@
 			\small
-			\caption{Block-wise \gls{rcg} update for asymmetric \gls{bd}-\gls{ris}}
+			\caption{Block-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
 			\label{ag:rcg}
@@
 				\Ensure $\mathbf{\Theta}^\star$
-				\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
+				\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
 				\Repeat
+					\For {$g \gets 1$ to $G$}
+						\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean}, \eqref{eq:gradient_riemannian} \label{ln:gradient_euclidean}
+						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:parameter_cg}, \eqref{eq:direction_cg}
+						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
+							\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
+						\EndIf
+						\State $\mu \gets 1$
+						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
+							\State $\mu \gets 2 \mu$
+						\EndWhile
+						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
+							\State $\mu \gets \mu / 2$
+						\EndWhile
+						\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:update_geodesic}
+					\EndFor
 					\State $r \gets r+1$
-					\For {$g \gets 1$ to $G$}
-						\State $\nabla_{\mathrm{E},g}^{(r)} \gets {\partial f(\mathbf{\Theta}_g^{(r)})}/{\partial \mathbf{\Theta}_g^*}$\label{ln:gradient_euclidean}
-						\State $\nabla_{\mathrm{R},g}^{(r)} \gets \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}$\label{ln:gradient_riemannian}
-						\State $\gamma_g^{(r)} \gets {\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}/{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}$\label{ln:parameter_polak_approx}
-						\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}$\label{ln:direction_conjugate}
-						\State $\mu_g^{(r)} \gets \arg\max_{\mu_g} f\bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\bigr)$\label{ln:step_armijo}
-						\State $\mathbf{\Theta}_g^{(r+1)} \gets \exp\bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}$\label{ln:update_geodesic}
-					\EndFor
-				\Until $\lvert R^{(r)} - R^{(r-1)} \rvert / R^{(r-1)} \le \epsilon$
+				\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
 			\end{algorithmic}
@@
 
-		% fun = @(Theta_g) rho' * svd(H_d + H_b(:, S) * Theta_g * H_f(S, :) + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :));
-		% G_e(S, S) = gradient_euclidean(H, H_f(S, :), H_b(:, S), rho);
-		% G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
-		% D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
-		% Theta(S, S) = step_armijo(fun, Theta(S, S), D(S, S));
+		% \setalgorithmcaptionfont{\small}
+		% \begin{algorithm}[!t]
+		% 	\small
+		% 	\caption{Block-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
+		% 	\label{ag:rcg}
+		% 	\begin{algorithmic}[1]
+		% 		\Require $f(\mathbf{\Theta})$, $G$
+		% 		\Ensure $\mathbf{\Theta}^\star$
+		% 		\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
+		% 		\Repeat
+		% 			\State $r \gets r+1$
+		% 			\For {$g \gets 1$ to $G$}
+		% 				\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean}, \eqref{eq:gradient_riemannian} \label{ln:gradient_euclidean}
+		% 				\State $\gamma_g^{(r)} \gets \begin{cases} 0, & \text{if } r = 1\\ \eqref{eq:parameter_cg}, & \text{otherwise} \end{cases}$
+		% 				% \If {$r = 1$}
+		% 				% 	\State $\gamma_g^{(r)} \gets 0$
+		% 				% \Else
+		% 				% 	\State $\gamma_g^{(r)} \gets$ \eqref{eq:parameter_cg}
+		% 				% \EndIf
+		% 				% \State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
+		% 				% \If {$\Re\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\} < 0$}
+		% 				% 	\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
+		% 				% \EndIf
+		% 				% \State $\nabla_{\mathrm{R},g}^{(r)} \gets \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}$\label{ln:gradient_riemannian}
+		% 				% \State $\gamma_g^{(r)} \gets {\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}/{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}$\label{ln:parameter_polak_approx}
+		% 				% \State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}$\label{ln:direction_conjugate}
+		% 				% \State $\mu_g^{(r)} \gets \arg\max_{\mu_g} f\bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\bigr)$\label{ln:step_armijo}
+		% 				% \State $\mathbf{\Theta}_g^{(r+1)} \gets \exp\bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}$\label{ln:update_geodesic}
+		% 			\EndFor
+		% 		\Until $\lvert R^{(r)} - R^{(r-1)} \rvert / R^{(r-1)} \le \epsilon$
+		% 	\end{algorithmic}
+		% \end{algorithm}
 
-		% we update $\mathbf{\Theta}$ by \gls{rcg} method along the geodesics.
+		% For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)$ is the objective function also evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'<g}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'>g} \bigr\}$.
+		% \begin{enumerate}
+		% 	\item Compute the Euclidean gradient
+		% 	\begin{equation}
+		% 		{\nabla_g^\mathrm{E}}^{(r)} = \frac{\partial f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)}{\partial \mathbf{\Theta}_g^*};
+		% 		\label{eq:rcg_gradient_euclidean}
+		% 	\end{equation}
+		% 	\item Translate to the Riemannian gradient
+		% 	\begin{equation}
+		% 		{\nabla_g^\mathrm{R}}^{(r)} = {\nabla_g^\mathrm{E}}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {{\nabla_g^\mathrm{E}}^{(r)}}^\mathsf{H};
+		% 		\label{eq:rcg_gradient_riemannian}
+		% 	\end{equation}
+		% 	\item Determine the weight factor
+		% 	\begin{equation}
+		% 		\gamma_g^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl({\nabla_g^\mathrm{R}}^{(r)} - {\nabla_g^\mathrm{R}}^{(r-1)}\bigr) {{\nabla_g^\mathrm{R}}^{(r)}}^\mathsf{H}\Bigr)}{\mathrm{tr}\Bigl({\nabla_g^\mathrm{R}}^{(r-1)} {{\nabla_g^\mathrm{R}}^{(r-1)}}^\mathsf{H}\Bigr)};
+		% 		\label{eq:rcg_weight}
+		% 	\end{equation}
+		% 	\item Compute the conjugate direction
+		% 	\begin{equation}
+		% 		\mathbf{D}_g^{(r)} = {\nabla_g^\mathrm{R}}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)};
+		% 		\label{eq:rcg_direction}
+		% 	\end{equation}
+		% 	\item Determine the Armijo step size\footnote{To double the step size, simply square the argument instead of recomputing the matrix exponential, i.e., $\exp(2 \mu_g \mathbf{D}_g) = \exp^2(\mu_g \mathbf{D}_g)$.}
+		% 	\begin{equation}
+		% 		\mu_g^{(r)} = \arg\max_{\mu_g} f\Bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr);
+		% 		\label{eq:rcg_step}
+		% 	\end{equation}
+		% 	\item Perform rotational update along local geodesics
+		% 	\begin{equation}
+		% 		\mathbf{\Theta}_g^{(r+1)} = \exp\Bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\Bigr) \mathbf{\Theta}_g^{(r)}.
+		% 		\label{eq:rcg_update}
+		% 	\end{equation}
+		% \end{enumerate}
+
 		% \begin{remark}
-		% 	A geodesic refers to the shortest path between two points in a Riemannian manifold.
-		% 	% For unitary constraint \eqref{cs:pc_rate_unitary}, the
-		% 	Unitary constraint \eqref{cs:pc_rate_unitary} translates to a Stiefel manifold where the geodesics have simple expressions described by the exponential map \cite{Abrudan2008}.
-		% 	% Geodesics are the locally shortest paths in a Riemannian manifold.
-		% 	% A Geodesics are the locally shortest paths in a Riemannian manifold.
-		% 	% on Riemannian manifold are the shortest path between two points.
+		% 	The adapted \gls{rcg} method leverages the fact that block unitary matrices are closed under multiplication (but not necessarily under addition).
+		% 	Its advantage over universal manifold optimization \cite{Absil2009,Pan2022d} is trifold:
+		% 	\begin{itemize}
+		% 		\item No retraction is involved;
+		% 		\item Lower computational complexity per iteration \cite{Abrudan2008};
+		% 		\item Faster convergence thanks appropriate operational space.
+		% 	\end{itemize}
 		% \end{remark}
-		For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)$ is the objective function also evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'<g}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'>g} \bigr\}$.
-		\begin{enumerate}
-			\item Compute the Euclidean gradient
-			\begin{equation}
-				{\nabla_g^\mathrm{E}}^{(r)} = \frac{\partial f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)}{\partial \mathbf{\Theta}_g^*};
-				\label{eq:rcg_gradient_euclidean}
-			\end{equation}
-			\item Translate to the Riemannian gradient
-			\begin{equation}
-				{\nabla_g^\mathrm{R}}^{(r)} = {\nabla_g^\mathrm{E}}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {{\nabla_g^\mathrm{E}}^{(r)}}^\mathsf{H};
-				\label{eq:rcg_gradient_riemannian}
-			\end{equation}
-			\item Determine the weight factor
-			\begin{equation}
-				\gamma_g^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl({\nabla_g^\mathrm{R}}^{(r)} - {\nabla_g^\mathrm{R}}^{(r-1)}\bigr) {{\nabla_g^\mathrm{R}}^{(r)}}^\mathsf{H}\Bigr)}{\mathrm{tr}\Bigl({\nabla_g^\mathrm{R}}^{(r-1)} {{\nabla_g^\mathrm{R}}^{(r-1)}}^\mathsf{H}\Bigr)};
-				\label{eq:rcg_weight}
-			\end{equation}
-			\item Compute the conjugate direction
-			\begin{equation}
-				\mathbf{D}_g^{(r)} = {\nabla_g^\mathrm{R}}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)};
-				\label{eq:rcg_direction}
-			\end{equation}
-			\item Determine the Armijo step size\footnote{To double the step size, simply square the argument instead of recomputing the matrix exponential, i.e., $\exp(2 \mu_g \mathbf{D}_g) = \exp^2(\mu_g \mathbf{D}_g)$.}
-			\begin{equation}
-				\mu_g^{(r)} = \arg\max_{\mu_g} f\Bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr);
-				\label{eq:rcg_step}
-			\end{equation}
-			\item Perform rotational update along local geodesics
-			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \exp\Bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\Bigr) \mathbf{\Theta}_g^{(r)}.
-				\label{eq:rcg_update}
-			\end{equation}
-		\end{enumerate}
-
-		\begin{remark}
-			The adapted \gls{rcg} method leverages the fact that block unitary matrices are closed under multiplication (but not necessarily under addition).
-			Its advantage over universal manifold optimization \cite{Absil2009,Pan2022d} is trifold:
-			\begin{itemize}
-				\item No retraction is involved;
-				\item Lower computational complexity per iteration \cite{Abrudan2008};
-				\item Faster convergence thanks appropriate operational space.
-			\end{itemize}
-		\end{remark}
 

### 2024-02-01 main.tex
:dizzy: Confused at proof

@@
 	$\mathbb{C}$ represents the set of complex numbers.
-	% $\mathrm{U}(n)$ is the group of $n \times n$ unitary matrices.
 	$\mathbb{U}^{n \times n}$ denotes the set of $n \times n$ unitary matrices.
@@
 	$\lVert \cdot \rVert _\mathrm{F}$ represents the Frobenius norm.
-	% $(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and optimal results, respectively.
-	% The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
 	$\sim$ means ``distributed as''.
 	$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
-	% The \gls{cscg} distribution with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$.
 \end{section}
@@
 	Each group contains $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	% To simplify the analysis, we assume the \gls{bd}-\gls{ris} features lossless asymmetric\footnote{While symmetric impedance network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
-Asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.} in-group connections without mutual coupling.
 	To simplify the analysis, we assume there are no mutual coupling and the in-group connections can be lossless and asymmetric\footnote{While symmetric impedance network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
@@
 		In particular, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		% For a fair comparison, we also consider symmetric impedance network with $\beta = \pi / 2$.
 		We also enforce symmetry by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
-		% also enforce symmetry with $\beta = \pi / 2$.
 		\begin{figure}
@@
 			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
-			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris}. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$. Direct link is absent.}
+			\caption{$2 \times 2 \times 2$ channel singular value shaping by diagonal and symmetry unitary \gls{ris}. Direct link is absent.}
 			\label{sm:pc_singular_toy}
@@
 		Thus, the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
-		% For group $g$, the objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}_g$ and the feasible domain \eqref{co:pareto.unitary} corresponds to the Stiefel manifold.
 		The objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} for group $g$ corresponds to the Stiefel manifold.
-		% Next, we zoom out to solve general smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-		% Those properties motivate us to propose a \gls{rcg} algorithm for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-		% Those motivate us to propose a general \gls{rcg} algorithm for asymmetric \gls{bd}-\gls{ris} with arbitrary group size, which will be detailed in Section~\ref{sc:rcg}.
-		% Those properties motivate us to zoom out to general smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-		Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
+		Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
 
@@
 		\end{equation}
-		% In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu_g$ is described compactly by the exponential map \cite{Edelman1998}
-		% In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu_g^{(r)}$ is described compactly by the exponential map \cite{Edelman1998}
 		In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
@@
 		\end{equation}
-		% \begin{gather}
-		% 	\mathbf{T}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}),\label{eq:exponential_map}\\
-		% 	\mathbf{G}_g^{(r)}(\mu) = \mathbf{T}_g^{(r)}(\mu) \mathbf{\Theta}_g^{(r)}.\label{eq:geodesic}
-		% \end{gather}
 		An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.\footnote{To double the step size, one only need to square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.}
@@
 		\end{equation}
-		% Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} update for asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-		Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
+		Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
 		Convergence to stationary points is guaranteed as updating each block iteratively does not reduce the objective function.
@@
 			Compared with universal manifold optimization \cite{Absil2009,Pan2022d}, Algorithm~\ref{ag:rcg} inherits a trifold benefit from \cite{Abrudan2008,Abrudan2009}:
-			% The advantage of the proposed block-wise \gls{rcg} algorithm over universal manifold optimization \cite{Absil2009,Pan2022d} is trifold:
 			\begin{enumerate}
-				\item No retraction thanks to rotational update;
+				\item No retraction thanks to rotational update \eqref{eq:geodesic}, \eqref{eq:update_geodesic};
 				\item Lower computational complexity per iteration;
@@
 					\For {$g \gets 1$ to $G$}
-						\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean}, \eqref{eq:gradient_riemannian} \label{ln:gradient_euclidean}
-						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:parameter_cg}, \eqref{eq:direction_cg}
+						\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean} \label{ln:gradient_euclidean}
+						\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riemannian}
+						\State $\gamma_g^{(r)} \gets$ \eqref{eq:parameter_cg}
+						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
 						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
@@
 						\State $\mu \gets 1$
+						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic}
 						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
@@
 
-		% \setalgorithmcaptionfont{\small}
-		% \begin{algorithm}[!t]
-		% 	\small
-		% 	\caption{Block-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
-		% 	\label{ag:rcg}
-		% 	\begin{algorithmic}[1]
-		% 		\Require $f(\mathbf{\Theta})$, $G$
-		% 		\Ensure $\mathbf{\Theta}^\star$
-		% 		\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
-		% 		\Repeat
-		% 			\State $r \gets r+1$
-		% 			\For {$g \gets 1$ to $G$}
-		% 				\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean}, \eqref{eq:gradient_riemannian} \label{ln:gradient_euclidean}
-		% 				\State $\gamma_g^{(r)} \gets \begin{cases} 0, & \text{if } r = 1\\ \eqref{eq:parameter_cg}, & \text{otherwise} \end{cases}$
-		% 				% \If {$r = 1$}
-		% 				% 	\State $\gamma_g^{(r)} \gets 0$
-		% 				% \Else
-		% 				% 	\State $\gamma_g^{(r)} \gets$ \eqref{eq:parameter_cg}
-		% 				% \EndIf
-		% 				% \State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
-		% 				% \If {$\Re\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\} < 0$}
-		% 				% 	\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
-		% 				% \EndIf
-		% 				% \State $\nabla_{\mathrm{R},g}^{(r)} \gets \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}$\label{ln:gradient_riemannian}
-		% 				% \State $\gamma_g^{(r)} \gets {\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}/{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}$\label{ln:parameter_polak_approx}
-		% 				% \State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}$\label{ln:direction_conjugate}
-		% 				% \State $\mu_g^{(r)} \gets \arg\max_{\mu_g} f\bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\bigr)$\label{ln:step_armijo}
-		% 				% \State $\mathbf{\Theta}_g^{(r+1)} \gets \exp\bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}$\label{ln:update_geodesic}
-		% 			\EndFor
-		% 		\Until $\lvert R^{(r)} - R^{(r-1)} \rvert / R^{(r-1)} \le \epsilon$
-		% 	\end{algorithmic}
-		% \end{algorithm}
-
-		% For general optimization problems with block unitary constraint, the adapted \gls{rcg} method at iteration $r$ for block $g$ is summarized below, where $f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)$ is the objective function also evaluated over $\bigl\{ \{\mathbf{\Theta}_{g'}^{(r+1)}\}_{g'<g}, \{\mathbf{\Theta}_{g'}^{(r)}\}_{g'>g} \bigr\}$.
-		% \begin{enumerate}
-		% 	\item Compute the Euclidean gradient
-		% 	\begin{equation}
-		% 		{\nabla_g^\mathrm{E}}^{(r)} = \frac{\partial f\bigl(\mathbf{\Theta}_g^{(r)}\bigr)}{\partial \mathbf{\Theta}_g^*};
-		% 		\label{eq:rcg_gradient_euclidean}
-		% 	\end{equation}
-		% 	\item Translate to the Riemannian gradient
-		% 	\begin{equation}
-		% 		{\nabla_g^\mathrm{R}}^{(r)} = {\nabla_g^\mathrm{E}}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {{\nabla_g^\mathrm{E}}^{(r)}}^\mathsf{H};
-		% 		\label{eq:rcg_gradient_riemannian}
-		% 	\end{equation}
-		% 	\item Determine the weight factor
-		% 	\begin{equation}
-		% 		\gamma_g^{(r)} = \frac{\mathrm{tr}\Bigl(\bigl({\nabla_g^\mathrm{R}}^{(r)} - {\nabla_g^\mathrm{R}}^{(r-1)}\bigr) {{\nabla_g^\mathrm{R}}^{(r)}}^\mathsf{H}\Bigr)}{\mathrm{tr}\Bigl({\nabla_g^\mathrm{R}}^{(r-1)} {{\nabla_g^\mathrm{R}}^{(r-1)}}^\mathsf{H}\Bigr)};
-		% 		\label{eq:rcg_weight}
-		% 	\end{equation}
-		% 	\item Compute the conjugate direction
-		% 	\begin{equation}
-		% 		\mathbf{D}_g^{(r)} = {\nabla_g^\mathrm{R}}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)};
-		% 		\label{eq:rcg_direction}
-		% 	\end{equation}
-		% 	\item Determine the Armijo step size\footnote{To double the step size, simply square the argument instead of recomputing the matrix exponential, i.e., $\exp(2 \mu_g \mathbf{D}_g) = \exp^2(\mu_g \mathbf{D}_g)$.}
-		% 	\begin{equation}
-		% 		\mu_g^{(r)} = \arg\max_{\mu_g} f\Bigl(\exp\bigl(\mu_g \mathbf{D}_g^{(r)}\bigr) \mathbf{\Theta}_g^{(r)}\Bigr);
-		% 		\label{eq:rcg_step}
-		% 	\end{equation}
-		% 	\item Perform rotational update along local geodesics
-		% 	\begin{equation}
-		% 		\mathbf{\Theta}_g^{(r+1)} = \exp\Bigl(\mu_g^{(r)} \mathbf{D}_g^{(r)}\Bigr) \mathbf{\Theta}_g^{(r)}.
-		% 		\label{eq:rcg_update}
-		% 	\end{equation}
-		% \end{enumerate}
-
-		% \begin{remark}
-		% 	The adapted \gls{rcg} method leverages the fact that block unitary matrices are closed under multiplication (but not necessarily under addition).
-		% 	Its advantage over universal manifold optimization \cite{Absil2009,Pan2022d} is trifold:
-		% 	\begin{itemize}
-		% 		\item No retraction is involved;
-		% 		\item Lower computational complexity per iteration \cite{Abrudan2008};
-		% 		\item Faster convergence thanks appropriate operational space.
-		% 	\end{itemize}
-		% \end{remark}
-
+		Back to the Pareto channel singular value problem \eqref{op:pareto}. The Euclidean gradient of \gls{bd}-\gls{ris} group $g$ is computed as
+		\begin{equation}
+			\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathrm{diag}(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
+			\label{eq:pareto_gradient}
+		\end{equation}
+		where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
+		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto}, where expression \eqref{eq:pareto_gradient} should be used in line \ref{ln:gradient_euclidean}.
 	\end{subsection}
 
-	\begin{subsection}{Analytical Bounds}
-		We then analyze the channel shaping \emph{capability} of \gls{bd}-\gls{ris} under specific setups.
-		\begin{subsubsection}{Rank-Deficient Channel}
-			\label{sc:pc_rank_deficient}
-			In rank-deficient channels, \gls{bd}-\gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
-			This is because $\mathrm{sv}(\mathbf{\Theta}^\mathrm{B}) = \mathrm{sv}(\mathbf{\Theta}^\mathrm{D}) = \boldsymbol{1}$ and
+	\begin{subsection}{Some Analytical Bounds}
+		% We then analyze the channel shaping \emph{capability} of \gls{bd}-\gls{ris} under specific setups.
+		We then discuss some analytical bounds related to channel singular values.
+			% \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
+			\begin{proposition}
+				In rank-deficient point-to-point channel, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
+			\end{proposition}
+			\begin{proof}
+				The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as
 				\begin{equation}
-				\begin{split}
-					\mathrm{rank}(\mathbf{H})
-					& \le \mathrm{rank}(\mathbf{H}^\mathrm{D}) + \mathrm{rank}(\mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F}) \\
-					& \le \mathrm{rank}(\mathbf{H}^\mathrm{D}) + \min \bigl( \mathrm{rank}(\mathbf{H}^\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}), \mathrm{rank}(\mathbf{H}^\mathrm{F}) \bigr).
-				\end{split}
+					\mathbf{\Theta} = \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H},
 				\end{equation}
-			% However, \gls{bd}-\gls{ris} can still guarantee a higher rate at finite \gls{snr}.
-			Note \gls{bd}-\gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
-		\end{subsubsection}
+				where $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block diagonal matrices of $L \times L$ unitary blocks and $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris}.
+				% However, manipulating $\mathbf{L}$ and $\mathbf{R}$ does not change the rank of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$.
+				Manipulating $\mathbf{L}$ and $\mathbf{R}$ only rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and keeps their rank.
+				On the other hand, there exists
+				\begin{equation}
+					\arg_{\mathbf{\Theta}_\mathrm{D}} \max \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F}) = \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr).
+				\end{equation}
+				% Therefore,
+				% \begin{align}
+				% 	\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) & = \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}) \\
+				% 	& = \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \bar{\mathbf{H}}_\mathrm{F}) \\
+				% 	& \le \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr).
+				% \end{align}
+				% On the other hand, we have
+				% \begin{align}
+				% 	\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+				% \end{align}
+				% Therefore,
+				% \begin{align}
+				% 	& \arg_\mathbf{\Theta} \max \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \\
+				% 	= & \arg_{\mathbf{\Theta}_\mathrm{D},\mathbf{L},\mathbf{R}} \max \ \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \bar{\mathbf{H}}_\mathrm{F}) \\
+				% 	= & \arg_{\mathbf{L},\mathbf{R}} \max \  \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr) \\
+				% 	= & \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\mathbf{H}_\mathrm{F}) \bigr).
+				% \end{align}
+				% That is, $\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})$
+				% That is, $\mathrm{rank}(\mathbf{H}) = \mathrm{rank}(\mathbf{H}_\mathrm{D}) + \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \bar{\mathbf{H}}_\mathrm{F})$.
+				% When direct link is present,
+				% does not change the rank of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$.
+				% Although \gls{bd}-\gls{ris} can
+				% It follows straightforwardly from the rank inequality
+				% \begin{equation}
+				% 	\begin{split}
+				% 		\mathrm{rank}(\mathbf{H})
+				% 		& \le \mathrm{rank}(\mathbf{H}_\mathrm{D}) + \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \\
+				% 		& \le \mathrm{rank}(\mathbf{H}_\mathrm{D}) + \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}), \mathrm{rank}(\mathbf{H}^\mathrm{F}) \bigr).
+				% 	\end{split}
+				% \end{equation}
+				% % The \gls{dof} upper bound of \gls{bd}-\gls{ris} $\mathbf{\Theta}_\mathrm{B}$ and diagonal \gls{ris} $\mathbf{\Theta}_\mathrm{D}$ coincide as they are both full-rank with repeating singular value 1.
+				% The \gls{dof} upper bound of \gls{bd}-\gls{ris} and diagonal \gls{ris} coincide because their scattering matrices are both full-rank (with all singular values equal to 1).
+				% On the other hand, diagonal \gls{ris} can already achieve the maximum \gls{dof} $\max(N, U)$
+
+				% ?
+				% \gls{bd}-\gls{ris} and diagonal \gls{ris} are both full-rank with all singular values equal 1, so their \gls{dof} upper bound coincide.
+				% On the other hand, a diagonal $\mathrm{span}(\mathbf{H}_\mathrm{D}) \cap \mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \varnothing$
+				% On the other hand, a diagonal $\mathrm{span}(\mathbf{H}_\mathrm{D}) \cap \mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \varnothing$
+				% diagonal \gls{ris} can already achieve $\mathrm{span}(\mathbf{H}_\mathrm{D}) \cap \mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \varnothing$ by designing the diagonal phase shift matrix.
+				% $\mathrm{span}(\mathbf{H}_\mathrm{D}) \cap \mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \varnothing$
+				% $\mathrm{span}(\mathbf{H}_\mathrm{D})$ and $\mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})$ can be made disjoint by choosing $\mathbf{\Theta}$ properly, so the \gls{dof} lower bound of \gls{bd}-\gls{ris} is no larger than that of diagonal \gls{ris}.
+				% are disjoint, so the \gls{dof} lower bound of \gls{bd}-\gls{ris} is no larger than that of diagonal \gls{ris}.
+				% the linear spans of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$ are disjoint, so the \gls{dof} lower bound of \gls{bd}-\gls{ris} is no larger than that of diagonal \gls{ris}.
+				% using diagonal \gls{ris} can already achieve the upper bound.
+			\end{proof}
+
+		% \begin{subsubsection}{Rank-Deficient Channel}
+		% 	\label{sc:pc_rank_deficient}
+
+		% 	% % In rank-deficient channels, \gls{bd}-\gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
+		% 	% % This is because $\mathrm{sv}(\mathbf{\Theta}^\mathrm{B}) = \mathrm{sv}(\mathbf{\Theta}^\mathrm{D}) = \boldsymbol{1}$ and
+
+		% 	% % However, \gls{bd}-\gls{ris} can still guarantee a higher rate at finite \gls{snr}.
+		% 	% Note \gls{bd}-\gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
+		% \end{subsubsection}
 
@@
 		The complex derivative of \eqref{ob:pc_singular} w.r.t. \gls{ris} block $g$ is
-		\begin{equation}
-			\frac{\partial J_1}{\partial \mathbf{\Theta}_g^*} = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{U} \mathrm{diag}(\boldsymbol{\rho}) \mathbf{V}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H},
-			\label{eq:pc_singular_gradient_ris}
-		\end{equation}
+		% \begin{equation}
+		% 	\frac{\partial J_1}{\partial \mathbf{\Theta}_g^*} = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{U} \mathrm{diag}(\boldsymbol{\rho}) \mathbf{V}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H},
+		% 	\label{eq:pc_singular_gradient_ris}
+		% \end{equation}
 		where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{H}$.

### 2024-02-02 main.tex
:pencil: Add proposition 1 and 2

@@
 	\begin{subsection}{Some Analytical Bounds}
-		% We then analyze the channel shaping \emph{capability} of \gls{bd}-\gls{ris} under specific setups.
 		We then discuss some analytical bounds related to channel singular values.
-			% \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
-			\begin{proposition}
-				In rank-deficient point-to-point channel, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
+		\begin{proposition}[rank-deficient channel]
+			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
 		\end{proposition}
@@
 			\end{equation}
-				where $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block diagonal matrices of $L \times L$ unitary blocks and $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris}.
-				% However, manipulating $\mathbf{L}$ and $\mathbf{R}$ does not change the rank of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$.
-				Manipulating $\mathbf{L}$ and $\mathbf{R}$ only rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and keeps their rank.
-				On the other hand, there exists
-				\begin{equation}
-					\arg_{\mathbf{\Theta}_\mathrm{D}} \max \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F}) = \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr).
-				\end{equation}
-				% Therefore,
-				% \begin{align}
-				% 	\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) & = \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}) \\
-				% 	& = \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \bar{\mathbf{H}}_\mathrm{F}) \\
-				% 	& \le \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr).
-				% \end{align}
-				% On the other hand, we have
-				% \begin{align}
-				% 	\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
-				% \end{align}
-				% Therefore,
-				% \begin{align}
-				% 	& \arg_\mathbf{\Theta} \max \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \\
-				% 	= & \arg_{\mathbf{\Theta}_\mathrm{D},\mathbf{L},\mathbf{R}} \max \ \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \bar{\mathbf{H}}_\mathrm{F}) \\
-				% 	= & \arg_{\mathbf{L},\mathbf{R}} \max \  \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr) \\
-				% 	= & \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\mathbf{H}_\mathrm{F}) \bigr).
-				% \end{align}
-				% That is, $\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})$
-				% That is, $\mathrm{rank}(\mathbf{H}) = \mathrm{rank}(\mathbf{H}_\mathrm{D}) + \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \bar{\mathbf{H}}_\mathrm{F})$.
-				% When direct link is present,
-				% does not change the rank of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$.
-				% Although \gls{bd}-\gls{ris} can
-				% It follows straightforwardly from the rank inequality
-				% \begin{equation}
-				% 	\begin{split}
-				% 		\mathrm{rank}(\mathbf{H})
-				% 		& \le \mathrm{rank}(\mathbf{H}_\mathrm{D}) + \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \\
-				% 		& \le \mathrm{rank}(\mathbf{H}_\mathrm{D}) + \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}), \mathrm{rank}(\mathbf{H}^\mathrm{F}) \bigr).
-				% 	\end{split}
-				% \end{equation}
-				% % The \gls{dof} upper bound of \gls{bd}-\gls{ris} $\mathbf{\Theta}_\mathrm{B}$ and diagonal \gls{ris} $\mathbf{\Theta}_\mathrm{D}$ coincide as they are both full-rank with repeating singular value 1.
-				% The \gls{dof} upper bound of \gls{bd}-\gls{ris} and diagonal \gls{ris} coincide because their scattering matrices are both full-rank (with all singular values equal to 1).
-				% On the other hand, diagonal \gls{ris} can already achieve the maximum \gls{dof} $\max(N, U)$
-
-				% ?
-				% \gls{bd}-\gls{ris} and diagonal \gls{ris} are both full-rank with all singular values equal 1, so their \gls{dof} upper bound coincide.
-				% On the other hand, a diagonal $\mathrm{span}(\mathbf{H}_\mathrm{D}) \cap \mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \varnothing$
-				% On the other hand, a diagonal $\mathrm{span}(\mathbf{H}_\mathrm{D}) \cap \mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \varnothing$
-				% diagonal \gls{ris} can already achieve $\mathrm{span}(\mathbf{H}_\mathrm{D}) \cap \mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \varnothing$ by designing the diagonal phase shift matrix.
-				% $\mathrm{span}(\mathbf{H}_\mathrm{D}) \cap \mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) = \varnothing$
-				% $\mathrm{span}(\mathbf{H}_\mathrm{D})$ and $\mathrm{span}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})$ can be made disjoint by choosing $\mathbf{\Theta}$ properly, so the \gls{dof} lower bound of \gls{bd}-\gls{ris} is no larger than that of diagonal \gls{ris}.
-				% are disjoint, so the \gls{dof} lower bound of \gls{bd}-\gls{ris} is no larger than that of diagonal \gls{ris}.
-				% the linear spans of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$ are disjoint, so the \gls{dof} lower bound of \gls{bd}-\gls{ris} is no larger than that of diagonal \gls{ris}.
-				% using diagonal \gls{ris} can already achieve the upper bound.
+			where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block diagonal matrices of $L \times L$ unitary blocks.
+			Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
+			On the other hand, there exists a $\mathbf{\Theta}_\mathrm{D}$ such that
+			\begin{equation*}
+				\begin{split}
+					\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
+					& = \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\mathbf{H}_\mathrm{F}) \bigr) \\
+					& = \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr) \\
+					& = \max_\mathbf{\Theta} \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+				\end{split}
+			\end{equation*}
+			The same result holds if the direct link is present.
 		\end{proof}
 
-		% \begin{subsubsection}{Rank-Deficient Channel}
-		% 	\label{sc:pc_rank_deficient}
+		\begin{proposition}[\gls{los} forward\footnote{A similar result holds for \gls{los} backward channel.} channel]
+			If the forward channel is rank-1, then \gls{bd}-\gls{ris} can at most enlarge (resp.
+suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
+$n$-th) singular value of $\mathbf{T}$, that is,
+			\begin{equation}
+				\sigma_1(\mathbf{T}) \ge {\color{orange}\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\color{orange}\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}),
+				\label{iq:sv_bound_los}
+			\end{equation}
+			where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{v}_\mathrm{F}$ is the right compact singular vector of $\mathbf{H}_\mathrm{F}$.
+			Note that $\sigma_1(\mathbf{H})$ is unbounded with a sufficiently large \gls{ris}.
+		\end{proposition}
+		\begin{proof}
+			Let $\mathbf{H}_\mathrm{F} = \sigma_\mathrm{F} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ be the compact \gls{svd} of the forward channel.
+			The channel Gram matrix can be written as Hermitian-plus-rank-1:
+			\begin{equation}
+				\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
+			\end{equation}
+			where $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{z} \triangleq \sigma_\mathrm{F} \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{u}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{v}_\mathrm{F}$.
+			By the Cauchy interlacing formula \cite{Golub2013}, the $n$-th ($n \ge 2$) eigenvalues of $\mathbf{G}$ are bounded by
+			\begin{equation}
+				\lambda_1(\mathbf{Y}) \ge \lambda_2(\mathbf{G}) \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge \lambda_N(\mathbf{G}) \ge \lambda_N(\mathbf{Y}).
+				\label{iq:ev_bound_los}
+			\end{equation}
+			Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, the eigenvalues are non-negative and taking the square root of \eqref{iq:ev_bound_los} gives \eqref{iq:sv_bound_los}.
+		\end{proof}
+		It is worth notice that a similar conclusion holds for diagonal \gls{ris} \cite{Semmler2023}.
+		We will later show that for a finite $N_\mathrm{S}$, using a larger group size can better approach those bounds.
 
-		% 	% % In rank-deficient channels, \gls{bd}-\gls{ris} $\mathbf{\Theta}^\mathrm{B}$ cannot achieve a higher \gls{dof} than diagonal \gls{ris} $\mathbf{\Theta}^\mathrm{D}$.
-		% 	% % This is because $\mathrm{sv}(\mathbf{\Theta}^\mathrm{B}) = \mathrm{sv}(\mathbf{\Theta}^\mathrm{D}) = \boldsymbol{1}$ and
-
-		% 	% % However, \gls{bd}-\gls{ris} can still guarantee a higher rate at finite \gls{snr}.
-		% 	% Note \gls{bd}-\gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
-		% \end{subsubsection}
+		\begin{proposition}[fully-connected \gls{ris} without direct link]
+			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			% \begin{equation}
+			% 	\prod_{k \in {K}} \sigma_k(\mathbf{H}) \leq \prod_{i \in {I}} \sigma_i(\mathbf{B}) \prod_{j \in {J}} \sigma_j(\mathbf{F}),
+			% \end{equation}
+			% where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+		\end{proposition}
 

### 2024-02-03 main.tex
:pencil: Update analytical bounds

@@
 		\begin{proof}
-			The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as
+			The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as\footnote{This is because (block) unitary matrices are closed under multiplication.}
 			\begin{equation}
@@
 			\begin{equation}
-				\sigma_1(\mathbf{T}) \ge {\color{orange}\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\color{orange}\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}),
+				\sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}),
 				\label{iq:sv_bound_los}
@@
 		It is worth notice that a similar conclusion holds for diagonal \gls{ris} \cite{Semmler2023}.
-		We will later show that for a finite $N_\mathrm{S}$, using a larger group size can better approach those bounds.
+		We will later show that for a finite $N_\mathrm{S}$, using a larger group size can approach those bounds better.
 
 		\begin{proposition}[fully-connected \gls{ris} without direct link]
-			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-			% \begin{equation}
-			% 	\prod_{k \in {K}} \sigma_k(\mathbf{H}) \leq \prod_{i \in {I}} \sigma_i(\mathbf{B}) \prod_{j \in {J}} \sigma_j(\mathbf{F}),
-			% \end{equation}
-			% where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then
+			\begin{equation}
+				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
+			\end{equation}
+			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
 		\end{proposition}
 
-		\begin{subsubsection}{Rank-1 Indirect Channel}
-			The indirect channel is rank-1 iff the forward or backward channel is rank-1.
-			Let $\mathbf{H}^\mathrm{F} = \sigma^\mathrm{F} \mathbf{u}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}$ without loss of generality.
-			In this case, the channel Gram matrix can be written as Hermitian-plus-rank-1:
+		\begin{proof}
+			Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
+			The scattering matrix of fully-connected \gls{ris} can be decomposed as
 			\begin{equation}
-				\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
+				\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{X} \mathbf{U}_\mathrm{F}^\mathsf{H},
+				\label{eq:scattering_fc}
 			\end{equation}
-			where $\mathbf{Y} \triangleq \mathbf{H}^\mathrm{D} (\mathbf{I} - \mathbf{v}^\mathrm{F} {\mathbf{v}^\mathrm{F}}^\mathsf{H}) \mathbf{H}^\mathrm{D} = \mathbf{T} \mathbf{T}^\mathsf{H}$ and $\mathbf{z} \triangleq \sigma^\mathrm{F} \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{u}^\mathrm{F} + \mathbf{H}^\mathrm{D} \mathbf{v}^\mathrm{F}$.
-			Regardless of \gls{ris} size and structure\footnote{A similar conclusion was made for diagonal \gls{ris} in \cite{Semmler2023}.}, its $n$-th ($n \ge 2$) eigenvalues are bounded by the Cauchy interlacing formula \cite{Golub2013}
+			where $\mathbf{X} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ is a unitary matrix to be designed.
+			The equivalent channel is thus a function of $\mathbf{X}$
 			\begin{equation}
-				\lambda_1(\mathbf{Y}) \ge {\color{blue}\lambda_2(\mathbf{G})} \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge {\color{blue}\lambda_N(\mathbf{G})} \ge \lambda_N(\mathbf{Y}).
+				\mathbf{H} = \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}.
+				\label{eq:channel_equivalent_fc}
 			\end{equation}
-			The equivalent singular value inequality is
+			Since $\mathrm{sv}(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \mathrm{sv}(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
+			\begin{align*}
+				\mathrm{sv}(\mathbf{H}) & = \mathrm{sv}(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})\\
+				& = \mathrm{sv}(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})\\
+				& = \mathrm{sv}(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H})\\
+				& = \mathrm{sv}(\mathbf{BF}),
+			\end{align*}
+			where $\bar{\mathbf{U}}_{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}_{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
+		\end{proof}
+
+		There exist many singular value bounds on the product of two matrices in terms of their own singular values.
+		One comprehensive answer is \cite{Fulton2000}
 		\begin{equation}
-				\sigma_1(\mathbf{T}) \ge {\color{blue}\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\color{blue}\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
-				\label{iq:singular_value_interlacing}
+			\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
+			\label{iq:sv_bound_fc}
 		\end{equation}
-			\eqref{iq:singular_value_interlacing} implies that, if the indirect channel is rank-1, then the \gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$.
-			Note that the largest channel singular value is unbounded with a sufficiently large \gls{ris}.
-		\end{subsubsection}
+		for all admissible triples $(I, J, K) \in T_r^n$ with $r < n$, where
+		\begin{equation}
+			\begin{gathered}
+				% T_r^n \triangleq \Bigl\{(I, J, K) \in U_r^n \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
+				% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
+				T_r^n \triangleq \Bigl\{(I, J, K) \in U_r^n \mid \forall p < r, (F, G, H) \in T_p^r,\\
+				\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
+			\end{gathered}
+		\end{equation}
+		\begin{equation}
+			U_r^n = \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
+		\end{equation}
+		It implies the following special cases:
+		\begin{itemize}
+			\item upper bound on the largest singular value
+			\begin{equation}
+				\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F});
+			\end{equation}
+			\item lower bound on the smallest singular value
+			\begin{equation}
+				\sigma_N(\mathbf{H}) \ge \sigma_N(\mathbf{H}_\mathrm{B}) \sigma_N(\mathbf{H}_\mathrm{F});
+			\end{equation}
+			\item upper bound on the product of first $k$ singular values
+			\begin{equation}
+				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F});
+			\end{equation}
+			\item lower bound on the product of last $k$ singular values
+			\begin{equation}
+				\prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{F});
+			\end{equation}
+			\item upper bound on the sum of first $k$ singular values to the power of $p > 0$
+			\begin{equation}
+				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F});
+				\label{iq:sv_bound_fc_power}
+			\end{equation}
+			when $k = N$ and $p = 2$, it suggests the channel power is upper bounded by the sum of element-wise product of backward and forward subchannel power.
+		\end{itemize}
 
-		\begin{subsubsection}{Fully-Connected \glsentryshort{ris} Without Direct Link}
-			Denote the singular value decomposition of forward / backward channels as $\mathbf{H}^{\mathrm{B}/\mathrm{F}} = \mathbf{U}^{\mathrm{B}/\mathrm{F}} \mathbf{\Sigma}^{\mathrm{B}/\mathrm{F}} {\mathbf{V}^{\mathrm{B}/\mathrm{F}}}^\mathsf{H}$.
-			The composite channel is
-			\begin{equation}
-				\mathbf{H} = \mathbf{H}^\mathrm{B} \mathbf{\Theta} \mathbf{H}^\mathrm{F} = \mathbf{U}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{X} \mathbf{\Sigma}^\mathrm{F} {\mathbf{V}^\mathrm{F}}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{X} = {\mathbf{V}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta} \mathbf{U}^\mathrm{F}$.
-			% Since unitary matrices are closed under multiplication,
-			\begin{proposition}
-				In this case, the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with singular values $\mathbf{\Sigma}^\mathrm{B}$ and $\mathbf{\Sigma}^\mathrm{F}$.
-				% The only singular value bounds applied here are those apply to the singular value bound of $\mathbf{F}\mathbf{B}$
-			\end{proposition}
-			\begin{proof}
-				We first observe that singular value control problem can be solved w.r.t.
-unitary $\mathbf{X}$ and retrieved by $\mathbf{\Theta} = \mathbf{V}^\mathrm{B} \mathbf{X} {\mathbf{U}^\mathrm{F}}^\mathsf{H}$.
-				Also, $\mathrm{sv}(\mathbf{U}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{X} \mathbf{\Sigma}^\mathrm{F} {\mathbf{V}^\mathrm{F}}^\mathsf{H}) = \mathrm{sv}(\bar{\mathbf{U}}^\mathrm{B} \mathbf{\Sigma}^\mathrm{B} \mathbf{\bar{V}}{{}^\mathrm{B}}^\mathsf{H} \bar{\mathbf{U}}^\mathrm{F} \mathbf{\Sigma}^\mathrm{F} \mathbf{\bar{V}}{{}^\mathrm{F}}^\mathsf{H}) = \mathrm{sv}(\mathbf{BF})$ where $\bar{\mathbf{U}}^{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}^{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
-			\end{proof}
-			The problem now becomes, given $\mathbf{\Sigma}^\mathrm{B}$ and $\mathbf{\Sigma}^\mathrm{F}$, what can we say about the singular value of $\mathbf{BF}$.
-			One comprehensive answer is Horn's inequality \cite{Bhatia2001}: for all admissible triples $(I, J, K)$,
-			\begin{equation}
-				\prod_{k \in {K}} \sigma_k(\mathbf{BF}) \leq \prod_{i \in {I}} \sigma_i(\mathbf{B}) \prod_{j \in {J}} \sigma_j(\mathbf{F}).
-			\end{equation}
-			It gives upper bound on the largest singular value and lower bound on the smallest singular value:
-			\begin{align}
-				\sigma_1(\mathbf{BF}) \le \sigma_1(\mathbf{B}) \sigma_1(\mathbf{F})\label{iq:singular_value_largest}\\
-				\sigma_N(\mathbf{BF}) \geq \sigma_N(\mathbf{B}) \sigma_N(\mathbf{F})\label{iq:singular_value_smallest}.
-			\end{align}
-			Another useful result is introduced in \cite{Hogben2013}: for all $p>0$,
-			\begin{equation}
-				\sum_n \sigma_n^p(\mathbf{BF}) \leq \sum_n \sigma_n^p(\mathbf{B}) \sigma_n^p(\mathbf{F})\label{iq:singular_value_power_sum}.
-			\end{equation}
-			When $p=2$, it implies the channel energy is upper bounded by the sum of element-wise power product of the forward and backward channels, as illustrated in Fig.~\subref*{sm:pc_power_bond_nd}.
-			Interestingly, \eqref{iq:singular_value_largest}--\eqref{iq:singular_value_power_sum} are simultaneously tight when $\mathbf{X} = \mathbf{I}$ and $\mathbf{\Theta} = \mathbf{V}^\mathrm{B} {\mathbf{U}^\mathrm{F}}^\mathsf{H}$.
-			This solution was claimed in \cite{Bartoli2023} to achieve channel capacity, but it is not true at moderate \gls{snr}.
-		\end{subsubsection}
+		\begin{remark}
+			Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
+			From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc}, we conclude the off-diagonal entries can enhance the capabilities of
+			\begin{itemize}
+				\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
+				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the components of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by strength, which is optimal by rearrangement inequality.
+			\end{itemize}
+		\end{remark}
 
-		Finally, we characterize the \emph{Pareto frontier} of channel singular values via optimization approach.
-		% \begin{maxi!}
-		% 	{\scriptstyle{\mathbf{\Theta}}}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
-		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		% \end{maxi!}
-
-		% \begin{customopti!}
-		% 	{\underset{\scriptstyle{\mathbf{\Theta}}}{max / min}}{}{J_1 = \sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pc_singular}}{\label{ob:pc_singular}}
-		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		% \end{customopti!}
-
-		where $\rho_n$ is the weight of $n$-th singular value.
-		The complex derivative of \eqref{ob:pc_singular} w.r.t. \gls{ris} block $g$ is
-		% \begin{equation}
-		% 	\frac{\partial J_1}{\partial \mathbf{\Theta}_g^*} = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{U} \mathrm{diag}(\boldsymbol{\rho}) \mathbf{V}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H},
-		% 	\label{eq:pc_singular_gradient_ris}
-		% \end{equation}
-		where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{H}$.
-		\eqref{op:pc_singular} can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:pc_singular_gradient_ris}.
+		Tight bounds are generally unavailable when the direct link exists, as the \gls{ris} needs to balance the backward-forward (multiplicative) and direct-indirect (additive) alignments.
 

### 2024-02-04 main.tex
:pencil: Add AO rate maximization

@@
 \newtheorem{remark}{Remark}
+\newtheorem{lemma}{Lemma}
 
@@
 
-		Back to the Pareto channel singular value problem \eqref{op:pareto}. The Euclidean gradient of \gls{bd}-\gls{ris} group $g$ is computed as
+		% The Pareto singular value problem \eqref{op:pareto} can thus be solved by Algorithm~\ref{ag:rcg}.
+		\begin{lemma}
+			The Euclidean gradient of \eqref{ob:pareto} w.r.t. \gls{bd}-\gls{ris} group $g$ is
 			\begin{equation}
@@
 			where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
-		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto}, where expression \eqref{eq:pareto_gradient} should be used in line \ref{ln:gradient_euclidean}.
+		\end{lemma}
+		\begin{proof}
+			Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the compact \gls{svd} of the equivalent channel.
+			Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
+			\begin{equation}
+				\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*,
+			\end{equation}
+			whose differential w.r.t. $\mathbf{\Theta}_g^*$ is
+			\begin{align*}
+				\partial \sigma_n
+				& = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^*\\
+				& = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}\\
+				& = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\\
+				& = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \cdot \partial \mathbf{\Theta}_g^*).
+			\end{align*}
+			According to \cite{Hjorungnes2007}, the corresponding complex derivative is
+			\begin{equation}
+				\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+				\label{eq:derivative_sv}
+			\end{equation}
+			Linear combination of \eqref{eq:derivative_sv} yields \eqref{eq:pareto_gradient}.
+		\end{proof}
+
+		%  The Euclidean gradient of \gls{bd}-\gls{ris} group $g$ is computed as
+		% where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
+		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto}, where line \ref{ln:gradient_euclidean} uses explicit expression \eqref{eq:pareto_gradient}.
+		% \eqref{eq:pareto_gradient} is used in line \ref{ln:gradient_euclidean}.
 	\end{subsection}
@@
 		\begin{equation}
-			U_r^n = \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
+			U_r^n \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
 		\end{equation}
@@
 			\end{equation}
-			when $k = N$ and $p = 2$, it suggests the channel power is upper bounded by the sum of element-wise product of backward and forward subchannel power.
+			when $k = N$ and $p = 2$, it suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannel.
 		\end{itemize}
@@
 				\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the components of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by strength, which is optimal by rearrangement inequality.
+				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which is optimal by rearrangement inequality.
 			\end{itemize}
@@
 
-		Tight bounds are generally unavailable when the direct link exists, as the \gls{ris} needs to balance the backward-forward (multiplicative) and direct-indirect (additive) alignments.
+		Tight bounds are generally unavailable when \gls{mimo} direct link is present.
+		This is because the \gls{ris} needs to balance the backward-forward (multiplicative) and direct-indirect (additive) subspace alignments.
 
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/pc_singular_pareto.tex}
-			}
-			\caption{Singular value Pareto frontier. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 64, 2)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-			\label{sm:pc_singular_pareto}
-		\end{figure}
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\resizebox{0.65\columnwidth}{!}{
+		% 		\input{assets/simulation/pc_singular_pareto.tex}
+		% 	}
+		% 	\caption{Singular value Pareto frontier. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 64, 2)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
+		% 	\label{sm:pc_singular_pareto}
+		% \end{figure}
 
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/pc_singular_bound.tex}
-			}
-			\caption{Singular value bounds for rank-1 indirect channel.
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\resizebox{0.65\columnwidth}{!}{
+		% 		\input{assets/simulation/pc_singular_bound.tex}
+		% 	}
+		% 	\caption{Singular value bounds for rank-1 indirect channel.
 $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-			\label{sm:pc_singular_bound}
-		\end{figure}
+		% 	\label{sm:pc_singular_bound}
+		% \end{figure}
 
-		The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
-		Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
+		% The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
+		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
 	\end{subsection}
+
+\end{section}
+
+\begin{section}{Rate Maximization}
+	The \gls{mimo} rate maximization problem is formulated w.r.t. joint active and passive beamforming
+	\begin{maxi!}
+		{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
+		\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
+		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+	\end{maxi!}
+	where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the noise power, and $P$ is the transmit power budget.
+	Two methods are proposed below to solve problem \eqref{op:rate}.
+
+	\begin{subsection}{Alternating Optimization}
+		We first consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
+		For a given $\mathbf{W}$, the passive beamforming subproblem is
+		\begin{maxi!}
+			% {\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{Q} (\mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H})}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
+			{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		\end{maxi!}
+		where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
+		\begin{lemma}
+			The Euclidean gradient of \eqref{ob:rate_passive} w.r.t. \gls{bd}-\gls{ris} block $g$ is
+			\begin{equation}
+				\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+				\label{eq:rate_gradient}
+			\end{equation}
+		\end{lemma}
+
+		\begin{proof}
+			The differential of $R$ w.r.t. $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
+			\begin{align*}
+				\partial R
+				& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
+				& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
+				& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
+			\end{align*}
+			and the corresponding complex derivative is \eqref{eq:rate_gradient}.
+		\end{proof}
+		Problem \eqref{op:rate_passive} is then solved by Algorithm \ref{ag:rcg}, where line \ref{ln:gradient_euclidean} uses explicit expression \eqref{eq:rate_gradient}.
+		For a given $\mathbf{\Theta}$, the optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
+		\begin{equation}
+			\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
+		\end{equation}
+		where $\mathbf{V}$ is the right singular matrix of $\mathbf{H}$ and $\mathbf{S}^\star$ is the optimal power allocation matrix obtained by the water-filling algorithm.
+	\end{subsection}
+
+	\begin{subsection}{Low-Complexity Solution}
+
+	\end{subsection}
+
+	% \begin{figure}[!t]
+	% 	\centering
+	% 	\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{sm:pc_rate_sx}]{
+	% 		\resizebox{0.48\columnwidth}{!}{
+	% 			\input{assets/simulation/pc_rate_sx.tex}
+	% 		}
+	% 	}
+	% 	\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{sm:pc_rate_tx}]{
+	% 		\resizebox{0.48\columnwidth}{!}{
+	% 			\input{assets/simulation/pc_rate_tx.tex}
+	% 		}
+	% 	}
+	% 	\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+	% 	\label{sm:pc_rate}
+	% \end{figure}
+
+	% Fig.~\ref{sm:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
+	% To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
+	% This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
+	% If tetrads can be formed in \gls{bd}-\gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
+	% Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
+	% We thus conclude dyadic or tetradic \gls{bd}-\gls{ris} usually strike a good balance between performance and complexity.
+
 	\begin{subsection}{Channel Power Maximization}
@@
 		% When the direct link is absent, a large $L$ can align the forward-backward eigenspace but cannot preserve the forward-backward power balance.
-	\end{subsection}
-
-	\begin{subsection}{Rate Maximization}
-		The problem is formulated w.r.t. precoder (instead of transmit covariance matrix) for reference:
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:pc_rate}}{\label{ob:pc_rate}}
-			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{\label{cs:pc_rate_unitary}}
-		\end{maxi!}
-
-		\eqref{op:pc_rate} is jointly non-convex and solved by \gls{ao}.
-		For a given $\mathbf{\Theta}$, the optimal precoder is given by
-		\begin{equation}
-			\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
-		\end{equation}
-		where $\mathbf{V}$ is right singular matrix of $\mathbf{H}$ and $\mathbf{S}^\star$ is a diagonal matrix of the water-filling power allocation.
-		For a given $\mathbf{W}$,
-		The complex derivative of \eqref{ob:pc_rate} w.r.t. \gls{ris} block $g$ is
-		\begin{equation}
-			\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{HW} \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)^{-1} \mathbf{W}^\mathsf{H} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H}.
-			\label{eq:pc_rate_gradient_ris}
-		\end{equation}
-		Algorithm~\ref{ag:pc_rate_ris} summarizes the adapted \gls{rcg} method for the \gls{ris} rate maximization subproblem.
-
-		\setalgorithmcaptionfont{\small}
-		\begin{algorithm}[!t]
-			\small
-			\caption{\gls{rcg} Method for \gls{ris} \gls{mimo}-\gls{pc} Rate Maximization}
-			\label{ag:pc_rate_ris}
-			\begin{algorithmic}[1]
-				\Require $\mathbf{H}^\mathrm{D}$, $\mathbf{H}^\mathrm{F}$, $\mathbf{H}^\mathrm{B}$, $\mathbf{W}$, $L$, $\eta$
-				\Ensure $\mathbf{\Theta}^\star$
-				\State $r \gets 0$, $\mathbf{\Theta}^{(0)}$
-				\Repeat
-					\State $r \gets r+1$
-					\For {$g \gets 1$ to $G$}
-						\State $\mathbf{\Theta}_g^{(r)} \gets$ \eqref{eq:pc_rate_gradient_ris}, \eqref{eq:rcg_gradient_riemannian}--\eqref{eq:rcg_update}
-					\EndFor
-				\Until $\lvert R^{(r)} - R^{(r-1)} \rvert / R^{(r-1)} \le \epsilon$
-			\end{algorithmic}
-		\end{algorithm}
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{sm:pc_rate_sx}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_rate_sx.tex}
-				}
-			}
-			\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{sm:pc_rate_tx}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_rate_tx.tex}
-				}
-			}
-			\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-			\label{sm:pc_rate}
-		\end{figure}
-
-		Fig.~\ref{sm:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
-		To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
-		This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
-		If tetrads can be formed in \gls{bd}-\gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
-		Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
-		We thus conclude dyadic or tetradic \gls{bd}-\gls{ris} usually strike a good balance between performance and complexity.
 	\end{subsection}

### 2024-02-05 main.tex
:pencil: Update low-complexity solution

@@
 \newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
+\newacronym{sca}{SCA}{Successive Convex Approximation}
 
@@
 	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), $r$-th iterated point, and final solution, respectively.
+	$(\cdot)_{[x:y]}$ is a shortcut for $(\cdot)_x,(\cdot)_{x+1},\ldots,(\cdot)_y$.
 	$\lvert \cdot \rvert$ denotes the absolute value.
-	$\lVert \cdot \rVert _p$ means the $p$-norm and $\lVert \cdot \rVert$ suggests $p = 2$.
+	% $\lVert \cdot \rVert _p$ means the $p$-norm and $\lVert \cdot \rVert$ suggests $p = 2$.
+	$\lVert \cdot \rVert$ means the Euclidean norm.
 	$\lVert \cdot \rVert _\mathrm{F}$ represents the Frobenius norm.
+	$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
 	$\sim$ means ``distributed as''.
-	$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
 \end{section}
@@
 		Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
-		Convergence to stationary points is guaranteed as updating each block iteratively does not reduce the objective function.
+		Convergence to stationary points is guaranteed.
 
@@
 		% where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
-		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto}, where line \ref{ln:gradient_euclidean} uses explicit expression \eqref{eq:pareto_gradient}.
+		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto} where line \ref{ln:gradient_euclidean} uses \eqref{eq:pareto_gradient} explicitly.
 		% \eqref{eq:pareto_gradient} is used in line \ref{ln:gradient_euclidean}.
@@
 				\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which is optimal by rearrangement inequality.
+				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains maximal in rearrangement inequality.
 			\end{itemize}
@@
 	\begin{subsection}{Alternating Optimization}
-		We first consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
+		Consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
 		For a given $\mathbf{W}$, the passive beamforming subproblem is
@@
 		\end{proof}
-		Problem \eqref{op:rate_passive} is then solved by Algorithm \ref{ag:rcg}, where line \ref{ln:gradient_euclidean} uses explicit expression \eqref{eq:rate_gradient}.
-		For a given $\mathbf{\Theta}$, the optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
+		% Problem \eqref{op:rate_passive} is then solved by Algorithm \ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
+		% Problem \eqref{op:rate_passive} is then solved by Algorithm \ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
+		Algorithm \ref{ag:rcg} is then invoked to solve problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
+		Since \eqref{ob:rate_passive} is a concave function of $\mathbf{\Theta}$, convergence to local-optimal points is guaranteed.
+		On the other hand, the global optimal transmit precoder for a fixed $\mathbf{\Theta}$ is given by the eigenmode transmission \cite{Clerckx2013}
+		% For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
 		\begin{equation}
 			\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
+			\label{eq:precoder_eigenmode}
 		\end{equation}
-		where $\mathbf{V}$ is the right singular matrix of $\mathbf{H}$ and $\mathbf{S}^\star$ is the optimal power allocation matrix obtained by the water-filling algorithm.
+		where $\mathbf{V}$ is the right channel singular matrix and $\mathbf{S}^\star$ is the optimal water-filling power allocation matrix.
+		The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded from above.
+		% is a first-order method to \eqref{op:rate_passive} and the water-filling algorithm is a global optimal solution to the convex problem \eqref{op:rate}.
 	\end{subsection}
@@
 	\begin{subsection}{Low-Complexity Solution}
+		We then propose a low-complexity solution to problem \eqref{op:rate} inspired by channel shaping.
+		The passive beamforming subproblem \eqref{op:rate_passive} involves transmit covariance matrix $\mathbf{Q}$ and thus requires iterative \gls{rcg} update.
+		Instead, we decouple the joint \gls{ris}-transceiver design by recasting \eqref{op:rate_passive} as channel power maximization
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		\end{maxi!}
+		which only accounts for channel characteristics but is still non-trivial.
+		Inspired by \cite{Nie2017}, we successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each iteration in closed form.
+		% approximate the quadratic objective \eqref{ob:power_passive} with a sequence of affines and solve each problem
+		% iterative algorithm to solve \eqref{op:pc_power}.
+		% The idea is to successively approximate the quadratic objective with a sequence of affine functions and solve the resulting subproblems in closed form.
 
+		\begin{proposition}
+			Start from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
+			\begin{equation}
+				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+			\end{equation}
+			converges to a local-optimal point of \eqref{op:pc_power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right singular matrix of
+			\begin{equation}
+				% \mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Phi}_g^{(r)} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+				% \mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}(\mathbf{\Theta}_1^{(r+1)},\ldots,\mathbf{\Theta}_{g-1}^{(r+1)},\mathbf{\Theta}_g^{(r)},\ldots,\mathbf{\Theta}_G^{(r)}) \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+				% \mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_g^{(r)} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
+			\end{equation}
+			% where $\mathbf{H}_g^{(r)} \triangleq \mathbf{H}_\mathrm{B} \mathrm{diag}(\mathbf{\Theta}_1^{(r+1)},\ldots,\mathbf{\Theta}_{g-1}^{(r+1)},\mathbf{\Theta}_g^{(r)},\ldots,\mathbf{\Theta}_G^{(r)}) \mathbf{H}_\mathrm{F}$.
+			% \begin{equation}
+			% 	\begin{split}
+			% 		\mathbf{M}_g^{(r)}
+			% 		& = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{H}^\mathrm{D} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H} + \sum_{g' < g} {\mathbf{H}_{g'}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{g'}^\mathrm{B} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{g'}^\mathrm{F} {\mathbf{H}_{g'}^\mathrm{F}}^\mathsf{H} \\
+			% 		& \quad + \sum_{g' \ge g} {\mathbf{H}_{g'}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{g'}^\mathrm{B} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{g'}^\mathrm{F} {\mathbf{H}_{g'}^\mathrm{F}}^\mathsf{H}.
+			% 	\end{split}
+			% \end{equation}
+		\end{proposition}
+
+		\begin{proof}
+			To be added.
+		\end{proof}
 	\end{subsection}
@@
 		\end{remark}
-
-		Inspired by \cite{Nie2017}, we propose an iterative algorithm to solve \eqref{op:pc_power}.
-		The idea is to successively approximate the quadratic objective with a sequence of affine functions and solve the resulting subproblems in closed form.
-
-		\begin{proposition}
-			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
-			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-			\end{equation}
-			converges to a stationary point of \eqref{op:pc_power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
-			\begin{equation}
-				\begin{split}
-					\mathbf{M}_g^{(r)}
-					& = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{H}^\mathrm{D} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H} + \sum_{g' < g} {\mathbf{H}_{g'}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{g'}^\mathrm{B} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{g'}^\mathrm{F} {\mathbf{H}_{g'}^\mathrm{F}}^\mathsf{H} \\
-					& \quad + \sum_{g' \ge g} {\mathbf{H}_{g'}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{g'}^\mathrm{B} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{g'}^\mathrm{F} {\mathbf{H}_{g'}^\mathrm{F}}^\mathsf{H}.
-				\end{split}
-			\end{equation}
-		\end{proposition}
-
-		\begin{proof}
-			To be added.
-		\end{proof}
 

### 2024-02-06 main.tex
:pencil: Update proposition 4

@@
 \newacronym{sca}{SCA}{Successive Convex Approximation}
+\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
 
@@
 	$\mathbf{0}$ and $\mathbf{I}$ are the all-zero and identity matrices with appropriate size, respectively.
+	$\Re\{\cdot\}$ takes the real part of a complex number.
 	$\mathrm{tr}(\cdot)$ and $\det(\cdot)$ evaluates the trace and determinant of a square matrix, respectively.
@@
 				& = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}\\
-				& = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\\
-				& = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \cdot \partial \mathbf{\Theta}_g^*).
+				& = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\\
+				& = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
 			\end{align*}
@@
 		\begin{maxi!}
-			% {\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{Q} (\mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H})}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
 			{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
@@
 		\end{proof}
-		% Problem \eqref{op:rate_passive} is then solved by Algorithm \ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
-		% Problem \eqref{op:rate_passive} is then solved by Algorithm \ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
 		Algorithm \ref{ag:rcg} is then invoked to solve problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
@@
 		On the other hand, the global optimal transmit precoder for a fixed $\mathbf{\Theta}$ is given by the eigenmode transmission \cite{Clerckx2013}
-		% For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
 		\begin{equation}
@@
 		The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded from above.
-		% is a first-order method to \eqref{op:rate_passive} and the water-filling algorithm is a global optimal solution to the convex problem \eqref{op:rate}.
 	\end{subsection}
@@
 	\begin{subsection}{Low-Complexity Solution}
-		We then propose a low-complexity solution to problem \eqref{op:rate} inspired by channel shaping.
+		We then propose a low-complexity solution to problem \eqref{op:rate} based on channel shaping.
 		The passive beamforming subproblem \eqref{op:rate_passive} involves transmit covariance matrix $\mathbf{Q}$ and thus requires iterative \gls{rcg} update.
@@
 		\end{maxi!}
-		which only accounts for channel characteristics but is still non-trivial.
+		which only accounts for channel characteristics but has no trivial solution.
 		Inspired by \cite{Nie2017}, we successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each iteration in closed form.
-		% approximate the quadratic objective \eqref{ob:power_passive} with a sequence of affines and solve each problem
-		% iterative algorithm to solve \eqref{op:pc_power}.
-		% The idea is to successively approximate the quadratic objective with a sequence of affine functions and solve the resulting subproblems in closed form.
 
@@
 			\end{equation}
-			converges to a local-optimal point of \eqref{op:pc_power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right singular matrix of
+			converges to a stationary point of \eqref{op:pc_power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
 			\begin{equation}
-				% \mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Phi}_g^{(r)} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-				% \mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}(\mathbf{\Theta}_1^{(r+1)},\ldots,\mathbf{\Theta}_{g-1}^{(r+1)},\mathbf{\Theta}_g^{(r)},\ldots,\mathbf{\Theta}_G^{(r)}) \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
 				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-				% \mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_g^{(r)} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
 			\end{equation}
-			% where $\mathbf{H}_g^{(r)} \triangleq \mathbf{H}_\mathrm{B} \mathrm{diag}(\mathbf{\Theta}_1^{(r+1)},\ldots,\mathbf{\Theta}_{g-1}^{(r+1)},\mathbf{\Theta}_g^{(r)},\ldots,\mathbf{\Theta}_G^{(r)}) \mathbf{H}_\mathrm{F}$.
-			% \begin{equation}
-			% 	\begin{split}
-			% 		\mathbf{M}_g^{(r)}
-			% 		& = {\mathbf{H}_g^\mathrm{B}}^\mathsf{H} \mathbf{H}^\mathrm{D} {\mathbf{H}_g^\mathrm{F}}^\mathsf{H} + \sum_{g' < g} {\mathbf{H}_{g'}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{g'}^\mathrm{B} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{g'}^\mathrm{F} {\mathbf{H}_{g'}^\mathrm{F}}^\mathsf{H} \\
-			% 		& \quad + \sum_{g' \ge g} {\mathbf{H}_{g'}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{g'}^\mathrm{B} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{g'}^\mathrm{F} {\mathbf{H}_{g'}^\mathrm{F}}^\mathsf{H}.
-			% 	\end{split}
-			% \end{equation}
 		\end{proposition}
@@
 		\begin{proof}
-			To be added.
+			The differential of \eqref{ob:power_passive} w.r.t. $\mathbf{\Theta}_g^*$ is
+			\begin{align*}
+				\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
+				& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr)\\
+				& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
+			\end{align*}
+			and the corresponding complex derivative is
+			\begin{equation}
+				\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{M}_g.
+			\end{equation}
+			% For a given $\mathbf{\Theta}$, we approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansion and recast problem \eqref{op:power_passive} as
+
+			First, we approximate the quadratic objective \eqref{ob:power_passive} by its local Taylor expansion
+			\begin{maxi!}
+				{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_passive_approx}}{\label{ob:power_passive_approx}}
+				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
+			\end{maxi!}
+			Let $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$ be the compact \gls{svd} of $\mathbf{M}_g$.
+			We have
+			\begin{equation}
+				\Re \bigl\{\mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \mathrm{tr}(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \mathrm{tr}(\mathbf{\Sigma}_g).
+			\end{equation}
+			The upper bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$, which implies the optimal solution of \eqref{op:power_passive_approx} is $\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$, $\forall g$.
+
+			Next, we prove that solving \eqref{op:power_passive_approx} successively does not decrease \eqref{ob:power_passive}.
+			Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
+			% Expanding both side gives \eqref{iq:power_passive_approx}.
+			On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:nonnegative_norm_square}.
+			Adding \eqref{iq:power_passive_approx} and \eqref{iq:nonnegative_norm_square}, we have
+			\begin{multline}
+				2 \Re \Bigl\{\mathrm{tr}(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
+				\ge 2 \Re \Bigl\{\mathrm{tr}({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
+			\end{multline}
+			which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
+			\begin{figure*}
+				\begin{equation}
+					\label{iq:power_passive_approx}
+					\resizebox{0.95\textwidth}{!}{
+						$2 \Re \Bigl\{\sum\limits_g \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \mathrm{tr}({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
+					}
+				\end{equation}
+				\begin{equation}
+					\label{iq:nonnegative_norm_square}
+					\resizebox{0.95\textwidth}{!}{
+						$\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
+					}
+				\end{equation}
+				\hrulefill
+			\end{figure*}
+
+			Finally, we prove that the converging point of \eqref{op:power_passive_approx}, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power_passive}.
+			The \gls{kkt} conditions of \eqref{op:power_passive} and \eqref{op:power_passive_approx} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
+			\begin{gather}
+				\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_passive_stationary}\\
+				\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_passive_approx_stationary}
+			\end{gather}
+			On convergence, \eqref{eq:power_passive_approx_stationary} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
+\mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^?
+\mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_passive_stationary}.
+			The proof is thus completed.
+			% As for the stat
+			% The Lagrangian of problem \eqref{op:power_passive} and \eqref{op:power_passive_approx} are respectively
+			% \begin{align}
+			% 	\mathcal{L}(\mathbf{\Theta},\mathbf{\Lambda}) & = \sum_g 2 \Re \bigl\{\mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} + \sum_g \mathrm{tr} \bigl(\mathbf{\Lambda}_g^\mathsf{H} (\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g - \mathbf{I})\bigr),\\
+			% 	\mathcal{L}(\mathbf{\Theta},\mathbf{\Lambda}) & = \lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 + \sum_g \mathrm{tr} \bigl(\mathbf{\Lambda}_g^\mathsf{H} (\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g - \mathbf{I})\bigr),
+			% \end{align}
+			% That is, we only need to show the stationary condition of \eqref{op:power_passive} is satisfied by $\tilde{\mathbf{\Theta}}^?$.
+			% Let $\tilde{\mathbf{\Theta}}^?$ be the converging point of \eqref{op:power_passive_approx}, which satisfies the \gls{kkt} conditions
+
+			% The Lagrangian of problem \eqref{op:power_passive} is
+			% \begin{equation}
+			% 	\mathcal{L}(\mathbf{\Theta},\mathbf{\Theta}^*) = \lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 + \sum_g \mathrm{tr} \bigl(\mathbf{\Lambda}_g^\mathsf{H} (\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g - \mathbf{I})\bigr),
+			% \end{equation}
 		\end{proof}

### 2024-02-08 main.tex
:pencil: Add parameters

@@
 	% $\boldsymbol{\sigma}(\cdot)$ and $\boldsymbol{\lambda}(\cdot)$ are the corresponding vectors.
-	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), $r$-th iterated point, and final solution, respectively.
+	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^\dagger$ $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), Moore-Penrose inverse, $r$-th iterated point, and final solution, respectively.
 	$(\cdot)_{[x:y]}$ is a shortcut for $(\cdot)_x,(\cdot)_{x+1},\ldots,(\cdot)_y$.
@@
 
-\begin{section}{Channel Singular Value Redistribution}
+\begin{section}{Channel Singular Values Redistribution}
 	\begin{subsection}{A Toy Example}
@@
 		% The Pareto singular value problem \eqref{op:pareto} can thus be solved by Algorithm~\ref{ag:rcg}.
-		\begin{lemma}
+		\begin{lemma}\label{lm:pareto_gradient}
 			The Euclidean gradient of \eqref{ob:pareto} w.r.t. \gls{bd}-\gls{ris} group $g$ is
@@
 
-	\begin{subsection}{Some Analytical Bounds}
+	\begin{subsection}{Some Analytical Bounds}\label{ss:bounds}
 		We then discuss some analytical bounds related to channel singular values.
-		\begin{proposition}[rank-deficient channel]
+		\begin{proposition}[rank-deficient channel]\label{pp:dof}
 			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
@@
 
-		\begin{proposition}[\gls{los} forward\footnote{A similar result holds for \gls{los} backward channel.} channel]
+		\begin{proposition}[\gls{los} forward\footnote{A similar result holds for \gls{los} backward channel.} channel]\label{pp:los}
 			If the forward channel is rank-1, then \gls{bd}-\gls{ris} can at most enlarge (resp.
@@
 				\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains maximal in rearrangement inequality.
+				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximal in rearrangement inequality.
 			\end{itemize}
@@
 		Tight bounds are generally unavailable when \gls{mimo} direct link is present.
-		This is because the \gls{ris} needs to balance the backward-forward (multiplicative) and direct-indirect (additive) subspace alignments.
-
-		% \begin{figure}[!t]
-		% 	\centering
-		% 	\resizebox{0.65\columnwidth}{!}{
-		% 		\input{assets/simulation/pc_singular_pareto.tex}
-		% 	}
-		% 	\caption{Singular value Pareto frontier. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 64, 2)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-		% 	\label{sm:pc_singular_pareto}
-		% \end{figure}
-
-		% \begin{figure}[!t]
-		% 	\centering
-		% 	\resizebox{0.65\columnwidth}{!}{
-		% 		\input{assets/simulation/pc_singular_bound.tex}
-		% 	}
-		% 	\caption{Singular value bounds for rank-1 indirect channel.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-		% 	\label{sm:pc_singular_bound}
-		% \end{figure}
-
-		% The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
-		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
+		This is because the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
 	\end{subsection}
@@
 
-\begin{section}{Rate Maximization}
-	The \gls{mimo} rate maximization problem is formulated w.r.t. joint active and passive beamforming
+\begin{section}{Achievable Rate Maximization}
+	The \gls{mimo} achievable rate maximization problem is formulated w.r.t. joint active and passive beamforming
 	\begin{maxi!}
@@
 		where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-		\begin{lemma}
+		\begin{lemma}\label{lm:rate_gradient}
 			The Euclidean gradient of \eqref{ob:rate_passive} w.r.t. \gls{bd}-\gls{ris} block $g$ is
@@
 			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
 		\end{maxi!}
-		which only accounts for channel characteristics but has no trivial solution.
+		% which only accounts for channel characteristics but has no trivial solution.
+		\begin{remark}
+			As mentioned in Section \ref{ss:bounds}, the key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
+			Problem \eqref{op:power_passive} is very similar (in terms of maximizing the inner product of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$) to the weighted orthogonal Procrustes problem \cite{Gower2004}
+			\begin{mini!}
+				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
+				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
+			\end{mini!}
+			which has no trivial solution.
+			One lossy transformation, by moving $\mathbf{\Theta}$ to one side \cite{Bell2003}, formulates standard orthogonal Procrustes problems
+			\begin{mini!}
+				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
+				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
+			\end{mini!}
+			which has global optimal solutions $\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}$ where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
+			This naive solution will be compared with the one proposed below.
+		\end{remark}
+
 		Inspired by \cite{Nie2017}, we successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each iteration in closed form.
 
-		\begin{proposition}
+		\begin{proposition}\label{pp:power}
 			Start from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
@@
 			\end{equation}
-			converges to a stationary point of \eqref{op:pc_power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
+			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
 			\begin{equation}
@@
 			\end{multline}
-			which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
+			which confirms that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
 			\begin{figure*}
@@
 \mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_passive_stationary}.
-			The proof is thus completed.
-			% As for the stat
-			% The Lagrangian of problem \eqref{op:power_passive} and \eqref{op:power_passive_approx} are respectively
-			% \begin{align}
-			% 	\mathcal{L}(\mathbf{\Theta},\mathbf{\Lambda}) & = \sum_g 2 \Re \bigl\{\mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} + \sum_g \mathrm{tr} \bigl(\mathbf{\Lambda}_g^\mathsf{H} (\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g - \mathbf{I})\bigr),\\
-			% 	\mathcal{L}(\mathbf{\Theta},\mathbf{\Lambda}) & = \lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 + \sum_g \mathrm{tr} \bigl(\mathbf{\Lambda}_g^\mathsf{H} (\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g - \mathbf{I})\bigr),
-			% \end{align}
-			% That is, we only need to show the stationary condition of \eqref{op:power_passive} is satisfied by $\tilde{\mathbf{\Theta}}^?$.
-			% Let $\tilde{\mathbf{\Theta}}^?$ be the converging point of \eqref{op:power_passive_approx}, which satisfies the \gls{kkt} conditions
-
-			% The Lagrangian of problem \eqref{op:power_passive} is
-			% \begin{equation}
-			% 	\mathcal{L}(\mathbf{\Theta},\mathbf{\Theta}^*) = \lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 + \sum_g \mathrm{tr} \bigl(\mathbf{\Lambda}_g^\mathsf{H} (\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g - \mathbf{I})\bigr),
-			% \end{equation}
+			The proof is completed.
 		\end{proof}
+		Once the channel shaping problem \eqref{op:power_passive} is solved, the transmit precoder can be obtained by \eqref{eq:precoder_eigenmode}.
+		This two-stage approach decouples both blocks and is computationally efficient.
 	\end{subsection}
@@
 
-	\begin{subsection}{Channel Power Maximization}
-		Consider a \gls{bd}-\gls{ris} with $N^\mathrm{S}$ elements, which is divided into $G$ groups of equal $L$ elements.
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\left\lVert \mathbf{H}^\mathrm{D} + \sum_g\nolimits \mathbf{H}_g^\mathrm{B} \mathbf{\Theta}_g \mathbf{H}_g^\mathrm{F} \right\rVert _\mathrm{F}^2}{\label{op:pc_power}}{}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g \in \mathcal{G} \triangleq \{1,\ldots,G\}.}{}{}
-		\end{maxi!}
-		For \emph{symmetric} BD-RIS, the problem has been solved in
-		\begin{itemize}
-			\item Matteo's paper \cite{Nerini2023}: SISO and equivalent\footnote{Single-stream MIMO with given precoder and combiner.};
-			\item Ignacio's paper \cite{Santamaria2023}: SISO and directless MISO/SIMO.
-		\end{itemize}
-
-		\begin{remark}
-			% The difficulty of \eqref{op:pc_power} is that the \gls{ris} needs to balance the (additive) direct-indirect eigenspace alignment and the (multiplicative) forward-backward eigenspace alignment.
-			The difficulty of \eqref{op:pc_power} is that the \gls{ris} needs to balance the additive (direct-indirect) and multiplicative (forward-backward) eigenspace alignment.
-			% align the direct and indirect eigenspaces while preserving the
-			Interestingly, it has the same form as the \emph{weighted orthogonal Procrustes problem} \cite{Gower2004}:
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{C} - \mathbf{A \Theta B} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I}.}{}{}
-			\end{mini!}
-			There exists no trivial solution to \eqref{op:weighted_orthogonal_procrustes}.
-			One lossy transformation, by moving $\mathbf{\Theta}$ to one side \cite{Bell2003}, formulates a standard orthogonal Procrustes problem:
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{A}^\dagger \mathbf{C} - \mathbf{\Theta B} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I}.}{}{}
-			\end{mini!}
-			\eqref{op:standard_orthogonal_procrustes} has a global optimal solution $\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}$, where $\mathbf{U}$ and $\mathbf{V}$ are left and right singular matrix of $\mathbf{\mathbf{A}^\dagger \mathbf{C} \mathbf{B}^\mathsf{H}}$ \cite{Golub2013}.
-			This low-complexity solution will be compared with the one proposed later.
-		\end{remark}
-
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\resizebox{0.65\columnwidth}{!}{
+		% 		\input{assets/simulation/pc_power_sx.tex}
+		% 	}
+		% 	\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
+$(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+		% 	\label{sm:pc_power_sx}
+		% \end{figure}
+
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\subfloat[Without Direct Link\label{sm:pc_power_bond_nd}]{
+		% 		\resizebox{0.48\columnwidth}{!}{
+		% 			\input{assets/simulation/pc_power_bond_nd.tex}
+		% 		}
+		% 	}
+		% 	\subfloat[With Direct Link\label{sm:pc_power_bond_hd}]{
+		% 		\resizebox{0.48\columnwidth}{!}{
+		% 			\input{assets/simulation/pc_power_bond_hd.tex}
+		% 		}
+		% 	}
+		% 	\caption{Average channel power versus \gls{ris} group size $L$.
+$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
+		% 	\label{sm:pc_power_bond}
+		% \end{figure}
+		% % Fig.~\ref{sm:pc_power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
+		% % Fig.~\ref{sm:pc_power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
+		% Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
+		% % The behavior is more obvious for a large \gls{ris}.
+		% This behavior is more pronounced for a large \gls{ris}.
+		% For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
+		% % \gls{bd}-\gls{ris} provides a higher channel power than conventional \gls{ris}.
+		% % As $L$ increases from 1 to 2,
+		% It implies that the channel shaping capability of \gls{bd}-\gls{ris} scales with group size $L$.
+
+		% Fig.~\ref{sm:pc_power_bond_hd} and \ref{sm:pc_power_bond_nd} compare the average channel power without and with direct link.
+		% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
+		% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
+		% % ``Cascaded'' means the maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
+		% % maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
+		% % ? ``Cascaded'' means the \emph{power product} of the forward and backward channels.
+		% % ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues of the forward and backward channels.
+		% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
+		% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect eigenspace.
+		% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
+		% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward eigenspace alignment for an optimal channel boost.
+		% It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
+		% This again emphasizes the advantage of in-group connection of \gls{bd}-\gls{ris}.
+		% % This is because the direct and indirect channels superpose
+		% % the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
+		% % When the direct link is present, a small $L$ cannot align the direct-indirect eigenspace.
+
+		% % neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect eigenspace.
+		% % We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect eigenspace.
+		% % For conventional \gls{ris},
+		% % align the direct-indirect eigenspace.
+		% % When the direct link is present, a small $L$ can neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
+		% % For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
+		% % neither the direct-indirect nor the forward-backward eigenspace can be effectively aligned with a small $L$.
+
+		% % When the direct link is present, a small $L$ can neither preserve the
+		% % neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
+
+		% % When the direct link is absent, a large $L$ can align the forward-backward eigenspace but cannot preserve the forward-backward power balance.
+
+\end{section}
+
+\begin{section}{Simulation Results}
+	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
+	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
+	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
+	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$, $\gamma_\mathrm{B}=2$, $\kappa_\mathrm{D}=\kappa_\mathrm{F}=\kappa_\mathrm{B}=5$ for reference, which corresponds to an indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
+
+	\begin{subsection}{Channel Singular Values Redistribution}
 		\begin{figure}[!t]
@@
 			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/pc_power_sx.tex}
+				\input{assets/simulation/pc_singular_pareto.tex}
 			}
-			\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
-$(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-			\label{sm:pc_power_sx}
+			\caption{Singular value bounds for rank-1 indirect channel.
+$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
+			\label{fg:pc_singular_pareto}
 		\end{figure}
 
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Without Direct Link\label{sm:pc_power_bond_nd}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_power_bond_nd.tex}
-				}
-			}
-			\subfloat[With Direct Link\label{sm:pc_power_bond_hd}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_power_bond_hd.tex}
-				}
-			}
-			\caption{Average channel power versus \gls{ris} group size $L$.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-			\label{sm:pc_power_bond}
-		\end{figure}
-		% Fig.~\ref{sm:pc_power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
-		% Fig.~\ref{sm:pc_power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
-		Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
-		% The behavior is more obvious for a large \gls{ris}.
-		This behavior is more pronounced for a large \gls{ris}.
-		For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
-		% \gls{bd}-\gls{ris} provides a higher channel power than conventional \gls{ris}.
-		% As $L$ increases from 1 to 2,
-		It implies that the channel shaping capability of \gls{bd}-\gls{ris} scales with group size $L$.
-
-		Fig.~\ref{sm:pc_power_bond_hd} and \ref{sm:pc_power_bond_nd} compare the average channel power without and with direct link.
-		% where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-		% where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-		% ``Cascaded'' means the maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-		% maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-		% ? ``Cascaded'' means the \emph{power product} of the forward and backward channels.
-		% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues of the forward and backward channels.
-		``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
-		We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect eigenspace.
-		When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
-		When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward eigenspace alignment for an optimal channel boost.
-		It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
-		This again emphasizes the advantage of in-group connection of \gls{bd}-\gls{ris}.
-		% This is because the direct and indirect channels superpose
-		% the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
-		% When the direct link is present, a small $L$ cannot align the direct-indirect eigenspace.
-
-		% neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect eigenspace.
-		% We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect eigenspace.
-		% For conventional \gls{ris},
-		% align the direct-indirect eigenspace.
-		% When the direct link is present, a small $L$ can neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
-		% For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
-		% neither the direct-indirect nor the forward-backward eigenspace can be effectively aligned with a small $L$.
-
-		% When the direct link is present, a small $L$ can neither preserve the
-		% neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
-
-		% When the direct link is absent, a large $L$ can align the forward-backward eigenspace but cannot preserve the forward-backward power balance.
+		The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:pc_singular_pareto}.
+		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:pc_singular_pareto}.
+		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:pc_singular_pareto}.
+		% Clearly, a larger group size provides
+		% and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
+		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
 	\end{subsection}
-
+	% [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);
+
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\resizebox{0.65\columnwidth}{!}{
+		% 		\input{assets/simulation/pc_singular_bound.tex}
+		% 	}
+		% 	\caption{Singular value bounds for rank-1 indirect channel.
+$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
+		% 	\label{sm:pc_singular_bound}
+		% \end{figure}
+
+		% The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
+		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
 \end{section}
 
-\begin{section}{\glsentryshort{mimo}-\glsentryshort{ic}}
-	\begin{subsection}{Leakage Interference Minimization}
-		\begin{mini!}
-			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}_{kj}^\mathrm{D} + \mathbf{H}_k^\mathrm{B} \mathbf{\Theta} \mathbf{H}_j^\mathrm{F}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{}{}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-			\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad \mathbf{W}_k^\mathsf{H} \mathbf{W}_k=\mathbf{I}, \quad \forall k.}{}{}
-		\end{mini!}
-		The non-convex problem can be solved by \gls{bcd} method.
-		For a given $\mathbf{\Theta}$, it reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
-		At iteration $r$, the combiner at receiver $k$ is updated as
-		\begin{equation}
-			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
-		\end{equation}
-		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H}$.
-		The precoder at transmitter $j$ is updated as
-		\begin{equation}
-			\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
-		\end{equation}
-		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds to interference covariance matrix $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} \mathbf{H}_{kj}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} \mathbf{H}_{kj}$ in the reciprocal network.
-		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_k\}$ are determined, we define $\bar{\mathbf{H}}_{kj}^\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}_{kj}^\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}_k^\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}_k^\mathrm{B}$, and $\bar{\mathbf{H}}_j^\mathrm{F} \triangleq \mathbf{H}_j^\mathrm{F} \mathbf{W}_j$.
-		The \gls{bd}-\gls{ris} subproblem reduces to
-		\begin{mini!}
-			{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}_{kj}^\mathrm{D} + \bar{\mathbf{H}}_k^\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}_j^\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
-		\end{mini!}
-
-		\begin{proposition}
-			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
-			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-			\end{equation}
-			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
-			\begin{equation}
-				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}_{j,g}^\mathrm{F} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{D}_{kj,g}^{(r)}\bigr) {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{k,g}^\mathrm{B}$ and
-			\begin{equation}
-				\mathbf{D}_{kj,g}^{(r)} = \mathbf{H}_{jk}^\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
-			\end{equation}
-		\end{proposition}
-		\begin{proof}
-			To be added.
-		\end{proof}
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/ic_interference_sx.tex}
-			}
-			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
+% \begin{appendix}
+	% \begin{subsection}{Proof of Lemma \ref{lm:pareto_gradient}}\label{ap:pareto_gradient}
+	% 	Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the compact \gls{svd} of the equivalent channel.
+	% 	Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
+	% 	\begin{equation}
+	% 		\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*,
+	% 	\end{equation}
+	% 	whose differential w.r.t. $\mathbf{\Theta}_g^*$ is
+	% 	\begin{align*}
+	% 		\partial \sigma_n
+	% 		& = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^*\\
+	% 		& = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}\\
+	% 		& = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\\
+	% 		& = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
+	% 	\end{align*}
+	% 	According to \cite{Hjorungnes2007}, the corresponding complex derivative is
+	% 	\begin{equation}
+	% 		\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+	% 		\label{eq:derivative_sv}
+	% 	\end{equation}
+	% 	Linear combination of \eqref{eq:derivative_sv} yields \eqref{eq:pareto_gradient}.
+	% \end{subsection}
+
+	% \begin{subsection}{Proof of Proposition \ref{pp:dof}}\label{ap:dof}
+	% 	The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as\footnote{This is because (block) unitary matrices are closed under multiplication.}
+	% 	\begin{equation}
+	% 		\mathbf{\Theta} = \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H},
+	% 	\end{equation}
+	% 	where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block diagonal matrices of $L \times L$ unitary blocks.
+	% 	Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
+	% 	On the other hand, there exists a $\mathbf{\Theta}_\mathrm{D}$ such that
+	% 	\begin{equation*}
+	% 		\begin{split}
+	% 			\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
+	% 			& = \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\mathbf{H}_\mathrm{F}) \bigr) \\
+	% 			& = \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr) \\
+	% 			& = \max_\mathbf{\Theta} \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+	% 		\end{split}
+	% 	\end{equation*}
+	% 	The same result holds if the direct link is present.
+	% \end{subsection}
+
+	% \begin{subsection}{Proof of Proposition \ref{pp:los}}\label{ap:los}
+	% 	Let $\mathbf{H}_\mathrm{F} = \sigma_\mathrm{F} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ be the compact \gls{svd} of the forward channel.
+	% 	The channel Gram matrix can be written as Hermitian-plus-rank-1:
+	% 	\begin{equation}
+	% 		\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
+	% 	\end{equation}
+	% 	where $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{z} \triangleq \sigma_\mathrm{F} \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{u}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{v}_\mathrm{F}$.
+	% 	By the Cauchy interlacing formula \cite{Golub2013}, the $n$-th ($n \ge 2$) eigenvalues of $\mathbf{G}$ are bounded by
+	% 	\begin{equation}
+	% 		\lambda_1(\mathbf{Y}) \ge \lambda_2(\mathbf{G}) \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge \lambda_N(\mathbf{G}) \ge \lambda_N(\mathbf{Y}).
+	% 		\label{iq:ev_bound_los}
+	% 	\end{equation}
+	% 	Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, the eigenvalues are non-negative and taking the square root of \eqref{iq:ev_bound_los} gives \eqref{iq:sv_bound_los}.
+	% \end{subsection}
+
+	% \begin{subsection}{Proof of Lemma \ref{lm:rate_gradient}}\label{ap:rate_gradient}
+	% 	The differential of $R$ w.r.t. $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
+	% 	\begin{align*}
+	% 		\partial R
+	% 		& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
+	% 		& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
+	% 		& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
+	% 	\end{align*}
+	% 	and the corresponding complex derivative is \eqref{eq:rate_gradient}.
+	% \end{subsection}
+
+% 	\begin{subsection}{Proof of Proposition \ref{pp:power}}\label{ap:power}
+% 		The differential of \eqref{ob:power_passive} w.r.t. $\mathbf{\Theta}_g^*$ is
+% 		\begin{align*}
+% 			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
+% 			& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr)\\
+% 			& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
+% 		\end{align*}
+% 		and the corresponding complex derivative is
+% 		\begin{equation}
+% 			\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{M}_g.
+% 		\end{equation}
+% 		% For a given $\mathbf{\Theta}$, we approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansion and recast problem \eqref{op:power_passive} as
+
+% 		First, we approximate the quadratic objective \eqref{ob:power_passive} by its local Taylor expansion
+% 		\begin{maxi!}
+% 			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_passive_approx}}{\label{ob:power_passive_approx}}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
+% 		\end{maxi!}
+% 		Let $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$ be the compact \gls{svd} of $\mathbf{M}_g$.
+% 		We have
+% 		\begin{equation}
+% 			\Re \bigl\{\mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \mathrm{tr}(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \mathrm{tr}(\mathbf{\Sigma}_g).
+% 		\end{equation}
+% 		The upper bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$, which implies the optimal solution of \eqref{op:power_passive_approx} is $\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$, $\forall g$.
+
+% 		Next, we prove that solving \eqref{op:power_passive_approx} successively does not decrease \eqref{ob:power_passive}.
+% 		Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
+% 		% Expanding both side gives \eqref{iq:power_passive_approx}.
+% 		On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:nonnegative_norm_square}.
+% 		Adding \eqref{iq:power_passive_approx} and \eqref{iq:nonnegative_norm_square}, we have
+% 		\begin{multline}
+% 			2 \Re \Bigl\{\mathrm{tr}(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
+% 			\ge 2 \Re \Bigl\{\mathrm{tr}({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
+% 		\end{multline}
+% 		which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
+% 		\begin{figure*}
+% 			\begin{equation}
+% 				\label{iq:power_passive_approx}
+% 				\resizebox{0.95\textwidth}{!}{
+% 					$2 \Re \Bigl\{\sum\limits_g \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \mathrm{tr}({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
+% 				}
+% 			\end{equation}
+% 			\begin{equation}
+% 				\label{iq:nonnegative_norm_square}
+% 				\resizebox{0.95\textwidth}{!}{
+% 					$\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
+% 				}
+% 			\end{equation}
+% 			\hrulefill
+% 		\end{figure*}
+
+% 		Finally, we prove that the converging point of \eqref{op:power_passive_approx}, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power_passive}.
+% 		The \gls{kkt} conditions of \eqref{op:power_passive} and \eqref{op:power_passive_approx} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
+% 		\begin{gather}
+% 			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_passive_stationary}\\
+% 			\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_passive_approx_stationary}
+% 		\end{gather}
+% 		On convergence, \eqref{eq:power_passive_approx_stationary} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
+\mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^?
+\mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_passive_stationary}.
+% 		The proof is thus completed.
+% 	\end{subsection}
+% \end{appendix}
+
+% \begin{section}{\glsentryshort{mimo}-\glsentryshort{ic}}
+% 	\begin{subsection}{Leakage Interference Minimization}
+% 		\begin{mini!}
+% 			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}_{kj}^\mathrm{D} + \mathbf{H}_k^\mathrm{B} \mathbf{\Theta} \mathbf{H}_j^\mathrm{F}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{}{}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+% 			\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad \mathbf{W}_k^\mathsf{H} \mathbf{W}_k=\mathbf{I}, \quad \forall k.}{}{}
+% 		\end{mini!}
+% 		The non-convex problem can be solved by \gls{bcd} method.
+% 		For a given $\mathbf{\Theta}$, it reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
+% 		At iteration $r$, the combiner at receiver $k$ is updated as
+% 		\begin{equation}
+% 			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
+% 		\end{equation}
+% 		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H}$.
+% 		The precoder at transmitter $j$ is updated as
+% 		\begin{equation}
+% 			\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
+% 		\end{equation}
+% 		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds to interference covariance matrix $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} \mathbf{H}_{kj}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} \mathbf{H}_{kj}$ in the reciprocal network.
+% 		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_k\}$ are determined, we define $\bar{\mathbf{H}}_{kj}^\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}_{kj}^\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}_k^\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}_k^\mathrm{B}$, and $\bar{\mathbf{H}}_j^\mathrm{F} \triangleq \mathbf{H}_j^\mathrm{F} \mathbf{W}_j$.
+% 		The \gls{bd}-\gls{ris} subproblem reduces to
+% 		\begin{mini!}
+% 			{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}_{kj}^\mathrm{D} + \bar{\mathbf{H}}_k^\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}_j^\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
+% 		\end{mini!}
+
+% 		\begin{proposition}
+% 			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
+% 			\begin{equation}
+% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+% 			\end{equation}
+% 			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
+% 			\begin{equation}
+% 				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}_{j,g}^\mathrm{F} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{D}_{kj,g}^{(r)}\bigr) {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H},
+% 			\end{equation}
+% 			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{k,g}^\mathrm{B}$ and
+% 			\begin{equation}
+% 				\mathbf{D}_{kj,g}^{(r)} = \mathbf{H}_{jk}^\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
+% 			\end{equation}
+% 		\end{proposition}
+% 		\begin{proof}
+% 			To be added.
+% 		\end{proof}
+
+% 		\begin{figure}[!t]
+% 			\centering
+% 			\resizebox{0.65\columnwidth}{!}{
+% 				\input{assets/simulation/ic_interference_sx.tex}
+% 			}
+% 			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
 Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}.
 $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$, and reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB}.}
-			\label{sm:ic_interference_sx}
-		\end{figure}
-		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
-		In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
-		Interestingly, the result suggests that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
-	\end{subsection}
-
-	\begin{subsection}{Weighted Sum-Rate Maximization}
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{J_2 = \sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k \mathbf{H}_{kj}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kj} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-			\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
-		\end{maxi!}
-		where $\rho_k$ is the weight of user $k$ and $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix
-		\begin{equation}
-			\mathbf{Q}_k = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H} + \eta \mathbf{I}.
-		\end{equation}
-		For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution based on \gls{wsr}-\gls{wmmse} relationship is proposed in \cite{Negro2010}.
-		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
-		\begin{equation}
-			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H}\bigr)^{-1},
-		\end{equation}
-		the corresponding error matrix is
-		\begin{equation}
-			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{(r-1)} \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
-		\end{equation}
-		the \gls{mse} weight is
-		\begin{equation}
-			\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
-		\end{equation}
-		the Lagrange multiplier is
+% 			\label{sm:ic_interference_sx}
+% 		\end{figure}
+% 		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
+% 		In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
+% 		Interestingly, the result suggests that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
+% 	\end{subsection}
+
+% 	\begin{subsection}{Weighted Sum-Rate Maximization}
+% 		\begin{maxi!}
+% 			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{J_2 = \sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k \mathbf{H}_{kj}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kj} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+% 			\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
+% 		\end{maxi!}
+% 		where $\rho_k$ is the weight of user $k$ and $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix
+% 		\begin{equation}
+% 			\mathbf{Q}_k = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H} + \eta \mathbf{I}.
+% 		\end{equation}
+% 		For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution based on \gls{wsr}-\gls{wmmse} relationship is proposed in \cite{Negro2010}.
+% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
+% 		\begin{equation}
+% 			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H}\bigr)^{-1},
+% 		\end{equation}
+% 		the corresponding error matrix is
+% 		\begin{equation}
+% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{(r-1)} \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+% 		\end{equation}
+% 		the \gls{mse} weight is
+% 		\begin{equation}
+% 			\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
+% 		\end{equation}
+% 		the Lagrange multiplier is
+% 		% \begin{equation}
+% 		% 	\begin{split}
+% 		% 		\lambda_k^{(r)}
+% 		% 		& = \frac{\sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)}}^\mathsf{H}) - \sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)}}^\mathsf{H})}{P_k} \\
+% 		% 		& \quad + \frac{\mathrm{tr}(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H})}{P_k}
+% 		% 	\end{split}
+% 		% \end{equation}
+% 		\begin{equation}
+% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)}}^\mathsf{H} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
+% 		\end{equation}
+% 		where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} \mathbf{H}_{kj} \mathbf{W}_j^{(r)}$.
+% 		The precoder at transmitter $k$ is
+% 		\begin{equation}
+% 			\mathbf{W}_k^{(r)} = \Bigl(\sum_j \mathbf{H}_{jk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}_{jk} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \mathbf{H}_{kk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
+% 		\end{equation}
+% 		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} w.r.t. \gls{ris} block $g$ is
 % 		\begin{equation}
 % 			\begin{split}
-		% 		\lambda_k^{(r)}
-		% 		& = \frac{\sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)}}^\mathsf{H}) - \sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)}}^\mathsf{H})}{P_k} \\
-		% 		& \quad + \frac{\mathrm{tr}(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H})}{P_k}
+% 				\frac{\partial J_2}{\partial \mathbf{\Theta}_g^*}
+% 				& = \sum_k \rho_k {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kk} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
+% 				& \quad \times \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H}\bigr).
 % 			\end{split}
-		% \end{equation}
-		\begin{equation}
-			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)}}^\mathsf{H} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
-		\end{equation}
-		where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} \mathbf{H}_{kj} \mathbf{W}_j^{(r)}$.
-		The precoder at transmitter $k$ is
-		\begin{equation}
-			\mathbf{W}_k^{(r)} = \Bigl(\sum_j \mathbf{H}_{jk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}_{jk} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \mathbf{H}_{kk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
-		\end{equation}
-		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} w.r.t. \gls{ris} block $g$ is
-		\begin{equation}
-			\begin{split}
-				\frac{\partial J_2}{\partial \mathbf{\Theta}_g^*}
-				& = \sum_k \rho_k {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kk} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
-				& \quad \times \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H}\bigr).
-			\end{split}
-			\label{eq:ic_rate_gradient_ris}
-		\end{equation}
-		The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:ic_rate_gradient_ris}.
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/ic_rate_sx.tex}
-			}
-			\caption{Average weighted sum-rate versus \gls{snr}, \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
+% 			\label{eq:ic_rate_gradient_ris}
+% 		\end{equation}
+% 		The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:ic_rate_gradient_ris}.
+
+% 		\begin{figure}[!t]
+% 			\centering
+% 			\resizebox{0.65\columnwidth}{!}{
+% 				\input{assets/simulation/ic_rate_sx.tex}
+% 			}
+% 			\caption{Average weighted sum-rate versus \gls{snr}, \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
 $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
-			\label{sm:ic_rate_sx}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/ic_rate_user.tex}
-			}
-			\caption{Average weighted sum-rate versus user pairs $K$, \gls{ris} elements $N^\mathrm{S}$ and group size $L$ at $\mathrm{SNR} = \qty{15}{dB}$.
+% 			\label{sm:ic_rate_sx}
+% 		\end{figure}
+
+% 		\begin{figure}[!t]
+% 			\centering
+% 			\resizebox{0.65\columnwidth}{!}{
+% 				\input{assets/simulation/ic_rate_user.tex}
+% 			}
+% 			\caption{Average weighted sum-rate versus user pairs $K$, \gls{ris} elements $N^\mathrm{S}$ and group size $L$ at $\mathrm{SNR} = \qty{15}{dB}$.
 $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}) = (4, 4, 3)$, $\rho_k = 1, \ \forall k$.}
-			\label{sm:ic_rate_user}
-		\end{figure}
-
-		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd}-\gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
-	\end{subsection}
-\end{section}
+% 			\label{sm:ic_rate_user}
+% 		\end{figure}
+
+% 		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd}-\gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
+% 	\end{subsection}
+% \end{section}
 

### 2024-02-08 src/pc_singular_pareto.m

@@ -1,9 +1,9 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 32, 2);
-[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2 .^ (0 : 1 : log2(reflect.antenna)));
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 64, 2);
+[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2 .^ (0 : 2 : log2(reflect.antenna)));
 assert(channel.rank == 2, 'The plot function is only for 2-sv case.');
-[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(1, db2pow(-17.5), db2pow(-17.5));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
 [channel.weight(1, :, 1), channel.weight(2, :, 1)] = pol2cart(pi / 4 : pi / 64 : pi * 3 / 4, 1);
 [channel.weight(1, :, 2), channel.weight(2, :, 2)] = pol2cart(pi / 4 : -pi / 64 : -pi / 4, 1);
 [channel.weight(1, :, 3), channel.weight(2, :, 3)] = pol2cart(5 * pi / 4 : pi / 64 : pi * 7 / 4, 1);

### 2024-02-10 assets/simulation/pc_singular_bound.tex
:paintbrush: Update plot functions

@@
 %
-\definecolor{mycolor1}{rgb}{0.58039,0.76863,0.96078}%
-\definecolor{mycolor2}{rgb}{0.25882,0.37647,0.66667}%
-\definecolor{mycolor3}{rgb}{0.94902,0.38039,0.38039}%
-\definecolor{mycolor4}{rgb}{0.91765,0.03529,0.03529}%
+\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
+\definecolor{mycolor2}{rgb}{0.00000,0.44706,0.74118}%
+\definecolor{mycolor3}{rgb}{0.85098,0.32549,0.09804}%
+\definecolor{mycolor4}{rgb}{0.49400,0.18400,0.55600}%
 \definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
@@
 scale only axis,
-bar shift auto,
-xmin=0,
-xmax=5,
+bar width=0.325,
+xmin=-0.125,
+xmax=5.125,
 xtick={1,2,3,4},
-xticklabels={{$\sigma_1$},{$\sigma_2$},{$\sigma_3$},{$\sigma_4$}},
+xticklabels={{$\sigma_1(\mathbf{H})$},{$\sigma_2(\mathbf{H})$},{$\sigma_3(\mathbf{H})$},{$\sigma_4(\mathbf{H})$}},
 ymin=0,
-ymax=4.5,
+ymax=0.002,
 ylabel style={font=\color{white!15!black}},
@@
 ]
-\addplot[ybar, bar width=0.123, fill=black, draw=black, area legend] table[row sep=crcr] {%
-1	3.11578483462081\\
-2	2.33621539044729\\
-3	1.33501504737837\\
-4	0.346232804852115\\
+\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=black, area legend] table[row sep=crcr] {%
+0.8375	0.00172515536422714\\
+1.8375	0.00100217806517558\\
+2.8375	0.000352757538105714\\
+3.8375	0.000123939298123254\\
 };
 \addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0	0\\
-5	0\\
+-0.125	0\\
+5.125	0\\
 };
-\addlegendentry{Direct}
-
-\addplot[ybar, bar width=0.123, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
-1	2.74905207049567\\
-2	1.83843449000086\\
-3	0.952844790933556\\
-4	0.022527302733258\\
+\addplot[ybar stacked, fill=mycolor2, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
+0.8375	1.77586704705756e-05\\
+1.8375	0.000127158817727647\\
+2.8375	0.0002203611436369\\
+3.8375	0.000174937536612442\\
 };
 \addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0	0\\
-5	0\\
+-0.125	0\\
+5.125	0\\
 };
-\addlegendentry{Min, $L = 1$}
+\addlegendentry{D-max}
 
-\addplot[ybar, bar width=0.123, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
-1	2.71936092735902\\
-2	1.81605826060481\\
-3	0.906339746943746\\
-4	0.00914697809349159\\
+\addplot[ybar stacked, fill=mycolor3, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
+0.8375	0.000181872601837377\\
+1.8375	0.000366753236169139\\
+2.8375	0.000296256103311964\\
+3.8375	3.0817049708412e-05\\
 };
 \addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0	0\\
-5	0\\
+-0.125	0\\
+5.125	0\\
 };
-\addlegendentry{Min, $L = 32$}
+\addlegendentry{D-min}
 
-\addplot[ybar, bar width=0.123, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
-1	3.8960081771894\\
-2	2.67136418131802\\
-3	1.64221742934803\\
-4	0.603919247269453\\
+\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=black, area legend] table[row sep=crcr] {%
+1.1625	0.00172516728828725\\
+2.1625	0.00100306026989406\\
+3.1625	0.000335153436324708\\
+4.1625	0.000105743462680291\\
 };
 \addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0	0\\
-5	0\\
+-0.125	0\\
+5.125	0\\
 };
-\addlegendentry{Max, $L = 1$}
-
-\addplot[ybar, bar width=0.123, fill=mycolor4, draw=black, area legend] table[row sep=crcr] {%
-1	4.03127940593837\\
-2	2.67500105747776\\
-3	1.67178857361767\\
-4	0.628233917896107\\
+\addplot[ybar stacked, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
+1.1625	1.77467464104629e-05\\
+2.1625	0.000126276613009161\\
+3.1625	0.000237965245417907\\
+4.1625	0.000193133372055405\\
 };
 \addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0	0\\
-5	0\\
+-0.125	0\\
+5.125	0\\
 };
-\addlegendentry{Max, $L = 32$}
+\addlegendentry{BD-max}
+
+\addplot[ybar stacked, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
+1.1625	0.000222406605491606\\
+2.1625	0.000415962829151039\\
+3.1625	0.000325674699988366\\
+4.1625	3.0817049696797e-05\\
+};
+\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
+-0.125	0\\
+5.125	0\\
+};
+\addlegendentry{BD-min}
 
@@
   table[row sep=crcr]{%
-0	2.68074858002325\\
-5	2.68074858002325\\
+-0.125	0.00172515536418547\\
+5.125	0.00172515536418547\\
 };
@@
   table[row sep=crcr]{%
-0	1.7029380545254\\
-5	1.7029380545254\\
+-0.125	0.00100217806517392\\
+5.125	0.00100217806517392\\
 };
@@
   table[row sep=crcr]{%
-0	0.745179150575099\\
-5	0.745179150575099\\
+-0.125	0.000329693884444316\\
+5.125	0.000329693884444316\\
 };
@@
   table[row sep=crcr]{%
-0	1.47492426026826e-08\\
-5	1.47492426026826e-08\\
+-0.125	1.01657134672358e-11\\
+5.125	1.01657134672358e-11\\
 };

### 2024-02-10 src/pc_singular_bound.m

@@ -1,8 +1,8 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 32, 4);
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 64, 4);
 [channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), [1, reflect.antenna]);
-[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(1, db2pow(-17.5), db2pow(-17.5));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
 channel.weight = eye(channel.rank);
 [number.weight, number.bond, number.realization] = deal(size(channel.weight, 2), length(reflect.bond), 2);
 
@@ -13,14 +13,15 @@ for r = 1 : number.realization
 	channel.auxiliary = channel_auxiliary(channel.direct, channel.forward);
 	channel.singular.direct(:, r) = svd(channel.direct);
 	channel.singular.auxiliary(:, r) = svd(channel.auxiliary);
-	for w = 1 : number.weight
-		for b = 1 : number.bond
+	for b = 1 : number.bond
+		for w = 1 : number.weight
 			clear scatter_singular_pc;
 			[reflect.beamformer.min, channel.aggregate.min] = scatter_singular_pc(channel.direct, channel.forward, channel.backward, -channel.weight(:, w), reflect.bond(b));
 			clear scatter_singular_pc;
 			[reflect.beamformer.max, channel.aggregate.max] = scatter_singular_pc(channel.direct, channel.forward, channel.backward, channel.weight(:, w), reflect.bond(b));
-			channel.singular.aggregate.min(:, w, b, r) = svd(channel.aggregate.min);
-			channel.singular.aggregate.max(:, w, b, r) = svd(channel.aggregate.max);
+            [s.min, s.max] = deal(svd(channel.aggregate.min), svd(channel.aggregate.max));
+			channel.singular.aggregate.min(w, b, r) = s.min(w);
+			channel.singular.aggregate.max(w, b, r) = s.max(w);
 		end
 	end
 end
[…]

### 2024-02-12 assets/simulation/pc_singular_bound_32.tex
:paintbrush: Update plot functions

--- 2024-02-10 assets/simulation/pc_singular_bound.tex
@@
 \definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
+%
+\makeatletter
+\newcommand\resetstackedplots{
+    \makeatletter
+    \pgfplots@stacked@isfirstplottrue
+    \makeatother
+    \addplot [forget plot,draw=none] coordinates{(1,0) (5,0) (10,0) (15,0) (20,0)};
+}
+\makeatother
 %
@@
 legend style={legend cell align=left, align=left, draw=white!15!black},
-legend columns=5,
+legend columns=4,
 transpose legend,
@@
 ]
-\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=black, area legend] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
 0.8375	0.00172515536422714\\
@@
 };
-\addlegendentry{D-max}
+\addlegendentry{D-min}
 
@@
 };
-\addlegendentry{D-min}
+\addlegendentry{D-max}
 
-\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=black, area legend] table[row sep=crcr] {%
+\resetstackedplots
+
+\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
 1.1625	0.00172516728828725\\
@@
 };
-\addlegendentry{BD-max}
+\addlegendentry{BD-min}
 
@@
 };
-\addlegendentry{BD-min}
+\addlegendentry{BD-max}
 
@@
 
-\begin{axis}[%
-width=12.27cm,
-height=9.202cm,
-at={(-1.595cm,-1.012cm)},
-scale only axis,
-xmin=0,
-xmax=1,
-ymin=0,
-ymax=1,
-axis line style={draw=none},
-ticks=none,
-axis x line*=bottom,
-axis y line*=left,
-legend columns=5,
-transpose legend,
-legend style={/tikz/column 2/.style={column sep=5pt}}
-]
-\end{axis}
+% \begin{axis}[%
+% width=12.27cm,
+% height=9.202cm,
+% at={(-1.595cm,-1.012cm)},
+% scale only axis,
+% xmin=0,
+% xmax=1,
+% ymin=0,
+% ymax=1,
+% axis line style={draw=none},
+% ticks=none,
+% axis x line*=bottom,
+% axis y line*=left,
+% legend columns=5,
+% transpose legend,
+% legend style={/tikz/column 2/.style={column sep=5pt}}
+% ]
+% \end{axis}
 \end{tikzpicture}%

### 2024-02-12 assets/simulation/pc_singular_bound_64.tex
:paintbrush: Update plot functions

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor3}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor4}{rgb}{0.49400,0.18400,0.55600}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\makeatletter
\newcommand\resetstackedplots{
    \makeatletter
    \pgfplots@stacked@isfirstplottrue
    \makeatother
    \addplot [forget plot,draw=none] coordinates{(1,0) (5,0) (10,0) (15,0) (20,0)};
}
\makeatother
%
\begin{tikzpicture}

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
bar width=0.325,
xmin=-0.125,
xmax=5.125,
xtick={1,2,3,4},
xticklabels={{$\sigma_1(\mathbf{H})$},{$\sigma_2(\mathbf{H})$},{$\sigma_3(\mathbf{H})$},{$\sigma_4(\mathbf{H})$}},
ymin=0,
ymax=0.003,
ylabel style={font=\color{white!15!black}},
ylabel={Amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
legend columns=4,
transpose legend,
legend style={/tikz/column 2/.style={column sep=5pt}}
]
\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
0.8375	0.00195358578718362\\
1.8375	0.000905403110314898\\
2.8375	0.000478480067807894\\
3.8375	3.24792561983075e-17\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	4.10673634284198e-05\\
1.8375	9.08396603062443e-05\\
2.8375	0.000280905224832324\\
3.8375	0.000316345482660046\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-min}

\addplot[ybar stacked, fill=mycolor3, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.00057247498440489\\
1.8375	0.000934081190202522\\
2.8375	0.00014601781767251\\
3.8375	0.000162134585145759\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-max}

\resetstackedplots

\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
1.1625	0.00195358621182515\\
2.1625	0.000905405810406567\\
3.1625	0.000478484657925968\\
4.1625	3.62951302572638e-06\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1.1625	4.10669387868874e-05\\
2.1625	9.0836960214575e-05\\
3.1625	0.000280900634714249\\
4.1625	0.000312715969634352\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{BD-min}

\addplot[ybar stacked, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1.1625	0.000668204539596567\\
2.1625	0.000957343016500992\\
3.1625	0.000146017817609404\\
4.1625	0.000162134585134279\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{BD-max}

\addplot [color=mycolor5, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	0.00195358578716264\\
5.125	0.00195358578716264\\
};
\addlegendentry{$\sigma_1(\mathbf{T})$}

\addplot [color=mycolor5, dashed, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	0.000905403110313456\\
5.125	0.000905403110313456\\
};
\addlegendentry{$\sigma_2(\mathbf{T})$}

\addplot [color=mycolor5, dotted, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	0.000478480067806991\\
5.125	0.000478480067806991\\
};
\addlegendentry{$\sigma_3(\mathbf{T})$}

\addplot [color=mycolor5, dashdotted, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	1.20606340074858e-11\\
5.125	1.20606340074858e-11\\
};
\addlegendentry{$\sigma_4(\mathbf{T})$}

\end{axis}
\end{tikzpicture}%

### 2024-02-12 main.tex
:paintbrush: Update plot functions

@@
 	\begin{subsection}{Channel Singular Values Redistribution}
+		% \begin{figure}[!t]
+		% 	\centering
+		% 	\resizebox{0.65\columnwidth}{!}{
+		% 		\input{assets/simulation/pc_singular_pareto.tex}
+		% 	}
+		% 	\caption{Singular value bounds for rank-1 indirect channel.
+$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
+		% 	\label{fg:pc_singular_pareto}
+		% \end{figure}
+
 		\begin{figure}[!t]
 			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/pc_singular_pareto.tex}
-			}
-			\caption{Singular value bounds for rank-1 indirect channel.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-			\label{fg:pc_singular_pareto}
+			\subfloat[$2 \times 32 \times 2$ (no direct link)\label{fg:pc_singular_pareto_32_nd}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_singular_pareto_32_nd.tex}
+				}
+			}
+			\subfloat[$2 \times 32 \times 2$\label{fg:pc_singular_pareto_32}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_singular_pareto_32.tex}
+				}
+			}
+			\\
+			\subfloat[$2 \times 64 \times 2$\label{fg:pc_singular_pareto_64}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_singular_pareto_64.tex}
+				}
+			}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[$4 \times 32 \times 4$\label{fg:pc_singular_bound_32}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_singular_bound_32.tex}
+				}
+			}
+			\subfloat[$4 \times 64 \times 4$\label{fg:pc_singular_bound_64}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_singular_bound_64.tex}
+				}
+			}
+			\caption{
+				Channel singular values with \gls{los} forward channel: analytical bounds (green lines) and optimized results (blue and red bars).
+				`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
+				% $\kappa_\mathrm{D}=\kappa_\mathrm{B}=0$, $\kappa_\mathrm{F}=\infty$.
+			}
+			% \caption{Singular values of equivalent channel with \gls{los} forward channel: analytical bounds (green lines) and optimized results (blue and red bars).}
+			\label{fg:pc_singular_bound}
 		\end{figure}

### 2024-02-12 src/pc_singular_bound.m

@@ -39,7 +39,7 @@ set(handle.bound, {'Color'}, {'#77AC30'}, {'LineStyle'}, {'-'; '--'; ':'; '-.'},
 hold off; grid on; box on; legend('Location', 'ne', 'NumColumns', 2);
 ylabel('Amplitude');
 savefig('plots/pc_singular_bound.fig');
-% matlab2tikz('../assets/simulation/pc_singular_bound.tex', 'width', '10cm', 'height', '7.5cm', 'extraaxisoptions', {'legend columns=5', 'transpose legend', 'legend style={/tikz/column 2/.style={column sep=5pt}}'});
+matlab2tikz('../assets/simulation/pc_singular_bound.tex', 'width', '10cm', 'height', '7.5cm', 'extraaxisoptions', {'legend columns=4', 'transpose legend', 'legend style={/tikz/column 2/.style={column sep=5pt}}'});
 
 function [H_a] = channel_auxiliary(H_d, H_f)
 	[~, ~, v_f] = svds(H_f, 1);

### 2024-02-13 assets/simulation/pc_singular_extreme.tex
:paintbrush: Update plot functions

--- 2024-02-12 assets/simulation/pc_singular_bound_64.tex
@@
 \definecolor{mycolor4}{rgb}{0.49400,0.18400,0.55600}%
-\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
-%
-\makeatletter
-\newcommand\resetstackedplots{
-    \makeatletter
-    \pgfplots@stacked@isfirstplottrue
-    \makeatother
-    \addplot [forget plot,draw=none] coordinates{(1,0) (5,0) (10,0) (15,0) (20,0)};
-}
-\makeatother
 %
@@
 ]
-\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
-0.8375	0.00195358578718362\\
-1.8375	0.000905403110314898\\
-2.8375	0.000478480067807894\\
-3.8375	3.24792561983075e-17\\
+\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=black, area legend] table[row sep=crcr] {%
+0.8375	0.00143117804054061\\
+1.8375	0.000743199099777249\\
+2.8375	0.000269283237979035\\
+3.8375	8.24218765062706e-09\\
 };
@@
 \addplot[ybar stacked, fill=mycolor2, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
-0.8375	4.10673634284198e-05\\
-1.8375	9.08396603062443e-05\\
-2.8375	0.000280905224832324\\
-3.8375	0.000316345482660046\\
+0.8375	0.000462878936482017\\
+1.8375	0.00042549634196207\\
+2.8375	0.00041106144944578\\
+3.8375	0.00024003624027829\\
 };
@@
 \addplot[ybar stacked, fill=mycolor3, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
-0.8375	0.00057247498440489\\
-1.8375	0.000934081190202522\\
-2.8375	0.00014601781767251\\
-3.8375	0.000162134585145759\\
+0.8375	0.000506636656075082\\
+1.8375	0.000495702837065026\\
+2.8375	0.000451079141362691\\
+3.8375	0.000460530423624515\\
 };
@@
 
-\resetstackedplots
-
-\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
-1.1625	0.00195358621182515\\
-2.1625	0.000905405810406567\\
-3.1625	0.000478484657925968\\
-4.1625	3.62951302572638e-06\\
+\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=black, area legend] table[row sep=crcr] {%
+1.1625	0.00129022242555956\\
+2.1625	0.000545548715650276\\
+3.1625	8.37754891714641e-05\\
+4.1625	1.02575159048296e-08\\
 };
@@
 \addplot[ybar stacked, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
-1.1625	4.10669387868874e-05\\
-2.1625	9.0836960214575e-05\\
-3.1625	0.000280900634714249\\
-4.1625	0.000312715969634352\\
+1.1625	0.000603834551463065\\
+2.1625	0.000623146726089043\\
+3.1625	0.000596569198253351\\
+4.1625	0.000240034224950036\\
 };
@@
 \addplot[ybar stacked, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
-1.1625	0.000668204539596567\\
-2.1625	0.000957343016500992\\
-3.1625	0.000146017817609404\\
-4.1625	0.000162134585134279\\
+1.1625	0.000631314400677068\\
+2.1625	0.00064060657290608\\
+3.1625	0.000623100053838356\\
+4.1625	0.000631935100972121\\
 };
@@
 
-\addplot [color=mycolor5, line width=2.0pt]
-  table[row sep=crcr]{%
--0.125	0.00195358578716264\\
-5.125	0.00195358578716264\\
-};
-\addlegendentry{$\sigma_1(\mathbf{T})$}
-
-\addplot [color=mycolor5, dashed, line width=2.0pt]
-  table[row sep=crcr]{%
--0.125	0.000905403110313456\\
-5.125	0.000905403110313456\\
-};
-\addlegendentry{$\sigma_2(\mathbf{T})$}
-
-\addplot [color=mycolor5, dotted, line width=2.0pt]
-  table[row sep=crcr]{%
--0.125	0.000478480067806991\\
-5.125	0.000478480067806991\\
-};
-\addlegendentry{$\sigma_3(\mathbf{T})$}
-
-\addplot [color=mycolor5, dashdotted, line width=2.0pt]
-  table[row sep=crcr]{%
--0.125	1.20606340074858e-11\\
-5.125	1.20606340074858e-11\\
-};
-\addlegendentry{$\sigma_4(\mathbf{T})$}
-
 \end{axis}

### 2024-02-13 assets/simulation/pc_singular_rank.tex
:paintbrush: Update plot functions

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor3}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor4}{rgb}{0.49400,0.18400,0.55600}%
%
\begin{tikzpicture}

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
bar width=0.325,
xmin=-0.125,
xmax=5.125,
xtick={1,2,3,4},
xticklabels={{$\sigma_1(\mathbf{H})$},{$\sigma_2(\mathbf{H})$},{$\sigma_3(\mathbf{H})$},{$\sigma_4(\mathbf{H})$}},
ymin=0,
ymax=0.0035,
ylabel style={font=\color{white!15!black}},
ylabel={Amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
legend columns=4,
transpose legend,
legend style={/tikz/column 2/.style={column sep=5pt}}
]
\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.0012783984510597\\
1.8375	0.000755927497323383\\
2.8375	2.45713322253816e-05\\
3.8375	8.06474101750415e-20\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.000430608943515784\\
1.8375	0.000307344043879747\\
2.8375	0.000767652597424499\\
3.8375	0.000103757373637032\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-min}

\addplot[ybar stacked, fill=mycolor3, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.00134333869298983\\
1.8375	0.00111640080271814\\
2.8375	0.000450125859707777\\
3.8375	0.000620574925146492\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-max}

\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=black, area legend] table[row sep=crcr] {%
1.1625	0.00127840941167134\\
2.1625	0.000755931488018856\\
3.1625	1.92538964772042e-06\\
4.1625	2.39864749917709e-09\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1.1625	0.000430597982904148\\
2.1625	0.000307340053184274\\
3.1625	0.00079029854000216\\
4.1625	0.000103754974989533\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{BD-min}

\addplot[ybar stacked, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1.1625	0.00161372587060955\\
2.1625	0.00171623770226479\\
3.1625	0.000486174471126013\\
4.1625	0.000637595849936804\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{BD-max}

\end{axis}
\end{tikzpicture}%

### 2024-02-13 main.tex
:paintbrush: Update plot functions

@@
 			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
-			\caption{$2 \times 2 \times 2$ channel singular value shaping by diagonal and symmetry unitary \gls{ris}. Direct link is absent.}
+			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetry unitary \gls{ris}.}
 			\label{sm:pc_singular_toy}
@@
 	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
-	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$, $\gamma_\mathrm{B}=2$, $\kappa_\mathrm{D}=\kappa_\mathrm{F}=\kappa_\mathrm{B}=5$ for reference, which corresponds to an indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
+	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
+	Rayleigh fading is assumed for all channels $\kappa_\mathrm{D},\kappa_\mathrm{B},\kappa_\mathrm{F} \to \infty$ unless otherwise specified.
 
 	\begin{subsection}{Channel Singular Values Redistribution}
-		% \begin{figure}[!t]
-		% 	\centering
-		% 	\resizebox{0.65\columnwidth}{!}{
-		% 		\input{assets/simulation/pc_singular_pareto.tex}
-		% 	}
-		% 	\caption{Singular value bounds for rank-1 indirect channel.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-		% 	\label{fg:pc_singular_pareto}
-		% \end{figure}
-
 		\begin{figure}[!t]
@@
 			}
+			\subfloat[$2 \times 128 \times 2$\label{fg:pc_singular_pareto_128}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/pc_singular_pareto_128.tex}
+				}
+			}
+			\caption{Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.}
 		\end{figure}
@@
 			\caption{
-				Channel singular values with \gls{los} forward channel: analytical bounds (green lines) and optimized results (blue and red bars).
+				Channel singular values with \gls{los} forward channel ($\kappa_\mathrm{F} = 0$): analytical bounds (green lines) and optimized results (blue and red bars).
 				`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.

### 2024-02-13 src/lib/fading_rankn.m

@@ -1,0 +1,7 @@
+function [H] = fading_rankn(N_r, N_t, N)
+	H = zeros(N_r, N_t, N);
+	for n = 1 : N
+		H(:, :, n) = fading_los(N_r, N_t);
+	end
+	H = sqrt(1 / N) * sum(H, 3);
+end

### 2024-02-13 src/pc_singular_extreme.m

@@ -3,16 +3,15 @@ clc; clear; close; setup;
 [transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 64, 4);
 [channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), [1, reflect.antenna]);
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[channel.kfactor.direct, channel.kfactor.forward, channel.kfactor.backward] = deal(0);
 channel.weight = eye(channel.rank);
-[number.weight, number.bond, number.realization] = deal(size(channel.weight, 2), length(reflect.bond), 2);
+[number.weight, number.bond, number.realization] = deal(size(channel.weight, 2), length(reflect.bond), 10);
 
 for r = 1 : number.realization
-	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
-	channel.forward = sqrt(channel.pathloss.forward) * fading_los(reflect.antenna, transmit.antenna);
-	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
-	channel.auxiliary = channel_auxiliary(channel.direct, channel.forward);
+	channel.direct = sqrt(channel.pathloss.direct) * fading_ricean(receive.antenna, transmit.antenna, channel.kfactor.direct);
+	channel.forward = sqrt(channel.pathloss.forward) * fading_ricean(reflect.antenna, transmit.antenna, channel.kfactor.forward);
+	channel.backward = sqrt(channel.pathloss.backward) * fading_ricean(receive.antenna, reflect.antenna, channel.kfactor.backward);
 	channel.singular.direct(:, r) = svd(channel.direct);
-	channel.singular.auxiliary(:, r) = svd(channel.auxiliary);
 	for b = 1 : number.bond
 		for w = 1 : number.weight
 			clear scatter_singular_pc;
@@ -26,25 +25,15 @@ for r = 1 : number.realization
 	end
 end
 channel.singular.direct = mean(channel.singular.direct, ndims(channel.singular.direct));
-channel.singular.auxiliary = mean(channel.singular.auxiliary, ndims(channel.singular.auxiliary));
[…]

### 2024-02-13 src/pc_singular_pareto.m

@@ -1,15 +1,14 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 64, 2);
-% [channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2 .^ (0 : 1 : log2(reflect.antenna)));
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 128, 2);
 [channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), [1, 4, 16, reflect.antenna]);
 assert(channel.rank == 2, 'The plot function is only for 2-sv case.');
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[channel.weight(1, :, 1), channel.weight(2, :, 1)] = pol2cart(pi / 4 : pi / 256 : pi * 3 / 4, 1);
-[channel.weight(1, :, 2), channel.weight(2, :, 2)] = pol2cart(pi / 4 : -pi / 256 : -pi / 4, 1);
-[channel.weight(1, :, 3), channel.weight(2, :, 3)] = pol2cart(5 * pi / 4 : pi / 256 : pi * 7 / 4, 1);
-[channel.weight(1, :, 4), channel.weight(2, :, 4)] = pol2cart(5 * pi / 4 : -pi / 256 : pi * 3 / 4, 1);
-[number.weight, number.case, number.bond, number.realization, flag.direct] = deal(size(channel.weight, 2), size(channel.weight, 3), length(reflect.bond), 2, false);
+[channel.weight(1, :, 1), channel.weight(2, :, 1)] = pol2cart(pi / 4 : pi / 64 : pi * 3 / 4, 1);
+[channel.weight(1, :, 2), channel.weight(2, :, 2)] = pol2cart(pi / 4 : -pi / 64 : -pi / 4, 1);
+[channel.weight(1, :, 3), channel.weight(2, :, 3)] = pol2cart(5 * pi / 4 : pi / 64 : pi * 7 / 4, 1);
+[channel.weight(1, :, 4), channel.weight(2, :, 4)] = pol2cart(5 * pi / 4 : -pi / 64 : pi * 3 / 4, 1);
+[number.weight, number.case, number.bond, number.realization, flag.direct] = deal(size(channel.weight, 2), size(channel.weight, 3), length(reflect.bond), 2, true);
 
 for r = 1 : number.realization
[…]

### 2024-02-13 src/pc_singular_rank.m

@@ -1,18 +1,18 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 64, 4);
-[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), [1, reflect.antenna]);
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 128, 4);
+[channel.rank.direct, channel.rank.forward, channel.rank.backward, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2, min(reflect.antenna, receive.antenna), [1, reflect.antenna]);
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-channel.weight = eye(channel.rank);
+channel.weight = eye(channel.rank.direct);
 [number.weight, number.bond, number.realization] = deal(size(channel.weight, 2), length(reflect.bond), 2);
 
 for r = 1 : number.realization
 	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
-	channel.forward = sqrt(channel.pathloss.forward) * fading_los(reflect.antenna, transmit.antenna);
+	channel.forward = sqrt(channel.pathloss.forward) * fading_rankn(reflect.antenna, transmit.antenna, channel.rank.forward);
 	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
-	channel.auxiliary = channel_auxiliary(channel.direct, channel.forward);
+	% channel.auxiliary = channel_auxiliary(channel.direct, channel.forward);
 	channel.singular.direct(:, r) = svd(channel.direct);
-	channel.singular.auxiliary(:, r) = svd(channel.auxiliary);
+	% channel.singular.auxiliary(:, r) = svd(channel.auxiliary);
 	for b = 1 : number.bond
 		for w = 1 : number.weight
 			clear scatter_singular_pc;
@@ -26,36 +26,36 @@ for r = 1 : number.realization
 	end
 end
 channel.singular.direct = mean(channel.singular.direct, ndims(channel.singular.direct));
[…]

### 2024-02-14 abstract.tex
:sparkles: Refactor code

@@
 			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/pc_power_sx.tex}
+				\input{assets/simulation/power_sx.tex}
 			}
@@
 $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-			\label{sm:pc_power_sx}
+			\label{sm:power_sx}
 		\end{figure}
@@
 		\end{figure}
-		% Fig.~\ref{sm:pc_power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
-		% Fig.~\ref{sm:pc_power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
-		Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
+		% Fig.~\ref{sm:power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
+		% Fig.~\ref{sm:power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
+		Fig.~\ref{sm:power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
 		% The behavior is more obvious for a large \gls{ris}.
@@
 			\centering
-			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
+			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
 			\caption{Channel singular value shaping by diagonal and symmetry unitary \gls{ris}. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (2, 2, 2)$. Direct link is absent.}
-			\label{sm:pc_singular_toy}
+			\label{sm:singular_trend}
 		\end{figure}
-		Fig.~\ref{sm:pc_singular_toy} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
+		Fig.~\ref{sm:singular_trend} illustrates all possible channel singular values achieved by diagonal and symmetry unitary \gls{ris}.
 		Despite using the same number of elements and parameters, \gls{bd} \gls{ris} provides much wider dynamic ranges of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ than diagonal \gls{ris}.
@@
 			% However, \gls{bd} \gls{ris} can still guarantee a higher rate at finite \gls{snr}.
-			Note \gls{bd} \gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:pc_power_sx} and \ref{sm:pc_power_bond}.
+			Note \gls{bd} \gls{ris} can still provide a higher indirect \gls{snr} as shown in Fig.~\ref{sm:power_sx} and \ref{sm:pc_power_bond}.
 		\end{subsubsection}
@@
 			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/simulation/pc_singular_pareto.tex}
+				\input{assets/simulation/singular_pareto.tex}
 			}
 			\caption{Singular value Pareto front. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 64, 2)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-			\label{sm:pc_singular_pareto}
+			\label{sm:singular_pareto}
 		\end{figure}
@@
 
-		The Pareto front and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
+		The Pareto front and evolving trend of channel singular values are shown in Fig.~\ref{sm:singular_pareto} and \ref{sm:pc_singular_bound}.
 		Clearly, \gls{bd} \gls{ris} with a larger group size can redistribute the channel singular values to a wider range.

### 2024-02-14 assets/simulation/power_sx_txrx16.tex
:sparkles: Refactor code

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor3}{rgb}{0.92941,0.69412,0.12549}%
\definecolor{mycolor4}{rgb}{0.49412,0.18431,0.55686}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\begin{tikzpicture}

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymode=log,
ymin=7.63413889612284e-05,
ymax=0.000357009156162705,
yminorticks=true,
ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
1	8.03593568012931e-05\\
2	8.03593568012931e-05\\
3	8.03593568012931e-05\\
4	8.03593568012931e-05\\
5	8.03593568012931e-05\\
6	8.03593568012931e-05\\
7	8.03593568012931e-05\\
8	8.03593568012931e-05\\
9	8.03593568012931e-05\\
};
\addlegendentry{No RIS}

\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	8.32187269864919e-05\\
2	8.41922087195748e-05\\
3	8.55795092915898e-05\\
4	8.71382957344062e-05\\
5	8.87320958720005e-05\\
};
\addlegendentry{$N_\mathrm{S} = 16$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	8.6466574171426e-05\\
2	8.81326989213474e-05\\
3	9.06190783177407e-05\\
4	9.40273928578491e-05\\
5	9.73131338921825e-05\\
6	9.94886394941543e-05\\
};
\addlegendentry{$N_\mathrm{S} = 32$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	9.23552447351784e-05\\
2	9.66298198027635e-05\\
3	0.000102096862854765\\
4	0.000109010799564887\\
5	0.00011684562278114\\
6	0.000121837810358247\\
7	0.000124553664322635\\
};
\addlegendentry{$N_\mathrm{S} = 64$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	0.000104965329801996\\
2	0.00011389799786835\\
3	0.000126536878725085\\
4	0.000142525515494825\\
5	0.000160952430585978\\
6	0.000173883585167439\\
7	0.000180725719749113\\
8	0.000184115133386408\\
};
\addlegendentry{$N_\mathrm{S} = 128$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	0.000134020224284578\\
2	0.000153465030738225\\
3	0.000181252804375544\\
4	0.000220639327233136\\
5	0.000268738002904876\\
6	0.000305073448328176\\
7	0.000324412126742617\\
8	0.000334907924545081\\
9	0.000340008720154957\\
};
\addlegendentry{$N_\mathrm{S} = 256$}

\end{axis}
\end{tikzpicture}%

### 2024-02-14 assets/simulation/singular_bound_rank2_sx128.tex
:sparkles: Refactor code

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor3}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor4}{rgb}{0.49400,0.18400,0.55600}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\makeatletter
\newcommand\resetstackedplots{
    \makeatletter
    \pgfplots@stacked@isfirstplottrue
    \makeatother
    \addplot [forget plot,draw=none] coordinates{(1,0) (5,0) (10,0) (15,0) (20,0)};
}
\makeatother
%
\begin{tikzpicture}

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
bar width=0.325,
xmin=-0.125,
xmax=5.125,
xtick={1,2,3,4},
xticklabels={{$\sigma_1(\mathbf{H})$},{$\sigma_2(\mathbf{H})$},{$\sigma_3(\mathbf{H})$},{$\sigma_4(\mathbf{H})$}},
ymin=0,
ymax=0.004,
ylabel style={font=\color{white!15!black}},
ylabel={Amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
legend columns=4,
transpose legend,
legend style={/tikz/column 2/.style={column sep=5pt}}
]
\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
0.8375	0.00142543267002251\\
1.8375	0.000656306214245826\\
2.8375	0.000132970460937413\\
3.8375	3.2994096547908e-20\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.000316188517375316\\
1.8375	0.000636356951614819\\
2.8375	0.000675093172956787\\
3.8375	0.000311028141103694\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-min}

\addplot[ybar stacked, fill=mycolor3, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.00143103448582135\\
1.8375	0.000911508088276409\\
2.8375	0.000557699498413843\\
3.8375	0.000345278073129164\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-max}

\resetstackedplots

\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
1.1625	0.00142543579700608\\
2.1625	0.00065631304524136\\
3.1625	5.27477395632166e-06\\
4.1625	4.21048388214027e-08\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1.1625	0.000316185390391755\\
2.1625	0.000636350120619285\\
3.1625	0.000802788859937878\\
4.1625	0.000310986036264873\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{BD-min}

\addplot[ybar stacked, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1.1625	0.00179647322615157\\
2.1625	0.00141980780340078\\
3.1625	0.000617369035963568\\
4.1625	0.000345278072973618\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{BD-max}

\addplot [color=mycolor5, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	0.00142543266997377\\
5.125	0.00142543266997377\\
};
\addlegendentry{$\sigma_1(\mathbf{T})$}

\addplot [color=mycolor5, dashed, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	0.000656306214237067\\
5.125	0.000656306214237067\\
};
\addlegendentry{$\sigma_2(\mathbf{T})$}

\addplot [color=mycolor5, dotted, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	1.83134593569563e-11\\
5.125	1.83134593569563e-11\\
};
\addlegendentry{$\sigma_3(\mathbf{T})$}

\addplot [color=mycolor5, dashdotted, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	8.07634856586464e-12\\
5.125	8.07634856586464e-12\\
};
\addlegendentry{$\sigma_4(\mathbf{T})$}

\end{axis}
\end{tikzpicture}%

### 2024-02-14 assets/simulation/singular_bound_rank4_sx256.tex
:sparkles: Refactor code

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor3}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor4}{rgb}{0.49400,0.18400,0.55600}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\makeatletter
\newcommand\resetstackedplots{
    \makeatletter
    \pgfplots@stacked@isfirstplottrue
    \makeatother
    \addplot [forget plot,draw=none] coordinates{(1,0) (5,0) (10,0) (15,0) (20,0)};
}
\makeatother
%
\begin{tikzpicture}

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
bar width=0.325,
xmin=-0.125,
xmax=5.125,
xtick={1,2,3,4},
xticklabels={{$\sigma_1(\mathbf{H})$},{$\sigma_2(\mathbf{H})$},{$\sigma_3(\mathbf{H})$},{$\sigma_4(\mathbf{H})$}},
ymin=0,
ymax=0.005,
ylabel style={font=\color{white!15!black}},
ylabel={Amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
legend columns=4,
transpose legend,
legend style={/tikz/column 2/.style={column sep=5pt}}
]
\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
0.8375	0.000590158480426682\\
1.8375	0.000129241592659798\\
2.8375	2.58214028253461e-05\\
3.8375	6.14844865636593e-20\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.00131538553898149\\
1.8375	0.000939081061667071\\
2.8375	0.00068542783385897\\
3.8375	0.000169352904449523\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-min}

\addplot[ybar stacked, fill=mycolor3, fill opacity=0.5, draw=black, area legend] table[row sep=crcr] {%
0.8375	0.0023951194667282\\
1.8375	0.00184094568953638\\
2.8375	0.00115975659942478\\
3.8375	0.000827148080235149\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{D-max}

\resetstackedplots

\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
1.1625	0.000346385584583973\\
2.1625	7.78556027220081e-08\\
3.1625	3.09245924695688e-10\\
4.1625	3.0971797863086e-11\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addplot[ybar stacked, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1.1625	0.00155915843482419\\
2.1625	0.00106824479872415\\
3.1625	0.000711248927438391\\
4.1625	0.000169352873477725\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{BD-min}

\addplot[ybar stacked, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1.1625	0.002953753985213\\
2.1625	0.002904805544911\\
3.1625	0.00250318921193009\\
4.1625	0.00168645690620485\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
-0.125	0\\
5.125	0\\
};
\addlegendentry{BD-max}

\addplot [color=mycolor5, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	3.45656762152605e-11\\
5.125	3.45656762152605e-11\\
};
\addlegendentry{$\sigma_1(\mathbf{T})$}

\addplot [color=mycolor5, dashed, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	1.40250773872945e-11\\
5.125	1.40250773872945e-11\\
};
\addlegendentry{$\sigma_2(\mathbf{T})$}

\addplot [color=mycolor5, dotted, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	9.62701814871279e-12\\
5.125	9.62701814871279e-12\\
};
\addlegendentry{$\sigma_3(\mathbf{T})$}

\addplot [color=mycolor5, dashdotted, line width=2.0pt]
  table[row sep=crcr]{%
-0.125	3.69974075950399e-12\\
5.125	3.69974075950399e-12\\
};
\addlegendentry{$\sigma_4(\mathbf{T})$}

\end{axis}
\end{tikzpicture}%

### 2024-02-14 main.tex
:sparkles: Refactor code

@@
 			\centering
-			\includegraphics[width=\columnwidth]{assets/simulation/pc_singular_toy.eps}
+			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
 			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetry unitary \gls{ris}.}
-			\label{sm:pc_singular_toy}
+			\label{fg:singular_trend}
 		\end{figure}
-		Fig.~\ref{sm:pc_singular_toy} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
+		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
 		It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and design parameters.
@@
 	% 	\centering
-	% 	\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{sm:pc_rate_sx}]{
+	% 	\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{fg:pc_rate_sx}]{
 	% 		\resizebox{0.48\columnwidth}{!}{
@@
 	% 	}
-	% 	\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{sm:pc_rate_tx}]{
+	% 	\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{fg:pc_rate_tx}]{
 	% 		\resizebox{0.48\columnwidth}{!}{
@@
 	% 	\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{sm:pc_rate}
+	% 	\label{fg:pc_rate}
 	% \end{figure}
 
-	% Fig.~\ref{sm:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
+	% Fig.~\ref{fg:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
 	% To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
@@
 		% 	\resizebox{0.65\columnwidth}{!}{
-		% 		\input{assets/simulation/pc_power_sx.tex}
+		% 		\input{assets/simulation/power_sx.tex}
 		% 	}
@@
 $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-		% 	\label{sm:pc_power_sx}
+		% 	\label{fg:power_sx}
 		% \end{figure}
@@
 		% 	\centering
-		% 	\subfloat[Without Direct Link\label{sm:pc_power_bond_nd}]{
+		% 	\subfloat[Without Direct Link\label{fg:pc_power_bond_nd}]{
 		% 		\resizebox{0.48\columnwidth}{!}{
@@
 		% 	}
-		% 	\subfloat[With Direct Link\label{sm:pc_power_bond_hd}]{
+		% 	\subfloat[With Direct Link\label{fg:pc_power_bond_hd}]{
 		% 		\resizebox{0.48\columnwidth}{!}{
@@
 $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-		% 	\label{sm:pc_power_bond}
+		% 	\label{fg:pc_power_bond}
 		% \end{figure}
-		% % Fig.~\ref{sm:pc_power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
-		% % Fig.~\ref{sm:pc_power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
-		% Fig.~\ref{sm:pc_power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
+		% % Fig.~\ref{fg:power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
+		% % Fig.~\ref{fg:power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
+		% Fig.~\ref{fg:power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
 		% % The behavior is more obvious for a large \gls{ris}.
@@
 
-		% Fig.~\ref{sm:pc_power_bond_hd} and \ref{sm:pc_power_bond_nd} compare the average channel power without and with direct link.
+		% Fig.~\ref{fg:pc_power_bond_hd} and \ref{fg:pc_power_bond_nd} compare the average channel power without and with direct link.
 		% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
@@
 	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
+	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
 	Rayleigh fading is assumed for all channels $\kappa_\mathrm{D},\kappa_\mathrm{B},\kappa_\mathrm{F} \to \infty$ unless otherwise specified.
@@
 			\centering
-			\subfloat[$2 \times 32 \times 2$ (no direct link)\label{fg:pc_singular_pareto_32_nd}]{
+			\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
 				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_singular_pareto_32_nd.tex}
-				}
-			}
-			\subfloat[$2 \times 32 \times 2$\label{fg:pc_singular_pareto_32}]{
+					\input{assets/simulation/singular_pareto_sx32_nd.tex}
+				}
+			}
+			\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
 				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_singular_pareto_32.tex}
+					\input{assets/simulation/singular_pareto_sx32.tex}
 				}
@@
 			\\
-			\subfloat[$2 \times 64 \times 2$\label{fg:pc_singular_pareto_64}]{
+			\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
 				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_singular_pareto_64.tex}
-				}
-			}
-			\subfloat[$2 \times 128 \times 2$\label{fg:pc_singular_pareto_128}]{
+					\input{assets/simulation/singular_pareto_sx64.tex}
+				}
+			}
+			\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
 				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_singular_pareto_128.tex}
+					\input{assets/simulation/singular_pareto_sx128.tex}
 				}
@@
 			\caption{Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.}
+			\label{fg:singular_pareto}
 		\end{figure}
@@
 			\centering
-			\subfloat[$4 \times 32 \times 4$\label{fg:pc_singular_bound_32}]{
+			\subfloat[$4 \times 32 \times 4$\label{fg:singular_bound_rank1_sx32}]{
 				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_singular_bound_32.tex}
-				}
-			}
-			\subfloat[$4 \times 64 \times 4$\label{fg:pc_singular_bound_64}]{
+					\input{assets/simulation/singular_bound_rank1_sx32.tex}
+				}
+			}
+			\subfloat[$4 \times 64 \times 4$\label{fg:singular_bound_rank1_sx64}]{
 				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/simulation/pc_singular_bound_64.tex}
+					\input{assets/simulation/singular_bound_rank1_sx64.tex}
+				}
+			}
+			\\
+			\subfloat[$4 \times 128 \times 4$\label{fg:singular_bound_rank2_sx128}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/singular_bound_rank2_sx128.tex}
+				}
+			}
+			\subfloat[$4 \times 256 \times 4$\label{fg:singular_bound_rank4_sx256}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/simulation/singular_bound_rank4_sx256.tex}
 				}
@@
 			\caption{
-				Channel singular values with \gls{los} forward channel ($\kappa_\mathrm{F} = 0$): analytical bounds (green lines) and optimized results (blue and red bars).
+				Achievable channel singular values: analytical bounds (green lines) and optimized results (blue and red bars).
 				`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
-				% $\kappa_\mathrm{D}=\kappa_\mathrm{B}=0$, $\kappa_\mathrm{F}=\infty$.
-			}
-			% \caption{Singular values of equivalent channel with \gls{los} forward channel: analytical bounds (green lines) and optimized results (blue and red bars).}
-			\label{fg:pc_singular_bound}
+			}
+			\label{fg:singular_bound}
 		\end{figure}
 
-		The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:pc_singular_pareto}.
-		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:pc_singular_pareto}.
-		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:pc_singular_pareto}.
+		The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
+		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
+		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
 		% Clearly, a larger group size provides
-		% and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
+		% and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
 		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
+	\end{subsection}
+
+	\begin{subsection}{Achievable Rate Maximization}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
+				\resizebox{0.4725\columnwidth}{!}{
+					\input{assets/simulation/power_bond_txrx1_nd.tex}
+				}
+			}
+			\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
+				\resizebox{0.4875\columnwidth}{!}{
+					\input{assets/simulation/power_bond_txrx4_nd.tex}
+				}
+			}
+			\caption{
+				Average channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
+			}
+			\label{fg:power_bond}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[$4 \times N_\mathrm{S} \times 4$ (no direct)\label{fg:power_sx_txrx4_nd}]{
+				\resizebox{0.49\columnwidth}{!}{
+					\input{assets/simulation/power_sx_txrx4_nd.tex}
+				}
+			}
+			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
+				\resizebox{0.47\columnwidth}{!}{
+					\input{assets/simulation/power_sx_txrx16.tex}
+				}
+			}
+			\caption{
+				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
+			}
+			\label{fg:power_sx}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
+				\resizebox{0.49\columnwidth}{!}{
+					\input{assets/simulation/rate_beamforming.tex}
+				}
+			}
+			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
+				\resizebox{0.47\columnwidth}{!}{
+					\input{assets/simulation/rate_txrx.tex}
+				}
+			}
+			\\
+			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
+				\resizebox{0.47\columnwidth}{!}{
+					\input{assets/simulation/rate_sx.tex}
+				}
+			}
+			\subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
+				\resizebox{0.47\columnwidth}{!}{
+					\input{assets/simulation/rate_kfactor.tex}
+				}
+			}
+			\caption{
+				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
+			}
+			\label{fg:rate}
+		\end{figure}
 	\end{subsection}
@@
 $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-		% 	\label{sm:pc_singular_bound}
+		% 	\label{fg:pc_singular_bound}
 		% \end{figure}
 
-		% The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{sm:pc_singular_pareto} and \ref{sm:pc_singular_bound}.
+		% The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
 		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
@@
 $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$, and reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB}.}
-% 			\label{sm:ic_interference_sx}
+% 			\label{fg:ic_interference_sx}
 % 		\end{figure}
-% 		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
+% 		Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
 % 		In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
@@
 $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
-% 			\label{sm:ic_rate_sx}
+% 			\label{fg:ic_rate_sx}
 % 		\end{figure}
@@
 $(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}) = (4, 4, 3)$, $\rho_k = 1, \ \forall k$.}
-% 			\label{sm:ic_rate_user}
+% 			\label{fg:ic_rate_user}
 % 		\end{figure}
 
-% 		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd}-\gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
+% 		A new observation from Fig.~\ref{fg:ic_rate_sx} that the interference alignment capability of \gls{bd}-\gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
 % 	\end{subsection}

### 2024-02-14 src/ic_rate_sx.m

@@ -1,57 +1,0 @@
-clc; clear; close; setup;
-
-[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream, network.pair] = deal(8, 2 .^ [5, 8], 4, 3, 5);
-[transmit.power, receive.noise, receive.weight] = deal(db2pow(-20), db2pow(-75 : -10 : -115), ones(network.pair, 1));
-[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-transmit.snr = pow2db(transmit.power * channel.pathloss.direct ./ receive.noise);
-[number.bond, number.noise, number.antenna, number.realization] = deal(3, length(receive.noise), length(reflect.antenna), 2);
-
-for r = 1 : number.realization
-	% * No RIS
-	channel.direct = sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair, network.pair);
-	transmit.beamformer = precoder_initial_ic(channel.direct, transmit.stream, transmit.power);
-	for n = 1 : number.noise
-		transmit.beamformer = precoder_rate_explicit_ic(channel.direct, transmit.beamformer, transmit.power, receive.noise(n), receive.weight);
-		receive.wsr.direct(n, r) = receive.weight' * rate_mimo(channel.direct, transmit.beamformer, receive.noise(n));
-	end
-	% * Have RIS
-	for a = 1 : number.antenna
-		reflect.bond = [1, 4, reflect.antenna(a)];
-		channel.forward = sqrt(channel.pathloss.forward) .* fading_nlos(reflect.antenna(a), transmit.antenna, 1, network.pair);
-		channel.backward = sqrt(channel.pathloss.backward) .* fading_nlos(receive.antenna, reflect.antenna(a), network.pair, 1);
-		clear scatter_rate_ic;
-		for b = 1 : number.bond
-			transmit.beamformer = precoder_initial_ic(channel.direct, transmit.stream, transmit.power);
-			for n = 1 : number.noise
-				[iter.converge, iter.tolerance, iter.counter, iter.wsr] = deal(false, 1e-4, 0, receive.weight' * rate_mimo(channel.direct, transmit.beamformer, receive.noise(n)));
-				while ~iter.converge
[…]

### 2024-02-14 src/ic_rate_user.m

@@ -1,59 +1,0 @@
-clc; clear; close; setup;
-
-[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream, network.pair] = deal(4, 2 .^ [4, 6], 4, 3, 2 : 2 : 10);
-[transmit.power, receive.noise] = deal(db2pow(-20), db2pow(-100));
-[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.bond, number.antenna, number.pair, number.realization] = deal(3, length(reflect.antenna), length(network.pair), 20);
-
-for r = 1 : number.realization
-	% * No RIS
-	for p = 1 : number.pair
-		receive.weight = ones(network.pair(p), 1);
-		channel.direct = sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair(p), network.pair(p));
-		transmit.beamformer = precoder_initial_ic(channel.direct, transmit.stream, transmit.power);
-		transmit.beamformer = precoder_rate_bisection_ic(channel.direct, transmit.beamformer, transmit.power, receive.noise, receive.weight);
-		receive.wsr.direct(p, r) = receive.weight' * rate_mimo(channel.direct, transmit.beamformer, receive.noise);
-	end
-	% * Have RIS
-	for a = 1 : number.antenna
-		reflect.bond = [1, 4, reflect.antenna(a)];
-		for p = 1 : number.pair
-			receive.weight = ones(network.pair(p), 1);
-			channel.direct = sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair(p), network.pair(p));
-			channel.forward = sqrt(channel.pathloss.forward) .* fading_nlos(reflect.antenna(a), transmit.antenna, 1, network.pair(p));
-			channel.backward = sqrt(channel.pathloss.backward) .* fading_nlos(receive.antenna, reflect.antenna(a), network.pair(p), 1);
-			transmit.beamformer = precoder_initial_ic(channel.direct, transmit.stream, transmit.power);
-			clear scatter_rate_ic;
-			for b = 1 : number.bond
[…]

### 2024-02-14 src/lib/combiner_initial_ic.m

@@ -1,5 +1,0 @@
-function [G] = combiner_initial_ic(H, N_e)
-	K = size(H, 3);
-	[U, ~, ~] = pagesvd(H(:, :, logical(eye(K))));
-	G = pagectranspose(U(:, 1 : N_e, :));
-end

### 2024-02-14 src/lib/combiner_interference_ic.m

@@ -1,6 +1,0 @@
-function [G] = combiner_interference_ic(H, W)
-	[N_e, K] = deal(size(W, 2), size(W, 4));
-	T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
-    [U, ~] = pageeig(sum(T, 4) - T(:, :, logical(eye(K))));
-    G = pagectranspose(U(:, 1 : N_e, :));
-end

### 2024-02-14 src/lib/precoder_initial_ic.m

@@ -1,9 +1,0 @@
-function [W] = precoder_initial_ic(H, N_e, P_t)
-	K = size(H, 3);
-	[~, ~, V] = pagesvd(H(:, :, logical(eye(K))));
-	W = sqrt(P_t / N_e) * pageswap(V(:, 1 : N_e, :));
-end
-
-function [A] = pageswap(A)
-	A = permute(A, [1, 2, 4, 3]);
-end

### 2024-02-14 src/lib/precoder_rate.m

@@ -1,0 +1,7 @@
+function [W] = precoder_rate(H, P_t, P_n)
+	[~, S, V] = svd(H, 'vector');
+	P_n = P_n ./ S' .^ 2;
+	P_s = waterfill(P_t, P_n(~isinf(P_n)));
+	N_e = nnz(P_s);
+	W = V(:, 1 : N_e) * diag(sqrt(P_s(1 : N_e)));
+end

### 2024-02-14 src/lib/precoder_rate_bisection_ic.m

@@ -1,52 +1,0 @@
-function [W] = precoder_rate_bisection_ic(H, W, P_t, P_n, rho)
-	[N_r, N_t, N_e, K] = deal(size(H, 1), size(H, 2), size(W, 2), size(W, 4));
-	[iter.converge, iter.tolerance, iter.counter] = deal(false, 1e-4, 0);
-	iter.J = rho' * rate_mimo(H, W, P_n);
-	while ~iter.converge
-		T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
-		Q = sum(T, 4) - T(:, :, logical(eye(K))) + P_n * eye(N_r);
-		F = pagemtimes(H(:, :, logical(eye(K))), pageswap(W));
-		G = pagemrdivide(pagectranspose(F), Q + T(:, :, logical(eye(K))));
-		V = shiftdim(rho, -2) .* pagehermitize(eye(N_e) + pagemtimes(pagemrdivide(pagectranspose(F), Q), F));
-		Y = pagemtimes(pagemtimes(pagemtimes(G, H), 'ctranspose', V, 'none'), pagemtimes(G, H));
-		for k = 1 : K
-			fun = @(lambda) norm(mldivide(sum(Y(:, :, :, k), 3) + lambda * eye(N_t), H(:, :, k, k)' * G(:, :, k)' * V(:, :, k)), 'fro') ^ 2 - P_t;
-			[lb, ub] = deal(0, 1e3);
-			if fun(lb) * fun(ub) < 0
-				lambda = bisection(fun, lb, ub);
-			else
-				lambda = 0;
-			end
-			W(:, :, :, k) = mldivide(sum(Y(:, :, :, k), 3) + lambda * eye(N_t), H(:, :, k, k)' * G(:, :, k)' * V(:, :, k));
-		end
-		J = rho' * rate_mimo(H, W, P_n);
-		iter.converge = (abs(J - iter.J) / iter.J <= iter.tolerance) && all(abs(pagenorm(W, 'fro') .^ 2 - P_t) ./ P_t < iter.tolerance | abs(pagenorm(W, 'fro') .^ 2) < iter.tolerance);
-		iter.J = J;
-		iter.counter = iter.counter + 1;
-	end
-end
-
-function [A] = pageswap(A)
-	A = permute(A, [1, 2, 4, 3]);
-end
-
-function [A] = pagehermitize(A)
[…]

### 2024-02-14 src/lib/precoder_rate_explicit_ic.m

@@ -1,32 +1,0 @@
-function [W] = precoder_rate_explicit_ic(H, W, P_t, P_n, rho)
-	[N_r, N_t, N_e, K] = deal(size(H, 1), size(H, 2), size(W, 2), size(W, 4));
-	[iter.converge, iter.tolerance, iter.counter] = deal(false, 1e-4, 0);
-	iter.J = rho' * rate_mimo(H, W, P_n);
-	while ~iter.converge
-		T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
-		Q = sum(T, 4) - T(:, :, logical(eye(K))) + P_n * eye(N_r);
-		F = pagemtimes(H(:, :, logical(eye(K))), pageswap(W));
-		G = pagemrdivide(pagectranspose(F), Q + T(:, :, logical(eye(K))));
-		V = shiftdim(rho, -2) .* pagehermitize(eye(N_e) + pagemtimes(pagemrdivide(pagectranspose(F), Q), F));
-		Y = pagemtimes(pagemtimes(pagemtimes(G, H), 'ctranspose', V, 'none'), pagemtimes(G, H));
-		Z = pagehermitize(pagemtimes(pagemtimes(W, 'ctranspose', Y, 'none'), W));
-		lambda = (pageswap(pagetrace(P_n * pagehermitize(pagemtimes(pagemtimes(G, 'ctranspose', V, 'none'), G))) + pagetrace(sum(Z, 4))) - pagetrace(sum(Z, 3))) ./ P_t;
-		W = pagemldivide(sum(Y, 3) + lambda .* eye(N_t), pageswap(pagemtimes(pagemtimes(G, H(:, :, logical(eye(K)))), 'ctranspose', V, 'none')));
-		J = rho' * rate_mimo(H, W, P_n);
-		iter.converge = (abs(J - iter.J) / iter.J <= iter.tolerance) && all(abs(pagenorm(W, 'fro') .^ 2 - P_t) ./ P_t < iter.tolerance | abs(pagenorm(W, 'fro') .^ 2 - P_t) < iter.tolerance);
-		iter.J = J;
-		iter.counter = iter.counter + 1;
-	end
-end
-
-function [b] = pagetrace(A)
-	b = sum(pageeig(A), 1);
-end
-
-function [A] = pageswap(A)
-	A = permute(A, [1, 2, 4, 3]);
-end
-
-function [A] = pagehermitize(A)
-	A = 0.5 * (A + pagectranspose(A));
-end

### 2024-02-14 src/lib/precoder_rate_pc.m

@@ -1,7 +1,0 @@
-function [W] = precoder_rate_pc(H, P_t, P_n)
-	[~, S, V] = svd(H, 'vector');
-	P_n = P_n ./ S' .^ 2;
-	P_s = waterfill(P_t, P_n(~isinf(P_n)));
-	N_e = nnz(P_s);
-	W = V(:, 1 : N_e) * diag(sqrt(P_s(1 : N_e)));
-end

### 2024-02-14 src/lib/rate_mimo.m

@@ -1,24 +1,4 @@
 function [R] = rate_mimo(H, W, P_n)
-	if size(H, 3) == 1
-		R = rate_mimo_pc(H, W, P_n);
-	else
-		R = rate_mimo_ic(H, W, P_n);
-	end
-end
-
-function [R] = rate_mimo_pc(H, W, P_n)
 	R = log(det(eye(size(W, 2)) + (H * W)' * (H * W) / P_n));
 	R = real(R);
-end
-
-function [R] = rate_mimo_ic(H, W, P_n)
-	[N_r, K] = deal(size(H, 1), size(H, 3));
-	T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
-	Q = sum(T, 4) - T(:, :, logical(eye(K))) + P_n * eye(N_r);
-	X = eye(N_r) + pagemldivide(Q, T(:, :, logical(eye(K))));
-	R = log(shiftdim(pagedet(X)));
-end
-
-function [d] = pagedet(A)
-	d = prod(pagesvd(A), 1);
 end

### 2024-02-14 src/lib/scatter_interference_ic.m

@@ -1,31 +1,0 @@
-function [Theta, H] = scatter_interference_ic(H_d, H_f, H_b, L)
-	persistent iter;
-	if isempty(iter)
-		Theta = eye(size(H_f, 1));
-	else
-		Theta = iter.Theta;
-	end
-
-	[K, G] = deal(size(H_d, 3), length(Theta) / L);
-	H = channel_aggregate(H_d, H_f, H_b, Theta);
-	[iter.converge, iter.tolerance, iter.counter, iter.I] = deal(false, 1e-4, 0, interference_leakage(H));
-	while ~iter.converge
-		for g = 1 : G
-			S = (g - 1) * L + 1 : g * L;
-			S_c = setdiff(1 : length(Theta), S);
-			D = H_d + pagemtimes(pagemtimes(H_b(:, S_c, :), Theta(S_c, S_c)), H_f(S_c, :, :, :));
-            T = pagemtimes(H_b(:, S, :), 'ctranspose', H_b(:, S, :), 'none');
-            B = max(pageeig(T)) .* repmat(eye(L), [1, 1, K]) - T + eps;
-			Q = pagemtimes(pagemtimes(pagemtimes(B, Theta(S, S)), H_f(S, :, :, :)) - pagemtimes(pagectranspose(H_b(:, S, :)), D), pagectranspose(H_f(S, :, :, :)));
-			M = sum(Q(:, :, ~logical(eye(K))), 3);
-			[U, ~, V] = svd(M);
-			Theta(S, S) = U * V';
-		end
-		H = channel_aggregate(H_d, H_f, H_b, Theta);
-		I = interference_leakage(H);
-		iter.converge = (abs(I - iter.I) / iter.I <= iter.tolerance);
-		iter.I = I;
-		iter.counter = iter.counter + 1;
-	end
-	iter.Theta = Theta;
-end

### 2024-02-14 src/lib/scatter_power_max.m

@@ -1,0 +1,26 @@
+function [Theta, H] = scatter_power_max(H_d, H_f, H_b, L)
+	persistent iter;
+	if isempty(iter)
+		Theta = eye(size(H_f, 1));
+	else
+		Theta = iter.Theta;
+	end
+
+	G = length(Theta) / L;
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+	[iter.converge, iter.tolerance, iter.counter, iter.P] = deal(false, 1e-4, 0, norm(H, 'fro') ^ 2);
+	while ~iter.converge
+		for g = 1 : G
+			S = (g - 1) * L + 1 : g * L;
+			M = H_b(:, S)' * (H_d + H_b * Theta * H_f) * H_f(S, :)';
+			[U, ~, V] = svd(M);
+			Theta(S, S) = U * V';
+		end
+		H = channel_aggregate(H_d, H_f, H_b, Theta);
+		P = norm(H, 'fro') ^ 2;
+		iter.converge = (abs(P - iter.P) / iter.P <= iter.tolerance);
+		iter.P = P;
+		iter.counter = iter.counter + 1;
+	end
+	iter.Theta = Theta;
+end

### 2024-02-14 src/lib/scatter_power_min.m

@@ -1,0 +1,30 @@
+function [Theta, H] = scatter_power_min(H_d, H_f, H_b, L)
+	persistent iter;
+	if isempty(iter)
+		Theta = eye(size(H_f, 1));
+	else
+		Theta = iter.Theta;
+	end
+
+	G = length(Theta) / L;
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+	[iter.converge, iter.tolerance, iter.counter, iter.P] = deal(false, 1e-4, 0, norm(H, 'fro') ^ 2);
+	while ~iter.converge
+		for g = 1 : G
+			S = (g - 1) * L + 1 : g * L;
+			S_c = setdiff(1 : length(Theta), S);
+			D = H_d + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :);
+			T = H_b(:, S)' * H_b(:, S);
+			B = max(eig(T)) * eye(L) - T + eps;
+			M = (B * Theta(S, S) * H_f(S, :) - H_b(:, S)' * D) * H_f(S, :)';
+			[U, ~, V] = svd(M);
+			Theta(S, S) = U * V';
+		end
+		H = channel_aggregate(H_d, H_f, H_b, Theta);
+		P = norm(H, 'fro') ^ 2;
+		iter.converge = (abs(P - iter.P) / iter.P <= iter.tolerance);
+		iter.P = P;
+		iter.counter = iter.counter + 1;
+	end
+	iter.Theta = Theta;
+end

### 2024-02-14 src/lib/scatter_power_min_pc.m

@@ -1,30 +1,0 @@
-function [Theta, H] = scatter_power_min_pc(H_d, H_f, H_b, L)
-	persistent iter;
-	if isempty(iter)
-		Theta = eye(size(H_f, 1));
-	else
-		Theta = iter.Theta;
-	end
-
-	G = length(Theta) / L;
-	H = channel_aggregate(H_d, H_f, H_b, Theta);
-	[iter.converge, iter.tolerance, iter.counter, iter.P] = deal(false, 1e-4, 0, norm(H, 'fro') ^ 2);
-	while ~iter.converge
-		for g = 1 : G
-			S = (g - 1) * L + 1 : g * L;
-			S_c = setdiff(1 : length(Theta), S);
-			D = H_d + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :);
-			T = H_b(:, S)' * H_b(:, S);
-			B = max(eig(T)) * eye(L) - T + eps;
-			M = (B * Theta(S, S) * H_f(S, :) - H_b(:, S)' * D) * H_f(S, :)';
-			[U, ~, V] = svd(M);
-			Theta(S, S) = U * V';
-		end
-		H = channel_aggregate(H_d, H_f, H_b, Theta);
-		P = norm(H, 'fro') ^ 2;
-		iter.converge = (abs(P - iter.P) / iter.P <= iter.tolerance);
-		iter.P = P;
-		iter.counter = iter.counter + 1;
-	end
-	iter.Theta = Theta;
-end

### 2024-02-14 src/lib/scatter_rate.m

@@ -1,0 +1,35 @@
+function [Theta, H] = scatter_rate(H_d, H_f, H_b, W, L, P_n)
+	persistent iter;
+	if isempty(iter)
+		Theta = eye(size(H_f, 1));
+	else
+		Theta = iter.Theta;
+	end
+
+	G = length(Theta) / L;
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+	[G_e, G_r, D] = deal(zeros(size(Theta)));
+	[iter.converge, iter.tolerance, iter.counter, iter.R] = deal(false, 1e-4, 0, rate_mimo(H, W, P_n));
+	while ~iter.converge
+		[iter.G_r, iter.D] = deal(G_r, D);
+		for g = 1 : G
+			S = (g - 1) * L + 1 : g * L;
+			S_c = setdiff(1 : length(Theta), S);
+			fun = @(Theta_g) rate_mimo(H_d + H_b(:, S) * Theta_g * H_f(S, :) + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :), W, P_n);
+			G_e(S, S) = gradient_euclidean(H, H_f(S, :), H_b(:, S), W, P_n);
+			G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
+			D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
+			Theta(S, S) = step_armijo(fun, Theta(S, S), D(S, S));
+			H = channel_aggregate(H_d, H_f, H_b, Theta);
+		end
+		R = rate_mimo(H, W, P_n);
+		iter.converge = (abs(R - iter.R) / iter.R <= iter.tolerance);
+		iter.R = R;
+		iter.counter = iter.counter + 1;
+	end
+	iter.Theta = Theta;
+end
+
+function [G_e] = gradient_euclidean(H, H_f, H_b, W, P_n)
+	G_e = H_b' * H * W / (eye(size(W, 2)) + (H * W)' * (H * W) / P_n) * W' * H_f' / P_n;
+end

### 2024-02-14 src/lib/scatter_rate_ic.m

@@ -1,44 +1,0 @@
-function [Theta, H] = scatter_rate_ic(H_d, H_f, H_b, W, L, P_n, rho)
-	persistent iter;
-	if isempty(iter)
-		Theta = eye(size(H_f, 1));
-	else
-		Theta = iter.Theta;
-	end
-
-	G = length(Theta) / L;
-	H = channel_aggregate(H_d, H_f, H_b, Theta);
-	[G_e, G_r, D] = deal(zeros(size(Theta)));
-	[iter.converge, iter.tolerance, iter.counter, iter.J] = deal(false, 1e-3, 0, rho' * rate_mimo(H, W, P_n));
-	while ~iter.converge
-		[iter.G_r, iter.D] = deal(G_r, D);
-		for g = 1 : G
-			S = (g - 1) * L + 1 : g * L;
-			S_c = setdiff(1 : length(Theta), S);
-			fun = @(Theta_g) rho' * rate_mimo(H_d + pagemtimes(pagemtimes(H_b(:, S, :, :), Theta_g), H_f(S, :, :, :)) + pagemtimes(pagemtimes(H_b(:, S_c, :, :), Theta(S_c, S_c)), H_f(S_c, :, :, :)), W, P_n);
-			G_e(S, S) = gradient_euclidean(H, H_f(S, :, :, :), H_b(:, S, :, :), W, P_n, rho);
-			G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
-			D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
-			Theta(S, S) = step_armijo(fun, Theta(S, S), D(S, S));
-			H = channel_aggregate(H_d, H_f, H_b, Theta);
-		end
-		J = rho' * rate_mimo(H, W, P_n);
-		iter.converge = (abs(J - iter.J) / iter.J <= iter.tolerance);
-		iter.J = J;
-		iter.counter = iter.counter + 1;
-	end
-	iter.Theta = Theta;
-end
-
-function [G_e] = gradient_euclidean(H, H_f, H_b, W, P_n, rho)
-	[N_r, N_e, K] = deal(size(H, 1), size(W, 2), size(W, 4));
-	T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
[…]

### 2024-02-14 src/lib/scatter_rate_pc.m

@@ -1,35 +1,0 @@
-function [Theta, H] = scatter_rate_pc(H_d, H_f, H_b, W, L, P_n)
-	persistent iter;
-	if isempty(iter)
-		Theta = eye(size(H_f, 1));
-	else
-		Theta = iter.Theta;
-	end
-
-	G = length(Theta) / L;
-	H = channel_aggregate(H_d, H_f, H_b, Theta);
-	[G_e, G_r, D] = deal(zeros(size(Theta)));
-	[iter.converge, iter.tolerance, iter.counter, iter.R] = deal(false, 1e-4, 0, rate_mimo(H, W, P_n));
-	while ~iter.converge
-		[iter.G_r, iter.D] = deal(G_r, D);
-		for g = 1 : G
-			S = (g - 1) * L + 1 : g * L;
-			S_c = setdiff(1 : length(Theta), S);
-			fun = @(Theta_g) rate_mimo(H_d + H_b(:, S) * Theta_g * H_f(S, :) + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :), W, P_n);
-			G_e(S, S) = gradient_euclidean(H, H_f(S, :), H_b(:, S), W, P_n);
-			G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
-			D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
-			Theta(S, S) = step_armijo(fun, Theta(S, S), D(S, S));
-			H = channel_aggregate(H_d, H_f, H_b, Theta);
-		end
-		R = rate_mimo(H, W, P_n);
-		iter.converge = (abs(R - iter.R) / iter.R <= iter.tolerance);
-		iter.R = R;
-		iter.counter = iter.counter + 1;
-	end
-	iter.Theta = Theta;
-end
-
-function [G_e] = gradient_euclidean(H, H_f, H_b, W, P_n)
-	G_e = H_b' * H * W / (eye(size(W, 2)) + (H * W)' * (H * W) / P_n) * W' * H_f' / P_n;
-end

### 2024-02-14 src/lib/scatter_singular_pc.m

@@ -1,44 +1,0 @@
-function [Theta, H] = scatter_singular_pc(H_d, H_f, H_b, rho, L)
-	persistent iter;
-	if isempty(iter)
-		clear scatter_power_max_pc scatter_power_min_pc;
-		if all(rho >= 0)
-			Theta = scatter_power_max_pc(H_d, H_f, H_b, L);
-		elseif all(rho <= 0)
-			Theta = scatter_power_min_pc(H_d, H_f, H_b, L);
-		else
-			Theta = eye(size(H_f, 1));
-		end
-	else
-		Theta = iter.Theta;
-	end
-
-	G = length(Theta) / L;
-	H = channel_aggregate(H_d, H_f, H_b, Theta);
-	[G_e, G_r, D] = deal(zeros(size(Theta)));
-	[iter.converge, iter.tolerance, iter.counter, iter.J] = deal(false, 1e-9, 0, rho' * svd(H));
-	while ~iter.converge
-		[iter.G_r, iter.D] = deal(G_r, D);
-		for g = 1 : G
-			S = (g - 1) * L + 1 : g * L;
-			S_c = setdiff(1 : length(Theta), S);
-			fun = @(Theta_g) rho' * svd(H_d + H_b(:, S) * Theta_g * H_f(S, :) + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :));
-			G_e(S, S) = gradient_euclidean(H, H_f(S, :), H_b(:, S), rho);
-			G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
-			D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
-			Theta(S, S) = step_armijo(fun, Theta(S, S), D(S, S));
-			H = channel_aggregate(H_d, H_f, H_b, Theta);
-		end
-		J = rho' * svd(H);
-		iter.converge = (abs(J - iter.J) / iter.J <= iter.tolerance);
-		iter.J = J;
-		iter.counter = iter.counter + 1;
-	end
-	iter.Theta = Theta;
-end
-
-function [G_e] = gradient_euclidean(H, H_f, H_b, rho)
-	[U, S, V] = svd(H);
-	S(logical(eye(length(rho)))) = rho;
-	G_e = H_b' * U * S * V' * H_f';
-end

### 2024-02-14 src/lib/simplex_standard.m

@@ -1,5 +1,0 @@
-function [S] = simplex_standard(K, delta)
-	N = ceil(1 / delta);
-	T = nchoosek(1 : K + N - 1, N) - (0 : N - 1);
-	S = histc(T', 1 : K) / N;
-end

### 2024-02-14 src/pc_power_bond.m

@@ -1,48 +1,0 @@
-clc; clear; close; setup;
-
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(8, 256, 4);
-[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2 .^ (0 : 2 : log2(reflect.antenna)));
-[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.bond, number.realization, flag.direct] = deal(length(reflect.bond), 1e1, true);
-
-for r = 1 : number.realization
-	% * No RIS
-	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
-	channel.power.direct(r) = norm(channel.direct, 'fro') ^ 2;
-	% * Have RIS
-	channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna);
-	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
-	channel.power.cascaded(r) = sum(svds(channel.backward, channel.rank) .^ 2 .* svds(channel.forward, channel.rank) .^ 2);
-	clear scatter_power_max_pc;
-	for b = 1 : number.bond
-		[reflect.beamformer, channel.aggregate] = scatter_power_max_pc(channel.direct, channel.forward, channel.backward, reflect.bond(b));
-		channel.power.aggregate(b, r) = norm(channel.aggregate, 'fro') ^ 2;
-	end
-end
-channel.power.direct = mean(channel.power.direct, ndims(channel.power.direct));
-channel.power.cascaded = mean(channel.power.cascaded, ndims(channel.power.cascaded));
-channel.power.aggregate = mean(channel.power.aggregate, ndims(channel.power.aggregate));
-if flag.direct == true
-	save('data/pc_power_bond_hd.mat');
-else
-	save('data/pc_power_bond_nd.mat');
-end
-
-figure('Name', 'Channel Power vs RIS Group Size', 'Position', [0, 0, 500, 400]);
-set(gca, 'XLim', [0, number.bond + 1], 'XTick', 1 : number.bond, 'XTickLabel', reflect.bond);
-hold all;
[…]

### 2024-02-14 src/pc_singular_bound.m

@@ -1,96 +1,0 @@
-clc; clear; close; setup;
-
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 64, 4);
-[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), [1, reflect.antenna]);
-[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-channel.weight = eye(channel.rank);
-[number.weight, number.bond, number.realization] = deal(size(channel.weight, 2), length(reflect.bond), 2);
-
-for r = 1 : number.realization
-	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
-	channel.forward = sqrt(channel.pathloss.forward) * fading_los(reflect.antenna, transmit.antenna);
-	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
-	channel.auxiliary = channel_auxiliary(channel.direct, channel.forward);
-	channel.singular.direct(:, r) = svd(channel.direct);
-	channel.singular.auxiliary(:, r) = svd(channel.auxiliary);
-	for b = 1 : number.bond
-		for w = 1 : number.weight
-			clear scatter_singular_pc;
-			[reflect.beamformer.min, channel.aggregate.min] = scatter_singular_pc(channel.direct, channel.forward, channel.backward, -channel.weight(:, w), reflect.bond(b));
-			clear scatter_singular_pc;
-			[reflect.beamformer.max, channel.aggregate.max] = scatter_singular_pc(channel.direct, channel.forward, channel.backward, channel.weight(:, w), reflect.bond(b));
-            [s.min, s.max] = deal(svd(channel.aggregate.min), svd(channel.aggregate.max));
-			channel.singular.aggregate.min(w, b, r) = s.min(w);
-			channel.singular.aggregate.max(w, b, r) = s.max(w);
-		end
-	end
-end
-channel.singular.direct = mean(channel.singular.direct, ndims(channel.singular.direct));
-channel.singular.auxiliary = mean(channel.singular.auxiliary, ndims(channel.singular.auxiliary));
[…]

### 2024-02-14 src/pc_singular_toy.m

@@ -1,64 +1,0 @@
-clc; clear; close; setup;
-
-[transmit.antenna, reflect.antenna, receive.antenna, reflect.sample] = deal(2, 2, 2, 1e2);
-[reflect.azimuth, reflect.elevation] = meshgrid(2 * pi * (1 : reflect.sample) / reflect.sample);
-
-channel.forward = fading_nlos(reflect.antenna, transmit.antenna);
-channel.backward = fading_nlos(receive.antenna, reflect.antenna);
-for s1 = 1 : reflect.sample
-	for s2 = 1 : reflect.sample
-		channel.singular.diagonal(s1, s2, :) = svd(channel.backward * scatter_2x2_diagonal(reflect.azimuth(s1, s2), reflect.elevation(s1, s2)) * channel.forward);
-		channel.singular.symmtary(s1, s2, :) = svd(channel.backward * scatter_2x2_symmtary(reflect.azimuth(s1, s2), reflect.elevation(s1, s2)) * channel.forward);
-	end
-end
-save('data/pc_singular_toy.mat');
-
-figure('Name', 'Channel Singular Value vs RIS Configuration', 'Position', [0, 0, 500, 400]);
-handle.window = tiledlayout(2, 1);
-handle.axis(1) = nexttile;
-for s = 1 : 2
-	handle.mesh(1, s) = mesh(reflect.azimuth, reflect.elevation, channel.singular.diagonal(:, :, s), 'DisplayName', '$\sigma_' + string(s) + '(\mathbf{H})$');
-	datatip(handle.mesh(1, s), 'DataIndex', find(vec(channel.singular.diagonal(:, :, s)) == max(vec(channel.singular.diagonal(:, :, s))), 1));
-	datatip(handle.mesh(1, s), 'DataIndex', find(vec(channel.singular.diagonal(:, :, s)) == min(vec(channel.singular.diagonal(:, :, s))), 1));
-	handle.mesh(1, s).DataTipTemplate.DataTipRows = handle.mesh(1, s).DataTipTemplate.DataTipRows(end);
-	handle.mesh(1, s).DataTipTemplate.DataTipRows.Label = '\sigma';
-	handle.mesh(1, s).DataTipTemplate.DataTipRows.Format = '%.3f';
-	hold on;
-end
[…]

### 2024-02-14 src/power_bond.m

@@ -1,0 +1,41 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(1, 256, 1);
+[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 2 .^ (0 : 2 : log2(reflect.antenna)));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[number.bond, number.realization, flag.direct] = deal(length(reflect.bond), 1e2, false);
+
+for r = 1 : number.realization
+	% * No RIS
+	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	channel.power.direct(r) = norm(channel.direct, 'fro') ^ 2;
+	% * Have RIS
+	channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna);
+	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
+	channel.power.cascaded(r) = sum(svds(channel.backward, channel.rank) .^ 2 .* svds(channel.forward, channel.rank) .^ 2);
+	clear scatter_power_max;
+	for b = 1 : number.bond
+		[reflect.beamformer, channel.aggregate] = scatter_power_max(channel.direct, channel.forward, channel.backward, reflect.bond(b));
+		channel.power.aggregate(b, r) = norm(channel.aggregate, 'fro') ^ 2;
+	end
+end
+channel.power.direct = mean(channel.power.direct, ndims(channel.power.direct));
+channel.power.cascaded = mean(channel.power.cascaded, ndims(channel.power.cascaded));
+channel.power.aggregate = mean(channel.power.aggregate, ndims(channel.power.aggregate));
+save('data/power_bond.mat');
+
+figure('Name', 'Channel Power vs RIS Group Size', 'Position', [0, 0, 500, 400]);
+set(gca, 'XLim', [0, number.bond + 1], 'XTick', 1 : number.bond, 'XTickLabel', reflect.bond, 'YLim', [0, max(channel.power.aggregate) * 1.1]);
+hold all;
+handle.power.aggregate = bar(channel.power.aggregate, 'FaceColor', '#77AC30', 'DisplayName', 'Equivalent');
[…]

### 2024-02-14 src/rate_kfactor.m

@@ -1,0 +1,51 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 128, 4);
+[transmit.power, receive.noise] = deal(db2pow(-20 : 5 : 20), db2pow(-75));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[channel.kfactor.direct, channel.kfactor.forward, channel.kfactor.backward] = deal(0, [0, 10, inf], [0, 10, inf]);
+[transmit.snr, reflect.bond] = deal(pow2db(transmit.power * channel.pathloss.direct ./ receive.noise), [1, reflect.antenna]);
+[number.bond, number.power, number.kfactor, number.realization] = deal(length(reflect.bond), length(transmit.power), length(channel.kfactor.forward), 100);
+
+for r = 1 : number.realization
+	for k = 1 : number.kfactor
+		channel.direct = sqrt(channel.pathloss.direct) * fading_ricean(receive.antenna, transmit.antenna, channel.kfactor.direct);
+		channel.forward = sqrt(channel.pathloss.forward) * fading_ricean(reflect.antenna, transmit.antenna, channel.kfactor.forward(k));
+		channel.backward = sqrt(channel.pathloss.backward) * fading_ricean(receive.antenna, reflect.antenna, channel.kfactor.backward(k));
+		clear scatter_rate;
+		for b = 1 : number.bond
+			for p = 1 : number.power
+				transmit.beamformer = precoder_rate(channel.direct, transmit.power(p), receive.noise);
+				[iter.converge, iter.tolerance, iter.counter, iter.rate] = deal(false, 1e-4, 0, rate_mimo(channel.direct, transmit.beamformer, receive.noise));
+				while ~iter.converge
+					[reflect.beamformer, channel.aggregate] = scatter_rate(channel.direct, channel.forward, channel.backward, transmit.beamformer, reflect.bond(b), receive.noise);
+					transmit.beamformer = precoder_rate(channel.aggregate, transmit.power(p), receive.noise);
+					receive.rate(p, b, k, r) = rate_mimo(channel.aggregate, transmit.beamformer, receive.noise);
[…]

### 2024-02-14 src/rate_sx.m

@@ -1,0 +1,54 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 2 .^ (4 : 2 : 8), 4);
+[transmit.power, receive.noise] = deal(db2pow(-20 : 5 : 20), db2pow(-75));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+transmit.snr = pow2db(transmit.power * channel.pathloss.direct ./ receive.noise);
+[number.bond, number.power, number.antenna, number.realization] = deal(2, length(transmit.power), length(reflect.antenna), 100);
+
+for r = 1 : number.realization
+	% * No RIS
+	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	for p = 1 : number.power
+		transmit.beamformer = precoder_rate(channel.direct, transmit.power(p), receive.noise);
+		receive.rate.direct(p, r) = rate_mimo(channel.direct, transmit.beamformer, receive.noise);
+	end
+	% * Have RIS
+	for a = 1 : number.antenna
+		reflect.bond = [1, reflect.antenna(a)];
+		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
+		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
+		clear scatter_rate;
+		for b = 1 : number.bond
+			for p = 1 : number.power
+				transmit.beamformer = precoder_rate(channel.direct, transmit.power(p), receive.noise);
+				[iter.converge, iter.tolerance, iter.counter, iter.rate] = deal(false, 1e-4, 0, rate_mimo(channel.direct, transmit.beamformer, receive.noise));
+				while ~iter.converge
+					[reflect.beamformer, channel.aggregate] = scatter_rate(channel.direct, channel.forward, channel.backward, transmit.beamformer, reflect.bond(b), receive.noise);
+					transmit.beamformer = precoder_rate(channel.aggregate, transmit.power(p), receive.noise);
+					receive.rate.aggregate(p, b, a, r) = rate_mimo(channel.aggregate, transmit.beamformer, receive.noise);
[…]

### 2024-02-14 src/rate_txrx.m

@@ -1,0 +1,45 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(2 .^ (0 : 2 : 4), 128, 2 .^ (0 : 2 : 4));
+[transmit.power, receive.noise] = deal(db2pow(-20 : 5 : 20), db2pow(-75));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[transmit.snr, reflect.bond] = deal(pow2db(transmit.power * channel.pathloss.direct ./ receive.noise), [1, reflect.antenna]);
+[number.bond, number.power, number.antenna, number.realization] = deal(length(reflect.bond), length(transmit.power), length(transmit.antenna), 100);
+
+for r = 1 : number.realization
+	for a = 1 : number.antenna
+		channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna(a), transmit.antenna(a));
+		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna(a));
+		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna(a), reflect.antenna);
+		clear scatter_rate;
+		for b = 1 : number.bond
+			for p = 1 : number.power
+				transmit.beamformer = precoder_rate(channel.direct, transmit.power(p), receive.noise);
+				[iter.converge, iter.tolerance, iter.counter, iter.rate] = deal(false, 1e-4, 0, rate_mimo(channel.direct, transmit.beamformer, receive.noise));
+				while ~iter.converge
+					[reflect.beamformer, channel.aggregate] = scatter_rate(channel.direct, channel.forward, channel.backward, transmit.beamformer, reflect.bond(b), receive.noise);
+					transmit.beamformer = precoder_rate(channel.aggregate, transmit.power(p), receive.noise);
+					receive.rate(p, b, a, r) = rate_mimo(channel.aggregate, transmit.beamformer, receive.noise);
+					iter.converge = (abs(receive.rate(p, b, a, r) - iter.rate) / iter.rate <= iter.tolerance);
+					iter.rate = receive.rate(p, b, a, r);
+					iter.counter = iter.counter + 1;
+				end
[…]

### 2024-02-14 src/singular_pareto.m

@@ -1,0 +1,57 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 128, 2);
+[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), [1, 4, 16, reflect.antenna]);
+assert(channel.rank == 2, 'The plot function is only for 2-sv case.');
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[channel.weight(1, :, 1), channel.weight(2, :, 1)] = pol2cart(pi / 4 : pi / 64 : pi * 3 / 4, 1);
+[channel.weight(1, :, 2), channel.weight(2, :, 2)] = pol2cart(pi / 4 : -pi / 64 : -pi / 4, 1);
+[channel.weight(1, :, 3), channel.weight(2, :, 3)] = pol2cart(5 * pi / 4 : pi / 64 : pi * 7 / 4, 1);
+[channel.weight(1, :, 4), channel.weight(2, :, 4)] = pol2cart(5 * pi / 4 : -pi / 64 : pi * 3 / 4, 1);
+[number.weight, number.case, number.bond, number.realization, flag.direct] = deal(size(channel.weight, 2), size(channel.weight, 3), length(reflect.bond), 2, true);
+
+for r = 1 : number.realization
+	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna);
+	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
+	channel.singular.direct(:, r) = svd(channel.direct);
+	if flag.direct
+		for b = 1 : number.bond
+			for c = 1 : number.case
+				clear scatter_singular;
+				for w = 1 : number.weight
+					[reflect.beamformer, channel.aggregate] = scatter_singular(channel.direct, channel.forward, channel.backward, channel.weight(:, w, c), reflect.bond(b));
+					channel.singular.aggregate(:, w, c, b, r) = svd(channel.aggregate);
+				end
+			end
+		end
+	else
+		for c = 1 : number.case
+			for w = 1 : number.weight
+				for b = 1 : number.bond
+					clear scatter_singular;
[…]

### 2024-02-14 src/singular_trend.m

@@ -1,0 +1,64 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna, reflect.sample] = deal(2, 2, 2, 1e2);
+[reflect.azimuth, reflect.elevation] = meshgrid(2 * pi * (1 : reflect.sample) / reflect.sample);
+
+channel.forward = fading_nlos(reflect.antenna, transmit.antenna);
+channel.backward = fading_nlos(receive.antenna, reflect.antenna);
+for s1 = 1 : reflect.sample
+	for s2 = 1 : reflect.sample
+		channel.singular.diagonal(s1, s2, :) = svd(channel.backward * scatter_2x2_diagonal(reflect.azimuth(s1, s2), reflect.elevation(s1, s2)) * channel.forward);
+		channel.singular.symmtary(s1, s2, :) = svd(channel.backward * scatter_2x2_symmtary(reflect.azimuth(s1, s2), reflect.elevation(s1, s2)) * channel.forward);
+	end
+end
+save('data/singular_trend.mat');
+
+figure('Name', 'Channel Singular Value vs RIS Configuration', 'Position', [0, 0, 500, 400]);
+handle.window = tiledlayout(2, 1);
+handle.axis(1) = nexttile;
+for s = 1 : 2
+	handle.mesh(1, s) = mesh(reflect.azimuth, reflect.elevation, channel.singular.diagonal(:, :, s), 'DisplayName', '$\sigma_' + string(s) + '(\mathbf{H})$');
+	datatip(handle.mesh(1, s), 'DataIndex', find(vec(channel.singular.diagonal(:, :, s)) == max(vec(channel.singular.diagonal(:, :, s))), 1));
+	datatip(handle.mesh(1, s), 'DataIndex', find(vec(channel.singular.diagonal(:, :, s)) == min(vec(channel.singular.diagonal(:, :, s))), 1));
+	handle.mesh(1, s).DataTipTemplate.DataTipRows = handle.mesh(1, s).DataTipTemplate.DataTipRows(end);
+	handle.mesh(1, s).DataTipTemplate.DataTipRows.Label = '\sigma';
+	handle.mesh(1, s).DataTipTemplate.DataTipRows.Format = '%.3f';
+	hold on;
+end
[…]

### 2024-02-15 main.tex
:pencil: Update propositions

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}[proposition]
 
@@
 	$\mathbb{C}$ represents the set of complex numbers.
-	$\mathbb{U}^{n \times n}$ denotes the set of $n \times n$ unitary matrices.
+	$\mathbb{H}^{n \times n}$ and $\mathbb{U}^{n \times n}$ denotes the set of $n \times n$ Hermitian and unitary matrices, respectively.
+	% $\mathbb{U}^{n \times n}$ denotes the set of $n \times n$ unitary matrices.
 	$\mathbf{0}$ and $\mathbf{I}$ are the all-zero and identity matrices with appropriate size, respectively.
@@
 		\end{maxi!}
-		where $n \in \{1,\ldots,\min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
+		where $n \in \{1,\ldots,N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
 		Varying $\{\rho_n\}$ unveils the entire achievable singular value region.
@@
 			\end{equation}
-			where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
+			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}$, respectively.
 		\end{lemma}
 		\begin{proof}
-			Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the compact \gls{svd} of the equivalent channel.
-			Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
-			\begin{equation}
-				\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*,
-			\end{equation}
-			whose differential w.r.t. $\mathbf{\Theta}_g^*$ is
-			\begin{align*}
-				\partial \sigma_n
-				& = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^*\\
-				& = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}\\
-				& = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\\
-				& = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
-			\end{align*}
-			According to \cite{Hjorungnes2007}, the corresponding complex derivative is
-			\begin{equation}
-				\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-				\label{eq:derivative_sv}
-			\end{equation}
-			Linear combination of \eqref{eq:derivative_sv} yields \eqref{eq:pareto_gradient}.
+			Please refer to Appendix~\ref{ap:pareto_gradient}.
 		\end{proof}
@@
 
-	\begin{subsection}{Some Analytical Bounds}\label{ss:bounds}
+	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
 		We then discuss some analytical bounds related to channel singular values.
-		\begin{proposition}[rank-deficient channel]\label{pp:dof}
+		\begin{proposition}[degree of freedom]\label{pp:dof}
 			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
@@
 		\begin{proof}
-			The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as\footnote{This is because (block) unitary matrices are closed under multiplication.}
-			\begin{equation}
-				\mathbf{\Theta} = \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block diagonal matrices of $L \times L$ unitary blocks.
-			Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
-			On the other hand, there exists a $\mathbf{\Theta}_\mathrm{D}$ such that
-			\begin{equation*}
-				\begin{split}
-					\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
-					& = \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\mathbf{H}_\mathrm{F}) \bigr) \\
-					& = \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr) \\
-					& = \max_\mathbf{\Theta} \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
-				\end{split}
-			\end{equation*}
-			The same result holds if the direct link is present.
+			Please refer to Appendix~\ref{ap:dof}.
 		\end{proof}
 
-		\begin{proposition}[\gls{los} forward\footnote{A similar result holds for \gls{los} backward channel.} channel]\label{pp:los}
-			If the forward channel is rank-1, then \gls{bd}-\gls{ris} can at most enlarge (resp.
+		\begin{proposition}[rank-deficient channel]\label{pp:rank_deficient}
+			% If the forward/backward channel is rank-$k$, then a \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n > k$) channel singular value to the $n-k$-th singular value of $\mathbf{T}$, or suppress the $n$-th ($n < N - k + 1$) channel singular value to the $n$-th singular value of $\mathbf{T}$.
+			% If the forward/backward channel is rank-$k$, then a sufficiently large \gls{bd}-\gls{ris} can at most enlarge (resp.
+suppress) the first (resp.
+last) $k$ equivalent channel singular values without bounds.
+			If the forward or backward channel is rank-$k$, then regardless of the \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
+			\begin{align}
+				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), && \text{if } n > k, \label{iq:sv_bound_enlarge}\\
+				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}), && \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
+			\end{align}
+			where
+			% \begin{align}
+			% 	\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
+			% 	\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k.
+			% \end{align}
+			\begin{equation}
+				\mathbf{T} \mathbf{T}^\mathsf{H} =
+				\begin{cases}
+					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
+					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
+				\end{cases}
+			\end{equation}
+			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
+			% where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the forward channel is rank-$k$ and $\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the backward channel is rank-$k$.
+		\end{proposition}
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:rank_deficient}.
+		\end{proof}
+
+		% \begin{corollary}[degree of freedom]
+		% 	In point-to-point \gls{mimo} with or without direct link, \gls{bd}-\gls{ris} cannot provide a higher \gls{dof} than diagonal \gls{ris}.
+		% \end{corollary}
+
+		\begin{corollary}[extreme singular values]
+			With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded from above while the last $k$ channel singular values can be suppressed to zero.
+			% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded from above while the last $k$ singular values can be suppressed to zero.
+			% If the forward or backward channel is rank-$k$ and the \gls{ris} is sufficiently large, then the first $k$ singular values of the equivalent channel are unbounded from above while the last $k$ singular values can be suppressed to zero.
+			% If the forward/backward channel is rank-$k$, then the first (resp. last) $k$ singular values of the equivalent channel are unbounded from above (resp. below).
+			% a sufficiently large \gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ singular values of the equivalent channel without bounds.
+		\end{corollary}
+
+		\begin{corollary}[\gls{los} channel]
+			If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
 suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
@@
 			\begin{equation}
-				\sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}),
+				\sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
 				\label{iq:sv_bound_los}
 			\end{equation}
-			where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{v}_\mathrm{F}$ is the right compact singular vector of $\mathbf{H}_\mathrm{F}$.
-			Note that $\sigma_1(\mathbf{H})$ is unbounded with a sufficiently large \gls{ris}.
+		\end{corollary}
+
+		% \begin{proposition}[\gls{los} forward\footnote{A similar result holds for \gls{los} backward channel.} channel]\label{pp:los}
+		% 	If the forward channel is rank-1, then \gls{bd}-\gls{ris} can at most enlarge (resp.
+suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
+$n$-th) singular value of $\mathbf{T}$, that is,
+		% 	\begin{equation}
+		% 		\sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}),
+		% 		\label{iq:sv_bound_los}
+		% 	\end{equation}
+		% 	where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{v}_\mathrm{F}$ is the right compact singular vector of $\mathbf{H}_\mathrm{F}$.
+		% 	Note that $\sigma_1(\mathbf{H})$ is unbounded with a sufficiently large \gls{ris}.
+		% \end{proposition}
+		% \begin{proof}
+		% 	Let $\mathbf{H}_\mathrm{F} = \sigma_\mathrm{F} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ be the compact \gls{svd} of the forward channel.
+		% 	The channel Gram matrix can be written as Hermitian-plus-rank-1:
+		% 	\begin{equation}
+		% 		\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
+		% 	\end{equation}
+		% 	where $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{z} \triangleq \sigma_\mathrm{F} \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{u}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{v}_\mathrm{F}$.
+		% 	By the Cauchy interlacing formula \cite{Golub2013}, the $n$-th ($n \ge 2$) eigenvalues of $\mathbf{G}$ are bounded by
+		% 	\begin{equation}
+		% 		\lambda_1(\mathbf{Y}) \ge \lambda_2(\mathbf{G}) \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge \lambda_N(\mathbf{G}) \ge \lambda_N(\mathbf{Y}).
+		% 		\label{iq:ev_bound_los}
+		% 	\end{equation}
+		% 	Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, the eigenvalues are non-negative and taking the square root of \eqref{iq:ev_bound_los} gives \eqref{iq:sv_bound_los}.
+		% \end{proof}
+		% It is worth notice that a similar conclusion holds for diagonal \gls{ris} \cite{Semmler2023}.
+		% We will later show that for a finite $N_\mathrm{S}$, using a larger group size can approach those bounds better.
+		% We will later
+		In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.
+
+		% \begin{proposition}[fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
+		% 	% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+		% 	If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then
+		% 	\begin{equation}
+		% 		\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
+		% 	\end{equation}
+		% 	where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+		% \end{proposition}
+
+		\begin{proposition}[fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
+			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the channel singular values can be manipulated up to
+			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
+			% only bounds that apply here are those that apply to the singular values of
+			\begin{equation}
+				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
+			\end{equation}
+			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			The problem now becomes how the singular values of matrix product are bounded by the singular values of its individual factors.
+			% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
 		\end{proposition}
+
 		\begin{proof}
-			Let $\mathbf{H}_\mathrm{F} = \sigma_\mathrm{F} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ be the compact \gls{svd} of the forward channel.
-			The channel Gram matrix can be written as Hermitian-plus-rank-1:
-			\begin{equation}
-				\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{z} \triangleq \sigma_\mathrm{F} \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{u}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{v}_\mathrm{F}$.
-			By the Cauchy interlacing formula \cite{Golub2013}, the $n$-th ($n \ge 2$) eigenvalues of $\mathbf{G}$ are bounded by
-			\begin{equation}
-				\lambda_1(\mathbf{Y}) \ge \lambda_2(\mathbf{G}) \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge \lambda_N(\mathbf{G}) \ge \lambda_N(\mathbf{Y}).
-				\label{iq:ev_bound_los}
-			\end{equation}
-			Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, the eigenvalues are non-negative and taking the square root of \eqref{iq:ev_bound_los} gives \eqref{iq:sv_bound_los}.
+			Please refer to Appendix~\ref{ap:fully_connected}.
 		\end{proof}
-		It is worth notice that a similar conclusion holds for diagonal \gls{ris} \cite{Semmler2023}.
-		We will later show that for a finite $N_\mathrm{S}$, using a larger group size can approach those bounds better.
-
-		\begin{proposition}[fully-connected \gls{ris} without direct link]
-			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then
-			\begin{equation}
-				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
-			\end{equation}
-			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-		\end{proposition}
-
-		\begin{proof}
-			Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
-			The scattering matrix of fully-connected \gls{ris} can be decomposed as
-			\begin{equation}
-				\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{X} \mathbf{U}_\mathrm{F}^\mathsf{H},
-				\label{eq:scattering_fc}
-			\end{equation}
-			where $\mathbf{X} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ is a unitary matrix to be designed.
-			The equivalent channel is thus a function of $\mathbf{X}$
-			\begin{equation}
-				\mathbf{H} = \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}.
-				\label{eq:channel_equivalent_fc}
-			\end{equation}
-			Since $\mathrm{sv}(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \mathrm{sv}(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
-			\begin{align*}
-				\mathrm{sv}(\mathbf{H}) & = \mathrm{sv}(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})\\
-				& = \mathrm{sv}(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})\\
-				& = \mathrm{sv}(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H})\\
-				& = \mathrm{sv}(\mathbf{BF}),
-			\end{align*}
-			where $\bar{\mathbf{U}}_{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}_{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
-		\end{proof}
-
-		There exist many singular value bounds on the product of two matrices in terms of their own singular values.
-		One comprehensive answer is \cite{Fulton2000}
+
+		% We now seek to relate the singular values of the matrix product to the singular values of its factors.
+
+		% The problem now becomes, what can we say about the singular values of the matrix product in terms of the singular values of the factors?
+
+		\begin{corollary}[generic singular value bounds \cite{Fulton2000}]
 			\begin{equation}
@@
 			\end{equation}
-		It implies the following special cases:
-		\begin{itemize}
-			\item upper bound on the largest singular value
-			\begin{equation}
-				\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F});
-			\end{equation}
-			\item lower bound on the smallest singular value
-			\begin{equation}
-				\sigma_N(\mathbf{H}) \ge \sigma_N(\mathbf{H}_\mathrm{B}) \sigma_N(\mathbf{H}_\mathrm{F});
-			\end{equation}
-			\item upper bound on the product of first $k$ singular values
-			\begin{equation}
-				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F});
-			\end{equation}
-			\item lower bound on the product of last $k$ singular values
-			\begin{equation}
-				\prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{F});
-			\end{equation}
-			\item upper bound on the sum of first $k$ singular values to the power of $p > 0$
-			\begin{equation}
-				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F});
+		\end{corollary}
+
+		\begin{corollary}[upper bound on the largest singular value]
+			\begin{equation}
+				\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}).
+			\end{equation}
+		\end{corollary}
+
+		\begin{corollary}[lower bound on the smallest singular value]
+			\begin{equation}
+				\sigma_N(\mathbf{H}) \ge \sigma_N(\mathbf{H}_\mathrm{B}) \sigma_N(\mathbf{H}_\mathrm{F}).
+			\end{equation}
+		\end{corollary}
+
+		\begin{corollary}[upper bound on the product of first $k$ singular values]
+			\begin{equation}
+				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
+			\end{equation}
+		\end{corollary}
+
+		\begin{corollary}[lower bound on the product of last $k$ singular values]
+			\begin{equation}
+				\prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
+			\end{equation}
+		\end{corollary}
+
+		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$]
+			\begin{equation}
+				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
 				\label{iq:sv_bound_fc_power}
 			\end{equation}
-			when $k = N$ and $p = 2$, it suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannel.
-		\end{itemize}
+			When $k = N$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannel.
+		\end{corollary}
+		% There exist many singular value bounds on the product of two matrices in terms of their own singular values.
+		% One comprehensive answer is \cite{Fulton2000}
+		% \begin{equation}
+		% 	\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
+		% 	\label{iq:sv_bound_fc}
+		% \end{equation}
+		% for all admissible triples $(I, J, K) \in T_r^n$ with $r < n$, where
+		% \begin{equation}
+		% 	\begin{gathered}
+		% 		% T_r^n \triangleq \Bigl\{(I, J, K) \in U_r^n \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
+		% 		% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
+		% 		T_r^n \triangleq \Bigl\{(I, J, K) \in U_r^n \mid \forall p < r, (F, G, H) \in T_p^r,\\
+		% 		\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
+		% 	\end{gathered}
+		% \end{equation}
+		% \begin{equation}
+		% 	U_r^n \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
+		% \end{equation}
+		% It implies the following special cases:
+		% \begin{itemize}
+		% 	\item upper bound on the largest singular value
+		% 	\begin{equation}
+		% 		\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F});
+		% 	\end{equation}
+		% 	\item lower bound on the smallest singular value
+		% 	\begin{equation}
+		% 		\sigma_N(\mathbf{H}) \ge \sigma_N(\mathbf{H}_\mathrm{B}) \sigma_N(\mathbf{H}_\mathrm{F});
+		% 	\end{equation}
+		% 	\item upper bound on the product of first $k$ singular values
+		% 	\begin{equation}
+		% 		\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F});
+		% 	\end{equation}
+		% 	\item lower bound on the product of last $k$ singular values
+		% 	\begin{equation}
+		% 		\prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{F});
+		% 	\end{equation}
+		% 	\item upper bound on the sum of first $k$ singular values to the power of $p > 0$
+		% 	\begin{equation}
+		% 		\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F});
+		% 		\label{iq:sv_bound_fc_power}
+		% 	\end{equation}
+		% 	when $k = N$ and $p = 2$, it suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannel.
+		% \end{itemize}
 
@@
 			Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
-			From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc}, we conclude the off-diagonal entries can enhance the capabilities of
+			We thus conclude the off-diagonal entries can enhance the capabilities of
 			\begin{itemize}
@@
 
-		Tight bounds are generally unavailable when \gls{mimo} direct link is present.
+		General tight bounds are missing when a \gls{mimo} direct link is present.
 		This is because the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
@@
 		\begin{proof}
-			The differential of $R$ w.r.t. $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
-			\begin{align*}
-				\partial R
-				& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
-				& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
-				& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
-			\end{align*}
-			and the corresponding complex derivative is \eqref{eq:rate_gradient}.
+			Please refer to Appendix~\ref{ap:rate_gradient}.
 		\end{proof}
@@
 		\begin{remark}
-			As mentioned in Section \ref{ss:bounds}, the key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
+			As mentioned in Section \ref{sc:bounds}, the key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
 			Problem \eqref{op:power_passive} is very similar (in terms of maximizing the inner product of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$) to the weighted orthogonal Procrustes problem \cite{Gower2004}
@@
 		\begin{proof}
-			The differential of \eqref{ob:power_passive} w.r.t. $\mathbf{\Theta}_g^*$ is
-			\begin{align*}
-				\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
-				& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr)\\
-				& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
-			\end{align*}
-			and the corresponding complex derivative is
-			\begin{equation}
-				\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{M}_g.
-			\end{equation}
-			% For a given $\mathbf{\Theta}$, we approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansion and recast problem \eqref{op:power_passive} as
-
-			First, we approximate the quadratic objective \eqref{ob:power_passive} by its local Taylor expansion
-			\begin{maxi!}
-				{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_passive_approx}}{\label{ob:power_passive_approx}}
-				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
-			\end{maxi!}
-			Let $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$ be the compact \gls{svd} of $\mathbf{M}_g$.
-			We have
-			\begin{equation}
-				\Re \bigl\{\mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \mathrm{tr}(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \mathrm{tr}(\mathbf{\Sigma}_g).
-			\end{equation}
-			The upper bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$, which implies the optimal solution of \eqref{op:power_passive_approx} is $\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$, $\forall g$.
-
-			Next, we prove that solving \eqref{op:power_passive_approx} successively does not decrease \eqref{ob:power_passive}.
-			Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
-			% Expanding both side gives \eqref{iq:power_passive_approx}.
-			On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:nonnegative_norm_square}.
-			Adding \eqref{iq:power_passive_approx} and \eqref{iq:nonnegative_norm_square}, we have
-			\begin{multline}
-				2 \Re \Bigl\{\mathrm{tr}(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
-				\ge 2 \Re \Bigl\{\mathrm{tr}({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
-			\end{multline}
-			which confirms that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
-			\begin{figure*}
-				\begin{equation}
-					\label{iq:power_passive_approx}
-					\resizebox{0.95\textwidth}{!}{
-						$2 \Re \Bigl\{\sum\limits_g \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \mathrm{tr}({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
-					}
-				\end{equation}
-				\begin{equation}
-					\label{iq:nonnegative_norm_square}
-					\resizebox{0.95\textwidth}{!}{
-						$\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
-					}
-				\end{equation}
-				\hrulefill
-			\end{figure*}
-
-			Finally, we prove that the converging point of \eqref{op:power_passive_approx}, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power_passive}.
-			The \gls{kkt} conditions of \eqref{op:power_passive} and \eqref{op:power_passive_approx} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
-			\begin{gather}
-				\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_passive_stationary}\\
-				\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_passive_approx_stationary}
-			\end{gather}
-			On convergence, \eqref{eq:power_passive_approx_stationary} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
-\mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^?
-\mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_passive_stationary}.
-			The proof is completed.
+			Please refer to Appendix~\ref{ap:power}.
 		\end{proof}
@@
 
-\begin{section}{Simulation Results}
+\begin{section}{Simulation Results}\label{sc:simulation}
 	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
@@
 
-% \begin{appendix}
-	% \begin{subsection}{Proof of Lemma \ref{lm:pareto_gradient}}\label{ap:pareto_gradient}
-	% 	Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the compact \gls{svd} of the equivalent channel.
-	% 	Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
-	% 	\begin{equation}
-	% 		\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*,
-	% 	\end{equation}
-	% 	whose differential w.r.t. $\mathbf{\Theta}_g^*$ is
-	% 	\begin{align*}
-	% 		\partial \sigma_n
-	% 		& = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^*\\
-	% 		& = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}\\
-	% 		& = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\\
-	% 		& = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
-	% 	\end{align*}
-	% 	According to \cite{Hjorungnes2007}, the corresponding complex derivative is
-	% 	\begin{equation}
-	% 		\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-	% 		\label{eq:derivative_sv}
-	% 	\end{equation}
-	% 	Linear combination of \eqref{eq:derivative_sv} yields \eqref{eq:pareto_gradient}.
-	% \end{subsection}
-
-	% \begin{subsection}{Proof of Proposition \ref{pp:dof}}\label{ap:dof}
-	% 	The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as\footnote{This is because (block) unitary matrices are closed under multiplication.}
-	% 	\begin{equation}
-	% 		\mathbf{\Theta} = \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H},
-	% 	\end{equation}
-	% 	where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block diagonal matrices of $L \times L$ unitary blocks.
-	% 	Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
-	% 	On the other hand, there exists a $\mathbf{\Theta}_\mathrm{D}$ such that
-	% 	\begin{equation*}
-	% 		\begin{split}
-	% 			\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
-	% 			& = \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\mathbf{H}_\mathrm{F}) \bigr) \\
-	% 			& = \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr) \\
-	% 			& = \max_\mathbf{\Theta} \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
-	% 		\end{split}
-	% 	\end{equation*}
-	% 	The same result holds if the direct link is present.
-	% \end{subsection}
-
-	% \begin{subsection}{Proof of Proposition \ref{pp:los}}\label{ap:los}
-	% 	Let $\mathbf{H}_\mathrm{F} = \sigma_\mathrm{F} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ be the compact \gls{svd} of the forward channel.
-	% 	The channel Gram matrix can be written as Hermitian-plus-rank-1:
-	% 	\begin{equation}
-	% 		\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
-	% 	\end{equation}
-	% 	where $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{z} \triangleq \sigma_\mathrm{F} \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{u}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{v}_\mathrm{F}$.
-	% 	By the Cauchy interlacing formula \cite{Golub2013}, the $n$-th ($n \ge 2$) eigenvalues of $\mathbf{G}$ are bounded by
-	% 	\begin{equation}
-	% 		\lambda_1(\mathbf{Y}) \ge \lambda_2(\mathbf{G}) \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge \lambda_N(\mathbf{G}) \ge \lambda_N(\mathbf{Y}).
-	% 		\label{iq:ev_bound_los}
-	% 	\end{equation}
-	% 	Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, the eigenvalues are non-negative and taking the square root of \eqref{iq:ev_bound_los} gives \eqref{iq:sv_bound_los}.
-	% \end{subsection}
-
-	% \begin{subsection}{Proof of Lemma \ref{lm:rate_gradient}}\label{ap:rate_gradient}
-	% 	The differential of $R$ w.r.t. $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
-	% 	\begin{align*}
-	% 		\partial R
-	% 		& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
-	% 		& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
-	% 		& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
-	% 	\end{align*}
-	% 	and the corresponding complex derivative is \eqref{eq:rate_gradient}.
-	% \end{subsection}
-
-% 	\begin{subsection}{Proof of Proposition \ref{pp:power}}\label{ap:power}
-% 		The differential of \eqref{ob:power_passive} w.r.t. $\mathbf{\Theta}_g^*$ is
-% 		\begin{align*}
-% 			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
-% 			& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr)\\
-% 			& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
-% 		\end{align*}
-% 		and the corresponding complex derivative is
-% 		\begin{equation}
-% 			\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{M}_g.
-% 		\end{equation}
-% 		% For a given $\mathbf{\Theta}$, we approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansion and recast problem \eqref{op:power_passive} as
-
-% 		First, we approximate the quadratic objective \eqref{ob:power_passive} by its local Taylor expansion
-% 		\begin{maxi!}
-% 			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_passive_approx}}{\label{ob:power_passive_approx}}
-% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
-% 		\end{maxi!}
-% 		Let $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$ be the compact \gls{svd} of $\mathbf{M}_g$.
-% 		We have
-% 		\begin{equation}
-% 			\Re \bigl\{\mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \mathrm{tr}(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \mathrm{tr}(\mathbf{\Sigma}_g).
-% 		\end{equation}
-% 		The upper bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$, which implies the optimal solution of \eqref{op:power_passive_approx} is $\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$, $\forall g$.
-
-% 		Next, we prove that solving \eqref{op:power_passive_approx} successively does not decrease \eqref{ob:power_passive}.
-% 		Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
-% 		% Expanding both side gives \eqref{iq:power_passive_approx}.
-% 		On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:nonnegative_norm_square}.
-% 		Adding \eqref{iq:power_passive_approx} and \eqref{iq:nonnegative_norm_square}, we have
-% 		\begin{multline}
-% 			2 \Re \Bigl\{\mathrm{tr}(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
-% 			\ge 2 \Re \Bigl\{\mathrm{tr}({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
-% 		\end{multline}
-% 		which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
-% 		\begin{figure*}
-% 			\begin{equation}
-% 				\label{iq:power_passive_approx}
-% 				\resizebox{0.95\textwidth}{!}{
-% 					$2 \Re \Bigl\{\sum\limits_g \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \mathrm{tr}({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
-% 				}
-% 			\end{equation}
-% 			\begin{equation}
-% 				\label{iq:nonnegative_norm_square}
-% 				\resizebox{0.95\textwidth}{!}{
-% 					$\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
-% 				}
-% 			\end{equation}
-% 			\hrulefill
-% 		\end{figure*}
-
-% 		Finally, we prove that the converging point of \eqref{op:power_passive_approx}, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power_passive}.
-% 		The \gls{kkt} conditions of \eqref{op:power_passive} and \eqref{op:power_passive_approx} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
-% 		\begin{gather}
-% 			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_passive_stationary}\\
-% 			\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_passive_approx_stationary}
-% 		\end{gather}
-% 		On convergence, \eqref{eq:power_passive_approx_stationary} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
+\begin{appendix}
+	\begin{subsection}{Proof of Lemma \ref{lm:pareto_gradient}}\label{ap:pareto_gradient}
+		Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the compact \gls{svd} of the equivalent channel.
+		Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
+		\begin{equation}
+			\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*,
+		\end{equation}
+		whose differential w.r.t. $\mathbf{\Theta}_g^*$ is
+		\begin{align*}
+			\partial \sigma_n
+			& = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^*\\
+			& = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}\\
+			& = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\\
+			& = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
+		\end{align*}
+		According to \cite{Hjorungnes2007}, the corresponding complex derivative is
+		\begin{equation}
+			\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+			\label{eq:derivative_sv}
+		\end{equation}
+		A linear combination of \eqref{eq:derivative_sv} yields \eqref{eq:pareto_gradient}.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Proposition \ref{pp:dof}}\label{ap:dof}
+		The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as\footnote{This is because (block) unitary matrices are closed under multiplication.}
+		\begin{equation}
+			\mathbf{\Theta} = \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H},
+		\end{equation}
+		where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block diagonal matrices of $L \times L$ unitary blocks.
+		Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
+		On the other hand, there exists a $\mathbf{\Theta}_\mathrm{D}$ such that
+		\begin{equation*}
+			\begin{split}
+				\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
+				& = \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\mathbf{H}_\mathrm{F}) \bigr) \\
+				& = \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr) \\
+				& = \max_\mathbf{\Theta} \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+			\end{split}
+		\end{equation*}
+		The same result holds if the direct link is present.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Proposition \ref{pp:rank_deficient}}\label{ap:rank_deficient}
+		We consider rank-$k$ forward channel and the proof follows similarly for rank-$k$ backward channel.
+		Let $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the compact \gls{svd} of the forward channel.
+		The channel Gram matrix $\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} $ can be written as
+		\begin{equation*}
+			\begin{split}
+				\mathbf{G}
+				& = \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \\
+				& \quad + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \\
+				& = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H} \\
+				& \quad + (\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F}) (\mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} + \mathbf{V}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{D}^\mathsf{H}) \\
+				& = \mathbf{Y} + \mathbf{Z} \mathbf{Z}^\mathsf{H},
+			\end{split}
+		\end{equation*}
+		where we define $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H} \in \mathbb{H}^{N_\mathrm{R} \times N_\mathrm{R}}$ and $\mathbf{Z} \triangleq \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{R} \times k}$.
+		That is to say, $\mathbf{G}$ can be expressed as a Hermitian matrix plus $k$ rank-1 perturbations.
+		According to the Cauchy interlacing formula \cite{Golub2013}, the $n$-th eigenvalue of $\mathbf{G}$ is bounded by
+		\begin{align}
+			\lambda_n(\mathbf{G}) & \le \lambda_{n-k}(\mathbf{Y}), && \text{if } n > k, \label{iq:ev:bound_enlarge} \\
+			\lambda_n(\mathbf{G}) & \ge \lambda_n(\mathbf{Y}), && \text{if } n < N - k + 1 \label{iq:ev_bound_suppress}.
+		\end{align}
+		Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, taking the square roots of \eqref{iq:ev:bound_enlarge} and \eqref{iq:ev_bound_suppress} gives \eqref{iq:sv_bound_enlarge} and \eqref{iq:sv_bound_suppress}.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Proposition \ref{pp:fully_connected}}\label{ap:fully_connected}
+		Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
+		The scattering matrix of fully-connected \gls{ris} can be decomposed as
+		\begin{equation}
+			\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{X} \mathbf{U}_\mathrm{F}^\mathsf{H},
+			\label{eq:scattering_fc}
+		\end{equation}
+		where $\mathbf{X} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ is a unitary matrix to be designed.
+		The equivalent channel is thus a function of $\mathbf{X}$
+		\begin{equation}
+			\mathbf{H} = \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}.
+			\label{eq:channel_equivalent_fc}
+		\end{equation}
+		Since $\mathrm{sv}(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \mathrm{sv}(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
+		\begin{align*}
+			\mathrm{sv}(\mathbf{H}) & = \mathrm{sv}(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})\\
+			& = \mathrm{sv}(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})\\
+			& = \mathrm{sv}(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H})\\
+			& = \mathrm{sv}(\mathbf{BF}),
+		\end{align*}
+		where $\bar{\mathbf{U}}_{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}_{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Lemma \ref{lm:rate_gradient}}\label{ap:rate_gradient}
+		The differential of $R$ w.r.t. $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
+		\begin{align*}
+			\partial R
+			& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
+			& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
+			& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
+		\end{align*}
+		and the corresponding complex derivative is \eqref{eq:rate_gradient}.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Proposition \ref{pp:power}}\label{ap:power}
+		The differential of \eqref{ob:power_passive} w.r.t. $\mathbf{\Theta}_g^*$ is
+		\begin{align*}
+			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
+			& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr)\\
+			& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
+		\end{align*}
+		and the corresponding complex derivative is
+		\begin{equation}
+			\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{M}_g.
+		\end{equation}
+		% For a given $\mathbf{\Theta}$, we approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansion and recast problem \eqref{op:power_passive} as
+
+		First, we approximate the quadratic objective \eqref{ob:power_passive} by its local Taylor expansion
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_passive_approx}}{\label{ob:power_passive_approx}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
+		\end{maxi!}
+		Let $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$ be the compact \gls{svd} of $\mathbf{M}_g$.
+		We have
+		\begin{equation}
+			\Re \bigl\{\mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \mathrm{tr}(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \mathrm{tr}(\mathbf{\Sigma}_g).
+		\end{equation}
+		The upper bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$, which implies the optimal solution of \eqref{op:power_passive_approx} is $\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$, $\forall g$.
+
+		Next, we prove that solving \eqref{op:power_passive_approx} successively does not decrease \eqref{ob:power_passive}.
+		Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
+		% Expanding both side gives \eqref{iq:power_passive_approx}.
+		On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:nonnegative_norm_square}.
+		Adding \eqref{iq:power_passive_approx} and \eqref{iq:nonnegative_norm_square}, we have
+		\begin{multline}
+			2 \Re \Bigl\{\mathrm{tr}(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
+			\ge 2 \Re \Bigl\{\mathrm{tr}({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
+		\end{multline}
+		which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
+		\begin{figure*}
+			\begin{equation}
+				\label{iq:power_passive_approx}
+				\resizebox{0.95\textwidth}{!}{
+					$2 \Re \Bigl\{\sum\limits_g \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \mathrm{tr}({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
+				}
+			\end{equation}
+			\begin{equation}
+				\label{iq:nonnegative_norm_square}
+				\resizebox{0.95\textwidth}{!}{
+					$\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
+				}
+			\end{equation}
+			\hrulefill
+		\end{figure*}
+
+		Finally, we prove that the converging point of \eqref{op:power_passive_approx}, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power_passive}.
+		The \gls{kkt} conditions of \eqref{op:power_passive} and \eqref{op:power_passive_approx} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
+		\begin{gather}
+			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_passive_stationary}\\
+			\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_passive_approx_stationary}
+		\end{gather}
+		On convergence, \eqref{eq:power_passive_approx_stationary} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
 \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^?
 \mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_passive_stationary}.
-% 		The proof is thus completed.
-% 	\end{subsection}
-% \end{appendix}
+		The proof is thus completed.
+	\end{subsection}
+\end{appendix}
 

### 2024-02-16 main.tex
:pencil: Add results

@@
 	% 	The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
-	% 	B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
 	% }
@@
 \begin{section}{Channel Singular Values Redistribution}
-	\begin{subsection}{A Toy Example}
+	\begin{subsection}{A Toy Example}\label{sc:toy_example}
 		We first illustrate the channel shaping capabilities of different \gls{ris} by a toy example.
@@
 
-		% The Pareto singular value problem \eqref{op:pareto} can thus be solved by Algorithm~\ref{ag:rcg}.
 		\begin{lemma}\label{lm:pareto_gradient}
@@
 				\end{cases}
+				\label{eq:auxiliary_matrix}
 			\end{equation}
@@
 
-		\begin{corollary}[extreme singular values]
-			With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded from above while the last $k$ channel singular values can be suppressed to zero.
-			% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded from above while the last $k$ singular values can be suppressed to zero.
-			% If the forward or backward channel is rank-$k$ and the \gls{ris} is sufficiently large, then the first $k$ singular values of the equivalent channel are unbounded from above while the last $k$ singular values can be suppressed to zero.
-			% If the forward/backward channel is rank-$k$, then the first (resp. last) $k$ singular values of the equivalent channel are unbounded from above (resp. below).
+		\begin{corollary}[extreme singular values\label{co:extreme}]
+			With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded above while the last $k$ channel singular values can be suppressed to zero.
+			% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
+			% If the forward or backward channel is rank-$k$ and the \gls{ris} is sufficiently large, then the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
+			% If the forward/backward channel is rank-$k$, then the first (resp. last) $k$ singular values of the equivalent channel are unbounded above (resp. below).
 			% a sufficiently large \gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ singular values of the equivalent channel without bounds.
@@
 
-		\begin{corollary}[\gls{los} channel]
+		\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} in \cite{Semmler2023}.}\label{co:los}]
 			If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
@@
 			\begin{equation}
-				\sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
+				\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
 				\label{iq:sv_bound_los}
@@
 
-		% \begin{proposition}[\gls{los} forward\footnote{A similar result holds for \gls{los} backward channel.} channel]\label{pp:los}
-		% 	If the forward channel is rank-1, then \gls{bd}-\gls{ris} can at most enlarge (resp.
-suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
-$n$-th) singular value of $\mathbf{T}$, that is,
-		% 	\begin{equation}
-		% 		\sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \sigma_2(\mathbf{T}) \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}),
-		% 		\label{iq:sv_bound_los}
-		% 	\end{equation}
-		% 	where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{v}_\mathrm{F}$ is the right compact singular vector of $\mathbf{H}_\mathrm{F}$.
-		% 	Note that $\sigma_1(\mathbf{H})$ is unbounded with a sufficiently large \gls{ris}.
-		% \end{proposition}
-		% \begin{proof}
-		% 	Let $\mathbf{H}_\mathrm{F} = \sigma_\mathrm{F} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ be the compact \gls{svd} of the forward channel.
-		% 	The channel Gram matrix can be written as Hermitian-plus-rank-1:
-		% 	\begin{equation}
-		% 		\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} = \mathbf{Y} + \mathbf{z} \mathbf{z}^\mathsf{H},
-		% 	\end{equation}
-		% 	where $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{v}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ and $\mathbf{z} \triangleq \sigma_\mathrm{F} \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{u}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{v}_\mathrm{F}$.
-		% 	By the Cauchy interlacing formula \cite{Golub2013}, the $n$-th ($n \ge 2$) eigenvalues of $\mathbf{G}$ are bounded by
-		% 	\begin{equation}
-		% 		\lambda_1(\mathbf{Y}) \ge \lambda_2(\mathbf{G}) \ge \lambda_2(\mathbf{Y}) \ge \ldots \ge \lambda_{N-1}(\mathbf{Y}) \ge \lambda_N(\mathbf{G}) \ge \lambda_N(\mathbf{Y}).
-		% 		\label{iq:ev_bound_los}
-		% 	\end{equation}
-		% 	Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, the eigenvalues are non-negative and taking the square root of \eqref{iq:ev_bound_los} gives \eqref{iq:sv_bound_los}.
-		% \end{proof}
-		% It is worth notice that a similar conclusion holds for diagonal \gls{ris} \cite{Semmler2023}.
-		% We will later show that for a finite $N_\mathrm{S}$, using a larger group size can approach those bounds better.
-		% We will later
 		In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.
-
-		% \begin{proposition}[fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
-		% 	% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-		% 	If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then
-		% 	\begin{equation}
-		% 		\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
-		% 	\end{equation}
-		% 	where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-		% \end{proposition}
 
@@
 			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-			The problem now becomes how the singular values of matrix product are bounded by the singular values of its individual factors.
 			% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
@@
 
-		% We now seek to relate the singular values of the matrix product to the singular values of its factors.
-
-		% The problem now becomes, what can we say about the singular values of the matrix product in terms of the singular values of the factors?
+		The problem now becomes how the singular values of matrix product are bounded by the singular values of its individual factors.
+		Let $N' = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le N'$.
+		We have the following corollaries.
 
@@
 			\end{equation}
-			for all admissible triples $(I, J, K) \in T_r^n$ with $r < n$, where
-			\begin{equation}
+			for all admissible triples $(I, J, K) \in T_r^{N'}$ with $r < N'$, where
+			\begin{equation*}
 				\begin{gathered}
-					% T_r^n \triangleq \Bigl\{(I, J, K) \in U_r^n \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
+					% T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
 					% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-					T_r^n \triangleq \Bigl\{(I, J, K) \in U_r^n \mid \forall p < r, (F, G, H) \in T_p^r,\\
+					T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \forall p < r, (F, G, H) \in T_p^r,\\
 					\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
 				\end{gathered}
-			\end{equation}
-			\begin{equation}
-				U_r^n \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
-			\end{equation}
+			\end{equation*}
+			\begin{equation*}
+				U_r^{N'} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
+			\end{equation*}
 		\end{corollary}
@@
 
-		\begin{corollary}[lower bound on the smallest singular value]
-			\begin{equation}
-				\sigma_N(\mathbf{H}) \ge \sigma_N(\mathbf{H}_\mathrm{B}) \sigma_N(\mathbf{H}_\mathrm{F}).
+		% \begin{corollary}[lower bound on the smallest singular value]
+		% 	\begin{equation}
+		% 		\sigma_{N'}(\mathbf{H}) \ge \sigma_{N'}(\mathbf{H}_\mathrm{B}) \sigma_{N'}(\mathbf{H}_\mathrm{F}).
+		% 	\end{equation}
+		% \end{corollary}
+
+		\begin{corollary}[upper bound on the product of first $k$ singular values]
+			\begin{equation}
+				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
 			\end{equation}
@@
 
-		\begin{corollary}[upper bound on the product of first $k$ singular values]
-			\begin{equation}
-				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
-			\end{equation}
-		\end{corollary}
-
-		\begin{corollary}[lower bound on the product of last $k$ singular values]
-			\begin{equation}
-				\prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
-			\end{equation}
-		\end{corollary}
+		% \begin{corollary}[lower bound on the product of last $k$ singular values]
+		% 	\begin{equation}
+		% 		\prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
+		% 	\end{equation}
+		% \end{corollary}
 
@@
 			\end{equation}
-			When $k = N$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannel.
+			When $k = N'$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels.
 		\end{corollary}
-		% There exist many singular value bounds on the product of two matrices in terms of their own singular values.
-		% One comprehensive answer is \cite{Fulton2000}
-		% \begin{equation}
-		% 	\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
-		% 	\label{iq:sv_bound_fc}
-		% \end{equation}
-		% for all admissible triples $(I, J, K) \in T_r^n$ with $r < n$, where
-		% \begin{equation}
-		% 	\begin{gathered}
-		% 		% T_r^n \triangleq \Bigl\{(I, J, K) \in U_r^n \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
-		% 		% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-		% 		T_r^n \triangleq \Bigl\{(I, J, K) \in U_r^n \mid \forall p < r, (F, G, H) \in T_p^r,\\
-		% 		\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-		% 	\end{gathered}
-		% \end{equation}
-		% \begin{equation}
-		% 	U_r^n \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
-		% \end{equation}
-		% It implies the following special cases:
-		% \begin{itemize}
-		% 	\item upper bound on the largest singular value
-		% 	\begin{equation}
-		% 		\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F});
-		% 	\end{equation}
-		% 	\item lower bound on the smallest singular value
-		% 	\begin{equation}
-		% 		\sigma_N(\mathbf{H}) \ge \sigma_N(\mathbf{H}_\mathrm{B}) \sigma_N(\mathbf{H}_\mathrm{F});
-		% 	\end{equation}
-		% 	\item upper bound on the product of first $k$ singular values
-		% 	\begin{equation}
-		% 		\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F});
-		% 	\end{equation}
-		% 	\item lower bound on the product of last $k$ singular values
-		% 	\begin{equation}
-		% 		\prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N}^{N-k+1} \sigma_n(\mathbf{H}_\mathrm{F});
-		% 	\end{equation}
-		% 	\item upper bound on the sum of first $k$ singular values to the power of $p > 0$
-		% 	\begin{equation}
-		% 		\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F});
-		% 		\label{iq:sv_bound_fc_power}
-		% 	\end{equation}
-		% 	when $k = N$ and $p = 2$, it suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannel.
-		% \end{itemize}
 
@@
 
-		General tight bounds are missing when a \gls{mimo} direct link is present.
-		This is because the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
+		Tight bounds are inapplicable when a \gls{mimo} direct link is present, as the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
+		Such a balance often involves optimization approaches and another example will be discussed in Section~\ref{sc:low_complexity}.
 	\end{subsection}
@@
 
-\begin{section}{Achievable Rate Maximization}
+\begin{section}{Achievable Rate Maximization}\label{sc:rate}
 	The \gls{mimo} achievable rate maximization problem is formulated w.r.t. joint active and passive beamforming
@@
 		where $\mathbf{V}$ is the right channel singular matrix and $\mathbf{S}^\star$ is the optimal water-filling power allocation matrix.
-		The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded from above.
+		The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
 	\end{subsection}
 
-	\begin{subsection}{Low-Complexity Solution}
+	\begin{subsection}{Low-Complexity Solution}\label{sc:low_complexity}
 		We then propose a low-complexity solution to problem \eqref{op:rate} based on channel shaping.
@@
 	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
-	Rayleigh fading is assumed for all channels $\kappa_\mathrm{D},\kappa_\mathrm{B},\kappa_\mathrm{F} \to \infty$ unless otherwise specified.
+	$\kappa \to \infty$ is assumed for all channels unless otherwise specified.
 
 	\begin{subsection}{Channel Singular Values Redistribution}
+		\begin{subsubsection}{Pareto Frontier}
 			\begin{figure}[!t]
@@
 				}
-			\caption{Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.}
+				\caption{Pareto frontiers of 2T2R channel singular values reshaped by a \gls{ris}.}
 				\label{fg:singular_pareto}
 			\end{figure}
-
+			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
+			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
+			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
+			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			When the direct link is present, the region shape depends heavily on the relative channel strength.
+			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} cannot compensate the \qty{35}{dB} direct-indirect power imbalance and results in a limited range of singular values.
+			The achievable regions are thus symmetric around the direct point.
+			Interestingly, the shape evolves from oval to square as the group size $L$ increases, which suggests that \gls{bd}-\gls{ris} can achieve a better tradeoff in subchannel manipulation.
+			As the number of scattering elements $N_\mathrm{S}$ increases, the dynamic range of singular values is widened and the achievable region becomes more trapezoidal.
+			It is also worth noticing in Fig. \subref*{fg:singular_pareto_sx128} that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and the importance of in-group connections.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Analytical and Numerical Results}
 			\begin{figure}[!t]
 				\centering
-			\subfloat[$4 \times 32 \times 4$\label{fg:singular_bound_rank1_sx32}]{
+				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
 					\resizebox{0.48\columnwidth}{!}{
@@
 				}
-			\subfloat[$4 \times 64 \times 4$\label{fg:singular_bound_rank1_sx64}]{
+				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
 					\resizebox{0.48\columnwidth}{!}{
@@
 				\\
-			\subfloat[$4 \times 128 \times 4$\label{fg:singular_bound_rank2_sx128}]{
+				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
 					\resizebox{0.48\columnwidth}{!}{
@@
 				}
-			\subfloat[$4 \times 256 \times 4$\label{fg:singular_bound_rank4_sx256}]{
+				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
 					\resizebox{0.48\columnwidth}{!}{
@@
 				\caption{
-				Achievable channel singular values: analytical bounds (green lines) and optimized results (blue and red bars).
+					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
 					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
+					`rank-$k$' refers to the forward channel.
 				}
@@
 			\end{figure}
-
-		The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
+			Fig.
+\ref{fg:singular_bound} illustrates the analytical bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
+			Here we assme a rank-$k$ forward channel without loss of generality.
+			When the \gls{ris} is in the vicinity of the transmitter, Figs.
+\subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
+			We also observe that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
+			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
+			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
+			As expected from Corollary \ref{co:extreme}, the largest 2 singular values are unbounded above and the smallest 2 singular values can be suppressed to zero (with a sufficiently large \gls{ris}).
+			Proposition \ref{pp:rank_deficient} also predicts the fact that $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{H}) \ge \sigma_2(\mathbf{T})$, $\sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{T})$, and $\sigma_4(\mathbf{H}) \le \sigma_2(\mathbf{T})$.
+			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra bounds when both forward and backward channels are full-rank.
+			This is because in \eqref{eq:auxiliary_matrix} the compact singular matrices $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{F}$ become unitary such that $\mathbf{T}=\mathbf{0}$.
+			The numerical results are consistent with the analytical bounds, and we also conclude that the advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.
+		\end{subsubsection}
+
+		% The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
 		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.

### 2024-02-16 src/singular_pareto.m

@@ -1,14 +1,14 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 128, 2);
-[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), [1, 4, 16, reflect.antenna]);
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 16, 2);
+[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), unique([1, 4, 16, reflect.antenna]));
 assert(channel.rank == 2, 'The plot function is only for 2-sv case.');
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
 [channel.weight(1, :, 1), channel.weight(2, :, 1)] = pol2cart(pi / 4 : pi / 64 : pi * 3 / 4, 1);
 [channel.weight(1, :, 2), channel.weight(2, :, 2)] = pol2cart(pi / 4 : -pi / 64 : -pi / 4, 1);
 [channel.weight(1, :, 3), channel.weight(2, :, 3)] = pol2cart(5 * pi / 4 : pi / 64 : pi * 7 / 4, 1);
 [channel.weight(1, :, 4), channel.weight(2, :, 4)] = pol2cart(5 * pi / 4 : -pi / 64 : pi * 3 / 4, 1);
-[number.weight, number.case, number.bond, number.realization, flag.direct] = deal(size(channel.weight, 2), size(channel.weight, 3), length(reflect.bond), 2, true);
+[number.weight, number.case, number.bond, number.realization, flag.direct] = deal(size(channel.weight, 2), size(channel.weight, 3), length(reflect.bond), 2, false);
 
 for r = 1 : number.realization
 	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
@@ -39,7 +39,7 @@ for r = 1 : number.realization
 end
 channel.singular.direct = mean(channel.singular.direct, ndims(channel.singular.direct));
 channel.singular.aggregate = mean(channel.singular.aggregate, ndims(channel.singular.aggregate));
-save('data/singular_pareto.mat');
+% save('data/singular_pareto.mat');
 
[…]

### 2024-02-17 main.tex
:pencil: Channel singular redistribution

@@
 
-		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$]
+		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
 			\begin{equation}
@@
 		\begin{remark}
-			Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
-			We thus conclude the off-diagonal entries can enhance the capabilities of
+			From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+			% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+			\begin{equation}
+				\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
+				\label{eq:scattering_fc_tight}
+			\end{equation}
+			An interpretation is that the off-diagonal entries can enhance the capabilities of
 			\begin{itemize}
@@
 		\begin{proposition}\label{pp:power}
-			Start from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
+			Starting from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
 			\begin{equation}
 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+				\label{eq:scattering_power}
 			\end{equation}
@@
 				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+				\label{eq:auxiliary_matrix_power}
 			\end{equation}
@@
 				}
-				\caption{Pareto frontiers of 2T2R channel singular values reshaped by a \gls{ris}.}
+				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
 				\label{fg:singular_pareto}
@@
 			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
-			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
+			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
+			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
+			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
 			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
-			When the direct link is present, the region shape depends heavily on the relative channel strength.
-			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} cannot compensate the \qty{35}{dB} direct-indirect power imbalance and results in a limited range of singular values.
-			The achievable regions are thus symmetric around the direct point.
-			Interestingly, the shape evolves from oval to square as the group size $L$ increases, which suggests that \gls{bd}-\gls{ris} can achieve a better tradeoff in subchannel manipulation.
-			As the number of scattering elements $N_\mathrm{S}$ increases, the dynamic range of singular values is widened and the achievable region becomes more trapezoidal.
-			It is also worth noticing in Fig. \subref*{fg:singular_pareto_sx128} that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and the importance of in-group connections.
+			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
+			In Fig.
+\subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
+			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
+			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
+			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
+			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
 		\end{subsubsection}
 
-		\begin{subsubsection}{Analytical and Numerical Results}
+		\begin{subsubsection}{Analytical Bounds and Numerical Results}
 			\begin{figure}[!t]
@@
 			Fig.
-\ref{fg:singular_bound} illustrates the analytical bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
+\ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
 			Here we assme a rank-$k$ forward channel without loss of generality.
@@
 \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
-			We also observe that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
+			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
 			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
-			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
-			As expected from Corollary \ref{co:extreme}, the largest 2 singular values are unbounded above and the smallest 2 singular values can be suppressed to zero (with a sufficiently large \gls{ris}).
-			Proposition \ref{pp:rank_deficient} also predicts the fact that $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{H}) \ge \sigma_2(\mathbf{T})$, $\sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{T})$, and $\sigma_4(\mathbf{H}) \le \sigma_2(\mathbf{T})$.
-			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra bounds when both forward and backward channels are full-rank.
-			This is because in \eqref{eq:auxiliary_matrix} the compact singular matrices $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{F}$ become unitary such that $\mathbf{T}=\mathbf{0}$.
-			The numerical results are consistent with the analytical bounds, and we also conclude that the advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.
+			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
+			% The observations align with Proposition \ref{pp:rank_deficient} that t
+			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
+			Those observations align with Proposition \ref{pp:rank_deficient} and Corollary \ref{co:extreme}.
+			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
+			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
+			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.
+
+			\begin{figure}[!t]
+				\centering
+				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
+					\resizebox{0.4725\columnwidth}{!}{
+						\input{assets/simulation/power_bond_txrx1_nd.tex}
+					}
+				}
+				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
+					\resizebox{0.4875\columnwidth}{!}{
+						\input{assets/simulation/power_bond_txrx4_nd.tex}
+					}
+				}
+				\caption{
+					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
+					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward subchannels.
+				}
+				\label{fg:power_bond}
+			\end{figure}
+
+			Fig.
+\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
+			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_tight} or via optimization approach \eqref{eq:scattering_power}.
+			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
+			% We observe that the bound is also tight for fully-connected \gls{bd}-\gls{ris}.
+			% Increasing the group size of \gls{bd}-\gls{ris} significantly improves the channel power especially for a large \gls{mimo}.
+			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a fully-connected one can achieve the bound.
+			% The bound here indicates how much power can potentially be extracted from the forward and backward channels.
+			% We observe that using a larger group size can approach the bound better, and full
+			% We observe that the bound is tight for fully-connected \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
+			For the \gls{siso} case in Fig.
+\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
+			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
+			Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
+			This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
+			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
+			Now consider a diagonal \gls{ris} in \gls{mimo}.
+			Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
+			Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
+			It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
+			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
 		\end{subsubsection}
@@
 	\begin{subsection}{Achievable Rate Maximization}
-		\begin{figure}[!t]
-			\centering
-			\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
-				\resizebox{0.4725\columnwidth}{!}{
-					\input{assets/simulation/power_bond_txrx1_nd.tex}
-				}
-			}
-			\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
-				\resizebox{0.4875\columnwidth}{!}{
-					\input{assets/simulation/power_bond_txrx4_nd.tex}
-				}
-			}
-			\caption{
-				Average channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
-			}
-			\label{fg:power_bond}
-		\end{figure}
-
 		\begin{figure}[!t]

### 2024-02-17 assets/simulation/power_sx_txrx16.tex
:pencil: Channel singular redistribution

@@
 %
-\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
-\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
-\definecolor{mycolor3}{rgb}{0.92941,0.69412,0.12549}%
-\definecolor{mycolor4}{rgb}{0.49412,0.18431,0.55686}%
-\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
+\definecolor{mycolor1}{rgb}{0.85000,0.32500,0.09800}%
+\definecolor{mycolor2}{rgb}{0.00000,0.44706,0.74118}%
+\definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
+\definecolor{mycolor4}{rgb}{0.49400,0.18400,0.55600}%
+\definecolor{mycolor5}{rgb}{0.85098,0.32549,0.09804}%
+\definecolor{mycolor6}{rgb}{0.46600,0.67400,0.18800}%
+\definecolor{mycolor7}{rgb}{0.30100,0.74500,0.93300}%
+\definecolor{mycolor8}{rgb}{0.92941,0.69412,0.12549}%
+\definecolor{mycolor9}{rgb}{0.63500,0.07800,0.18400}%
+\definecolor{mycolor10}{rgb}{0.00000,0.44700,0.74100}%
+\definecolor{mycolor11}{rgb}{0.49412,0.18431,0.55686}%
+\definecolor{mycolor12}{rgb}{0.46667,0.67451,0.18824}%
+\definecolor{mycolor13}{rgb}{0.50196,0.50196,0.50196}%
 %
@@
 ymode=log,
-ymin=7.63413889612284e-05,
-ymax=0.000357009156162705,
+ymin=7.71952537202106e-05,
+ymax=0.000358145391898644,
 yminorticks=true,
@@
   table[row sep=crcr]{%
-1	8.03593568012931e-05\\
-2	8.03593568012931e-05\\
-3	8.03593568012931e-05\\
-4	8.03593568012931e-05\\
-5	8.03593568012931e-05\\
-6	8.03593568012931e-05\\
-7	8.03593568012931e-05\\
-8	8.03593568012931e-05\\
-9	8.03593568012931e-05\\
+1	8.12581618107481e-05\\
+2	8.12581618107481e-05\\
+3	8.12581618107481e-05\\
+4	8.12581618107481e-05\\
+5	8.12581618107481e-05\\
+6	8.12581618107481e-05\\
+7	8.12581618107481e-05\\
+8	8.12581618107481e-05\\
+9	8.12581618107481e-05\\
 };
@@
 
-\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
+\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
+x	y\\
+5	8.74153313091917e-05\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
+x	y\\
+5	8.74291033971713e-05\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor5, forget plot] table[row sep=crcr]{%
+x	y\\
+6	9.91843205545709e-05\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor5, forget plot] table[row sep=crcr]{%
+x	y\\
+6	9.91780210311253e-05\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
+x	y\\
+7	0.00012405412223482\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
+x	y\\
+7	0.000124044149009442\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor11, forget plot] table[row sep=crcr]{%
+x	y\\
+8	0.000182844868229739\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor11, forget plot] table[row sep=crcr]{%
+x	y\\
+8	0.000182852647982853\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor12, forget plot] table[row sep=crcr]{%
+x	y\\
+9	0.000339584399340245\\
+};
+\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor12, forget plot] table[row sep=crcr]{%
+x	y\\
+9	0.000339587956470715\\
+};
+
+\addplot[draw=none, only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor13] table[row sep=crcr]{%
+x	y\\
+1	1\\
+};
+\addlegendentry{OP-left}
+
+\addplot[draw=none, only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor13] table[row sep=crcr]{%
+x	y\\
+1	1\\
+};
+\addlegendentry{OP-right}
+
+\addplot [color=mycolor2, line width=2.0pt]
   table[row sep=crcr]{%
-1	8.32187269864919e-05\\
-2	8.41922087195748e-05\\
-3	8.55795092915898e-05\\
-4	8.71382957344062e-05\\
-5	8.87320958720005e-05\\
+1	8.41788427928869e-05\\
+2	8.50641788557691e-05\\
+3	8.63696852707132e-05\\
+4	8.79903454326538e-05\\
+5	8.96339735645668e-05\\
 };
@@
 
-\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
+\addplot [color=mycolor5, dashed, line width=2.0pt]
   table[row sep=crcr]{%
-1	8.6466574171426e-05\\
-2	8.81326989213474e-05\\
-3	9.06190783177407e-05\\
-4	9.40273928578491e-05\\
-5	9.73131338921825e-05\\
-6	9.94886394941543e-05\\
+1	8.72783634122255e-05\\
+2	8.91184079692796e-05\\
+3	9.17640563659579e-05\\
+4	9.50977289249081e-05\\
+5	9.85503564245316e-05\\
+6	0.00010076742152366\\
 };
@@
 
-\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
+\addplot [color=mycolor8, dotted, line width=2.0pt]
   table[row sep=crcr]{%
-1	9.23552447351784e-05\\
-2	9.66298198027635e-05\\
-3	0.000102096862854765\\
-4	0.000109010799564887\\
-5	0.00011684562278114\\
-6	0.000121837810358247\\
-7	0.000124553664322635\\
+1	9.36120443845964e-05\\
+2	9.75056089045287e-05\\
+3	0.000102998044584118\\
+4	0.000110120638452998\\
+5	0.0001177772588008\\
+6	0.000122854470762259\\
+7	0.000125497666976946\\
 };
@@
 
-\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
+\addplot [color=mycolor11, dashdotted, line width=2.0pt]
   table[row sep=crcr]{%
-1	0.000104965329801996\\
-2	0.00011389799786835\\
-3	0.000126536878725085\\
-4	0.000142525515494825\\
-5	0.000160952430585978\\
-6	0.000173883585167439\\
-7	0.000180725719749113\\
-8	0.000184115133386408\\
+1	0.000106289915229579\\
+2	0.000114680256721358\\
+3	0.000126826397397359\\
+4	0.000142994695102657\\
+5	0.00016107230730003\\
+6	0.000173889895707073\\
+7	0.000180752926606848\\
+8	0.000184267352458571\\
 };
@@
 
-\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
+\addplot [color=mycolor12, line width=2.0pt]
   table[row sep=crcr]{%
-1	0.000134020224284578\\
-2	0.000153465030738225\\
-3	0.000181252804375544\\
-4	0.000220639327233136\\
-5	0.000268738002904876\\
-6	0.000305073448328176\\
-7	0.000324412126742617\\
-8	0.000334907924545081\\
-9	0.000340008720154957\\
+1	0.000134334856638143\\
+2	0.000153364621257308\\
+3	0.000182125698990213\\
+4	0.000221951821498391\\
+5	0.000269865717893532\\
+6	0.000305861046930524\\
+7	0.00032571637890533\\
+8	0.000335868097136638\\
+9	0.00034109084942728\\
 };
@@
 \end{axis}
+
+\begin{axis}[%
+width=9.816cm,
+height=7.362cm,
+at={(-1.276cm,-0.81cm)},
+scale only axis,
+xmin=0,
+xmax=1,
+ymin=0,
+ymax=1,
+axis line style={draw=none},
+ticks=none,
+axis x line*=bottom,
+axis y line*=left
+]
+\end{axis}
 \end{tikzpicture}%

### 2024-02-17 main.tex
:pencil: Channel singular redistribution

@@
 	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\%, 312\%, 537\% over single-connected in $1 \times 1$, $4 \times 4$, $16 \times 16$ \gls{mimo} under independent Rayleigh fading, respectively.
+	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
 	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
@@
 				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/singular_pareto_sx32_nd.tex}
@@
 				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/singular_pareto_sx32.tex}
@@
 				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/singular_pareto_sx64.tex}
@@
 				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/singular_pareto_sx128.tex}
@@
 				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/singular_bound_rank1_sx32.tex}
@@
 				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/singular_bound_rank1_sx64.tex}
@@
 				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/singular_bound_rank2_sx128.tex}
@@
 				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/singular_bound_rank4_sx256.tex}
@@
 				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
-					\resizebox{0.4725\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/power_bond_txrx1_nd.tex}
@@
 				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
-					\resizebox{0.4875\columnwidth}{!}{
+					\resizebox{!}{3.25cm}{
 						\input{assets/simulation/power_bond_txrx4_nd.tex}
@@
 			\subfloat[$4 \times N_\mathrm{S} \times 4$ (no direct)\label{fg:power_sx_txrx4_nd}]{
-				\resizebox{0.49\columnwidth}{!}{
+				\resizebox{!}{3.25cm}{
 					\input{assets/simulation/power_sx_txrx4_nd.tex}
@@
 			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
-				\resizebox{0.47\columnwidth}{!}{
+				\resizebox{!}{3.25cm}{
 					\input{assets/simulation/power_sx_txrx16.tex}
@@
 			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
-				\resizebox{0.49\columnwidth}{!}{
+				\resizebox{!}{3.25cm}{
 					\input{assets/simulation/rate_beamforming.tex}
@@
 			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
-				\resizebox{0.47\columnwidth}{!}{
+				\resizebox{!}{3.25cm}{
 					\input{assets/simulation/rate_txrx.tex}
@@
 			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
-				\resizebox{0.47\columnwidth}{!}{
+				\resizebox{!}{3.25cm}{
 					\input{assets/simulation/rate_sx.tex}
@@
 			\subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
-				\resizebox{0.47\columnwidth}{!}{
+				\resizebox{!}{3.25cm}{
 					\input{assets/simulation/rate_kfactor.tex}

### 2024-02-17 src/lib/scatter_procrustes_left.m

@@ -1,0 +1,5 @@
+function [Theta, H] = scatter_procrustes_left(H_d, H_f, H_b)
+	[U, ~, V] = svd(pinv(H_b) * H_d * H_f');
+	Theta = U * V';
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+end

### 2024-02-17 src/lib/scatter_procrustes_right.m

@@ -1,0 +1,5 @@
+function [Theta, H] = scatter_procrustes_right(H_d, H_f, H_b)
+	[U, ~, V] = svd(H_b' * H_d * pinv(H_f));
+	Theta = U * V';
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+end

### 2024-02-17 src/power_sx.m

@@ -3,7 +3,7 @@ clc; clear; close; setup;
 [transmit.antenna, reflect.antenna, receive.antenna] = deal(16, 2 .^ (4 : 8), 16);
 % [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e1, true);
+[number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e2, true);
 
 for r = 1 : number.realization
 	% * No RIS
@@ -19,25 +19,53 @@ for r = 1 : number.realization
 			[reflect.beamformer, channel.aggregate] = scatter_power_max(channel.direct, channel.forward, channel.backward, reflect.bond);
 			channel.power.aggregate(b, a, r) = norm(channel.aggregate, 'fro') ^ 2;
 		end
+		if flag.direct
+			[~, channel.procrustes.left] = scatter_procrustes_left(channel.direct, channel.forward, channel.backward);
+			[~, channel.procrustes.right] = scatter_procrustes_right(channel.direct, channel.forward, channel.backward);
+			channel.power.procrustes.left(a, r) = norm(channel.procrustes.left, 'fro') ^ 2;
+			channel.power.procrustes.right(a, r) = norm(channel.procrustes.right, 'fro') ^ 2;
+		end
 	end
 end
 channel.power.direct = mean(channel.power.direct, ndims(channel.power.direct));
 channel.power.aggregate = mean(channel.power.aggregate, ndims(channel.power.aggregate));
-save('data/power_sx.mat');
+if flag.direct
+    channel.power.procrustes.left = mean(channel.power.procrustes.left, ndims(channel.power.procrustes.left));
[…]

### 2024-02-18 main.tex
:pencil: Add conclusion

@@
 	An efficient \gls{rcg} algorithm is tailored for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size, then invoked for the Pareto frontier of channel singular values.
-	To understand the gain from off-diagonal entries, we also derive analytical singular value bounds in \gls{los} and fully-connected scenarios.
+	To understand the gain from off-diagonal entries, we also derive analytical singular value bounds in rank-deficient and fully-connected scenarios.
 	As a side product, we tackle \gls{mimo} rate maximization problem by alternating between active beamformer (eigenmode transmission) and passive beamformer (\gls{rcg} algorithm) until convergence.
@@
 	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-	We then discuss some analytical singular value bounds in \gls{los} and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
+	We then discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
 	This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
@@
 			\end{mini!}
-			which has global optimal solutions $\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}$ where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-			This naive solution will be compared with the one proposed below.
+			which has global optimal solutions
+			\begin{equation}
+				\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}
+				\label{eq:orthogonal_procrustes_solution}
+			\end{equation}
+			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
+			This suboptimal solution only applies to fully-connected \gls{bd}-\gls{ris}.
 		\end{remark}
 
-		Inspired by \cite{Nie2017}, we successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each iteration in closed form.
+		Inspired by \cite{Nie2017}, we propose a general solution to problem \eqref{op:power_passive} with arbitrary group size.
+		The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form.
 
@@
 			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
 				\label{eq:scattering_power}
@@
 		% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
-		% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect eigenspace.
+		% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect subspace.
 		% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
-		% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward eigenspace alignment for an optimal channel boost.
+		% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward subspace alignment for an optimal channel boost.
 		% It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
@@
 		% % the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
-		% % When the direct link is present, a small $L$ cannot align the direct-indirect eigenspace.
-
-		% % neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect eigenspace.
-		% % We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect eigenspace.
+		% % When the direct link is present, a small $L$ cannot align the direct-indirect subspace.
+
+		% % neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
+		% % We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
 		% % For conventional \gls{ris},
-		% % align the direct-indirect eigenspace.
-		% % When the direct link is present, a small $L$ can neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
+		% % align the direct-indirect subspace.
+		% % When the direct link is present, a small $L$ can neither align the direct-indirect subspace nor the forward-backward subspace.
 		% % For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
-		% % neither the direct-indirect nor the forward-backward eigenspace can be effectively aligned with a small $L$.
+		% % neither the direct-indirect nor the forward-backward subspace can be effectively aligned with a small $L$.
 
 		% % When the direct link is present, a small $L$ can neither preserve the
-		% % neither align the direct-indirect eigenspace nor the forward-backward eigenspace.
-
-		% % When the direct link is absent, a large $L$ can align the forward-backward eigenspace but cannot preserve the forward-backward power balance.
+		% % neither align the direct-indirect subspace nor the forward-backward subspace.
+
+		% % When the direct link is absent, a large $L$ can align the forward-backward subspace but cannot preserve the forward-backward power balance.
 
@@
 			\centering
-			\subfloat[$4 \times N_\mathrm{S} \times 4$ (no direct)\label{fg:power_sx_txrx4_nd}]{
-				\resizebox{!}{3.25cm}{
-					\input{assets/simulation/power_sx_txrx4_nd.tex}
+			\subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)\label{fg:power_sx_txrx16_nd}]{
+				\resizebox{!}{3.25cm}{
+					\input{assets/simulation/power_sx_txrx16_nd.tex}
 				}
@@
 			\caption{
-				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
+				Average maximum channel power versus \gls{ris} configuration.
+				`OP-left' and `OP-right' refer to the suboptimal solutions to problem \eqref{op:power_passive} by lossy transformation \eqref{op:standard_orthogonal_procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
 			}
@@
 		\end{figure}
+
+		We first focus on channel shaping subproblem \eqref{op:power_passive_approx}.
+		Fig. \ref{fg:power_sx} shows the achievable channel power under different \gls{ris} configurations.
+		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} is even larger with direct link.
+		For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power as a 256-element diagonal \gls{ris} in Fig.
+\ref{fg:power_sx_txrx16}, but not in Fig.
+\ref{fg:power_sx_txrx16_nd}.
+		% This again credits to the superior subspace alignment capability of \gls{bd}-\gls{ris}.
+		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the subspace alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
+		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
 
@@
 			\caption{
-				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
+				Average achievable rate versus \gls{mimo} and \gls{ris} configurations.
+				The noise power is $\eta = \qty{-75}{dB}$, corresponding to a direct \gls{snr} of \num{-10} to \qty{30}{dB}.
+				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
+				`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
 			}
@@
 		\end{figure}
+
+		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
+		At a transmit power of \qty{10}{dB}, Fig.
+\subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to 4T4R \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
+		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
+		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
+		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
+		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
+		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better tradeoff between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
+		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
+		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
 	\end{subsection}
-	% [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);
-
-		% \begin{figure}[!t]
-		% 	\centering
-		% 	\resizebox{0.65\columnwidth}{!}{
-		% 		\input{assets/simulation/pc_singular_bound.tex}
-		% 	}
-		% 	\caption{Singular value bounds for rank-1 indirect channel.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (4, 32, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (0, -17.5, -17.5) \unit{dB}$.}
-		% 	\label{fg:pc_singular_bound}
-		% \end{figure}
-
-		% The Pareto frontier and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
-		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
 \end{section}
+
+\begin{section}{Conclusion}
+	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
+	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
+	This translates to a wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
+	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.
+	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
+	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
+	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior subspace alignment and subchannel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
+
+	One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
+	Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
+	Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward subspaces simultaneously.
+	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
+	% into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
+	% even better channel shaping can be achieved by incorporating the \gls{ris} into the \gls{mimo} precoding and combining design.
+\end{section}
+
+		% achieving comparable channel power with significantly fewer elements, showcasing its potential for energy-efficient and cost-effective wireless communication systems, particularly in scenarios with direct link availability.
 

### 2024-02-18 src/power_sx.m

@@ -3,7 +3,7 @@ clc; clear; close; setup;
 [transmit.antenna, reflect.antenna, receive.antenna] = deal(16, 2 .^ (4 : 8), 16);
 % [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e2, true);
+[number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e2, false);
 
 for r = 1 : number.realization
 	% * No RIS

### 2024-02-22 src/complexity_test.m
:test_tube: Add complexity test

@@ -1,0 +1,122 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, [64, 256], 4);
+[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 4);
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+channel.weight = ones(channel.rank, 1);
+[number.antenna, number.realization, flag.direct] = deal(length(reflect.antenna), 1e2, true);
+
+for r = 1 : number.realization
+	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	for a = 1 : number.antenna
+		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
+		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
+
+		tic;
+		[objective.geodesic(a, r), counter.geodesic(a, r)] = scatter_singular_geodesic(channel.direct, channel.forward, channel.backward, channel.weight, reflect.bond);
+		timer.geodesic(a, r) = toc;
+
+		tic;
+		[objective.nongeodesic(a, r), counter.nongeodesic(a, r)] = scatter_singular_nongeodesic(channel.direct, channel.forward, channel.backward, channel.weight, reflect.bond);
+		timer.nongeodesic(a, r) = toc;
+	end
+end
+
+[objective.geodesic, objective.nongeodesic] = deal(mean(objective.geodesic, ndims(objective.geodesic)), mean(objective.nongeodesic, ndims(objective.nongeodesic)));
+[counter.geodesic, counter.nongeodesic] = deal(mean(counter.geodesic, ndims(counter.geodesic)), mean(counter.nongeodesic, ndims(counter.nongeodesic)));
[…]

### 2024-02-23 main.tex
:test_tube: Add complexity test
:sparkles: Add complexity test

@@
 \usepackage{epstopdf}
+\usepackage{multirow}
+\usepackage{booktabs}
 % \usepackage{cleveref}
@@
 	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
-	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$.
-	The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ individual groups.
-	Each group contains $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume there are no mutual coupling and the in-group connections can be lossless and asymmetric\footnote{While symmetric impedance network is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric passive components (e.g., ring hybrids and branch-line hybrids) may also be reconfigured in real time \cite{Ahn2006}.
-Asymmetric \gls{bd}-\gls{ris} has been discussed in \cite{Li2023b,Li2023c,Bartoli2023}.}.
-	The overall scattering matrix is thus block diagonal $\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix corresponding to group $g \in \mathcal{G} \triangleq \{1,\ldots,G\}$.
+	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
+	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
+	To simplify the analysis, we assume a lossless asymmetric network \footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
+	The overall scattering matrix of the \gls{bd}-\gls{ris} is
+	\begin{equation}
+		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
+	\end{equation}
+	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix describing the scatter response of group $g$.
+	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size 1 and $N_\mathrm{S}$, respectively.
+	The potential physical architectures of \gls{bd}-\gls{ris} are shown in \cite[Fig.
+3]{Shen2020a}, \cite[Fig.
+5]{Li2023c}, and \cite[Fig.
+2]{Nerini2023a}, where the antenna radiation patterns and circuit network structures are taken into account.
+	% Note that \gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size equal to 1 and $N_\mathrm{S}$, respectively.
+	% Note that \gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size equal to 1 and $N_\mathrm{S}$, respectively.
+
 	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$ denote the direct (transmitter-receiver), forward (transmitter-\gls{ris}), and backward (\gls{ris}-receiver) channels, respectively.
@@
 	\begin{remark}
-		\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size 1 and $N_\mathrm{S}$, respectively.
+		\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
 	\end{remark}
@@
 			\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
-			\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian}
+			\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
 		\end{gather}
@@
 		\begin{equation}
-			\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)},
+			\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
 			\label{eq:parameter_cg}
@@
 		\begin{equation}
-			\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}.
+			\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}. % $\mathcal{O}(N_\mathrm{S}^2)$
 			\label{eq:direction_cg}
@@
 		\begin{equation}
-			\mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}.
+			\mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}. % $\mathcal{O}(N_\mathrm{S}^3)$
 			\label{eq:geodesic}
@@
 			\begin{align}
-				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), && \text{if } n > k, \label{iq:sv_bound_enlarge}\\
-				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}), && \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
+				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_bound_enlarge}          \\
+				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
 			\end{align}
@@
 
+	\begin{table*}[!t]
+		\caption{Average Performance of \gls{bd}-\gls{ris} Designs}
+		\label{tb:complexity_test}
+		\centering
+		\begin{tabular}{ccccccc}
+			\toprule
+			\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                             \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
+			                                & Objective                             & Iterations                             & Time [s]        & Objective       & Iterations & Time [s] \\ \midrule
+			Geodesic                        & $\num{4.36e-3}$                       & 11.61                                  & $\num{2.04e-2}$ & $\num{1.16e-2}$ & 25.78      & 3.21     \\
+			Non-geodesic                    & $\num{4.17e-3}$                       & 169.50                                 & $\num{1.42e-1}$ & $\num{8.87e-3}$ & 278.08     & 27.81    \\ \bottomrule
+		\end{tabular}
+	\end{table*}
+
 	\begin{subsection}{Channel Singular Values Redistribution}
@@
 			\partial \sigma_n
-			& = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^*\\
-			& = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}\\
-			& = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\\
+			 & = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^* \\
+			 & = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}                                                                                                                  \\
+			 & = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*                                                                                                                                                                                                                                                 \\
 			 & = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
@@
 		\begin{align}
-			\lambda_n(\mathbf{G}) & \le \lambda_{n-k}(\mathbf{Y}), && \text{if } n > k, \label{iq:ev:bound_enlarge} \\
-			\lambda_n(\mathbf{G}) & \ge \lambda_n(\mathbf{Y}), && \text{if } n < N - k + 1 \label{iq:ev_bound_suppress}.
+			\lambda_n(\mathbf{G}) & \le \lambda_{n-k}(\mathbf{Y}), &  & \text{if } n > k, \label{iq:ev:bound_enlarge}          \\
+			\lambda_n(\mathbf{G}) & \ge \lambda_n(\mathbf{Y}),     &  & \text{if } n < N - k + 1 \label{iq:ev_bound_suppress}.
 		\end{align}
@@
 		\begin{align*}
-			\mathrm{sv}(\mathbf{H}) & = \mathrm{sv}(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})\\
-			& = \mathrm{sv}(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})\\
-			& = \mathrm{sv}(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H})\\
+			\mathrm{sv}(\mathbf{H}) & = \mathrm{sv}(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})                                                                     \\
+			                        & = \mathrm{sv}(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})                                                                                                                            \\
+			                        & = \mathrm{sv}(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H}) \\
 			                        & = \mathrm{sv}(\mathbf{BF}),
@@
 			\partial R
-			& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
-			& = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}\\
+			 & = \frac{1}{\eta} \mathrm{tr} \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}                                                                      \\
+			 & = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\} \\
 			 & = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
@@
 			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
-			& = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr)\\
+			 & = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr) \\
 			 & = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)

### 2024-02-23 src/complexity_test.m

@@ -1,6 +1,6 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, [64, 256], 4);
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, [16, 256], 4);
 [channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 4);
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
 channel.weight = ones(channel.rank, 1);

### 2024-02-23 main.tex
:pencil: Remove remarks 1 and 2

@@
 	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume a lossless asymmetric network \footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
+	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
 	The overall scattering matrix of the \gls{bd}-\gls{ris} is
@@
 	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix describing the scatter response of group $g$.
-	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size 1 and $N_\mathrm{S}$, respectively.
+	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
 	The potential physical architectures of \gls{bd}-\gls{ris} are shown in \cite[Fig.
@@
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2023a}, where the antenna radiation patterns and circuit network structures are taken into account.
-	% Note that \gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size equal to 1 and $N_\mathrm{S}$, respectively.
-	% Note that \gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size equal to 1 and $N_\mathrm{S}$, respectively.
-
-	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$ denote the direct (transmitter-receiver), forward (transmitter-\gls{ris}), and backward (\gls{ris}-receiver) channels, respectively.
-	The equivalent channel is
+2]{Nerini2023a}, where the radiation pattern and circuit topology significantly influence the scattering matrix.
+
+	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (transmitter-receiver), backward (\gls{ris}-receiver), and forward (transmitter-\gls{ris}) channels, respectively.
+	The equivalent channel is a function of the scattering matrix
 	\begin{equation}
@@
 	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels of \gls{ris} group $g$, respectively.
-	\begin{remark}
-		\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
-	\end{remark}
-	\begin{remark}
-		Individual forward and backward \gls{csi} are required for \gls{bd}-\gls{ris} designs.
-		This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
-		% Later we will show the potential benefits from the \gls{csi} overhead.
-	\end{remark}
+
+	Since unitary matrices constitute a field with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
+	\begin{equation}
+		\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{R}_g^\mathsf{H},
+	\end{equation}
+	where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary factor matrices.
+	Let $\mathbf{H}_{\mathrm{B},g} = \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \mathbf{V}_{\mathrm{B},g}^\mathsf{H}$ and $\mathbf{H}_{\mathrm{F},g} = \mathbf{U}_{\mathrm{F},g} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}$ be the compact \gls{svd} of the backward and forward channels, respectively.
+	One can thus rewrite the equivalent channel as
+	\begin{equation}
+		\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect},
+	\end{equation}
+	where the \gls{ris} design involves two critical issues: \emph{subspace alignment} and \emph{subchannel rearrangement}.
+	\begin{itemize}
+		\item 
+	\end{itemize}
+	% types of \emph{subspace alignment} problems: direct-indirect (additive) and backward-forward (multiplicative).
+	% which involves two types of \emph{subspace alignment} problems: direct-indirect (additive) and backward-forward (multiplicative).
+
+	% \begin{equation}
+	% 	\mathbf{H} = \underbrace{\mathbf{H}_\mathrm{D} + \underbrace{\sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}_\text{group-wise}}_\text{direct-indirect},
+	% \end{equation}
+	% which involves three subspace alignment problems:
+	% which involves three subspace alignment problems
+	% \begin{equation}
+	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{backward-forward}\\\text{additive alignment}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
+	% \end{equation}
+	% \begin{equation}
+	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g}_{\substack{\text{backward}\\\text{align}}} \underbrace{\mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{forward}\\\text{align}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
+	% \end{equation}
+	% Then the equivalent channel can be rewritten as
+	% Since the field of (block) unitary matrices formulate a field that is closed under multiplication
+	% Since block unitary matrices satisfy the axioms of a field under matrix multiplication
+	% \begin{remark}
+	% 	% To understand the \gls{b} gain from in-group connections
+	% \end{remark}
+
+	% \begin{remark}
+	% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+	% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+	% 	\begin{equation}
+	% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
+	% 		\label{eq:scattering_fc_tight}
+	% 	\end{equation}
+	% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
+	% 	\begin{itemize}
+	% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
+	% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximal in rearrangement inequality.
+	% 	\end{itemize}
+	% \end{remark}
+
+	% \begin{remark}
+	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
+	% \end{remark}
+	% \begin{remark}
+	% 	Individual forward and backward \gls{csi} are required for \gls{bd}-\gls{ris} designs.
+	% 	This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
+	% 	% Later we will show the potential benefits from the \gls{csi} overhead.
+	% \end{remark}
 \end{section}
@@
 
-		\begin{remark}
-			From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-			% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-			\begin{equation}
-				\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
-				\label{eq:scattering_fc_tight}
-			\end{equation}
-			An interpretation is that the off-diagonal entries can enhance the capabilities of
-			\begin{itemize}
-				\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximal in rearrangement inequality.
-			\end{itemize}
-		\end{remark}
+		% \begin{remark}
+		% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+		% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+		% 	\begin{equation}
+		% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
+		% 		\label{eq:scattering_fc_tight}
+		% 	\end{equation}
+		% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
+		% 	\begin{itemize}
+		% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
+		% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximal in rearrangement inequality.
+		% 	\end{itemize}
+		% \end{remark}
 

### 2024-02-23 main.tex
:dizzy: Subspace alignment

@@
 	\end{equation}
-	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix describing the scatter response of group $g$.
+	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
+	That is, $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{H}$ and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
 	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
-	The potential physical architectures of \gls{bd}-\gls{ris} are shown in \cite[Fig.
+	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
 3]{Shen2020a}, \cite[Fig.
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2023a}, where the radiation pattern and circuit topology significantly influence the scattering matrix.
+2]{Nerini2023a}, where the radiation pattern and circuit topology have appreciable impacts on the scattering matrix.
 
@@
 	\end{equation}
-	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels of \gls{ris} group $g$, respectively.
-
+	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
+	% That is, $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns (resp. rows) of $\mathbf{H}_\mathrm{B}$ (resp. $\mathbf{H}_\mathrm{F}$).
+	% , corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$.
+	% $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$
 	Since unitary matrices constitute a field with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
@@
 	Let $\mathbf{H}_{\mathrm{B},g} = \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \mathbf{V}_{\mathrm{B},g}^\mathsf{H}$ and $\mathbf{H}_{\mathrm{F},g} = \mathbf{U}_{\mathrm{F},g} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}$ be the compact \gls{svd} of the backward and forward channels, respectively.
-	One can thus rewrite the equivalent channel as
-	\begin{equation}
-		\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect},
-	\end{equation}
-	where the \gls{ris} design involves two critical issues: \emph{subspace alignment} and \emph{subchannel rearrangement}.
+	The equivalent channel can thus be rewritten as
+	\begin{equation}
+		\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
+		\label{eq:channel_equivalent_svd}
+	\end{equation}
+	Clearly, channel shaping involves two critical issues:
+	% From \eqref{eq:channel_equivalent_svd}, we can see that channel shaping via \gls{ris} involves two critical aspects:
 	\begin{itemize}
-		\item 
+		\item \emph{Subspace alignment:} there exists a tradeoff between the additive (direct-indirect) and multiplicative (backward-forward) alignments of channel singular matrices;
+		% group $g$ can completely align the subspaces of backward and forward subchannel
+		\item \emph{Subchannel rearrangement:} the backward and forward subchannels associated with any group can be rearranged and combined.
+		% , which grants better performance due to the rearrangement inequalities \cite{Zhao2022}.
 	\end{itemize}
@@
 			                                & Objective                              & Iterations                             & Time [s]         & Objective        & Iterations & Time [s]  \\ \midrule
-			Geodesic                        & $\num{4.36e-3}$                       & 11.61                                  & $\num{2.04e-2}$ & $\num{1.16e-2}$ & 25.78      & 3.21     \\
-			Non-geodesic                    & $\num{4.17e-3}$                       & 169.50                                 & $\num{1.42e-1}$ & $\num{8.87e-3}$ & 278.08     & 27.81    \\ \bottomrule
+			Geodesic                        & $\num{4.355e-3}$                       & 11.61                                  & $\num{2.038e-2}$ & $\num{1.164e-2}$ & 25.78      & 3.216     \\
+			Non-geodesic                    & $\num{4.168e-3}$                       & 169.5                                  & $\num{1.420e-1}$ & $\num{8.873e-3}$ & 278.1      & 27.81     \\ \bottomrule
 		\end{tabular}

### 2024-02-25 main.tex
:pencil: Update remark 1

@@
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2023a}, where the radiation pattern and circuit topology have appreciable impacts on the scattering matrix.
+2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
 
@@
 	\end{equation}
-	Clearly, channel shaping involves two critical issues:
-	% From \eqref{eq:channel_equivalent_svd}, we can see that channel shaping via \gls{ris} involves two critical aspects:
+
+	\begin{remark}
+		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} involves two critical challenges:
 		\begin{itemize}
-		\item \emph{Subspace alignment:} there exists a tradeoff between the additive (direct-indirect) and multiplicative (backward-forward) alignments of channel singular matrices;
-		% group $g$ can completely align the subspaces of backward and forward subchannel
-		\item \emph{Subchannel rearrangement:} the backward and forward subchannels associated with any group can be rearranged and combined.
-		% , which grants better performance due to the rearrangement inequalities \cite{Zhao2022}.
+			% \item Subspace alignment: the singular matrices of backward and forward channels
+			\item \textbf{Subspace alignment:} each group needs to balance the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) alignments of the singular matrices.
+			\item \textbf{Subchannel rearrangement:} each group can rearrange and combine the backward and forward subchannels from strongest to weakest, which attains the maximal in rearrangement inequality.
 		\end{itemize}
-	% types of \emph{subspace alignment} problems: direct-indirect (additive) and backward-forward (multiplicative).
-	% which involves two types of \emph{subspace alignment} problems: direct-indirect (additive) and backward-forward (multiplicative).
+	\end{remark}
+
+	% TODO: add illustrations for both
+
+	% In \gls{siso}, the equivalent channel can be further simplified as
+	% \begin{equation}
+	% 	h = h_\mathrm{D} + \sum_g \mathbf{h}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{h}_{\mathrm{F},g},
+	% \end{equation}
+	% subspace alignment boils down to phase matching
+
+	% For the \gls{siso} case in Fig.
+\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
+	% This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
+	% Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
+	% This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
+	% That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
+	% Now consider a diagonal \gls{ris} in \gls{mimo}.
+	% Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
+	% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
+	% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
+	% We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
 

### 2024-02-26 main.tex
:pencil: Update remark 1

@@
 	$\Re\{\cdot\}$ takes the real part of a complex number.
+	$\mathrm{arg}(\cdot)$ gives the argument of a complex number.
 	$\mathrm{tr}(\cdot)$ and $\det(\cdot)$ evaluates the trace and determinant of a square matrix, respectively.
@@
 	% $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$
-	Since unitary matrices constitute a field with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
+	Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
 	\begin{equation}
@@
 	\begin{remark}
-		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} involves two critical challenges:
+		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} creates two critical opportunities:
 		\begin{itemize}
-			% \item Subspace alignment: the singular matrices of backward and forward channels
-			\item \textbf{Subspace alignment:} each group needs to balance the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) alignments of the singular matrices.
-			\item \textbf{Subchannel rearrangement:} each group can rearrange and combine the backward and forward subchannels from strongest to weakest, which attains the maximal in rearrangement inequality.
+			\item \textbf{Subspace alignment:} each group can align the singular matrices of the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) channels.
+In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ is
+			\begin{equation}
+				\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
+			\end{equation}
+			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr]$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr]$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
+			Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R} \times N_\mathrm{T}$ passing through itself.
+			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the direct-indirect and backward-forward alignments.
+			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}.
+but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
+			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}, but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
+			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching. However,
+			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching.
+However, in \gls{mimo} each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
+			% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
+			% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
+			% is sufficient for perfect alignment
+			% and is sufficient for perfect subspace alignment.
+			% In \gls{mimo}, perfect subspace alignment is generally impossible due to the lack of direct control over the indirect channels.aa
+			% backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) alignments of the singular matrices.
+			\item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
+In \gls{siso}, diagonal \gls{ris} provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
+By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
+			The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{R} \times N_\mathrm{T}$.
+			% effect is more pronounced in \gls{mimo} since the number of subchannels associated with each group grows quadratically with the dimensions.
+			% The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
+since the number of subchannels associated with each group grows quadratically with the dimensions.
+			% It suggests that the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
+			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
+In \gls{siso}, the maximum indirect channel amplitude by diagonal \gls{ris} is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are independent permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
+By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
+			% \begin{equation}
+			% 	\item \
+			% \end{equation}
+			% and $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
+By rearrangement inequality,
+			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
+In \gls{siso}, the optimal indirect channel amplitude is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ by diagonal \gls{ris} and $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},\pi_\mathrm{B}(n)} \rvert \lvert h_{\mathrm{F},\pi_\mathrm{F}(n)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi(\cdot)$ is a permutation of $\{1, \ldots, N_\mathrm{S}\}$.
+			% this is unique to \gls{bd}-\gls{ris} --- each group can rearrange and combine the backward and forward subchannels by strength.
+In \gls{siso}, the optimal indirect channel amplitude is relaxed from $\sum_n \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ to $\sum_n \lvert h_{\mathrm{B},\pi(n)} \rvert \lvert h_{\mathrm{F},\pi(n)} \rvert$ where $\pi(\cdot)$ is a permutation of $\{1, \ldots, L\}$.
+			% from strongest to weakest, which attains the maximum in rearrangement inequality.
 		\end{itemize}
@@
 	% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-	% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximal in rearrangement inequality.
+	% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
 	% 	\end{itemize}
@@
 		% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-		% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximal in rearrangement inequality.
+		% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
 		% 	\end{itemize}

### 2024-03-09 main.tex
:pencil: Fix typos

@@
 	This paper investigates how a passive \gls{ris} can reshape the \gls{mimo} point-to-point channel in terms of singular values.
-	We depart from the widely-adapted diagonal phase shift model to a general \gls{bd} architecture, which provides superior shaping capability thanks to in-group connections between elements.
+	We depart from the widely-adopted diagonal phase shift model to a general \gls{bd} architecture, which provides superior shaping capability thanks to in-group connections between elements.
 	An efficient \gls{rcg} algorithm is tailored for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size, then invoked for the Pareto frontier of channel singular values.
@@
 			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr]$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr]$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-			Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R} \times N_\mathrm{T}$ passing through itself.
+			Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R}$-by-$N_\mathrm{T}$ passing through itself.
 			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the direct-indirect and backward-forward alignments.
@@
 By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
-			The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{R} \times N_\mathrm{T}$.
+			The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{T} N_\mathrm{R}$.
 			% effect is more pronounced in \gls{mimo} since the number of subchannels associated with each group grows quadratically with the dimensions.

### 2024-04-05 main.tex
:pencil: Update abstract

@@
 
-% tabularx, ragged2e
-\newcolumntype{L}{>{\RaggedRight}X}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\renewcommand\tabularxcolumn[1]{m{#1}}
-
 % algpseudocode
@@
 }
-
-% optidef
-\DeclareDocumentEnvironment{customopti}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
-	\ifthenelse{\equal{#3}{b}}{%
-		\ifthenelse{\equal{#1}{s}}%
-		% Short version problem
-		{\setFormatShort{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
-		% Long version problem
-		{\setFormatLong{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
-	}{%
-		\ifthenelse{\equal{#1}{s}}%
-		% Short version problem
-		{\setFormatShort{#4}{#5}\BaseMini{#2}{#5}{#6}{#7}{#8}{#4}}%
-		% Long version problem
-		{\setFormatLong{#4}{#5}\BaseMini{#2}{#5}{#6}{#7}{#8}{#4}}%
-	}%
-}%
-{\endBaseMini\toggletrue{bodyCon}}
-
-\DeclareDocumentEnvironment{customopti*}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
-	\ifthenelse{\equal{#1}{s}}%
-	% Short version problem
-	{\setFormatShort{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
-	% Long version problem
-	{\setFormatLong{#4}{#5}\BaseMiniStar{#2}{#5}{#6}{#8}{#4}{#3}}%
-}{\endBaseMiniStar\toggletrue{bodyCon}}
-
-\DeclareDocumentEnvironment{customopti!}{D||{\defaultProblemFormat} O{\defaultConstraintFormat} D<>{} m m m m m}{%
-	\ifthenelse{\equal{#1}{s}}%
-	% Short version problem
-	{\setFormatShort{#4}{#5}\BaseMiniExclam{#2}{#5}{#6}{#7}{#8}{#4}{#3}}%
-	% Long version problem
-	{\setFormatLong{#4}{#5}\BaseMiniExclam{#2}{#5}{#6}{#7}{#8}{#4}{#3}}%
-}{\endBaseMiniExclam\toggletrue{bodyCon}}
 
@@
 \begin{document}
-\title{Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond}
+\title{Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal Model to Beyond}
 \author{
@@
 \begin{abstract}
-	This paper investigates how a passive \gls{ris} can reshape the \gls{mimo} point-to-point channel in terms of singular values.
-	We depart from the widely-adopted diagonal phase shift model to a general \gls{bd} architecture, which provides superior shaping capability thanks to in-group connections between elements.
-	An efficient \gls{rcg} algorithm is tailored for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size, then invoked for the Pareto frontier of channel singular values.
-	To understand the gain from off-diagonal entries, we also derive analytical singular value bounds in rank-deficient and fully-connected scenarios.
-	As a side product, we tackle \gls{mimo} rate maximization problem by alternating between active beamformer (eigenmode transmission) and passive beamformer (\gls{rcg} algorithm) until convergence.
-	A low-complexity suboptimal solution based on channel shaping is also proposed, where the decoupled problem is formulated as channel power maximization and solved in closed form iteratively.
-	% We then show how channel shaping decouples the design and amounts to a low-complexity suboptimal solution.
-	% A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved in closed form iteratively.
-	Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions, stemming from stronger subchannel rearrangement and subspace alignment capabilities.
+	This paper investigates how a passive \gls{ris} can manipulate the \gls{mimo} point-to-point channel in terms of singular values and power gain.
+	We depart from the widely-adopted diagonal phase shift model to a \gls{bd} architecture, which enables \emph{cooperative} wave scattering thanks to in-group connections between elements.
+	An efficient and universal asymmetric \gls{bd}-\gls{ris} design framework is proposed over group-wise \emph{geodesic} \gls{rcg} update in the Stiefel manifold.
+	For the singular value shaping problem, we characterize their Pareto frontiers by weighted sum optimization via geodesic \gls{rcg}, which generalizes most relevant metrics (e.g., degree of freedom and condition number).
+	Many useful analytical singular value bounds are also derived in rank-deficient and fully-connected (a.k.a. unitary) scenarios.
+	% For the singular value problem, we consider a numerical optimization approach that characterizes the Pareto frontiers as well as an analytical bounding approach in special (i.e., rank-deficient and fully-connected) scenarios.
+	For the power gain maximization problem, we provide a closed-form iterative solution by group-wise \gls{svd} that is even faster than geodesic \gls{rcg}.
+	% Those channel shaping designs have a two-fold advantage.
+	Those channel shaping designs have two major implications.
+	First, they demystify the performance gain from off-diagonal entries in terms of \emph{subchannel rearrangement} and \emph{subspace alignment}.
+	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment.
+	Second, they inspire a two-stage suboptimal solution to decouple the joint active and passive beamforming design.
+	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
+	As a side product, we tackle the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} approach and a two-stage shaping-inspired approach.
+	Simulation results indicate that the rate deficit from the latter diminishes as the \gls{bd}-\gls{ris} evolves towards unitary, while its shaping advantages over diagonal \gls{ris} increase \gls{mimo} dimensions and decrease with spatial correlation.
+
+	% , and .
+
+	% (i) , and (ii) the gap between the two approaches vanishes as \gls{bd}-\gls{ris} evolves from diagonal to unitary.
+	% not only demystify the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment, but also decouple the joint \gls{ris}-transceiver optimization.
+	% Those channel shaping designs not only demystify the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment, but also decouple the joint \gls{ris}-transceiver optimization.
+
+	% geodesic \gls{rcg} algorithm is tailored for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size, then invoked for the Pareto frontier of channel singular values.
+	% To understand the gain from off-diagonal entries, we also derive analytical singular value bounds in rank-deficient and fully-connected scenarios.
+	% As a side product, we tackle \gls{mimo} rate maximization problem by alternating between active beamformer (eigenmode transmission) and passive beamformer (\gls{rcg} algorithm) until convergence.
+	% A low-complexity suboptimal solution based on channel shaping is also proposed, where the decoupled problem is formulated as channel power maximization and solved in closed form iteratively.
+	% % We then show how channel shaping decouples the design and amounts to a low-complexity suboptimal solution.
+	% % A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved in closed form iteratively.
+	% Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions, stemming from stronger subchannel rearrangement and subspace alignment capabilities.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Reconfigurable intelligent surface, multi-input multi-output, manifold optimization, singular value control, rate maximization.
+	Reconfigurable intelligent surface, multi-input multi-output, manifold optimization, channel shaping, rate maximization.
 \end{IEEEkeywords}

### 2024-04-06 main.tex
:pencil: Update abstract and background

@@
 	We depart from the widely-adopted diagonal phase shift model to a \gls{bd} architecture, which enables \emph{cooperative} wave scattering thanks to in-group connections between elements.
-	An efficient and universal asymmetric \gls{bd}-\gls{ris} design framework is proposed over group-wise \emph{geodesic} \gls{rcg} update in the Stiefel manifold.
-	For the singular value shaping problem, we characterize their Pareto frontiers by weighted sum optimization via geodesic \gls{rcg}, which generalizes most relevant metrics (e.g., degree of freedom and condition number).
-	Many useful analytical singular value bounds are also derived in rank-deficient and fully-connected (a.k.a. unitary) scenarios.
+	An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise \emph{geodesic} \gls{rcg} in the Stiefel manifold, which performs multiplicative (instead of add-then-project) updates along the exponential map for faster convergence.
+	% For the singular value shaping problem, we numerically characterize their Pareto frontiers by weighted sum optimization via geodesic \gls{rcg}, which generalizes most relevant metrics (e.g., degree of freedom and condition number).
+	% Many analytical singular value bounds are also derived for rank-deficient channels and fully-connected (a.k.a. unitary) \gls{ris}.
+	For the singular value shaping problem, we characterize their Pareto frontiers by geodesic \gls{rcg} and derive analytical bounds for rank-deficient channels and fully-connected (a.k.a.
+unitary) \gls{ris}.
 	% For the singular value problem, we consider a numerical optimization approach that characterizes the Pareto frontiers as well as an analytical bounding approach in special (i.e., rank-deficient and fully-connected) scenarios.
-	For the power gain maximization problem, we provide a closed-form iterative solution by group-wise \gls{svd} that is even faster than geodesic \gls{rcg}.
+	For the power gain maximization problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
 	% Those channel shaping designs have a two-fold advantage.
@@
 	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment.
-	Second, they inspire a two-stage suboptimal solution to decouple the joint active and passive beamforming design.
+	Second, they inspire a two-stage suboptimal solution that decouples joint active and passive beamforming design.
 	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
 	As a side product, we tackle the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} approach and a two-stage shaping-inspired approach.
-	Simulation results indicate that the rate deficit from the latter diminishes as the \gls{bd}-\gls{ris} evolves towards unitary, while its shaping advantages over diagonal \gls{ris} increase \gls{mimo} dimensions and decrease with spatial correlation.
+	Simulation results indicate that the rate deficit from the latter diminishes as the \gls{bd}-\gls{ris} evolves towards unitary, while its shaping advantages over diagonal \gls{ris} increase with \gls{mimo} dimensions and decrease with spatial correlation.
 
@@
 	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
-	This is empowered by the recent advances in \gls{ris}, a real-time programmable metasurface of numerous non-resonant sub-wavelength scattering elements.
-	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than relays.
-	Using \gls{ris} for {passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
-	On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
-	Despite fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
+	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
+	This is empowered by the recent advances in \gls{ris}, a programmable metasurface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
+	A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
+	It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo}.
+	The most popular \gls{ris} application is \emph{joint beamforming} design with transceivers, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
+	Since coherent scattering can be decomposed as equal-gain combining and transmission, \gls{ris} elements usually offer a squared asymptotic performance (e.g., second-order array gain and fourth-order power scaling law \cite{Zhao2022}) than transceiver antennas.
+	% However, a large-dimensional \gls{ris} is generally required to compensate the power loss from double fading.
+	% a second-order array gain and a fourth-order power scaling law has been reported for \gls{ris} elements \cite{Zhao2022} --- both achieves squared improvements than transceiver antennas.
+	% since the coherent scattering can be viewed as equal-gain combining and transmission.
+	On the other hand, \gls{ris} can also be employed for \emph{backscatter modulation} by periodically switching its reflection pattern.
+	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) that can be either integrated into the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or exploited by surrounding low-power devices for energy-efficient uplink communications \cite{Liang2020,Zhao2022a,Yang2024}.
+
+	% which has been investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
+
+	% which could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or simply placed in space as a standalone device for \emph{channel shaping}.
+	% Using \gls{ris} for {passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
+	% On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
+	Despite great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
 
@@
 	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
-	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
+	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2024}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
 	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.

### 2024-04-07 main.tex
:pencil: Update BD-RIS literature review

@@
 	% On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
-	Despite great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
-
-	The answer indeed depends on the hardware architecture and scattering model.
-	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
-	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which groups adjacent elements using passive components.
-	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
-	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
-	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2024}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
-	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
-	Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
+	Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
+	The answer depends heavily on the scattering model and hardware architecture.
+	In diagonal \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
+	This ideally translates to a diagonal scattering matrix with unit-magnitude entries, which only controls the phase of the scattered waves but cannot redistribute their amplitude.
+	% This allows the \gls{ris} to control the phase of the scattered wave, but not its amplitude.
+	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} which physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices respectively.}
+	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate losslessly within the circuit and depart partially from any element in the same group.
+	It can thus control both the amplitude and phase of the scattered wave, generalizing the scattering matrix to block-diagonal with unitary blocks.
+	Such a powerful model can be realized at reduced hardware complexity using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
+	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
+	Many practical design challenges have been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
+	Its superiority has been studied extensively in \gls{siso} and \gls{miso} systems in terms of single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+	When it comes to \gls{mimo}, most existing works are limited to very specific scenarios.
+	For example, the authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design under the assumption of unitary \gls{ris} without direct link.
+	% \gls{mimo} channel power maximization problem has been considered in \cite{Nerini2023,Nerini2023b}
+	Received power maximization problem is extended to \gls{mimo} for continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} scattering matrices, but it only considered single-stream transmission with given precoder and combiner (which is equivalent to \gls{siso}).
+	Transmitter-side \gls{bd}-\gls{ris} design over statistical \gls{csi} has been introduced to massive \gls{mimo} networks for improved spectral efficiency \cite{Mishra2024}, but was again constrained to unitary \gls{ris} without direct link.
+	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
+	Although the results are insightful, it remains unclear whether and why the advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} depends on \gls{mimo} dimensions.
+	% , and there lacks a deep understanding of
+
+	% Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
+
+	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
+	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
+	Channel shaping is different from passive beamforming because \gls{ris} is exploited as a stand-alone device to modify the inherent properties of the wireless channel.
+	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of wave manipulation.
+	Relevant design criteria can be roughly classified into two categories:
+	\begin{itemize}
+		\item \emph{Singular value centric:} Focus on the singular values of the equivalent channel matrix, which are closely related to the channel capacity and the diversity-multiplexing trade-off.
+Relevant designs are more complicated since they involve the entire channel matrix.
+		\item \emph{Power centric:} Focus on the second-order characteristics of the channel matrix, which are useful in \gls{miso} but less informative in \gls{mimo}.
+Relevant designs are more practical and straightforward.
+	\end{itemize}
+	The former has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023} in \gls{pc}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023} in \gls{ic}.
+	The latter has been studied in terms of channel power \cite{Wu2019,Nerini2023,Santamaria2023} in \gls{pc} and leakage interference \cite{Santamaria2023a} in \gls{ic}.
+	Although the results are insightful, the big picture is far from complete since there exists neither a systematic channel shaping study nor a universal \gls{ris} optimization framework.
+	To the best of our knowledge, the most general channel shaping scenario (\gls{bd}-\gls{ris}-aided \gls{mimo}) has not been studied, and the great potential of \gls{bd}-\gls{ris} has not been fully exploited or understood.
+	This chapter aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
+	The contributions are summarized below.
 
@@
 	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
+	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2024,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
 	The overall scattering matrix of the \gls{bd}-\gls{ris} is
@@
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
+2]{Nerini2024}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
 
@@
 		\end{equation}
-		where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block diagonal matrices of $L \times L$ unitary blocks.
+		where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block-diagonal matrices of $L \times L$ unitary blocks.
 		Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.

### 2024-04-08 main.tex
:pencil: Update channel shaping literature review

@@
 	}
-	% \thanks{
-	% 	The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
-	% }
+	\thanks{
+		Yang Zhao, Hongyu Li, and Bruno Clerckx are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K.
+(e-mail: \{yang.zhao18, c.li21, b.clerckx\}@imperial.ac.uk).
+
+		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California at San Diego, La Jolla CA 92093, USA (e-mail: massimo@ece.ucsd.edu).
+	}
 }
@@
 	This paper investigates how a passive \gls{ris} can manipulate the \gls{mimo} point-to-point channel in terms of singular values and power gain.
-	We depart from the widely-adopted diagonal phase shift model to a \gls{bd} architecture, which enables \emph{cooperative} wave scattering thanks to in-group connections between elements.
-	An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise \emph{geodesic} \gls{rcg} in the Stiefel manifold, which performs multiplicative (instead of add-then-project) updates along the exponential map for faster convergence.
+	We depart from the widely-adopted diagonal phase shift model to a \gls{bd} architecture, which enables {cooperative} wave scattering thanks to in-group connections between elements.
+	An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} in the Stiefel manifold, which performs multiplicative (instead of add-then-retract) updates along the exponential map for faster convergence.
 	% For the singular value shaping problem, we numerically characterize their Pareto frontiers by weighted sum optimization via geodesic \gls{rcg}, which generalizes most relevant metrics (e.g., degree of freedom and condition number).
 	% Many analytical singular value bounds are also derived for rank-deficient channels and fully-connected (a.k.a. unitary) \gls{ris}.
-	For the singular value shaping problem, we characterize their Pareto frontiers by geodesic \gls{rcg} and derive analytical bounds for rank-deficient channels and fully-connected (a.k.a.
-unitary) \gls{ris}.
+	For the singular value problem, we characterize their Pareto frontiers by geodesic \gls{rcg} and derive analytical bounds for rank-deficient channels and fully-connected (a.k.a. unitary) \gls{ris}.
 	% For the singular value problem, we consider a numerical optimization approach that characterizes the Pareto frontiers as well as an analytical bounding approach in special (i.e., rank-deficient and fully-connected) scenarios.
-	For the power gain maximization problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
+	For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
 	% Those channel shaping designs have a two-fold advantage.
 	Those channel shaping designs have two major implications.
-	First, they demystify the performance gain from off-diagonal entries in terms of \emph{subchannel rearrangement} and \emph{subspace alignment}.
+	First, they demystify the performance gain from off-diagonal entries in terms of {subchannel rearrangement} and {subspace alignment}.
 	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment.
@@
 	As a side product, we tackle the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} approach and a two-stage shaping-inspired approach.
-	Simulation results indicate that the rate deficit from the latter diminishes as the \gls{bd}-\gls{ris} evolves towards unitary, while its shaping advantages over diagonal \gls{ris} increase with \gls{mimo} dimensions and decrease with spatial correlation.
+	Simulation results indicate that the rate deficit from the latter diminishes as the \gls{ris} evolves from diagonal towards unitary, while the relative gain of \gls{bd}-\gls{ris} increase with \gls{mimo} dimensions and decrease with spatial correlation.
 
@@
 \begin{section}{Introduction}
-	% The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
-	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
 	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
@@
 	% However, a large-dimensional \gls{ris} is generally required to compensate the power loss from double fading.
-	% a second-order array gain and a fourth-order power scaling law has been reported for \gls{ris} elements \cite{Zhao2022} --- both achieves squared improvements than transceiver antennas.
-	% since the coherent scattering can be viewed as equal-gain combining and transmission.
 	On the other hand, \gls{ris} can also be employed for \emph{backscatter modulation} by periodically switching its reflection pattern.
@@
 
-	% which has been investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
-
-	% which could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or simply placed in space as a standalone device for \emph{channel shaping}.
-	% Using \gls{ris} for {passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
-	% On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
-	Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
+	Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape a \gls{mimo} channel?}
 	The answer depends heavily on the scattering model and hardware architecture.
@@
 	This ideally translates to a diagonal scattering matrix with unit-magnitude entries, which only controls the phase of the scattered waves but cannot redistribute their amplitude.
-	% This allows the \gls{ris} to control the phase of the scattered wave, but not its amplitude.
 	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} which physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices respectively.}
 	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate losslessly within the circuit and depart partially from any element in the same group.
-	It can thus control both the amplitude and phase of the scattered wave, generalizing the scattering matrix to block-diagonal with unitary blocks.
+	It can thus control both the amplitude and phase of the scattered wave without power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
 	Such a powerful model can be realized at reduced hardware complexity using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
@@
 	Its superiority has been studied extensively in \gls{siso} and \gls{miso} systems in terms of single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
-	When it comes to \gls{mimo}, most existing works are limited to very specific scenarios.
+	When it comes to \gls{mimo}, most existing works have been limited to very specific scenarios.
 	For example, the authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design under the assumption of unitary \gls{ris} without direct link.
-	% \gls{mimo} channel power maximization problem has been considered in \cite{Nerini2023,Nerini2023b}
-	Received power maximization problem is extended to \gls{mimo} for continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} scattering matrices, but it only considered single-stream transmission with given precoder and combiner (which is equivalent to \gls{siso}).
+	Received power maximization problem is extended to \gls{mimo} for continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} scattering matrices, but they only considered single-stream transmission with given precoder and combiner (which is equivalent to \gls{siso}).
 	Transmitter-side \gls{bd}-\gls{ris} design over statistical \gls{csi} has been introduced to massive \gls{mimo} networks for improved spectral efficiency \cite{Mishra2024}, but was again constrained to unitary \gls{ris} without direct link.
 	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
-	Although the results are insightful, it remains unclear whether and why the advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} depends on \gls{mimo} dimensions.
-	% , and there lacks a deep understanding of
-
+	Although the results are insightful, it remains unclear how the off-diagonal entries contribute to channel shaping and whether the relative gain of \gls{bd}-\gls{ris} scales with \gls{mimo} dimensions.
 	% Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
 
-	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
-	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
-	Channel shaping is different from passive beamforming because \gls{ris} is exploited as a stand-alone device to modify the inherent properties of the wireless channel.
-	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of wave manipulation.
-	Relevant design criteria can be roughly classified into two categories:
+	Channel shaping is different from passive beamforming since the \gls{ris} is exploited as a stand-alone device to modify the inherent properties of the channel itself, instead of optimizing for a specific performance metric.
+	This not only allows one to decouple the joint \gls{ris}-transceiver design, but also unveils the fundamental limits of wave manipulation and provides an all-in-one benchmark for various wireless applications.
+	Relevant designs can be classified into two categories:
 	\begin{itemize}
-		\item \emph{Singular value centric:} Focus on the singular values of the equivalent channel matrix, which are closely related to the channel capacity and the diversity-multiplexing trade-off.
-Relevant designs are more complicated since they involve the entire channel matrix.
-		\item \emph{Power centric:} Focus on the second-order characteristics of the channel matrix, which are useful in \gls{miso} but less informative in \gls{mimo}.
-Relevant designs are more practical and straightforward.
+		\item \emph{Singular value centric:} Focus on the singular values of the equivalent channel matrix, which are sensitive to minor perturbations but precisely related to the capacity and diversity-multiplexing trade-off.
+It has been mainly studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
+		\item \emph{Power centric:} Focus on the second-order characteristics of the equivalent channel matrix, which are useful in \gls{siso} and \gls{miso} but less informative in \gls{mimo}.
+It has been mainly studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
 	\end{itemize}
-	The former has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023} in \gls{pc}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023} in \gls{ic}.
-	The latter has been studied in terms of channel power \cite{Wu2019,Nerini2023,Santamaria2023} in \gls{pc} and leakage interference \cite{Santamaria2023a} in \gls{ic}.
-	Although the results are insightful, the big picture is far from complete since there exists neither a systematic channel shaping study nor a universal \gls{ris} optimization framework.
-	To the best of our knowledge, the most general channel shaping scenario (\gls{bd}-\gls{ris}-aided \gls{mimo}) has not been studied, and the great potential of \gls{bd}-\gls{ris} has not been fully exploited or understood.
+
+	While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, the big picture remains incomplete because they neither suggest the achievable singular value region nor address the most general \gls{bd}-\gls{ris}-aided \gls{mimo} scenario.
+	On the other hand, the great potential of \gls{bd}-\gls{ris} has not been fully understood and an efficient design framework is still missing.
 	This chapter aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
@@
 
-	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
-	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
-	Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself.
-	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of channel manipulation.
-	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
-	In contrast, \gls{bd}-\gls{ris} can provide a higher channel power but existing results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
-\cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
-	While these studies offer promising glimpses into the channel shaping potential, a comprehensive understanding of the capabilities and limitations is desired, and a universal design framework is missing.
-	This paper aims to answer the channel shaping question through theoretical analysis and numerical optimization.
-	The contributions are summarized below.
-
-	First, we quantify the capability of a \gls{bd}-\gls{ris} to reshape the \gls{mimo} point-to-point channel in terms of singular values.
+	First, we exploit the Riemannian geometry of the Stiefel manifold to design a novel geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization.
+	This method modified from \cite{Abrudan2008,Abrudan2009} not only features lower complexity and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also fits arbitrary group size and any smooth optimization problem.
+	Specifically, block-wise multiplicative rotational updates are performed along the geodesics of the Stiefel manifold, which are compactly evaluated as the exponential map \cite{Edelman1998}.
+	By exploiting the inherent structure of unitary matrices, this method avoids retractions from the Euclidean space and improves the computational efficiency and stability.
+	This is the first work to tailor an efficient and universal optimization framework for \gls{bd}-\gls{ris}.
+
+	Second, we demystify the gain from off-diagonal entries of \gls{bd}-\gls{ris} in terms of subchannel rearrangement and subspace alignment.
+
+	% Specifically,  we show that BD-RIS enables cooperative groups to rearrange subchannels according to their strengths, maximizing the effective channel gain.
+Additionally, intra-group cooperation allows for finer control over subspace alignment compared to diagonal RIS, especially in higher-dimensional MIMO systems.
+This analysis highlights a key advantage of BD-RIS and its potential for significant performance improvement.
+
+	Third, we quantify the capability of a \gls{bd}-\gls{ris} to redistribute the singular values of a point-to-point \gls{mimo} channel.
 	The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
-	% This generalizes most singular value metrics and provides a powerful design framework.
-	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-	We then discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
-	This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
-
-	Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
-	It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
-	This is the first paper to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
-
-	Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
-	The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
+	This problem is solved by the proposed geodesic \gls{rcg} algorithm.
+	The resulting achievable singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected (a.k.a. unitary) \gls{ris}.
+	This is the first work to comprehensively answer the channel shaping question and fully unveil the potential of \gls{bd}-\gls{ris} in multi-antenna systems.
+
+	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization with a local-optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
+	The former updates active and passive beamforming by eigenmode transmission and \gls{rcg} algorithm, respectively.
 	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
-	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
-	It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.
+	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal to unitary.
+	It suggests channel shaping helps to decouple the \gls{ris}-transceiver design and offers a promising low-complexity solution.
+	This is the first work to discuss the implications of channel shaping on joint active-passive beamforming optimization.
+
+	Fifth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
+	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
+	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
+	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
+
+	% First, we quantify the capability of a \gls{bd}-\gls{ris} to reshape the \gls{mimo} point-to-point channel in terms of singular values.
+	% The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
+	% % This generalizes most singular value metrics and provides a powerful design framework.
+	% The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	% We then discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
+	% This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
+
+	% Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
+	% Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
+	% It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
+	% This is the first paper to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
+
+	% Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
+	% The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
+	% The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
+	% Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
+	% It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.
 
@@
 	% Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.
-
-	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
-	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
-	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
 
@@
 
-\begin{section}{\gls{bd}-\gls{ris} Model}
+\begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Model}
 	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.

### 2024-04-09 main.tex
:pencil: Update contributions

@@
 	We depart from the widely-adopted diagonal phase shift model to a \gls{bd} architecture, which enables {cooperative} wave scattering thanks to in-group connections between elements.
-	An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} in the Stiefel manifold, which performs multiplicative (instead of add-then-retract) updates along the exponential map for faster convergence.
+	An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} in the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
 	% For the singular value shaping problem, we numerically characterize their Pareto frontiers by weighted sum optimization via geodesic \gls{rcg}, which generalizes most relevant metrics (e.g., degree of freedom and condition number).
 	% Many analytical singular value bounds are also derived for rank-deficient channels and fully-connected (a.k.a. unitary) \gls{ris}.
-	For the singular value problem, we characterize their Pareto frontiers by geodesic \gls{rcg} and derive analytical bounds for rank-deficient channels and fully-connected (a.k.a. unitary) \gls{ris}.
+	For the singular value problem, we numerically characterize their Pareto frontiers by geodesic \gls{rcg} and derive analytical bounds for rank-deficient channels and fully-connected (a.k.a.
+unitary) \gls{ris}.
 	% For the singular value problem, we consider a numerical optimization approach that characterizes the Pareto frontiers as well as an analytical bounding approach in special (i.e., rank-deficient and fully-connected) scenarios.
@@
 	A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
-	It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo}.
+	It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
 	The most popular \gls{ris} application is \emph{joint beamforming} design with transceivers, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
@@
 
-	Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape a \gls{mimo} channel?}
+	Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
 	The answer depends heavily on the scattering model and hardware architecture.
-	In diagonal \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
+	Most existing works assumed that each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
 	This ideally translates to a diagonal scattering matrix with unit-magnitude entries, which only controls the phase of the scattered waves but cannot redistribute their amplitude.
@@
 	It can thus control both the amplitude and phase of the scattered wave without power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
-	Such a powerful model can be realized at reduced hardware complexity using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
+	Such a powerful model can be realized at reduced hardware complexity using tree- and forest-connected architectures using graph theory \cite{Nerini2024}.
 	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
@@
 	Its superiority has been studied extensively in \gls{siso} and \gls{miso} systems in terms of single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
-	When it comes to \gls{mimo}, most existing works have been limited to very specific scenarios.
+	When it comes to \gls{mimo}, most existing works are limited to very specific scenarios.
 	For example, the authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design under the assumption of unitary \gls{ris} without direct link.
@@
 	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
-	Although the results are insightful, it remains unclear how the off-diagonal entries contribute to channel shaping and whether the relative gain of \gls{bd}-\gls{ris} scales with \gls{mimo} dimensions.
+	Although the results are insightful, it remains unclear how the off-diagonal entries contribute to channel shaping and whether the relative gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with \gls{mimo} dimensions.
 	% Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
@@
 	Channel shaping is different from passive beamforming since the \gls{ris} is exploited as a stand-alone device to modify the inherent properties of the channel itself, instead of optimizing for a specific performance metric.
-	This not only allows one to decouple the joint \gls{ris}-transceiver design, but also unveils the fundamental limits of wave manipulation and provides an all-in-one benchmark for various wireless applications.
+	This not only allows one to decouple the joint \gls{ris}-transceiver design, but also unveils the fundamental limits of wave manipulation and provides an all-in-one tool for various wireless applications.
 	Relevant designs can be classified into two categories:
@@
 
-	While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, the big picture remains incomplete because they neither suggest the achievable singular value region nor address the most general \gls{bd}-\gls{ris}-aided \gls{mimo} scenario.
-	On the other hand, the great potential of \gls{bd}-\gls{ris} has not been fully understood and an efficient design framework is still missing.
-	This chapter aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
+	While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, they neither suggest the achievable singular value region nor address the most general \gls{bd}-\gls{ris}-aided \gls{mimo} scenario with direct link and arbitrary group size.
+	On the other hand, the great potential of \gls{bd}-\gls{ris} (especially in \gls{mimo}) has not been fully understood and an efficient design framework is still missing.
+	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
 	The contributions are summarized below.
 
-	First, we exploit the Riemannian geometry of the Stiefel manifold to design a novel geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization.
-	This method modified from \cite{Abrudan2008,Abrudan2009} not only features lower complexity and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also fits arbitrary group size and any smooth optimization problem.
-	Specifically, block-wise multiplicative rotational updates are performed along the geodesics of the Stiefel manifold, which are compactly evaluated as the exponential map \cite{Edelman1998}.
+	First, we demystify the gain from off-diagonal entries of \gls{bd}-\gls{ris} in terms of subchannel rearrangement and subspace alignment.
+	Subchannel rearrangement is a unique feature of cooperative scattering that allows each group to rearrange and recombine the associated forward and backward subchannels.
+	This translates to a higher design flexibility and better shaping capability by exploiting the spatial diversity.
+	On the other hand, phase matching in \gls{siso} generalizes to subspace alignment in \gls{mimo} and introduces a trade-off between the multiplicative backward-forward channel combination and the additive direct-indirect channel combination.
+	As the \gls{mimo} dimensions expand, we show the benefits of \gls{bd}-\gls{ris} in subchannel rearrangement and the limitations of diagonal \gls{ris} in subspace alignment become increasingly apparent.
+	This is the first paper to unveil and interpret the potential of \gls{bd}-\gls{ris} in multi-antenna systems.
+
+	% where the \gls{bd}-\gls{ris} demonstrates a superior control on the multiplicative backward-forward channels and additive direct-indirect channels.
+	% Both potentials
+
+	Second, we exploit the Riemannian geometry of the Stiefel manifold and propose an efficient \gls{bd}-\gls{ris} design framework based on geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
+	This method modified from \cite{Abrudan2008,Abrudan2009} not only features lower complexity and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also works for arbitrary group size and any smooth optimization problem.
+	Specifically, block-wise multiplicative rotational updates are performed along the geodesics of the Stiefel manifold and compactly evaluated as the exponential map \cite{Edelman1998}.
 	By exploiting the inherent structure of unitary matrices, this method avoids retractions from the Euclidean space and improves the computational efficiency and stability.
@@
 
-	Second, we demystify the gain from off-diagonal entries of \gls{bd}-\gls{ris} in terms of subchannel rearrangement and subspace alignment.
-
-	% Specifically,  we show that BD-RIS enables cooperative groups to rearrange subchannels according to their strengths, maximizing the effective channel gain.
-Additionally, intra-group cooperation allows for finer control over subspace alignment compared to diagonal RIS, especially in higher-dimensional MIMO systems.
-This analysis highlights a key advantage of BD-RIS and its potential for significant performance improvement.
-
 	Third, we quantify the capability of a \gls{bd}-\gls{ris} to redistribute the singular values of a point-to-point \gls{mimo} channel.
-	The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
+	The {Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
 	This problem is solved by the proposed geodesic \gls{rcg} algorithm.
@@
 	We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected (a.k.a. unitary) \gls{ris}.
-	This is the first work to comprehensively answer the channel shaping question and fully unveil the potential of \gls{bd}-\gls{ris} in multi-antenna systems.
-
-	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization with a local-optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
-	The former updates active and passive beamforming by eigenmode transmission and \gls{rcg} algorithm, respectively.
-	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
-	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal to unitary.
-	It suggests channel shaping helps to decouple the \gls{ris}-transceiver design and offers a promising low-complexity solution.
-	This is the first work to discuss the implications of channel shaping on joint active-passive beamforming optimization.
-
-	Fifth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
-	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
-	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
+	This is the first work to comprehensively answer the channel shaping capability question from a Pareto perspective.
+
+	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization problem with two beamforming solutions: a local-optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
+	The former iteratively updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.
+	The latter suboptimally decouples the joint design into a channel power gain maximization subproblem and a conventional \gls{mimo} transmission subproblem, then propose a two-stage solution in closed form.
+	Interestingly, the rate deficit from the latter diminishes as the \gls{ris} evolves from diagonal to unitary.
+	It suggests that channel shaping offers a promising path towards simplified and practical \gls{bd}-\gls{ris} (and transceiver) designs.
+	% via \gls{bd}-\gls{ris} offers a promising path towards simplified and practical design.
+	% offers a promising path towards simplified and practical desi
+	% It suggests channel shaping helps to decouple the joint \gls{ris}-transceiver design and offers a promising low-complexity solution.
+	% This is the first work to discuss the implications of channel shaping on joint active-passive beamforming optimization.
+
+	% Fifth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
+	% In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
+	% The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
+	% It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
 
@@
 	$\mathbb{H}^{n \times n}$ and $\mathbb{U}^{n \times n}$ denotes the set of $n \times n$ Hermitian and unitary matrices, respectively.
-	% $\mathbb{U}^{n \times n}$ denotes the set of $n \times n$ unitary matrices.
 	$\mathbf{0}$ and $\mathbf{I}$ are the all-zero and identity matrices with appropriate size, respectively.
@@
 	% $\boldsymbol{\sigma}(\cdot)$ and $\boldsymbol{\lambda}(\cdot)$ are the corresponding vectors.
-	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^\dagger$ $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), Moore-Penrose inverse, $r$-th iterated point, and final solution, respectively.
+	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^\dagger$ $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), Moore-Penrose inverse, $r$-th iterated point, and stationary point, respectively.
 	$(\cdot)_{[x:y]}$ is a shortcut for $(\cdot)_x,(\cdot)_{x+1},\ldots,(\cdot)_y$.
-	$\lvert \cdot \rvert$ denotes the absolute value.
-	% $\lVert \cdot \rVert _p$ means the $p$-norm and $\lVert \cdot \rVert$ suggests $p = 2$.
-	$\lVert \cdot \rVert$ means the Euclidean norm.
-	$\lVert \cdot \rVert _\mathrm{F}$ represents the Frobenius norm.
+	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
 	$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
@@
 	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
-	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2024,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
-	The overall scattering matrix of the \gls{bd}-\gls{ris} is
+	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
+	To simplify the analysis and explore the performance limits, we assume a lossless asymmetric network without mutual coupling between scattering elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
+	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-unitary
 	\begin{equation}
@@
 	\end{equation}
-	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
-	That is, $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{H}$ and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
-	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
+	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary block (i.e., $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$) that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
+	Note that diagonal and unitary \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
 	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
@@
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2024}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
+2]{Nerini2024}, where the radiation pattern and circuit topology should be modelled in the scattering matrix.
 
@@
 	\begin{equation}
-		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
+		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \underbrace{\mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}}_{\triangleq \mathbf{H}_g},
 		\label{eq:channel_equivalent}
 	\end{equation}
-	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
-	% That is, $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns (resp. rows) of $\mathbf{H}_\mathrm{B}$ (resp. $\mathbf{H}_\mathrm{F}$).
-	% , corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$.
-	% $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$
+	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g{-}1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
+	Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via \gls{bd}-\gls{ris} group $g$.
 	Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
@@
 	\begin{remark}
-		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} creates two critical opportunities:
+		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
 		\begin{itemize}
-			\item \textbf{Subspace alignment:} each group can align the singular matrices of the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) channels.
-In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ is
+			\item \textbf{Subchannel rearrangement:} This unique feature of \gls{bd}-\gls{ris} allows each group to rearrange and recombine the backward and forward subchannels by strength.
+In \gls{siso}, diagonal \gls{ris} with perfect phase matching provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
+			Note the first summation is over groups and the second summation is over permuted subchannels.
+			By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels within each group.
+			Since the number of subchannels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions,
+			\item \textbf{Subspace alignment:} Each group can align the singular vectors of the associated backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
+In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ that maximizes the channel gain is
 			\begin{equation}
@@
 			\end{equation}
-			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr]$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr]$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-			Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R}$-by-$N_\mathrm{T}$ passing through itself.
-			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the direct-indirect and backward-forward alignments.
-			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}.
-but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
-			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}, but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
-			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching. However,
-			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching.
-However, in \gls{mimo} each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-			% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
-			% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
-			% is sufficient for perfect alignment
-			% and is sufficient for perfect subspace alignment.
-			% In \gls{mimo}, perfect subspace alignment is generally impossible due to the lack of direct control over the indirect channels.aa
-			% backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) alignments of the singular matrices.
-			\item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, diagonal \gls{ris} provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
-			The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{T} N_\mathrm{R}$.
-			% effect is more pronounced in \gls{mimo} since the number of subchannels associated with each group grows quadratically with the dimensions.
-			% The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
-since the number of subchannels associated with each group grows quadratically with the dimensions.
-			% It suggests that the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
-			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the maximum indirect channel amplitude by diagonal \gls{ris} is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are independent permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
-			% \begin{equation}
-			% 	\item \
-			% \end{equation}
-			% and $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality,
-			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the optimal indirect channel amplitude is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ by diagonal \gls{ris} and $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},\pi_\mathrm{B}(n)} \rvert \lvert h_{\mathrm{F},\pi_\mathrm{F}(n)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi(\cdot)$ is a permutation of $\{1, \ldots, N_\mathrm{S}\}$.
-			% this is unique to \gls{bd}-\gls{ris} --- each group can rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the optimal indirect channel amplitude is relaxed from $\sum_n \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ to $\sum_n \lvert h_{\mathrm{B},\pi(n)} \rvert \lvert h_{\mathrm{F},\pi(n)} \rvert$ where $\pi(\cdot)$ is a permutation of $\{1, \ldots, L\}$.
-			% from strongest to weakest, which attains the maximum in rearrangement inequality.
+			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
+			Diagonal \gls{ris} ($L=1$, empty null spaces) thus suffices for perfect phase matching in \gls{siso}.
+			When it comes to \gls{mimo}, each individual scattering element can only apply a common phase shift to the ``pinhole'' indirect channel $\mathbf{H}_g \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ passing through itself.
+			That is, the disadvantage of diagonal \gls{ris} in subspace alignment scales with \gls{mimo} dimensions.
+			As will be shown later, even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the alignment of direct-indirect and backward-forward subspaces.
 		\end{itemize}

### 2024-04-11 main.tex
:dizzy: Geodesic RCG

@@
 
+% Double superscript
+\newcommand\herm[2][-4]{{#2}^{\mkern#1mu\mathsf{H}}}
+
 % algpseudocode
@@
 		Yang Zhao, Hongyu Li, and Bruno Clerckx are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K.
-(e-mail: \{yang.zhao18, c.li21, b.clerckx\}@imperial.ac.uk).
-
-		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California at San Diego, La Jolla CA 92093, USA (e-mail: massimo@ece.ucsd.edu).
+(e-mail: \{\href{mailto:yang.zhao18@imperial.ac.uk}{yang.zhao18}, \href{mailto:c.li21@imperial.ac.uk}{c.li21}, \href{mailto:b.clerckx@imperial.ac.uk}{b.clerckx}\}@imperial.ac.uk).
+
+		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California at San Diego, La Jolla CA 92093, USA (e-mail: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).
 	}
@@
 	We depart from the widely-adopted diagonal phase shift model to a \gls{bd} architecture, which enables {cooperative} wave scattering thanks to in-group connections between elements.
-	An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} in the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
+	An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} on the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
 	% For the singular value shaping problem, we numerically characterize their Pareto frontiers by weighted sum optimization via geodesic \gls{rcg}, which generalizes most relevant metrics (e.g., degree of freedom and condition number).
-	% Many analytical singular value bounds are also derived for rank-deficient channels and fully-connected (a.k.a. unitary) \gls{ris}.
+	% Many analytical singular value bounds are also derived for rank-deficient channels and unitary (a.k.a. unitary) \gls{ris}.
 	For the singular value problem, we numerically characterize their Pareto frontiers by geodesic \gls{rcg} and derive analytical bounds for rank-deficient channels and fully-connected (a.k.a.
@@
 
-	While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, they neither suggest the achievable singular value region nor address the most general \gls{bd}-\gls{ris}-aided \gls{mimo} scenario with direct link and arbitrary group size.
-	On the other hand, the great potential of \gls{bd}-\gls{ris} (especially in \gls{mimo}) has not been fully understood and an efficient design framework is still missing.
+	While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, they neither suggest the achievable singular value region nor address the most general scenario with direct link and arbitrary group size.
+	On the other hand, \gls{bd}-\gls{ris} has been mainly investigated for beamforming and its channel shaping potential in \gls{mimo} has not been fully understood.
+	% the great potential of \gls{bd}-\gls{ris} (especially in \gls{mimo}) has not been fully understood and an efficient design framework is still missing.
 	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
@@
 	Second, we exploit the Riemannian geometry of the Stiefel manifold and propose an efficient \gls{bd}-\gls{ris} design framework based on geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
-	This method modified from \cite{Abrudan2008,Abrudan2009} not only features lower complexity and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also works for arbitrary group size and any smooth optimization problem.
-	Specifically, block-wise multiplicative rotational updates are performed along the geodesics of the Stiefel manifold and compactly evaluated as the exponential map \cite{Edelman1998}.
+	This method modified from \cite{Abrudan2008,Abrudan2009} not only provides better objective value and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also works for arbitrary group size and any smooth optimization problem.
+	Specifically, group-wise multiplicative rotational updates are performed along the geodesics of the Stiefel manifold and compactly evaluated as the exponential map \cite{Edelman1998}.
 	By exploiting the inherent structure of unitary matrices, this method avoids retractions from the Euclidean space and improves the computational efficiency and stability.
@@
 	% Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-	% Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
+	% Specifically, group-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
 	% It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
@@
 		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
+		\label{eq:bd_ris}
 	\end{equation}
@@
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2024}, where the radiation pattern and circuit topology should be modelled in the scattering matrix.
+2]{Nerini2024}, where the radiation pattern and circuit topology need to be modelled in the scattering matrix.
 
@@
 
-	\begin{remark}
+	% \begin{remark}
 	By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
 	\begin{itemize}
-			\item \textbf{Subchannel rearrangement:} This unique feature of \gls{bd}-\gls{ris} allows each group to rearrange and recombine the backward and forward subchannels by strength.
+		\item \emph{Subchannel rearrangement:} This unique feature of \gls{bd}-\gls{ris} allows each group to rearrange and recombine the backward and forward subchannels by their strength.
 In \gls{siso}, diagonal \gls{ris} with perfect phase matching provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
@@
 		Since the number of subchannels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions,
-			\item \textbf{Subspace alignment:} Each group can align the singular vectors of the associated backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
+		\item \emph{Subspace alignment:} Each group can align the singular vectors of the associated backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
 In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ that maximizes the channel gain is
@@
 		That is, the disadvantage of diagonal \gls{ris} in subspace alignment scales with \gls{mimo} dimensions.
-			As will be shown later, even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the alignment of direct-indirect and backward-forward subspaces.
+		As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward subspaces.
 	\end{itemize}
-	\end{remark}
+	% \end{remark}
 
@@
 
-\begin{section}{Channel Singular Values Redistribution}
-	\begin{subsection}{A Toy Example}\label{sc:toy_example}
-		We first illustrate the channel shaping capabilities of different \gls{ris} by a toy example.
-		% We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
-		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{bd}-\gls{ris} has 4 independent angular parameters
-		\begin{equation}
-			\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
-				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
-				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
-			\end{bmatrix}.
-		\end{equation}
-		In particular, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		We also enforce symmetry by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
-		\begin{figure}
-			\centering
-			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
-			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetry unitary \gls{ris}.}
-			\label{fg:singular_trend}
-		\end{figure}
-		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
-		It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and design parameters.
-		A larger performance gap is expected when asymmetric \gls{bd}-\gls{ris} is available.
-		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
+\begin{section}{Group-Wise Geodesic \glsfmtshort{rcg}}
+	In this section, we first provide an overview on signal processing techniques for general \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group to operate directly on the Stiefel manifold.
+	% The proposed method is applicable to any smooth optimization problem on the Stiefel manifold and is particularly suitable for \gls{bd}-\gls{ris} design problems.
+	We will later show that the proposed method not only provides better objective value and faster convergence than other approaches, but also works for arbitrary group size and any smooth optimization problem.
+	\begin{subsection}{Conventional Techniques}
+		General \gls{bd}-\gls{ris} design techniques can be classified into two categories based on the optimization variable and hardware architecture:
+		\begin{itemize}
+			\item \emph{Scattering matrix $\mathbf{\Theta}$:} This approach is often exploited for asymmetric architectures where the feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
+Due to its non-convexity, relevant problems are usually solved by general non-geodesic manifold optimization \cite{Li2023b,Li2023c,Bartoli2023} or relax-then-project methods \cite{Fang2023}.
+The former will be discussed in the next subsection.
+			\item \emph{Reactance matrix $\mathbf{X}$:} This approach is often exploited for symmetric architectures where every pair of elements in the same group are connected by capacitors and inductors.
+According to network theory \cite{Pozar2011}, it maps to the scattering matrix by $\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I})$, which formulates an unconstrained optimization problem on the upper triangular entries of $\{\mathbf{X}_g\}_{g \in \mathcal{G}}$ that is solvable by quasi-Newton methods \cite{Shen2020a}.
+		\end{itemize}
 	\end{subsection}
 
-	\begin{subsection}{Pareto Frontier Characterization}
-		We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:pareto_unitary}}
-		\end{maxi!}
-		where $n \in \{1,\ldots,N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
-		Varying $\{\rho_n\}$ unveils the entire achievable singular value region.
-		Thus, the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
-		The objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} for group $g$ corresponds to the Stiefel manifold.
-		Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
-
-		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a block-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
+	\begin{subsection}{Geodesic vs Non-Geodesic \glsfmtshort{rcg}}
+		We first revisit the general non-geodesic \gls{rcg} method that is applicable to optimization problems over arbitrary manifolds \cite{Absil2009,Pan2022d}.
+		The main idea is to perform group-wise \emph{additive} updates along the conjugate direction [not in, but guided by] the tangent space, then project the solution back onto the manifold.
+		% update the feasible point by progressing along conjugate directions then project back to the manifold.
+		% The main idea is to update the feasible point by progressing along conjugate directions then project back to the manifold.
+		For maximization problem with smooth objective $f$ and block-unitary constraint \eqref{eq:bd_ris}, the steps for group $g$ at iteration $r$ are summarized below:
+		\begin{enumerate}
+			\item \emph{Compute the Euclidean gradient \cite{Hjorungnes2007}:} The gradient of $f$ with respect to $\mathbf{\Theta}_g^*$ in the Euclidean space is
+			\begin{equation}
+				\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
+				\label{eq:gradient_euclidean}
+			\end{equation}
+			\item \emph{Translate to the Riemannian gradient \cite{Absil2009,Abrudan2008}:} At point $\mathbf{\Theta}^{(r)}$, the Riemannian gradient lies in the tangent space of the Stiefel manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} \mathbf{M} = \mathbf{0}\}$.
+It can be obtained by projecting the Euclidean gradient onto the tangent space:
+			\begin{equation}
+				% \nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H};
+				\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H} \mathbf{\Theta}_g^{(r)};
+				\label{eq:gradient_riemannian}
+			\end{equation}
+			\item \emph{Determine the conjugate direction \cite{Nocedal2006,Abrudan2009}:} The conjugate direction is updated over the Riemannian gradient and previous direction as
+			\begin{equation}
+				\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}, % $\mathcal{O}(N_\mathrm{S}^2)$
+				\label{eq:direction_cg}
+			\end{equation}
+			where $\gamma_g^{(r)}$ is the deviation parameter that accelerates the convergence. One common choice is the Polak-Ribierre formula \cite{Hager2006}
+			\begin{equation}
+				\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}; % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+				\label{eq:parameter_cg}
+			\end{equation}
+			\item \emph{Update [aided by] the tangent space}
+		\end{enumerate}
+		% It is worth noting that the objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} corresponds to the Stiefel manifold for group $g$.
+
+		% Both properties are often satisfied in \gls{bd}-\gls{ris} optimization problems, and there exists two general solutions in the literature:
+		% \begin{itemize}
+		% 	\item \emph{Quasi-Newton method \cite{Shen2020a}:}
+		% 	% This is a general-purpose optimization algorithm that approximates the Hessian matrix by the gradient and iteratively updates the scattering matrix along the negative gradient direction.
+		% \end{itemize}
+
+		% have exploited either the quasi-Newton method on the reactance
+		% Instead of solving it directly, we zoom out to general \gls{bd}-\gls{ris} optimization problem and propose an efficient and universal solution.
+		% Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
+
+		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a group-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
 		It leverages the fact that unitary matrices are closed under multiplication.
 		At iteration $r$, the gradient is computed in the Euclidean space and translated to the Riemannian manifold \cite{Absil2009}
-		\begin{gather}
-			\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
-			\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
-		\end{gather}
-		The Polak-Ribierre parameter \cite{Polak1969} is approximated as \cite{Abrudan2009}
-		\begin{equation}
-			\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-			\label{eq:parameter_cg}
-		\end{equation}
-		and the conjugate direction is
-		\begin{equation}
-			\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}. % $\mathcal{O}(N_\mathrm{S}^2)$
-			\label{eq:direction_cg}
-		\end{equation}
-		In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
+		% \begin{gather}
+		% 	\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
+		% 	\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
+		% \end{gather}
+		% The Polak-Ribierre parameter \cite{Polak1969} is approximated as \cite{Abrudan2009}
+		% \begin{equation}
+		% 	\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+		% 	\label{eq:parameter_cg}
+		% \end{equation}
+		% and the conjugate direction is
+		% \begin{equation}
+		% 	\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}. % $\mathcal{O}(N_\mathrm{S}^2)$
+		% 	\label{eq:direction_cg}
+		% \end{equation}
+		on the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
 		\begin{equation}
@@
 		\end{equation}
-		Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
+
+		It is worth mentioning that the updates can be performed in parallel for all groups, which is particularly suitable for large-scale \gls{bd}-\gls{ris} optimization problems.
+		One can also avoid group-wise updates by treating the entire scattering matrix as a single optimization variable, but this may lead to higher computational complexity and slower convergence.
+
+		Algorithm~\ref{ag:rcg} summarizes the proposed group-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
 		Convergence to stationary points is guaranteed.
@@
 			\small
-			\caption{Block-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
+			\caption{Group-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
 			\label{ag:rcg}
@@
 		\end{algorithm}
+	\end{subsection}
+
+\end{section}
+
+\begin{section}{Channel Singular Values Redistribution}
+	\begin{subsection}{Toy Example}\label{sc:toy_example}
+		We first illustrate the channel shaping capabilities of different \gls{ris} architectures by a toy example.
+		% We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
+		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
+		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{bd}-\gls{ris} has 4 independent angular parameters
+		\begin{equation}
+			\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
+				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
+				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
+			\end{bmatrix}.
+			\label{eq:unitary_ris}
+		\end{equation}
+		It is worth noting that $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
+		For a fair comparison, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
+		\begin{figure}
+			\centering
+			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
+			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetry unitary \gls{ris}.}
+			\label{fg:singular_trend}
+		\end{figure}
+		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
+		It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements.
+		A larger performance gap is expected when the symmetric constraint on \eqref{eq:unitary_ris} can be relaxed.
+		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
+	\end{subsection}
+
+	\begin{subsection}{Pareto Frontier Characterization}
+		We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:pareto_unitary}}
+		\end{maxi!}
+		where $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ is the maximum channel rank, and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
+		Varying $\{\rho_n\}_{n \in \mathcal{N}}$ characterizes the Pareto frontier that encloses the entire achievable singular value region.
+		Thus, we claim \eqref{op:pareto} generalizes most relevant channel shaping problems.
+		% It is worth noting that the objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} corresponds to the Stiefel manifold for group $g$.
 
@@
 
-		\begin{proposition}[fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
-			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the channel singular values can be manipulated up to
-			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
+		\begin{proposition}[unitary \gls{ris} without direct link]\label{pp:fully_connected}
+			% If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the channel singular values can be manipulated up to
+			% If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
 			% only bounds that apply here are those that apply to the singular values of
@@
 			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-			This suboptimal solution only applies to fully-connected \gls{bd}-\gls{ris}.
+			This suboptimal solution only applies to unitary \gls{bd}-\gls{ris}.
 		\end{remark}
@@
 	% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect subspace.
-	% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
+	% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by unitary \gls{ris}.
 	% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward subspace alignment for an optimal channel boost.
@@
 	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
-	$\kappa \to \infty$ is assumed for all channels unless otherwise specified.
+	$\kappa = 0$ is assumed for all channels unless otherwise specified.
 
@@
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
-			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by unitary \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
 			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
@@
 					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
-					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
+					`D' means diagonal \gls{ris} and `BD' means unitary \gls{bd}-\gls{ris}.
 					`rank-$k$' refers to the forward channel.
@@
 \ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
-			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_tight} or via optimization approach \eqref{eq:scattering_power}.
-			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
-			% We observe that the bound is also tight for fully-connected \gls{bd}-\gls{ris}.
+			Here, a unitary \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_tight} or via optimization approach \eqref{eq:scattering_power}.
+			% Recall that a unitary \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
+			% We observe that the bound is also tight for unitary \gls{bd}-\gls{ris}.
 			% Increasing the group size of \gls{bd}-\gls{ris} significantly improves the channel power especially for a large \gls{mimo}.
-			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a fully-connected one can achieve the bound.
+			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a unitary one can achieve the bound.
 			% The bound here indicates how much power can potentially be extracted from the forward and backward channels.
 			% We observe that using a larger group size can approach the bound better, and full
-			% We observe that the bound is tight for fully-connected \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
+			% We observe that the bound is tight for unitary \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
 			For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
+\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by unitary \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
 			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
@@
 		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the subspace alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
-		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
+		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for unitary \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
 
@@
 				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
-				`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
+				`D' means diagonal \gls{ris} and `BD' means unitary \gls{bd}-\gls{ris}.
 			}
@@
 		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a unitary \gls{bd}-\gls{ris}.
 		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
@@
 	This translates to a wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
-	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.
-	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
+	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and unitary scenarios.
+	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers better objective value and faster convergence than existing methods.
 	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
@@
 		Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
-		The scattering matrix of fully-connected \gls{ris} can be decomposed as
+		The scattering matrix of unitary \gls{ris} can be decomposed as
 		\begin{equation}
@@
 % 		Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
-% 		In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
+% 		In this case, a unitary $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
 % 		Interestingly, the result suggests that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).

### 2024-04-12 main.tex
:construction: Update complexity test

@@
 		We first revisit the general non-geodesic \gls{rcg} method that is applicable to optimization problems over arbitrary manifolds \cite{Absil2009,Pan2022d}.
-		The main idea is to perform group-wise \emph{additive} updates along the conjugate direction [not in, but guided by] the tangent space, then project the solution back onto the manifold.
+		The main idea is to perform \emph{additive} updates along the conjugate direction guided by the Riemannian gradient, then project the solution back onto the manifold.
 		% update the feasible point by progressing along conjugate directions then project back to the manifold.
 		% The main idea is to update the feasible point by progressing along conjugate directions then project back to the manifold.
-		For maximization problem with smooth objective $f$ and block-unitary constraint \eqref{eq:bd_ris}, the steps for group $g$ at iteration $r$ are summarized below:
+		For maximization problem with smooth objective $f$ and block-unitary constraint \eqref{eq:bd_ris}, the steps for \gls{bd}-\gls{ris} group $g$ at iteration $r$ are summarized below:
 		\begin{enumerate}
@@
 			\end{equation}
-			\item \emph{Translate to the Riemannian gradient \cite{Absil2009,Abrudan2008}:} At point $\mathbf{\Theta}^{(r)}$, the Riemannian gradient lies in the tangent space of the Stiefel manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} \mathbf{M} = \mathbf{0}\}$.
-It can be obtained by projecting the Euclidean gradient onto the tangent space:
-			\begin{equation}
-				% \nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H};
-				\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H} \mathbf{\Theta}_g^{(r)};
+			\item \emph{Translate to the Riemannian gradient \cite{Absil2009}:} At point $\mathbf{\Theta}^{(r)}$, the Riemannian gradient lies in the tangent space of the Stiefel manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$.
+It gives the steepest ascent direction of the objective on the manifold can be obtained by projecting the Euclidean gradient onto the tangent space:
+			\begin{equation}
+				% \nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)\mathsf{H}}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}};
+				\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}} \mathbf{\Theta}_g^{(r)};
 				\label{eq:gradient_riemannian}
 			\end{equation}
-			\item \emph{Determine the conjugate direction \cite{Nocedal2006,Abrudan2009}:} The conjugate direction is updated over the Riemannian gradient and previous direction as
+			\item \emph{Determine the conjugate direction \cite{Nocedal2006}:} The conjugate direction is obtained over the Riemannian gradient and previous direction as
 			\begin{equation}
@@
 			\end{equation}
-			where $\gamma_g^{(r)}$ is the deviation parameter that accelerates the convergence. One common choice is the Polak-Ribierre formula \cite{Hager2006}
-			\begin{equation}
-				\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}; % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+			where $\gamma_g^{(r)}$ is the parameter that deviates the conjugate direction from the tangent space for accelerated convergence. A popular choice is the Polak-Ribi\`{e}re formula
+			\begin{equation}
+				\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}; % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
 				\label{eq:parameter_cg}
 			\end{equation}
-			\item \emph{Update [aided by] the tangent space}
+			\item \emph{Perform additive update \cite{Pan2022d}:} The point is updated by moving along a straight path in the conjugate direction
+			\begin{equation}
+				\bar{\mathbf{\Theta}}_g^{(r+1)} = \mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)},
+				\label{eq:update_additive}
+			\end{equation}
+			where $\gamma$ is the step size refinable by the Armijo rule \cite{Armijo1966};
+			\item \emph{Retract for feasibility \cite{Absil2009,Li2023b}:} The resulting point needs to be projected back onto the Stiefel manifold by
+			\begin{equation}
+				\mathbf{\Theta}_g^{(r+1)} = \bar{\mathbf{\Theta}}_g^{(r+1)} \bigl({\bar{\mathbf{\Theta}}_g^{(r+1)\mathsf{H}}} \bar{\mathbf{\Theta}}_g^{(r+1)}\bigr)^{-1/2}.
+				\label{eq:retraction}
+			\end{equation}
+			One can also combine the addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction} in one step
+			\begin{equation}
+				\mathbf{\Theta}_g^{(r+1)} = \bigl(\mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)}\bigr) \bigl( \mathbf{I} + \mu^2 {\mathbf{D}_g^{(r)\mathsf{H}}} \mathbf{D}_g^{(r)} \bigr)^{-1/2},
+			\end{equation}
+			and determine the step size therein.
 		\end{enumerate}
+
+		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transported along the curve.
+		The above method is called non-geodesic since the points are updated in the linear embedding spaces of the manifold by addition and retraction, instead of on the Stiefel manifold itself.
+		Next, we revisit some concepts in differential geometry and introduce a group-wise geodesic \gls{rcg} method on top of \cite{Abrudan2008,Abrudan2009}.
+
+		A Lie group is simultaneously a continuous group and a differentiable manifold.
+		Lie algebra refers to the tangent space of the Lie group at the identity element.
+		The exponential map acts as a bridge between the Lie algebra and Lie group, which allows one to recapture the local group structure using linear algebra techniques.
+		% On the other hand, a geodesic is a curve representing the shortest path between two points in a Riemannian manifold.
+		% Its tangent vectors remain parallel when transported along the curve and the acceleration vectors stay normal to the motion.
+		Since unitary matrices forms a Lie group that is closed under multiplication and inversion, and the corresponding geodesic emanating from $\mathbf{\Theta}_g$ with a velocity matrix $\mathbf{S}$ can be described by \cite{Edelman1998}
+		\begin{equation}
+			\mathbf{G}_g = \exp(t \mathbf{S}) \mathbf{\Theta}_g,
+		\end{equation}
+
+		% Lie groups are closed under multiplication and inversion, and the set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group.
+		% The set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group that is closed under multiplication and inversion.
+		% Since unitary matrices in the Stiefel manifold $\mathbb{U}^{L \times L}$ constitute a Lie group, the corresponding geodesic emanating from $\mathbf{\Theta}_g$ with velocity $\mathbf{S}$ is described by the exponential map \cite{Edelman1998}
+		% \begin{equation}
+		% 	\mathbf{G}_g = \exp(t \mathbf{S}) \mathbf{\Theta}_g,
+		% \end{equation}
+		% $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
+
+		% A Lie group is a group that is also a differentiable manifold.
+		% The Lie group of unitary matrices $\mathbb{U}^{L \times L}$ is a manifold that is closed under multiplication and inversion.
+		% A geodesic is a curve representing the shortest path between two points in a Riemannian manifold.
+		% locally minimizes the distance between two points in a Riemannian manifold.
+
+		% Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a group-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
+
+		% It is worth noticing that the feasible domain
+
 		% It is worth noting that the objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} corresponds to the Stiefel manifold for group $g$.
@@
 		% 	\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
-		% 	\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
+		% 	\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)\mathsf{H}}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
 		% \end{gather}
@@
 		% \begin{equation}
-		% 	\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+		% 	\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
 		% 	\label{eq:parameter_cg}
@@
 						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
-						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
+						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)\mathsf{H}}} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
 							\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
@@
 						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic}
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
+						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
 							\State $\mu \gets 2 \mu$
 						\EndWhile
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
+						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
 							\State $\mu \gets \mu / 2$
@@
 			                                & Objective                             & Iterations                             & Time [s]         & Objective        & Iterations & Time [s] \\ \midrule
-			Geodesic                        & $\num{4.355e-3}$                      & 11.61                                  & $\num{2.038e-2}$ & $\num{1.164e-2}$ & 25.78      & 3.216    \\
-			Non-geodesic                    & $\num{4.168e-3}$                      & 169.5                                  & $\num{1.420e-1}$ & $\num{8.873e-3}$ & 278.1      & 27.81    \\ \bottomrule
+			Geodesic                        & $\num{4.359e-3}$                      & 11.59                                  & $\num{1.839e-2}$ & $\num{1.163e-2}$ & 25.58      & 3.461    \\
+			Non-geodesic                    & $\num{4.329e-3}$                      & 30.92                                  & $\num{5.743e-2}$ & $\num{1.116e-2}$ & 61.40      & 13.50    \\ \bottomrule
 		\end{tabular}
@@
 % 		\begin{equation}
-% 			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
-% 		\end{equation}
-% 		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H}$.
+% 			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)\mathsf{H}}},
+% 		\end{equation}
+% 		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)\mathsf{H}}} \mathbf{H}_{kj}^\mathsf{H}$.
 % 		The precoder at transmitter $j$ is updated as
@@
 % 		\end{equation}
-% 		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds to interference covariance matrix $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} \mathbf{H}_{kj}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} \mathbf{H}_{kj}$ in the reciprocal network.
+% 		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds to interference covariance matrix $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} \mathbf{H}_{kj}^\mathsf{H} {\mathbf{G}_k^{(r)\mathsf{H}}} \mathbf{G}_k^{(r)} \mathbf{H}_{kj}$ in the reciprocal network.
 % 		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_k\}$ are determined, we define $\bar{\mathbf{H}}_{kj}^\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}_{kj}^\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}_k^\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}_k^\mathrm{B}$, and $\bar{\mathbf{H}}_j^\mathrm{F} \triangleq \mathbf{H}_j^\mathrm{F} \mathbf{W}_j$.
@@
 % 		\begin{equation}
-% 			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H}\bigr)^{-1},
+% 			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)\mathsf{H}}} \mathbf{H}_{kk}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} \mathbf{H}_{kk}^\mathsf{H}\bigr)^{-1},
 % 		\end{equation}
@@
 % 		\begin{equation}
-% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{(r-1)} \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{(r-1)} \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
 % 		\end{equation}
@@
 % 		% 		\lambda_k^{(r)}
-% 		% 		& = \frac{\sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)}}^\mathsf{H}) - \sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)}}^\mathsf{H})}{P_k} \\
-% 		% 		& \quad + \frac{\mathrm{tr}(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H})}{P_k}
+% 		% 		& = \frac{\sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)\mathsf{H}}}) - \sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)\mathsf{H}}})}{P_k} \\
+% 		% 		& \quad + \frac{\mathrm{tr}(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}})}{P_k}
 % 		% 	\end{split}
@@
 % 		\begin{equation}
-% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)}}^\mathsf{H} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
+% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
 % 		\end{equation}
@@
 % 		\begin{equation}
-% 			\mathbf{W}_k^{(r)} = \Bigl(\sum_j \mathbf{H}_{jk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}_{jk} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \mathbf{H}_{kk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
+% 			\mathbf{W}_k^{(r)} = \Bigl(\sum_j \mathbf{H}_{jk}^\mathsf{H} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}_{jk} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \mathbf{H}_{kk}^\mathsf{H} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)}.
 % 		\end{equation}

### 2024-04-12 src/complexity_test.m

@@ -75,7 +75,7 @@ function [J, r] = scatter_singular_nongeodesic(H_d, H_f, H_b, rho, L)
 			S_c = setdiff(1 : length(Theta), S);
 			fun = @(Theta_g) rho' * svd(H_d + H_b(:, S) * Theta_g * H_f(S, :) + H_b(:, S_c) * Theta(S_c, S_c) * H_f(S_c, :));
 			G_e(S, S) = gradient_euclidean(H, H_f(S, :), H_b(:, S), rho);
-			G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
+			G_r(S, S) = gradient_riemannian_nongeodesic(Theta(S, S), G_e(S, S));
 			D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
 			Theta(S, S) = step_armijo_nongeodesic(fun, Theta(S, S), D(S, S));
 			H = channel_aggregate(H_d, H_f, H_b, Theta);
@@ -111,12 +111,18 @@ function [Theta] = step_armijo_nongeodesic(fun, Theta, D)
 	W = (Theta + mu * D) * ((Theta + mu * D)' * (Theta + mu * D)) ^ -0.5;
 	while (fun(W) - O) >= (mu * 0.5 * trace(D * D'))
 		mu = mu * 2;
-		W = (Theta + mu * D) * ((Theta + mu * D)' * (Theta + mu * D)) ^ -0.5;
+		% W = (Theta + mu * D) * ((Theta + mu * D)' * (Theta + mu * D)) ^ -0.5;
+		W = (Theta + mu * D) * (eye(size(Theta)) + mu ^ 2 * (D' * D)) ^ -0.5;
 	end
 	% * Overshoot, halve the step size
 	while (fun(W) - O) < (0.5 * mu * 0.5 * trace(D * D')) && (mu >= eps)
 		mu = mu * 0.5;
-		W = (Theta + mu * D) * ((Theta + mu * D)' * (Theta + mu * D)) ^ -0.5;
+		% W = (Theta + mu * D) * ((Theta + mu * D)' * (Theta + mu * D)) ^ -0.5;
+		W = (Theta + mu * D) * (eye(size(Theta)) + mu ^ 2 * (D' * D)) ^ -0.5;
 	end
 	Theta = W;
+end
+
[…]

### 2024-04-13 main.tex
:pencil: Update geodesic RCG

@@
 		We first revisit the general non-geodesic \gls{rcg} method that is applicable to optimization problems over arbitrary manifolds \cite{Absil2009,Pan2022d}.
-		The main idea is to perform \emph{additive} updates along the conjugate direction guided by the Riemannian gradient, then project the solution back onto the manifold.
+		The main idea is to perform {additive} updates along the conjugate direction guided by the Riemannian gradient, then {project} the solution back onto the manifold.
 		% update the feasible point by progressing along conjugate directions then project back to the manifold.
@@
 			\end{equation}
-			\item \emph{Translate to the Riemannian gradient \cite{Absil2009}:} At point $\mathbf{\Theta}^{(r)}$, the Riemannian gradient lies in the tangent space of the Stiefel manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$.
+			\item \emph{Translate to the Riemannian gradient \cite{Absil2009}:} At point $\mathbf{\Theta}^{(r)}$, the Riemannian gradient lies in the tangent space of the Stiefel manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$.
 It gives the steepest ascent direction of the objective on the manifold can be obtained by projecting the Euclidean gradient onto the tangent space:
@@
 			\end{equation}
-			where $\gamma$ is the step size refinable by the Armijo rule \cite{Armijo1966};
+			where $\mu$ is the step size refinable by the Armijo rule \cite{Armijo1966};
 			\item \emph{Retract for feasibility \cite{Absil2009,Li2023b}:} The resulting point needs to be projected back onto the Stiefel manifold by
@@
 				\mathbf{\Theta}_g^{(r+1)} = \bigl(\mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)}\bigr) \bigl( \mathbf{I} + \mu^2 {\mathbf{D}_g^{(r)\mathsf{H}}} \mathbf{D}_g^{(r)} \bigr)^{-1/2},
+				\label{eq:add_then_retract}
 			\end{equation}
@@
 		The exponential map acts as a bridge between the Lie algebra and Lie group, which allows one to recapture the local group structure using linear algebra techniques.
-		% On the other hand, a geodesic is a curve representing the shortest path between two points in a Riemannian manifold.
-		% Its tangent vectors remain parallel when transported along the curve and the acceleration vectors stay normal to the motion.
-		Since unitary matrices forms a Lie group that is closed under multiplication and inversion, and the corresponding geodesic emanating from $\mathbf{\Theta}_g$ with a velocity matrix $\mathbf{S}$ can be described by \cite{Edelman1998}
-		\begin{equation}
-			\mathbf{G}_g = \exp(t \mathbf{S}) \mathbf{\Theta}_g,
-		\end{equation}
-
-		% Lie groups are closed under multiplication and inversion, and the set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group.
-		% The set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group that is closed under multiplication and inversion.
-		% Since unitary matrices in the Stiefel manifold $\mathbb{U}^{L \times L}$ constitute a Lie group, the corresponding geodesic emanating from $\mathbf{\Theta}_g$ with velocity $\mathbf{S}$ is described by the exponential map \cite{Edelman1998}
-		% \begin{equation}
-		% 	\mathbf{G}_g = \exp(t \mathbf{S}) \mathbf{\Theta}_g,
-		% \end{equation}
-		% $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
-
-		% A Lie group is a group that is also a differentiable manifold.
-		% The Lie group of unitary matrices $\mathbb{U}^{L \times L}$ is a manifold that is closed under multiplication and inversion.
-		% A geodesic is a curve representing the shortest path between two points in a Riemannian manifold.
-		% locally minimizes the distance between two points in a Riemannian manifold.
-
-		% Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a group-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
-
-		% It is worth noticing that the feasible domain
-
-		% It is worth noting that the objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} corresponds to the Stiefel manifold for group $g$.
-
-		% Both properties are often satisfied in \gls{bd}-\gls{ris} optimization problems, and there exists two general solutions in the literature:
-		% \begin{itemize}
-		% 	\item \emph{Quasi-Newton method \cite{Shen2020a}:}
-		% 	% This is a general-purpose optimization algorithm that approximates the Hessian matrix by the gradient and iteratively updates the scattering matrix along the negative gradient direction.
-		% \end{itemize}
-
-		% have exploited either the quasi-Newton method on the reactance
-		% Instead of solving it directly, we zoom out to general \gls{bd}-\gls{ris} optimization problem and propose an efficient and universal solution.
-		% Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
-
-		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a group-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
-		It leverages the fact that unitary matrices are closed under multiplication.
-		At iteration $r$, the gradient is computed in the Euclidean space and translated to the Riemannian manifold \cite{Absil2009}
-		% \begin{gather}
-		% 	\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
-		% 	\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)\mathsf{H}}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
-		% \end{gather}
-		% The Polak-Ribierre parameter \cite{Polak1969} is approximated as \cite{Abrudan2009}
-		% \begin{equation}
-		% 	\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-		% 	\label{eq:parameter_cg}
-		% \end{equation}
-		% and the conjugate direction is
-		% \begin{equation}
-		% 	\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}. % $\mathcal{O}(N_\mathrm{S}^2)$
-		% 	\label{eq:direction_cg}
-		% \end{equation}
-		on the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
-		\begin{equation}
-			\mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}. % $\mathcal{O}(N_\mathrm{S}^3)$
-			\label{eq:geodesic}
-		\end{equation}
-		An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.\footnote{To double the step size, one only need to square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.}
-		Finally, the scattering matrix is updated along the geodesic as
-		\begin{equation}
-			\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
+		Note that the set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group $U(L)$ under multiplication, and the corresponding Lie algebra $\mathfrak{u}(L) \triangleq \mathcal{T}_{\mathbf{I}}\mathbb{U}^{L \times L} = \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} + \mathbf{M} = \mathbf{0}\}$ consists of skew-Hermitian matrices.
+		A geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ can be described by \cite{Edelman1998}
+		\begin{equation}
+			\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D}),
+			\label{eq:geodesic_identity}
+		\end{equation}
+		where $\exp(\mathbf{A}) = \sum_{k=0}^\infty (\mathbf{A}^k/k!)$ is the matrix exponential and $\mu$ is the step size (i.e., magnitude of the tangent vector).
+		Note that the right translation is an isometry in $U(L)$.
+		During the optimization of group $g$, the geodesic evaluated at the identity \eqref{eq:geodesic_identity} should be translated to $\mathbf{\Theta}_g^{(r)}$ for successive updates \cite{Abrudan2008}
+		\begin{equation}
+			\mathbf{G}_g^{(r)}(\mu) = \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
+			\label{eq:geodesic_translated}
+		\end{equation}
+		while the Riemannian gradient evaluated at $\mathbf{\Theta}_g^{(r)}$ \eqref{eq:gradient_riemannian} should be translated back to the identity for exploiting the Lie algebra \cite{Abrudan2008}
+		\begin{equation}
+			\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{R},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.
+			\label{eq:gradient_translated}
+		\end{equation}
+		After gradient translation, the deviation parameter and conjugate direction can be determined similarly to \eqref{eq:parameter_cg} and \eqref{eq:direction_cg}
+		\begin{equation}
+			\tilde{\gamma}_g^{(r)} = \frac{\mathrm{tr}\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\mathrm{tr}\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}.
+% $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+			\label{eq:parameter_cg_geodesic}
+		\end{equation}
+		\begin{equation}
+			{\mathbf{D}}_g^{(r)} = \tilde{\nabla}_{\mathrm{R},g}^{(r)} + \tilde{\gamma}_g^{(r)} {\mathbf{D}}_g^{(r-1)},
+			\label{eq:direction_cg_geodesic}
+		\end{equation}
+		The solution can thus be updated along the geodesic in a multiplicative rotational manner
+		\begin{equation}
+			\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
 			\label{eq:update_geodesic}
 		\end{equation}
-
-		It is worth mentioning that the updates can be performed in parallel for all groups, which is particularly suitable for large-scale \gls{bd}-\gls{ris} optimization problems.
-		One can also avoid group-wise updates by treating the entire scattering matrix as a single optimization variable, but this may lead to higher computational complexity and slower convergence.
-
-		Algorithm~\ref{ag:rcg} summarizes the proposed group-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
-		Convergence to stationary points is guaranteed.
-
-		\begin{remark}
-			Compared with universal manifold optimization \cite{Absil2009,Pan2022d}, Algorithm~\ref{ag:rcg} inherits a trifold benefit from \cite{Abrudan2008,Abrudan2009}:
-			\begin{enumerate}
-				\item No retraction thanks to rotational update \eqref{eq:geodesic}, \eqref{eq:update_geodesic};
-				\item Lower computational complexity per iteration;
-				\item Faster convergence thanks to proper parameter space.
-			\end{enumerate}
-		\end{remark}
+		where an appropriate $\mu$ may be obtained by the Armijo rule.
+		To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, since $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.
 
@@
 			\small
-			\caption{Group-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
+			\caption{Group-wise geodesic \gls{rcg} for \gls{bd}-\gls{ris} design}
 			\label{ag:rcg}
@@
 						\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean} \label{ln:gradient_euclidean}
-						\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riemannian}
-						\State $\gamma_g^{(r)} \gets$ \eqref{eq:parameter_cg}
-						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
-						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)\mathsf{H}}} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
+						\State $\tilde{\nabla}_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_translated}
+						\State $\tilde{\gamma}_g^{(r)} \gets$ \eqref{eq:parameter_cg_geodesic}
+						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg_geodesic}
+						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
 							\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
@@
 						\State $\mu \gets 1$
-						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic}
+						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic_translated}
 						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
@@
 		\end{algorithm}
+
+		Algorithm~\ref{ag:rcg} summarizes the proposed \gls{bd}-\gls{ris} design framework based on group-wise geodesic \gls{rcg}.
+		Compared to the non-geodesic approach, our method leverages the properties of unitary group to replace the add-then-retract update \eqref{eq:add_then_retract} with a multiplicative rotational update \eqref{eq:update_geodesic} along the geodesic.
+		This leads to faster convergence and simplifies the step size tuning thanks to an appropriate parameter space.
+
+		Both approaches can be performed in parallel for all groups to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
+		Since block-unitary matrices are also closed under multiplication, one can avoid group-wise updates by operating directly on $\mathbf{\Theta}$ and pinching (i.e., keeping the block diagonal and nulling the other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, at the cost of higher computational complexity and slower convergence.
 	\end{subsection}
-
 \end{section}

### 2024-04-15 main.tex
:pencil: Update corollaries

@@
 	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
+	$\odot$ represents the element-wise (Hadamard) product.
 	$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
@@
 			\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
+			\label{eq:scattering_siso}
 		\end{equation}
@@
 		The exponential map acts as a bridge between the Lie algebra and Lie group, which allows one to recapture the local group structure using linear algebra techniques.
-		Note that the set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group $U(L)$ under multiplication, and the corresponding Lie algebra $\mathfrak{u}(L) \triangleq \mathcal{T}_{\mathbf{I}}\mathbb{U}^{L \times L} = \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} + \mathbf{M} = \mathbf{0}\}$ consists of skew-Hermitian matrices.
+		The set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group $U(L)$ under multiplication, and the corresponding Lie algebra $\mathfrak{u}(L) \triangleq \mathcal{T}_{\mathbf{I}}\mathbb{U}^{L \times L} = \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} + \mathbf{M} = \mathbf{0}\}$ consists of skew-Hermitian matrices.
 		A geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ can be described by \cite{Edelman1998}
@@
 		Both approaches can be performed in parallel for all groups to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
-		Since block-unitary matrices are also closed under multiplication, one can avoid group-wise updates by operating directly on $\mathbf{\Theta}$ and pinching (i.e., keeping the block diagonal and nulling the other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, at the cost of higher computational complexity and slower convergence.
+		Since block-unitary matrices are also closed under multiplication, one can avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the block diagonal and nulling the other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, at the cost of higher computational complexity and slower convergence.
 	\end{subsection}
@@
 	\begin{subsection}{Toy Example}\label{sc:toy_example}
-		We first illustrate the channel shaping capabilities of different \gls{ris} architectures by a toy example.
-		% We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
+		We first illustrate the channel shaping capabilities of different \gls{ris} models by a toy example.
 		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
@@
 
-	\begin{subsection}{Pareto Frontier Characterization}
-		We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
+	\begin{subsection}{Pareto Frontier Characterization}\label{sc:pareto_frontier}
+		We then characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel_equivalent} by maximizing their weighted sum
 		\begin{maxi!}
@@
 		Varying $\{\rho_n\}_{n \in \mathcal{N}}$ characterizes the Pareto frontier that encloses the entire achievable singular value region.
-		Thus, we claim \eqref{op:pareto} generalizes most relevant channel shaping problems.
-		% It is worth noting that the objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} corresponds to the Stiefel manifold for group $g$.
+		Thus, we claim the singular value Pareto problem \eqref{op:pareto} generalizes most relevant channel shaping problems.
+		It can be solved by the proposed group-wise geodesic \gls{rcg} method with the following gradient expression.
 
@@
 
-		%  The Euclidean gradient of \gls{bd}-\gls{ris} group $g$ is computed as
-		% where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
-		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto} where line \ref{ln:gradient_euclidean} uses \eqref{eq:pareto_gradient} explicitly.
-		% \eqref{eq:pareto_gradient} is used in line \ref{ln:gradient_euclidean}.
+		Algorithm~\ref{ag:rcg} can thus be invoked for problem \eqref{op:pareto} where line \ref{ln:gradient_euclidean} uses \eqref{eq:pareto_gradient} explicitly.
+		With proper initialization, it is guaranteed to converge to (at least local) optimal points.
 	\end{subsection}
@@
 		We then discuss some analytical bounds related to channel singular values.
-		\begin{proposition}[degree of freedom]\label{pp:dof}
+		\begin{proposition}[Degree of freedom]\label{pp:dof}
 			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
@@
 
-		\begin{proposition}[rank-deficient channel]\label{pp:rank_deficient}
-			% If the forward/backward channel is rank-$k$, then a \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n > k$) channel singular value to the $n-k$-th singular value of $\mathbf{T}$, or suppress the $n$-th ($n < N - k + 1$) channel singular value to the $n$-th singular value of $\mathbf{T}$.
-			% If the forward/backward channel is rank-$k$, then a sufficiently large \gls{bd}-\gls{ris} can at most enlarge (resp.
-suppress) the first (resp.
-last) $k$ equivalent channel singular values without bounds.
-			If the forward or backward channel is rank-$k$, then regardless of the \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
+		\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
+			If the forward or backward channel is rank-$k$ ($k \le N$), then regardless of the passive \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
+			\begin{subequations}
 				\begin{align}
@@
 				\end{align}
+				\label{iq:sv_bound_rank_deficient}
+			\end{subequations}
 			where
-			% \begin{align}
-			% 	\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
-			% 	\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k.
-			% \end{align}
 			\begin{equation}
@@
 			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
-			% where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the forward channel is rank-$k$ and $\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the backward channel is rank-$k$.
 		\end{proposition}
@@
 
-		% \begin{corollary}[degree of freedom]
-		% 	In point-to-point \gls{mimo} with or without direct link, \gls{bd}-\gls{ris} cannot provide a higher \gls{dof} than diagonal \gls{ris}.
-		% \end{corollary}
-
-		\begin{corollary}[extreme singular values\label{co:extreme}]
-			With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded above while the last $k$ channel singular values can be suppressed to zero.
-			% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
-			% If the forward or backward channel is rank-$k$ and the \gls{ris} is sufficiently large, then the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
-			% If the forward/backward channel is rank-$k$, then the first (resp. last) $k$ singular values of the equivalent channel are unbounded above (resp. below).
-			% a sufficiently large \gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ singular values of the equivalent channel without bounds.
+		\begin{corollary}[Extreme singular values\label{co:extreme}]
+			With a sufficiently large passive \gls{ris} of arbitrary architecture, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
+This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
 		\end{corollary}
 
-		\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} in \cite{Semmler2023}.}\label{co:los}]
-			If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
+		\begin{proof}
+			This is a direct result of \eqref{iq:sv_bound_rank_deficient}.
+		\end{proof}
+
+		\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} \cite{Semmler2023}.}\label{co:los}]
+			% If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
 suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
 $n$-th) singular value of $\mathbf{T}$, that is,
+			If the forward or backward channel is \gls{los}, then a passive \gls{ris} of arbitrary architecture can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
+			That is,
 			\begin{equation}
@@
 
-		In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.
-
-		\begin{proposition}[unitary \gls{ris} without direct link]\label{pp:fully_connected}
+		\begin{proof}
+			This is a direct result of \eqref{iq:sv_bound_rank_deficient} with $k = 1$.
+		\end{proof}
+
+		In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can better approach those bounds than diagonal \gls{ris}.
+
+		\begin{proposition}[Unitary \gls{ris} without direct link]\label{pp:fully_connected}
 			% If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
@@
 
-		The problem now becomes how the singular values of matrix product are bounded by the singular values of its individual factors.
-		Let $N' = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le N'$.
+		The problem now becomes, how the singular values of matrix product are bounded by the singular values of its individual factors.
+		Let $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le \bar{N}$.
 		We have the following corollaries.
 
-		\begin{corollary}[generic singular value bounds \cite{Fulton2000}]
+		\begin{corollary}[Generic singular value bounds\label{co:sv_bound_horn}]
 			\begin{equation}
@@
 			\end{equation}
-			for all admissible triples $(I, J, K) \in T_r^{N'}$ with $r < N'$, where
+			for all admissible triples $(I, J, K) \in T_r^{\bar{N}}$ with $r < \bar{N}$, where
 			\begin{equation*}
 				\begin{gathered}
-					% T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
+					% T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
 					% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-					T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \forall p < r, (F, G, H) \in T_p^r,\\
+					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \mid \forall p < r, (F, G, H) \in T_p^r,\\
 					\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
@@
 			\begin{equation*}
-				U_r^{N'} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
+				U_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
 			\end{equation*}
@@
 
-		\begin{corollary}[upper bound on the largest singular value]
+		\begin{proof}
+			Please refer to \cite[Theorem~8]{Fulton2000}.
+		\end{proof}
+
+		Corollary \eqref{co:sv_bound_horn} is by far the most comprehensive singular value bound over Proposition~\ref{pp:fully_connected}, which is also recognized as a variation of Horn's inequality \cite{Bhatia2001}.
+		It is worth mentioning that the number of admissible triples (and bounds) grows exponentially with $\bar{N}$.
+		For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $\bar{N}$ increases from 3 to 7.
+		This renders it computationally expensive for applications in large-scale \gls{mimo} systems.
+		Next, we showcase some useful inequalities enclosed by \eqref{iq:sv_bound_fc}.
+		Readers are referred to \cite[Chapter 16, 24]{Hogben2013} for more examples.
+
+		\begin{corollary}[Upper bound on the largest singular value\label{co:sv_largest}]
 			\begin{equation}
@@
 
-		% \begin{corollary}[lower bound on the smallest singular value]
-		% 	\begin{equation}
-		% 		\sigma_{N'}(\mathbf{H}) \ge \sigma_{N'}(\mathbf{H}_\mathrm{B}) \sigma_{N'}(\mathbf{H}_\mathrm{F}).
+		\begin{proof}
+			This is a direct result of \eqref{iq:sv_bound_fc} with $r = 1$.
+		\end{proof}
+
+		\begin{corollary}[Lower bound on the smallest singular value\label{co:sv_smallest}]
+			\begin{equation}
+				\sigma_{\bar{N}}(\mathbf{H}) \ge \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}).
+			\end{equation}
+		\end{corollary}
+
+		\begin{proof}
+			This can be deducted from \eqref{iq:sv_bound_fc} with $r_1 = \bar{N}{-}1$ and $r_2 = \bar{N}$.
+		\end{proof}
+
+		\begin{corollary}[Upper bound on the product of first $k$ singular values]
+			\begin{equation}
+				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
+			\end{equation}
+		\end{corollary}
+
+		\begin{proof}
+			This is a direct result of \eqref{iq:sv_bound_fc} with $r = k$.
+		\end{proof}
+
+		\begin{corollary}[Lower bound on the product of last $k$ singular values\label{co:sv_product_smallest}]
+			\begin{equation}
+				\prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
+			\end{equation}
+		\end{corollary}
+
+		\begin{proof}
+			This can be deducted from \eqref{iq:sv_bound_fc} with $r_1 = \bar{N}-k$ and $r_2 = \bar{N}$.
+		\end{proof}
+
+		Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., unequal number of transmit, scatter, and receive antennas) as the lower bounds would be zero.
+
+		% \begin{corollary}[Upper bound on the sum of first $k$ singular values to the positive $p$-th power\label{co:sum_power} {\cite[Inequality~24.4.7]{Hogben2013}}]
+		% 	\begin{equation}
+		% 		\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
+		% 		\label{iq:sv_bound_fc_power}
+		% 	\end{equation}
+		% 	When $k = N$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels
+		% 	\begin{equation}
+		% 		\lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
 		% 	\end{equation}
@@
 
-		\begin{corollary}[upper bound on the product of first $k$ singular values]
-			\begin{equation}
-				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
+		\begin{corollary}[Upper bound on the channel power gain\label{co:sum_power}]
+			% The channel power gain is upper bounded by the sum of sorted element-wise power product of backward and forward subchannels
+			The channel power gain is upper bounded by the sum of sorted element-wise product of squared singular values of backward and forward subchannels
+			\begin{equation}
+				\lVert \mathbf{H} \rVert _\mathrm{F}^2 = \sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}).
+				\label{iq:power_gain}
 			\end{equation}
@@
 
-		% \begin{corollary}[lower bound on the product of last $k$ singular values]
-		% 	\begin{equation}
-		% 		\prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
-		% 	\end{equation}
-		% \end{corollary}
-
-		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
-			\begin{equation}
-				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
-				\label{iq:sv_bound_fc_power}
-			\end{equation}
-			When $k = N'$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels.
-		\end{corollary}
+		\begin{proof}
+			Please refer to \cite[Inequality~24.4.7]{Hogben2013}.
+		\end{proof}
+
+		To achieve the equalities in Corollaries \eqref{co:sv_largest} -- \eqref{co:sum_power}, the \gls{ris} needs to completely align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		The resulting scattering matrix is generally required to be unitary
+		\begin{equation}
+			\mathbf{\Theta}^\star = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H},
+			\label{eq:scattering_fc_optimal}
+		\end{equation}
+		which can be concluded from \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in Appendix~\ref{ap:fully_connected}.
+		Interestingly, diagonal \gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
+		In such case, the equivalent channel reduces to $\mathbf{H} = \sigma_\mathrm{B} \sigma_\mathrm{F} \mathbf{u}_\mathrm{B} \mathbf{v}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ and the \gls{ris} only needs to align $\mathbf{v}_\mathrm{B}^\mathsf{H}$ and $\mathbf{u}_\mathrm{F}$ by
+		\begin{equation}
+			\mathbf{\Theta}^\star = \mathbf{v}_\mathrm{B} \mathbf{u}_\mathrm{F}^\mathsf{H} \odot \mathbf{I},
+		\end{equation}
+		which becomes a special case of \eqref{eq:scattering_siso}.
+		On the other hand, when $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both in Rayleigh fading, the expected maximum channel power gain $\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F} \bigr\}_{\max}$ can be evaluated as
+		\begin{equation}
+			\sum_{n=1}^N \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x_n) d x_n \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x_n) d x_n,
+			\label{eq:power_gain_rayleigh}
+		\end{equation}
+		where $\lambda_n^{\dot{N}}$ is the $n$-th eigenvalue of the complex $\dot{N} \times \dot{N}$ Wishart matrix with probability density function $f_{\lambda_n^{\dot{N}}}(x_n)$ given by \cite[Equation 51]{Zanella2009}.
+		We notice \eqref{eq:power_gain_rayleigh} is a generalization of \cite[Equation 58]{Shen2020a} to \gls{mimo}.
+
+		% and $f_{\lambda_{\mathrm{F},n}}$ are their corresponding probability density functions.
+
+		% the singular values of a rank-1 matrix are invariant under unitary transformations.
+
+		% unless both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are rank-1.
+		% optimal passive \gls{ris} design should align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation and pair the subchannels from strongest to weakest.
+		% When both backward and forward channels are rank-1
+		% When the backward and forward channels are in Rayleigh fading,
+		% we can derive an explicit upper bound on the channel power gain when the backward and forward channels are Rayleigh fading.
 
@@
 
-		Tight bounds are inapplicable when a \gls{mimo} direct link is present, as the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
-		Such a balance often involves optimization approaches and another example will be discussed in Section~\ref{sc:low_complexity}.
+		Tighter bounds than Proposition \ref{pp:rank_deficient} are generally inapplicable when a \gls{mimo} direct link is present or the \gls{bd}-\gls{ris} is not unitary.
+		% Proposition \ref{pp:fully_connected} only applies to unitary \gls{ris} without direct link, since t
+		This is because there exists a trade-off between the direct-indirect and backward-forward subspace alignments.
+		In such case, a balance could be struck by optimization approaches from a singular value perspective (discussed in Section~\ref{sc:pareto_frontier}) or a power gain perspective (will be discussed in Section~\ref{sc:rate}).
 	\end{subsection}
-
 \end{section}
@@
 			Fig.
-\ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
+\ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{\bar{N}} = 0$, $\forall \bar{N} \ne n$.
 			Here we assme a rank-$k$ forward channel without loss of generality.
@@
 			Fig.
-\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
+\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=\bar{N}$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
 			Here, a unitary \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_tight} or via optimization approach \eqref{eq:scattering_power}.
@@
 	\begin{subsection}{Proof of Proposition \ref{pp:dof}}\label{ap:dof}
-		The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as\footnote{This is because (block) unitary matrices are closed under multiplication.}
+		The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as
 		\begin{equation}

### 2024-04-16 main.tex
:pencil: Update manuscript

@@
 	$\mathrm{tr}(\cdot)$ and $\det(\cdot)$ evaluates the trace and determinant of a square matrix, respectively.
-	$\mathrm{diag}(\cdot)$ constructs a square matrix with arguments on the main diagonal and zeros elsewhere.
+	$\mathrm{diag}(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
 	$\mathrm{sv}(\cdot)$ returns the singular value vector.
@@
 		\begin{lemma}\label{lm:pareto_gradient}
-			The Euclidean gradient of \eqref{ob:pareto} w.r.t. \gls{bd}-\gls{ris} group $g$ is
+			The Euclidean gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
 			\begin{equation}
@@
 
-		Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., unequal number of transmit, scatter, and receive antennas) as the lower bounds would be zero.
+		Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., unequal number of transmit, scatter, and receive antennas) as the lower bounds would coincide at zero.
 
@@
 
-		% and $f_{\lambda_{\mathrm{F},n}}$ are their corresponding probability density functions.
-
-		% the singular values of a rank-1 matrix are invariant under unitary transformations.
-
-		% unless both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are rank-1.
-		% optimal passive \gls{ris} design should align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation and pair the subchannels from strongest to weakest.
-		% When both backward and forward channels are rank-1
-		% When the backward and forward channels are in Rayleigh fading,
-		% we can derive an explicit upper bound on the channel power gain when the backward and forward channels are Rayleigh fading.
-
-		% \begin{remark}
-		% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-		% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-		% 	\begin{equation}
-		% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
-		% 		\label{eq:scattering_fc_tight}
-		% 	\end{equation}
-		% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
-		% 	\begin{itemize}
-		% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-		% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
-		% 	\end{itemize}
-		% \end{remark}
-
-		Tighter bounds than Proposition \ref{pp:rank_deficient} are generally inapplicable when a \gls{mimo} direct link is present or the \gls{bd}-\gls{ris} is not unitary.
-		% Proposition \ref{pp:fully_connected} only applies to unitary \gls{ris} without direct link, since t
-		This is because there exists a trade-off between the direct-indirect and backward-forward subspace alignments.
-		In such case, a balance could be struck by optimization approaches from a singular value perspective (discussed in Section~\ref{sc:pareto_frontier}) or a power gain perspective (will be discussed in Section~\ref{sc:rate}).
+		Tighter bounds are generally inapplicable when the direct link is present or the \gls{bd}-\gls{ris} is not unitary, since the direct-indirect channels and backward-forward channels cannot be completely aligned at the same time.
+		In such case, we can exploit optimization approaches from a singular value perspective (Section~\ref{sc:pareto_frontier}) or a power gain perspective (Section~\ref{sc:power}).
 	\end{subsection}
@@
 
-\begin{section}{Achievable Rate Maximization}\label{sc:rate}
-	The \gls{mimo} achievable rate maximization problem is formulated w.r.t. joint active and passive beamforming
+\begin{section}{Power Gain and Achievable Rate Maximization}\label{sc:power_rate}
+	\begin{subsection}{Channel Power Gain}\label{sc:power}
+		The \gls{mimo} channel power gain maximization problem is formulated with respect to the \gls{bd}-\gls{ris} scattering matrix
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		\end{maxi!}
+		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct-less \gls{mimo} with unitary \gls{ris} \eqref{eq:scattering_fc_optimal}.
+		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
+		Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
+		\begin{mini!}
+			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
+			\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_block_unitary}}{}
+		\end{mini!}
+		which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary but still has no trivial solution.
+		One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
+		\begin{mini!}
+			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
+			\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
+		\end{mini!}
+		which have global optimal solutions
+		\begin{equation}
+			\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
+			\label{eq:orthogonal_procrustes_solution}
+		\end{equation}
+		where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
+		We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid unitary \gls{ris} solutions to \eqref{op:power_passive} when the direct link is absent and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
+
+		Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power_passive} with arbitrary group size.
+		The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
+
+		\begin{proposition}\label{pp:power}
+			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
+			\begin{equation}
+				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
+				\label{eq:scattering_power}
+			\end{equation}
+			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
+			\begin{equation}
+				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+				\label{eq:auxiliary_matrix_power}
+			\end{equation}
+		\end{proposition}
+
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:power}.
+		\end{proof}
+	\end{subsection}
+
+	\begin{subsection}{Achievable Rate Maximization}\label{sc:rate}
+		We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
 		\begin{maxi!}
 			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
-		\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
-		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cs:rate_block_unitary}}
 		\end{maxi!}
-	where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the noise power, and $P$ is the transmit power budget.
-	Two methods are proposed below to solve problem \eqref{op:rate}.
-
-	\begin{subsection}{Alternating Optimization}
-		Consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
+		where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
+		Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cs:rate_block_unitary} and the coupling between variables.
+		We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
+
+		\begin{subsubsection}{Alternating Optimization}
+			This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
 			For a given $\mathbf{W}$, the passive beamforming subproblem is
@@
 			\begin{lemma}\label{lm:rate_gradient}
-			The Euclidean gradient of \eqref{ob:rate_passive} w.r.t. \gls{bd}-\gls{ris} block $g$ is
+				The Euclidean gradient of \eqref{ob:rate_passive} with respect to \gls{bd}-\gls{ris} block $g$ is
 				\begin{equation}
@@
 			\end{proof}
-		Algorithm \ref{ag:rcg} is then invoked to solve problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
-		Since \eqref{ob:rate_passive} is a concave function of $\mathbf{\Theta}$, convergence to local-optimal points is guaranteed.
-		On the other hand, the global optimal transmit precoder for a fixed $\mathbf{\Theta}$ is given by the eigenmode transmission \cite{Clerckx2013}
-		\begin{equation}
-			\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
+			Algorithm \ref{ag:rcg} can thus be invoked for problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
+			Since \eqref{ob:rate_passive} is a concave function of $\mathbf{\Theta}$, convergence to (at least local) optimal points is guaranteed.
+			For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
+			\begin{equation}
+				\mathbf{W}^\star = \mathbf{V} {\mathrm{diag}(\mathbf{s}^\star)}^{1/2},
 				\label{eq:precoder_eigenmode}
 			\end{equation}
-		where $\mathbf{V}$ is the right channel singular matrix and $\mathbf{S}^\star$ is the optimal water-filling power allocation matrix.
-		The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-	\end{subsection}
-
-	\begin{subsection}{Low-Complexity Solution}\label{sc:low_complexity}
-		We then propose a low-complexity solution to problem \eqref{op:rate} based on channel shaping.
-		The passive beamforming subproblem \eqref{op:rate_passive} involves transmit covariance matrix $\mathbf{Q}$ and thus requires iterative \gls{rcg} update.
-		Instead, we decouple the joint \gls{ris}-transceiver design by recasting \eqref{op:rate_passive} as channel power maximization
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
-		\end{maxi!}
-		% which only accounts for channel characteristics but has no trivial solution.
-		\begin{remark}
-			As mentioned in Section \ref{sc:bounds}, the key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
-			Problem \eqref{op:power_passive} is very similar (in terms of maximizing the inner product of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$) to the weighted orthogonal Procrustes problem \cite{Gower2004}
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
-			\end{mini!}
-			which has no trivial solution.
-			One lossy transformation, by moving $\mathbf{\Theta}$ to one side \cite{Bell2003}, formulates standard orthogonal Procrustes problems
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
-			\end{mini!}
-			which has global optimal solutions
-			\begin{equation}
-				\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}
-				\label{eq:orthogonal_procrustes_solution}
-			\end{equation}
-			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-			This suboptimal solution only applies to unitary \gls{bd}-\gls{ris}.
-		\end{remark}
-
-		Inspired by \cite{Nie2017}, we propose a general solution to problem \eqref{op:power_passive} with arbitrary group size.
-		The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form.
-
-		\begin{proposition}\label{pp:power}
-			Starting from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
-			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
-				\label{eq:scattering_power}
-			\end{equation}
-			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
-			\begin{equation}
-				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-				\label{eq:auxiliary_matrix_power}
-			\end{equation}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:power}.
-		\end{proof}
-		Once the channel shaping problem \eqref{op:power_passive} is solved, the transmit precoder can be obtained by \eqref{eq:precoder_eigenmode}.
-		This two-stage approach decouples both blocks and is computationally efficient.
-	\end{subsection}
-
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{fg:pc_rate_sx}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/simulation/pc_rate_sx.tex}
-	% 		}
-	% 	}
-	% 	\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{fg:pc_rate_tx}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/simulation/pc_rate_tx.tex}
-	% 		}
-	% 	}
-	% 	\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:pc_rate}
-	% \end{figure}
-
-	% Fig.~\ref{fg:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
-	% To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
-	% This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
-	% If tetrads can be formed in \gls{bd}-\gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
-	% Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
-	% We thus conclude dyadic or tetradic \gls{bd}-\gls{ris} usually strike a good balance between performance and complexity.
-
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{0.65\columnwidth}{!}{
-	% 		\input{assets/simulation/power_sx.tex}
-	% 	}
-	% 	\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
-$(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:power_sx}
-	% \end{figure}
-
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\subfloat[Without Direct Link\label{fg:pc_power_bond_nd}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/simulation/pc_power_bond_nd.tex}
-	% 		}
-	% 	}
-	% 	\subfloat[With Direct Link\label{fg:pc_power_bond_hd}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/simulation/pc_power_bond_hd.tex}
-	% 		}
-	% 	}
-	% 	\caption{Average channel power versus \gls{ris} group size $L$.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:pc_power_bond}
-	% \end{figure}
-	% % Fig.~\ref{fg:power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
-	% % Fig.~\ref{fg:power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
-	% Fig.~\ref{fg:power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
-	% % The behavior is more obvious for a large \gls{ris}.
-	% This behavior is more pronounced for a large \gls{ris}.
-	% For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
-	% % \gls{bd}-\gls{ris} provides a higher channel power than conventional \gls{ris}.
-	% % As $L$ increases from 1 to 2,
-	% It implies that the channel shaping capability of \gls{bd}-\gls{ris} scales with group size $L$.
-
-	% Fig.~\ref{fg:pc_power_bond_hd} and \ref{fg:pc_power_bond_nd} compare the average channel power without and with direct link.
-	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % ``Cascaded'' means the maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % ? ``Cascaded'' means the \emph{power product} of the forward and backward channels.
-	% % ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues of the forward and backward channels.
-	% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
-	% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect subspace.
-	% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by unitary \gls{ris}.
-	% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward subspace alignment for an optimal channel boost.
-	% It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
-	% This again emphasizes the advantage of in-group connection of \gls{bd}-\gls{ris}.
-	% % This is because the direct and indirect channels superpose
-	% % the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
-	% % When the direct link is present, a small $L$ cannot align the direct-indirect subspace.
-
-	% % neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
-	% % We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
-	% % For conventional \gls{ris},
-	% % align the direct-indirect subspace.
-	% % When the direct link is present, a small $L$ can neither align the direct-indirect subspace nor the forward-backward subspace.
-	% % For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
-	% % neither the direct-indirect nor the forward-backward subspace can be effectively aligned with a small $L$.
-
-	% % When the direct link is present, a small $L$ can neither preserve the
-	% % neither align the direct-indirect subspace nor the forward-backward subspace.
-
-	% % When the direct link is absent, a large $L$ can align the forward-backward subspace but cannot preserve the forward-backward power balance.
-
+			where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation obtainable by the iterative method \cite{Tse2005}.
+			The overall \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Low-Complexity Solution}\label{sc:low_complexity}
+			We then propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
+			The idea is to first consider channel shaping and replace the rate maximization problem \eqref{op:rate_passive} by channel power gain maximization problem \eqref{op:power_passive}, then proceed to conventional eigenmode transmission \eqref{eq:precoder_eigenmode}.
+			Both steps are solved in closed form and the computational complexity is significantly reduced.
+		\end{subsubsection}
+	\end{subsection}
 \end{section}
@@
 \begin{section}{Simulation Results}\label{sc:simulation}
-	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
-	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
-	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
-	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
-	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
-	$\kappa = 0$ is assumed for all channels unless otherwise specified.
-
 	\begin{table*}[!t]
-		\caption{Average Performance of \gls{bd}-\gls{ris} Designs}
+		\caption{Average Performance of Geodesic and Non-Geodesic \gls{rcg} Algorithms on Problem \eqref{op:pareto}}
 		\label{tb:complexity_test}
@@
 	\end{table*}
+	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
+	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
+	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
+	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
+	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
+	Rayleigh fading (i.e., $\kappa = 0$) is assumed for all channels unless otherwise specified.
+
+	\begin{subsection}{Algorithm Evaluation}
+		We first compare the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in a 4T4R system with \gls{bd}-\gls{ris} group size $L=4$.
+		The statistics are averaged over \num{100} independent runs.
+		It is observed that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (up to 3$\times$) lower number of iterations and shorter (up to 4$\times$) computational time than the non-geodesic method.
+		The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially in large-scale \gls{bd}-\gls{ris} design problems.
+		If the scattering matrix is constrained to be symmetric, one can project the solution to the feasible domain by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.
+	\end{subsection}
 
@@
 			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
-			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
+			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two subspaces.
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
-			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by unitary \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We observe that the smallest singular value can be enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by unitary \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
 			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
@@
 			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
-			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
+			This transformation not only provides a better trade-off in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
 			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
-			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
+			In particular, Fig.
+\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris}.
 		\end{subsubsection}
@@
 					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
-					`D' means diagonal \gls{ris} and `BD' means unitary \gls{bd}-\gls{ris}.
-					`rank-$k$' refers to the forward channel.
+					The intersections of the blue and red bars denote the singular values of the direct channel.
+					The blue (resp. red) bars are obtained by solving problem \eqref{op:pareto} with $\rho_n = -1$ (resp. $+1$) and $\rho_{n'} = 0$, $\forall n' \ne n$.
+					`D' means diagonal \gls{ris} and `BD' refers to unitary \gls{bd}-\gls{ris}.
+					`rank-$k$' refers to the rank of the forward channel.
 				}
@@
 			Fig.
-\ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{\bar{N}} = 0$, $\forall \bar{N} \ne n$.
+\ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
 			Here we assme a rank-$k$ forward channel without loss of generality.
@@
 			Fig.
-\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=\bar{N}$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
-			Here, a unitary \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_tight} or via optimization approach \eqref{eq:scattering_power}.
-			% Recall that a unitary \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
-			% We observe that the bound is also tight for unitary \gls{bd}-\gls{ris}.
+\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
+			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_optimal} or via optimization approach \eqref{eq:scattering_power}.
+			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
+			% We observe that the bound is also tight for fully-connected \gls{bd}-\gls{ris}.
 			% Increasing the group size of \gls{bd}-\gls{ris} significantly improves the channel power especially for a large \gls{mimo}.
-			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a unitary one can achieve the bound.
+			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a fully-connected one can achieve the bound.
 			% The bound here indicates how much power can potentially be extracted from the forward and backward channels.
 			% We observe that using a larger group size can approach the bound better, and full
-			% We observe that the bound is tight for unitary \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
+			% We observe that the bound is tight for fully-connected \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
 			For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by unitary \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
+\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
 			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
@@
 			This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
+			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement.
 			Now consider a diagonal \gls{ris} in \gls{mimo}.
@@
 
-	\begin{subsection}{Achievable Rate Maximization}
+	\begin{subsection}{Power Gain and Achievable Rate Maximization}
 		\begin{figure}[!t]
@@
 			\subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)\label{fg:power_sx_txrx16_nd}]{
-				\resizebox{!}{3.25cm}{
+				\resizebox{!}{3.0625cm}{
 					\input{assets/simulation/power_sx_txrx16_nd.tex}
@@
 			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
-				\resizebox{!}{3.25cm}{
+				\resizebox{!}{3.0625cm}{
 					\input{assets/simulation/power_sx_txrx16.tex}
@@
 
-		We first focus on channel shaping subproblem \eqref{op:power_passive_approx}.
+		We first focus on channel power gain maximization problem \eqref{op:power_passive}.
 		Fig. \ref{fg:power_sx} shows the achievable channel power under different \gls{ris} configurations.
@@
 		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the subspace alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
-		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for unitary \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
+		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
 
@@
 				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
-				`D' means diagonal \gls{ris} and `BD' means unitary \gls{bd}-\gls{ris}.
+				`D' means diagonal \gls{ris} and `BD' refers to unitary \gls{bd}-\gls{ris}.
 			}
@@
 		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a unitary \gls{bd}-\gls{ris}.
-		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
+		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+		This implies that the \gls{ris}-transceiver design can often be decoupled via channel shaping with marginal performance loss.
 		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
 		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
-		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better tradeoff between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
+		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better trade-off between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
 		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
@@
 		\end{equation}
-		whose differential w.r.t. $\mathbf{\Theta}_g^*$ is
+		whose differential with respect to $\mathbf{\Theta}_g^*$ is
 		\begin{align*}
@@
 	\begin{subsection}{Proof of Lemma \ref{lm:rate_gradient}}\label{ap:rate_gradient}
-		The differential of $R$ w.r.t. $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
+		The differential of $R$ with respect to $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
 		\begin{align*}
@@
 	\begin{subsection}{Proof of Proposition \ref{pp:power}}\label{ap:power}
-		The differential of \eqref{ob:power_passive} w.r.t. $\mathbf{\Theta}_g^*$ is
+		The differential of \eqref{ob:power_passive} with respect to $\mathbf{\Theta}_g^*$ is
 		\begin{align*}
@@
 % 		\end{equation}
-% 		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} w.r.t. \gls{ris} block $g$ is
+% 		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} with respect to \gls{ris} block $g$ is
 % 		\begin{equation}

### 2024-04-22 main.tex
:pencil: Update abstract

@@
 \begin{abstract}
-	This paper investigates how a passive \gls{ris} can manipulate the \gls{mimo} point-to-point channel in terms of singular values and power gain.
-	We depart from the widely-adopted diagonal phase shift model to a \gls{bd} architecture, which enables {cooperative} wave scattering thanks to in-group connections between elements.
-	An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} on the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
-	% For the singular value shaping problem, we numerically characterize their Pareto frontiers by weighted sum optimization via geodesic \gls{rcg}, which generalizes most relevant metrics (e.g., degree of freedom and condition number).
-	% Many analytical singular value bounds are also derived for rank-deficient channels and unitary (a.k.a. unitary) \gls{ris}.
-	For the singular value problem, we numerically characterize their Pareto frontiers by geodesic \gls{rcg} and derive analytical bounds for rank-deficient channels and fully-connected (a.k.a.
-unitary) \gls{ris}.
-	% For the singular value problem, we consider a numerical optimization approach that characterizes the Pareto frontiers as well as an analytical bounding approach in special (i.e., rank-deficient and fully-connected) scenarios.
-	For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
-	% Those channel shaping designs have a two-fold advantage.
-	Those channel shaping designs have two major implications.
-	First, they demystify the performance gain from off-diagonal entries in terms of {subchannel rearrangement} and {subspace alignment}.
+	This paper investigates the limit to which a passive \gls{ris} can redistribute the singular values of a point-to-point \gls{mimo} channel.
+	We depart from the widely-adopted diagonal phase shift model to a \gls{bd}-\gls{ris} architecture, which enables {cooperative} wave scattering thanks to in-group connections between elements.
+	% An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} on the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
+	The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., degree of freedom and condition number).
+	To quantify the shaping capability of diagonal and \gls{bd}-\gls{ris}, we also derive individual and collective singular value bounds for rank-deficient channels and fully-connected \gls{ris} via matrix analysis.
+	% For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
+	Those results help to explain the shaping advantage from off-diagonal entries in terms of subchannel rearrangement and subspace alignment.
+	% Subchannel rearrangement is a unique feature of off-diagonal entries that allows each group to rearrange and recombine the forward and backward subchannels.
+	% Subspace alignment generalizes phase matching in \gls{siso} and introduces a trade-off between multiplicative backward-forward and additive direct-indirect channel combinations.
+	% Those channel shaping designs have two major implications.
+	% First, they demystify the performance gain from off-diagonal entries in terms of {subchannel rearrangement} and {subspace alignment}.
 	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment.
-	Second, they inspire a two-stage suboptimal solution that decouples joint active and passive beamforming design.
+	% Second, they inspire a two-stage suboptimal solution that decouples joint active and passive beamforming design.
 	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
-	As a side product, we tackle the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} approach and a two-stage shaping-inspired approach.
-	Simulation results indicate that the rate deficit from the latter diminishes as the \gls{ris} evolves from diagonal towards unitary, while the relative gain of \gls{bd}-\gls{ris} increase with \gls{mimo} dimensions and decrease with spatial correlation.
+	As a side product, we tackle \gls{ris}-aided \gls{mimo} rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-based approach.
+	Simulation results highlight that \gls{bd}-\gls{ris} provides a wider dynamic range and better trade-off on channel singular values, while its power and rate gains over diagonal \gls{ris} scale with \gls{mimo} dimensions.
+
+	% wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
+
+	% indicate that the rate deficit from the latter diminishes as the \gls{ris} evolves from diagonal towards unitary, while the relative gain of \gls{bd}-\gls{ris} increase with \gls{mimo} dimensions and decrease with spatial correlation.
 

### 2024-04-24 main.tex
:pencil: Update background

@@
 \begin{abstract}
-	This paper investigates the limit to which a passive \gls{ris} can redistribute the singular values of a point-to-point \gls{mimo} channel.
-	We depart from the widely-adopted diagonal phase shift model to a \gls{bd}-\gls{ris} architecture, which enables {cooperative} wave scattering thanks to in-group connections between elements.
+	This paper investigates how significantly a passive \gls{ris} can redistribute the singular values of a \gls{mimo} point-to-point channel.
+	% the limit to which
+	We depart from the widely-adopted diagonal phase shift model to a \gls{bd}-\gls{ris} architecture featuring in-group connections between elements.
+	% This powerful model allows cooperative wave scattering with both amplitude and phase control, and we uniquely attribute the shaping advantage to subchannel rearrangement and subspace alignment.
+	This powerful model enables cooperative wave scattering with both amplitude and phase control, and we provide unique shaping insights in terms of subchannel rearrangement and subspace alignment.
+	% uniquely explain the extra design freedom from off-diagonal entries as subchannel rearrangement and subspace alignment.
+	% while the shaping advantage from off-diagonal entries is uniquely attributed to subchannel rearrangement and subspace alignment.
 	% An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} on the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
-	The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., degree of freedom and condition number).
+	The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
 	To quantify the shaping capability of diagonal and \gls{bd}-\gls{ris}, we also derive individual and collective singular value bounds for rank-deficient channels and fully-connected \gls{ris} via matrix analysis.
 	% For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
-	Those results help to explain the shaping advantage from off-diagonal entries in terms of subchannel rearrangement and subspace alignment.
+	% We uniquely attribute the shaping advantage from off-diagonal entries to subchannel rearrangement and subspace alignment.
 	% Subchannel rearrangement is a unique feature of off-diagonal entries that allows each group to rearrange and recombine the forward and backward subchannels.
@@
 	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
-	As a side product, we tackle \gls{ris}-aided \gls{mimo} rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-based approach.
-	Simulation results highlight that \gls{bd}-\gls{ris} provides a wider dynamic range and better trade-off on channel singular values, while its power and rate gains over diagonal \gls{ris} scale with \gls{mimo} dimensions.
+	As a side product, we tackle \gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-based approach.
+	Simulation results highlight that \gls{bd}-\gls{ris} provides a wider dynamic range and better trade-off on channel singular values, while its power and rate gains over diagonal \gls{ris} increase with \gls{mimo} dimensions.
 
@@
 	It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
-	The most popular \gls{ris} application is \emph{joint beamforming} design with transceivers, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
-	Since coherent scattering can be decomposed as equal-gain combining and transmission, \gls{ris} elements usually offer a squared asymptotic performance (e.g., second-order array gain and fourth-order power scaling law \cite{Zhao2022}) than transceiver antennas.
-	% However, a large-dimensional \gls{ris} is generally required to compensate the power loss from double fading.
-	On the other hand, \gls{ris} can also be employed for \emph{backscatter modulation} by periodically switching its reflection pattern.
-	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) that can be either integrated into the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or exploited by surrounding low-power devices for energy-efficient uplink communications \cite{Liang2020,Zhao2022a,Yang2024}.
-
-	Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
+	The most popular \gls{ris} research direction is \emph{joint beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
+	While passive beamforming suffers severe attenuation from double fading, it usually offers a squared asymptotic behavior than active beamforming (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
+	On the other hand, \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within channel coherence time.
+	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for passive uplink communication \cite{Liang2020,Zhao2022a,Yang2024}.
+	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment.
+	This provides a ubiquitous wave scattering benchmark for different wireless applications and greatly simplifies the \gls{ris}-transceiver design.
+	Relevant shaping metrics can be classified into two categories:
+	\begin{itemize}
+		\item \emph{Singular value centric:} Closely related to the performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to numerical perturbations.
+The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
+		\item \emph{Power centric:} The second-order statistics are less informative in \gls{mimo} but easier to analyze and optimize.
+The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
+	\end{itemize}
+
+	While those works offer initial glimpses into the channel shaping potential, one critical question remains unaddressed: \emph{To what extent can a passive \gls{ris} reshape the \gls{mimo} channel in terms of singular values?}
+	% \begin{enumerate}
+	% 	\item What is the entire achievable singular value region of a \gls{mimo} channel with \gls{ris}?
+	% \end{enumerate}
+	% they neither discuss the limitation
+	% depict the entire singular value region nor provide a universal optimization framework.
+	% It motivates the ultimate question: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels in terms of singular values?}
+	% Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
 	The answer depends heavily on the scattering model and hardware architecture.
-	Most existing works assumed that each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
-	This ideally translates to a diagonal scattering matrix with unit-magnitude entries, which only controls the phase of the scattered waves but cannot redistribute their amplitude.
-	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} which physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices respectively.}
-	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate losslessly within the circuit and depart partially from any element in the same group.
-	It can thus control both the amplitude and phase of the scattered wave without power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
-	Such a powerful model can be realized at reduced hardware complexity using tree- and forest-connected architectures using graph theory \cite{Nerini2024}.
+	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} assumed that each \gls{ris} element is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
+	This ideally translates to a scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the signal.
+	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} that physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}
+	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
+	It can thus redistribute both amplitude and phase of the scattered wave with zero power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
+	Such a powerful model can be realized at reduced cost using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
 	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
 	Many practical design challenges have been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
-	Its superiority has been studied extensively in \gls{siso} and \gls{miso} systems in terms of single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
-	When it comes to \gls{mimo}, most existing works are limited to very specific scenarios.
-	For example, the authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design under the assumption of unitary \gls{ris} without direct link.
-	Received power maximization problem is extended to \gls{mimo} for continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} scattering matrices, but they only considered single-stream transmission with given precoder and combiner (which is equivalent to \gls{siso}).
-	Transmitter-side \gls{bd}-\gls{ris} design over statistical \gls{csi} has been introduced to massive \gls{mimo} networks for improved spectral efficiency \cite{Mishra2024}, but was again constrained to unitary \gls{ris} without direct link.
+	Its beamforming superiority has been studied extensively in \gls{siso} and \gls{miso} systems in terms of single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} systems is still in the infancy stage.
+	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a specific \gls{bd}-\gls{ris}-aided \gls{mimo} system with blocked direct link and unitary (a.k.a.
+fully-connected) \gls{ris}.
+	Similar constraints were also adopted in \cite{Mishra2024}, which introduces transmitter-side \gls{bd}-\gls{ris} to massive \gls{mimo} for improved spectral efficiency.
+	Received power maximization problem was studied over continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} block-unitary scattering matrices, but the proposed single-stream transceiver is rate-suboptimal and the problem is equivalent to \gls{siso}.
 	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
-	Although the results are insightful, it remains unclear how the off-diagonal entries contribute to channel shaping and whether the relative gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with \gls{mimo} dimensions.
-	% Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
-
-	Channel shaping is different from passive beamforming since the \gls{ris} is exploited as a stand-alone device to modify the inherent properties of the channel itself, instead of optimizing for a specific performance metric.
-	This not only allows one to decouple the joint \gls{ris}-transceiver design, but also unveils the fundamental limits of wave manipulation and provides an all-in-one tool for various wireless applications.
-	Relevant designs can be classified into two categories:
-	\begin{itemize}
-		\item \emph{Singular value centric:} Focus on the singular values of the equivalent channel matrix, which are sensitive to minor perturbations but precisely related to the capacity and diversity-multiplexing trade-off.
-It has been mainly studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
-		\item \emph{Power centric:} Focus on the second-order characteristics of the equivalent channel matrix, which are useful in \gls{siso} and \gls{miso} but less informative in \gls{mimo}.
-It has been mainly studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
-	\end{itemize}
-
-	While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, they neither suggest the achievable singular value region nor address the most general scenario with direct link and arbitrary group size.
-	On the other hand, \gls{bd}-\gls{ris} has been mainly investigated for beamforming and its channel shaping potential in \gls{mimo} has not been fully understood.
+	Although the results are promising, there lacks a study of \gls{bd}-\gls{ris} in general \gls{mimo} systems and its shaping potential over diagonal \gls{ris} has not been fully understood.
+	% remains unclear how the off-diagonal entries contribute to channel shaping and whether the relative gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with \gls{mimo} dimensions.
+	% While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, they neither suggest the achievable singular value region nor address the most general scenario with direct link and arbitrary group size.
+	% On the other hand, \gls{bd}-\gls{ris} has been mainly investigated for beamforming and its channel shaping potential in \gls{mimo} has not been fully understood.
 	% the great potential of \gls{bd}-\gls{ris} (especially in \gls{mimo}) has not been fully understood and an efficient design framework is still missing.
@@
 	The contributions are summarized below.
+
+	% 1. need a general study on BD-RIS x MIMO and explain the potential from off-diagonal entries
+	% 2. need a general optimization framework for BD-RIS
+	% 3. need a comprehensive answer to the channel shaping question
+	% 4. need a low-complexity solution from shaping
 
@@
 		\end{maxi!}
-		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct-less \gls{mimo} with unitary \gls{ris} \eqref{eq:scattering_fc_optimal}.
+		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with unitary \gls{ris} \eqref{eq:scattering_fc_optimal}.
 		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.

### 2024-04-27 main.tex
:pencil: Update contributions

@@
 	The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
-	To quantify the shaping capability of diagonal and \gls{bd}-\gls{ris}, we also derive individual and collective singular value bounds for rank-deficient channels and fully-connected \gls{ris} via matrix analysis.
+	To explore the shaping limits of different \gls{ris} architectures, we also derive individual and collective singular value bounds for rank-deficient channels and fully-connected \gls{ris} via matrix analysis.
 	% For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
@@
 	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
-	As a side product, we tackle \gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-based approach.
-	Simulation results highlight that \gls{bd}-\gls{ris} provides a wider dynamic range and better trade-off on channel singular values, while its power and rate gains over diagonal \gls{ris} increase with \gls{mimo} dimensions.
+	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-inspired approach.
+	Simulation results highlight that \gls{bd}-\gls{ris} significantly improves the dynamic range and trade-off of channel singular values, while its power and rate gains over diagonal \gls{ris} increase with \gls{mimo} dimensions.
 
@@
 	A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
-	It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
+	% It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
+	It enables low-noise, full-duplex operation, and also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
 	The most popular \gls{ris} research direction is \emph{joint beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
@@
 	On the other hand, \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within channel coherence time.
-	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for passive uplink communication \cite{Liang2020,Zhao2022a,Yang2024}.
+	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for low-power uplink communication \cite{Liang2020,Zhao2022a,Yang2024}.
 	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment.
-	This provides a ubiquitous wave scattering benchmark for different wireless applications and greatly simplifies the \gls{ris}-transceiver design.
+	This provides a ubiquitous wave scattering benchmark for different wireless applications and helps to decouple the \gls{ris}-transceiver design.
 	Relevant shaping metrics can be classified into two categories:
@@
 	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} assumed that each \gls{ris} element is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
-	This ideally translates to a scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the signal.
+	This ideally translates to a scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the incoming signal.
 	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} that physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}
@@
 	It can thus redistribute both amplitude and phase of the scattered wave with zero power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
-	Such a powerful model can be realized at reduced cost using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
-	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
+	Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
+	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} to provide full-space coverage and multi-user support.
 	Many practical design challenges have been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
-	Its beamforming superiority has been studied extensively in \gls{siso} and \gls{miso} systems in terms of single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+	Its beamforming superiority has been studied extensively in \gls{siso} and \gls{miso} systems, where the problems were cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
 	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} systems is still in the infancy stage.
@@
 fully-connected) \gls{ris}.
-	Similar constraints were also adopted in \cite{Mishra2024}, which introduces transmitter-side \gls{bd}-\gls{ris} to massive \gls{mimo} for improved spectral efficiency.
-	Received power maximization problem was studied over continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} block-unitary scattering matrices, but the proposed single-stream transceiver is rate-suboptimal and the problem is equivalent to \gls{siso}.
+	Similar constraints were also adopted in \cite{Mishra2024}, which introduces a transmitter-side \gls{bd}-\gls{ris} to massive \gls{mimo} that exploits statistical \gls{csi} for improved spectral efficiency.
+	Received power maximization problem was studied over continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} \gls{bd}-\gls{ris}, but the proposed single-stream transceiver is rate-suboptimal and the passive beamforming problem is equivalent to \gls{siso}.
 	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
-	Although the results are promising, there lacks a study of \gls{bd}-\gls{ris} in general \gls{mimo} systems and its shaping potential over diagonal \gls{ris} has not been fully understood.
-	% remains unclear how the off-diagonal entries contribute to channel shaping and whether the relative gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with \gls{mimo} dimensions.
-	% While the above works offer promising glimpses into the channel shaping potential of passive \gls{ris}, they neither suggest the achievable singular value region nor address the most general scenario with direct link and arbitrary group size.
-	% On the other hand, \gls{bd}-\gls{ris} has been mainly investigated for beamforming and its channel shaping potential in \gls{mimo} has not been fully understood.
-	% the great potential of \gls{bd}-\gls{ris} (especially in \gls{mimo}) has not been fully understood and an efficient design framework is still missing.
+	Although the results are promising, the channel shaping capability from off-diagonal entries deserves further investigation, and there lacks a universal yet efficient \gls{bd}-\gls{ris} design framework.
+	Furthermore, no previous work has attempted to characterize the singular value region of a \gls{mimo} channel manipulated by any type of \gls{ris}, and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
 	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
@@
 
-	First, we demystify the gain from off-diagonal entries of \gls{bd}-\gls{ris} in terms of subchannel rearrangement and subspace alignment.
-	Subchannel rearrangement is a unique feature of cooperative scattering that allows each group to rearrange and recombine the associated forward and backward subchannels.
-	This translates to a higher design flexibility and better shaping capability by exploiting the spatial diversity.
-	On the other hand, phase matching in \gls{siso} generalizes to subspace alignment in \gls{mimo} and introduces a trade-off between the multiplicative backward-forward channel combination and the additive direct-indirect channel combination.
-	As the \gls{mimo} dimensions expand, we show the benefits of \gls{bd}-\gls{ris} in subchannel rearrangement and the limitations of diagonal \gls{ris} in subspace alignment become increasingly apparent.
-	This is the first paper to unveil and interpret the potential of \gls{bd}-\gls{ris} in multi-antenna systems.
-
-	% where the \gls{bd}-\gls{ris} demonstrates a superior control on the multiplicative backward-forward channels and additive direct-indirect channels.
-	% Both potentials
+	First, we discuss the shaping potential from off-diagonal entries of \gls{bd}-\gls{ris} in terms of subchannel rearrangement and subspace alignment.
+	Subchannel rearrangement enables a flexible in-group permutation and combination of backward and forward channels by their strength.
+	This unique feature of \gls{bd}-\gls{ris} provides a higher shaping freedom and exploits spatial diversity more effectively than diagonal \gls{ris}.
+	On the other hand, subspace alignment in \gls{mimo} generalizes phase matching in \gls{siso} and \gls{miso} to the high-dimensional singular vector space.
+	The scattering matrix simultaneously affects the multiplicative intra-group alignment and additive inter-group alignment.
+	However, both subspaces cannot be perfectly aligned at the same time and a balance needs to be struck in between.
+	Increasing \gls{mimo} dimensions highlights the advantage of \gls{bd}-\gls{ris} for subchannel rearrangement while exposing the limitation of diagonal \gls{ris} in subspace alignment.
+	This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems and discuss its shaping potential.
+	% unveil and interpret the potential of \gls{bd}-\gls{ris} in general \gls{mimo} systems.
 
@@
 	Specifically, group-wise multiplicative rotational updates are performed along the geodesics of the Stiefel manifold and compactly evaluated as the exponential map \cite{Edelman1998}.
-	By exploiting the inherent structure of unitary matrices, this method avoids retractions from the Euclidean space and improves the computational efficiency and stability.
+	By exploiting the inherent structure of unitary matrices, this method avoids retractions from the Euclidean space and facilitates the step size selection, which improves the computational efficiency and stability.
 	This is the first work to tailor an efficient and universal optimization framework for \gls{bd}-\gls{ris}.
 
+	% pioneer
 	Third, we quantify the capability of a \gls{bd}-\gls{ris} to redistribute the singular values of a point-to-point \gls{mimo} channel.
@@
 	The resulting achievable singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-	We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected (a.k.a. unitary) \gls{ris}.
-	This is the first work to comprehensively answer the channel shaping capability question from a Pareto perspective.
+	% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and unitary \gls{ris}.
+	To explore the shaping limits of different \gls{ris} architectures, we also derive individual and collective singular value bounds for rank-deficient channels and unitary \gls{ris} via matrix analysis.
+	Results validate those bounds and show that increasing \gls{bd}-\gls{ris} group size significantly enlarges the singular value region, providing wider dynamic range and better trade-off.
+	% dynamic range and trade-off of singular values are significantly improved by \gls{bd}-\gls{ris}, especially in large-scale \gls{mimo} systems.
+	This is the first work to comprehensively answer the channel shaping capability question from both numerical and analytical perspectives in the most general \gls{bd}-\gls{ris} setup.
+	% from a Pareto perspective.
 
@@
 	The former iteratively updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.
-	The latter suboptimally decouples the joint design into a channel power gain maximization subproblem and a conventional \gls{mimo} transmission subproblem, then propose a two-stage solution in closed form.
-	Interestingly, the rate deficit from the latter diminishes as the \gls{ris} evolves from diagonal to unitary.
-	It suggests that channel shaping offers a promising path towards simplified and practical \gls{bd}-\gls{ris} (and transceiver) designs.
+	The latter suboptimally decouples the joint design into a channel power gain maximization subproblem and a conventional \gls{mimo} transmission subproblem, then propose a closed-form two-stage solution.
+	We observe that \gls{bd}-\gls{ris} yields higher channel power and achievable rate than diagonal \gls{ris}, while the relative gains scale with the group size and \gls{mimo} dimensions.
+	% especially with large group sizes and \gls{mimo} dimensions.
+	Moreover, the rate difference between the optimal and shaping-inspired designs diminishes as the \gls{ris} evolves from diagonal to unitary.
+	% Interestingly, the rate difference between the optimal and low-complexity designs diminishes as the \gls{ris} evolves from diagonal to unitary.
+	Those results emphasize the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems and suggest channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
+	% a promising channel shaping path towards practical \gls{ris} and transceiver design.
+	% that channel shaping offers a promising path towards simplified and practical \gls{bd}-
+	% It suggests that channel shaping offers a promising path towards simplified and practical \gls{bd}-\gls{ris} (and transceiver) designs.
 	% via \gls{bd}-\gls{ris} offers a promising path towards simplified and practical design.
@@
 	\begin{itemize}
-		\item \emph{Subchannel rearrangement:} This unique feature of \gls{bd}-\gls{ris} allows each group to rearrange and recombine the backward and forward subchannels by their strength.
-In \gls{siso}, diagonal \gls{ris} with perfect phase matching provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
+		\item \emph{Subchannel rearrangement:} This unique feature of \gls{bd}-\gls{ris} exploits the spatial diversity by rearranging and combining the backward and forward channel branches within each group.
+In \gls{siso}, diagonal \gls{ris} with perfect phase matching provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
 		Note the first summation is over groups and the second summation is over permuted subchannels.
-		By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels within each group.
+		By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
+		% , providing up to \qty{62.5}{\percent} asymptotic power gain over diagonal \gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
 		Since the number of subchannels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions,
@@
 		\end{equation}
-		where $\lambda_n^{\dot{N}}$ is the $n$-th eigenvalue of the complex $\dot{N} \times \dot{N}$ Wishart matrix with probability density function $f_{\lambda_n^{\dot{N}}}(x_n)$ given by \cite[Equation 51]{Zanella2009}.
+		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(x_n)$ given by \cite[Equation 51]{Zanella2009}.
 		We notice \eqref{eq:power_gain_rayleigh} is a generalization of \cite[Equation 58]{Shen2020a} to \gls{mimo}.
@@
 \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris}.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of cooperative wave scattering.
 		\end{subsubsection}

### 2024-05-01 main.tex
:sparkles: Add complexity analysis

@@
 	% \begin{enumerate}
-	% 	\item What is the entire achievable singular value region of a \gls{mimo} channel with \gls{ris}?
+	% 	\item What is the entire singular value region of a \gls{mimo} channel with \gls{ris}?
 	% \end{enumerate}
@@
 	This problem is solved by the proposed geodesic \gls{rcg} algorithm.
-	The resulting achievable singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
 	% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and unitary \gls{ris}.
@@
 			\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{R},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.
+			% $\mathcal{O}(2 L^3)$
 			\label{eq:gradient_translated}
@@
 						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
-							\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
+							\State $\mathbf{D}_g^{(r)} \gets \tilde{\nabla}_{\mathrm{R},g}^{(r)}$
 						\EndIf
@@
 						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic_translated}
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
+						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
 							\State $\mu \gets 2 \mu$
@@
 							\State $\mu \gets \mu / 2$
-						\EndWhile
+						\EndWhile \label{ln:armijo_end}
 						\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:update_geodesic}
@@
 		Algorithm~\ref{ag:rcg} summarizes the proposed \gls{bd}-\gls{ris} design framework based on group-wise geodesic \gls{rcg}.
-		Compared to the non-geodesic approach, our method leverages the properties of unitary group to replace the add-then-retract update \eqref{eq:add_then_retract} with a multiplicative rotational update \eqref{eq:update_geodesic} along the geodesic.
-		This leads to faster convergence and simplifies the step size tuning thanks to an appropriate parameter space.
-
-		Both approaches can be performed in parallel for all groups to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
-		Since block-unitary matrices are also closed under multiplication, one can avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the block diagonal and nulling the other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, at the cost of higher computational complexity and slower convergence.
+		Compared to the non-geodesic approach, it leverages the Lie group properties to replace the add-then-retract update \eqref{eq:add_then_retract} with a multiplicative rotational update \eqref{eq:update_geodesic} along the geodesic.
+		This leads to faster convergence and simplifies the step size tuning thanks to appropriate parameter space.
+		% Despite the difference in
+		Convergence to a local optimum is still guaranteed if not initialized at a stationary point.
+		Note that the group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
+		Since block-unitary matrices are also closed under multiplication, one can avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the block diagonal and nulling the other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, with potentially higher computational complexity and slower convergence.
 	\end{subsection}
@@
 		where $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ is the maximum channel rank, and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
-		Varying $\{\rho_n\}_{n \in \mathcal{N}}$ characterizes the Pareto frontier that encloses the entire achievable singular value region.
-		Thus, we claim the singular value Pareto problem \eqref{op:pareto} generalizes most relevant channel shaping problems.
-		It can be solved by the proposed group-wise geodesic \gls{rcg} method with the following gradient expression.
+		Varying $\{\rho_n\}_{n \in \mathcal{N}}$ characterizes the Pareto frontier that encloses the entire singular value region.
+		Thus, we claim problem \eqref{op:pareto} generalizes most singular value shaping problems.
+		It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given by Lemma \ref{lm:pareto_gradient}.
+		% It can be solved optimally by Algorithm~\ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses the following Euclidean gradient expression \eqref{eq:pareto_gradient}.
 
@@
 			\end{equation}
-			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}$, respectively.
+			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
 		\end{lemma}
@@
 
-		Algorithm~\ref{ag:rcg} can thus be invoked for problem \eqref{op:pareto} where line \ref{ln:gradient_euclidean} uses \eqref{eq:pareto_gradient} explicitly.
-		With proper initialization, it is guaranteed to converge to (at least local) optimal points.
+		We then analyze the computational complexity of solving Pareto singular value problem \eqref{op:pareto} by Algorithm~\ref{ag:rcg}.
+		To update each \gls{bd}-\gls{ris} group, compact \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:pareto_gradient} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_translated} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:parameter_cg_geodesic} and conjugate direction \eqref{eq:direction_cg_geodesic} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:update_geodesic} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
+		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (line \ref{ln:armijo_start}--\ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
 	\end{subsection}
@@
 		\end{equation}
-		where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
+		where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right compact singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
 		We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid unitary \gls{ris} solutions to \eqref{op:power_passive} when the direct link is absent and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
@@
 			\end{equation}
-			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
+			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrices of
 			\begin{equation}
@@
 		\end{proof}
+
+		We then analyze the computational complexity of solving channel gain maximization problem \eqref{op:power_passive} by Proposition \ref{pp:power}.
+		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_matrix_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its compact \gls{svd} requires $\mathcal{O}(L^3)$ operations.
+		The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
 	\end{subsection}
@@
 			where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
+			Problem \eqref{op:rate_passive} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given by Lemma \ref{lm:rate_gradient}.
 			\begin{lemma}\label{lm:rate_gradient}
@@
 			\end{proof}
-			Algorithm \ref{ag:rcg} can thus be invoked for problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
-			Since \eqref{ob:rate_passive} is a concave function of $\mathbf{\Theta}$, convergence to (at least local) optimal points is guaranteed.
 			For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
@@
 			where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation obtainable by the iterative method \cite{Tse2005}.
-			The overall \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
+
+			The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
+			Similar to the analysis in Section \ref{sc:pareto_frontier}, the computational complexity of solving subproblem \eqref{op:rate_passive} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
+			On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder_eigenmode} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+			The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
 		\end{subsubsection}
@@
 			We then propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
-			The idea is to first consider channel shaping and replace the rate maximization problem \eqref{op:rate_passive} by channel power gain maximization problem \eqref{op:power_passive}, then proceed to conventional eigenmode transmission \eqref{eq:precoder_eigenmode}.
-			Both steps are solved in closed form and the computational complexity is significantly reduced.
+			The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_passive} by channel power gain maximization problem \eqref{op:power_passive}, then proceed to conventional eigenmode transmission \eqref{eq:precoder_eigenmode}.
+			Both steps are solved in closed form and the computational complexity is $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr) + N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+			While suboptimal, this shaping-inspired solution avoids outer iterations and implements inner iterations more efficiently.
 		\end{subsubsection}
@@
 			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
-			This transformation not only provides a better trade-off in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
-			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
+			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
+			It suggests the design freedom from larger group size allows better alignment of multiple subspaces simultaneously.
+			% not only provides a better trade-off in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
+			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
 			In particular, Fig.

### 2024-05-01 main.tex
:construction: Update library

@@
 	On the other hand, \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within channel coherence time.
-	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for low-power uplink communication \cite{Liang2020,Zhao2022a,Yang2024}.
+	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
 	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment.
@@
 
-	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization problem with two beamforming solutions: a local-optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
+	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} \gls{pc} achievable rate maximization problem with two beamforming solutions: a local-optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
 	The former iteratively updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.

### 2024-05-13 main.tex
:triangular_flag_on_post: Hongyu 240513

@@
 \begin{abstract}
-	This paper investigates how significantly a passive \gls{ris} can redistribute the singular values of a \gls{mimo} point-to-point channel.
+	This paper investigates to what extent a passive \gls{ris} can redistribute the singular values of a \gls{mimo} point-to-point channel.
 	% the limit to which
-	We depart from the widely-adopted diagonal phase shift model to a \gls{bd}-\gls{ris} architecture featuring in-group connections between elements.
-	% This powerful model allows cooperative wave scattering with both amplitude and phase control, and we uniquely attribute the shaping advantage to subchannel rearrangement and subspace alignment.
-	This powerful model enables cooperative wave scattering with both amplitude and phase control, and we provide unique shaping insights in terms of subchannel rearrangement and subspace alignment.
-	% uniquely explain the extra design freedom from off-diagonal entries as subchannel rearrangement and subspace alignment.
-	% while the shaping advantage from off-diagonal entries is uniquely attributed to subchannel rearrangement and subspace alignment.
+	We depart from the widely-adopted diagonal phase shift model to a \gls{bd}-\gls{ris} architecture featuring in-group connections between elements, which enables cooperative wave scattering with amplitude and phase control.
+	% This powerful model allows cooperative wave scattering with both amplitude and phase control, and we uniquely attribute the shaping advantage to channel rearrangement and space alignment.
+	% This powerful model enables cooperative wave scattering with both amplitude and phase control, and we provide unique shaping insights in terms of channel rearrangement and space alignment.
+	% uniquely explain the extra design freedom from off-diagonal entries as channel rearrangement and space alignment.
+	% while the shaping advantage from off-diagonal entries is uniquely attributed to channel rearrangement and space alignment.
 	% An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} on the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
-	The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
-	To explore the shaping limits of different \gls{ris} architectures, we also derive individual and collective singular value bounds for rank-deficient channels and fully-connected \gls{ris} via matrix analysis.
+	% The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
+	Specifically, we first provide unique shaping insights by characterizing the Pareto frontiers of channel singular values via a novel geodesic manifold optimization.
+	The resulting region comprehensively encapsulates most relevant metrics (e.g., spectral norm and condition number).
+	To explore the shaping limits of passive \gls{bd}-\gls{ris}, we also derive individual and collective singular value bounds respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris} via matrix analysis.
 	% For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
-	% We uniquely attribute the shaping advantage from off-diagonal entries to subchannel rearrangement and subspace alignment.
-	% Subchannel rearrangement is a unique feature of off-diagonal entries that allows each group to rearrange and recombine the forward and backward subchannels.
-	% Subspace alignment generalizes phase matching in \gls{siso} and introduces a trade-off between multiplicative backward-forward and additive direct-indirect channel combinations.
+	% We uniquely attribute the shaping advantage from off-diagonal entries to channel rearrangement and space alignment.
+	% Channel rearrangement is a unique feature of off-diagonal entries that allows each group to rearrange and recombine the forward and backward channels.
+	% Space alignment generalizes phase matching in \gls{siso} and introduces a trade-off between multiplicative backward-forward and additive direct-indirect channel combinations.
 	% Those channel shaping designs have two major implications.
-	% First, they demystify the performance gain from off-diagonal entries in terms of {subchannel rearrangement} and {subspace alignment}.
-	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment.
+	% First, they demystify the performance gain from off-diagonal entries in terms of {channel rearrangement} and {space alignment}.
+	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in channel rearrangement and space alignment.
 	% Second, they inspire a two-stage suboptimal solution that decouples joint active and passive beamforming design.
@@
 	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-inspired approach.
-	Simulation results highlight that \gls{bd}-\gls{ris} significantly improves the dynamic range and trade-off of channel singular values, while its power and rate gains over diagonal \gls{ris} increase with \gls{mimo} dimensions.
+	Simulation results highlight that \gls{bd}-\gls{ris} significantly improves the dynamic range of and trade-off between channel singular values.
+	Results also show the power and rate gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} increase with \gls{mimo} dimensions.
 
@@
 	% (i) , and (ii) the gap between the two approaches vanishes as \gls{bd}-\gls{ris} evolves from diagonal to unitary.
-	% not only demystify the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment, but also decouple the joint \gls{ris}-transceiver optimization.
-	% Those channel shaping designs not only demystify the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement and subspace alignment, but also decouple the joint \gls{ris}-transceiver optimization.
+	% not only demystify the advantage of \gls{bd}-\gls{ris} in channel rearrangement and space alignment, but also decouple the joint \gls{ris}-transceiver optimization.
+	% Those channel shaping designs not only demystify the advantage of \gls{bd}-\gls{ris} in channel rearrangement and space alignment, but also decouple the joint \gls{ris}-transceiver optimization.
 
@@
 	% % A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved in closed form iteratively.
-	% Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions, stemming from stronger subchannel rearrangement and subspace alignment capabilities.
+	% Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions, stemming from stronger channel rearrangement and space alignment capabilities.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Reconfigurable intelligent surface, multi-input multi-output, manifold optimization, channel shaping, rate maximization.
+	Beyond diagonal reconfigurable intelligent surface, multi-input multi-output, manifold optimization, channel shaping, rate maximization.
 \end{IEEEkeywords}
@@
 	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
-	This is empowered by the recent advances in \gls{ris}, a programmable metasurface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
+	This is empowered by the recent advances in \gls{ris}, a programmable passive planar surface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
 	A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
 	% It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
-	It enables low-noise, full-duplex operation, and also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
-	The most popular \gls{ris} research direction is \emph{joint beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
-	While passive beamforming suffers severe attenuation from double fading, it usually offers a squared asymptotic behavior than active beamforming (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
-	On the other hand, \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within channel coherence time.
+	It enables low-noise, full-duplex operation, and also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional \gls{mimo} systems.
+	The most popular \gls{ris} research direction is \emph{joint passive and active beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
+	While passive beamforming at \gls{ris} suffers severe attenuation from double fading, it usually offers a squared asymptotic behavior than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
+	On the other hand, \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within the channel coherence time.
 	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
-	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment.
-	This provides a ubiquitous wave scattering benchmark for different wireless applications and helps to decouple the \gls{ris}-transceiver design.
-	Relevant shaping metrics can be classified into two categories:
+	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the wireless.
+	To name a few, it can compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for \gls{mimo} systems \cite{Ozdogan2020a}, and create artificial time diversity for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple accesses.
+	Channel shaping also provides a ubiquitous benchmark for different wireless applications and helps to decouple the \gls{ris}-transceiver design.
+	At a specific time and frequency, channel statistics can be roughly classified into two categories:
+	% shaping metrics can be classified into two categories:
 	\begin{itemize}
-		\item \emph{Singular value centric:} Closely related to the performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to numerical perturbations.
+		\item \emph{Singular value:} Those metrics are in general closely related to the performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to numerical perturbations of the channel matrix.
 The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
-		\item \emph{Power centric:} The second-order statistics are less informative in \gls{mimo} but easier to analyze and optimize.
+		\item \emph{Power:} Those second-order statistics are less informative in \gls{mimo} but easier to analyze and optimize.
 The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
@@
 
-	While those works offer initial glimpses into the channel shaping potential, one critical question remains unaddressed: \emph{To what extent can a passive \gls{ris} reshape the \gls{mimo} channel in terms of singular values?}
+	Although those works offer initial glimpses into the channel shaping potential, one critical question remains unaddressed: \emph{To what extent can a passive \gls{ris} reshape the \gls{mimo} channel in terms of singular values?}
 	% \begin{enumerate}
@@
 	% Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
-	The answer depends heavily on the scattering model and hardware architecture.
-	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} assumed that each \gls{ris} element is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
-	This ideally translates to a scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the incoming signal.
-	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} that physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}
+	The answer depends heavily on the hardware architecture of \gls{ris} and its scattering model.
+	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} follows a conventional path where each \gls{ris} element is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
+	This simple architecture translates mathematically to a diagonal scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the incoming signal.
+	The concept was soon generalized to \gls{bd}-\gls{ris} with a group-connected architecture \cite{Shen2020a} that groups adjacent elements and connects them via passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}
 	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
@@
 	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} to provide full-space coverage and multi-user support.
-	Many practical design challenges have been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
-	Its beamforming superiority has been studied extensively in \gls{siso} and \gls{miso} systems, where the problems were cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+	Many practical design challenges of \gls{bd}-\gls{ris} have also been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
+	From the beamforming perspective, the superiority of \gls{bd}-\gls{ris} over diagonal \gls{ris} has been studied extensively in \gls{siso} and \gls{miso} systems, where the problems were cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
 	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} systems is still in the infancy stage.
@@
 	Received power maximization problem was studied over continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} \gls{bd}-\gls{ris}, but the proposed single-stream transceiver is rate-suboptimal and the passive beamforming problem is equivalent to \gls{siso}.
-	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
-	Although the results are promising, the channel shaping capability from off-diagonal entries deserves further investigation, and there lacks a universal yet efficient \gls{bd}-\gls{ris} design framework.
+	% A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
+	% Although the results are promising, the channel shaping capability from off-diagonal entries deserves further investigation, and there lacks a universal yet efficient \gls{bd}-\gls{ris} design framework.
+	Although the results are promising, the channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
 	Furthermore, no previous work has attempted to characterize the singular value region of a \gls{mimo} channel manipulated by any type of \gls{ris}, and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
-	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
+	This paper aims for a comprehensive answer to the channel shaping capability of \gls{bd}-\gls{ris} through theoretical analysis and numerical optimization.
 	The contributions are summarized below.
@@
 
-	First, we discuss the shaping potential from off-diagonal entries of \gls{bd}-\gls{ris} in terms of subchannel rearrangement and subspace alignment.
-	Subchannel rearrangement enables a flexible in-group permutation and combination of backward and forward channels by their strength.
-	This unique feature of \gls{bd}-\gls{ris} provides a higher shaping freedom and exploits spatial diversity more effectively than diagonal \gls{ris}.
-	On the other hand, subspace alignment in \gls{mimo} generalizes phase matching in \gls{siso} and \gls{miso} to the high-dimensional singular vector space.
-	The scattering matrix simultaneously affects the multiplicative intra-group alignment and additive inter-group alignment.
-	However, both subspaces cannot be perfectly aligned at the same time and a balance needs to be struck in between.
-	Increasing \gls{mimo} dimensions highlights the advantage of \gls{bd}-\gls{ris} for subchannel rearrangement while exposing the limitation of diagonal \gls{ris} in subspace alignment.
-	This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems and discuss its shaping potential.
-	% unveil and interpret the potential of \gls{bd}-\gls{ris} in general \gls{mimo} systems.
-
-	Second, we exploit the Riemannian geometry of the Stiefel manifold and propose an efficient \gls{bd}-\gls{ris} design framework based on geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
-	This method modified from \cite{Abrudan2008,Abrudan2009} not only provides better objective value and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also works for arbitrary group size and any smooth optimization problem.
-	Specifically, group-wise multiplicative rotational updates are performed along the geodesics of the Stiefel manifold and compactly evaluated as the exponential map \cite{Edelman1998}.
-	By exploiting the inherent structure of unitary matrices, this method avoids retractions from the Euclidean space and facilitates the step size selection, which improves the computational efficiency and stability.
+	First, we interpret the channel shaping potential of \gls{bd}-\gls{ris} in terms of channel rearrangement and space alignment.
+	Channel rearrangement refers to rearrange and recombine the forward and backward channel branches by their strength.
+	Space alignment generalizes phase matching in \gls{siso} and \gls{miso} to the high-dimensional singular vector space in \gls{mimo}.
+	The off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix provides a higher design freedom and exploits spatial diversity more effectively than diagonal \gls{ris}.
+	This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems.
+	%  and discuss its shaping potential.
+
+	Second, we propose an efficient \gls{bd}-\gls{ris} design framework based on geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
+	% to numerically analyze the channel shaping capability of \gls{bd}-\gls{ris}, we exploit the Riemannian geometry of the Stiefel manifold and
+	This method modified from \cite{Abrudan2008,Abrudan2009} exploits the Riemannian geometry of the Stiefel manifold, which not only converges faster than non-geodesic approach \cite{Absil2009,Pan2022d} but also works for general optimization problems of group-connected \gls{bd}-\gls{ris}.
+	Specifically, group-wise multiplicative updates are performed along the geodesics to avoid retraction and facilitate step size selection.
+	It greatly improves computational efficiency and stability.
 	This is the first work to tailor an efficient and universal optimization framework for \gls{bd}-\gls{ris}.
@@
 	% pioneer
-	Third, we quantify the capability of a \gls{bd}-\gls{ris} to redistribute the singular values of a point-to-point \gls{mimo} channel.
-	The {Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
-	This problem is solved by the proposed geodesic \gls{rcg} algorithm.
-	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	Third, we adopt the proposed geodesic \gls{rcg} and provide a numerical answer to the singular value shaping question.
+	% to answer the channel singular value shaping question via numerical optimization.
+	% to redistribute the singular values of a point-to-point \gls{mimo} channel.
+	The {Pareto frontiers} of channel singular values are characterized by solving a series of weighted sum maximization problems, where the weight associated with each singular value can be positive, zero, or negative.
+	% optimizing their weighted sum, where the weights can be positive, zero, or negative.
+	% This problem is solved by the proposed geodesic \gls{rcg} algorithm.
+	The enclosed region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	Results show that increasing \gls{bd}-\gls{ris} group size enlarges the singular value region, improving both dynamic range of and trade-off between singular values.
+	% , where the dynamic range and trade-off between are both improved.
+	% significantly enlarges the singular value region, improveing the dynamic range and trade-off in-between.
 	% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and unitary \gls{ris}.
-	To explore the shaping limits of different \gls{ris} architectures, we also derive individual and collective singular value bounds for rank-deficient channels and unitary \gls{ris} via matrix analysis.
-	Results validate those bounds and show that increasing \gls{bd}-\gls{ris} group size significantly enlarges the singular value region, providing wider dynamic range and better trade-off.
+
+	Fourth, we leverage matrix analysis tools and provide an analytical answer to the singular value shaping question.
+	% revisit the channel singular value shaping problem from an analytical perspective via matrix analysis.
+	% To explore the ultimate shaping limits, we derive individual and collective singular value bounds for rank-deficient forward/backward channel and blocked direct channel.
+	% Asymptotic bounds shared by diagonal and \gls{bd}-\gls{ris} are derived in the former case, while exact bounds for unitary \gls{bd}-\gls{ris} are derived in the latter case.
+	Asymptotic channel singular value bounds shared by diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient forward/backward channel.
+	On the other hand, attainable bounds in the presence of unitary \gls{bd}-\gls{ris} are derived for blocked direct channel.
+	Results validate those bounds and emphasizes the shaping advantage of \gls{bd}-\gls{ris}.
+	This is the first work to quantify the singular value redistribution capability from either numerical or analytical perspective.
+	% Results validate those bounds and show that
+	% fully-connected \gls{bd}-\gls{ris} without direct link.
+
+	% In the rank-deficient scenario, we show that the asymptotic performace
+
+	% % respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris}
+	% collective singular value bounds	for rank-deficient channels and unitary \gls{ris}, respectively.
+	% 	Results validate those bounds and show
+	% for rank-deficient channels and unitary \gls{ris}, respectively.
+	% Results validate those bounds and show that increasing \gls{bd}-\gls{ris} group size significantly enlarges the singular value region, providing wider dynamic range and better trade-off.
 	% dynamic range and trade-off of singular values are significantly improved by \gls{bd}-\gls{ris}, especially in large-scale \gls{mimo} systems.
-	This is the first work to comprehensively answer the channel shaping capability question from both numerical and analytical perspectives in the most general \gls{bd}-\gls{ris} setup.
+	% This is the first work to comprehensively answer the channel shaping capability question from both numerical and analytical perspectives in the most general \gls{bd}-\gls{ris} setup.
 	% from a Pareto perspective.
 
-	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} \gls{pc} achievable rate maximization problem with two beamforming solutions: a local-optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
-	The former iteratively updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.
-	The latter suboptimally decouples the joint design into a channel power gain maximization subproblem and a conventional \gls{mimo} transmission subproblem, then propose a closed-form two-stage solution.
-	We observe that \gls{bd}-\gls{ris} yields higher channel power and achievable rate than diagonal \gls{ris}, while the relative gains scale with the group size and \gls{mimo} dimensions.
-	% especially with large group sizes and \gls{mimo} dimensions.
-	Moreover, the rate difference between the optimal and shaping-inspired designs diminishes as the \gls{ris} evolves from diagonal to unitary.
+	Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by two beamforming solutions: a local-optimal \gls{ao} approach and a low-complexity approach inspired by channel shaping insights.
+	The former updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.
+	The latter suboptimally decouples the problem as channel power gain maximization at \gls{ris} and conventional \gls{mimo} transmission at transceiver, then solves both in closed form.
+	% The problem is solved by a closed-form two-stage method.
+	Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than diagonal \gls{ris}, and the rate gap between two approaches diminishes as the \gls{ris} evolves from diagonal to unitary.
+	It suggests channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
 	% Interestingly, the rate difference between the optimal and low-complexity designs diminishes as the \gls{ris} evolves from diagonal to unitary.
-	Those results emphasize the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems and suggest channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
+	% Those results emphasize the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems and suggest channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
 	% a promising channel shaping path towards practical \gls{ris} and transceiver design.
@@
 	% In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
-	% The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
+	% The superiority stems from stronger \emph{channel rearrangement} and \emph{space alignment} capabilities empowered by in-group cooperation.
 	% It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
@@
 	Note that diagonal and unitary \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
-	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
-3]{Shen2020a}, \cite[Fig.
-5]{Li2023c}, and \cite[Fig.
-2]{Nerini2024}, where the radiation pattern and circuit topology need to be modelled in the scattering matrix.
+	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2024}, where the
+	% radiation pattern and
+	circuit topology need to be modelled in the scattering matrix.
 
@@
 	\end{equation}
-	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g{-}1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
+	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels for \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
 	Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via \gls{bd}-\gls{ris} group $g$.
@@
 	By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
+	% Channel rearrangement refers to rearrange and recombine the forward and backward channel branches by their strength.
+	% Space alignment generalizes phase matching in \gls{siso} and \gls{miso} to the high-dimensional singular vector space in \gls{mimo}.
 	\begin{itemize}
-		\item \emph{Subchannel rearrangement:} This unique feature of \gls{bd}-\gls{ris} exploits the spatial diversity by rearranging and combining the backward and forward channel branches within each group.
+		\item \emph{Channel rearrangement:} It refers to rearrange and recombine the backward and forward channel branches associated with each group by their strength.
+		This unique feature of \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
+		% This unique feature of \gls{bd}-\gls{ris} exploits the spatial diversity by rearranging and combining the backward and forward channel branches within each group.
 		In \gls{siso}, diagonal \gls{ris} with perfect phase matching provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-		Note the first summation is over groups and the second summation is over permuted subchannels.
+		Note the first summation is over groups and the second summation is over permuted channels.
 		By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
 		% , providing up to \qty{62.5}{\percent} asymptotic power gain over diagonal \gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
-		Since the number of subchannels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions,
-		\item \emph{Subspace alignment:} Each group can align the singular vectors of the associated backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
-In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ that maximizes the channel gain is
+		Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.
+		\item \emph{Space alignment:} It refers to align the direct, forward, and backward channels by their singular vectors.
+		The \gls{bd}-\gls{ris} needs to strike a balance between the alignment of backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
+In \gls{siso}, space alignment boils down to phase matching and the optimal scattering matrix of group $g$ that maximizes the channel gain is
 		\begin{equation}
@@
 		When it comes to \gls{mimo}, each individual scattering element can only apply a common phase shift to the ``pinhole'' indirect channel $\mathbf{H}_g \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ passing through itself.
-		That is, the disadvantage of diagonal \gls{ris} in subspace alignment scales with \gls{mimo} dimensions.
-		As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward subspaces.
+		That is, the disadvantage of diagonal \gls{ris} in space alignment scales with \gls{mimo} dimensions.
+		% As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward spaces.
 	\end{itemize}
@@
 	% \end{equation}
-	% subspace alignment boils down to phase matching
+	% space alignment boils down to phase matching
 
@@
 	% Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
-	% This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-	% That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
+	% This is because space alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
+	% That is, diagonal \gls{ris} is sufficient for space alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from channel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
 	% Now consider a diagonal \gls{ris} in \gls{mimo}.
 	% Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-	% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
-	% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
+	% Therefore, perfect space alignment of indirect channels through different elements is generally impossible.
+	% It means the disadvantage of diagonal \gls{ris} in space alignment and channel rearrangement scales with \gls{mimo} dimensions.
 	% We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
@@
 	% \end{equation}
-	% which involves three subspace alignment problems:
-	% which involves three subspace alignment problems
+	% which involves three space alignment problems:
+	% which involves three space alignment problems
 	% \begin{equation}
@@
 	% 	\begin{itemize}
-	% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-	% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
+	% 		\item space alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
+	% 		\item channel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the channels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
 	% 	\end{itemize}
@@
 The former will be discussed in the next subsection.
-			\item \emph{Reactance matrix $\mathbf{X}$:} This approach is often exploited for symmetric architectures where every pair of elements in the same group are connected by capacitors and inductors.
+			\item \emph{Reactance matrix $\mathbf{X}$:\footnote{Similar design over susceptance matrix $\mathbf{B}$ can be found in \cite{Nerini2024}.}} This approach is often exploited for symmetric architectures where every pair of elements in the same group are connected by capacitors and inductors.
 According to network theory \cite{Pozar2011}, it maps to the scattering matrix by $\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I})$, which formulates an unconstrained optimization problem on the upper triangular entries of $\{\mathbf{X}_g\}_{g \in \mathcal{G}}$ that is solvable by quasi-Newton methods \cite{Shen2020a}.
@@
 
-		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transported along the curve.
+		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
 		The above method is called non-geodesic since the points are updated in the linear embedding spaces of the manifold by addition and retraction, instead of on the Stiefel manifold itself.
@@
 \begin{section}{Channel Singular Values Redistribution}
+	In this section, we first provide a toy example to illustrate the channel shaping advantage of \gls{bd}-\gls{ris} architecture.
+	Next, we numerically characterize the channel singular value region based on the proposed Algorithm \ref{ag:rcg}.
+	Finally, we derive some analytical singular value bounds in specific scenarios.
 	\begin{subsection}{Toy Example}\label{sc:toy_example}
@@
 		% 	\end{equation}
-		% 	When $k = N$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels
+		% 	When $k = N$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward channels
 		% 	\begin{equation}
@@
 		\begin{corollary}[Upper bound on the channel power gain\label{co:sum_power}]
-			% The channel power gain is upper bounded by the sum of sorted element-wise power product of backward and forward subchannels
-			The channel power gain is upper bounded by the sum of sorted element-wise product of squared singular values of backward and forward subchannels
+			% The channel power gain is upper bounded by the sum of sorted element-wise power product of backward and forward channels
+			The channel power gain is upper bounded by the sum of sorted element-wise product of squared singular values of backward and forward channels
 			\begin{equation}
@@
 
-		To achieve the equalities in Corollaries \eqref{co:sv_largest} -- \eqref{co:sum_power}, the \gls{ris} needs to completely align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		To achieve the equalities in Corollaries \eqref{co:sv_largest} -- \eqref{co:sum_power}, the \gls{ris} needs to completely align the spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
 		The resulting scattering matrix is generally required to be unitary
@@
 		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with unitary \gls{ris} \eqref{eq:scattering_fc_optimal}.
-		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
+		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative space alignments.
 		Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
@@
 		It is observed that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (up to 3$\times$) lower number of iterations and shorter (up to 4$\times$) computational time than the non-geodesic method.
-		The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially in large-scale \gls{bd}-\gls{ris} design problems.
-		If the scattering matrix is constrained to be symmetric, one can project the solution to the feasible domain by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.
+		The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially in large-scale \gls{bd}-\gls{ris} design problems.\footnote{If the scattering matrix is constrained to be symmetric, one can project the solution to the feasible domain by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.}
 	\end{subsection}
@@
 			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
-			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two subspaces.
+			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two spaces.
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
@@
 			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
-			It suggests the design freedom from larger group size allows better alignment of multiple subspaces simultaneously.
-			% not only provides a better trade-off in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
+			It suggests the design freedom from larger group size allows better alignment of multiple spaces simultaneously.
+			% not only provides a better trade-off in channel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
 			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
@@
 					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
-					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward subchannels.
+					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward channels.
 				}
@@
 			Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
-			This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement.
+			This is because space alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
+			That is, diagonal \gls{ris} is sufficient for space alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from channel rearrangement.
 			Now consider a diagonal \gls{ris} in \gls{mimo}.
 			Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-			Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
-			It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
+			Therefore, perfect space alignment of indirect channels through different elements is generally impossible.
+			It means the disadvantage of diagonal \gls{ris} in space alignment and channel rearrangement scales with \gls{mimo} dimensions.
 			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
@@
 \ref{fg:power_sx_txrx16_nd}.
-		% This again credits to the superior subspace alignment capability of \gls{bd}-\gls{ris}.
-		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the subspace alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
+		% This again credits to the superior space alignment capability of \gls{bd}-\gls{ris}.
+		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the space alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
 		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
@@
 		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
-		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better trade-off between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
+		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better trade-off between channels (c.f. Fig. \ref{fg:singular_pareto}).
 		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
@@
 	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and unitary scenarios.
-	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers better objective value and faster convergence than existing methods.
+	Specifically, the former is done by proposing an efficient \gls{rcg} algorithm for smooth \gls{bd}-\gls{ris} optimization problems, which offers better objective value and faster convergence than existing methods.
 	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
-	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior subspace alignment and subchannel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
+	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior space alignment and channel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
 
@@
 	Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
-	Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward subspaces simultaneously.
+	Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward spaces simultaneously.
 	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.

### 2024-05-14 main.tex
:triangular_flag_on_post: Bruno 240514

@@
 \usepackage{cite}
-\usepackage{fixmath}
+% \usepackage{fixmath}
 \usepackage[acronym]{glossaries-extra}
@@
 \begin{document}
-\title{Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal Model to Beyond}
+\title{Channel Shaping Using Beyond Diagonal Reconfigurable Intelligent Surfaces}
 \author{
@@
 	The most popular \gls{ris} research direction is \emph{joint passive and active beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
-	While passive beamforming at \gls{ris} suffers severe attenuation from double fading, it usually offers a squared asymptotic behavior than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
-	On the other hand, \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within the channel coherence time.
+	While passive beamforming at \gls{ris} suffers severe attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
+	Another feature is that \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within the channel coherence time.
 	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
-	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the wireless.
+	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment.
 	To name a few, it can compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for \gls{mimo} systems \cite{Ozdogan2020a}, and create artificial time diversity for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple accesses.
-	Channel shaping also provides a ubiquitous benchmark for different wireless applications and helps to decouple the \gls{ris}-transceiver design.
-	At a specific time and frequency, channel statistics can be roughly classified into two categories:
+	Channel shaping also provides a ubiquitous benchmark for different wireless applications and helps to decouple the \gls{ris}-transceiver design in a shape-then-transmit manner.
+	At a specific time and frequency, channel metrics can be roughly classified into two categories:
 	% shaping metrics can be classified into two categories:
 	\begin{itemize}
-		\item \emph{Singular value:} Those metrics are in general closely related to the performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to numerical perturbations of the channel matrix.
+		\item \emph{Singular value:} Relevant metrics are in general closely related to the performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to numerical perturbations of the channel matrix.
 The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
-		\item \emph{Power:} Those second-order statistics are less informative in \gls{mimo} but easier to analyze and optimize.
+		\item \emph{Power:} Second-order statistics are less informative in \gls{mimo} but easier to analyze and optimize.
 The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
@@
 
-	Although those works offer initial glimpses into the channel shaping potential, one critical question remains unaddressed: \emph{To what extent can a passive \gls{ris} reshape the \gls{mimo} channel in terms of singular values?}
+	Although those works offer initial glimpses into the channel shaping potential, one critical question has not been fully addressed: \emph{What is the ultimate channel shaping capability of a passive \gls{ris} in terms of singular values?}
 	% \begin{enumerate}
@@
 	The answer depends heavily on the hardware architecture of \gls{ris} and its scattering model.
-	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} follows a conventional path where each \gls{ris} element is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
-	This simple architecture translates mathematically to a diagonal scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the incoming signal.
-	The concept was soon generalized to \gls{bd}-\gls{ris} with a group-connected architecture \cite{Shen2020a} that groups adjacent elements and connects them via passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}
-	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
+	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} considered a diagonal \gls{ris} model where each element is connected to a dedicated impedance and is disconnected from others, such that wave impinging on one element is entirely reflected by the same element.
+	% is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
+	This simple architecture mathematically translates to a diagonal scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the incoming signal.
+	The concept was soon generalized to \gls{bd}-\gls{ris} with a group-connected architecture \cite{Shen2020a} that groups adjacent elements and connects them via passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}
+	This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
 	It can thus redistribute both amplitude and phase of the scattered wave with zero power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
@@
 	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} systems is still in the infancy stage.
-	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a specific \gls{bd}-\gls{ris}-aided \gls{mimo} system with blocked direct link and unitary (a.k.a.
-fully-connected) \gls{ris}.
+	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a specific \gls{bd}-\gls{ris}-aided \gls{mimo} system with blocked direct link and fully-connected \gls{ris}.
 	Similar constraints were also adopted in \cite{Mishra2024}, which introduces a transmitter-side \gls{bd}-\gls{ris} to massive \gls{mimo} that exploits statistical \gls{csi} for improved spectral efficiency.
@@
 	Although the results are promising, the channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
-	Furthermore, no previous work has attempted to characterize the singular value region of a \gls{mimo} channel manipulated by any type of \gls{ris}, and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
+	Moreover, no previous work has attempted to characterize the singular value region of a \gls{mimo} channel manipulated by any type of \gls{ris}, and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
 	This paper aims for a comprehensive answer to the channel shaping capability of \gls{bd}-\gls{ris} through theoretical analysis and numerical optimization.
@@
 	First, we interpret the channel shaping potential of \gls{bd}-\gls{ris} in terms of channel rearrangement and space alignment.
-	Channel rearrangement refers to rearrange and recombine the forward and backward channel branches by their strength.
+	Channel rearrangement refers to rearranging and recombining the forward and backward channel branches (i.e., entries of the channel matrix) according to their strength.
 	Space alignment generalizes phase matching in \gls{siso} and \gls{miso} to the high-dimensional singular vector space in \gls{mimo}.
-	The off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix provides a higher design freedom and exploits spatial diversity more effectively than diagonal \gls{ris}.
+	The off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix provides a higher design freedom and exploits channel spatial diversity more effectively than diagonal \gls{ris}.
 	This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems.
@@
 
-	Second, we propose an efficient \gls{bd}-\gls{ris} design framework based on geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
+	Second, we propose an efficient \gls{bd}-\gls{ris} design framework that solves general optimization problems by geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
 	% to numerically analyze the channel shaping capability of \gls{bd}-\gls{ris}, we exploit the Riemannian geometry of the Stiefel manifold and
-	This method modified from \cite{Abrudan2008,Abrudan2009} exploits the Riemannian geometry of the Stiefel manifold, which not only converges faster than non-geodesic approach \cite{Absil2009,Pan2022d} but also works for general optimization problems of group-connected \gls{bd}-\gls{ris}.
-	Specifically, group-wise multiplicative updates are performed along the geodesics to avoid retraction and facilitate step size selection.
-	It greatly improves computational efficiency and stability.
-	This is the first work to tailor an efficient and universal optimization framework for \gls{bd}-\gls{ris}.
+	This method modified from \cite{Abrudan2008,Abrudan2009} exploits the Riemannian geometry of the Stiefel manifold and performs group-wise multiplicative rotational updates along the geodesics, which avoids retraction and facilitates step size selection.
+	It thus converges faster than existing non-geodesic approaches \cite{Absil2009,Pan2022d}.
+	This is the first work to tailor an efficient optimization framework for \gls{bd}-\gls{ris}.
 
@@
 	% significantly enlarges the singular value region, improveing the dynamic range and trade-off in-between.
-	% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and unitary \gls{ris}.
+	% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected \gls{ris}.
 
@@
 	Asymptotic channel singular value bounds shared by diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient forward/backward channel.
-	On the other hand, attainable bounds in the presence of unitary \gls{bd}-\gls{ris} are derived for blocked direct channel.
+	On the other hand, attainable bounds in the presence of fully-connected \gls{ris} are derived for blocked direct channel.
 	Results validate those bounds and emphasizes the shaping advantage of \gls{bd}-\gls{ris}.
@@
 	% % respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris}
-	% collective singular value bounds	for rank-deficient channels and unitary \gls{ris}, respectively.
+	% collective singular value bounds	for rank-deficient channels and fully-connected \gls{ris}, respectively.
 	% 	Results validate those bounds and show
-	% for rank-deficient channels and unitary \gls{ris}, respectively.
+	% for rank-deficient channels and fully-connected \gls{ris}, respectively.
 	% Results validate those bounds and show that increasing \gls{bd}-\gls{ris} group size significantly enlarges the singular value region, providing wider dynamic range and better trade-off.
@@
 	% The problem is solved by a closed-form two-stage method.
-	Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than diagonal \gls{ris}, and the rate gap between two approaches diminishes as the \gls{ris} evolves from diagonal to unitary.
+	Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than diagonal \gls{ris}, and the rate gap between two approaches diminishes as the \gls{ris} evolves from single-connected to fully-connected.
 	It suggests channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
@@
 	To simplify the analysis and explore the performance limits, we assume a lossless asymmetric network without mutual coupling between scattering elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
-	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-unitary
+	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-unitary\footnote{Following footnote \ref{fn:symmetric}, we do not assume the scattering matrix to be symmetric.
+If required, one can enforce symmetry over the block-unitary result by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.}
 	\begin{equation}
@@
 	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary block (i.e., $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$) that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
-	Note that diagonal and unitary \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
+	Note that diagonal \gls{ris} can be regarded as its extreme case with group size $L=1$.
 	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2024}, where the
@@
 	\begin{itemize}
-		\item \emph{Channel rearrangement:} It refers to rearrange and recombine the backward and forward channel branches associated with each group by their strength.
-		This unique feature of \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
+		\item \emph{Channel rearrangement:} It refers to rearranging and recombining the backward and forward channel branches (i.e., entries of the channel matrix) associated with each group by their strength.
+		% This unique feature of \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
 		% This unique feature of \gls{bd}-\gls{ris} exploits the spatial diversity by rearranging and combining the backward and forward channel branches within each group.
@@
 		Note the first summation is over groups and the second summation is over permuted channels.
+		We thus conclude that \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
 		By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
@@
 		Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.
-		\item \emph{Space alignment:} It refers to align the direct, forward, and backward channels by their singular vectors.
+		\item \emph{Space alignment:} It refers to aligning the singular vectors of the direct, forward, and backward channels.
 		The \gls{bd}-\gls{ris} needs to strike a balance between the alignment of backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
-In \gls{siso}, space alignment boils down to phase matching and the optimal scattering matrix of group $g$ that maximizes the channel gain is
+In \gls{siso}, singular vectors become scalars and space alignment boils down to phase matching, such that the optimal scattering matrix of group $g$ that maximizes the channel gain is
 		\begin{equation}
@@
 		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-		Diagonal \gls{ris} ($L=1$, empty null spaces) thus suffices for perfect phase matching in \gls{siso}.
-		When it comes to \gls{mimo}, each individual scattering element can only apply a common phase shift to the ``pinhole'' indirect channel $\mathbf{H}_g \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ passing through itself.
+		Diagonal \gls{ris} with empty null space thus suffices for perfect phase matching in \gls{siso}.
+		When it comes to \gls{mimo}, each element of diagonal \gls{ris} can only apply a common phase shift to the ``pinhole'' indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
 		That is, the disadvantage of diagonal \gls{ris} in space alignment scales with \gls{mimo} dimensions.
@@
 	% \begin{remark}
-	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
+	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and fully-connected \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
 	% \end{remark}
@@
 
-\begin{section}{Group-Wise Geodesic \glsfmtshort{rcg}}
-	In this section, we first provide an overview on signal processing techniques for general \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group to operate directly on the Stiefel manifold.
+\begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Design by Geodesic \glsfmtshort{rcg}}
+	% In this section, we first provide an overview on signal processing techniques for group-connected \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group and operates directly on the Stiefel manifold.
 	% The proposed method is applicable to any smooth optimization problem on the Stiefel manifold and is particularly suitable for \gls{bd}-\gls{ris} design problems.
-	We will later show that the proposed method not only provides better objective value and faster convergence than other approaches, but also works for arbitrary group size and any smooth optimization problem.
-	\begin{subsection}{Conventional Techniques}
-		General \gls{bd}-\gls{ris} design techniques can be classified into two categories based on the optimization variable and hardware architecture:
-		\begin{itemize}
-			\item \emph{Scattering matrix $\mathbf{\Theta}$:} This approach is often exploited for asymmetric architectures where the feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
-Due to its non-convexity, relevant problems are usually solved by general non-geodesic manifold optimization \cite{Li2023b,Li2023c,Bartoli2023} or relax-then-project methods \cite{Fang2023}.
-The former will be discussed in the next subsection.
-			\item \emph{Reactance matrix $\mathbf{X}$:\footnote{Similar design over susceptance matrix $\mathbf{B}$ can be found in \cite{Nerini2024}.}} This approach is often exploited for symmetric architectures where every pair of elements in the same group are connected by capacitors and inductors.
-According to network theory \cite{Pozar2011}, it maps to the scattering matrix by $\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I})$, which formulates an unconstrained optimization problem on the upper triangular entries of $\{\mathbf{X}_g\}_{g \in \mathcal{G}}$ that is solvable by quasi-Newton methods \cite{Shen2020a}.
-		\end{itemize}
-	\end{subsection}
-
-	\begin{subsection}{Geodesic vs Non-Geodesic \glsfmtshort{rcg}}
-		We first revisit the general non-geodesic \gls{rcg} method that is applicable to optimization problems over arbitrary manifolds \cite{Absil2009,Pan2022d}.
+	% We will later show that the proposed method provides better objective value and faster convergence for smooth optimization problems of arbitrary group size.
+	A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
+	We notice that the feasible domain of scattering matrix of each \gls{bd}-\gls{ris} group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$, which is non-convex and non-Euclidean.
+	Therefore, relevant optimization problems are usually solved by relax-then-project methods \cite{Fang2023} or universal non-geodesic manifold \gls{rcg} \cite{Li2023b,Li2023c,Bartoli2023}.
+	The former solves an unconstrained version of original problem by quasi-Newton methods, then projects the solution back to the Stiefel manifold.
+	It has no guarantee of optimality and may suffer from numerical instability.
+	The latter generalizes the conjugate gradient methods to any Riemannian manifold, which updates the feasible point by progressing along the conjugate direction and projecting back to the manifold at each step.
+	In this section, we first discuss the existing non-geodesic \gls{rcg} method and its drawbacks, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
+
+	\begin{subsection}{Non-Geodesic \glsfmtshort{rcg}}
+		This universal \gls{rcg} method is applicable to optimization problems over arbitrary manifolds \cite{Absil2009,Pan2022d}.
 		The main idea is to perform {additive} updates along the conjugate direction guided by the Riemannian gradient, then {project} the solution back onto the manifold.
@@
 			where $\mu$ is the step size refinable by the Armijo rule \cite{Armijo1966};
-			\item \emph{Retract for feasibility \cite{Absil2009,Li2023b}:} The resulting point needs to be projected back onto the Stiefel manifold by
+			\item \emph{Retract for feasibility \cite{Absil2009,Li2023b}:} The resulting point needs to be projected to the closest point (in terms of Euclidean distance) on the Stiefel manifold by
 			\begin{equation}
@@
 
-		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
-		The above method is called non-geodesic since the points are updated in the linear embedding spaces of the manifold by addition and retraction, instead of on the Stiefel manifold itself.
-		Next, we revisit some concepts in differential geometry and introduce a group-wise geodesic \gls{rcg} method on top of \cite{Abrudan2008,Abrudan2009}.
+		The above method is called non-geodesic since the points are updated in the linear embedding spaces by addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction}, instead of on the Stiefel manifold itself.
+		It converges to stationary points of the original problem but usually requires a large number of iterations due to inefficient operations in the Euclidean space.
+
+		% additive update \eqref{eq:update_additive} in the Euclidean space and retraction \eqref{eq:retraction}.
+		% Those
+	\end{subsection}
+
+	% \begin{subsection}{Conventional Techniques}
+	% 	Group-connected \gls{bd}-\gls{ris} design techniques formulated in terms of scattering matrix can be classified into two categories based on the optimization variable and hardware architecture:
+	% 	\begin{itemize}
+	% 		\item \emph{Scattering matrix $\mathbf{\Theta}$:} This approach is often exploited for asymmetric architectures where the feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
+Due to its non-convexity, relevant problems are usually solved by general non-geodesic manifold optimization \cite{Li2023b,Li2023c,Bartoli2023} or relax-then-project methods \cite{Fang2023}.
+The former will be discussed in the next subsection.
+	% 		\item \emph{Reactance matrix $\mathbf{X}$:\footnote{Similar design over susceptance matrix $\mathbf{B}$ can be found in \cite{Nerini2024}.}} This approach is often exploited for symmetric architectures where every pair of elements in the same group are connected by capacitors and inductors.
+According to network theory \cite{Pozar2011}, it maps to the scattering matrix by $\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I})$, which formulates an unconstrained optimization problem on the upper triangular entries of $\{\mathbf{X}_g\}_{g \in \mathcal{G}}$ that is solvable by quasi-Newton methods \cite{Shen2020a}.
+	% 	\end{itemize}
+	% \end{subsection}
+
+	\begin{subsection}{Geodesic \glsfmtshort{rcg}}
+		Before introducing geodesic \gls{rcg}, we revisit some basic concepts in differential geometry and Lie algebra.
+
+		% \cite{Abrudan2008,Abrudan2009}.
 
@@
 		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{bd}-\gls{ris} has 4 independent angular parameters
+		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{ris} has 4 independent angular parameters
 		\begin{equation}
@@
 		It is worth noting that $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		For a fair comparison, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
+		To simplify the analysis, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of optimization variables.
 		\begin{figure}
@@
 			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
-			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetry unitary \gls{ris}.}
+			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetric fully-connected \gls{ris}.}
 			\label{fg:singular_trend}
 		\end{figure}
-		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
-		It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements.
+		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric fully-connected \gls{ris}.
+		In this particular example, we observe that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and optimization variables.\footnote{However, \gls{bd}-\gls{ris} does require more reconfigurable components that interconnect the scattering elements.}
 		A larger performance gap is expected when the symmetric constraint on \eqref{eq:unitary_ris} can be relaxed.
@@
 
-		\begin{proposition}[Unitary \gls{ris} without direct link]\label{pp:fully_connected}
+		\begin{proposition}[Fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
 			% If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
@@
 		\end{maxi!}
-		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with unitary \gls{ris} \eqref{eq:scattering_fc_optimal}.
+		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with fully-connected \gls{ris} \eqref{eq:scattering_fc_optimal}.
 		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative space alignments.
@@
 		where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right compact singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-		We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid unitary \gls{ris} solutions to \eqref{op:power_passive} when the direct link is absent and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
+		We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{ris} solutions to \eqref{op:power_passive} when the direct link is absent and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
 
@@
 		It is observed that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (up to 3$\times$) lower number of iterations and shorter (up to 4$\times$) computational time than the non-geodesic method.
-		The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially in large-scale \gls{bd}-\gls{ris} design problems.\footnote{If the scattering matrix is constrained to be symmetric, one can project the solution to the feasible domain by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.}
+		The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially in large-scale \gls{bd}-\gls{ris} design problems.
 	\end{subsection}
@@
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
-			We observe that the smallest singular value can be enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by unitary \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We observe that the smallest singular value can be enhanced up to \num{2e-4} by single-connected \gls{ris} and \num{3e-4} by fully-connected \gls{ris}, corresponding to a \qty{50}{\percent} gain.
 			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
@@
 					The blue (resp. red) bars are obtained by solving problem \eqref{op:pareto} with $\rho_n = -1$ (resp. $+1$) and $\rho_{n'} = 0$, $\forall n' \ne n$.
-					`D' means diagonal \gls{ris} and `BD' refers to unitary \gls{bd}-\gls{ris}.
+					`D' means diagonal \gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
 					`rank-$k$' refers to the rank of the forward channel.
@@
 				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
-				`D' means diagonal \gls{ris} and `BD' refers to unitary \gls{bd}-\gls{ris}.
+				`D' means diagonal \gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
 			}
@@
 		Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
-		The scattering matrix of unitary \gls{ris} can be decomposed as
+		The scattering matrix of fully-connected \gls{ris} can be decomposed as
 		\begin{equation}

### 2024-05-15 main.tex
:triangular_flag_on_post: Bruno 240515

@@
 
-	Second, we propose an efficient \gls{bd}-\gls{ris} design framework that solves general optimization problems by geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
+	Second, we propose an efficient \gls{bd}-\gls{ris} design framework that solves general optimization problems (e.g., singular value redistribution and rate maximization) by geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
 	% to numerically analyze the channel shaping capability of \gls{bd}-\gls{ris}, we exploit the Riemannian geometry of the Stiefel manifold and
@@
 	% We will later show that the proposed method provides better objective value and faster convergence for smooth optimization problems of arbitrary group size.
-	A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
-	We notice that the feasible domain of scattering matrix of each \gls{bd}-\gls{ris} group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$, which is non-convex and non-Euclidean.
+
+	Many group-connected \gls{bd}-\gls{ris} design problems can be formulated in the following general form
+	\begin{maxi!}
+		{\scriptstyle{\mathbf{\Theta}}}{f(\mathbf{\Theta})}{\label{op:general}}{\label{ob:general}}
+		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:general_unitary}}
+	\end{maxi!}
+	where the objective function $f(\mathbf{\Theta})$ can be any function of the \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$, for example, channel singular value (to be discussed in Section \ref{sc:singular_value}) and achievable rate (to be discussed in Section \ref{sc:power_rate}).
+	The feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$, which is non-convex and non-Euclidean.
 	Therefore, relevant optimization problems are usually solved by relax-then-project methods \cite{Fang2023} or universal non-geodesic manifold \gls{rcg} \cite{Li2023b,Li2023c,Bartoli2023}.
-	The former solves an unconstrained version of original problem by quasi-Newton methods, then projects the solution back to the Stiefel manifold.
+	The former solves an unconstrained problem \eqref{ob:general} by quasi-Newton methods, then projects the solution back to the Stiefel manifold.
 	It has no guarantee of optimality and may suffer from numerical instability.
 	The latter generalizes the conjugate gradient methods to any Riemannian manifold, which updates the feasible point by progressing along the conjugate direction and projecting back to the manifold at each step.
-	In this section, we first discuss the existing non-geodesic \gls{rcg} method and its drawbacks, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
+	In the following context, we first discuss the existing non-geodesic \gls{rcg} method and its drawbacks, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
 
 	\begin{subsection}{Non-Geodesic \glsfmtshort{rcg}}
-		This universal \gls{rcg} method is applicable to optimization problems over arbitrary manifolds \cite{Absil2009,Pan2022d}.
+		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
+		The universal \gls{rcg} method proposed in \cite{Absil2009,Pan2022d} is non-geodesic and applicable to optimization problems over arbitrary manifolds.
 		The main idea is to perform {additive} updates along the conjugate direction guided by the Riemannian gradient, then {project} the solution back onto the manifold.
@@
 		% The main idea is to update the feasible point by progressing along conjugate directions then project back to the manifold.
-		For maximization problem with smooth objective $f$ and block-unitary constraint \eqref{eq:bd_ris}, the steps for \gls{bd}-\gls{ris} group $g$ at iteration $r$ are summarized below:
+		For optimization problem \eqref{op:general}, the steps for \gls{bd}-\gls{ris} group $g$ at iteration $r$ are summarized below:
 		\begin{enumerate}
@@
 		Before introducing geodesic \gls{rcg}, we revisit some basic concepts in differential geometry and Lie algebra.
-
 		% \cite{Abrudan2008,Abrudan2009}.
-
 		A Lie group is simultaneously a continuous group and a differentiable manifold.
@@
 \begin{section}{Channel Singular Values Redistribution}
+	\label{sc:singular_value}
 	In this section, we first provide a toy example to illustrate the channel shaping advantage of \gls{bd}-\gls{ris} architecture.
@@
 
-\begin{section}{Power Gain and Achievable Rate Maximization}\label{sc:power_rate}
+\begin{section}{Power Gain and Achievable Rate Maximization}
+	\label{sc:power_rate}
 	\begin{subsection}{Channel Power Gain}\label{sc:power}
@@
 	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and unitary scenarios.
-	Specifically, the former is done by proposing an efficient \gls{rcg} algorithm for smooth \gls{bd}-\gls{ris} optimization problems, which offers better objective value and faster convergence than existing methods.
+	Specifically, the former is done by proposing an efficient \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization problems, which offers better objective value and faster convergence than existing methods.
 	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.

### 2024-05-27 assets/simulation/singular_bound_rank1_sx32.tex
:pencil: Update manuscript

--- 2024-02-12 assets/simulation/pc_singular_bound_32.tex
@@
 ymax=0.002,
-ylabel style={font=\color{white!15!black}},
+% ylabel style={font=\color{white!15!black}},
 ylabel={Amplitude},

### 2024-05-27 assets/simulation/singular_bound_rank1_sx64.tex
:pencil: Update manuscript

--- 2024-02-12 assets/simulation/pc_singular_bound_64.tex
@@
 ymax=0.003,
-ylabel style={font=\color{white!15!black}},
+% ylabel style={font=\color{white!15!black}},
 ylabel={Amplitude},

### 2024-05-27 assets/simulation/singular_bound_rank2_sx128.tex
:pencil: Update manuscript

@@
 ymax=0.004,
-ylabel style={font=\color{white!15!black}},
+% ylabel style={font=\color{white!15!black}},
 ylabel={Amplitude},

### 2024-05-27 assets/simulation/singular_bound_rank4_sx256.tex
:pencil: Update manuscript

@@
 ymax=0.005,
-ylabel style={font=\color{white!15!black}},
+% ylabel style={font=\color{white!15!black}},
 ylabel={Amplitude},

### 2024-05-27 main.tex
:pencil: Update manuscript

@@
 \pgfplotsset{compat=newest}
+\pgfplotsset{every axis/.append style={
+	title style={font=\Large},
+	label style={font=\Large},
+	tick label style={font=\Large},
+	legend style={font=\Large},
+}}
 
@@
 	% the limit to which
-	We depart from the widely-adopted diagonal phase shift model to a \gls{bd}-\gls{ris} architecture featuring in-group connections between elements, which enables cooperative wave scattering with amplitude and phase control.
+	We depart from the conventional diagonal phase shift model and adopt a \gls{bd}-\gls{ris} architecture featuring in-group connections between elements, which enables signal amplitude and phase control.
 	% This powerful model allows cooperative wave scattering with both amplitude and phase control, and we uniquely attribute the shaping advantage to channel rearrangement and space alignment.
@@
 	% The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
-	Specifically, we first provide unique shaping insights by characterizing the Pareto frontiers of channel singular values via a novel geodesic manifold optimization.
+	Specifically, we first provide shaping insights by characterizing the Pareto frontiers of channel singular values via a novel geodesic manifold optimization.
 	The resulting region comprehensively encapsulates most relevant metrics (e.g., spectral norm and condition number).
-	To explore the shaping limits of passive \gls{bd}-\gls{ris}, we also derive individual and collective singular value bounds respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris} via matrix analysis.
+	To explore the shaping limits of passive \gls{bd}-\gls{ris}, we also derive
+	% 0ol. individual and collective
+	singular value bounds for 1) rank-deficient forward/backward channel and 2) blocked direct channel.
+	% respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris} via matrix analysis.
 	% For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
@@
 	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
-	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a low-complexity shaping-inspired approach.
-	Simulation results highlight that \gls{bd}-\gls{ris} significantly improves the dynamic range of and trade-off between channel singular values.
-	Results also show the power and rate gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} increase with \gls{mimo} dimensions.
+	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a suboptimal shaping-inspired design over channel gain maximization.
+	% The former alternates between active and passive beamformers until convergence, while the latter maximizes
+	% solves the problem in closed form by a channel power maximization and \gls{mimo} transmission subproblem.
+	% shaping-inspired approach.
+	Simulation results show that \gls{bd}-\gls{ris} improves the dynamic range of and trade-off between channel singular values significantly, compared to conventional diagonal \gls{ris}.
+	Results also highlight that the power and rate gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} increase with \gls{mimo} dimensions.
 
@@
 	% It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
-	It enables low-noise, full-duplex operation, and also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional \gls{mimo} systems.
+	It enables low-noise, full-duplex operation, and also features better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo} systems.
 	The most popular \gls{ris} research direction is \emph{joint passive and active beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
-	While passive beamforming at \gls{ris} suffers severe attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
-	Another feature is that \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within the channel coherence time.
-	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
-	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment.
+	While passive beamforming at \gls{ris} suffers signal attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
+	Another \gls{ris} application is \emph{backscatter modulation} by periodically switching its reflection pattern within the channel coherence time.
+	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as an information source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
+	Different from above, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment.
 	To name a few, it can compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for \gls{mimo} systems \cite{Ozdogan2020a}, and create artificial time diversity for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple accesses.
-	Channel shaping also provides a ubiquitous benchmark for different wireless applications and helps to decouple the \gls{ris}-transceiver design in a shape-then-transmit manner.
-	At a specific time and frequency, channel metrics can be roughly classified into two categories:
+	Channel shaping also provides a ubiquitous solution for different wireless applications, which decouples joint \gls{ris}-transceiver designs by first optimizing the channel and then the communication system.
+	% and helps to decouple the \gls{ris}-transceiver design in a distributed manner.
+	At a specific resource block, relevant metrics can be classified into two categories:
 	% shaping metrics can be classified into two categories:
 	\begin{itemize}
-		\item \emph{Singular value:} Relevant metrics are in general closely related to the performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to numerical perturbations of the channel matrix.
-The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
-		\item \emph{Power:} Second-order statistics are less informative in \gls{mimo} but easier to analyze and optimize.
-The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
+		\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
+Those metrics are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to small perturbations of the channel matrix.
+		\item \emph{Power:} The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} in point-to-point channels and leakage interference \cite{Santamaria2023a} in interference channels.
+Those second-order metrics are less informative in \gls{mimo} but easier to analyze and optimize.
 	\end{itemize}
 
-	Although those works offer initial glimpses into the channel shaping potential, one critical question has not been fully addressed: \emph{What is the ultimate channel shaping capability of a passive \gls{ris} in terms of singular values?}
+	Although above works offer initial glimpses into the channel shaping potential of \gls{ris}, one critical question has not been fully addressed: \emph{What is the ultimate channel singular value shaping capability of a passive \gls{ris}?}
 	% \begin{enumerate}
@@
 	% Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
-	The answer depends heavily on the hardware architecture of \gls{ris} and its scattering model.
-	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} considered a diagonal \gls{ris} model where each element is connected to a dedicated impedance and is disconnected from others, such that wave impinging on one element is entirely reflected by the same element.
+	The answer depends heavily on \gls{ris} hardware architecture and scattering model.
+	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} considered a diagonal \gls{ris} model where each element is connected to a dedicated impedance and disconnected from others, such that wave impinging on one element is entirely reflected by the same element.
 	% is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
-	This simple architecture mathematically translates to a diagonal scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the incoming signal.
-	The concept was soon generalized to \gls{bd}-\gls{ris} with a group-connected architecture \cite{Shen2020a} that groups adjacent elements and connects them via passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}
-	This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
-	It can thus redistribute both amplitude and phase of the scattered wave with zero power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
-	Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
+	This simple architecture ideally maps to a diagonal scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, which only applies a phase shift to the incoming signal.
+	The concept was then generalized to \gls{bd}-\gls{ris} with a group-connected architecture \cite{Shen2020a} that connects adjacent elements via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}.
+	This allows wave impinging on one element to propagate losslessly within the circuit and depart partially from any element in the same group.
+	It can thus manipulate both amplitude and phase of the scattered wave, generalizing the scattering matrix from diagonal to block-diagonal with unitary blocks.
+	Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures according to graph theory \cite{Nerini2024}.
 	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} to provide full-space coverage and multi-user support.
-	Many practical design challenges of \gls{bd}-\gls{ris} have also been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
-	From the beamforming perspective, the superiority of \gls{bd}-\gls{ris} over diagonal \gls{ris} has been studied extensively in \gls{siso} and \gls{miso} systems, where the problems were cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+	Many practical \gls{bd}-\gls{ris} design challenges, including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}, have also been investigated in the literature.
+	The passive beamforming superiority of \gls{bd}-\gls{ris} over diagonal \gls{ris} has been studied mainly in \gls{siso} and \gls{miso} communication systems, where the problems have been cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
 	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} systems is still in the infancy stage.
-	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a specific \gls{bd}-\gls{ris}-aided \gls{mimo} system with blocked direct link and fully-connected \gls{ris}.
-	Similar constraints were also adopted in \cite{Mishra2024}, which introduces a transmitter-side \gls{bd}-\gls{ris} to massive \gls{mimo} that exploits statistical \gls{csi} for improved spectral efficiency.
-	Received power maximization problem was studied over continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} \gls{bd}-\gls{ris}, but the proposed single-stream transceiver is rate-suboptimal and the passive beamforming problem is equivalent to \gls{siso}.
+	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a \gls{bd}-\gls{ris}-aided \gls{mimo} system with blocked direct link and fully-connected \gls{bd}-\gls{ris}.
+	Those assumptions simplify the problem but limit the generality of the results.
+	A transmitter-side \gls{bd}-\gls{ris} was introduced to massive \gls{mimo} systems for improved spectral efficiency \cite{Mishra2024}, but the problem was again limited to blocked direct link and fully-connected \gls{bd}-\gls{ris}.
+	Received power maximization with continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} \gls{bd}-\gls{ris} have also been tackled in the literature, but the resulting single-stream transceiver is rate-suboptimal and the corresponding \gls{bd}-\gls{ris} design is equivalent to \gls{siso} shaping.
 	% A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
 	% Although the results are promising, the channel shaping capability from off-diagonal entries deserves further investigation, and there lacks a universal yet efficient \gls{bd}-\gls{ris} design framework.
-	Although the results are promising, the channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
-	Moreover, no previous work has attempted to characterize the singular value region of a \gls{mimo} channel manipulated by any type of \gls{ris}, and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
-	This paper aims for a comprehensive answer to the channel shaping capability of \gls{bd}-\gls{ris} through theoretical analysis and numerical optimization.
+	We notice that there lacks a comprehensive study of \gls{bd}-\gls{ris} in point-to-point \gls{mimo} systems --- the shaping benefits of \gls{bd}-\gls{ris} are not fully understood and the general rate maximization problem remains open.
+	% and the channel shaping potential of \gls{bd}-\gls{ris} remains unexplored.
+	% The channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
+	% Although the results are promising, the channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
+	Moreover, no previous work has characterized the \gls{mimo} channel singular value region manipulated by any type of \gls{ris}.
+	% , and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
+	This paper aims to narrow those gaps and provide a comprehensive answer to the channel shaping capability question through theoretical analysis and numerical optimization.
 	The contributions are summarized below.
@@
 
-	First, we interpret the channel shaping potential of \gls{bd}-\gls{ris} in terms of channel rearrangement and space alignment.
+	First, we interpret the channel shaping potential of \gls{bd}-\gls{ris} in \gls{mimo} as channel rearrangement and space alignment.
 	Channel rearrangement refers to rearranging and recombining the forward and backward channel branches (i.e., entries of the channel matrix) according to their strength.
@@
 	% significantly enlarges the singular value region, improveing the dynamic range and trade-off in-between.
-	% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected \gls{ris}.
+	% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected \gls{bd}-\gls{ris}.
 
@@
 	% Asymptotic bounds shared by diagonal and \gls{bd}-\gls{ris} are derived in the former case, while exact bounds for unitary \gls{bd}-\gls{ris} are derived in the latter case.
-	Asymptotic channel singular value bounds shared by diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient forward/backward channel.
-	On the other hand, attainable bounds in the presence of fully-connected \gls{ris} are derived for blocked direct channel.
+	Asymptotic channel singular value bounds applying to diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient forward/backward channel.
+	On the other hand, tight bounds for fully-connected \gls{bd}-\gls{ris} with finite number of elements are derived for blocked direct channel.
 	Results validate those bounds and emphasizes the shaping advantage of \gls{bd}-\gls{ris}.
-	This is the first work to quantify the singular value redistribution capability from either numerical or analytical perspective.
+	This is the first work to quantify the singular value redistribution capability of \gls{bd}-\gls{ris} from either numerical or analytical perspective.
 	% Results validate those bounds and show that
@@
 	% % respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris}
-	% collective singular value bounds	for rank-deficient channels and fully-connected \gls{ris}, respectively.
+	% collective singular value bounds	for rank-deficient channels and fully-connected \gls{bd}-\gls{ris}, respectively.
 	% 	Results validate those bounds and show
-	% for rank-deficient channels and fully-connected \gls{ris}, respectively.
+	% for rank-deficient channels and fully-connected \gls{bd}-\gls{ris}, respectively.
 	% Results validate those bounds and show that increasing \gls{bd}-\gls{ris} group size significantly enlarges the singular value region, providing wider dynamic range and better trade-off.
@@
 	Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by two beamforming solutions: a local-optimal \gls{ao} approach and a low-complexity approach inspired by channel shaping insights.
-	The former updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.
-	The latter suboptimally decouples the problem as channel power gain maximization at \gls{ris} and conventional \gls{mimo} transmission at transceiver, then solves both in closed form.
+	The former updates active beamforming by eigenmode transmission and passive beamforming by proposed geodesic \gls{rcg} until convergence.
+	The latter suboptimally decouples the problem as channel power gain maximization at \gls{bd}-\gls{ris} and conventional \gls{mimo} transmission at transceiver, then solves both in closed form.
 	% The problem is solved by a closed-form two-stage method.
-	Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than diagonal \gls{ris}, and the rate gap between two approaches diminishes as the \gls{ris} evolves from single-connected to fully-connected.
+	Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than diagonal \gls{ris}, and the rate gap of two approaches diminishes as the \gls{bd}-\gls{ris} evolves from single-connected to fully-connected.
 	It suggests channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
@@
 \begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Model}
-	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
+	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
 	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
@@
 	% radiation pattern and
-	circuit topology need to be modelled in the scattering matrix.
-
-	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (transmitter-receiver), backward (\gls{ris}-receiver), and forward (transmitter-\gls{ris}) channels, respectively.
+	circuit topology is modelled in the scattering matrix.
+
+	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (i.e., transmitter-receiver), backward (i.e., \gls{ris}-receiver), and forward (i.e., transmitter-\gls{ris}) channels, respectively.
 	The equivalent channel is a function of the scattering matrix
@@
 		Diagonal \gls{ris} with empty null space thus suffices for perfect phase matching in \gls{siso}.
-		When it comes to \gls{mimo}, each element of diagonal \gls{ris} can only apply a common phase shift to the ``pinhole'' indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
+		When it comes to \gls{mimo}, element $g$ of diagonal \gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
+For element $g$ of diagonal \gls{ris}, the indirect channel $\mathbf{H}_g$ is rank-1 and the pinhole is $\Theta_g$.} indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
 		That is, the disadvantage of diagonal \gls{ris} in space alignment scales with \gls{mimo} dimensions.
@@
 	% This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
-	% Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
+	% Interestingly, the gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{S}=4$ \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
 	% This is because space alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
@@
 	% \begin{remark}
-	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and fully-connected \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
+	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and fully-connected \gls{bd}-\gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
 	% \end{remark}
@@
 
-	Many group-connected \gls{bd}-\gls{ris} design problems can be formulated in the following general form
+	Most group-connected \gls{bd}-\gls{ris} design problems can be formulated in the following general form
 	\begin{maxi!}
@@
 		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{ris} has 4 independent angular parameters
+		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} has 4 independent angular parameters
 		\begin{equation}
@@
 		It is worth noting that $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		To simplify the analysis, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of optimization variables.
+		To simplify the analysis, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of variables in the scattering matrix.
 		\begin{figure}
@@
 			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
-			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetric fully-connected \gls{ris}.}
+			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal \gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris}.}
 			\label{fg:singular_trend}
 		\end{figure}
-		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric fully-connected \gls{ris}.
-		In this particular example, we observe that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and optimization variables.\footnote{However, \gls{bd}-\gls{ris} does require more reconfigurable components that interconnect the scattering elements.}
-		A larger performance gap is expected when the symmetric constraint on \eqref{eq:unitary_ris} can be relaxed.
-		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
+		Fig.~\ref{fg:singular_trend} compares the achievable singular values of one typical channel realization, where the direct channel is blocked and the forward and backward channels are normalized Rayleigh fading
+		\begin{equation*}
+			\begin{split}
+				\mathbf{H}_\mathrm{B} & =
+				\begin{bmatrix}
+					-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
+					0.4131 + 0.2651 \jmath & -0.1960 + 0.4650 \jmath
+				\end{bmatrix},
+				\\
+				\mathbf{H}_\mathrm{F} & =
+				\begin{bmatrix}
+					-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
+					0.0196 + 0.4011 \jmath & -0.3170 - 0.2303 \jmath
+				\end{bmatrix}.
+			\end{split}
+		\end{equation*}
+		The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric fully-connected \gls{bd}-\gls{ris}.
+		In this example, we observe that both singular values can be manipulated up to\footnote{The percentage for manipulating the $n$-th channel singular value is calculated by $\eta_n = \frac{\max \sigma_n(\mathbf{H}) - \min \sigma_n(\mathbf{H})}{2 \bar{\sigma}_n(\mathbf{H})} \times 100\%$.
+In this case, we notice $\eta_1=\eta_2$ for both \gls{ris} architectures.} $9\%$ by diagonal \gls{ris} (using 2 reconfigurable impedances) and $42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (using 3 reconfigurable impedances).
+		% , where the former needs 2 reconfigurable impedances and the latter needs 3.
+		The extra performance gain comes purely from connecting both scattering elements, and a larger gain is expected an asymmetric reconfigurable component is available.
+		% and a larger gain is expected when an asymmetric connection is available.
+		This example shows that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
 	\end{subsection}
@@
 	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
-		We then discuss some analytical bounds related to channel singular values.
+		We then discuss some analytical bounds related to channel singular values, which help us to explore and understand the channel shaping limits of passive \gls{ris}.
+
+		\gls{dof} (a.k.a. multiplexing gain) refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, which is defined as
+		\begin{equation}
+			d = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho},
+		\end{equation}
+		where $\rho$ is the \gls{snr}.
 		\begin{proposition}[Degree of freedom]\label{pp:dof}
@@
 		\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
-			If the forward or backward channel is rank-$k$ ($k \le N$), then regardless of the passive \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
+			% If the forward or backward channel is rank-$k$ ($k \le N$),
+			If the minimum rank of forward and backward channels is $k$ ($k \le N$),
+			then for diagonal \gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
 			\begin{subequations}
@@
 			\end{subequations}
-			where
+			where $\mathbf{T}$ is an auxiliary matrix satisfying
 			\begin{equation}
@@
 
-		\begin{corollary}[Extreme singular values\label{co:extreme}]
-			With a sufficiently large passive \gls{ris} of arbitrary architecture, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
+		Inequality \eqref{iq:sv_bound_enlarge} states that
+		if the forward and backward channels are at least rank $k$, then
+		% with a diagonal \gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements,
+		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
+		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
 This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
-		\end{corollary}
-
-		\begin{proof}
-			This is a direct result of \eqref{iq:sv_bound_rank_deficient}.
-		\end{proof}
-
-		\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} \cite{Semmler2023}.}\label{co:los}]
+		An example is given in Corollary \ref{co:los} for \gls{los} channels (i.e., $k=1$)\footnote{We notice a similar eigenvalue result has been derived in \cite{Semmler2023} but is limited to diagonal \gls{ris}.}.
+		% states that the $n$-th channel singular value can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$.
+
+		% We would like to give some insights into Proposition \ref{pp:rank_deficient}.
+
+		% \begin{corollary}[Extreme singular values\label{co:extreme}]
+		% 	If the minimum rank of forward and backward channels is $k$ ($k \le N$), then with a diagonal \gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
+This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
+		% \end{corollary}
+
+		% \begin{proof}
+		% 	This is a direct result of \eqref{iq:sv_bound_rank_deficient}.
+		% \end{proof}
+
+		\begin{corollary}[\gls{los} channel\label{co:los}]
 			% If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
@@
 $n$-th) singular value of $\mathbf{T}$, that is,
-			If the forward or backward channel is \gls{los}, then a passive \gls{ris} of arbitrary architecture can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
+			If the forward or backward channel is \gls{los}, then a diagonal \gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
 			That is,
@@
 
-		In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can better approach those bounds than diagonal \gls{ris}.
-
-		\begin{proposition}[Fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
-			% If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-			If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the channel singular values can be manipulated up to
-			% If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
+		We would like to highlight that Proposition \ref{pp:rank_deficient} holds for both diagonal and \gls{bd}-\gls{ris} with arbitrary number of elements, regardless of the presence of direct channel.
+		The bounds are asymptotically tight when the number of scattering elements approaches infinity.
+		On the other hand, we will show in Section \ref{sc:simulation} that with a finite number of elements, \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.
+		Proposition \ref{pp:rank_deficient} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a selection guideline for scattering element number in a practical deployment scenario.
+
+		\begin{proposition}[Blocked direct channel]\label{pp:fully_connected}
+			% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+
+			If the direct link is blocked and the \gls{bd}-\gls{ris} is fully-connected, then the channel singular values can be manipulated up to
+			% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
 			% only bounds that apply here are those that apply to the singular values of
@@
 			\end{equation}
-			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with $\mathrm{sv}(\mathbf{B})=\mathrm{sv}(\mathbf{H}_\mathrm{B})$ and $\mathrm{sv}(\mathbf{F})=\mathrm{sv}(\mathbf{H}_\mathrm{F})$.
 			% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
@@
 
-		The problem now becomes, how the singular values of matrix product are bounded by the singular values of its individual factors.
+		Proposition \ref{pp:fully_connected} states that if the direct channel is blocked and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are the singular value bounds on the product of unitary-transformed forward and backward channels.
+		% , a group-connected \gls{bd}-\gls{ris} in its most powerful form can manipulate the channel singular values to any possible state with zero power loss.
+		For example, consider a $2 \times 2 \times 2$ setup with
+		% $\mathrm{sv}(\mathbf{H}_\mathrm{B}) = [3, 2]^\mathsf{T}$ and $\mathrm{sv}(\mathbf{H}_\mathrm{B}) = [4, 1]^\mathsf{T}$.
+		\begin{equation*}
+			\mathbf{H}_\mathrm{B} =
+				\begin{bmatrix}
+					3 & 0 \\
+					0 & 2
+				\end{bmatrix},
+				\quad
+				\mathbf{H}_\mathrm{F} =
+				\begin{bmatrix}
+					1 & 0 \\
+					0 & 4
+				\end{bmatrix}.
+		\end{equation*}
+		It is apparent that any diagonal \gls{ris} can only achieve singular values $\mathrm{sv}(\mathbf{H}) = [8, 3]^\mathsf{T}$, but a fully connected \gls{bd}-\gls{ris} with $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can achieve $\mathrm{sv}(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+
+		Proposition \ref{pp:fully_connected} transforms the shaping capacity question to a mathematical one, namely how the singular values of matrix product are bounded by the singular values of its individual factors.
 		Let $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le \bar{N}$.
@@
 		For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $\bar{N}$ increases from 3 to 7.
-		This renders it computationally expensive for applications in large-scale \gls{mimo} systems.
+		This renders the analytic approach computationally expensive for large-scale \gls{mimo} systems.
 		Next, we showcase some useful inequalities enclosed by \eqref{iq:sv_bound_fc}.
@@
 
-		Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., unequal number of transmit, scatter, and receive antennas) as the lower bounds would coincide at zero.
+		Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., unequal number of transmit and receive antennas and scattering elements) as the lower bounds would coincide at zero.
 
@@
 
-		Tighter bounds are generally inapplicable when the direct link is present or the \gls{bd}-\gls{ris} is not unitary, since the direct-indirect channels and backward-forward channels cannot be completely aligned at the same time.
+		Proposition \ref{pp:fully_connected} and Corollaries \ref{co:sv_largest} -- \ref{co:sum_power} provide a comprehensive answer to singular value bounds and channel power gain limits for fully-connected \gls{bd}-\gls{ris} with blocked direct channel.
+		% understanding of the channel power gain limits of passive \gls{ris}.
+		% and suggest the impact of channel rearrangement and space alignment on redistributing channel singular values.
+		Tight bounds are inapplicable in more general cases since the direct-indirect channels and backward-forward channels cannot be completely aligned at the same time.
 		In such case, we can exploit optimization approaches from a singular value perspective (Section~\ref{sc:pareto_frontier}) or a power gain perspective (Section~\ref{sc:power}).
@@
 		\end{maxi!}
-		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with fully-connected \gls{ris} \eqref{eq:scattering_fc_optimal}.
+		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with fully-connected \gls{bd}-\gls{ris} \eqref{eq:scattering_fc_optimal}.
 		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative space alignments.
+
+		\begin{remark}
 			Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
@@
 			where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right compact singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-		We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{ris} solutions to \eqref{op:power_passive} when the direct link is absent and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
+			We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power_passive} when the direct link is blocked and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
+		\end{remark}
 
@@
 \begin{section}{Simulation Results}\label{sc:simulation}
+	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
+	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
+	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
+	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
+	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
+	Rayleigh fading (i.e., $\kappa = 0$) is assumed for all channels unless otherwise specified.
+
+	\begin{subsection}{Algorithm Evaluation}
 		\begin{table*}[!t]
@@
 		\end{table*}
-	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
-	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
-	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
-	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
-	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
-	Rayleigh fading (i.e., $\kappa = 0$) is assumed for all channels unless otherwise specified.
-
-	\begin{subsection}{Algorithm Evaluation}
-		We first compare the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in a 4T4R system with \gls{bd}-\gls{ris} group size $L=4$.
+		We first compare in Table \ref{tb:complexity_test} the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in an $N_\mathrm{T}=N_\mathrm{S}=4$ system with \gls{bd}-\gls{ris} group size $L=4$.
 		The statistics are averaged over \num{100} independent runs.
@@
 				}
-				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
+				\caption{Pareto frontiers of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel reshaped by a \gls{ris}.}
 				\label{fg:singular_pareto}
@@
 			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
-			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
-			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
+			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ \gls{mimo} reshaped by a \gls{ris}.
+			When the direct link is blocked, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
 			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two spaces.
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
-			We observe that the smallest singular value can be enhanced up to \num{2e-4} by single-connected \gls{ris} and \num{3e-4} by fully-connected \gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We observe that the smallest singular value can be enhanced up to \num{2e-4} by single-connected \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
 			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
@@
 			In particular, Fig.
-\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of cooperative wave scattering.
+\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} thanks to its superior channel shaping capability, but not by a diagonal one.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of reconfigurable inter-connection between elements.
 		\end{subsubsection}
@@
 \ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
-			Here we assme a rank-$k$ forward channel without loss of generality.
+			Here we assume a rank-$k$ forward channel without loss of generality.
 			When the \gls{ris} is in the vicinity of the transmitter, Figs.
@@
 			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
-			Those observations align with Proposition \ref{pp:rank_deficient} and Corollary \ref{co:extreme}.
+			Those observations align with Proposition \ref{pp:rank_deficient}.
 			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
@@
 					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
+					The direct channel is blocked.
 					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward channels.
@@
 			Fig.
-\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
+\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is blocked.
 			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_optimal} or via optimization approach \eqref{eq:scattering_power}.
@@
 			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
-			Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
+			Interestingly, the gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{S}=4$ \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
 			This is because space alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
@@
 		For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power as a 256-element diagonal \gls{ris} in Fig.
-\ref{fg:power_sx_txrx16}, but not in Fig.
-\ref{fg:power_sx_txrx16_nd}.
+\subref*{fg:power_sx_txrx16}, but not in Fig.
+\subref*{fg:power_sx_txrx16_nd}.
 		% This again credits to the superior space alignment capability of \gls{bd}-\gls{ris}.
@@
 		At a transmit power of \qty{10}{dB}, Fig.
-\subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to 4T4R \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
+\subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to $N_\mathrm{T}=N_\mathrm{S}=4$ \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
 		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
@@
 		This implies that the \gls{ris}-transceiver design can often be decoupled via channel shaping with marginal performance loss.
-		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
+		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit and receive antennas and scattering elements.
 		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
@@
 	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
-	This translates to a wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
-	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and unitary scenarios.
+	This translates to a wider dynamic range of and better tradeoff between singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
+	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds for rank-deficient forward/backward channel and blocked direct channel.
 	Specifically, the former is done by proposing an efficient \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization problems, which offers better objective value and faster convergence than existing methods.
@@
 
-	One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
-	Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
-	Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward spaces simultaneously.
+	% One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
+	% Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
+	% Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward spaces simultaneously.
 	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
@@
 		Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
-		The scattering matrix of fully-connected \gls{ris} can be decomposed as
+		The scattering matrix of fully-connected \gls{bd}-\gls{ris} can be decomposed as
 		\begin{equation}

### 2024-05-27 src/singular_trend.m

@@ -47,7 +47,7 @@ xlabel('$\alpha$');
 ylabel('$\psi$');
 zlabel({'Singular Value'});
 set(gca, 'XTick', 0 : pi / 2 : 2 * pi, 'YTick', 0 : pi / 2 : 2 * pi, 'XTickLabel',{'0', '0.5$\pi$', '$\pi$', '1.5$\pi$', '2$\pi$'}, 'YTickLabel',{'0', '0.5$\pi$', '$\pi$', '1.5$\pi$', '2$\pi$'});
-title('Symmetry Unitary RIS');
+title('Symmetry Unitary BD-RIS');
 linkaxes(handle.axis);
 savefig('plots/singular_trend.fig');
 saveas(gcf, '../assets/simulation/singular_trend', 'epsc');

### 2024-06-18 main.tex
:pencil: Revision 240618

@@
 % amsthm
+\newtheorem{definition}{Definition}
 \newtheorem{proposition}{Proposition}
@@
 \begin{abstract}
-	This paper investigates to what extent a passive \gls{ris} can redistribute the singular values of a \gls{mimo} point-to-point channel.
+	This paper investigates the extent to which a passive \gls{ris} can redistribute
+	% This paper investigates to what extent can a passive \gls{ris} redistribute
+	% singular values to achieve power and rate gains in point-to-point \gls{mimo} channels.
+	singular values of a point-to-point \gls{mimo} channel for power and rate gains.
 	% the limit to which
-	We depart from the conventional diagonal phase shift model and adopt a \gls{bd}-\gls{ris} architecture featuring in-group connections between elements, which enables signal amplitude and phase control.
+	We depart from the conventional diagonal phase shift model and adopt a \gls{bd}-\gls{ris} architecture featuring element-wise connections for signal amplitude and phase control.
+	% featuring element-wise connections for amplitude and phase control.
+	% in-group connections between elements, which enables signal amplitude and phase control.
 	% This powerful model allows cooperative wave scattering with both amplitude and phase control, and we uniquely attribute the shaping advantage to channel rearrangement and space alignment.
@@
 	% The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
-	Specifically, we first provide shaping insights by characterizing the Pareto frontiers of channel singular values via a novel geodesic manifold optimization.
-	The resulting region comprehensively encapsulates most relevant metrics (e.g., spectral norm and condition number).
-	To explore the shaping limits of passive \gls{bd}-\gls{ris}, we also derive
+	Specifically, we first provide
+	shaping insights by characterizing the
+	channel singular value region manipulated by diagonal and \gls{bd}-\gls{ris} via a novel geodesic manifold optimization.
+	% Pareto frontiers of channel singular values via a novel geodesic manifold optimization.
+	% channel shaping insights by characterizing the Pareto singular value frontiers via a novel geodesic manifold optimization.
+	% The resulting region comprehensively encapsulates most relevant metrics (e.g., spectral norm and condition number).
+	To explore the shaping limits, we also derive
 	% 0ol. individual and collective
-	singular value bounds for 1) rank-deficient forward/backward channel and 2) blocked direct channel.
+	analytical singular value bounds in special channel conditions.
+	% ? in two common scenarios: 1) forward/backward channel is rank-deficient and 2) direct channel is blocked.
 	% respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris} via matrix analysis.
@@
 	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
-	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a suboptimal shaping-inspired design over channel gain maximization.
+	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a suboptimal shaping-inspired two-stage approach.
+	%  over channel power gain maximization.
+	% (i.e., power gain maximization).
+	% over channel gain maximization.
 	% The former alternates between active and passive beamformers until convergence, while the latter maximizes
@@
 	% shaping-inspired approach.
-	Simulation results show that \gls{bd}-\gls{ris} improves the dynamic range of and trade-off between channel singular values significantly, compared to conventional diagonal \gls{ris}.
-	Results also highlight that the power and rate gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} increase with \gls{mimo} dimensions.
+	Compared to diagonal \gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them.
+	% , compared to conventional diagonal \gls{ris}.
+	Results also highlight that the power and rate gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
 
@@
 \begin{section}{Introduction}
+	\begin{subsection}{Background}
 		Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
-	This is empowered by the recent advances in \gls{ris}, a programmable passive planar surface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
+		This is empowered by recent advances in \gls{ris}, a programmable passive planar surface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
 		A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
 		% It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
-	It enables low-noise, full-duplex operation, and also features better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo} systems.
-	The most popular \gls{ris} research direction is \emph{joint passive and active beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
-	While passive beamforming at \gls{ris} suffers signal attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
+		It enables low-noise full-duplex operation, featuring better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo} systems.
+		One popular \gls{ris} research direction is \emph{joint passive and active beamforming} design with transceivers to enhance a specific performance measure, which has attracted significant interests in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
+		While passive beamforming at \gls{ris} suffers attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
 		Another \gls{ris} application is \emph{backscatter modulation} by periodically switching its reflection pattern within the channel coherence time.
-	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as an information source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
-	Different from above, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment.
-	To name a few, it can compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for \gls{mimo} systems \cite{Ozdogan2020a}, and create artificial time diversity for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple accesses.
-	Channel shaping also provides a ubiquitous solution for different wireless applications, which decouples joint \gls{ris}-transceiver designs by first optimizing the channel and then the communication system.
+		This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or serving as individual information source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
+		Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment.
+		It can compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for \gls{mimo} systems \cite{Ozdogan2020a}, and create artificial time diversity for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
+		Channel shaping also provides a ubiquitous solution for different wireless systems, decoupling joint beamforming design by first optimizing the channel and then the transceiver.
+		% decouples joint \gls{ris}-transceiver design by first optimizing the channel and then the system, providing a ubiquitous solution for different wireless applications
+		% different wireless applications
+		% different wireless applications
+		% into a channel design stage and a communication system design stage.
+		% provides a ubiquitous solution for different wireless applications, decoupling the joint \gls{ris}-transceiver designs into a channel design stage and a communication system design stage.
+		% which decouples joint \gls{ris}-transceiver designs by first optimizing the channel and then the communication system.
 		% and helps to decouple the \gls{ris}-transceiver design in a distributed manner.
-	At a specific resource block, relevant metrics can be classified into two categories:
+	\end{subsection}
+
+	\begin{subsection}{Related Works}
+		At a specific resource block, channel shaping metrics can be classified into two categories:
 		% shaping metrics can be classified into two categories:
@@
 			\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
-Those metrics are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to small perturbations of the channel matrix.
+Those are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to minor perturbations of the channel matrix.
 			\item \emph{Power:} The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} in point-to-point channels and leakage interference \cite{Santamaria2023a} in interference channels.
@@
 
-	Although above works offer initial glimpses into the channel shaping potential of \gls{ris}, one critical question has not been fully addressed: \emph{What is the ultimate channel singular value shaping capability of a passive \gls{ris}?}
+		Although above works offered inspiring glimpses into the channel shaping potential,
+		there exist no attempts to characterize the channel singular value region manipulated by passive \gls{ris}.
+		% no previous work has characterized the \gls{mimo} channel singular value region manipulated by any type of \gls{ris}.
+		Besides, most relevant literature \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} adopted a diagonal \gls{ris} model where each element is connected to a dedicated impedance and disconnected from others, such that wave impinging on one element is entirely scattered by the same element.
+		% is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
+		This simple architecture is modelled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal.
+		The concept was soon generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a} that connects adjacent elements from the same group via  passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}.
+		This allows wave impinging on one element to propagate losslessly within the circuit and depart partially from any element in the same group.
+		It can thus manipulate both amplitude and phase of the scattered wave while remaining passive, generalizing the scattering matrix to block-diagonal with unitary blocks.
+		Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
+		\gls{bd}-\gls{ris}
+		% also supports
+		can also function in
+		% hybrid transmitting-and-reflecting mode \cite{Li2023b} and
+		multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
+		Many practical design challenges, such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}, have also been investigated in recent publications.
+		Its beamforming superiority over diagonal \gls{ris} has been studied extensively in \gls{siso} and \gls{miso} systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}, however, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
+		% On the other hand, the beamforming superiority of \gls{bd}-\gls{ris} over diagonal \gls{ris} has been extensively studied in \gls{siso} and \gls{miso} communication systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+		% % , where the problems have been cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+		% However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
+		The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a fully-connected \gls{bd}-\gls{ris}-aided \gls{mimo} system where the direct link is blocked.
+% 		The work
+% 		% For a massive \gls{mimo} without direct link,
+% 		Similar assumptions were also adopted in
+% [47], which introduces a transmitter-side BD-RIS to massive
+% MIMO that exploits statistical Channel State Information (CSI)
+% for improved spectral efficiency
+% 		% with blocked direct link and \gls{bd}-\gls{ris}.
+% 		% Those assumptions simplify the problem but limit the generality of the results.
+		A transmitter-side \gls{bd}-\gls{ris} was introduced to
+		% improve the spectral efficiency of massive \gls{mimo} systems where the direct link is blocked \cite{Mishra2024}.
+		massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, but was again limited to blocked direct channel and fully-connected \gls{bd}-\gls{ris}.
+		Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal and the \gls{bd}-\gls{ris} design problem is equivalent to \gls{siso} shaping.
+
+		% in single-stream \gls{mimo} transmission
+
+		% in the literature, but the resulting single-stream transceiver is rate-suboptimal and the corresponding \gls{bd}-\gls{ris} design is equivalent to \gls{siso} shaping.
+		% A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
+		% Although the results are promising, the channel shaping capability from off-diagonal entries deserves further investigation, and there lacks a universal yet efficient \gls{bd}-\gls{ris} design framework.
+	\end{subsection}
+
+	\begin{subsection}{Contributions}
+		% We notice that there lacks a comprehensive study of \gls{bd}-\gls{ris} in point-to-point \gls{mimo} systems
+
+		% This paper investigates the shaping capability of passive \gls{ris} in point-to-point \gls{mimo} channels.
+		% We aim to answer the ultimate question:
+		% \emph{What is the channel singular value (and power gain) shaping capability of \gls{bd}-\gls{ris}?}
+
+		This paper is motivated by the critical question:
+		\emph{What is the singular value (and power gain) shaping capability of a passive \gls{ris} in point-to-point \gls{mimo} channels?}
+		We aim for a comprehensive answer via theoretical analysis and numerical optimization.
+		The contributions are summarized below.
+
+		% This paper aims to answer a critical question:
+		% \emph{What is the singular value (and power gain) shaping capability of passive \gls{ris} in point-to-point \gls{mimo} channels?}
+		% We provide a comprehensive answer through theoretical analysis and numerical optimization.
+
+		% This paper investigates the shaping capability of passive \gls{ris} in point-to-point \gls{mimo} channels.
+		% We aim to answer the ultimate question:
+		% \emph{What is the channel singular value and power gain shaping capability of \gls{bd}-\gls{ris}?}
+		% \emph{What is the ultimate channel singular value shaping capability of a passive \gls{ris}?}
+
+		% We notice that there lacks a comprehensive study of \gls{bd}-\gls{ris} in point-to-point \gls{mimo} systems --- the shaping benefits of \gls{bd}-\gls{ris} are not fully understood and the general rate maximization problem remains open.
+		% and the channel shaping potential of \gls{bd}-\gls{ris} remains unexplored.
+		% The channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
+		% Although the results are promising, the channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
+		% Moreover, no previous work has characterized the \gls{mimo} channel singular value region manipulated by any type of \gls{ris}.
+		% , and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
+		% one critical question has not been fully addressed: \emph{What is the ultimate channel singular value shaping capability of a passive \gls{ris}?}
 		% \begin{enumerate}
@@
 		% Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
-	The answer depends heavily on \gls{ris} hardware architecture and scattering model.
-	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} considered a diagonal \gls{ris} model where each element is connected to a dedicated impedance and disconnected from others, such that wave impinging on one element is entirely reflected by the same element.
-	% is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
-	This simple architecture ideally maps to a diagonal scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, which only applies a phase shift to the incoming signal.
-	The concept was then generalized to \gls{bd}-\gls{ris} with a group-connected architecture \cite{Shen2020a} that connects adjacent elements via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}.
-	This allows wave impinging on one element to propagate losslessly within the circuit and depart partially from any element in the same group.
-	It can thus manipulate both amplitude and phase of the scattered wave, generalizing the scattering matrix from diagonal to block-diagonal with unitary blocks.
-	Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures according to graph theory \cite{Nerini2024}.
-	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} to provide full-space coverage and multi-user support.
-	Many practical \gls{bd}-\gls{ris} design challenges, including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}, have also been investigated in the literature.
-	The passive beamforming superiority of \gls{bd}-\gls{ris} over diagonal \gls{ris} has been studied mainly in \gls{siso} and \gls{miso} communication systems, where the problems have been cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
-	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} systems is still in the infancy stage.
-	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a \gls{bd}-\gls{ris}-aided \gls{mimo} system with blocked direct link and fully-connected \gls{bd}-\gls{ris}.
-	Those assumptions simplify the problem but limit the generality of the results.
-	A transmitter-side \gls{bd}-\gls{ris} was introduced to massive \gls{mimo} systems for improved spectral efficiency \cite{Mishra2024}, but the problem was again limited to blocked direct link and fully-connected \gls{bd}-\gls{ris}.
-	Received power maximization with continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} \gls{bd}-\gls{ris} have also been tackled in the literature, but the resulting single-stream transceiver is rate-suboptimal and the corresponding \gls{bd}-\gls{ris} design is equivalent to \gls{siso} shaping.
-	% A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
-	% Although the results are promising, the channel shaping capability from off-diagonal entries deserves further investigation, and there lacks a universal yet efficient \gls{bd}-\gls{ris} design framework.
-	We notice that there lacks a comprehensive study of \gls{bd}-\gls{ris} in point-to-point \gls{mimo} systems --- the shaping benefits of \gls{bd}-\gls{ris} are not fully understood and the general rate maximization problem remains open.
-	% and the channel shaping potential of \gls{bd}-\gls{ris} remains unexplored.
-	% The channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
-	% Although the results are promising, the channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
-	Moreover, no previous work has characterized the \gls{mimo} channel singular value region manipulated by any type of \gls{ris}.
-	% , and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
-	This paper aims to narrow those gaps and provide a comprehensive answer to the channel shaping capability question through theoretical analysis and numerical optimization.
-	The contributions are summarized below.
+		% The answer depends heavily on \gls{ris} hardware architecture and scattering model.
+		% This paper aims to narrow those gaps and provide a comprehensive answer to the channel shaping capability question through theoretical analysis and numerical optimization.
+		% The contributions are summarized below.
 
@@
 
-	First, we interpret the channel shaping potential of \gls{bd}-\gls{ris} in \gls{mimo} as channel rearrangement and space alignment.
-	Channel rearrangement refers to rearranging and recombining the forward and backward channel branches (i.e., entries of the channel matrix) according to their strength.
-	Space alignment generalizes phase matching in \gls{siso} and \gls{miso} to the high-dimensional singular vector space in \gls{mimo}.
-	The off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix provides a higher design freedom and exploits channel spatial diversity more effectively than diagonal \gls{ris}.
-	This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems.
+		% Specifically, we propose a novel design method that allows reshaping of the available channels through singular values manipulation.
+Our method compares favorably with respect to existing solutions in that
+
+		First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping potential as channel rearrangement and space alignment.
+		% % systems
+		% interpret the channel shaping potential of \gls{bd}-\gls{ris} in \gls{mimo} as channel rearrangement and space alignment.
+		Channel rearrangement refers to rearranging and recombining the entries of transmitter-\gls{ris} and \gls{ris}-receiver channel matrices by their strength.
+		Space alignment generalizes phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to singular vector space in \gls{mimo}.
+		We highlight that the off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix exploits spatial diversity more effectively than diagonal \gls{ris}.
+		% This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems.
 		%  and discuss its shaping potential.
 
-	Second, we propose an efficient \gls{bd}-\gls{ris} design framework that solves general optimization problems (e.g., singular value redistribution and rate maximization) by geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
-	% to numerically analyze the channel shaping capability of \gls{bd}-\gls{ris}, we exploit the Riemannian geometry of the Stiefel manifold and
-	This method modified from \cite{Abrudan2008,Abrudan2009} exploits the Riemannian geometry of the Stiefel manifold and performs group-wise multiplicative rotational updates along the geodesics, which avoids retraction and facilitates step size selection.
-	It thus converges faster than existing non-geodesic approaches \cite{Absil2009,Pan2022d}.
-	This is the first work to tailor an efficient optimization framework for \gls{bd}-\gls{ris}.
+		Second, we propose a novel \gls{bd}-\gls{ris} design method that allows reshaping of the available channels through singular values manipulation.
+		Our method based on \gls{rcg} compares favorably with respect to existing solutions in that the updates are along the geodesics (i.e., the shortest path between two points in a Riemannian manifold) of the feasible domain to accelerate convergence.
+		It also works for general \gls{bd}-\gls{ris} optimization problems.
+
+		% Second, we propose an efficient \gls{bd}-\gls{ris} design framework that solves general optimization problems (e.g., singular value redistribution and rate maximization) by geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
+		% % to numerically analyze the channel shaping capability of \gls{bd}-\gls{ris}, we exploit the Riemannian geometry of the Stiefel manifold and
+		% This method modified from \cite{Abrudan2008,Abrudan2009} exploits the Riemannian geometry of the Stiefel manifold and performs group-wise multiplicative rotational updates along the geodesics, which avoids retraction and facilitates step size selection.
+		% It thus converges faster than existing non-geodesic approaches \cite{Absil2009,Pan2022d}.
+		% This is the first work to tailor an efficient optimization framework for \gls{bd}-\gls{ris}.
 
 		% pioneer
-	Third, we adopt the proposed geodesic \gls{rcg} and provide a numerical answer to the singular value shaping question.
-	% to answer the channel singular value shaping question via numerical optimization.
-	% to redistribute the singular values of a point-to-point \gls{mimo} channel.
-	The {Pareto frontiers} of channel singular values are characterized by solving a series of weighted sum maximization problems, where the weight associated with each singular value can be positive, zero, or negative.
+		Third, we provide a numerical answer to the shaping question by characterizing the Pareto frontiers of channel singular values.
+		The enclosed region generalizes most relevant metrics and provides an intuitive singular value shaping benchmark.
+		Results show that increasing \gls{bd}-\gls{ris} group size enlarges this region, improving the dynamic range of all singular values and the trade-off in manipulating them.
+		% enlarges the singular value region, improving both dynamic range of and trade-off between singular values.
+
+		% adopt the proposed geodesic \gls{rcg} and provide a numerical answer to the singular value shaping question.
+		% % to answer the channel singular value shaping question via numerical optimization.
+		% % to redistribute the singular values of a point-to-point \gls{mimo} channel.
+		% The {Pareto frontiers} of channel singular values are characterized by solving a series of weighted sum maximization problems, where the weight associated with each singular value can be positive, zero, or negative.
 		% optimizing their weighted sum, where the weights can be positive, zero, or negative.
 		% This problem is solved by the proposed geodesic \gls{rcg} algorithm.
-	The enclosed region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-	Results show that increasing \gls{bd}-\gls{ris} group size enlarges the singular value region, improving both dynamic range of and trade-off between singular values.
+		% The enclosed region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+		% Results show that increasing \gls{bd}-\gls{ris} group size enlarges the singular value region, improving both dynamic range of and trade-off between singular values.
 		% , where the dynamic range and trade-off between are both improved.
@@
 
-	Fourth, we leverage matrix analysis tools and provide an analytical answer to the singular value shaping question.
-	% revisit the channel singular value shaping problem from an analytical perspective via matrix analysis.
-	% To explore the ultimate shaping limits, we derive individual and collective singular value bounds for rank-deficient forward/backward channel and blocked direct channel.
-	% Asymptotic bounds shared by diagonal and \gls{bd}-\gls{ris} are derived in the former case, while exact bounds for unitary \gls{bd}-\gls{ris} are derived in the latter case.
-	Asymptotic channel singular value bounds applying to diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient forward/backward channel.
-	On the other hand, tight bounds for fully-connected \gls{bd}-\gls{ris} with finite number of elements are derived for blocked direct channel.
-	Results validate those bounds and emphasizes the shaping advantage of \gls{bd}-\gls{ris}.
-	This is the first work to quantify the singular value redistribution capability of \gls{bd}-\gls{ris} from either numerical or analytical perspective.
+		Fourth, we provide an analytical answer to the shaping question in two special channel conditions.
+		For rank-deficient forward/backward channel, we derive asymptotic singular value bounds applying to diagonal and \gls{bd}-\gls{ris}.
+		For blocked direct channel, we derive singular value bounds applying to fully-connected \gls{bd}-\gls{ris} with arbitrary number of elements.
+		Those bounds are validated by comparing with numerical results above.
+		Results show that for a fixed number of elements, \gls{bd}-\gls{ris} can approach the asymptotic bounds better than diagonal \gls{ris}.
+
+		% Results validate those bounds and emphasizes the shaping advantage of \gls{bd}-\gls{ris}.
+		% This is the first work to quantify the singular value redistribution capability of \gls{bd}-\gls{ris} from either numerical or analytical perspective.
+
+		% 1) rank-deficient forward/backward channel and 2) direct channel being blocked.
+
+		% % leverage matrix analysis tools and provide an analytical answer to the singular value shaping question.
+		% % revisit the channel singular value shaping problem from an analytical perspective via matrix analysis.
+		% % To explore the ultimate shaping limits, we derive individual and collective singular value bounds for rank-deficient forward/backward channel and blocked direct channel.
+		% % Asymptotic bounds shared by diagonal and \gls{bd}-\gls{ris} are derived in the former case, while exact bounds for unitary \gls{bd}-\gls{ris} are derived in the latter case.
+		% Asymptotic channel singular value bounds applying to diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient forward/backward channel.
+		% On the other hand, tight bounds for fully-connected \gls{bd}-\gls{ris} with finite number of elements are derived for blocked direct channel.
+		% Results validate those bounds and emphasizes the shaping advantage of \gls{bd}-\gls{ris}.
+		% This is the first work to quantify the singular value redistribution capability of \gls{bd}-\gls{ris} from either numerical or analytical perspective.
 		% Results validate those bounds and show that
@@
 
-	Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by two beamforming solutions: a local-optimal \gls{ao} approach and a low-complexity approach inspired by channel shaping insights.
-	The former updates active beamforming by eigenmode transmission and passive beamforming by proposed geodesic \gls{rcg} until convergence.
-	The latter suboptimally decouples the problem as channel power gain maximization at \gls{bd}-\gls{ris} and conventional \gls{mimo} transmission at transceiver, then solves both in closed form.
+	% We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
+	% Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior space alignment and channel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
+
+		Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by two solutions.
+		The first is a local-optimal approach through \gls{ao} that iteratively updates active and passive beamformers by eigenmode transmission and geodesic \gls{rcg}, respectively.
+		The second is a low-complexity approach that shape the channel for maximum power gain then perform eigenmode transmission.
+		Interestingly, the rate gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
+		It suggests that channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
+		% inspired by channel shaping that decouples the joint \gls{ris}-transceiver design.
+
+		% : a local-optimal \gls{ao} approach and a low-complexity approach inspired by channel shaping insights.
+		% The former updates active beamforming by eigenmode transmission and passive beamforming by proposed geodesic \gls{rcg} until convergence.
+		% The latter suboptimally decouples the problem as channel power gain maximization at \gls{bd}-\gls{ris} and conventional \gls{mimo} transmission at transceiver, then solves both in closed form.
 		% The problem is solved by a closed-form two-stage method.
-	Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than diagonal \gls{ris}, and the rate gap of two approaches diminishes as the \gls{bd}-\gls{ris} evolves from single-connected to fully-connected.
-	It suggests channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
+		% Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than diagonal \gls{ris}, and the rate gap of two approaches diminishes as the \gls{bd}-\gls{ris} evolves from diagonal to fully-connected.
+		% It suggests channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
 		% Interestingly, the rate difference between the optimal and low-complexity designs diminishes as the \gls{ris} evolves from diagonal to unitary.
@@
 		% The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
-	% Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
+		% Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (diagonal) to unitary (fully-connected).
 		% It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.
@@
 		% Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.
+	\end{subsection}
 
@@
 	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis and explore the performance limits, we assume a lossless asymmetric network without mutual coupling between scattering elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
-	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-unitary\footnote{Following footnote \ref{fn:symmetric}, we do not assume the scattering matrix to be symmetric.
-If required, one can enforce symmetry over the block-unitary result by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.}
+	To simplify the analysis, we assume a lossless asymmetric network without mutual coupling between scattering elements, as have been previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
+	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-unitary\footnote{Following footnote \ref{fn:symmetric}, we do not limit the scattering matrix to be symmetric.
+One can enforce symmetry over the result by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$ if necessary.}
 	\begin{equation}
@@
 	% radiation pattern and
-	circuit topology is modelled in the scattering matrix.
-
+	circuit topology has been modelled in the scattering matrix.
 	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (i.e., transmitter-receiver), backward (i.e., \gls{ris}-receiver), and forward (i.e., transmitter-\gls{ris}) channels, respectively.
@@
 	\end{equation}
-	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels for \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
+	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels associated with \gls{bd}-\gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
 	Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via \gls{bd}-\gls{ris} group $g$.
@@
 	\begin{itemize}
-		\item \emph{Channel rearrangement:} It refers to rearranging and recombining the backward and forward channel branches (i.e., entries of the channel matrix) associated with each group by their strength.
+		\item \emph{Channel rearrangement:} It refers to rearranging and recombining the backward and forward channel branches (i.e., entries of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$)
+		% associated with each group
+		by their strength.
 		% This unique feature of \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
 		% This unique feature of \gls{bd}-\gls{ris} exploits the spatial diversity by rearranging and combining the backward and forward channel branches within each group.
-		In \gls{siso}, diagonal \gls{ris} with perfect phase matching provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
+		In \gls{siso}, diagonal \gls{ris} with perfect phase matching can provide a maximum indirect channel gain $g_\mathrm{D}=\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$,
+		% Thanks to in-group connections,
+		while the in-group connections of
+		\gls{bd}-\gls{ris} can exploit spatial diversity and generalize this gain to
+		% this indirect channel gain to
+		$g_\mathrm{BD}=\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert$,
+		% $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$,
+		% $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,l} \rvert \lvert h_{\mathrm{F},g,\pi_g(l)} \rvert$,
+		where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are arbitrary permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
 		Note the first summation is over groups and the second summation is over permuted channels.
-		We thus conclude that \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
-		By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
+		By rearrangement inequality \cite[Inequality 10.2.1]{Hardy1952}, for \gls{bd}-\gls{ris} we have
+		\begin{equation}
+			g_\mathrm{BD} \le \sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi^\downarrow_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi^\downarrow_{\mathrm{F},g}(l)} \rvert,
+		\end{equation}
+		where $\pi^\downarrow_{\mathrm{B},g}$ and $\pi^\downarrow_{\mathrm{F},g}$ sort $\{\lvert h_{\mathrm{B},g,l} \rvert\}_{l=1}^L$ and $\{\lvert h_{\mathrm{F},g,l} \rvert\}_{l=1}^L$ in descending orders, respectively.
+		% are the descending permutations of $\lvert h_{\mathrm{B},g,l} \rvert$ and $\lvert h_{\mathrm{F},g,l} \rvert$, respectively.
+		That is to say, when the direct channel is blocked,
+		the maximum \gls{siso} channel gain is attained if the \gls{bd}-\gls{ris} pairs the $l$-th strongest backward and forward branches within each group.
+		% \footnote{Similarly, the minimum is attained when we pair the $l$-th strongest backward branch and the $L{-}l{+}1$-th strongest forward branch within each group.}
+		% We thus conclude that \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
+		% By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
 		% , providing up to \qty{62.5}{\percent} asymptotic power gain over diagonal \gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
-		Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.
+		Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude that {the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.}
 		\item \emph{Space alignment:} It refers to aligning the singular vectors of the direct, forward, and backward channels.
 		The \gls{bd}-\gls{ris} needs to strike a balance between the alignment of backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
-In \gls{siso}, singular vectors become scalars and space alignment boils down to phase matching, such that the optimal scattering matrix of group $g$ that maximizes the channel gain is
+In \gls{siso}, singular vectors become scalars and space alignment boils down to phase matching, such that the scattering matrix of group $g$ maximizing the channel gain is
 		\begin{equation}
@@
 		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-		Diagonal \gls{ris} with empty null space thus suffices for perfect phase matching in \gls{siso}.
+		It is thus apparent that diagonal \gls{ris} suffices
+		% Diagonal \gls{ris} thus suffices
+		for perfect phase matching in \gls{siso}.
 		When it comes to \gls{mimo}, element $g$ of diagonal \gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
 For element $g$ of diagonal \gls{ris}, the indirect channel $\mathbf{H}_g$ is rank-1 and the pinhole is $\Theta_g$.} indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
-		That is, the disadvantage of diagonal \gls{ris} in space alignment scales with \gls{mimo} dimensions.
+		Thus, we conclude that
+		% We can thus see that
+		{the disadvantage of diagonal \gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.}
 		% As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward spaces.
@@
 
-\begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Design by Geodesic \glsfmtshort{rcg}}
+\begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Design Frameworks}
 	% In this section, we first provide an overview on signal processing techniques for group-connected \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group and operates directly on the Stiefel manifold.
@@
 	\end{maxi!}
-	where the objective function $f(\mathbf{\Theta})$ can be any function of the \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$, for example, channel singular value (to be discussed in Section \ref{sc:singular_value}) and achievable rate (to be discussed in Section \ref{sc:power_rate}).
+	where the objective function $f(\mathbf{\Theta})$ can be any function of the \gls{bd}-\gls{ris} scattering matrix, for example, channel singular value (to be discussed in Section \ref{sc:singular_value}) and achievable rate (to be discussed in Section \ref{sc:power_rate}).
 	The feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$, which is non-convex and non-Euclidean.
-	Therefore, relevant optimization problems are usually solved by relax-then-project methods \cite{Fang2023} or universal non-geodesic manifold \gls{rcg} \cite{Li2023b,Li2023c,Bartoli2023}.
+	Therefore, relevant optimization problems are usually solved by relax-then-project methods \cite{Fang2023} or universal manifold \gls{rcg} \cite{Li2023b,Li2023c,Zhou2023}.
 	The former solves an unconstrained problem \eqref{ob:general} by quasi-Newton methods, then projects the solution back to the Stiefel manifold.
-	It has no guarantee of optimality and may suffer from numerical instability.
-	The latter generalizes the conjugate gradient methods to any Riemannian manifold, which updates the feasible point by progressing along the conjugate direction and projecting back to the manifold at each step.
-	In the following context, we first discuss the existing non-geodesic \gls{rcg} method and its drawbacks, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
-
-	\begin{subsection}{Non-Geodesic \glsfmtshort{rcg}}
+	It has no guarantee of optimality and usually suffers from poor performance.
+	The latter generalizes the conjugate gradient methods to Riemannian manifolds, which iteratively refines the solution by addition and retraction.
+	% progressing along the conjugate direction and retracting back to the manifold.
+	% refining the solution iteratively by progressing along the conjugate direction and projecting back to the manifold at each step.
+	% which progresse along the conjugate direction and projecting back to the manifold at each step
+	% updates the feasible point by progressing along the conjugate direction and projecting back to the manifold at each step.
+	In the following context, we first provide an overview on the general \gls{rcg} method that is widely adopted in diagonal and \gls{bd}-\gls{ris} literature, discuss its drawbacks inherited from the non-geodesic nature, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
+	% provide a brief overview on the general \gls{rcg} method used in \gls{bd}-\gls{ris} optimization, namely non-geodesic \gls{rcg}, and discuss its drawbacks.
+	% explain the existing manifold RCG method used in BD-RIS optimization, namely non-geodesic RCG, and discuss its drawbacks,
+	% first discuss the existing non-geodesic \gls{rcg} method and its drawbacks, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
+
+	\begin{subsection}{General (Non-Geodesic) \glsfmtshort{rcg}}
 		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
-		The universal \gls{rcg} method proposed in \cite{Absil2009,Pan2022d} is non-geodesic and applicable to optimization problems over arbitrary manifolds.
-		The main idea is to perform {additive} updates along the conjugate direction guided by the Riemannian gradient, then {project} the solution back onto the manifold.
+		The universal \gls{rcg} method proposed in \cite{Absil2009,Pan2022d} is applicable to optimization problems over arbitrary manifolds.
+		The idea is to perform {additive} updates along the conjugate direction guided by the Riemannian gradient, {project} the solution back onto the manifold, and repeat until convergence.
+		% It is non-geodesic because the updates constitute a zigzag path aided by the Euclidean space instead of carried entirely on the manifold.
+		% updates are not entirely on the manifold
+		% we progress along a direct path in the tangent space and departs from the manifold in each step.
+		% the updates are not entirely
+		% , at each step, we progress along a direct path in the tangent space and departs from the manifold in each step.
+		% project back to the manifold.
 		% update the feasible point by progressing along conjugate directions then project back to the manifold.
@@
 
-		The above method is called non-geodesic since the points are updated in the linear embedding spaces by addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction}, instead of on the Stiefel manifold itself.
+		The method is called non-geodesic since the addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction} in each step constitute a zigzag path departing from and returning to the manifold, instead of carried directly on the manifold.
+		% aided by the Euclidean space instead of carried entirely on the manifold.
+		% the points are updated in the linear embedding spaces by addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction}, instead of on the Stiefel manifold itself.
 		It converges to stationary points of the original problem but usually requires a large number of iterations due to inefficient operations in the Euclidean space.
-
+		% usually suffers from numerical instability
 		% additive update \eqref{eq:update_additive} in the Euclidean space and retraction \eqref{eq:retraction}.
@@
 		To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, since $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.
+		We would like to highlight that the proposed geodesic \gls{rcg} method has been tailored to the Stiefel manifold.
 
@@
 		Algorithm~\ref{ag:rcg} summarizes the proposed \gls{bd}-\gls{ris} design framework based on group-wise geodesic \gls{rcg}.
-		Compared to the non-geodesic approach, it leverages the Lie group properties to replace the add-then-retract update \eqref{eq:add_then_retract} with a multiplicative rotational update \eqref{eq:update_geodesic} along the geodesic.
+		Compared to the general non-geodesic approach, it leverages the Lie group properties to replace the add-then-retract update \eqref{eq:add_then_retract} with a multiplicative rotational update \eqref{eq:update_geodesic} along geodesics of the Stiefel manifold.
 		This leads to faster convergence and simplifies the step size tuning thanks to appropriate parameter space.
-		% Despite the difference in
 		Convergence to a local optimum is still guaranteed if not initialized at a stationary point.
 		Note that the group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
-		Since block-unitary matrices are also closed under multiplication, one can avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the block diagonal and nulling the other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, with potentially higher computational complexity and slower convergence.
+		Since the set of block-unitary matrices are algebraically closed under multiplication, one can also avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, with potentially higher computational complexity and slower convergence.
 	\end{subsection}
@@
 	Next, we numerically characterize the channel singular value region based on the proposed Algorithm \ref{ag:rcg}.
-	Finally, we derive some analytical singular value bounds in specific scenarios.
+	Finally, we derive some analytical singular value bounds in specific channel conditions.
 	\begin{subsection}{Toy Example}\label{sc:toy_example}
@@
 		% , where the former needs 2 reconfigurable impedances and the latter needs 3.
-		The extra performance gain comes purely from connecting both scattering elements, and a larger gain is expected an asymmetric reconfigurable component is available.
+		The extra performance gain comes purely from connecting both elements, and a larger gain is expected when an asymmetric reconfigurable component is available.
 		% and a larger gain is expected when an asymmetric connection is available.
@@
 	\begin{subsection}{Pareto Frontier Characterization}\label{sc:pareto_frontier}
-		We then characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel_equivalent} by maximizing their weighted sum
+		We now characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel_equivalent} by maximizing their weighted sum
 		\begin{maxi!}
@@
 
-		We then analyze the computational complexity of solving Pareto singular value problem \eqref{op:pareto} by Algorithm~\ref{ag:rcg}.
+		We now analyze the computational complexity of solving Pareto singular value problem \eqref{op:pareto} by Algorithm~\ref{ag:rcg}.
 		To update each \gls{bd}-\gls{ris} group, compact \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:pareto_gradient} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_translated} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:parameter_cg_geodesic} and conjugate direction \eqref{eq:direction_cg_geodesic} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:update_geodesic} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
-		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (line \ref{ln:armijo_start}--\ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
+		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (line \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
 	\end{subsection}
@@
 	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
-		We then discuss some analytical bounds related to channel singular values, which help us to explore and understand the channel shaping limits of passive \gls{ris}.
-
+		We also provide some analytical bounds related to channel singular values, which help us to explore the channel shaping limits of passive \gls{ris}.
+
+		\begin{definition}[Degree of freedom]
 			\gls{dof} (a.k.a. multiplexing gain) refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, which is defined as
@@
 			where $\rho$ is the \gls{snr}.
+
+		\end{definition}
+
 		\begin{proposition}[Degree of freedom]\label{pp:dof}
-			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
+			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than diagonal \gls{ris}.
 		\end{proposition}
@@
 		\end{proof}
+
+		Proposition \ref{pp:dof} suggests that we cannot hope for a \gls{dof} gain (i.e., more parallel channels) by interconnecting the scattering elements.
+		We thus focus on the question of reshaping the available channels through manipulation of the singular values.
+
+		% you cannot hope for degrees of freedom gain (i.e. more channels) thus we focus ont he question of reshaping of the available channels through manipulation of the singular values.
 
@@
 This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
-		An example is given in Corollary \ref{co:los} for \gls{los} channels (i.e., $k=1$)\footnote{We notice a similar eigenvalue result has been derived in \cite{Semmler2023} but is limited to diagonal \gls{ris}.}.
+		An example is given in Corollary \ref{co:los} for \gls{los} channels (i.e., $k=1$)\footnote{A similar eigenvalue result has been derived in \cite{Semmler2023} only for diagonal \gls{ris}.}.
 		% states that the $n$-th channel singular value can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$.
@@
 $n$-th) singular value of $\mathbf{T}$, that is,
-			If the forward or backward channel is \gls{los}, then a diagonal \gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
+			If at least one of forward and backward channels is \gls{los}, then a diagonal \gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
 			That is,
@@
 		It is apparent that any diagonal \gls{ris} can only achieve singular values $\mathrm{sv}(\mathbf{H}) = [8, 3]^\mathsf{T}$, but a fully connected \gls{bd}-\gls{ris} with $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can achieve $\mathrm{sv}(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-
-		Proposition \ref{pp:fully_connected} transforms the shaping capacity question to a mathematical one, namely how the singular values of matrix product are bounded by the singular values of its individual factors.
+		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this case.
+
+		Proposition \ref{pp:fully_connected} transforms the channel shaping capability question to a mathematical question: How the singular values of matrix product are bounded by the singular values of its individual factors.
 		Let $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le \bar{N}$.
@@
 
-		To achieve the equalities in Corollaries \eqref{co:sv_largest} -- \eqref{co:sum_power}, the \gls{ris} needs to completely align the spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		To achieve equalities in Corollaries \ref{co:sv_largest} -- \ref{co:sum_power}, the \gls{ris} needs to completely align the singular spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
 		The resulting scattering matrix is generally required to be unitary
@@
 		which can be concluded from \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in Appendix~\ref{ap:fully_connected}.
-		Interestingly, diagonal \gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
+		We notice that diagonal \gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
 		In such case, the equivalent channel reduces to $\mathbf{H} = \sigma_\mathrm{B} \sigma_\mathrm{F} \mathbf{u}_\mathrm{B} \mathbf{v}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ and the \gls{ris} only needs to align $\mathbf{v}_\mathrm{B}^\mathsf{H}$ and $\mathbf{u}_\mathrm{F}$ by
@@
 		which becomes a special case of \eqref{eq:scattering_siso}.
-		On the other hand, when $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both in Rayleigh fading, the expected maximum channel power gain $\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F} \bigr\}_{\max}$ can be evaluated as
+		However, in general diagonal \gls{ris} is not sufficient to achieve the upper bound of channel power gain.
+		This again highlights the benefit of \gls{bd}-\gls{ris} in reshaping available channels.
+		Finally, when $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ both follow Rayleigh fading, the maximum expected channel power gain $\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\}$ can be numerically evaluated as
 		\begin{equation}
@@
 		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(x_n)$ given by \cite[Equation 51]{Zanella2009}.
-		We notice \eqref{eq:power_gain_rayleigh} is a generalization of \cite[Equation 58]{Shen2020a} to \gls{mimo}.
-
-		Proposition \ref{pp:fully_connected} and Corollaries \ref{co:sv_largest} -- \ref{co:sum_power} provide a comprehensive answer to singular value bounds and channel power gain limits for fully-connected \gls{bd}-\gls{ris} with blocked direct channel.
+		We notice \eqref{eq:power_gain_rayleigh} is a generalization of \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo}, which unveils how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
+		% However, a closed-form expression is non-trivial due to the complexity of distribution of ordered eigenvalues of Wishart matrices.
+		% ordered Wishart matrix eigenvalue distribution.
+		% provides a benchmark for the channel power gain of \gls{bd}-\gls{ris} in Rayleigh fading channels.
+
+		Proposition \ref{pp:fully_connected} and Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} provide a comprehensive answer to singular value bounds and channel power gain limits for blocked direct channel with fully-connected \gls{bd}-\gls{ris}.
 		% understanding of the channel power gain limits of passive \gls{ris}.
 		% and suggest the impact of channel rearrangement and space alignment on redistributing channel singular values.
-		Tight bounds are inapplicable in more general cases since the direct-indirect channels and backward-forward channels cannot be completely aligned at the same time.
-		In such case, we can exploit optimization approaches from a singular value perspective (Section~\ref{sc:pareto_frontier}) or a power gain perspective (Section~\ref{sc:power}).
+		Tight bounds are generally inapplicable since the direct-indirect channels and backward-forward channels cannot be completely aligned at the same time.
+		In such case, we can invoke optimization approaches from a singular value perspective (Section~\ref{sc:pareto_frontier}) or a power gain perspective (Section~\ref{sc:power}).
 	\end{subsection}
@@
 			where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right compact singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-			We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power_passive} when the direct link is blocked and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
 		\end{remark}
+
+		It is worth noting that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power_passive} when the direct link is blocked and present, respectively.
+		However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
 
@@
 
-		We then analyze the computational complexity of solving channel gain maximization problem \eqref{op:power_passive} by Proposition \ref{pp:power}.
+		We now analyze the computational complexity of solving channel gain maximization problem \eqref{op:power_passive} by Proposition \ref{pp:power}.
 		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_matrix_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its compact \gls{svd} requires $\mathcal{O}(L^3)$ operations.
@@
 		\begin{subsubsection}{Low-Complexity Solution}\label{sc:low_complexity}
-			We then propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
+			We finally propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
 			The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_passive} by channel power gain maximization problem \eqref{op:power_passive}, then proceed to conventional eigenmode transmission \eqref{eq:precoder_eigenmode}.
@@
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
-			We observe that the smallest singular value can be enhanced up to \num{2e-4} by single-connected \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We observe that the smallest singular value can be enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
 			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
@@
 		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive} -- \eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
 		This implies that the \gls{ris}-transceiver design can often be decoupled via channel shaping with marginal performance loss.
@@
 	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds for rank-deficient forward/backward channel and blocked direct channel.
-	Specifically, the former is done by proposing an efficient \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization problems, which offers better objective value and faster convergence than existing methods.
+	Specifically, the former is done by proposing an efficient \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization problems, which converges much faster than existing methods.
 	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.

### 2024-06-18 main.tex
:balloon: Add code link

@@
 \begin{section}{Simulation Results}\label{sc:simulation}
-	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
+	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{The simulation code is publicly available at \url{https://github.com/snowztail/channel-shaping/}.}
 	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.

### 2024-07-09 main.tex
:construction: Addressing comments

@@
 \newacronym{bcd}{BCD}{Block Coordinate Descent}
+\newacronym{d}{D}{Diagonal}
 \newacronym{dof}{DoF}{Degree of Freedom}
@@
 \begin{abstract}
-	This paper investigates the extent to which a passive \gls{ris} can redistribute
+	% This paper investigates the extent to which a passive \gls{ris} can redistribute
+	% singular values of a point-to-point \gls{mimo} channel for power and rate gains.
 	% This paper investigates to what extent can a passive \gls{ris} redistribute
 	% singular values to achieve power and rate gains in point-to-point \gls{mimo} channels.
-	singular values of a point-to-point \gls{mimo} channel for power and rate gains.
 	% the limit to which
-	We depart from the conventional diagonal phase shift model and adopt a \gls{bd}-\gls{ris} architecture featuring element-wise connections for signal amplitude and phase control.
+	This paper investigates the capability of a passive \gls{ris} to redistribute the singular values of point-to-point \gls{mimo} channels for achieving power and rate gains.
+	We depart from the conventional \gls{d}-\gls{ris} with diagonal phase shift matrix
+	and adopt a \gls{bd} architecture featuring element-wise connections for signal amplitude and phase control.
+	% featuring element-wise connections for signal amplitude and phase control.
 	% featuring element-wise connections for amplitude and phase control.
@@
 	% The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
-	Specifically, we first provide
-	shaping insights by characterizing the
-	channel singular value region manipulated by diagonal and \gls{bd}-\gls{ris} via a novel geodesic manifold optimization.
+	Specifically, we first
+	provide shaping insights by characterizing
+	% characterize
+	the channel singular value regions attainable by \gls{d}-\gls{ris} and \gls{bd}-\gls{ris} via a novel geodesic optimization.
+	Analytical singular value bounds are then derived to explore their shaping limits in typical deployment scenarios.
 	% Pareto frontiers of channel singular values via a novel geodesic manifold optimization.
@@
 	% The resulting region comprehensively encapsulates most relevant metrics (e.g., spectral norm and condition number).
-	To explore the shaping limits, we also derive
+	% To explore the shaping limits, we also derive
 	% 0ol. individual and collective
-	analytical singular value bounds in special channel conditions.
-	% ? in two common scenarios: 1) forward/backward channel is rank-deficient and 2) direct channel is blocked.
+	% analytical singular value bounds for common \gls{ris} deployment scenarios.
+	% in special channel conditions.
+	% in two common scenarios: 1) forward/backward channel is rank-deficient and 2) direct channel is blocked.
 	% respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris} via matrix analysis.
@@
 	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
-	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by a local-optimal \gls{ao} approach and a suboptimal shaping-inspired two-stage approach.
+	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and then propose a shaping-inspired low-complexity approach.
 	%  over channel power gain maximization.
@@
 	% shaping-inspired approach.
-	Compared to diagonal \gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them.
-	% , compared to conventional diagonal \gls{ris}.
-	Results also highlight that the power and rate gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
-
+	Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values, the trade-off in manipulating them, and thus the channel power gain and achievable rate.
+	Those observations become more pronounced when \gls{mimo} and \gls{ris} dimensions increase.
+	% Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values as well as the trade-off in manipulating them.
+	% We also notice the power and rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
+	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence enhancing the \gls{mimo} multiplexing gain at low \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
 	% wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
@@
 \begin{IEEEkeywords}
-	Beyond diagonal reconfigurable intelligent surface, multi-input multi-output, manifold optimization, channel shaping, rate maximization.
+	Reconfigurable intelligent surface, channel shaping, rate maximization, manifold optimization.
 \end{IEEEkeywords}
@@
 		While passive beamforming at \gls{ris} suffers attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
-		Another \gls{ris} application is \emph{backscatter modulation} by periodically switching its reflection pattern within the channel coherence time.
-		This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or serving as individual information source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
+		Another \gls{ris} application is \emph{information modulation} by periodically switching its reflection pattern within the channel coherence time.
+		This creates a free-ride message stream with dual benefits: integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or serving as individual information source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
 		Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment.
-		It can compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for \gls{mimo} systems \cite{Ozdogan2020a}, and create artificial time diversity for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
+		It can compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the channel rank for \gls{mimo} systems \cite{Ozdogan2020a}, and create artificial time diversity for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
 		Channel shaping also provides a ubiquitous solution for different wireless systems, decoupling joint beamforming design by first optimizing the channel and then the transceiver.
@@
 		% no previous work has characterized the \gls{mimo} channel singular value region manipulated by any type of \gls{ris}.
-		Besides, most relevant literature \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} adopted a diagonal \gls{ris} model where each element is connected to a dedicated impedance and disconnected from others, such that wave impinging on one element is entirely scattered by the same element.
+		Besides, most relevant literature \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} adopted a \gls{d}-\gls{ris} model where each element is connected to a dedicated impedance and disconnected from others, such that wave impinging on one element is entirely scattered by the same element.
 		% is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
@@
 		The concept was soon generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a} that connects adjacent elements from the same group via  passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}.
-		This allows wave impinging on one element to propagate losslessly within the circuit and depart partially from any element in the same group.
+		This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
 		It can thus manipulate both amplitude and phase of the scattered wave while remaining passive, generalizing the scattering matrix to block-diagonal with unitary blocks.
@@
 		Many practical design challenges, such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}, have also been investigated in recent publications.
-		Its beamforming superiority over diagonal \gls{ris} has been studied extensively in \gls{siso} and \gls{miso} systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}, however, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
-		% On the other hand, the beamforming superiority of \gls{bd}-\gls{ris} over diagonal \gls{ris} has been extensively studied in \gls{siso} and \gls{miso} communication systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+		Its beamforming superiority over \gls{d}-\gls{ris} has been studied extensively in \gls{siso} and \gls{miso} systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}, however, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
+		% On the other hand, the beamforming superiority of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} has been extensively studied in \gls{siso} and \gls{miso} communication systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}.
 		% % , where the problems have been cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
@@
 		Channel rearrangement refers to rearranging and recombining the entries of transmitter-\gls{ris} and \gls{ris}-receiver channel matrices by their strength.
-		Space alignment generalizes phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to singular vector space in \gls{mimo}.
-		We highlight that the off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix exploits spatial diversity more effectively than diagonal \gls{ris}.
+		Space alignment generalizes phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to the singular vector space in \gls{mimo}.
+		We highlight that the off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix exploits spatial diversity more effectively than \gls{d}-\gls{ris}.
 		% This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems.
@@
 		Fourth, we provide an analytical answer to the shaping question in two special channel conditions.
-		For rank-deficient forward/backward channel, we derive asymptotic singular value bounds applying to diagonal and \gls{bd}-\gls{ris}.
+		For rank-deficient forward/backward channel, we derive asymptotic singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris}.
 		For blocked direct channel, we derive singular value bounds applying to fully-connected \gls{bd}-\gls{ris} with arbitrary number of elements.
 		Those bounds are validated by comparing with numerical results above.
-		Results show that for a fixed number of elements, \gls{bd}-\gls{ris} can approach the asymptotic bounds better than diagonal \gls{ris}.
+		Results show that for a fixed number of elements, \gls{bd}-\gls{ris} can approach the asymptotic bounds better than \gls{d}-\gls{ris}.
 
@@
 		% The problem is solved by a closed-form two-stage method.
-		% Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than diagonal \gls{ris}, and the rate gap of two approaches diminishes as the \gls{bd}-\gls{ris} evolves from diagonal to fully-connected.
+		% Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than \gls{d}-\gls{ris}, and the rate gap of two approaches diminishes as the \gls{bd}-\gls{ris} evolves from diagonal to fully-connected.
 		% It suggests channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
@@
 		% Fifth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-		% In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
+		% In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over \gls{d}-\gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
 		% The superiority stems from stronger \emph{channel rearrangement} and \emph{space alignment} capabilities empowered by in-group cooperation.
@@
 	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary block (i.e., $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$) that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
-	Note that diagonal \gls{ris} can be regarded as its extreme case with group size $L=1$.
+	Note that \gls{d}-\gls{ris} can be regarded as its extreme case with group size $L=1$.
 	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2024}, where the
@@
 		% This unique feature of \gls{bd}-\gls{ris} exploits the spatial diversity by rearranging and combining the backward and forward channel branches within each group.
-		In \gls{siso}, diagonal \gls{ris} with perfect phase matching can provide a maximum indirect channel gain $g_\mathrm{D}=\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$,
+		In \gls{siso}, \gls{d}-\gls{ris} with perfect phase matching can provide a maximum indirect channel gain $g_\mathrm{D}=\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$,
 		% Thanks to in-group connections,
@@
 		% By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
-		% , providing up to \qty{62.5}{\percent} asymptotic power gain over diagonal \gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
+		% , providing up to \qty{62.5}{\percent} asymptotic power gain over \gls{d}-\gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
 		Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude that {the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.}
@@
 		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-		It is thus apparent that diagonal \gls{ris} suffices
-		% Diagonal \gls{ris} thus suffices
+		It is thus apparent that \gls{d}-\gls{ris} suffices
+		% \gls{d}-\gls{ris} thus suffices
 		for perfect phase matching in \gls{siso}.
-		When it comes to \gls{mimo}, element $g$ of diagonal \gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
-For element $g$ of diagonal \gls{ris}, the indirect channel $\mathbf{H}_g$ is rank-1 and the pinhole is $\Theta_g$.} indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
+		When it comes to \gls{mimo}, element $g$ of \gls{d}-\gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
+For element $g$ of \gls{d}-\gls{ris}, the indirect channel $\mathbf{H}_g$ is rank-1 and the pinhole is $\Theta_g$.} indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
 		Thus, we conclude that
 		% We can thus see that
-		{the disadvantage of diagonal \gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.}
+		{the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.}
 		% As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward spaces.
@@
 	% For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
+\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
 	% This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
-	% Interestingly, the gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{S}=4$ \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
+	% Interestingly, the gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
 	% This is because space alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-	% That is, diagonal \gls{ris} is sufficient for space alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from channel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
-	% Now consider a diagonal \gls{ris} in \gls{mimo}.
+	% That is, \gls{d}-\gls{ris} is sufficient for space alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from channel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
+	% Now consider a \gls{d}-\gls{ris} in \gls{mimo}.
 	% Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
 	% Therefore, perfect space alignment of indirect channels through different elements is generally impossible.
-	% It means the disadvantage of diagonal \gls{ris} in space alignment and channel rearrangement scales with \gls{mimo} dimensions.
+	% It means the disadvantage of \gls{d}-\gls{ris} in space alignment and channel rearrangement scales with \gls{mimo} dimensions.
 	% We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
@@
 	% \begin{remark}
-	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and fully-connected \gls{bd}-\gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
+	% 	\gls{bd}-\gls{ris} reduces to \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
 	% \end{remark}
@@
 	% 	Individual forward and backward \gls{csi} are required for \gls{bd}-\gls{ris} designs.
-	% 	This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
+	% 	This is different from \gls{d}-\gls{ris} where estimating their product is usually sufficient.
 	% 	% Later we will show the potential benefits from the \gls{csi} overhead.
@@
 
-\begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Design Frameworks}
+\begin{section}{Group-Connected \glsfmtshort{bd}-\glsfmtshort{ris} Design Frameworks}
 	% In this section, we first provide an overview on signal processing techniques for group-connected \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group and operates directly on the Stiefel manifold.
@@
 
-	Most group-connected \gls{bd}-\gls{ris} design problems can be formulated in the following general form
+	This section aims for an efficient yet universal optimization framework for group-connected \gls{bd}-\gls{ris} design.
+	Most relevant optimization problems can be formulated as
 	\begin{maxi!}
@@
 	% updates the feasible point by progressing along the conjugate direction and projecting back to the manifold at each step.
-	In the following context, we first provide an overview on the general \gls{rcg} method that is widely adopted in diagonal and \gls{bd}-\gls{ris} literature, discuss its drawbacks inherited from the non-geodesic nature, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
+	In the following context, we first provide an overview on the general \gls{rcg} method that is widely adopted in \gls{d}- and \gls{bd}-\gls{ris} literature, discuss its drawbacks inherited from the non-geodesic nature, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
 	% provide a brief overview on the general \gls{rcg} method used in \gls{bd}-\gls{ris} optimization, namely non-geodesic \gls{rcg}, and discuss its drawbacks.
@@
 		\begin{enumerate}
-			\item \emph{Compute the Euclidean gradient \cite{Hjorungnes2007}:} The gradient of $f$ with respect to $\mathbf{\Theta}_g^*$ in the Euclidean space is
+			\item \emph{Compute the Euclidean gradient:} The gradient of $f$ with respect to $\mathbf{\Theta}_g^*$ in the Euclidean space is
 			\begin{equation}
@@
 		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} has 4 independent angular parameters
+		The \gls{d}-\gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} has 4 independent angular parameters
 		\begin{equation}
@@
 			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
-			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal \gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris}.}
+			\caption{$2 \times 2 \times 2$ channel singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is blocked.
+$\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
+			Their maximum and minimum have been marked explicitly on the plot.}
 			\label{fg:singular_trend}
@@
 		\end{equation*}
-		The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric fully-connected \gls{bd}-\gls{ris}.
-		In this example, we observe that both singular values can be manipulated up to\footnote{The percentage for manipulating the $n$-th channel singular value is calculated by $\eta_n = \frac{\max \sigma_n(\mathbf{H}) - \min \sigma_n(\mathbf{H})}{2 \bar{\sigma}_n(\mathbf{H})} \times 100\%$.
-In this case, we notice $\eta_1=\eta_2$ for both \gls{ris} architectures.} $9\%$ by diagonal \gls{ris} (using 2 reconfigurable impedances) and $42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (using 3 reconfigurable impedances).
-		% , where the former needs 2 reconfigurable impedances and the latter needs 3.
+		The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for \gls{d}-\gls{ris} and $(\alpha, \psi)$ for symmetric fully-connected \gls{bd}-\gls{ris}.
+		In this example, we observe that both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} (using 2 reconfigurable impedance) and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (using 3 reconfigurable impedance).
+		% , where the former needs 2 reconfigurable impedance and the latter needs 3.
 		The extra performance gain comes purely from connecting both elements, and a larger gain is expected when an asymmetric reconfigurable component is available.
@@
 		\begin{proposition}[Degree of freedom]\label{pp:dof}
-			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than diagonal \gls{ris}.
+			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
 		\end{proposition}
@@
 			If the minimum rank of forward and backward channels is $k$ ($k \le N$),
-			then for diagonal \gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
+			then for \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
 			\begin{subequations}
@@
 		if the forward and backward channels are at least rank $k$, then
-		% with a diagonal \gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements,
+		% with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements,
 		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
@@
 This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
-		An example is given in Corollary \ref{co:los} for \gls{los} channels (i.e., $k=1$)\footnote{A similar eigenvalue result has been derived in \cite{Semmler2023} only for diagonal \gls{ris}.}.
+		An example is given in Corollary \ref{co:los} for \gls{los} channels (i.e., $k=1$)\footnote{A similar eigenvalue result has been derived in \cite{Semmler2023} only for \gls{d}-\gls{ris}.}.
 		% states that the $n$-th channel singular value can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$.
@@
 		% \begin{corollary}[Extreme singular values\label{co:extreme}]
-		% 	If the minimum rank of forward and backward channels is $k$ ($k \le N$), then with a diagonal \gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
+		% 	If the minimum rank of forward and backward channels is $k$ ($k \le N$), then with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
 This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
@@
 $n$-th) singular value of $\mathbf{T}$, that is,
-			If at least one of forward and backward channels is \gls{los}, then a diagonal \gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
+			If at least one of forward and backward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
 			That is,
@@
 
-		We would like to highlight that Proposition \ref{pp:rank_deficient} holds for both diagonal and \gls{bd}-\gls{ris} with arbitrary number of elements, regardless of the presence of direct channel.
+		We would like to highlight that Proposition \ref{pp:rank_deficient} holds for both \gls{d}- and \gls{bd}-\gls{ris} with arbitrary number of elements, regardless of the presence of direct channel.
 		The bounds are asymptotically tight when the number of scattering elements approaches infinity.
-		On the other hand, we will show in Section \ref{sc:simulation} that with a finite number of elements, \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.
+		On the other hand, we will show in Section \ref{sc:simulation} that with a finite number of elements, \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris}.
 		Proposition \ref{pp:rank_deficient} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a selection guideline for scattering element number in a practical deployment scenario.
@@
 		\end{equation*}
-		It is apparent that any diagonal \gls{ris} can only achieve singular values $\mathrm{sv}(\mathbf{H}) = [8, 3]^\mathsf{T}$, but a fully connected \gls{bd}-\gls{ris} with $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can achieve $\mathrm{sv}(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+		It is apparent that any \gls{d}-\gls{ris} can only achieve singular values $\mathrm{sv}(\mathbf{H}) = [8, 3]^\mathsf{T}$, but a fully connected \gls{bd}-\gls{ris} with $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can achieve $\mathrm{sv}(\mathbf{H}) = [12, 2]^\mathsf{T}$.
 		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this case.
@@
 
-		Corollary \eqref{co:sv_bound_horn} is by far the most comprehensive singular value bound over Proposition~\ref{pp:fully_connected}, which is also recognized as a variation of Horn's inequality \cite{Bhatia2001}.
-		It is worth mentioning that the number of admissible triples (and bounds) grows exponentially with $\bar{N}$.
+		Corollary \eqref{co:sv_bound_horn} is by far the most comprehensive channel singular value bound attainable by passive \gls{ris} when the direct channel is blocked.
+		It is also recognized as a variation of Horn's inequality \cite{Bhatia2001}.
+		We observe that the number of admissible triples (and thus bounds) grows exponentially with $\bar{N}$.
 		For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $\bar{N}$ increases from 3 to 7.
@@
 		which can be concluded from \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in Appendix~\ref{ap:fully_connected}.
-		We notice that diagonal \gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
+		We notice that \gls{d}-\gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
 		In such case, the equivalent channel reduces to $\mathbf{H} = \sigma_\mathrm{B} \sigma_\mathrm{F} \mathbf{u}_\mathrm{B} \mathbf{v}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ and the \gls{ris} only needs to align $\mathbf{v}_\mathrm{B}^\mathsf{H}$ and $\mathbf{u}_\mathrm{F}$ by
@@
 		which becomes a special case of \eqref{eq:scattering_siso}.
-		However, in general diagonal \gls{ris} is not sufficient to achieve the upper bound of channel power gain.
+		However, in general \gls{d}-\gls{ris} is not sufficient to achieve the upper bound of channel power gain.
 		This again highlights the benefit of \gls{bd}-\gls{ris} in reshaping available channels.
@@
 		\end{table*}
-		We first compare in Table \ref{tb:complexity_test} the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in an $N_\mathrm{T}=N_\mathrm{S}=4$ system with \gls{bd}-\gls{ris} group size $L=4$.
+		We first compare in Table \ref{tb:complexity_test} the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in an $N_\mathrm{T}=N_\mathrm{R}=4$ system with \gls{bd}-\gls{ris} group size $L=4$.
 		The statistics are averaged over \num{100} independent runs.
@@
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
-			We observe that the smallest singular value can be enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We observe that the smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
 			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
@@
 					The blue (resp. red) bars are obtained by solving problem \eqref{op:pareto} with $\rho_n = -1$ (resp. $+1$) and $\rho_{n'} = 0$, $\forall n' \ne n$.
-					`D' means diagonal \gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
+					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
 					`rank-$k$' refers to the rank of the forward channel.
@@
 \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
-			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
+			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris} especially for a small $N_\mathrm{S}$.
 			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
@@
 			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
-			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.
+			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scales with forward and backward channel ranks.
 
@@
 				\caption{
-					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
+					Average maximum channel power gain versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
 					The direct channel is blocked.
@@
 			For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
+\subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
 			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
-			Interestingly, the gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{S}=4$ \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
+			Interestingly, the gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
 			This is because space alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-			That is, diagonal \gls{ris} is sufficient for space alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from channel rearrangement.
-			Now consider a diagonal \gls{ris} in \gls{mimo}.
+			That is, \gls{d}-\gls{ris} is sufficient for space alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from channel rearrangement.
+			Now consider a \gls{d}-\gls{ris} in \gls{mimo}.
 			Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
 			Therefore, perfect space alignment of indirect channels through different elements is generally impossible.
-			It means the disadvantage of diagonal \gls{ris} in space alignment and channel rearrangement scales with \gls{mimo} dimensions.
+			It means the disadvantage of \gls{d}-\gls{ris} in space alignment and channel rearrangement scales with \gls{mimo} dimensions.
 			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
@@
 			\caption{
-				Average maximum channel power versus \gls{ris} configuration.
+				Average maximum channel power gain versus \gls{ris} configuration.
 				`OP-left' and `OP-right' refer to the suboptimal solutions to problem \eqref{op:power_passive} by lossy transformation \eqref{op:standard_orthogonal_procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
@@
 		We first focus on channel power gain maximization problem \eqref{op:power_passive}.
-		Fig. \ref{fg:power_sx} shows the achievable channel power under different \gls{ris} configurations.
-		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} is even larger with direct link.
-		For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power as a 256-element diagonal \gls{ris} in Fig.
+		Fig. \ref{fg:power_sx} shows the maximum channel power under different \gls{ris} configurations.
+		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is even larger with direct link.
+		For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power gain as a 256-element \gls{d}-\gls{ris} in Fig.
 \subref*{fg:power_sx_txrx16}, but not in Fig.
@@
 				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
-				`D' means diagonal \gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
+				`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
 			}
@@
 		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
-		At a transmit power of \qty{10}{dB}, Fig.
-\subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to $N_\mathrm{T}=N_\mathrm{S}=4$ \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
-		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive} -- \eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
-		This implies that the \gls{ris}-transceiver design can often be decoupled via channel shaping with marginal performance loss.
-		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit and receive antennas and scattering elements.
+		At a transmit power $P = \qty{10}{dB}$, Fig.
+\subref*{fg:rate_beamforming} shows that introducing a 128-element \gls{d}-\gls{ris} to $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
+		A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
+		An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_passive} -- \eqref{eq:precoder_eigenmode} and the shaping-inspired solution \eqref{eq:scattering_power}, \eqref{eq:precoder_eigenmode} narrows at a larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+		This implies that joint \gls{ris}-transceiver designs can be decoupled with marginal performance loss by first shaping the wireless channel and then optimizing the precoder and combiner.
+		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} versus \gls{d}-\gls{ris}
+		increases with the number of transmit and receive antennas and scattering elements.
+		% Being consistent with the power gain results in Fig. \ref{fg:power_sx}, this phenomenon is more pronounced at a high \gls{snr}.
+		For $N_\mathrm{S}=128$ at $P = \qty{20}{dB}$,
+		the achievable rate ratio of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is \num{1.04}, \num{1.11}, and \num{1.13} for $N_\mathrm{T}=N_\mathrm{R}=1$, \num{4}, and \num{16}, respectively.
+		% increases from \num{1.04} in \gls{siso} to \num{1.11} for $N_\mathrm{T}=N_\mathrm{R}=4$ and \num{1.13} for $N_\mathrm{T}=N_\mathrm{R}=16$.
+		On the other hand, for $N_\mathrm{T}=N_\mathrm{R}=4$ at $P = \qty{20}{dB}$, the ratio evaluates to \num{1.03}, \num{1.08}, and \num{1.13} for $N_\mathrm{S}=16$, \num{64}, and \num{256}, respectively.
+		This phenomenon aligns with the power gain results in Fig. \ref{fg:power_sx} and highlight the shaping benefits of \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
+
 		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
 		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better trade-off between channels (c.f. Fig. \ref{fg:singular_pareto}).
-		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
+		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
 		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
@@
 	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
-	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
+	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than \gls{d}-\gls{ris}.
 	This translates to a wider dynamic range of and better tradeoff between singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
@@
 
+	It would be interesting to investigate the impact of channel shaping through \gls{ris} on other wireless applications such as sensing and far-field power transfer.
 	% One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
@@
 		\end{equation}
-		where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to diagonal \gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block-diagonal matrices of $L \times L$ unitary blocks.
+		where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to \gls{d}-\gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block-diagonal matrices of $L \times L$ unitary blocks.
 		Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
@@
 % 		In this case, a unitary $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
-% 		Interestingly, the result suggests that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
+% 		Interestingly, the result suggests that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than \gls{d}-\gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
 % 	\end{subsection}

### 2024-07-16 main.tex
:pencil: Update manuscript

@@
 \begin{document}
-\title{Channel Shaping Using Beyond Diagonal Reconfigurable Intelligent Surfaces}
+\title{Channel Shaping Using Beyond-Diagonal Reconfigurable Intelligent Surface:\\Analysis, Optimization, and Implications}
 \author{
@@
 	% We also notice the power and rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
-	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence enhancing the \gls{mimo} multiplexing gain at low \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
+	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence attaining the full \gls{dof} at lower \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
 	% wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
@@
 \begin{IEEEkeywords}
-	Reconfigurable intelligent surface, channel shaping, rate maximization, manifold optimization.
+	Reconfigurable intelligent surface, channel singular value redistribution, rate maximization, manifold optimization.
 \end{IEEEkeywords}
@@
 		First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping potential as channel rearrangement and space alignment.
-		% % systems
-		% interpret the channel shaping potential of \gls{bd}-\gls{ris} in \gls{mimo} as channel rearrangement and space alignment.
-		Channel rearrangement refers to rearranging and recombining the entries of transmitter-\gls{ris} and \gls{ris}-receiver channel matrices by their strength.
+		Channel rearrangement refers to rearranging and recombining the entries of forward (i.e., transmitter-\gls{ris}) and backward (i.e., \gls{ris}-receiver) channel matrices by their strength.
 		Space alignment generalizes phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to the singular vector space in \gls{mimo}.
-		We highlight that the off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix exploits spatial diversity more effectively than \gls{d}-\gls{ris}.
+		The former is uniquely attributed to the off-diagonal entries of the scattering matrix of \gls{bd}-\gls{ris}.
+
+		% We highlight that the off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix provides higher signal processing flexibility than \gls{d}-\gls{ris}.
+		% exploits more effectively than \gls{d}-\gls{ris}.
 		% This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems.
@@
 
-		Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization by two solutions.
-		The first is a local-optimal approach through \gls{ao} that iteratively updates active and passive beamformers by eigenmode transmission and geodesic \gls{rcg}, respectively.
-		The second is a low-complexity approach that shape the channel for maximum power gain then perform eigenmode transmission.
+		Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem through a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
+		The former updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.
+		The latter shapes the channel for maximum power gain and then performs eigenmode transmission.
 		Interestingly, the rate gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
-		It suggests that channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
+		We highlight that the power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
+		Besides, \gls{bd}-\gls{ris} can help to activate more streams and better approach the \gls{dof} than \gls{d}-\gls{ris} at low transmit \gls{snr}.
+		% \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence attaining the full \gls{dof} at lower \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
+
+		% Fifth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
+		% In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over \gls{d}-\gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
+		% The superiority stems from stronger \emph{channel rearrangement} and \emph{space alignment} capabilities empowered by in-group cooperation.
+		% It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
+
+		% is a local-optimal approach through \gls{ao} that iteratively updates active and passive beamformers by eigenmode transmission and geodesic \gls{rcg}, respectively.
+		% The second is a low-complexity approach that shape the channel for maximum power gain then perform eigenmode transmission.
+		% It suggests that channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
 		% inspired by channel shaping that decouples the joint \gls{ris}-transceiver design.
@@
 		by their strength.
-		% This unique feature of \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
-		% This unique feature of \gls{bd}-\gls{ris} exploits the spatial diversity by rearranging and combining the backward and forward channel branches within each group.
-		In \gls{siso}, \gls{d}-\gls{ris} with perfect phase matching can provide a maximum indirect channel gain $g_\mathrm{D}=\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$,
+		% This unique feature of \gls{bd}-\gls{ris} exploits \textcolor{red}{spatial diversity} effectively thanks to in-group connections.
+		% This unique feature of \gls{bd}-\gls{ris} exploits the \textcolor{red}{spatial diversity} by rearranging and combining the backward and forward channel branches within each group.
+		In \gls{siso}\footnote{Following previous notation, here we denote the direct channel as $h_\mathrm{D}$, the backward and forward channels as $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$ and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, whose $n$-th entries are $h_{\mathrm{B},n}$ and $h_{\mathrm{F},n}$, respectively.
+		The channels associated with \gls{bd}-\gls{ris} group $g$ are also denoted as $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{1 \times L}$, whose $l$-th entries are $h_{\mathrm{B},g,l}$ and $h_{\mathrm{F},g,l}$, respectively.}, \gls{d}-\gls{ris} with perfect phase matching can provide a maximum indirect channel gain $g_\mathrm{D}=\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$,
 		% Thanks to in-group connections,
-		while the in-group connections of
-		\gls{bd}-\gls{ris} can exploit spatial diversity and generalize this gain to
+		while \gls{bd}-\gls{ris} can exploit in-group connections and generalize it to
 		% this indirect channel gain to
@@
 		% \footnote{Similarly, the minimum is attained when we pair the $l$-th strongest backward branch and the $L{-}l{+}1$-th strongest forward branch within each group.}
-		% We thus conclude that \gls{bd}-\gls{ris} exploits spatial diversity effectively thanks to in-group connections.
+		% We thus conclude that \gls{bd}-\gls{ris} exploits \textcolor{red}{spatial diversity} effectively thanks to in-group connections.
 		% By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
@@
 		for perfect phase matching in \gls{siso}.
-		When it comes to \gls{mimo}, element $g$ of \gls{d}-\gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
+		When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a common phase shift to the rank-1 indirect channel matrix passing through itself.
+		We thus conclude that the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.
+		% When it comes to \gls{mimo}, element $g$ of \gls{d}-\gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
 For element $g$ of \gls{d}-\gls{ris}, the indirect channel $\mathbf{H}_g$ is rank-1 and the pinhole is $\Theta_g$.} indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
-		Thus, we conclude that
+		% Thus, we conclude that
 		% We can thus see that
-		{the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.}
+		% {the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.}
 		% As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward spaces.
@@
 	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
-	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
+	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician K-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
 	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
@@
 		A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_passive} -- \eqref{eq:precoder_eigenmode} and the shaping-inspired solution \eqref{eq:scattering_power}, \eqref{eq:precoder_eigenmode} narrows at a larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
-		This implies that joint \gls{ris}-transceiver designs can be decoupled with marginal performance loss by first shaping the wireless channel and then optimizing the precoder and combiner.
+		An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_passive} -- \eqref{eq:precoder_eigenmode} and the shaping-inspired solution \eqref{eq:scattering_power}, \eqref{eq:precoder_eigenmode} narrows at larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+		This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the precoder and combiner, which significantly simplifies the process at marginal performance cost.
 		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} versus \gls{d}-\gls{ris}
-		increases with the number of transmit and receive antennas and scattering elements.
+		increases with the number of transmit and receive antennas and scattering elements, especially at high \gls{snr}.
 		% Being consistent with the power gain results in Fig. \ref{fg:power_sx}, this phenomenon is more pronounced at a high \gls{snr}.
-		For $N_\mathrm{S}=128$ at $P = \qty{20}{dB}$,
+		For $N_\mathrm{S}=128$ and $P = \qty{20}{dB}$,
 		the achievable rate ratio of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is \num{1.04}, \num{1.11}, and \num{1.13} for $N_\mathrm{T}=N_\mathrm{R}=1$, \num{4}, and \num{16}, respectively.
 		% increases from \num{1.04} in \gls{siso} to \num{1.11} for $N_\mathrm{T}=N_\mathrm{R}=4$ and \num{1.13} for $N_\mathrm{T}=N_\mathrm{R}=16$.
-		On the other hand, for $N_\mathrm{T}=N_\mathrm{R}=4$ at $P = \qty{20}{dB}$, the ratio evaluates to \num{1.03}, \num{1.08}, and \num{1.13} for $N_\mathrm{S}=16$, \num{64}, and \num{256}, respectively.
-		This phenomenon aligns with the power gain results in Fig. \ref{fg:power_sx} and highlight the shaping benefits of \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
-
-		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
-		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better trade-off between channels (c.f. Fig. \ref{fg:singular_pareto}).
-		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
+		For $N_\mathrm{T}=N_\mathrm{R}=4$ and $P = \qty{20}{dB}$, this ratio amounts to \num{1.03}, \num{1.08}, and \num{1.13} for $N_\mathrm{S}=16$, \num{64}, and \num{256}, respectively.
+		Those observations align with the power gain results in Fig. \ref{fg:power_sx} and highlight the rate benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} in large-scale \gls{mimo} systems.
+		In the low power regime (\num{-20} to \qty{-10}{dB}), we also notice that the slope of the achievable rate of \gls{bd}-\gls{ris} is steeper than that of \gls{d}-\gls{ris}.
+		That is, \gls{bd}-\gls{ris} can help to activate more streams and better approach the \gls{dof} at a low transmit \gls{snr}.
+		This is particularly visible in Fig. \subref*{fg:rate_sx} where the topmost curve is almost a linear function of the transmit power.
+		% It is interesting to see that the topmost curve of Fig.
+\subref*{fg:rate_sx} is almost a linear function of the transmit power, suggesting that \gls{bd}-\gls{ris} can help to activate multiple streams and achieve full \gls{dof} at low transmit \gls{snr}.
+		This is expected from the shaping results in Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
+		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician K-factor increases and becomes indistinguishable in \gls{los} environment.
 		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.

### 2024-07-19 main.tex
:pencil: Update manuscript

@@
 \newacronym{ao}{AO}{Alternating Optimization}
-\newacronym{bd}{BD}{Beyond-Diagonal}
+\newacronym{bd}{BD}{Beyond Diagonal}
 \newacronym{bcd}{BCD}{Block Coordinate Descent}
@@
 \begin{document}
-\title{Channel Shaping Using Beyond-Diagonal Reconfigurable Intelligent Surface:\\Analysis, Optimization, and Implications}
+\title{Channel Shaping Using Beyond Diagonal Reconfigurable Intelligent Surface:\\Analysis, Optimization, and Enhanced Flexibility}
 \author{
@@
 	We depart from the conventional \gls{d}-\gls{ris} with diagonal phase shift matrix
-	and adopt a \gls{bd} architecture featuring element-wise connections for signal amplitude and phase control.
+	and adopt a \gls{bd} architecture not restricted to diagonal scattering matrix and featuring element-wise connections for extra wave manipulation flexibility.
 	% featuring element-wise connections for signal amplitude and phase control.
@@
 	% We also notice the power and rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
-	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence attaining the full \gls{dof} at lower \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
+	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence better approaching \gls{dof} at low \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
 	% wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
@@
 		Third, we provide a numerical answer to the shaping question by characterizing the Pareto frontiers of channel singular values.
-		The enclosed region generalizes most relevant metrics and provides an intuitive singular value shaping benchmark.
+		The enclosed region generalizes most relevant metrics and provides an intuitive shaping benchmark.
 		Results show that increasing \gls{bd}-\gls{ris} group size enlarges this region, improving the dynamic range of all singular values and the trade-off in manipulating them.
@@
 		Fourth, we provide an analytical answer to the shaping question in two special channel conditions.
-		For rank-deficient forward/backward channel, we derive asymptotic singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris}.
+		For rank-deficient forward/backward channel, we derive singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris} with asymptotically large number of elements.
 		For blocked direct channel, we derive singular value bounds applying to fully-connected \gls{bd}-\gls{ris} with arbitrary number of elements.
-		Those bounds are validated by comparing with numerical results above.
+		Those bounds are validated by comparing with the numerical results above.
 		Results show that for a fixed number of elements, \gls{bd}-\gls{ris} can approach the asymptotic bounds better than \gls{d}-\gls{ris}.
@@
 
-		Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem through a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
-		The former updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.
-		The latter shapes the channel for maximum power gain and then performs eigenmode transmission.
-		Interestingly, the rate gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
-		We highlight that the power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
-		Besides, \gls{bd}-\gls{ris} can help to activate more streams and better approach the \gls{dof} than \gls{d}-\gls{ris} at low transmit \gls{snr}.
+		Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
+		The former iteratively updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg}, until convergence.
+		The latter exploits the \gls{bd}-\gls{ris} to shape the channel for maximum power gain then performs eigenmode transmission.
+		% simply shapes the channel by \gls{bd}-\gls{ris} for maximum power gain and performs eigenmode transmission.
+		Interestingly, the rate deficit from the shaping-inspired approach diminishes as the \gls{bd}-\gls{ris} evolves towards fully-connected.
+		% gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
+		We conclude that: 1) channel shaping decouples joint beamforming for reduced design complexity; 2) the power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions; 3) at low transmit power, \gls{bd}-\gls{ris} can activate more streams and better approach \gls{dof} than \gls{d}-\gls{ris}, thanks to its higher flexibility of shaping the distribution of channel singular values.
+		% Interestingly, the rate gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
+		% Channel shaping helps to decouple joint beamforming by first designing the channel and then the transmitter.
+
+		% We highlight that the power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
+		% Besides, \gls{bd}-\gls{ris} can help to activate more streams and achieves higher \gls{dof} than \gls{d}-\gls{ris} at low transmit \gls{snr}.
 		% \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence attaining the full \gls{dof} at lower \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
@@
 		for perfect phase matching in \gls{siso}.
-		When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a common phase shift to the rank-1 indirect channel matrix passing through itself.
+		When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a scalar phase shift to the associated indirect channel matrix of size $N_\mathrm{R} \times N_\mathrm{T}$ defined in \eqref{eq:channel_equivalent}.
 		We thus conclude that the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.

### 2024-07-21 main.tex
:triangular_flag_on_post: TSP 240721

@@
 % \usepackage{setspace}
-% ! \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
+% \usepackage[compact]{titlesec}
+% % ! \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
 % \abovedisplayskip=1mm
@@
 \newacronym{d}{D}{Diagonal}
-\newacronym{dof}{DoF}{Degree of Freedom}
+\newacronym{dof}{DoF}{Degrees of Freedom}
 \newacronym{siso}{SISO}{Single-Input Single-Output}
@@
 
-		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California at San Diego, La Jolla CA 92093, USA (e-mail: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).
+		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California, San Diego, La Jolla CA 92093, USA (e-mail: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).
+
+		This work has been partially supported by UKRI grant EP/Y004086/1, EP/X040569/1, EP/Y037197/1, EP/X04047X/1, EP/Y037243/1.
 	}
@@
 	We depart from the conventional \gls{d}-\gls{ris} with diagonal phase shift matrix
-	and adopt a \gls{bd} architecture not restricted to diagonal scattering matrix and featuring element-wise connections for extra wave manipulation flexibility.
+	and adopt a \gls{bd} architecture that offers greater wave manipulation flexibility through element-wise connections.
+	% ? not restricted to diagonal scattering matrix and featuring element-wise connections for extra wave manipulation flexibility.
 	% featuring element-wise connections for signal amplitude and phase control.
@@
 	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
-	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and then propose a shaping-inspired low-complexity approach.
+	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a shaping-inspired low-complexity approach.
 	%  over channel power gain maximization.
@@
 	% shaping-inspired approach.
-	Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values, the trade-off in manipulating them, and thus the channel power gain and achievable rate.
-	Those observations become more pronounced when \gls{mimo} and \gls{ris} dimensions increase.
+	Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values, the trade-off in manipulating them, and thus the channel power and achievable rate.
+	Those observations become more pronounced when the number of \gls{ris} elements and \gls{mimo} dimensions increase.
 	% Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values as well as the trade-off in manipulating them.
 	% We also notice the power and rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
-	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence better approaching \gls{dof} at low \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
+	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence achieving the asymptotic \gls{dof} at low \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
 	% wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
@@
 		Another \gls{ris} application is \emph{information modulation} by periodically switching its reflection pattern within the channel coherence time.
-		This creates a free-ride message stream with dual benefits: integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or serving as individual information source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
-		Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment.
-		It can compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the channel rank for \gls{mimo} systems \cite{Ozdogan2020a}, and create artificial time diversity for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
-		Channel shaping also provides a ubiquitous solution for different wireless systems, decoupling joint beamforming design by first optimizing the channel and then the transceiver.
+		This creates a free-ride message stream with dual benefits: integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or serving as individual source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
+		Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment, for example, compensate for the Doppler effect \cite{Basar2021}, flatten frequency-selective channels \cite{Arslan2022}, improve \gls{mimo} channel rank \cite{Ozdogan2020a}, and artificially diversify channel over time for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
+		This helps to decouple joint beamforming problems into a channel shaping stage and a legacy transceiver design stage, providing a versatile solution for various wireless applications.
+		% provides a ubiquitous solution for various wireless applications by decoupling the joint \gls{ris}-transceiver design into a channel design stage and a legacy system design stage.
+		% decoupling joint beamforming design by first optimizing the channel and then the transceiver.
 		% decouples joint \gls{ris}-transceiver design by first optimizing the channel and then the system, providing a ubiquitous solution for different wireless applications
@@
 
-		Although above works offered inspiring glimpses into the channel shaping potential,
-		there exist no attempts to characterize the channel singular value region manipulated by passive \gls{ris}.
+		Although above works offered inspiring glimpses into the channel shaping potential of passive \gls{ris}, none attempted to disclose the entire attainable channel singular value region.
+		% to characterize the channel singular value region manipulated by passive \gls{ris}.
 		% no previous work has characterized the \gls{mimo} channel singular value region manipulated by any type of \gls{ris}.
-		Besides, most relevant literature \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} adopted a \gls{d}-\gls{ris} model where each element is connected to a dedicated impedance and disconnected from others, such that wave impinging on one element is entirely scattered by the same element.
+		Most relevant literature \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} have also been limited to a \gls{d}-\gls{ris} model where each element is connected to a dedicated impedance and disconnected from others.
+		As such, wave impinging on one element is entirely scattered by the same element.
 		% is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
-		This simple architecture is modelled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal.
-		The concept was soon generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a} that connects adjacent elements from the same group via  passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}.
+		This simple architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal.
+		The idea was soon generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}.
 		This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
-		It can thus manipulate both amplitude and phase of the scattered wave while remaining passive, generalizing the scattering matrix to block-diagonal with unitary blocks.
-		Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
+		It can thus manipulate both amplitude and phase of the scattered wave while remaining passive.
+		Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures by graph theory \cite{Nerini2024}.
 		\gls{bd}-\gls{ris}
@@
 		multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
-		Many practical design challenges, such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}, have also been investigated in recent publications.
-		Its beamforming superiority over \gls{d}-\gls{ris} has been studied extensively in \gls{siso} and \gls{miso} systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}, however, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
+		Practical challenges such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a} have also been studied in recent literature.
+		Its beamforming superiority over \gls{d}-\gls{ris} has been proved in \gls{siso} and \gls{miso} systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}, however, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
 		% On the other hand, the beamforming superiority of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} has been extensively studied in \gls{siso} and \gls{miso} communication systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}.
@@
 		% improve the spectral efficiency of massive \gls{mimo} systems where the direct link is blocked \cite{Mishra2024}.
-		massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, but was again limited to blocked direct channel and fully-connected \gls{bd}-\gls{ris}.
-		Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal and the \gls{bd}-\gls{ris} design problem is equivalent to \gls{siso} shaping.
+		massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, which again assumed blocked direct channel and fully-connected \gls{bd}-\gls{ris}.
+		Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal.
+		%  and the \gls{bd}-\gls{ris} design problem is equivalent to \gls{siso} shaping.
 
@@
 
-		This paper is motivated by the critical question:
+		This paper is motivated by a fundamental question:
 		\emph{What is the singular value (and power gain) shaping capability of a passive \gls{ris} in point-to-point \gls{mimo} channels?}
-		We aim for a comprehensive answer via theoretical analysis and numerical optimization.
+		We aim for a comprehensive answer via analysis and optimization.
 		The contributions are summarized below.
@@
 		First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping potential as channel rearrangement and space alignment.
-		Channel rearrangement refers to rearranging and recombining the entries of forward (i.e., transmitter-\gls{ris}) and backward (i.e., \gls{ris}-receiver) channel matrices by their strength.
-		Space alignment generalizes phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to the singular vector space in \gls{mimo}.
+		Channel rearrangement refers to rearranging and recombining the entries of backward (i.e., \gls{ris}-receiver) and forward (i.e., transmitter-\gls{ris}) channel matrices by their strength.
+		Space alignment generalizes the phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to the singular vector space in \gls{mimo}.
 		The former is uniquely attributed to the off-diagonal entries of the scattering matrix of \gls{bd}-\gls{ris}.
@@
 		Second, we propose a novel \gls{bd}-\gls{ris} design method that allows reshaping of the available channels through singular values manipulation.
-		Our method based on \gls{rcg} compares favorably with respect to existing solutions in that the updates are along the geodesics (i.e., the shortest path between two points in a Riemannian manifold) of the feasible domain to accelerate convergence.
-		It also works for general \gls{bd}-\gls{ris} optimization problems.
+		Our \gls{rcg} method compares favorably with respect to existing ones in that the updates are along the geodesics (i.e., the shortest path between two points in a Riemannian manifold) of the feasible domain to accelerate convergence.
+		It also works for general design problems of group-connected \gls{bd}-\gls{ris}.
 
@@
 
-		Fourth, we provide an analytical answer to the shaping question in two special channel conditions.
+		Fourth, we provide an analytical answer to the shaping question in typical deployment scenarios.
 		For rank-deficient forward/backward channel, we derive singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris} with asymptotically large number of elements.
@@
 
-		Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
+		Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a shaping-inspired low-complexity approach.
 		The former iteratively updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg}, until convergence.
@@
 		% gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
-		We conclude that: 1) channel shaping decouples joint beamforming for reduced design complexity; 2) the power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions; 3) at low transmit power, \gls{bd}-\gls{ris} can activate more streams and better approach \gls{dof} than \gls{d}-\gls{ris}, thanks to its higher flexibility of shaping the distribution of channel singular values.
+		We conclude that: 1) channel shaping decouples joint beamforming for reduced design complexity; 2) the power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions; 3) at low transmit power, \gls{bd}-\gls{ris} can activate more streams than \gls{d}-\gls{ris} and achieve the asymptotic \gls{dof}, thanks to its higher flexibility of shaping the distribution of channel singular values.
 		% Interestingly, the rate gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
@@
 	To simplify the analysis, we assume a lossless asymmetric network without mutual coupling between scattering elements, as have been previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
-	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-unitary\footnote{Following footnote \ref{fn:symmetric}, we do not limit the scattering matrix to be symmetric.
+	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-diagonal with unitary diagonal blocks\footnote{Following footnote \ref{fn:symmetric}, we do not limit the scattering matrix to be symmetric.
 One can enforce symmetry over the result by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$ if necessary.}
@@
 	% radiation pattern and
-	circuit topology has been modelled in the scattering matrix.
+	circuit topology has been modeled in the scattering matrix.
 	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (i.e., transmitter-receiver), backward (i.e., \gls{ris}-receiver), and forward (i.e., transmitter-\gls{ris}) channels, respectively.
@@
 			g_\mathrm{BD} \le \sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi^\downarrow_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi^\downarrow_{\mathrm{F},g}(l)} \rvert,
+			\label{eq:gain_rearrangement}
 		\end{equation}
@@
 		Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude that {the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.}
-		\item \emph{Space alignment:} It refers to aligning the singular vectors of the direct, forward, and backward channels.
-		The \gls{bd}-\gls{ris} needs to strike a balance between the alignment of backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
-In \gls{siso}, singular vectors become scalars and space alignment boils down to phase matching, such that the scattering matrix of group $g$ maximizing the channel gain is
+		\item \emph{Space alignment:} It refers to aligning the singular vector spaces of the direct, forward, and backward channels.
+		The \gls{bd}-\gls{ris} needs to strike a balance between the space alignment of backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
+In \gls{siso}, singular vectors reduce to scalars and space alignment reduce to phase matching, such that the scattering matrix of group $g$ maximizing the channel gain is
 		\begin{equation}
@@
 		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-		It is thus apparent that \gls{d}-\gls{ris} suffices
+		We notice that \gls{d}-\gls{ris} (i.e., $L=1$) suffices
 		% \gls{d}-\gls{ris} thus suffices
 		for perfect phase matching in \gls{siso}.
-		When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a scalar phase shift to the associated indirect channel matrix of size $N_\mathrm{R} \times N_\mathrm{T}$ defined in \eqref{eq:channel_equivalent}.
+		When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a scalar phase shift to the corresponding indirect channel matrix of size $N_\mathrm{R} \times N_\mathrm{T}$ defined in \eqref{eq:channel_equivalent}.
 		We thus conclude that the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.
@@
 
-\begin{section}{Group-Connected \glsfmtshort{bd}-\glsfmtshort{ris} Design Frameworks}
+\begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Design Frameworks}
 	% In this section, we first provide an overview on signal processing techniques for group-connected \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group and operates directly on the Stiefel manifold.
@@
 	\end{maxi!}
-	where the objective function $f(\mathbf{\Theta})$ can be any function of the \gls{bd}-\gls{ris} scattering matrix, for example, channel singular value (to be discussed in Section \ref{sc:singular_value}) and achievable rate (to be discussed in Section \ref{sc:power_rate}).
-	The feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$, which is non-convex and non-Euclidean.
-	Therefore, relevant optimization problems are usually solved by relax-then-project methods \cite{Fang2023} or universal manifold \gls{rcg} \cite{Li2023b,Li2023c,Zhou2023}.
-	The former solves an unconstrained problem \eqref{ob:general} by quasi-Newton methods, then projects the solution back to the Stiefel manifold.
-	It has no guarantee of optimality and usually suffers from poor performance.
-	The latter generalizes the conjugate gradient methods to Riemannian manifolds, which iteratively refines the solution by addition and retraction.
+	where the objective function $f(\mathbf{\Theta})$ can be any function of the \gls{bd}-\gls{ris} scattering matrix, for example, channel singular value (covered in Section \ref{sc:singular_value}), channel power gain (covered in Section \ref{sc:power_rate}), and achievable rate (covered in Section \ref{sc:power_rate}).
+	The feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ that is non-convex and non-Euclidean.
+	Therefore, most \gls{bd}-\gls{ris} optimization problems are solved by \emph{relax-then-project} methods \cite{Fang2023} or \emph{general manifold \gls{rcg}} \cite{Li2023b,Li2023c,Zhou2023}.
+	The former solves unconstrained problem \eqref{ob:general} by quasi-Newton methods then projects the solution back to domain \eqref{co:general_unitary}, which often ends up far from optimal.
+	The latter generalizes the conjugate gradient methods to Riemannian manifolds and iteratively updates the solution by addition and retraction.
+	% It has been widely adopted in \gls{d}- and \gls{bd}-\gls{ris} literature.
 	% progressing along the conjugate direction and retracting back to the manifold.
@@
 	% updates the feasible point by progressing along the conjugate direction and projecting back to the manifold at each step.
-	In the following context, we first provide an overview on the general \gls{rcg} method that is widely adopted in \gls{d}- and \gls{bd}-\gls{ris} literature, discuss its drawbacks inherited from the non-geodesic nature, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
+	In the following context, we briefly review the general \gls{rcg} method and discuss its drawbacks inherited from the non-geodesic nature, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
 	% provide a brief overview on the general \gls{rcg} method used in \gls{bd}-\gls{ris} optimization, namely non-geodesic \gls{rcg}, and discuss its drawbacks.
@@
 		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
-		The universal \gls{rcg} method proposed in \cite{Absil2009,Pan2022d} is applicable to optimization problems over arbitrary manifolds.
+		The general \gls{rcg} method proposed in \cite{Absil2009,Pan2022d} is applicable to optimization problems over arbitrary manifolds.
 		The idea is to perform {additive} updates along the conjugate direction guided by the Riemannian gradient, {project} the solution back onto the manifold, and repeat until convergence.
@@
 
-		The method is called non-geodesic since the addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction} in each step constitute a zigzag path departing from and returning to the manifold, instead of carried directly on the manifold.
+		The method is called non-geodesic since the addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction} constitute a zigzag path departing from and returning to the manifold.
 		% aided by the Euclidean space instead of carried entirely on the manifold.
@@
 	\begin{subsection}{Geodesic \glsfmtshort{rcg}}
-		Before introducing geodesic \gls{rcg}, we revisit some basic concepts in differential geometry and Lie algebra.
+		Before introducing geodesic \gls{rcg}, we revisit some basic concepts in differential geometry.
 		% \cite{Abrudan2008,Abrudan2009}.
@@
 		where an appropriate $\mu$ may be obtained by the Armijo rule.
-		To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, since $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.
-		We would like to highlight that the proposed geodesic \gls{rcg} method has been tailored to the Stiefel manifold.
+		To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, that is, $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.
+		We highlight that the proposed geodesic \gls{rcg} method has been tailored to the Stiefel manifold.
 
@@
 		Note that the group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
-		Since the set of block-unitary matrices are algebraically closed under multiplication, one can also avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, with potentially higher computational complexity and slower convergence.
+		Since the set of block-unitary matrices are algebraically closed under multiplication, one can also avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) the Euclidean gradient \eqref{eq:gradient_euclidean}, which can further accelerate the algorithm when the number of group is large.
 	\end{subsection}
@@
 	In this section, we first provide a toy example to illustrate the channel shaping advantage of \gls{bd}-\gls{ris} architecture.
-	Next, we numerically characterize the channel singular value region based on the proposed Algorithm \ref{ag:rcg}.
+	Next, we numerically characterize the attainable channel singular value region on top of Algorithm \ref{ag:rcg}.
 	Finally, we derive some analytical singular value bounds in specific channel conditions.
 	\begin{subsection}{Toy Example}\label{sc:toy_example}
-		We first illustrate the channel shaping capabilities of different \gls{ris} models by a toy example.
+		We showcase the channel shaping capabilities of different \gls{ris} models by a toy example.
 		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-		The \gls{d}-\gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} has 4 independent angular parameters
+		The \gls{d}-\gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} can be modeled by 4 independent angular parameters
 		\begin{equation}
@@
 		\end{figure}
-		Fig.~\ref{fg:singular_trend} compares the achievable singular values of one typical channel realization, where the direct channel is blocked and the forward and backward channels are normalized Rayleigh fading
+		Fig.~\ref{fg:singular_trend} compares the achievable singular values of one typical channel realization, where the backward and forward channels are given by
 		\begin{equation*}
@@
 		\end{equation*}
-		The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for \gls{d}-\gls{ris} and $(\alpha, \psi)$ for symmetric fully-connected \gls{bd}-\gls{ris}.
+		The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for \gls{d}-\gls{ris} and $(\alpha, \psi)$ for symmetric \gls{bd}-\gls{ris}.
 		In this example, we observe that both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} (using 2 reconfigurable impedance) and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (using 3 reconfigurable impedance).
 		% , where the former needs 2 reconfigurable impedance and the latter needs 3.
-		The extra performance gain comes purely from connecting both elements, and a larger gain is expected when an asymmetric reconfigurable component is available.
+		% It is interesting that the huge difference comes purely from connecting both elements.
+		Such a large gain comes from simply connecting both elements, and it can be even larger using an asymmetric component.
+		% an even larger gain is expected when an asymmetric reconfigurable component is available.
+		% An even larger gain is expected when an asymmetric reconfigurable component is available.
 		% and a larger gain is expected when an asymmetric connection is available.
@@
 		To update each \gls{bd}-\gls{ris} group, compact \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:pareto_gradient} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_translated} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:parameter_cg_geodesic} and conjugate direction \eqref{eq:direction_cg_geodesic} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:update_geodesic} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
-		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (line \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
+		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., line \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
 	\end{subsection}
@@
 	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
-		We also provide some analytical bounds related to channel singular values, which help us to explore the channel shaping limits of passive \gls{ris}.
-
-		\begin{definition}[Degree of freedom]
-			\gls{dof} (a.k.a. multiplexing gain) refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, which is defined as
+		We also provide some analytical bounds related to channel singular values, which help us to explore the limits of channel shaping using passive \gls{ris}.
+
+		\begin{definition}[Degrees of freedom]
+			\gls{dof} (a.k.a. multiplexing gain) refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, which is defined asymptotically as
 			\begin{equation}
@@
 
-		\begin{proposition}[Degree of freedom]\label{pp:dof}
+		\begin{proposition}[Degrees of freedom]\label{pp:dof}
 			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
@@
 
-		Proposition \ref{pp:dof} suggests that we cannot hope for a \gls{dof} gain (i.e., more parallel channels) by interconnecting the scattering elements.
+		Proposition \ref{pp:dof} suggests that we cannot hope for a \gls{dof} gain (i.e., more parallel channels) by simply connecting the \gls{ris} elements.
 		We thus focus on the question of reshaping the available channels through manipulation of the singular values.
@@
 			% If the forward or backward channel is rank-$k$ ($k \le N$),
-			If the minimum rank of forward and backward channels is $k$ ($k \le N$),
+			If the minimum rank of backward and forward channels is $k$ ($k \le N$),
 			then for \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
@@
 		Inequality \eqref{iq:sv_bound_enlarge} states that
-		if the forward and backward channels are at least rank $k$, then
+		if the backward and backward channels are at least rank $k$, then
 		% with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements,
@@
 This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
-		An example is given in Corollary \ref{co:los} for \gls{los} channels (i.e., $k=1$)\footnote{A similar eigenvalue result has been derived in \cite{Semmler2023} only for \gls{d}-\gls{ris}.}.
+		An example is given in Corollary \ref{co:los} for \gls{los} channels (i.e., $k=1$)\footnote{A similar eigenvalue result for \gls{d}-\gls{ris} has been derived in \cite{Semmler2023}.}.
 		% states that the $n$-th channel singular value can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$.
@@
 $n$-th) singular value of $\mathbf{T}$, that is,
-			If at least one of forward and backward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
+			If at least one of backward and forward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
 			That is,
@@
 
-		We would like to highlight that Proposition \ref{pp:rank_deficient} holds for both \gls{d}- and \gls{bd}-\gls{ris} with arbitrary number of elements, regardless of the presence of direct channel.
+		We highlight that Proposition \ref{pp:rank_deficient} is an asymptotic result and the inequalities apply to \gls{d}- and \gls{bd}-\gls{ris} with arbitrary number of elements, regardless of the presence of direct channel.
 		The bounds are asymptotically tight when the number of scattering elements approaches infinity.
 		On the other hand, we will show in Section \ref{sc:simulation} that with a finite number of elements, \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris}.
-		Proposition \ref{pp:rank_deficient} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a selection guideline for scattering element number in a practical deployment scenario.
+		Proposition \ref{pp:rank_deficient} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a reference for choosing the number of scattering elements in a practical deployment scenario.
 
@@
 
-		Proposition \ref{pp:fully_connected} states that if the direct channel is blocked and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are the singular value bounds on the product of unitary-transformed forward and backward channels.
+		Proposition \ref{pp:fully_connected} states that if the direct channel is blocked and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are the singular value bounds on the product of unitary-transformed backward and forward channels.
 		% , a group-connected \gls{bd}-\gls{ris} in its most powerful form can manipulate the channel singular values to any possible state with zero power loss.
@@
 		\end{equation*}
-		It is apparent that any \gls{d}-\gls{ris} can only achieve singular values $\mathrm{sv}(\mathbf{H}) = [8, 3]^\mathsf{T}$, but a fully connected \gls{bd}-\gls{ris} with $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can achieve $\mathrm{sv}(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this case.
-
-		Proposition \ref{pp:fully_connected} transforms the channel shaping capability question to a mathematical question: How the singular values of matrix product are bounded by the singular values of its individual factors.
+		It is obvious that any \gls{d}-\gls{ris} can only attain $\mathrm{sv}(\mathbf{H}) = [8, 3]^\mathsf{T}$ while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ results in $\mathrm{sv}(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+		% We thus conclude that a fully-connected \gls{bd}-\gls{ris} can apply right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, which widens channel singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this example.
+
+		% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this case.
+
+		Proposition \ref{pp:fully_connected} is important since it transforms the channel shaping question to a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
 		Let $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le \bar{N}$.
@@
 
-		Corollary \eqref{co:sv_bound_horn} is by far the most comprehensive channel singular value bound attainable by passive \gls{ris} when the direct channel is blocked.
-		It is also recognized as a variation of Horn's inequality \cite{Bhatia2001}.
+		Corollary \eqref{co:sv_bound_horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is the most comprehensive channel singular value bound attainable by passive \gls{ris} when the direct channel is blocked.
 		We observe that the number of admissible triples (and thus bounds) grows exponentially with $\bar{N}$.
@@
 		Next, we showcase some useful inequalities enclosed by \eqref{iq:sv_bound_fc}.
-		Readers are referred to \cite[Chapter 16, 24]{Hogben2013} for more examples.
+		Interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} for more information.
 
@@
 
-		\begin{corollary}[Lower bound on the product of last $k$ singular values\label{co:sv_product_smallest}]
+		\begin{corollary}[Lower bound on the product of last $k$ singular values\label{co:sv_product_smallest}]\footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
 			\begin{equation}
@@
 		\end{proof}
-
-		Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., unequal number of transmit and receive antennas and scattering elements) as the lower bounds would coincide at zero.
 
@@
 			% The channel power gain is upper bounded by the sum of sorted element-wise power product of backward and forward channels
-			The channel power gain is upper bounded by the sum of sorted element-wise product of squared singular values of backward and forward channels
+			The channel power gain is upper bounded by the sum of element-wise product of squared singular values of backward and forward channels
 			\begin{equation}
@@
 
-		To achieve equalities in Corollaries \ref{co:sv_largest} -- \ref{co:sum_power}, the \gls{ris} needs to completely align the singular spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		To achieve equalities in Corollaries \ref{co:sv_largest} -- \ref{co:sum_power}, the \gls{ris} needs to completely align the singular vector spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
 		The resulting scattering matrix is generally required to be unitary
@@
 		This again highlights the benefit of \gls{bd}-\gls{ris} in reshaping available channels.
-		Finally, when $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ both follow Rayleigh fading, the maximum expected channel power gain $\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\}$ can be numerically evaluated as
-		\begin{equation}
-			\sum_{n=1}^N \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x_n) d x_n \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x_n) d x_n,
+		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the maximum expected channel power gain can be numerically evaluated as
+		\begin{equation}
+			\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\} = \sum_{n=1}^N \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x) d x,
 			\label{eq:power_gain_rayleigh}
 		\end{equation}
-		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(x_n)$ given by \cite[Equation 51]{Zanella2009}.
-		We notice \eqref{eq:power_gain_rayleigh} is a generalization of \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo}, which unveils how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
+		% \begin{equation}
+		% 	\begin{split}
+		% 		\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\}
+		% 		& = \sum_{n=1}^N \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x_n) d x_n \\
+		% 		& \quad \times \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x_n) d x_n,
+		% 	\end{split}
+		% 	\label{eq:power_gain_rayleigh}
+		% \end{equation}
+		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(x)$ given by \cite[Equation 51]{Zanella2009}.
+		We note that \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain attainable by \gls{bd}-\gls{ris} \cite[Equation 58]{Shen2020a} to \gls{mimo} and models the contribution of transmit and receive antennas under double Rayleigh fading.
+		In Section \ref{sc:simulation}, we will numerically evaluate the channel power gain and compare it with the theoretical upper bound.
+
+		% Expression \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo} and unveils
+
+		% , unveiling how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
+		% is a generalization of \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo}, which unveils how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
 		% However, a closed-form expression is non-trivial due to the complexity of distribution of ordered eigenvalues of Wishart matrices.
@@
 
-		Proposition \ref{pp:fully_connected} and Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} provide a comprehensive answer to singular value bounds and channel power gain limits for blocked direct channel with fully-connected \gls{bd}-\gls{ris}.
+		Proposition \ref{pp:fully_connected} and Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} provide a comprehensive answer to the shaping capability question in terms of singular value bounds and channel power gain limits.
 		% understanding of the channel power gain limits of passive \gls{ris}.
 		% and suggest the impact of channel rearrangement and space alignment on redistributing channel singular values.
-		Tight bounds are generally inapplicable since the direct-indirect channels and backward-forward channels cannot be completely aligned at the same time.
+		% When the direct channel is present,
+		% Similar results are inapplicable
+		Extending those results to the case of direct channel is non-trivial since the singular vector spaces of direct-indirect channels and backward-forward channels cannot be aligned at the same time.
 		In such case, we can invoke optimization approaches from a singular value perspective (Section~\ref{sc:pareto_frontier}) or a power gain perspective (Section~\ref{sc:power}).
@@
 	\label{sc:power_rate}
+	In this section, we solve channel power gain maximization problem in closed-form and then extend the discussion to achievable rate maximization problem.
+	The implication of the former on the latter is investigated.
+
 	\begin{subsection}{Channel Power Gain}\label{sc:power}
@@
 			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{\label{cs:power_block_unitary}}{}
 		\end{maxi!}
 		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with fully-connected \gls{bd}-\gls{ris} \eqref{eq:scattering_fc_optimal}.
-		The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative space alignments.
+		Solving \eqref{op:power_passive} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
+		% The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative space alignments.
 
@@
 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_block_unitary}}{}
+				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_unitary}}{}
 			\end{mini!}
-			which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary but still has no trivial solution.
+			which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary \eqref{cs:power_unitary} but still has no trivial solution.
 			One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
@@
 		However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
-
 		Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power_passive} with arbitrary group size.
@@
 			Both steps are solved in closed form and the computational complexity is $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr) + N N_\mathrm{T} N_\mathrm{R}\bigr)$.
-			While suboptimal, this shaping-inspired solution avoids outer iterations and implements inner iterations more efficiently.
+			While suboptimal, this shaping-inspired solution avoids outer iterations and efficiently handles inner iterations.
 		\end{subsubsection}
@@
 \begin{section}{Simulation Results}\label{sc:simulation}
-	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{The simulation code is publicly available at \url{https://github.com/snowztail/channel-shaping/}.}
+	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{The simulation code is publicly available at \url{https://github.com/snowztail/channel-shaping}.}
 	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
@@
 		The statistics are averaged over \num{100} independent runs.
-		It is observed that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (up to 3$\times$) lower number of iterations and shorter (up to 4$\times$) computational time than the non-geodesic method.
-		The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially in large-scale \gls{bd}-\gls{ris} design problems.
+		It is observed that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) computational time than the non-geodesic method.
+		The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially for large-scale \gls{bd}-\gls{ris} design problems.
 	\end{subsection}
@@
 				}
-				\caption{Pareto frontiers of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel reshaped by a \gls{ris}.}
+				\caption{Pareto frontiers of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel reshaped by \gls{bd}-\gls{ris}.}
 				\label{fg:singular_pareto}
@@
 			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
-			It suggests the design freedom from larger group size allows better alignment of multiple spaces simultaneously.
+			It suggests the design flexibility from larger group size allows better alignment of multiple singular vector spaces simultaneously.
 			% not only provides a better trade-off in channel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
@@
 \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} thanks to its superior channel shaping capability, but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of reconfigurable inter-connection between elements.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of reconfigurable inter-connections between elements.
 		\end{subsubsection}
@@
 			Those observations align with Proposition \ref{pp:rank_deficient}.
-			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
+			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both backward and forward channels are full-rank.
 			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
-			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scales with forward and backward channel ranks.
+			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scales with backward and forward channel ranks.
 
@@
 \subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
-			Interestingly, the gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
-			This is because space alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-			That is, \gls{d}-\gls{ris} is sufficient for space alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from channel rearrangement.
-			Now consider a \gls{d}-\gls{ris} in \gls{mimo}.
-			Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-			Therefore, perfect space alignment of indirect channels through different elements is generally impossible.
-			It means the disadvantage of \gls{d}-\gls{ris} in space alignment and channel rearrangement scales with \gls{mimo} dimensions.
+			It comes purely from channel rearrangement in \eqref{eq:gain_rearrangement} and aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite[Equation 30]{Shen2020a}.
+			Interestingly, this relative power gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig.
+\subref*{fg:power_bond_txrx4_nd}, which can also be predicted from the expectation analysis \eqref{eq:power_gain_rayleigh}.
 			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
@@
 		An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_passive} -- \eqref{eq:precoder_eigenmode} and the shaping-inspired solution \eqref{eq:scattering_power}, \eqref{eq:precoder_eigenmode} narrows at larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
-		This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the precoder and combiner, which significantly simplifies the process at marginal performance cost.
+		This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the active beamformer, which significantly simplifies the process at marginal performance cost.
 		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} versus \gls{d}-\gls{ris}
@@
 		In the low power regime (\num{-20} to \qty{-10}{dB}), we also notice that the slope of the achievable rate of \gls{bd}-\gls{ris} is steeper than that of \gls{d}-\gls{ris}.
-		That is, \gls{bd}-\gls{ris} can help to activate more streams and better approach the \gls{dof} at a low transmit \gls{snr}.
+		That is, \gls{bd}-\gls{ris} can help to activate more streams and achieve the asymptotic \gls{dof} at a low transmit \gls{snr}.
 		This is particularly visible in Fig. \subref*{fg:rate_sx} where the topmost curve is almost a linear function of the transmit power.
@@
 \subref*{fg:rate_sx} is almost a linear function of the transmit power, suggesting that \gls{bd}-\gls{ris} can help to activate multiple streams and achieve full \gls{dof} at low transmit \gls{snr}.
-		This is expected from the shaping results in Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
+		It is expected from the shaping results in Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
 		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician K-factor increases and becomes indistinguishable in \gls{los} environment.
@@
 	This translates to a wider dynamic range of and better tradeoff between singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
-	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds for rank-deficient forward/backward channel and blocked direct channel.
+	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds for practical deployment scenarios.
 	Specifically, the former is done by proposing an efficient \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization problems, which converges much faster than existing methods.
-	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
-	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior space alignment and channel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
-
-	It would be interesting to investigate the impact of channel shaping through \gls{ris} on other wireless applications such as sensing and far-field power transfer.
+	We also present two beamforming designs for rate maximization problem, one for optimal performance and the other exploits channel shaping for lower complexity.
+	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior space alignment and channel rearrangement capability, which scales with the number of elements, group size, and \gls{mimo} dimensions.
+
+	% It would be interesting to investigate the impact of channel shaping through \gls{ris} on other wireless applications such as sensing and far-field power transfer.
 	% One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.

### 2024-07-23 assets/simulation/singular_bound_rank2_sx128.tex
:ambulance: Fix arXiv render issue

@@
 ]
-\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
 0.8375	0.00142543267002251\\
@@
 
-\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
 1.1625	0.00142543579700608\\

### 2024-11-16 main.tex
:ambulance: Fix arXiv render issue
:construction: Adding Corollary 3.3

@@
 \usepackage[makeroom]{cancel}
+% \usepackage{cases}
 \usepackage[american]{circuitikz}
@@
 
+% amsmath
+\DeclareMathOperator{\diag}{diag}
+\DeclareMathOperator{\tr}{tr}
+\DeclareMathOperator{\sv}{sv}
+\DeclareMathOperator{\card}{card}
+
 % amsthm
 \newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 \newtheorem{proposition}{Proposition}
@@
 \usepgfplotslibrary{groupplots,patchplots}
-\pgfplotsset{compat=newest}
+\pgfplotsset{compat=1.18}
 \pgfplotsset{every axis/.append style={
@@
 		% However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
-		The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a fully-connected \gls{bd}-\gls{ris}-aided \gls{mimo} system where the direct link is blocked.
+		The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a fully-connected \gls{bd}-\gls{ris}-aided \gls{mimo} system where the direct channel is negligible.
 % 		The work
@@
 % for improved spectral efficiency
-% 		% with blocked direct link and \gls{bd}-\gls{ris}.
+% 		% with negligible direct link and \gls{bd}-\gls{ris}.
 % 		% Those assumptions simplify the problem but limit the generality of the results.
 		A transmitter-side \gls{bd}-\gls{ris} was introduced to
-		% improve the spectral efficiency of massive \gls{mimo} systems where the direct link is blocked \cite{Mishra2024}.
-		massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, which again assumed blocked direct channel and fully-connected \gls{bd}-\gls{ris}.
+		% improve the spectral efficiency of massive \gls{mimo} systems where the direct channel is negligible \cite{Mishra2024}.
+		massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, which again assumed negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
 		Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal.
@@
 	\begin{subsection}{Contributions}
+		\label{sc:contributions}
 		% We notice that there lacks a comprehensive study of \gls{bd}-\gls{ris} in point-to-point \gls{mimo} systems
@@
 
-		First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping potential as channel rearrangement and space alignment.
-		Channel rearrangement refers to rearranging and recombining the entries of backward (i.e., \gls{ris}-receiver) and forward (i.e., transmitter-\gls{ris}) channel matrices by their strength.
-		Space alignment generalizes the phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to the singular vector space in \gls{mimo}.
+		First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping potential as branch matching and mode alignment.
+		Branch matching refers to pairing and combining the branches (i.e., entries) of backward and forward channels associated with each \gls{bd}-\gls{ris} group.
+		Mode alignment refers to aligning and ordering the modes (i.e., singular vectors) of indirect channels with those of direct channel.
+		% channel rearrangement and space alignment.
+		% Channel rearrangement refers to rearranging and recombining the entries of backward (i.e., \gls{ris}-receiver) and forward (i.e., transmitter-\gls{ris}) channel matrices by their strength.
+		% Space alignment generalizes the phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to the singular vector space in \gls{mimo}.
 		The former is uniquely attributed to the off-diagonal entries of the scattering matrix of \gls{bd}-\gls{ris}.
@@
 		Fourth, we provide an analytical answer to the shaping question in typical deployment scenarios.
-		For rank-deficient forward/backward channel, we derive singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris} with asymptotically large number of elements.
-		For blocked direct channel, we derive singular value bounds applying to fully-connected \gls{bd}-\gls{ris} with arbitrary number of elements.
+		% For rank-deficient forward/backward channel,
+		When the forward/backward channel is rank-deficient, we derive singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris} with asymptotically large number of elements.
+		% For negligible direct channel
+		When the direct channel is negligible, we derive singular value bounds applying to fully-connected \gls{bd}-\gls{ris} with arbitrary number of elements.
 		Those bounds are validated by comparing with the numerical results above.
@@
 	$\mathbb{C}$ represents the set of complex numbers.
-	$\mathbb{H}^{n \times n}$ and $\mathbb{U}^{n \times n}$ denotes the set of $n \times n$ Hermitian and unitary matrices, respectively.
+	$\mathbb{H}^{n \times n}$, $\mathbb{H}_+^{n \times n}$, and $\mathbb{U}^{n \times n}$ denote the set of $n \times n$ Hermitian, positive semi-definite, and unitary matrices, respectively.
 	$\mathbf{0}$ and $\mathbf{I}$ are the all-zero and identity matrices with appropriate size, respectively.
+	% $\Re\{\cdot\}$ and $\mathrm{arg}(\cdot)$ take the real part and argument of a complex number, respectively.
 	$\Re\{\cdot\}$ takes the real part of a complex number.
-	$\mathrm{arg}(\cdot)$ gives the argument of a complex number.
-	$\mathrm{tr}(\cdot)$ and $\det(\cdot)$ evaluates the trace and determinant of a square matrix, respectively.
-	$\mathrm{diag}(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
-	$\mathrm{sv}(\cdot)$ returns the singular value vector.
-	$\sigma_n(\cdot)$ and $\lambda_n(\cdot)$ is the $n$-th largest singular value and eigenvalue, respectively.
+	$\tr(\cdot)$ and $\det(\cdot)$ evaluate the trace and determinant of a square matrix, respectively.
+	$\diag(\cdot)$ constructs a square matrix by placing the inputs on the main (block) diagonal and zeros elsewhere.
+	$\sv(\cdot)$ extracts the singular values of a matrix as a non-ascending vector.
+	$\card(\cdot)$ returns the cardinality of a set.
+	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
+	$\sigma_n(\cdot)$ and $\lambda_n(\cdot)$ are the $n$-th largest singular value and eigenvalue, respectively.
 	% $\boldsymbol{\sigma}(\cdot)$ and $\boldsymbol{\lambda}(\cdot)$ are the corresponding vectors.
 	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^\dagger$ $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), Moore-Penrose inverse, $r$-th iterated point, and stationary point, respectively.
+	$[N]$ is a shortcut for $\{1,2,\ldots,N\}$.
 	$(\cdot)_{[x:y]}$ is a shortcut for $(\cdot)_x,(\cdot)_{x+1},\ldots,(\cdot)_y$.
-	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
-	$\odot$ represents the element-wise (Hadamard) product.
+	$\odot$ denotes the element-wise (Hadamard) product.
 	$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
@@
 	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
-	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
-	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume a lossless asymmetric network without mutual coupling between scattering elements, as have been previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
-	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-diagonal with unitary diagonal blocks\footnote{Following footnote \ref{fn:symmetric}, we do not limit the scattering matrix to be symmetric.
-One can enforce symmetry over the result by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$ if necessary.}
-	\begin{equation}
-		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
+	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ throughout the paper.
+	The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
+	Apparently $N_\mathrm{S} = \sum_{g=1}^G N_g$.
+	We assume all groups have the same size $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$ yet the discussion is extendable to \gls{bd}-\gls{ris} with unequal group size.
+	To establish a theoretical performance bound, we consider a lossless asymmetric\footnote{A symmetric solution can be enforced by projection $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$ if necessary.
+We will compare the performance of symmetric and asymmetric \gls{bd}-\gls{ris} in Section~\ref{sc:simulation}.} \gls{bd}-\gls{ris} without mutual coupling as previously discussed in \cite{Li2023b,Li2023c,Bartoli2023}.
+	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-diagonal
+	% \footnote{Following footnote \ref{fn:symmetric}, we do not constrain the scattering matrix to be symmetric in the paper.
+One can enforce such by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$ if necessary.}
+	\begin{equation}
+		\mathbf{\Theta} = \diag(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
 		\label{eq:bd_ris}
 	\end{equation}
-	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary block (i.e., $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$) that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
-	Note that \gls{d}-\gls{ris} can be regarded as its extreme case with group size $L=1$.
+	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary diagonal block modeling the response of group $g$.
+	It is noteworthy that the conventional \gls{d}-\gls{ris} is an extreme case of \gls{bd}-\gls{ris} with group size $L=1$.
+	% We highlight that conventional \gls{d}-\gls{ris} is an extreme case of \gls{bd}-\gls{ris} with group size $L=1$.
 	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2024}, where the
-	% radiation pattern and
+	array geometry and
 	circuit topology has been modeled in the scattering matrix.
 	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (i.e., transmitter-receiver), backward (i.e., \gls{ris}-receiver), and forward (i.e., transmitter-\gls{ris}) channels, respectively.
-	The equivalent channel is a function of the scattering matrix
-	\begin{equation}
-		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \underbrace{\mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}}_{\triangleq \mathbf{H}_g},
+	The equivalent channel depends on the \gls{bd}-\gls{ris} scattering matrix
+	\begin{equation}
+		% \mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \underbrace{\mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}}_{\triangleq \mathbf{H}_g} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
+		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \triangleq \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
 		\label{eq:channel_equivalent}
 	\end{equation}
-	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels associated with \gls{bd}-\gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
-	Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via \gls{bd}-\gls{ris} group $g$.
+	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels associated with group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively, and $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ is the indirect channel via group $g$.
 	Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
@@
 	% \begin{remark}
-	By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
+	We observe from \eqref{eq:channel_equivalent_svd} that the \gls{bd}-\gls{ris} plays a crucial role in combining
+	% needs to strike a balance between
+	backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
+	These two attributes are refined below and discussed in an example.
+	% We conclude from \eqref{eq:channel_equivalent_svd} that the scattering matrix of \gls{bd}-\gls{ris} provide two channel shaping potentials:
+	% By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
 	% Channel rearrangement refers to rearrange and recombine the forward and backward channel branches by their strength.
@@
 	\begin{itemize}
-		\item \emph{Channel rearrangement:} It refers to rearranging and recombining the backward and forward channel branches (i.e., entries of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$)
-		% associated with each group
-		by their strength.
-		% This unique feature of \gls{bd}-\gls{ris} exploits \textcolor{red}{spatial diversity} effectively thanks to in-group connections.
-		% This unique feature of \gls{bd}-\gls{ris} exploits the \textcolor{red}{spatial diversity} by rearranging and combining the backward and forward channel branches within each group.
-		In \gls{siso}\footnote{Following previous notation, here we denote the direct channel as $h_\mathrm{D}$, the backward and forward channels as $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$ and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, whose $n$-th entries are $h_{\mathrm{B},n}$ and $h_{\mathrm{F},n}$, respectively.
-		The channels associated with \gls{bd}-\gls{ris} group $g$ are also denoted as $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{1 \times L}$, whose $l$-th entries are $h_{\mathrm{B},g,l}$ and $h_{\mathrm{F},g,l}$, respectively.}, \gls{d}-\gls{ris} with perfect phase matching can provide a maximum indirect channel gain $g_\mathrm{D}=\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$,
-		% Thanks to in-group connections,
-		while \gls{bd}-\gls{ris} can exploit in-group connections and generalize it to
-		% this indirect channel gain to
-		$g_\mathrm{BD}=\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert$,
-		% $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$,
-		% $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,l} \rvert \lvert h_{\mathrm{F},g,\pi_g(l)} \rvert$,
-		where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are arbitrary permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-		Note the first summation is over groups and the second summation is over permuted channels.
-		By rearrangement inequality \cite[Inequality 10.2.1]{Hardy1952}, for \gls{bd}-\gls{ris} we have
-		\begin{equation}
-			g_\mathrm{BD} \le \sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi^\downarrow_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi^\downarrow_{\mathrm{F},g}(l)} \rvert,
-			\label{eq:gain_rearrangement}
-		\end{equation}
-		where $\pi^\downarrow_{\mathrm{B},g}$ and $\pi^\downarrow_{\mathrm{F},g}$ sort $\{\lvert h_{\mathrm{B},g,l} \rvert\}_{l=1}^L$ and $\{\lvert h_{\mathrm{F},g,l} \rvert\}_{l=1}^L$ in descending orders, respectively.
-		% are the descending permutations of $\lvert h_{\mathrm{B},g,l} \rvert$ and $\lvert h_{\mathrm{F},g,l} \rvert$, respectively.
-		That is to say, when the direct channel is blocked,
-		the maximum \gls{siso} channel gain is attained if the \gls{bd}-\gls{ris} pairs the $l$-th strongest backward and forward branches within each group.
-		% \footnote{Similarly, the minimum is attained when we pair the $l$-th strongest backward branch and the $L{-}l{+}1$-th strongest forward branch within each group.}
-		% We thus conclude that \gls{bd}-\gls{ris} exploits \textcolor{red}{spatial diversity} effectively thanks to in-group connections.
-		% By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
-		% , providing up to \qty{62.5}{\percent} asymptotic power gain over \gls{d}-\gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
-		Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude that {the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.}
-		\item \emph{Space alignment:} It refers to aligning the singular vector spaces of the direct, forward, and backward channels.
-		The \gls{bd}-\gls{ris} needs to strike a balance between the space alignment of backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
+		\item \emph{Branch matching:} It refers to pairing and combining the branches (i.e., entries) of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ through unitary transformation $\mathbf{\Theta}_g$.
+		% That is,
+		% % entries of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ by their strength.
+		% % rearranging and recombining the backward and forward channel branches (i.e., entries of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$)
+		% % associated with each group
+		% % by their strength.
+		% % This unique feature of \gls{bd}-\gls{ris} exploits \textcolor{red}{spatial diversity} effectively thanks to in-group connections.
+		% % This unique feature of \gls{bd}-\gls{ris} exploits the \textcolor{red}{spatial diversity} by rearranging and combining the backward and forward channel branches within each group.
+		% In \gls{siso}\footnote{Following previous notation, here we denote the direct channel as $h_\mathrm{D}$, the backward and forward channels as $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$ and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, whose $n$-th entries are $h_{\mathrm{B},n}$ and $h_{\mathrm{F},n}$, respectively.
+		% The channels associated with \gls{bd}-\gls{ris} group $g$ are also denoted as $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{1 \times L}$, whose $l$-th entries are $h_{\mathrm{B},g,l}$ and $h_{\mathrm{F},g,l}$, respectively.}, \gls{d}-\gls{ris} with perfect phase matching can provide a maximum indirect channel gain $g_\mathrm{D}=\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$,
+		% % Thanks to in-group connections,
+		% while \gls{bd}-\gls{ris} can exploit in-group connections and generalize it to
+		% % this indirect channel gain to
+		% $g_\mathrm{BD}=\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert$,
+		% % $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$,
+		% % $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,l} \rvert \lvert h_{\mathrm{F},g,\pi_g(l)} \rvert$,
+		% where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are arbitrary permutations of $[L]$.
+		% Note the first summation is over groups and the second summation is over permuted channels.
+		% By rearrangement inequality \cite[Inequality 10.2.1]{Hardy1952}, for \gls{bd}-\gls{ris} we have
+		% \begin{equation}
+		% 	g_\mathrm{BD} \le \sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi^\downarrow_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi^\downarrow_{\mathrm{F},g}(l)} \rvert,
+		% 	\label{eq:gain_rearrangement}
+		% \end{equation}
+		% where $\pi^\downarrow_{\mathrm{B},g}$ and $\pi^\downarrow_{\mathrm{F},g}$ sort $\{\lvert h_{\mathrm{B},g,l} \rvert\}_{l=1}^L$ and $\{\lvert h_{\mathrm{F},g,l} \rvert\}_{l=1}^L$ in descending orders, respectively.
+		% % are the descending permutations of $\lvert h_{\mathrm{B},g,l} \rvert$ and $\lvert h_{\mathrm{F},g,l} \rvert$, respectively.
+		% That is to say, when the direct channel is blocked,
+		% the maximum \gls{siso} channel gain is attained if the \gls{bd}-\gls{ris} pairs the $l$-th strongest backward and forward branches within each group.
+		% % \footnote{Similarly, the minimum is attained when we pair the $l$-th strongest backward branch and the $L{-}l{+}1$-th strongest forward branch within each group.}
+		% % We thus conclude that \gls{bd}-\gls{ris} exploits \textcolor{red}{spatial diversity} effectively thanks to in-group connections.
+		% % By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
+		% % , providing up to \qty{62.5}{\percent} asymptotic power gain over \gls{d}-\gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
+		% Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude that {the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.}
+		\item \emph{Mode alignment:} It refers to aligning and ordering the modes (i.e., singular vectors) of $\{\mathbf{H}_g\}_{g \in [G]}$ with those of $\mathbf{H}_\mathrm{D}$ through unitary transformations $\{\mathbf{\Theta}_g\}_{g \in [G]}$.
+		% The \gls{bd}-\gls{ris} needs to strike a balance between the space alignment of backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
 In \gls{siso}, singular vectors reduce to scalars and space alignment reduce to phase matching, such that the scattering matrix of group $g$ maximizing the channel gain is
-		\begin{equation}
-			\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
-			\label{eq:scattering_siso}
-		\end{equation}
-		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-		We notice that \gls{d}-\gls{ris} (i.e., $L=1$) suffices
-		% \gls{d}-\gls{ris} thus suffices
-		for perfect phase matching in \gls{siso}.
-		When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a scalar phase shift to the corresponding indirect channel matrix of size $N_\mathrm{R} \times N_\mathrm{T}$ defined in \eqref{eq:channel_equivalent}.
-		We thus conclude that the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.
-		% When it comes to \gls{mimo}, element $g$ of \gls{d}-\gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
+		% \begin{equation}
+		% 	\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
+		% 	\label{eq:scattering_siso}
+		% \end{equation}
+		% where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
+		% We notice that \gls{d}-\gls{ris} (i.e., $L=1$) suffices
+		% % \gls{d}-\gls{ris} thus suffices
+		% for perfect phase matching in \gls{siso}.
+		% When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a scalar phase shift to the corresponding indirect channel matrix of size $N_\mathrm{R} \times N_\mathrm{T}$ defined in \eqref{eq:channel_equivalent}.
+		% We thus conclude that the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.
+		% % When it comes to \gls{mimo}, element $g$ of \gls{d}-\gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
 For element $g$ of \gls{d}-\gls{ris}, the indirect channel $\mathbf{H}_g$ is rank-1 and the pinhole is $\Theta_g$.} indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
-		% Thus, we conclude that
-		% We can thus see that
-		% {the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.}
-		% As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward spaces.
+		% % Thus, we conclude that
+		% % We can thus see that
+		% % {the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.}
+		% % As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward spaces.
 	\end{itemize}
 	% \end{remark}
+
+	% We use the following examples to show that a stronger branch matching capability enables better mode alignment and results in more flexible channel shaping.
+	% The following example clarifies the difference in between and show their impacts on channel shaping.
+
+	\begin{example}[\gls{siso} channel gain maximization]\label{eg:siso_gain}
+		Denote the direct, backward, forward channels as $h_\mathrm{D}$, $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$, and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, respectively.
+		In this case, mode alignment boils down to phase matching and any $L \in [N_\mathrm{S}]$ (including \gls{d}-\gls{ris}) suffices for perfect alignment between $h_\mathrm{D}$ and indirect channels $\{h_g\}_{g \in [G]}$ using
+		% the scattering matrix maximizing the channel gain is
+		\begin{equation}
+			\mathbf{\Theta}_g^\textnormal{\gls{siso}} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H}, \quad \forall g,
+			\label{eq:scattering_siso}
+		\end{equation}
+		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of null spaces of $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g} \in \mathbb{C}^{1 \times L}$, respectively.
+		The corresponding channel gain is a function of $L$
+		% Here any $L \in [N_\mathrm{S}]$ (including \gls{d}-\gls{ris}) suffices for perfect mode alignment between $h_\mathrm{D}$ and indirect channels $\{h_g\}_{g \in [G]}$ using \eqref{eq:scattering_siso}.
+		% However, the branch matching capability is a function of $L$ and the channel gain can be manipulated
+		\begin{equation}
+			\lvert h \rvert _{\max} = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
+			\label{eq:gain_siso}
+		\end{equation}
+		where $h_{\mathrm{B},g,l}$, $h_{\mathrm{F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively, and $\pi_{\mathrm{B},g}$, $\pi_{\mathrm{F},g}$ are permutations of $[L]$ sorting their magnitude in non-ascending orders.
+		That is, the maximum channel gain is attained when each group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
+		A larger $L$ provides better branch matching flexibility and can thus grant a higher channel gain.
+		% It is evident that the branch matching capability increases with $L$.
+		% the backward and forward channels as $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$ and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, whose $n$-th entries are $h_{\mathrm{B},n}$ and $h_{\mathrm{F},n}$, respectively.
+		% The channels associated with \gls{bd}-\gls{ris} group $g$ are also denoted as $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{1 \times L}$, whose $l$-th entries are $h_{\mathrm{B},g,l}$ and $h_{\mathrm{F},g,l}$, respectively.
+	\end{example}
+
+	Example~\ref{eg:siso_gain} clarifies the difference between branch matching and mode alignment and show their impacts on channel shaping.
+	When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching is more pronounced since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$.
+On the other hand, the disadvantage of \gls{d}-\gls{ris} in mode alignment deteriorates since each element can only apply a scalar phase shift to the resulting indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ modes.
+	% of size $N_\mathrm{R} \times N_\mathrm{T}$, which renders the alignment of multiple modes difficult.
+	% following examples aim to help the readers understanding both potentials.
 
@@
 	% \begin{remark}
-	% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+	% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:direct_negligible}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
 	% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
@@
 
+\begin{section}{Analytical Bounds on Singular Value Shaping}
+	\label{sc:singular_value}
+	In this section, we first provide an example demonstrating the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds related to channel singular values under specific channel conditions.
+	% the channel singular values for both architectures.
+	% Next, we numerically characterize the attainable channel singular value region using Algorithm \ref{ag:rcg}.
+	% Finally, we derive
+	% Some analytical bounds on the channel singular values are derived for \gls{bd}-\gls{ris} and \gls{d}-\gls{ris} architectures.
+	% singular value bounds in specific channel conditions.
+
+	\begin{example}[$2 \times 2 \times 2$ shaping]\label{eg:d_vs_bd}
+		% We showcase the channel shaping capabilities of different \gls{ris} models by a toy example.
+		% Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
+		Here \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} can be modeled by 2 and 4 independent angular parameters, respectively:
+		% is modeled by $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} can be modeled by 4 independent angular parameters
+		\begin{equation*}
+			\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}), \quad
+			\mathbf{\Theta}_\mathrm{BD} = e^{\jmath \phi} \begin{bmatrix}
+				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
+				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
+			\end{bmatrix},
+			% \label{eq:unitary_ris}
+		\end{equation*}
+		% where $\phi$ has no impact on $\sv(\mathbf{H})$ since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
+		We consider a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
+		The singular value shaping capabilities of two \gls{ris} architectures can thus be compared visually over 2 tunable parameters.
+		\begin{figure}
+			\centering
+			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
+			\caption{$2 \times 2 \times 2$ singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is negligible.
+$\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
+			Their maximum and minimum are marked explicitly on the plot.}
+			\label{fg:singular_trend}
+		\end{figure}
+		With an exhaustive grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$, Fig.~\ref{fg:singular_trend} shows the achievable singular values of a specific channel realization
+		\begin{equation*}
+			\begin{split}
+				\mathbf{H}_\mathrm{B} & =
+				\begin{bmatrix}
+					-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
+					0.4131 + 0.2651 \jmath & -0.1960 + 0.4650 \jmath
+				\end{bmatrix},
+				\\
+				\mathbf{H}_\mathrm{F} & =
+				\begin{bmatrix}
+					-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
+					0.0196 + 0.4011 \jmath & -0.3170 - 0.2303 \jmath
+				\end{bmatrix}.
+			\end{split}
+		\end{equation*}
+		% The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for \gls{d}-\gls{ris} and $(\alpha, \psi)$ for symmetric \gls{bd}-\gls{ris}.
+		In this example, both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} using 2 symmetric components and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} using 3 symmetric components.
+	\end{example}
+
+	% Example~\ref{eg:d_vs_bd} shows that physically grouping some scattering elements produces a ``cooperation effect'' that significantly enhances the dynamic range of channel singular values.
+	Example~\ref{eg:d_vs_bd} highlights that the physical grouping of \gls{ris} elements, even if using symmetric components, can produce a much wider dynamic range of channel singular values.
+	This motivates analytical and numerical studies on singular value shaping using \gls{bd}-\gls{ris}.
+	A selection of analytical bounds are presented in Propositions~\ref{pp:dof} -- \ref{pp:direct_negligible} and the resulting corollaries.
+	% The remainder of this section is organized as follows.
+
+	% We also provide some analytical bounds related to channel singular values, which help us to explore the limits of channel shaping using passive \gls{ris}.
+
+		\begin{definition}[Degrees of freedom]
+			\gls{dof} (a.k.a. multiplexing gain) refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, which is defined asymptotically as
+			\begin{equation}
+				d = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho},
+			\end{equation}
+			where $\rho$ is the \gls{snr}.
+
+		\end{definition}
+
+		\begin{proposition}[Degrees of freedom]\label{pp:dof}
+			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
+		\end{proposition}
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:dof}.
+		\end{proof}
+
+		Proposition \ref{pp:dof} suggests that we cannot hope for a \gls{dof} gain (i.e., more parallel channels) by simply connecting the \gls{ris} elements.
+		We thus focus on the question of reshaping the available channels through manipulation of the singular values.
+
+		% you cannot hope for degrees of freedom gain (i.e. more channels) thus we focus ont he question of reshaping of the available channels through manipulation of the singular values.
+
+		\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
+			% If the forward or backward channel is rank-$k$ ($k \le N$),
+			If the minimum rank of backward and forward channels is $k$ ($k \le N$),
+			then for \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
+			\begin{subequations}
+				\begin{align}
+					\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_bound_enlarge}          \\
+					\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
+				\end{align}
+				\label{iq:sv_bound_rank_deficient}
+			\end{subequations}
+			where $\mathbf{T}$ is arbitrary auxiliary matrix satisfying
+			\begin{equation}
+				\mathbf{T} \mathbf{T}^\mathsf{H} =
+				\begin{cases}
+					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
+					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
+				\end{cases}
+				\label{eq:auxiliary_matrix}
+			\end{equation}
+			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
+		\end{proposition}
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:rank_deficient}.
+		\end{proof}
+
+		Inequality \eqref{iq:sv_bound_enlarge} states that
+		if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are at least rank $k$, then
+		% with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements,
+		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
+		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected in all cases.
+This constraint is omitted in context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
+		A special case is Corollary \ref{co:los} for \gls{los} channel\footnote{A similar eigenvalue result has been derived for \gls{d}-\gls{ris} only \cite{Semmler2023}.}.
+		% states that the $n$-th channel singular value can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$.
+
+		% We would like to give some insights into Proposition \ref{pp:rank_deficient}.
+
+		% \begin{corollary}[Extreme singular values\label{co:extreme}]
+		% 	If the minimum rank of forward and backward channels is $k$ ($k \le N$), then with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
+This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
+		% \end{corollary}
+
+		% \begin{proof}
+		% 	This is a direct result of \eqref{iq:sv_bound_rank_deficient}.
+		% \end{proof}
+
+		\begin{corollary}[\gls{los} channel\label{co:los}]
+			% If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
+suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
+$n$-th) singular value of $\mathbf{T}$, that is,
+			If at least one of backward and forward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
+			That is,
+			\begin{equation}
+				\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
+				\label{iq:sv_bound_los}
+			\end{equation}
+		\end{corollary}
+
+		\begin{proof}
+			This is a direct result of \eqref{iq:sv_bound_rank_deficient} with $k = 1$.
+		\end{proof}
+
+		We emphasize that
+		% the inequalities in \eqref{iq:sv_bound_rank_deficient} and \eqref{iq:sv_bound_los}
+		Proposition \ref{pp:rank_deficient} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
+		Out of $2N$ bounds in \eqref{iq:sv_bound_rank_deficient} or \eqref{iq:sv_bound_los}, $N$ of them
+		% The equalities in \eqref{iq:sv_bound_rank_deficient} and \eqref{iq:sv_bound_los}
+		can be \emph{simultaneously} tight as $N_\mathrm{S}$ goes to infinity, namely, when the direct channel becomes negligible\footnote{Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
+This can result from a very large number of \gls{ris} elements (as discussed in Proposition~\ref{pp:rank_deficient}) or physical obstacles in the propagation path (as discussed in Proposition~\ref{pp:direct_negligible}).}.
+		For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes, and we will later show by simulation that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
+		Proposition \ref{pp:rank_deficient} provides a reference on the selection of $N_\mathrm{S}$ in low-multipath application scenarios.
+		% Proposition \ref{pp:rank_deficient} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a benchmark for $N_\mathrm{S}$ selection in low-multipath deployment scenarios.
+		Next, we shift the focus to another popular \gls{ris} deployment scenario where the direct channel is blocked.
+		% finite-size fully-connected \gls{bd}-\gls{ris}.
+
+		\begin{proposition}[Negligible direct channel]\label{pp:direct_negligible}
+			% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+
+			If the direct channel is negligible, then a fully-connected \gls{bd}-\gls{ris} can manipulate the channel singular values up to
+			% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
+			% only bounds that apply here are those that apply to the singular values of
+			\begin{equation}
+				\sv(\mathbf{H}) = \sv(\mathbf{BF}),
+				\label{eq:sv_fully_connected}
+			\end{equation}
+			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with $\sv(\mathbf{B})=\sv(\mathbf{H}_\mathrm{B})$ and $\sv(\mathbf{F})=\sv(\mathbf{H}_\mathrm{F})$.
+			% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
+		\end{proposition}
+
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:direct_negligible}.
+		\end{proof}
+
+		Proposition \ref{pp:direct_negligible} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
+		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
+		Its importance lies in the fact that the channel shaping question in Section \ref{sc:contributions} can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
+		The question is partially answered in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} over the notation\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [\bar{N}] \setminus [N]$.
+		% $N < n \le \bar{N}$.
+		These results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
+		% We have the following corollaries.
+
+		\begin{corollary}[Product of subset of singular values\label{co:sv_bound_horn}]
+			The product of subset of singular values of $\mathbf{H}$ is bounded from above by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
+			\begin{equation}
+				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
+				\label{iq:sv_bound_fc}
+			\end{equation}
+			for all admissible triples $(I, J, K) \in T_r^{\bar{N}}$ with $r < \bar{N}$, where
+			\begin{equation*}
+				\begin{split}
+					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} & \bigm\vert \forall p < r, \ \forall (F, G, H) \in T_p^r,\\
+					& \quad \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + \frac{p(p+1)}{2} \Bigr\},
+				\end{split}
+			\end{equation*}
+			\begin{equation*}
+				U_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \subseteq [\bar{N}]^3 \bigm\vert \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + \frac{r(r+1)}{2}\Bigr\}.
+			\end{equation*}
+		\end{corollary}
+
+		\begin{proof}
+			Please refer to \cite[Theorem~8]{Fulton2000}.
+		\end{proof}
+
+		Corollary \ref{co:sv_bound_horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result under the assumption of Proposition \ref{pp:direct_negligible} (i.e., negligible direct channel and fully-connected \gls{bd}-\gls{ris}).
+		% It is worth mentioning that t
+		% It also helps to induce lower bounds on the channel singular values.
+		The number of admissible triples increases exponentially with $\bar{N}$ despite some resulting inequalities can be redundant.
+		Apart from upper bounds, \eqref{iq:sv_bound_fc} can also induce lower bounds on channel singular values.
+		% It also helps to induce lower (instead of upper) bounds on channel singular values.
+		% ! For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $\bar{N}$ increases from 3 to 7.
+		% Besides, \eqref{iq:sv_bound_fc} helps to induce lower bounds
+		Those facts render the shaping limit analysis non-trivial for massive \gls{ris}-aided \gls{mimo} systems.
+		Below we showcase some useful results that can be derived from Corollary \ref{co:sv_bound_horn}.
+
+		\begin{corollary}[Product of some largest or smallest singular values\label{co:sv_product}]
+			% \footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
+			% For any $k \in [\bar{N}]$,
+			The product of the first (resp. last) $k$ singular values of $\mathbf{H}$ is bounded from above (resp. below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
+			% the product of the first (resp. last) $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
+			% upper bounded by the product of first and last $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
+			% $k$ singular values of $\mathbf{H}$ can be upper bounded by the product of first $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
+			\begin{subequations}
+				\begin{align}
+					\prod_{n=1}^k \sigma_n(\mathbf{H}) & \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:sv_product_largest} \\
+					\prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}) & \ge \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:sv_product_smallest}
+				\end{align}
+			\end{subequations}
+		\end{corollary}
+
+		\begin{proof}
+			Please refer to and Appendix~\ref{ap:sv_product}.
+		\end{proof}
+
+		\begin{corollary}[Individual singular value\label{co:sv_nth}]
+			The $n$-th channel singular value can be manipulated up to
+			\begin{equation}
+				\max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
+				\label{iq:sv_nth}
+			\end{equation}
+			where $(i, j) \in [\bar{N}]^2$.
+			The upper and lower bounds are attained respectively at
+			% \begin{subequations}
+			% 	\begin{align}
+			% 		\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_max} \\
+			% 		\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_min}
+			% 	\end{align}
+			% \end{subequations}
+			\begin{subequations}
+				\begin{align}
+					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{L} \mathbf{P} \mathbf{R} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_max} \\
+					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{L} \mathbf{Q} \mathbf{R} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_min}
+				\end{align}
+			\end{subequations}
+			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are the right and left singular matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively, $\mathbf{L}, \mathbf{R}$ are arbitrary block-diagonal unitary matrices with size of block $n \in [N_\mathrm{S}]$ equal to the multiplicity of $\sigma_n(\mathbf{H}_\mathrm{B})$ and $\sigma_n(\mathbf{H}_\mathrm{B})$, respectively,
+			% $\mathbf{\Theta}_\mathrm{D}$ is arbitrary diagonal matrix with unit-magnitude diagonal entries,
+			and $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary doubly stochastic matrices of dimension $N_\mathrm{S}$ satisfying:
+			\begin{itemize}
+				\item The $(i, j)$-th entries sum up to $1$, where
+				\begin{equation*}
+					(i, j) =
+					\begin{cases}
+						\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \triangleq \mathcal{S}_n(\mathbf{P}) & \text{for } \mathbf{P}, \\
+						\underset{i+j=n+\bar{N}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \triangleq \mathcal{S}_n(\mathbf{Q}) & \text{for } \mathbf{Q};
+					\end{cases}
+				\end{equation*}
+				\item The submatrix with $i$-th rows and $j$-th columns deleted, $(i,j) \in \mathcal{S}_n$, denoted as $\mathbf{Y}$, is arbitrary doubly stochastic matrix of dimension $N_\mathrm{S}-\card(\mathcal{S}_n)$ satisfying
+				\begin{align*}
+					\sigma_{n-1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \ge \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{for } \mathbf{P}, \\
+					\sigma_{n+1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \le \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{for } \mathbf{Q},
+				\end{align*}
+				where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with the $i$-th rows and $j$-th columns deleted, $(i,j) \in \mathcal{S}_n$.
+			\end{itemize}
+
+			% where $\mathbf{P}, \mathbf{Q}$ can be any unitary matrix whose $(i, j)$-th entry is of unit-magnitude, and $(i, j) = \arg \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{P}$ and $(i, j) = \arg \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{Q}$.
+			% where $\mathbf{P}, \mathbf{Q}$ can be any unitary matrix whose $(i, j)$-th entry is of unit-magnitude, and $(i, j) = \arg \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{P}$ and $(i, j) = \arg \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{Q}$.
+			% that reorders the singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		\end{corollary}
+
+		\begin{proof}
+			In \eqref{iq:sv_nth}, the set of upper bounds
+			\begin{equation}
+				\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+1\bigr\}
+				\label{iq:sv_nth_upper_set}
+			\end{equation}
+			is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [\bar{N}]^3$.
+			The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
+However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nth_upper_set} is selected as the tightest upper bound in \eqref{iq:sv_nth}.
+			On the other hand, the set of lower bounds
+			\begin{equation}
+				\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+\bar{N}\bigr\}
+				\label{iq:sv_nth_lower_set}
+			\end{equation}
+			can be induced by \eqref{iq:sv_nth_upper_set}, \eqref{eq:sv_product}, and the non-negativity of singular values.
+			The maximum of \eqref{iq:sv_nth_lower_set} is selected as the tightest lower bound in \eqref{iq:sv_nth}.
+
+			To attain the upper bound, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ singular values of $\mathbf{H}$.
+			It follows from \eqref{eq:sv_nth_max} that
+			\begin{equation*}
+				\begin{split}
+					\sv(\mathbf{H})
+					& = \sv(\mathbf{H}_\mathrm{B} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{F}) \\
+					& = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Theta}_\mathrm{D} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \\
+					& = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H}) \\
+					& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Sigma}_\mathrm{F}) \\
+				\end{split}
+			\end{equation*}
+			where $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$.
+
+			The doubly stochastic matrix $\mathbf{P}$ should align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that the first $n$ modes of $\mathbf{H}$ are maximized.
+
+			One feasible solution is to align and order the first $n$ modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, resulting in $\sigma_n(\mathbf{H}) = \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$.
+			If such $(i,j)$ pairs are not unique, then any mixture of them would produce the same result.
+			% We emphasize that the solution is not unique and mixture of such $(i,j)$ pairs would produce the same result.
+			% It is worth mentioning that the solution is not unique and any mixture of such $(i,j)$ pairs would produce the same result.
+			However, since we only care about the $n$-th singular value, the first $n-1$ singular values can be arbitrarily reordered.
+			% This is achieved by aligning and reordering the first $n$ modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+
+			proper matching of the first $n$ modes of $\mathbf{H}_\mathrm{B}$ to the first $n$ modes of $\mathbf{H}_\mathrm{F}$.
+			In particular, mode $i$ of $\mathbf{H}_\mathrm{B}$ should be completely aligned with mode $j$ of $\mathbf{H}_\mathrm{F}$ where $(i, j) = \arg \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{P}$
+
+			% Interested readers are referred to \cite[Equation~2.0.3]{Zhang2005} for more information.
+			% $i$-th mode of $\mathbf{H}_\mathrm{B}$ with the $j$-th mode of $\mathbf{H}_\mathrm{F}$ such that the $n$-th mode of $\mathbf{H}$ is maximized.
+
+			% Maximizing $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is equivalent to maximizing the minimum of the first $n$ channel singular values.
+			% As such, the \gls{bd}-\gls{ris} needs to align t
+			% align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that the first $n$ modes of $\mathbf{H}$ are maximized.
+			% To maximize the $n$-th channel singular value, the \gls{bd}-\gls{ris} needs to ensure
+			% that the first $n$ modes of $\mathbf{H}$ are
+
+			% should align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that
+
+			% \cite[Equation~2.0.3]{Zhang2005}
+
+			% Please refer to Appendix~\ref{ap:sv_nth}.
+		\end{proof}
+
+		Now we can see the alignment by $V_B$ $U_F$ and ordering by $P$ $Q$.
+
+		We highlight the solution (15) is not unique.
+
+		In particular, the extreme singular values can be manipulated up to
+		\begin{subequations}
+			\label{iq:sv_extreme}
+			\begin{gather}
+				\max_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_largest} \\
+				\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\ge} \sigma_{\bar{N}}(\mathbf{H}) {\ge} \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}), \label{iq:sv_smallest}
+			\end{gather}
+		\end{subequations}
+		where the arguments of $\max$ and $\min$ are essentially $\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}-1}(\mathbf{H}_\mathrm{F}), \ldots, \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
+		We notice that the right side inequalities in \eqref{iq:sv_largest} and \eqref{iq:sv_smallest} are special cases of \eqref{iq:sv_product_largest} and \eqref{iq:sv_product_smallest} when $k=1$, respectively.
+		It is evident from \eqref{iq:sv_nth} that to enlarge the $n$-th singular value of $\mathbf{H}$, one should
+
+		enumerate all matching pairs $(i, j) \in [\bar{N}]^2 \mid i+j=n+1$, find the one with the minimum product singular value
+
+		match the singular
+
+		align the $i$-th singular value of $\mathbf{H}_\mathrm{B}$ with the $j$-th singular value of $\mathbf{H}_\mathrm{F}$ such that $i+j=n+\bar{N}$.
+
+		% The lower bound on the smallest singular value reduces to 0 when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).
+		% in \eqref{iq:sv_smallest} is less informative when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.
+		% in \eqref{iq:sv_product_smallest} and \eqref{iq:sv_smallest} reduce to 0 when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).
+
+		\begin{corollary}[Channel power gain\label{co:sum_power}]
+			The channel power gain is bounded from above (resp.
+below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp.
+oppositely), that is,
+			\begin{equation}
+				\sum_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
+				\label{iq:power_gain}
+			\end{equation}
+			whose\footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
+This is a looser version of \eqref{iq:power_gain} and cannot take equalities unless the extreme singular values are of multiplicity $\bar{N}$.} upper and lower bounds are attained respectively at
+			\begin{subequations}
+				\begin{align}
+					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H}, \\
+					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H},
+				\end{align}
+			\end{subequations}
+			% \begin{equation}
+			% 	\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \quad \mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H},
+			% \end{equation}
+			where $\mathbf{J}$ is the exchange (a.k.a. backward identity) matrix of dimension $N_\mathrm{S}$.
+		\end{corollary}
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:sum_power}.
+		\end{proof}
+
+		% ! Talk about when is the assumption hold.
+		% We highlight that the bounds in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} are asymptotically tight as $N_\mathrm{S}$ goes to infinity.
+
+		\begin{example}[Bounds on $3 \times 3 \times 3$ shaping]\label{eg:bounds}
+			Consider a $3 \times 3 \times 3$ setup with negligible direct channel.
+			Let $\mathbf{H}_\mathrm{B} = \diag(4, 5, 6)$, $\mathbf{H}_\mathrm{F} = \diag(3, 1, 2)$.
+			% $\sv(\mathbf{H}_\mathrm{B}) = [3, 2]^\mathsf{T}$ and $\sv(\mathbf{H}_\mathrm{B}) = [4, 1]^\mathsf{T}$.
+			% \begin{equation*}
+			% 	\mathbf{H}_\mathrm{B} =
+			% 		\begin{bmatrix}
+			% 			4 & 0 & 0 \\
+			% 			0 & 5 & 0 \\
+			% 			0 & 0 & 6
+			% 		\end{bmatrix},
+			% 		\quad
+			% 		\mathbf{H}_\mathrm{F} =
+			% 		\begin{bmatrix}
+			% 			1 & 0 \\
+			% 			0 & 4
+			% 		\end{bmatrix}.
+			% \end{equation*}
+			Apparently any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 12, 5]^\mathsf{T}$ due to limited branch matching capability.
+			On the other hand, Corollary \ref{co:sv_bound_horn} suggests that a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
+
+			\begin{align*}
+				\sigma_1(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_2(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \\
+				\sigma_2(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}) \\
+				\sigma_3(\mathbf{H}) &\leq \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F})
+			\end{align*}
+
+			while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can match the stronger branches by unitary transformation to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+			The bounds on individual singular values are $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+			However, the upper/lower bounds are not simultaneously achievable due to the trade-off between two modes.
+			% and the singular value region is a subset of the rectangle due to the trade-off between the alignment of two modes.
+			% but there exists a trade-off in between due to mode alignment.
+			% It is obvious that any \gls{d}-\gls{ris} can only attain $\sv(\mathbf{H}) = [8, 3]^\mathsf{T}$ while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ exploits branch matching to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+
+			% results in $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+			% The singular value
+			% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+		\end{example}
+
+		% % TODO enumerate all bounds for 2x2x2
+		% \begin{example}[Individual (no, all) singular value bounds on $2 \times 2 \times 2$ shaping]\label{eg:bounds}
+		% 	Consider a $2 \times 2 \times 2$ setup with
+		% 	% $\sv(\mathbf{H}_\mathrm{B}) = [3, 2]^\mathsf{T}$ and $\sv(\mathbf{H}_\mathrm{B}) = [4, 1]^\mathsf{T}$.
+		% 	\begin{equation*}
+		% 		\mathbf{H}_\mathrm{B} =
+		% 			\begin{bmatrix}
+		% 				3 & 0 \\
+		% 				0 & 2
+		% 			\end{bmatrix},
+		% 			\quad
+		% 			\mathbf{H}_\mathrm{F} =
+		% 			\begin{bmatrix}
+		% 				1 & 0 \\
+		% 				0 & 4
+		% 			\end{bmatrix}.
+		% 	\end{equation*}
+		% 	It is obvious that any \gls{d}-\gls{ris} can only attain $\sv(\mathbf{H}) = [8, 3]^\mathsf{T}$ while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can match the stronger branches by unitary transformation to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+		% 	The bounds on individual singular values are $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+		% 	However, the upper/lower bounds are not simultaneously achievable due to the trade-off between two modes.
+		% 	% and the singular value region is a subset of the rectangle due to the trade-off between the alignment of two modes.
+		% 	% but there exists a trade-off in between due to mode alignment.
+		% 	% It is obvious that any \gls{d}-\gls{ris} can only attain $\sv(\mathbf{H}) = [8, 3]^\mathsf{T}$ while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ exploits branch matching to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+
+		% 	% results in $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+		% 	% The singular value
+		% 	% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+		% \end{example}
+
+		Example~\ref{eg:bounds} shows that a fully-connected \gls{bd}-\gls{ris} can apply right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$
+		% , widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+
+		% We thus conclude that a fully-connected \gls{bd}-\gls{ris} can apply right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, which widens channel singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this example.
+
+		% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this case.
+
+		All equalities achieved by perfect alignment of all modes.
+
+		To achieve equalities in Corollaries \ref{co:sv_extreme} -- \ref{co:sum_power}, the \gls{ris} needs to completely align the singular vector spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		The resulting scattering matrix is generally required to be unitary
+		\begin{equation}
+			\mathbf{\Theta}^\star = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H},
+			\label{eq:scattering_fc_optimal}
+		\end{equation}
+		which can be concluded from \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in Appendix~\ref{ap:direct_negligible}.
+		We notice that \gls{d}-\gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
+		In such case, the equivalent channel reduces to $\mathbf{H} = \sigma_\mathrm{B} \sigma_\mathrm{F} \mathbf{u}_\mathrm{B} \mathbf{v}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ and the \gls{ris} only needs to align $\mathbf{v}_\mathrm{B}^\mathsf{H}$ and $\mathbf{u}_\mathrm{F}$ by
+		\begin{equation}
+			\mathbf{\Theta}^\star = \mathbf{v}_\mathrm{B} \mathbf{u}_\mathrm{F}^\mathsf{H} \odot \mathbf{I},
+		\end{equation}
+		which reduces to a special case of \eqref{eq:scattering_siso} with $L=1$.
+		However, in general \gls{d}-\gls{ris} is not sufficient to achieve the upper bound of channel power gain.
+		This again highlights the benefit of \gls{bd}-\gls{ris} in reshaping available channels.
+
+		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the maximum expected channel power gain can be numerically evaluated as
+		\begin{equation}
+			\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\} = \sum_n \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x) d x,
+			\label{eq:power_gain_rayleigh}
+		\end{equation}
+		% \begin{equation}
+		% 	\begin{split}
+		% 		\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\}
+		% 		& = \sum_n \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x_n) d x_n \\
+		% 		& \quad \times \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x_n) d x_n,
+		% 	\end{split}
+		% 	\label{eq:power_gain_rayleigh}
+		% \end{equation}
+		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(x)$ given by \cite[Equation 51]{Zanella2009}.
+		We note that \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain attainable by \gls{bd}-\gls{ris} \cite[Equation 58]{Shen2020a} to \gls{mimo} and models the contribution of transmit and receive antennas under double Rayleigh fading.
+		In Section \ref{sc:simulation}, we will numerically evaluate the channel power gain and compare it with the theoretical upper bound.
+
+		% Expression \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo} and unveils
+
+		% , unveiling how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
+		% is a generalization of \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo}, which unveils how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
+		% However, a closed-form expression is non-trivial due to the complexity of distribution of ordered eigenvalues of Wishart matrices.
+		% ordered Wishart matrix eigenvalue distribution.
+		% provides a benchmark for the channel power gain of \gls{bd}-\gls{ris} in Rayleigh fading channels.
+
+		Proposition \ref{pp:direct_negligible} and Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} provide a comprehensive answer to the shaping capability question in terms of singular value bounds and channel power gain limits.
+		% understanding of the channel power gain limits of passive \gls{ris}.
+		% and suggest the impact of channel rearrangement and space alignment on redistributing channel singular values.
+		% When the direct channel is present,
+		% Similar results are inapplicable
+		Extending those results to the case of direct channel is non-trivial since the singular vector spaces of direct-indirect channels and backward-forward channels cannot be aligned at the same time.
+		In such case, we can invoke optimization approaches from a singular value perspective (discussed in Section~\ref{sc:pareto_frontier}) or a power gain perspective (to be discussed in Section~\ref{sc:power}).
+	% numerical and analytical studies on singular value redistribution by \gls{bd}-\gls{ris} in Sections~\ref{sc:pareto_frontier} and \ref{sc:bounds}, respectively.
+	% further studies on channel shaping.
+
+	% Interestingly, connecting two scattering elements via a symmetric component can provide a much larger dynamic range of channel singular values.
+	% singular value manipulation range than using two independent elements.
+	% that such a large difference comes from connecting both scattering elements using a symmetric component.
+	% , where the former needs 2 reconfigurable impedance and the latter needs 3.
+	% It is interesting that the huge difference comes purely from connecting both elements.
+	% Such a large gain comes from simply connecting both elements
+	% , and it can be even larger using an asymmetric component.
+	% an even larger gain is expected when an asymmetric reconfigurable component is available.
+	% An even larger gain is expected when an asymmetric reconfigurable component is available.
+	% and a larger gain is expected when an asymmetric connection is available.
+	% This example shows that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
+	% \begin{subsection}{Toy Example}\label{sc:toy_example}
+	% 	We showcase the channel shaping capabilities of different \gls{ris} models by a toy example.
+	% 	Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
+	% 	The \gls{d}-\gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} can be modeled by 4 independent angular parameters
+	% 	\begin{equation}
+	% 		\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
+	% 			e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
+	% 			-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
+	% 		\end{bmatrix}.
+	% 		\label{eq:unitary_ris}
+	% 	\end{equation}
+	% 	It is worth noting that $\phi$ has no impact on the singular value because $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
+	% 	To simplify the analysis, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of variables in the scattering matrix.
+	% 	\begin{figure}
+	% 		\centering
+	% 		\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
+	% 		\caption{$2 \times 2 \times 2$ channel singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is blocked.
+$\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
+	% 		Their maximum and minimum have been marked explicitly on the plot.}
+	% 		\label{fg:singular_trend}
+	% 	\end{figure}
+	% 	Fig.~\ref{fg:singular_trend} compares the achievable singular values of one typical channel realization, where the backward and forward channels are given by
+	% 	\begin{equation*}
+	% 		\begin{split}
+	% 			\mathbf{H}_\mathrm{B} & =
+	% 			\begin{bmatrix}
+	% 				-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
+	% 				0.4131 + 0.2651 \jmath & -0.1960 + 0.4650 \jmath
+	% 			\end{bmatrix},
+	% 			\\
+	% 			\mathbf{H}_\mathrm{F} & =
+	% 			\begin{bmatrix}
+	% 				-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
+	% 				0.0196 + 0.4011 \jmath & -0.3170 - 0.2303 \jmath
+	% 			\end{bmatrix}.
+	% 		\end{split}
+	% 	\end{equation*}
+	% 	The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for \gls{d}-\gls{ris} and $(\alpha, \psi)$ for symmetric \gls{bd}-\gls{ris}.
+	% 	In this example, we observe that both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} (using 2 reconfigurable impedance) and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (using 3 reconfigurable impedance).
+	% 	% , where the former needs 2 reconfigurable impedance and the latter needs 3.
+	% 	% It is interesting that the huge difference comes purely from connecting both elements.
+	% 	Such a large gain comes from simply connecting both elements, and it can be even larger using an asymmetric component.
+	% 	% an even larger gain is expected when an asymmetric reconfigurable component is available.
+	% 	% An even larger gain is expected when an asymmetric reconfigurable component is available.
+	% 	% and a larger gain is expected when an asymmetric connection is available.
+	% 	This example shows that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
+	% \end{subsection}
+
+	% \begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
+
+	% \end{subsection}
+\end{section}
+
 \begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Design Frameworks}
@@
 	\end{maxi!}
-	where the objective function $f(\mathbf{\Theta})$ can be any function of the \gls{bd}-\gls{ris} scattering matrix, for example, channel singular value (covered in Section \ref{sc:singular_value}), channel power gain (covered in Section \ref{sc:power_rate}), and achievable rate (covered in Section \ref{sc:power_rate}).
+	where the objective function $f(\mathbf{\Theta})$ is a function of the \gls{bd}-\gls{ris} scattering matrix, for example, channel singular value (to be discussed in Section \ref{sc:pareto_frontier}), channel power gain (to be discussed in Section \ref{sc:power}), and achievable rate (to be discussed in Section \ref{sc:rate}).
 	The feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ that is non-convex and non-Euclidean.
 	Therefore, most \gls{bd}-\gls{ris} optimization problems are solved by \emph{relax-then-project} methods \cite{Fang2023} or \emph{general manifold \gls{rcg}} \cite{Li2023b,Li2023c,Zhou2023}.
-	The former solves unconstrained problem \eqref{ob:general} by quasi-Newton methods then projects the solution back to domain \eqref{co:general_unitary}, which often ends up far from optimal.
+	The former solves unconstrained problem \eqref{ob:general} by quasi-Newton methods then projects the solution back to domain \ref{co:general_unitary}, which often ends up far from optimal.
 	The latter generalizes the conjugate gradient methods to Riemannian manifolds and iteratively updates the solution by addition and retraction.
@@
 			\begin{equation}
-				\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}; % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+				\gamma_g^{(r)} = \frac{\tr\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}; % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
 				\label{eq:parameter_cg}
@@
 		\begin{equation}
-			\tilde{\gamma}_g^{(r)} = \frac{\mathrm{tr}\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\mathrm{tr}\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}.
+			\tilde{\gamma}_g^{(r)} = \frac{\tr\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}.
 % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
@@
 						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg_geodesic}
-						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
+						\If {$\Re\bigl\{\tr({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
 							\State $\mathbf{D}_g^{(r)} \gets \tilde{\nabla}_{\mathrm{R},g}^{(r)}$
@@
 						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic_translated}
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
+						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
 							\State $\mu \gets 2 \mu$
 						\EndWhile
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
+						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
 							\State $\mu \gets \mu / 2$
@@
 	\end{subsection}
-\end{section}
-
-\begin{section}{Channel Singular Values Redistribution}
-	\label{sc:singular_value}
-	In this section, we first provide a toy example to illustrate the channel shaping advantage of \gls{bd}-\gls{ris} architecture.
-	Next, we numerically characterize the attainable channel singular value region on top of Algorithm \ref{ag:rcg}.
-	Finally, we derive some analytical singular value bounds in specific channel conditions.
-	\begin{subsection}{Toy Example}\label{sc:toy_example}
-		We showcase the channel shaping capabilities of different \gls{ris} models by a toy example.
-		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-		The \gls{d}-\gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} can be modeled by 4 independent angular parameters
-		\begin{equation}
-			\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
-				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
-				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
-			\end{bmatrix}.
-			\label{eq:unitary_ris}
-		\end{equation}
-		It is worth noting that $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		To simplify the analysis, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of variables in the scattering matrix.
-		\begin{figure}
-			\centering
-			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
-			\caption{$2 \times 2 \times 2$ channel singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is blocked.
-$\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
-			Their maximum and minimum have been marked explicitly on the plot.}
-			\label{fg:singular_trend}
-		\end{figure}
-		Fig.~\ref{fg:singular_trend} compares the achievable singular values of one typical channel realization, where the backward and forward channels are given by
-		\begin{equation*}
-			\begin{split}
-				\mathbf{H}_\mathrm{B} & =
-				\begin{bmatrix}
-					-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
-					0.4131 + 0.2651 \jmath & -0.1960 + 0.4650 \jmath
-				\end{bmatrix},
-				\\
-				\mathbf{H}_\mathrm{F} & =
-				\begin{bmatrix}
-					-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
-					0.0196 + 0.4011 \jmath & -0.3170 - 0.2303 \jmath
-				\end{bmatrix}.
-			\end{split}
-		\end{equation*}
-		The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for \gls{d}-\gls{ris} and $(\alpha, \psi)$ for symmetric \gls{bd}-\gls{ris}.
-		In this example, we observe that both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} (using 2 reconfigurable impedance) and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (using 3 reconfigurable impedance).
-		% , where the former needs 2 reconfigurable impedance and the latter needs 3.
-		% It is interesting that the huge difference comes purely from connecting both elements.
-		Such a large gain comes from simply connecting both elements, and it can be even larger using an asymmetric component.
-		% an even larger gain is expected when an asymmetric reconfigurable component is available.
-		% An even larger gain is expected when an asymmetric reconfigurable component is available.
-		% and a larger gain is expected when an asymmetric connection is available.
-		This example shows that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
-	\end{subsection}
+
+% 	\label{sc:power_rate}
+	We would like to give a quick overview of what we have done so far.
+	[say why the analytical results are limited to what cases.]
+	In this section, we solve channel power gain maximization problem in closed-form and then extend the discussion to achievable rate maximization problem.
+	The implication of the former on the latter is investigated.
 
@@
 		\end{maxi!}
-		where $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ is the maximum channel rank, and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
-		Varying $\{\rho_n\}_{n \in \mathcal{N}}$ characterizes the Pareto frontier that encloses the entire singular value region.
-		Thus, we claim problem \eqref{op:pareto} generalizes most singular value shaping problems.
-		It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given by Lemma \ref{lm:pareto_gradient}.
+		where $n \in [N]$ is the maximum channel rank, and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
+		Varying $\{\rho_n\}_{n \in [N]}$ characterizes the Pareto frontier enclosing the singular value region such that problem \eqref{op:pareto} generalizes most singular value shaping problems.
+		It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:pareto_gradient}.
 		% It can be solved optimally by Algorithm~\ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses the following Euclidean gradient expression \eqref{eq:pareto_gradient}.
@@
 			\begin{equation}
-				\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathrm{diag}(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
+				\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \diag(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
 				\label{eq:pareto_gradient}
@@
 	\end{subsection}
-
-	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
-		We also provide some analytical bounds related to channel singular values, which help us to explore the limits of channel shaping using passive \gls{ris}.
-
-		\begin{definition}[Degrees of freedom]
-			\gls{dof} (a.k.a. multiplexing gain) refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, which is defined asymptotically as
-			\begin{equation}
-				d = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho},
-			\end{equation}
-			where $\rho$ is the \gls{snr}.
-
-		\end{definition}
-
-		\begin{proposition}[Degrees of freedom]\label{pp:dof}
-			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:dof}.
-		\end{proof}
-
-		Proposition \ref{pp:dof} suggests that we cannot hope for a \gls{dof} gain (i.e., more parallel channels) by simply connecting the \gls{ris} elements.
-		We thus focus on the question of reshaping the available channels through manipulation of the singular values.
-
-		% you cannot hope for degrees of freedom gain (i.e. more channels) thus we focus ont he question of reshaping of the available channels through manipulation of the singular values.
-
-		\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
-			% If the forward or backward channel is rank-$k$ ($k \le N$),
-			If the minimum rank of backward and forward channels is $k$ ($k \le N$),
-			then for \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
-			\begin{subequations}
-				\begin{align}
-					\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_bound_enlarge}          \\
-					\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
-				\end{align}
-				\label{iq:sv_bound_rank_deficient}
-			\end{subequations}
-			where $\mathbf{T}$ is an auxiliary matrix satisfying
-			\begin{equation}
-				\mathbf{T} \mathbf{T}^\mathsf{H} =
-				\begin{cases}
-					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
-					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
-				\end{cases}
-				\label{eq:auxiliary_matrix}
-			\end{equation}
-			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:rank_deficient}.
-		\end{proof}
-
-		Inequality \eqref{iq:sv_bound_enlarge} states that
-		if the backward and backward channels are at least rank $k$, then
-		% with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements,
-		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
-		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
-This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
-		An example is given in Corollary \ref{co:los} for \gls{los} channels (i.e., $k=1$)\footnote{A similar eigenvalue result for \gls{d}-\gls{ris} has been derived in \cite{Semmler2023}.}.
-		% states that the $n$-th channel singular value can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$.
-
-		% We would like to give some insights into Proposition \ref{pp:rank_deficient}.
-
-		% \begin{corollary}[Extreme singular values\label{co:extreme}]
-		% 	If the minimum rank of forward and backward channels is $k$ ($k \le N$), then with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
-This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
-		% \end{corollary}
-
-		% \begin{proof}
-		% 	This is a direct result of \eqref{iq:sv_bound_rank_deficient}.
-		% \end{proof}
-
-		\begin{corollary}[\gls{los} channel\label{co:los}]
-			% If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
-suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
-$n$-th) singular value of $\mathbf{T}$, that is,
-			If at least one of backward and forward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
-			That is,
-			\begin{equation}
-				\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
-				\label{iq:sv_bound_los}
-			\end{equation}
-		\end{corollary}
-
-		\begin{proof}
-			This is a direct result of \eqref{iq:sv_bound_rank_deficient} with $k = 1$.
-		\end{proof}
-
-		We highlight that Proposition \ref{pp:rank_deficient} is an asymptotic result and the inequalities apply to \gls{d}- and \gls{bd}-\gls{ris} with arbitrary number of elements, regardless of the presence of direct channel.
-		The bounds are asymptotically tight when the number of scattering elements approaches infinity.
-		On the other hand, we will show in Section \ref{sc:simulation} that with a finite number of elements, \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris}.
-		Proposition \ref{pp:rank_deficient} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a reference for choosing the number of scattering elements in a practical deployment scenario.
-
-		\begin{proposition}[Blocked direct channel]\label{pp:fully_connected}
-			% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-
-			If the direct link is blocked and the \gls{bd}-\gls{ris} is fully-connected, then the channel singular values can be manipulated up to
-			% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
-			% only bounds that apply here are those that apply to the singular values of
-			\begin{equation}
-				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
-			\end{equation}
-			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with $\mathrm{sv}(\mathbf{B})=\mathrm{sv}(\mathbf{H}_\mathrm{B})$ and $\mathrm{sv}(\mathbf{F})=\mathrm{sv}(\mathbf{H}_\mathrm{F})$.
-			% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:fully_connected}.
-		\end{proof}
-
-		Proposition \ref{pp:fully_connected} states that if the direct channel is blocked and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are the singular value bounds on the product of unitary-transformed backward and forward channels.
-		% , a group-connected \gls{bd}-\gls{ris} in its most powerful form can manipulate the channel singular values to any possible state with zero power loss.
-		For example, consider a $2 \times 2 \times 2$ setup with
-		% $\mathrm{sv}(\mathbf{H}_\mathrm{B}) = [3, 2]^\mathsf{T}$ and $\mathrm{sv}(\mathbf{H}_\mathrm{B}) = [4, 1]^\mathsf{T}$.
-		\begin{equation*}
-			\mathbf{H}_\mathrm{B} =
-				\begin{bmatrix}
-					3 & 0 \\
-					0 & 2
-				\end{bmatrix},
-				\quad
-				\mathbf{H}_\mathrm{F} =
-				\begin{bmatrix}
-					1 & 0 \\
-					0 & 4
-				\end{bmatrix}.
-		\end{equation*}
-		It is obvious that any \gls{d}-\gls{ris} can only attain $\mathrm{sv}(\mathbf{H}) = [8, 3]^\mathsf{T}$ while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ results in $\mathrm{sv}(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-		% We thus conclude that a fully-connected \gls{bd}-\gls{ris} can apply right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, which widens channel singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this example.
-
-		% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this case.
-
-		Proposition \ref{pp:fully_connected} is important since it transforms the channel shaping question to a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
-		Let $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le \bar{N}$.
-		We have the following corollaries.
-
-		\begin{corollary}[Generic singular value bounds\label{co:sv_bound_horn}]
-			\begin{equation}
-				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
-				\label{iq:sv_bound_fc}
-			\end{equation}
-			for all admissible triples $(I, J, K) \in T_r^{\bar{N}}$ with $r < \bar{N}$, where
-			\begin{equation*}
-				\begin{gathered}
-					% T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
-					% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \mid \forall p < r, (F, G, H) \in T_p^r,\\
-					\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-				\end{gathered}
-			\end{equation*}
-			\begin{equation*}
-				U_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
-			\end{equation*}
-		\end{corollary}
-
-		\begin{proof}
-			Please refer to \cite[Theorem~8]{Fulton2000}.
-		\end{proof}
-
-		Corollary \eqref{co:sv_bound_horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is the most comprehensive channel singular value bound attainable by passive \gls{ris} when the direct channel is blocked.
-		We observe that the number of admissible triples (and thus bounds) grows exponentially with $\bar{N}$.
-		For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $\bar{N}$ increases from 3 to 7.
-		This renders the analytic approach computationally expensive for large-scale \gls{mimo} systems.
-		Next, we showcase some useful inequalities enclosed by \eqref{iq:sv_bound_fc}.
-		Interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} for more information.
-
-		\begin{corollary}[Upper bound on the largest singular value\label{co:sv_largest}]
-			\begin{equation}
-				\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}).
-			\end{equation}
-		\end{corollary}
-
-		\begin{proof}
-			This is a direct result of \eqref{iq:sv_bound_fc} with $r = 1$.
-		\end{proof}
-
-		\begin{corollary}[Lower bound on the smallest singular value\label{co:sv_smallest}]
-			\begin{equation}
-				\sigma_{\bar{N}}(\mathbf{H}) \ge \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}).
-			\end{equation}
-		\end{corollary}
-
-		\begin{proof}
-			This can be deducted from \eqref{iq:sv_bound_fc} with $r_1 = \bar{N}{-}1$ and $r_2 = \bar{N}$.
-		\end{proof}
-
-		\begin{corollary}[Upper bound on the product of first $k$ singular values]
-			\begin{equation}
-				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
-			\end{equation}
-		\end{corollary}
-
-		\begin{proof}
-			This is a direct result of \eqref{iq:sv_bound_fc} with $r = k$.
-		\end{proof}
-
-		\begin{corollary}[Lower bound on the product of last $k$ singular values\label{co:sv_product_smallest}]\footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
-			\begin{equation}
-				\prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
-			\end{equation}
-		\end{corollary}
-
-		\begin{proof}
-			This can be deducted from \eqref{iq:sv_bound_fc} with $r_1 = \bar{N}-k$ and $r_2 = \bar{N}$.
-		\end{proof}
-
-		% \begin{corollary}[Upper bound on the sum of first $k$ singular values to the positive $p$-th power\label{co:sum_power} {\cite[Inequality~24.4.7]{Hogben2013}}]
-		% 	\begin{equation}
-		% 		\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
-		% 		\label{iq:sv_bound_fc_power}
-		% 	\end{equation}
-		% 	When $k = N$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward channels
-		% 	\begin{equation}
-		% 		\lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
-		% 	\end{equation}
-		% \end{corollary}
-
-		\begin{corollary}[Upper bound on the channel power gain\label{co:sum_power}]
-			% The channel power gain is upper bounded by the sum of sorted element-wise power product of backward and forward channels
-			The channel power gain is upper bounded by the sum of element-wise product of squared singular values of backward and forward channels
-			\begin{equation}
-				\lVert \mathbf{H} \rVert _\mathrm{F}^2 = \sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}).
-				\label{iq:power_gain}
-			\end{equation}
-		\end{corollary}
-
-		\begin{proof}
-			Please refer to \cite[Inequality~24.4.7]{Hogben2013}.
-		\end{proof}
-
-		To achieve equalities in Corollaries \ref{co:sv_largest} -- \ref{co:sum_power}, the \gls{ris} needs to completely align the singular vector spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
-		The resulting scattering matrix is generally required to be unitary
-		\begin{equation}
-			\mathbf{\Theta}^\star = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H},
-			\label{eq:scattering_fc_optimal}
-		\end{equation}
-		which can be concluded from \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in Appendix~\ref{ap:fully_connected}.
-		We notice that \gls{d}-\gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
-		In such case, the equivalent channel reduces to $\mathbf{H} = \sigma_\mathrm{B} \sigma_\mathrm{F} \mathbf{u}_\mathrm{B} \mathbf{v}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ and the \gls{ris} only needs to align $\mathbf{v}_\mathrm{B}^\mathsf{H}$ and $\mathbf{u}_\mathrm{F}$ by
-		\begin{equation}
-			\mathbf{\Theta}^\star = \mathbf{v}_\mathrm{B} \mathbf{u}_\mathrm{F}^\mathsf{H} \odot \mathbf{I},
-		\end{equation}
-		which becomes a special case of \eqref{eq:scattering_siso}.
-		However, in general \gls{d}-\gls{ris} is not sufficient to achieve the upper bound of channel power gain.
-		This again highlights the benefit of \gls{bd}-\gls{ris} in reshaping available channels.
-		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the maximum expected channel power gain can be numerically evaluated as
-		\begin{equation}
-			\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\} = \sum_{n=1}^N \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x) d x,
-			\label{eq:power_gain_rayleigh}
-		\end{equation}
-		% \begin{equation}
-		% 	\begin{split}
-		% 		\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\}
-		% 		& = \sum_{n=1}^N \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x_n) d x_n \\
-		% 		& \quad \times \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x_n) d x_n,
-		% 	\end{split}
-		% 	\label{eq:power_gain_rayleigh}
-		% \end{equation}
-		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(x)$ given by \cite[Equation 51]{Zanella2009}.
-		We note that \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain attainable by \gls{bd}-\gls{ris} \cite[Equation 58]{Shen2020a} to \gls{mimo} and models the contribution of transmit and receive antennas under double Rayleigh fading.
-		In Section \ref{sc:simulation}, we will numerically evaluate the channel power gain and compare it with the theoretical upper bound.
-
-		% Expression \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo} and unveils
-
-		% , unveiling how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
-		% is a generalization of \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo}, which unveils how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
-		% However, a closed-form expression is non-trivial due to the complexity of distribution of ordered eigenvalues of Wishart matrices.
-		% ordered Wishart matrix eigenvalue distribution.
-		% provides a benchmark for the channel power gain of \gls{bd}-\gls{ris} in Rayleigh fading channels.
-
-		Proposition \ref{pp:fully_connected} and Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} provide a comprehensive answer to the shaping capability question in terms of singular value bounds and channel power gain limits.
-		% understanding of the channel power gain limits of passive \gls{ris}.
-		% and suggest the impact of channel rearrangement and space alignment on redistributing channel singular values.
-		% When the direct channel is present,
-		% Similar results are inapplicable
-		Extending those results to the case of direct channel is non-trivial since the singular vector spaces of direct-indirect channels and backward-forward channels cannot be aligned at the same time.
-		In such case, we can invoke optimization approaches from a singular value perspective (Section~\ref{sc:pareto_frontier}) or a power gain perspective (Section~\ref{sc:power}).
-	\end{subsection}
-\end{section}
-
-\begin{section}{Power Gain and Achievable Rate Maximization}
-	\label{sc:power_rate}
-	In this section, we solve channel power gain maximization problem in closed-form and then extend the discussion to achievable rate maximization problem.
-	The implication of the former on the latter is investigated.
 
@@
 		\end{maxi!}
-		which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with fully-connected \gls{bd}-\gls{ris} \eqref{eq:scattering_fc_optimal}.
+		which generalizes the problem of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and \gls{mimo} with negligible direct channel and fully-connected \gls{bd}-\gls{ris} \eqref{eq:scattering_fc_optimal}.
 		Solving \eqref{op:power_passive} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
@@
 
-		It is worth noting that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power_passive} when the direct link is blocked and present, respectively.
+		It is worth noting that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power_passive} when the direct channel is negligible and significant, respectively.
 		However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
@@
 			\begin{equation}
-				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
 				\label{eq:auxiliary_matrix_power}
 			\end{equation}
+			% \begin{equation}
+			% 	% \begin{split}
+			% 		\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{1}^{(r+1)},\ldots,\mathbf{\Theta}_{g-1}^{(r+1)},\mathbf{\Theta}_{g}^{(r)},\ldots,\mathbf{\Theta}_{G}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+			% 	% \end{split}
+			% 	\label{eq:auxiliary_matrix_power}
+			% \end{equation}
 		\end{proposition}
@@
 			where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-			Problem \eqref{op:rate_passive} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given by Lemma \ref{lm:rate_gradient}.
+			Problem \eqref{op:rate_passive} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate_gradient}.
 			\begin{lemma}\label{lm:rate_gradient}
@@
 			\begin{equation}
-				\mathbf{W}^\star = \mathbf{V} {\mathrm{diag}(\mathbf{s}^\star)}^{1/2},
+				\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
 				\label{eq:precoder_eigenmode}
@@
 \end{section}
+
+% \begin{section}{Power Gain and Achievable Rate Maximization}
+% 	\label{sc:power_rate}
+% 	In this section, we solve channel power gain maximization problem in closed-form and then extend the discussion to achievable rate maximization problem.
+% 	The implication of the former on the latter is investigated.
+
+% 	\begin{subsection}{Channel Power Gain}\label{sc:power}
+% 		The \gls{mimo} channel power gain maximization problem is formulated with respect to the \gls{bd}-\gls{ris} scattering matrix
+% 		\begin{maxi!}
+% 			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{\label{cs:power_block_unitary}}{}
+% 		\end{maxi!}
+% 		which generalizes the problem of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and \gls{mimo} with negligible direct channel and fully-connected \gls{bd}-\gls{ris} \eqref{eq:scattering_fc_optimal}.
+% 		Solving \eqref{op:power_passive} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
+% 		% The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative space alignments.
+
+% 		\begin{remark}
+% 			Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
+% 			\begin{mini!}
+% 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
+% 				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_unitary}}{}
+% 			\end{mini!}
+% 			which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary \eqref{cs:power_unitary} but still has no trivial solution.
+% 			One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
+% 			\begin{mini!}
+% 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
+% 				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
+% 			\end{mini!}
+% 			which have global optimal solutions
+% 			\begin{equation}
+% 				\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
+% 				\label{eq:orthogonal_procrustes_solution}
+% 			\end{equation}
+% 			where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right compact singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
+% 		\end{remark}
+
+% 		It is worth noting that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power_passive} when the direct channel is negligible and significant, respectively.
+% 		However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
+% 		Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power_passive} with arbitrary group size.
+% 		The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
+
+% 		\begin{proposition}\label{pp:power}
+% 			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
+% 			\begin{equation}
+% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
+% 				\label{eq:scattering_power}
+% 			\end{equation}
+% 			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrices of
+% 			\begin{equation}
+% 				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+% 				\label{eq:auxiliary_matrix_power}
+% 			\end{equation}
+% 			% \begin{equation}
+% 			% 	% \begin{split}
+% 			% 		\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{1}^{(r+1)},\ldots,\mathbf{\Theta}_{g-1}^{(r+1)},\mathbf{\Theta}_{g}^{(r)},\ldots,\mathbf{\Theta}_{G}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+% 			% 	% \end{split}
+% 			% 	\label{eq:auxiliary_matrix_power}
+% 			% \end{equation}
+% 		\end{proposition}
+
+% 		\begin{proof}
+% 			Please refer to Appendix~\ref{ap:power}.
+% 		\end{proof}
+
+% 		We now analyze the computational complexity of solving channel gain maximization problem \eqref{op:power_passive} by Proposition \ref{pp:power}.
+% 		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_matrix_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its compact \gls{svd} requires $\mathcal{O}(L^3)$ operations.
+% 		The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
+% 	\end{subsection}
+
+% 	\begin{subsection}{Achievable Rate Maximization}\label{sc:rate}
+% 		We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
+% 		\begin{maxi!}
+% 			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
+% 			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cs:rate_block_unitary}}
+% 		\end{maxi!}
+% 		where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
+% 		Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cs:rate_block_unitary} and the coupling between variables.
+% 		We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
+
+% 		\begin{subsubsection}{Alternating Optimization}
+% 			This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
+% 			For a given $\mathbf{W}$, the passive beamforming subproblem is
+% 			\begin{maxi!}
+% 				{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
+% 				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+% 			\end{maxi!}
+% 			where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
+% 			Problem \eqref{op:rate_passive} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate_gradient}.
+% 			\begin{lemma}\label{lm:rate_gradient}
+% 				The Euclidean gradient of \eqref{ob:rate_passive} with respect to \gls{bd}-\gls{ris} block $g$ is
+% 				\begin{equation}
+% 					\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+% 					\label{eq:rate_gradient}
+% 				\end{equation}
+% 			\end{lemma}
+
+% 			\begin{proof}
+% 				Please refer to Appendix~\ref{ap:rate_gradient}.
+% 			\end{proof}
+% 			For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
+% 			\begin{equation}
+% 				\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
+% 				\label{eq:precoder_eigenmode}
+% 			\end{equation}
+% 			where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation obtainable by the iterative method \cite{Tse2005}.
+
+% 			The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
+% 			Similar to the analysis in Section \ref{sc:pareto_frontier}, the computational complexity of solving subproblem \eqref{op:rate_passive} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
+% 			On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder_eigenmode} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+% 			The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
+% 		\end{subsubsection}
+
+% 		\begin{subsubsection}{Low-Complexity Solution}\label{sc:low_complexity}
+% 			We finally propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
+% 			The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_passive} by channel power gain maximization problem \eqref{op:power_passive}, then proceed to conventional eigenmode transmission \eqref{eq:precoder_eigenmode}.
+% 			Both steps are solved in closed form and the computational complexity is $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr) + N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+% 			While suboptimal, this shaping-inspired solution avoids outer iterations and efficiently handles inner iterations.
+% 		\end{subsubsection}
+% 	\end{subsection}
+% \end{section}
 
@@
 			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ \gls{mimo} reshaped by a \gls{ris}.
-			When the direct link is blocked, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
+			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
 			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two spaces.
@@
 			We observe that the smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
-			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
+			When the direct channel is significant, the shape of the singular value region depends heavily on the relative strength of the indirect channels.
 			In Fig.
@@
 					Average maximum channel power gain versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
-					The direct channel is blocked.
+					The direct channel is negligible.
 					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward channels.
@@
 			Fig.
-\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is blocked.
+\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct channel is negligible.
 			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_optimal} or via optimization approach \eqref{eq:scattering_power}.
@@
 \subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-			It comes purely from channel rearrangement in \eqref{eq:gain_rearrangement} and aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite[Equation 30]{Shen2020a}.
+			It comes purely from branch matching and agrees with the asymptotic power scaling law derived for \gls{siso} in \cite[Equation 30]{Shen2020a}.
 			Interestingly, this relative power gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig.
@@
 		Fig. \ref{fg:power_sx} shows the maximum channel power under different \gls{ris} configurations.
-		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is even larger with direct link.
+		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is even larger when the direct channel is significant.
 		For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power gain as a 256-element \gls{d}-\gls{ris} in Fig.
@@
 		% This again credits to the superior space alignment capability of \gls{bd}-\gls{ris}.
-		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the space alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
+		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the mode alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
 		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
@@
 	We also present two beamforming designs for rate maximization problem, one for optimal performance and the other exploits channel shaping for lower complexity.
-	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior space alignment and channel rearrangement capability, which scales with the number of elements, group size, and \gls{mimo} dimensions.
+	Extensive simulations show that the shaping advantage of \gls{bd}-\gls{ris} stems from its superior branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.
 
@@
 \begin{appendix}
-	\begin{subsection}{Proof of Lemma \ref{lm:pareto_gradient}}\label{ap:pareto_gradient}
-		Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the compact \gls{svd} of the equivalent channel.
-		Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
-		\begin{equation}
-			\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*,
-		\end{equation}
-		whose differential with respect to $\mathbf{\Theta}_g^*$ is
-		\begin{align*}
-			\partial \sigma_n
-			 & = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^* \\
-			 & = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}                                                                                                                  \\
-			 & = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*                                                                                                                                                                                                                                                 \\
-			 & = \mathrm{tr}(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
-		\end{align*}
-		According to \cite{Hjorungnes2007}, the corresponding complex derivative is
-		\begin{equation}
-			\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-			\label{eq:derivative_sv}
-		\end{equation}
-		A linear combination of \eqref{eq:derivative_sv} yields \eqref{eq:pareto_gradient}.
-	\end{subsection}
-
 	\begin{subsection}{Proof of Proposition \ref{pp:dof}}\label{ap:dof}
@@
 		\end{equation*}
-		The same result holds if the direct link is present.
+		The same result holds if the direct channel is significant and the proof is omitted here.
 	\end{subsection}
@@
 		That is to say, $\mathbf{G}$ can be expressed as a Hermitian matrix plus $k$ rank-1 perturbations.
-		According to the Cauchy interlacing formula \cite{Golub2013}, the $n$-th eigenvalue of $\mathbf{G}$ is bounded by
+		According to the Cauchy interlacing formula \cite[Theorem 8.4.3]{Golub2013}, the $n$-th eigenvalue of $\mathbf{G}$ is bounded by
 		\begin{align}
@@
 
-	\begin{subsection}{Proof of Proposition \ref{pp:fully_connected}}\label{ap:fully_connected}
+	\begin{subsection}{Proof of Proposition \ref{pp:direct_negligible}}\label{ap:direct_negligible}
 		Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
@@
 		\end{equation}
-		Since $\mathrm{sv}(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \mathrm{sv}(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
+		Since $\sv(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \sv(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
 		\begin{align*}
-			\mathrm{sv}(\mathbf{H}) & = \mathrm{sv}(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})                                                                     \\
-			                        & = \mathrm{sv}(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})                                                                                                                            \\
-			                        & = \mathrm{sv}(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H}) \\
-			                        & = \mathrm{sv}(\mathbf{BF}),
+			\sv(\mathbf{H}) & = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})                                                                     \\
+			                        & = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})                                                                                                                            \\
+			                        & = \sv(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H}) \\
+			                        & = \sv(\mathbf{BF}),
 		\end{align*}
@@
 
-	\begin{subsection}{Proof of Lemma \ref{lm:rate_gradient}}\label{ap:rate_gradient}
-		The differential of $R$ with respect to $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
+	\begin{subsection}{Proof of Corollary \ref{co:sv_product}}\label{ap:sv_product}
+		\eqref{iq:sv_product_largest} is one of the many inequalities enclosed in \eqref{iq:sv_bound_fc} when $r = k$.
+			On the other hand, \ref{eq:sv_fully_connected} implies that
+			$\det(\mathbf{H}) = \det(\mathbf{B}\mathbf{F}) = \det(\mathbf{B})\det(\mathbf{F}) = \det(\mathbf{H}_\mathrm{B})\det(\mathbf{H}_\mathrm{F})$ and thus
+			\begin{equation}
+				\prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}).
+				\label{eq:sv_product}
+			\end{equation}
+			\eqref{eq:sv_product} together with \eqref{iq:sv_product_largest} and the non-negativity of singular values results in \eqref{iq:sv_product_smallest}.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Corollary \ref{co:sv_nth}}\label{ap:sv_nth}
+		% In \eqref{iq:sv_nth}, the set of upper bounds
+		% \begin{equation}
+		% 	\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+1\bigr\}
+		% 	\label{iq:sv_nth_upper_set}
+		% \end{equation}
+		% is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [\bar{N}]^3$.
+		% The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
+However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nth_upper_set} is selected as the tightest upper bound in \eqref{iq:sv_nth}.
+		% On the other hand, the set of lower bounds
+		% \begin{equation}
+		% 	\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+\bar{N}\bigr\}
+		% 	\label{iq:sv_nth_lower_set}
+		% \end{equation}
+		% can be induced by \eqref{iq:sv_nth_upper_set}, \eqref{eq:sv_product}, and the non-negativity of singular values.
+		% The maximum of \eqref{iq:sv_nth_lower_set} is selected as the tightest lower bound in \eqref{iq:sv_nth}.
+
+		% To attain the upper bound of $\sigma_n(\mathbf{H})$, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ channel singular values.
+		% This is achieved by proper matching of the first $n$ modes of $\mathbf{H}_\mathrm{B}$ to the first $n$ modes of $\mathbf{H}_\mathrm{F}$.
+		% In particular, mode $i$ of $\mathbf{H}_\mathrm{B}$ should be completely aligned with mode $j$ of $\mathbf{H}_\mathrm{F}$ where $(i, j) = \arg \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{P}$
+
+		% % Interested readers are referred to \cite[Equation~2.0.3]{Zhang2005} for more information.
+		% % $i$-th mode of $\mathbf{H}_\mathrm{B}$ with the $j$-th mode of $\mathbf{H}_\mathrm{F}$ such that the $n$-th mode of $\mathbf{H}$ is maximized.
+
+		% % Maximizing $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is equivalent to maximizing the minimum of the first $n$ channel singular values.
+		% % As such, the \gls{bd}-\gls{ris} needs to align t
+		% % align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that the first $n$ modes of $\mathbf{H}$ are maximized.
+		% % To maximize the $n$-th channel singular value, the \gls{bd}-\gls{ris} needs to ensure
+		% % that the first $n$ modes of $\mathbf{H}$ are
+
+		% % should align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that
+
+		% % \cite[Equation~2.0.3]{Zhang2005}
+	\end{subsection}
+
+	\begin{subsection}{Proof of Corollary \ref{co:sum_power}}\label{ap:sum_power}
+		From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} we have
+		\begin{equation}
+			\begin{split}
+				\lVert \mathbf{H} \rVert _\mathrm{F}^2
+				& = \tr \bigl(\mathbf{V}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{U}_\mathrm{B}^\mathsf{H} \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}\bigr) \\
+				& = \tr \bigl(\mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \cdot \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H}\bigr) \\
+				& \triangleq \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr),
+			\end{split}
+			\label{eq:channel_power_gain}
+		\end{equation}
+		where $\mathbf{X} \triangleq \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, $\tilde{\mathbf{B}} \triangleq \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\tilde{\mathbf{F}} \triangleq \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$.
+		By Ruhe's trace inequality for positive semi-definite matrices \cite[H.1.g and H.1.h]{Marshall2010},
+		\begin{equation*}
+			\sum_n \lambda_n(\tilde{\mathbf{B}}) \lambda_{N_\mathrm{S}-n+1}(\tilde{\mathbf{F}}) \le \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr) \le \sum_n \lambda_n(\tilde{\mathbf{B}}) \lambda_n(\tilde{\mathbf{F}}),
+		\end{equation*}
+		which simplifies to \eqref{iq:power_gain}.
+		The upper bound is attained when $\mathbf{X}$ is chosen to match the singular values of $\tilde{\mathbf{F}}$ to those of $\tilde{\mathbf{B}}$ in similar order.
+		Apparently this occurs at $\mathbf{X} = \mathbf{I}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
+		On the other hand, the lower bound is attained when the singular values of $\tilde{\mathbf{F}}$ and $\tilde{\mathbf{B}}$ are matched in reverse order, namely $\mathbf{X} = \mathbf{J}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Lemma \ref{lm:pareto_gradient}}\label{ap:pareto_gradient}
+		Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the compact \gls{svd} of the equivalent channel.
+		Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
+		\begin{equation}
+			\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*,
+		\end{equation}
+		whose differential with respect to $\mathbf{\Theta}_g^*$ is
 		\begin{align*}
-			\partial R
-			 & = \frac{1}{\eta} \mathrm{tr} \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}                                                                      \\
-			 & = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\} \\
-			 & = \frac{1}{\eta} \mathrm{tr} \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
+			\partial \sigma_n
+			 & = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^* \\
+			 & = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}                                                                                                                  \\
+			 & = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*                                                                                                                                                                                                                                                 \\
+			 & = \tr(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
 		\end{align*}
-		and the corresponding complex derivative is \eqref{eq:rate_gradient}.
+		According to \cite{Hjorungnes2007}, the corresponding complex derivative is
+		\begin{equation}
+			\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+			\label{eq:derivative_sv}
+		\end{equation}
+		A linear combination of \eqref{eq:derivative_sv} yields \eqref{eq:pareto_gradient}.
 	\end{subsection}
@@
 			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
-			 & = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr) \\
-			 & = \mathrm{tr}\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
+			 & = \tr\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr) \\
+			 & = \tr\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
 		\end{align*}
@@
 		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_passive_approx}}{\label{ob:power_passive_approx}}
+			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_passive_approx}}{\label{ob:power_passive_approx}}
 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
@@
 		\begin{equation}
-			\Re \bigl\{\mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \mathrm{tr}(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \mathrm{tr}(\mathbf{\Sigma}_g).
+			\Re \bigl\{\tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \tr(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \tr(\mathbf{\Sigma}_g).
 		\end{equation}
@@
 		Next, we prove that solving \eqref{op:power_passive_approx} successively does not decrease \eqref{ob:power_passive}.
-		Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \mathrm{tr}(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
+		Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
 		% Expanding both side gives \eqref{iq:power_passive_approx}.
@@
 		\begin{multline}
-			2 \Re \Bigl\{\mathrm{tr}(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
-			\ge 2 \Re \Bigl\{\mathrm{tr}({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \mathrm{tr}(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
+			2 \Re \Bigl\{\tr(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
+			\ge 2 \Re \Bigl\{\tr({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
 		\end{multline}
@@
 				\resizebox{0.95\textwidth}{!}{
-					$2 \Re \Bigl\{\sum\limits_g \mathrm{tr}(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \mathrm{tr}({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \mathrm{tr}({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
+					$2 \Re \Bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
 				}
@@
 				\resizebox{0.95\textwidth}{!}{
-					$\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \mathrm{tr}(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
+					$\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
 				}
@@
 	\end{subsection}
+
+	\begin{subsection}{Proof of Lemma \ref{lm:rate_gradient}}\label{ap:rate_gradient}
+		The differential of $R$ with respect to $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
+		\begin{align*}
+			\partial R
+			 & = \frac{1}{\eta} \tr \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}                                                                      \\
+			 & = \frac{1}{\eta} \tr \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\} \\
+			 & = \frac{1}{\eta} \tr \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
+		\end{align*}
+		and the corresponding complex derivative is \eqref{eq:rate_gradient}.
+	\end{subsection}
+
 \end{appendix}
@@
 % 		% 		\lambda_k^{(r)}
-% 		% 		& = \frac{\sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)\mathsf{H}}}) - \sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)\mathsf{H}}})}{P_k} \\
-% 		% 		& \quad + \frac{\mathrm{tr}(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}})}{P_k}
+% 		% 		& = \frac{\sum_{j \ne k} \tr(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)\mathsf{H}}}) - \sum_{j \ne k} \tr(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)\mathsf{H}}})}{P_k} \\
+% 		% 		& \quad + \frac{\tr(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}})}{P_k}
 % 		% 	\end{split}
@@
 % 		\begin{equation}
-% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
+% 			\lambda_k^{(r)} = \frac{\tr\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
 % 		\end{equation}

### 2024-11-18 main.tex
:construction: Updating Proposition 3

@@
 \usepackage[makeroom]{cancel}
-% \usepackage{cases}
+\usepackage{cases}
 \usepackage[american]{circuitikz}
@@
 % \usepackage{cleveref}
+\usepackage{enumitem}
 
@@
 \newtheorem{corollary}{Corollary}[proposition]
+
+% enumitem
+\setlist[itemize]{leftmargin=5mm}
+\setlist[enumerate]{leftmargin=5mm}
 
@@
 		% The equalities in \eqref{iq:sv_bound_rank_deficient} and \eqref{iq:sv_bound_los}
-		can be \emph{simultaneously} tight as $N_\mathrm{S}$ goes to infinity, namely, when the direct channel becomes negligible\footnote{Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
+		can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible\footnote{Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
 This can result from a very large number of \gls{ris} elements (as discussed in Proposition~\ref{pp:rank_deficient}) or physical obstacles in the propagation path (as discussed in Proposition~\ref{pp:direct_negligible}).}.
@@
 			The upper and lower bounds are attained respectively at
+			\begin{subequations}
+				\label{eq:sv_nth}
+				\begin{align}
+					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_max} \\
+					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_min}
+				\end{align}
+			\end{subequations}
+			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are the right and left singular matrices\footnote{We highlight the non-uniqueness of $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$.
+When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace.
+Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.} of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			and $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary permutation matrices of dimension $N_\mathrm{S}$ satisfying:
+			\begin{itemize}
+				\item The $(i, j)$-th entry is $1$, where
+				% \begin{equation*}
+				% 	(i, j) =
+				% 	\begin{cases}
+				% 		\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{P}, \\
+				% 		\underset{i+j=n+\bar{N}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{Q},
+				% 	\end{cases}
+				% \end{equation*}
+				\begin{subnumcases}{(i, j) =}
+					\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:sv_nth_max_pair} \\
+					\underset{i+j=n+\bar{N}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:sv_nth_min_pair}
+				\end{subnumcases}
+				% \begin{equation*}
+				% 	(i, j) =
+				% 	\begin{cases}
+				% 		\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{P}, \\
+				% 		\underset{i+j=n+\bar{N}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{Q},
+				% 	\end{cases}
+				% \end{equation*}
+				and ties may be broken arbitrarily;
+				% with ties broken arbitrarily;
+				% and the tie-breaking rule is arbitrary.
+				\item After deleting the $i$-th row and $j$-th column, the resulting submatrix $\mathbf{Y}$ is arbitrary permutation matrix of dimension $N_\mathrm{S}-1$ satisfying
+				% \begin{subequations}
+				% 	\begin{alignat}{1}
+				% 		\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{P}, \hspace{-0.17cm} \label{eq:sv_nth_max_condition} \\
+				% 		\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\le} \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{Q}, \hspace{-0.17cm} \label{eq:sv_nth_min_condition}
+				% 	\end{alignat}
+				% \end{subequations}
+
+				\begin{subequations}
+					\begin{alignat}{2}
+						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{P}, \label{eq:sv_nth_max_condition} \\
+						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
+					\end{alignat}
+				\end{subequations}
 				% \begin{subequations}
 				% 	\begin{align}
-			% 		\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_max} \\
-			% 		\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_min}
+				% 		\sigma_{n-1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \ge \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{P}, \label{eq:sv_nth_max_condition} \MoveEqLeft[1] \\
+				% 		\sigma_{n+1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \le \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
 				% 	\end{align}
 				% \end{subequations}
-			\begin{subequations}
-				\begin{align}
-					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{L} \mathbf{P} \mathbf{R} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_max} \\
-					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{L} \mathbf{Q} \mathbf{R} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_min}
-				\end{align}
-			\end{subequations}
-			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are the right and left singular matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively, $\mathbf{L}, \mathbf{R}$ are arbitrary block-diagonal unitary matrices with size of block $n \in [N_\mathrm{S}]$ equal to the multiplicity of $\sigma_n(\mathbf{H}_\mathrm{B})$ and $\sigma_n(\mathbf{H}_\mathrm{B})$, respectively,
-			% $\mathbf{\Theta}_\mathrm{D}$ is arbitrary diagonal matrix with unit-magnitude diagonal entries,
-			and $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary doubly stochastic matrices of dimension $N_\mathrm{S}$ satisfying:
-			\begin{itemize}
-				\item The $(i, j)$-th entries sum up to $1$, where
-				\begin{equation*}
-					(i, j) =
-					\begin{cases}
-						\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \triangleq \mathcal{S}_n(\mathbf{P}) & \text{for } \mathbf{P}, \\
-						\underset{i+j=n+\bar{N}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \triangleq \mathcal{S}_n(\mathbf{Q}) & \text{for } \mathbf{Q};
-					\end{cases}
-				\end{equation*}
-				\item The submatrix with $i$-th rows and $j$-th columns deleted, $(i,j) \in \mathcal{S}_n$, denoted as $\mathbf{Y}$, is arbitrary doubly stochastic matrix of dimension $N_\mathrm{S}-\card(\mathcal{S}_n)$ satisfying
-				\begin{align*}
-					\sigma_{n-1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \ge \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{for } \mathbf{P}, \\
-					\sigma_{n+1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \le \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{for } \mathbf{Q},
-				\end{align*}
-				where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with the $i$-th rows and $j$-th columns deleted, $(i,j) \in \mathcal{S}_n$.
+				where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with both $i$-th row and $j$-th column deleted, respectively.
 			\end{itemize}
-
-			% where $\mathbf{P}, \mathbf{Q}$ can be any unitary matrix whose $(i, j)$-th entry is of unit-magnitude, and $(i, j) = \arg \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{P}$ and $(i, j) = \arg \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{Q}$.
-			% where $\mathbf{P}, \mathbf{Q}$ can be any unitary matrix whose $(i, j)$-th entry is of unit-magnitude, and $(i, j) = \arg \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{P}$ and $(i, j) = \arg \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{Q}$.
-			% that reorders the singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
 		\end{corollary}
@@
 		\begin{proof}
-			In \eqref{iq:sv_nth}, the set of upper bounds
-			\begin{equation}
-				\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+1\bigr\}
-				\label{iq:sv_nth_upper_set}
-			\end{equation}
-			is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [\bar{N}]^3$.
-			The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
-However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nth_upper_set} is selected as the tightest upper bound in \eqref{iq:sv_nth}.
-			On the other hand, the set of lower bounds
-			\begin{equation}
-				\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+\bar{N}\bigr\}
-				\label{iq:sv_nth_lower_set}
-			\end{equation}
-			can be induced by \eqref{iq:sv_nth_upper_set}, \eqref{eq:sv_product}, and the non-negativity of singular values.
-			The maximum of \eqref{iq:sv_nth_lower_set} is selected as the tightest lower bound in \eqref{iq:sv_nth}.
-
-			To attain the upper bound, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ singular values of $\mathbf{H}$.
-			It follows from \eqref{eq:sv_nth_max} that
-			\begin{equation*}
-				\begin{split}
-					\sv(\mathbf{H})
-					& = \sv(\mathbf{H}_\mathrm{B} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{F}) \\
-					& = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Theta}_\mathrm{D} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \\
-					& = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H}) \\
-					& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Sigma}_\mathrm{F}) \\
-				\end{split}
-			\end{equation*}
-			where $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$.
-
-			The doubly stochastic matrix $\mathbf{P}$ should align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that the first $n$ modes of $\mathbf{H}$ are maximized.
-
-			One feasible solution is to align and order the first $n$ modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, resulting in $\sigma_n(\mathbf{H}) = \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$.
-			If such $(i,j)$ pairs are not unique, then any mixture of them would produce the same result.
-			% We emphasize that the solution is not unique and mixture of such $(i,j)$ pairs would produce the same result.
-			% It is worth mentioning that the solution is not unique and any mixture of such $(i,j)$ pairs would produce the same result.
-			However, since we only care about the $n$-th singular value, the first $n-1$ singular values can be arbitrarily reordered.
-			% This is achieved by aligning and reordering the first $n$ modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
-
-			proper matching of the first $n$ modes of $\mathbf{H}_\mathrm{B}$ to the first $n$ modes of $\mathbf{H}_\mathrm{F}$.
-			In particular, mode $i$ of $\mathbf{H}_\mathrm{B}$ should be completely aligned with mode $j$ of $\mathbf{H}_\mathrm{F}$ where $(i, j) = \arg \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{P}$
-
-			% Interested readers are referred to \cite[Equation~2.0.3]{Zhang2005} for more information.
-			% $i$-th mode of $\mathbf{H}_\mathrm{B}$ with the $j$-th mode of $\mathbf{H}_\mathrm{F}$ such that the $n$-th mode of $\mathbf{H}$ is maximized.
-
-			% Maximizing $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is equivalent to maximizing the minimum of the first $n$ channel singular values.
-			% As such, the \gls{bd}-\gls{ris} needs to align t
-			% align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that the first $n$ modes of $\mathbf{H}$ are maximized.
-			% To maximize the $n$-th channel singular value, the \gls{bd}-\gls{ris} needs to ensure
-			% that the first $n$ modes of $\mathbf{H}$ are
-
-			% should align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that
-
-			% \cite[Equation~2.0.3]{Zhang2005}
-
-			% Please refer to Appendix~\ref{ap:sv_nth}.
+			Please refer to Appendix~\ref{ap:sv_nth}.
 		\end{proof}
 
-		Now we can see the alignment by $V_B$ $U_F$ and ordering by $P$ $Q$.
-
-		We highlight the solution (15) is not unique.
-
-		In particular, the extreme singular values can be manipulated up to
+		% Although Corollary \ref{co:sv_nth} and Proposition \ref{pp:direct_negligible}
+		% are derived under the assumption of negligible direct channel and fully-connected \gls{bd}-\gls{ris}, they are still useful for practical scenarios.
+		Corollary \ref{co:sv_nth} and Proposition \ref{pp:rank_deficient} both reveal the shaping limits of individual channel singular values.
+		They are not special cases of each other and are derived under different assumptions.
+		Importantly, Corollary \ref{co:sv_nth} establishes upper and lower bounds for \emph{all} channel singular values and provides general structures for fully-connected \gls{bd}-\gls{ris} of \emph{arbitrary size} to achieve those.
+		We emphasize in \eqref{eq:sv_nth} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ and the ordering is enabled by $\mathbf{P}$ and $\mathbf{Q}$ which are special cases of unitary $\mathbf{X}$ defined in \eqref{eq:scattering_fc}.
+		Specially, the extreme channel singular values can be manipulated up to
 		\begin{subequations}
@@
 		\end{subequations}
-		where the arguments of $\max$ and $\min$ are essentially $\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}-1}(\mathbf{H}_\mathrm{F}), \ldots, \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
-		We notice that the right side inequalities in \eqref{iq:sv_largest} and \eqref{iq:sv_smallest} are special cases of \eqref{iq:sv_product_largest} and \eqref{iq:sv_product_smallest} when $k=1$, respectively.
-		It is evident from \eqref{iq:sv_nth} that to enlarge the $n$-th singular value of $\mathbf{H}$, one should
-
-		enumerate all matching pairs $(i, j) \in [\bar{N}]^2 \mid i+j=n+1$, find the one with the minimum product singular value
-
-		match the singular
-
-		align the $i$-th singular value of $\mathbf{H}_\mathrm{B}$ with the $j$-th singular value of $\mathbf{H}_\mathrm{F}$ such that $i+j=n+\bar{N}$.
-
-		% The lower bound on the smallest singular value reduces to 0 when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).
-		% in \eqref{iq:sv_smallest} is less informative when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.
-		% in \eqref{iq:sv_product_smallest} and \eqref{iq:sv_smallest} reduce to 0 when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).
+		where the arguments of $\max$ and $\min$ coincide at $\bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}-1}(\mathbf{H}_\mathrm{F}), \ldots, \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}$.
+		We notice that the right halves in \eqref{iq:sv_largest} and \eqref{iq:sv_smallest} are special cases of \eqref{iq:sv_product_largest} and \eqref{iq:sv_product_smallest} when $k=1$.
 
@@
 				\begin{align}
-					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H}, \\
-					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{\Theta}_\mathrm{D} \mathbf{U}_\mathrm{F}^\mathsf{H},
+					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:power_max} \\
+					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H} \label{eq:power_min},
 				\end{align}
@@
 		\end{proof}
+
+		We notice that \eqref{eq:power_max} and \eqref{eq:power_min} are special cases of \eqref{eq:sv_nth_max} and \eqref{eq:sv_nth_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_extreme}, respectively.
 
@@
 	\begin{subsection}{Proof of Corollary \ref{co:sv_nth}}\label{ap:sv_nth}
+		In \eqref{iq:sv_nth}, the set of upper bounds
+		\begin{equation}
+			\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+1\bigr\}
+			\label{iq:sv_nth_upper_set}
+		\end{equation}
+		is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [\bar{N}]^3$.
+		The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
+However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nth_upper_set} is selected as the tightest upper bound in \eqref{iq:sv_nth}.
+		On the other hand, the set of lower bounds
+		\begin{equation}
+			\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+\bar{N}\bigr\}
+			\label{iq:sv_nth_lower_set}
+		\end{equation}
+		can be induced by \eqref{iq:sv_nth_upper_set}, \eqref{eq:sv_product}, and the non-negativity of singular values.
+		The maximum of \eqref{iq:sv_nth_lower_set} is selected as the tightest lower bound in \eqref{iq:sv_nth}.
+		Interested readers are also referred to \cite[Equation~2.0.3]{Zhang2005}.
+
+		To attain the upper bound, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ channel singular values.
+		It follows from \eqref{eq:sv_nth_max} that
+		\begin{equation*}
+			\begin{split}
+				\sv(\mathbf{H})
+				& = \sv(\mathbf{H}_\mathrm{B} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{F}) \\
+				& = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \\
+				& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Sigma}_\mathrm{F}).
+			\end{split}
+		\end{equation*}
+		On the one hand, $\mathbf{P}_{ij}=1$ with $(i, j)$ satisfying \eqref{eq:sv_nth_max_pair} ensures $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is a singular value of $\mathbf{H}$.
+		It is actually among the first $n$ since the number of pairs $(i',j')$ not majorized by $(i,j)$ is $n-1$.
+		On the other hand, \eqref{eq:sv_nth_max_condition} ensures the first $(n-1)$-th singular values are no smaller than $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$.
+		Combining both facts, we claim the upper bound $\sigma_n(\mathbf{H}) = \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is attainable by \eqref{eq:sv_nth_max}.
+		The attainability of the lower bound can be proved similarly and the details are omitted.
+
 		% In \eqref{iq:sv_nth}, the set of upper bounds

### 2024-11-19 main.tex
:construction: Add corollary 3.5

@@
 % enumitem
-\setlist[itemize]{leftmargin=5mm}
-\setlist[enumerate]{leftmargin=5mm}
+\setlist[itemize]{leftmargin=4mm}
+\setlist[enumerate]{leftmargin=4mm}
 
@@
 \newacronym{ic}{IC}{Interference Channel}
+\newacronym{wsr}{WSR}{Weighted Sum-Rate}
 \newacronym{snr}{SNR}{Signal-to-Noise Ratio}
-\newacronym{wsr}{WSR}{Weighted Sum-Rate}
 \newacronym{svd}{SVD}{Singular Value Decomposition}
@@
 		\end{equation}
-		where $h_{\mathrm{B},g,l}$, $h_{\mathrm{F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively, and $\pi_{\mathrm{B},g}$, $\pi_{\mathrm{F},g}$ are permutations of $[L]$ sorting their magnitude in non-ascending orders.
+		where $h_{\mathrm{B},g,l}$, $h_{\mathrm{F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively, and $\pi_{\mathrm{B},g}$, $\pi_{\mathrm{F},g}$ are permutations of $[L]$ sorting their magnitude in similar orders.
 		That is, the maximum channel gain is attained when each group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
@@
 		Its importance lies in the fact that the channel shaping question in Section \ref{sc:contributions} can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
-		The question is partially answered in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} over the notation\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [\bar{N}] \setminus [N]$.
-		% $N < n \le \bar{N}$.
-		These results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
+		The question is partially answered in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sv_nth} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
+		% define\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [\bar{N}] \setminus [N]$.
+		% where we assume $N \le N_\mathrm{S}$ for the ease of notation and define\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices.} $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N_\mathrm{S}] \setminus [N]$.
+		% \footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $N = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N] \setminus [N]$}.
+		% over the notation\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $N = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N] \setminus [N]$.
+		% $N < n \le N$.
+		The results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
 		% We have the following corollaries.
@@
 		\begin{corollary}[Product of subset of singular values\label{co:sv_bound_horn}]
-			The product of subset of singular values of $\mathbf{H}$ is bounded from above by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
+			If the direct channel is negligible,
+			% and $N \le N_\mathrm{S}$
+			then the product of subset of singular values of $\mathbf{H}$ is bounded from above by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
 			\begin{equation}
@@
 				\begin{split}
-					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} & \bigm\vert \forall p < r, \ \forall (F, G, H) \in T_p^r,\\
-					& \quad \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + \frac{p(p+1)}{2} \Bigr\},
+					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \bigm\vert & \forall p < r, \ \forall (F, G, H) \in T_p^r,\\
+					& \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + \frac{p(p+1)}{2} \Bigr\},
 				\end{split}
@@
 
-		Corollary \ref{co:sv_bound_horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result under the assumption of Proposition \ref{pp:direct_negligible} (i.e., negligible direct channel and fully-connected \gls{bd}-\gls{ris}).
+		\eqref{iq:sv_bound_fc}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:direct_negligible}.
 		% It is worth mentioning that t
 		% It also helps to induce lower bounds on the channel singular values.
-		The number of admissible triples increases exponentially with $\bar{N}$ despite some resulting inequalities can be redundant.
-		Apart from upper bounds, \eqref{iq:sv_bound_fc} can also induce lower bounds on channel singular values.
+		The number of admissible triples increases exponentially with $N_\mathrm{S}$ despite some resulting bounds can be redundant.
+		Apart from the upper bounds, we will shortly see \eqref{iq:sv_bound_fc} can also induce lower bounds on channel singular values.
 		% It also helps to induce lower (instead of upper) bounds on channel singular values.
-		% ! For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $\bar{N}$ increases from 3 to 7.
+		% ! For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.
 		% Besides, \eqref{iq:sv_bound_fc} helps to induce lower bounds
-		Those facts render the shaping limit analysis non-trivial for massive \gls{ris}-aided \gls{mimo} systems.
-		Below we showcase some useful results that can be derived from Corollary \ref{co:sv_bound_horn}.
+		Those facts render the analysis of shaping limit non-trivial for massive \gls{ris}-aided \gls{mimo} systems.
+		Below we showcase some useful resulting bounds.
 
 		\begin{corollary}[Product of some largest or smallest singular values\label{co:sv_product}]
-			% \footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
-			% For any $k \in [\bar{N}]$,
-			The product of the first (resp. last) $k$ singular values of $\mathbf{H}$ is bounded from above (resp. below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
+			% \footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $N \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
+			% For any $k \in [N]$,
+			If the direct channel is negligible,
+			% and $N \le N_\mathrm{S}$
+			then the product of the first (resp.
+last\footnote{The lower bounds coincide at zero when $N \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).}) $k$ singular values of $\mathbf{H}$ is bounded from above (resp.
+below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
 			% the product of the first (resp. last) $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
@@
 		\begin{proof}
-			Please refer to and Appendix~\ref{ap:sv_product}.
+			Please refer to Appendix~\ref{ap:sv_product}.
 		\end{proof}
 
+		% The assumption $N \le N_\mathrm{S}$
+
 		\begin{corollary}[Individual singular value\label{co:sv_nth}]
-			The $n$-th channel singular value can be manipulated up to
-			\begin{equation}
-				\max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
+			If the direct channel is negligible,
+			% and $N \le N_\mathrm{S}$,
+			then the $n$-th channel singular value can be manipulated up to
+			\begin{equation}
+				\max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
 				\label{iq:sv_nth}
 			\end{equation}
-			where $(i, j) \in [\bar{N}]^2$.
+			where $(i, j) \in [N_\mathrm{S}]^2$.
 			The upper and lower bounds are attained respectively at
@@
 				% 		\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{P}, \\
-				% 		\underset{i+j=n+\bar{N}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{Q},
+				% 		\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{Q},
 				% 	\end{cases}
@@
 					\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:sv_nth_max_pair} \\
-					\underset{i+j=n+\bar{N}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:sv_nth_min_pair}
+					\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:sv_nth_min_pair}
 				\end{subnumcases}
@@
 				% 		\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{P}, \hspace{-0.17cm} \label{eq:sv_nth_max_condition} \\
-				% 		\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\le} \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{Q}, \hspace{-0.17cm} \label{eq:sv_nth_min_condition}
+				% 		\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\le} \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{Q}, \hspace{-0.17cm} \label{eq:sv_nth_min_condition}
 				% 	\end{alignat}
@@
 						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{P}, \label{eq:sv_nth_max_condition} \\
-						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
+						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
 					\end{alignat}
@@
 				% 		\sigma_{n-1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \ge \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{P}, \label{eq:sv_nth_max_condition} \MoveEqLeft[1] \\
-				% 		\sigma_{n+1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \le \max_{i+j=n+\bar{N}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
+				% 		\sigma_{n+1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \le \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
 				% 	\end{align}
@@
 		Corollary \ref{co:sv_nth} and Proposition \ref{pp:rank_deficient} both reveal the shaping limits of individual channel singular values.
-		They are not special cases of each other and are derived under different assumptions.
-		Importantly, Corollary \ref{co:sv_nth} establishes upper and lower bounds for \emph{all} channel singular values and provides general structures for fully-connected \gls{bd}-\gls{ris} of \emph{arbitrary size} to achieve those.
-		We emphasize in \eqref{eq:sv_nth} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ and the ordering is enabled by $\mathbf{P}$ and $\mathbf{Q}$ which are special cases of unitary $\mathbf{X}$ defined in \eqref{eq:scattering_fc}.
+		They are derived under different assumptions are not special cases of each other.
+		Importantly, Corollary \ref{co:sv_nth} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
+first and last few in Proposition \ref{pp:rank_deficient}), applies to fully-connected \gls{bd}-\gls{ris} of arbitrary size, and provides a general solution structure.
+		We emphasize that in \eqref{eq:sv_nth} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of unitary $\mathbf{X}$ defined in \eqref{eq:scattering_fc}.
 		Specially, the extreme channel singular values can be manipulated up to
@@
 			\begin{gather}
-				\max_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_largest} \\
-				\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\ge} \sigma_{\bar{N}}(\mathbf{H}) {\ge} \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}), \label{iq:sv_smallest}
+				\max_{i+j=N_\mathrm{S}+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_largest} \\
+				\min_{i+j=\bar{N}+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\ge} \sigma_{\bar{N}}(\mathbf{H}) {\ge} \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}).
+\label{iq:sv_smallest}
 			\end{gather}
 		\end{subequations}
-		where the arguments of $\max$ and $\min$ coincide at $\bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}-1}(\mathbf{H}_\mathrm{F}), \ldots, \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}$.
+		% where the arguments of $\max$ and $\min$ coincide at $\bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}}(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-1}(\mathbf{H}_\mathrm{F}), \ldots, \sigma_{N_\mathrm{S}}(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}$.
 		We notice that the right halves in \eqref{iq:sv_largest} and \eqref{iq:sv_smallest} are special cases of \eqref{iq:sv_product_largest} and \eqref{iq:sv_product_smallest} when $k=1$.
 
-		\begin{corollary}[Channel power gain\label{co:sum_power}]
-			The channel power gain is bounded from above (resp.
-below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp.
-oppositely), that is,
-			\begin{equation}
-				\sum_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
-				\label{iq:power_gain}
-			\end{equation}
-			whose\footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
-This is a looser version of \eqref{iq:power_gain} and cannot take equalities unless the extreme singular values are of multiplicity $\bar{N}$.} upper and lower bounds are attained respectively at
-			\begin{subequations}
-				\begin{align}
-					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:power_max} \\
-					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H} \label{eq:power_min},
-				\end{align}
-			\end{subequations}
-			% \begin{equation}
-			% 	\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \quad \mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H},
-			% \end{equation}
-			where $\mathbf{J}$ is the exchange (a.k.a. backward identity) matrix of dimension $N_\mathrm{S}$.
-		\end{corollary}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:sum_power}.
-		\end{proof}
-
-		We notice that \eqref{eq:power_max} and \eqref{eq:power_min} are special cases of \eqref{eq:sv_nth_max} and \eqref{eq:sv_nth_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_extreme}, respectively.
-
-		% ! Talk about when is the assumption hold.
-		% We highlight that the bounds in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} are asymptotically tight as $N_\mathrm{S}$ goes to infinity.
-
 		\begin{example}[Bounds on $3 \times 3 \times 3$ shaping]\label{eg:bounds}
-			Consider a $3 \times 3 \times 3$ setup with negligible direct channel.
-			Let $\mathbf{H}_\mathrm{B} = \diag(4, 5, 6)$, $\mathbf{H}_\mathrm{F} = \diag(3, 1, 2)$.
+			Consider a $3 \times 3 \times 3$ setup with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} = \diag(3, 2, 1)$, and $\mathbf{H}_\mathrm{F} = \diag(4, 0, 5)$.
+			\begin{itemize}
+				\item \gls{d}-\gls{ris}: It is evident that any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode alignment capability.
+				\item \gls{bd}-\gls{ris}: According to \eqref{iq:sv_nth}, a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
+				% \begin{align*}
+				% 	8 & \le \sigma_1(\mathbf{H}) \le 15, \\
+				% 	4 & \le \sigma_2(\mathbf{H}) \le 10, \\
+				% 	0 & \le \sigma_3(\mathbf{H}) \le 0,
+				% \end{align*}
+				\begin{equation*}
+					8 \le \sigma_1(\mathbf{H}) \le 15, \quad 4 \le \sigma_2(\mathbf{H}) \le 10, \quad 0 \le \sigma_3(\mathbf{H}) \le 0,
+				\end{equation*}
+				which is consistent with Proposition \ref{pp:dof} that \gls{bd}-\gls{ris} cannot achieve a larger \gls{dof} than \gls{d}-\gls{ris}.
+				To attain the upper and lower bounds, $(i,j)$ in \eqref{eq:sv_nth_max} and \eqref{eq:sv_nth_min} takes $(1, 1)$ and $(2, 2)$ when $n=1$, and $(2, 1)$ and $(3, 2)$ when $n=2$, respectively.
+				% for the upper and lower bounds of $\sigma_1(\mathbf{H})$, respectively.
+				% \begin{equation}
+				% 	\begin{bmatrix}
+				% 		8 \\
+				% 		4 \\
+				% 		0 \\
+				% 	\end{bmatrix}
+				% 	\le \sv(\mathbf{H}) \le
+				% 	\begin{bmatrix}
+				% 		15 \\
+				% 		10 \\
+				% 		0 \\
+				% 	\end{bmatrix}
+				% \end{equation}
+				% \begin{figure*}
+				% 	\begin{subequations}
+				% 		\begin{equation}
+				% 			\begin{alignedat}{2}
+				% 				\max \bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\} &\le \sigma_1(\mathbf{H}) &&\le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \\
+				% 				\max \bigl\{\sigma_2(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F})\bigr\} &\le \sigma_2(\mathbf{H}) &&\le \min \bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}, \\
+				% 				\sigma_3(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}) &\le \sigma_3(\mathbf{H}) &&\le \min \bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}.
+				% 			\end{alignedat}
+				% 		\end{equation}
+				% 		\begin{equation}
+				% 			\begin{alignedat}{1}
+				% 				\sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}) & \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+				% 				\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) & \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}),
+				% 			\end{alignedat}
+				% 		\end{equation}
+				% 		\begin{equation}
+				% 			\begin{alignedat}{1}
+				% 				\sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) & \le \min \bigl\{\sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) \sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}), \sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}) \sigma_1(\mathbf{H}) \sigma_3(\mathbf{H})\bigr\}, \\
+				% 				\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) & \le \min \bigl\{\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) \sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}), \sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}) \sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}), \sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) \sigma_1(\mathbf{H}) \sigma_3(\mathbf{H})\bigr\}
+				% 			\end{alignedat}
+				% 		\end{equation}
+				% 	\end{subequations}
+				% \end{figure*}
+
+				% \begin{align*}
+				% 	\sigma_1(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_2(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \\
+				% 	\sigma_2(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}) \\
+				% 	\sigma_3(\mathbf{H}) &\leq \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F})
+				% \end{align*}
+			\end{itemize}
 			% $\sv(\mathbf{H}_\mathrm{B}) = [3, 2]^\mathsf{T}$ and $\sv(\mathbf{H}_\mathrm{B}) = [4, 1]^\mathsf{T}$.
@@
 			% \end{equation*}
-			Apparently any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 12, 5]^\mathsf{T}$ due to limited branch matching capability.
-			On the other hand, Corollary \ref{co:sv_bound_horn} suggests that a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
-
-			\begin{align*}
-				\sigma_1(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_2(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \\
-				\sigma_2(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}) \\
-				\sigma_3(\mathbf{H}) &\leq \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F})
-			\end{align*}
-
-			while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can match the stronger branches by unitary transformation to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-			The bounds on individual singular values are $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-			However, the upper/lower bounds are not simultaneously achievable due to the trade-off between two modes.
+			% Evidently, any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode ordering capability.
+			% On the other hand, Corollary \ref{co:sv_bound_horn} suggests that a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
+
+			% \begin{align*}
+			% 	\sigma_1(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_2(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \\
+			% 	\sigma_2(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}) \\
+			% 	\sigma_3(\mathbf{H}) &\leq \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F})
+			% \end{align*}
+
+			% while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can match the stronger branches by unitary transformation to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
+			% The bounds on individual singular values are $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+			% However, the upper/lower bounds are not simultaneously achievable due to the trade-off between two modes.
 			% and the singular value region is a subset of the rectangle due to the trade-off between the alignment of two modes.
@@
 
-		% % TODO enumerate all bounds for 2x2x2
-		% \begin{example}[Individual (no, all) singular value bounds on $2 \times 2 \times 2$ shaping]\label{eg:bounds}
-		% 	Consider a $2 \times 2 \times 2$ setup with
-		% 	% $\sv(\mathbf{H}_\mathrm{B}) = [3, 2]^\mathsf{T}$ and $\sv(\mathbf{H}_\mathrm{B}) = [4, 1]^\mathsf{T}$.
-		% 	\begin{equation*}
-		% 		\mathbf{H}_\mathrm{B} =
-		% 			\begin{bmatrix}
-		% 				3 & 0 \\
-		% 				0 & 2
-		% 			\end{bmatrix},
-		% 			\quad
-		% 			\mathbf{H}_\mathrm{F} =
-		% 			\begin{bmatrix}
-		% 				1 & 0 \\
-		% 				0 & 4
-		% 			\end{bmatrix}.
-		% 	\end{equation*}
-		% 	It is obvious that any \gls{d}-\gls{ris} can only attain $\sv(\mathbf{H}) = [8, 3]^\mathsf{T}$ while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can match the stronger branches by unitary transformation to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-		% 	The bounds on individual singular values are $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-		% 	However, the upper/lower bounds are not simultaneously achievable due to the trade-off between two modes.
-		% 	% and the singular value region is a subset of the rectangle due to the trade-off between the alignment of two modes.
-		% 	% but there exists a trade-off in between due to mode alignment.
-		% 	% It is obvious that any \gls{d}-\gls{ris} can only attain $\sv(\mathbf{H}) = [8, 3]^\mathsf{T}$ while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ exploits branch matching to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-
-		% 	% results in $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-		% 	% The singular value
-		% 	% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-		% \end{example}
-
-		Example~\ref{eg:bounds} shows that a fully-connected \gls{bd}-\gls{ris} can apply right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$
-		% , widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-		That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-
-		% We thus conclude that a fully-connected \gls{bd}-\gls{ris} can apply right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, which widens channel singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this example.
-
-		% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$ in this case.
-
-		All equalities achieved by perfect alignment of all modes.
-
-		To achieve equalities in Corollaries \ref{co:sv_extreme} -- \ref{co:sum_power}, the \gls{ris} needs to completely align the singular vector spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
-		The resulting scattering matrix is generally required to be unitary
-		\begin{equation}
-			\mathbf{\Theta}^\star = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H},
-			\label{eq:scattering_fc_optimal}
-		\end{equation}
-		which can be concluded from \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in Appendix~\ref{ap:direct_negligible}.
-		We notice that \gls{d}-\gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
-		In such case, the equivalent channel reduces to $\mathbf{H} = \sigma_\mathrm{B} \sigma_\mathrm{F} \mathbf{u}_\mathrm{B} \mathbf{v}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ and the \gls{ris} only needs to align $\mathbf{v}_\mathrm{B}^\mathsf{H}$ and $\mathbf{u}_\mathrm{F}$ by
-		\begin{equation}
-			\mathbf{\Theta}^\star = \mathbf{v}_\mathrm{B} \mathbf{u}_\mathrm{F}^\mathsf{H} \odot \mathbf{I},
-		\end{equation}
-		which reduces to a special case of \eqref{eq:scattering_siso} with $L=1$.
-		However, in general \gls{d}-\gls{ris} is not sufficient to achieve the upper bound of channel power gain.
-		This again highlights the benefit of \gls{bd}-\gls{ris} in reshaping available channels.
-
-		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the maximum expected channel power gain can be numerically evaluated as
-		\begin{equation}
-			\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\} = \sum_n \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x) d x,
+		We conclude from Example \ref{eg:bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		% performing right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, which properly aligns and orders their modes.
+		% properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		% enables right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values
+		% illustrates the shaping limits of a $3 \times 3 \times 3$ setup with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} = \diag(3, 2, 1)$, and $\mathbf{H}_\mathrm{F} = \diag(4, 0, 5)$.
+			% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
+		However, when the problem of interest is a function of multiple singular values, their individual bounds \eqref{iq:sv_nth} may not be simultaneously tight.
+		Two case studies are presented below.
+
+		\begin{corollary}[Channel power gain\label{co:sum_power}]
+			If the direct channel is negligible, then the channel power gain is bounded from above (resp.
+below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp.
+oppositely), that is,
+			\begin{equation}
+				\sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
+				\label{iq:power_gain}
+			\end{equation}
+			whose\footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
+This is a looser version of \eqref{iq:power_gain} and cannot take equalities unless the extreme singular values are of multiplicity $N$.} upper and lower bounds are attained respectively at
+			\begin{subequations}
+				\begin{align}
+					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:power_max} \\
+					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H} \label{eq:power_min},
+				\end{align}
+			\end{subequations}
+			where $\mathbf{J}$ is the exchange (a.k.a. backward identity) matrix of dimension $N_\mathrm{S}$.
+		\end{corollary}
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:sum_power}.
+		\end{proof}
+
+		We notice that \eqref{eq:power_max} and \eqref{eq:power_min} are special cases of \eqref{eq:sv_nth_max} and \eqref{eq:sv_nth_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_extreme}, respectively.
+		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the expectation of maximum channel power gain can be numerically evaluated as
+		\begin{equation}
+			\begin{split}
+				\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\} = \sum_{n=1}^N
+				& \int_0^\infty x f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x \\
+				& \times \int_0^\infty y f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(y) d y,
+			\end{split}
 			\label{eq:power_gain_rayleigh}
 		\end{equation}
-		% \begin{equation}
-		% 	\begin{split}
-		% 		\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\}
-		% 		& = \sum_n \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x_n) d x_n \\
-		% 		& \quad \times \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x_n) d x_n,
-		% 	\end{split}
-		% 	\label{eq:power_gain_rayleigh}
-		% \end{equation}
-		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(x)$ given by \cite[Equation 51]{Zanella2009}.
-		We note that \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain attainable by \gls{bd}-\gls{ris} \cite[Equation 58]{Shen2020a} to \gls{mimo} and models the contribution of transmit and receive antennas under double Rayleigh fading.
-		In Section \ref{sc:simulation}, we will numerically evaluate the channel power gain and compare it with the theoretical upper bound.
-
-		% Expression \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo} and unveils
-
-		% , unveiling how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
-		% is a generalization of \gls{siso} power gain \cite[Equation 58]{Shen2020a} to \gls{mimo}, which unveils how the channel power gain scales with the number of transmit and receive antennas and \gls{bd}-\gls{ris} elements under double Rayleigh fading.
-		% However, a closed-form expression is non-trivial due to the complexity of distribution of ordered eigenvalues of Wishart matrices.
-		% ordered Wishart matrix eigenvalue distribution.
-		% provides a benchmark for the channel power gain of \gls{bd}-\gls{ris} in Rayleigh fading channels.
-
-		Proposition \ref{pp:direct_negligible} and Corollaries \ref{co:sv_bound_horn} -- \ref{co:sum_power} provide a comprehensive answer to the shaping capability question in terms of singular value bounds and channel power gain limits.
-		% understanding of the channel power gain limits of passive \gls{ris}.
-		% and suggest the impact of channel rearrangement and space alignment on redistributing channel singular values.
-		% When the direct channel is present,
-		% Similar results are inapplicable
-		Extending those results to the case of direct channel is non-trivial since the singular vector spaces of direct-indirect channels and backward-forward channels cannot be aligned at the same time.
-		In such case, we can invoke optimization approaches from a singular value perspective (discussed in Section~\ref{sc:pareto_frontier}) or a power gain perspective (to be discussed in Section~\ref{sc:power}).
+		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(\cdot)$ given by \cite[(51)]{Zanella2009}.
+		We note that \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain attainable by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} under double Rayleigh fading.
+
+		\begin{corollary}[Channel capacity at very low and high \gls{snr}\label{co:capacity}]
+			If the direct channel is negligible, then the channel capacity at very low and high \gls{snr} are approximately bounded from above by
+			\begin{subequations}
+				\begin{align}
+					C_{\rho_\downarrow} & \lessapprox \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \label{iq:capacity_snr_low} \\
+					C_{\rho_\uparrow} & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:capacity_snr_high}
+				\end{align}
+			\end{subequations}
+			where $\rho$ is the \gls{snr} and the unit is nats/s/Hz.
+			Their upper bounds can be attained by, for example, \eqref{eq:power_max}.
+		\end{corollary}
+
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:capacity}.
+		\end{proof}
+
+		Similar to \eqref{eq:power_gain_rayleigh}, the ergodic counterparts of \eqref{iq:capacity_snr_low} and \eqref{iq:capacity_snr_high} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be numerically evaluated as
+		\begin{subequations}
+			\begin{equation}
+				\mathbb{E} \{C_{\rho_\downarrow}\} = \int_0^\infty x f_{\lambda_1^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x  \int_0^\infty y f_{\lambda_1^{\min(N_\mathrm{S},N_\mathrm{T})}}(y) d y,
+			\end{equation}
+			\begin{equation}
+				\begin{split}
+					\mathbb{E} \{C_{\rho_\uparrow}\} = N \log \frac{\rho}{N} + \sum_{n=1}^N \log \Bigl( & \int_0^\infty x f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x \\
+					\times & \int_0^\infty y f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(y) d y \Bigr).
+				\end{split}
+			\end{equation}
+		\end{subequations}
+
+		Proposition \ref{pp:dof} -- \ref{pp:direct_negligible} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
+		Extending the analysis to more general cases (e.g., non-negligible direct channel and arbitrary \gls{bd}-\gls{ris} group size) is non-trivial due to limited branch matching and mode alignment capabilities therein.
+		% since the mode alignment and ordering are not guaranteed to be simultaneously achievable.
+		% ose results to the case of direct channel is non-trivial since the singular vector spaces of direct-indirect channels and backward-forward channels cannot be aligned at the same time.
+		To provide a complete channel shaping solution, we invoke optimization approaches and tackle some relevant problems in the next section.
+
+		% from a singular value perspective (discussed in Section~\ref{sc:pareto_frontier}) or a power gain perspective (to be discussed in Section~\ref{sc:power}).
 	% numerical and analytical studies on singular value redistribution by \gls{bd}-\gls{ris} in Sections~\ref{sc:pareto_frontier} and \ref{sc:bounds}, respectively.
@@
 		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
+			{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:pareto_unitary}}
 		\end{maxi!}
-		where $n \in [N]$ is the maximum channel rank, and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
+		where $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
 		Varying $\{\rho_n\}_{n \in [N]}$ characterizes the Pareto frontier enclosing the singular value region such that problem \eqref{op:pareto} generalizes most singular value shaping problems.
@@
 \ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct channel is negligible.
-			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_optimal} or via optimization approach \eqref{eq:scattering_power}.
+			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:power_max} or via optimization approach \eqref{eq:scattering_power}.
 			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
@@
 \subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-			It comes purely from branch matching and agrees with the asymptotic power scaling law derived for \gls{siso} in \cite[Equation 30]{Shen2020a}.
+			It comes purely from branch matching and agrees with the asymptotic power scaling law derived for \gls{siso} in \cite[(30)]{Shen2020a}.
 			Interestingly, this relative power gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig.
@@
 		Since $\sv(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \sv(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
-		\begin{align*}
+		\begin{equation}
+			\label{eq:sv_factorization}
+			\begin{split}
 				\sv(\mathbf{H}) & = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})                                                                     \\
@@
 			                        & = \sv(\mathbf{BF}),
-		\end{align*}
-		where $\bar{\mathbf{U}}_{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}_{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
+			\end{split}
+		\end{equation}
+		% where $\bar{\mathbf{U}}_{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}_{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
+		where $\bar{\mathbf{U}}_{\mathrm{B}} \in \mathbb{U}^{N_\mathrm{R} \times N_\mathrm{R}}$, $\bar{\mathbf{V}}_\mathrm{B}, \bar{\mathbf{U}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\bar{\mathbf{V}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{T} \times N_\mathrm{T}}$ can be designed arbitrarily.
 	\end{subsection}
@@
 	\begin{subsection}{Proof of Corollary \ref{co:sv_product}}\label{ap:sv_product}
-		\eqref{iq:sv_product_largest} is one of the many inequalities enclosed in \eqref{iq:sv_bound_fc} when $r = k$.
-			On the other hand, \ref{eq:sv_fully_connected} implies that
-			$\det(\mathbf{H}) = \det(\mathbf{B}\mathbf{F}) = \det(\mathbf{B})\det(\mathbf{F}) = \det(\mathbf{H}_\mathrm{B})\det(\mathbf{H}_\mathrm{F})$ and thus
-			\begin{equation}
-				\prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}).
+		\eqref{iq:sv_product_largest} follows from \eqref{iq:sv_bound_fc} when $r = k$.
+		On the other hand, if we can prove
+		\begin{equation}
+			\prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
+			\label{eq:sv_product_all}
+		\end{equation}
+		then \eqref{iq:sv_product_smallest} follows from \eqref{iq:sv_product_largest} and the non-negativity of singular values.
+		To see \eqref{eq:sv_product_all}, we start from a stricter result
+		\begin{equation}
+			\prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
 			\label{eq:sv_product}
 		\end{equation}
-			\eqref{eq:sv_product} together with \eqref{iq:sv_product_largest} and the non-negativity of singular values results in \eqref{iq:sv_product_smallest}.
+		which is provable by cases.
+		When $N_\mathrm{S} > N$, both sides of \eqref{eq:sv_product} become zero since $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}_\mathrm{B}) = \sigma_n(\mathbf{H}_\mathrm{F}) = 0$ for $n > N$.
+		When $N_\mathrm{S} \le N$, we have
+		\begin{equation*}
+			\begin{split}
+				\prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H})
+				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F}) \\
+				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\hat{\mathbf{\Sigma}}_\mathrm{B} \mathbf{X} \hat{\mathbf{\Sigma}}_\mathrm{F}) \\
+				& = \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{B} \mathbf{X} \hat{\mathbf{\Sigma}}_\mathrm{F}\bigr) \\
+				& = \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{B}\bigr) \det(\mathbf{X}) \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{F}\bigr) \\
+				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{\Sigma}_\mathrm{B}) \sigma_n(\mathbf{\Sigma}_\mathrm{F}),
+			\end{split}
+		\end{equation*}
+		where the first equality follows from \eqref{eq:sv_factorization} and $\hat{\mathbf{\Sigma}}_\mathrm{B}, \hat{\mathbf{\Sigma}}_\mathrm{F}$ truncate $\mathbf{\Sigma}_\mathrm{B}, \mathbf{\Sigma}_\mathrm{F}$ to square matrices of dimension $N_\mathrm{S}$, respectively.
+		It is evident that \eqref{eq:sv_product} implies \eqref{eq:sv_product_all} and thus \eqref{iq:sv_product_smallest}.
 	\end{subsection}
@@
 		\begin{equation}
-			\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+1\bigr\}
+			\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+1\bigr\}
 			\label{iq:sv_nth_upper_set}
 		\end{equation}
-		is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [\bar{N}]^3$.
+		is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [N_\mathrm{S}]^3$.
 		The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
@@
 		\begin{equation}
-			\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+\bar{N}\bigr\}
+			\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+N_\mathrm{S}\bigr\}
 			\label{iq:sv_nth_lower_set}
@@
 		The maximum of \eqref{iq:sv_nth_lower_set} is selected as the tightest lower bound in \eqref{iq:sv_nth}.
-		Interested readers are also referred to \cite[Equation~2.0.3]{Zhang2005}.
+		Interested readers are also referred to \cite[(2.0.3)]{Zhang2005}.
 
@@
 		% \begin{equation}
-		% 	\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+1\bigr\}
+		% 	\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N]^3, i+j=n+1\bigr\}
 		% 	\label{iq:sv_nth_upper_set}
 		% \end{equation}
-		% is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [\bar{N}]^3$.
+		% is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [N]^3$.
 		% The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
@@
 		% \begin{equation}
-		% 	\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [\bar{N}]^3, i+j=n+\bar{N}\bigr\}
+		% 	\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N]^3, i+j=n+N\bigr\}
 		% 	\label{iq:sv_nth_lower_set}
@@
 		where $\mathbf{X} \triangleq \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, $\tilde{\mathbf{B}} \triangleq \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\tilde{\mathbf{F}} \triangleq \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$.
-		By Ruhe's trace inequality for positive semi-definite matrices \cite[H.1.g and H.1.h]{Marshall2010},
+		By Ruhe's trace inequality for positive semi-definite matrices \cite[(H.1.g) and (H.1.h)]{Marshall2010},
 		\begin{equation*}
@@
 		On the other hand, the lower bound is attained when the singular values of $\tilde{\mathbf{F}}$ and $\tilde{\mathbf{B}}$ are matched in reverse order, namely $\mathbf{X} = \mathbf{J}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Corollary \ref{co:capacity}}\label{ap:capacity}
+		When perfect \gls{csi} is available at the transmitter, in the low-\gls{snr} regime, the capacity is achieved by dominant eigenmode transmission \cite[(5.26)]{Clerckx2013}
+		\begin{align*}
+			C_{\rho_\downarrow}
+			& = \log\bigl(1 + \rho \lambda_1(\mathbf{H}^\mathsf{H} \mathbf{H})\bigr) \\
+			& = \log\bigl(1 + \rho \sigma_1^2(\mathbf{H})\bigr) \\
+			& \approx \rho \sigma_1^2(\mathbf{H}) \\
+			& \le \rho \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}),
+		\end{align*}
+		where the approximation is $\log(1 + x) \approx x$ for small $x$ and the inequality follows from \eqref{iq:sv_product_largest} with $k=1$.
+		In the high-\gls{snr} regime, the capacity is achieved by multiple eigenmode transmission with uniform power location \cite[(5.27)]{Clerckx2013}
+		\begin{align*}
+			C_{\rho_\uparrow}
+			& = \sum\nolimits_{n=1}^N \log\Bigl(1 + \frac{\rho}{N} \lambda_n(\mathbf{H}^\mathsf{H} \mathbf{H})\Bigr) \\
+			& \approx \sum\nolimits_{n=1}^N \log\Bigl(\frac{\rho}{N} \sigma_n^2(\mathbf{H})\Bigr) \\
+			& = N \log \frac{\rho}{N} + \sum\nolimits_{n=1}^N \log \sigma_n^2(\mathbf{H}) \\
+			& = N \log \frac{\rho}{N} + \log \prod\nolimits_{n=1}^N \sigma_n^2(\mathbf{H}) \\
+			& \le N \log \frac{\rho}{N} + 2 \log \prod\nolimits_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
+		\end{align*}
+		where the approximation is $\log(1 + x) \approx \log(x)$ for large $x$ and the inequality follows from \eqref{iq:sv_product_largest} with $k=N$.
+
+		We then show \eqref{eq:power_max} can achieve the upper bounds in \eqref{iq:capacity_snr_low} and \eqref{iq:capacity_snr_high} simultaneously.
+		On the one hand, \eqref{eq:power_max} is a special case of \eqref{eq:sv_nth_max} with $\mathbf{P} = \mathbf{I}$, which satisfies \eqref{eq:sv_nth_max_pair} and \eqref{eq:sv_nth_max_condition} for $n=1$ and thus attain $\sigma_1(\mathbf{H}) = \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
+		On the other hand, since $\log(\cdot)$ is a monotonic function, we can prove similar to Appendix \ref{ap:sum_power} that $\sum_{n=1}^N \log \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \log \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})$ and the bound is tight at \eqref{eq:power_max}.
+		The proof is complete.
 	\end{subsection}

### 2024-11-20 assets/poster/power_sx_txrx16.tex
:triangular_flag_on_post: Add poster

--- 2024-02-17 assets/simulation/power_sx_txrx16.tex
@@
 xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
-xlabel style={font=\color{white!15!black}},
+% xlabel style={font=\color{white!15!black}},
 xlabel={RIS Group Size},
@@
 yminorticks=true,
-ylabel style={font=\color{white!15!black}},
+% ylabel style={font=\color{white!15!black}},
 ylabel={Channel Power [W]},
@@
 yminorgrids,
-legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
+legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
+font=\tiny,
+title style={font=\tiny},
+label style={font=\tiny},
+ticklabel style={font=\tiny},
+legend style={font=\tiny},
+x label style={yshift=10pt},
+y label style={yshift=-7pt}
 ]
@@
 
-\begin{axis}[%
-width=9.816cm,
-height=7.362cm,
-at={(-1.276cm,-0.81cm)},
-scale only axis,
-xmin=0,
-xmax=1,
-ymin=0,
-ymax=1,
-axis line style={draw=none},
-ticks=none,
-axis x line*=bottom,
-axis y line*=left
-]
-\end{axis}
 \end{tikzpicture}%

### 2024-11-20 assets/poster/singular_bound_rank2_sx128.tex
:triangular_flag_on_post: Add poster

--- 2024-07-23 assets/simulation/singular_bound_rank2_sx128.tex
@@
 transpose legend,
-legend style={/tikz/column 2/.style={column sep=5pt}}
+legend style={/tikz/column 2/.style={column sep=5pt}},
+font=\tiny,
+title style={font=\tiny},
+label style={font=\tiny},
+ticklabel style={font=\tiny},
+legend style={font=\tiny},
+y label style={yshift=-7pt}
 ]

### 2024-11-20 main.tex
:triangular_flag_on_post: Add poster

@@
 \DeclareMathOperator{\card}{card}
+\DeclareMathOperator{\rank}{rank}
 
@@
 		\end{equation}
-		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of null spaces of $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g} \in \mathbb{C}^{1 \times L}$, respectively.
+		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are orthonormal bases of null spaces of $\mathbf{h}_{\mathrm{B},g}, \mathbf{h}_{\mathrm{F},g} \in \mathbb{C}^{L \times 1}$, respectively.
 		The corresponding channel gain is a function of $L$
@@
 		\begin{equation}
-			\lvert h \rvert _{\max} = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
+			\max_\mathbf{\Theta} \ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
 			\label{eq:gain_siso}
@@
 				\begin{cases}
-					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
-					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
+					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \rank(\mathbf{H}_\mathrm{F}) = k, \\
+					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \rank(\mathbf{H}_\mathrm{B}) = k,
 				\end{cases}
@@
 \begin{section}{Simulation Results}\label{sc:simulation}
-	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{The simulation code is publicly available at \url{https://github.com/snowztail/channel-shaping}.}
+	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{Source code is available at \url{https://github.com/snowztail/channel-shaping}.}
 	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
@@
 			\begin{split}
-				\mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
-				 & = \min \bigl( \mathrm{rank}(\mathbf{H}_\mathrm{B}), \mathrm{rank}(\mathbf{\Theta}_\mathrm{D}), \mathrm{rank}(\mathbf{H}_\mathrm{F}) \bigr) \\
-				 & = \min \bigl( \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \mathrm{rank}(\bar{\mathbf{H}}_\mathrm{F}) \bigr)                  \\
-				 & = \max_\mathbf{\Theta} \ \mathrm{rank}(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+				\rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
+				 & = \min \bigl( \rank(\mathbf{H}_\mathrm{B}), \rank(\mathbf{\Theta}_\mathrm{D}), \rank(\mathbf{H}_\mathrm{F}) \bigr) \\
+				 & = \min \bigl( \rank(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \rank(\bar{\mathbf{H}}_\mathrm{F}) \bigr)                  \\
+				 & = \max_\mathbf{\Theta} \ \rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
 			\end{split}

### 2024-11-20 poster/beamer.tex
:triangular_flag_on_post: Add poster

\documentclass[final,xcolor={table}]{beamer}
%% Possible paper sizes: a0, a0b, a1, a2, a3, a4.
%% Possible orientations: portrait, landscape
%% Font sizes can be changed using the scale option.
\usepackage[size=a0,orientation=landscape]{beamerposter}

\usetheme{gemini}
\usecolortheme{seagull}
\useinnertheme{rectangles}
\usefonttheme[onlymath]{serif}

% amsmath
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\sv}{sv}
\DeclareMathOperator{\card}{card}
\DeclareMathOperator{\svd}{svd}
\DeclareMathOperator{\rank}{rank}

\setlength\lineskip{20pt}
% \let\OLDitemize\itemize
% \renewcommand\itemize{\OLDitemize\addtolength{\itemsep}{20pt}}
% \renewcommand\baselinestretch{1.25}

% ====================
% Packages
% ====================

% \usepackage[utf8]{inputenc}
% \usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{FiraSans}
\usepackage[acronym]{glossaries-extra}
\usepackage{siunitx}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[american]{circuitikz}
\usepackage[short]{optidef}

\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,decorations.shapes,shapes.geometric}
\usepgfplotslibrary{groupplots,patchplots}
\pgfplotsset{compat=newest}

\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{ao}{AO}{Alternating Optimization}
\newacronym{bd}{BD}{Beyond Diagonal}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{d}{D}{Diagonal}
\newacronym{dof}{DoF}{Degrees of Freedom}
\newacronym{siso}{SISO}{Single-Input Single-Output}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{pc}{PC}{Point-to-point Channel}
\newacronym{ic}{IC}{Interference Channel}
\newacronym{wsr}{WSR}{Weighted Sum-Rate}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{svd}{SVD}{Singular Value Decomposition}
\newacronym{mmse}{MMSE}{Minimum Mean-Square Error}
\newacronym{wmmse}{WMMSE}{Weighted \gls{mmse}}
\newacronym{mse}{MSE}{Mean-Square Error}
\newacronym{los}{LoS}{Line-of-Sight}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{sca}{SCA}{Successive Convex Approximation}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}

% ====================
% Lengths
% ====================

% If you have N columns, choose \sepwidth and \colwidth such that
% (N+1)*\sepwidth + N*\colwidth = \paperwidth
\newlength{\sepwidth}
\newlength{\colwidth}
\setlength{\sepwidth}{0.025\paperwidth}
\setlength{\colwidth}{0.3\paperwidth}
% \setlength{\sepwidth}{0.03\paperwidth}
% \setlength{\colwidth}{0.45\paperwidth}

\newcommand{\separatorcolumn}{\begin{column}{\sepwidth}\end{column}}

% ====================
% Logo (optional)
% ====================

% LaTeX logo taken from https://commons.wikimedia.org/wiki/File:LaTeX_logo.svg
% use this to include logos on the left and/or right side of the header:
\logoleft{\includegraphics[height=1.5cm]{../assets/poster/logo_imperial.eps}}
\logoright{\includegraphics[height=4cm]{../assets/poster/qrcode_github.png}}

% ====================
% Footer (optional)
% ====================

\footercontent{
	IEEE ComSoc Workshops @ ICL \hfill
	November 25 \& 26, 2024 \hfill
	\href{mailto:yang.zhao@ieee.org}{yang.zhao@ieee.org}
}
% (can be left out to remove footer)

% ====================
% My own customization
% - BibLaTeX
% - Boxes with tcolorbox
% - User-defined commands
% ====================
\input{custom-defs.tex}

%% Reference Sources
% \addbibresource{library.bib}
\renewcommand{\pgfuseimage}[1]{\includegraphics[scale=2.0]{#1}}

\title{Channel Shaping Using Beyond Diagonal RIS: Analysis, Optimization, and Enhanced Flexibility}

\author{Yang Zhao \and Hongyu Li \and Massimo Franceschetti \and Bruno Clerckx}

\date{January 01, 2025}

\begin{document}

\begin{frame}[t]
	\begin{columns}[t]
		\separatorcolumn

		\begin{column}{\colwidth}
			\begin{block}{Overview}
				\begin{itemize}\setlength\itemsep{20pt}
					\item \textbf{What does this paper investigate?}

					The capability of \gls{d} and \gls{bd} \gls{ris} to redistribute the singular values of \glsfmtshort{mimo} channels.
					\item \textbf{How does it differ from previous work?}

					It derives analytical singular value bounds for specific channel conditions. And proposes a novel \gls{bd}-\gls{ris} optimization framework for general problems.
					\item \textbf{What are the benefits?}

					\gls{bd}-\gls{ris} improves the dynamic range of individual channel singular values and the trade-off in manipulating them. This boosts channel power gain and capacity.
				\end{itemize}
			\end{block}

			\begin{block}{\gls{bd}-\gls{ris} model}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				Consider an $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ setup with \gls{bd}-\gls{ris} divided into $G$ groups of $L$ elements each.
				Define $N = \min(N_\mathrm{T}, N_\mathrm{R})$, $\bar{N} = \max(N_\mathrm{T}, N_\mathrm{S}, N_\mathrm{R})$, and $\mathbf{H}_{\mathrm{B}/\mathrm{F}}\stackrel{\svd}{=} \mathbf{U}_{\mathrm{B}/\mathrm{F}} \boldsymbol{\Sigma}_{\mathrm{B}/\mathrm{F}} \mathbf{V}_{\mathrm{B}/\mathrm{F}}^\mathsf{H}$.
				\begin{equation*}
					\mathbf{\Theta} = \diag(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),\quad \mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}_L \ \forall g, \quad \mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum\nolimits_g \underbrace{\mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}}_{\small{\substack{\text{backward-forward:}\\\text{intra-group, multiplicative}}}}}^{\small{\substack{\text{direct-indirect:}\\\text{inter-group, additive}}}}.
				\end{equation*}

				\begin{itemize}
					\setlength{\rightskip}{\leftmargini}
					\item \textcolor{imperialblue}{Branch matching:} Pairing and combining the entries of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ through unitary transformation $\mathbf{\Theta}_g$.
					\item \textcolor{imperialblue}{Mode alignment:} Aligning and ordering the singular vectors of $\{\mathbf{H}_g\}$ with those of $\mathbf{H}_\mathrm{D}$ through unitary transformations $\{\mathbf{\Theta}_g\}$.
				\end{itemize}
			\end{block}

			\begin{exampleblock}{Example 1: \glsfmtshort{siso} channel gain maximization}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				\glsfmtshort{siso} mode alignment reduces to phase matching and any $L$ (incl. \gls{d}-\gls{ris}) suffices by
				\begin{equation*}
					\mathbf{\Theta}_g^\text{\gls{siso}} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H} \ \forall g,
					\label{eq:scattering_siso}
				\end{equation*}
				where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr]$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr]$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g}$ are orthonormal bases of null spaces of $\mathbf{h}_{\mathrm{B},g}, \mathbf{h}_{\mathrm{F},g}$.
				The channel gain is a function of $L$
				\begin{equation*}
					\max\nolimits_{\mathbf{\Theta}_{\mathrm{BD}}} \ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum\nolimits_g \sum\nolimits_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
				\end{equation*}
				which generalizes $\max_{\mathbf{\Theta}_{\mathrm{D}}} \ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ using permutations $\pi_{\mathrm{B},g}, \pi_{\mathrm{F},g}$ that pair the $l$-th strongest backward and forward branches.
				% This generalizes $\max_{\mathbf{\Theta}_{\mathrm{D}}} \ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$.
			\end{exampleblock}

			\begin{exampleblock}{Example 2: $2 \times 2 \times 2$ shaping}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				\gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} can be modeled by 2 and 4 angular parameters:
				\begin{equation*}
					\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}), \quad
					\mathbf{\Theta}_\mathrm{BD} = e^{\jmath \phi} \begin{bmatrix}
						e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
						-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
					\end{bmatrix}.
				\end{equation*}

				Assume the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible (i.e., $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$).
				The plot relies on grid search for one channel realization.
				\begin{figure}
					\centering
					\includegraphics[width=0.44\columnwidth]{../assets/simulation/singular_trend.eps}
					% \caption{
					% 	\setlength{\leftskip}{\leftmargini}
					% 	\setlength{\rightskip}{\leftmargini}
					% 	Singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris}.
					% 	The maximum and minimum singular values are marked explicitly on the plot.}
				\end{figure}
				Here, both singular values are manipulated up to $\pm 9\%$ by \gls{d}-\gls{ris} and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris}, using 2 and 3 circuit components respectively.
			\end{exampleblock}
		\end{column}

		\separatorcolumn

		\begin{column}{\colwidth}
			\vspace{-0.5cm}
			\begin{prop}{\gls{dof}}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				In point-to-point \glsfmtshort{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
			\end{prop}

			\begin{prop}{Rank-deficient channels}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				If the minimum rank of backward and forward channels is $k$,
				then for \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th channel singular value is bounded by
				\begin{align*}
					\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \\
					\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1,
				\end{align*}
				where $\mathbf{T}$ is arbitrary auxiliary matrix satisfying
				\begin{equation*}
					\mathbf{T} \mathbf{T}^\mathsf{H} =
					\begin{cases}
						\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
						\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k.
					\end{cases}
				\end{equation*}
				\vspace{-0.5cm}
			\end{prop}

			\begin{coro}{\gls{los} channel}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				If one of backward and forward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can only manipulate the channel singular values up to
				\begin{equation*}
					\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
				\end{equation*}
				As $N_\mathrm{S} \to \infty$, $N$ out of those $2N$ bounds can be \emph{simultaneously} tight.
			\end{coro}

			\begin{prop}{Negligible direct channel}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				If the direct channel is negligible, then a fully-connected \gls{bd}-\gls{ris} can manipulate the channel singular values up to
				\begin{equation*}
					\sv(\mathbf{H}) = \sv(\mathbf{BF}),
				\end{equation*}
				where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with $\sv(\mathbf{B})=\sv(\mathbf{H}_\mathrm{B})$ and $\sv(\mathbf{F})=\sv(\mathbf{H}_\mathrm{F})$.
			\end{prop}

			\setcounter{coro}{2}

			\begin{coro}{Individual singular value}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				If the direct channel is negligible,
				then the $n$-th channel singular value is bounded by
				\begin{equation*}
					\max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
				\end{equation*}
				which are attained respectively at
				\begin{equation*}
					\mathbf{\Theta}_{\text{sv-}n\text{-max}}^\text{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \quad \mathbf{\Theta}_{\text{sv-}n\text{-min}}^\text{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H},
				\end{equation*}
				where $\mathbf{P}, \mathbf{Q}$ are permutation matrices of dimension $N_\mathrm{S}$ satisfying:
				\begin{itemize}\color{black}
					\item The $(i, j)$-th entry is $1$, where
					\begin{equation*}
						(i, j) =
						\begin{cases}
							\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{P}, \\
							\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{Q},
						\end{cases}
					\end{equation*}
					and ties may be broken arbitrarily;
					\item After deleting the $i$-th row and $j$-th column, the resulting submatrix $\mathbf{Y}$ is arbitrary permutation matrix of dimension $N_\mathrm{S}-1$ satisfying
					\begin{alignat*}{2}
						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{P}, \\
						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{Q},
					\end{alignat*}
					where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}, \hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are ${\mathbf{\Sigma}}_{\mathrm{B}}, {\mathbf{\Sigma}}_{\mathrm{F}}$ with both $i$-th row and $j$-th column deleted.
				\end{itemize}
			\end{coro}

			\begin{coro}{Channel power gain}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				If the direct channel is negligible, then the channel power gain is bounded by
				\begin{equation*}
					\sum\nolimits_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum\nolimits_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
				\end{equation*}
				which are attained respectively at
				\begin{equation*}
					\mathbf{\Theta}_\text{P-max}^\text{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \quad \mathbf{\Theta}_\text{P-min}^\text{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H},
				\end{equation*}
				where $\mathbf{J}$ is the backward identity matrix.
			\end{coro}

			\begin{coro}{Channel capacity at very low and high \glsfmtshort{snr}}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				If the direct channel is negligible, then the channel capacity at very low and high \glsfmtshort{snr} are approximately bounded from above by
				\begin{align*}
					C_{\rho_\downarrow} & \lessapprox \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \\
					C_{\rho_\uparrow} & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod\nolimits_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}).
				\end{align*}
				Their upper bounds can be attained at, for example, $\mathbf{\Theta}_\text{P-max}^\text{MIMO-ND}$.
			\end{coro}
		\end{column}

		\separatorcolumn

		\begin{column}{\colwidth}
			\vspace{-0.5cm}
			\begin{algo}{Group-wise geodesic optimization}{}
				\setlength{\leftskip}{\leftmargini}
				\setlength{\rightskip}{\leftmargini}
				% A geodesic is a curve representing the shortest path between two points in a Riemannian manifold.
				For \gls{bd}-\gls{ris} optimization problem of the form
				\begin{maxi*}
					{\scriptstyle{\mathbf{\Theta}}}{f(\mathbf{\Theta})}{}{}
					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{}
				\end{maxi*}
				% At iteration $r$, the $g$-th group is updated by \textcolor{imperialblue}{geodesic} \gls{rcg}
				we propose a \textcolor{pink!50!pink!75!black}{geodesic} \gls{rcg} algorithm below.
				\vspace{0.5cm}

				\begin{enumerate}\color{black}
					\item \emph{Compute the Euclidean gradient:}
					\begin{equation*}
						\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
					\end{equation*}
					\item \emph{Translate to the Riemannian gradient evaluated at the identity:}
					\begin{equation*}
						\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}};
					\end{equation*}
					\item \emph{Determine the conjugate direction:}
					\begin{equation*}
						{\mathbf{D}}_g^{(r)} = \tilde{\nabla}_{\mathrm{R},g}^{(r)} + \tilde{\gamma}_g^{(r)} {\mathbf{D}}_g^{(r-1)}, \quad \tilde{\gamma}_g^{(r)} = \frac{\tr\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)};
					\end{equation*}
					\item \emph{Perform \textcolor{pink!50!pink!75!black}{multiplicative} update along geodesic:}
					\begin{equation*}
						\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
					\end{equation*}
					where $\mu$ is refinable by the Armijo rule.
				\end{enumerate}
				\vspace{0.5cm}
			\end{algo}

			\begin{exampleblock}{Result 1: Algorithm evaluation}
				\begin{table}[!t]
					\centering
					\begin{tabular}{ccccccc}
						\toprule
						\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                                     \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
														& Objective                             & Iterations                               & Time [s]         & Objective        & Iterations   & Time [s]   \\ \midrule
						Geodesic                        & $\num{4.359e-3}$                      & $11.59$                                  & $\num{1.839e-2}$ & $\num{1.163e-2}$ & $25.58$      & $3.461$    \\
						Non-geodesic                    & $\num{4.329e-3}$                      & $30.92$                                  & $\num{5.743e-2}$ & $\num{1.116e-2}$ & $61.40$      & $13.50$    \\ \bottomrule
					\end{tabular}
				\end{table}
			\end{exampleblock}

			\begin{exampleblock}{Result 2: Bounds and Pareto frontier of singular values}
				\begin{figure}[!t]
					\centering
					\subfloat[Analytical vs numerical results: $4 \times 128 \times 4, \rank(\mathbf{H}_\mathrm{F}) = 2$]{
						\resizebox{0.492\linewidth}{!}{
							\input{../assets/poster/singular_bound_rank2_sx128.tex}
						}
					}
					\subfloat[Pareto frontier: $2 \times 64 \times 2$]{
						\resizebox{0.462\linewidth}{!}{
							\input{../assets/poster/singular_pareto_sx64.tex}
						}
					}
				\end{figure}
			\end{exampleblock}

			\begin{exampleblock}{Result 3: Channel power gain and achievable rate}
				\begin{figure}[!t]
					\centering
					\subfloat[Channel power gain: $16 \times N_\mathrm{S} \times 16$]{
						\resizebox{0.492\linewidth}{!}{
							\input{../assets/poster/power_sx_txrx16.tex}
						}
					}
					\subfloat[Achievable rate: $N_\mathrm{T} \times 128 \times N_\mathrm{R}$]{
						\resizebox{0.462\linewidth}{!}{
							\input{../assets/poster/rate_txrx.tex}
						}
					}
				\end{figure}

			\end{exampleblock}
		\end{column}

		\separatorcolumn
	\end{columns}
\end{frame}
\end{document}

### 2024-11-20 poster/custom-defs.tex
:triangular_flag_on_post: Add poster

% ====================
% BibLaTeX
% ====================

% \usepackage[backend=biber,
% 	bibstyle=authoryear,
% 	citestyle=authoryear,
% 	style=authoryear,
% 	maxcitenames=2,
% 	maxbibnames=20, % limit the length of list of names (authors/editors/etc.)
% 	sorting=ydnt, % sort references by year (descending), name, title
% 	dashed=false, % show authors instead of dash in publications having the same authors
% 	giveninits=true % render authors' given name initials and not the full given names
% ]{biblatex}
% %% Biblatex with Beamer bibliography icons
% \setbeamertemplate{bibliography item}{%
% 	\ifboolexpr{ test {\ifentrytype{book}} or test {\ifentrytype{mvbook}}
% 		or test {\ifentrytype{collection}} or test {\ifentrytype{mvcollection}}
% 		or test {\ifentrytype{reference}} or test {\ifentrytype{mvreference}} }
% 	{\setbeamertemplate{bibliography item}[book]}
% 	{\ifentrytype{online}
% 		{\setbeamertemplate{bibliography item}[online]}
% 		{\setbeamertemplate{bibliography item}[article]}}%
% 	\usebeamertemplate{bibliography item}}
% \defbibenvironment{bibliography}
% {\list{}
% 	{\settowidth{\labelwidth}{\usebeamertemplate{bibliography item}}%
% 		\setlength{\leftmargin}{\labelwidth}%
% 		\setlength{\labelsep}{\biblabelsep}%
% 		\addtolength{\leftmargin}{\labelsep}%
% 		\setlength{\itemsep}{\bibitemsep}%
% 		\setlength{\parsep}{\bibparsep}}}
% {\endlist}
% {\item}
% %% Redefine \refname
% \renewcommand{\bibname}{References}
% %% Redefine \parencite to use square brackets instead of braces
% \DeclareCiteCommand{\parencite}
% {\usebibmacro{prenote}}
% {\usebibmacro{citeindex}%
% 	\printtext[bibhyperref]{[\usebibmacro{cite}]}}
% {\multicitedelim}
% {\usebibmacro{postnote}}
% %% Highlight author names using Beamer data annotation
% %% Usage: add a new line `author+an = {<author-order>=highlight}` to an entry
% %% For example: author+an = {3=highlight} => highlight the 3rd author name
% \AtBeginBibliography{
% 	\renewcommand*{\mkbibnamegiven}[1]{%
% 		\ifitemannotation{highlight}
% 		{\textbf{#1}}
% 		{#1}%
% 	}

% 	\renewcommand*{\mkbibnamefamily}[1]{%
% 		\ifitemannotation{highlight}
% 		{\textbf{#1}}
% 		{#1}%
% 	}
% }

% ====================
% Boxes with tcolorbox
% ====================
\usepackage[most]{tcolorbox}

%%% Beamer colors in boxes

\newcommand{\beamercolorsinboxes}[1]{
	\setbeamercolor{itemize item}{fg=#1!75!black}
	\setbeamercolor{itemize/enumerate body}{fg=#1!65!white}
	\setbeamercolor{itemize/enumerate subbody}{fg=#1!65!white}
	\setbeamercolor{item projected}{fg=white, bg=#1!75!black}
}

%%% Highlight Oval Box
\newtcbox{\xmybox}[1][red]{on line,
	arc=7pt,colback=#1!10!white,colframe=#1!50!black,
	before upper={\rule[-3pt]{0pt}{10pt}},boxrule=1pt,
	boxsep=0pt,left=6pt,right=6pt,top=2pt,bottom=2pt}
%%% Box for stating problems
%%%%%%%%
%Usage: (similar for infobox)
%	\begin{defbox}{title}
%		contents
%	\end{defbox}
%%%%%%%%
\newtcolorbox{defbox}[1]{%
	enhanced,
	attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	colback=cyan!5!white,
	colframe=cyan!75!black,
	coltitle=cyan!80!black,
	%	left=0mm,right=0mm,top=2mm,bottom=0mm,
	title={#1},
	fonttitle=\bfseries\large, fontupper=\color{cyan!65!white},
	boxed title style={colback=cyan!5!white,colframe=cyan!75!black},
	before upper={
			\beamercolorsinboxes{cyan}
		}
}%
%%% Box for announcement
\newtcolorbox{infobox}[1]{%
	enhanced,
	attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	colback=yellow,
	colframe=red!75!black,
	coltitle=red!75!black,
	%	left=0mm,right=0mm,top=2mm,bottom=0mm,
	title={#1},
	fonttitle=\bfseries\large, fontupper=\color{red!65!white},
	boxed title style={colback=yellow,colframe=red!75!black},
	before upper={
			\beamercolorsinboxes{red}
		}
}%
%%% Box for example
\newtcolorbox{exabox}[1]{%
	enhanced,
	attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	colframe=brown!75!black,colback=brown!5!white,coltitle=brown!50!brown!75!black,
	%	left=0mm,right=0mm,top=2mm,bottom=0mm,
	title={#1},
	fonttitle=\bfseries\large, fontupper=\color{brown!65!white},
	boxed title style={colback=brown!5!white,coltitle=brown!50!brown!75!black},
	before upper={
			\beamercolorsinboxes{brown}
		}
}%
%%% Theorem Box
%%%%%%%%
%Usage: (similar for conjecture, lemma, etc.)
%	\begin{thm}{title}{nameref}
%		contents
%	\end{thm}
% Use \ref{thm:nameref} to refer to the theorem
%%%%%%%%
%%%% Use \newtcbtheorem[number within=section]{thm} to number within each section
\newcounter{thm}
\newtcbtheorem[use counter=thm]{thm}%
{Theorem}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	top=2mm,bottom=6mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\itshape\color{blue!65!white},
	fonttitle=\bfseries\large,fontupper=\color{blue!65!white},
	colframe=blue!75!black,colback=blue!5!white,coltitle=blue!50!blue!75!black,
	boxed title style={colback=blue!5!white,coltitle=blue!50!blue!75!black},
	before upper={
			\beamercolorsinboxes{blue}
		}
}{thm}%
%%% Proposition Box
\newcounter{prop}
\newtcbtheorem[use counter=prop]{prop}%
{Proposition}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	top=2mm,bottom=0mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\itshape,
	colframe=orange!75!black,colback=orange!5!white,coltitle=orange!50!orange!75!black,
	boxed title style={colback=orange!5!white,coltitle=orange!50!orange!75!black},
	before upper={
			\beamercolorsinboxes{orange}
		}
}{prop}%
%%% Corollary Box
\newcounter{coro}
\newtcbtheorem[use counter=coro,number within=prop]{coro}%
{Corollary}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	%	top=2mm,bottom=0mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\slshape,
	colframe=gray!75!black,colback=gray!5!white,coltitle=gray!50!gray!75!black,
	boxed title style={colback=gray!5!white,coltitle=gray!50!gray!75!black},
	before upper={
			\beamercolorsinboxes{gray}
		}
}{coro}%
%%% Lemma Box
\newcounter{lem}
\newtcbtheorem[use counter=lem]{lem}%
{Lemma}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	%	top=2mm,bottom=0mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\itshape,
	colframe=green!75!black,colback=green!5!white,coltitle=green!50!green!75!black,
	boxed title style={colback=green!5!white,coltitle=green!50!green!75!black},
	before upper={
			\beamercolorsinboxes{green}
		}
}{lem}%
%%% Algorithm Box
\newcounter{algo}
\newtcbtheorem[use counter=algo]{algo}%
{Algorithm}{attach boxed title to top 	left={xshift=5mm,yshift=-5mm,yshifttext=-5mm},
	enhanced jigsaw,
	%	top=2mm,bottom=0mm,left=0mm,right=0mm,
	fonttitle=\bfseries\large,fontupper=\itshape,
	colframe=pink!75!black,colback=pink!5!white,coltitle=pink!50!pink!75!black,
	boxed title style={colback=pink!5!white,coltitle=pink!50!pink!75!black},
	before upper={
			\beamercolorsinboxes{pink}
		}
}{algo}%

### 2024-11-20 poster/beamer.tex
:lipstick: Update poster

@@
 
-					The capability of \gls{d} and \gls{bd} \gls{ris} to redistribute the singular values of \glsfmtshort{mimo} channels.
+					The capability of \gls{d}- and \gls{bd}-\gls{ris} to redistribute the singular values of \glsfmtshort{mimo} channels.
 					\item \textbf{How does it differ from previous work?}
@@
 				Consider an $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ setup with \gls{bd}-\gls{ris} divided into $G$ groups of $L$ elements each.
-				Define $N = \min(N_\mathrm{T}, N_\mathrm{R})$, $\bar{N} = \max(N_\mathrm{T}, N_\mathrm{S}, N_\mathrm{R})$, and $\mathbf{H}_{\mathrm{B}/\mathrm{F}}\stackrel{\svd}{=} \mathbf{U}_{\mathrm{B}/\mathrm{F}} \boldsymbol{\Sigma}_{\mathrm{B}/\mathrm{F}} \mathbf{V}_{\mathrm{B}/\mathrm{F}}^\mathsf{H}$.
+				Define $N = \min(N_\mathrm{T}, N_\mathrm{R})$ and $\mathbf{H}_{\mathrm{B}/\mathrm{F}}\stackrel{\svd}{=} \mathbf{U}_{\mathrm{B}/\mathrm{F}} \boldsymbol{\Sigma}_{\mathrm{B}/\mathrm{F}} \mathbf{V}_{\mathrm{B}/\mathrm{F}}^\mathsf{H}$.
 				\begin{equation*}
@@
 				Assume the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible (i.e., $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$).
-				The plot relies on grid search for one channel realization.
+				For one channel realization, we can reveal channel singular values achieved by \gls{d}- and \gls{bd}-\gls{ris} by grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$.
 				\begin{figure}
 					\centering
-					\includegraphics[width=0.44\columnwidth]{../assets/simulation/singular_trend.eps}
+					\includegraphics[width=0.41\columnwidth]{../assets/simulation/singular_trend.eps}
 					% \caption{
@@
 			\vspace{-0.5cm}
-			\begin{algo}{Group-wise geodesic optimization}{}
+			\begin{algo}{Group-wise geodesic optimization for \gls{bd}-\gls{ris}}{}
 				\setlength{\leftskip}{\leftmargini}
@@
 					\end{equation*}
-					where $\mu$ is refinable by the Armijo rule.
+					where $\mu$ is refinable by the Armijo rule. To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential.
 				\end{enumerate}
-				\vspace{0.5cm}
+				% \vspace{0.5cm}
 			\end{algo}
@@
 					\subfloat[Analytical vs numerical results: $4 \times 128 \times 4, \rank(\mathbf{H}_\mathrm{F}) = 2$]{
-						\resizebox{0.492\linewidth}{!}{
+						\resizebox{0.485\linewidth}{!}{
 							\input{../assets/poster/singular_bound_rank2_sx128.tex}
@@
 					\subfloat[Pareto frontier: $2 \times 64 \times 2$]{
-						\resizebox{0.462\linewidth}{!}{
+						\resizebox{0.454\linewidth}{!}{
 							\input{../assets/poster/singular_pareto_sx64.tex}
@@
 					\subfloat[Channel power gain: $16 \times N_\mathrm{S} \times 16$]{
-						\resizebox{0.492\linewidth}{!}{
+						\resizebox{0.485\linewidth}{!}{
 							\input{../assets/poster/power_sx_txrx16.tex}
@@
 					\subfloat[Achievable rate: $N_\mathrm{T} \times 128 \times N_\mathrm{R}$]{
-						\resizebox{0.462\linewidth}{!}{
+						\resizebox{0.454\linewidth}{!}{
 							\input{../assets/poster/rate_txrx.tex}

### 2024-12-06 review/response_241203.tex
:construction: Adding response

\documentclass[
	fontsize=11pt,
	paper=a4,
	foldmarks=false
]{scrartcl}

\usepackage{response}

\setkomavar{signature}{Yang Zhao, Hongyu Li, Bruno Clerckx, and Massimo Franceschetti}
\setkomavar{date}{\today}
\setkomavar{subject}{Response to Decision on Manuscript T-SP-32387-2024}

\begin{document}
\begin{letter}{%
		Prof. Wei Yi\\
		Associate Editor\\
		IEEE Transactions on Signal Processing
	}
	\opening{Dear Editor and Reviewers,}
	Thank you for giving us the opportunity to submit a revised version of \emph{Channel Shaping Using Beyond Diagonal RIS: Analysis, Optimization, and Enhanced Flexibility}.
	Your comments and suggestions have been invaluable in helping us improve the quality of the manuscript.
	% We would like to express our sincere gratitude to your critical comments and suggestions, which helped us improve the quality of the manuscript significantly.
	Below we prepare a point-to-point response and highlight the corresponding changes made to the manuscript.
	We hope that the revisions and clarifications make the manuscript meet the standards of TSP publications.
	\closing{Yours sincerely,}
\end{letter}

\begin{editor}
	\summary{The reviewers raised a number of concerns regarding the paper's contribution, novelty, and mathematical correctness, which led to the recommendation for rejection. The main issues identified include: 1) the contribution of the paper is unclear. Specifically, the proposed framework in (7) is not sufficiently general as it does not consider BD-RIS dependent constraints (e.g., QoS, sensing quality). A more general case has already been investigated and solved in the authors' previous work [41]. Some content in Section III are well established methods in the literature [54]. 2) The optimization problems (38) and (45) lacks of novelty. The reviewer pointed that they can be possibly solved by existing methods through appropriate adjustment [33], [47]. Also, it is also pointed out that Corollaries 3.1-3.5 are the standard results from matrix textbook. 3) The correctness and usefulness of the mathematical derivations. For example, the derivation in the proof of Lamma (Appendix A) is incorrect. Convergence proof in Appendix F is questionable. The usefulness of these bounds on singular values of the effective channel H is unclear. 4) The literature review can be enhanced to cover a boarder range of papers that related to the problem addressed. 5) The simulation study can be enhanced. For example, comparisons with the diagonal RIS (D-RIS) and a globally passive BD-RIS were suggested by the reviewer.}

	\reply{
		bbb \ref{iq:sv_bound_rank_deficient} \cite{Fotock2023}
	}

\end{editor}

\begin{reviewer}
	\summary{This manuscript investigates the impact of beyond-diagonal (BD)-Reconfigurable Intelligent Surface (RIS) to the distribution of singular values of Multiple-Input Multiple-Output (MIMO) channel of a point-to-point communication system. Especially, the authors derive bounds of singular values of BD-RIS channel and propose algorithms to design BD-RIS configuration.}

	\comment{RIS \cite{Moler2003} has been hailed as one of "the" 6G technologies by the academia, but much less so by the industry. How to do you see the potential of your scheme to change this, since it also speaks along the line of Ambient IoT?}
	\label{cm:1.1}

	% \reply{
	% 	Many researchers and companies expect RIS to be a massive surface mounted to walls and windows, functioning as an all-purpose programmable RF lens to focus ambient waves on the target. See \eqref{eq:1}.
	% }

	\reply{
		Many researchers and companies expect RIS to be a massive surface mounted to walls and windows, functioning as an all-purpose programmable RF lens to focus ambient waves on the target. See \eqref{eq:1}.

		\begin{equation}
			\label{eq:1}
			a = 1;
		\end{equation}

		This, on paper, could mitigate two major challenges in 5G: reduce energy consumption of massive MIMO and improve channel condition for mmWave radios.
		However, outdoor deployment of such large surfaces shall comply with local regulations and requires a cooperation between building constructors, network operators, and equipment vendors, which could be a long-term project.
		Our RIScatter scheme, on the other hand, aims to unify RIS (wireless channel shaper) and backscatter device (information source) into one batteryless cognitive radio featuring heterogeneous traffic control and universal hardware design.
		This is especially suitable for indoor environments where the scattering nodes can be geometrically distributed in the proximity of transceivers.
		Imagine a wireless future where the boundary between the network and environment is blurred --- everything can be “smartened” by coating with a metamaterial layer and attaching a microcontroller. Only a few radiating sources (like the sun) are active, while most objects (like the universe) can exploit ambient waves to energize themselves, sense the environment, communicate with devices, and assist legacy transmissions when idle.
		% Indoor deployment of RIS seems more feasible,
		% For the indoor scenario, the cost-effectiveness of RIS over conventional relays remains an open question.
		% This vision calls for a rethinking of waveform design, receiver architecture, and multiple access schemes to accommodate the new paradigm of ambient IoT.
	}

	\comment{We can think of a future in which a number of ambient IoT devices do not have a transmitter and instead they communicate based on backscattering. Where do you see the main challenges towards wide adoption of those devices?}
	\label{cm:1.2}

	\reply{
		We would like to highlight three main challenges for batteryless ambient IoT devices: energy harvesting, spectrum sharing, and security issue.
		Far-field wireless power transfer has been recognized as a promising solution to energize ultra-low power devices, but the operation range is quite short (within few meters) and the end-to-end power efficiency is usually low (less than few percents).
		In such case, idle RIScatter nodes can operate in full RIS mode and redirect local RF waves to those in transmitting mode for higher energy efficiency and backscatter SNR.
		Spectrum sharing with legacy wireless systems is another challenge, as backscatter devices manipulate existing radio signals to transmit data.
		This raises concerns about potential interference with other wireless applications operating in the same spectrum, and calls for a rethinking of waveform design, receiver architecture, modulation and coding scheme, and multiple access strategy to ensure a symbiotic coexistence.
		Finally, security issue is a major concern for batteryless devices since they are vulnerable to eavesdropping, jamming, and spoofing attacks.
		Please refer to \ref{cm:1.1}
	}

	\comment{What was the main criticism you have received during the review process and how did you address it?}
	\reply{
		The main technical criticism we received during the review process was the uncompleteness of simulation results.
		Reviewers were interested in the impact of imperfect CSI and primary/backscatter SNR on the achievable rate region.
		Those results evaluate the practicality of RIScatter systems and have been added to the revised manuscript.
		One reviewer also suggested including analytical and numerical results on BER vs SNR.
		While we fully acknowledge its importance, the BER analysis is non-trivial due to the coexistence of both links, and we would like to reserve this for a future work.
		Another interesting question was the optimal primary input distribution that maximizes the weighted sum mutual information.
		It deserves further research but we decided to stay with CSCG primary source for a tractable rate expression.
		Two reviewers also pointed out that perfect symbol-level synchronization of both links is a strong assumption, especially for large-scale RIScatter system with small spreading ratio.
		If necessary, some penalty factor can be introduced to the rate expression to compensate for the synchronization error.
		Please refer to \ref{cm:1.2}
	}

\end{reviewer}

\bibliographystyle{IEEEtran}
\bibliography{supplement}
\end{document}

### 2024-12-06 manuscript/main.tex
:construction: Adding response

--- 2024-11-20 main.tex
@@
-\documentclass[journal]{IEEEtran}
-% \documentclass[journal,12pt,onecolumn,draftclsnofoot]{IEEEtran}
-
-\usepackage[table]{xcolor}
-\usepackage{adjustbox}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{bookmark}
-\usepackage{booktabs}
-\usepackage[makeroom]{cancel}
-\usepackage{cases}
-\usepackage[american]{circuitikz}
-\usepackage{cite}
-% \usepackage{fixmath}
-\usepackage[acronym]{glossaries-extra}
-\usepackage{hyperref}
-\usepackage{import}
-\usepackage{mathtools}
-\usepackage{microtype}
-\usepackage[short]{optidef}
-\usepackage{pgfplots}
-\usepackage{ragged2e}
-\usepackage[subtle]{savetrees}
-\usepackage{siunitx}
-\usepackage{stfloats}
-\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
-\usepackage{tabularx}
-\usepackage{tikz}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\usepackage{multirow}
-\usepackage{booktabs}
-% \usepackage{cleveref}
-\usepackage{enumitem}
-
-% page limit hacks
-% \usepackage{setspace}
-% \usepackage[compact]{titlesec}
-% % ! \usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
-% \abovedisplayskip=1mm
-% \belowdisplayskip=1mm
-% \abovedisplayshortskip=1mm
-% \belowdisplayshortskip=1mm
-% \setlength{\jot}{0.1mm}
-% \setlength{\floatsep}{1mm}
-% \setlength{\textfloatsep}{1mm}
-% \setlength{\intextsep}{1mm}
-% \setlength{\skip\footins}{2mm}
-
-% amsmath
-\DeclareMathOperator{\diag}{diag}
-\DeclareMathOperator{\tr}{tr}
-\DeclareMathOperator{\sv}{sv}
-\DeclareMathOperator{\card}{card}
-\DeclareMathOperator{\rank}{rank}
-
-% amsthm
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{proposition}{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}[proposition]
-
-% enumitem
-\setlist[itemize]{leftmargin=4mm}
-\setlist[enumerate]{leftmargin=4mm}
-
-% PGF/TikZ
-\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
-\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,decorations.shapes,shapes.geometric}
-\usepgfplotslibrary{groupplots,patchplots}
-\pgfplotsset{compat=1.18}
-\pgfplotsset{every axis/.append style={
-	title style={font=\Large},
-	label style={font=\Large},
-	tick label style={font=\Large},
-	legend style={font=\Large},
-}}
-
-% Double superscript
-\newcommand\herm[2][-4]{{#2}^{\mkern#1mu\mathsf{H}}}
-
-% algpseudocode
-\makeatletter
-\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
-\newcommand\setalgorithmcaptionfont[1]{%
-	\let\my@floatc@ruled\floatc@ruled          % save \floatc@ruled
-	\def\floatc@ruled{%
-		\global\let\floatc@ruled\my@floatc@ruled % restore \floatc@ruled
-		#1\floatc@ruled}}
-\makeatother
-
-\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
-\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
-\algrenewcommand{\algorithmicwhile}{\textbf{While}}
-\algrenewcommand{\algorithmicend}{\textbf{End}}
-\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
-\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
-\algrenewcommand{\algorithmicfor}{\textbf{For}}
-\algrenewcommand{\algorithmicif}{\textbf{If}}
-\algrenewcommand{\algorithmicelse}{\textbf{Else}}
-\algrenewcommand{\algorithmicdo}{}
-\algrenewcommand{\algorithmicthen}{}
-\algnewcommand{\Initialize}[1]{%
-	\State \textbf{Initialize }{#1}
-}
-
-% glossaries-extra
-\glsdisablehyper
-\setabbreviationstyle[acronym]{long-short}
-\newacronym{ao}{AO}{Alternating Optimization}
-\newacronym{bd}{BD}{Beyond Diagonal}
-\newacronym{bcd}{BCD}{Block Coordinate Descent}
-\newacronym{d}{D}{Diagonal}
-\newacronym{dof}{DoF}{Degrees of Freedom}
-\newacronym{siso}{SISO}{Single-Input Single-Output}
-\newacronym{miso}{MISO}{Multiple-Input Single-Output}
-\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
-\newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
-\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
-\newacronym{pc}{PC}{Point-to-point Channel}
-\newacronym{ic}{IC}{Interference Channel}
-\newacronym{wsr}{WSR}{Weighted Sum-Rate}
-\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
-\newacronym{svd}{SVD}{Singular Value Decomposition}
-\newacronym{mmse}{MMSE}{Minimum Mean-Square Error}
-\newacronym{wmmse}{WMMSE}{Weighted \gls{mmse}}
-\newacronym{mse}{MSE}{Mean-Square Error}
-\newacronym{los}{LoS}{Line-of-Sight}
-\newacronym{csi}{CSI}{Channel State Information}
-\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
-\newacronym{sca}{SCA}{Successive Convex Approximation}
-\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
-
-\begin{document}
-\title{Channel Shaping Using Beyond Diagonal Reconfigurable Intelligent Surface:\\Analysis, Optimization, and Enhanced Flexibility}
+\input{preamble}
+
+\title{Channel Shaping Using Beyond Diagonal RIS:\\Analysis, Optimization, and Enhanced Flexibility}
 \author{
 	\IEEEauthorblockN{
-		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
-		Hongyu~Li,~\IEEEmembership{Graduate Student Member,~IEEE,}\\
-		Massimo~Franceschetti,~\IEEEmembership{Fellow,~IEEE,}
-		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
+		Yang Zhao, \IEEEmembership{Member, IEEE,}
+		Hongyu Li, \IEEEmembership{Graduate Student Member, IEEE,}\\
+		Massimo Franceschetti, \IEEEmembership{Fellow, IEEE,}
+		and Bruno Clerckx, \IEEEmembership{Fellow, IEEE}
 	}
@@
 }
+
+\begin{document}
+
 \maketitle
@@
 		This simple architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal.
-		The idea was soon generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.\label{fn:symmetric}}.
+		The idea was soon generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}.
 		This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
@@
 	\begin{subsection}{Contributions}
-		\label{sc:contributions}
 		% We notice that there lacks a comprehensive study of \gls{bd}-\gls{ris} in point-to-point \gls{mimo} systems
@@
 
-\begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Model}
+	\begin{section}{BD-RIS Model}
 	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
@@
 		\mathbf{\Theta} = \diag(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
-		\label{eq:bd_ris}
 	\end{equation}
@@
 			\centering
-			\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
+			\includegraphics[width=\columnwidth]{../assets/simulation/singular_trend.eps}
 			\caption{$2 \times 2 \times 2$ singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is negligible.
@@
 	It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
-		Its importance lies in the fact that the channel shaping question in Section \ref{sc:contributions} can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
+	Its importance lies in the fact that the initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
 	The question is partially answered in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sv_nth} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
@@
 			\begin{split}
-					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \bigm\vert & \forall p < r, \ \forall (F, G, H) \in T_p^r,\\
+				T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \bigm\vert & \forall p < r, \ \forall (F, G, H) \in T_p^r,                                              \\
 																						& \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + \frac{p(p+1)}{2} \Bigr\},
@@
 				\prod_{n=1}^k \sigma_n(\mathbf{H})                   & \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:sv_product_largest}                    \\
-					\prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}) & \ge \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:sv_product_smallest}
+				\prod_{n=\bar{N}}^{\mathclap{\bar{N}-k+1}} \sigma_n(\mathbf{H}) & \ge \prod_{n=\bar{N}}^{\mathclap{\bar{N}-k+1}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}).
+\label{iq:sv_product_smallest}
 			\end{align}
@@
 		\begin{equation}
-				\max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
+			\max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
 			\label{iq:sv_nth}
@@
 				\begin{subnumcases}{(i, j) =}
-					\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:sv_nth_max_pair} \\
-					\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:sv_nth_min_pair}
+					\ \underset{\mathclap{i+j=n+1}}{\arg\min} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:sv_nth_max_pair} \\
+					\ \underset{\mathclap{i+j=n+N_\mathrm{S}}}{\arg\max} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:sv_nth_min_pair}
 				\end{subnumcases}
@@
 					\begin{alignat}{2}
-						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{P}, \label{eq:sv_nth_max_condition} \\
-						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) && \text{ for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
+						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \ \ \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})            &  & \text{ for } \mathbf{P}, \label{eq:sv_nth_max_condition} \\
+						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \ \ \max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) &  & \text{ for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
 					\end{alignat}
@@
 		\begin{gather}
-				\max_{i+j=N_\mathrm{S}+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_largest} \\
-				\min_{i+j=\bar{N}+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\ge} \sigma_{\bar{N}}(\mathbf{H}) {\ge} \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}).
+			\max_{\mathclap{i+j=N_\mathrm{S}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_largest} \\
+			\min_{\mathclap{i+j=\bar{N}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\ge} \sigma_{\bar{N}}(\mathbf{H}) {\ge} \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}).
 \label{iq:sv_smallest}
@@
 	% 		\centering
-	% 		\includegraphics[width=\columnwidth]{assets/simulation/singular_trend.eps}
+	% 		\includegraphics[width=\columnwidth]{../assets/simulation/singular_trend.eps}
 	% 		\caption{$2 \times 2 \times 2$ channel singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is blocked.
@@
 
-\begin{section}{\glsfmtshort{bd}-\glsfmtshort{ris} Design Frameworks}
+	\begin{section}{BD-RIS Design Frameworks}
 	% In this section, we first provide an overview on signal processing techniques for group-connected \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group and operates directly on the Stiefel manifold.
@@
 
-	\begin{subsection}{General (Non-Geodesic) \glsfmtshort{rcg}}
+	\begin{subsection}{General (Non-Geodesic) RCG}
 		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
@@
 
-	\begin{subsection}{Geodesic \glsfmtshort{rcg}}
+\begin{subsection}{Geodesic RCG}
 	Before introducing geodesic \gls{rcg}, we revisit some basic concepts in differential geometry.
@@
 
-		\setalgorithmcaptionfont{\small}
+	% \setalgorithmcaptionfont{\small}
 	\begin{algorithm}[!t]
-			\small
+		% \small
 		\caption{Group-wise geodesic \gls{rcg} for \gls{bd}-\gls{ris} design}
@@
 			\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic_translated}
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
+			\While {$\scriptstyle f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
 			\State $\mu \gets 2 \mu$
 			\EndWhile
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
+			\While {$\scriptstyle f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
 			\State $\mu \gets \mu / 2$
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/singular_pareto_sx32_nd.tex}
+					 \input{../assets/simulation/singular_pareto_sx32_nd.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/singular_pareto_sx32.tex}
+					 \input{../assets/simulation/singular_pareto_sx32.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/singular_pareto_sx64.tex}
+					 \input{../assets/simulation/singular_pareto_sx64.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/singular_pareto_sx128.tex}
+					 \input{../assets/simulation/singular_pareto_sx128.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/singular_bound_rank1_sx32.tex}
+					 \input{../assets/simulation/singular_bound_rank1_sx32.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/singular_bound_rank1_sx64.tex}
+					 \input{../assets/simulation/singular_bound_rank1_sx64.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/singular_bound_rank2_sx128.tex}
+					 \input{../assets/simulation/singular_bound_rank2_sx128.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/singular_bound_rank4_sx256.tex}
+					 \input{../assets/simulation/singular_bound_rank4_sx256.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/power_bond_txrx1_nd.tex}
+					 \input{../assets/simulation/power_bond_txrx1_nd.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-						\input{assets/simulation/power_bond_txrx4_nd.tex}
+					 \input{../assets/simulation/power_bond_txrx4_nd.tex}
 				 }
@@
 			 \resizebox{!}{3.0625cm}{
-					\input{assets/simulation/power_sx_txrx16_nd.tex}
+				 \input{../assets/simulation/power_sx_txrx16_nd.tex}
 			 }
@@
 			 \resizebox{!}{3.0625cm}{
-					\input{assets/simulation/power_sx_txrx16.tex}
+				 \input{../assets/simulation/power_sx_txrx16.tex}
 			 }
@@
 			 \resizebox{!}{3.25cm}{
-					\input{assets/simulation/rate_beamforming.tex}
+				 \input{../assets/simulation/rate_beamforming.tex}
 			 }
@@
 			 \resizebox{!}{3.25cm}{
-					\input{assets/simulation/rate_txrx.tex}
+				 \input{../assets/simulation/rate_txrx.tex}
 			 }
@@
 			 \resizebox{!}{3.25cm}{
-					\input{assets/simulation/rate_sx.tex}
+				 \input{../assets/simulation/rate_sx.tex}
 			 }
@@
 			 \resizebox{!}{3.25cm}{
-					\input{assets/simulation/rate_kfactor.tex}
+				 \input{../assets/simulation/rate_kfactor.tex}
 			 }
@@
 Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
+% \begin{equation}
+% 	\label{iq:power_passive_approx}
+% 	\scriptstyle
+% 	\begin{split}
+% 		2 \Re \Bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \\
+% 		\ge 2 \Re \Bigl\{\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}
+% 	\end{split}
+% \end{equation}
+\begin{multline}
+	\label{iq:power_passive_approx}
+	\scriptstyle{2 \Re \bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}} \\
+	\scriptstyle{\ge 2 \Re \bigl\{\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}}
+\end{multline}
 % Expanding both side gives \eqref{iq:power_passive_approx}.
 On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:nonnegative_norm_square}.
+\begin{multline}
+	\label{iq:nonnegative_norm_square}
+	\scriptstyle{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} }\\
+		\scriptstyle{\mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\bigr\} + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0}
+\end{multline}
 Adding \eqref{iq:power_passive_approx} and \eqref{iq:nonnegative_norm_square}, we have
 \begin{multline}
-			2 \Re \Bigl\{\tr(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
-			\ge 2 \Re \Bigl\{\tr({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \Bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
+	2 \Re \bigl\{\tr(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
+	\ge 2 \Re \bigl\{\tr({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
 \end{multline}
 which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
-		\begin{figure*}
-			\begin{equation}
-				\label{iq:power_passive_approx}
-				\resizebox{0.95\textwidth}{!}{
-					$2 \Re \Bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
-				}
-			\end{equation}
-			\begin{equation}
-				\label{iq:nonnegative_norm_square}
-				\resizebox{0.95\textwidth}{!}{
-					$\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
-				}
-			\end{equation}
-			\hrulefill
-		\end{figure*}
+% \begin{figure*}
+% \begin{equation}
+% 	\label{iq:power_passive_approx}
+% 	\resizebox{0.95\textwidth}{!}{
+% 		$2 \Re \Bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
+% 	}
+% \end{equation}
+% 	\begin{equation}
+% 		\label{iq:nonnegative_norm_square}
+% 		\resizebox{0.95\textwidth}{!}{
+% 			$\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
+% 		}
+% 	\end{equation}
+% 	\hrulefill
+% \end{figure*}
 
@@
 % 			\resizebox{0.65\columnwidth}{!}{
-% 				\input{assets/simulation/ic_interference_sx.tex}
+% 				\input{../assets/simulation/ic_interference_sx.tex}
 % 			}
@@
 % 			\resizebox{0.65\columnwidth}{!}{
-% 				\input{assets/simulation/ic_rate_sx.tex}
+% 				\input{../assets/simulation/ic_rate_sx.tex}
 % 			}
@@
 % 			\resizebox{0.65\columnwidth}{!}{
-% 				\input{assets/simulation/ic_rate_user.tex}
+% 				\input{../assets/simulation/ic_rate_user.tex}
 % 			}

### 2024-12-13 review/response_241203.tex
:construction: Updating structure

@@
 
+\input{../manuscript/preamble}
 \usepackage{response}
@@
 	Your comments and suggestions have been invaluable in helping us improve the quality of the manuscript.
-	% We would like to express our sincere gratitude to your critical comments and suggestions, which helped us improve the quality of the manuscript significantly.
-	Below we prepare a point-to-point response and highlight the corresponding changes made to the manuscript.
+	Below we prepare a point-to-point response and highlight the corresponding in-text changes, where labels have been matched to the latest manuscript for your convenience.
 	We hope that the revisions and clarifications make the manuscript meet the standards of TSP publications.
@@
 \begin{editor}
-	\summary{The reviewers raised a number of concerns regarding the paper's contribution, novelty, and mathematical correctness, which led to the recommendation for rejection.
-The main issues identified include: 1) the contribution of the paper is unclear.
-Specifically, the proposed framework in (7) is not sufficiently general as it does not consider BD-RIS dependent constraints (e.g., QoS, sensing quality).
-A more general case has already been investigated and solved in the authors' previous work [41].
-Some content in Section III are well established methods in the literature [54].
-2) The optimization problems (38) and (45) lacks of novelty.
-The reviewer pointed that they can be possibly solved by existing methods through appropriate adjustment [33], [47].
-Also, it is also pointed out that Corollaries 3.1-3.5 are the standard results from matrix textbook.
-3) The correctness and usefulness of the mathematical derivations.
-For example, the derivation in the proof of Lamma (Appendix A) is incorrect.
-Convergence proof in Appendix F is questionable.
-The usefulness of these bounds on singular values of the effective channel H is unclear.
-4) The literature review can be enhanced to cover a boarder range of papers that related to the problem addressed.
-5) The simulation study can be enhanced.
-For example, comparisons with the diagonal RIS (D-RIS) and a globally passive BD-RIS were suggested by the reviewer.}
+	\summary{
+		The reviewers raised a number of concerns regarding the paper's contribution, novelty, and mathematical correctness, which led to the recommendation for rejection.
+The main issues identified include:
+		\begin{enumerate}
+			\item The contribution of the paper is unclear.
+Specifically, the proposed framework in \eqref{op:general} is not sufficiently general as it does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality).
+A more general case has already been investigated and solved in the authors' previous work \cite{Zhou2023}.
+Some content in Section \ref{sc:framework} are well established methods in the literature \cite{Abrudan2008}.
+			\item The optimization problems \eqref{op:power} and \eqref{op:rate_ris} lacks of novelty.
+The reviewer pointed that they can be possibly solved by existing methods through appropriate adjustment \cite{Santamaria2023,Li2023b}.
+Also, it is also pointed out that Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are the standard results from matrix textbook.
+			\item The correctness and usefulness of the mathematical derivations.
+For example, the derivation in the proof of Appendix \ref{ap:pareto} is incorrect.
+Convergence proof in Appendix \ref{ap:power} is questionable.
+The usefulness of these bounds on singular values of the effective channel $\mathbf{H}$ is unclear.
+			\item The literature review can be enhanced to cover a boarder range of papers that related to the problem addressed.
+			\item The simulation study can be enhanced. For example, comparisons with the \gls{d}-\gls{ris} and a globally passive \gls{bd}-\gls{ris} were suggested by the reviewer.
+		\end{enumerate}
+	}
 
 	\reply{
-		bbb \ref{iq:sv_bound_rank_deficient} \cite{Fotock2023}
+		Good. \cite{Fotock2023}
 	}
@@
 \begin{reviewer}
-	\summary{This manuscript investigates the impact of beyond-diagonal (BD)-Reconfigurable Intelligent Surface (RIS) to the distribution of singular values of Multiple-Input Multiple-Output (MIMO) channel of a point-to-point communication system.
-Especially, the authors derive bounds of singular values of BD-RIS channel and propose algorithms to design BD-RIS configuration.}
-
-	\comment{RIS \cite{Moler2003} has been hailed as one of "the" 6G technologies by the academia, but much less so by the industry.
-How to do you see the potential of your scheme to change this, since it also speaks along the line of Ambient IoT?}
-	\label{cm:1.1}
-
-	% \reply{
-	% 	Many researchers and companies expect RIS to be a massive surface mounted to walls and windows, functioning as an all-purpose programmable RF lens to focus ambient waves on the target.
-See \eqref{eq:1}.
-	% }
-
-	\reply{
-		Many researchers and companies expect RIS to be a massive surface mounted to walls and windows, functioning as an all-purpose programmable RF lens to focus ambient waves on the target.
-See \eqref{eq:1}.
-
-		\begin{equation}
-			\label{eq:1}
-			a = 1;
-		\end{equation}
-
-		This, on paper, could mitigate two major challenges in 5G: reduce energy consumption of massive MIMO and improve channel condition for mmWave radios.
-		However, outdoor deployment of such large surfaces shall comply with local regulations and requires a cooperation between building constructors, network operators, and equipment vendors, which could be a long-term project.
-		Our RIScatter scheme, on the other hand, aims to unify RIS (wireless channel shaper) and backscatter device (information source) into one batteryless cognitive radio featuring heterogeneous traffic control and universal hardware design.
-		This is especially suitable for indoor environments where the scattering nodes can be geometrically distributed in the proximity of transceivers.
-		Imagine a wireless future where the boundary between the network and environment is blurred --- everything can be “smartened” by coating with a metamaterial layer and attaching a microcontroller.
-Only a few radiating sources (like the sun) are active, while most objects (like the universe) can exploit ambient waves to energize themselves, sense the environment, communicate with devices, and assist legacy transmissions when idle.
-		% Indoor deployment of RIS seems more feasible,
-		% For the indoor scenario, the cost-effectiveness of RIS over conventional relays remains an open question.
-		% This vision calls for a rethinking of waveform design, receiver architecture, and multiple access schemes to accommodate the new paradigm of ambient IoT.
+	\summary{
+		This manuscript investigates the impact of \gls{bd}-\gls{ris} to the distribution of singular values of \gls{mimo} channel of a point-to-point communication system.
+Especially, the authors derive bounds of singular values of \gls{bd}-\gls{ris} channel and propose algorithms to design \gls{bd}-\gls{ris} configuration.
 	}
 
-	\comment{We can think of a future in which a number of ambient IoT devices do not have a transmitter and instead they communicate based on backscattering.
-Where do you see the main challenges towards wide adoption of those devices?}
-	\label{cm:1.2}
-
-	\reply{
-		We would like to highlight three main challenges for batteryless ambient IoT devices: energy harvesting, spectrum sharing, and security issue.
-		Far-field wireless power transfer has been recognized as a promising solution to energize ultra-low power devices, but the operation range is quite short (within few meters) and the end-to-end power efficiency is usually low (less than few percents).
-		In such case, idle RIScatter nodes can operate in full RIS mode and redirect local RF waves to those in transmitting mode for higher energy efficiency and backscatter SNR.
-		Spectrum sharing with legacy wireless systems is another challenge, as backscatter devices manipulate existing radio signals to transmit data.
-		This raises concerns about potential interference with other wireless applications operating in the same spectrum, and calls for a rethinking of waveform design, receiver architecture, modulation and coding scheme, and multiple access strategy to ensure a symbiotic coexistence.
-		Finally, security issue is a major concern for batteryless devices since they are vulnerable to eavesdropping, jamming, and spoofing attacks.
-		Please refer to \ref{cm:1.1}
+	\comment{
+		The contribution of Sec. \ref{sc:framework} is unclear for the following two reasons.
+		\begin{enumerate}
+			\item The manuscript claims to propose a universal optimization framework for \gls{bd}-\gls{ris} as in \eqref{op:general}.
+However, the framework in \eqref{op:general} is indeed not sufficiently general.
+It does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality) besides the orthogonal conditions \eqref{cn:general_unitary}.
+The reviewer notice that a more general framework, which considers \gls{bd}-\gls{ris} constraints in addition to \eqref{cn:general_unitary}, has already been investigated and solved in the authors' previous work \cite{Zhou2023}.
+			\item Besides, both the non-geodesic \gls{rcg} (Sec.
+\ref{sc:rcg_general}) and geodesic \gls{rcg} (Sec.
+\ref{sc:rcg_geodesic}) algorithms, e.g., \eqref{eq:geodesic_iden}--\eqref{eq:iterate_mul}, are well established methods in the literature, e.g., \cite{Abrudan2008}.
+Therefore, the novelty of Sec.
+\ref{sc:framework} unclear.
+		\end{enumerate}
 	}
 
-	\comment{What was the main criticism you have received during the review process and how did you address it?}
-	\reply{
-		The main technical criticism we received during the review process was the uncompleteness of simulation results.
-		Reviewers were interested in the impact of imperfect CSI and primary/backscatter SNR on the achievable rate region.
-		Those results evaluate the practicality of RIScatter systems and have been added to the revised manuscript.
-		One reviewer also suggested including analytical and numerical results on BER vs SNR.
-		While we fully acknowledge its importance, the BER analysis is non-trivial due to the coexistence of both links, and we would like to reserve this for a future work.
-		Another interesting question was the optimal primary input distribution that maximizes the weighted sum mutual information.
-		It deserves further research but we decided to stay with CSCG primary source for a tractable rate expression.
-		Two reviewers also pointed out that perfect symbol-level synchronization of both links is a strong assumption, especially for large-scale RIScatter system with small spreading ratio.
-		If necessary, some penalty factor can be introduced to the rate expression to compensate for the synchronization error.
-		Please refer to \ref{cm:1.2}
+	\comment{
+		In Sec.
+\ref{sc:pareto}, the manuscript proposes to maximize weighted sum of singular values of the effective channel $\mathbf{H}$.
+The optimization objective is rather vague.
+Is the weighted sum of singular values related to any meaningful performance metric (e.g., capacity, power gain, and so on)?
 	}
+
+	\comment{
+		Derivation in the proof of Lemma \ref{lm:pareto} (Appendix \ref{ap:pareto}) is incorrect.
+Specifically, $(\partial \mathbf{u}^\mathsf{T}) \cdot \mathbf{u}$ is not equal to $\partial (\mathbf{u}^T \mathbf{u})$.
+Similar error occurs to $\mathbf{v}$.
+Please note that the derivative of singular value of a matrix with respect to the matrix itself does not exist.
+In fact, sub-differential should be used instead, e.g., \cite{Cai2010}.
+	}
+
+	\comment{
+		The rank equation in the proof of Prop.
+\ref{pp:dof} (Appendix \ref{ap:dof}) seems confusing.
+The rank of product of two matrices is: $\rank(\mathbf{AB}) = \rank(\mathbf{B}) - \dim(\ker(\mathbf{A}) \cap \ran(\mathbf{B}))$.
+How could one obtain the rank equation in Appendix \ref{ap:dof}?
+Please clarify.
+	}
+
+	\comment{
+		In Sec.
+\ref{sc:bounds}, the manuscript provides a number of bounds on singular values of the effective channel $\mathbf{H}$.
+However, the usefulness of these bounds is unclear.
+What can these bounds be used for?
+Note the results Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are quite standard results from matrix textbook.
+The (upper) bound in Corollary \ref{co:nd_power}, which is achieved by aligning its left and right singular-value vectors to that of the forward and backward channels, respectively, is reminiscent of the results in seminal papers on relay beamforming design, e.g., \cite{Rong2009,Rong2009a}.
+	}
+
+	\comment{
+		The optimization problems \eqref{op:power} and \eqref{op:rate_ris} lacks of novelty.
+In fact, they can still be solved by the methods proposed in existing literature, e.g., \cite{Santamaria2023,Li2023b} through appropriate adjustment.
+	}
+
+	\comment{
+		Convergence proof in Appendix \ref{ap:power} is questionable.
+First, the manuscript just assumes that solution iterates $\tilde{\mathbf{\Theta}}$ converge.
+This may not be true (solution iterate could oscillate actually) and is hard to prove.
+Second, stationary point for constrained problem is more complicated than for the non-constrained case (e.g.
+gradient equals zero).
+Please refer to \cite{Pang2017}.
+	}
+\end{reviewer}
+
+\begin{reviewer}
+	\summary{
+	This paper studies the potential of a group-connected \gls{bd}-\gls{ris} to manipulate the \gls{mimo} channel in terms of singular values, power gain, and achievable rate.
+The analysis and optimization are based on the assumption of asymmetric and lossless \gls{ris} circuit network without mutual coupling.
+A geodesic design framework is proposed and tested on Pareto frontier shaping and joint beamforming problems.
+Some analytical bounds on channel singular values and power gain are also provided.
+Overall, it is a solid work with interesting results.
+I have some further comments for the authors' reference.
+	}
+
+	\comment{
+		How practical is it to consider asymmetric reconfigurable \gls{bd}-\gls{ris}? How much gain is expected over symmetric ones and at what cost?
+	}
+
+	\comment{
+		The geodesic \gls{rcg} method seems promising especially at large group size $L$.
+Is it possible to extend the design framework to advanced \gls{bd}-\gls{ris} architectures (e.g., multi-sector mode)?
+	}
+
+	\comment{
+		For fully-connected \gls{bd}-\gls{ris}, the authors mentioned in the result section that power gain-optimal scattering matrix is also rate-optimal. Can you provide a proof on this point?
+	}
+
+	\comment{
+		The authors refer to \cite{Li2024} for estimating forward and backward channels individually.
+However, it can be challenging to implement those in real time without RF chains at the \gls{ris}.
+The impact of imperfect \gls{csi} on the achievable rates may also be studied.
+	}
+
+	\comment{
+		Some sentences are confusing to me and the presentation can be improved.
+For example, ``a group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold''.
+Please elaborate more on this.
+	}
+\end{reviewer}
+
+\begin{reviewer}
+	\summary{
+		This paper analyzes the channel shaping of a \gls{p2p} \gls{mimo} system, assisted by passive diagonal and/or non-diagonal \glspl{ris} to enhance power and rate gains.
+Overall, the topic is timely and interesting.
+Using \gls{ao}, a local optimal solution of the rate maximization for the \gls{bd}-\gls{ris}-assisted \gls{mimo} \gls{p2p} system is obtained.
+It is shown that \gls{bd}-\gls{ris} improve the achievable rate.
+To the best of my knowledge, the analysis is solid.
+However, there are some suggestions for improving the paper further.
+	}
+
+	\comment{
+		The results for the \gls{p2p} system are insightful.
+However, a \gls{p2p} system is not typically considered a practical system.
+It is challenging to extend the results to a system with interfering signals, where the goal is not only to enhance the channel gain of the desired links but also simultaneously to reduce the channel gain of the interfering links.
+It is more interesting to investigate the rate region of $K$-user \glspl{ic}.
+It is expected that the authors provide an analysis of the (max-min and sum) rate maximization of multi-user \gls{mimo} systems, assisted by \gls{bd}-\glspl{ris}.
+	}
+
+	\comment{
+		\gls{bd}-\glspl{ris} provide a greater number of optimization variables but at the expense of increased computational and implementation complexities.
+While the computational complexities of the proposed solutions are discussed in the paper, a comparison with \gls{d}-\gls{ris} is missing, which should be explicitly addressed in both the introduction and the main body.
+Additionally, the implementation complexities of \gls{bd}-\glspl{ris}, particularly in comparison to \gls{d}-\gls{ris}, necessitate a more comprehensive analysis.
+For instance, as highlighted in \cite{Soleymani2024b}, the energy efficiency of a \gls{bd}-\gls{ris} is significantly influenced by the static power consumption of its circuit elements.
+If the implementation cost of a \gls{bd}-\gls{ris} is substantial, its performance advantages could be considerably reduced.
+	}
+
+	\comment{
+		The authors considered a passive \gls{ris} architecture.
+However, another passive configuration, termed \gls{gp}, is discussed in \cite{Fotock2023,Soleymani2024a}.
+Employing \gls{ao}, the resulting optimization problem to update $\mathbf{\Theta}$ is convex.
+Comparing the proposed solutions with a globally passive \gls{bd}-\gls{ris} would provide valuable insights into the performance gains obtained by relaxing the (locally) passive assumption.
+Hence, it is highly recommended to add the \gls{gp} (both \gls{bd} and diagonal) architecture as a benchmark in the numerical results.
+	}
+
+% 3) The authors considered a passive RIS architecture.
+However, another passive configuration, termed globally passive (GP), is discussed in [b], [c].
+Employing AO, the resulting optimization problem to update $\Theta$ is convex.
+Comparing the proposed solutions with a globally passive BD-RIS would provide valuable insights into the performance gains obtained by relaxing the (locally) passive assumption.
+Hence, it is highly recommended to add the GP (both BD and diagonal) architecture as a benchmark in the numerical results.
 

### 2024-12-13 manuscript/main.tex
:construction: Updating structure

@@
+\documentclass[journal]{IEEEtran}
+
 \input{preamble}
 
-\title{Channel Shaping Using Beyond Diagonal RIS:\\Analysis, Optimization, and Enhanced Flexibility}
+% TODO compact or standard SVD
+
+% \title{Channel Shaping Using Beyond Diagonal RIS:\\Analysis, Optimization, and Enhanced Flexibility}
+% \title{MIMO Channel Shaping and Rate Maximization via Beyond Diagonal RIS}
+\title{Beyond Diagonal RIS: MIMO Channel Shaping and Rate Maximization}
+% \title{MIMO Channel Shaping Using Beyond Diagonal RIS: Singular Value Redistribution and Rate Maximization}
 \author{
@@
 	$\sv(\cdot)$ extracts the singular values of a matrix as a non-ascending vector.
-	$\card(\cdot)$ returns the cardinality of a set.
+	% $\card(\cdot)$ returns the cardinality of a set.
+	$\conv(\cdot)$ returns the convex hull of arguments.
 	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
@@
 
-	\begin{section}{BD-RIS Model}
+	\begin{section}{System Model}
 	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
@@
 	\begin{equation}
+		\label{eq:channel}
 		% \mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \underbrace{\mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}}_{\triangleq \mathbf{H}_g} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
 		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \triangleq \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
-		\label{eq:channel_equivalent}
 	\end{equation}
@@
 	where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary factor matrices.
-	Let $\mathbf{H}_{\mathrm{B},g} = \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \mathbf{V}_{\mathrm{B},g}^\mathsf{H}$ and $\mathbf{H}_{\mathrm{F},g} = \mathbf{U}_{\mathrm{F},g} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}$ be the compact \gls{svd} of the backward and forward channels, respectively.
+	Let $\mathbf{H}_{\mathrm{B},g} = \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \mathbf{V}_{\mathrm{B},g}^\mathsf{H}$ and $\mathbf{H}_{\mathrm{F},g} = \mathbf{U}_{\mathrm{F},g} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
 	The equivalent channel can thus be rewritten as
 	\begin{equation}
+		\label{eq:channel_svd}
 		\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
-		\label{eq:channel_equivalent_svd}
 	\end{equation}
@@
 	% \begin{remark}
-	We observe from \eqref{eq:channel_equivalent_svd} that the \gls{bd}-\gls{ris} plays a crucial role in combining
+	We observe from \eqref{eq:channel_svd} that the \gls{bd}-\gls{ris} plays a crucial role in combining
 	% needs to strike a balance between
@@
 	These two attributes are refined below and discussed in an example.
-	% We conclude from \eqref{eq:channel_equivalent_svd} that the scattering matrix of \gls{bd}-\gls{ris} provide two channel shaping potentials:
-	% By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
+	% We conclude from \eqref{eq:channel_svd} that the scattering matrix of \gls{bd}-\gls{ris} provide two channel shaping potentials:
+	% By analyzing \eqref{eq:channel_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
 	% Channel rearrangement refers to rearrange and recombine the forward and backward channel branches by their strength.
@@
 			% for perfect phase matching in \gls{siso}.
-			% When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a scalar phase shift to the corresponding indirect channel matrix of size $N_\mathrm{R} \times N_\mathrm{T}$ defined in \eqref{eq:channel_equivalent}.
+			% When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a scalar phase shift to the corresponding indirect channel matrix of size $N_\mathrm{R} \times N_\mathrm{T}$ defined in \eqref{eq:channel}.
 			% We thus conclude that the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.
@@
 
-	\begin{example}[\gls{siso} channel gain maximization]\label{eg:siso_gain}
+	\begin{example}[\gls{siso} channel gain maximization]
+		\label{eg:siso}
 		Denote the direct, backward, forward channels as $h_\mathrm{D}$, $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$, and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, respectively.
@@
 			\mathbf{\Theta}_g^\textnormal{\gls{siso}} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H}, \quad \forall g,
-			\label{eq:scattering_siso}
 		\end{equation}
@@
 			\max_\mathbf{\Theta} \ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
-			\label{eq:gain_siso}
 		\end{equation}
@@
 
-	Example~\ref{eg:siso_gain} clarifies the difference between branch matching and mode alignment and show their impacts on channel shaping.
+	Example~\ref{eg:siso} clarifies the difference between branch matching and mode alignment and show their impacts on channel shaping.
 	When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching is more pronounced since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$.
@@
 	% \begin{remark}
-	% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:direct_negligible}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-	% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+	% 	From \eqref{eq:ris_decompose} and \eqref{eq:channel_nd} in the proof of Proposition \ref{pp:nd}, we notice that \eqref{iq:horn}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+	% 	% Interestingly, \eqref{iq:horn}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
 	% 	\begin{equation}
@@
 	% 	\begin{itemize}
-	% 		\item space alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-	% 		\item channel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the channels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
+	% 		\item space alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:ris_decompose} fully align the spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
+	% 		\item channel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_nd} pairs the channels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
 	% 	\end{itemize}
@@
 
-	\begin{section}{Analytical Bounds on Singular Value Shaping}
-	\label{sc:singular_value}
+	\begin{section}{Analytical Shaping Bounds}
+		\label{sc:bounds}
 	In this section, we first provide an example demonstrating the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds related to channel singular values under specific channel conditions.
@@
 
-	\begin{example}[$2 \times 2 \times 2$ shaping]\label{eg:d_vs_bd}
+	\begin{example}[$2 \times 2 \times 2$ shaping]
+		\label{eg:shaping_potential}
 		% We showcase the channel shaping capabilities of different \gls{ris} models by a toy example.
@@
 			\end{bmatrix},
-			% \label{eq:unitary_ris}
 		\end{equation*}
@@
 				Their maximum and minimum are marked explicitly on the plot.}
-			\label{fg:singular_trend}
+			\label{fg:shaping_potential}
 		\end{figure}
-		With an exhaustive grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$, Fig.~\ref{fg:singular_trend} shows the achievable singular values of a specific channel realization
+		With an exhaustive grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$, Fig.~\ref{fg:shaping_potential} shows the achievable singular values of a specific channel realization
 		\begin{equation*}
@@
 
-	% Example~\ref{eg:d_vs_bd} shows that physically grouping some scattering elements produces a ``cooperation effect'' that significantly enhances the dynamic range of channel singular values.
-	Example~\ref{eg:d_vs_bd} highlights that the physical grouping of \gls{ris} elements, even if using symmetric components, can produce a much wider dynamic range of channel singular values.
+	% Example~\ref{eg:shaping_potential} shows that physically grouping some scattering elements produces a ``cooperation effect'' that significantly enhances the dynamic range of channel singular values.
+	Example~\ref{eg:shaping_potential} highlights that the physical grouping of \gls{ris} elements, even if using symmetric components, can produce a much wider dynamic range of channel singular values.
 	This motivates analytical and numerical studies on singular value shaping using \gls{bd}-\gls{ris}.
-	A selection of analytical bounds are presented in Propositions~\ref{pp:dof} -- \ref{pp:direct_negligible} and the resulting corollaries.
+	A selection of analytical bounds are presented in Propositions~\ref{pp:dof} -- \ref{pp:nd} and the resulting corollaries.
 	% The remainder of this section is organized as follows.
@@
 
-	\begin{proposition}[Degrees of freedom]\label{pp:dof}
-		In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
+	% \begin{proposition}[Degrees of freedom]
+	% 	\label{pp:dof}
+	% 	In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
+	% \end{proposition}
+
+	\begin{proposition}[Degrees of freedom]
+		\label{pp:dof}
+		In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{dof} than \gls{d}-\gls{ris}.
 	\end{proposition}
@@
 
-	\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
+	\begin{proposition}[Rank-deficient channel]
+		\label{pp:rd}
 		% If the forward or backward channel is rank-$k$ ($k \le N$),
@@
 		\begin{subequations}
+			\label{iq:sv_rd}
 			\begin{align}
-				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_bound_enlarge}          \\
-				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
+				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_rd_max}          \\
+				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_rd_min}
 			\end{align}
-			\label{iq:sv_bound_rank_deficient}
 		\end{subequations}
@@
 		\begin{equation}
+			\label{eq:auxiliary_rd}
 			\mathbf{T} \mathbf{T}^\mathsf{H} =
@@
 			\end{cases}
-			\label{eq:auxiliary_matrix}
-		\end{equation}
-		and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
+		\end{equation}
+		and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are any right and left singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
 	\end{proposition}
@@
 
-	Inequality \eqref{iq:sv_bound_enlarge} states that
+	Inequality \eqref{iq:sv_rd_max} states that
 	if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are at least rank $k$, then
@@
 
-	% We would like to give some insights into Proposition \ref{pp:rank_deficient}.
-
-	% \begin{corollary}[Extreme singular values\label{co:extreme}]
-	% 	If the minimum rank of forward and backward channels is $k$ ($k \le N$), then with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
-This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
-	% \end{corollary}
-
-	% \begin{proof}
-	% 	This is a direct result of \eqref{iq:sv_bound_rank_deficient}.
-	% \end{proof}
-
-	\begin{corollary}[\gls{los} channel\label{co:los}]
+	\begin{corollary}[\gls{los} channel]
+		\label{co:los}
 		% If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
@@
 		\begin{equation}
+			\label{iq:sv_los}
 			\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
-			\label{iq:sv_bound_los}
 		\end{equation}
@@
 	\begin{proof}
-		This is a direct result of \eqref{iq:sv_bound_rank_deficient} with $k = 1$.
+		This is a direct result of \eqref{iq:sv_rd} with $k = 1$.
 	\end{proof}
@@
 	We emphasize that
-	% the inequalities in \eqref{iq:sv_bound_rank_deficient} and \eqref{iq:sv_bound_los}
-	Proposition \ref{pp:rank_deficient} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
-	Out of $2N$ bounds in \eqref{iq:sv_bound_rank_deficient} or \eqref{iq:sv_bound_los}, $N$ of them
-	% The equalities in \eqref{iq:sv_bound_rank_deficient} and \eqref{iq:sv_bound_los}
+	% the inequalities in \eqref{iq:sv_rd} and \eqref{iq:sv_los}
+	Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
+	Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them
+	% The equalities in \eqref{iq:sv_rd} and \eqref{iq:sv_los}
 	can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible\footnote{Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
-This can result from a very large number of \gls{ris} elements (as discussed in Proposition~\ref{pp:rank_deficient}) or physical obstacles in the propagation path (as discussed in Proposition~\ref{pp:direct_negligible}).}.
+This can result from a very large number of \gls{ris} elements (as discussed in Proposition~\ref{pp:rd}) or physical obstacles in the propagation path (as discussed in Proposition~\ref{pp:nd}).}.
 	For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes, and we will later show by simulation that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
-	Proposition \ref{pp:rank_deficient} provides a reference on the selection of $N_\mathrm{S}$ in low-multipath application scenarios.
-	% Proposition \ref{pp:rank_deficient} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a benchmark for $N_\mathrm{S}$ selection in low-multipath deployment scenarios.
+	Proposition \ref{pp:rd} provides a reference on the selection of $N_\mathrm{S}$ in low-multipath application scenarios.
+	% Proposition \ref{pp:rd} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a benchmark for $N_\mathrm{S}$ selection in low-multipath deployment scenarios.
 	Next, we shift the focus to another popular \gls{ris} deployment scenario where the direct channel is blocked.
@@
 
-	\begin{proposition}[Negligible direct channel]\label{pp:direct_negligible}
+	\begin{proposition}[Negligible direct channel]
+		\label{pp:nd}
 		% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
@@
 			\sv(\mathbf{H}) = \sv(\mathbf{BF}),
-			\label{eq:sv_fully_connected}
 		\end{equation}
@@
 	\begin{proof}
-		Please refer to Appendix~\ref{ap:direct_negligible}.
+		Please refer to Appendix~\ref{ap:nd}.
 	\end{proof}
 
-	Proposition \ref{pp:direct_negligible} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
+	Proposition \ref{pp:nd} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
 	It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
 	Its importance lies in the fact that the initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
-	The question is partially answered in Corollaries \ref{co:sv_bound_horn} -- \ref{co:sv_nth} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
+	The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
 	% define\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [\bar{N}] \setminus [N]$.
@@
 
-	\begin{corollary}[Product of subset of singular values\label{co:sv_bound_horn}]
+	\begin{corollary}[Product of subset of singular values]
+		\label{co:nd_sv_prod_subset}
 		If the direct channel is negligible,
@@
 		\begin{equation}
+			\label{iq:horn}
 			\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
-			\label{iq:sv_bound_fc}
 		\end{equation}
@@
 
-	\eqref{iq:sv_bound_fc}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:direct_negligible}.
+	\eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:nd}.
 	% It is worth mentioning that t
@@
 	The number of admissible triples increases exponentially with $N_\mathrm{S}$ despite some resulting bounds can be redundant.
-	Apart from the upper bounds, we will shortly see \eqref{iq:sv_bound_fc} can also induce lower bounds on channel singular values.
+	Apart from the upper bounds, we will shortly see \eqref{iq:horn} can also induce lower bounds on channel singular values.
 	% It also helps to induce lower (instead of upper) bounds on channel singular values.
-	% ! For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.
-	% Besides, \eqref{iq:sv_bound_fc} helps to induce lower bounds
+	% ! For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.
+	% Besides, \eqref{iq:horn} helps to induce lower bounds
 	Those facts render the analysis of shaping limit non-trivial for massive \gls{ris}-aided \gls{mimo} systems.
@@
 
-	\begin{corollary}[Product of some largest or smallest singular values\label{co:sv_product}]
+	\begin{corollary}[Product of some largest or smallest singular values]
+		\label{co:nd_sv_prod_tail}
 		% \footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $N \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
@@
 			\begin{align}
-				\prod_{n=1}^k \sigma_n(\mathbf{H})                   & \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:sv_product_largest}                    \\
+				\prod_{n=1}^k \sigma_n(\mathbf{H})                   & \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:sv_nd_prod_largest}                    \\
 				\prod_{n=\bar{N}}^{\mathclap{\bar{N}-k+1}} \sigma_n(\mathbf{H}) & \ge \prod_{n=\bar{N}}^{\mathclap{\bar{N}-k+1}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}).
-\label{iq:sv_product_smallest}
+\label{iq:sv_nd_prod_smallest}
 			\end{align}
@@
 	\begin{proof}
-		Please refer to Appendix~\ref{ap:sv_product}.
+		Please refer to Appendix~\ref{ap:nd_sv_prod_tail}.
 	\end{proof}
@@
 
-	\begin{corollary}[Individual singular value\label{co:sv_nth}]
+	\begin{corollary}[Individual singular value]
+		\label{co:nd_sv_indl}
 		If the direct channel is negligible,
@@
 		\begin{equation}
+			\label{iq:sv_nd_indl}
 			\max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
-			\label{iq:sv_nth}
 		\end{equation}
@@
 		\begin{subequations}
-			\label{eq:sv_nth}
+			\label{eq:ris_nd_sv_indl}
 			\begin{align}
-				\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_max} \\
-				\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:sv_nth_min}
+				\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_sv_indl_max} \\
+				\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_sv_indl_min}
 			\end{align}
 		\end{subequations}
-		where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are the right and left singular matrices\footnote{We highlight the non-uniqueness of $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$.
+		where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices\footnote{
+			\label{fn:svd_non_uniqueness}
+			We highlight the non-uniqueness of $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$.
 When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace.
@@
 			\item The $(i, j)$-th entry is $1$, where
-				% \begin{equation*}
-				% 	(i, j) =
-				% 	\begin{cases}
-				% 		\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{P}, \\
-				% 		\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{Q},
-				% 	\end{cases}
-				% \end{equation*}
 				\begin{subnumcases}{(i, j) =}
-					\ \underset{\mathclap{i+j=n+1}}{\arg\min} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:sv_nth_max_pair} \\
-					\ \underset{\mathclap{i+j=n+N_\mathrm{S}}}{\arg\max} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:sv_nth_min_pair}
+					\ \underset{\mathclap{i+j=n+1}}{\arg\min} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:idx_nd_sv_indl_max} \\
+					\ \underset{\mathclap{i+j=n+N_\mathrm{S}}}{\arg\max} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:idx_nd_sv_indl_min}
 				\end{subnumcases}
-				% \begin{equation*}
-				% 	(i, j) =
-				% 	\begin{cases}
-				% 		\underset{i+j=n+1}{\arg\min} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{P}, \\
-				% 		\underset{i+j=n+N_\mathrm{S}}{\arg\max} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{for } \mathbf{Q},
-				% 	\end{cases}
-				% \end{equation*}
 				and ties may be broken arbitrarily;
-				% with ties broken arbitrarily;
-				% and the tie-breaking rule is arbitrary.
 			\item After deleting the $i$-th row and $j$-th column, the resulting submatrix $\mathbf{Y}$ is arbitrary permutation matrix of dimension $N_\mathrm{S}-1$ satisfying
-				% \begin{subequations}
-				% 	\begin{alignat}{1}
-				% 		\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\ge} \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{P}, \hspace{-0.17cm} \label{eq:sv_nth_max_condition} \\
-				% 		\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) {\le} \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & \text{ for } \mathbf{Q}, \hspace{-0.17cm} \label{eq:sv_nth_min_condition}
-				% 	\end{alignat}
-				% \end{subequations}
-
 				\begin{subequations}
 					\begin{alignat}{2}
-						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \ \ \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})            &  & \text{ for } \mathbf{P}, \label{eq:sv_nth_max_condition} \\
-						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \ \ \max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) &  & \text{ for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
+						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \ \ \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})            &  & \text{ for } \mathbf{P}, \label{eq:perm_nd_sv_indl_max} \\
+						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \ \ \max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) &  & \text{ for } \mathbf{Q}, \label{eq:perm_nd_sv_indl_min}
 					\end{alignat}
 				\end{subequations}
-				% \begin{subequations}
-				% 	\begin{align}
-				% 		\sigma_{n-1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \ge \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{P}, \label{eq:sv_nth_max_condition} \MoveEqLeft[1] \\
-				% 		\sigma_{n+1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & \le \max_{i+j=n+N_\mathrm{S}} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \text{for } \mathbf{Q}, \label{eq:sv_nth_min_condition}
-				% 	\end{align}
-				% \end{subequations}
 				where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with both $i$-th row and $j$-th column deleted, respectively.
@@
 	\begin{proof}
-		Please refer to Appendix~\ref{ap:sv_nth}.
+		Please refer to Appendix~\ref{ap:nd_sv_indl}.
 	\end{proof}
 
-	% Although Corollary \ref{co:sv_nth} and Proposition \ref{pp:direct_negligible}
+	% Although Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:nd}
 	% are derived under the assumption of negligible direct channel and fully-connected \gls{bd}-\gls{ris}, they are still useful for practical scenarios.
-	Corollary \ref{co:sv_nth} and Proposition \ref{pp:rank_deficient} both reveal the shaping limits of individual channel singular values.
+	Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of individual channel singular values.
 	They are derived under different assumptions are not special cases of each other.
-	Importantly, Corollary \ref{co:sv_nth} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
-first and last few in Proposition \ref{pp:rank_deficient}), applies to fully-connected \gls{bd}-\gls{ris} of arbitrary size, and provides a general solution structure.
-	We emphasize that in \eqref{eq:sv_nth} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of unitary $\mathbf{X}$ defined in \eqref{eq:scattering_fc}.
+	Importantly, Corollary \ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
+first and last few in Proposition \ref{pp:rd}), applies to fully-connected \gls{bd}-\gls{ris} of arbitrary size, and provides a general solution structure.
+	We emphasize that in \eqref{eq:ris_nd_sv_indl} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of unitary $\mathbf{X}$ defined in \eqref{eq:ris_decompose}.
 	Specially, the extreme channel singular values can be manipulated up to
 	\begin{subequations}
-		\label{iq:sv_extreme}
+		\label{iq:sv_nd_extreme}
 		\begin{gather}
-			\max_{\mathclap{i+j=N_\mathrm{S}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_largest} \\
+			\max_{\mathclap{i+j=N_\mathrm{S}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_nd_largest} \\
 			\min_{\mathclap{i+j=\bar{N}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\ge} \sigma_{\bar{N}}(\mathbf{H}) {\ge} \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}).
-\label{iq:sv_smallest}
+\label{iq:sv_nd_smallest}
 		\end{gather}
@@
 	% where the arguments of $\max$ and $\min$ coincide at $\bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}}(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-1}(\mathbf{H}_\mathrm{F}), \ldots, \sigma_{N_\mathrm{S}}(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}$.
-	We notice that the right halves in \eqref{iq:sv_largest} and \eqref{iq:sv_smallest} are special cases of \eqref{iq:sv_product_largest} and \eqref{iq:sv_product_smallest} when $k=1$.
-
-	\begin{example}[Bounds on $3 \times 3 \times 3$ shaping]\label{eg:bounds}
+	We notice that the right halves in \eqref{iq:sv_nd_largest} and \eqref{iq:sv_nd_smallest} are special cases of \eqref{iq:sv_nd_prod_largest} and \eqref{iq:sv_nd_prod_smallest} when $k=1$.
+
+	\begin{example}[Bounds on $3 \times 3 \times 3$ shaping]
+		\label{eg:shaping_bounds}
 		Consider a $3 \times 3 \times 3$ setup with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} = \diag(3, 2, 1)$, and $\mathbf{H}_\mathrm{F} = \diag(4, 0, 5)$.
@@
 			\item \gls{d}-\gls{ris}: It is evident that any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode alignment capability.
-			\item \gls{bd}-\gls{ris}: According to \eqref{iq:sv_nth}, a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
+			\item \gls{bd}-\gls{ris}: According to \eqref{iq:sv_nd_indl}, a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
 				% \begin{align*}
@@
 				which is consistent with Proposition \ref{pp:dof} that \gls{bd}-\gls{ris} cannot achieve a larger \gls{dof} than \gls{d}-\gls{ris}.
-				To attain the upper and lower bounds, $(i,j)$ in \eqref{eq:sv_nth_max} and \eqref{eq:sv_nth_min} takes $(1, 1)$ and $(2, 2)$ when $n=1$, and $(2, 1)$ and $(3, 2)$ when $n=2$, respectively.
+				To attain the upper and lower bounds, $(i,j)$ in \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} takes $(1, 1)$ and $(2, 2)$ when $n=1$, and $(2, 1)$ and $(3, 2)$ when $n=2$, respectively.
 				% for the upper and lower bounds of $\sigma_1(\mathbf{H})$, respectively.
@@
 		% Evidently, any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode ordering capability.
-		% On the other hand, Corollary \ref{co:sv_bound_horn} suggests that a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
+		% On the other hand, Corollary \ref{co:nd_sv_prod_subset} suggests that a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
 
@@
 
-	We conclude from Example \ref{eg:bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+	We conclude from Example \ref{eg:shaping_bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
 	% performing right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, which properly aligns and orders their modes.
@@
 	% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-	However, when the problem of interest is a function of multiple singular values, their individual bounds \eqref{iq:sv_nth} may not be simultaneously tight.
+	However, when the problem of interest is a function of multiple singular values, their individual bounds \eqref{iq:sv_nd_indl} may not be simultaneously tight.
 	Two case studies are presented below.
 
-	\begin{corollary}[Channel power gain\label{co:sum_power}]
+	\begin{corollary}[Channel power gain]
+		\label{co:nd_power}
 		If the direct channel is negligible, then the channel power gain is bounded from above (resp.
@@
 		\begin{equation}
+			\label{iq:power_nd}
 			\sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
-			\label{iq:power_gain}
 		\end{equation}
 		whose\footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
-This is a looser version of \eqref{iq:power_gain} and cannot take equalities unless the extreme singular values are of multiplicity $N$.} upper and lower bounds are attained respectively at
+This is a looser version of \eqref{iq:power_nd} and cannot take equalities unless the extreme singular values are of multiplicity $N$.} upper and lower bounds are attained respectively at
 		\begin{subequations}
 			\begin{align}
-				\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:power_max}            \\
-				\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H} \label{eq:power_min},
+				\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_power_max}            \\
+				\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H} \label{eq:ris_nd_power_min},
 			\end{align}
@@
 	\begin{proof}
-		Please refer to Appendix~\ref{ap:sum_power}.
+		Please refer to Appendix~\ref{ap:nd_power}.
 	\end{proof}
 
-	We notice that \eqref{eq:power_max} and \eqref{eq:power_min} are special cases of \eqref{eq:sv_nth_max} and \eqref{eq:sv_nth_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_extreme}, respectively.
+	We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
 	As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the expectation of maximum channel power gain can be numerically evaluated as
 	\begin{equation}
+		\label{eq:power_nd_rayleigh}
 		\begin{split}
@@
 		\end{split}
-		\label{eq:power_gain_rayleigh}
 	\end{equation}
 	where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(\cdot)$ given by \cite[(51)]{Zanella2009}.
-	We note that \eqref{eq:power_gain_rayleigh} generalizes the \gls{siso} power gain attainable by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} under double Rayleigh fading.
-
-	\begin{corollary}[Channel capacity at very low and high \gls{snr}\label{co:capacity}]
+	We note that \eqref{eq:power_nd_rayleigh} generalizes the \gls{siso} power gain attainable by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} under double Rayleigh fading.
+
+	\begin{corollary}[Channel capacity at very low and high \gls{snr}]
+		\label{co:nd_capacity}
 		If the direct channel is negligible, then the channel capacity at very low and high \gls{snr} are approximately bounded from above by
@@
 			\begin{align}
-				C_{\rho_\downarrow} & \lessapprox \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \label{iq:capacity_snr_low}                                           \\
-				C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:capacity_snr_high}
+				C_{\rho_\downarrow} & \lessapprox \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \label{iq:capacity_nd_snr_low}                                           \\
+				C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:capacity_nd_snr_high}
 			\end{align}
@@
 		where $\rho$ is the \gls{snr} and the unit is nats/s/Hz.
-		Their upper bounds can be attained by, for example, \eqref{eq:power_max}.
+		Their upper bounds can be attained by, for example, \eqref{eq:ris_nd_power_max}.
 	\end{corollary}
@@
 	\begin{proof}
-		Please refer to Appendix~\ref{ap:capacity}.
+		Please refer to Appendix~\ref{ap:nd_capacity}.
 	\end{proof}
 
-	Similar to \eqref{eq:power_gain_rayleigh}, the ergodic counterparts of \eqref{iq:capacity_snr_low} and \eqref{iq:capacity_snr_high} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be numerically evaluated as
+	Similar to \eqref{eq:power_nd_rayleigh}, the ergodic counterparts of \eqref{iq:capacity_nd_snr_low} and \eqref{iq:capacity_nd_snr_high} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be numerically evaluated as
 	\begin{subequations}
@@
 
-	Proposition \ref{pp:dof} -- \ref{pp:direct_negligible} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
+	Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
 	Extending the analysis to more general cases (e.g., non-negligible direct channel and arbitrary \gls{bd}-\gls{ris} group size) is non-trivial due to limited branch matching and mode alignment capabilities therein.
@@
 	% ose results to the case of direct channel is non-trivial since the singular vector spaces of direct-indirect channels and backward-forward channels cannot be aligned at the same time.
-	To provide a complete channel shaping solution, we invoke optimization approaches and tackle some relevant problems in the next section.
-
-	% from a singular value perspective (discussed in Section~\ref{sc:pareto_frontier}) or a power gain perspective (to be discussed in Section~\ref{sc:power}).
-	% numerical and analytical studies on singular value redistribution by \gls{bd}-\gls{ris} in Sections~\ref{sc:pareto_frontier} and \ref{sc:bounds}, respectively.
-	% further studies on channel shaping.
-
-	% Interestingly, connecting two scattering elements via a symmetric component can provide a much larger dynamic range of channel singular values.
-	% singular value manipulation range than using two independent elements.
-	% that such a large difference comes from connecting both scattering elements using a symmetric component.
-	% , where the former needs 2 reconfigurable impedance and the latter needs 3.
-	% It is interesting that the huge difference comes purely from connecting both elements.
-	% Such a large gain comes from simply connecting both elements
-	% , and it can be even larger using an asymmetric component.
-	% an even larger gain is expected when an asymmetric reconfigurable component is available.
-	% An even larger gain is expected when an asymmetric reconfigurable component is available.
-	% and a larger gain is expected when an asymmetric connection is available.
-	% This example shows that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
-	% \begin{subsection}{Toy Example}\label{sc:toy_example}
-	% 	We showcase the channel shaping capabilities of different \gls{ris} models by a toy example.
-	% 	Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-	% 	The \gls{d}-\gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} can be modeled by 4 independent angular parameters
-	% 	\begin{equation}
-	% 		\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
-	% 			e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
-	% 			-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
-	% 		\end{bmatrix}.
-	% 		\label{eq:unitary_ris}
-	% 	\end{equation}
-	% 	It is worth noting that $\phi$ has no impact on the singular value because $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
-	% 	To simplify the analysis, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of variables in the scattering matrix.
-	% 	\begin{figure}
-	% 		\centering
-	% 		\includegraphics[width=\columnwidth]{../assets/simulation/singular_trend.eps}
-	% 		\caption{$2 \times 2 \times 2$ channel singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is blocked.
-$\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
-	% 		Their maximum and minimum have been marked explicitly on the plot.}
-	% 		\label{fg:singular_trend}
-	% 	\end{figure}
-	% 	Fig.~\ref{fg:singular_trend} compares the achievable singular values of one typical channel realization, where the backward and forward channels are given by
-	% 	\begin{equation*}
-	% 		\begin{split}
-	% 			\mathbf{H}_\mathrm{B} & =
-	% 			\begin{bmatrix}
-	% 				-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
-	% 				0.4131 + 0.2651 \jmath & -0.1960 + 0.4650 \jmath
-	% 			\end{bmatrix},
-	% 			\\
-	% 			\mathbf{H}_\mathrm{F} & =
-	% 			\begin{bmatrix}
-	% 				-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
-	% 				0.0196 + 0.4011 \jmath & -0.3170 - 0.2303 \jmath
-	% 			\end{bmatrix}.
-	% 		\end{split}
-	% 	\end{equation*}
-	% 	The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for \gls{d}-\gls{ris} and $(\alpha, \psi)$ for symmetric \gls{bd}-\gls{ris}.
-	% 	In this example, we observe that both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} (using 2 reconfigurable impedance) and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (using 3 reconfigurable impedance).
-	% 	% , where the former needs 2 reconfigurable impedance and the latter needs 3.
-	% 	% It is interesting that the huge difference comes purely from connecting both elements.
-	% 	Such a large gain comes from simply connecting both elements, and it can be even larger using an asymmetric component.
-	% 	% an even larger gain is expected when an asymmetric reconfigurable component is available.
-	% 	% An even larger gain is expected when an asymmetric reconfigurable component is available.
-	% 	% and a larger gain is expected when an asymmetric connection is available.
-	% 	This example shows that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
-	% \end{subsection}
-
-	% \begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
-
-	% \end{subsection}
+	% To provide a complete channel shaping solution, we invoke optimization approaches and tackle some relevant problems in the next section.
+
 	\end{section}
 
-	\begin{section}{BD-RIS Design Frameworks}
+	\begin{section}{Numerical Shaping Solutions}
+		\label{sc:framework}
+		% Consider a special class of channel shaping problem
+		% \begin{maxi!}
+		% 	{\scriptstyle{\mathbf{\Theta}}}{f(\mathbf{H})}{\label{op:shaping}}{\label{ob:shaping}}
+		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
+		% \end{maxi!}
+		% where $f: \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}} \to \mathbb{R}$ is a unitary invariant function satisfying $f(\mathbf{U}^\mathsf{H} \mathbf{H} \mathbf{V}) = f(\mathbf{H})$ for any $\mathbf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{U} \in \mathbb{U}^{N_\mathrm{R} \times N_\mathrm{R}}$, $\mathbf{V} \in \mathbb{U}^{N_\mathrm{T} \times N_\mathrm{T}}$.
+		% Examples of such $f$ include the $n$-th channel singular value, channel power gain, and channel capacity.
+		% According to
+		Consider a special class of channel shaping problem
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{\label{op:shaping}}{\label{ob:shaping}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
+		\end{maxi!}
+		where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
+		Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
+		Problem \eqref{op:shaping} can be solved by a \gls{rcg} method over proposition \ref{pp:shaping}.
+		% Although
+
+		\begin{proposition}
+			\label{pp:shaping}
+			The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
+			\begin{equation}
+				\label{eq:shaping_subdiff}
+				\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
+			\end{equation}
+			where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
+			% $d_n \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
+
+			% One Euclidean sub-gradient of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
+			% \begin{equation}
+			% 	\frac{\partial f\bigl(\sv(\mathbf{H})\bigr)}{\partial \mathbf{\Theta}_g} = \sum_{n=1}^N \frac{\partial f\bigl(\sv(\mathbf{H})\bigr)}{\partial \sigma_n(\mathbf{H})} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
+			% \end{equation}
+			% where $\mathbf{u}_n$ and $\mathbf{v}_n$ are any (c.f. Footnote \ref{fn:svd_non_uniqueness}) left and right singular vectors of $\mathbf{H}$ corresponding to $\sigma_n(\mathbf{H})$.
+		\end{proposition}
+
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:shaping}.
+		\end{proof}
 	% In this section, we first provide an overview on signal processing techniques for group-connected \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group and operates directly on the Stiefel manifold.
@@
 	{\scriptstyle{\mathbf{\Theta}}}{f(\mathbf{\Theta})}{\label{op:general}}{\label{ob:general}}
-	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:general_unitary}}
+	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:general_unitary}}
 	\end{maxi!}
-	where the objective function $f(\mathbf{\Theta})$ is a function of the \gls{bd}-\gls{ris} scattering matrix, for example, channel singular value (to be discussed in Section \ref{sc:pareto_frontier}), channel power gain (to be discussed in Section \ref{sc:power}), and achievable rate (to be discussed in Section \ref{sc:rate}).
+	where the objective function $f(\mathbf{\Theta})$ is a function of the \gls{bd}-\gls{ris} scattering matrix, for example, channel singular value (to be discussed in Section \ref{sc:pareto}), channel power gain (to be discussed in Section \ref{sc:power}), and achievable rate (to be discussed in Section \ref{sc:rate}).
 	The feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ that is non-convex and non-Euclidean.
 	Therefore, most \gls{bd}-\gls{ris} optimization problems are solved by \emph{relax-then-project} methods \cite{Fang2023} or \emph{general manifold \gls{rcg}} \cite{Li2023b,Li2023c,Zhou2023}.
-	The former solves unconstrained problem \eqref{ob:general} by quasi-Newton methods then projects the solution back to domain \ref{co:general_unitary}, which often ends up far from optimal.
+	The former solves unconstrained problem \eqref{ob:general} by quasi-Newton methods then projects the solution back to domain \ref{cn:general_unitary}, which often ends up far from optimal.
 	The latter generalizes the conjugate gradient methods to Riemannian manifolds and iteratively updates the solution by addition and retraction.
@@
 
-	\begin{subsection}{General (Non-Geodesic) RCG}
+	\begin{subsection}{Optimization}
+
+		\label{sc:rcg_general}
 		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
@@
 		\begin{enumerate}
-		\item \emph{Compute the Euclidean gradient:} The gradient of $f$ with respect to $\mathbf{\Theta}_g^*$ in the Euclidean space is
-			\begin{equation}
-				\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
-				\label{eq:gradient_euclidean}
+		\item \emph{Compute the Euclidean gradient:} The gradient of $f$ with respect to $\mathbf{\Theta}_g$ in the Euclidean space is \cite[(A.3.6)]{Fischer2005}
+			\begin{equation}
+				\label{eq:gradient_eucl}
+				\nabla_{\mathrm{E},g}^{(r)} = 2 \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
 			\end{equation}
@@
 			\begin{equation}
-				% \nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)\mathsf{H}}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}};
+				\label{eq:gradient_riem}
 				\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}} \mathbf{\Theta}_g^{(r)};
-				\label{eq:gradient_riemannian}
 			\end{equation}
@@
 			\begin{equation}
+				\label{eq:conjugate_dirn}
 				\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}, % $\mathcal{O}(N_\mathrm{S}^2)$
-				\label{eq:direction_cg}
 			\end{equation}
@@
 			\begin{equation}
+				\label{eq:conjugate_parm}
 				\gamma_g^{(r)} = \frac{\tr\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}; % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-				\label{eq:parameter_cg}
 			\end{equation}
@@
 			\begin{equation}
+				\label{eq:iterate_add}
 				\bar{\mathbf{\Theta}}_g^{(r+1)} = \mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)},
-				\label{eq:update_additive}
 			\end{equation}
@@
 			\begin{equation}
+				\label{eq:iterate_retr}
 				\mathbf{\Theta}_g^{(r+1)} = \bar{\mathbf{\Theta}}_g^{(r+1)} \bigl({\bar{\mathbf{\Theta}}_g^{(r+1)\mathsf{H}}} \bar{\mathbf{\Theta}}_g^{(r+1)}\bigr)^{-1/2}.
-				\label{eq:retraction}
-			\end{equation}
-			One can also combine the addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction} in one step
-			\begin{equation}
+			\end{equation}
+			One can also combine the addition \eqref{eq:iterate_add} and retraction \eqref{eq:iterate_retr} in one step
+			\begin{equation}
+				\label{eq:iterate_comb}
 				\mathbf{\Theta}_g^{(r+1)} = \bigl(\mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)}\bigr) \bigl( \mathbf{I} + \mu^2 {\mathbf{D}_g^{(r)\mathsf{H}}} \mathbf{D}_g^{(r)} \bigr)^{-1/2},
-				\label{eq:add_then_retract}
 			\end{equation}
@@
 
-	The method is called non-geodesic since the addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction} constitute a zigzag path departing from and returning to the manifold.
+	The method is called non-geodesic since the addition \eqref{eq:iterate_add} and retraction \eqref{eq:iterate_retr} constitute a zigzag path departing from and returning to the manifold.
 	% aided by the Euclidean space instead of carried entirely on the manifold.
-	% the points are updated in the linear embedding spaces by addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction}, instead of on the Stiefel manifold itself.
+	% the points are updated in the linear embedding spaces by addition \eqref{eq:iterate_add} and retraction \eqref{eq:iterate_retr}, instead of on the Stiefel manifold itself.
 	It converges to stationary points of the original problem but usually requires a large number of iterations due to inefficient operations in the Euclidean space.
 	% usually suffers from numerical instability
-	% additive update \eqref{eq:update_additive} in the Euclidean space and retraction \eqref{eq:retraction}.
+	% additive update \eqref{eq:iterate_add} in the Euclidean space and retraction \eqref{eq:iterate_retr}.
 	% Those
@@
 \begin{subsection}{Geodesic RCG}
+	\label{sc:rcg_geodesic}
 	Before introducing geodesic \gls{rcg}, we revisit some basic concepts in differential geometry.
@@
 	\begin{equation}
+		\label{eq:geodesic_iden}
 		\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D}),
-		\label{eq:geodesic_identity}
 	\end{equation}
@@
 	Note that the right translation is an isometry in $U(L)$.
-	During the optimization of group $g$, the geodesic evaluated at the identity \eqref{eq:geodesic_identity} should be translated to $\mathbf{\Theta}_g^{(r)}$ for successive updates \cite{Abrudan2008}
-	\begin{equation}
+	During the optimization of group $g$, the geodesic evaluated at the identity \eqref{eq:geodesic_iden} should be translated to $\mathbf{\Theta}_g^{(r)}$ for successive updates \cite{Abrudan2008}
+	\begin{equation}
+		\label{eq:geodesic_tran}
 		\mathbf{G}_g^{(r)}(\mu) = \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
-		\label{eq:geodesic_translated}
-	\end{equation}
-	while the Riemannian gradient evaluated at $\mathbf{\Theta}_g^{(r)}$ \eqref{eq:gradient_riemannian} should be translated back to the identity for exploiting the Lie algebra \cite{Abrudan2008}
-	\begin{equation}
+	\end{equation}
+	while the Riemannian gradient evaluated at $\mathbf{\Theta}_g^{(r)}$ \eqref{eq:gradient_riem} should be translated back to the identity for exploiting the Lie algebra \cite{Abrudan2008}
+	\begin{equation}
+		\label{eq:gradient_riem_tran}
 		\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{R},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.
 		% $\mathcal{O}(2 L^3)$
-		\label{eq:gradient_translated}
-	\end{equation}
-	After gradient translation, the deviation parameter and conjugate direction can be determined similarly to \eqref{eq:parameter_cg} and \eqref{eq:direction_cg}
-	\begin{equation}
+	\end{equation}
+	After gradient translation, the deviation parameter and conjugate direction can be determined similarly to \eqref{eq:conjugate_parm} and \eqref{eq:conjugate_dirn}
+	\begin{equation}
+		\label{eq:conjugate_parm_geod}
 		\tilde{\gamma}_g^{(r)} = \frac{\tr\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}.
 % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-		\label{eq:parameter_cg_geodesic}
-	\end{equation}
-	\begin{equation}
+	\end{equation}
+	\begin{equation}
+		\label{eq:conjugate_dirn_geod}
 		{\mathbf{D}}_g^{(r)} = \tilde{\nabla}_{\mathrm{R},g}^{(r)} + \tilde{\gamma}_g^{(r)} {\mathbf{D}}_g^{(r-1)},
-		\label{eq:direction_cg_geodesic}
 	\end{equation}
@@
 	\begin{equation}
+		\label{eq:iterate_mul}
 		\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
-		\label{eq:update_geodesic}
 	\end{equation}
@@
 
-	% \setalgorithmcaptionfont{\small}
 	\begin{algorithm}[!t]
-		% \small
 		\caption{Group-wise geodesic \gls{rcg} for \gls{bd}-\gls{ris} design}
@@
 			\For {$g \gets 1$ to $G$}
-			\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean} \label{ln:gradient_euclidean}
-			\State $\tilde{\nabla}_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_translated}
-			\State $\tilde{\gamma}_g^{(r)} \gets$ \eqref{eq:parameter_cg_geodesic}
-			\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg_geodesic}
+			\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_eucl}
+			\State $\tilde{\nabla}_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riem_tran}
+			\State $\tilde{\gamma}_g^{(r)} \gets$ \eqref{eq:conjugate_parm_geod}
+			\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:conjugate_dirn_geod}
 			\If {$\Re\bigl\{\tr({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
@@
 			\State $\mu \gets 1$
-			\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic_translated}
+			\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic_tran}
 			\While {$\scriptstyle f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
@@
 			\EndWhile \label{ln:armijo_end}
-			\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:update_geodesic}
+			\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:iterate_mul}
 			\EndFor
@@
 	Algorithm~\ref{ag:rcg} summarizes the proposed \gls{bd}-\gls{ris} design framework based on group-wise geodesic \gls{rcg}.
-	Compared to the general non-geodesic approach, it leverages the Lie group properties to replace the add-then-retract update \eqref{eq:add_then_retract} with a multiplicative rotational update \eqref{eq:update_geodesic} along geodesics of the Stiefel manifold.
+	Compared to the general non-geodesic approach, it leverages the Lie group properties to replace the add-then-retract update \eqref{eq:iterate_comb} with a multiplicative rotational update \eqref{eq:iterate_mul} along geodesics of the Stiefel manifold.
 	This leads to faster convergence and simplifies the step size tuning thanks to appropriate parameter space.
@@
 	Note that the group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
-	Since the set of block-unitary matrices are algebraically closed under multiplication, one can also avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) the Euclidean gradient \eqref{eq:gradient_euclidean}, which can further accelerate the algorithm when the number of group is large.
+	Since the set of block-unitary matrices are algebraically closed under multiplication, one can also avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) the Euclidean gradient \eqref{eq:gradient_eucl}, which can further accelerate the algorithm when the number of group is large.
 \end{subsection}
@@
 
-\begin{subsection}{Pareto Frontier Characterization}\label{sc:pareto_frontier}
-We now characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel_equivalent} by maximizing their weighted sum
+\begin{subsection}{Pareto Frontier Characterization}
+	\label{sc:pareto}
+We now characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel} by maximizing their weighted sum
 \begin{maxi!}
 {\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
-\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:pareto_unitary}}
+\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:pareto_unitary}}
 \end{maxi!}
-where $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
+where $\rho_n \ge 0$ is the weight of the $n$-th singular value.
+% that can be positive, zero, or negative.
 Varying $\{\rho_n\}_{n \in [N]}$ characterizes the Pareto frontier enclosing the singular value region such that problem \eqref{op:pareto} generalizes most singular value shaping problems.
-It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:pareto_gradient}.
-% It can be solved optimally by Algorithm~\ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses the following Euclidean gradient expression \eqref{eq:pareto_gradient}.
-
-\begin{lemma}\label{lm:pareto_gradient}
-	The Euclidean gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
-	\begin{equation}
-		\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \diag(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
-		\label{eq:pareto_gradient}
-	\end{equation}
-	where $\mathbf{U}$ and $\mathbf{V}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
+It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:pareto}.
+% It can be solved optimally by Algorithm~\ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses the following Euclidean gradient expression \eqref{eq:gradient_eucl_pareto}.
+
+% \begin{lemma}
+% 	\label{lm:pareto}
+% 	The Euclidean gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
+% 	\begin{equation}
+% 		\label{eq:gradient_eucl_pareto}
+% 		\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \diag(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
+% 	\end{equation}
+% 	where $\mathbf{U}$ and $\mathbf{V}$ are any left and right compact singular matrices of $\mathbf{H}$, respectively.
+% \end{lemma}
+
+\begin{lemma}
+	\label{lm:pareto}
+	One Euclidean sub-gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
+	\begin{equation}
+		\label{eq:gradient_eucl_pareto}
+		% \frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} =
+		\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \diag(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \in \frac{\partial \sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*}
+	\end{equation}
+	where $\mathbf{U}$ and $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$, respectively.
 \end{lemma}
 \begin{proof}
-	Please refer to Appendix~\ref{ap:pareto_gradient}.
+	Please refer to Appendix~\ref{ap:pareto}.
 \end{proof}
@@
 We now analyze the computational complexity of solving Pareto singular value problem \eqref{op:pareto} by Algorithm~\ref{ag:rcg}.
-To update each \gls{bd}-\gls{ris} group, compact \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:pareto_gradient} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_translated} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:parameter_cg_geodesic} and conjugate direction \eqref{eq:direction_cg_geodesic} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:update_geodesic} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
+To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:gradient_eucl_pareto} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:iterate_mul} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
 The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., line \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
@@
 
-\begin{subsection}{Channel Power Gain}\label{sc:power}
+\begin{subsection}{Channel Power Gain}
+	\label{sc:power}
 The \gls{mimo} channel power gain maximization problem is formulated with respect to the \gls{bd}-\gls{ris} scattering matrix
 \begin{maxi!}
-{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
-\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{\label{cs:power_block_unitary}}{}
+{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power}}{\label{ob:power}}
+\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{\label{cn:power_unitary}}{}
 \end{maxi!}
-which generalizes the problem of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and \gls{mimo} with negligible direct channel and fully-connected \gls{bd}-\gls{ris} \eqref{eq:scattering_fc_optimal}.
-Solving \eqref{op:power_passive} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
-% The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative space alignments.
+which generalizes the problem of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and \gls{mimo} with negligible direct channel and fully-connected \gls{bd}-\gls{ris} ??.
+Solving \eqref{op:power} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
+% The key of solving \eqref{op:power} is to balance the additive and multiplicative space alignments.
 
 \begin{remark}
-Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
+Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
 \begin{mini!}
-{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
-\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_unitary}}{}
+{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:procrustes_wt}}{}
+\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cn:procrustes_wt}}{}
 \end{mini!}
-which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary \eqref{cs:power_unitary} but still has no trivial solution.
+which relaxes the block-unitary constraint \eqref{cn:power_unitary} to unitary \eqref{cn:procrustes_wt} but still has no trivial solution.
 One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
 \begin{mini!}
-{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
+{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:procrustes}}{}
 \addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
@@
 \begin{equation}
+	\label{eq:ris_procrustes}
 	\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
-	\label{eq:orthogonal_procrustes_solution}
-\end{equation}
-where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right compact singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
+\end{equation}
+where $\mathbf{U}$ and $\mathbf{V}$ are respectively any left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
 \end{remark}
 
-It is worth noting that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power_passive} when the direct channel is negligible and significant, respectively.
+It is worth noting that ?? and \eqref{eq:ris_procrustes} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power} when the direct channel is negligible and significant, respectively.
 However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
-Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power_passive} with arbitrary group size.
-The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
-
-\begin{proposition}\label{pp:power}
+Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power} with arbitrary group size.
+The idea is to successively approximate the quadratic objective \eqref{ob:power} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
+
+\begin{proposition}
+	\label{pp:power}
 	Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
 	\begin{equation}
+		\label{eq:ris_power}
 		\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
-		\label{eq:scattering_power}
-	\end{equation}
-	converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrices of
-	\begin{equation}
+	\end{equation}
+	converges to a stationary point of \eqref{op:power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
+	\begin{equation}
+		\label{eq:auxiliary_power}
 		\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-		\label{eq:auxiliary_matrix_power}
 	\end{equation}
@@
 	% 	% \end{split}
-	% 	\label{eq:auxiliary_matrix_power}
+	% 	\label{eq:auxiliary_power}
 	% \end{equation}
@@
 
-We now analyze the computational complexity of solving channel gain maximization problem \eqref{op:power_passive} by Proposition \ref{pp:power}.
-To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_matrix_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its compact \gls{svd} requires $\mathcal{O}(L^3)$ operations.
+We now analyze the computational complexity of solving channel gain maximization problem \eqref{op:power} by Proposition \ref{pp:power}.
+To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its \gls{svd} requires $\mathcal{O}(L^3)$ operations.
 The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
@@
 
-\begin{subsection}{Achievable Rate Maximization}\label{sc:rate}
+\begin{subsection}{Achievable Rate Maximization}
+	\label{sc:rate}
 We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
@@
 \addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
-\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cs:rate_block_unitary}}
+\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cn:rate_unitary}}
 \end{maxi!}
 where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
-Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cs:rate_block_unitary} and the coupling between variables.
+Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
 We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
@@
 \begin{maxi!}
-{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
+{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_ris}}{\label{ob:rate_ris}}
 \addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
@@
 where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-Problem \eqref{op:rate_passive} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate_gradient}.
-\begin{lemma}\label{lm:rate_gradient}
-	The Euclidean gradient of \eqref{ob:rate_passive} with respect to \gls{bd}-\gls{ris} block $g$ is
-	\begin{equation}
+Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate}.
+\begin{lemma}
+	\label{lm:rate}
+	The Euclidean gradient of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
+	\begin{equation}
+		\label{eq:gradient_eucl_rate}
 		\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-		\label{eq:rate_gradient}
 	\end{equation}
@@
 \begin{proof}
-	Please refer to Appendix~\ref{ap:rate_gradient}.
+	Please refer to Appendix~\ref{ap:rate}.
 \end{proof}
@@
 \begin{equation}
+	\label{eq:precoder}
 	\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
-	\label{eq:precoder_eigenmode}
 \end{equation}
@@
 The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-Similar to the analysis in Section \ref{sc:pareto_frontier}, the computational complexity of solving subproblem \eqref{op:rate_passive} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
-On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder_eigenmode} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+Similar to the analysis in Section \ref{sc:pareto}, the computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
+On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
 The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
@@
 
-\begin{subsubsection}{Low-Complexity Solution}\label{sc:low_complexity}
+\begin{subsubsection}{Low-Complexity Solution}
+	\label{sc:low_complexity}
 	We finally propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
-	The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_passive} by channel power gain maximization problem \eqref{op:power_passive}, then proceed to conventional eigenmode transmission \eqref{eq:precoder_eigenmode}.
+	The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_ris} by channel power gain maximization problem \eqref{op:power}, then proceed to conventional eigenmode transmission \eqref{eq:precoder}.
 	Both steps are solved in closed form and the computational complexity is $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr) + N N_\mathrm{T} N_\mathrm{R}\bigr)$.
@@
 % 		\begin{maxi!}
-% 			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
-% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{\label{cs:power_block_unitary}}{}
+% 			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power}}{\label{ob:power}}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{\label{cn:power_unitary}}{}
 % 		\end{maxi!}
-% 		which generalizes the problem of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and \gls{mimo} with negligible direct channel and fully-connected \gls{bd}-\gls{ris} \eqref{eq:scattering_fc_optimal}.
-% 		Solving \eqref{op:power_passive} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
-% 		% The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative space alignments.
+% 		which generalizes the problem of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and \gls{mimo} with negligible direct channel and fully-connected \gls{bd}-\gls{ris} ??.
+% 		Solving \eqref{op:power} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
+% 		% The key of solving \eqref{op:power} is to balance the additive and multiplicative space alignments.
 
 % 		\begin{remark}
-% 			Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
+% 			Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
 % 			\begin{mini!}
-% 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
-% 				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_unitary}}{}
+% 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:procrustes_wt}}{}
+% 				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cn:procrustes_wt}}{}
 % 			\end{mini!}
-% 			which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary \eqref{cs:power_unitary} but still has no trivial solution.
+% 			which relaxes the block-unitary constraint \eqref{cn:power_unitary} to unitary \eqref{cn:procrustes_wt} but still has no trivial solution.
 % 			One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
 % 			\begin{mini!}
-% 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
+% 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:procrustes}}{}
 % 				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
@@
 % 				\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
-% 				\label{eq:orthogonal_procrustes_solution}
+% 				\label{eq:ris_procrustes}
 % 			\end{equation}
@@
 
-% 		It is worth noting that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power_passive} when the direct channel is negligible and significant, respectively.
+% 		It is worth noting that ??
+and \eqref{eq:ris_procrustes} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power} when the direct channel is negligible and significant, respectively.
 % 		However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
-% 		Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power_passive} with arbitrary group size.
-% 		The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
+% 		Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power} with arbitrary group size.
+% 		The idea is to successively approximate the quadratic objective \eqref{ob:power} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
 
@@
 % 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
-% 				\label{eq:scattering_power}
-% 			\end{equation}
-% 			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrices of
+% 				\label{eq:ris_power}
+% 			\end{equation}
+% 			converges to a stationary point of \eqref{op:power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right compact singular matrices of
 % 			\begin{equation}
 % 				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-% 				\label{eq:auxiliary_matrix_power}
+% 				\label{eq:auxiliary_power}
 % 			\end{equation}
@@
 % 			% 	% \end{split}
-% 			% 	\label{eq:auxiliary_matrix_power}
+% 			% 	\label{eq:auxiliary_power}
 % 			% \end{equation}
@@
 
-% 		We now analyze the computational complexity of solving channel gain maximization problem \eqref{op:power_passive} by Proposition \ref{pp:power}.
-% 		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_matrix_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its compact \gls{svd} requires $\mathcal{O}(L^3)$ operations.
+% 		We now analyze the computational complexity of solving channel gain maximization problem \eqref{op:power} by Proposition \ref{pp:power}.
+% 		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its compact \gls{svd} requires $\mathcal{O}(L^3)$ operations.
 % 		The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
@@
 % 			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
-% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cs:rate_block_unitary}}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cn:rate_unitary}}
 % 		\end{maxi!}
 % 		where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
-% 		Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cs:rate_block_unitary} and the coupling between variables.
+% 		Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
 % 		We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
@@
 % 			\begin{maxi!}
-% 				{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
+% 				{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_ris}}{\label{ob:rate_ris}}
 % 				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
@@
 % 			where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-% 			Problem \eqref{op:rate_passive} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate_gradient}.
-% 			\begin{lemma}\label{lm:rate_gradient}
-% 				The Euclidean gradient of \eqref{ob:rate_passive} with respect to \gls{bd}-\gls{ris} block $g$ is
+% 			Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate}.
+% 			\begin{lemma}\label{lm:rate}
+% 				The Euclidean gradient of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
 % 				\begin{equation}
 % 					\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-% 					\label{eq:rate_gradient}
+% 					\label{eq:gradient_eucl_rate}
 % 				\end{equation}
@@
 % 			\begin{proof}
-% 				Please refer to Appendix~\ref{ap:rate_gradient}.
+% 				Please refer to Appendix~\ref{ap:rate}.
 % 			\end{proof}
@@
 % 				\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
-% 				\label{eq:precoder_eigenmode}
+% 				\label{eq:precoder}
 % 			\end{equation}
@@
 % 			The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-% 			Similar to the analysis in Section \ref{sc:pareto_frontier}, the computational complexity of solving subproblem \eqref{op:rate_passive} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
-% 			On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder_eigenmode} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+% 			Similar to the analysis in Section \ref{sc:pareto}, the computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
+% 			On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
 % 			The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
@@
 % 			We finally propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
-% 			The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_passive} by channel power gain maximization problem \eqref{op:power_passive}, then proceed to conventional eigenmode transmission \eqref{eq:precoder_eigenmode}.
+% 			The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_ris} by channel power gain maximization problem \eqref{op:power}, then proceed to conventional eigenmode transmission \eqref{eq:precoder}.
 % 			Both steps are solved in closed form and the computational complexity is $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr) + N N_\mathrm{T} N_\mathrm{R}\bigr)$.
@@
 
-\begin{section}{Simulation Results}\label{sc:simulation}
+\begin{section}{Simulation Results}
+	\label{sc:simulation}
  In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{Source code is available at \url{https://github.com/snowztail/channel-shaping}.}
@@
 		 \caption{Average Performance of Geodesic and Non-Geodesic \gls{rcg} Algorithms on Problem \eqref{op:pareto}}
-		 \label{tb:complexity_test}
+		 \label{tb:complexity}
 		 \centering
@@
 	 \end{table*}
-	 We first compare in Table \ref{tb:complexity_test} the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in an $N_\mathrm{T}=N_\mathrm{R}=4$ system with \gls{bd}-\gls{ris} group size $L=4$.
+	 We first compare in Table \ref{tb:complexity} the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in an $N_\mathrm{T}=N_\mathrm{R}=4$ system with \gls{bd}-\gls{ris} group size $L=4$.
 	 The statistics are averaged over \num{100} independent runs.
@@
 			 \centering
-			 \subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
+			 \subfloat[$2 \times 32 \times 2$ (no direct)]{
+				\label{fg:singular_pareto_sx32_nd}
 				 \resizebox{!}{3.25cm}{
 					 \input{../assets/simulation/singular_pareto_sx32_nd.tex}
-				 }
-			 }
-			 \subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
+
+				 }
+			 }
+			 \subfloat[$2 \times 32 \times 2$]{
+				\label{fg:singular_pareto_sx32}
 				 \resizebox{!}{3.25cm}{
@@
 			 \\
-			 \subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
+			 \subfloat[$2 \times 64 \times 2$]{
+				\label{fg:singular_pareto_sx64}
 				 \resizebox{!}{3.25cm}{
@@
 			 }
-			 \subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
+			 \subfloat[$2 \times 128 \times 2$]{
+				\label{fg:singular_pareto_sx128}
 				 \resizebox{!}{3.25cm}{
@@
 			 \centering
-			 \subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
+			 \subfloat[$4 \times 32 \times 4$ (rank-1)]{
+				\label{fg:singular_bound_rank1_sx32}
 				 \resizebox{!}{3.25cm}{
@@
 			 }
-			 \subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
+			 \subfloat[$4 \times 64 \times 4$ (rank-1)]{
+				\label{fg:singular_bound_rank1_sx64}
 				 \resizebox{!}{3.25cm}{
@@
 			 \\
-			 \subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
+			 \subfloat[$4 \times 128 \times 4$ (rank-2)]{
+				\label{fg:singular_bound_rank2_sx128}
 				 \resizebox{!}{3.25cm}{
@@
 			 }
-			 \subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
+			 \subfloat[$4 \times 256 \times 4$ (rank-4)]{
+				\label{fg:singular_bound_rank4_sx256}
 				 \resizebox{!}{3.25cm}{
@@
 			 \caption{
-				 Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
-				 The intersections of the blue and red bars denote the singular values of the direct channel.
-				 The blue (resp. red) bars are obtained by solving problem \eqref{op:pareto} with $\rho_n = -1$ (resp. $+1$) and $\rho_{n'} = 0$, $\forall n' \ne n$.
+				 Achievable channel singular values: analytical bounds (lines) and numerical results (bars).
+				 Baselines of bars denote the singular values of the direct channel.
+				 Blue (resp.
+red) bars denote the lower (resp.
+upper) dynamic range of singular values obtained by solving \eqref{op:pareto} with $\rho_n/\rho_{n'} \to 0$ (resp.
+$\to \infty$), $\forall n, \ n' \ne n$.
 				 `D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
@@
 		 \end{figure}
-		 Fig.
-\ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
-		 Here we assume a rank-$k$ forward channel without loss of generality.
+		 Fig. \ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rd} and the numerical results obtained by solving problem \eqref{op:pareto}.
+		 Here we consider a rank-$k$ forward channel without loss of generality.
 		 When the \gls{ris} is in the vicinity of the transmitter, Figs.
@@
 		 Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
-		 % The observations align with Proposition \ref{pp:rank_deficient} that t
+		 % The observations align with Proposition \ref{pp:rd} that t
 		 The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
-		 Those observations align with Proposition \ref{pp:rank_deficient}.
+		 Those observations align with Proposition \ref{pp:rd}.
 		 Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both backward and forward channels are full-rank.
-		 This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
+		 This can be predicted from \eqref{eq:auxiliary_rd} where the singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
 		 The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scales with backward and forward channel ranks.
@@
 			 \centering
-			 \subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
+			 \subfloat[$1 \times 256 \times 1$ (no direct)]{
+				\label{fg:power_bond_txrx1_nd}
 				 \resizebox{!}{3.25cm}{
@@
 			 }
-			 \subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
+			 \subfloat[$4 \times 256 \times 4$ (no direct)]{
+				\label{fg:power_bond_txrx4_nd}
 				 \resizebox{!}{3.25cm}{
@@
 		 Fig.
-\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct channel is negligible.
-		 Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:power_max} or via optimization approach \eqref{eq:scattering_power}.
+\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
+		 Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:ris_nd_power_max} or via optimization approach \eqref{eq:ris_power}.
 		 % Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
@@
 		 Interestingly, this relative power gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig.
-\subref*{fg:power_bond_txrx4_nd}, which can also be predicted from the expectation analysis \eqref{eq:power_gain_rayleigh}.
+\subref*{fg:power_bond_txrx4_nd}, which can also be predicted from the expectation analysis \eqref{eq:power_nd_rayleigh}.
 		 We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
@@
 		 \centering
-		 \subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)\label{fg:power_sx_txrx16_nd}]{
+		 \subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)]{
+			\label{fg:power_sx_txrx16_nd}
 			 \resizebox{!}{3.0625cm}{
@@
 		 }
-		 \subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
+		 \subfloat[$16 \times N_\mathrm{S} \times 16$]{
+			\label{fg:power_sx_txrx16}
 			 \resizebox{!}{3.0625cm}{
@@
 			 Average maximum channel power gain versus \gls{ris} configuration.
-			 `OP-left' and `OP-right' refer to the suboptimal solutions to problem \eqref{op:power_passive} by lossy transformation \eqref{op:standard_orthogonal_procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
+			 `OP-left' and `OP-right' refer to the suboptimal solutions to problem \eqref{op:power} by lossy transformation \eqref{op:procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
 		 }
@@
 
-	 We first focus on channel power gain maximization problem \eqref{op:power_passive}.
+	 We first focus on channel power gain maximization problem \eqref{op:power}.
 	 Fig. \ref{fg:power_sx} shows the maximum channel power under different \gls{ris} configurations.
@@
 	 This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the mode alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
-	 We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
+	 We also notice that the suboptimal solutions \eqref{eq:ris_procrustes} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
 
@@
 		 \centering
-		 \subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
+		 \subfloat[$4 \times 128 \times 4$]{
+			\label{fg:rate_beamforming}
 			 \resizebox{!}{3.25cm}{
@@
 		 }
-		 \subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
+		 \subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$]{
+			\label{fg:rate_txrx}
 			 \resizebox{!}{3.25cm}{
@@
 		 \\
-		 \subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
+		 \subfloat[$4 \times N_\mathrm{S} \times 4$]{
+			\label{fg:rate_sx}
 			 \resizebox{!}{3.25cm}{
@@
 		 }
-		 \subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
+		 \subfloat[$4 \times 128 \times 4$]{
+			\label{fg:rate_kfactor}
 			 \resizebox{!}{3.25cm}{
@@
 	 A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-	 An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_passive} -- \eqref{eq:precoder_eigenmode} and the shaping-inspired solution \eqref{eq:scattering_power}, \eqref{eq:precoder_eigenmode} narrows at larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+	 An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_ris} -- \eqref{eq:precoder} and the shaping-inspired solution \eqref{eq:ris_power}, \eqref{eq:precoder} narrows at larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
 	 This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the active beamformer, which significantly simplifies the process at marginal performance cost.
@@
 \begin{appendix}
-\begin{subsection}{Proof of Proposition \ref{pp:dof}}\label{ap:dof}
-	The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as
-	\begin{equation}
-		\mathbf{\Theta} = \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H},
-	\end{equation}
-	where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to \gls{d}-\gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block-diagonal matrices of $L \times L$ unitary blocks.
-	Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
-	On the other hand, there exists a $\mathbf{\Theta}_\mathrm{D}$ such that
+% \begin{subsection}{Proof of Proposition \ref{pp:dof}}
+% 	\label{ap:dof}
+% 	The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as
+% 	\begin{equation}
+% 		\mathbf{\Theta} = \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H},
+% 	\end{equation}
+% 	where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to \gls{d}-\gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block-diagonal matrices of $L \times L$ unitary blocks.
+% 	Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
+% 	On the other hand, there exists a $\mathbf{\Theta}_\mathrm{D}$ such that
+% 	\begin{equation*}
+% 		\begin{split}
+% 			\rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
+% 			 & = \min \bigl( \rank(\mathbf{H}_\mathrm{B}), \rank(\mathbf{\Theta}_\mathrm{D}), \rank(\mathbf{H}_\mathrm{F}) \bigr) \\
+% 			 & = \min \bigl( \rank(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \rank(\bar{\mathbf{H}}_\mathrm{F}) \bigr)          \\
+% 			 & = \max_\mathbf{\Theta} \ \rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+% 		\end{split}
+% 	\end{equation*}
+% 	The same result holds if the direct channel is significant and the proof is omitted here.
+% \end{subsection}
+
+\begin{subsection}{Proof of Proposition \ref{pp:dof}}
+	\label{ap:dof}
+	It suffices to consider the rank of the indirect channel.
+	% Denote the rank of the
+	% Let $r_\mathrm{B}$ and $r_\mathrm{F}$ be the ranks of the backward and forward channels, respectively.
+	Denote the \gls{svd} of the backward and forward channels as
+	\begin{equation*}
+		\mathbf{H}_\mathrm{B/F} = \begin{bmatrix}
+			\mathbf{U}_{\mathrm{B/F},1} & \mathbf{U}_{\mathrm{B/F},2}
+		\end{bmatrix}
+		\begin{bmatrix}
+			\mathbf{\Sigma}_{\mathrm{B/F},1} & \mathbf{0} \\
+			\mathbf{0}                     & \mathbf{0}
+		\end{bmatrix}
+		\begin{bmatrix}
+			\mathbf{V}_{\mathrm{B/F},1}^\mathsf{H} \\
+			\mathbf{V}_{\mathrm{B/F},2}^\mathsf{H}
+		\end{bmatrix},
+	\end{equation*}
+	where $\mathbf{U}_{\mathrm{B/F},1}$ and $\mathbf{V}_{\mathrm{B/F},1}$ are any left and right singular matrices of $\mathbf{H}_\mathrm{B/F}$ corresponding to non-zero singular values $\mathbf{\Sigma}_{\mathrm{B/F},1}$, and $\mathbf{U}_{\mathrm{B/F},2}$ and $\mathbf{V}_{\mathrm{B/F},2}$ are those corresponding to zero singular values.
+	The rank of the indirect channel is \cite[(16.5.10.b)]{Hogben2013}
 	\begin{equation*}
 		\begin{split}
-			\rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
-			 & = \min \bigl( \rank(\mathbf{H}_\mathrm{B}), \rank(\mathbf{\Theta}_\mathrm{D}), \rank(\mathbf{H}_\mathrm{F}) \bigr) \\
-			 & = \min \bigl( \rank(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \rank(\bar{\mathbf{H}}_\mathrm{F}) \bigr)          \\
-			 & = \max_\mathbf{\Theta} \ \rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+			\rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+			 & = \rank(\mathbf{H}_\mathrm{B}) - \dim \bigl(\ker(\mathbf{H}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H}) \cap \ran(\mathbf{H}_\mathrm{B}^\mathsf{H})\bigr) \\
+			 & = \rank(\mathbf{H}_\mathrm{B}) - \dim \bigl(\ran(\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}) \cap \ran(\mathbf{V}_{\mathrm{B},1})\bigr) \\
+			 & \triangleq r_\mathrm{B} - r_\mathrm{L}(\mathbf{\Theta}),
 		\end{split}
 	\end{equation*}
-	The same result holds if the direct channel is significant and the proof is omitted here.
+	where we define $r_\mathrm{L}(\mathbf{\Theta}) \triangleq \dim \bigl(\ran(\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}) \cap \ran(\mathbf{V}_{\mathrm{B},1})\bigr)$ and $r_\mathrm{B/F} \triangleq \rank(\mathbf{H}_\mathrm{B/F})$.
+	Since $\mathbf{U}_{\mathrm{F},2} \in \mathbb{U}^{N_\mathrm{S} \times (N_\mathrm{S} - r_\mathrm{F})}$ and $\mathbf{V}_{\mathrm{B},1} \in \mathbb{U}^{N_\mathrm{S} \times r_\mathrm{B}}$, we have $\max(r_\mathrm{B} - r_\mathrm{F}, 0) \le r_\mathrm{L}(\mathbf{\Theta}) \le \min(N_\mathrm{S} - r_\mathrm{F}, r_\mathrm{B})$
+	and thus
+	% the following inequality holds
+	% \begin{equation}
+	% 	\max(r_\mathrm{B} - r_\mathrm{F}, 0) \le r_\mathrm{L}(\mathbf{\Theta}) \le \min(N_\mathrm{S} - r_\mathrm{F}, r_\mathrm{B}),
+	% \end{equation}
+	% which implies
+	\begin{equation}
+		\label{iq:rank_indirect}
+		\max(r_\mathrm{B} + r_\mathrm{F} - N_\mathrm{S}, 0) \le \rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \le \min(r_\mathrm{B}, r_\mathrm{F}).
+	\end{equation}
+	To attain the upper bound in \eqref{iq:rank_indirect}, the \gls{ris} needs to minimize $r_\mathrm{L}(\mathbf{\Theta})$ by aligning the ranges of $\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}$ and $\mathbf{V}_{\mathrm{B},2}$ as possible.
+	This is achieved by
+	\begin{equation}
+		\label{eq:ris_dof_max}
+		\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} = \mathbf{Q}_{\mathrm{B},2} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H},
+	\end{equation}
+	where $\mathbf{Q}_{\mathrm{B},2}$ and $\mathbf{Q}_{\mathrm{F},2}$ are the unitary matrices of the QR decomposition of $\mathbf{V}_{\mathrm{B},2}$ and $\mathbf{U}_{\mathrm{F},2}$, respectively.
+	Similarly, the lower bound in \eqref{iq:rank_indirect} is attained at
+	\begin{equation}
+		\label{eq:ris_dof_min}
+		\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} = \mathbf{Q}_{\mathrm{B},1} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H},
+	\end{equation}
+	where $\mathbf{Q}_{\mathrm{B},1}$ is the unitary matrix of the QR decomposition of $\mathbf{V}_{\mathrm{B},1}$.
+	While the \gls{dof}-optimal structures \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min} are always feasible for fully-connected \gls{bd}-\gls{ris}, they are generally infeasible for \gls{d}-\gls{ris} unless there exist some QR decomposition that diagonalize $\mathbf{Q}_{\mathrm{B},2} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H}$ and $\mathbf{Q}_{\mathrm{B},1} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H}$ simultaneously.
+	That is, \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{dof} of indirect channel, and thus equivalent channel, than \gls{d}-\gls{ris}.
 \end{subsection}
 
-\begin{subsection}{Proof of Proposition \ref{pp:rank_deficient}}\label{ap:rank_deficient}
+\begin{subsection}{Proof of Proposition \ref{pp:rd}}
+	\label{ap:rank_deficient}
 	We consider rank-$k$ forward channel and the proof follows similarly for rank-$k$ backward channel.
-	Let $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the compact \gls{svd} of the forward channel.
+	Let $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the forward channel.
 	The channel Gram matrix $\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} $ can be written as
@@
 	\begin{align}
-		\lambda_n(\mathbf{G}) & \le \lambda_{n-k}(\mathbf{Y}), &  & \text{if } n > k, \label{iq:ev:bound_enlarge}          \\
-		\lambda_n(\mathbf{G}) & \ge \lambda_n(\mathbf{Y}),     &  & \text{if } n < N - k + 1 \label{iq:ev_bound_suppress}.
+		\lambda_n(\mathbf{G}) & \le \lambda_{n-k}(\mathbf{Y}), &  & \text{if } n > k, \label{iq:ev_rd_max}          \\
+		\lambda_n(\mathbf{G}) & \ge \lambda_n(\mathbf{Y}),     &  & \text{if } n < N - k + 1 \label{iq:ev_rd_min}.
 	\end{align}
-	Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, taking the square roots of \eqref{iq:ev:bound_enlarge} and \eqref{iq:ev_bound_suppress} gives \eqref{iq:sv_bound_enlarge} and \eqref{iq:sv_bound_suppress}.
+	Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, taking the square roots of \eqref{iq:ev_rd_max} and \eqref{iq:ev_rd_min} gives \eqref{iq:sv_rd_max} and \eqref{iq:sv_rd_min}.
 \end{subsection}
 
-\begin{subsection}{Proof of Proposition \ref{pp:direct_negligible}}\label{ap:direct_negligible}
+\begin{subsection}{Proof of Proposition \ref{pp:nd}}
+	\label{ap:nd}
 	Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
@@
 	\begin{equation}
+		\label{eq:ris_decompose}
 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{X} \mathbf{U}_\mathrm{F}^\mathsf{H},
-		\label{eq:scattering_fc}
 	\end{equation}
@@
 	\begin{equation}
+		\label{eq:channel_nd}
 		\mathbf{H} = \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}.
-		\label{eq:channel_equivalent_fc}
 	\end{equation}
@@
 	\begin{equation}
-		\label{eq:sv_factorization}
+		\label{eq:sv_factor}
 		\begin{split}
@@
 
-\begin{subsection}{Proof of Corollary \ref{co:sv_product}}\label{ap:sv_product}
-	\eqref{iq:sv_product_largest} follows from \eqref{iq:sv_bound_fc} when $r = k$.
+\begin{subsection}{Proof of Corollary \ref{co:nd_sv_prod_tail}}
+	\label{ap:nd_sv_prod_tail}
+	\eqref{iq:sv_nd_prod_largest} follows from \eqref{iq:horn} when $r = k$.
 	On the other hand, if we can prove
 	\begin{equation}
+		\label{eq:sv_prod_all_ext}
 		\prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
+	\end{equation}
+	then \eqref{iq:sv_nd_prod_smallest} follows from \eqref{iq:sv_nd_prod_largest} and the non-negativity of singular values.
+	To see \eqref{eq:sv_prod_all_ext}, we start from a stricter result
+	\begin{equation}
 		\label{eq:sv_product_all}
-	\end{equation}
-	then \eqref{iq:sv_product_smallest} follows from \eqref{iq:sv_product_largest} and the non-negativity of singular values.
-	To see \eqref{eq:sv_product_all}, we start from a stricter result
-	\begin{equation}
 		\prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
-		\label{eq:sv_product}
 	\end{equation}
 	which is provable by cases.
-	When $N_\mathrm{S} > N$, both sides of \eqref{eq:sv_product} become zero since $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}_\mathrm{B}) = \sigma_n(\mathbf{H}_\mathrm{F}) = 0$ for $n > N$.
+	When $N_\mathrm{S} > N$, both sides of \eqref{eq:sv_product_all} become zero since $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}_\mathrm{B}) = \sigma_n(\mathbf{H}_\mathrm{F}) = 0$ for $n > N$.
 	When $N_\mathrm{S} \le N$, we have
@@
 	\end{equation*}
-	where the first equality follows from \eqref{eq:sv_factorization} and $\hat{\mathbf{\Sigma}}_\mathrm{B}, \hat{\mathbf{\Sigma}}_\mathrm{F}$ truncate $\mathbf{\Sigma}_\mathrm{B}, \mathbf{\Sigma}_\mathrm{F}$ to square matrices of dimension $N_\mathrm{S}$, respectively.
-	It is evident that \eqref{eq:sv_product} implies \eqref{eq:sv_product_all} and thus \eqref{iq:sv_product_smallest}.
+	where the first equality follows from \eqref{eq:sv_factor} and $\hat{\mathbf{\Sigma}}_\mathrm{B}, \hat{\mathbf{\Sigma}}_\mathrm{F}$ truncate $\mathbf{\Sigma}_\mathrm{B}, \mathbf{\Sigma}_\mathrm{F}$ to square matrices of dimension $N_\mathrm{S}$, respectively.
+	It is evident that \eqref{eq:sv_product_all} implies \eqref{eq:sv_prod_all_ext} and thus \eqref{iq:sv_nd_prod_smallest}.
 \end{subsection}
 
-\begin{subsection}{Proof of Corollary \ref{co:sv_nth}}\label{ap:sv_nth}
-	In \eqref{iq:sv_nth}, the set of upper bounds
-	\begin{equation}
+\begin{subsection}{Proof of Corollary \ref{co:nd_sv_indl}}
+	\label{ap:nd_sv_indl}
+	In \eqref{iq:sv_nd_indl}, the set of upper bounds
+	\begin{equation}
+		\label{iq:sv_nd_indl_set_max}
 		\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+1\bigr\}
-		\label{iq:sv_nth_upper_set}
-	\end{equation}
-	is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [N_\mathrm{S}]^3$.
+	\end{equation}
+	is a special case of \eqref{iq:horn} with $(I, J, K) \in [N_\mathrm{S}]^3$.
 	The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
-However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nth_upper_set} is selected as the tightest upper bound in \eqref{iq:sv_nth}.
+However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
 	On the other hand, the set of lower bounds
 	\begin{equation}
+		\label{iq:sv_nd_indl_set_min}
 		\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+N_\mathrm{S}\bigr\}
-		\label{iq:sv_nth_lower_set}
-	\end{equation}
-	can be induced by \eqref{iq:sv_nth_upper_set}, \eqref{eq:sv_product}, and the non-negativity of singular values.
-	The maximum of \eqref{iq:sv_nth_lower_set} is selected as the tightest lower bound in \eqref{iq:sv_nth}.
+	\end{equation}
+	can be induced by \eqref{iq:sv_nd_indl_set_max}, \eqref{eq:sv_product_all}, and the non-negativity of singular values.
+	The maximum of \eqref{iq:sv_nd_indl_set_min} is selected as the tightest lower bound in \eqref{iq:sv_nd_indl}.
 	Interested readers are also referred to \cite[(2.0.3)]{Zhang2005}.
@@
 	To attain the upper bound, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ channel singular values.
-	It follows from \eqref{eq:sv_nth_max} that
+	It follows from \eqref{eq:ris_nd_sv_indl_max} that
 	\begin{equation*}
@@
 	\end{equation*}
-	On the one hand, $\mathbf{P}_{ij}=1$ with $(i, j)$ satisfying \eqref{eq:sv_nth_max_pair} ensures $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is a singular value of $\mathbf{H}$.
+	On the one hand, $\mathbf{P}_{ij}=1$ with $(i, j)$ satisfying \eqref{eq:idx_nd_sv_indl_max} ensures $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is a singular value of $\mathbf{H}$.
 	It is actually among the first $n$ since the number of pairs $(i',j')$ not majorized by $(i,j)$ is $n-1$.
-	On the other hand, \eqref{eq:sv_nth_max_condition} ensures the first $(n-1)$-th singular values are no smaller than $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$.
-	Combining both facts, we claim the upper bound $\sigma_n(\mathbf{H}) = \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is attainable by \eqref{eq:sv_nth_max}.
+	On the other hand, \eqref{eq:perm_nd_sv_indl_max} ensures the first $(n-1)$-th singular values are no smaller than $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$.
+	Combining both facts, we claim the upper bound $\sigma_n(\mathbf{H}) = \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is attainable by \eqref{eq:ris_nd_sv_indl_max}.
 	The attainability of the lower bound can be proved similarly and the details are omitted.
 
-	% In \eqref{iq:sv_nth}, the set of upper bounds
+	% In \eqref{iq:sv_nd_indl}, the set of upper bounds
 	% \begin{equation}
 	% 	\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N]^3, i+j=n+1\bigr\}
-	% 	\label{iq:sv_nth_upper_set}
-	% \end{equation}
-	% is a special case of \eqref{iq:sv_bound_fc} with $(I, J, K) \in [N]^3$.
+	% 	\label{iq:sv_nd_indl_set_max}
+	% \end{equation}
+	% is a special case of \eqref{iq:horn} with $(I, J, K) \in [N]^3$.
 	% The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
-However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nth_upper_set} is selected as the tightest upper bound in \eqref{iq:sv_nth}.
+However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
 	% On the other hand, the set of lower bounds
@@
 	% 	\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N]^3, i+j=n+N\bigr\}
-	% 	\label{iq:sv_nth_lower_set}
-	% \end{equation}
-	% can be induced by \eqref{iq:sv_nth_upper_set}, \eqref{eq:sv_product}, and the non-negativity of singular values.
-	% The maximum of \eqref{iq:sv_nth_lower_set} is selected as the tightest lower bound in \eqref{iq:sv_nth}.
+	% 	\label{iq:sv_nd_indl_set_min}
+	% \end{equation}
+	% can be induced by \eqref{iq:sv_nd_indl_set_max}, \eqref{eq:sv_product_all}, and the non-negativity of singular values.
+	% The maximum of \eqref{iq:sv_nd_indl_set_min} is selected as the tightest lower bound in \eqref{iq:sv_nd_indl}.
 
@@
 
-\begin{subsection}{Proof of Corollary \ref{co:sum_power}}\label{ap:sum_power}
-	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} we have
+\begin{subsection}{Proof of Corollary \ref{co:nd_power}}
+	\label{ap:nd_power}
+	From \eqref{eq:ris_decompose} and \eqref{eq:channel_nd} we have
 	\begin{equation}
@@
 		\end{split}
-		\label{eq:channel_power_gain}
 	\end{equation}
@@
 	\end{equation*}
-	which simplifies to \eqref{iq:power_gain}.
+	which simplifies to \eqref{iq:power_nd}.
 	The upper bound is attained when $\mathbf{X}$ is chosen to match the singular values of $\tilde{\mathbf{F}}$ to those of $\tilde{\mathbf{B}}$ in similar order.
@@
 
-\begin{subsection}{Proof of Corollary \ref{co:capacity}}\label{ap:capacity}
+\begin{subsection}{Proof of Corollary \ref{co:nd_capacity}}
+	\label{ap:nd_capacity}
 	When perfect \gls{csi} is available at the transmitter, in the low-\gls{snr} regime, the capacity is achieved by dominant eigenmode transmission \cite[(5.26)]{Clerckx2013}
@@
 	\end{align*}
-	where the approximation is $\log(1 + x) \approx x$ for small $x$ and the inequality follows from \eqref{iq:sv_product_largest} with $k=1$.
+	where the approximation is $\log(1 + x) \approx x$ for small $x$ and the inequality follows from \eqref{iq:sv_nd_prod_largest} with $k=1$.
 	In the high-\gls{snr} regime, the capacity is achieved by multiple eigenmode transmission with uniform power location \cite[(5.27)]{Clerckx2013}
@@
 	\end{align*}
-	where the approximation is $\log(1 + x) \approx \log(x)$ for large $x$ and the inequality follows from \eqref{iq:sv_product_largest} with $k=N$.
-
-	We then show \eqref{eq:power_max} can achieve the upper bounds in \eqref{iq:capacity_snr_low} and \eqref{iq:capacity_snr_high} simultaneously.
-	On the one hand, \eqref{eq:power_max} is a special case of \eqref{eq:sv_nth_max} with $\mathbf{P} = \mathbf{I}$, which satisfies \eqref{eq:sv_nth_max_pair} and \eqref{eq:sv_nth_max_condition} for $n=1$ and thus attain $\sigma_1(\mathbf{H}) = \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
-	On the other hand, since $\log(\cdot)$ is a monotonic function, we can prove similar to Appendix \ref{ap:sum_power} that $\sum_{n=1}^N \log \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \log \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})$ and the bound is tight at \eqref{eq:power_max}.
+	where the approximation is $\log(1 + x) \approx \log(x)$ for large $x$ and the inequality follows from \eqref{iq:sv_nd_prod_largest} with $k=N$.
+
+	We then show \eqref{eq:ris_nd_power_max} can achieve the upper bounds in \eqref{iq:capacity_nd_snr_low} and \eqref{iq:capacity_nd_snr_high} simultaneously.
+	On the one hand, \eqref{eq:ris_nd_power_max} is a special case of \eqref{eq:ris_nd_sv_indl_max} with $\mathbf{P} = \mathbf{I}$, which satisfies \eqref{eq:idx_nd_sv_indl_max} and \eqref{eq:perm_nd_sv_indl_max} for $n=1$ and thus attain $\sigma_1(\mathbf{H}) = \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
+	On the other hand, since $\log(\cdot)$ is a monotonic function, we can prove similar to Appendix \ref{ap:nd_power} that $\sum_{n=1}^N \log \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \log \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})$ and the bound is tight at \eqref{eq:ris_nd_power_max}.
 	The proof is complete.
@@
 
-\begin{subsection}{Proof of Lemma \ref{lm:pareto_gradient}}\label{ap:pareto_gradient}
-	Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the compact \gls{svd} of the equivalent channel.
+\begin{subsection}{Proof of Proposition \ref{pp:shaping}}
+	\label{ap:shaping}
+	The sub-differential of a symmetric gauge function of singular values of a matrix with respect to the matrix itself is given by \cite[Theorem 2]{Watson1992}
+	\begin{equation}
+		\partial_{\mathbf{H}^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \bigr\},
+	\end{equation}
+	% $$\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$$
+	where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
+	It implies
+	\begin{align*}
+		\partial f\bigl(\sv(\mathbf{H})\bigr)
+		& \ni \tr \bigl(\mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \partial \mathbf{H}^*\bigr) \\
+		& = \tr \bigl(\mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \mathbf{H}_{\mathrm{F},g}^*\bigr) \\
+		& = \tr \bigl(\mathbf{H}_{\mathrm{F},g}^* \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \bigr),
+	\end{align*}
+	% \begin{align*}
+	% 	\partial f\bigl(\sv(\mathbf{H})\bigr)
+	% 	& = \tr \bigl(\conv \{ \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \} \partial \mathbf{H}^*\bigr) \\
+	% 	& = \tr \bigl(\conv \{ \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \mathbf{H}_{\mathrm{F},g}^* \}\bigr) \\
+	% 	& = \tr \bigl(\conv \{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \}\partial {\mathbf{\Theta}_g^*} \bigr)
+	% \end{align*}
+	and therefore $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ constitutes a sub-gradient of $f\bigl(\sv(\mathbf{H})\bigr)$ with respect to $\mathbf{\Theta}_g$.
+	The convex hull of those sub-gradients is the sub-differential \eqref{eq:shaping_subdiff}.
+\end{subsection}
+
+\begin{subsection}{Proof of Lemma \ref{lm:pareto}}
+	\label{ap:pareto}
+	The sub-differential of $\sigma_n(\mathbf{H})$ with respect to $\mathbf{H}$ is given by
+	\begin{equation*}
+		\partial \sigma_n(\mathbf{H}) = \mathbf{u}_n \mathbf{v}_n^\mathsf{H},
+	\end{equation*}
+
+	Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the \gls{svd} of the equivalent channel.
 	Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
 	\begin{equation}
-		\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*,
-	\end{equation}
-	whose differential with respect to $\mathbf{\Theta}_g^*$ is
+		\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*.
+	\end{equation}
+
+	Let $f(\mathbf{\Theta}_g) = \sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})$. Its sub-differential is defined as
+	\begin{equation}
+		\Bigl\{\mathbf{Y} \mid f(\tilde{\mathbf{\Theta}}_g) \ge f(\mathbf{\Theta}_g) + \tr\bigl(\mathbf{Y}^\mathsf{H} (\tilde{\mathbf{\Theta}}_g - \mathbf{\Theta}_g)\bigr), \forall \tilde{\mathbf{\Theta}}_g \in \mathbb{U}^{L \times L}\Bigr\}.
+	\end{equation}
+
+	whose sub-gradient with respect to $\mathbf{\Theta}_g^*$ is
 	\begin{align*}
 		\partial \sigma_n
-		 & = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^* \\
+		 & = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n^*} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^* \\
 		 & = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}                                                                                                                  \\
@@
 	\begin{equation}
+		\label{eq:gradient_eucl_sv_indl}
 		\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-		\label{eq:derivative_sv}
-	\end{equation}
-	A linear combination of \eqref{eq:derivative_sv} yields \eqref{eq:pareto_gradient}.
+	\end{equation}
+	A linear combination of \eqref{eq:gradient_eucl_sv_indl} yields \eqref{eq:gradient_eucl_pareto}.
 \end{subsection}
 
-\begin{subsection}{Proof of Proposition \ref{pp:power}}\label{ap:power}
-The differential of \eqref{ob:power_passive} with respect to $\mathbf{\Theta}_g^*$ is
+\begin{subsection}{Proof of Proposition \ref{pp:power}}
+	\label{ap:power}
+The differential of \eqref{ob:power} with respect to $\mathbf{\Theta}_g^*$ is
 \begin{align*}
@@
 \end{equation}
-% For a given $\mathbf{\Theta}$, we approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansion and recast problem \eqref{op:power_passive} as
-
-First, we approximate the quadratic objective \eqref{ob:power_passive} by its local Taylor expansion
+% For a given $\mathbf{\Theta}$, we approximate the quadratic objective \eqref{ob:power} by local Taylor expansion and recast problem \eqref{op:power} as
+
+First, we approximate the quadratic objective \eqref{ob:power} by its local Taylor expansion
 \begin{maxi!}
-{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_passive_approx}}{\label{ob:power_passive_approx}}
+{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_ris_taylor}}{\label{ob:power_ris_taylor}}
 \addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
 \end{maxi!}
-Let $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$ be the compact \gls{svd} of $\mathbf{M}_g$.
+Let $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$ be the \gls{svd} of $\mathbf{M}_g$.
 We have
@@
 \end{equation}
-The upper bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$, which implies the optimal solution of \eqref{op:power_passive_approx} is $\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$, $\forall g$.
-
-Next, we prove that solving \eqref{op:power_passive_approx} successively does not decrease \eqref{ob:power_passive}.
-Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_passive_approx}, we have $\sum_g 2 \Re\bigl\{ \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_passive_approx}.
-% \begin{equation}
-% 	\label{iq:power_passive_approx}
+The upper bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$, which implies the optimal solution of \eqref{op:power_ris_taylor} is $\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$, $\forall g$.
+
+Next, we prove that solving \eqref{op:power_ris_taylor} successively does not decrease \eqref{ob:power}.
+Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_ris_taylor}, we have $\sum_g 2 \Re\bigl\{ \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_ris_taylor}.
+% \begin{equation}
+% 	\label{iq:power_ris_taylor}
 % 	\scriptstyle
@@
 \begin{multline}
-	\label{iq:power_passive_approx}
+	\label{iq:power_ris_taylor}
 	\scriptstyle{2 \Re \bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}} \\
@@
 \end{multline}
-% Expanding both side gives \eqref{iq:power_passive_approx}.
-On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:nonnegative_norm_square}.
+% Expanding both side gives \eqref{iq:power_ris_taylor}.
+On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:auxiliary_nonnegative}.
 \begin{multline}
-	\label{iq:nonnegative_norm_square}
+	\label{iq:auxiliary_nonnegative}
 	\scriptstyle{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} }\\
@@
 \end{multline}
-Adding \eqref{iq:power_passive_approx} and \eqref{iq:nonnegative_norm_square}, we have
+Adding \eqref{iq:power_ris_taylor} and \eqref{iq:auxiliary_nonnegative}, we have
 \begin{multline}
@@
 \end{multline}
-which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power_passive}.
+which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power}.
 % \begin{figure*}
 % \begin{equation}
-% 	\label{iq:power_passive_approx}
+% 	\label{iq:power_ris_taylor}
 % 	\resizebox{0.95\textwidth}{!}{
@@
 % 	\begin{equation}
-% 		\label{iq:nonnegative_norm_square}
+% 		\label{iq:auxiliary_nonnegative}
 % 		\resizebox{0.95\textwidth}{!}{
@@
 
-Finally, we prove that the converging point of \eqref{op:power_passive_approx}, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power_passive}.
-The \gls{kkt} conditions of \eqref{op:power_passive} and \eqref{op:power_passive_approx} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
+Finally, we prove that the converging point of \eqref{op:power_ris_taylor}, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power}.
+The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
 \begin{gather}
-	\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_passive_stationary}\\
-	\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_passive_approx_stationary}
+	\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_ris_optimal}\\
+	\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_ris_taylor_optimal}
 \end{gather}
-On convergence, \eqref{eq:power_passive_approx_stationary} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
+On convergence, \eqref{eq:power_ris_taylor_optimal} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
 \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^?
-\mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_passive_stationary}.
+\mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_ris_optimal}.
 The proof is thus completed.
@@
 
-\begin{subsection}{Proof of Lemma \ref{lm:rate_gradient}}\label{ap:rate_gradient}
+\begin{subsection}{Proof of Lemma \ref{lm:rate}}
+	\label{ap:rate}
 	The differential of $R$ with respect to $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
@@
 	\end{align*}
-	and the corresponding complex derivative is \eqref{eq:rate_gradient}.
+	and the corresponding complex derivative is \eqref{eq:gradient_eucl_rate}.
 \end{subsection}

### 2024-12-20 assets/simulation/pc_power_sx_txrx16.tex
:construction: Updating structure

--- 2024-11-20 assets/poster/power_sx_txrx16.tex
@@
 yminorgrids,
-legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
-font=\tiny,
-title style={font=\tiny},
-label style={font=\tiny},
-ticklabel style={font=\tiny},
-legend style={font=\tiny},
-x label style={yshift=10pt},
-y label style={yshift=-7pt}
+legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
 ]

### 2024-12-20 assets/simulation/pc_power_sx_txrx16_nd.tex
:construction: Updating structure

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor3}{rgb}{0.92941,0.69412,0.12549}%
\definecolor{mycolor4}{rgb}{0.49412,0.18431,0.55686}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\begin{tikzpicture}

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
% xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymode=log,
% ymin=0,
ymax=0.000115917330108446,
yminorticks=true,
% ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot [color=mycolor1, line width=2.0pt]
  table[row sep=crcr]{%
1	5.62265231393471e-07\\
2	6.30889582242226e-07\\
3	7.11254960263e-07\\
4	7.81326631210281e-07\\
5	8.14448482525861e-07\\
};
\addlegendentry{$N_\mathrm{S} = 16$}

\addplot [color=mycolor2, dashed, line width=2.0pt]
  table[row sep=crcr]{%
1	1.28776059362021e-06\\
2	1.49666859439015e-06\\
3	1.7748873501561e-06\\
4	2.08628203322482e-06\\
5	2.32064182394341e-06\\
6	2.40700699069632e-06\\
};
\addlegendentry{$N_\mathrm{S} = 32$}

\addplot [color=mycolor3, dotted, line width=2.0pt]
  table[row sep=crcr]{%
1	3.15006337524297e-06\\
2	3.87312444339353e-06\\
3	4.86242306926796e-06\\
4	6.08760688271974e-06\\
5	7.25680982863437e-06\\
6	7.92125259488618e-06\\
7	8.12946998504463e-06\\
};
\addlegendentry{$N_\mathrm{S} = 64$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt]
  table[row sep=crcr]{%
1	8.09679926499813e-06\\
2	1.03932623438214e-05\\
3	1.38959563603953e-05\\
4	1.85906493199221e-05\\
5	2.38130628567437e-05\\
6	2.73295770613527e-05\\
7	2.8861300924676e-05\\
8	2.93516301422595e-05\\
};
\addlegendentry{$N_\mathrm{S} = 128$}

\addplot [color=mycolor5, line width=2.0pt]
  table[row sep=crcr]{%
1	2.17722070426804e-05\\
2	2.9526076730669e-05\\
3	4.18291043077588e-05\\
4	5.97087109667717e-05\\
5	8.17036753929845e-05\\
6	9.7962703850956e-05\\
7	0.000105935331911385\\
8	0.000109247922920587\\
9	0.000110397457246139\\
};
\addlegendentry{$N_\mathrm{S} = 256$}

\end{axis}
\end{tikzpicture}%

### 2024-12-20 assets/simulation/pc_singular_bound_rank1_sx32.tex
:construction: Updating structure

--- 2024-05-27 assets/simulation/singular_bound_rank1_sx32.tex
@@
 ]
-\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
 0.8375	0.00172515536422714\\
@@
 
-\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
 1.1625	0.00172516728828725\\

### 2024-12-20 assets/simulation/pc_singular_bound_rank1_sx64.tex
:construction: Updating structure

--- 2024-05-27 assets/simulation/singular_bound_rank1_sx64.tex
@@
 ]
-\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
 0.8375	0.00195358578718362\\
@@
 
-\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
 1.1625	0.00195358621182515\\

### 2024-12-20 assets/simulation/pc_singular_bound_rank4_sx256.tex
:construction: Updating structure

--- 2024-05-27 assets/simulation/singular_bound_rank4_sx256.tex
@@
 ]
-\addplot[ybar stacked, fill=mycolor1, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
 0.8375	0.000590158480426682\\
@@
 
-\addplot[ybar stacked, fill=mycolor4, fill opacity=0, draw=none, forget plot] table[row sep=crcr] {%
+\addplot[ybar stacked, fill=none, draw=none, forget plot] table[row sep=crcr] {%
 1.1625	0.000346385584583973\\

### 2024-12-20 manuscript/main.tex
:construction: Updating structure

@@
 % \title{MIMO Channel Shaping and Rate Maximization via Beyond Diagonal RIS}
+% \title{MIMO Channel Shaping Using Beyond Diagonal RIS: Singular Value Redistribution and Rate Maximization}
 \title{Beyond Diagonal RIS: MIMO Channel Shaping and Rate Maximization}
-% \title{MIMO Channel Shaping Using Beyond Diagonal RIS: Singular Value Redistribution and Rate Maximization}
 \author{
@@
 	% A low-complexity suboptimal solution based on channel shaping is also proposed, where the decoupled problem is formulated as channel power maximization and solved in closed form iteratively.
-	% % We then show how channel shaping decouples the design and amounts to a low-complexity suboptimal solution.
+	% % We now show how channel shaping decouples the design and amounts to a low-complexity suboptimal solution.
 	% % A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved in closed form iteratively.
@@
 		% The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-		% We then discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
+		% We now discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
 		% This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
@@
 	$\jmath$ denotes the imaginary unit.
-	$\mathbb{C}$ represents the set of complex numbers.
+	% $\mathbb{C}$ represents the set of complex numbers.
 	$\mathbb{H}^{n \times n}$, $\mathbb{H}_+^{n \times n}$, and $\mathbb{U}^{n \times n}$ denote the set of $n \times n$ Hermitian, positive semi-definite, and unitary matrices, respectively.
-	$\mathbf{0}$ and $\mathbf{I}$ are the all-zero and identity matrices with appropriate size, respectively.
-	% $\Re\{\cdot\}$ and $\mathrm{arg}(\cdot)$ take the real part and argument of a complex number, respectively.
+	% $\mathbf{0}$ and $\mathbf{I}$ are the all-zero and identity matrices with appropriate size, respectively.
 	$\Re\{\cdot\}$ takes the real part of a complex number.
-	$\tr(\cdot)$ and $\det(\cdot)$ evaluate the trace and determinant of a square matrix, respectively.
-	$\diag(\cdot)$ constructs a square matrix by placing the inputs on the main (block) diagonal and zeros elsewhere.
-	$\sv(\cdot)$ extracts the singular values of a matrix as a non-ascending vector.
+	% $\tr(\cdot)$ and $\det(\cdot)$ evaluate the trace and determinant of a square matrix, respectively.
+	$\diag(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
+	$\sv(\cdot)$, $\ran(\cdot)$, and $\ker(\cdot)$ evaluate the singular values (in descending order), column space (range), and kernel of a matrix, respectively.
+	% $\sv(\cdot)$ extracts the singular values of a matrix as a non-ascending vector.
 	% $\card(\cdot)$ returns the cardinality of a set.
@@
 	$\odot$ denotes the element-wise (Hadamard) product.
-	$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
+	$\mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
 	$\sim$ means ``distributed as''.
@@
 \begin{section}{System Model}
-	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
-	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ throughout the paper.
-	The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
+	\begin{subsection}{BD-RIS}
+		The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
 		Apparently $N_\mathrm{S} = \sum_{g=1}^G N_g$.
-	We assume all groups have the same size $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$ yet the discussion is extendable to \gls{bd}-\gls{ris} with unequal group size.
-	To establish a theoretical performance bound, we consider a lossless asymmetric\footnote{A symmetric solution can be enforced by projection $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$ if necessary.
-We will compare the performance of symmetric and asymmetric \gls{bd}-\gls{ris} in Section~\ref{sc:simulation}.} \gls{bd}-\gls{ris} without mutual coupling as previously discussed in \cite{Li2023b,Li2023c,Bartoli2023}.
-	The overall scattering matrix of the \gls{bd}-\gls{ris} is block-diagonal
-	% \footnote{Following footnote \ref{fn:symmetric}, we do not constrain the scattering matrix to be symmetric in the paper.
-One can enforce such by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$ if necessary.}
-	\begin{equation}
+		Without loss of generality we assume equal size for all groups $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$ and no mutual coupling between elements.
+		For asymmetric \gls{bd}-\gls{ris}, the overall scattering matrix is block-diagonal with unitary blocks\footnote{We assume asymmetric network by default to establish a benchmark for passive \gls{ris}.
+Some symmetric solutions (i.e., $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$) will be discussed and their performance will be evaluated in Section~\ref{sc:simulation}.}
+		\begin{equation}
+			\label{eq:ris}
 			\mathbf{\Theta} = \diag(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
 		\end{equation}
-	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary diagonal block modeling the response of group $g$.
-	It is noteworthy that the conventional \gls{d}-\gls{ris} is an extreme case of \gls{bd}-\gls{ris} with group size $L=1$.
-	% We highlight that conventional \gls{d}-\gls{ris} is an extreme case of \gls{bd}-\gls{ris} with group size $L=1$.
-	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2024}, where the
-	array geometry and
-	circuit topology has been modeled in the scattering matrix.
+		where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th diagonal block modeling the response of group $g$.
+		It is noteworthy that \gls{d}-\gls{ris} is an extreme case of \eqref{eq:ris} with group size $L=1$, that is, each element is an individual.
+		Some viable architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
+3]{Shen2020a}, \cite[Fig.
+5]{Li2023c}, \cite[Fig.
+2]{Nerini2024} where the array geometry and circuit topology are modeled in $\mathbf{\Theta}$.
+	\end{subsection}
+
+	\begin{subsection}{MIMO Point-to-Point Channel}
+		Consider a \gls{bd}-\gls{ris} aided \gls{mimo} \gls{pc} with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
+		This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$.
 		Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (i.e., transmitter-receiver), backward (i.e., \gls{ris}-receiver), and forward (i.e., transmitter-\gls{ris}) channels, respectively.
@@
 			\label{eq:channel}
-		% \mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \underbrace{\mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}}_{\triangleq \mathbf{H}_g} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
 			\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \triangleq \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
@@
 		where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary factor matrices.
-	Let $\mathbf{H}_{\mathrm{B},g} = \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \mathbf{V}_{\mathrm{B},g}^\mathsf{H}$ and $\mathbf{H}_{\mathrm{F},g} = \mathbf{U}_{\mathrm{F},g} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
-	The equivalent channel can thus be rewritten as
+		Let $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
+		The equivalent channel is thus
 		\begin{equation}
@@
 
-	% \begin{remark}
-	We observe from \eqref{eq:channel_svd} that the \gls{bd}-\gls{ris} plays a crucial role in combining
-	% needs to strike a balance between
-	backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
-	These two attributes are refined below and discussed in an example.
-	% We conclude from \eqref{eq:channel_svd} that the scattering matrix of \gls{bd}-\gls{ris} provide two channel shaping potentials:
-	% By analyzing \eqref{eq:channel_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
-	% Channel rearrangement refers to rearrange and recombine the forward and backward channel branches by their strength.
-	% Space alignment generalizes phase matching in \gls{siso} and \gls{miso} to the high-dimensional singular vector space in \gls{mimo}.
+		\begin{remark}
+		In \eqref{eq:channel_svd}, the \gls{bd}-\gls{ris} performs a blockwise unitary transformation to combine the backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
+		These two attributes are refined as:
 		\begin{itemize}
-		\item \emph{Branch matching:} It refers to pairing and combining the branches (i.e., entries) of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ through unitary transformation $\mathbf{\Theta}_g$.
-			% That is,
-			% % entries of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ by their strength.
-			% % rearranging and recombining the backward and forward channel branches (i.e., entries of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$)
-			% % associated with each group
-			% % by their strength.
-			% % This unique feature of \gls{bd}-\gls{ris} exploits \textcolor{red}{spatial diversity} effectively thanks to in-group connections.
-			% % This unique feature of \gls{bd}-\gls{ris} exploits the \textcolor{red}{spatial diversity} by rearranging and combining the backward and forward channel branches within each group.
-			% In \gls{siso}\footnote{Following previous notation, here we denote the direct channel as $h_\mathrm{D}$, the backward and forward channels as $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$ and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, whose $n$-th entries are $h_{\mathrm{B},n}$ and $h_{\mathrm{F},n}$, respectively.
-			% The channels associated with \gls{bd}-\gls{ris} group $g$ are also denoted as $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{1 \times L}$, whose $l$-th entries are $h_{\mathrm{B},g,l}$ and $h_{\mathrm{F},g,l}$, respectively.}, \gls{d}-\gls{ris} with perfect phase matching can provide a maximum indirect channel gain $g_\mathrm{D}=\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$,
-			% % Thanks to in-group connections,
-			% while \gls{bd}-\gls{ris} can exploit in-group connections and generalize it to
-			% % this indirect channel gain to
-			% $g_\mathrm{BD}=\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert$,
-			% % $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$,
-			% % $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,l} \rvert \lvert h_{\mathrm{F},g,\pi_g(l)} \rvert$,
-			% where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are arbitrary permutations of $[L]$.
-			% Note the first summation is over groups and the second summation is over permuted channels.
-			% By rearrangement inequality \cite[Inequality 10.2.1]{Hardy1952}, for \gls{bd}-\gls{ris} we have
-			% \begin{equation}
-			% 	g_\mathrm{BD} \le \sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},g,\pi^\downarrow_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi^\downarrow_{\mathrm{F},g}(l)} \rvert,
-			% 	\label{eq:gain_rearrangement}
-			% \end{equation}
-			% where $\pi^\downarrow_{\mathrm{B},g}$ and $\pi^\downarrow_{\mathrm{F},g}$ sort $\{\lvert h_{\mathrm{B},g,l} \rvert\}_{l=1}^L$ and $\{\lvert h_{\mathrm{F},g,l} \rvert\}_{l=1}^L$ in descending orders, respectively.
-			% % are the descending permutations of $\lvert h_{\mathrm{B},g,l} \rvert$ and $\lvert h_{\mathrm{F},g,l} \rvert$, respectively.
-			% That is to say, when the direct channel is blocked,
-			% the maximum \gls{siso} channel gain is attained if the \gls{bd}-\gls{ris} pairs the $l$-th strongest backward and forward branches within each group.
-			% % \footnote{Similarly, the minimum is attained when we pair the $l$-th strongest backward branch and the $L{-}l{+}1$-th strongest forward branch within each group.}
-			% % We thus conclude that \gls{bd}-\gls{ris} exploits \textcolor{red}{spatial diversity} effectively thanks to in-group connections.
-			% % By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
-			% % , providing up to \qty{62.5}{\percent} asymptotic power gain over \gls{d}-\gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
-			% Since the number of channels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude that {the advantage of \gls{bd}-\gls{ris} in channel rearrangement scales with \gls{mimo} dimensions.}
-		\item \emph{Mode alignment:} It refers to aligning and ordering the modes (i.e., singular vectors) of $\{\mathbf{H}_g\}_{g \in [G]}$ with those of $\mathbf{H}_\mathrm{D}$ through unitary transformations $\{\mathbf{\Theta}_g\}_{g \in [G]}$.
-			% The \gls{bd}-\gls{ris} needs to strike a balance between the space alignment of backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
-In \gls{siso}, singular vectors reduce to scalars and space alignment reduce to phase matching, such that the scattering matrix of group $g$ maximizing the channel gain is
-			% \begin{equation}
-			% 	\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
-			% 	\label{eq:scattering_siso}
-			% \end{equation}
-			% where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-			% We notice that \gls{d}-\gls{ris} (i.e., $L=1$) suffices
-			% % \gls{d}-\gls{ris} thus suffices
-			% for perfect phase matching in \gls{siso}.
-			% When it comes to \gls{mimo}, each \gls{d}-\gls{ris} element can only apply a scalar phase shift to the corresponding indirect channel matrix of size $N_\mathrm{R} \times N_\mathrm{T}$ defined in \eqref{eq:channel}.
-			% We thus conclude that the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.
-			% % When it comes to \gls{mimo}, element $g$ of \gls{d}-\gls{ris} can only apply a common phase shift to the ``pinhole''\footnote{The pinhole effect refers to channel rank reduction due to diffraction in the propagation environment \cite{Almers2006}.
-For element $g$ of \gls{d}-\gls{ris}, the indirect channel $\mathbf{H}_g$ is rank-1 and the pinhole is $\Theta_g$.} indirect channel passing through itself by $\mathbf{H}_g = \mathbf{h}_{\mathrm{B},g} \Theta_g \mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$.
-			% % Thus, we conclude that
-			% % We can thus see that
-			% % {the disadvantage of \gls{d}-\gls{ris} in space alignment deteriorates with \gls{mimo} dimensions.}
-			% % As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward spaces.
+			\item \emph{Branch matching:} It refers to pairing and combining the branches (i.e., entries) of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ through $\mathbf{\Theta}_g$.
+			\item \emph{Mode alignment:} It refers to aligning and ordering the modes (i.e., singular vectors) of $\{\mathbf{H}_g\}_{g \in [G]}$ with those of $\mathbf{H}_\mathrm{D}$ through $\{\mathbf{\Theta}_g\}_{g \in [G]}$.
 		\end{itemize}
-	% \end{remark}
-
-	% We use the following examples to show that a stronger branch matching capability enables better mode alignment and results in more flexible channel shaping.
-	% The following example clarifies the difference in between and show their impacts on channel shaping.
+		\end{remark}
 
@@
 			Denote the direct, backward, forward channels as $h_\mathrm{D}$, $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$, and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, respectively.
-		In this case, mode alignment boils down to phase matching and any $L \in [N_\mathrm{S}]$ (including \gls{d}-\gls{ris}) suffices for perfect alignment between $h_\mathrm{D}$ and indirect channels $\{h_g\}_{g \in [G]}$ using
-		% the scattering matrix maximizing the channel gain is
-		\begin{equation}
-			\mathbf{\Theta}_g^\textnormal{\gls{siso}} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H}, \quad \forall g,
-		\end{equation}
-		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are orthonormal bases of null spaces of $\mathbf{h}_{\mathrm{B},g}, \mathbf{h}_{\mathrm{F},g} \in \mathbb{C}^{L \times 1}$, respectively.
-		The corresponding channel gain is a function of $L$
-		% Here any $L \in [N_\mathrm{S}]$ (including \gls{d}-\gls{ris}) suffices for perfect mode alignment between $h_\mathrm{D}$ and indirect channels $\{h_g\}_{g \in [G]}$ using \eqref{eq:scattering_siso}.
-		% However, the branch matching capability is a function of $L$ and the channel gain can be manipulated
-		\begin{equation}
-			\max_\mathbf{\Theta} \ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
-		\end{equation}
-		where $h_{\mathrm{B},g,l}$, $h_{\mathrm{F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively, and $\pi_{\mathrm{B},g}$, $\pi_{\mathrm{F},g}$ are permutations of $[L]$ sorting their magnitude in similar orders.
-		That is, the maximum channel gain is attained when each group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
-		A larger $L$ provides better branch matching flexibility and can thus grant a higher channel gain.
-		% It is evident that the branch matching capability increases with $L$.
-		% the backward and forward channels as $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$ and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, whose $n$-th entries are $h_{\mathrm{B},n}$ and $h_{\mathrm{F},n}$, respectively.
-		% The channels associated with \gls{bd}-\gls{ris} group $g$ are also denoted as $\mathbf{h}_{\mathrm{B},g} \in \mathbb{C}^{L \times 1}$ and $\mathbf{h}_{\mathrm{F},g}^\mathsf{H} \in \mathbb{C}^{1 \times L}$, whose $l$-th entries are $h_{\mathrm{B},g,l}$ and $h_{\mathrm{F},g,l}$, respectively.
+			In this case, mode alignment boils down to phase matching and any $L \in [N_\mathrm{S}]$, including \gls{d}-\gls{ris}, suffices for perfect mode alignment using
+			\begin{equation}
+				\mathbf{\Theta}_{\textnormal{P-max},g}^\textnormal{SISO} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H}, \quad \forall g,
+			\end{equation}
+			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B/F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of kernels of $\mathbf{h}_{\mathrm{B/F},g}$.
+			Evidently, the maximum channel gain is a function of $L$
+			\begin{equation}
+				\ \lvert h \rvert _{\max} = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
+			\end{equation}
+			where $h_{\mathrm{B/F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B/F},g}$, and $\pi_{\mathrm{B/F},g}$ are permutations of $[L]$ sorting their magnitude in similar orders.
+			That is, the maximum \gls{siso} channel gain is attained when each \gls{bd}-\gls{ris} group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches therein.
+			A larger $L$ provides more flexible branch matching and thus higher channel gain.
 		\end{example}
@@
 		Example~\ref{eg:siso} clarifies the difference between branch matching and mode alignment and show their impacts on channel shaping.
-	When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching is more pronounced since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$.
-On the other hand, the disadvantage of \gls{d}-\gls{ris} in mode alignment deteriorates since each element can only apply a scalar phase shift to the resulting indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ modes.
-	% of size $N_\mathrm{R} \times N_\mathrm{T}$, which renders the alignment of multiple modes difficult.
-	% following examples aim to help the readers understanding both potentials.
-
-	% TODO: add illustrations for both
-
-	% In \gls{siso}, the equivalent channel can be further simplified as
-	% \begin{equation}
-	% 	h = h_\mathrm{D} + \sum_g \mathbf{h}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{h}_{\mathrm{F},g},
-	% \end{equation}
-	% space alignment boils down to phase matching
-
-	% For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-	% This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
-	% Interestingly, the gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
-	% This is because space alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-	% That is, \gls{d}-\gls{ris} is sufficient for space alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from channel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
-	% Now consider a \gls{d}-\gls{ris} in \gls{mimo}.
-	% Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-	% Therefore, perfect space alignment of indirect channels through different elements is generally impossible.
-	% It means the disadvantage of \gls{d}-\gls{ris} in space alignment and channel rearrangement scales with \gls{mimo} dimensions.
-	% We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
-
-	% \begin{equation}
-	% 	\mathbf{H} = \underbrace{\mathbf{H}_\mathrm{D} + \underbrace{\sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}_\text{group-wise}}_\text{direct-indirect},
-	% \end{equation}
-	% which involves three space alignment problems:
-	% which involves three space alignment problems
-	% \begin{equation}
-	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{backward-forward}\\\text{additive alignment}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
-	% \end{equation}
-	% \begin{equation}
-	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g}_{\substack{\text{backward}\\\text{align}}} \underbrace{\mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{forward}\\\text{align}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
-	% \end{equation}
-	% Then the equivalent channel can be rewritten as
-	% Since the field of (block) unitary matrices formulate a field that is closed under multiplication
-	% Since block unitary matrices satisfy the axioms of a field under matrix multiplication
-	% \begin{remark}
-	% 	% To understand the \gls{b} gain from in-group connections
-	% \end{remark}
-
-	% \begin{remark}
-	% 	From \eqref{eq:ris_decompose} and \eqref{eq:channel_nd} in the proof of Proposition \ref{pp:nd}, we notice that \eqref{iq:horn}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-	% 	% Interestingly, \eqref{iq:horn}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-	% 	\begin{equation}
-	% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
-	% 		\label{eq:scattering_fc_tight}
-	% 	\end{equation}
-	% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
-	% 	\begin{itemize}
-	% 		\item space alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:ris_decompose} fully align the spaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-	% 		\item channel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_nd} pairs the channels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
-	% 	\end{itemize}
-	% \end{remark}
-
-	% \begin{remark}
-	% 	\gls{bd}-\gls{ris} reduces to \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
-	% \end{remark}
-	% \begin{remark}
-	% 	Individual forward and backward \gls{csi} are required for \gls{bd}-\gls{ris} designs.
-	% 	This is different from \gls{d}-\gls{ris} where estimating their product is usually sufficient.
-	% 	% Later we will show the potential benefits from the \gls{csi} overhead.
-	% \end{remark}
+		When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching improves since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$.
+On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment worsens since each element can only apply a phase shift to the indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ modes.
+	\end{subsection}
+
+	\begin{subsection}{MIMO Interference Channel}
+		We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} \gls{ic} of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
+		This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
+		Let $\mathbf{H}_\mathrm{D}^{[kj]} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{[k]} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{[j]} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
+		Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
+		The equivalent channel from transmitter $j$ to receiver $k$ is
+		\begin{equation}
+			\mathbf{H}^{[kj]} = \mathbf{H}_\mathrm{D}^{[kj]} + \mathbf{H}_\mathrm{B}^{[k]} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{[j]} = \mathbf{H}_\mathrm{D}^{[kj]} + \sum_g \mathbf{H}_{\mathrm{B},g}^{[k]} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{[j]},
+			\label{eq:channel_equivalent_ic}
+		\end{equation}
+		where $\mathbf{H}_{\mathrm{B},g}^{[k]} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{[j]} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B},g}^{[k]}$ and rows of $\mathbf{H}_{\mathrm{F},g}^{[j]}$, respectively,
+	\end{subsection}
 \end{section}
 
-	\begin{section}{Analytical Shaping Bounds}
-		\label{sc:bounds}
-	In this section, we first provide an example demonstrating the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds related to channel singular values under specific channel conditions.
-	% the channel singular values for both architectures.
-	% Next, we numerically characterize the attainable channel singular value region using Algorithm \ref{ag:rcg}.
-	% Finally, we derive
-	% Some analytical bounds on the channel singular values are derived for \gls{bd}-\gls{ris} and \gls{d}-\gls{ris} architectures.
-	% singular value bounds in specific channel conditions.
+\begin{section}{Channel Shaping}
+	In this section, we first provide an example demonstrating the \gls{mimo} channel shaping advantages of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds related to channel singular values under specific channel conditions, and provide closed-form \gls{bd}-\gls{ris} solution for several cases of interest.
+	Finally, we propose a numerical method to optimize the \gls{bd}-\gls{ris} for a special class of singular value function under general channel conditions.
 
@@
 		\label{eg:shaping_potential}
-		% We showcase the channel shaping capabilities of different \gls{ris} models by a toy example.
-		% Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
 		Here \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} can be modeled by 2 and 4 independent angular parameters, respectively:
-		% is modeled by $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the fully-connected \gls{bd}-\gls{ris} can be modeled by 4 independent angular parameters
 		\begin{equation*}
@@
 		\end{equation*}
-		% where $\phi$ has no impact on $\sv(\mathbf{H})$ since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
-		We consider a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
-		The singular value shaping capabilities of two \gls{ris} architectures can thus be compared visually over 2 tunable parameters.
+		We restrict the discussion to a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
+		The singular value shaping capabilities of $\mathbf{\Theta}_\mathrm{D}$ and $\mathbf{\Theta}_\mathrm{BD}$ can thus be compared visually over 2 tunable parameters.
 		\begin{figure}
 			\centering
-			\includegraphics[width=\columnwidth]{../assets/simulation/singular_trend.eps}
+			\includegraphics[width=\columnwidth]{../assets/simulation/pc_singular_trend.eps}
 			\caption{$2 \times 2 \times 2$ singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is negligible.
@@
 		\end{equation*}
-		% The results are obtained by an exhaustive grid search over $(\theta_1, \theta_2)$ for \gls{d}-\gls{ris} and $(\alpha, \psi)$ for symmetric \gls{bd}-\gls{ris}.
-		In this example, both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} using 2 symmetric components and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} using 3 symmetric components.
+		In this example, both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris}.
+		It is noteworthy that the former requires 2 circuit components and the latter requires 3.
 	\end{example}
 
-	% Example~\ref{eg:shaping_potential} shows that physically grouping some scattering elements produces a ``cooperation effect'' that significantly enhances the dynamic range of channel singular values.
-	Example~\ref{eg:shaping_potential} highlights that the physical grouping of \gls{ris} elements, even if using symmetric components, can produce a much wider dynamic range of channel singular values.
-	This motivates analytical and numerical studies on singular value shaping using \gls{bd}-\gls{ris}.
-	A selection of analytical bounds are presented in Propositions~\ref{pp:dof} -- \ref{pp:nd} and the resulting corollaries.
-	% The remainder of this section is organized as follows.
-
-	% We also provide some analytical bounds related to channel singular values, which help us to explore the limits of channel shaping using passive \gls{ris}.
-
-	\begin{definition}[Degrees of freedom]
-		\gls{dof} (a.k.a. multiplexing gain) refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, which is defined asymptotically as
-		\begin{equation}
-			d = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho},
-		\end{equation}
-		where $\rho$ is the \gls{snr}.
-
-	\end{definition}
-
-	% \begin{proposition}[Degrees of freedom]
-	% 	\label{pp:dof}
-	% 	In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
-	% \end{proposition}
-
+	Example~\ref{eg:shaping_potential} suggests that the physical interconnection of \gls{ris} elements, even if using symmetric circuit components, can create a ``cooperation effect'' that significantly enhances the dynamic range of channel singular values.
+	This motivates the analytical and numerical channel shaping studies in Section~\ref{sc:shaping_analytical} and \ref{sc:shaping_numerical}, respectively.
+
+	\begin{subsection}{Analytical Shaping Bounds}
+		\label{sc:shaping_analytical}
+		The main results of this subsection are presented in the following Propositions and Corollaries.
 		\begin{proposition}[Degrees of freedom]
 			\label{pp:dof}
-		In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{dof} than \gls{d}-\gls{ris}.
+			\gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof}\footnote{\gls{dof} refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel.
+It is defined as $\mathrm{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.} than \gls{d}-\gls{ris}.
 		\end{proposition}
@@
 
-	Proposition \ref{pp:dof} suggests that we cannot hope for a \gls{dof} gain (i.e., more parallel channels) by simply connecting the \gls{ris} elements.
-	We thus focus on the question of reshaping the available channels through manipulation of the singular values.
-
-	% you cannot hope for degrees of freedom gain (i.e. more channels) thus we focus ont he question of reshaping of the available channels through manipulation of the singular values.
+		Proposition \ref{pp:dof} suggests that we can expect more parallel streams or less interference when shaping the channel with \gls{bd}-\gls{ris}.
+		We now take a step further to examine the limits of redistributing channel singular values under specific channel conditions.
 
@@
 			\label{pp:rd}
-		% If the forward or backward channel is rank-$k$ ($k \le N$),
 			If the minimum rank of backward and forward channels is $k$ ($k \le N$),
@@
 		if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are at least rank $k$, then
-	% with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large number of scattering elements,
+		with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large $N_\mathrm{S}$,
 		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
@@
 		A special case is Corollary \ref{co:los} for \gls{los} channel\footnote{A similar eigenvalue result has been derived for \gls{d}-\gls{ris} only \cite{Semmler2023}.}.
-	% states that the $n$-th channel singular value can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$.
 
@@
 			\label{co:los}
-		% If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
-suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
-$n$-th) singular value of $\mathbf{T}$, that is,
 			If at least one of backward and forward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
@@
 
-	We emphasize that
-	% the inequalities in \eqref{iq:sv_rd} and \eqref{iq:sv_los}
-	Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
-	Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them
-	% The equalities in \eqref{iq:sv_rd} and \eqref{iq:sv_los}
-	can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible\footnote{Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
+		We emphasize that Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
+		Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible\footnote{Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
 This can result from a very large number of \gls{ris} elements (as discussed in Proposition~\ref{pp:rd}) or physical obstacles in the propagation path (as discussed in Proposition~\ref{pp:nd}).}.
@@
 		Proposition \ref{pp:rd} provides a reference on the selection of $N_\mathrm{S}$ in low-multipath application scenarios.
-	% Proposition \ref{pp:rd} evaluates the ultimate channel shaping limits of passive \gls{ris} and provides a benchmark for $N_\mathrm{S}$ selection in low-multipath deployment scenarios.
 		Next, we shift the focus to another popular \gls{ris} deployment scenario where the direct channel is blocked.
-	% finite-size fully-connected \gls{bd}-\gls{ris}.
 
@@
 			\label{pp:nd}
-		% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-
 			If the direct channel is negligible, then a fully-connected \gls{bd}-\gls{ris} can manipulate the channel singular values up to
-		% If the \gls{bd}-\gls{ris} is unitary and the direct link is blocked, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
-		% only bounds that apply here are those that apply to the singular values of
 			\begin{equation}
@@
 			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with $\sv(\mathbf{B})=\sv(\mathbf{H}_\mathrm{B})$ and $\sv(\mathbf{F})=\sv(\mathbf{H}_\mathrm{F})$.
-		% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
 		\end{proposition}
@@
 		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
-	Its importance lies in the fact that the initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
-	The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
-	% define\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [\bar{N}] \setminus [N]$.
-	% where we assume $N \le N_\mathrm{S}$ for the ease of notation and define\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices.} $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N_\mathrm{S}] \setminus [N]$.
-	% \footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $N = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N] \setminus [N]$}.
-	% over the notation\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}$, $\mathbf{H}_\mathrm{B}$, and $\mathbf{H}_\mathrm{F}$ to make square matrices, which generalizes relevant results to non-square case.} $N = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $n \in [N] \setminus [N]$.
-	% $N < n \le N$.
+		Its importance lies in the fact that our initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
+		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset}--\ref{co:nd_sv_indl} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
 		The results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
-	% We have the following corollaries.
 
@@
 			If the direct channel is negligible,
-		% and $N \le N_\mathrm{S}$
 			then the product of subset of singular values of $\mathbf{H}$ is bounded from above by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
@@
 
-	\eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:nd}.
-	% It is worth mentioning that t
-	% It also helps to induce lower bounds on the channel singular values.
-	The number of admissible triples increases exponentially with $N_\mathrm{S}$ despite some resulting bounds can be redundant.
-	Apart from the upper bounds, we will shortly see \eqref{iq:horn} can also induce lower bounds on channel singular values.
-	% It also helps to induce lower (instead of upper) bounds on channel singular values.
-	% ! For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.
-	% Besides, \eqref{iq:horn} helps to induce lower bounds
-	Those facts render the analysis of shaping limit non-trivial for massive \gls{ris}-aided \gls{mimo} systems.
-	Below we showcase some useful resulting bounds.
+		Inequality \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:nd}.
+		However, the number of admissible triples increases exponentially\footnote{For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.} with $N_\mathrm{S}$ despite some resulting bounds can be redundant.
+		We will shortly see \eqref{iq:horn} can also induce lower bounds on channel singular values.
+		Those facts render the shaping limit analysis non-trivial for large-scale \gls{ris}-aided \gls{mimo} systems.
+		Below we showcase some useful bounds therein.
 
@@
 			\label{co:nd_sv_prod_tail}
-		% \footnote{Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $N \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false) as the lower bounds would coincide at zero.}
-		% For any $k \in [N]$,
 			If the direct channel is negligible,
-		% and $N \le N_\mathrm{S}$
 			then the product of the first (resp.
@@
 below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
-		% the product of the first (resp. last) $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
-		% upper bounded by the product of first and last $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
-		% $k$ singular values of $\mathbf{H}$ can be upper bounded by the product of first $k$ singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by
 			\begin{subequations}
@@
 
-	% The assumption $N \le N_\mathrm{S}$
-
 		\begin{corollary}[Individual singular value]
@@
 			If the direct channel is negligible,
-		% and $N \le N_\mathrm{S}$,
 			then the $n$-th channel singular value can be manipulated up to
@@
 
-	% Although Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:nd}
-	% are derived under the assumption of negligible direct channel and fully-connected \gls{bd}-\gls{ris}, they are still useful for practical scenarios.
 		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of individual channel singular values.
@@
 		\end{subequations}
-	% where the arguments of $\max$ and $\min$ coincide at $\bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}}(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-1}(\mathbf{H}_\mathrm{F}), \ldots, \sigma_{N_\mathrm{S}}(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}$.
 		We notice that the right halves in \eqref{iq:sv_nd_largest} and \eqref{iq:sv_nd_smallest} are special cases of \eqref{iq:sv_nd_prod_largest} and \eqref{iq:sv_nd_prod_smallest} when $k=1$.
@@
 				\item \gls{bd}-\gls{ris}: According to \eqref{iq:sv_nd_indl}, a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
-				% \begin{align*}
-				% 	8 & \le \sigma_1(\mathbf{H}) \le 15, \\
-				% 	4 & \le \sigma_2(\mathbf{H}) \le 10, \\
-				% 	0 & \le \sigma_3(\mathbf{H}) \le 0,
-				% \end{align*}
 					\begin{equation*}
-					8 \le \sigma_1(\mathbf{H}) \le 15, \quad 4 \le \sigma_2(\mathbf{H}) \le 10, \quad 0 \le \sigma_3(\mathbf{H}) \le 0,
+						8 \le \sigma_1(\mathbf{H}) \le 15, \quad 4 \le \sigma_2(\mathbf{H}) \le 10, \quad 0 \le \sigma_3(\mathbf{H}) \le 0.
 					\end{equation*}
-				which is consistent with Proposition \ref{pp:dof} that \gls{bd}-\gls{ris} cannot achieve a larger \gls{dof} than \gls{d}-\gls{ris}.
 					To attain the upper and lower bounds, $(i,j)$ in \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} takes $(1, 1)$ and $(2, 2)$ when $n=1$, and $(2, 1)$ and $(3, 2)$ when $n=2$, respectively.
-				% for the upper and lower bounds of $\sigma_1(\mathbf{H})$, respectively.
-				% \begin{equation}
-				% 	\begin{bmatrix}
-				% 		8 \\
-				% 		4 \\
-				% 		0 \\
-				% 	\end{bmatrix}
-				% 	\le \sv(\mathbf{H}) \le
-				% 	\begin{bmatrix}
-				% 		15 \\
-				% 		10 \\
-				% 		0 \\
-				% 	\end{bmatrix}
-				% \end{equation}
-				% \begin{figure*}
-				% 	\begin{subequations}
-				% 		\begin{equation}
-				% 			\begin{alignedat}{2}
-				% 				\max \bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\} &\le \sigma_1(\mathbf{H}) &&\le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \\
-				% 				\max \bigl\{\sigma_2(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F})\bigr\} &\le \sigma_2(\mathbf{H}) &&\le \min \bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}, \\
-				% 				\sigma_3(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}) &\le \sigma_3(\mathbf{H}) &&\le \min \bigl\{\sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})\bigr\}.
-				% 			\end{alignedat}
-				% 		\end{equation}
-				% 		\begin{equation}
-				% 			\begin{alignedat}{1}
-				% 				\sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}) & \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
-				% 				\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) & \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}),
-				% 			\end{alignedat}
-				% 		\end{equation}
-				% 		\begin{equation}
-				% 			\begin{alignedat}{1}
-				% 				\sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) & \le \min \bigl\{\sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) \sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}), \sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}) \sigma_1(\mathbf{H}) \sigma_3(\mathbf{H})\bigr\}, \\
-				% 				\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) & \le \min \bigl\{\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) \sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}), \sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}) \sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}), \sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) \sigma_1(\mathbf{H}) \sigma_3(\mathbf{H})\bigr\}
-				% 			\end{alignedat}
-				% 		\end{equation}
-				% 	\end{subequations}
-				% \end{figure*}
-
-				% \begin{align*}
-				% 	\sigma_1(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_2(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \\
-				% 	\sigma_2(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}) \\
-				% 	\sigma_3(\mathbf{H}) &\leq \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F})
-				% \end{align*}
 			\end{itemize}
-		% $\sv(\mathbf{H}_\mathrm{B}) = [3, 2]^\mathsf{T}$ and $\sv(\mathbf{H}_\mathrm{B}) = [4, 1]^\mathsf{T}$.
-		% \begin{equation*}
-		% 	\mathbf{H}_\mathrm{B} =
-		% 		\begin{bmatrix}
-		% 			4 & 0 & 0 \\
-		% 			0 & 5 & 0 \\
-		% 			0 & 0 & 6
-		% 		\end{bmatrix},
-		% 		\quad
-		% 		\mathbf{H}_\mathrm{F} =
-		% 		\begin{bmatrix}
-		% 			1 & 0 \\
-		% 			0 & 4
-		% 		\end{bmatrix}.
-		% \end{equation*}
-		% Evidently, any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode ordering capability.
-		% On the other hand, Corollary \ref{co:nd_sv_prod_subset} suggests that a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
-
-		% \begin{align*}
-		% 	\sigma_1(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_2(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \\
-		% 	\sigma_2(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}) \\
-		% 	\sigma_3(\mathbf{H}) &\leq \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), & \sigma_3(\mathbf{H}) &\leq \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F})
-		% \end{align*}
-
-		% while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ can match the stronger branches by unitary transformation to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-		% The bounds on individual singular values are $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
-		% However, the upper/lower bounds are not simultaneously achievable due to the trade-off between two modes.
-		% and the singular value region is a subset of the rectangle due to the trade-off between the alignment of two modes.
-		% but there exists a trade-off in between due to mode alignment.
-		% It is obvious that any \gls{d}-\gls{ris} can only attain $\sv(\mathbf{H}) = [8, 3]^\mathsf{T}$ while a \gls{bd}-\gls{ris} $\mathbf{\Theta} = \begin{bsmallmatrix} 0 & 1 \\ 1 & 0 \end{bsmallmatrix}$ exploits branch matching to achieve $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-
-		% results in $\sv(\mathbf{H}) = [12, 2]^\mathsf{T}$.
-		% The singular value
-		% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
 		\end{example}
@@
 		We conclude from Example \ref{eg:shaping_bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
-	% performing right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, which properly aligns and orders their modes.
-	% properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
-	% enables right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values
-	% illustrates the shaping limits of a $3 \times 3 \times 3$ setup with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} = \diag(3, 2, 1)$, and $\mathbf{H}_\mathrm{F} = \diag(4, 0, 5)$.
-	% That is, fully-connected \gls{bd}-\gls{ris} applies right unitary transformation on $\mathbf{H}_\mathrm{B}$ and left unitary transformation on $\mathbf{H}_\mathrm{F}$, widening the singular values to $8 \le \sigma_1(\mathbf{H}) \le 12$ and $2 \le \sigma_2(\mathbf{H}) \le 3$.
 		However, when the problem of interest is a function of multiple singular values, their individual bounds \eqref{iq:sv_nd_indl} may not be simultaneously tight.
-	Two case studies are presented below.
+		Some case studies are presented below.
 
@@
 		We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
+		% TODO relay
 		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the expectation of maximum channel power gain can be numerically evaluated as
@@
 		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(\cdot)$ given by \cite[(51)]{Zanella2009}.
-	We note that \eqref{eq:power_nd_rayleigh} generalizes the \gls{siso} power gain attainable by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} under double Rayleigh fading.
-
-	\begin{corollary}[Channel capacity at very low and high \gls{snr}]
-		\label{co:nd_capacity}
-		If the direct channel is negligible, then the channel capacity at very low and high \gls{snr} are approximately bounded from above by
+		\eqref{eq:power_nd_rayleigh} generalizes the \gls{siso} channel power gain aided by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} under double Rayleigh fading, but a closed-form expression seems nontrivial.
+		The next corollary has been derived in \cite{Bartoli2023} independently from Proposition \ref{pp:nd} and we include it here for completeness of results.
+		\begin{corollary}[Channel capacity at general \gls{snr}]
+			\label{co:nd_capacity_snr_general}
+			If the direct channel is negligible, then the \gls{bd}-\gls{ris} aided \gls{mimo} channel capacity is
+			\begin{equation}
+				\label{eq:capacity_nd}
+				C^\textnormal{MIMO-ND} = \sum_{n=1}^N \log \left(1 + \frac{s_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}{\eta}\right),
+			\end{equation}
+			where $\eta$ is the average noise power, $s_n = \mu - \frac{\eta}{\sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}$ is the power allocated to the $n$-th mode obtainable by the water-filling algorithm \cite{Clerckx2013}.
+			The capacity-achieving \gls{bd}-\gls{ris} scattering matrix is
+			\begin{equation}
+				\label{eq:ris_nd_rate_max}
+				\mathbf{\Theta}_\textnormal{R-max}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
+			\end{equation}
+		\end{corollary}
+
+		\begin{proof}
+			Please refer to \cite[Appendix~A]{Bartoli2023}.
+		\end{proof}
+
+		Corollary \ref{co:nd_capacity_snr_general} also suggests that the power- and rate-optimal scattering matrices \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
+		When either condition is not satisfied, active and passive beamforming are coupled and the rate-optimal solution involves alternating optimization.
+		However, the power-optimal \gls{ris} still provides for a low-complexity decoupled solution.
+		The details will be discussed in Section~\ref{sc:rate}.
+
+		\begin{corollary}[Channel capacity at extreme \gls{snr}]
+			\label{co:nd_capacity_snr_extreme}
+			If the direct channel is negligible, then the channel capacity when the \gls{snr} $\rho$ is very low and high are approximately bounded from above by
 			\begin{subequations}
+				\label{iq:capacity_nd_snr_extreme}
 				\begin{align}
 					C_{\rho_\downarrow} & \lessapprox \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \label{iq:capacity_nd_snr_low}                                           \\
-				C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:capacity_nd_snr_high}
+					C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:capacity_nd_snr_high}
 				\end{align}
 			\end{subequations}
-		where $\rho$ is the \gls{snr} and the unit is nats/s/Hz.
-		Their upper bounds can be attained by, for example, \eqref{eq:ris_nd_power_max}.
 		\end{corollary}
@@
 
-	Similar to \eqref{eq:power_nd_rayleigh}, the ergodic counterparts of \eqref{iq:capacity_nd_snr_low} and \eqref{iq:capacity_nd_snr_high} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be numerically evaluated as
-	\begin{subequations}
-		\begin{equation}
-			\mathbb{E} \{C_{\rho_\downarrow}\} = \int_0^\infty x f_{\lambda_1^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x  \int_0^\infty y f_{\lambda_1^{\min(N_\mathrm{S},N_\mathrm{T})}}(y) d y,
-		\end{equation}
-		\begin{equation}
-			\begin{split}
-				\mathbb{E} \{C_{\rho_\uparrow}\} = N \log \frac{\rho}{N} + \sum_{n=1}^N \log \Bigl( & \int_0^\infty x f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x         \\
-				\times                                                                              & \int_0^\infty y f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(y) d y \Bigr).
-			\end{split}
-		\end{equation}
-	\end{subequations}
-
-	Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
+		The ergodic counterparts of \eqref{eq:capacity_nd} and \eqref{iq:capacity_nd_snr_extreme} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be evaluated similarly to \eqref{eq:power_nd_rayleigh}.
+		Proposition \ref{pp:dof}--\ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
 		Extending the analysis to more general cases (e.g., non-negligible direct channel and arbitrary \gls{bd}-\gls{ris} group size) is non-trivial due to limited branch matching and mode alignment capabilities therein.
-	% since the mode alignment and ordering are not guaranteed to be simultaneously achievable.
-	% ose results to the case of direct channel is non-trivial since the singular vector spaces of direct-indirect channels and backward-forward channels cannot be aligned at the same time.
-	% To provide a complete channel shaping solution, we invoke optimization approaches and tackle some relevant problems in the next section.
-
+		A numerical solution will be discussed in Section~\ref{sc:shaping_numerical}.
+	\end{subsection}
+
+	\begin{subsection}{Numerical Shaping Solution}
+		\label{sc:shaping_numerical}
+		Consider a special class of channel shaping problem
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{\label{op:shaping}}{\label{ob:shaping}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
+		\end{maxi!}
+		where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
+		Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
+		Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary}.
+		\begin{proposition}
+			\label{pp:shaping}
+			The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
+			\begin{equation}
+				\label{eq:shaping_subdiff}
+				\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
+			\end{equation}
+			where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
+		\end{proposition}
+
+		\begin{proof}
+			Please refer to Appendix~\ref{ap:shaping}.
+		\end{proof}
+
+		With Proposition \ref{pp:shaping}, one can apply the \emph{relax-then-project} method \cite{Shen2020a,Fang2023} or \emph{non-geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}} \cite{Li2023b,Li2023c,Zhou2023} to solve Problem \eqref{op:shaping}.
+		The former solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without guarantee of optimality.
+		The latter generalizes the conjugate gradient methods to Riemannian manifolds and updates the solution by addition and retraction, constituting a zigzag path departing from and returning to the manifold.
+		Next, we introduce a group-wise \emph{geodesic \gls{rcg}} method modified from \cite{Abrudan2008,Abrudan2009} that performs multiplicative updates along the geodesics on the Stiefel manifold for faster convergence.
+		It is applicable to a wide range of \gls{bd}-\gls{ris} design problems where the objective $f$ is smooth or convex non-smooth (not necessarily the symmetric gauge function \eqref{ob:shaping}) and the only constraint is group-wise unitarity \eqref{cn:shaping_unitary}.
+		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below:
+		\begin{enumerate}
+			\item \emph{Compute the Euclidean (sub-)gradient at $\mathbf{\Theta}_g^{(r)}$:} The (sub-)gradient of $f$ with respect to $\mathbf{\Theta}_g$ in the Euclidean space is
+			% \cite[(A.3.6)]{Fischer2005}
+				\begin{equation}
+					\label{eq:gradient_eucl}
+					\nabla_{\mathrm{E},g}^{(r)} = 2 \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
+				\end{equation}
+			\item \emph{Translate to the Riemannian gradient at $\mathbf{\Theta}_g^{(r)}$:} At point $\mathbf{\Theta}_g^{(r)}$, the Riemannian gradient gives the steepest ascent direction on the manifold.
+It lies in the tangent space of the manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$ and is obtainable by projection:
+				\begin{equation}
+					\label{eq:gradient_riem}
+					\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}} \mathbf{\Theta}_g^{(r)};
+				\end{equation}
+			\item \emph{Translate to the Riemannian gradient at the identity:} The Riemannian gradient should be translated back to the identity for exploiting the Lie algebra\footnote{Lie algebra refers to the tangent space of the Lie group at the identity element.
+A Lie group is simultaneously a continuous group and a differentiable manifold.
+In this example, $\mathbb{U}^{L \times L}$ formulates a Lie group and the corresponding Lie algebra consists of skew-Hermitian matrices $\mathfrak{u}(L) \triangleq \mathcal{T}_{\mathbf{I}}\mathbb{U}^{L \times L} = \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} + \mathbf{M} = \mathbf{0}\}$.}:
+				\begin{equation}
+					\label{eq:gradient_riem_tran}
+					\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{R},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.
+					% $\mathcal{O}(2 L^3)$
+				\end{equation}
+			\item \emph{Determine the conjugate direction:} The conjugate direction is obtained over the Riemannian gradient and previous direction as
+				\begin{equation}
+					\label{eq:conjugate_dirn_geod}
+					{\mathbf{D}}_g^{(r)} = \tilde{\nabla}_{\mathrm{R},g}^{(r)} + {\gamma}_g^{(r)} {\mathbf{D}}_g^{(r-1)},
+				\end{equation}
+				where $\gamma_g^{(r)}$ is the parameter that deviates the conjugate direction from the tangent space for accelerated convergence. A popular choice is the Polak-Ribi\`{e}re formula \cite{Hager2006}
+				\begin{equation}
+					\label{eq:conjugate_parm_geod}
+					{\gamma}_g^{(r)} = \frac{\tr\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}.
+% $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+				\end{equation}
+			\item \emph{Evaluate the geodesic at the identity:} The geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ is described by
+				\begin{equation}
+					\label{eq:geodesic_iden}
+					\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D}),
+				\end{equation}
+				where $\exp(\mathbf{A}) = \sum_{k=0}^\infty (\mathbf{A}^k/k!)$ is the matrix exponential and $\mu$ is the step size (i.e., magnitude of the tangent vector).
+			\item \emph{Translate to the geodesic at $\mathbf{\Theta}_g^{(r)}$:} The geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ terminates at $\mathbf{\Theta}_g^{(r+1)}$ by multiplicative updates
+				\begin{equation}
+					\label{eq:geodesic_tran}
+					\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu) = \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
+				\end{equation}
+				where $\mu$ is the step size refinable\footnote{To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, that is, $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.} by the Armijo rule \cite{Armijo1966}.
+		\end{enumerate}
+
+		\begin{algorithm}[!t]
+			\caption{Group-wise geodesic \gls{rcg}}
+			\label{ag:rcg}
+			\begin{algorithmic}[1]
+				\Require $f(\mathbf{\Theta})$, $G$
+				\Ensure $\mathbf{\Theta}^\star$
+				\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
+				\Repeat
+				\For {$g \gets 1$ to $G$}
+				\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_eucl}, $\tilde{\nabla}_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riem_tran}
+				\State $\tilde{\gamma}_g^{(r)} \gets$ \eqref{eq:conjugate_parm_geod}, $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:conjugate_dirn_geod}
+				\If {$\Re\bigl\{\tr({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{Non-ascent}
+				\State $\mathbf{D}_g^{(r)} \gets \tilde{\nabla}_{\mathrm{R},g}^{(r)}$
+				\EndIf
+				\State $\mu \gets 0.1$ \Comment{Doubling cheaper than halving}
+				\State $\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu) \gets$ \eqref{eq:geodesic_tran}
+				\While {$\scriptstyle f(\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(2\mu)) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
+				\State $\mu \gets 2 \mu$
+				\EndWhile
+				\While {$\scriptstyle f(\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu)) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
+				\State $\mu \gets \mu / 2$
+				\EndWhile \label{ln:armijo_end}
+				\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:geodesic_tran}
+				\EndFor
+				\State $r \gets r+1$
+				\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
+			\end{algorithmic}
+		\end{algorithm}
+
+		Algorithm~\ref{ag:rcg} summarizes the proposed group-wise geodesic \gls{rcg} method for group-connected \gls{bd}-\gls{ris} design when the objective is smooth or convex non-smooth and the only constraint is group-wise unitarity.
+		Compared to the non-geodesic approach, it leverages Lie algebra to replace the add-then-retract update with a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
+		This appropriate parameter space leads to faster convergence and easier step size tuning.
+		Convergence to a local optimum is still guaranteed if not initialized at a stationary point.
+		The group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} design problems.
+		One can also directly operate on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) relevant expressions to accelerate the algorithm for a large $G$.
+
+		We now analyze the computational complexity of solving singular value shaping problem \eqref{op:shaping} by Algorithm~\ref{ag:rcg}.
+		To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:shaping_subdiff} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:geodesic_tran} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
+		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., line \ref{ln:armijo_start}--\ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
+
+		% TODO: compare O(D) and O(BD)
+
+		% \begin{subsubsection}{Pareto Frontier Characterization}
+		% 	\label{sc:pareto}
+		% 	We now characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel} by maximizing their weighted sum
+		% 	\begin{maxi!}
+		% 	{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
+		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:pareto_unitary}}
+		% 	\end{maxi!}
+		% 	where $\rho_n \ge 0$ is the weight of the $n$-th singular value.
+		% 	% that can be positive, zero, or negative.
+		% 	Varying $\{\rho_n\}_{n \in [N]}$ characterizes the Pareto frontier enclosing the singular value region such that problem \eqref{op:pareto} generalizes most singular value shaping problems.
+		% 	It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:pareto}.
+		% 	\begin{lemma}
+		% 		\label{lm:pareto}
+		% 		One Euclidean sub-gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
+		% 		\begin{equation}
+		% 			\label{eq:gradient_eucl_pareto}
+		% 			% \frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} =
+		% 			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \diag(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \in \frac{\partial \sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*}
+		% 		\end{equation}
+		% 		where $\mathbf{U}$ and $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$, respectively.
+		% 	\end{lemma}
+		% 	\begin{proof}
+		% 		Please refer to Appendix~\ref{ap:pareto}.
+		% 	\end{proof}
+		% \end{subsubsection}
+	\end{subsection}
 \end{section}
 
-	\begin{section}{Numerical Shaping Solutions}
+	\begin{section}{Rate Maximization}
 		\label{sc:framework}
@@
 		% According to
-		Consider a special class of channel shaping problem
+
+		\begin{subsection}{MIMO Point-to-Point Channel}
+			\label{sc:rate}
+			We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
 			\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{\label{op:shaping}}{\label{ob:shaping}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
+			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
+			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cn:rate_unitary}}
 			\end{maxi!}
-		where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
-		Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
-		Problem \eqref{op:shaping} can be solved by a \gls{rcg} method over proposition \ref{pp:shaping}.
-		% Although
-
-		\begin{proposition}
-			\label{pp:shaping}
-			The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
-			\begin{equation}
-				\label{eq:shaping_subdiff}
-				\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
-			\end{equation}
-			where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
-			% $d_n \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
-
-			% One Euclidean sub-gradient of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
-			% \begin{equation}
-			% 	\frac{\partial f\bigl(\sv(\mathbf{H})\bigr)}{\partial \mathbf{\Theta}_g} = \sum_{n=1}^N \frac{\partial f\bigl(\sv(\mathbf{H})\bigr)}{\partial \sigma_n(\mathbf{H})} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
-			% \end{equation}
-			% where $\mathbf{u}_n$ and $\mathbf{v}_n$ are any (c.f. Footnote \ref{fn:svd_non_uniqueness}) left and right singular vectors of $\mathbf{H}$ corresponding to $\sigma_n(\mathbf{H})$.
-		\end{proposition}
+			where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
+			Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
+			We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
+
+			\begin{subsubsection}{Alternating Optimization}
+			This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
+			For a given $\mathbf{W}$, the passive beamforming subproblem is
+			\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_ris}}{\label{ob:rate_ris}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+			\end{maxi!}
+			where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
+			Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate}.
+			\begin{lemma}
+				\label{lm:rate}
+				The Euclidean gradient of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
+				\begin{equation}
+					\label{eq:gradient_eucl_rate}
+					\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+				\end{equation}
+			\end{lemma}
 
 			\begin{proof}
-			Please refer to Appendix~\ref{ap:shaping}.
+				Please refer to Appendix~\ref{ap:rate}.
 			\end{proof}
-	% In this section, we first provide an overview on signal processing techniques for group-connected \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group and operates directly on the Stiefel manifold.
-	% The proposed method is applicable to any smooth optimization problem on the Stiefel manifold and is particularly suitable for \gls{bd}-\gls{ris} design problems.
-	% We will later show that the proposed method provides better objective value and faster convergence for smooth optimization problems of arbitrary group size.
-
-	This section aims for an efficient yet universal optimization framework for group-connected \gls{bd}-\gls{ris} design.
-	Most relevant optimization problems can be formulated as
-	\begin{maxi!}
-	{\scriptstyle{\mathbf{\Theta}}}{f(\mathbf{\Theta})}{\label{op:general}}{\label{ob:general}}
-	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:general_unitary}}
-	\end{maxi!}
-	where the objective function $f(\mathbf{\Theta})$ is a function of the \gls{bd}-\gls{ris} scattering matrix, for example, channel singular value (to be discussed in Section \ref{sc:pareto}), channel power gain (to be discussed in Section \ref{sc:power}), and achievable rate (to be discussed in Section \ref{sc:rate}).
-	The feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ that is non-convex and non-Euclidean.
-	Therefore, most \gls{bd}-\gls{ris} optimization problems are solved by \emph{relax-then-project} methods \cite{Fang2023} or \emph{general manifold \gls{rcg}} \cite{Li2023b,Li2023c,Zhou2023}.
-	The former solves unconstrained problem \eqref{ob:general} by quasi-Newton methods then projects the solution back to domain \ref{cn:general_unitary}, which often ends up far from optimal.
-	The latter generalizes the conjugate gradient methods to Riemannian manifolds and iteratively updates the solution by addition and retraction.
-	% It has been widely adopted in \gls{d}- and \gls{bd}-\gls{ris} literature.
-	% progressing along the conjugate direction and retracting back to the manifold.
-	% refining the solution iteratively by progressing along the conjugate direction and projecting back to the manifold at each step.
-	% which progresse along the conjugate direction and projecting back to the manifold at each step
-	% updates the feasible point by progressing along the conjugate direction and projecting back to the manifold at each step.
-	In the following context, we briefly review the general \gls{rcg} method and discuss its drawbacks inherited from the non-geodesic nature, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
-	% provide a brief overview on the general \gls{rcg} method used in \gls{bd}-\gls{ris} optimization, namely non-geodesic \gls{rcg}, and discuss its drawbacks.
-	% explain the existing manifold RCG method used in BD-RIS optimization, namely non-geodesic RCG, and discuss its drawbacks,
-	% first discuss the existing non-geodesic \gls{rcg} method and its drawbacks, then propose a novel group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold for faster convergence.
-
-	\begin{subsection}{Optimization}
-
-		\label{sc:rcg_general}
-		A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.
-		The general \gls{rcg} method proposed in \cite{Absil2009,Pan2022d} is applicable to optimization problems over arbitrary manifolds.
-		The idea is to perform {additive} updates along the conjugate direction guided by the Riemannian gradient, {project} the solution back onto the manifold, and repeat until convergence.
-		% It is non-geodesic because the updates constitute a zigzag path aided by the Euclidean space instead of carried entirely on the manifold.
-		% updates are not entirely on the manifold
-		% we progress along a direct path in the tangent space and departs from the manifold in each step.
-		% the updates are not entirely
-		% , at each step, we progress along a direct path in the tangent space and departs from the manifold in each step.
-		% project back to the manifold.
-		% update the feasible point by progressing along conjugate directions then project back to the manifold.
-		% The main idea is to update the feasible point by progressing along conjugate directions then project back to the manifold.
-		For optimization problem \eqref{op:general}, the steps for \gls{bd}-\gls{ris} group $g$ at iteration $r$ are summarized below:
-		\begin{enumerate}
-		\item \emph{Compute the Euclidean gradient:} The gradient of $f$ with respect to $\mathbf{\Theta}_g$ in the Euclidean space is \cite[(A.3.6)]{Fischer2005}
-			\begin{equation}
-				\label{eq:gradient_eucl}
-				\nabla_{\mathrm{E},g}^{(r)} = 2 \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
-			\end{equation}
-		\item \emph{Translate to the Riemannian gradient \cite{Absil2009}:} At point $\mathbf{\Theta}^{(r)}$, the Riemannian gradient lies in the tangent space of the Stiefel manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$.
-It gives the steepest ascent direction of the objective on the manifold can be obtained by projecting the Euclidean gradient onto the tangent space:
-			\begin{equation}
-				\label{eq:gradient_riem}
-				\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}} \mathbf{\Theta}_g^{(r)};
-			\end{equation}
-		\item \emph{Determine the conjugate direction \cite{Nocedal2006}:} The conjugate direction is obtained over the Riemannian gradient and previous direction as
-			\begin{equation}
-				\label{eq:conjugate_dirn}
-				\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}, % $\mathcal{O}(N_\mathrm{S}^2)$
-			\end{equation}
-			where $\gamma_g^{(r)}$ is the parameter that deviates the conjugate direction from the tangent space for accelerated convergence. A popular choice is the Polak-Ribi\`{e}re formula
-			\begin{equation}
-				\label{eq:conjugate_parm}
-				\gamma_g^{(r)} = \frac{\tr\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}; % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-			\end{equation}
-		\item \emph{Perform additive update \cite{Pan2022d}:} The point is updated by moving along a straight path in the conjugate direction
-			\begin{equation}
-				\label{eq:iterate_add}
-				\bar{\mathbf{\Theta}}_g^{(r+1)} = \mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)},
-			\end{equation}
-			where $\mu$ is the step size refinable by the Armijo rule \cite{Armijo1966};
-		\item \emph{Retract for feasibility \cite{Absil2009,Li2023b}:} The resulting point needs to be projected to the closest point (in terms of Euclidean distance) on the Stiefel manifold by
-			\begin{equation}
-				\label{eq:iterate_retr}
-				\mathbf{\Theta}_g^{(r+1)} = \bar{\mathbf{\Theta}}_g^{(r+1)} \bigl({\bar{\mathbf{\Theta}}_g^{(r+1)\mathsf{H}}} \bar{\mathbf{\Theta}}_g^{(r+1)}\bigr)^{-1/2}.
-			\end{equation}
-			One can also combine the addition \eqref{eq:iterate_add} and retraction \eqref{eq:iterate_retr} in one step
-			\begin{equation}
-				\label{eq:iterate_comb}
-				\mathbf{\Theta}_g^{(r+1)} = \bigl(\mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)}\bigr) \bigl( \mathbf{I} + \mu^2 {\mathbf{D}_g^{(r)\mathsf{H}}} \mathbf{D}_g^{(r)} \bigr)^{-1/2},
-			\end{equation}
-			and determine the step size therein.
-	\end{enumerate}
-
-	The method is called non-geodesic since the addition \eqref{eq:iterate_add} and retraction \eqref{eq:iterate_retr} constitute a zigzag path departing from and returning to the manifold.
-	% aided by the Euclidean space instead of carried entirely on the manifold.
-	% the points are updated in the linear embedding spaces by addition \eqref{eq:iterate_add} and retraction \eqref{eq:iterate_retr}, instead of on the Stiefel manifold itself.
-	It converges to stationary points of the original problem but usually requires a large number of iterations due to inefficient operations in the Euclidean space.
-	% usually suffers from numerical instability
-	% additive update \eqref{eq:iterate_add} in the Euclidean space and retraction \eqref{eq:iterate_retr}.
-	% Those
-\end{subsection}
-
-% \begin{subsection}{Conventional Techniques}
-% 	Group-connected \gls{bd}-\gls{ris} design techniques formulated in terms of scattering matrix can be classified into two categories based on the optimization variable and hardware architecture:
-% 	\begin{itemize}
-% 		\item \emph{Scattering matrix $\mathbf{\Theta}$:} This approach is often exploited for asymmetric architectures where the feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
-Due to its non-convexity, relevant problems are usually solved by general non-geodesic manifold optimization \cite{Li2023b,Li2023c,Bartoli2023} or relax-then-project methods \cite{Fang2023}.
-The former will be discussed in the next subsection.
-% 		\item \emph{Reactance matrix $\mathbf{X}$:\footnote{Similar design over susceptance matrix $\mathbf{B}$ can be found in \cite{Nerini2024}.}} This approach is often exploited for symmetric architectures where every pair of elements in the same group are connected by capacitors and inductors.
-According to network theory \cite{Pozar2011}, it maps to the scattering matrix by $\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I})$, which formulates an unconstrained optimization problem on the upper triangular entries of $\{\mathbf{X}_g\}_{g \in \mathcal{G}}$ that is solvable by quasi-Newton methods \cite{Shen2020a}.
-% 	\end{itemize}
-% \end{subsection}
-
-\begin{subsection}{Geodesic RCG}
-	\label{sc:rcg_geodesic}
-	Before introducing geodesic \gls{rcg}, we revisit some basic concepts in differential geometry.
-	% \cite{Abrudan2008,Abrudan2009}.
-	A Lie group is simultaneously a continuous group and a differentiable manifold.
-	Lie algebra refers to the tangent space of the Lie group at the identity element.
-	The exponential map acts as a bridge between the Lie algebra and Lie group, which allows one to recapture the local group structure using linear algebra techniques.
-	The set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group $U(L)$ under multiplication, and the corresponding Lie algebra $\mathfrak{u}(L) \triangleq \mathcal{T}_{\mathbf{I}}\mathbb{U}^{L \times L} = \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} + \mathbf{M} = \mathbf{0}\}$ consists of skew-Hermitian matrices.
-	A geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ can be described by \cite{Edelman1998}
-	\begin{equation}
-		\label{eq:geodesic_iden}
-		\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D}),
-	\end{equation}
-	where $\exp(\mathbf{A}) = \sum_{k=0}^\infty (\mathbf{A}^k/k!)$ is the matrix exponential and $\mu$ is the step size (i.e., magnitude of the tangent vector).
-	Note that the right translation is an isometry in $U(L)$.
-	During the optimization of group $g$, the geodesic evaluated at the identity \eqref{eq:geodesic_iden} should be translated to $\mathbf{\Theta}_g^{(r)}$ for successive updates \cite{Abrudan2008}
-	\begin{equation}
-		\label{eq:geodesic_tran}
-		\mathbf{G}_g^{(r)}(\mu) = \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
-	\end{equation}
-	while the Riemannian gradient evaluated at $\mathbf{\Theta}_g^{(r)}$ \eqref{eq:gradient_riem} should be translated back to the identity for exploiting the Lie algebra \cite{Abrudan2008}
-	\begin{equation}
-		\label{eq:gradient_riem_tran}
-		\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{R},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.
-		% $\mathcal{O}(2 L^3)$
-	\end{equation}
-	After gradient translation, the deviation parameter and conjugate direction can be determined similarly to \eqref{eq:conjugate_parm} and \eqref{eq:conjugate_dirn}
-	\begin{equation}
-		\label{eq:conjugate_parm_geod}
-		\tilde{\gamma}_g^{(r)} = \frac{\tr\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}.
-% $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-	\end{equation}
-	\begin{equation}
-		\label{eq:conjugate_dirn_geod}
-		{\mathbf{D}}_g^{(r)} = \tilde{\nabla}_{\mathrm{R},g}^{(r)} + \tilde{\gamma}_g^{(r)} {\mathbf{D}}_g^{(r-1)},
-	\end{equation}
-	The solution can thus be updated along the geodesic in a multiplicative rotational manner
-	\begin{equation}
-		\label{eq:iterate_mul}
-		\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
-	\end{equation}
-	where an appropriate $\mu$ may be obtained by the Armijo rule.
-	To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, that is, $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.
-	We highlight that the proposed geodesic \gls{rcg} method has been tailored to the Stiefel manifold.
-
-	\begin{algorithm}[!t]
-		\caption{Group-wise geodesic \gls{rcg} for \gls{bd}-\gls{ris} design}
-		\label{ag:rcg}
-		\begin{algorithmic}[1]
-			\Require $f(\mathbf{\Theta})$, $G$
-			\Ensure $\mathbf{\Theta}^\star$
-			\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
-			\Repeat
-			\For {$g \gets 1$ to $G$}
-			\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_eucl}
-			\State $\tilde{\nabla}_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riem_tran}
-			\State $\tilde{\gamma}_g^{(r)} \gets$ \eqref{eq:conjugate_parm_geod}
-			\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:conjugate_dirn_geod}
-			\If {$\Re\bigl\{\tr({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
-			\State $\mathbf{D}_g^{(r)} \gets \tilde{\nabla}_{\mathrm{R},g}^{(r)}$
-			\EndIf
-			\State $\mu \gets 1$
-			\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic_tran}
-			\While {$\scriptstyle f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
-			\State $\mu \gets 2 \mu$
-			\EndWhile
-			\While {$\scriptstyle f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
-			\State $\mu \gets \mu / 2$
-			\EndWhile \label{ln:armijo_end}
-			\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:iterate_mul}
-			\EndFor
-			\State $r \gets r+1$
-			\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
-		\end{algorithmic}
-	\end{algorithm}
-
-	Algorithm~\ref{ag:rcg} summarizes the proposed \gls{bd}-\gls{ris} design framework based on group-wise geodesic \gls{rcg}.
-	Compared to the general non-geodesic approach, it leverages the Lie group properties to replace the add-then-retract update \eqref{eq:iterate_comb} with a multiplicative rotational update \eqref{eq:iterate_mul} along geodesics of the Stiefel manifold.
-	This leads to faster convergence and simplifies the step size tuning thanks to appropriate parameter space.
-	Convergence to a local optimum is still guaranteed if not initialized at a stationary point.
-	Note that the group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
-	Since the set of block-unitary matrices are algebraically closed under multiplication, one can also avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) the Euclidean gradient \eqref{eq:gradient_eucl}, which can further accelerate the algorithm when the number of group is large.
-\end{subsection}
-
-% 	\label{sc:power_rate}
-We would like to give a quick overview of what we have done so far.
-	[say why the analytical results are limited to what cases.]
-In this section, we solve channel power gain maximization problem in closed-form and then extend the discussion to achievable rate maximization problem.
-The implication of the former on the latter is investigated.
-
-\begin{subsection}{Pareto Frontier Characterization}
-	\label{sc:pareto}
-We now characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel} by maximizing their weighted sum
-\begin{maxi!}
-{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
-\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:pareto_unitary}}
-\end{maxi!}
-where $\rho_n \ge 0$ is the weight of the $n$-th singular value.
-% that can be positive, zero, or negative.
-Varying $\{\rho_n\}_{n \in [N]}$ characterizes the Pareto frontier enclosing the singular value region such that problem \eqref{op:pareto} generalizes most singular value shaping problems.
-It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:pareto}.
-% It can be solved optimally by Algorithm~\ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses the following Euclidean gradient expression \eqref{eq:gradient_eucl_pareto}.
-
-% \begin{lemma}
-% 	\label{lm:pareto}
-% 	The Euclidean gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
-% 	\begin{equation}
-% 		\label{eq:gradient_eucl_pareto}
-% 		\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \diag(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
-% 	\end{equation}
-% 	where $\mathbf{U}$ and $\mathbf{V}$ are any left and right compact singular matrices of $\mathbf{H}$, respectively.
-% \end{lemma}
-
-\begin{lemma}
-	\label{lm:pareto}
-	One Euclidean sub-gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
-	\begin{equation}
-		\label{eq:gradient_eucl_pareto}
-		% \frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} =
-		\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \diag(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \in \frac{\partial \sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*}
-	\end{equation}
-	where $\mathbf{U}$ and $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$, respectively.
-\end{lemma}
-\begin{proof}
-	Please refer to Appendix~\ref{ap:pareto}.
-\end{proof}
-
-We now analyze the computational complexity of solving Pareto singular value problem \eqref{op:pareto} by Algorithm~\ref{ag:rcg}.
-To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:gradient_eucl_pareto} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:iterate_mul} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
-The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., line \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
-\end{subsection}
-
-\begin{subsection}{Channel Power Gain}
+			For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
+			\begin{equation}
+				\label{eq:precoder}
+				\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
+			\end{equation}
+			where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation \cite{Clerckx2013}.
+
+			The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
+			Similar to the analysis in Section \ref{sc:pareto}, the computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
+			On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+			The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
+			\end{subsubsection}
+
+			\begin{subsubsection}{Low-Complexity Solution}
+				\label{sc:low_complexity}
+
+				\begin{paragraph}{Channel Power Gain}
 					\label{sc:power}
@@
 
-It is worth noting that ?? and \eqref{eq:ris_procrustes} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power} when the direct channel is negligible and significant, respectively.
+				It is worth noting that ??
+and \eqref{eq:ris_procrustes} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power} when the direct channel is negligible and significant, respectively.
 				However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
@@
 				The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
-\end{subsection}
-
-\begin{subsection}{Achievable Rate Maximization}
-	\label{sc:rate}
-We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
-\begin{maxi!}
-{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
-\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
-\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cn:rate_unitary}}
-\end{maxi!}
-where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
-Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
-We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
-
-\begin{subsubsection}{Alternating Optimization}
-This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
-For a given $\mathbf{W}$, the passive beamforming subproblem is
-\begin{maxi!}
-{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_ris}}{\label{ob:rate_ris}}
-\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-\end{maxi!}
-where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate}.
-\begin{lemma}
-	\label{lm:rate}
-	The Euclidean gradient of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
-	\begin{equation}
-		\label{eq:gradient_eucl_rate}
-		\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-	\end{equation}
-\end{lemma}
-
-\begin{proof}
-	Please refer to Appendix~\ref{ap:rate}.
-\end{proof}
-For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
-\begin{equation}
-	\label{eq:precoder}
-	\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
-\end{equation}
-where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation obtainable by the iterative method \cite{Tse2005}.
-
-The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-Similar to the analysis in Section \ref{sc:pareto}, the computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
-On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
-The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
-\end{subsubsection}
-
-\begin{subsubsection}{Low-Complexity Solution}
-	\label{sc:low_complexity}
+				\end{paragraph}
+
 				We finally propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
@@
 		\end{subsection}
+
+		% \begin{subsection}{MIMO Interference Channel}
+
+			\begin{subsection}{Leakage Interference Minimization}
+				Leakage interference refers to the sum of all interference terms in \gls{ic}.
+				Assume all transmitter sends $N_\mathrm{E} \le N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ data streams to its intended receiver.
+				The leakage interference minimization problem is formulated with respect to all transmit precoders, all receiver combiners, and the scattering matrix as
+				\begin{mini!}
+					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}^{[kj]}_\mathrm{D} + \mathbf{H}^{[k]}_\mathrm{B} \mathbf{\Theta} \mathbf{H}^{[j]}_{\mathrm{F}}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
+					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
+					\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
+					\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
+				\end{mini!}
+				where $\mathbf{G}_k \in \mathbb{C}^{N_\mathrm{D} \times N_\mathrm{R}}$ is the combiner at receiver $k$ and $\mathbf{W}_j \in \mathbb{C}^{N_\mathrm{T} \times N_\mathrm{D}}$ is the precoder at transmitter $j$.
+				It is worth noting that $\mathbf{\Theta}_g$ is a square unitary matrix and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}$ is equivalent to $\mathbf{\Theta}_g \mathbf{\Theta}_g^\mathsf{H}=\mathbf{I}$, while $\mathbf{G}_k$ and $\mathbf{W}_j$ may be respectively ``fat'' and ``tall'' rectangular semi-unitary matrices such that \eqref{co:combiner} and \eqref{co:precoder} are required.
+				The non-convex problem can be solved iteratively by the \gls{bcd} method detailed below.
+
+				\begin{subsubsection}{Combiner and Precoder Design}
+					For a given $\mathbf{\Theta}$, problem \eqref{op:leakage} reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
+					At iteration $r$, the combiner at receiver $k$ is updated as
+					\begin{equation}
+						\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
+						\label{eq:combiner_leakage}
+					\end{equation}
+					where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of the interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H}$.
+					The precoder at transmitter $j$ is updated as
+					\begin{equation}
+						\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
+						\label{eq:precoder_leakage}
+					\end{equation}
+					where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} {\mathbf{H}^{[kj]}}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} {\mathbf{H}^{[kj]}}$ in the reciprocal network.
+				\end{subsubsection}
+
+				\begin{subsubsection}{Scattering Matrix Design}
+					Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_j\}$ are determined, we define $\bar{\mathbf{H}}^{[kj]}_\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}^{[kj]}_\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}^{[k]}_\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}^{[k]}_\mathrm{B}$, and $\bar{\mathbf{H}}^{[j]}_\mathrm{F} \triangleq \mathbf{H}^{[j]}_\mathrm{F} \mathbf{W}_j$.
+					The \gls{bd}-\gls{ris} subproblem boils down to
+					\begin{mini!}
+						{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}^{[kj]}_\mathrm{D} + \bar{\mathbf{H}}^{[k]}_\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}^{[j]}_\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
+						\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+					\end{mini!}
+					which can be viewed as a channel shaping problem on $\bar{\mathbf{H}}^{[kj]}_\mathrm{D}$, $\bar{\mathbf{H}}^{[k]}_\mathrm{B}$, and $\bar{\mathbf{H}}^{[j]}_\mathrm{F}$.
+
+					\begin{proposition}
+						Start from any $\mathbf{\Theta}^{(0)}$, the sequence
+						\begin{equation}
+							\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+							\label{eq:scatter_leakage}
+						\end{equation}
+						converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
+						\begin{equation}
+							\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{[j]}_{\mathrm{F},g} - {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} {\mathbf{D}^{[kj]}_{g}}^{(r)}\bigr) {\mathbf{H}^{[j]}_{\mathrm{F},g}}^\mathsf{H},
+						\end{equation}
+						where $\mathbf{B}_{k,g} = \lambda_1\bigl({\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{H}^{[k]}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{H}^{[k]}_{\mathrm{B},g}$ and
+						\begin{equation}
+							{\mathbf{D}^{[kj]}_{g}}^{(r)} = \mathbf{H}^{[jk]}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
+						\end{equation}
+					\end{proposition}
+					\begin{proof}
+						The proof is similar to Appendix~\ref{ap:power} and omitted here.
+					\end{proof}
+				\end{subsubsection}
+
+				Problem \eqref{op:leakage} can be solved iteratively by \eqref{eq:combiner_leakage}, \eqref{eq:precoder_leakage}, and \eqref{eq:scatter_leakage}.
+				Convergence to local-optimal points is guaranteed since each subproblem is solved optimally and the objective is bounded above.
+
+			\end{subsection}
+
+			\begin{subsection}{Weighted Sum-Rate Maximization}
+				Finally, we consider weighted sum-rate maximization in \gls{mimo}-\gls{ic} by joint active beamforming design at the transmitters and passive beamforming design at the \gls{ris}.
+				The achievable rate of transmission $k$ is given by
+				\begin{equation}
+					R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{[kj]}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kj]}} \mathbf{W}_k\biggr),
+				\end{equation}
+				where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
+				\begin{equation}
+					\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H} + \eta \mathbf{I},
+				\end{equation}
+				and $\eta$ is the average noise power.
+				The optimization problem is formulated as
+				\begin{maxi!}
+					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{\sum_k \rho_k R_k}{\label{op:ic_rate}}{\label{ob:ic_rate}}
+					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+					\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
+				\end{maxi!}
+				where $\rho_k$ is the weight that denotes the priority of transmission $k$.
+				The problem is non-convex and can be solved by the \gls{ao} method detailed below.
+
+				\begin{subsubsection}{Precoder Design}
+					For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution has been proposed in \cite{Negro2010} based on mutual information-\gls{mmse} relationship \cite{Guo2005}.
+					We restate the steps as follows.
+
+					At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
+					\begin{equation}
+						\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{[kk]}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H}\bigr)^{-1},
+					\end{equation}
+					the corresponding error matrix is
+					\begin{equation}
+						\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{[kk]}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+					\end{equation}
+					the \gls{mse} weight is
+					\begin{equation}
+						\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
+					\end{equation}
+					the Lagrange multiplier is
+					\begin{equation}
+						\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)}}^\mathsf{H} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
+					\end{equation}
+					where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{[kj]}} \mathbf{W}_j^{(r)}$.
+					The optimal precoder at transmitter $k$ is given by
+					\begin{equation}
+						\mathbf{W}_k^{(r)} = \Bigl(\sum_j {\mathbf{H}^{[jk]}}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{[jk]} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} {\mathbf{H}^{[kk]}}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
+					\end{equation}
+				\end{subsubsection}
+
+				\begin{subsubsection}{Scattering Matrix Design}
+					Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} with respect to \gls{ris} block $g$ is
+					\begin{equation}
+						\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_k \rho_k {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kk]}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - {\mathbf{H}^{[kk]}}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{[j]}_{\mathrm{F},g}}^\mathsf{H}\bigr).
+						\label{eq:ic_rate_gradient_ris}
+					\end{equation}
+				\end{subsubsection}
+				The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:rcg} where line ?? uses \eqref{eq:ic_rate_gradient_ris} explicitly.
+			\end{subsection}
+		% \end{subsection}
 \end{section}
+
+	% ! shit
 
@@
 % 			\end{equation}
-% 			where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation obtainable by the iterative method \cite{Tse2005}.
+% 			where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation obtainable by the iterative method \cite{Clerckx2013}.
 
@@
  Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
- The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician K-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
+ The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician K-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
  We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/singular_pareto_sx32_nd.tex}
+					 \input{../assets/simulation/pc_singular_pareto_sx32_nd.tex}
 
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/singular_pareto_sx32.tex}
+					 \input{../assets/simulation/pc_singular_pareto_sx32.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/singular_pareto_sx64.tex}
+					 \input{../assets/simulation/pc_singular_pareto_sx64.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/singular_pareto_sx128.tex}
+					 \input{../assets/simulation/pc_singular_pareto_sx128.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/singular_bound_rank1_sx32.tex}
+					 \input{../assets/simulation/pc_singular_bound_rank1_sx32.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/singular_bound_rank1_sx64.tex}
+					 \input{../assets/simulation/pc_singular_bound_rank1_sx64.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/singular_bound_rank2_sx128.tex}
+					 \input{../assets/simulation/pc_singular_bound_rank2_sx128.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/singular_bound_rank4_sx256.tex}
+					 \input{../assets/simulation/pc_singular_bound_rank4_sx256.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/power_bond_txrx1_nd.tex}
+					 \input{../assets/simulation/pc_power_bond_txrx1_nd.tex}
 				 }
@@
 				 \resizebox{!}{3.25cm}{
-					 \input{../assets/simulation/power_bond_txrx4_nd.tex}
+					 \input{../assets/simulation/pc_power_bond_txrx4_nd.tex}
 				 }
@@
 			 \resizebox{!}{3.0625cm}{
-				 \input{../assets/simulation/power_sx_txrx16_nd.tex}
+				 \input{../assets/simulation/pc_power_sx_txrx16_nd.tex}
 			 }
@@
 			 \resizebox{!}{3.0625cm}{
-				 \input{../assets/simulation/power_sx_txrx16.tex}
+				 \input{../assets/simulation/pc_power_sx_txrx16.tex}
 			 }
@@
 			 \resizebox{!}{3.25cm}{
-				 \input{../assets/simulation/rate_beamforming.tex}
+				 \input{../assets/simulation/pc_rate_beamforming.tex}
 			 }
@@
 			 \resizebox{!}{3.25cm}{
-				 \input{../assets/simulation/rate_txrx.tex}
+				 \input{../assets/simulation/pc_rate_txrx.tex}
 			 }
@@
 			 \resizebox{!}{3.25cm}{
-				 \input{../assets/simulation/rate_sx.tex}
+				 \input{../assets/simulation/pc_rate_sx.tex}
 			 }
@@
 			 \resizebox{!}{3.25cm}{
-				 \input{../assets/simulation/rate_kfactor.tex}
+				 \input{../assets/simulation/pc_rate_kfactor.tex}
 			 }
@@
 	 A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-	 An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_ris} -- \eqref{eq:precoder} and the shaping-inspired solution \eqref{eq:ris_power}, \eqref{eq:precoder} narrows at larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+	 An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_ris}--\eqref{eq:precoder} and the shaping-inspired solution \eqref{eq:ris_power}, \eqref{eq:precoder} narrows at larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
 	 This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the active beamformer, which significantly simplifies the process at marginal performance cost.
@@
 	\end{equation}
-	To attain the upper bound in \eqref{iq:rank_indirect}, the \gls{ris} needs to minimize $r_\mathrm{L}(\mathbf{\Theta})$ by aligning the ranges of $\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}$ and $\mathbf{V}_{\mathrm{B},2}$ as possible.
+	To attain the upper bound in \eqref{iq:rank_indirect}, the \gls{ris} needs to minimize $r_\mathrm{L}(\mathbf{\Theta})$ by aligning the ranges of $\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}$ and $\mathbf{V}_{\mathrm{B},2}$ as much as possible.
 	This is achieved by
@@
 
-\begin{subsection}{Proof of Corollary \ref{co:nd_capacity}}
+\begin{subsection}{Proof of Corollary \ref{co:nd_capacity_snr_extreme}}
 	\label{ap:nd_capacity}
@@
 
-	We then show \eqref{eq:ris_nd_power_max} can achieve the upper bounds in \eqref{iq:capacity_nd_snr_low} and \eqref{iq:capacity_nd_snr_high} simultaneously.
-	On the one hand, \eqref{eq:ris_nd_power_max} is a special case of \eqref{eq:ris_nd_sv_indl_max} with $\mathbf{P} = \mathbf{I}$, which satisfies \eqref{eq:idx_nd_sv_indl_max} and \eqref{eq:perm_nd_sv_indl_max} for $n=1$ and thus attain $\sigma_1(\mathbf{H}) = \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
-	On the other hand, since $\log(\cdot)$ is a monotonic function, we can prove similar to Appendix \ref{ap:nd_power} that $\sum_{n=1}^N \log \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \log \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})$ and the bound is tight at \eqref{eq:ris_nd_power_max}.
+	We now show \eqref{eq:ris_nd_rate_max} can achieve the upper bounds in \eqref{iq:capacity_nd_snr_low} and \eqref{iq:capacity_nd_snr_high} simultaneously.
+	On the one hand, \eqref{eq:ris_nd_rate_max} is a special case of \eqref{eq:ris_nd_sv_indl_max} with $\mathbf{P} = \mathbf{I}$, which satisfies \eqref{eq:idx_nd_sv_indl_max} and \eqref{eq:perm_nd_sv_indl_max} for $n=1$ and thus attain $\sigma_1(\mathbf{H}) = \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
+	On the other hand, since $\log(\cdot)$ is a monotonic function, we can prove similar to Appendix \ref{ap:nd_power} that $\sum_{n=1}^N \log \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \log \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})$ and the bound is tight at \eqref{eq:ris_nd_rate_max}.
 	The proof is complete.
@@
 
-\begin{subsection}{Proof of Lemma \ref{lm:pareto}}
-	\label{ap:pareto}
-	The sub-differential of $\sigma_n(\mathbf{H})$ with respect to $\mathbf{H}$ is given by
-	\begin{equation*}
-		\partial \sigma_n(\mathbf{H}) = \mathbf{u}_n \mathbf{v}_n^\mathsf{H},
-	\end{equation*}
-
-	Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the \gls{svd} of the equivalent channel.
-	Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
-	\begin{equation}
-		\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*.
-	\end{equation}
-
-	Let $f(\mathbf{\Theta}_g) = \sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})$. Its sub-differential is defined as
-	\begin{equation}
-		\Bigl\{\mathbf{Y} \mid f(\tilde{\mathbf{\Theta}}_g) \ge f(\mathbf{\Theta}_g) + \tr\bigl(\mathbf{Y}^\mathsf{H} (\tilde{\mathbf{\Theta}}_g - \mathbf{\Theta}_g)\bigr), \forall \tilde{\mathbf{\Theta}}_g \in \mathbb{U}^{L \times L}\Bigr\}.
-	\end{equation}
-
-	whose sub-gradient with respect to $\mathbf{\Theta}_g^*$ is
-	\begin{align*}
-		\partial \sigma_n
-		 & = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n^*} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^* \\
-		 & = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}                                                                                                                  \\
-		 & = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*                                                                                                                                                                                                                                                 \\
-		 & = \tr(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
-	\end{align*}
-	According to \cite{Hjorungnes2007}, the corresponding complex derivative is
-	\begin{equation}
-		\label{eq:gradient_eucl_sv_indl}
-		\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-	\end{equation}
-	A linear combination of \eqref{eq:gradient_eucl_sv_indl} yields \eqref{eq:gradient_eucl_pareto}.
-\end{subsection}
+% \begin{subsection}{Proof of Lemma \ref{lm:pareto}}
+% 	\label{ap:pareto}
+% 	The sub-differential of $\sigma_n(\mathbf{H})$ with respect to $\mathbf{H}$ is given by
+% 	\begin{equation*}
+% 		\partial \sigma_n(\mathbf{H}) = \mathbf{u}_n \mathbf{v}_n^\mathsf{H},
+% 	\end{equation*}
+
+% 	Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the \gls{svd} of the equivalent channel.
+% 	Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
+% 	\begin{equation}
+% 		\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*.
+% 	\end{equation}
+
+% 	Let $f(\mathbf{\Theta}_g) = \sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})$. Its sub-differential is defined as
+% 	\begin{equation}
+% 		\Bigl\{\mathbf{Y} \mid f(\tilde{\mathbf{\Theta}}_g) \ge f(\mathbf{\Theta}_g) + \tr\bigl(\mathbf{Y}^\mathsf{H} (\tilde{\mathbf{\Theta}}_g - \mathbf{\Theta}_g)\bigr), \forall \tilde{\mathbf{\Theta}}_g \in \mathbb{U}^{L \times L}\Bigr\}.
+% 	\end{equation}
+
+% 	whose sub-gradient with respect to $\mathbf{\Theta}_g^*$ is
+% 	\begin{align*}
+% 		\partial \sigma_n
+% 		 & = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n^*} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^* \\
+% 		 & = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}                                                                                                                  \\
+% 		 & = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*                                                                                                                                                                                                                                                 \\
+% 		 & = \tr(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
+% 	\end{align*}
+% 	According to \cite{Hjorungnes2007}, the corresponding complex derivative is
+% 	\begin{equation}
+% 		\label{eq:gradient_eucl_sv_indl}
+% 		\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+% 	\end{equation}
+% 	A linear combination of \eqref{eq:gradient_eucl_sv_indl} yields \eqref{eq:gradient_eucl_pareto}.
+% \end{subsection}
 

### 2024-12-20 src/ic_interference_sx.m

@@ -1,0 +1,67 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 2 .^ (2 : 2 : 8), 4);
+[network.coverage, network.pair] = deal(50, 5);
+[channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(db2pow(-30), 3, 2.4, 2.4);
+[number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e2, true);
+
+for r = 1 : number.realization
+	[network.coordinate.transmit, network.coordinate.reflect, network.coordinate.receive] = deal(distribution_disk(network.coverage, network.pair), [0; 0], distribution_disk(network.coverage, network.pair));
+	channel.pathloss.direct = pathloss(channel.pathloss.reference, vecnorm(network.coordinate.receive - network.coordinate.transmit), channel.pathloss.exponent.direct);
+	channel.pathloss.forward = pageswap(pathloss(channel.pathloss.reference, vecnorm(network.coordinate.reflect - network.coordinate.transmit), channel.pathloss.exponent.forward));
+	channel.pathloss.backward = pathloss(channel.pathloss.reference, vecnorm(network.coordinate.receive - network.coordinate.reflect), channel.pathloss.exponent.backward);
+	% * No RIS
+	channel.direct = flag.direct * sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair, network.pair);
+	channel.interference.direct(r) = interference_leakage(channel.direct);
+	% * Have RIS
+	for a = 1 : number.antenna
+		channel.forward = sqrt(channel.pathloss.forward) .* fading_nlos(reflect.antenna(a), transmit.antenna, 1, network.pair);
+		channel.backward = sqrt(channel.pathloss.backward) .* fading_nlos(receive.antenna, reflect.antenna(a), network.pair, 1);
+		for b = 1 : number.bond(a)
+			clear scatter_interference;
+			reflect.bond = 2 .^ (b - 1);
+			[reflect.beamformer, channel.aggregate] = scatter_interference(channel.direct, channel.forward, channel.backward, reflect.bond);
[…]

### 2024-12-20 src/ic_wsr_pair.m

@@ -1,0 +1,87 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream] = deal(4, 64, 4, 2);
+[network.coverage, network.pair] = deal(20, 2 : 2 : 10);
+[transmit.power, receive.noise] = deal(db2pow(20), db2pow(-75));
+[channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(db2pow(-30), 3, 2.4, 2.4);
+[reflect.bond, channel.uncertainty] = deal([1, reflect.antenna], [1e-2, 1e-1, 5e-1]);
+[number.bond, number.pair, number.uncertainty, number.realization] = deal(2, length(network.pair), length(channel.uncertainty), 1e2);
+
+for r = 1 : number.realization
+	for p = 1 : number.pair
+		network.weight = ones(1, 1, network.pair(p));
+		[network.coordinate.transmit, network.coordinate.reflect, network.coordinate.receive] = deal(distribution_disk(network.coverage, network.pair(p)), [0; 0], distribution_disk(network.coverage, network.pair(p)));
+		channel.pathloss.direct = pathloss(channel.pathloss.reference, vecnorm(network.coordinate.receive - network.coordinate.transmit), channel.pathloss.exponent.direct);
+		channel.pathloss.forward = pageswap(pathloss(channel.pathloss.reference, vecnorm(network.coordinate.reflect - network.coordinate.transmit), channel.pathloss.exponent.forward));
+		channel.pathloss.backward = pathloss(channel.pathloss.reference, vecnorm(network.coordinate.receive - network.coordinate.reflect), channel.pathloss.exponent.backward);
+		channel.direct.actual = sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair(p), network.pair(p));
+		channel.forward.actual = sqrt(channel.pathloss.forward) .* fading_nlos(reflect.antenna, transmit.antenna, 1, network.pair(p));
+		channel.backward.actual = sqrt(channel.pathloss.backward) .* fading_nlos(receive.antenna, reflect.antenna, network.pair(p), 1);
+		% * No RIS
[…]

### 2024-12-20 src/ic_wsr_sx.m

@@ -1,0 +1,79 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream] = deal(4, 2 .^ (4 : 2 : 8), 2, 4);
+[network.coverage, network.pair] = deal(20, 5);
+[transmit.power, receive.noise, network.weight] = deal(db2pow(-20 : 5 : 20), db2pow(-75), ones(1, 1, network.pair));
+[channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(db2pow(-30), 3, 2.4, 2.4);
+[number.bond, number.power, number.antenna, number.realization] = deal(2, length(transmit.power), length(reflect.antenna), 1e2);
+
+for r = 1 : number.realization
+	[network.coordinate.transmit, network.coordinate.reflect, network.coordinate.receive] = deal(distribution_disk(network.coverage, network.pair), [0; 0], distribution_disk(network.coverage, network.pair));
+	channel.pathloss.direct = pathloss(channel.pathloss.reference, vecnorm(network.coordinate.receive - network.coordinate.transmit), channel.pathloss.exponent.direct);
+	channel.pathloss.forward = pageswap(pathloss(channel.pathloss.reference, vecnorm(network.coordinate.reflect - network.coordinate.transmit), channel.pathloss.exponent.forward));
+	channel.pathloss.backward = pathloss(channel.pathloss.reference, vecnorm(network.coordinate.receive - network.coordinate.reflect), channel.pathloss.exponent.backward);
+	% * No RIS
+	channel.direct = sqrt(channel.pathloss.direct) .* fading_nlos(receive.antenna, transmit.antenna, network.pair, network.pair);
+	for p = 1 : number.power
+		transmit.beamformer = precoder_initialize(channel.direct, transmit.stream, transmit.power(p));
+		transmit.beamformer = precoder_wsr(channel.direct, transmit.beamformer, transmit.power(p), receive.noise, network.weight);
+		network.wsr.direct(p, r) = sum(network.weight .* rate_mimo(channel.direct, transmit.beamformer, receive.noise), 3);
+	end
+	% * Have RIS
[…]

### 2024-12-20 src/lib/interference_leakage.m

@@ -1,0 +1,4 @@
+function [I] = interference_leakage(H)
+	K = size(H, 3);
+	I = norm(H(:, :, ~logical(eye(K))), 'fro') ^ 2;
+end

### 2024-12-20 src/lib/precoder_wsr.m

@@ -1,0 +1,52 @@
+function [W] = precoder_wsr(H, W, P_t, P_n, rho)
+	[N_r, N_t, N_e, K] = deal(size(H, 1), size(H, 2), size(W, 2), size(W, 4));
+	[iter.converge, iter.tolerance, iter.counter] = deal(false, 1e-4, 0);
+	iter.J = sum(rho .* rate_mimo(H, W, P_n), 3);
+	while ~iter.converge
+		T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
+		Q = sum(T, 4) - T(:, :, logical(eye(K))) + P_n * eye(N_r);
+		F = pagemtimes(H(:, :, logical(eye(K))), pageswap(W));
+		G = pagemrdivide(pagectranspose(F), Q + T(:, :, logical(eye(K))));
+		V = rho .* pagehermitize(eye(N_e) + pagemtimes(pagemrdivide(pagectranspose(F), Q), F));
+		Y = pagemtimes(pagemtimes(pagemtimes(G, H), 'ctranspose', V, 'none'), pagemtimes(G, H));
+		for k = 1 : K
+			fun = @(lambda) norm(mldivide(sum(Y(:, :, :, k), 3) + lambda * eye(N_t), H(:, :, k, k)' * G(:, :, k)' * V(:, :, k)), 'fro') ^ 2 - P_t;
+			[lb, ub] = deal(0, 1e3);
+			if fun(lb) * fun(ub) < 0
+				lambda = bisection(fun, lb, ub);
+			else
+				lambda = 0;
+			end
+			W(:, :, :, k) = mldivide(sum(Y(:, :, :, k), 3) + lambda * eye(N_t), H(:, :, k, k)' * G(:, :, k)' * V(:, :, k));
+		end
+		J = sum(rho .* rate_mimo(H, W, P_n), 3);
+		iter.converge = (abs(J - iter.J) / iter.J <= iter.tolerance);
+		iter.J = J;
+		iter.counter = iter.counter + 1;
+	end
+end
+
+function [A] = pageswap(A)
+	A = permute(A, [1, 2, 4, 3]);
+end
+
+function [A] = pagehermitize(A)
+	A = 0.5 * (A + pagectranspose(A));
+end
+
+function [x] = bisection(fun, lb, ub)
+	assert(lb < ub, 'Lower bound must be smaller than upper bound.');
[…]

### 2024-12-20 src/lib/rate_mimo.m

@@ -1,4 +1,16 @@
 function [R] = rate_mimo(H, W, P_n)
-	R = log(det(eye(size(W, 2)) + (H * W)' * (H * W) / P_n));
+	if size(H, 3) == 1
+		R = log(det(eye(size(W, 2)) + (H * W)' * (H * W) / P_n));
+	else
+		[N_r, K] = deal(size(H, 1), size(H, 3));
+		T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
+		Q = sum(T, 4) - T(:, :, logical(eye(K))) + P_n * eye(N_r);
+		X = eye(N_r) + pagemldivide(Q, T(:, :, logical(eye(K))));
+		R = log(pagedet(X));
+	end
 	R = real(R);
+end
+
+function [d] = pagedet(A)
+	d = prod(pagesvd(A), 1);
 end

### 2024-12-20 src/lib/scatter_interference.m

@@ -1,0 +1,31 @@
+function [Theta, H] = scatter_interference(H_d, H_f, H_b, L)
+	persistent iter;
+	if isempty(iter)
+		Theta = eye(size(H_f, 1));
+	else
+		Theta = iter.Theta;
+	end
+
+	[K, G] = deal(size(H_d, 3), length(Theta) / L);
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+	[iter.converge, iter.tolerance, iter.counter, iter.I] = deal(false, 1e-4, 0, interference_leakage(H));
+	while ~iter.converge
+		for g = 1 : G
+			S = (g - 1) * L + 1 : g * L;
+			S_c = setdiff(1 : length(Theta), S);
+			D = H_d + pagemtimes(pagemtimes(H_b(:, S_c, :), Theta(S_c, S_c)), H_f(S_c, :, :, :));
+            T = pagemtimes(H_b(:, S, :), 'ctranspose', H_b(:, S, :), 'none');
+            B = max(pageeig(T)) .* repmat(eye(L), [1, 1, K]) - T + eps;
+			Q = pagemtimes(pagemtimes(pagemtimes(B, Theta(S, S)), H_f(S, :, :, :)) - pagemtimes(pagectranspose(H_b(:, S, :)), D), pagectranspose(H_f(S, :, :, :)));
+			M = sum(Q(:, :, ~logical(eye(K))), 3);
+			[U, ~, V] = svd(M);
+			Theta(S, S) = U * V';
+		end
+		H = channel_aggregate(H_d, H_f, H_b, Theta);
+		I = interference_leakage(H);
+		iter.converge = (abs(I - iter.I) / iter.I <= iter.tolerance);
+		iter.I = I;
+		iter.counter = iter.counter + 1;
+	end
+	iter.Theta = Theta;
+end

### 2024-12-20 src/lib/scatter_procrustes.m

@@ -1,0 +1,9 @@
+function [Theta, H] = scatter_procrustes(H_d, H_f, H_b, opt)
+	if opt == "left"
+		[U, ~, V] = svd(pinv(H_b) * H_d * H_f');
+	elseif opt == "right"
+		[U, ~, V] = svd(H_b' * H_d * pinv(H_f));
+	end
+	Theta = U * V';
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+end

### 2024-12-20 src/lib/scatter_procrustes_left.m

@@ -1,5 +1,0 @@
-function [Theta, H] = scatter_procrustes_left(H_d, H_f, H_b)
-	[U, ~, V] = svd(pinv(H_b) * H_d * H_f');
-	Theta = U * V';
-	H = channel_aggregate(H_d, H_f, H_b, Theta);
-end

### 2024-12-20 src/lib/scatter_procrustes_right.m

@@ -1,5 +1,0 @@
-function [Theta, H] = scatter_procrustes_right(H_d, H_f, H_b)
-	[U, ~, V] = svd(H_b' * H_d * pinv(H_f));
-	Theta = U * V';
-	H = channel_aggregate(H_d, H_f, H_b, Theta);
-end

### 2024-12-20 src/lib/scatter_rate.m

@@ -9,7 +9,7 @@ function [Theta, H] = scatter_rate(H_d, H_f, H_b, W, L, P_n)
 	G = length(Theta) / L;
 	H = channel_aggregate(H_d, H_f, H_b, Theta);
 	[G_e, G_r, D] = deal(zeros(size(Theta)));
-	[iter.converge, iter.tolerance, iter.counter, iter.R] = deal(false, 1e-4, 0, rate_mimo(H, W, P_n));
+	[iter.converge, iter.tolerance, iter.counter, iter.R] = deal(false, 1e-3, 0, rate_mimo(H, W, P_n));
 	while ~iter.converge
 		[iter.G_r, iter.D] = deal(G_r, D);
 		for g = 1 : G

### 2024-12-20 src/lib/scatter_wsr.m

@@ -1,0 +1,44 @@
+function [Theta, H] = scatter_wsr(H_d, H_f, H_b, W, L, P_n, rho)
+	persistent iter;
+	if isempty(iter)
+		Theta = eye(size(H_f, 1));
+	else
+		Theta = iter.Theta;
+	end
+
+	G = length(Theta) / L;
+	H = channel_aggregate(H_d, H_f, H_b, Theta);
+	[G_e, G_r, D] = deal(zeros(size(Theta)));
+	[iter.converge, iter.tolerance, iter.counter, iter.J] = deal(false, 1e-4, 0, sum(rho .* rate_mimo(H, W, P_n), 3));
+	while ~iter.converge
+		[iter.G_r, iter.D] = deal(G_r, D);
+		for g = 1 : G
+			S = (g - 1) * L + 1 : g * L;
+			S_c = setdiff(1 : length(Theta), S);
+			fun = @(Theta_g) sum(rho .* rate_mimo(H_d + pagemtimes(pagemtimes(H_b(:, S, :, :), Theta_g), H_f(S, :, :, :)) + pagemtimes(pagemtimes(H_b(:, S_c, :, :), Theta(S_c, S_c)), H_f(S_c, :, :, :)), W, P_n), 3);
+			G_e(S, S) = gradient_euclidean(H, H_f(S, :, :, :), H_b(:, S, :, :), W, P_n, rho);
+			G_r(S, S) = gradient_riemannian(Theta(S, S), G_e(S, S));
+			D(S, S) = direction_conjugate(G_r(S, S), struct('G_r', iter.G_r(S, S), 'D', iter.D(S, S), 'counter', iter.counter));
+			Theta(S, S) = step_armijo(fun, Theta(S, S), D(S, S));
+			H = channel_aggregate(H_d, H_f, H_b, Theta);
+		end
+		J = sum(rho .* rate_mimo(H, W, P_n), 3);
+		iter.converge = (abs(J - iter.J) / iter.J <= iter.tolerance);
+		iter.J = J;
+		iter.counter = iter.counter + 1;
+	end
+	iter.Theta = Theta;
+end
+
+function [G_e] = gradient_euclidean(H, H_f, H_b, W, P_n, rho)
+	[N_r, N_e, K] = deal(size(H, 1), size(W, 2), size(W, 4));
+	T = pagemtimes(pagemtimes(H, W), 'none', pagemtimes(H, W), 'ctranspose');
[…]

### 2024-12-20 src/lib/takagi_factorization.m

@@ -1,0 +1,10 @@
+function [Q, S] = takagi_factorization(A)
+    if norm(A - A.', 'fro') > 1e-10
+        error('Matrix A must be symmetric.');
+    end
+
+    [U, S, V] = svd(A);
+    t = diag(U' * conj(V));
+    phi = angle(t) / 2;
+    Q = U * diag(exp(1i * phi));
+end

### 2024-12-20 src/pc_power_sx.m

@@ -1,0 +1,92 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(16, 2 .^ (4 : 8), 16);
+% [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e2, false);
+
+for r = 1 : number.realization
+	% * No RIS
+	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	channel.power.direct(r) = norm(channel.direct, 'fro') ^ 2;
+	% * Have RIS
+	for a = 1 : number.antenna
+		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
+		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
+		for b = 1 : number.bond(a)
+			clear scatter_power_max;
+			reflect.bond = 2 .^ (b - 1);
+			[reflect.beamformer.iterative, channel.aggregate.iterative] = scatter_power_max(channel.direct, channel.forward, channel.backward, reflect.bond);
+			channel.power.aggregate.iterative(b, a, r) = norm(channel.aggregate.iterative, 'fro') ^ 2;
+		end
+		if flag.direct
+			[reflect.beamformer.procrustes.left, channel.aggregate.procrustes.left] = scatter_procrustes(channel.direct, channel.forward, channel.backward, "left");
+			[reflect.beamformer.procrustes.right, channel.aggregate.procrustes.right] = scatter_procrustes(channel.direct, channel.forward, channel.backward, "right");
+			channel.power.aggregate.procrustes.left(a, r) = norm(channel.aggregate.procrustes.left, 'fro') ^ 2;
[…]

### 2024-12-20 src/pc_power_symmetry.m

@@ -1,0 +1,98 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 2 .^ (4 : 2 : 6), 2);
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e2, false);
+
+for r = 1 : number.realization
+	% * No RIS
+	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	channel.power.direct(r) = norm(channel.direct, 'fro') ^ 2;
+	% * Have RIS
+	for a = 1 : number.antenna
+		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
+		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
+		for b = 1 : number.bond(a)
+			clear scatter_power_max;
+			reflect.bond = 2 .^ (b - 1);
+			[reflect.beamformer.asymmetric, channel.aggregate.asymmetric] = scatter_power_max(channel.direct, channel.forward, channel.backward, reflect.bond);
+			channel.power.aggregate.asymmetric(b, a, r) = norm(channel.aggregate.asymmetric, 'fro') ^ 2;
+
+			reflect.beamformer.symmetric.enforced = projection_symmetry(reflect.beamformer.asymmetric);
+			channel.aggregate.symmetric.enforced = channel_aggregate(channel.direct, channel.forward, channel.backward, reflect.beamformer.symmetric.enforced);
+			channel.power.aggregate.symmetric.enforced(b, a, r) = norm(channel.aggregate.symmetric.enforced, 'fro') ^ 2;
+
+			[reflect.beamformer.symmetric.legacy, channel.aggregate.symmetric.legacy] = scatter_power_max_symmetric_legacy(channel.forward, channel.backward, reflect.bond);
[…]

### 2024-12-20 src/pc_rate_symmetry.m

@@ -1,0 +1,106 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 2 .^ (4 : 4 : 8), 4);
+[transmit.power, receive.noise] = deal(db2pow(-20 : 5 : 20), db2pow(-75));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+transmit.snr = pow2db(transmit.power * channel.pathloss.direct ./ receive.noise);
+[number.power, number.antenna, number.realization] = deal(length(transmit.power), length(reflect.antenna), 1e2);
+
+for r = 1 : number.realization
+	% * No RIS
+	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	for p = 1 : number.power
+		transmit.beamformer.direct = precoder_rate(channel.direct, transmit.power(p), receive.noise);
+		receive.rate.direct(p, r) = rate_mimo(channel.direct, transmit.beamformer.direct, receive.noise);
+	end
+	% * Have RIS
+	for a = 1 : number.antenna
+		reflect.bond = reflect.antenna(a);
+		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
+		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
+		clear scatter_rate;
+		for p = 1 : number.power
+			transmit.beamformer.asymmetric = precoder_rate(channel.direct, transmit.power(p), receive.noise);
+			[iter.converge, iter.tolerance, iter.counter, iter.rate] = deal(false, 1e-4, 0, rate_mimo(channel.direct, transmit.beamformer.asymmetric, receive.noise));
+			while ~iter.converge
+				[reflect.beamformer.asymmetric, channel.aggregate.asymmetric] = scatter_rate(channel.direct, channel.forward, channel.backward, transmit.beamformer.asymmetric, reflect.bond, receive.noise);
+				transmit.beamformer.asymmetric = precoder_rate(channel.aggregate.asymmetric, transmit.power(p), receive.noise);
[…]

### 2024-12-20 src/pc_rate_txrx.m

@@ -4,7 +4,7 @@ clc; clear; close; setup;
 [transmit.power, receive.noise] = deal(db2pow(-20 : 5 : 20), db2pow(-75));
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
 [transmit.snr, reflect.bond] = deal(pow2db(transmit.power * channel.pathloss.direct ./ receive.noise), [1, reflect.antenna]);
-[number.bond, number.power, number.antenna, number.realization] = deal(length(reflect.bond), length(transmit.power), length(transmit.antenna), 100);
+[number.bond, number.power, number.antenna, number.realization] = deal(length(reflect.bond), length(transmit.power), length(transmit.antenna), 1e2);
 
 for r = 1 : number.realization
 	for a = 1 : number.antenna
@@ -29,7 +29,7 @@ for r = 1 : number.realization
 	end
 end
 receive.rate = mean(receive.rate, ndims(receive.rate));
-save('data/rate_txrx.mat');
+save('data/pc_rate_txrx.mat');
 
 figure('Name', 'Achievable Rate vs Transmit and Receive Antenna', 'Position', [0, 0, 500, 400]);
 hold all;
@@ -41,5 +41,5 @@ style_plot(handle.rate, 2);
 hold off; grid on; box on; legend('Location', 'nw');
 xlabel('Transmit Power [dB]');
 ylabel('Achievable Rate [bit/s/Hz]');
-savefig('plots/rate_txrx.fig');
-matlab2tikz('../assets/simulation/rate_txrx.tex', 'width', '10cm', 'height', '7.5cm');
+savefig('plots/pc_rate_txrx.fig');
+matlab2tikz('../assets/simulation/pc_rate_txrx.tex', 'width', '10cm', 'height', '7.5cm');

### 2024-12-20 src/pc_singular_bound.m

@@ -29,7 +29,7 @@ channel.singular.direct = mean(channel.singular.direct, ndims(channel.singular.d
 channel.singular.auxiliary = mean(channel.singular.auxiliary, ndims(channel.singular.auxiliary));
 channel.singular.aggregate.min = mean(channel.singular.aggregate.min, ndims(channel.singular.aggregate.min));
 channel.singular.aggregate.max = mean(channel.singular.aggregate.max, ndims(channel.singular.aggregate.max));
-save('data/singular_bound.mat');
+save('data/pc_singular_bound.mat');
 
 handle.singular = plotBarStackGroups(cat(3, channel.singular.aggregate.min, channel.singular.direct - channel.singular.aggregate.min, channel.singular.aggregate.max - channel.singular.direct), cellstr('$\sigma_' + string(vec(1 : channel.rank.direct)) + '(\mathbf{H})$'));
 for w = 1 : number.weight
@@ -38,8 +38,8 @@ end
 set(handle.bound, {'Color'}, {'#77AC30'}, {'LineStyle'}, {'-'; '--'; ':'; '-.'}, {'DisplayName'}, cellstr('$\sigma_' + string(vec(1 : channel.rank.direct)) + '(\mathbf{T})$'));
 hold off; grid on; box on; legend('Location', 'ne', 'NumColumns', 2);
 ylabel('Amplitude');
-savefig('plots/singular_bound.fig');
-matlab2tikz('../assets/simulation/singular_bound.tex', 'width', '10cm', 'height', '7.5cm', 'extraaxisoptions', {'legend columns=4', 'transpose legend', 'legend style={/tikz/column 2/.style={column sep=5pt}}'});
+savefig('plots/pc_singular_bound.fig');
+matlab2tikz('../assets/simulation/pc_singular_bound.tex', 'width', '10cm', 'height', '7.5cm', 'extraaxisoptions', {'legend columns=4', 'transpose legend', 'legend style={/tikz/column 2/.style={column sep=5pt}}'});
 
 function [H_a] = channel_auxiliary(H_d, H_f)
 	[~, ~, V_f] = svds(H_f, rank(H_f));

### 2024-12-20 src/power_sx.m

@@ -1,71 +1,0 @@
-clc; clear; close; setup;
-
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(16, 2 .^ (4 : 8), 16);
-% [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);
-[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e2, false);
-
-for r = 1 : number.realization
-	% * No RIS
-	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
-	channel.power.direct(r) = norm(channel.direct, 'fro') ^ 2;
-	% * Have RIS
-	for a = 1 : number.antenna
-		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
-		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
-		clear scatter_power_max;
-		for b = 1 : number.bond(a)
-			reflect.bond = 2 .^ (b - 1);
-			[reflect.beamformer, channel.aggregate] = scatter_power_max(channel.direct, channel.forward, channel.backward, reflect.bond);
-			channel.power.aggregate(b, a, r) = norm(channel.aggregate, 'fro') ^ 2;
-		end
-		if flag.direct
-			[~, channel.procrustes.left] = scatter_procrustes_left(channel.direct, channel.forward, channel.backward);
-			[~, channel.procrustes.right] = scatter_procrustes_right(channel.direct, channel.forward, channel.backward);
-			channel.power.procrustes.left(a, r) = norm(channel.procrustes.left, 'fro') ^ 2;
-			channel.power.procrustes.right(a, r) = norm(channel.procrustes.right, 'fro') ^ 2;
-		end
-	end
-end
[…]

### 2024-12-29 manuscript/main.tex
:dizzy: Convergence proof

@@
 % \title{Channel Shaping Using Beyond Diagonal RIS:\\Analysis, Optimization, and Enhanced Flexibility}
-% \title{MIMO Channel Shaping and Rate Maximization via Beyond Diagonal RIS}
+\title{MIMO Channel Shaping and Rate Maximization\\Using Beyond Diagonal RIS}
 % \title{MIMO Channel Shaping Using Beyond Diagonal RIS: Singular Value Redistribution and Rate Maximization}
-\title{Beyond Diagonal RIS: MIMO Channel Shaping and Rate Maximization}
+% \title{Beyond Diagonal RIS: MIMO Channel Shaping and Rate Maximization}
 \author{
@@
 	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence achieving the asymptotic \gls{dof} at low \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
-	% wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
+	% wider dynamic range (with better trade-off) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
 
@@
 	% $\boldsymbol{\sigma}(\cdot)$ and $\boldsymbol{\lambda}(\cdot)$ are the corresponding vectors.
-	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^\dagger$ $(\cdot)^{(r)}$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), Moore-Penrose inverse, $r$-th iterated point, and stationary point, respectively.
+	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^\dagger$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), Moore-Penrose inverse, and stationary point, respectively.
 	$[N]$ is a shortcut for $\{1,2,\ldots,N\}$.
@@
 		This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
-		Let $\mathbf{H}_\mathrm{D}^{[kj]} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{[k]} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{[j]} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
+		Let $\mathbf{H}_\mathrm{D}^{(kj)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{(j)} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
 		Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
@@
 		\begin{equation}
-			\mathbf{H}^{[kj]} = \mathbf{H}_\mathrm{D}^{[kj]} + \mathbf{H}_\mathrm{B}^{[k]} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{[j]} = \mathbf{H}_\mathrm{D}^{[kj]} + \sum_g \mathbf{H}_{\mathrm{B},g}^{[k]} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{[j]},
-			\label{eq:channel_equivalent_ic}
-		\end{equation}
-		where $\mathbf{H}_{\mathrm{B},g}^{[k]} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{[j]} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B},g}^{[k]}$ and rows of $\mathbf{H}_{\mathrm{F},g}^{[j]}$, respectively,
+			\label{eq:channel_interference}
+			\mathbf{H}^{(kj)} = \mathbf{H}_\mathrm{D}^{(kj)} + \mathbf{H}_\mathrm{B}^{(k)} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{(j)} = \mathbf{H}_\mathrm{D}^{(kj)} + \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)},
+		\end{equation}
+		where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B},g}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F},g}^{(j)}$, respectively,
 	\end{subsection}
@@
 		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
-		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected in all cases.
+		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected in all cases.
 This constraint is omitted in context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
@@
 		However, the power-optimal \gls{ris} still provides for a low-complexity decoupled solution.
-		The details will be discussed in Section~\ref{sc:rate}.
+		The details will be discussed in Section~\ref{sc:rate_pc}.
 
@@
 		The former solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without guarantee of optimality.
-		The latter generalizes the conjugate gradient methods to Riemannian manifolds and updates the solution by addition and retraction, constituting a zigzag path departing from and returning to the manifold.
+		The latter generalizes the conjugate gradient methods to Riemannian manifolds and updates the solution by addition and retraction, which constitutes a zigzag path departing from and returning to the manifold.
 		Next, we introduce a group-wise \emph{geodesic \gls{rcg}} method modified from \cite{Abrudan2008,Abrudan2009} that performs multiplicative updates along the geodesics on the Stiefel manifold for faster convergence.
-		It is applicable to a wide range of \gls{bd}-\gls{ris} design problems where the objective $f$ is smooth or convex non-smooth (not necessarily the symmetric gauge function \eqref{ob:shaping}) and the only constraint is group-wise unitarity \eqref{cn:shaping_unitary}.
+		It is applicable to a wide range of \gls{bd}-\gls{ris} design problems where the objective $f$ is smooth or convex non-smooth\footnote{$f$ is not necessarily the symmetric gauge function \eqref{ob:shaping}.} and the only constraint is group-wise unitarity \eqref{cn:shaping_unitary}.
 		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below:
@@
 				\end{equation}
-			\item \emph{Translate to the Riemannian gradient at $\mathbf{\Theta}_g^{(r)}$:} At point $\mathbf{\Theta}_g^{(r)}$, the Riemannian gradient gives the steepest ascent direction on the manifold.
+			\item \emph{Translate to the Riemannian (sub-)gradient at $\mathbf{\Theta}_g^{(r)}$:} At point $\mathbf{\Theta}_g^{(r)}$, the Riemannian (sub-)gradient gives the steepest ascent direction on the manifold.
 It lies in the tangent space of the manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$ and is obtainable by projection:
@@
 				\end{equation}
-			\item \emph{Translate to the Riemannian gradient at the identity:} The Riemannian gradient should be translated back to the identity for exploiting the Lie algebra\footnote{Lie algebra refers to the tangent space of the Lie group at the identity element.
+			\item \emph{Translate to the Riemannian (sub-)gradient at the identity:} The Riemannian (sub-)gradient should be translated back to the identity for exploiting the Lie algebra\footnote{Lie algebra refers to the tangent space of the Lie group at the identity element.
 A Lie group is simultaneously a continuous group and a differentiable manifold.
@@
 				\end{equation}
-			\item \emph{Determine the conjugate direction:} The conjugate direction is obtained over the Riemannian gradient and previous direction as
+			\item \emph{Determine the conjugate direction:} The conjugate direction is obtained over the Riemannian (sub-)gradient and previous direction as
 				\begin{equation}
@@
 				\State $\tilde{\gamma}_g^{(r)} \gets$ \eqref{eq:conjugate_parm_geod}, $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:conjugate_dirn_geod}
-				\If {$\Re\bigl\{\tr({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{Non-ascent}
+				\If {$\Re\bigl\{\tr({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{Not ascent}
 				\State $\mathbf{D}_g^{(r)} \gets \tilde{\nabla}_{\mathrm{R},g}^{(r)}$
 				\EndIf
-				\State $\mu \gets 0.1$ \Comment{Doubling cheaper than halving}
+				\State $\mu \gets 0.1$
 				\State $\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu) \gets$ \eqref{eq:geodesic_tran}
-				\While {$\scriptstyle f(\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(2\mu)) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
+				\While {$ f\bigl(\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \frac{\tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}})}{2}$}\label{ln:armijo_start}
 				\State $\mu \gets 2 \mu$
 				\EndWhile
-				\While {$\scriptstyle f(\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu)) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
+				\While {$f\bigl(\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \frac{\mu}{2} \cdot \frac{\tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}})}{2}$}
 				\State $\mu \gets \mu / 2$
@@
 
-		Algorithm~\ref{ag:rcg} summarizes the proposed group-wise geodesic \gls{rcg} method for group-connected \gls{bd}-\gls{ris} design when the objective is smooth or convex non-smooth and the only constraint is group-wise unitarity.
+		Algorithm~\ref{ag:rcg} summarizes the introduced group-wise geodesic \gls{rcg} method.
 		Compared to the non-geodesic approach, it leverages Lie algebra to replace the add-then-retract update with a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
@@
 		We now analyze the computational complexity of solving singular value shaping problem \eqref{op:shaping} by Algorithm~\ref{ag:rcg}.
-		To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:shaping_subdiff} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:geodesic_tran} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
-		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., line \ref{ln:armijo_start}--\ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
-
-		% TODO: compare O(D) and O(BD)
-
-		% \begin{subsubsection}{Pareto Frontier Characterization}
-		% 	\label{sc:pareto}
-		% 	We now characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel} by maximizing their weighted sum
-		% 	\begin{maxi!}
-		% 	{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
-		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:pareto_unitary}}
-		% 	\end{maxi!}
-		% 	where $\rho_n \ge 0$ is the weight of the $n$-th singular value.
-		% 	% that can be positive, zero, or negative.
-		% 	Varying $\{\rho_n\}_{n \in [N]}$ characterizes the Pareto frontier enclosing the singular value region such that problem \eqref{op:pareto} generalizes most singular value shaping problems.
-		% 	It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:pareto}.
-		% 	\begin{lemma}
-		% 		\label{lm:pareto}
-		% 		One Euclidean sub-gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
-		% 		\begin{equation}
-		% 			\label{eq:gradient_eucl_pareto}
-		% 			% \frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} =
-		% 			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \diag(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \in \frac{\partial \sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*}
-		% 		\end{equation}
-		% 		where $\mathbf{U}$ and $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$, respectively.
-		% 	\end{lemma}
-		% 	\begin{proof}
-		% 		Please refer to Appendix~\ref{ap:pareto}.
-		% 	\end{proof}
-		% \end{subsubsection}
+		To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean sub-gradient \eqref{eq:shaping_subdiff} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L) \bigr)$, Riemannian sub-gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:geodesic_tran} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
+		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., line \ref{ln:armijo_start}--\ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
+		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{RCG} N_\mathrm{S} \bigl(N N_\mathrm{T} N_\mathrm{R} + N (N_\mathrm{T}+N_\mathrm{R}) + I_\text{BLS}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{RCG} \bigl(N N_\mathrm{T} N_\mathrm{R} + N_\mathrm{S} N (N_\mathrm{T}+N_\mathrm{R}+N_\mathrm{S}) + I_\text{BLS} N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+
+		To validate Algorithm~\ref{ag:rcg} and quantify the shaping capability of \gls{bd}-\gls{ris}, we characterize the achievable singular value region of \gls{bd}-\gls{ris}-aided \gls{mimo} channel by considering the Pareto optimization problem
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:pareto_unitary}}
+		\end{maxi!}
+		where $\rho_n \ge 0$ is the weight associated with the $n$-th channel singular value.
+		Varying those weights help to characterize the Pareto frontier of singular values that encloses the achievable region.
+		While the objective \eqref{ob:pareto} does not suggest any meaningful performance metric (e.g., capacity or power gain), there exists an implicit relation since stronger channel shaping capability translates to better wireless performance.
+		Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd}.
+		It can be solved optimally by Algorithm~\ref{ag:rcg} with $\mathbf{D}_{[n,n]} = \rho_n$ in \eqref{eq:shaping_subdiff}.
 	\end{subsection}
@@
 	\begin{section}{Rate Maximization}
-		\label{sc:framework}
-		% Consider a special class of channel shaping problem
-		% \begin{maxi!}
-		% 	{\scriptstyle{\mathbf{\Theta}}}{f(\mathbf{H})}{\label{op:shaping}}{\label{ob:shaping}}
-		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
-		% \end{maxi!}
-		% where $f: \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}} \to \mathbb{R}$ is a unitary invariant function satisfying $f(\mathbf{U}^\mathsf{H} \mathbf{H} \mathbf{V}) = f(\mathbf{H})$ for any $\mathbf{H} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{U} \in \mathbb{U}^{N_\mathrm{R} \times N_\mathrm{R}}$, $\mathbf{V} \in \mathbb{U}^{N_\mathrm{T} \times N_\mathrm{T}}$.
-		% Examples of such $f$ include the $n$-th channel singular value, channel power gain, and channel capacity.
-		% According to
+		\label{sc:rate}
+		In this section, we first solve rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point and interference channels optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
 
 		\begin{subsection}{MIMO Point-to-Point Channel}
-			\label{sc:rate}
-			We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
+			\label{sc:rate_pc}
+			The achievable rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel is formulated as
 			\begin{maxi!}
@@
 			\end{maxi!}
-			where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
+			where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is maximum average transmit power.
 			Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
-			We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
+			Two approaches are proposed to solve it optimally or efficiently.
+			% We propose a local-optimal approach based on \gls{ao} and a low-complexity approach based on channel shaping.
 
@@
 				where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-			Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate}.
+				Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:rate}.
 				\begin{lemma}
 					\label{lm:rate}
-				The Euclidean gradient of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
+					The partial derivative of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
 					\begin{equation}
@@
 				\end{proof}
-			For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
-			\begin{equation}
-				\label{eq:precoder}
+				For a given $\mathbf{\Theta}$, the optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
+				\begin{equation}
+					\label{eq:precoder_rate}
 					\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
 				\end{equation}
-			where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation \cite{Clerckx2013}.
-
+				where $\mathbf{V}$ is the right singular matrix of $\mathbf{H}$ and $\mathbf{s}^\star$ is the optimal water-filling power allocation \cite{Clerckx2013}.
 				The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-			Similar to the analysis in Section \ref{sc:pareto}, the computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
-			On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+				The computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
+				On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder_rate} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
 				The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
+				That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+				% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{AO}\bigl(I_\text{RCG} N_\mathrm{S} (N + N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS}) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{AO}\bigl(I_\text{RCG} (NN_\mathrm{S}^2 + N_\mathrm{S} N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} N_\mathrm{S}^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
 			\end{subsubsection}
@@
 			\begin{subsubsection}{Low-Complexity Solution}
-				\label{sc:low_complexity}
-
-				\begin{paragraph}{Channel Power Gain}
-					\label{sc:power}
-				The \gls{mimo} channel power gain maximization problem is formulated with respect to the \gls{bd}-\gls{ris} scattering matrix
+				\label{sc:rate_pc_lc}
+				To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for maximum power gain and then optimize the active beamforming.
+				The channel power gain maximization problem is formulated as\footnote{Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
+Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.}
 				\begin{maxi!}
 					{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power}}{\label{ob:power}}
-				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{\label{cn:power_unitary}}{}
+					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{\label{cn:power_unitary}}{}
 				\end{maxi!}
-				which generalizes the problem of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and \gls{mimo} with negligible direct channel and fully-connected \gls{bd}-\gls{ris} ??.
-				Solving \eqref{op:power} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
-				% The key of solving \eqref{op:power} is to balance the additive and multiplicative space alignments.
-
-				\begin{remark}
-				Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
+				Inspired by \cite{Nie2017}, we propose a closed-form iterative solution that converges to a stationary point of Problem \eqref{op:power}.
+				The idea is to approximate the quadratic objective \eqref{ob:power} successively by Taylor expansion and solve each subproblem by group-wise \gls{svd}.
+
+				\begin{proposition}
+					\label{pp:power}
+					Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
+					\begin{equation}
+						\label{eq:ris_power}
+						\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+					\end{equation}
+					leads to a convergence of the objective function \eqref{ob:power} towards a stationary point,\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point due to the non-uniqueness of \gls{svd}, especially when $\mathbf{M}_g$ is rank-deficient.}
+					% Multiple solutions may yield similar objective function convergence behavior.}
+					where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of\footnote{We notice that the orthogonal projection of $\mathbf{M}_g$ onto the Stiefel manifold $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g$ coincides with $\mathbf{\Theta}_g$.} % \cite{Manton2002}
+					\begin{equation}
+						\label{eq:auxiliary_power}
+						\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+					\end{equation}
+				\end{proposition}
+
+				\begin{proof}
+					Please refer to Appendix~\ref{ap:power}.
+				\end{proof}
+
+				To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L\bigr)$ operations and its \gls{svd} requires $\mathcal{O}(L^3)$ operations.
+				The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
+				That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+				% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{SAA} N_\mathrm{S} \bigl(N_\mathrm{T} N_\mathrm{R} + N+N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{SAA} \bigl(N_\mathrm{T} N_\mathrm{R} + NN_\mathrm{S}^2+N_\mathrm{T} N_\mathrm{R} N_\mathrm{S} + N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+				% It is noteworthy that the computational complexity can be further reduced
+				For the latter, the computational complexity can be further reduced:
+				\begin{itemize}
+					\item \emph{Negligible direct channel:} The optimal solution to \eqref{op:power} has been solved in closed form by \eqref{eq:ris_nd_power_max}.
+					\item \emph{Non-negligible direct channel:} In terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
 					\begin{mini!}
@@
 					\end{mini!}
-				which relaxes the block-unitary constraint \eqref{cn:power_unitary} to unitary \eqref{cn:procrustes_wt} but still has no trivial solution.
-				One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
+					which still has no trivial solution.
+					One \emph{lossy} transformation \cite{Bell2003} shifts $\mathbf{\Theta}$ to sides of the product by Moore-Penrose inverse, formulating standard orthogonal Procrustes problems
 					\begin{mini!}
@@
 					\end{mini!}
-				which have global optimal solutions
+					with optimal solutions \cite[(6.4.1)]{Golub2013}
 					\begin{equation}
 						\label{eq:ris_procrustes}
-					\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
-				\end{equation}
-				where $\mathbf{U}$ and $\mathbf{V}$ are respectively any left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-				\end{remark}
-
-				It is worth noting that ??
-and \eqref{eq:ris_procrustes} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power} when the direct channel is negligible and significant, respectively.
-				However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
-				Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power} with arbitrary group size.
-				The idea is to successively approximate the quadratic objective \eqref{ob:power} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
-
-				\begin{proposition}
-					\label{pp:power}
-					Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
-					\begin{equation}
-						\label{eq:ris_power}
-						\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
-					\end{equation}
-					converges to a stationary point of \eqref{op:power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
-					\begin{equation}
-						\label{eq:auxiliary_power}
-						\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-					\end{equation}
-					% \begin{equation}
-					% 	% \begin{split}
-					% 		\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{1}^{(r+1)},\ldots,\mathbf{\Theta}_{g-1}^{(r+1)},\mathbf{\Theta}_{g}^{(r)},\ldots,\mathbf{\Theta}_{G}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-					% 	% \end{split}
-					% 	\label{eq:auxiliary_power}
-					% \end{equation}
-				\end{proposition}
-
-				\begin{proof}
-					Please refer to Appendix~\ref{ap:power}.
-				\end{proof}
-
-				We now analyze the computational complexity of solving channel gain maximization problem \eqref{op:power} by Proposition \ref{pp:power}.
-				To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its \gls{svd} requires $\mathcal{O}(L^3)$ operations.
-				The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
-				\end{paragraph}
-
-				We finally propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
-				The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_ris} by channel power gain maximization problem \eqref{op:power}, then proceed to conventional eigenmode transmission \eqref{eq:precoder}.
-				Both steps are solved in closed form and the computational complexity is $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr) + N N_\mathrm{T} N_\mathrm{R}\bigr)$.
-				While suboptimal, this shaping-inspired solution avoids outer iterations and efficiently handles inner iterations.
+						\mathbf{\Theta}_\textnormal{P-max-approx}^\textnormal{MIMO-HD} = \mathbf{U} \mathbf{V}^\mathsf{H},
+					\end{equation}
+					where $\mathbf{U}$ and $\mathbf{V}$ are respectively any left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$.
+				\end{itemize}
+
+				Although \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_procrustes} are of similar form, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
+				We will show in Section \ref{sc:simulation} that $\mathbf{\Theta}_\textnormal{P-max-approx}^\textnormal{MIMO-HD}$ is very close to optimal especially for a large $N_\mathrm{S}$.
+				Once the channel is shaped by \eqref{eq:ris_power} or \eqref{eq:ris_nd_power_max} or \eqref{eq:ris_procrustes}, the active beamforming is retrieved by \eqref{eq:precoder_rate}.
+				This two-stage solution avoids outer iterations and efficiently handles (or avoids) inner iterations.
 			\end{subsubsection}
@@
 
-		% \begin{subsection}{MIMO Interference Channel}
-
-			\begin{subsection}{Leakage Interference Minimization}
-				Leakage interference refers to the sum of all interference terms in \gls{ic}.
-				Assume all transmitter sends $N_\mathrm{E} \le N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ data streams to its intended receiver.
-				The leakage interference minimization problem is formulated with respect to all transmit precoders, all receiver combiners, and the scattering matrix as
-				\begin{mini!}
-					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}^{[kj]}_\mathrm{D} + \mathbf{H}^{[k]}_\mathrm{B} \mathbf{\Theta} \mathbf{H}^{[j]}_{\mathrm{F}}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
-					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
-					\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
-					\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
-				\end{mini!}
-				where $\mathbf{G}_k \in \mathbb{C}^{N_\mathrm{D} \times N_\mathrm{R}}$ is the combiner at receiver $k$ and $\mathbf{W}_j \in \mathbb{C}^{N_\mathrm{T} \times N_\mathrm{D}}$ is the precoder at transmitter $j$.
-				It is worth noting that $\mathbf{\Theta}_g$ is a square unitary matrix and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}$ is equivalent to $\mathbf{\Theta}_g \mathbf{\Theta}_g^\mathsf{H}=\mathbf{I}$, while $\mathbf{G}_k$ and $\mathbf{W}_j$ may be respectively ``fat'' and ``tall'' rectangular semi-unitary matrices such that \eqref{co:combiner} and \eqref{co:precoder} are required.
-				The non-convex problem can be solved iteratively by the \gls{bcd} method detailed below.
-
-				\begin{subsubsection}{Combiner and Precoder Design}
-					For a given $\mathbf{\Theta}$, problem \eqref{op:leakage} reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
-					At iteration $r$, the combiner at receiver $k$ is updated as
-					\begin{equation}
-						\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
-						\label{eq:combiner_leakage}
-					\end{equation}
-					where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of the interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H}$.
-					The precoder at transmitter $j$ is updated as
-					\begin{equation}
-						\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
-						\label{eq:precoder_leakage}
-					\end{equation}
-					where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} {\mathbf{H}^{[kj]}}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} {\mathbf{H}^{[kj]}}$ in the reciprocal network.
-				\end{subsubsection}
-
-				\begin{subsubsection}{Scattering Matrix Design}
-					Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_j\}$ are determined, we define $\bar{\mathbf{H}}^{[kj]}_\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}^{[kj]}_\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}^{[k]}_\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}^{[k]}_\mathrm{B}$, and $\bar{\mathbf{H}}^{[j]}_\mathrm{F} \triangleq \mathbf{H}^{[j]}_\mathrm{F} \mathbf{W}_j$.
-					The \gls{bd}-\gls{ris} subproblem boils down to
-					\begin{mini!}
-						{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}^{[kj]}_\mathrm{D} + \bar{\mathbf{H}}^{[k]}_\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}^{[j]}_\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
-						\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-					\end{mini!}
-					which can be viewed as a channel shaping problem on $\bar{\mathbf{H}}^{[kj]}_\mathrm{D}$, $\bar{\mathbf{H}}^{[k]}_\mathrm{B}$, and $\bar{\mathbf{H}}^{[j]}_\mathrm{F}$.
-
-					\begin{proposition}
-						Start from any $\mathbf{\Theta}^{(0)}$, the sequence
-						\begin{equation}
-							\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-							\label{eq:scatter_leakage}
-						\end{equation}
-						converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
-						\begin{equation}
-							\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{[j]}_{\mathrm{F},g} - {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} {\mathbf{D}^{[kj]}_{g}}^{(r)}\bigr) {\mathbf{H}^{[j]}_{\mathrm{F},g}}^\mathsf{H},
-						\end{equation}
-						where $\mathbf{B}_{k,g} = \lambda_1\bigl({\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{H}^{[k]}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{H}^{[k]}_{\mathrm{B},g}$ and
-						\begin{equation}
-							{\mathbf{D}^{[kj]}_{g}}^{(r)} = \mathbf{H}^{[jk]}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
-						\end{equation}
-					\end{proposition}
-					\begin{proof}
-						The proof is similar to Appendix~\ref{ap:power} and omitted here.
-					\end{proof}
-				\end{subsubsection}
-
-				Problem \eqref{op:leakage} can be solved iteratively by \eqref{eq:combiner_leakage}, \eqref{eq:precoder_leakage}, and \eqref{eq:scatter_leakage}.
-				Convergence to local-optimal points is guaranteed since each subproblem is solved optimally and the objective is bounded above.
-
-			\end{subsection}
-
-			\begin{subsection}{Weighted Sum-Rate Maximization}
-				Finally, we consider weighted sum-rate maximization in \gls{mimo}-\gls{ic} by joint active beamforming design at the transmitters and passive beamforming design at the \gls{ris}.
-				The achievable rate of transmission $k$ is given by
-				\begin{equation}
-					R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{[kj]}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kj]}} \mathbf{W}_k\biggr),
-				\end{equation}
-				where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
-				\begin{equation}
-					\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H} + \eta \mathbf{I},
-				\end{equation}
-				and $\eta$ is the average noise power.
-				The optimization problem is formulated as
+		\begin{subsection}{MIMO Interference Channel}
+			On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
+			\begin{equation}
+				R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kj)}} \mathbf{W}_k\biggr),
+			\end{equation}
+			where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
+			The weighted sum-rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
 			\begin{maxi!}
-					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{\sum_k \rho_k R_k}{\label{op:ic_rate}}{\label{ob:ic_rate}}
+				{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr}}{\label{ob:wsr}}
 				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
@@
 			\end{maxi!}
-				where $\rho_k$ is the weight that denotes the priority of transmission $k$.
-				The problem is non-convex and can be solved by the \gls{ao} method detailed below.
-
-				\begin{subsubsection}{Precoder Design}
-					For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution has been proposed in \cite{Negro2010} based on mutual information-\gls{mmse} relationship \cite{Guo2005}.
-					We restate the steps as follows.
-
+			where $\rho_k \ge 0$ is the weight associated with transmission $k$.
+			This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate_pc} as detailed below.
+
+			\begin{subsubsection}{Alternating Optimization}
+				This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
+				For a given precoder set, the passive beamforming subproblem is
+				\begin{maxi!}
+					{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr_ris}}{\label{ob:wsr_ris}}
+					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+				\end{maxi!}
+				which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.
+
+				\begin{lemma}
+					\label{lm:wsr}
+					The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
+					\begin{equation}
+						\label{eq:gradient_eucl_wsr}
+						\begin{split}
+							\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K & \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
+							& \times \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
+						\end{split}
+					\end{equation}
+					where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
+				\end{lemma}
+
+				\begin{proof}
+					Please refer to Appendix~\ref{ap:wsr}.
+				\end{proof}
+
+				For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
+				A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
 				At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
 				\begin{equation}
-						\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{[kk]}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H}\bigr)^{-1},
+					\begin{split}
+						\mathbf{G}_k^{(r)} &= {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \\
+						& \quad \times \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
+					\end{split}
 				\end{equation}
@@
 				\begin{equation}
-						\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{[kk]}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
-					\end{equation}
-					the \gls{mse} weight is
-					\begin{equation}
-						\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
-					\end{equation}
-					the Lagrange multiplier is
-					\begin{equation}
-						\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)}}^\mathsf{H} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
-					\end{equation}
-					where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{[kj]}} \mathbf{W}_j^{(r)}$.
-					The optimal precoder at transmitter $k$ is given by
-					\begin{equation}
-						\mathbf{W}_k^{(r)} = \Bigl(\sum_j {\mathbf{H}^{[jk]}}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{[jk]} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} {\mathbf{H}^{[kk]}}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
-					\end{equation}
+					\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+				\end{equation}
+				and the optimal precoder at transmitter $k$ is given by
+				\begin{equation}
+					\label{eq:precoder_wsr}
+					\begin{split}
+						\mathbf{W}_k^{(r)} & = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \\
+						& \quad \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
+					\end{split}
+				\end{equation}
+				where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
+				\begin{equation}
+					\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
+					% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
+				\end{equation}
+				where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.
+
+				The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
+				That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
 			\end{subsubsection}
 
-				\begin{subsubsection}{Scattering Matrix Design}
-					Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} with respect to \gls{ris} block $g$ is
-					\begin{equation}
-						\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_k \rho_k {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kk]}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - {\mathbf{H}^{[kk]}}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{[j]}_{\mathrm{F},g}}^\mathsf{H}\bigr).
-						\label{eq:ic_rate_gradient_ris}
-					\end{equation}
+			\begin{subsubsection}{Low-Complexity Solution}
+				Similar to Section \ref{sc:rate_pc_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
+				The leakage interference minimization problem is formulated as
+				\begin{mini!}
+					{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{\label{op:interference}}{\label{ob:interference}}
+					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+				\end{mini!}
+				which can be solved iteratively in closed form.
+
+				\begin{proposition}
+					\label{pp:interference}
+					Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
+					\begin{equation}
+						\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+						\label{eq:scatter_leakage}
+					\end{equation}
+					converges to a stationary point of \eqref{op:interference}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
+					\begin{equation}
+						\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
+					\end{equation}
+					where $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}.$
+				\end{proposition}
+				\begin{proof}
+					Please refer to Appendix~\ref{ap:interference}.
+				\end{proof}
 			\end{subsubsection}
-				The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:rcg} where line ?? uses \eqref{eq:ic_rate_gradient_ris} explicitly.
-			\end{subsection}
+			Once the channel is shaped by \eqref{eq:scatter_leakage}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
+			This Two-stage solution avoids outer iterations and efficiently handles inner iterations.
+		\end{subsection}
+
+			% \begin{subsection}{Leakage Interference Minimization}
+			% 	Leakage interference refers to the sum of all interference terms in \gls{ic}.
+			% 	Assume all transmitter sends $N_\mathrm{E} \le N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ data streams to its intended receiver.
+			% 	The leakage interference minimization problem is formulated with respect to all transmit precoders, all receiver combiners, and the scattering matrix as
+			% 	\begin{mini!}
+			% 		{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}_{k \in [K]}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}^{(kj)}_\mathrm{D} + \mathbf{H}^{(k)}_\mathrm{B} \mathbf{\Theta} \mathbf{H}^{(j)}_{\mathrm{F}}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
+			% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
+			% 		\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
+			% 		\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
+			% 	\end{mini!}
+			% 	where $\mathbf{G}_k \in \mathbb{C}^{N_\mathrm{D} \times N_\mathrm{R}}$ is the combiner at receiver $k$ and $\mathbf{W}_j \in \mathbb{C}^{N_\mathrm{T} \times N_\mathrm{D}}$ is the precoder at transmitter $j$.
+			% 	It is worth noting that $\mathbf{\Theta}_g$ is a square unitary matrix and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}$ is equivalent to $\mathbf{\Theta}_g \mathbf{\Theta}_g^\mathsf{H}=\mathbf{I}$, while $\mathbf{G}_k$ and $\mathbf{W}_j$ may be respectively ``fat'' and ``tall'' rectangular semi-unitary matrices such that \eqref{co:combiner} and \eqref{co:precoder} are required.
+			% 	The non-convex problem can be solved iteratively by the \gls{bcd} method detailed below.
+
+			% 	\begin{subsubsection}{Combiner and Precoder Design}
+			% 		For a given $\mathbf{\Theta}$, problem \eqref{op:leakage} reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
+			% 		At iteration $r$, the combiner at receiver $k$ is updated as
+			% 		\begin{equation}
+			% 			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
+			% 			\label{eq:combiner_leakage}
+			% 		\end{equation}
+			% 		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of the interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}}$.
+			% 		The precoder at transmitter $j$ is updated as
+			% 		\begin{equation}
+			% 			\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
+			% 			\label{eq:precoder_leakage}
+			% 		\end{equation}
+			% 		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} {\mathbf{H}^{(kj)\mathsf{H}}} {\mathbf{G}_k^{(r)\mathsf{H}}} \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}}$ in the reciprocal network.
+			% 	\end{subsubsection}
+
+			% 	\begin{subsubsection}{Scattering Matrix Design}
+			% 		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_j\}$ are determined, we define $\bar{\mathbf{H}}^{(kj)}_\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}^{(kj)}_\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}^{(k)}_\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}^{(k)}_\mathrm{B}$, and $\bar{\mathbf{H}}^{(j)}_\mathrm{F} \triangleq \mathbf{H}^{(j)}_\mathrm{F} \mathbf{W}_j$.
+			% 		The \gls{bd}-\gls{ris} subproblem boils down to
+			% 		\begin{mini!}
+			% 			{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}^{(kj)}_\mathrm{D} + \bar{\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}^{(j)}_\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
+			% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+			% 		\end{mini!}
+			% 		which can be viewed as a channel shaping problem on $\bar{\mathbf{H}}^{(kj)}_\mathrm{D}$, $\bar{\mathbf{H}}^{(k)}_\mathrm{B}$, and $\bar{\mathbf{H}}^{(j)}_\mathrm{F}$.
+
+			% 		\begin{proposition}
+			% 			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
+			% 			\begin{equation}
+			% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+			% 				\label{eq:scatter_leakage}
+			% 			\end{equation}
+			% 			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
+			% 			\begin{equation}
+			% 				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)}_{g}}^{(r)}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
+			% 			\end{equation}
+			% 			where $\mathbf{B}_{k,g} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and
+			% 			\begin{equation}
+			% 				{\mathbf{D}^{(kj)}_{g}}^{(r)} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
+			% 			\end{equation}
+			% 		\end{proposition}
+			% 		\begin{proof}
+			% 			The proof is similar to Appendix~\ref{ap:power} and omitted here.
+			% 		\end{proof}
+			% 	\end{subsubsection}
+
+			% 	Problem \eqref{op:leakage} can be solved iteratively by \eqref{eq:combiner_leakage}, \eqref{eq:precoder_leakage}, and \eqref{eq:scatter_leakage}.
+			% 	Convergence to local-optimal points is guaranteed since each subproblem is solved optimally and the objective is bounded above.
+
+			% \end{subsection}
+
+			% \begin{subsection}{Weighted Sum-Rate Maximization}
+			% 	Finally, we consider weighted sum-rate maximization in \gls{mimo}-\gls{ic} by joint active beamforming design at the transmitters and passive beamforming design at the \gls{ris}.
+			% 	The achievable rate of transmission $k$ is given by
+			% 	\begin{equation}
+			% 		R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kj)}} \mathbf{W}_k\biggr),
+			% 	\end{equation}
+			% 	where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
+			% 	\begin{equation}
+			% 		\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I},
+			% 	\end{equation}
+			% 	and $\eta$ is the average noise power.
+			% 	The optimization problem is formulated as
+			% 	\begin{maxi!}
+			% 		{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_k \rho_k R_k}{\label{op:ic_rate}}{\label{ob:ic_rate}}
+			% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+			% 		\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
+			% 	\end{maxi!}
+			% 	where $\rho_k$ is the weight that denotes the priority of transmission $k$.
+			% 	The problem is non-convex and can be solved by the \gls{ao} method detailed below.
+
+			% 	\begin{subsubsection}{Precoder Design}
+			% 		For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution has been proposed in \cite{Negro2010} based on mutual information-\gls{mmse} relationship \cite{Guo2005}.
+			% 		We restate the steps as follows.
+
+			% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
+			% 		\begin{equation}
+			% 			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
+			% 		\end{equation}
+			% 		the corresponding error matrix is
+			% 		\begin{equation}
+			% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+			% 		\end{equation}
+			% 		the \gls{mse} weight is
+			% 		\begin{equation}
+			% 			\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
+			% 		\end{equation}
+			% 		the Lagrange multiplier is
+			% 		\begin{equation}
+			% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
+			% 		\end{equation}
+			% 		where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.
+			% 		The optimal precoder at transmitter $k$ is given by
+			% 		\begin{equation}
+			% 			\mathbf{W}_k^{(r)} = \Bigl(\sum_j {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)}.
+			% 		\end{equation}
+			% 	\end{subsubsection}
+
+			% 	\begin{subsubsection}{Scattering Matrix Design}
+			% 		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} with respect to \gls{ris} block $g$ is
+			% 		\begin{equation}
+			% 			\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_k \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr).
+			% 			\label{eq:ic_rate_gradient_ris}
+			% 		\end{equation}
+			% 	\end{subsubsection}
+			% 	The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:rcg} where line ?? uses \eqref{eq:ic_rate_gradient_ris} explicitly.
+			% \end{subsection}
 		% \end{subsection}
@@
 
-% 	\begin{subsection}{Achievable Rate Maximization}\label{sc:rate}
+% 	\begin{subsection}{Achievable Rate Maximization}\label{sc:rate_pc}
 % 		We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
@@
  We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than \gls{d}-\gls{ris}.
- This translates to a wider dynamic range of and better tradeoff between singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
+ This translates to a wider dynamic range of and better trade-off between singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
  We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds for practical deployment scenarios.
@@
 \begin{appendix}
-% \begin{subsection}{Proof of Proposition \ref{pp:dof}}
-% 	\label{ap:dof}
-% 	The scattering matrix of \gls{bd}-\gls{ris} can be decomposed as
-% 	\begin{equation}
-% 		\mathbf{\Theta} = \mathbf{L} \mathbf{\Theta}_\mathrm{D} \mathbf{R}^\mathsf{H},
-% 	\end{equation}
-% 	where $\mathbf{\Theta}_\mathrm{D} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ corresponds to \gls{d}-\gls{ris} and $\mathbf{L}, \mathbf{R} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are block-diagonal matrices of $L \times L$ unitary blocks.
-% 	Manipulating $\mathbf{L}$ and $\mathbf{R}$ rotates the linear spans of $\bar{\mathbf{H}}_\mathrm{B} \triangleq \mathbf{H}_\mathrm{B} \mathbf{L}$ and $\bar{\mathbf{H}}_\mathrm{F} \triangleq \mathbf{R}^\mathsf{H} \mathbf{H}_\mathrm{F}$ and maintains their rank.
-% 	On the other hand, there exists a $\mathbf{\Theta}_\mathrm{D}$ such that
-% 	\begin{equation*}
-% 		\begin{split}
-% 			\rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta}_\mathrm{D} \mathbf{H}_\mathrm{F})
-% 			 & = \min \bigl( \rank(\mathbf{H}_\mathrm{B}), \rank(\mathbf{\Theta}_\mathrm{D}), \rank(\mathbf{H}_\mathrm{F}) \bigr) \\
-% 			 & = \min \bigl( \rank(\bar{\mathbf{H}}_\mathrm{B}), N_\mathrm{S}, \rank(\bar{\mathbf{H}}_\mathrm{F}) \bigr)          \\
-% 			 & = \max_\mathbf{\Theta} \ \rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
-% 		\end{split}
-% 	\end{equation*}
-% 	The same result holds if the direct channel is significant and the proof is omitted here.
-% \end{subsection}
-
 	\begin{subsection}{Proof of Proposition \ref{pp:dof}}
@@
 		It suffices to consider the rank of the indirect channel.
-	% Denote the rank of the
-	% Let $r_\mathrm{B}$ and $r_\mathrm{F}$ be the ranks of the backward and forward channels, respectively.
 		Denote the \gls{svd} of the backward and forward channels as
@@
 		and thus
-	% the following inequality holds
-	% \begin{equation}
-	% 	\max(r_\mathrm{B} - r_\mathrm{F}, 0) \le r_\mathrm{L}(\mathbf{\Theta}) \le \min(N_\mathrm{S} - r_\mathrm{F}, r_\mathrm{B}),
-	% \end{equation}
-	% which implies
 		\begin{equation}
@@
 		\end{equation}
-	% where $\bar{\mathbf{U}}_{\mathrm{B}/\mathrm{F}}$ and $\bar{\mathbf{V}}_{\mathrm{B}/\mathrm{F}}$ are arbitrary unitary matrices.
 		where $\bar{\mathbf{U}}_{\mathrm{B}} \in \mathbb{U}^{N_\mathrm{R} \times N_\mathrm{R}}$, $\bar{\mathbf{V}}_\mathrm{B}, \bar{\mathbf{U}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\bar{\mathbf{V}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{T} \times N_\mathrm{T}}$ can be designed arbitrarily.
@@
 		The attainability of the lower bound can be proved similarly and the details are omitted.
-
-	% In \eqref{iq:sv_nd_indl}, the set of upper bounds
-	% \begin{equation}
-	% 	\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N]^3, i+j=n+1\bigr\}
-	% 	\label{iq:sv_nd_indl_set_max}
-	% \end{equation}
-	% is a special case of \eqref{iq:horn} with $(I, J, K) \in [N]^3$.
-	% The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
-However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
-	% On the other hand, the set of lower bounds
-	% \begin{equation}
-	% 	\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N]^3, i+j=n+N\bigr\}
-	% 	\label{iq:sv_nd_indl_set_min}
-	% \end{equation}
-	% can be induced by \eqref{iq:sv_nd_indl_set_max}, \eqref{eq:sv_product_all}, and the non-negativity of singular values.
-	% The maximum of \eqref{iq:sv_nd_indl_set_min} is selected as the tightest lower bound in \eqref{iq:sv_nd_indl}.
-
-	% To attain the upper bound of $\sigma_n(\mathbf{H})$, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ channel singular values.
-	% This is achieved by proper matching of the first $n$ modes of $\mathbf{H}_\mathrm{B}$ to the first $n$ modes of $\mathbf{H}_\mathrm{F}$.
-	% In particular, mode $i$ of $\mathbf{H}_\mathrm{B}$ should be completely aligned with mode $j$ of $\mathbf{H}_\mathrm{F}$ where $(i, j) = \arg \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ for $\mathbf{P}$
-
-	% % Interested readers are referred to \cite[Equation~2.0.3]{Zhang2005} for more information.
-	% % $i$-th mode of $\mathbf{H}_\mathrm{B}$ with the $j$-th mode of $\mathbf{H}_\mathrm{F}$ such that the $n$-th mode of $\mathbf{H}$ is maximized.
-
-	% % Maximizing $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}) \le \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is equivalent to maximizing the minimum of the first $n$ channel singular values.
-	% % As such, the \gls{bd}-\gls{ris} needs to align t
-	% % align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that the first $n$ modes of $\mathbf{H}$ are maximized.
-	% % To maximize the $n$-th channel singular value, the \gls{bd}-\gls{ris} needs to ensure
-	% % that the first $n$ modes of $\mathbf{H}$ are
-
-	% % should align the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ such that
-
-	% % \cite[Equation~2.0.3]{Zhang2005}
 	\end{subsection}
@@
 		\begin{equation*}
-		\sum_n \lambda_n(\tilde{\mathbf{B}}) \lambda_{N_\mathrm{S}-n+1}(\tilde{\mathbf{F}}) \le \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr) \le \sum_n \lambda_n(\tilde{\mathbf{B}}) \lambda_n(\tilde{\mathbf{F}}),
+			\sum_{n=1}^N \lambda_n(\tilde{\mathbf{B}}) \lambda_{N_\mathrm{S}-n+1}(\tilde{\mathbf{F}}) \le \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr) \le \sum_{n=1}^N \lambda_n(\tilde{\mathbf{B}}) \lambda_n(\tilde{\mathbf{F}}),
 		\end{equation*}
@@
 		\end{equation}
-	% $$\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$$
 		where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
@@
 
-% \begin{subsection}{Proof of Lemma \ref{lm:pareto}}
-% 	\label{ap:pareto}
-% 	The sub-differential of $\sigma_n(\mathbf{H})$ with respect to $\mathbf{H}$ is given by
-% 	\begin{equation*}
-% 		\partial \sigma_n(\mathbf{H}) = \mathbf{u}_n \mathbf{v}_n^\mathsf{H},
-% 	\end{equation*}
-
-% 	Let $\mathbf{H} = \sum_n \mathbf{u}_n \sigma_n \mathbf{v}_n^\mathsf{H}$ be the \gls{svd} of the equivalent channel.
-% 	Since the singular vectors are orthonormal, the $n$-th singular value can be expressed as
-% 	\begin{equation}
-% 		\sigma_n = \mathbf{u}_n^\mathsf{H} \mathbf{H} \mathbf{v}_n = \mathbf{u}_n^\mathsf{T} \mathbf{H}^* \mathbf{v}_n^*.
-% 	\end{equation}
-
-% 	Let $f(\mathbf{\Theta}_g) = \sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})$. Its sub-differential is defined as
-% 	\begin{equation}
-% 		\Bigl\{\mathbf{Y} \mid f(\tilde{\mathbf{\Theta}}_g) \ge f(\mathbf{\Theta}_g) + \tr\bigl(\mathbf{Y}^\mathsf{H} (\tilde{\mathbf{\Theta}}_g - \mathbf{\Theta}_g)\bigr), \forall \tilde{\mathbf{\Theta}}_g \in \mathbb{U}^{L \times L}\Bigr\}.
-% 	\end{equation}
-
-% 	whose sub-gradient with respect to $\mathbf{\Theta}_g^*$ is
-% 	\begin{align*}
-% 		\partial \sigma_n
-% 		 & = \partial \mathbf{u}_n^\mathsf{T} \underbrace{\mathbf{H}^* \mathbf{v}_n^*}_{\sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T} \mathbf{v}_n^*} + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \underbrace{\mathbf{u}_n^\mathsf{T} \mathbf{H}^*}_{\mathbf{u}_n^\mathsf{T} \sum_m \mathbf{u}_m^* \sigma_m \mathbf{v}_m^\mathsf{T}} \partial \mathbf{v}_n^* \\
-% 		 & = \underbrace{\partial \mathbf{u}_n^\mathsf{T} \mathbf{u}_n^*}_{\partial 1 = 0} \cdot \sigma_n + \mathbf{u}_n^\mathsf{T} \cdot \partial \mathbf{H}^* \cdot \mathbf{v}_n^* + \sigma_n \cdot \underbrace{\mathbf{v}_n^\mathsf{T} \partial \mathbf{v}_n^*}_{\partial 1 = 0}                                                                                                                  \\
-% 		 & = \mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*                                                                                                                                                                                                                                                 \\
-% 		 & = \tr(\mathbf{H}_{\mathrm{F},g}^* \mathbf{v}_n^*\mathbf{u}_n^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*).
-% 	\end{align*}
-% 	According to \cite{Hjorungnes2007}, the corresponding complex derivative is
-% 	\begin{equation}
-% 		\label{eq:gradient_eucl_sv_indl}
-% 		\frac{\partial \sigma_n}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{u}_n \mathbf{v}_n^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-% 	\end{equation}
-% 	A linear combination of \eqref{eq:gradient_eucl_sv_indl} yields \eqref{eq:gradient_eucl_pareto}.
-% \end{subsection}
-
-\begin{subsection}{Proof of Proposition \ref{pp:power}}
-	\label{ap:power}
-The differential of \eqref{ob:power} with respect to $\mathbf{\Theta}_g^*$ is
-\begin{align*}
-	\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
-	 & = \tr\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr) \\
-	 & = \tr\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
-\end{align*}
-and the corresponding complex derivative is
-\begin{equation}
-	\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{M}_g.
-\end{equation}
-% For a given $\mathbf{\Theta}$, we approximate the quadratic objective \eqref{ob:power} by local Taylor expansion and recast problem \eqref{op:power} as
-
-First, we approximate the quadratic objective \eqref{ob:power} by its local Taylor expansion
-\begin{maxi!}
-{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_ris_taylor}}{\label{ob:power_ris_taylor}}
-\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
-\end{maxi!}
-Let $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$ be the \gls{svd} of $\mathbf{M}_g$.
-We have
-\begin{equation}
-	\Re \bigl\{\tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \tr(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \tr(\mathbf{\Sigma}_g).
-\end{equation}
-The upper bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$, which implies the optimal solution of \eqref{op:power_ris_taylor} is $\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$, $\forall g$.
-
-Next, we prove that solving \eqref{op:power_ris_taylor} successively does not decrease \eqref{ob:power}.
-Since $\tilde{\mathbf{\Theta}}$ optimal for problem \eqref{op:power_ris_taylor}, we have $\sum_g 2 \Re\bigl\{ \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{M}_g) \bigr\} \ge \sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}$ which is explicitly expressed by \eqref{iq:power_ris_taylor}.
-% \begin{equation}
-% 	\label{iq:power_ris_taylor}
-% 	\scriptstyle
-% 	\begin{split}
-% 		2 \Re \Bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \\
-% 		\ge 2 \Re \Bigl\{\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}
-% 	\end{split}
-% \end{equation}
-\begin{multline}
-	\label{iq:power_ris_taylor}
-	\scriptstyle{2 \Re \bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}} \\
-	\scriptstyle{\ge 2 \Re \bigl\{\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}}
-\end{multline}
-% Expanding both side gives \eqref{iq:power_ris_taylor}.
-On the other hand, expanding $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ gives \eqref{iq:auxiliary_nonnegative}.
-\begin{multline}
-	\label{iq:auxiliary_nonnegative}
-	\scriptstyle{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} }\\
-		\scriptstyle{\mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\bigr\} + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0}
-\end{multline}
-Adding \eqref{iq:power_ris_taylor} and \eqref{iq:auxiliary_nonnegative}, we have
-\begin{multline}
-	2 \Re \bigl\{\tr(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
-	\ge 2 \Re \bigl\{\tr({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
-\end{multline}
-which suggests that updating $\tilde{\mathbf{\Theta}}$ does not decrease \eqref{ob:power}.
-% \begin{figure*}
-% \begin{equation}
-% 	\label{iq:power_ris_taylor}
-% 	\resizebox{0.95\textwidth}{!}{
-% 		$2 \Re \Bigl\{\sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\} \ge 2 \Re \Bigl\{\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\Bigr\}$
-% 	}
-% \end{equation}
-% 	\begin{equation}
-% 		\label{iq:auxiliary_nonnegative}
-% 		\resizebox{0.95\textwidth}{!}{
-% 			$\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) - 2 \Re \Bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\Bigr\} + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \ge 0$
-% 		}
-% 	\end{equation}
-% 	\hrulefill
-% \end{figure*}
-
-Finally, we prove that the converging point of \eqref{op:power_ris_taylor}, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power}.
-The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
-\begin{gather}
-	\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_ris_optimal}\\
-	\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_ris_taylor_optimal}
-\end{gather}
-On convergence, \eqref{eq:power_ris_taylor_optimal} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
-\mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^?
-\mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_ris_optimal}.
-The proof is thus completed.
-\end{subsection}
-
 	\begin{subsection}{Proof of Lemma \ref{lm:rate}}
@@
 
+	\begin{subsection}{Proof of Proposition \ref{pp:power}}
+		\label{ap:power}
+		The differential of \eqref{ob:power} with respect to $\mathbf{\Theta}_g^*$ is
+		\begin{align*}
+			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
+			& = \tr\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr) \\
+			& = \tr\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
+		\end{align*}
+		and the corresponding complex derivative is
+		\begin{equation}
+			\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \triangleq \mathbf{M}_g,
+		\end{equation}
+		whose \gls{svd} is denoted as $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$.
+		The quadratic objective \eqref{ob:power} can be successively approximated by its first-order Taylor expansion, resulting in the subproblem
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_ris_taylor}}{\label{ob:power_ris_taylor}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+		\end{maxi!}
+		whose optimal solution is
+		\begin{equation}
+			\label{eq:ris_power_taylor}
+			\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}, \quad \forall g.
+		\end{equation}
+		This is because $\Re \bigl\{\tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \tr(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \tr(\mathbf{\Sigma}_g)$ and the bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$.
+
+		Next, we prove that solving the affine approximation \eqref{op:power_ris_taylor} by \eqref{eq:ris_power_taylor} does not decrease \eqref{ob:power}.
+		Since $\tilde{\mathbf{\Theta}} = \diag(\tilde{\mathbf{\Theta}}_1, \ldots, \tilde{\mathbf{\Theta}}_G)$ is optimal for \eqref{op:power_ris_taylor}, we have
+		\begin{equation}
+			\label{iq:power_ris_taylor}
+			\begin{split}
+				2 \Re \bigl\{ & \sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
+				& + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\} \\
+				\ge 2 \Re \bigl\{ &\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
+				& + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}.
+			\end{split}
+		\end{equation}
+		Besides, $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ implies
+		\begin{equation}
+			\label{iq:auxiliary_nonnegative}
+			\begin{split}
+				& \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \\
+				& \quad + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \\
+				\ge & 2 \Re \bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\bigr\}.
+			\end{split}
+		\end{equation}
+		Adding \eqref{iq:power_ris_taylor} and \eqref{iq:auxiliary_nonnegative}, we have
+		\begin{equation}
+			\begin{split}
+				& 2 \Re \bigl\{\tr(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
+				\ge & 2 \Re \bigl\{\tr({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
+			\end{split}
+		\end{equation}
+		which suggests that \eqref{ob:power} is non-decreasing as the solution iterates over \eqref{eq:ris_power_taylor}.
+		Since \eqref{ob:power} is also bounded from above, the sequence of objective values converges.
+
+		Finally, we prove that any solution when \eqref{ob:power} converges, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power}.
+		The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
+		\begin{gather}
+			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_ris_optimal}\\
+			\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_ris_taylor_optimal}
+		\end{gather}
+		On convergence of \eqref{ob:power}, we have $\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^? \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2$
+
+		\eqref{eq:power_ris_taylor_optimal} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
+\mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^?
+\mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_ris_optimal}.
+		The proof is thus completed.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Lemma \ref{lm:wsr}}
+		\label{ap:wsr}
+		The differential of $f = \sum_{k=1}^K \rho_k R_k$ with respect to $\mathbf{\Theta}_g^*$ is
+		\begin{align*}
+			\partial f
+			& = \sum_{k=1}^K \rho_k \tr \Bigl\{ \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \Bigl( \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \\
+			& \quad + \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(k)} - \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \\
+			& \quad \times \sum_{j \ne k} \Bigl(\mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \\
+			& \quad + \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \Bigr) \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \Bigr) \mathbf{W}_k \Bigr\} \\
+			& = \sum_{k=1}^K \rho_k \Bigl( \tr \Bigl\{ \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H}\Bigr\} \\
+			& \quad + \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g \Bigr\} \\
+			& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \\
+			& \quad \quad \times \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+			& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \\
+			& \quad \quad \times \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \Bigr\} \Bigr),
+		\end{align*}
+		and the corresponding complex derivative is \eqref{eq:gradient_eucl_wsr}.
+	\end{subsection}
+
+	\begin{subsection}{Proof of Proposition \ref{pp:interference}}
+		\label{ap:interference}
+		Minimizing \eqref{ob:interference} is equivalent to maximizing
+		% \begin{align*}
+		% 	f &= \sum_{k=1}^K \sum_{j \ne k} \tr \Bigl\{ \sum_g \bigl(- \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H}\bigr)\Bigr\}
+		% \end{align*}
+		\begin{align*}
+			f(\mathbf{\Theta}) & = - I + \sum_g \beta_g^{(k)} \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \Bigr\} \\
+			& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
+			& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+			& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
+			& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
+			& \quad + \tr \Bigl\{ \sum_g \beta_g^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
+			& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
+			& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+			& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
+			& \quad + \tr \Bigl\{ \sum_g \mathbf{B}_{g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\},
+		\end{align*}
+		where $\mathbf{B}_{g}^{(k)} = \beta_g^{(k)} \mathbf{I} - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)}$ and the relaxation constant $\beta_g^{(k)}$ can be chosen arbitrarily.
+		One can choose $\beta_g^{(k)} = \lambda_1(\mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)})$ to ensure the positive semi-definiteness of $\mathbf{B}_{g}^{(k)}$ and formulate a quadratic function to be maximized.
+		The remaining proof is similar to Appendix \ref{ap:power} and omitted here.
+	\end{subsection}
 \end{appendix}
 
-% \begin{section}{\glsentryshort{mimo}-\glsentryshort{ic}}
-% 	\begin{subsection}{Leakage Interference Minimization}
-% 		\begin{mini!}
-% 			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}_{kj}^\mathrm{D} + \mathbf{H}_k^\mathrm{B} \mathbf{\Theta} \mathbf{H}_j^\mathrm{F}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{}{}
-% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-% 			\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad \mathbf{W}_k^\mathsf{H} \mathbf{W}_k=\mathbf{I}, \quad \forall k.}{}{}
-% 		\end{mini!}
-% 		The non-convex problem can be solved by \gls{bcd} method.
-% 		For a given $\mathbf{\Theta}$, it reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
-% 		At iteration $r$, the combiner at receiver $k$ is updated as
-% 		\begin{equation}
-% 			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)\mathsf{H}}},
-% 		\end{equation}
-% 		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)\mathsf{H}}} \mathbf{H}_{kj}^\mathsf{H}$.
-% 		The precoder at transmitter $j$ is updated as
-% 		\begin{equation}
-% 			\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
-% 		\end{equation}
-% 		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds to interference covariance matrix $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} \mathbf{H}_{kj}^\mathsf{H} {\mathbf{G}_k^{(r)\mathsf{H}}} \mathbf{G}_k^{(r)} \mathbf{H}_{kj}$ in the reciprocal network.
-% 		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_k\}$ are determined, we define $\bar{\mathbf{H}}_{kj}^\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}_{kj}^\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}_k^\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}_k^\mathrm{B}$, and $\bar{\mathbf{H}}_j^\mathrm{F} \triangleq \mathbf{H}_j^\mathrm{F} \mathbf{W}_j$.
-% 		The \gls{bd}-\gls{ris} subproblem reduces to
-% 		\begin{mini!}
-% 			{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}_{kj}^\mathrm{D} + \bar{\mathbf{H}}_k^\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}_j^\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
-% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
-% 		\end{mini!}
-
-% 		\begin{proposition}
-% 			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
-% 			\begin{equation}
-% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-% 			\end{equation}
-% 			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
-% 			\begin{equation}
-% 				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}_{j,g}^\mathrm{F} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{D}_{kj,g}^{(r)}\bigr) {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H},
-% 			\end{equation}
-% 			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{k,g}^\mathrm{B}$ and
-% 			\begin{equation}
-% 				\mathbf{D}_{kj,g}^{(r)} = \mathbf{H}_{jk}^\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
-% 			\end{equation}
-% 		\end{proposition}
-% 		\begin{proof}
-% 			To be added.
-% 		\end{proof}
-
-% 		\begin{figure}[!t]
-% 			\centering
-% 			\resizebox{0.65\columnwidth}{!}{
-% 				\input{../assets/simulation/ic_interference_sx.tex}
-% 			}
-% 			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
-Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}.
-$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$, and reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB}.}
-% 			\label{fg:ic_interference_sx}
-% 		\end{figure}
-% 		Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
-% 		In this case, a unitary $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
-% 		Interestingly, the result suggests that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than \gls{d}-\gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
-% 	\end{subsection}
-
-% 	\begin{subsection}{Weighted Sum-Rate Maximization}
-% 		\begin{maxi!}
-% 			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{J_2 = \sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k \mathbf{H}_{kj}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kj} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
-% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-% 			\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
-% 		\end{maxi!}
-% 		where $\rho_k$ is the weight of user $k$ and $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix
-% 		\begin{equation}
-% 			\mathbf{Q}_k = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H} + \eta \mathbf{I}.
-% 		\end{equation}
-% 		For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution based on \gls{wsr}-\gls{wmmse} relationship is proposed in \cite{Negro2010}.
-% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
-% 		\begin{equation}
-% 			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)\mathsf{H}}} \mathbf{H}_{kk}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} \mathbf{H}_{kk}^\mathsf{H}\bigr)^{-1},
-% 		\end{equation}
-% 		the corresponding error matrix is
-% 		\begin{equation}
-% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{(r-1)} \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
-% 		\end{equation}
-% 		the \gls{mse} weight is
-% 		\begin{equation}
-% 			\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
-% 		\end{equation}
-% 		the Lagrange multiplier is
-% 		% \begin{equation}
-% 		% 	\begin{split}
-% 		% 		\lambda_k^{(r)}
-% 		% 		& = \frac{\sum_{j \ne k} \tr(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)\mathsf{H}}}) - \sum_{j \ne k} \tr(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)\mathsf{H}}})}{P_k} \\
-% 		% 		& \quad + \frac{\tr(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}})}{P_k}
-% 		% 	\end{split}
-% 		% \end{equation}
-% 		\begin{equation}
-% 			\lambda_k^{(r)} = \frac{\tr\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
-% 		\end{equation}
-% 		where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} \mathbf{H}_{kj} \mathbf{W}_j^{(r)}$.
-% 		The precoder at transmitter $k$ is
-% 		\begin{equation}
-% 			\mathbf{W}_k^{(r)} = \Bigl(\sum_j \mathbf{H}_{jk}^\mathsf{H} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}_{jk} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \mathbf{H}_{kk}^\mathsf{H} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)}.
-% 		\end{equation}
-% 		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} with respect to \gls{ris} block $g$ is
-% 		\begin{equation}
-% 			\begin{split}
-% 				\frac{\partial J_2}{\partial \mathbf{\Theta}_g^*}
-% 				& = \sum_k \rho_k {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kk} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
-% 				& \quad \times \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H}\bigr).
-% 			\end{split}
-% 			\label{eq:ic_rate_gradient_ris}
-% 		\end{equation}
-% 		The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:ic_rate_gradient_ris}.
-
-% 		\begin{figure}[!t]
-% 			\centering
-% 			\resizebox{0.65\columnwidth}{!}{
-% 				\input{../assets/simulation/ic_rate_sx.tex}
-% 			}
-% 			\caption{Average weighted sum-rate versus \gls{snr}, \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
-$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
-% 			\label{fg:ic_rate_sx}
-% 		\end{figure}
-
-% 		\begin{figure}[!t]
-% 			\centering
-% 			\resizebox{0.65\columnwidth}{!}{
-% 				\input{../assets/simulation/ic_rate_user.tex}
-% 			}
-% 			\caption{Average weighted sum-rate versus user pairs $K$, \gls{ris} elements $N^\mathrm{S}$ and group size $L$ at $\mathrm{SNR} = \qty{15}{dB}$.
-$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}) = (4, 4, 3)$, $\rho_k = 1, \ \forall k$.}
-% 			\label{fg:ic_rate_user}
-% 		\end{figure}
-
-% 		A new observation from Fig.~\ref{fg:ic_rate_sx} that the interference alignment capability of \gls{bd}-\gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
-% 	\end{subsection}
-% \end{section}
+\begin{section}{Acknowledgement}
+	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct some technical errors and improve the clarity of the manuscript.
+\end{section}
 

### 2024-12-30 assets/simulation/pc_power_sx_txrx16_nd.tex
:construction: Add interference channel results

@@
 %
-\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
-\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
-\definecolor{mycolor3}{rgb}{0.92941,0.69412,0.12549}%
-\definecolor{mycolor4}{rgb}{0.49412,0.18431,0.55686}%
-\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
+\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
+\definecolor{mycolor2}{rgb}{0.00000,0.44706,0.74118}%
+\definecolor{mycolor3}{rgb}{0.85000,0.32500,0.09800}%
+\definecolor{mycolor4}{rgb}{0.85098,0.32549,0.09804}%
+\definecolor{mycolor5}{rgb}{0.92900,0.69400,0.12500}%
+\definecolor{mycolor6}{rgb}{0.92941,0.69412,0.12549}%
+\definecolor{mycolor7}{rgb}{0.49400,0.18400,0.55600}%
+\definecolor{mycolor8}{rgb}{0.49412,0.18431,0.55686}%
+\definecolor{mycolor9}{rgb}{0.46600,0.67400,0.18800}%
+\definecolor{mycolor10}{rgb}{0.46667,0.67451,0.18824}%
+\definecolor{mycolor11}{rgb}{0.30100,0.74500,0.93300}%
+\definecolor{mycolor12}{rgb}{0.50196,0.50196,0.50196}%
 %
@@
 xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
-% xlabel style={font=\color{white!15!black}},
+xlabel style={font=\color{white!15!black}},
 xlabel={RIS Group Size},
-ymode=log,
-% ymin=0,
-ymax=0.000115917330108446,
-yminorticks=true,
-% ylabel style={font=\color{white!15!black}},
+ymin=0,
+ymax=0.000116439758271769,
+ylabel style={font=\color{white!15!black}},
 ylabel={Channel Power [W]},
@@
 ymajorgrids,
-yminorgrids,
 legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
 ]
-\addplot [color=mycolor1, line width=2.0pt]
+\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
+x	y\\
+5	8.18421179472296e-07\\
+};
+\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor4, forget plot] table[row sep=crcr]{%
+x	y\\
+6	2.47795062804422e-06\\
+};
+\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor6, forget plot] table[row sep=crcr]{%
+x	y\\
+7	8.20088397806638e-06\\
+};
+\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
+x	y\\
+8	2.94451091720999e-05\\
+};
+\addplot[only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor10, forget plot] table[row sep=crcr]{%
+x	y\\
+9	0.000111552731718914\\
+};
+\addplot[draw=none, only marks, mark=o, mark options={solid}, mark size=2pt, line width=2pt, draw=mycolor12] table[row sep=crcr]{%
+x	y\\
+0	0\\
+};
+\addlegendentry{Explicit}
+
+\addplot [color=mycolor2, line width=2.0pt]
   table[row sep=crcr]{%
-1	5.62265231393471e-07\\
-2	6.30889582242226e-07\\
-3	7.11254960263e-07\\
-4	7.81326631210281e-07\\
-5	8.14448482525861e-07\\
+1	5.66270957115429e-07\\
+2	6.32214073230813e-07\\
+3	7.11789599032912e-07\\
+4	7.83501502399535e-07\\
+5	8.1582630412623e-07\\
 };
@@
 
-\addplot [color=mycolor2, dashed, line width=2.0pt]
+\addplot [color=mycolor4, dashed, line width=2.0pt]
   table[row sep=crcr]{%
-1	1.28776059362021e-06\\
-2	1.49666859439015e-06\\
-3	1.7748873501561e-06\\
-4	2.08628203322482e-06\\
-5	2.32064182394341e-06\\
-6	2.40700699069632e-06\\
+1	1.31853309573688e-06\\
+2	1.53662356650387e-06\\
+3	1.82774899163227e-06\\
+4	2.1412614461017e-06\\
+5	2.38070294433103e-06\\
+6	2.46743024417076e-06\\
 };
@@
 
-\addplot [color=mycolor3, dotted, line width=2.0pt]
+\addplot [color=mycolor6, dotted, line width=2.0pt]
   table[row sep=crcr]{%
-1	3.15006337524297e-06\\
-2	3.87312444339353e-06\\
-3	4.86242306926796e-06\\
-4	6.08760688271974e-06\\
-5	7.25680982863437e-06\\
-6	7.92125259488618e-06\\
-7	8.12946998504463e-06\\
+1	3.16991712195604e-06\\
+2	3.88139289638628e-06\\
+3	4.87508772014936e-06\\
+4	6.11547438007159e-06\\
+5	7.2872459799269e-06\\
+6	7.95147687920036e-06\\
+7	8.1598841971569e-06\\
 };
@@
 
-\addplot [color=mycolor4, dashdotted, line width=2.0pt]
+\addplot [color=mycolor8, dashdotted, line width=2.0pt]
   table[row sep=crcr]{%
-1	8.09679926499813e-06\\
-2	1.03932623438214e-05\\
-3	1.38959563603953e-05\\
-4	1.85906493199221e-05\\
-5	2.38130628567437e-05\\
-6	2.73295770613527e-05\\
-7	2.8861300924676e-05\\
-8	2.93516301422595e-05\\
+1	8.08840132190028e-06\\
+2	1.03513925278208e-05\\
+3	1.38370561575957e-05\\
+4	1.85667340754753e-05\\
+5	2.37528268575109e-05\\
+6	2.72839029873604e-05\\
+7	2.87929093680483e-05\\
+8	2.92781883450922e-05\\
 };
@@
 
-\addplot [color=mycolor5, line width=2.0pt]
+\addplot [color=mycolor10, line width=2.0pt]
   table[row sep=crcr]{%
-1	2.17722070426804e-05\\
-2	2.9526076730669e-05\\
-3	4.18291043077588e-05\\
-4	5.97087109667717e-05\\
-5	8.17036753929845e-05\\
-6	9.7962703850956e-05\\
-7	0.000105935331911385\\
-8	0.000109247922920587\\
-9	0.000110397457246139\\
+1	2.18463432534312e-05\\
+2	2.96551238699234e-05\\
+3	4.20172201243997e-05\\
+4	5.99730466582087e-05\\
+5	8.20696998678401e-05\\
+6	9.8504151463339e-05\\
+7	0.00010650814145777\\
+8	0.000109789012745988\\
+9	0.000110895007877875\\
 };

### 2024-12-30 manuscript/main.tex
:construction: Add interference channel results

@@
 	% in special channel conditions.
-	% in two common scenarios: 1) forward/backward channel is rank-deficient and 2) direct channel is blocked.
+	% in two common scenarios: 1) backward/forward channel is rank-deficient and 2) direct channel is blocked.
 	% respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris} via matrix analysis.
@@
 	\begin{subsection}{Related Works}
-		At a specific resource block, channel shaping metrics can be classified into two categories:
+		At a specific resource block, channel shaping metrics can be categorized into two types.
 		% shaping metrics can be classified into two categories:
@@
 		Fourth, we provide an analytical answer to the shaping question in typical deployment scenarios.
-		% For rank-deficient forward/backward channel,
-		When the forward/backward channel is rank-deficient, we derive singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris} with asymptotically large number of elements.
+		% For rank-deficient backward/forward channel,
+		When the backward/forward channel is rank-deficient, we derive singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris} with asymptotically large number of elements.
 		% For negligible direct channel
@@
 
-		% 1) rank-deficient forward/backward channel and 2) direct channel being blocked.
+		% 1) rank-deficient backward/forward channel and 2) direct channel being blocked.
 
@@
 		% % revisit the channel singular value shaping problem from an analytical perspective via matrix analysis.
-		% % To explore the ultimate shaping limits, we derive individual and collective singular value bounds for rank-deficient forward/backward channel and blocked direct channel.
+		% % To explore the ultimate shaping limits, we derive individual and collective singular value bounds for rank-deficient backward/forward channel and blocked direct channel.
 		% % Asymptotic bounds shared by diagonal and \gls{bd}-\gls{ris} are derived in the former case, while exact bounds for unitary \gls{bd}-\gls{ris} are derived in the latter case.
-		% Asymptotic channel singular value bounds applying to diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient forward/backward channel.
+		% Asymptotic channel singular value bounds applying to diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient backward/forward channel.
 		% On the other hand, tight bounds for fully-connected \gls{bd}-\gls{ris} with finite number of elements are derived for blocked direct channel.
@@
 	$\conv(\cdot)$ returns the convex hull of arguments.
+	$\mathrm{vec}(\cdot)$ stacks the columns of a matrix sequentially into a vector.
 	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
@@
 			\begin{subequations}
+				\label{eq:ris_nd_power}
 				\begin{align}
@@
 		However, the power-optimal \gls{ris} still provides for a low-complexity decoupled solution.
-		The details will be discussed in Section~\ref{sc:rate_pc}.
+		The details will be discussed in Section~\ref{sc:rate}.
 
@@
 		Proposition \ref{pp:dof}--\ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
-		Extending the analysis to more general cases (e.g., non-negligible direct channel and arbitrary \gls{bd}-\gls{ris} group size) is non-trivial due to limited branch matching and mode alignment capabilities therein.
+		Extending the analysis to more general cases (e.g., significant direct channel and arbitrary \gls{bd}-\gls{ris} group size) is non-trivial due to limited branch matching and mode alignment capabilities therein.
 		A numerical solution will be discussed in Section~\ref{sc:shaping_numerical}.
@@
 
-		With Proposition \ref{pp:shaping}, one can apply the \emph{relax-then-project} method \cite{Shen2020a,Fang2023} or \emph{non-geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}} \cite{Li2023b,Li2023c,Zhou2023} to solve Problem \eqref{op:shaping}.
+		With Proposition \ref{pp:shaping}, one can apply the \emph{relax-then-project} method \cite{Shen2020a,Fang2023} or \emph{non-geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}} \cite{Li2023b,Li2023c,Zhou2023} to solve problem \eqref{op:shaping}.
 		The former solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without guarantee of optimality.
@@
 		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below:
-		\begin{enumerate}
+		\begin{enumerate}[label=(\roman*)]
 			\item \emph{Compute the Euclidean (sub-)gradient at $\mathbf{\Theta}_g^{(r)}$:} The (sub-)gradient of $f$ with respect to $\mathbf{\Theta}_g$ in the Euclidean space is
@@
 \begin{section}{Rate Maximization}
+	In this section, we first solve rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point and interference channels optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
+
+	\begin{subsection}{MIMO Point-to-Point Channel}
 		\label{sc:rate}
-		In this section, we first solve rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point and interference channels optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
-
-		\begin{subsection}{MIMO Point-to-Point Channel}
-			\label{sc:rate_pc}
 		The achievable rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel is formulated as
@@
 		Two approaches are proposed to solve it optimally or efficiently.
-			% We propose a local-optimal approach based on \gls{ao} and a low-complexity approach based on channel shaping.
 
 		\begin{subsubsection}{Alternating Optimization}
+			\label{sc:rate_ao}
 			This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
@@
 		\begin{subsubsection}{Low-Complexity Solution}
-				\label{sc:rate_pc_lc}
+			\label{sc:rate_lc}
 			To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for maximum power gain and then optimize the active beamforming.
@@
 			\end{maxi!}
-				Inspired by \cite{Nie2017}, we propose a closed-form iterative solution that converges to a stationary point of Problem \eqref{op:power}.
+			Inspired by \cite{Nie2017}, we propose a closed-form iterative solution that converges to a stationary point of problem \eqref{op:power}.
 			The idea is to approximate the quadratic objective \eqref{ob:power} successively by Taylor expansion and solve each subproblem by group-wise \gls{svd}.
@@
 			% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{SAA} N_\mathrm{S} \bigl(N_\mathrm{T} N_\mathrm{R} + N+N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{SAA} \bigl(N_\mathrm{T} N_\mathrm{R} + NN_\mathrm{S}^2+N_\mathrm{T} N_\mathrm{R} N_\mathrm{S} + N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-				% It is noteworthy that the computational complexity can be further reduced
 			For the latter, the computational complexity can be further reduced:
@@
 		where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
-			The weighted sum-rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
+		The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
 		\begin{maxi!}
@@
 		where $\rho_k \ge 0$ is the weight associated with transmission $k$.
-			This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate_pc} as detailed below.
+		This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
 
 		\begin{subsubsection}{Alternating Optimization}
+			\label{sc:wsr_ao}
 			This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
@@
 		\begin{subsubsection}{Low-Complexity Solution}
-				Similar to Section \ref{sc:rate_pc_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
+			\label{sc:wsr_lc}
+			Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
 			The leakage interference minimization problem is formulated as
@@
 		Once the channel is shaped by \eqref{eq:scatter_leakage}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
-			This Two-stage solution avoids outer iterations and efficiently handles inner iterations.
-		\end{subsection}
-
-			% \begin{subsection}{Leakage Interference Minimization}
-			% 	Leakage interference refers to the sum of all interference terms in \gls{ic}.
-			% 	Assume all transmitter sends $N_\mathrm{E} \le N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ data streams to its intended receiver.
-			% 	The leakage interference minimization problem is formulated with respect to all transmit precoders, all receiver combiners, and the scattering matrix as
-			% 	\begin{mini!}
-			% 		{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}_{k \in [K]}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}^{(kj)}_\mathrm{D} + \mathbf{H}^{(k)}_\mathrm{B} \mathbf{\Theta} \mathbf{H}^{(j)}_{\mathrm{F}}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
-			% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
-			% 		\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
-			% 		\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
-			% 	\end{mini!}
-			% 	where $\mathbf{G}_k \in \mathbb{C}^{N_\mathrm{D} \times N_\mathrm{R}}$ is the combiner at receiver $k$ and $\mathbf{W}_j \in \mathbb{C}^{N_\mathrm{T} \times N_\mathrm{D}}$ is the precoder at transmitter $j$.
-			% 	It is worth noting that $\mathbf{\Theta}_g$ is a square unitary matrix and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}$ is equivalent to $\mathbf{\Theta}_g \mathbf{\Theta}_g^\mathsf{H}=\mathbf{I}$, while $\mathbf{G}_k$ and $\mathbf{W}_j$ may be respectively ``fat'' and ``tall'' rectangular semi-unitary matrices such that \eqref{co:combiner} and \eqref{co:precoder} are required.
-			% 	The non-convex problem can be solved iteratively by the \gls{bcd} method detailed below.
-
-			% 	\begin{subsubsection}{Combiner and Precoder Design}
-			% 		For a given $\mathbf{\Theta}$, problem \eqref{op:leakage} reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
-			% 		At iteration $r$, the combiner at receiver $k$ is updated as
-			% 		\begin{equation}
-			% 			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
-			% 			\label{eq:combiner_leakage}
-			% 		\end{equation}
-			% 		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of the interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}}$.
-			% 		The precoder at transmitter $j$ is updated as
-			% 		\begin{equation}
-			% 			\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
-			% 			\label{eq:precoder_leakage}
-			% 		\end{equation}
-			% 		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} {\mathbf{H}^{(kj)\mathsf{H}}} {\mathbf{G}_k^{(r)\mathsf{H}}} \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}}$ in the reciprocal network.
-			% 	\end{subsubsection}
-
-			% 	\begin{subsubsection}{Scattering Matrix Design}
-			% 		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_j\}$ are determined, we define $\bar{\mathbf{H}}^{(kj)}_\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}^{(kj)}_\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}^{(k)}_\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}^{(k)}_\mathrm{B}$, and $\bar{\mathbf{H}}^{(j)}_\mathrm{F} \triangleq \mathbf{H}^{(j)}_\mathrm{F} \mathbf{W}_j$.
-			% 		The \gls{bd}-\gls{ris} subproblem boils down to
-			% 		\begin{mini!}
-			% 			{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}^{(kj)}_\mathrm{D} + \bar{\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}^{(j)}_\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
-			% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-			% 		\end{mini!}
-			% 		which can be viewed as a channel shaping problem on $\bar{\mathbf{H}}^{(kj)}_\mathrm{D}$, $\bar{\mathbf{H}}^{(k)}_\mathrm{B}$, and $\bar{\mathbf{H}}^{(j)}_\mathrm{F}$.
-
-			% 		\begin{proposition}
-			% 			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
-			% 			\begin{equation}
-			% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-			% 				\label{eq:scatter_leakage}
-			% 			\end{equation}
-			% 			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
-			% 			\begin{equation}
-			% 				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)}_{g}}^{(r)}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
-			% 			\end{equation}
-			% 			where $\mathbf{B}_{k,g} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and
-			% 			\begin{equation}
-			% 				{\mathbf{D}^{(kj)}_{g}}^{(r)} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
-			% 			\end{equation}
-			% 		\end{proposition}
-			% 		\begin{proof}
-			% 			The proof is similar to Appendix~\ref{ap:power} and omitted here.
-			% 		\end{proof}
-			% 	\end{subsubsection}
-
-			% 	Problem \eqref{op:leakage} can be solved iteratively by \eqref{eq:combiner_leakage}, \eqref{eq:precoder_leakage}, and \eqref{eq:scatter_leakage}.
-			% 	Convergence to local-optimal points is guaranteed since each subproblem is solved optimally and the objective is bounded above.
-
-			% \end{subsection}
-
-			% \begin{subsection}{Weighted Sum-Rate Maximization}
-			% 	Finally, we consider weighted sum-rate maximization in \gls{mimo}-\gls{ic} by joint active beamforming design at the transmitters and passive beamforming design at the \gls{ris}.
-			% 	The achievable rate of transmission $k$ is given by
-			% 	\begin{equation}
-			% 		R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kj)}} \mathbf{W}_k\biggr),
-			% 	\end{equation}
-			% 	where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
-			% 	\begin{equation}
-			% 		\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I},
-			% 	\end{equation}
-			% 	and $\eta$ is the average noise power.
-			% 	The optimization problem is formulated as
-			% 	\begin{maxi!}
-			% 		{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_k \rho_k R_k}{\label{op:ic_rate}}{\label{ob:ic_rate}}
-			% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-			% 		\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
-			% 	\end{maxi!}
-			% 	where $\rho_k$ is the weight that denotes the priority of transmission $k$.
-			% 	The problem is non-convex and can be solved by the \gls{ao} method detailed below.
-
-			% 	\begin{subsubsection}{Precoder Design}
-			% 		For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution has been proposed in \cite{Negro2010} based on mutual information-\gls{mmse} relationship \cite{Guo2005}.
-			% 		We restate the steps as follows.
-
-			% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
-			% 		\begin{equation}
-			% 			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
-			% 		\end{equation}
-			% 		the corresponding error matrix is
-			% 		\begin{equation}
-			% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
-			% 		\end{equation}
-			% 		the \gls{mse} weight is
-			% 		\begin{equation}
-			% 			\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
-			% 		\end{equation}
-			% 		the Lagrange multiplier is
-			% 		\begin{equation}
-			% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
-			% 		\end{equation}
-			% 		where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.
-			% 		The optimal precoder at transmitter $k$ is given by
-			% 		\begin{equation}
-			% 			\mathbf{W}_k^{(r)} = \Bigl(\sum_j {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)}.
-			% 		\end{equation}
-			% 	\end{subsubsection}
-
-			% 	\begin{subsubsection}{Scattering Matrix Design}
-			% 		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} with respect to \gls{ris} block $g$ is
-			% 		\begin{equation}
-			% 			\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_k \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr).
-			% 			\label{eq:ic_rate_gradient_ris}
-			% 		\end{equation}
-			% 	\end{subsubsection}
-			% 	The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:rcg} where line ?? uses \eqref{eq:ic_rate_gradient_ris} explicitly.
-			% \end{subsection}
-		% \end{subsection}
+		This two-stage solution avoids outer iterations and efficiently handles inner iterations.
+	\end{subsection}
 \end{section}
-
-	% ! shit
-
-% \begin{section}{Power Gain and Achievable Rate Maximization}
-% 	\label{sc:power_rate}
-% 	In this section, we solve channel power gain maximization problem in closed-form and then extend the discussion to achievable rate maximization problem.
-% 	The implication of the former on the latter is investigated.
-
-% 	\begin{subsection}{Channel Power Gain}\label{sc:power}
-% 		The \gls{mimo} channel power gain maximization problem is formulated with respect to the \gls{bd}-\gls{ris} scattering matrix
-% 		\begin{maxi!}
-% 			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power}}{\label{ob:power}}
-% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{\label{cn:power_unitary}}{}
-% 		\end{maxi!}
-% 		which generalizes the problem of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and \gls{mimo} with negligible direct channel and fully-connected \gls{bd}-\gls{ris} ??.
-% 		Solving \eqref{op:power} calls for a balance between the additive direct-indirect combining and the multiplicative backward-forward combining.
-% 		% The key of solving \eqref{op:power} is to balance the additive and multiplicative space alignments.
-
-% 		\begin{remark}
-% 			Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
-% 			\begin{mini!}
-% 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:procrustes_wt}}{}
-% 				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cn:procrustes_wt}}{}
-% 			\end{mini!}
-% 			which relaxes the block-unitary constraint \eqref{cn:power_unitary} to unitary \eqref{cn:procrustes_wt} but still has no trivial solution.
-% 			One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
-% 			\begin{mini!}
-% 				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:procrustes}}{}
-% 				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
-% 			\end{mini!}
-% 			which have global optimal solutions
-% 			\begin{equation}
-% 				\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
-% 				\label{eq:ris_procrustes}
-% 			\end{equation}
-% 			where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right compact singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-% 		\end{remark}
-
-% 		It is worth noting that ??
-and \eqref{eq:ris_procrustes} are valid fully-connected \gls{bd}-\gls{ris} solutions to \eqref{op:power} when the direct channel is negligible and significant, respectively.
-% 		However, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
-% 		Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power} with arbitrary group size.
-% 		The idea is to successively approximate the quadratic objective \eqref{ob:power} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
-
-% 		\begin{proposition}\label{pp:power}
-% 			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
-% 			\begin{equation}
-% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
-% 				\label{eq:ris_power}
-% 			\end{equation}
-% 			converges to a stationary point of \eqref{op:power}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right compact singular matrices of
-% 			\begin{equation}
-% 				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-% 				\label{eq:auxiliary_power}
-% 			\end{equation}
-% 			% \begin{equation}
-% 			% 	% \begin{split}
-% 			% 		\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{1}^{(r+1)},\ldots,\mathbf{\Theta}_{g-1}^{(r+1)},\mathbf{\Theta}_{g}^{(r)},\ldots,\mathbf{\Theta}_{G}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-% 			% 	% \end{split}
-% 			% 	\label{eq:auxiliary_power}
-% 			% \end{equation}
-% 		\end{proposition}
-
-% 		\begin{proof}
-% 			Please refer to Appendix~\ref{ap:power}.
-% 		\end{proof}
-
-% 		We now analyze the computational complexity of solving channel gain maximization problem \eqref{op:power} by Proposition \ref{pp:power}.
-% 		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its compact \gls{svd} requires $\mathcal{O}(L^3)$ operations.
-% 		The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
-% 	\end{subsection}
-
-% 	\begin{subsection}{Achievable Rate Maximization}\label{sc:rate_pc}
-% 		We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
-% 		\begin{maxi!}
-% 			{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
-% 			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
-% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cn:rate_unitary}}
-% 		\end{maxi!}
-% 		where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
-% 		Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
-% 		We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
-
-% 		\begin{subsubsection}{Alternating Optimization}
-% 			This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
-% 			For a given $\mathbf{W}$, the passive beamforming subproblem is
-% 			\begin{maxi!}
-% 				{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_ris}}{\label{ob:rate_ris}}
-% 				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-% 			\end{maxi!}
-% 			where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-% 			Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given in Lemma \ref{lm:rate}.
-% 			\begin{lemma}\label{lm:rate}
-% 				The Euclidean gradient of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
-% 				\begin{equation}
-% 					\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-% 					\label{eq:gradient_eucl_rate}
-% 				\end{equation}
-% 			\end{lemma}
-
-% 			\begin{proof}
-% 				Please refer to Appendix~\ref{ap:rate}.
-% 			\end{proof}
-% 			For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
-% 			\begin{equation}
-% 				\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
-% 				\label{eq:precoder}
-% 			\end{equation}
-% 			where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation obtainable by the iterative method \cite{Clerckx2013}.
-
-% 			The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-% 			Similar to the analysis in Section \ref{sc:pareto}, the computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
-% 			On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
-% 			The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
-% 		\end{subsubsection}
-
-% 		\begin{subsubsection}{Low-Complexity Solution}\label{sc:low_complexity}
-% 			We finally propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
-% 			The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_ris} by channel power gain maximization problem \eqref{op:power}, then proceed to conventional eigenmode transmission \eqref{eq:precoder}.
-% 			Both steps are solved in closed form and the computational complexity is $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr) + N N_\mathrm{T} N_\mathrm{R}\bigr)$.
-% 			While suboptimal, this shaping-inspired solution avoids outer iterations and efficiently handles inner iterations.
-% 		\end{subsubsection}
-% 	\end{subsection}
-% \end{section}
 
@@
 	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
+	We set $\Lambda_0=\qty{-30}{dB}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$, and $\gamma_\mathrm{B}=2$ for reference.
 	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician K-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
- We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
- The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
- Rayleigh fading (i.e., $\kappa = 0$) is assumed for all channels unless otherwise specified.
+	Unless otherwise specified, we assume $\kappa = 0$ (i.e., Rayleigh fading) for all channels and $\eta = \qty{-75}{dB}$ for all receivers.
+	For point-to-point channel, we set $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
+	For interference channel, we assume $K$ transmitters and receivers are independently and uniformly distributed in a disk of radius \qty{20}{m}, and all transmissions are of equal weight $\rho_k=1$, $\forall k$.
 
@@
 		\end{table*}
-	 We first compare in Table \ref{tb:complexity} the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in an $N_\mathrm{T}=N_\mathrm{R}=4$ system with \gls{bd}-\gls{ris} group size $L=4$.
+		Table \ref{tb:complexity} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023b,Li2023c,Zhou2023} on problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
 		The statistics are averaged over \num{100} independent runs.
-	 It is observed that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) computational time than the non-geodesic method.
-	 The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially for large-scale \gls{bd}-\gls{ris} design problems.
- \end{subsection}
-
- \begin{subsection}{Channel Singular Values Redistribution}
-	 \begin{subsubsection}{Pareto Frontier}
+		We observe that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) elapsed time than the non-geodesic method.
+		The results demonstrate the efficiency of the geodesic \gls{rcg} algorithm \ref{ag:rcg} on large-scale \gls{bd}-\gls{ris} design problems.
+	\end{subsection}
+
+	\begin{subsection}{Channel Singular Value Redistribution}
+		\begin{subsubsection}{Achievable Singular Value Region}
 			\begin{figure}[!t]
@@
 			\end{figure}
-		 % Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
-		 Fig. \ref{fg:singular_pareto} shows the Pareto singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ \gls{mimo} reshaped by a \gls{ris}.
+			Fig. \ref{fg:singular_pareto} illustrates the Pareto frontiers of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} aided by \gls{ris}.
 			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
 			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two spaces.
-		 %  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
 			We observe that the smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
-		 When the direct channel is significant, the shape of the singular value region depends heavily on the relative strength of the indirect channels.
-		 In Fig.
-\subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
+			When the direct channel is significant, the shape of the singular value region depends heavily on the relative strength of the indirect channels, which is $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$ in this case.
+			Fig.
+\subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the point of direct channel.
 			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
 			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
-		 It suggests the design flexibility from larger group size allows better alignment of multiple singular vector spaces simultaneously.
+			It suggests the design flexibility from larger group size allows better alignment of multiple modes simultaneously.
 			% not only provides a better trade-off in channel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
@@
 			In particular, Fig.
-\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} thanks to its superior channel shaping capability, but not by a diagonal one.
-		 Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of reconfigurable inter-connections between elements.
+\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable inter-connections between elements.
 		\end{subsubsection}
@@
 			\end{figure}
-		 Fig. \ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rd} and the numerical results obtained by solving problem \eqref{op:pareto}.
-		 Here we consider a rank-$k$ forward channel without loss of generality.
-		 When the \gls{ris} is in the vicinity of the transmitter, Figs.
+			We focus on achieving the analytical bounds in Proposition \ref{pp:rd} since many bounds in Proposition \ref{pp:nd} are provided with closed-form \gls{ris} solutions.
+			For a rank-$k$ forward channel, Fig.
+\ref{fg:singular_bound} compares the individual singular value bounds in Proposition \ref{pp:rd} and the numerical results obtained by solving problem \eqref{op:pareto} with proper weights.
+			When the \gls{ris} is in \gls{los} of the transmitter, Figs.
 \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
-		 It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris} especially for a small $N_\mathrm{S}$.
-		 % Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
+			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris} using a small $N_\mathrm{S}$.
 			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
-		 % The observations align with Proposition \ref{pp:rd} that t
 			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
@@
 			This can be predicted from \eqref{eq:auxiliary_rd} where the singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
-		 The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scales with backward and forward channel ranks.
+			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scales with the rank of backward and forward channels.
 
@@
 			Fig.
-\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
+\ref{fg:power_bond} compares the analytical bound on channel power gain in Corollary \ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
 			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:ris_nd_power_max} or via optimization approach \eqref{eq:ris_power}.
-		 % Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
-		 % We observe that the bound is also tight for fully-connected \gls{bd}-\gls{ris}.
-		 % Increasing the group size of \gls{bd}-\gls{ris} significantly improves the channel power especially for a large \gls{mimo}.
-		 % Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a fully-connected one can achieve the bound.
-		 % The bound here indicates how much power can potentially be extracted from the forward and backward channels.
-		 % We observe that using a larger group size can approach the bound better, and full
-		 % We observe that the bound is tight for fully-connected \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
 			For the \gls{siso} case in Fig.
 \subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-		 It comes purely from branch matching and agrees with the asymptotic power scaling law derived for \gls{siso} in \cite[(30)]{Shen2020a}.
-		 Interestingly, this relative power gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} as shown in Fig.
-\subref*{fg:power_bond_txrx4_nd}, which can also be predicted from the expectation analysis \eqref{eq:power_nd_rayleigh}.
+			It comes purely from branch matching as discussed in Example \ref{eg:siso} and agrees with the asymptotic power scaling law derived in \cite[(30)]{Shen2020a}
+			Interestingly, Fig.
+\subref*{fg:power_bond_txrx4_nd} shows that this gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} and aligns with the expectation analysis \eqref{eq:power_nd_rayleigh}.
 			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
 		\end{subsubsection}
-
-	 % The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
-	 % The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
-	 % The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
-	 % Clearly, a larger group size provides
-	 % and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
-	 % Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
- \end{subsection}
-
- \begin{subsection}{Power Gain and Achievable Rate Maximization}
+	\end{subsection}
+
+	\begin{subsection}{Achievable Rate Maximization}
+		\begin{subsubsection}{MIMO Point-to-Point Channel}
 			\begin{figure}[!t]
@@
 					Average maximum channel power gain versus \gls{ris} configuration.
-			 `OP-left' and `OP-right' refer to the suboptimal solutions to problem \eqref{op:power} by lossy transformation \eqref{op:procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
+					`Explicit' refers to the optimal solution \eqref{eq:ris_nd_power_max} when the direct channel is negligible.
+					`OP-left' and `OP-right' refer to the suboptimal solutions, when the direct channel is significant, by lossy transformation \eqref{op:procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
 				}
@@
 
-	 We first focus on channel power gain maximization problem \eqref{op:power}.
-	 Fig. \ref{fg:power_sx} shows the maximum channel power under different \gls{ris} configurations.
+			We first focus on the channel power gain problem \eqref{op:power}.
+			Fig. \ref{fg:power_sx} shows the maximum channel power gain under different \gls{ris} configurations.
 			An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is even larger when the direct channel is significant.
-	 For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power gain as a 256-element \gls{d}-\gls{ris} in Fig.
-\subref*{fg:power_sx_txrx16}, but not in Fig.
-\subref*{fg:power_sx_txrx16_nd}.
-	 % This again credits to the superior space alignment capability of \gls{bd}-\gls{ris}.
-	 This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the mode alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
+			As shown in Figs.
+\subref*{fg:power_sx_txrx16_nd} and \subref*{fg:power_sx_txrx16}, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power gain as a 256-element \gls{d}-\gls{ris} when the direct channel is significant, but less so when it is negligible.
+			This is because the mode alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced when the modes of direct channel is taken into account.
 			We also notice that the suboptimal solutions \eqref{eq:ris_procrustes} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
@@
 					Average achievable rate versus \gls{mimo} and \gls{ris} configurations.
-			 The noise power is $\eta = \qty{-75}{dB}$, corresponding to a direct \gls{snr} of \num{-10} to \qty{30}{dB}.
+					The transmit power corresponds to a direct \gls{snr} of \num{-10} to \qty{30}{dB}.
 					`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
@@
 			A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-	 An interesting observation is that the rate gap between the optimal \gls{ao} approach \eqref{op:rate_ris}--\eqref{eq:precoder} and the shaping-inspired solution \eqref{eq:ris_power}, \eqref{eq:precoder} narrows at larger group size and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
-	 This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the active beamformer, which significantly simplifies the process at marginal performance cost.
-	 Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} versus \gls{d}-\gls{ris}
+			An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section \ref{sc:rate_ao} and the shaping-inspired low-complexity solution in Section \ref{sc:rate_lc} narrows as $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+			This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the active beamformer, which simplifies the design substantially.
+			Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}
 			increases with the number of transmit and receive antennas and scattering elements, especially at high \gls{snr}.
-	 % Being consistent with the power gain results in Fig. \ref{fg:power_sx}, this phenomenon is more pronounced at a high \gls{snr}.
 			For $N_\mathrm{S}=128$ and $P = \qty{20}{dB}$,
 			the achievable rate ratio of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is \num{1.04}, \num{1.11}, and \num{1.13} for $N_\mathrm{T}=N_\mathrm{R}=1$, \num{4}, and \num{16}, respectively.
-	 % increases from \num{1.04} in \gls{siso} to \num{1.11} for $N_\mathrm{T}=N_\mathrm{R}=4$ and \num{1.13} for $N_\mathrm{T}=N_\mathrm{R}=16$.
 			For $N_\mathrm{T}=N_\mathrm{R}=4$ and $P = \qty{20}{dB}$, this ratio amounts to \num{1.03}, \num{1.08}, and \num{1.13} for $N_\mathrm{S}=16$, \num{64}, and \num{256}, respectively.
@@
 			This is particularly visible in Fig. \subref*{fg:rate_sx} where the topmost curve is almost a linear function of the transmit power.
-	 % It is interesting to see that the topmost curve of Fig.
-\subref*{fg:rate_sx} is almost a linear function of the transmit power, suggesting that \gls{bd}-\gls{ris} can help to activate multiple streams and achieve full \gls{dof} at low transmit \gls{snr}.
-	 It is expected from the shaping results in Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
+			It is also expected from the shaping results in Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
 			Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician K-factor increases and becomes indistinguishable in \gls{los} environment.
 			The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
+		\end{subsubsection}
+
+		\begin{subsubsection}{MIMO Interference Channel}
+			\begin{figure}[!t]
+				\centering
+				\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
+					\label{fg:ic_interference_sx}
+					\resizebox{!}{3.0625cm}{
+						\input{../assets/simulation/ic_interference_sx.tex}
+					}
+				}
+				\subfloat[WSR: $(4 \times 64 \times 4)^5$]{
+					\label{fg:ic_wsr_beamforming}
+					\resizebox{!}{3.0625cm}{
+						\input{../assets/simulation/ic_wsr_beamforming.tex}
+					}
+				}
+				\\
+				\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5$]{
+					\label{fg:ic_wsr_sx}
+					\resizebox{!}{3.0625cm}{
+						\input{../assets/simulation/ic_wsr_sx.tex}
+					}
+				}
+				\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^5$]{
+					\label{fg:ic_wsr_txrx}
+					\resizebox{!}{3.0625cm}{
+						\input{../assets/simulation/ic_wsr_txrx.tex}
+					}
+				}
+				\caption{
+					Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
+					`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
+					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
+				}
+			\end{figure}
+
+			Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference by solving problem \eqref{op:interference}.
+			In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
+			The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.
+
+			Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section \ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
+			Unlike the point-to-point case, the latter is not as effective as the former.
+			The reason is that, for $K$ transmissions of different path loss, interference alignment using a shared passive beamformer alone is challenging especially when the direct channels are significant.
+			On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
+			We expect a narrower performance gap in between when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.
+
+			Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
+			Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
+			The reasons discussed in the point-to-point case also apply here.
+		\end{subsubsection}
+	\end{subsection}
+
+	\begin{subsection}{Practical Constraints}
+		\begin{subsubsection}{RIS Symmetry}
+			\begin{figure}[!t]
+				\centering
+				\subfloat[Power: $2 \times N_\mathrm{S} \times 2$]{
+					\label{fg:pc_power_symmetry}
+					\resizebox{!}{3.0625cm}{
+						\input{../assets/simulation/pc_power_symmetry.tex}
+					}
+				}
+				\subfloat[Rate: $4 \times N_\mathrm{S} \times 4$]{
+					\label{fg:pc_rate_symmetry}
+					\resizebox{!}{3.0625cm}{
+						\input{../assets/simulation/pc_rate_symmetry.tex}
+					}
+				}
+				\caption{
+					Impact of \gls{ris} symmetry on the power gain and achievable rate of \gls{mimo} point-to-point channel.
+				}
+			\end{figure}
+			Symmetric \gls{ris} satisfying $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$ are often considered in the literature due to hardware constraints.
+			This study aim to investigate the impact of \gls{ris} symmetry on the system performance.
+			\begin{remark}
+				All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry. In particular,
+				\begin{enumerate}[label=(\roman*)]
+					\item \emph{\gls{svd}-based (e.g., \eqref{eq:ris_nd_sv_indl}, \eqref{eq:ris_nd_power}, \eqref{eq:ris_nd_rate_max}, \eqref{eq:ris_power}, \eqref{eq:ris_procrustes}):} Those closed-form asymmetric solutions are constructed from the product of singular matrices.
+If symmetry is required, one can replace the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} and use unitary factor $\mathbf{Q}$ to construct the corresponding $\mathbf{\Theta}$.
+\label{it:takagi}
+					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}, \eqref{eq:gradient_eucl_wsr}):} The symmetry constraint is added to the corresponding optimization problems, and one simple strategy is to project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
+\label{it:projection}
+				\end{enumerate}
+
+				Figs.
+\ref{fg:pc_power_symmetry} and \ref{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
+				Here, `Asymmetric' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, `Enforced' refers to enforcing symmetry on `Asymmetric', `Legacy' refers to a straightforward extension of the \gls{siso} \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, `Takagi' refers to the modification \ref{it:takagi}, and `Projection' refers to the modification \ref{it:projection}.
+				We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and scale with the number of scattering elements.
+				The two proposed modifications also outperform other candidates in both problems.
+			\end{remark}
+		\end{subsubsection}
+
+		\begin{subsubsection}{Channel Estimation Error}
+			\begin{figure}[!t]
+				\centering
+				\resizebox{!}{3.0625cm}{
+					\input{../assets/simulation/ic_wsr_pair.tex}
+				}
+				\caption{
+					Impact of backward/forward channel estimation error and transceiver pairs on the weighted sum-rate of $(4 \times 64 \times 4)^K$ \gls{mimo} interference channel.
+				}
+				\label{fg:ic_wsr_pair}
+			\end{figure}
+
+			Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
+			Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
+			\begin{equation*}
+				\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
+			\end{equation*}
+			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
+			The \gls{wsr} is evaluated using the true channels.
+			We observe that the proposed joint beamforming design is robust to channel estimation error and thus suitable for practical implementations.
+			On the other hand, introducing a \gls{ris} to \gls{ic} systems is helpful to mitigate the rate saturation effect as the number of users increases.
+			In the overloaded regime ($K \ge 8$), \gls{bd}-\gls{ris} provides a larger \gls{wsr} slope than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
+			These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
+		\end{subsubsection}
 	\end{subsection}
@@
 \begin{section}{Conclusion}
- This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
+	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular value redistribution.
 	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than \gls{d}-\gls{ris}.

### 2024-12-30 src/ic_interference_sx.m

@@ -1,7 +1,7 @@
 clc; clear; close; setup;
 
 [transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 2 .^ (2 : 2 : 8), 4);
-[network.coverage, network.pair] = deal(50, 5);
+[network.coverage, network.pair] = deal(20, 5);
 [channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(db2pow(-30), 3, 2.4, 2.4);
 [number.bond, number.antenna, number.realization, flag.direct] = deal(log2(reflect.antenna) + 1, length(reflect.antenna), 1e2, true);
 

### 2024-12-30 src/ic_wsr_beamforming.m

@@ -62,7 +62,7 @@ hold off; grid on; ylim tight; box on; legend('Location', 'nw');
 xlabel('Transmit Power [dB]');
 ylabel('Weighted Sum-Rate [bit/s/Hz]');
 savefig('plots/ic_wsr_beamforming.fig');
-% matlab2tikz('../assets/simulation/ic_wsr_beamforming.tex', 'width', '10cm', 'height', '7.5cm');
+matlab2tikz('../assets/simulation/ic_wsr_beamforming.tex', 'width', '10cm', 'height', '7.5cm');
 
 
 function [C] = distribution_disk(r, K)

### 2024-12-30 src/ic_wsr_txrx.m

@@ -1,7 +1,7 @@
 clc; clear; close; setup;
 
 [transmit.antenna, reflect.antenna, receive.antenna, transmit.stream] = deal(2 .^ (2 : 2 : 4), 128, 2 .^ (2 : 2 : 4), 2);
-[network.coverage, network.pair] = deal(50, 10);
+[network.coverage, network.pair] = deal(20, 10);
 [transmit.power, receive.noise, network.weight] = deal(db2pow(-20 : 5 : 20), db2pow(-75), ones(1, 1, network.pair));
 [network.coordinate.transmit, network.coordinate.reflect, network.coordinate.receive] = deal(distribution_disk(network.coverage, network.pair), [0; 0], distribution_disk(network.coverage, network.pair));
 [channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(db2pow(-30), 3, 2.4, 2.4);

### 2024-12-30 src/pc_power_sx.m

@@ -38,7 +38,7 @@ if flag.direct
 else
 	channel.power.aggregate.explicit = mean(channel.power.aggregate.explicit, ndims(channel.power.aggregate.explicit));
 end
-save('data/pc_power_sx.mat');
+% save('data/pc_power_sx.mat');
 
 figure('Name', 'Channel Power vs RIS Configuration', 'Position', [0, 0, 500, 400]);
 if flag.direct
@@ -80,8 +80,8 @@ hold off; grid on; box on;
 set(gca, 'XLim', [1, max(number.bond)], 'XTick', 1 : max(number.bond), 'XTickLabel', '$2^' + string(vec(0 : max(number.bond) - 1)) + '$', 'YLim', [channel.power.direct * 0.95, max(vec(channel.power.aggregate.iterative)) * 1.05]);
 xlabel('RIS Group Size');
 ylabel('Channel Power [W]');
-savefig('plots/pc_power_sx.fig');
-matlab2tikz('../assets/simulation/pc_power_sx.tex', 'width', '8cm', 'height', '6cm');
+% savefig('plots/pc_power_sx.fig');
+% matlab2tikz('../assets/simulation/pc_power_sx.tex', 'width', '8cm', 'height', '6cm');
 
 
 function [Theta, H] = scatter_power_max_explicit(H_f, H_b)

### 2024-12-30 src/pc_power_symmetry.m

@@ -55,7 +55,7 @@ set(gca, 'XLim', [1, max(number.bond)], 'XTick', 1 : max(number.bond), 'XTickLab
 xlabel('RIS Group Size');
 ylabel('Channel Power [W]');
 savefig('plots/pc_power_symmetry.fig');
-matlab2tikz('../assets/simulation/pc_power_symmetry.tex', 'width', '8cm', 'height', '6cm');
+matlab2tikz('../assets/simulation/pc_power_symmetry.tex', 'width', '12cm', 'height', '9cm');
 
 
 function [Theta, H] = scatter_power_max_symmetric_legacy(H_f, H_b, L)

### 2025-01-01 review/response_241203.tex
:construction: Updating structure
:construction: Updating results

@@
 
+	\reply{
+		We appreciate the reviewer's insightful comments.
+We have revised the manuscript to clarify the contributions of Sec.
+\ref{sc:framework} and the novelty of the proposed optimization framework.
+Specifically, we have added a discussion on the limitations of the proposed framework in \eqref{op:general} and the novelty of the proposed geodesic \gls{rcg} method.
+We have also added a comparison with the existing literature to highlight the novelty of the proposed framework.
+We believe that the revised manuscript now clearly articulates the contributions of Sec.
+\ref{sc:framework} and the novelty of the proposed optimization framework.
+	}
+
 	\comment{
@@
 		In Sec.
-\ref{sc:bounds}, the manuscript provides a number of bounds on singular values of the effective channel $\mathbf{H}$.
+\ref{sc:shaping_analytical}, the manuscript provides a number of bounds on singular values of the effective channel $\mathbf{H}$.
 However, the usefulness of these bounds is unclear.

### 2025-01-01 src/ic_wsr_beamforming.m

@@ -1,7 +1,7 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream] = deal(4, 64, 4, 2);
-[network.coverage, network.pair] = deal(20, 5);
+[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream] = deal(4, 128, 4, 2);
+[network.coverage, network.pair] = deal(20, 2);
 [transmit.power, receive.noise, network.weight] = deal(db2pow(-20 : 5 : 20), db2pow(-75), ones(1, 1, network.pair));
 [channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(db2pow(-30), 3, 2.4, 2.4);
 reflect.bond = [1, reflect.antenna];
@@ -22,14 +22,15 @@ for r = 1 : number.realization
 		network.wsr.direct(p, r) = sum(network.weight .* rate_mimo(channel.direct, transmit.beamformer.direct, receive.noise), 3);
 	end
 	% * Have RIS
+    clear scatter_interference;
 	for b = 1 : number.bond
 		[reflect.beamformer.decouple, channel.aggregate.decouple] = scatter_interference(channel.direct, channel.forward, channel.backward, reflect.bond(b));
 		clear scatter_wsr;
 		for p = 1 : number.power
 			% * alternating optimization
 			transmit.beamformer.alternate = precoder_initialize(channel.direct, transmit.stream, transmit.power(p));
-			[iter.converge, iter.tolerance, iter.counter, iter.wsr] = deal(false, 1e-4, 0, sum(network.weight .* rate_mimo(channel.direct, transmit.beamformer.alternate, receive.noise), 3));
-			while ~iter.converge
+			[iter.converge, iter.tolerance, iter.counter, iter.wsr] = deal(false, 1e-3, 0, sum(network.weight .* rate_mimo(channel.direct, transmit.beamformer.alternate, receive.noise), 3));
+			while ~iter.converge && iter.counter <= 1e2
 				[reflect.beamformer.alternate, channel.aggregate.alternate] = scatter_wsr(channel.direct, channel.forward, channel.backward, transmit.beamformer.alternate, reflect.bond(b), receive.noise, network.weight);
[…]

### 2025-01-01 src/ic_wsr_sx.m

@@ -27,8 +27,8 @@ for r = 1 : number.realization
 			clear scatter_wsr;
 			for p = 1 : number.power
 				transmit.beamformer = precoder_initialize(channel.direct, transmit.stream, transmit.power(p));
-				[iter.converge, iter.tolerance, iter.counter, iter.wsr] = deal(false, 1e-4, 0, sum(network.weight .* rate_mimo(channel.direct, transmit.beamformer, receive.noise), 3));
-				while ~iter.converge
+				[iter.converge, iter.tolerance, iter.counter, iter.wsr] = deal(false, 1e-3, 0, sum(network.weight .* rate_mimo(channel.direct, transmit.beamformer, receive.noise), 3));
+				while ~iter.converge && iter.counter <= 1e2
 					[reflect.beamformer, channel.aggregate] = scatter_wsr(channel.direct, channel.forward, channel.backward, transmit.beamformer, reflect.bond(b), receive.noise, network.weight);
 					transmit.beamformer = precoder_wsr(channel.aggregate, transmit.beamformer, transmit.power(p), receive.noise, network.weight);
 					network.wsr.aggregate(p, b, a, r) = sum(network.weight .* rate_mimo(channel.aggregate, transmit.beamformer, receive.noise), 3);
@@ -56,7 +56,7 @@ hold off; grid on; ylim tight; box on; legend('Location', 'nw');
 xlabel('Transmit Power [dB]');
 ylabel('Weighted Sum-Rate [bit/s/Hz]');
 savefig('plots/ic_wsr_sx.fig');
-% matlab2tikz('../assets/simulation/ic_wsr_sx.tex', 'width', '10cm', 'height', '7.5cm');
+matlab2tikz('../assets/simulation/ic_wsr_sx.tex', 'width', '10cm', 'height', '7.5cm');
 
 
 function [C] = distribution_disk(r, K)

### 2025-01-01 src/lib/scatter_wsr.m

@@ -9,8 +9,8 @@ function [Theta, H] = scatter_wsr(H_d, H_f, H_b, W, L, P_n, rho)
 	G = length(Theta) / L;
 	H = channel_aggregate(H_d, H_f, H_b, Theta);
 	[G_e, G_r, D] = deal(zeros(size(Theta)));
-	[iter.converge, iter.tolerance, iter.counter, iter.J] = deal(false, 1e-4, 0, sum(rho .* rate_mimo(H, W, P_n), 3));
-	while ~iter.converge
+	[iter.converge, iter.tolerance, iter.counter, iter.J] = deal(false, 1e-3, 0, sum(rho .* rate_mimo(H, W, P_n), 3));
+	while ~iter.converge && iter.counter <= 1e2
 		[iter.G_r, iter.D] = deal(G_r, D);
 		for g = 1 : G
 			S = (g - 1) * L + 1 : g * L;

### 2025-01-03 review/response_241203.tex
:pencil: Update manuscript and add response

--- 2024-12-13 review/response_241203.tex
@@
 	Your comments and suggestions have been invaluable in helping us improve the quality of the manuscript.
-	Below we prepare a point-to-point response and highlight the corresponding in-text changes, where labels have been matched to the latest manuscript for your convenience.
+	Below we prepare a point-to-point response and highlight the corresponding in-text changes, where labels have been matched to the latest version for your convenience.
+	The title has been changed to \emph{MIMO Channel Shaping and Rate Maximization Using Beyond Diagonal RIS} to better reflect the content of the manuscript.
 	We hope that the revisions and clarifications make the manuscript meet the standards of TSP publications.
@@
 			\item The contribution of the paper is unclear.
-Specifically, the proposed framework in \eqref{op:general} is not sufficiently general as it does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality).
+Specifically, the proposed framework in \eqref{op:shaping} is not sufficiently general as it does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality).
 A more general case has already been investigated and solved in the authors' previous work \cite{Zhou2023}.
-Some content in Section \ref{sc:framework} are well established methods in the literature \cite{Abrudan2008}.
+Some content in Section \ref{sc:shaping_numerical} are well established methods in the literature \cite{Abrudan2008}.
 			\item The optimization problems \eqref{op:power} and \eqref{op:rate_ris} lacks of novelty.
@@
 			\item The correctness and usefulness of the mathematical derivations.
-For example, the derivation in the proof of Appendix \ref{ap:pareto} is incorrect.
+For example, the derivation in the proof of Appendix \ref{ap:shaping} is incorrect.
 Convergence proof in Appendix \ref{ap:power} is questionable.
@@
 	\reply{
-		Good. \cite{Fotock2023}
+		We appreciate the editor's summary of the comments.
+We have carefully considered each point raised and have made significant revisions to address these concerns.
+Please refer to the following responses for a detailed explanation of the changes made in the revised manuscript.
 	}
@@
 	\comment{
-		The contribution of Sec. \ref{sc:framework} is unclear for the following two reasons.
+		The contribution of Sec. \ref{sc:shaping_numerical} is unclear for the following two reasons.
 		\begin{enumerate}
-			\item The manuscript claims to propose a universal optimization framework for \gls{bd}-\gls{ris} as in \eqref{op:general}.
-However, the framework in \eqref{op:general} is indeed not sufficiently general.
-It does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality) besides the orthogonal conditions \eqref{cn:general_unitary}.
-The reviewer notice that a more general framework, which considers \gls{bd}-\gls{ris} constraints in addition to \eqref{cn:general_unitary}, has already been investigated and solved in the authors' previous work \cite{Zhou2023}.
-			\item Besides, both the non-geodesic \gls{rcg} (Sec.
-\ref{sc:rcg_general}) and geodesic \gls{rcg} (Sec.
-\ref{sc:rcg_geodesic}) algorithms, e.g., \eqref{eq:geodesic_iden}--\eqref{eq:iterate_mul}, are well established methods in the literature, e.g., \cite{Abrudan2008}.
+			\item The manuscript claims to propose a universal optimization framework for \gls{bd}-\gls{ris} as in \eqref{op:shaping}.
+However, the framework in \eqref{op:shaping} is indeed not sufficiently general.
+It does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality) besides the orthogonal conditions \eqref{cn:shaping_unitary}.
+The reviewer notice that a more general framework, which considers \gls{bd}-\gls{ris} constraints in addition to \eqref{cn:shaping_unitary}, has already been investigated and solved in the authors' previous work \cite{Zhou2023}.
+			\item Besides, both the non-geodesic \gls{rcg} and geodesic \gls{rcg} algorithms, e.g., \eqref{eq:gradient_eucl} -- \eqref{eq:geodesic_tran}, are well established methods in the literature, e.g., \cite{Abrudan2008}.
 Therefore, the novelty of Sec.
-\ref{sc:framework} unclear.
+\ref{sc:shaping_numerical} unclear.
 		\end{enumerate}
+	}
+
+	\reply{
+		We appreciate the reviewer's insightful comments.
+		The claim of ``universal optimization framework'' and the non-geodesic \gls{rcg} method have been removed from the revised manuscript, and we have carefully rephrased Sections \ref{sc:contributions} and \ref{sc:shaping_numerical} to reflect the specific contributions of our work.
+		Indeed, the geodesic \gls{rcg} algorithm is well studied in the literature and our intention was to extend it to block-unitary cases with parallel or unified updates, which is particularly suitable for the design of group-connected \gls{bd}-\gls{ris}.
 	}
@@
 		In Sec.
-\ref{sc:pareto}, the manuscript proposes to maximize weighted sum of singular values of the effective channel $\mathbf{H}$.
+\ref{sc:shaping_numerical}, the manuscript proposes to maximize weighted sum of singular values of the effective channel $\mathbf{H}$.
 The optimization objective is rather vague.
@@
 
+	\reply{
+		We agree with the reviewer that the optimization objective of weighted sum of singular values is not directly related to a specific performance metric.
+		However, it helps to reveal the achievable region of channel singular values (which covers all related metrics) and we believe itself could serve as a metric for measuring the \gls{mimo} channel shaping capability of different \gls{ris}.
+		In the revised manuscript, we also generalize the objective to symmetric gauge functions to further address this concern.
+
+		\change{
+			Consider a special class of channel shaping problem
+			\begin{maxi*}
+				{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{}{}
+				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{}
+			\end{maxi*}
+			where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
+			Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
+		}
+	}
+
 	\comment{
-		Derivation in the proof of Lemma \ref{lm:pareto} (Appendix \ref{ap:pareto}) is incorrect.
+		Derivation in the proof of Appendix \ref{ap:shaping} is incorrect.
 Specifically, $(\partial \mathbf{u}^\mathsf{T}) \cdot \mathbf{u}$ is not equal to $\partial (\mathbf{u}^T \mathbf{u})$.
@@
 In fact, sub-differential should be used instead, e.g., \cite{Cai2010}.
+	}
+
+	\reply{
+		We appreciate the reviewer's careful reading of the manuscript.
+		We have corrected the derivation in the proof of Appendix \ref{ap:shaping} and have used the sub-differential to handle the non-differentiability of the singular value function.
+		\change{
+			\setcounter{proposition}{3}
+			\begin{proposition}
+				The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
+				\begin{equation*}
+					\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
+				\end{equation*}
+				where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
+			\end{proposition}
+		}
 	}
@@
 
+	\reply{
+		Using the rank equation pointed out by the reviewer, we realized that the achievability proof in the previous version was incorrect. In fact, the proposition was incorrect.
+		A new proof in Appendix \ref{ap:dof} shows that \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
+		We apologize for the confusion and appreciate the reviewer for pointing out this mistake.
+		\change{
+			\setcounter{proposition}{0}
+			\begin{proposition}[Degrees of freedom]
+				\gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
+			\end{proposition}
+		}
+	}
+
 	\comment{
 		In Sec.
-\ref{sc:bounds}, the manuscript provides a number of bounds on singular values of the effective channel $\mathbf{H}$.
+\ref{sc:shaping_analytical}, the manuscript provides a number of bounds on singular values of the effective channel $\mathbf{H}$.
 However, the usefulness of these bounds is unclear.
 What can these bounds be used for?
-Note the results Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are quite standard results from matrix textbook.
+Note the results in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are quite standard results from matrix textbook.
 The (upper) bound in Corollary \ref{co:nd_power}, which is achieved by aligning its left and right singular-value vectors to that of the forward and backward channels, respectively, is reminiscent of the results in seminal papers on relay beamforming design, e.g., \cite{Rong2009,Rong2009a}.
+	}
+
+	\reply{
+		The aim of Proposition \ref{pp:nd} is to transform the channel shaping limit question into a well-studied linear algebra question, such that Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} (previously 3.1 -- 3.4) follows from standard results.
+		In the revised manuscript, we have also added
+		\begin{itemize}
+			\item Upper and lower bounds on individual singular value in Corollary \ref{co:nd_sv_indl};
+			\item Lower bound on channel power gain in Corollary \ref{co:nd_power};
+			\item Upper bound on channel capacity at general and extreme \gls{snr} in Corollaries \ref{co:nd_capacity_snr_general} and \ref{co:nd_capacity_snr_extreme};
+		\end{itemize}
+		and derived the corresponding \gls{ris} scattering matrices in closed form.
+		We also notice that the bounds on the $n$-th singular value can be used, for example, to simplify the precoder design in \gls{mimo} systems with limited number $n$ of RF chains.
+		The comparison to relay beamforming design is insightful and we have added footnote \ref{fn:power_nd_max} to highlight the connection.
+		\change{
+			\setcounter{proposition}{3}
+			\setcounter{corollary}{2}
+			\begin{corollary}[Individual singular value]
+				If the direct channel is negligible,
+				then the $n$-th channel singular value can be manipulated up to
+				\begin{equation*}
+					\max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
+				\end{equation*}
+				where $(i, j) \in [N_\mathrm{S}]^2$.
+				The upper and lower bounds are attained respectively at
+				\begin{align*}
+					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \\
+					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H},
+				\end{align*}
+				where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices\footnotetext{%
+					We highlight the non-uniqueness of $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$.
+When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace.
+Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.} of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+				and $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary permutation matrices of dimension $N_\mathrm{S}$ satisfying:
+				\begin{itemize}
+					\item The $(i, j)$-th entry is $1$, where
+					\begin{align*}
+						(i, j) &=
+						\begin{cases}
+							\underset{\mathclap{i+j=n+1}}{\arg\min} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}), & \text{for } \mathbf{P}, \\
+							\underset{\mathclap{i+j=n+N_\mathrm{S}}}{\arg\max} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}), & \text{for } \mathbf{Q}.
+						\end{cases}
+					\end{align*}
+					and ties may be broken arbitrarily;
+					\item After deleting the $i$-th row and $j$-th column, the resulting submatrix $\mathbf{Y}$ is arbitrary permutation matrix of dimension $N_\mathrm{S}-1$ satisfying
+					\begin{alignat*}{2}
+						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \ \ \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})            &  & \text{ for } \mathbf{P}, \\
+						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \ \ \max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) &  & \text{ for } \mathbf{Q},
+					\end{alignat*}
+					where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with both $i$-th row and $j$-th column deleted, respectively.
+				\end{itemize}
+			\end{corollary}
+		}
+
+		\change{
+			\begin{corollary}[Channel power gain]
+				If the direct channel is negligible, then the channel power gain is bounded from above (resp.
+below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp.
+oppositely), that is,\footnotetext{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
+This is a looser version of \eqref{iq:power_nd} and cannot take equalities unless the extreme singular values are of multiplicity $N$.}
+				\begin{equation*}
+					\sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
+				\end{equation*}
+				whose upper\footnotetext{The upper bound \eqref{eq:ris_nd_power_max} is reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.} and lower bounds are attained respectively at
+				\begin{align*}
+					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H},             \\
+					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H},
+				\end{align*}
+				where $\mathbf{J}$ is the exchange (a.k.a. backward identity) matrix of dimension $N_\mathrm{S}$.
+			\end{corollary}
+		}
+
+		\change{
+			\begin{corollary}[Channel capacity at general \gls{snr}]
+				If the direct channel is negligible, then the \gls{bd}-\gls{ris} aided \gls{mimo} channel capacity is
+				\begin{equation*}
+					C^\textnormal{MIMO-ND} = \sum_{n=1}^N \log \left(1 + \frac{s_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}{\eta}\right),
+				\end{equation*}
+				where $\eta$ is the average noise power, $s_n = \mu - \frac{\eta}{\sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}$ is the power allocated to the $n$-th mode obtainable by the water-filling algorithm \cite{Clerckx2013}.
+				The capacity-achieving \gls{bd}-\gls{ris} scattering matrix is
+				\begin{equation*}
+					\mathbf{\Theta}_\textnormal{R-max}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
+				\end{equation*}
+			\end{corollary}
+		}
+
+		\change{
+			\begin{corollary}[Channel capacity at extreme \gls{snr}]
+				If the direct channel is negligible, then the channel capacity when the \gls{snr} $\rho$ is very low and high are approximately bounded from above by
+				\begin{align*}
+					C_{\rho_\downarrow} & \lessapprox \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}),                                            \\
+					C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}).
+				\end{align*}
+			\end{corollary}
+		}
 	}
@@
 In fact, they can still be solved by the methods proposed in existing literature, e.g., \cite{Santamaria2023,Li2023b} through appropriate adjustment.
+	}
+
+	\reply{
+		We agree with the reviewer that problem \eqref{op:rate_ris} may be solved by the method proposed in \cite{Li2023b} with appropriate adjustment.
+		However, extending the single mode alignment in \cite{Santamaria2023} to solve problem \eqref{op:power} is far from optimal as shown in Fig. \ref{fg:pc_power_symmetry} (labelled as ``Legacy'').
+		We have added footnote \ref{fn:power_gain} to clarify the novelty of our approach.
+		\change{
+				The channel power gain maximization problem is formulated as\footnotetext{%
+				Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
+Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
+			}
+		}
+
+		\change{
+			\begin{figure}[H]
+				\centering
+				\resizebox{!}{6cm}{
+					\input{../assets/simulation/pc_power_symmetry.tex}
+				}
+				\caption*{
+					Fig. Impact of \gls{ris} symmetry on the power gain of $2 \times N_\mathrm{S} \times 2$ \gls{mimo} point-to-point channel.
+				}
+			\end{figure}
+		}
 	}
@@
 Please refer to \cite{Pang2017}.
+	}
+
+	\reply{
+		We sincerely appreciate the reviewer for pointing out the issue.
+		Indeed, the sequence of iterates may oscillate and the convergence proof in the previous version was incorrect.
+		We have revised the wording in Proposition \ref{pp:power} and clarified the condition when a stationary point can be reached.
+		The proof in Appendix \ref{ap:power} has been updated accordingly.
+		\setcounter{proposition}{4}
+		\change{
+			\begin{proposition}
+				Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence\footnotetext{However, \eqref{eq:ris_power} might not converge to a single solution point when $\mathbf{M}_g$ is rank-deficient due to the non-uniqueness of the orthonormal bases of kernels.}
+				\begin{equation*}
+					\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+				\end{equation*}
+				monotonically increases the objective function \eqref{ob:power},
+				where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of\footnotetext{We notice that $\mathbf{\Theta}_g$ coincides with the orthogonal projection of $\mathbf{M}_g$ onto the Stiefel manifold $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g$.} % \cite{Manton2002}
+				\begin{equation*}
+					\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
+				\end{equation*}
+				Besides, when \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
+			\end{proposition}
+		}
+
+		\change{
+			\begin{remark}
+				The sequence \eqref{eq:auxiliary_power} is constructed iteratively from its orthogonal projection.
+				Although a formal proof remains elusive, empirical evidence from simulation indicates that \eqref{eq:auxiliary_power} converge for vastly tested scenarios.
+				% We thus conjecture that the sequence \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
+			\end{remark}
+		}
 	}
@@
 
+	\reply{
+		Asymmetric \gls{ris} may be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids).
+		A 4-port ring hybrid is illustrated in the figure below \cite{Ahn2006}.
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=0.5\textwidth]{../assets/review/ring_hybrid.pdf}
+			\caption*{
+				Fig.
+A 4-port asymmetric ring hybrid.
+Here the arc length between ports are $\Theta_1 = \Theta_2 = \Theta_3 = \lambda / 4$ and $\Theta_4 = 3 \lambda / 4$ where $\lambda$ is the wavelength.
+The termination admittances $Y_a$ to $Y_d$ are arbitrary and the characteristic admittances of transmission-line sections are not necessarily the same, such that the scattering parameters can be asymmetric.
+Source: modified from \cite{Ahn2006}.
+			}
+		\end{figure}
+
+		On the other hand, symmetric \gls{ris} satisfying $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$ are often considered in the literature as they can be implemented with simpler circuit components (e.g., capacitors and inductors).
+		We have added Section \ref{sc:ris_symmetry} to investigate the impact of \gls{ris} symmetry on the system performance.
+
+		\change{
+			Symmetric \gls{ris} satisfying $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$ are often considered in the literature due to hardware constraints.
+			This study aim to investigate the impact of \gls{ris} symmetry on the system performance.
+			\begin{remark}
+				All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry. In particular,
+				\begin{enumerate}[label=(\roman*)]
+					\item \emph{\gls{svd}-based (e.g., \eqref{eq:ris_nd_sv_indl}, \eqref{eq:ris_nd_power}, \eqref{eq:ris_nd_rate_max}, \eqref{eq:ris_power}, \eqref{eq:ris_procrustes}):} Those closed-form asymmetric solutions are constructed from the product of singular matrices.
+If symmetry is required, one can replace the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} and use unitary factor $\mathbf{Q}$ to construct the corresponding $\mathbf{\Theta}$.
+					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}, \eqref{eq:gradient_eucl_wsr}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
+				\end{enumerate}
+			\end{remark}
+
+			\begin{figure}[H]
+				\centering
+				\subfloat[Power: $2 \times N_\mathrm{S} \times 2$]{
+					\resizebox{!}{5cm}{
+						\input{../assets/simulation/pc_power_symmetry.tex}
+					}
+				}
+				\subfloat[Rate: $4 \times N_\mathrm{S} \times 4$]{
+					\resizebox{!}{5cm}{
+						\input{../assets/simulation/pc_rate_symmetry.tex}
+					}
+				}
+				\caption*{
+					Fig. Impact of \gls{ris} symmetry on the power gain and achievable rate of \gls{mimo} point-to-point channel.
+				}
+			\end{figure}
+
+			Figs.
+\ref{fg:pc_power_symmetry} and \ref{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
+			Here, `Asymmetric' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, `Enforced' refers to enforcing symmetry on `Asymmetric', `Legacy' refers to a straightforward extension of the \gls{siso} \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, `Takagi' refers to the modification \ref{it:takagi}, and `Projection' refers to the modification \ref{it:projection}.
+			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and scale with the number of scattering elements.
+			The two proposed modifications also outperform other candidates in both problems.
+		}
+	}
+
 	\comment{
@@
 
+	\reply{
+		Unfortunately, the geodesic \gls{rcg} method relies on the block unitary property of the \gls{bd}-\gls{ris} scattering matrix and is not directly applicable to multi-sector mode \gls{bd}-\gls{ris} where the constraint is relaxed to $\sum_{s=1}^S \mathbf{\Theta}_{g,s}^\mathsf{H} \mathbf{\Theta}_{g,s} = \mathbf{I}, \ \forall g \in [G]$ with $S > 1$ sectors.
+	}
+
 	\comment{
 		For fully-connected \gls{bd}-\gls{ris}, the authors mentioned in the result section that power gain-optimal scattering matrix is also rate-optimal. Can you provide a proof on this point?
+	}
+
+	\reply{
+		This is indeed an interesting observation.
+		When the direct channel is negligible, the power gain-optimal scattering matrix is obtained in closed form \eqref{eq:ris_nd_power_max} and coincides with the rate-optimal scattering matrix \eqref{eq:ris_nd_rate_max} in the newly added Corollary \ref{co:nd_capacity_snr_general}.
+		When the direct channel is significant, the observation still holds, yet unfortunately we do not have a formal proof due to the non-trivial structure of both solutions.
+		The following context has been added to the manuscript to clarify this point.
+
+		\change{
+			Corollary \ref{co:nd_capacity_snr_general} also suggests that the power- and rate-optimal scattering matrices \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
+			When either condition is not satisfied, active and passive beamforming are coupled and the rate-optimal solution involves alternating optimization.
+			However, the power-optimal \gls{ris} still provides for a low-complexity decoupled solution.
+			The details will be discussed in Section~\ref{sc:rate}.
+		}
 	}
@@
 
+	\reply{
+		We agree with the reviewer that the estimation of individual forward and backward channels may be challenging in practice.
+		Section \ref{sc:estimation_error} has been added to investigate the impact of imperfect \gls{csi} on the proposed beamforming designs.
+
+		\change{
+			\begin{figure}[H]
+				\centering
+				\resizebox{!}{5cm}{
+					\input{../assets/simulation/ic_wsr_pair.tex}
+				}
+				\caption*{
+					Fig.
+Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
+				}
+			\end{figure}
+
+			Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
+			Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
+			\begin{equation*}
+				\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
+			\end{equation*}
+			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
+			The \gls{wsr} is evaluated using the true channels.
+			We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
+			On the other hand, introducing a \gls{ris} to \gls{ic} systems is helpful to mitigate the rate saturation effect as $K$ increases.
+			In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
+			These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
+		}
+	}
+
 	\comment{
@@
 	}
+
+	\reply{
+		Thank you for the feedback. The manuscript has been carefully restructured and proofread for improved clarity and readability.
+	}
+
 \end{reviewer}
@@
 
+	\reply{
+		We appreciate the reviewer's positive feedback and insightful suggestion.
+		Interference management by \gls{ris} in multi-user \gls{mimo} systems is indeed an interesting topic.
+		In the revised manuscript, we have extended the joint beamforming design to a $K$-user \gls{mimo} \gls{ic} system and provided a comprehensive study on \gls{wsr} maximization problem.
+		Please refer to Sections \ref{sc:mimo_ic}, \ref{sc:wsr}, and \ref{sc:simulation_wsr} for the model, optimization, and simulation results.
+
+		\change{
+			We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
+			This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
+			Let $\mathbf{H}_\mathrm{D}^{(kj)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{(j)} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
+			Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
+			The equivalent channel from transmitter $j$ to receiver $k$ is
+			\begin{equation*}
+				\mathbf{H}^{(kj)} = \mathbf{H}_\mathrm{D}^{(kj)} + \mathbf{H}_\mathrm{B}^{(k)} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{(j)} = \mathbf{H}_\mathrm{D}^{(kj)} + \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)},
+			\end{equation*}
+			where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B},g}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F},g}^{(j)}$, respectively.
+		}
+
+		\change{
+			On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
+			\begin{equation*}
+				R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kj)}} \mathbf{W}_k\biggr),
+			\end{equation*}
+			where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
+			The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
+			\begin{maxi*}
+				{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{}{}
+				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+				\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
+			\end{maxi*}
+			where $\rho_k \ge 0$ is the weight associated with transmission $k$.
+			This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
+		}
+
+		\change{
+				On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
+				\begin{equation*}
+					R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kj)}} \mathbf{W}_k\biggr),
+				\end{equation*}
+				where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
+				The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
+				\begin{maxi!}
+					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{}{}
+					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+					\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
+				\end{maxi!}
+				where $\rho_k \ge 0$ is the weight associated with transmission $k$.
+				This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
+
+				\begin{subsubsection}{Alternating Optimization}
+					This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
+					For a given precoder set, the passive beamforming subproblem is
+					\begin{maxi!}
+						{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{}{}
+						\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+					\end{maxi!}
+					which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.
+
+					\setcounter{lemma}{1}
+					\begin{lemma}
+						The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
+						\begin{equation*}
+							\begin{split}
+								\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K & \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
+								& \times \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
+							\end{split}
+						\end{equation*}
+						where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
+					\end{lemma}
+
+					\begin{proof}
+						Please refer to Appendix~\ref{ap:wsr}.
+					\end{proof}
+
+					For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
+					A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
+					At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
+					\begin{equation*}
+						\begin{split}
+							\mathbf{G}_k^{(r)} &= {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \\
+							& \quad \times \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
+						\end{split}
+					\end{equation*}
+					the corresponding error matrix is
+					\begin{equation*}
+						\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+					\end{equation*}
+					and the optimal precoder at transmitter $k$ is given by
+					\begin{equation*}
+						\begin{split}
+							\mathbf{W}_k^{(r)} & = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \\
+							& \quad \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
+						\end{split}
+					\end{equation*}
+					where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
+					\begin{equation*}
+						\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
+						% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
+					\end{equation*}
+					where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.
+
+					The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
+					That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+				\end{subsubsection}
+
+				\begin{subsubsection}{Low-Complexity Solution}
+					Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
+					The leakage interference minimization problem is formulated as
+					\begin{mini*}
+						{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{}{}
+						\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+					\end{mini*}
+					which can be solved iteratively in closed form.
+
+					\begin{proposition}
+						Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
+						\begin{equation*}
+							\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+						\end{equation*}
+						monotonically decreases the objective function \eqref{ob:interference},
+						% converges to a stationary point of \eqref{op:interference},
+						where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
+						\begin{equation*}
+							\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
+						\end{equation*}
+						where $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}.$
+						Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
+					\end{proposition}
+					\begin{proof}
+						Please refer to Appendix~\ref{ap:interference}.
+					\end{proof}
+					Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
+					This two-stage solution avoids outer iterations and efficiently handles inner iterations.
+				\end{subsubsection}
+		}
+
+		\change{
+			\setcounter{subfigure}{0}
+			\begin{figure}[H]
+				\centering
+				\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
+					\resizebox{!}{5cm}{
+						\input{../assets/simulation/ic_interference_sx.tex}
+					}
+				}
+				\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
+					\resizebox{!}{5cm}{
+						\input{../assets/simulation/ic_wsr_beamforming.tex}
+					}
+				}
+				\\
+				\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
+					\resizebox{!}{5cm}{
+						\input{../assets/simulation/ic_wsr_sx.tex}
+					}
+				}
+				\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
+					\resizebox{!}{5cm}{
+						\input{../assets/simulation/ic_wsr_txrx.tex}
+					}
+				}
+				\caption*{
+					Fig. Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
+					`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
+					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
+				}
+			\end{figure}
+
+			Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference by solving problem \eqref{op:interference}.
+			In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
+			The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.
+
+			Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section \ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
+			Unlike the point-to-point case, the latter is not as effective as the former.
+			The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
+			On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
+			A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.
+
+			Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
+			Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
+			The reasons have been discussed in the point-to-point case.
+
+			\begin{figure}[H]
+				\centering
+				\resizebox{!}{5cm}{
+					\input{../assets/simulation/ic_wsr_pair.tex}
+				}
+				\caption*{
+					Fig.
+Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
+				}
+			\end{figure}
+
+			Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
+			Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
+			\begin{equation*}
+				\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
+			\end{equation*}
+			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
+			The \gls{wsr} is evaluated using the true channels.
+			We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
+			On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
+			In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
+			These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
+		}
+	}
+
 	\comment{
@@
 If the implementation cost of a \gls{bd}-\gls{ris} is substantial, its performance advantages could be considerably reduced.
+	}
+
+	\reply{
+		We agree with the reviewer that the computational complexities of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} deserve further attention.
+		Apart from a summary in the introduction and an explicit analysis in the main body, we have also evaluated the average statistics of the \gls{ao} design for both architectures on the rate maximization problem \eqref{op:rate}.
+
+		On the other hand, the implementation complexities of \gls{bd}-\gls{ris} is indeed a critical issue.
+		An initial study has been conducted in \cite{Zhou2023} where the authors demonstrated the superior energy efficiency of \gls{bd}-\gls{ris} compared to both active \gls{ris} and relay systems.
+		Our colleagues are currently working on a more comprehensive analysis and the results will be published in a separate paper.
+
+		\change{
+			The additional optimization cost of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is affordable and the geodesic \gls{rcg} method is efficient on large-scale problems;
+		}
+
+		\change{
+			That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+		}
+
+		\change{
+			\begin{table}[H]
+				\caption*{Table: Performance of \gls{d}-\gls{ris} and Fully-Connected \gls{bd}-\gls{ris} on \eqref{op:rate}}
+				\centering
+				\resizebox{\columnwidth}{!}{
+					\begin{tabular}{ccccccc}
+						\toprule
+						\multirow{3}{*}{\gls{ris} type} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
+														& Objective                             & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular}                             & Time [s]         & Objective        & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular} & Time [s] \\ \midrule
+						Diagonal                        & $\num{25.33}$                      & 2.06                                  & $\num{2.620e-2}$ & $\num{32.22}$ & 2.92      & 1.277    \\
+						Fully-connected BD              & $\num{26.10}$                      & 3.84                                  & $\num{2.719e-2}$ & $\num{36.58}$ & 3.03      & 0.806    \\ \bottomrule
+					\end{tabular}
+				}
+			\end{table}
+			Table \ref{tb:complexity_bond} compares the performance of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} on rate maximization problem \eqref{op:rate} using the \gls{ao} design in Section \ref{sc:rate_ao}, where $N_\mathrm{T}=N_\mathrm{R}=4$ and $P=\qty{20}{dB}$.
+			The statistics are averaged over \num{100} independent runs.
+			The fact that fully-connected \gls{bd}-\gls{ris} provides a higher achievable rate using slightly more outer iterations $I_\text{AO}$ than \gls{d}-\gls{ris} is consistent with our analysis.
+			Interestingly, \emph{the former still ends up with shorter elapsed time,} which seems to contradict the complexity analysis that $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris} and $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris}.
+			One possible reason is that \gls{bd}-\gls{ris} only involves 1 backtracking line search per iteration while \gls{d}-\gls{ris} requires $N_\mathrm{S}$ times.
+			Another reason is that the group-wise update of \gls{d}-\gls{ris} leads to slower convergence of inner iterations.
+			These results suggest that optimizing \gls{bd}-\gls{ris} may be less computational intensive than expected.
+		}
 	}
@@
 
-% 3) The authors considered a passive RIS architecture.
-However, another passive configuration, termed globally passive (GP), is discussed in [b], [c].
-Employing AO, the resulting optimization problem to update $\Theta$ is convex.
-Comparing the proposed solutions with a globally passive BD-RIS would provide valuable insights into the performance gains obtained by relaxing the (locally) passive assumption.
-Hence, it is highly recommended to add the GP (both BD and diagonal) architecture as a benchmark in the numerical results.
+	\reply{
+		We appreciate the reviewer's suggestion and agree that the \gls{gp} architecture may serve as a canonical benchmark.
+		However, the current manuscript already exceeds the page limit and we decided not to overwhelm the readers with too many fancy \gls{ris} configurations.
+		An in-depth comparison between \gls{gp} and \gls{bd} architectures holds significant value to the \gls{ris} community and deserves a separate study in the future.
+	}
 

### 2025-01-03 manuscript/main.tex
:pencil: Update manuscript and add response

@@
 \input{preamble}
-
-% TODO compact or standard SVD
 
@@
 		Yang Zhao, Hongyu Li, and Bruno Clerckx are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K.
-(e-mail: \{\href{mailto:yang.zhao18@imperial.ac.uk}{yang.zhao18}, \href{mailto:c.li21@imperial.ac.uk}{c.li21}, \href{mailto:b.clerckx@imperial.ac.uk}{b.clerckx}\}@imperial.ac.uk).
-
-		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California, San Diego, La Jolla CA 92093, USA (e-mail: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).
+		% (e-mail: \{\href{mailto:yang.zhao18@imperial.ac.uk}{yang.zhao18}, \href{mailto:c.li21@imperial.ac.uk}{c.li21}, \href{mailto:b.clerckx@imperial.ac.uk}{b.clerckx}\}@imperial.ac.uk).
+
+		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California, San Diego, La Jolla CA 92093, USA.
+		% (e-mail: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).
 
@@
 \begin{abstract}
-	% This paper investigates the extent to which a passive \gls{ris} can redistribute
-	% singular values of a point-to-point \gls{mimo} channel for power and rate gains.
-	% This paper investigates to what extent can a passive \gls{ris} redistribute
-	% singular values to achieve power and rate gains in point-to-point \gls{mimo} channels.
-	% the limit to which
-	This paper investigates the capability of a passive \gls{ris} to redistribute the singular values of point-to-point \gls{mimo} channels for achieving power and rate gains.
-	We depart from the conventional \gls{d}-\gls{ris} with diagonal phase shift matrix
-	and adopt a \gls{bd} architecture that offers greater wave manipulation flexibility through element-wise connections.
-	% ? not restricted to diagonal scattering matrix and featuring element-wise connections for extra wave manipulation flexibility.
-	% featuring element-wise connections for signal amplitude and phase control.
-	% featuring element-wise connections for amplitude and phase control.
-	% in-group connections between elements, which enables signal amplitude and phase control.
-	% This powerful model allows cooperative wave scattering with both amplitude and phase control, and we uniquely attribute the shaping advantage to channel rearrangement and space alignment.
-	% This powerful model enables cooperative wave scattering with both amplitude and phase control, and we provide unique shaping insights in terms of channel rearrangement and space alignment.
-	% uniquely explain the extra design freedom from off-diagonal entries as channel rearrangement and space alignment.
-	% while the shaping advantage from off-diagonal entries is uniquely attributed to channel rearrangement and space alignment.
-	% An efficient and universal \gls{bd}-\gls{ris} design framework is proposed over group-wise {geodesic} \gls{rcg} on the Stiefel manifold, which performs multiplicative rotational (instead of add-then-retract) updates for faster convergence.
-	% The Pareto frontiers of channel singular values are characterized via a novel geodesic manifold optimization, and the resulting region comprehensively encapsulates relevant metrics (e.g., spectral norm and condition number).
-	Specifically, we first
-	provide shaping insights by characterizing
-	% characterize
-	the channel singular value regions attainable by \gls{d}-\gls{ris} and \gls{bd}-\gls{ris} via a novel geodesic optimization.
-	Analytical singular value bounds are then derived to explore their shaping limits in typical deployment scenarios.
-	% Pareto frontiers of channel singular values via a novel geodesic manifold optimization.
-	% channel shaping insights by characterizing the Pareto singular value frontiers via a novel geodesic manifold optimization.
-	% The resulting region comprehensively encapsulates most relevant metrics (e.g., spectral norm and condition number).
-	% To explore the shaping limits, we also derive
-	% 0ol. individual and collective
-	% analytical singular value bounds for common \gls{ris} deployment scenarios.
-	% in special channel conditions.
-	% in two common scenarios: 1) backward/forward channel is rank-deficient and 2) direct channel is blocked.
-	% respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris} via matrix analysis.
-	% For the power gain problem, we provide a closed-form iterative solution by group-wise \gls{svd} that features even faster convergence.
-	% We uniquely attribute the shaping advantage from off-diagonal entries to channel rearrangement and space alignment.
-	% Channel rearrangement is a unique feature of off-diagonal entries that allows each group to rearrange and recombine the forward and backward channels.
-	% Space alignment generalizes phase matching in \gls{siso} and introduces a trade-off between multiplicative backward-forward and additive direct-indirect channel combinations.
-	% Those channel shaping designs have two major implications.
-	% First, they demystify the performance gain from off-diagonal entries in terms of {channel rearrangement} and {space alignment}.
-	% help to demystify the gain from off-diagonal entries and reveal the shaping advantage of \gls{bd}-\gls{ris} in channel rearrangement and space alignment.
-	% Second, they inspire a two-stage suboptimal solution that decouples joint active and passive beamforming design.
-	% \gls{ris}-transceiver optimization and suggest a low-complexity suboptimal solution based on channel power maximization.
-	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a shaping-inspired low-complexity approach.
-	%  over channel power gain maximization.
-	% (i.e., power gain maximization).
-	% over channel gain maximization.
-	% The former alternates between active and passive beamformers until convergence, while the latter maximizes
-	% solves the problem in closed form by a channel power maximization and \gls{mimo} transmission subproblem.
-	% shaping-inspired approach.
-	Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values, the trade-off in manipulating them, and thus the channel power and achievable rate.
-	Those observations become more pronounced when the number of \gls{ris} elements and \gls{mimo} dimensions increase.
-	% Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values as well as the trade-off in manipulating them.
-	% We also notice the power and rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
-	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence achieving the asymptotic \gls{dof} at low \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
-	% wider dynamic range (with better trade-off) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
-
-	% indicate that the rate deficit from the latter diminishes as the \gls{ris} evolves from diagonal towards unitary, while the relative gain of \gls{bd}-\gls{ris} increase with \gls{mimo} dimensions and decrease with spatial correlation.
-
-	% , and .
-
-	% (i) , and (ii) the gap between the two approaches vanishes as \gls{bd}-\gls{ris} evolves from diagonal to unitary.
-	% not only demystify the advantage of \gls{bd}-\gls{ris} in channel rearrangement and space alignment, but also decouple the joint \gls{ris}-transceiver optimization.
-	% Those channel shaping designs not only demystify the advantage of \gls{bd}-\gls{ris} in channel rearrangement and space alignment, but also decouple the joint \gls{ris}-transceiver optimization.
-
-	% geodesic \gls{rcg} algorithm is tailored for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size, then invoked for the Pareto frontier of channel singular values.
-	% To understand the gain from off-diagonal entries, we also derive analytical singular value bounds in rank-deficient and fully-connected scenarios.
-	% As a side product, we tackle \gls{mimo} rate maximization problem by alternating between active beamformer (eigenmode transmission) and passive beamformer (\gls{rcg} algorithm) until convergence.
-	% A low-complexity suboptimal solution based on channel shaping is also proposed, where the decoupled problem is formulated as channel power maximization and solved in closed form iteratively.
-	% % We now show how channel shaping decouples the design and amounts to a low-complexity suboptimal solution.
-	% % A low-complexity suboptimal solution decoupling both blocks is also proposed, where the channel shaping subproblem is formulated as channel power maximization and solved in closed form iteratively.
-	% Theoretical analysis and numerical evaluation reveal that the shaping advantage of \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions, stemming from stronger channel rearrangement and space alignment capabilities.
+	This paper investigates the limits to which a passive \gls{ris} can redistribute the singular values of a point-to-point \gls{mimo} channel for providing power and rate gains.
+	We depart from conventional \gls{d}-\gls{ris} with diagonal phase shift matrix
+	and adopt a \gls{bd} architecture featuring group-wise connections for superior branch matching and mode alignment capabilities.
+	% wave manipulation flexibility.
+	Specifically, analytical channel singular value bounds are derived under the scenario of rank-deficient backward/forward channel or negligible direct channel, which imply the \gls{bd}-\gls{ris} shaping advantage in terms of dynamic range and \gls{dof}.
+	A numerical method is then proposed to optimize the \gls{bd}-\gls{ris} for a special class of singular value functions and invoked in a Pareto problem to reveal the singular value region.
+	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach, and extend both to \gls{wsr} maximization in \gls{mimo} interference channels.
+	Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate.
+	Those gaps become more pronounced when the number of \gls{ris} elements or \gls{mimo} dimensions increase.
+	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at much lower transmit power than \gls{d}-\gls{ris} thanks to its singular value redistribution capability.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	Reconfigurable intelligent surface, channel singular value redistribution, rate maximization, manifold optimization.
+	MIMO, RIS, channel shaping, rate maximization, singular value bounds, manifold optimization, interference channel.
 \end{IEEEkeywords}
@@
 		A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
-		% It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
 		It enables low-noise full-duplex operation, featuring better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo} systems.
@@
 		This helps to decouple joint beamforming problems into a channel shaping stage and a legacy transceiver design stage, providing a versatile solution for various wireless applications.
-		% provides a ubiquitous solution for various wireless applications by decoupling the joint \gls{ris}-transceiver design into a channel design stage and a legacy system design stage.
-		% decoupling joint beamforming design by first optimizing the channel and then the transceiver.
-		% decouples joint \gls{ris}-transceiver design by first optimizing the channel and then the system, providing a ubiquitous solution for different wireless applications
-		% different wireless applications
-		% different wireless applications
-		% into a channel design stage and a communication system design stage.
-		% provides a ubiquitous solution for different wireless applications, decoupling the joint \gls{ris}-transceiver designs into a channel design stage and a communication system design stage.
-		% which decouples joint \gls{ris}-transceiver designs by first optimizing the channel and then the communication system.
-		% and helps to decouple the \gls{ris}-transceiver design in a distributed manner.
 	\end{subsection}
@@
 	\begin{subsection}{Related Works}
-		At a specific resource block, channel shaping metrics can be categorized into two types.
-		% shaping metrics can be classified into two categories:
+		At a specific resource block, channel shaping metrics can be classified into two categories.
 		\begin{itemize}
@@
 
-		Although above works offered inspiring glimpses into the channel shaping potential of passive \gls{ris}, none attempted to disclose the entire attainable channel singular value region.
-		% to characterize the channel singular value region manipulated by passive \gls{ris}.
-		% no previous work has characterized the \gls{mimo} channel singular value region manipulated by any type of \gls{ris}.
+		Although above works offered inspiring glimpses into the channel shaping potential of passive \gls{ris}, none attempted to disclose the entire singular value region.
 		Most relevant literature \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} have also been limited to a \gls{d}-\gls{ris} model where each element is connected to a dedicated impedance and disconnected from others.
 		As such, wave impinging on one element is entirely scattered by the same element.
-		% is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
 		This simple architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal.
@@
 		Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures by graph theory \cite{Nerini2024}.
-		\gls{bd}-\gls{ris}
-		% also supports
-		can also function in
+		\gls{bd}-\gls{ris} can also function in
 		% hybrid transmitting-and-reflecting mode \cite{Li2023b} and
@@
 		Practical challenges such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a} have also been studied in recent literature.
-		Its beamforming superiority over \gls{d}-\gls{ris} has been proved in \gls{siso} and \gls{miso} systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}, however, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
-		% On the other hand, the beamforming superiority of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} has been extensively studied in \gls{siso} and \gls{miso} communication systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}.
-		% % , where the problems have been cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
-		% However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
+		Its beamforming effectiveness over \gls{d}-\gls{ris} and energy efficiency over active \gls{ris} and relay systems have been proved in \gls{siso} and \gls{miso} systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+		However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
 		The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a fully-connected \gls{bd}-\gls{ris}-aided \gls{mimo} system where the direct channel is negligible.
-		% 		The work
-		% 		% For a massive \gls{mimo} without direct link,
-		% 		Similar assumptions were also adopted in
-		% [47], which introduces a transmitter-side BD-RIS to massive
-		% MIMO that exploits statistical Channel State Information (CSI)
-		% for improved spectral efficiency
-		% 		% with negligible direct link and \gls{bd}-\gls{ris}.
-		% 		% Those assumptions simplify the problem but limit the generality of the results.
 		A transmitter-side \gls{bd}-\gls{ris} was introduced to
-		% improve the spectral efficiency of massive \gls{mimo} systems where the direct channel is negligible \cite{Mishra2024}.
 		massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, which again assumed negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
 		Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal.
-		%  and the \gls{bd}-\gls{ris} design problem is equivalent to \gls{siso} shaping.
-
-		% in single-stream \gls{mimo} transmission
-
-		% in the literature, but the resulting single-stream transceiver is rate-suboptimal and the corresponding \gls{bd}-\gls{ris} design is equivalent to \gls{siso} shaping.
-		% A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
-		% Although the results are promising, the channel shaping capability from off-diagonal entries deserves further investigation, and there lacks a universal yet efficient \gls{bd}-\gls{ris} design framework.
 	\end{subsection}
@@
 	\begin{subsection}{Contributions}
-		% We notice that there lacks a comprehensive study of \gls{bd}-\gls{ris} in point-to-point \gls{mimo} systems
-
-		% This paper investigates the shaping capability of passive \gls{ris} in point-to-point \gls{mimo} channels.
-		% We aim to answer the ultimate question:
-		% \emph{What is the channel singular value (and power gain) shaping capability of \gls{bd}-\gls{ris}?}
-
+		\label{sc:contributions}
 		This paper is motivated by a fundamental question:
-		\emph{What is the singular value (and power gain) shaping capability of a passive \gls{ris} in point-to-point \gls{mimo} channels?}
+		\emph{What is the singular value shaping capability of a passive \gls{ris} in \gls{mimo} channels?}
 		We aim for a comprehensive answer via analysis and optimization.
 		The contributions are summarized below.
-
-		% This paper aims to answer a critical question:
-		% \emph{What is the singular value (and power gain) shaping capability of passive \gls{ris} in point-to-point \gls{mimo} channels?}
-		% We provide a comprehensive answer through theoretical analysis and numerical optimization.
-
-		% This paper investigates the shaping capability of passive \gls{ris} in point-to-point \gls{mimo} channels.
-		% We aim to answer the ultimate question:
-		% \emph{What is the channel singular value and power gain shaping capability of \gls{bd}-\gls{ris}?}
-		% \emph{What is the ultimate channel singular value shaping capability of a passive \gls{ris}?}
-
-		% We notice that there lacks a comprehensive study of \gls{bd}-\gls{ris} in point-to-point \gls{mimo} systems --- the shaping benefits of \gls{bd}-\gls{ris} are not fully understood and the general rate maximization problem remains open.
-		% and the channel shaping potential of \gls{bd}-\gls{ris} remains unexplored.
-		% The channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
-		% Although the results are promising, the channel shaping capability of \gls{bd}-\gls{ris} deserves further investigation.
-		% Moreover, no previous work has characterized the \gls{mimo} channel singular value region manipulated by any type of \gls{ris}.
-		% , and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
-		% one critical question has not been fully addressed: \emph{What is the ultimate channel singular value shaping capability of a passive \gls{ris}?}
-		% \begin{enumerate}
-		% 	\item What is the entire singular value region of a \gls{mimo} channel with \gls{ris}?
-		% \end{enumerate}
-		% they neither discuss the limitation
-		% depict the entire singular value region nor provide a universal optimization framework.
-		% It motivates the ultimate question: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels in terms of singular values?}
-		% Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
-		% The answer depends heavily on \gls{ris} hardware architecture and scattering model.
-		% This paper aims to narrow those gaps and provide a comprehensive answer to the channel shaping capability question through theoretical analysis and numerical optimization.
-		% The contributions are summarized below.
-
-		% 1. need a general study on BD-RIS x MIMO and explain the potential from off-diagonal entries
-		% 2. need a general optimization framework for BD-RIS
-		% 3. need a comprehensive answer to the channel shaping question
-		% 4. need a low-complexity solution from shaping
-
-		% Specifically, we propose a novel design method that allows reshaping of the available channels through singular values manipulation.
-Our method compares favorably with respect to existing solutions in that
 
@@
 		Mode alignment refers to aligning and ordering the modes (i.e., singular vectors) of indirect channels with those of direct channel.
-		% channel rearrangement and space alignment.
-		% Channel rearrangement refers to rearranging and recombining the entries of backward (i.e., \gls{ris}-receiver) and forward (i.e., transmitter-\gls{ris}) channel matrices by their strength.
-		% Space alignment generalizes the phase matching of direct and indirect channels in \gls{siso} and \gls{miso} to the singular vector space in \gls{mimo}.
-		The former is uniquely attributed to the off-diagonal entries of the scattering matrix of \gls{bd}-\gls{ris}.
-
-		% We highlight that the off-diagonal entries of \gls{bd}-\gls{ris} scattering matrix provides higher signal processing flexibility than \gls{d}-\gls{ris}.
-		% exploits more effectively than \gls{d}-\gls{ris}.
-		% This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems.
-		%  and discuss its shaping potential.
-
-		Second, we propose a novel \gls{bd}-\gls{ris} design method that allows reshaping of the available channels through singular values manipulation.
-		Our \gls{rcg} method compares favorably with respect to existing ones in that the updates are along the geodesics (i.e., the shortest path between two points in a Riemannian manifold) of the feasible domain to accelerate convergence.
-		It also works for general design problems of group-connected \gls{bd}-\gls{ris}.
-
-		% Second, we propose an efficient \gls{bd}-\gls{ris} design framework that solves general optimization problems (e.g., singular value redistribution and rate maximization) by geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
-		% % to numerically analyze the channel shaping capability of \gls{bd}-\gls{ris}, we exploit the Riemannian geometry of the Stiefel manifold and
-		% This method modified from \cite{Abrudan2008,Abrudan2009} exploits the Riemannian geometry of the Stiefel manifold and performs group-wise multiplicative rotational updates along the geodesics, which avoids retraction and facilitates step size selection.
-		% It thus converges faster than existing non-geodesic approaches \cite{Absil2009,Pan2022d}.
-		% This is the first work to tailor an efficient optimization framework for \gls{bd}-\gls{ris}.
-
-		% pioneer
-		Third, we provide a numerical answer to the shaping question by characterizing the Pareto frontiers of channel singular values.
-		The enclosed region generalizes most relevant metrics and provides an intuitive shaping benchmark.
-		Results show that increasing \gls{bd}-\gls{ris} group size enlarges this region, improving the dynamic range of all singular values and the trade-off in manipulating them.
-		% enlarges the singular value region, improving both dynamic range of and trade-off between singular values.
-
-		% adopt the proposed geodesic \gls{rcg} and provide a numerical answer to the singular value shaping question.
-		% % to answer the channel singular value shaping question via numerical optimization.
-		% % to redistribute the singular values of a point-to-point \gls{mimo} channel.
-		% The {Pareto frontiers} of channel singular values are characterized by solving a series of weighted sum maximization problems, where the weight associated with each singular value can be positive, zero, or negative.
-		% optimizing their weighted sum, where the weights can be positive, zero, or negative.
-		% This problem is solved by the proposed geodesic \gls{rcg} algorithm.
-		% The enclosed region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-		% Results show that increasing \gls{bd}-\gls{ris} group size enlarges the singular value region, improving both dynamic range of and trade-off between singular values.
-		% , where the dynamic range and trade-off between are both improved.
-		% significantly enlarges the singular value region, improveing the dynamic range and trade-off in-between.
-		% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected \gls{bd}-\gls{ris}.
-
-		Fourth, we provide an analytical answer to the shaping question in typical deployment scenarios.
-		% For rank-deficient backward/forward channel,
-		When the backward/forward channel is rank-deficient, we derive singular value bounds applying to \gls{d}- and \gls{bd}-\gls{ris} with asymptotically large number of elements.
-		% For negligible direct channel
-		When the direct channel is negligible, we derive singular value bounds applying to fully-connected \gls{bd}-\gls{ris} with arbitrary number of elements.
-		Those bounds are validated by comparing with the numerical results above.
-		Results show that for a fixed number of elements, \gls{bd}-\gls{ris} can approach the asymptotic bounds better than \gls{d}-\gls{ris}.
-
-		% Results validate those bounds and emphasizes the shaping advantage of \gls{bd}-\gls{ris}.
-		% This is the first work to quantify the singular value redistribution capability of \gls{bd}-\gls{ris} from either numerical or analytical perspective.
-
-		% 1) rank-deficient backward/forward channel and 2) direct channel being blocked.
-
-		% % leverage matrix analysis tools and provide an analytical answer to the singular value shaping question.
-		% % revisit the channel singular value shaping problem from an analytical perspective via matrix analysis.
-		% % To explore the ultimate shaping limits, we derive individual and collective singular value bounds for rank-deficient backward/forward channel and blocked direct channel.
-		% % Asymptotic bounds shared by diagonal and \gls{bd}-\gls{ris} are derived in the former case, while exact bounds for unitary \gls{bd}-\gls{ris} are derived in the latter case.
-		% Asymptotic channel singular value bounds applying to diagonal and \gls{bd}-\gls{ris} are derived for rank-deficient backward/forward channel.
-		% On the other hand, tight bounds for fully-connected \gls{bd}-\gls{ris} with finite number of elements are derived for blocked direct channel.
-		% Results validate those bounds and emphasizes the shaping advantage of \gls{bd}-\gls{ris}.
-		% This is the first work to quantify the singular value redistribution capability of \gls{bd}-\gls{ris} from either numerical or analytical perspective.
-		% Results validate those bounds and show that
-		% fully-connected \gls{bd}-\gls{ris} without direct link.
-
-		% In the rank-deficient scenario, we show that the asymptotic performace
-
-		% % respectively in rank-deficient channels and for fully-connected \gls{bd}-\gls{ris}
-		% collective singular value bounds	for rank-deficient channels and fully-connected \gls{bd}-\gls{ris}, respectively.
-		% 	Results validate those bounds and show
-		% for rank-deficient channels and fully-connected \gls{bd}-\gls{ris}, respectively.
-		% Results validate those bounds and show that increasing \gls{bd}-\gls{ris} group size significantly enlarges the singular value region, providing wider dynamic range and better trade-off.
-		% dynamic range and trade-off of singular values are significantly improved by \gls{bd}-\gls{ris}, especially in large-scale \gls{mimo} systems.
-		% This is the first work to comprehensively answer the channel shaping capability question from both numerical and analytical perspectives in the most general \gls{bd}-\gls{ris} setup.
-		% from a Pareto perspective.
-
-		% We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
-		% Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior space alignment and channel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
-
-		Fifth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a shaping-inspired low-complexity approach.
-		The former iteratively updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg}, until convergence.
-		The latter exploits the \gls{bd}-\gls{ris} to shape the channel for maximum power gain then performs eigenmode transmission.
-		% simply shapes the channel by \gls{bd}-\gls{ris} for maximum power gain and performs eigenmode transmission.
-		Interestingly, the rate deficit from the shaping-inspired approach diminishes as the \gls{bd}-\gls{ris} evolves towards fully-connected.
-		% gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
-		We conclude that: 1) channel shaping decouples joint beamforming for reduced design complexity; 2) the power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions; 3) at low transmit power, \gls{bd}-\gls{ris} can activate more streams than \gls{d}-\gls{ris} and achieve the asymptotic \gls{dof}, thanks to its higher flexibility of shaping the distribution of channel singular values.
-		% Interestingly, the rate gap in between diminishes as the \gls{ris} evolves from diagonal to fully-connected.
-		% Channel shaping helps to decouple joint beamforming by first designing the channel and then the transmitter.
-
-		% We highlight that the power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions.
-		% Besides, \gls{bd}-\gls{ris} can help to activate more streams and achieves higher \gls{dof} than \gls{d}-\gls{ris} at low transmit \gls{snr}.
-		% \gls{bd}-\gls{ris} is shown to activate multi-stream transmission at lower transmit power than \gls{d}-\gls{ris}, hence attaining the full \gls{dof} at lower \gls{snr} thanks to its higher flexibility of shaping the distribution of channel singular values.
-
-		% Fifth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-		% In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over \gls{d}-\gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
-		% The superiority stems from stronger \emph{channel rearrangement} and \emph{space alignment} capabilities empowered by in-group cooperation.
-		% It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
-
-		% is a local-optimal approach through \gls{ao} that iteratively updates active and passive beamformers by eigenmode transmission and geodesic \gls{rcg}, respectively.
-		% The second is a low-complexity approach that shape the channel for maximum power gain then perform eigenmode transmission.
-		% It suggests that channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
-		% inspired by channel shaping that decouples the joint \gls{ris}-transceiver design.
-
-		% : a local-optimal \gls{ao} approach and a low-complexity approach inspired by channel shaping insights.
-		% The former updates active beamforming by eigenmode transmission and passive beamforming by proposed geodesic \gls{rcg} until convergence.
-		% The latter suboptimally decouples the problem as channel power gain maximization at \gls{bd}-\gls{ris} and conventional \gls{mimo} transmission at transceiver, then solves both in closed form.
-		% The problem is solved by a closed-form two-stage method.
-		% Results show that \gls{bd}-\gls{ris} provides higher power gain and achievable rate than \gls{d}-\gls{ris}, and the rate gap of two approaches diminishes as the \gls{bd}-\gls{ris} evolves from diagonal to fully-connected.
-		% It suggests channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
-		% Interestingly, the rate difference between the optimal and low-complexity designs diminishes as the \gls{ris} evolves from diagonal to unitary.
-		% Those results emphasize the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems and suggest channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
-		% a promising channel shaping path towards practical \gls{ris} and transceiver design.
-		% that channel shaping offers a promising path towards simplified and practical \gls{bd}-
-		% It suggests that channel shaping offers a promising path towards simplified and practical \gls{bd}-\gls{ris} (and transceiver) designs.
-		% via \gls{bd}-\gls{ris} offers a promising path towards simplified and practical design.
-		% offers a promising path towards simplified and practical desi
-		% It suggests channel shaping helps to decouple the joint \gls{ris}-transceiver design and offers a promising low-complexity solution.
-		% This is the first work to discuss the implications of channel shaping on joint active-passive beamforming optimization.
-
-		% Fifth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-		% In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over \gls{d}-\gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
-		% The superiority stems from stronger \emph{channel rearrangement} and \emph{space alignment} capabilities empowered by in-group cooperation.
-		% It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
-
-		% First, we quantify the capability of a \gls{bd}-\gls{ris} to reshape the \gls{mimo} point-to-point channel in terms of singular values.
-		% The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
-		% % This generalizes most singular value metrics and provides a powerful design framework.
-		% The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-		% We now discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
-		% This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
-
-		% Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-		% Specifically, group-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
-		% It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
-		% This is the first paper to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
-
-		% Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
-		% The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
-		% The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
-		% Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (diagonal) to unitary (fully-connected).
-		% It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.
-
-		% Third, we propose a closed-form iterative algorithm for power centric channel shaping problems.
-		% The idea is to successively approximate the quadratic objective by a sequence of affines and solve the local problems by \gls{svd}.
-		% Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.
+		The former origins uniquely from the off-diagonal entries of the scattering matrix of \gls{bd}-\gls{ris}.
+
+		Second, we provide an analytical answer to the shaping question under specific channel conditions.
+		It is proved that \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
+		When the backward or forward channel is rank-deficient, we derive asymptotic singular value bounds applying to both \gls{d}- and \gls{bd}-\gls{ris}.
+		When the direct channel is negligible, we recast the shaping question for fully-connected \gls{bd}-\gls{ris} as a well-studied linear algebra question and provide tight bounds on channel singular values, power gain, and capacity.
+		The corresponding \gls{ris} scattering matrices are also derived in closed form.
+
+		Third, we provide a numerical answer to the shaping question by exploiting a geodesic \gls{rcg} method to optimize the \gls{bd}-\gls{ris} for a special class of singular value functions.
+		It compares favorably to legacy \gls{ris} designs in that the updates are performed multiplicatively along the shortest paths on the manifold for accelerated convergence.
+		The method is then invoked in a Pareto problem to reveal the entire singular value region, which generalizes most relevant metrics and provides an intuitive shaping benchmark.
+
+		Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
+		The former iteratively updates the passive beamforming by geodesic \gls{rcg} and the active beamforming by eigenmode transmission, until convergence.
+		The latter exploits the \gls{bd}-\gls{ris} to shape the channel once for maximum power gain and then performs eigenmode transmission.
+		% Interestingly, the rate deficit from the low-complexity design diminishes as the \gls{bd}-\gls{ris} evolves towards fully-connected.
+		We also extend both approaches to \gls{wsr} maximization in \gls{mimo} interference channels where the low-complexity design aims for minimum leakage interference.
+
+		Fifth, we conduct extensive simulations to validate the analytical bounds and numerical methods.
+		It is concluded that:
+		\begin{enumerate}
+			\item \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate;
+			\item The shaping advantages of \gls{bd}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions;
+			\item \gls{bd}-\gls{ris} can activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at low transmit power thanks to its superior singular value redistribution capability;
+			\item The rate gap between the optimal and low-complexity beamforming designs diminishes as the \gls{ris} evolves from \gls{d} to fully-connected \gls{bd};
+			\item The additional optimization cost of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is affordable and the geodesic \gls{rcg} method is efficient on large-scale problems;
+			\item All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry with reasonable performance cost.
+		\end{enumerate}
 	\end{subsection}
@@
 	\begin{subsection}{MIMO Interference Channel}
-		We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} \gls{ic} of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
+		\label{sc:mimo_ic}
+		We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
 		This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
@@
 		\end{equation}
-		where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B},g}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F},g}^{(j)}$, respectively,
+		where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B},g}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F},g}^{(j)}$, respectively.
 	\end{subsection}
@@
 	In this section, we first provide an example demonstrating the \gls{mimo} channel shaping advantages of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds related to channel singular values under specific channel conditions, and provide closed-form \gls{bd}-\gls{ris} solution for several cases of interest.
-	Finally, we propose a numerical method to optimize the \gls{bd}-\gls{ris} for a special class of singular value function under general channel conditions.
+	Finally, we propose a numerical method to optimize the \gls{bd}-\gls{ris} for a special class of singular value functions under general channel conditions.
 
@@
 		Its importance lies in the fact that our initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
-		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset}--\ref{co:nd_sv_indl} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
+		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
 		The results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
@@
 			\end{subequations}
-			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices\footnote{
-				\label{fn:svd_non_uniqueness}
+			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices\footnote{%
+				\label{fn:svd_non_uniqueness}%
 				We highlight the non-uniqueness of $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$.
@@
 
-		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of individual channel singular values.
+		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of individual channel singular values, which may be used to simplify the precoder design of \gls{mimo} systems with limited number of \gls{rf} chains.
 		They are derived under different assumptions are not special cases of each other.
@@
 below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp.
-oppositely), that is,
+oppositely), that is,\footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
+This is a looser version of \eqref{iq:power_nd} and cannot take equalities unless the extreme singular values are of multiplicity $N$.}
 			\begin{equation}
@@
 			\end{equation}
-			whose\footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
-This is a looser version of \eqref{iq:power_nd} and cannot take equalities unless the extreme singular values are of multiplicity $N$.} upper and lower bounds are attained respectively at
+			whose upper\footnote{%
+				\label{fn:power_nd_max}%
+				The upper bound \eqref{eq:ris_nd_power_max} is reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.} and lower bounds are attained respectively at
 			\begin{subequations}
@@
 		The ergodic counterparts of \eqref{eq:capacity_nd} and \eqref{iq:capacity_nd_snr_extreme} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be evaluated similarly to \eqref{eq:power_nd_rayleigh}.
-		Proposition \ref{pp:dof}--\ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
+		Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
 		Extending the analysis to more general cases (e.g., significant direct channel and arbitrary \gls{bd}-\gls{ris} group size) is non-trivial due to limited branch matching and mode alignment capabilities therein.
@@
 		The group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} design problems.
-		One can also directly operate on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) relevant expressions to accelerate the algorithm for a large $G$.
+		One can also directly operate on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) relevant expressions to unify step size selection and accelerate the algorithm for a large $G$.
 
@@
 		To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean sub-gradient \eqref{eq:shaping_subdiff} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L) \bigr)$, Riemannian sub-gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:geodesic_tran} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
-		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., line \ref{ln:armijo_start}--\ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
+		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., lines \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
 		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
@@
 			To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for maximum power gain and then optimize the active beamforming.
-			The channel power gain maximization problem is formulated as\footnote{Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
-Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.}
+			The channel power gain maximization problem is formulated as\footnote{%
+				\label{fn:power_gain}%
+				Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
+Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
+			}
 			\begin{maxi!}
@@
 			\end{maxi!}
-			Inspired by \cite{Nie2017}, we propose a closed-form iterative solution that converges to a stationary point of problem \eqref{op:power}.
+			Inspired by \cite{Nie2017}, we propose a closed-form iterative solution that empirically converges to a stationary point of problem \eqref{op:power}.
 			The idea is to approximate the quadratic objective \eqref{ob:power} successively by Taylor expansion and solve each subproblem by group-wise \gls{svd}.
@@
 				\label{pp:power}
-				Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
+				Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point when $\mathbf{M}_g$ is rank-deficient due to the non-uniqueness of the orthonormal bases of kernels.}
 				\begin{equation}
@@
 				\end{equation}
-				leads to a convergence of the objective function \eqref{ob:power} towards a stationary point,\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point due to the non-uniqueness of \gls{svd}, especially when $\mathbf{M}_g$ is rank-deficient.}
-				% Multiple solutions may yield similar objective function convergence behavior.}
-				where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of\footnote{We notice that the orthogonal projection of $\mathbf{M}_g$ onto the Stiefel manifold $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g$ coincides with $\mathbf{\Theta}_g$.} % \cite{Manton2002}
+				monotonically increases the objective function \eqref{ob:power},
+				% leads to a convergence of the objective function \eqref{ob:power} towards a stationary point,\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point due to the non-uniqueness of \gls{svd}, especially when $\mathbf{M}_g$ is rank-deficient.}
+				where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of\footnote{We notice that $\mathbf{\Theta}_g$ coincides with the orthogonal projection of $\mathbf{M}_g$ onto the Stiefel manifold $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g$.} % \cite{Manton2002}
 				\begin{equation}
@@
 				\end{equation}
+				Besides, when \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
 			\end{proposition}
@@
 			\end{proof}
+
+			\begin{remark}
+				\label{re:power}
+				The sequence \eqref{eq:auxiliary_power} is constructed iteratively from its orthogonal projection.
+				Although a formal proof remains elusive, empirical evidence from simulation indicates that \eqref{eq:auxiliary_power} converge for vastly tested scenarios.
+				% We thus conjecture that the sequence \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
+			\end{remark}
 
@@
 	\begin{subsection}{MIMO Interference Channel}
+		\label{sc:wsr}
 		On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
@@
 				\begin{equation}
+					\label{eq:ris_interference}
 					\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-					\label{eq:scatter_leakage}
-				\end{equation}
-				converges to a stationary point of \eqref{op:interference}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
-				\begin{equation}
+				\end{equation}
+				monotonically decreases the objective function \eqref{ob:interference},
+				% converges to a stationary point of \eqref{op:interference},
+				where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
+				\begin{equation}
+					\label{eq:auxiliary_interference}
 					\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
@@
 				where $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}.$
+				Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
 			\end{proposition}
@@
 			\end{proof}
+			Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
+			This two-stage solution avoids outer iterations and efficiently handles inner iterations.
 		\end{subsubsection}
-		Once the channel is shaped by \eqref{eq:scatter_leakage}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
-		This two-stage solution avoids outer iterations and efficiently handles inner iterations.
 	\end{subsection}
@@
 	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician K-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
-	Unless otherwise specified, we assume $\kappa = 0$ (i.e., Rayleigh fading) for all channels and $\eta = \qty{-75}{dB}$ for all receivers.
+	Unless otherwise specified, we assume the direct channel is present, $\kappa = 0$ (i.e., Rayleigh fading) for all channels, and $\eta = \qty{-75}{dB}$ for all receivers.
 	For point-to-point channel, we set $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
-	For interference channel, we assume $K$ transmitters and receivers are independently and uniformly distributed in a disk of radius \qty{20}{m}, and all transmissions are of equal weight $\rho_k=1$, $\forall k$.
+	For interference channel, we assume $K$ transmitters and receivers are independently and uniformly distributed in a disk of radius \qty{20}{m}, and all transmissions use the same number of streams $N_\mathrm{E}$ and equal weight $\rho_k=1$, $\forall k$.
 
 	\begin{subsection}{Algorithm Evaluation}
-		\begin{table*}[!t]
-			\caption{Average Performance of Geodesic and Non-Geodesic \gls{rcg} Algorithms on Problem \eqref{op:pareto}}
-			\label{tb:complexity}
+		\begin{table}[!t]
+			\caption{Performance of Geodesic and Non-Geodesic \gls{rcg} on \eqref{op:pareto}}
+			\label{tb:complexity_algorithm}
 			\centering
+			\resizebox{\columnwidth}{!}{
 				\begin{tabular}{ccccccc}
@@
 				\end{tabular}
-		\end{table*}
-		Table \ref{tb:complexity} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023b,Li2023c,Zhou2023} on problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
+			}
+		\end{table}
+		Table \ref{tb:complexity_algorithm} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023b,Li2023c,Zhou2023} on Pareto singular value problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
 		The statistics are averaged over \num{100} independent runs.
-		We observe that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) elapsed time than the non-geodesic method.
+		We observe that the geodesic \gls{rcg} method achieves slightly higher objective values with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) elapsed time than the non-geodesic method.
 		The results demonstrate the efficiency of the geodesic \gls{rcg} algorithm \ref{ag:rcg} on large-scale \gls{bd}-\gls{ris} design problems.
+
+		\begin{table}[!t]
+			\caption{Performance of \gls{d}-\gls{ris} and Fully-Connected \gls{bd}-\gls{ris} on \eqref{op:rate}}
+			\label{tb:complexity_bond}
+			\centering
+			\resizebox{\columnwidth}{!}{
+				\begin{tabular}{ccccccc}
+					\toprule
+					\multirow{3}{*}{\gls{ris} type} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
+													& Objective                             & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular}                             & Time [s]         & Objective        & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular} & Time [s] \\ \midrule
+					Diagonal                        & $\num{25.33}$                      & 2.06                                  & $\num{2.620e-2}$ & $\num{32.22}$ & 2.92      & 1.277    \\
+					Fully-connected BD              & $\num{26.10}$                      & 3.84                                  & $\num{2.719e-2}$ & $\num{36.58}$ & 3.03      & 0.806    \\ \bottomrule
+				\end{tabular}
+			}
+		\end{table}
+		Table \ref{tb:complexity_bond} compares the performance of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} on rate maximization problem \eqref{op:rate} using the \gls{ao} design in Section \ref{sc:rate_ao}, where $N_\mathrm{T}=N_\mathrm{R}=4$ and $P=\qty{20}{dB}$.
+		The statistics are averaged over \num{100} independent runs.
+		The fact that fully-connected \gls{bd}-\gls{ris} provides a higher achievable rate using slightly more outer iterations $I_\text{AO}$ than \gls{d}-\gls{ris} is consistent with our analysis.
+		Interestingly, \emph{the former still ends up with shorter elapsed time,} which seems to contradict the complexity analysis that $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris} and $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris}.
+		One possible reason is that \gls{bd}-\gls{ris} only involves 1 backtracking line search per iteration while \gls{d}-\gls{ris} requires $N_\mathrm{S}$ times.
+		Another reason is that the group-wise update of \gls{d}-\gls{ris} leads to slower convergence of inner iterations.
+		These results suggest that optimizing \gls{bd}-\gls{ris} may be less computational intensive than expected.
 	\end{subsection}
@@
 					\label{fg:power_sx_txrx16_nd}
-					\resizebox{!}{3.0625cm}{
+					\resizebox{!}{3.15cm}{
 						\input{../assets/simulation/pc_power_sx_txrx16_nd.tex}
@@
 					\label{fg:power_sx_txrx16}
-					\resizebox{!}{3.0625cm}{
+					\resizebox{!}{3.15cm}{
 						\input{../assets/simulation/pc_power_sx_txrx16.tex}
@@
 			A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-			An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section \ref{sc:rate_ao} and the shaping-inspired low-complexity solution in Section \ref{sc:rate_lc} narrows as $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+			An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section \ref{sc:rate_ao} and the low-complexity shaping-inspired solution in Section \ref{sc:rate_lc} narrows as $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
 			This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the active beamformer, which simplifies the design substantially.
@@
 		\begin{subsubsection}{MIMO Interference Channel}
+			\label{sc:simulation_wsr}
 			\begin{figure}[!t]
@@
 					\label{fg:ic_interference_sx}
-					\resizebox{!}{3.0625cm}{
+					\resizebox{!}{3.15cm}{
 						\input{../assets/simulation/ic_interference_sx.tex}
@@
 				}
-				\subfloat[WSR: $(4 \times 64 \times 4)^5$]{
+				\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
 					\label{fg:ic_wsr_beamforming}
-					\resizebox{!}{3.0625cm}{
+					\resizebox{!}{3.15cm}{
 						\input{../assets/simulation/ic_wsr_beamforming.tex}
@@
 				\\
-				\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5$]{
+				\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
 					\label{fg:ic_wsr_sx}
-					\resizebox{!}{3.0625cm}{
+					\resizebox{!}{3.15cm}{
 						\input{../assets/simulation/ic_wsr_sx.tex}
@@
 				}
-				\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^5$]{
+				\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
 					\label{fg:ic_wsr_txrx}
-					\resizebox{!}{3.0625cm}{
+					\resizebox{!}{3.15cm}{
 						\input{../assets/simulation/ic_wsr_txrx.tex}
@@
 			Unlike the point-to-point case, the latter is not as effective as the former.
-			The reason is that, for $K$ transmissions of different path loss, interference alignment using a shared passive beamformer alone is challenging especially when the direct channels are significant.
+			The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
 			On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
-			We expect a narrower performance gap in between when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.
+			A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.
 
@@
 			Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
-			The reasons discussed in the point-to-point case also apply here.
+			The reasons have been discussed in the point-to-point case.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{RIS Symmetry}
+			\label{sc:ris_symmetry}
 			\begin{figure}[!t]
@@
 					\label{fg:pc_power_symmetry}
-					\resizebox{!}{3.0625cm}{
+					\resizebox{!}{3.15cm}{
 						\input{../assets/simulation/pc_power_symmetry.tex}
@@
 					\label{fg:pc_rate_symmetry}
-					\resizebox{!}{3.0625cm}{
+					\resizebox{!}{3.15cm}{
 						\input{../assets/simulation/pc_rate_symmetry.tex}
@@
 \label{it:takagi}
-					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}, \eqref{eq:gradient_eucl_wsr}):} The symmetry constraint is added to the corresponding optimization problems, and one simple strategy is to project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
+					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}, \eqref{eq:gradient_eucl_wsr}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
 \label{it:projection}
 				\end{enumerate}
+			\end{remark}
 
@@
 			The two proposed modifications also outperform other candidates in both problems.
-			\end{remark}
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Channel Estimation Error}
+			\label{sc:estimation_error}
 			\begin{figure}[!t]
 				\centering
-				\resizebox{!}{3.0625cm}{
+				\resizebox{!}{3.15cm}{
 					\input{../assets/simulation/ic_wsr_pair.tex}
@@
 				\caption{
-					Impact of backward/forward channel estimation error and transceiver pairs on the weighted sum-rate of $(4 \times 64 \times 4)^K$ \gls{mimo} interference channel.
+					Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
 				}
@@
 			The \gls{wsr} is evaluated using the true channels.
-			We observe that the proposed joint beamforming design is robust to channel estimation error and thus suitable for practical implementations.
-			On the other hand, introducing a \gls{ris} to \gls{ic} systems is helpful to mitigate the rate saturation effect as the number of users increases.
-			In the overloaded regime ($K \ge 8$), \gls{bd}-\gls{ris} provides a larger \gls{wsr} slope than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
+			We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
+			On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
+			In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
 			These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
@@
 \begin{section}{Conclusion}
-	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular value redistribution.
-	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than \gls{d}-\gls{ris}.
-	This translates to a wider dynamic range of and better trade-off between singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
-	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds for practical deployment scenarios.
-	Specifically, the former is done by proposing an efficient \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization problems, which converges much faster than existing methods.
-	We also present two beamforming designs for rate maximization problem, one for optimal performance and the other exploits channel shaping for lower complexity.
+	This paper analyzes the channel shaping capability of a passive \gls{ris} in terms of singular value redistribution.
+	We focus on a \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than \gls{d}-\gls{ris}.
+	This translates to a wider dynamic range of and better trade-off between singular values, resulting in significant power and rate gains.
+	Analytical singular value bounds are derived under typical \gls{ris} deployment scenarios and the Pareto frontiers are characterized via an efficient \gls{rcg} method.
+	We also present two beamforming designs for rate maximization problem in \gls{mimo} point-to-point channel and interference channel, one for optimal performance and the other exploits channel shaping for lower complexity.
 	Extensive simulations show that the shaping advantage of \gls{bd}-\gls{ris} stems from its superior branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.
@@
 \end{section}
-
-% achieving comparable channel power with significantly fewer elements, showcasing its potential for energy-efficient and cost-effective wireless communication systems, particularly in scenarios with direct link availability.
 
@@
 		\end{align*}
-		% \begin{align*}
-		% 	\partial f\bigl(\sv(\mathbf{H})\bigr)
-		% 	& = \tr \bigl(\conv \{ \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \} \partial \mathbf{H}^*\bigr) \\
-		% 	& = \tr \bigl(\conv \{ \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \mathbf{H}_{\mathrm{F},g}^* \}\bigr) \\
-		% 	& = \tr \bigl(\conv \{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \}\partial {\mathbf{\Theta}_g^*} \bigr)
-		% \end{align*}
 		and therefore $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ constitutes a sub-gradient of $f\bigl(\sv(\mathbf{H})\bigr)$ with respect to $\mathbf{\Theta}_g$.
@@
 		which suggests that \eqref{ob:power} is non-decreasing as the solution iterates over \eqref{eq:ris_power_taylor}.
-		Since \eqref{ob:power} is also bounded from above, the sequence of objective values converges.
-
-		Finally, we prove that any solution when \eqref{ob:power} converges, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power}.
+		Since \eqref{ob:power} is also bounded from above, the sequence of objective value converges.
+
+		Finally, we prove that any solution when \eqref{eq:auxiliary_power} converges, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power}.
 		The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
@@
 		\end{gather}
-		On convergence of \eqref{ob:power}, we have $\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^? \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2$
-
-		\eqref{eq:power_ris_taylor_optimal} becomes $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
-\mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^?
-\mathbf{\Lambda}_g^\mathsf{H} = 0$ and reduces to \eqref{eq:power_ris_optimal}.
+		When \eqref{eq:auxiliary_power} converges, $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
+\mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ and \eqref{eq:power_ris_taylor_optimal} reduces to \eqref{eq:power_ris_optimal}.
 		The proof is thus completed.
@@
 		Minimizing \eqref{ob:interference} is equivalent to maximizing
-		% \begin{align*}
-		% 	f &= \sum_{k=1}^K \sum_{j \ne k} \tr \Bigl\{ \sum_g \bigl(- \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H}\bigr)\Bigr\}
-		% \end{align*}
 		\begin{align*}

### 2025-01-03 src/ic_wsr_beamforming.m

@@ -1,6 +1,6 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream] = deal(4, 128, 4, 2);
+[transmit.antenna, reflect.antenna, receive.antenna, transmit.stream] = deal(2, 128, 2, 2);
 [network.coverage, network.pair] = deal(20, 2);
 [transmit.power, receive.noise, network.weight] = deal(db2pow(-20 : 5 : 20), db2pow(-75), ones(1, 1, network.pair));
 [channel.pathloss.reference, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(db2pow(-30), 3, 2.4, 2.4);
@@ -29,6 +29,7 @@ for r = 1 : number.realization
 		for p = 1 : number.power
 			% * alternating optimization
 			transmit.beamformer.alternate = precoder_initialize(channel.direct, transmit.stream, transmit.power(p));
+			% transmit.beamformer.alternate = precoder_wsr(channel.direct, transmit.beamformer.alternate, transmit.power(p), receive.noise, network.weight);
 			[iter.converge, iter.tolerance, iter.counter, iter.wsr] = deal(false, 1e-3, 0, sum(network.weight .* rate_mimo(channel.direct, transmit.beamformer.alternate, receive.noise), 3));
 			while ~iter.converge && iter.counter <= 1e2
 				[reflect.beamformer.alternate, channel.aggregate.alternate] = scatter_wsr(channel.direct, channel.forward, channel.backward, transmit.beamformer.alternate, reflect.bond(b), receive.noise, network.weight);

### 2025-01-03 src/ic_wsr_sx.m

@@ -27,6 +27,7 @@ for r = 1 : number.realization
 			clear scatter_wsr;
 			for p = 1 : number.power
 				transmit.beamformer = precoder_initialize(channel.direct, transmit.stream, transmit.power(p));
+				% transmit.beamformer = precoder_wsr(channel.direct, transmit.beamformer, transmit.power(p), receive.noise, network.weight);
 				[iter.converge, iter.tolerance, iter.counter, iter.wsr] = deal(false, 1e-3, 0, sum(network.weight .* rate_mimo(channel.direct, transmit.beamformer, receive.noise), 3));
 				while ~iter.converge && iter.counter <= 1e2
 					[reflect.beamformer, channel.aggregate] = scatter_wsr(channel.direct, channel.forward, channel.backward, transmit.beamformer, reflect.bond(b), receive.noise, network.weight);

### 2025-01-03 src/pc_complexity_algorithm.m

@@ -26,7 +26,7 @@ end
 [counter.geodesic, counter.nongeodesic] = deal(mean(counter.geodesic, ndims(counter.geodesic)), mean(counter.nongeodesic, ndims(counter.nongeodesic)));
 [timer.geodesic, timer.nongeodesic] = deal(mean(timer.geodesic, ndims(timer.geodesic)), mean(timer.nongeodesic, ndims(timer.nongeodesic)));
 
-save('data/pc_complexity_test.mat');
+save('data/pc_complexity_algorithm.mat');
 
 
 

### 2025-02-11 review/response_241203.tex
:construction: Updating results

@@
 	\opening{Dear Editor and Reviewers,}
-	Thank you for giving us the opportunity to submit a revised version of \emph{Channel Shaping Using Beyond Diagonal RIS: Analysis, Optimization, and Enhanced Flexibility}.
+	Thank you for giving us the opportunity to submit a revised version of T-SP-32387-2024.
 	Your comments and suggestions have been invaluable in helping us improve the quality of the manuscript.

### 2025-02-11 assets/simulation/pc_power_sx_txrx16_nd.tex
:construction: Updating results

@@
 ymax=0.000116439758271769,
-ylabel style={font=\color{white!15!black}},
+% ylabel style={font=\color{white!15!black}},
 ylabel={Channel Power [W]},

### 2025-02-11 manuscript/main.tex
:construction: Updating results

@@
 
-% \title{Channel Shaping Using Beyond Diagonal RIS:\\Analysis, Optimization, and Enhanced Flexibility}
 \title{MIMO Channel Shaping and Rate Maximization\\Using Beyond Diagonal RIS}
-% \title{MIMO Channel Shaping Using Beyond Diagonal RIS: Singular Value Redistribution and Rate Maximization}
-% \title{Beyond Diagonal RIS: MIMO Channel Shaping and Rate Maximization}
 \author{
@@
 	\thanks{
-		Yang Zhao, Hongyu Li, and Bruno Clerckx are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K.
-		% (e-mail: \{\href{mailto:yang.zhao18@imperial.ac.uk}{yang.zhao18}, \href{mailto:c.li21@imperial.ac.uk}{c.li21}, \href{mailto:b.clerckx@imperial.ac.uk}{b.clerckx}\}@imperial.ac.uk).
+		Yang Zhao is with the School of Electronic and Electrical Engineering, University of Leeds, LS2 9JT, U.K. (e-mail: \href{mailto:yang.zhao@ieee.org}{yang.zhao@ieee.org}.)
+
+		Hongyu Li and Bruno Clerckx are with the Department of Electrical and Electronic Engineering, Imperial College London, SW7 2AZ, U.K.
 
 		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California, San Diego, La Jolla CA 92093, USA.
-		% (e-mail: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).
 
@@
 \begin{abstract}
-	This paper investigates the limits to which a passive \gls{ris} can redistribute the singular values of a point-to-point \gls{mimo} channel for providing power and rate gains.
-	We depart from conventional \gls{d}-\gls{ris} with diagonal phase shift matrix
-	and adopt a \gls{bd} architecture featuring group-wise connections for superior branch matching and mode alignment capabilities.
-	% wave manipulation flexibility.
-	Specifically, analytical channel singular value bounds are derived under the scenario of rank-deficient backward/forward channel or negligible direct channel, which imply the \gls{bd}-\gls{ris} shaping advantage in terms of dynamic range and \gls{dof}.
-	A numerical method is then proposed to optimize the \gls{bd}-\gls{ris} for a special class of singular value functions and invoked in a Pareto problem to reveal the singular value region.
-	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach, and extend both to \gls{wsr} maximization in \gls{mimo} interference channels.
+	This paper investigates the limits to which a passive \gls{ris} can shape a point-to-point \gls{mimo} in terms of singular values
+	% and power gain
+	and thus improve the rate performance.
+	% redistribute the singular values of a point-to-point \gls{mimo} channel for providing power and rate gains.
+	We depart from the conventional \gls{ris} with \gls{d} phase shift matrix and adopt a \gls{bd} model interconnecting elements for wave amplitude and phase manipulation.
+	This translates to superior branch matching and mode alignment capabilities in \gls{mimo}.
+	% featuring group-wise connections for enhanced branch matching and mode alignment capabilities.
+	Specifically, analytical singular values bounds are derived under popular \gls{ris} deployment scenarios
+	% the scenario of rank-deficient backward/forward channel or negligible direct channel, which
+	to showcase the shaping advantages of \gls{bd}-\gls{ris} in terms of dynamic range and \gls{dof}.
+	A numerical optimization method is then proposed for a broader range of shaping problems and invoked to characterize the entire achievable singular value region.
+	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
 	Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate.
-	Those gaps become more pronounced when the number of \gls{ris} elements or \gls{mimo} dimensions increase.
-	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at much lower transmit power than \gls{d}-\gls{ris} thanks to its singular value redistribution capability.
+	Those benefits become more pronounced when the number of \gls{ris} elements or \gls{mimo} dimensions increase.
+	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at much lower transmit power than \gls{d}-\gls{ris} thanks to its singular value shaping proficiency.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	MIMO, RIS, channel shaping, rate maximization, singular value bounds, manifold optimization, interference channel.
+	MIMO, RIS, channel shaping, rate maximization, singular value bounds, manifold optimization.
 \end{IEEEkeywords}
@@
 \begin{section}{Introduction}
-	\begin{subsection}{Background}
+	% \begin{subsection}{Background}
 		Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
@@
 		Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment, for example, compensate for the Doppler effect \cite{Basar2021}, flatten frequency-selective channels \cite{Arslan2022}, improve \gls{mimo} channel rank \cite{Ozdogan2020a}, and artificially diversify channel over time for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
-		This helps to decouple joint beamforming problems into a channel shaping stage and a legacy transceiver design stage, providing a versatile solution for various wireless applications.
-	\end{subsection}
-
-	\begin{subsection}{Related Works}
+		This helps to decouple joint beamforming problems into a channel shaping stage and a conventional transceiver design stage, providing a versatile solution for various wireless applications.
+	% \end{subsection}
+
+	% \begin{subsection}{Related Works}
 		At a specific resource block, channel shaping metrics can be classified into two categories.
@@
 		Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal.
-	\end{subsection}
-
-	\begin{subsection}{Contributions}
+	% \end{subsection}
+
+	% \begin{subsection}{Contributions}
 		\label{sc:contributions}
 		This paper is motivated by a fundamental question:
-		\emph{What is the singular value shaping capability of a passive \gls{ris} in \gls{mimo} channels?}
-		We aim for a comprehensive answer via analysis and optimization.
+		\emph{What is the channel shaping capability (in terms of singular values and their functions) of a passive \gls{ris} in \gls{mimo} channels?}
+		Unlike existing works that focus on specific metrics or scenarios, we seek a general understanding of \gls{ris} in manipulating the wireless environment to provide insights for various wireless applications.
+		% We aim for a comprehensive answer via analysis and optimization.
 		The contributions are summarized below.
@@
 		Second, we provide an analytical answer to the shaping question under specific channel conditions.
-		It is proved that \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
-		When the backward or forward channel is rank-deficient, we derive asymptotic singular value bounds applying to both \gls{d}- and \gls{bd}-\gls{ris}.
-		When the direct channel is negligible, we recast the shaping question for fully-connected \gls{bd}-\gls{ris} as a well-studied linear algebra question and provide tight bounds on channel singular values, power gain, and capacity.
-		The corresponding \gls{ris} scattering matrices are also derived in closed form.
-
-		Third, we provide a numerical answer to the shaping question by exploiting a geodesic \gls{rcg} method to optimize the \gls{bd}-\gls{ris} for a special class of singular value functions.
+		It is shown that \gls{bd}-\gls{ris} may achieve a larger or smaller communication \gls{dof} than \gls{d}-\gls{ris}.
+		When the backward or forward channel is rank-deficient, we derive asymptotic bounds of individual singular values applying to \gls{d}- and \gls{bd}-\gls{ris}.
+		When the direct channel is negligible, we recast the shaping question for fully-connected \gls{bd}-\gls{ris} as a well-studied linear algebra question and provide tight bounds (with closed-form \gls{ris} expressions) on channel singular values, power gain, and capacity.
+		% The corresponding \gls{ris} scattering matrices are also derived in closed form.
+		% The results are insightful for understanding the shaping advantages of \gls{bd}-\gls{ris} in \gls{mimo} channels.
+		These results help to understand the fundamental limits of channel shaping and serve as a foundation for advanced \gls{ris} designs.
+
+		% guide the design and optimization of future wireless networks
+
+		Third, we provide a numerical answer to the shaping question by exploiting a geodesic \gls{rcg} method to optimize the \gls{bd}-\gls{ris} for a broad class of singular value functions.
 		It compares favorably to legacy \gls{ris} designs in that the updates are performed multiplicatively along the shortest paths on the manifold for accelerated convergence.
@@
 		The former iteratively updates the passive beamforming by geodesic \gls{rcg} and the active beamforming by eigenmode transmission, until convergence.
-		The latter exploits the \gls{bd}-\gls{ris} to shape the channel once for maximum power gain and then performs eigenmode transmission.
+		The latter shapes the channel with \gls{ris} for maximum power gain and then performs conventional precoding.
+		% Closed-form solutions are derived for the power gain maximization subproblem in different scenarios.
 		% Interestingly, the rate deficit from the low-complexity design diminishes as the \gls{bd}-\gls{ris} evolves towards fully-connected.
-		We also extend both approaches to \gls{wsr} maximization in \gls{mimo} interference channels where the low-complexity design aims for minimum leakage interference.
+		% We also extend both approaches to \gls{wsr} maximization in \gls{mimo} interference channels where the low-complexity design aims for minimum leakage interference instead.
 
@@
 		It is concluded that:
-		\begin{enumerate}
+		\begin{itemize}
 			\item \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate;
 			\item The shaping advantages of \gls{bd}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions;
-			\item \gls{bd}-\gls{ris} can activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at low transmit power thanks to its superior singular value redistribution capability;
+			\item \gls{bd}-\gls{ris} can activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at low transmit power thanks to its singular value shaping proficiency;
 			\item The rate gap between the optimal and low-complexity beamforming designs diminishes as the \gls{ris} evolves from \gls{d} to fully-connected \gls{bd};
@@
 			\item All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry with reasonable performance cost.
-		\end{enumerate}
-	\end{subsection}
+		\end{itemize}
+	% \end{subsection}
 
@@
 \begin{section}{System Model}
-	\begin{subsection}{BD-RIS}
+	% \begin{subsection}{BD-RIS}
 		The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
@@
 2]{Nerini2024} where the array geometry and circuit topology are modeled in $\mathbf{\Theta}$.
-	\end{subsection}
-
-	\begin{subsection}{MIMO Point-to-Point Channel}
+	% \end{subsection}
+
+	% \begin{subsection}{MIMO Point-to-Point Channel}
 		Consider a \gls{bd}-\gls{ris} aided \gls{mimo} \gls{pc} with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
@@
 			\label{eq:channel}
-			\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \triangleq \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
-		\end{equation}
-		where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels associated with group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively, and $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ is the indirect channel via group $g$.
+			\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
+			%  \triangleq \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
+		\end{equation}
+		where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels associated with group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
+		% , and $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ is the indirect channel via group $g$.
 		Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
 		\begin{equation}
-			\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{R}_g^\mathsf{H},
-		\end{equation}
-		where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary factor matrices.
-		Let $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
+			\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{X}_g \mathbf{R}_g^\mathsf{H},
+		\end{equation}
+		where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary matrices and $\mathbf{X}_g \in \mathbb{R}^{L \times L}$ is a permutation matrix.
+		Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via group $g$ and $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
 		The equivalent channel is thus
@@
 			\label{eq:channel_svd}
-			\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
+			\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{X}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
 		\end{equation}
@@
 			Denote the direct, backward, forward channels as $h_\mathrm{D}$, $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$, and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, respectively.
-			In this case, mode alignment boils down to phase matching and any $L \in [N_\mathrm{S}]$, including \gls{d}-\gls{ris}, suffices for perfect mode alignment using
+			In this case, mode alignment boils down to phase matching and the optimal \gls{bd}-\gls{ris} structure is
+			% any $L \in [N_\mathrm{S}]$, including \gls{d}-\gls{ris}, suffices for perfect mode alignment using
 			\begin{equation}
@@
 			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B/F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of kernels of $\mathbf{h}_{\mathrm{B/F},g}$.
-			Evidently, the maximum channel gain is a function of $L$
-			\begin{equation}
-				\ \lvert h \rvert _{\max} = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
+			Apparently, any group size $L$ (including \gls{d}-\gls{ris}) suffices for perfect phase matching.
+			The resulting maximum channel gain is a function of $L$
+			\begin{equation}
+				\ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
 			\end{equation}
 			where $h_{\mathrm{B/F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B/F},g}$, and $\pi_{\mathrm{B/F},g}$ are permutations of $[L]$ sorting their magnitude in similar orders.
-			That is, the maximum \gls{siso} channel gain is attained when each \gls{bd}-\gls{ris} group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches therein.
+			That is, the maximum \gls{siso} channel gain is attained when each \gls{bd}-\gls{ris} group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
 			A larger $L$ provides more flexible branch matching and thus higher channel gain.
@@
 		When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching improves since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$.
-On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment worsens since each element can only apply a phase shift to the indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ modes.
-	\end{subsection}
-
-	\begin{subsection}{MIMO Interference Channel}
-		\label{sc:mimo_ic}
-		We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
-		This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
-		Let $\mathbf{H}_\mathrm{D}^{(kj)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{(j)} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
-		Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
-		The equivalent channel from transmitter $j$ to receiver $k$ is
-		\begin{equation}
-			\label{eq:channel_interference}
-			\mathbf{H}^{(kj)} = \mathbf{H}_\mathrm{D}^{(kj)} + \mathbf{H}_\mathrm{B}^{(k)} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{(j)} = \mathbf{H}_\mathrm{D}^{(kj)} + \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)},
-		\end{equation}
-		where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B},g}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F},g}^{(j)}$, respectively.
-	\end{subsection}
+On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment intensifies since each element can only apply a scalar phase shift to the indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ modes.
+	% \end{subsection}
+
+	% \begin{subsection}{MIMO Interference Channel}
+		% \label{sc:mimo_ic}
+		% We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
+		% This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
+		% Let $\mathbf{H}_\mathrm{D}^{(kj)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{(j)} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
+		% Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
+		% The equivalent channel from transmitter $j$ to receiver $k$ is
+		% \begin{equation}
+		% 	\label{eq:channel_interference}
+		% 	\mathbf{H}^{(kj)} = \mathbf{H}_\mathrm{D}^{(kj)} {+} \mathbf{H}_\mathrm{B}^{(k)} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{(j)} = \mathbf{H}_\mathrm{D}^{(kj)} {+} \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)},
+		% \end{equation}
+		% where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B}}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F}}^{(j)}$, respectively.
+	% \end{subsection}
 \end{section}
@@
 			\centering
-			\includegraphics[width=\columnwidth]{../assets/simulation/pc_singular_trend.eps}
+			\includegraphics[width=0.7\columnwidth]{../assets/simulation/pc_singular_trend.eps}
 			\caption{$2 \times 2 \times 2$ singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is negligible.
-$\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
-				Their maximum and minimum are marked explicitly on the plot.}
+			% $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
+			% Their maximum and minimum are marked explicitly on the plot.
+			The maximum and minimum of both singular values are marked explicitly on the plot.}
 			\label{fg:shaping_potential}
@@
 			\label{pp:dof}
-			\gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof}\footnote{\gls{dof} refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel.
-It is defined as $\mathrm{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.} than \gls{d}-\gls{ris}.
+			\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof}\footnote{Here communication \gls{dof} refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\mathrm{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.
+The concept is closely related to radar \gls{dof} which refers to the number of independent measurements.} than \gls{d}-\gls{ris}.
 		\end{proposition}
@@
 
-		Proposition \ref{pp:dof} suggests that we can expect more parallel streams or less interference when shaping the channel with \gls{bd}-\gls{ris}.
+		While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the ability to reduce the \gls{dof} can be exploited to orthogonalize channels and align interference in multi-user scenarios.
+		% reducing the \gls{dof} does not necessarily degrade the rate at finite \gls{snr}.
+		% , it does not necessarily imply a higher rate at finite \gls{snr}.
+		% It is worth mentioning that a larger \gls{dof} implies more parallel streams or less interference, which is beneficial for high-rate communication.
+
+		\begin{example}[\gls{dof} of $4 \times 4 \times 4$ shaping]
+			\label{eg:dof}
+			Consider a $4 \times 4 \times 4$ shaping with $\mathbf{H}_\mathrm{D} = \mathbf{0}$ and
+			\begin{equation*}
+				\mathbf{H}_\mathrm{B} =
+				\begin{bmatrix}
+					1 & 1 & 0 & 0 \\
+					0 & 0 & 0 & 0 \\
+					0 & 0 & 1 & 0 \\
+					0 & 0 & 0 & 0
+				\end{bmatrix}, \quad
+				\mathbf{H}_\mathrm{F} =
+				\begin{bmatrix}
+					1 & 0 & 0 & 0 \\
+					0 & 1 & 0 & 0 \\
+					0 & 0 & 0 & 0 \\
+					0 & 0 & 0 & 0
+				\end{bmatrix}.
+			\end{equation*}
+			Evidently, any \gls{d}-\gls{ris} $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}, e^{\jmath \theta_3}, e^{\jmath \theta_4})$ results in
+			\begin{equation*}
+				\mathbf{H} =
+				\begin{bmatrix}
+					e^{\jmath \theta_1} & e^{\jmath \theta_2} & 0 & 0 \\
+					0 & 0 & 0 & 0 \\
+					0 & 0 & 0 & 0 \\
+					0 & 0 & 0 & 0
+				\end{bmatrix}
+			\end{equation*}
+			and achieves a \gls{dof} of 1.
+			On the other hand, as instructed by \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min}, fully-connected \gls{bd}-\gls{ris} $\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
+			\begin{bsmallmatrix}
+				0 & \frac{\sqrt{2}}{2} & 0 & -\frac{\sqrt{2}}{2} \\
+				0 & \frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} \\
+				-1 & 0 & 0 & 0 \\
+				0 & 0 & 1 & 0
+			\end{bsmallmatrix}$ and $\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} =
+			\begin{bsmallmatrix}
+				-\frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} & 0\\
+				\frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} & 0 \\
+				0 & 0 & 0 & 1 \\
+				0 & -1 & 0 & 0
+			\end{bsmallmatrix}$
+			result in
+			\begin{equation*}
+				\mathbf{H} =
+				\begin{bmatrix}
+					0 & \sqrt{2} & 0 & 0 \\
+					0 & 0 & 0 & 0 \\
+					-1 & 0 & 0 & 0 \\
+					0 & 0 & 0 & 0
+				\end{bmatrix}, \quad
+				\mathbf{H} = \mathbf{0},
+			\end{equation*}
+			and achieve \gls{dof} of 2 and 0, respectively.
+		\end{example}
+
+		Proposition \ref{pp:dof} and Example \ref{eg:dof} suggest that we can expect more parallel streams or less interference when shaping the channel with \gls{bd}-\gls{ris}.
 		We now take a step further to examine the limits of redistributing channel singular values under specific channel conditions.
@@
 This constraint is omitted in context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
+		Proposition \ref{pp:rd} complements Proposition \ref{pp:dof} and Example \ref{eg:dof} by quantifying the dynamic range of extreme singular values.
 		A special case is Corollary \ref{co:los} for \gls{los} channel\footnote{A similar eigenvalue result has been derived for \gls{d}-\gls{ris} only \cite{Semmler2023}.}.
@@
 			then the product of the first (resp.
-last\footnote{The lower bounds coincide at zero when $N \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).}) $k$ singular values of $\mathbf{H}$ is bounded from above (resp.
+last\footnote{The lower bounds coincide at zero when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).}) $k$ singular values of $\mathbf{H}$ is bounded from above (resp.
 below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
@@
 
-		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of individual channel singular values, which may be used to simplify the precoder design of \gls{mimo} systems with limited number of \gls{rf} chains.
+		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value, which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
 		They are derived under different assumptions are not special cases of each other.
@@
 				\label{fn:power_nd_max}%
-				The upper bound \eqref{eq:ris_nd_power_max} is reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.} and lower bounds are attained respectively at
+				The upper bound \eqref{eq:ris_nd_power_max} is reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.} and lower bounds are attained respectively at
 			\begin{subequations}
@@
 		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(\cdot)$ given by \cite[(51)]{Zanella2009}.
-		\eqref{eq:power_nd_rayleigh} generalizes the \gls{siso} channel power gain aided by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} under double Rayleigh fading, but a closed-form expression seems nontrivial.
-		The next corollary has been derived in \cite{Bartoli2023} independently from Proposition \ref{pp:nd} and we include it here for completeness of results.
+		\eqref{eq:power_nd_rayleigh} generalizes the \gls{siso} channel power gain aided by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} but a closed-form expression is non-trivial.
+		The next corollary has been derived in \cite{Bartoli2023} independently of Proposition \ref{pp:nd} and we include it here for completeness of results.
 		\begin{corollary}[Channel capacity at general \gls{snr}]
@@
 				\begin{align}
-					C_{\rho_\downarrow} & \lessapprox \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \label{iq:capacity_nd_snr_low}                                           \\
+					C_{\rho_\downarrow} & \lessapprox \rho \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \label{iq:capacity_nd_snr_low}                                           \\
 					C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:capacity_nd_snr_high}
@@
 		Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
-		Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary}.
+		Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
 		\begin{proposition}
@@
 		Next, we introduce a group-wise \emph{geodesic \gls{rcg}} method modified from \cite{Abrudan2008,Abrudan2009} that performs multiplicative updates along the geodesics on the Stiefel manifold for faster convergence.
-		It is applicable to a wide range of \gls{bd}-\gls{ris} design problems where the objective $f$ is smooth or convex non-smooth\footnote{$f$ is not necessarily the symmetric gauge function \eqref{ob:shaping}.} and the only constraint is group-wise unitarity \eqref{cn:shaping_unitary}.
+		\begin{remark}
+			The group-wise geodesic \gls{rcg} method is applicable to a wide range of \gls{bd}-\gls{ris} designs where the objective $f$ is smooth or convex non-smooth and the only constraint is block unitary \eqref{cn:shaping_unitary}.
+		\end{remark}
 		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below:
@@
 					\label{eq:geodesic_tran}
-					\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu) = \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
+					\mathbf{\Theta}_g^{(r+1)} {=} \mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu) {=} \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} {=} \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
 				\end{equation}
@@
 		Varying those weights help to characterize the Pareto frontier of singular values that encloses the achievable region.
-		While the objective \eqref{ob:pareto} does not suggest any meaningful performance metric (e.g., capacity or power gain), there exists an implicit relation since stronger channel shaping capability translates to better wireless performance.
+		While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication, detection probability for sensing, and harvestable energy for power transfer).
 		Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd}.
-		It can be solved optimally by Algorithm~\ref{ag:rcg} with $\mathbf{D}_{[n,n]} = \rho_n$ in \eqref{eq:shaping_subdiff}.
+		It can be solved optimally by Algorithm~\ref{ag:rcg} with $[\mathbf{D}]_{n,n} = \rho_n$ in \eqref{eq:shaping_subdiff}.
 	\end{subsection}
@@
 \begin{section}{Rate Maximization}
-	In this section, we first solve rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point and interference channels optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
-
-	\begin{subsection}{MIMO Point-to-Point Channel}
 	\label{sc:rate}
+	In this section, we first solve rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
+
 	The achievable rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel is formulated as
@@
 
-		\begin{subsubsection}{Alternating Optimization}
+	\begin{subsection}{Alternating Optimization}
 		\label{sc:rate_ao}
@@
 		The computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
-			On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder_rate} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+		On the other hand, the complexity of active beamforming \eqref{eq:precoder_rate} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
 		The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
@@
 		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{AO}\bigl(I_\text{RCG} N_\mathrm{S} (N + N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS}) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{AO}\bigl(I_\text{RCG} (NN_\mathrm{S}^2 + N_\mathrm{S} N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} N_\mathrm{S}^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Low-Complexity Solution}
+	\end{subsection}
+
+	\begin{subsection}{Low-Complexity Solution}
 		\label{sc:rate_lc}
-			To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for maximum power gain and then optimize the active beamforming.
-			The channel power gain maximization problem is formulated as\footnote{%
+		To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel for maximum power gain and then optimize the active beamforming.
+		The shaping subproblem is formulated as\footnote{%
 			\label{fn:power_gain}%
@@
 			The sequence \eqref{eq:auxiliary_power} is constructed iteratively from its orthogonal projection.
-				Although a formal proof remains elusive, empirical evidence from simulation indicates that \eqref{eq:auxiliary_power} converge for vastly tested scenarios.
+			Although a formal proof remains elusive, empirical evidence from simulation indicates that \eqref{eq:auxiliary_power} converge, and thus \eqref{eq:ris_power} converges to a stationary point, for extensively tested scenarios.
 			% We thus conjecture that the sequence \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
@@
 		Although \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_procrustes} are of similar form, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
-			We will show in Section \ref{sc:simulation} that $\mathbf{\Theta}_\textnormal{P-max-approx}^\textnormal{MIMO-HD}$ is very close to optimal especially for a large $N_\mathrm{S}$.
+		We will show in Section \ref{sc:simulation} that \eqref{eq:ris_procrustes} achieves near-optimal performance when $N_\mathrm{S}$ is large.
 		Once the channel is shaped by \eqref{eq:ris_power} or \eqref{eq:ris_nd_power_max} or \eqref{eq:ris_procrustes}, the active beamforming is retrieved by \eqref{eq:precoder_rate}.
 		This two-stage solution avoids outer iterations and efficiently handles (or avoids) inner iterations.
-		\end{subsubsection}
 	\end{subsection}
 
-	\begin{subsection}{MIMO Interference Channel}
-		\label{sc:wsr}
-		On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
-		\begin{equation}
-			R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kj)}} \mathbf{W}_k\biggr),
-		\end{equation}
-		where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
-		The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr}}{\label{ob:wsr}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-			\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
-		\end{maxi!}
-		where $\rho_k \ge 0$ is the weight associated with transmission $k$.
-		This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
-
-		\begin{subsubsection}{Alternating Optimization}
-			\label{sc:wsr_ao}
-			This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
-			For a given precoder set, the passive beamforming subproblem is
-			\begin{maxi!}
-				{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr_ris}}{\label{ob:wsr_ris}}
-				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-			\end{maxi!}
-			which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.
-
-			\begin{lemma}
-				\label{lm:wsr}
-				The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
-				\begin{equation}
-					\label{eq:gradient_eucl_wsr}
-					\begin{split}
-						\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K & \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
-						& \times \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
-					\end{split}
-				\end{equation}
-				where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
-			\end{lemma}
-
-			\begin{proof}
-				Please refer to Appendix~\ref{ap:wsr}.
-			\end{proof}
-
-			For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
-			A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
-			At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
-			\begin{equation}
-				\begin{split}
-					\mathbf{G}_k^{(r)} &= {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \\
-					& \quad \times \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
-				\end{split}
-			\end{equation}
-			the corresponding error matrix is
-			\begin{equation}
-				\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
-			\end{equation}
-			and the optimal precoder at transmitter $k$ is given by
-			\begin{equation}
-				\label{eq:precoder_wsr}
-				\begin{split}
-					\mathbf{W}_k^{(r)} & = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \\
-					& \quad \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
-				\end{split}
-			\end{equation}
-			where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
-			\begin{equation}
-				\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
-				% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
-			\end{equation}
-			where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.
-
-			The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
-			That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Low-Complexity Solution}
-			\label{sc:wsr_lc}
-			Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
-			The leakage interference minimization problem is formulated as
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{\label{op:interference}}{\label{ob:interference}}
-				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-			\end{mini!}
-			which can be solved iteratively in closed form.
-
-			\begin{proposition}
-				\label{pp:interference}
-				Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
-				\begin{equation}
-					\label{eq:ris_interference}
-					\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-				\end{equation}
-				monotonically decreases the objective function \eqref{ob:interference},
-				% converges to a stationary point of \eqref{op:interference},
-				where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
-				\begin{equation}
-					\label{eq:auxiliary_interference}
-					\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
-				\end{equation}
-				where $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}.$
-				Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
-			\end{proposition}
-			\begin{proof}
-				Please refer to Appendix~\ref{ap:interference}.
-			\end{proof}
-			Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
-			This two-stage solution avoids outer iterations and efficiently handles inner iterations.
-		\end{subsubsection}
-	\end{subsection}
+	% \begin{subsection}{MIMO Interference Channel}
+	% 	\label{sc:wsr}
+	% 	On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
+	% 	\begin{equation}
+	% 		R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k\biggr),
+	% 	\end{equation}
+	% 	where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
+	% 	The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
+	% 	\begin{maxi!}
+	% 		{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr}}{\label{ob:wsr}}
+	% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+	% 		\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
+	% 	\end{maxi!}
+	% 	where $\rho_k \ge 0$ is the weight associated with transmission $k$.
+	% 	This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
+
+	% 	\begin{subsubsection}{Alternating Optimization}
+	% 		\label{sc:wsr_ao}
+	% 		This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
+	% 		For a given precoder set, the passive beamforming subproblem is
+	% 		\begin{maxi!}
+	% 			{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr_ris}}{\label{ob:wsr_ris}}
+	% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+	% 		\end{maxi!}
+	% 		which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.
+
+	% 		\begin{lemma}
+	% 			\label{lm:wsr}
+	% 			The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
+	% 			\begin{equation}
+	% 				\label{eq:gradient_eucl_wsr}
+	% 				\begin{split}
+	% 					\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K & \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
+	% 					& \times \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
+	% 				\end{split}
+	% 			\end{equation}
+	% 			where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
+	% 		\end{lemma}
+
+	% 		\begin{proof}
+	% 			Please refer to Appendix~\ref{ap:wsr}.
+	% 		\end{proof}
+
+	% 		For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
+	% 		A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
+	% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
+	% 		\begin{equation}
+	% 			\begin{split}
+	% 				\mathbf{G}_k^{(r)} &= {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \\
+	% 				& \quad \times \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
+	% 			\end{split}
+	% 		\end{equation}
+	% 		the corresponding error matrix is
+	% 		\begin{equation}
+	% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+	% 		\end{equation}
+	% 		and the optimal precoder at transmitter $k$ is given by
+	% 		\begin{equation}
+	% 			\label{eq:precoder_wsr}
+	% 			\begin{split}
+	% 				\mathbf{W}_k^{(r)} & = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \\
+	% 				& \quad \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
+	% 			\end{split}
+	% 		\end{equation}
+	% 		where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
+	% 		\begin{equation}
+	% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
+	% 			% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
+	% 		\end{equation}
+	% 		where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.
+
+	% 		The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
+	% 		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+	% 	\end{subsubsection}
+
+	% 	\begin{subsubsection}{Low-Complexity Solution}
+	% 		\label{sc:wsr_lc}
+	% 		Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
+	% 		The leakage interference minimization problem is formulated as
+	% 		\begin{mini!}
+	% 			{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{\label{op:interference}}{\label{ob:interference}}
+	% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+	% 		\end{mini!}
+	% 		which can be solved iteratively in closed form.
+
+	% 		\begin{proposition}
+	% 			\label{pp:interference}
+	% 			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
+	% 			\begin{equation}
+	% 				\label{eq:ris_interference}
+	% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+	% 			\end{equation}
+	% 			monotonically decreases the objective function \eqref{ob:interference},
+	% 			% converges to a stationary point of \eqref{op:interference},
+	% 			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
+	% 			\begin{equation}
+	% 				\label{eq:auxiliary_interference}
+	% 				\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
+	% 			\end{equation}
+	% 			where $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}.$
+	% 			Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
+	% 		\end{proposition}
+	% 		\begin{proof}
+	% 			Please refer to Appendix~\ref{ap:interference}.
+	% 		\end{proof}
+	% 		Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
+	% 		This two-stage solution avoids outer iterations and efficiently handles inner iterations.
+	% 	\end{subsubsection}
+	% \end{subsection}
 \end{section}
@@
 	For point-to-point channel, we set $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
-	For interference channel, we assume $K$ transmitters and receivers are independently and uniformly distributed in a disk of radius \qty{20}{m}, and all transmissions use the same number of streams $N_\mathrm{E}$ and equal weight $\rho_k=1$, $\forall k$.
+	% For interference channel, we assume $K$ transmitters and receivers are independently and uniformly distributed in a disk of radius \qty{20}{m}, and all transmissions use the same number of streams $N_\mathrm{E}$ and equal weight $\rho_k=1$, $\forall k$.
 
@@
 					Average maximum channel power gain versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
-					The direct channel is negligible.
-					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward channels.
+					`Cascaded' refers to the upper bound in \eqref{iq:power_nd}.
 				}
@@
 	\begin{subsection}{Achievable Rate Maximization}
-		\begin{subsubsection}{MIMO Point-to-Point Channel}
 		\begin{figure}[!t]
@@
 		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
-		\end{subsubsection}
-
-		\begin{subsubsection}{MIMO Interference Channel}
-			\label{sc:simulation_wsr}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
-					\label{fg:ic_interference_sx}
-					\resizebox{!}{3.15cm}{
-						\input{../assets/simulation/ic_interference_sx.tex}
-					}
-				}
-				\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
-					\label{fg:ic_wsr_beamforming}
-					\resizebox{!}{3.15cm}{
-						\input{../assets/simulation/ic_wsr_beamforming.tex}
-					}
-				}
-				\\
-				\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
-					\label{fg:ic_wsr_sx}
-					\resizebox{!}{3.15cm}{
-						\input{../assets/simulation/ic_wsr_sx.tex}
-					}
-				}
-				\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
-					\label{fg:ic_wsr_txrx}
-					\resizebox{!}{3.15cm}{
-						\input{../assets/simulation/ic_wsr_txrx.tex}
-					}
-				}
-				\caption{
-					Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
-					`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
-					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
-				}
-			\end{figure}
-
-			Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference by solving problem \eqref{op:interference}.
-			In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
-			The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.
-
-			Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section \ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
-			Unlike the point-to-point case, the latter is not as effective as the former.
-			The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
-			On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
-			A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.
-
-			Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
-			Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
-			The reasons have been discussed in the point-to-point case.
-		\end{subsubsection}
+
+		% \begin{subsubsection}{MIMO Interference Channel}
+		% 	\label{sc:simulation_wsr}
+		% 	\begin{figure}[!t]
+		% 		\centering
+		% 		\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
+		% 			\label{fg:ic_interference_sx}
+		% 			\resizebox{!}{3.15cm}{
+		% 				\input{../assets/simulation/ic_interference_sx.tex}
+		% 			}
+		% 		}
+		% 		\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
+		% 			\label{fg:ic_wsr_beamforming}
+		% 			\resizebox{!}{3.15cm}{
+		% 				\input{../assets/simulation/ic_wsr_beamforming.tex}
+		% 			}
+		% 		}
+		% 		\\
+		% 		\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
+		% 			\label{fg:ic_wsr_sx}
+		% 			\resizebox{!}{3.15cm}{
+		% 				\input{../assets/simulation/ic_wsr_sx.tex}
+		% 			}
+		% 		}
+		% 		\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
+		% 			\label{fg:ic_wsr_txrx}
+		% 			\resizebox{!}{3.15cm}{
+		% 				\input{../assets/simulation/ic_wsr_txrx.tex}
+		% 			}
+		% 		}
+		% 		\caption{
+		% 			Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
+		% 			`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
+		% 			`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
+		% 		}
+		% 	\end{figure}
+
+		% 	Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference by solving problem \eqref{op:interference}.
+		% 	In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
+		% 	The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.
+
+		% 	Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section \ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
+		% 	Unlike the point-to-point case, the latter is not as effective as the former.
+		% 	The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
+		% 	On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
+		% 	A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.
+
+		% 	Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
+		% 	Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
+		% 	The reasons have been discussed in the point-to-point case.
+		% \end{subsubsection}
 	\end{subsection}
@@
 \label{it:takagi}
-					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}, \eqref{eq:gradient_eucl_wsr}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
+					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
 \label{it:projection}
@@
 			\label{sc:estimation_error}
-			\begin{figure}[!t]
-				\centering
-				\resizebox{!}{3.15cm}{
-					\input{../assets/simulation/ic_wsr_pair.tex}
-				}
-				\caption{
-					Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
-				}
-				\label{fg:ic_wsr_pair}
-			\end{figure}
-
-			Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
-			Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
-			\begin{equation*}
-				\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
-			\end{equation*}
-			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
-			The \gls{wsr} is evaluated using the true channels.
-			We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
-			On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
-			In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
-			These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
+			% \begin{figure}[!t]
+			% 	\centering
+			% 	\resizebox{!}{3.15cm}{
+			% 		\input{../assets/simulation/ic_wsr_pair.tex}
+			% 	}
+			% 	\caption{
+			% 		Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
+			% 	}
+			% 	\label{fg:ic_wsr_pair}
+			% \end{figure}
+
+			% Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
+			% Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
+			% \begin{equation*}
+			% 	\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
+			% \end{equation*}
+			% where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
+			% The \gls{wsr} is evaluated using the true channels.
+			% We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
+			% On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
+			% In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
+			% These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
 		\end{subsubsection}
@@
 
-		Finally, we prove that any solution when \eqref{eq:auxiliary_power} converges, denoted by $\tilde{\mathbf{\Theta}}^?$, is a stationary point of \eqref{op:power}.
+		Finally, we prove that any solution when \eqref{eq:auxiliary_power} converges, denoted by $\mathbf{\Theta}'$, is a stationary point of \eqref{op:power}.
 		The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
@@
 		\end{gather}
-		When \eqref{eq:auxiliary_power} converges, $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^?
-\mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ and \eqref{eq:power_ris_taylor_optimal} reduces to \eqref{eq:power_ris_optimal}.
+		When \eqref{eq:auxiliary_power} converges, $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}' \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ and \eqref{eq:power_ris_taylor_optimal} reduces to \eqref{eq:power_ris_optimal}.
 		The proof is thus completed.
@@
 
-	\begin{subsection}{Proof of Lemma \ref{lm:wsr}}
-		\label{ap:wsr}
-		The differential of $f = \sum_{k=1}^K \rho_k R_k$ with respect to $\mathbf{\Theta}_g^*$ is
-		\begin{align*}
-			\partial f
-			& = \sum_{k=1}^K \rho_k \tr \Bigl\{ \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \Bigl( \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \\
-			& \quad + \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(k)} - \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \\
-			& \quad \times \sum_{j \ne k} \Bigl(\mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \\
-			& \quad + \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \Bigr) \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \Bigr) \mathbf{W}_k \Bigr\} \\
-			& = \sum_{k=1}^K \rho_k \Bigl( \tr \Bigl\{ \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H}\Bigr\} \\
-			& \quad + \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g \Bigr\} \\
-			& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \\
-			& \quad \quad \times \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
-			& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \\
-			& \quad \quad \times \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \Bigr\} \Bigr),
-		\end{align*}
-		and the corresponding complex derivative is \eqref{eq:gradient_eucl_wsr}.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pp:interference}}
-		\label{ap:interference}
-		Minimizing \eqref{ob:interference} is equivalent to maximizing
-		\begin{align*}
-			f(\mathbf{\Theta}) & = - I + \sum_g \beta_g^{(k)} \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \Bigr\} \\
-			& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
-			& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
-			& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
-			& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
-			& \quad + \tr \Bigl\{ \sum_g \beta_g^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
-			& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
-			& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
-			& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
-			& \quad + \tr \Bigl\{ \sum_g \mathbf{B}_{g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\},
-		\end{align*}
-		where $\mathbf{B}_{g}^{(k)} = \beta_g^{(k)} \mathbf{I} - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)}$ and the relaxation constant $\beta_g^{(k)}$ can be chosen arbitrarily.
-		One can choose $\beta_g^{(k)} = \lambda_1(\mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)})$ to ensure the positive semi-definiteness of $\mathbf{B}_{g}^{(k)}$ and formulate a quadratic function to be maximized.
-		The remaining proof is similar to Appendix \ref{ap:power} and omitted here.
-	\end{subsection}
+	% \begin{subsection}{Proof of Lemma \ref{lm:wsr}}
+	% 	\label{ap:wsr}
+	% 	The differential of $f = \sum_{k=1}^K \rho_k R_k$ with respect to $\mathbf{\Theta}_g^*$ is
+	% 	\begin{align*}
+	% 		\partial f
+	% 		& = \sum_{k=1}^K \rho_k \tr \Bigl\{ \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \Bigl( \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \\
+	% 		& \quad + \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(k)} - \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \\
+	% 		& \quad \times \sum_{j \ne k} \Bigl(\mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \\
+	% 		& \quad + \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \Bigr) \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \Bigr) \mathbf{W}_k \Bigr\} \\
+	% 		& = \sum_{k=1}^K \rho_k \Bigl( \tr \Bigl\{ \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H}\Bigr\} \\
+	% 		& \quad + \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g \Bigr\} \\
+	% 		& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \\
+	% 		& \quad \quad \times \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+	% 		& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \\
+	% 		& \quad \quad \times \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \Bigr\} \Bigr),
+	% 	\end{align*}
+	% 	and the corresponding complex derivative is \eqref{eq:gradient_eucl_wsr}.
+	% \end{subsection}
+
+	% \begin{subsection}{Proof of Proposition \ref{pp:interference}}
+	% 	\label{ap:interference}
+	% 	Minimizing \eqref{ob:interference} is equivalent to maximizing
+	% 	\begin{align*}
+	% 		f(\mathbf{\Theta}) & = - I + \sum_g \beta_g^{(k)} \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \Bigr\} \\
+	% 		& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
+	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+	% 		& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
+	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
+	% 		& \quad + \tr \Bigl\{ \sum_g \beta_g^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
+	% 		& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
+	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+	% 		& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
+	% 		& \quad + \tr \Bigl\{ \sum_g \mathbf{B}_{g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\},
+	% 	\end{align*}
+	% 	where $\mathbf{B}_{g}^{(k)} = \beta_g^{(k)} \mathbf{I} - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)}$ and the relaxation constant $\beta_g^{(k)}$ can be chosen arbitrarily.
+	% 	One can choose $\beta_g^{(k)} = \lambda_1(\mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)})$ to ensure the positive semi-definiteness of $\mathbf{B}_{g}^{(k)}$ and formulate a quadratic function to be maximized.
+	% 	The remaining proof is similar to Appendix \ref{ap:power} and omitted here.
+	% \end{subsection}
 \end{appendix}
@@
 \begin{section}{Acknowledgement}
-	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct some technical errors and improve the clarity of the manuscript.
+	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct some technical errors.
 \end{section}

### 2025-02-11 poster/beamer.tex
:lipstick: Update poster
:construction: Updating results

@@
 		\begin{column}{\colwidth}
+			\vspace{-0.5cm}
 			\begin{block}{Overview}
@@
 					\centering
-					\includegraphics[width=0.41\columnwidth]{../assets/simulation/singular_trend.eps}
+					\includegraphics[width=0.41\columnwidth]{../assets/simulation/pc_singular_trend.eps}
 					% \caption{
@@
 		\begin{column}{\colwidth}
-			\vspace{-0.5cm}
+			\vspace{-1cm}
 			\begin{prop}{\gls{dof}}{}
@@
 				\setlength{\rightskip}{\leftmargini}
-				In point-to-point \glsfmtshort{mimo}, \gls{bd}-\gls{ris} cannot achieve a larger number of \gls{dof} than \gls{d}-\gls{ris}.
+				In point-to-point \glsfmtshort{mimo}, \gls{bd}-\gls{ris} may achieve a larger or smaller \gls{dof} than \gls{d}-\gls{ris}.
 			\end{prop}
@@
 		\begin{column}{\colwidth}
-			\vspace{-0.5cm}
+			\vspace{-1cm}
 			\begin{algo}{Group-wise geodesic optimization for \gls{bd}-\gls{ris}}{}

### 2025-02-13 review/response_241203.tex
:construction: Fix plot legend

@@
 Some content in Section \ref{sc:shaping_numerical} are well established methods in the literature \cite{Abrudan2008}.
+\label{sm:a}
 			\item The optimization problems \eqref{op:power} and \eqref{op:rate_ris} lacks of novelty.
@@
 Also, it is also pointed out that Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are the standard results from matrix textbook.
+\label{sm:b}
 			\item The correctness and usefulness of the mathematical derivations.
@@
 The usefulness of these bounds on singular values of the effective channel $\mathbf{H}$ is unclear.
-			\item The literature review can be enhanced to cover a boarder range of papers that related to the problem addressed.
-			\item The simulation study can be enhanced. For example, comparisons with the \gls{d}-\gls{ris} and a globally passive \gls{bd}-\gls{ris} were suggested by the reviewer.
+\label{sm:c}
+			\item The literature review can be enhanced to cover a boarder range of papers that related to the problem addressed. \label{sm:d}
+			\item The simulation study can be enhanced. For example, comparisons with the \gls{d}-\gls{ris} and a globally passive \gls{bd}-\gls{ris} were suggested by the reviewer. \label{sm:e}
 		\end{enumerate}
@@
 We have carefully considered each point raised and have made significant revisions to address these concerns.
-Please refer to the following responses for a detailed explanation of the changes made in the revised manuscript.
+Please refer to \ref{cm:a} for \ref{sm:a}, \ref{cm:b1} and \ref{cm:b2} for \ref{sm:b}, \ref{cm:c1} and \ref{cm:c2} and \ref{cm:b2} for \ref{sm:c}, \ref{cm:b1} for \ref{sm:d}, and \ref{cm:e} for \ref{sm:e} in the following responses.
 	}
@@
 	\comment{
+		\label{cm:a}
 		The contribution of Sec. \ref{sc:shaping_numerical} is unclear for the following two reasons.
@@
 		We appreciate the reviewer's insightful comments.
-		The claim of ``universal optimization framework'' and the non-geodesic \gls{rcg} method have been removed from the revised manuscript, and we have carefully rephrased Sections \ref{sc:contributions} and \ref{sc:shaping_numerical} to reflect the specific contributions of our work.
-		Indeed, the geodesic \gls{rcg} algorithm is well studied in the literature and our intention was to extend it to block-unitary cases with parallel or unified updates, which is particularly suitable for the design of group-connected \gls{bd}-\gls{ris}.
+		The geodesic \gls{rcg} algorithm for unitary-constrained problems has indeed been proposed in the optimization literature.
+		Our contribution is an extension to block-unitary cases with parallel or unified updates that accelerate the design of group-connected \gls{bd}-\gls{ris}.
+		The claim of ``universal optimization framework'' and the non-geodesic \gls{rcg} method have been remove and we have completely reworked the optimization part to reflect the particular contributions (channel shaping).
+		The content is too long to fit here and we kindly ask the reviewer to refer to Section \ref{sc:shaping_numerical} of the revised manuscript for details.
 	}
@@
 	\reply{
-		We agree with the reviewer that the optimization objective of weighted sum of singular values is not directly related to a specific performance metric.
-		However, it helps to reveal the achievable region of channel singular values (which covers all related metrics) and we believe itself could serve as a metric for measuring the \gls{mimo} channel shaping capability of different \gls{ris}.
-		In the revised manuscript, we also generalize the objective to symmetric gauge functions to further address this concern.
+		This is an important question.
+		The weighted sum of singular values plays a crucial role in channel shaping since it helps to reveal the achievable singular value region.
+		We believe itself could serve as a metric for measuring the \gls{mimo} channel shaping capability of different \gls{ris}.
+		We have added a detailed explanation in the revised manuscript and the answer comprises two parts below.
 
 		\change{
-			Consider a special class of channel shaping problem
+			To validate Algorithm~\ref{ag:rcg} and quantify the shaping capability of \gls{bd}-\gls{ris}, we characterize the achievable singular value region of \gls{bd}-\gls{ris}-aided \gls{mimo} channel by considering the Pareto optimization problem
 			\begin{maxi*}
-				{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{}{}
-				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{}
+				{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{}{}
+				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}
 			\end{maxi*}
-			where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
-			Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
+			where $\rho_n \ge 0$ is the weight associated with the $n$-th channel singular value.
+			Varying those weights help to characterize the Pareto frontier of singular values that encloses the achievable region.
+			While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication, detection probability for sensing, and harvestable energy for power transfer).
+			Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd}.
+			It can be solved optimally by Algorithm~\ref{ag:rcg} with $[\mathbf{D}]_{n,n} = \rho_n$ in \eqref{eq:shaping_subdiff}.
+		}
+
+		\change{
+			\setcounter{figure}{1}
+			\begin{figure}[H]
+				\centering
+				\subfloat[$2 \times 32 \times 2$ (no direct)]{
+					\resizebox{!}{3.25cm}{
+						\input{../assets/simulation/pc_singular_pareto_sx32_nd.tex}
+
+					}
+				}
+				\subfloat[$2 \times 32 \times 2$]{
+					\resizebox{!}{3.25cm}{
+						\input{../assets/simulation/pc_singular_pareto_sx32.tex}
+					}
+				}
+				\\
+				\subfloat[$2 \times 64 \times 2$]{
+					\resizebox{!}{3.25cm}{
+						\input{../assets/simulation/pc_singular_pareto_sx64.tex}
+					}
+				}
+				\subfloat[$2 \times 128 \times 2$]{
+					\resizebox{!}{3.25cm}{
+						\input{../assets/simulation/pc_singular_pareto_sx128.tex}
+					}
+				}
+				\caption{Achievable singular value regions of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel shaped by \gls{bd}-\gls{ris}. The singular value pair of the direct channel are marked as baseline.
+				On the Pareto frontiers, `P-max', `E-max', and `R-max' refer to the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc, respectively.}
+			\end{figure}
+			Fig.
+\ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc are highlighted on the Pareto frontiers.
+			As the \gls{snr} increases, the rate-optimal point proceeds on the arc from the east (favoring $\sigma_1(\mathbf{H})$) to the north (favoring $\sigma_2(\mathbf{H})$).
+			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
+			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
+			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H})$ and there exists a trade-off between the alignment of two modes.
+			The smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We also see that for fully-connected \gls{bd}-\gls{ris}, the power gain-optimal and rate-optimal points coincide with each other, as derived in  \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max}.
+			This observation still holds in Figs.
+\subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is significant, yet a formal proof is unavailable due to the non-trivial solution structures.
+			The shape of the singular value region depends heavily on the relative strength of the indirect channels, which is $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$.
+			Fig.
+\subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the direct point.
+			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
+			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
+			It verifies that the design flexibility of \gls{bd}-\gls{ris} allows better alignment of multiple modes simultaneously.
+			As a consequence, \emph{the optimally shaped channels for different applications coincide with each other,} which emphasizes the benefits of \emph{multi-functional} \gls{bd}-\gls{ris}.
+			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
+			In particular, Fig.
+\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one, which can be leveraged for interference mitigation and secure communication.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable inter-connections between elements.
 		}
@@
 	\comment{
+		\label{cm:c1}
 		Derivation in the proof of Appendix \ref{ap:shaping} is incorrect.
@@
 	\reply{
-		We appreciate the reviewer's careful reading of the manuscript.
+		We appreciate the reviewer for pointing out the error.
 		We have corrected the derivation in the proof of Appendix \ref{ap:shaping} and have used the sub-differential to handle the non-differentiability of the singular value function.
 		\change{
+			Consider a special class of channel shaping problem
+			\begin{maxi*}
+				{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{}{}
+				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}
+			\end{maxi*}
+			where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
+			Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
+			Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
 			\setcounter{proposition}{3}
@@
 	\comment{
+		\label{cm:c2}
 		The rank equation in the proof of Prop.
@@
 	\reply{
-		Using the rank equation pointed out by the reviewer, we realized that the achievability proof in the previous version was incorrect. In fact, the proposition was incorrect.
+		Using the rank equation pointed out by the reviewer, we realized that the achievability proof was incorrect, and the proposition itself was incorrect.
+		We really appreciate the reviewer for pointing out this mistake!
 		A new proof in Appendix \ref{ap:dof} shows that \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
-		We apologize for the confusion and appreciate the reviewer for pointing out this mistake.
+		The change in the main text is as follows.
 		\change{
@@
 			\begin{proposition}[Degrees of freedom]
-				\gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
+				\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof}\footnotetext{Here communication \gls{dof} refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\mathrm{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.
+The concept is closely related to radar \gls{dof} which refers to the number of independent measurements.} than \gls{d}-\gls{ris}.
 			\end{proposition}
+			\begin{proof}
+				Please refer to Appendix~\ref{ap:dof}.
+			\end{proof}
+
+			While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the ability to reduce the \gls{dof} can be exploited to orthogonalize channels and align interference in multi-user scenarios.
+			% reducing the \gls{dof} does not necessarily degrade the rate at finite \gls{snr}.
+			% , it does not necessarily imply a higher rate at finite \gls{snr}.
+			% It is worth mentioning that a larger \gls{dof} implies more parallel streams or less interference, which is beneficial for high-rate communication.
+
+			\begin{example}[\gls{dof} of $4 \times 4 \times 4$ shaping]
+				Consider a $4 \times 4 \times 4$ shaping with $\mathbf{H}_\mathrm{D} = \mathbf{0}$ and
+				\begin{equation*}
+					\mathbf{H}_\mathrm{B} =
+					\begin{bmatrix}
+						1 & 1 & 0 & 0 \\
+						0 & 0 & 0 & 0 \\
+						0 & 0 & 1 & 0 \\
+						0 & 0 & 0 & 0
+					\end{bmatrix}, \quad
+					\mathbf{H}_\mathrm{F} =
+					\begin{bmatrix}
+						1 & 0 & 0 & 0 \\
+						0 & 1 & 0 & 0 \\
+						0 & 0 & 0 & 0 \\
+						0 & 0 & 0 & 0
+					\end{bmatrix}.
+				\end{equation*}
+				Evidently, any \gls{d}-\gls{ris} $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}, e^{\jmath \theta_3}, e^{\jmath \theta_4})$ results in
+				\begin{equation*}
+					\mathbf{H} =
+					\begin{bmatrix}
+						e^{\jmath \theta_1} & e^{\jmath \theta_2} & 0 & 0 \\
+						0 & 0 & 0 & 0 \\
+						0 & 0 & 0 & 0 \\
+						0 & 0 & 0 & 0
+					\end{bmatrix}
+				\end{equation*}
+				and achieves a \gls{dof} of 1.
+				On the other hand, as instructed by \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min}, fully-connected \gls{bd}-\gls{ris} $\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
+				\begin{bsmallmatrix}
+					0 & \frac{\sqrt{2}}{2} & 0 & -\frac{\sqrt{2}}{2} \\
+					0 & \frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} \\
+					-1 & 0 & 0 & 0 \\
+					0 & 0 & 1 & 0
+				\end{bsmallmatrix}$ and $\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} =
+				\begin{bsmallmatrix}
+					-\frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} & 0\\
+					\frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} & 0 \\
+					0 & 0 & 0 & 1 \\
+					0 & -1 & 0 & 0
+				\end{bsmallmatrix}$
+				result in
+				\begin{equation*}
+					\mathbf{H} =
+					\begin{bmatrix}
+						0 & \sqrt{2} & 0 & 0 \\
+						0 & 0 & 0 & 0 \\
+						-1 & 0 & 0 & 0 \\
+						0 & 0 & 0 & 0
+					\end{bmatrix}, \quad
+					\mathbf{H} = \mathbf{0},
+				\end{equation*}
+				and achieve \gls{dof} of 2 and 0, respectively.
+			\end{example}
+
+			Proposition \ref{pp:dof} and Example \ref{eg:dof} suggest that we can expect more parallel streams or less interference when shaping the channel with \gls{bd}-\gls{ris}.
+			We now take a step further to examine the limits of redistributing channel singular values under specific channel conditions.
 		}
@@
 	\comment{
+		\label{cm:b1}
 		In Sec.
@@
 	\reply{
-		The aim of Proposition \ref{pp:nd} is to transform the channel shaping limit question into a well-studied linear algebra question, such that Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} (previously 3.1 -- 3.4) follows from standard results.
+		We would like to argue that, while Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are standard mathematical results, it is Proposition \ref{pp:nd} that allows one to recast the channel shaping question as a well-studied linear algebra problem and enable those.
 		In the revised manuscript, we have also added
@@
 			\item Lower bound on channel power gain in Corollary \ref{co:nd_power};
-			\item Upper bound on channel capacity at general and extreme \gls{snr} in Corollaries \ref{co:nd_capacity_snr_general} and \ref{co:nd_capacity_snr_extreme};
+			\item Upper bound on channel capacity at general \gls{snr} in Corollary \ref{co:nd_capacity_snr_general} and at extreme \gls{snr} in \ref{co:nd_capacity_snr_extreme}.
 		\end{itemize}
-		and derived the corresponding \gls{ris} scattering matrices in closed form.
-		We also notice that the bounds on the $n$-th singular value can be used, for example, to simplify the precoder design in \gls{mimo} systems with limited number $n$ of RF chains.
+		The corresponding \gls{ris} scattering matrices have also been derived in closed form.
+		We believe those bounds and \gls{ris} expressions not only serve as benchmarks but also motivate low-complexity designs (e.g., Section \ref{sc:rate_lc}) in various wireless applications.
+		For example, the bounds on the $n$-th singular value can be used to simplify precoding design in \gls{mimo} systems with limited number $n$ of RF chains.
 		The comparison to relay beamforming design is insightful and we have added footnote \ref{fn:power_nd_max} to highlight the connection.
@@
 			\end{corollary}
+			Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value, which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
+			They are derived under different assumptions are not special cases of each other.
+			Importantly, Corollary \ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
+first and last few in Proposition \ref{pp:rd}), applies to fully-connected \gls{bd}-\gls{ris} of arbitrary size, and provides a general solution structure.
 		}
@@
 			\end{corollary}
+			We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
 		}
@@
 			\end{corollary}
+			Corollary \ref{co:nd_capacity_snr_general} also suggests that the power- and rate-optimal scattering matrices \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
+			When either condition is not satisfied, active and passive beamforming are coupled and the rate-optimal solution involves alternating optimization.
+			However, the power-optimal \gls{ris} still provides for a low-complexity decoupled solution.
+			The details will be discussed in Section~\ref{sc:rate}.
 		}
@@
 	\comment{
+		\label{cm:b2}
 		The optimization problems \eqref{op:power} and \eqref{op:rate_ris} lacks of novelty.
@@
 		We agree with the reviewer that problem \eqref{op:rate_ris} may be solved by the method proposed in \cite{Li2023b} with appropriate adjustment.
-		However, extending the single mode alignment in \cite{Santamaria2023} to solve problem \eqref{op:power} is far from optimal as shown in Fig. \ref{fg:pc_power_symmetry} (labelled as ``Legacy'').
-		We have added footnote \ref{fn:power_gain} to clarify the novelty of our approach.
+		We believe our method is more efficient as evident from Table \ref{tb:complexity_algorithm}.
+		However, although problem \eqref{op:power} has been studied in symmetric \gls{bd}-\gls{ris}-aided \gls{miso} \cite{Santamaria2023} where only one mode is available, generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
+		We have also added footnote \ref{fn:power_gain} to clarify this point.
 		\change{
-				The channel power gain maximization problem is formulated as\footnotetext{%
 			Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
 Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
-			}
-		}
-
-		\change{
-			\begin{figure}[H]
-				\centering
-				\resizebox{!}{6cm}{
-					\input{../assets/simulation/pc_power_symmetry.tex}
-				}
-				\caption*{
-					Fig. Impact of \gls{ris} symmetry on the power gain of $2 \times N_\mathrm{S} \times 2$ \gls{mimo} point-to-point channel.
-				}
-			\end{figure}
 		}
@@
 	\reply{
-		We sincerely appreciate the reviewer for pointing out the issue.
+		We appreciate the reviewer for pointing out the issue.
 		Indeed, the sequence of iterates may oscillate and the convergence proof in the previous version was incorrect.
@@
 		\change{
+			\setcounter{remark}{2}
 			\begin{remark}
 				The sequence \eqref{eq:auxiliary_power} is constructed iteratively from its orthogonal projection.
-				Although a formal proof remains elusive, empirical evidence from simulation indicates that \eqref{eq:auxiliary_power} converge for vastly tested scenarios.
-				% We thus conjecture that the sequence \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
+				Although a formal proof remains elusive, empirical evidence from simulation indicates that \eqref{eq:auxiliary_power} converge, and thus \eqref{eq:ris_power} converges to a stationary point, for extensively tested scenarios.
 			\end{remark}
@@
 					\item \emph{\gls{svd}-based (e.g., \eqref{eq:ris_nd_sv_indl}, \eqref{eq:ris_nd_power}, \eqref{eq:ris_nd_rate_max}, \eqref{eq:ris_power}, \eqref{eq:ris_procrustes}):} Those closed-form asymmetric solutions are constructed from the product of singular matrices.
-If symmetry is required, one can replace the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} and use unitary factor $\mathbf{Q}$ to construct the corresponding $\mathbf{\Theta}$.
-					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}, \eqref{eq:gradient_eucl_wsr}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
+If symmetry is required, one can replace the $\mathbf{U}, \mathbf{V}$ from the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by the factor $\mathbf{Q}$ from the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} to construct the corresponding $\mathbf{\Theta}$;
+					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
 				\end{enumerate}
@@
 			Here, `Asymmetric' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, `Enforced' refers to enforcing symmetry on `Asymmetric', `Legacy' refers to a straightforward extension of the \gls{siso} \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, `Takagi' refers to the modification \ref{it:takagi}, and `Projection' refers to the modification \ref{it:projection}.
-			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and scale with the number of scattering elements.
+			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and tends to widen with the number of scattering elements.
 			The two proposed modifications also outperform other candidates in both problems.
@@
 	\reply{
-		This is indeed an interesting observation.
-		When the direct channel is negligible, the power gain-optimal scattering matrix is obtained in closed form \eqref{eq:ris_nd_power_max} and coincides with the rate-optimal scattering matrix \eqref{eq:ris_nd_rate_max} in the newly added Corollary \ref{co:nd_capacity_snr_general}.
-		When the direct channel is significant, the observation still holds, yet unfortunately we do not have a formal proof due to the non-trivial structure of both solutions.
-		The following context has been added to the manuscript to clarify this point.
+		This is truly an interesting observation.
+		When the direct channel is negligible and \gls{bd}-\gls{ris} is fully-connected, the power gain-optimal and rate-optimal scattering matrices derived in closed form \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} indeed coincide with each other.
+		When the direct channel is significant, the observation still holds, yet we do not have a formal proof due to the non-trivial solution structures.
+		The following context has been added to the manuscript to support this claim.
 
@@
 			When either condition is not satisfied, active and passive beamforming are coupled and the rate-optimal solution involves alternating optimization.
-			However, the power-optimal \gls{ris} still provides for a low-complexity decoupled solution.
-			The details will be discussed in Section~\ref{sc:rate}.
+			However, the power gain-optimal \gls{ris} still provides for a low-complexity decoupled solution.
+		}
+		\change{
+			We also see that for fully-connected \gls{bd}-\gls{ris}, the power gain-optimal and rate-optimal points coincide with each other, as derived in  \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max}.
+			This observation still holds in Figs.
+\subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is significant, yet a formal proof is unavailable due to the non-trivial solution structures.
 		}
@@
 				\centering
-				\resizebox{!}{5cm}{
-					\input{../assets/simulation/ic_wsr_pair.tex}
+				\subfloat[Pareto: $2 \times 64 \times 2$]{
+					\resizebox{!}{3.15cm}{
+						\input{../assets/simulation/pc_singular_csi.tex}
 					}
-				\caption*{
-					Fig.
-Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
+				}
+				\subfloat[Rate: $4 \times 128 \times 4$]{
+					\resizebox{!}{3.15cm}{
+						\input{../assets/simulation/pc_rate_csi.tex}
+					}
+				}
+				\caption{
+					Impact of \gls{ris} channel estimation error on the \gls{mimo} singular value region and achievable rate.
+					A higher transparency of the Pareto frontier indicates a larger channel estimation error.
+					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
 				}
@@
 
-			Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
-			Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
+			Figs. \ref{fg:pc_singular_csi} and \ref{fg:pc_rate_csi} investigates how \gls{ris} channel estimation errors affect the system performance in terms of singular value region and achievable rate.
+			We assume the direct channel can be perfectly acquired and the estimated backward and forward channels are modeled by
 			\begin{equation*}
-				\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
+				\hat{\mathbf{H}}_{\mathrm{B/F}} = \mathbf{H}_{\mathrm{B/F}} + \tilde{\mathbf{H}}_{\mathrm{B/F}},
 			\end{equation*}
-			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
-			The \gls{wsr} is evaluated using the true channels.
-			We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
-			On the other hand, introducing a \gls{ris} to \gls{ic} systems is helpful to mitigate the rate saturation effect as $K$ increases.
-			In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
-			These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
+			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
+			The results are evaluated over the ground truth channels.
+			It is observed that the proposed channel shaping and joint beamforming solutions are reasonably robust to channel estimation errors.
+			An interesting observation is that a \gls{bd}-\gls{ris} designed over extremely poorly estimated channels ($\epsilon = 0.5$) may still outpeform a \gls{d}-\gls{ris} designed over almost perfectly estimated channels ($\epsilon = 0.01$).
+			We hope those results can motivate further research on the robust shaping/beamforming design and provide insights for practical \gls{bd}-\gls{ris} deployment.
 		}
@@
 		We appreciate the reviewer's positive feedback and insightful suggestion.
-		Interference management by \gls{ris} in multi-user \gls{mimo} systems is indeed an interesting topic.
-		In the revised manuscript, we have extended the joint beamforming design to a $K$-user \gls{mimo} \gls{ic} system and provided a comprehensive study on \gls{wsr} maximization problem.
-		Please refer to Sections \ref{sc:mimo_ic}, \ref{sc:wsr}, and \ref{sc:simulation_wsr} for the model, optimization, and simulation results.
-
-		\change{
-			We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
-			This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
-			Let $\mathbf{H}_\mathrm{D}^{(kj)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{(j)} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
-			Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
-			The equivalent channel from transmitter $j$ to receiver $k$ is
-			\begin{equation*}
-				\mathbf{H}^{(kj)} = \mathbf{H}_\mathrm{D}^{(kj)} + \mathbf{H}_\mathrm{B}^{(k)} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{(j)} = \mathbf{H}_\mathrm{D}^{(kj)} + \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)},
-			\end{equation*}
-			where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B},g}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F},g}^{(j)}$, respectively.
-		}
-
-		\change{
-			On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
-			\begin{equation*}
-				R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kj)}} \mathbf{W}_k\biggr),
-			\end{equation*}
-			where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
-			The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
-			\begin{maxi*}
-				{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{}{}
-				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-				\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
-			\end{maxi*}
-			where $\rho_k \ge 0$ is the weight associated with transmission $k$.
-			This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
-		}
-
-		\change{
-				On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
-				\begin{equation*}
-					R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kj)}} \mathbf{W}_k\biggr),
-				\end{equation*}
-				where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
-				The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
-				\begin{maxi!}
-					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{}{}
-					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-					\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
-				\end{maxi!}
-				where $\rho_k \ge 0$ is the weight associated with transmission $k$.
-				This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
-
-				\begin{subsubsection}{Alternating Optimization}
-					This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
-					For a given precoder set, the passive beamforming subproblem is
-					\begin{maxi!}
-						{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{}{}
-						\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-					\end{maxi!}
-					which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.
-
-					\setcounter{lemma}{1}
-					\begin{lemma}
-						The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
-						\begin{equation*}
-							\begin{split}
-								\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K & \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
-								& \times \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
-							\end{split}
-						\end{equation*}
-						where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
-					\end{lemma}
-
-					\begin{proof}
-						Please refer to Appendix~\ref{ap:wsr}.
-					\end{proof}
-
-					For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
-					A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
-					At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
-					\begin{equation*}
-						\begin{split}
-							\mathbf{G}_k^{(r)} &= {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \\
-							& \quad \times \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
-						\end{split}
-					\end{equation*}
-					the corresponding error matrix is
-					\begin{equation*}
-						\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
-					\end{equation*}
-					and the optimal precoder at transmitter $k$ is given by
-					\begin{equation*}
-						\begin{split}
-							\mathbf{W}_k^{(r)} & = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \\
-							& \quad \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
-						\end{split}
-					\end{equation*}
-					where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
-					\begin{equation*}
-						\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
-						% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
-					\end{equation*}
-					where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.
-
-					The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
-					That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-				\end{subsubsection}
-
-				\begin{subsubsection}{Low-Complexity Solution}
-					Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
-					The leakage interference minimization problem is formulated as
-					\begin{mini*}
-						{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{}{}
-						\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-					\end{mini*}
-					which can be solved iteratively in closed form.
-
-					\begin{proposition}
-						Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
-						\begin{equation*}
-							\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-						\end{equation*}
-						monotonically decreases the objective function \eqref{ob:interference},
-						% converges to a stationary point of \eqref{op:interference},
-						where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
-						\begin{equation*}
-							\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
-						\end{equation*}
-						where $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}.$
-						Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
-					\end{proposition}
-					\begin{proof}
-						Please refer to Appendix~\ref{ap:interference}.
-					\end{proof}
-					Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
-					This two-stage solution avoids outer iterations and efficiently handles inner iterations.
-				\end{subsubsection}
-		}
+		Interference management by \gls{ris} in multi-user \gls{mimo} systems is indeed an interesting topic, but the page limit is a serious concern and we have to prioritize the point-to-point content.
+		The study on \gls{bd}-\gls{ris}-aided interference channel deserves another submission and we are happy to share some initial results with you.
 
@@
 				\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
+					\label{fg:ic_interference_sx}
 					\resizebox{!}{5cm}{
@@
 				\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
+					\label{fg:ic_wsr_beamforming}
 					\resizebox{!}{5cm}{
@@
 				\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
+					\label{fg:ic_wsr_sx}
 					\resizebox{!}{5cm}{
@@
 				\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
+					\label{fg:ic_wsr_txrx}
 					\resizebox{!}{5cm}{
@@
 				}
-				\caption*{
-					Fig. Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
+				\caption{
+					Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
 					`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
@@
 
-			Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference by solving problem \eqref{op:interference}.
+			Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
 			In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
@@
 
-			Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section \ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
+			Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs, respectively.
 			Unlike the point-to-point case, the latter is not as effective as the former.
@@
 				}
-				\caption*{
-					Fig.
-Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
+				\caption{Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
 				}
+				\label{fg:ic_wsr_pair}
 			\end{figure}
@@
 			Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
-			Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
+			Specifically, the active and passive beamformers are designed over the estimated backward and forward channels
 			\begin{equation*}
@@
 			The \gls{wsr} is evaluated using the true channels.
-			We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
+			We observe that the proposed joint beamforming design is reasonably robust to channel estimation error and thus viable for practical implementation.
 			On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
@@
 	\comment{
+		\label{cm:e}
 		The authors considered a passive \gls{ris} architecture.

### 2025-02-13 assets/poster/power_sx_txrx16.tex
:construction: Fix plot legend

@@
 \begin{axis}[%
-width=7.607cm,
-height=6cm,
+width=9.509cm,
+height=7.5cm,
 at={(0cm,0cm)},
@@
 legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
-font=\tiny,
-title style={font=\tiny},
-label style={font=\tiny},
-ticklabel style={font=\tiny},
-legend style={font=\tiny},
 x label style={yshift=10pt},

### 2025-02-13 assets/poster/singular_bound_rank2_sx128.tex
:construction: Fix plot legend

--- 2024-07-23 assets/simulation/singular_bound_rank2_sx128.tex
@@
 transpose legend,
-legend style={/tikz/column 2/.style={column sep=5pt}}
+legend style={/tikz/column 2/.style={column sep=5pt}},
+y label style={yshift=-7pt}
 ]

### 2025-02-13 manuscript/main.tex
:construction: Fix plot legend

@@
 \begin{abstract}
-	This paper investigates the limits to which a passive \gls{ris} can shape a point-to-point \gls{mimo} in terms of singular values
+	This paper investigates the limits to which a passive \gls{ris} can reshape a point-to-point \gls{mimo} in terms of singular values
 	% and power gain
@@
 	% redistribute the singular values of a point-to-point \gls{mimo} channel for providing power and rate gains.
-	We depart from the conventional \gls{ris} with \gls{d} phase shift matrix and adopt a \gls{bd} model interconnecting elements for wave amplitude and phase manipulation.
+	We depart from the conventional \gls{ris} with \gls{d} phase shift matrix and adopt a \gls{bd} model interconnecting elements for signal amplitude and phase manipulation.
 	This translates to superior branch matching and mode alignment capabilities in \gls{mimo}.
@@
 	to showcase the shaping advantages of \gls{bd}-\gls{ris} in terms of dynamic range and \gls{dof}.
-	A numerical optimization method is then proposed for a broader range of shaping problems and invoked to characterize the entire achievable singular value region.
+	A numerical optimization method is then proposed for a broader range of shaping problems and invoked to characterize the achievable singular value region.
 	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
@@
 			\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
-Those are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to minor perturbations of the channel matrix.
+Those are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to minor perturbations of the channel matrix;
 			\item \emph{Power:} The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} in point-to-point channels and leakage interference \cite{Santamaria2023a} in interference channels.
@@
 		This simple architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal.
-		The idea was soon generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}.
+		The idea was later generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}.
 		This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
@@
 			\item \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate;
+			\item A fully-connected \gls{bd}-\gls{ris} may be designed in closed-form for multi-functional optimality;
 			\item The shaping advantages of \gls{bd}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions;
@@
 			\item The additional optimization cost of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is affordable and the geodesic \gls{rcg} method is efficient on large-scale problems;
-			\item All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry with reasonable performance cost.
+			\item The proposed \gls{ris} designs are robust to channel estimation errors and can be modified for symmetry with reasonable performance cost.
 		\end{itemize}
@@
 	% \begin{subsection}{BD-RIS}
-		The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-		Apparently $N_\mathrm{S} = \sum_{g=1}^G N_g$.
-		Without loss of generality we assume equal size for all groups $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$ and no mutual coupling between elements.
+		The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a} such that $N_\mathrm{S} = \sum_{g=1}^G N_g$.
+		Without loss of generality we assume equal group size $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$ and no mutual coupling between elements.
 		For asymmetric \gls{bd}-\gls{ris}, the overall scattering matrix is block-diagonal with unitary blocks\footnote{We assume asymmetric network by default to establish a benchmark for passive \gls{ris}.
@@
 		where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th diagonal block modeling the response of group $g$.
-		It is noteworthy that \gls{d}-\gls{ris} is an extreme case of \eqref{eq:ris} with group size $L=1$, that is, each element is an individual.
+		Apparently, \gls{d}-\gls{ris} is an extreme case of \eqref{eq:ris} with group size $L=1$.
 		Some viable architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
@@
 5]{Li2023c}, \cite[Fig.
-2]{Nerini2024} where the array geometry and circuit topology are modeled in $\mathbf{\Theta}$.
+2]{Nerini2024} where the circuit topology have been modeled in $\mathbf{\Theta}$.
 	% \end{subsection}
@@
 	% \begin{subsection}{MIMO Point-to-Point Channel}
-		Consider a \gls{bd}-\gls{ris} aided \gls{mimo} \gls{pc} with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
+		Consider a \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
 		This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$.
@@
 		\begin{equation}
+			\label{eq:ris_decompose_group}
 			\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{X}_g \mathbf{R}_g^\mathsf{H},
 		\end{equation}
-		where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary matrices and $\mathbf{X}_g \in \mathbb{R}^{L \times L}$ is a permutation matrix.
+		where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary matrices and $\mathbf{X}_g$ is a permutation matrix.
 		Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via group $g$ and $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
@@
 			In \eqref{eq:channel_svd}, the \gls{bd}-\gls{ris} performs a blockwise unitary transformation to combine the backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
-			These two attributes are refined as:
+			These two attributes are refined respectively as:
 			\begin{itemize}
-				\item \emph{Branch matching:} It refers to pairing and combining the branches (i.e., entries) of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ through $\mathbf{\Theta}_g$.
-				\item \emph{Mode alignment:} It refers to aligning and ordering the modes (i.e., singular vectors) of $\{\mathbf{H}_g\}_{g \in [G]}$ with those of $\mathbf{H}_\mathrm{D}$ through $\{\mathbf{\Theta}_g\}_{g \in [G]}$.
+				\item \emph{Branch matching:} To pair and combine the branches (i.e., entries) of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ through $\mathbf{\Theta}_g$;
+				\item \emph{Mode alignment:} To align and order the modes (i.e., singular vectors) of $\{\mathbf{H}_g\}_{g \in [G]}$ with those of $\mathbf{H}_\mathrm{D}$ through $\mathbf{\Theta}$.
 			\end{itemize}
@@
 			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B/F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of kernels of $\mathbf{h}_{\mathrm{B/F},g}$.
-			Apparently, any group size $L$ (including \gls{d}-\gls{ris}) suffices for perfect phase matching.
-			The resulting maximum channel gain is a function of $L$
+			It is evident that any group size $L$ (including \gls{d}-\gls{ris}) suffices for perfect phase matching.
+			On the other hand, the resulting maximum channel gain depends on $L$
 			\begin{equation}
@@
 		% \label{sc:mimo_ic}
-		% We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
+		% We also consider a \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
 		% This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
@@
 		\end{equation*}
-		We restrict the discussion to a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
+		We consider a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
 		The singular value shaping capabilities of $\mathbf{\Theta}_\mathrm{D}$ and $\mathbf{\Theta}_\mathrm{BD}$ can thus be compared visually over 2 tunable parameters.
@@
 		With an exhaustive grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$, Fig.~\ref{fg:shaping_potential} shows the achievable singular values of a specific channel realization
+		% \begin{equation*}
+		% 	\mathbf{H}_\mathrm{B} =
+		% 		\begin{bsmallmatrix}
+		% 			-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
+		% 			0.4131 + 0.2651 \jmath  & -0.1960 + 0.4650 \jmath
+		% 		\end{bsmallmatrix},
+		% 		\mathbf{H}_\mathrm{F} =
+		% 		\begin{bsmallmatrix}
+		% 			-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
+		% 			0.0196 + 0.4011 \jmath  & -0.3170 - 0.2303 \jmath
+		% 		\end{bsmallmatrix}.
+		% \end{equation*}
 		\begin{equation*}
@@
 				\mathbf{H}_\mathrm{B} & =
-				\begin{bmatrix}
+				\begin{bsmallmatrix}
 					-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
 					0.4131 + 0.2651 \jmath  & -0.1960 + 0.4650 \jmath
-				\end{bmatrix},
+				\end{bsmallmatrix},
 				\\
 				\mathbf{H}_\mathrm{F} & =
-				\begin{bmatrix}
+				\begin{bsmallmatrix}
 					-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
 					0.0196 + 0.4011 \jmath  & -0.3170 - 0.2303 \jmath
-				\end{bmatrix}.
+				\end{bsmallmatrix}.
 			\end{split}
@@
 			\label{pp:dof}
-			\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof}\footnote{Here communication \gls{dof} refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\mathrm{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.
-The concept is closely related to radar \gls{dof} which refers to the number of independent measurements.} than \gls{d}-\gls{ris}.
+			\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof}\footnote{Here \gls{dof} refers to the maximum number of streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\textnormal{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.
+It is closely related to radar \gls{dof} which refers to the number of independent measurements.} than \gls{d}-\gls{ris}.
 		\end{proposition}
@@
 
-		While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the ability to reduce the \gls{dof} can be exploited to orthogonalize channels and align interference in multi-user scenarios.
+		While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the potential to reduce the \gls{dof} can be exploited to orthogonalize channels and align interference in multi-user scenarios.
 		% reducing the \gls{dof} does not necessarily degrade the rate at finite \gls{snr}.
@@
 				\mathbf{H}_\mathrm{B} =
-				\begin{bmatrix}
+				\begin{bsmallmatrix}
 					1 & 1 & 0 & 0 \\
@@
 					0 & 0 & 0 & 0
-				\end{bmatrix}, \quad
+				\end{bsmallmatrix}, \quad
 				\mathbf{H}_\mathrm{F} =
-				\begin{bmatrix}
-					1 & 0 & 0 & 0 \\
-					0 & 1 & 0 & 0 \\
-					0 & 0 & 0 & 0 \\
-					0 & 0 & 0 & 0
-				\end{bmatrix}.
+				\diag(1, 1, 0, 0).
+				% \begin{bsmallmatrix}
+				% 	1 & 0 & 0 & 0 \\
+				% 	0 & 1 & 0 & 0 \\
+				% 	0 & 0 & 0 & 0 \\
+				% 	0 & 0 & 0 & 0
+				% \end{bsmallmatrix}.
 			\end{equation*}
@@
 				\mathbf{H} =
-				\begin{bmatrix}
+				\begin{bsmallmatrix}
 					e^{\jmath \theta_1} & e^{\jmath \theta_2} & 0 & 0 \\
@@
 					0 & 0 & 0 & 0
-				\end{bmatrix}
+				\end{bsmallmatrix}
 			\end{equation*}
 			and achieves a \gls{dof} of 1.
-			On the other hand, as instructed by \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min}, fully-connected \gls{bd}-\gls{ris} $\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
+			In contrast, fully-connected \gls{bd}-\gls{ris} $\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
 			\begin{bsmallmatrix}
@@
 				0 & -1 & 0 & 0
-			\end{bsmallmatrix}$
+			\end{bsmallmatrix}$ in \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min}
 			result in
@@
 				\mathbf{H} =
-				\begin{bmatrix}
+				\begin{bsmallmatrix}
 					0 & \sqrt{2} & 0 & 0 \\
@@
 					0 & 0 & 0 & 0
-				\end{bmatrix}, \quad
+				\end{bsmallmatrix}, \quad
 				\mathbf{H} = \mathbf{0},
@@
 		if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are at least rank $k$, then
-		with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large $N_\mathrm{S}$,
+		with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of \emph{sufficiently large} $N_\mathrm{S}$,
 		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
-		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected in all cases.
-This constraint is omitted in context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
+		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected in all cases.} while the last $k$ channel singular values can be suppressed to zero.
 		Proposition \ref{pp:rd} complements Proposition \ref{pp:dof} and Example \ref{eg:dof} by quantifying the dynamic range of extreme singular values.
@@
 This can result from a very large number of \gls{ris} elements (as discussed in Proposition~\ref{pp:rd}) or physical obstacles in the propagation path (as discussed in Proposition~\ref{pp:nd}).}.
-		For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes, and we will later show by simulation that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
-		Proposition \ref{pp:rd} provides a reference on the selection of $N_\mathrm{S}$ in low-multipath application scenarios.
+		For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes, and we will later show in Section \ref{sc:simulation} that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
+		Proposition \ref{pp:rd} provides a reference on the selection of $N_\mathrm{S}$ in low-multipath application scenarios, highlighting its diminishing returns.
 		Next, we shift the focus to another popular \gls{ris} deployment scenario where the direct channel is blocked.
@@
 		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
-		Its importance lies in the fact that our initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
+		Its importance lies in that our initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
 		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
@@
 first and last few in Proposition \ref{pp:rd}), applies to fully-connected \gls{bd}-\gls{ris} of arbitrary size, and provides a general solution structure.
-		We emphasize that in \eqref{eq:ris_nd_sv_indl} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of unitary $\mathbf{X}$ defined in \eqref{eq:ris_decompose}.
+		We emphasize that in \eqref{eq:ris_nd_sv_indl} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of $\mathbf{X}$ defined in \eqref{eq:ris_decompose_group}.
 		Specially, the extreme channel singular values can be manipulated up to
@@
 		\end{subequations}
-		We notice that the right halves in \eqref{iq:sv_nd_largest} and \eqref{iq:sv_nd_smallest} are special cases of \eqref{iq:sv_nd_prod_largest} and \eqref{iq:sv_nd_prod_smallest} when $k=1$.
+		We notice that the right halves in \eqref{iq:sv_nd_largest} and \eqref{iq:sv_nd_smallest} are also special cases of \eqref{iq:sv_nd_prod_largest} and \eqref{iq:sv_nd_prod_smallest} with $k=1$.
 
@@
 			\begin{itemize}
-				\item \gls{d}-\gls{ris}: It is evident that any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode alignment capability.
+				\item \gls{d}-\gls{ris}: It is evident that any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode alignment capability;
 				\item \gls{bd}-\gls{ris}: According to \eqref{iq:sv_nd_indl}, a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
@@
 		We conclude from Example \ref{eg:shaping_bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
-		However, when the problem of interest is a function of multiple singular values, their individual bounds \eqref{iq:sv_nd_indl} may not be simultaneously tight.
+		However, the individual bounds \eqref{iq:sv_nd_indl} may not be simultaneously tight when the problem of interest is a function of multiple singular values.
 		Some case studies are presented below.
@@
 			\label{co:nd_capacity_snr_general}
-			If the direct channel is negligible, then the \gls{bd}-\gls{ris} aided \gls{mimo} channel capacity is
+			If the direct channel is negligible, then the \gls{bd}-\gls{ris}-aided \gls{mimo} channel capacity is
 			\begin{equation}
@@
 		When either condition is not satisfied, active and passive beamforming are coupled and the rate-optimal solution involves alternating optimization.
-		However, the power-optimal \gls{ris} still provides for a low-complexity decoupled solution.
+		However, the power gain-optimal \gls{ris} still provides for a low-complexity decoupled solution.
 		The details will be discussed in Section~\ref{sc:rate}.
@@
 			\label{co:nd_capacity_snr_extreme}
-			If the direct channel is negligible, then the channel capacity when the \gls{snr} $\rho$ is very low and high are approximately bounded from above by
+			If the direct channel is negligible, then the channel capacity at extremely low and high \gls{snr} $\rho$ are approximately bounded from above by
 			\begin{subequations}
@@
 		Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
-		Extending the analysis to more general cases (e.g., significant direct channel and arbitrary \gls{bd}-\gls{ris} group size) is non-trivial due to limited branch matching and mode alignment capabilities therein.
+		Extending the analysis to more general setups and objectives is non-trivial due to limited branch matching and mode alignment capabilities therein.
 		A numerical solution will be discussed in Section~\ref{sc:shaping_numerical}.
@@
 		\begin{remark}
-			The group-wise geodesic \gls{rcg} method is applicable to a wide range of \gls{bd}-\gls{ris} designs where the objective $f$ is smooth or convex non-smooth and the only constraint is block unitary \eqref{cn:shaping_unitary}.
+			The group-wise geodesic \gls{rcg} method is applicable to a wide range of \gls{bd}-\gls{ris} designs where the objective $f$ is smooth or convex non-smooth and \eqref{cn:shaping_unitary} is the only constraint.
 		\end{remark}
-		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below:
+		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below, where gradients can be replaced by sub-gradients for non-smooth $f$.
 		\begin{enumerate}[label=(\roman*)]
-			\item \emph{Compute the Euclidean (sub-)gradient at $\mathbf{\Theta}_g^{(r)}$:} The (sub-)gradient of $f$ with respect to $\mathbf{\Theta}_g$ in the Euclidean space is
+			\item \emph{Compute the Euclidean gradient at $\mathbf{\Theta}_g^{(r)}$:} The gradient of $f$ with respect to $\mathbf{\Theta}_g$ in the Euclidean space is
 			% \cite[(A.3.6)]{Fischer2005}
@@
 				\end{equation}
-			\item \emph{Translate to the Riemannian (sub-)gradient at $\mathbf{\Theta}_g^{(r)}$:} At point $\mathbf{\Theta}_g^{(r)}$, the Riemannian (sub-)gradient gives the steepest ascent direction on the manifold.
+			\item \emph{Translate to the Riemannian gradient at $\mathbf{\Theta}_g^{(r)}$:} At point $\mathbf{\Theta}_g^{(r)}$, the Riemannian gradient gives the steepest ascent direction on the manifold.
 It lies in the tangent space of the manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$ and is obtainable by projection:
@@
 				\end{equation}
-			\item \emph{Translate to the Riemannian (sub-)gradient at the identity:} The Riemannian (sub-)gradient should be translated back to the identity for exploiting the Lie algebra\footnote{Lie algebra refers to the tangent space of the Lie group at the identity element.
+			\item \emph{Translate to the Riemannian gradient at the identity:} The Riemannian gradient should be translated back to the identity for exploiting the Lie algebra\footnote{Lie algebra refers to the tangent space of the Lie group at the identity element.
 A Lie group is simultaneously a continuous group and a differentiable manifold.
@@
 				\end{equation}
-			\item \emph{Determine the conjugate direction:} The conjugate direction is obtained over the Riemannian (sub-)gradient and previous direction as
+			\item \emph{Determine the conjugate direction:} The conjugate direction is obtained over the Riemannian gradient and previous direction as
 				\begin{equation}
@@
 	\label{sc:rate}
-	In this section, we first solve rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
-
-	The achievable rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel is formulated as
+	In this section, we first solve the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
+	The problem is formulated as
+	% The achievable rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel is formulated as
 	\begin{maxi!}
@@
 	Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
-	Two approaches are proposed to solve it optimally or efficiently.
+	% Two approaches are proposed to solve it optimally or efficiently.
 
@@
 		To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel for maximum power gain and then optimize the active beamforming.
-		The shaping subproblem is formulated as\footnote{%
-			\label{fn:power_gain}%
-			Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
+		The shaping subproblem is formulated as
+		% \footnote{%
+		% 	\label{fn:power_gain}%
+		% 	Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
 Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
-		}
+		% }
 		\begin{maxi!}
@@
 		\end{maxi!}
+		Similar problems have been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
+Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
 		Inspired by \cite{Nie2017}, we propose a closed-form iterative solution that empirically converges to a stationary point of problem \eqref{op:power}.
@@
 		\begin{itemize}
-			\item \emph{Negligible direct channel:} The optimal solution to \eqref{op:power} has been solved in closed form by \eqref{eq:ris_nd_power_max}.
+			\item \emph{Negligible direct channel:} The optimal solution to \eqref{op:power} has been solved in closed form by \eqref{eq:ris_nd_power_max};
 			\item \emph{Non-negligible direct channel:} In terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
@@
 				\label{eq:ris_procrustes}
-				\mathbf{\Theta}_\textnormal{P-max-approx}^\textnormal{MIMO-HD} = \mathbf{U} \mathbf{V}^\mathsf{H},
+				\mathbf{\Theta}_\textnormal{P-max-approx}^\textnormal{MIMO} = \mathbf{U} \mathbf{V}^\mathsf{H},
 			\end{equation}
@@
 	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
-	We set $\Lambda_0=\qty{-30}{dB}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$, and $\gamma_\mathrm{B}=2$ for reference.
+	We set $\Lambda_0=\qty{-30}{dB}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$, $\gamma_\mathrm{B}=2$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
 	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician K-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
-	Unless otherwise specified, we assume the direct channel is present, $\kappa = 0$ (i.e., Rayleigh fading) for all channels, and $\eta = \qty{-75}{dB}$ for all receivers.
-	For point-to-point channel, we set $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
+	Unless otherwise specified, we assume the direct channel is present, $\kappa = 0$ (i.e., Rayleigh fading) for all channels, and $\eta = \qty{-75}{dB}$.
+	% For point-to-point channel, we set $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
 	% For interference channel, we assume $K$ transmitters and receivers are independently and uniformly distributed in a disk of radius \qty{20}{m}, and all transmissions use the same number of streams $N_\mathrm{E}$ and equal weight $\rho_k=1$, $\forall k$.
@@
 				}
-				\caption{Pareto frontiers of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel reshaped by \gls{bd}-\gls{ris}.}
+				\caption{Achievable singular value regions of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel shaped by \gls{bd}-\gls{ris}. The singular value pair of the direct channel are marked as baseline.
+				On the Pareto frontiers, `P-max', `E-max', and `R-max' refer to the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc, respectively.}
 				\label{fg:singular_pareto}
 			\end{figure}
-			Fig. \ref{fg:singular_pareto} illustrates the Pareto frontiers of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} aided by \gls{ris}.
+			Fig.
+\ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc are highlighted on the Pareto frontiers.
+			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
+			As the \gls{snr} increases, the rate-optimal point proceeds on the arc from the east (favoring $\sigma_1(\mathbf{H})$) to the north (favoring $\sigma_2(\mathbf{H})$).
+			% The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
 			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
-			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two spaces.
-			We observe that the smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
-			When the direct channel is significant, the shape of the singular value region depends heavily on the relative strength of the indirect channels, which is $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$ in this case.
+			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H})$ and there exists a trade-off between the alignment of two modes.
+			The smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We also see that for fully-connected \gls{bd}-\gls{ris}, the power gain-optimal and rate-optimal points coincide with each other, as have been proved in  \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max}.
+			This observation still holds in Figs.
+\subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is significant, yet a formal proof is unavailable due to the non-trivial solution structures.
+			The shape of the singular value region depends heavily on the relative strength of the indirect channels, which is $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$ here.
 			Fig.
-\subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the point of direct channel.
+\subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the direct point.
 			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
 			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
-			It suggests the design flexibility from larger group size allows better alignment of multiple modes simultaneously.
-			% not only provides a better trade-off in channel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
+			It verifies that the design flexibility of \gls{bd}-\gls{ris} allows better alignment of multiple modes simultaneously.
+			As a consequence, {the optimally shaped channels for power gain, communication, and power transfer coincide,} which implies that \emph{a fully-connected \gls{bd}-\gls{ris} may be designed in closed-form for multi-functional optimality.}
 			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
 			In particular, Fig.
-\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
+\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one, which may be leveraged for interference mitigation and secure communication.
 			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable inter-connections between elements.
@@
 			\end{figure}
-			We focus on achieving the analytical bounds in Proposition \ref{pp:rd} since many bounds in Proposition \ref{pp:nd} are provided with closed-form \gls{ris} solutions.
+			We focus on achieving the asymptotic bounds in Proposition \ref{pp:rd} as most results from Proposition \ref{pp:nd} are supplied with closed-form \gls{ris} solutions.
 			For a rank-$k$ forward channel, Fig.
@@
 		This is particularly visible in Fig. \subref*{fg:rate_sx} where the topmost curve is almost a linear function of the transmit power.
-		It is also expected from the shaping results in Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
+		It can be predicted from Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
 		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician K-factor increases and becomes indistinguishable in \gls{los} environment.
@@
 				\caption{
-					Impact of \gls{ris} symmetry on the power gain and achievable rate of \gls{mimo} point-to-point channel.
+					Impact of \gls{ris} symmetry on the \gls{mimo} power gain and achievable rate.
 				}
@@
 					\item \emph{\gls{svd}-based (e.g., \eqref{eq:ris_nd_sv_indl}, \eqref{eq:ris_nd_power}, \eqref{eq:ris_nd_rate_max}, \eqref{eq:ris_power}, \eqref{eq:ris_procrustes}):} Those closed-form asymmetric solutions are constructed from the product of singular matrices.
-If symmetry is required, one can replace the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} and use unitary factor $\mathbf{Q}$ to construct the corresponding $\mathbf{\Theta}$.
-\label{it:takagi}
+If symmetry is required, one can replace the $\mathbf{U}, \mathbf{V}$ from the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by the factor $\mathbf{Q}$ from the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} to construct the corresponding $\mathbf{\Theta}$; \label{it:takagi}
 					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
@@
 			Figs.
-\ref{fg:pc_power_symmetry} and \ref{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
+\subref*{fg:pc_power_symmetry} and \subref*{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
 			Here, `Asymmetric' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, `Enforced' refers to enforcing symmetry on `Asymmetric', `Legacy' refers to a straightforward extension of the \gls{siso} \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, `Takagi' refers to the modification \ref{it:takagi}, and `Projection' refers to the modification \ref{it:projection}.
-			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and scale with the number of scattering elements.
+			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and tends to widen with the number of scattering elements.
 			The two proposed modifications also outperform other candidates in both problems.
@@
 			\label{sc:estimation_error}
+			\begin{figure}[!t]
+				\centering
+				\subfloat[Pareto: $2 \times 64 \times 2$]{
+					\label{fg:pc_singular_csi}
+					\resizebox{!}{3.15cm}{
+						\input{../assets/simulation/pc_singular_csi.tex}
+					}
+				}
+				\subfloat[Rate: $4 \times 128 \times 4$]{
+					\label{fg:pc_rate_csi}
+					\resizebox{!}{3.15cm}{
+						\input{../assets/simulation/pc_rate_csi.tex}
+					}
+				}
+				\caption{
+					Impact of \gls{ris} channel estimation error on the \gls{mimo} singular value region and achievable rate.
+					A higher transparency of the Pareto frontier indicates a larger channel estimation error.
+					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
+				}
+			\end{figure}
+
+			Figs.
+\subref*{fg:pc_singular_csi} and \subref*{fg:pc_rate_csi} investigates how \gls{ris} channel estimation errors affect the system performance in terms of singular value region and achievable rate.
+			We assume the direct channel can be perfectly acquired and the estimated backward and forward channels are modeled by
+			\begin{equation*}
+				\hat{\mathbf{H}}_{\mathrm{B/F}} = \mathbf{H}_{\mathrm{B/F}} + \tilde{\mathbf{H}}_{\mathrm{B/F}},
+			\end{equation*}
+			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
+			The results are evaluated over the ground truth channels.
+			It is observed that the proposed channel shaping and joint beamforming solutions are reasonably robust to channel estimation errors.
+			An interesting observation is that a \gls{bd}-\gls{ris} designed over extremely poorly estimated channels ($\epsilon = 0.5$) may still outpeform a \gls{d}-\gls{ris} designed over almost perfectly estimated channels ($\epsilon = 0.01$).
+			We hope those results can motivate further research on the robust shaping design and provide insights for practical \gls{bd}-\gls{ris} deployment.
+
 			% \begin{figure}[!t]
@@
 		is a special case of \eqref{iq:horn} with $(I, J, K) \in [N_\mathrm{S}]^3$.
-		The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
-However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
+		The minimum\footnote{One may think to take the maximum of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
+However, this is infeasible since the singular values will be reordered.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
 		On the other hand, the set of lower bounds
@@
 \begin{section}{Acknowledgement}
-	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct some technical errors.
+	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct many technical errors.
 \end{section}

### 2025-02-13 src/pc_power_sx.m

@@ -38,7 +38,7 @@ if flag.direct
 else
 	channel.power.aggregate.explicit = mean(channel.power.aggregate.explicit, ndims(channel.power.aggregate.explicit));
 end
-% save('data/pc_power_sx.mat');
+save('data/pc_power_sx.mat');
 
 figure('Name', 'Channel Power vs RIS Configuration', 'Position', [0, 0, 500, 400]);
 if flag.direct
@@ -80,8 +80,8 @@ hold off; grid on; box on;
 set(gca, 'XLim', [1, max(number.bond)], 'XTick', 1 : max(number.bond), 'XTickLabel', '$2^' + string(vec(0 : max(number.bond) - 1)) + '$', 'YLim', [channel.power.direct * 0.95, max(vec(channel.power.aggregate.iterative)) * 1.05]);
 xlabel('RIS Group Size');
 ylabel('Channel Power [W]');
-% savefig('plots/pc_power_sx.fig');
-% matlab2tikz('../assets/simulation/pc_power_sx.tex', 'width', '8cm', 'height', '6cm');
+savefig('plots/pc_power_sx.fig');
+matlab2tikz('../assets/simulation/pc_power_sx.tex', 'width', '8cm', 'height', '6cm');
 
 
 function [Theta, H] = scatter_power_max_explicit(H_f, H_b)

### 2025-02-13 src/pc_rate_csi.m

@@ -1,0 +1,65 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, 128, 4);
+[transmit.power, receive.noise] = deal(db2pow(-20 : 5 : 20), db2pow(-75));
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[reflect.bond, channel.uncertainty] = deal([1, reflect.antenna], [1e-2, 1e-1, 5e-1]);
+[number.bond, number.power, number.uncertainty, number.realization] = deal(length(reflect.bond), length(transmit.power), length(channel.uncertainty), 2);
+
+for r = 1 : number.realization
+	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	% * No RIS
+	for p = 1 : number.power
+		transmit.beamformer = precoder_rate(channel.direct, transmit.power(p), receive.noise);
+		receive.rate.direct(p, r) = rate_mimo(channel.direct, transmit.beamformer, receive.noise);
+	end
+	% * Have RIS
+	channel.forward.actual = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna);
+	channel.backward.actual = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
+	for u = 1 : number.uncertainty
+		channel.forward.estimate = estimation_effect(channel.forward.actual, channel.uncertainty(u));
+		channel.backward.estimate = estimation_effect(channel.backward.actual, channel.uncertainty(u));
+		clear scatter_rate;
+		for b = 1 : number.bond
+			for p = 1 : number.power
+				transmit.beamformer = precoder_rate(channel.direct, transmit.power(p), receive.noise);
+				[iter.converge, iter.tolerance, iter.counter, iter.rate] = deal(false, 1e-4, 0, rate_mimo(channel.direct, transmit.beamformer, receive.noise));
+				while ~iter.converge
+					[reflect.beamformer, channel.aggregate.estimate] = scatter_rate(channel.direct, channel.forward.estimate, channel.backward.estimate, transmit.beamformer, reflect.bond(b), receive.noise);
[…]

### 2025-02-13 src/pc_singular_csi.m

@@ -1,0 +1,93 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 64, 2);
+[channel.rank, reflect.bond, channel.uncertainty] = deal(min(transmit.antenna, receive.antenna), [1, reflect.antenna], [1e-2, 1e-1, 5e-1]);
+assert(channel.rank == 2, 'The plot function is only for 2-sv case.');
+[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
+[channel.weight(1, :, 1), channel.weight(2, :, 1)] = pol2cart(pi / 4 : pi / 64 : pi * 3 / 4, 1);
+[channel.weight(1, :, 2), channel.weight(2, :, 2)] = pol2cart(pi / 4 : -pi / 64 : -pi / 4, 1);
+[channel.weight(1, :, 3), channel.weight(2, :, 3)] = pol2cart(5 * pi / 4 : pi / 64 : pi * 7 / 4, 1);
+[channel.weight(1, :, 4), channel.weight(2, :, 4)] = pol2cart(5 * pi / 4 : -pi / 64 : pi * 3 / 4, 1);
+[number.weight, number.case, number.bond, number.uncertainty, number.realization] = deal(size(channel.weight, 2), size(channel.weight, 3), 2, length(channel.uncertainty), 2);
+
+for r = 1 : number.realization
+	channel.direct = sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
+	% * No RIS
+	channel.singular.direct(:, r) = svd(channel.direct);
+	% * Have RIS
+	channel.forward.actual = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna);
+	channel.backward.actual = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
+	for u = 1 : number.uncertainty
+		channel.forward.estimate = estimation_effect(channel.forward.actual, channel.uncertainty(u));
+		channel.backward.estimate = estimation_effect(channel.backward.actual, channel.uncertainty(u));
+		for b = 1 : number.bond
+			for c = 1 : number.case
+				clear scatter_singular;
+				for w = 1 : number.weight
[…]

### 2025-02-13 src/pc_singular_pareto.m

@@ -1,65 +1,65 @@
-clc; clear; close; setup;
-
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 32, 2);
-[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), unique([1, 4, 16, reflect.antenna]));
-[transmit.power, receive.noise] = deal(db2pow([-20, 20]), db2pow(-75));
-[channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-assert(channel.rank == 2, 'The plot function is only for 2-sv case.');
-[channel.weight(1, :, 1), channel.weight(2, :, 1)] = pol2cart(pi / 4 : pi / 256 : pi * 3 / 4, 1);
-[channel.weight(1, :, 2), channel.weight(2, :, 2)] = pol2cart(pi / 4 : -pi / 256 : -pi / 4, 1);
-[channel.weight(1, :, 3), channel.weight(2, :, 3)] = pol2cart(5 * pi / 4 : pi / 256 : pi * 7 / 4, 1);
-[channel.weight(1, :, 4), channel.weight(2, :, 4)] = pol2cart(5 * pi / 4 : -pi / 256 : pi * 3 / 4, 1);
-[number.weight, number.case, number.bond, number.power, number.realization, flag.direct] = deal(size(channel.weight, 2), size(channel.weight, 3), length(reflect.bond), length(transmit.power), 1, false);
-
-for r = 1 : number.realization
-	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna) + eps;
-	channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna);
-	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
-	channel.singular.direct(:, r) = svd(channel.direct);
-	for b = 1 : number.bond
-		% * Pareto frontier
-		for c = 1 : number.case
-			for w = 1 : number.weight
-				clear scatter_singular;
-				[~, channel.aggregate] = scatter_singular(channel.direct, channel.forward, channel.backward, channel.weight(:, w, c), reflect.bond(b));
-				channel.singular.aggregate(:, w, c, b, r) = svd(channel.aggregate);
-				for p = 1 : number.power
[…]

### 2025-02-25 review/response_241203.tex
:construction: Merge footnotes

@@
 		Our contribution is an extension to block-unitary cases with parallel or unified updates that accelerate the design of group-connected \gls{bd}-\gls{ris}.
-		The claim of ``universal optimization framework'' and the non-geodesic \gls{rcg} method have been remove and we have completely reworked the optimization part to reflect the particular contributions (channel shaping).
+		The claim of ``universal optimization framework'' and the non-geodesic \gls{rcg} method have been removed and we have completely reworked the optimization part to reflect the particular contributions (channel shaping).
 		The content is too long to fit here and we kindly ask the reviewer to refer to Section \ref{sc:shaping_numerical} of the revised manuscript for details.
@@
 		We believe itself could serve as a metric for measuring the \gls{mimo} channel shaping capability of different \gls{ris}.
-		We have added a detailed explanation in the revised manuscript and the answer comprises two parts below.
+		We have added a detailed explanation in the revised manuscript and the answer which we copy in the two boxes below.
 
@@
 		We would like to argue that, while Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are standard mathematical results, it is Proposition \ref{pp:nd} that allows one to recast the channel shaping question as a well-studied linear algebra problem and enable those.
-		In the revised manuscript, we have also added
+		In the revised manuscript, we have emphasized above and have also added
 		\begin{itemize}

### 2025-02-25 manuscript/appendix.tex
:construction: Merge footnotes

--- 2025-02-11 manuscript/main.tex
@@
 \input{preamble}
+\externaldocument{main}
 
-\title{MIMO Channel Shaping and Rate Maximization\\Using Beyond Diagonal RIS}
-\author{
-	\IEEEauthorblockN{
-		Yang Zhao, \IEEEmembership{Member, IEEE,}
-		Hongyu Li, \IEEEmembership{Graduate Student Member, IEEE,}\\
-		Massimo Franceschetti, \IEEEmembership{Fellow, IEEE,}
-		and Bruno Clerckx, \IEEEmembership{Fellow, IEEE}
+\makeatletter
+\def\bibcite#1#2{%
+	\@newl@bel{b}{#1\@extra@binfo}{%
+		\hyper@@link[cite]{}{cite.#1\@extra@b@citeb}{\romannumeral 0#2}%
+	}%
 }
-	\thanks{
-		Yang Zhao is with the School of Electronic and Electrical Engineering, University of Leeds, LS2 9JT, U.K. (e-mail: \href{mailto:yang.zhao@ieee.org}{yang.zhao@ieee.org}.)
-
-		Hongyu Li and Bruno Clerckx are with the Department of Electrical and Electronic Engineering, Imperial College London, SW7 2AZ, U.K.
-
-		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California, San Diego, La Jolla CA 92093, USA.
-
-		This work has been partially supported by UKRI grant EP/Y004086/1, EP/X040569/1, EP/Y037197/1, EP/X04047X/1, EP/Y037243/1.
-	}
-}
+\renewcommand*{\@biblabel}[1]{[\romannumeral 0#1]}
+\renewcommand{\theequation}{\roman{equation}}
+\makeatother
 
 \begin{document}
-
-\maketitle
-
-\begin{abstract}
-	This paper investigates the limits to which a passive \gls{ris} can shape a point-to-point \gls{mimo} in terms of singular values
-	% and power gain
-	and thus improve the rate performance.
-	% redistribute the singular values of a point-to-point \gls{mimo} channel for providing power and rate gains.
-	We depart from the conventional \gls{ris} with \gls{d} phase shift matrix and adopt a \gls{bd} model interconnecting elements for wave amplitude and phase manipulation.
-	This translates to superior branch matching and mode alignment capabilities in \gls{mimo}.
-	% featuring group-wise connections for enhanced branch matching and mode alignment capabilities.
-	Specifically, analytical singular values bounds are derived under popular \gls{ris} deployment scenarios
-	% the scenario of rank-deficient backward/forward channel or negligible direct channel, which
-	to showcase the shaping advantages of \gls{bd}-\gls{ris} in terms of dynamic range and \gls{dof}.
-	A numerical optimization method is then proposed for a broader range of shaping problems and invoked to characterize the entire achievable singular value region.
-	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
-	Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate.
-	Those benefits become more pronounced when the number of \gls{ris} elements or \gls{mimo} dimensions increase.
-	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at much lower transmit power than \gls{d}-\gls{ris} thanks to its singular value shaping proficiency.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	MIMO, RIS, channel shaping, rate maximization, singular value bounds, manifold optimization.
-\end{IEEEkeywords}
-
-\glsresetall
-
-\begin{section}{Introduction}
-	% \begin{subsection}{Background}
-		Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
-		This is empowered by recent advances in \gls{ris}, a programmable passive planar surface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
-		A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
-		It enables low-noise full-duplex operation, featuring better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo} systems.
-		One popular \gls{ris} research direction is \emph{joint passive and active beamforming} design with transceivers to enhance a specific performance measure, which has attracted significant interests in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
-		While passive beamforming at \gls{ris} suffers attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
-		Another \gls{ris} application is \emph{information modulation} by periodically switching its reflection pattern within the channel coherence time.
-		This creates a free-ride message stream with dual benefits: integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022}, or serving as individual source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
-		Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment, for example, compensate for the Doppler effect \cite{Basar2021}, flatten frequency-selective channels \cite{Arslan2022}, improve \gls{mimo} channel rank \cite{Ozdogan2020a}, and artificially diversify channel over time for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
-		This helps to decouple joint beamforming problems into a channel shaping stage and a conventional transceiver design stage, providing a versatile solution for various wireless applications.
-	% \end{subsection}
-
-	% \begin{subsection}{Related Works}
-		At a specific resource block, channel shaping metrics can be classified into two categories.
-		\begin{itemize}
-			\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
-Those are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to minor perturbations of the channel matrix.
-			\item \emph{Power:} The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} in point-to-point channels and leakage interference \cite{Santamaria2023a} in interference channels.
-Those second-order metrics are less informative in \gls{mimo} but easier to analyze and optimize.
-		\end{itemize}
-
-		Although above works offered inspiring glimpses into the channel shaping potential of passive \gls{ris}, none attempted to disclose the entire singular value region.
-		Most relevant literature \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} have also been limited to a \gls{d}-\gls{ris} model where each element is connected to a dedicated impedance and disconnected from others.
-		As such, wave impinging on one element is entirely scattered by the same element.
-		This simple architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal.
-		The idea was soon generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}.
-		This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
-		It can thus manipulate both amplitude and phase of the scattered wave while remaining passive.
-		Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures by graph theory \cite{Nerini2024}.
-		\gls{bd}-\gls{ris} can also function in
-		% hybrid transmitting-and-reflecting mode \cite{Li2023b} and
-		multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
-		Practical challenges such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a} have also been studied in recent literature.
-		Its beamforming effectiveness over \gls{d}-\gls{ris} and energy efficiency over active \gls{ris} and relay systems have been proved in \gls{siso} and \gls{miso} systems \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c,Soleymani2024}.
-		However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
-		The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a fully-connected \gls{bd}-\gls{ris}-aided \gls{mimo} system where the direct channel is negligible.
-		A transmitter-side \gls{bd}-\gls{ris} was introduced to
-		massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, which again assumed negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
-		Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal.
-	% \end{subsection}
-
-	% \begin{subsection}{Contributions}
-		\label{sc:contributions}
-		This paper is motivated by a fundamental question:
-		\emph{What is the channel shaping capability (in terms of singular values and their functions) of a passive \gls{ris} in \gls{mimo} channels?}
-		Unlike existing works that focus on specific metrics or scenarios, we seek a general understanding of \gls{ris} in manipulating the wireless environment to provide insights for various wireless applications.
-		% We aim for a comprehensive answer via analysis and optimization.
-		The contributions are summarized below.
-
-		First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping potential as branch matching and mode alignment.
-		Branch matching refers to pairing and combining the branches (i.e., entries) of backward and forward channels associated with each \gls{bd}-\gls{ris} group.
-		Mode alignment refers to aligning and ordering the modes (i.e., singular vectors) of indirect channels with those of direct channel.
-		The former origins uniquely from the off-diagonal entries of the scattering matrix of \gls{bd}-\gls{ris}.
-
-		Second, we provide an analytical answer to the shaping question under specific channel conditions.
-		It is shown that \gls{bd}-\gls{ris} may achieve a larger or smaller communication \gls{dof} than \gls{d}-\gls{ris}.
-		When the backward or forward channel is rank-deficient, we derive asymptotic bounds of individual singular values applying to \gls{d}- and \gls{bd}-\gls{ris}.
-		When the direct channel is negligible, we recast the shaping question for fully-connected \gls{bd}-\gls{ris} as a well-studied linear algebra question and provide tight bounds (with closed-form \gls{ris} expressions) on channel singular values, power gain, and capacity.
-		% The corresponding \gls{ris} scattering matrices are also derived in closed form.
-		% The results are insightful for understanding the shaping advantages of \gls{bd}-\gls{ris} in \gls{mimo} channels.
-		These results help to understand the fundamental limits of channel shaping and serve as a foundation for advanced \gls{ris} designs.
-
-		% guide the design and optimization of future wireless networks
-
-		Third, we provide a numerical answer to the shaping question by exploiting a geodesic \gls{rcg} method to optimize the \gls{bd}-\gls{ris} for a broad class of singular value functions.
-		It compares favorably to legacy \gls{ris} designs in that the updates are performed multiplicatively along the shortest paths on the manifold for accelerated convergence.
-		The method is then invoked in a Pareto problem to reveal the entire singular value region, which generalizes most relevant metrics and provides an intuitive shaping benchmark.
-
-		Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
-		The former iteratively updates the passive beamforming by geodesic \gls{rcg} and the active beamforming by eigenmode transmission, until convergence.
-		The latter shapes the channel with \gls{ris} for maximum power gain and then performs conventional precoding.
-		% Closed-form solutions are derived for the power gain maximization subproblem in different scenarios.
-		% Interestingly, the rate deficit from the low-complexity design diminishes as the \gls{bd}-\gls{ris} evolves towards fully-connected.
-		% We also extend both approaches to \gls{wsr} maximization in \gls{mimo} interference channels where the low-complexity design aims for minimum leakage interference instead.
-
-		Fifth, we conduct extensive simulations to validate the analytical bounds and numerical methods.
-		It is concluded that:
-		\begin{itemize}
-			\item \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate;
-			\item The shaping advantages of \gls{bd}-\gls{ris} increase with the number of scattering elements and \gls{mimo} dimensions;
-			\item \gls{bd}-\gls{ris} can activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at low transmit power thanks to its singular value shaping proficiency;
-			\item The rate gap between the optimal and low-complexity beamforming designs diminishes as the \gls{ris} evolves from \gls{d} to fully-connected \gls{bd};
-			\item The additional optimization cost of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is affordable and the geodesic \gls{rcg} method is efficient on large-scale problems;
-			\item All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry with reasonable performance cost.
-		\end{itemize}
-	% \end{subsection}
-
-	\emph{Notation:}
-	Italic, bold lower-case, and bold upper-case letters indicate scalars, vectors and matrices, respectively.
-	$\jmath$ denotes the imaginary unit.
-	% $\mathbb{C}$ represents the set of complex numbers.
-	$\mathbb{H}^{n \times n}$, $\mathbb{H}_+^{n \times n}$, and $\mathbb{U}^{n \times n}$ denote the set of $n \times n$ Hermitian, positive semi-definite, and unitary matrices, respectively.
-	% $\mathbf{0}$ and $\mathbf{I}$ are the all-zero and identity matrices with appropriate size, respectively.
-	$\Re\{\cdot\}$ takes the real part of a complex number.
-	% $\tr(\cdot)$ and $\det(\cdot)$ evaluate the trace and determinant of a square matrix, respectively.
-	$\diag(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
-	$\sv(\cdot)$, $\ran(\cdot)$, and $\ker(\cdot)$ evaluate the singular values (in descending order), column space (range), and kernel of a matrix, respectively.
-	% $\sv(\cdot)$ extracts the singular values of a matrix as a non-ascending vector.
-	% $\card(\cdot)$ returns the cardinality of a set.
-	$\conv(\cdot)$ returns the convex hull of arguments.
-	$\mathrm{vec}(\cdot)$ stacks the columns of a matrix sequentially into a vector.
-	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
-	$\sigma_n(\cdot)$ and $\lambda_n(\cdot)$ are the $n$-th largest singular value and eigenvalue, respectively.
-	% $\boldsymbol{\sigma}(\cdot)$ and $\boldsymbol{\lambda}(\cdot)$ are the corresponding vectors.
-	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^\dagger$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), Moore-Penrose inverse, and stationary point, respectively.
-	$[N]$ is a shortcut for $\{1,2,\ldots,N\}$.
-	$(\cdot)_{[x:y]}$ is a shortcut for $(\cdot)_x,(\cdot)_{x+1},\ldots,(\cdot)_y$.
-	$\odot$ denotes the element-wise (Hadamard) product.
-	$\mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
-	$\sim$ means ``distributed as''.
-\end{section}
-
-\begin{section}{System Model}
-	% \begin{subsection}{BD-RIS}
-		The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-		Apparently $N_\mathrm{S} = \sum_{g=1}^G N_g$.
-		Without loss of generality we assume equal size for all groups $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$ and no mutual coupling between elements.
-		For asymmetric \gls{bd}-\gls{ris}, the overall scattering matrix is block-diagonal with unitary blocks\footnote{We assume asymmetric network by default to establish a benchmark for passive \gls{ris}.
-Some symmetric solutions (i.e., $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$) will be discussed and their performance will be evaluated in Section~\ref{sc:simulation}.}
-		\begin{equation}
-			\label{eq:ris}
-			\mathbf{\Theta} = \diag(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
-		\end{equation}
-		where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th diagonal block modeling the response of group $g$.
-		It is noteworthy that \gls{d}-\gls{ris} is an extreme case of \eqref{eq:ris} with group size $L=1$, that is, each element is an individual.
-		Some viable architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
-3]{Shen2020a}, \cite[Fig.
-5]{Li2023c}, \cite[Fig.
-2]{Nerini2024} where the array geometry and circuit topology are modeled in $\mathbf{\Theta}$.
-	% \end{subsection}
-
-	% \begin{subsection}{MIMO Point-to-Point Channel}
-		Consider a \gls{bd}-\gls{ris} aided \gls{mimo} \gls{pc} with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
-		This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$.
-		Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (i.e., transmitter-receiver), backward (i.e., \gls{ris}-receiver), and forward (i.e., transmitter-\gls{ris}) channels, respectively.
-		The equivalent channel depends on the \gls{bd}-\gls{ris} scattering matrix
-		\begin{equation}
-			\label{eq:channel}
-			\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
-			%  \triangleq \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
-		\end{equation}
-		where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels associated with group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
-		% , and $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ is the indirect channel via group $g$.
-		Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
-		\begin{equation}
-			\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{X}_g \mathbf{R}_g^\mathsf{H},
-		\end{equation}
-		where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary matrices and $\mathbf{X}_g \in \mathbb{R}^{L \times L}$ is a permutation matrix.
-		Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via group $g$ and $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
-		The equivalent channel is thus
-		\begin{equation}
-			\label{eq:channel_svd}
-			\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{X}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
-		\end{equation}
-
-		\begin{remark}
-			In \eqref{eq:channel_svd}, the \gls{bd}-\gls{ris} performs a blockwise unitary transformation to combine the backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
-			These two attributes are refined as:
-			\begin{itemize}
-				\item \emph{Branch matching:} It refers to pairing and combining the branches (i.e., entries) of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ through $\mathbf{\Theta}_g$.
-				\item \emph{Mode alignment:} It refers to aligning and ordering the modes (i.e., singular vectors) of $\{\mathbf{H}_g\}_{g \in [G]}$ with those of $\mathbf{H}_\mathrm{D}$ through $\{\mathbf{\Theta}_g\}_{g \in [G]}$.
-			\end{itemize}
-		\end{remark}
-
-		\begin{example}[\gls{siso} channel gain maximization]
-			\label{eg:siso}
-			Denote the direct, backward, forward channels as $h_\mathrm{D}$, $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$, and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, respectively.
-			In this case, mode alignment boils down to phase matching and the optimal \gls{bd}-\gls{ris} structure is
-			% any $L \in [N_\mathrm{S}]$, including \gls{d}-\gls{ris}, suffices for perfect mode alignment using
-			\begin{equation}
-				\mathbf{\Theta}_{\textnormal{P-max},g}^\textnormal{SISO} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H}, \quad \forall g,
-			\end{equation}
-			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B/F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of kernels of $\mathbf{h}_{\mathrm{B/F},g}$.
-			Apparently, any group size $L$ (including \gls{d}-\gls{ris}) suffices for perfect phase matching.
-			The resulting maximum channel gain is a function of $L$
-			\begin{equation}
-				\ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
-			\end{equation}
-			where $h_{\mathrm{B/F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B/F},g}$, and $\pi_{\mathrm{B/F},g}$ are permutations of $[L]$ sorting their magnitude in similar orders.
-			That is, the maximum \gls{siso} channel gain is attained when each \gls{bd}-\gls{ris} group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
-			A larger $L$ provides more flexible branch matching and thus higher channel gain.
-		\end{example}
-
-		Example~\ref{eg:siso} clarifies the difference between branch matching and mode alignment and show their impacts on channel shaping.
-		When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching improves since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$.
-On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment intensifies since each element can only apply a scalar phase shift to the indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ modes.
-	% \end{subsection}
-
-	% \begin{subsection}{MIMO Interference Channel}
-		% \label{sc:mimo_ic}
-		% We also consider a \gls{bd}-\gls{ris} aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
-		% This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
-		% Let $\mathbf{H}_\mathrm{D}^{(kj)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{(j)} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
-		% Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
-		% The equivalent channel from transmitter $j$ to receiver $k$ is
-		% \begin{equation}
-		% 	\label{eq:channel_interference}
-		% 	\mathbf{H}^{(kj)} = \mathbf{H}_\mathrm{D}^{(kj)} {+} \mathbf{H}_\mathrm{B}^{(k)} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{(j)} = \mathbf{H}_\mathrm{D}^{(kj)} {+} \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)},
-		% \end{equation}
-		% where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B}}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F}}^{(j)}$, respectively.
-	% \end{subsection}
-\end{section}
-
-\begin{section}{Channel Shaping}
-	In this section, we first provide an example demonstrating the \gls{mimo} channel shaping advantages of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds related to channel singular values under specific channel conditions, and provide closed-form \gls{bd}-\gls{ris} solution for several cases of interest.
-	Finally, we propose a numerical method to optimize the \gls{bd}-\gls{ris} for a special class of singular value functions under general channel conditions.
-
-	\begin{example}[$2 \times 2 \times 2$ shaping]
-		\label{eg:shaping_potential}
-		Here \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} can be modeled by 2 and 4 independent angular parameters, respectively:
-		\begin{equation*}
-			\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}), \quad
-			\mathbf{\Theta}_\mathrm{BD} = e^{\jmath \phi} \begin{bmatrix}
-				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
-				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
-			\end{bmatrix},
-		\end{equation*}
-		We restrict the discussion to a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
-		The singular value shaping capabilities of $\mathbf{\Theta}_\mathrm{D}$ and $\mathbf{\Theta}_\mathrm{BD}$ can thus be compared visually over 2 tunable parameters.
-		\begin{figure}
-			\centering
-			\includegraphics[width=0.7\columnwidth]{../assets/simulation/pc_singular_trend.eps}
-			\caption{$2 \times 2 \times 2$ singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is negligible.
-			% $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
-			% Their maximum and minimum are marked explicitly on the plot.
-			The maximum and minimum of both singular values are marked explicitly on the plot.}
-			\label{fg:shaping_potential}
-		\end{figure}
-		With an exhaustive grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$, Fig.~\ref{fg:shaping_potential} shows the achievable singular values of a specific channel realization
-		\begin{equation*}
-			\begin{split}
-				\mathbf{H}_\mathrm{B} & =
-				\begin{bmatrix}
-					-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
-					0.4131 + 0.2651 \jmath  & -0.1960 + 0.4650 \jmath
-				\end{bmatrix},
-				\\
-				\mathbf{H}_\mathrm{F} & =
-				\begin{bmatrix}
-					-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
-					0.0196 + 0.4011 \jmath  & -0.3170 - 0.2303 \jmath
-				\end{bmatrix}.
-			\end{split}
-		\end{equation*}
-		In this example, both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris}.
-		It is noteworthy that the former requires 2 circuit components and the latter requires 3.
-	\end{example}
-
-	Example~\ref{eg:shaping_potential} suggests that the physical interconnection of \gls{ris} elements, even if using symmetric circuit components, can create a ``cooperation effect'' that significantly enhances the dynamic range of channel singular values.
-	This motivates the analytical and numerical channel shaping studies in Section~\ref{sc:shaping_analytical} and \ref{sc:shaping_numerical}, respectively.
-
-	\begin{subsection}{Analytical Shaping Bounds}
-		\label{sc:shaping_analytical}
-		The main results of this subsection are presented in the following Propositions and Corollaries.
-		\begin{proposition}[Degrees of freedom]
-			\label{pp:dof}
-			\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof}\footnote{Here communication \gls{dof} refers to the maximum number of independent streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\mathrm{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.
-The concept is closely related to radar \gls{dof} which refers to the number of independent measurements.} than \gls{d}-\gls{ris}.
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:dof}.
-		\end{proof}
-
-		While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the ability to reduce the \gls{dof} can be exploited to orthogonalize channels and align interference in multi-user scenarios.
-		% reducing the \gls{dof} does not necessarily degrade the rate at finite \gls{snr}.
-		% , it does not necessarily imply a higher rate at finite \gls{snr}.
-		% It is worth mentioning that a larger \gls{dof} implies more parallel streams or less interference, which is beneficial for high-rate communication.
-
-		\begin{example}[\gls{dof} of $4 \times 4 \times 4$ shaping]
-			\label{eg:dof}
-			Consider a $4 \times 4 \times 4$ shaping with $\mathbf{H}_\mathrm{D} = \mathbf{0}$ and
-			\begin{equation*}
-				\mathbf{H}_\mathrm{B} =
-				\begin{bmatrix}
-					1 & 1 & 0 & 0 \\
-					0 & 0 & 0 & 0 \\
-					0 & 0 & 1 & 0 \\
-					0 & 0 & 0 & 0
-				\end{bmatrix}, \quad
-				\mathbf{H}_\mathrm{F} =
-				\begin{bmatrix}
-					1 & 0 & 0 & 0 \\
-					0 & 1 & 0 & 0 \\
-					0 & 0 & 0 & 0 \\
-					0 & 0 & 0 & 0
-				\end{bmatrix}.
-			\end{equation*}
-			Evidently, any \gls{d}-\gls{ris} $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}, e^{\jmath \theta_3}, e^{\jmath \theta_4})$ results in
-			\begin{equation*}
-				\mathbf{H} =
-				\begin{bmatrix}
-					e^{\jmath \theta_1} & e^{\jmath \theta_2} & 0 & 0 \\
-					0 & 0 & 0 & 0 \\
-					0 & 0 & 0 & 0 \\
-					0 & 0 & 0 & 0
-				\end{bmatrix}
-			\end{equation*}
-			and achieves a \gls{dof} of 1.
-			On the other hand, as instructed by \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min}, fully-connected \gls{bd}-\gls{ris} $\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
-			\begin{bsmallmatrix}
-				0 & \frac{\sqrt{2}}{2} & 0 & -\frac{\sqrt{2}}{2} \\
-				0 & \frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} \\
-				-1 & 0 & 0 & 0 \\
-				0 & 0 & 1 & 0
-			\end{bsmallmatrix}$ and $\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} =
-			\begin{bsmallmatrix}
-				-\frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} & 0\\
-				\frac{\sqrt{2}}{2} & 0 & \frac{\sqrt{2}}{2} & 0 \\
-				0 & 0 & 0 & 1 \\
-				0 & -1 & 0 & 0
-			\end{bsmallmatrix}$
-			result in
-			\begin{equation*}
-				\mathbf{H} =
-				\begin{bmatrix}
-					0 & \sqrt{2} & 0 & 0 \\
-					0 & 0 & 0 & 0 \\
-					-1 & 0 & 0 & 0 \\
-					0 & 0 & 0 & 0
-				\end{bmatrix}, \quad
-				\mathbf{H} = \mathbf{0},
-			\end{equation*}
-			and achieve \gls{dof} of 2 and 0, respectively.
-		\end{example}
-
-		Proposition \ref{pp:dof} and Example \ref{eg:dof} suggest that we can expect more parallel streams or less interference when shaping the channel with \gls{bd}-\gls{ris}.
-		We now take a step further to examine the limits of redistributing channel singular values under specific channel conditions.
-
-		\begin{proposition}[Rank-deficient channel]
-			\label{pp:rd}
-			If the minimum rank of backward and forward channels is $k$ ($k \le N$),
-			then for \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
-			\begin{subequations}
-				\label{iq:sv_rd}
-				\begin{align}
-					\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_rd_max}          \\
-					\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_rd_min}
-				\end{align}
-			\end{subequations}
-			where $\mathbf{T}$ is arbitrary auxiliary matrix satisfying
-			\begin{equation}
-				\label{eq:auxiliary_rd}
-				\mathbf{T} \mathbf{T}^\mathsf{H} =
-				\begin{cases}
-					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \rank(\mathbf{H}_\mathrm{F}) = k, \\
-					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \rank(\mathbf{H}_\mathrm{B}) = k,
-				\end{cases}
-			\end{equation}
-			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are any right and left singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:rank_deficient}.
-		\end{proof}
-
-		Inequality \eqref{iq:sv_rd_max} states that
-		if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are at least rank $k$, then
-		with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of sufficiently large $N_\mathrm{S}$,
-		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
-		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected in all cases.
-This constraint is omitted in context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
-		Proposition \ref{pp:rd} complements Proposition \ref{pp:dof} and Example \ref{eg:dof} by quantifying the dynamic range of extreme singular values.
-		A special case is Corollary \ref{co:los} for \gls{los} channel\footnote{A similar eigenvalue result has been derived for \gls{d}-\gls{ris} only \cite{Semmler2023}.}.
-
-		\begin{corollary}[\gls{los} channel]
-			\label{co:los}
-			If at least one of backward and forward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
-			That is,
-			\begin{equation}
-				\label{iq:sv_los}
-				\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
-			\end{equation}
-		\end{corollary}
-
-		\begin{proof}
-			This is a direct result of \eqref{iq:sv_rd} with $k = 1$.
-		\end{proof}
-
-		We emphasize that Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
-		Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible\footnote{Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
-This can result from a very large number of \gls{ris} elements (as discussed in Proposition~\ref{pp:rd}) or physical obstacles in the propagation path (as discussed in Proposition~\ref{pp:nd}).}.
-		For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes, and we will later show by simulation that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
-		Proposition \ref{pp:rd} provides a reference on the selection of $N_\mathrm{S}$ in low-multipath application scenarios.
-		Next, we shift the focus to another popular \gls{ris} deployment scenario where the direct channel is blocked.
-
-		\begin{proposition}[Negligible direct channel]
-			\label{pp:nd}
-			If the direct channel is negligible, then a fully-connected \gls{bd}-\gls{ris} can manipulate the channel singular values up to
-			\begin{equation}
-				\sv(\mathbf{H}) = \sv(\mathbf{BF}),
-			\end{equation}
-			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with $\sv(\mathbf{B})=\sv(\mathbf{H}_\mathrm{B})$ and $\sv(\mathbf{F})=\sv(\mathbf{H}_\mathrm{F})$.
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd}.
-		\end{proof}
-
-		Proposition \ref{pp:nd} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
-		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
-		Its importance lies in the fact that our initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
-		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
-		The results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
-
-		\begin{corollary}[Product of subset of singular values]
-			\label{co:nd_sv_prod_subset}
-			If the direct channel is negligible,
-			then the product of subset of singular values of $\mathbf{H}$ is bounded from above by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
-			\begin{equation}
-				\label{iq:horn}
-				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
-			\end{equation}
-			for all admissible triples $(I, J, K) \in T_r^{\bar{N}}$ with $r < \bar{N}$, where
-			\begin{equation*}
-				\begin{split}
-					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \bigm\vert & \forall p < r, \ \forall (F, G, H) \in T_p^r,                                              \\
-																							& \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + \frac{p(p+1)}{2} \Bigr\},
-				\end{split}
-			\end{equation*}
-			\begin{equation*}
-				U_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \subseteq [\bar{N}]^3 \bigm\vert \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + \frac{r(r+1)}{2}\Bigr\}.
-			\end{equation*}
-		\end{corollary}
-
-		\begin{proof}
-			Please refer to \cite[Theorem~8]{Fulton2000}.
-		\end{proof}
-
-		Inequality \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:nd}.
-		However, the number of admissible triples increases exponentially\footnote{For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.} with $N_\mathrm{S}$ despite some resulting bounds can be redundant.
-		We will shortly see \eqref{iq:horn} can also induce lower bounds on channel singular values.
-		Those facts render the shaping limit analysis non-trivial for large-scale \gls{ris}-aided \gls{mimo} systems.
-		Below we showcase some useful bounds therein.
-
-		\begin{corollary}[Product of some largest or smallest singular values]
-			\label{co:nd_sv_prod_tail}
-			If the direct channel is negligible,
-			then the product of the first (resp.
-last\footnote{The lower bounds coincide at zero when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).}) $k$ singular values of $\mathbf{H}$ is bounded from above (resp.
-below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
-			\begin{subequations}
-				\begin{align}
-					\prod_{n=1}^k \sigma_n(\mathbf{H})                   & \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:sv_nd_prod_largest}                    \\
-					\prod_{n=\bar{N}}^{\mathclap{\bar{N}-k+1}} \sigma_n(\mathbf{H}) & \ge \prod_{n=\bar{N}}^{\mathclap{\bar{N}-k+1}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}).
-\label{iq:sv_nd_prod_smallest}
-				\end{align}
-			\end{subequations}
-		\end{corollary}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd_sv_prod_tail}.
-		\end{proof}
-
-		\begin{corollary}[Individual singular value]
-			\label{co:nd_sv_indl}
-			If the direct channel is negligible,
-			then the $n$-th channel singular value can be manipulated up to
-			\begin{equation}
-				\label{iq:sv_nd_indl}
-				\max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
-			\end{equation}
-			where $(i, j) \in [N_\mathrm{S}]^2$.
-			The upper and lower bounds are attained respectively at
-			\begin{subequations}
-				\label{eq:ris_nd_sv_indl}
-				\begin{align}
-					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_sv_indl_max} \\
-					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_sv_indl_min}
-				\end{align}
-			\end{subequations}
-			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices\footnote{%
-				\label{fn:svd_non_uniqueness}%
-				We highlight the non-uniqueness of $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$.
-When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace.
-Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.} of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-			and $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary permutation matrices of dimension $N_\mathrm{S}$ satisfying:
-			\begin{itemize}
-				\item The $(i, j)$-th entry is $1$, where
-					\begin{subnumcases}{(i, j) =}
-						\ \underset{\mathclap{i+j=n+1}}{\arg\min} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:idx_nd_sv_indl_max} \\
-						\ \underset{\mathclap{i+j=n+N_\mathrm{S}}}{\arg\max} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:idx_nd_sv_indl_min}
-					\end{subnumcases}
-					and ties may be broken arbitrarily;
-				\item After deleting the $i$-th row and $j$-th column, the resulting submatrix $\mathbf{Y}$ is arbitrary permutation matrix of dimension $N_\mathrm{S}-1$ satisfying
-					\begin{subequations}
-						\begin{alignat}{2}
-							\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \ \ \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})            &  & \text{ for } \mathbf{P}, \label{eq:perm_nd_sv_indl_max} \\
-							\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \ \ \max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) &  & \text{ for } \mathbf{Q}, \label{eq:perm_nd_sv_indl_min}
-						\end{alignat}
-					\end{subequations}
-					where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with both $i$-th row and $j$-th column deleted, respectively.
-			\end{itemize}
-		\end{corollary}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd_sv_indl}.
-		\end{proof}
-
-		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value, which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
-		They are derived under different assumptions are not special cases of each other.
-		Importantly, Corollary \ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
-first and last few in Proposition \ref{pp:rd}), applies to fully-connected \gls{bd}-\gls{ris} of arbitrary size, and provides a general solution structure.
-		We emphasize that in \eqref{eq:ris_nd_sv_indl} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of unitary $\mathbf{X}$ defined in \eqref{eq:ris_decompose}.
-		Specially, the extreme channel singular values can be manipulated up to
-		\begin{subequations}
-			\label{iq:sv_nd_extreme}
-			\begin{gather}
-				\max_{\mathclap{i+j=N_\mathrm{S}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_nd_largest} \\
-				\min_{\mathclap{i+j=\bar{N}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\ge} \sigma_{\bar{N}}(\mathbf{H}) {\ge} \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}).
-\label{iq:sv_nd_smallest}
-			\end{gather}
-		\end{subequations}
-		We notice that the right halves in \eqref{iq:sv_nd_largest} and \eqref{iq:sv_nd_smallest} are special cases of \eqref{iq:sv_nd_prod_largest} and \eqref{iq:sv_nd_prod_smallest} when $k=1$.
-
-		\begin{example}[Bounds on $3 \times 3 \times 3$ shaping]
-			\label{eg:shaping_bounds}
-			Consider a $3 \times 3 \times 3$ setup with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} = \diag(3, 2, 1)$, and $\mathbf{H}_\mathrm{F} = \diag(4, 0, 5)$.
-			\begin{itemize}
-				\item \gls{d}-\gls{ris}: It is evident that any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode alignment capability.
-				\item \gls{bd}-\gls{ris}: According to \eqref{iq:sv_nd_indl}, a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values up to
-					\begin{equation*}
-						8 \le \sigma_1(\mathbf{H}) \le 15, \quad 4 \le \sigma_2(\mathbf{H}) \le 10, \quad 0 \le \sigma_3(\mathbf{H}) \le 0.
-					\end{equation*}
-					To attain the upper and lower bounds, $(i,j)$ in \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} takes $(1, 1)$ and $(2, 2)$ when $n=1$, and $(2, 1)$ and $(3, 2)$ when $n=2$, respectively.
-			\end{itemize}
-		\end{example}
-
-		We conclude from Example \ref{eg:shaping_bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
-		However, when the problem of interest is a function of multiple singular values, their individual bounds \eqref{iq:sv_nd_indl} may not be simultaneously tight.
-		Some case studies are presented below.
-
-		\begin{corollary}[Channel power gain]
-			\label{co:nd_power}
-			If the direct channel is negligible, then the channel power gain is bounded from above (resp.
-below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp.
-oppositely), that is,\footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
-This is a looser version of \eqref{iq:power_nd} and cannot take equalities unless the extreme singular values are of multiplicity $N$.}
-			\begin{equation}
-				\label{iq:power_nd}
-				\sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
-			\end{equation}
-			whose upper\footnote{%
-				\label{fn:power_nd_max}%
-				The upper bound \eqref{eq:ris_nd_power_max} is reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.} and lower bounds are attained respectively at
-			\begin{subequations}
-				\label{eq:ris_nd_power}
-				\begin{align}
-					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_power_max}            \\
-					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H} \label{eq:ris_nd_power_min},
-				\end{align}
-			\end{subequations}
-			where $\mathbf{J}$ is the exchange (a.k.a. backward identity) matrix of dimension $N_\mathrm{S}$.
-		\end{corollary}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd_power}.
-		\end{proof}
-
-		We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
-		% TODO relay
-		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the expectation of maximum channel power gain can be numerically evaluated as
-		\begin{equation}
-			\label{eq:power_nd_rayleigh}
-			\begin{split}
-				\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\} = \sum_{n=1}^N
-				& \int_0^\infty x f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x         \\
-				& \times \int_0^\infty y f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(y) d y,
-			\end{split}
-		\end{equation}
-		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(\cdot)$ given by \cite[(51)]{Zanella2009}.
-		\eqref{eq:power_nd_rayleigh} generalizes the \gls{siso} channel power gain aided by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} but a closed-form expression is non-trivial.
-		The next corollary has been derived in \cite{Bartoli2023} independently of Proposition \ref{pp:nd} and we include it here for completeness of results.
-		\begin{corollary}[Channel capacity at general \gls{snr}]
-			\label{co:nd_capacity_snr_general}
-			If the direct channel is negligible, then the \gls{bd}-\gls{ris} aided \gls{mimo} channel capacity is
-			\begin{equation}
-				\label{eq:capacity_nd}
-				C^\textnormal{MIMO-ND} = \sum_{n=1}^N \log \left(1 + \frac{s_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}{\eta}\right),
-			\end{equation}
-			where $\eta$ is the average noise power, $s_n = \mu - \frac{\eta}{\sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}$ is the power allocated to the $n$-th mode obtainable by the water-filling algorithm \cite{Clerckx2013}.
-			The capacity-achieving \gls{bd}-\gls{ris} scattering matrix is
-			\begin{equation}
-				\label{eq:ris_nd_rate_max}
-				\mathbf{\Theta}_\textnormal{R-max}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
-			\end{equation}
-		\end{corollary}
-
-		\begin{proof}
-			Please refer to \cite[Appendix~A]{Bartoli2023}.
-		\end{proof}
-
-		Corollary \ref{co:nd_capacity_snr_general} also suggests that the power- and rate-optimal scattering matrices \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
-		When either condition is not satisfied, active and passive beamforming are coupled and the rate-optimal solution involves alternating optimization.
-		However, the power-optimal \gls{ris} still provides for a low-complexity decoupled solution.
-		The details will be discussed in Section~\ref{sc:rate}.
-
-		\begin{corollary}[Channel capacity at extreme \gls{snr}]
-			\label{co:nd_capacity_snr_extreme}
-			If the direct channel is negligible, then the channel capacity when the \gls{snr} $\rho$ is very low and high are approximately bounded from above by
-			\begin{subequations}
-				\label{iq:capacity_nd_snr_extreme}
-				\begin{align}
-					C_{\rho_\downarrow} & \lessapprox \rho \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \label{iq:capacity_nd_snr_low}                                           \\
-					C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:capacity_nd_snr_high}
-				\end{align}
-			\end{subequations}
-		\end{corollary}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd_capacity}.
-		\end{proof}
-
-		The ergodic counterparts of \eqref{eq:capacity_nd} and \eqref{iq:capacity_nd_snr_extreme} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be evaluated similarly to \eqref{eq:power_nd_rayleigh}.
-		Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
-		Extending the analysis to more general cases (e.g., significant direct channel and arbitrary \gls{bd}-\gls{ris} group size) is non-trivial due to limited branch matching and mode alignment capabilities therein.
-		A numerical solution will be discussed in Section~\ref{sc:shaping_numerical}.
-	\end{subsection}
-
-	\begin{subsection}{Numerical Shaping Solution}
-		\label{sc:shaping_numerical}
-		Consider a special class of channel shaping problem
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{\label{op:shaping}}{\label{ob:shaping}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
-		\end{maxi!}
-		where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
-		Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
-		Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
-		\begin{proposition}
-			\label{pp:shaping}
-			The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
-			\begin{equation}
-				\label{eq:shaping_subdiff}
-				\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
-			\end{equation}
-			where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:shaping}.
-		\end{proof}
-
-		With Proposition \ref{pp:shaping}, one can apply the \emph{relax-then-project} method \cite{Shen2020a,Fang2023} or \emph{non-geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}} \cite{Li2023b,Li2023c,Zhou2023} to solve problem \eqref{op:shaping}.
-		The former solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without guarantee of optimality.
-		The latter generalizes the conjugate gradient methods to Riemannian manifolds and updates the solution by addition and retraction, which constitutes a zigzag path departing from and returning to the manifold.
-		Next, we introduce a group-wise \emph{geodesic \gls{rcg}} method modified from \cite{Abrudan2008,Abrudan2009} that performs multiplicative updates along the geodesics on the Stiefel manifold for faster convergence.
-		\begin{remark}
-			The group-wise geodesic \gls{rcg} method is applicable to a wide range of \gls{bd}-\gls{ris} designs where the objective $f$ is smooth or convex non-smooth and the only constraint is block unitary \eqref{cn:shaping_unitary}.
-		\end{remark}
-		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below:
-		\begin{enumerate}[label=(\roman*)]
-			\item \emph{Compute the Euclidean (sub-)gradient at $\mathbf{\Theta}_g^{(r)}$:} The (sub-)gradient of $f$ with respect to $\mathbf{\Theta}_g$ in the Euclidean space is
-			% \cite[(A.3.6)]{Fischer2005}
-				\begin{equation}
-					\label{eq:gradient_eucl}
-					\nabla_{\mathrm{E},g}^{(r)} = 2 \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
-				\end{equation}
-			\item \emph{Translate to the Riemannian (sub-)gradient at $\mathbf{\Theta}_g^{(r)}$:} At point $\mathbf{\Theta}_g^{(r)}$, the Riemannian (sub-)gradient gives the steepest ascent direction on the manifold.
-It lies in the tangent space of the manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$ and is obtainable by projection:
-				\begin{equation}
-					\label{eq:gradient_riem}
-					\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}} \mathbf{\Theta}_g^{(r)};
-				\end{equation}
-			\item \emph{Translate to the Riemannian (sub-)gradient at the identity:} The Riemannian (sub-)gradient should be translated back to the identity for exploiting the Lie algebra\footnote{Lie algebra refers to the tangent space of the Lie group at the identity element.
-A Lie group is simultaneously a continuous group and a differentiable manifold.
-In this example, $\mathbb{U}^{L \times L}$ formulates a Lie group and the corresponding Lie algebra consists of skew-Hermitian matrices $\mathfrak{u}(L) \triangleq \mathcal{T}_{\mathbf{I}}\mathbb{U}^{L \times L} = \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} + \mathbf{M} = \mathbf{0}\}$.}:
-				\begin{equation}
-					\label{eq:gradient_riem_tran}
-					\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{R},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.
-					% $\mathcal{O}(2 L^3)$
-				\end{equation}
-			\item \emph{Determine the conjugate direction:} The conjugate direction is obtained over the Riemannian (sub-)gradient and previous direction as
-				\begin{equation}
-					\label{eq:conjugate_dirn_geod}
-					{\mathbf{D}}_g^{(r)} = \tilde{\nabla}_{\mathrm{R},g}^{(r)} + {\gamma}_g^{(r)} {\mathbf{D}}_g^{(r-1)},
-				\end{equation}
-				where $\gamma_g^{(r)}$ is the parameter that deviates the conjugate direction from the tangent space for accelerated convergence. A popular choice is the Polak-Ribi\`{e}re formula \cite{Hager2006}
-				\begin{equation}
-					\label{eq:conjugate_parm_geod}
-					{\gamma}_g^{(r)} = \frac{\tr\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}.
-% $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-				\end{equation}
-			\item \emph{Evaluate the geodesic at the identity:} The geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ is described by
-				\begin{equation}
-					\label{eq:geodesic_iden}
-					\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D}),
-				\end{equation}
-				where $\exp(\mathbf{A}) = \sum_{k=0}^\infty (\mathbf{A}^k/k!)$ is the matrix exponential and $\mu$ is the step size (i.e., magnitude of the tangent vector).
-			\item \emph{Translate to the geodesic at $\mathbf{\Theta}_g^{(r)}$:} The geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ terminates at $\mathbf{\Theta}_g^{(r+1)}$ by multiplicative updates
-				\begin{equation}
-					\label{eq:geodesic_tran}
-					\mathbf{\Theta}_g^{(r+1)} {=} \mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu) {=} \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} {=} \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
-				\end{equation}
-				where $\mu$ is the step size refinable\footnote{To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, that is, $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.} by the Armijo rule \cite{Armijo1966}.
-		\end{enumerate}
-
-		\begin{algorithm}[!t]
-			\caption{Group-wise geodesic \gls{rcg}}
-			\label{ag:rcg}
-			\begin{algorithmic}[1]
-				\Require $f(\mathbf{\Theta})$, $G$
-				\Ensure $\mathbf{\Theta}^\star$
-				\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
-				\Repeat
-				\For {$g \gets 1$ to $G$}
-				\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_eucl}, $\tilde{\nabla}_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riem_tran}
-				\State $\tilde{\gamma}_g^{(r)} \gets$ \eqref{eq:conjugate_parm_geod}, $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:conjugate_dirn_geod}
-				\If {$\Re\bigl\{\tr({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{Not ascent}
-				\State $\mathbf{D}_g^{(r)} \gets \tilde{\nabla}_{\mathrm{R},g}^{(r)}$
-				\EndIf
-				\State $\mu \gets 0.1$
-				\State $\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu) \gets$ \eqref{eq:geodesic_tran}
-				\While {$ f\bigl(\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \frac{\tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}})}{2}$}\label{ln:armijo_start}
-				\State $\mu \gets 2 \mu$
-				\EndWhile
-				\While {$f\bigl(\mathbf{G}_{\mathbf{\Theta}_g^{(r)}}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \frac{\mu}{2} \cdot \frac{\tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}})}{2}$}
-				\State $\mu \gets \mu / 2$
-				\EndWhile \label{ln:armijo_end}
-				\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:geodesic_tran}
-				\EndFor
-				\State $r \gets r+1$
-				\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
-			\end{algorithmic}
-		\end{algorithm}
-
-		Algorithm~\ref{ag:rcg} summarizes the introduced group-wise geodesic \gls{rcg} method.
-		Compared to the non-geodesic approach, it leverages Lie algebra to replace the add-then-retract update with a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
-		This appropriate parameter space leads to faster convergence and easier step size tuning.
-		Convergence to a local optimum is still guaranteed if not initialized at a stationary point.
-		The group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} design problems.
-		One can also directly operate on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) relevant expressions to unify step size selection and accelerate the algorithm for a large $G$.
-
-		We now analyze the computational complexity of solving singular value shaping problem \eqref{op:shaping} by Algorithm~\ref{ag:rcg}.
-		To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean sub-gradient \eqref{eq:shaping_subdiff} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L) \bigr)$, Riemannian sub-gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:geodesic_tran} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
-		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., lines \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
-		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{RCG} N_\mathrm{S} \bigl(N N_\mathrm{T} N_\mathrm{R} + N (N_\mathrm{T}+N_\mathrm{R}) + I_\text{BLS}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{RCG} \bigl(N N_\mathrm{T} N_\mathrm{R} + N_\mathrm{S} N (N_\mathrm{T}+N_\mathrm{R}+N_\mathrm{S}) + I_\text{BLS} N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-
-		To validate Algorithm~\ref{ag:rcg} and quantify the shaping capability of \gls{bd}-\gls{ris}, we characterize the achievable singular value region of \gls{bd}-\gls{ris}-aided \gls{mimo} channel by considering the Pareto optimization problem
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:pareto_unitary}}
-		\end{maxi!}
-		where $\rho_n \ge 0$ is the weight associated with the $n$-th channel singular value.
-		Varying those weights help to characterize the Pareto frontier of singular values that encloses the achievable region.
-		While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication, detection probability for sensing, and harvestable energy for power transfer).
-		Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd}.
-		It can be solved optimally by Algorithm~\ref{ag:rcg} with $[\mathbf{D}]_{n,n} = \rho_n$ in \eqref{eq:shaping_subdiff}.
-	\end{subsection}
-\end{section}
-
-\begin{section}{Rate Maximization}
-	\label{sc:rate}
-	In this section, we first solve rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
-
-	The achievable rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel is formulated as
-	\begin{maxi!}
-		{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
-		\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
-		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cn:rate_unitary}}
-	\end{maxi!}
-	where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is maximum average transmit power.
-	Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
-	Two approaches are proposed to solve it optimally or efficiently.
-
-	\begin{subsection}{Alternating Optimization}
-		\label{sc:rate_ao}
-		This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
-		For a given $\mathbf{W}$, the passive beamforming subproblem is
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_ris}}{\label{ob:rate_ris}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		\end{maxi!}
-		where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-		Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:rate}.
-		\begin{lemma}
-			\label{lm:rate}
-			The partial derivative of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
-			\begin{equation}
-				\label{eq:gradient_eucl_rate}
-				\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-			\end{equation}
-		\end{lemma}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:rate}.
-		\end{proof}
-		For a given $\mathbf{\Theta}$, the optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
-		\begin{equation}
-			\label{eq:precoder_rate}
-			\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
-		\end{equation}
-		where $\mathbf{V}$ is the right singular matrix of $\mathbf{H}$ and $\mathbf{s}^\star$ is the optimal water-filling power allocation \cite{Clerckx2013}.
-		The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-		The computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
-		On the other hand, the complexity of active beamforming \eqref{eq:precoder_rate} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
-		The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
-		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{AO}\bigl(I_\text{RCG} N_\mathrm{S} (N + N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS}) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{AO}\bigl(I_\text{RCG} (NN_\mathrm{S}^2 + N_\mathrm{S} N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} N_\mathrm{S}^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-	\end{subsection}
-
-	\begin{subsection}{Low-Complexity Solution}
-		\label{sc:rate_lc}
-		To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel for maximum power gain and then optimize the active beamforming.
-		The shaping subproblem is formulated as\footnote{%
-			\label{fn:power_gain}%
-			Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
-Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
-		}
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power}}{\label{ob:power}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{\label{cn:power_unitary}}{}
-		\end{maxi!}
-		Inspired by \cite{Nie2017}, we propose a closed-form iterative solution that empirically converges to a stationary point of problem \eqref{op:power}.
-		The idea is to approximate the quadratic objective \eqref{ob:power} successively by Taylor expansion and solve each subproblem by group-wise \gls{svd}.
-
-		\begin{proposition}
-			\label{pp:power}
-			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point when $\mathbf{M}_g$ is rank-deficient due to the non-uniqueness of the orthonormal bases of kernels.}
-			\begin{equation}
-				\label{eq:ris_power}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-			\end{equation}
-			monotonically increases the objective function \eqref{ob:power},
-			% leads to a convergence of the objective function \eqref{ob:power} towards a stationary point,\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point due to the non-uniqueness of \gls{svd}, especially when $\mathbf{M}_g$ is rank-deficient.}
-			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of\footnote{We notice that $\mathbf{\Theta}_g$ coincides with the orthogonal projection of $\mathbf{M}_g$ onto the Stiefel manifold $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g$.} % \cite{Manton2002}
-			\begin{equation}
-				\label{eq:auxiliary_power}
-				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-			\end{equation}
-			Besides, when \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:power}.
-		\end{proof}
-
-		\begin{remark}
-			\label{re:power}
-			The sequence \eqref{eq:auxiliary_power} is constructed iteratively from its orthogonal projection.
-			Although a formal proof remains elusive, empirical evidence from simulation indicates that \eqref{eq:auxiliary_power} converge, and thus \eqref{eq:ris_power} converges to a stationary point, for extensively tested scenarios.
-			% We thus conjecture that the sequence \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
-		\end{remark}
-
-		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L\bigr)$ operations and its \gls{svd} requires $\mathcal{O}(L^3)$ operations.
-		The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
-		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{SAA} N_\mathrm{S} \bigl(N_\mathrm{T} N_\mathrm{R} + N+N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{SAA} \bigl(N_\mathrm{T} N_\mathrm{R} + NN_\mathrm{S}^2+N_\mathrm{T} N_\mathrm{R} N_\mathrm{S} + N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		For the latter, the computational complexity can be further reduced:
-		\begin{itemize}
-			\item \emph{Negligible direct channel:} The optimal solution to \eqref{op:power} has been solved in closed form by \eqref{eq:ris_nd_power_max}.
-			\item \emph{Non-negligible direct channel:} In terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:procrustes_wt}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cn:procrustes_wt}}{}
-			\end{mini!}
-			which still has no trivial solution.
-			One \emph{lossy} transformation \cite{Bell2003} shifts $\mathbf{\Theta}$ to sides of the product by Moore-Penrose inverse, formulating standard orthogonal Procrustes problems
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
-			\end{mini!}
-			with optimal solutions \cite[(6.4.1)]{Golub2013}
-			\begin{equation}
-				\label{eq:ris_procrustes}
-				\mathbf{\Theta}_\textnormal{P-max-approx}^\textnormal{MIMO-HD} = \mathbf{U} \mathbf{V}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{U}$ and $\mathbf{V}$ are respectively any left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$.
-		\end{itemize}
-
-		Although \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_procrustes} are of similar form, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
-		We will show in Section \ref{sc:simulation} that \eqref{eq:ris_procrustes} achieves near-optimal performance when $N_\mathrm{S}$ is large.
-		Once the channel is shaped by \eqref{eq:ris_power} or \eqref{eq:ris_nd_power_max} or \eqref{eq:ris_procrustes}, the active beamforming is retrieved by \eqref{eq:precoder_rate}.
-		This two-stage solution avoids outer iterations and efficiently handles (or avoids) inner iterations.
-	\end{subsection}
-
-	% \begin{subsection}{MIMO Interference Channel}
-	% 	\label{sc:wsr}
-	% 	On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
-	% 	\begin{equation}
-	% 		R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k\biggr),
-	% 	\end{equation}
-	% 	where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
-	% 	The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
-	% 	\begin{maxi!}
-	% 		{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr}}{\label{ob:wsr}}
-	% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-	% 		\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
-	% 	\end{maxi!}
-	% 	where $\rho_k \ge 0$ is the weight associated with transmission $k$.
-	% 	This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
-
-	% 	\begin{subsubsection}{Alternating Optimization}
-	% 		\label{sc:wsr_ao}
-	% 		This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
-	% 		For a given precoder set, the passive beamforming subproblem is
-	% 		\begin{maxi!}
-	% 			{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr_ris}}{\label{ob:wsr_ris}}
-	% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-	% 		\end{maxi!}
-	% 		which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.
-
-	% 		\begin{lemma}
-	% 			\label{lm:wsr}
-	% 			The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
-	% 			\begin{equation}
-	% 				\label{eq:gradient_eucl_wsr}
-	% 				\begin{split}
-	% 					\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K & \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
-	% 					& \times \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
-	% 				\end{split}
-	% 			\end{equation}
-	% 			where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
-	% 		\end{lemma}
-
-	% 		\begin{proof}
-	% 			Please refer to Appendix~\ref{ap:wsr}.
-	% 		\end{proof}
-
-	% 		For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
-	% 		A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
-	% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
-	% 		\begin{equation}
-	% 			\begin{split}
-	% 				\mathbf{G}_k^{(r)} &= {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \\
-	% 				& \quad \times \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
-	% 			\end{split}
-	% 		\end{equation}
-	% 		the corresponding error matrix is
-	% 		\begin{equation}
-	% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
-	% 		\end{equation}
-	% 		and the optimal precoder at transmitter $k$ is given by
-	% 		\begin{equation}
-	% 			\label{eq:precoder_wsr}
-	% 			\begin{split}
-	% 				\mathbf{W}_k^{(r)} & = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \\
-	% 				& \quad \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
-	% 			\end{split}
-	% 		\end{equation}
-	% 		where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
-	% 		\begin{equation}
-	% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
-	% 			% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
-	% 		\end{equation}
-	% 		where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.
-
-	% 		The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
-	% 		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-	% 	\end{subsubsection}
-
-	% 	\begin{subsubsection}{Low-Complexity Solution}
-	% 		\label{sc:wsr_lc}
-	% 		Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
-	% 		The leakage interference minimization problem is formulated as
-	% 		\begin{mini!}
-	% 			{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{\label{op:interference}}{\label{ob:interference}}
-	% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-	% 		\end{mini!}
-	% 		which can be solved iteratively in closed form.
-
-	% 		\begin{proposition}
-	% 			\label{pp:interference}
-	% 			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
-	% 			\begin{equation}
-	% 				\label{eq:ris_interference}
-	% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
-	% 			\end{equation}
-	% 			monotonically decreases the objective function \eqref{ob:interference},
-	% 			% converges to a stationary point of \eqref{op:interference},
-	% 			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
-	% 			\begin{equation}
-	% 				\label{eq:auxiliary_interference}
-	% 				\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
-	% 			\end{equation}
-	% 			where $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}.$
-	% 			Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
-	% 		\end{proposition}
-	% 		\begin{proof}
-	% 			Please refer to Appendix~\ref{ap:interference}.
-	% 		\end{proof}
-	% 		Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
-	% 		This two-stage solution avoids outer iterations and efficiently handles inner iterations.
-	% 	\end{subsubsection}
-	% \end{subsection}
-\end{section}
-
-\begin{section}{Simulation Results}
-	\label{sc:simulation}
-	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{Source code is available at \url{https://github.com/snowztail/channel-shaping}.}
-	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
-	We set $\Lambda_0=\qty{-30}{dB}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$, and $\gamma_\mathrm{B}=2$ for reference.
-	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician K-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
-	Unless otherwise specified, we assume the direct channel is present, $\kappa = 0$ (i.e., Rayleigh fading) for all channels, and $\eta = \qty{-75}{dB}$ for all receivers.
-	For point-to-point channel, we set $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
-	% For interference channel, we assume $K$ transmitters and receivers are independently and uniformly distributed in a disk of radius \qty{20}{m}, and all transmissions use the same number of streams $N_\mathrm{E}$ and equal weight $\rho_k=1$, $\forall k$.
-
-	\begin{subsection}{Algorithm Evaluation}
-		\begin{table}[!t]
-			\caption{Performance of Geodesic and Non-Geodesic \gls{rcg} on \eqref{op:pareto}}
-			\label{tb:complexity_algorithm}
-			\centering
-			\resizebox{\columnwidth}{!}{
-				\begin{tabular}{ccccccc}
-					\toprule
-					\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
-													& Objective                             & Iterations                             & Time [s]         & Objective        & Iterations & Time [s] \\ \midrule
-					Geodesic                        & $\num{4.359e-3}$                      & 11.59                                  & $\num{1.839e-2}$ & $\num{1.163e-2}$ & 25.58      & 3.461    \\
-					Non-geodesic                    & $\num{4.329e-3}$                      & 30.92                                  & $\num{5.743e-2}$ & $\num{1.116e-2}$ & 61.40      & 13.50    \\ \bottomrule
-				\end{tabular}
-			}
-		\end{table}
-		Table \ref{tb:complexity_algorithm} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023b,Li2023c,Zhou2023} on Pareto singular value problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
-		The statistics are averaged over \num{100} independent runs.
-		We observe that the geodesic \gls{rcg} method achieves slightly higher objective values with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) elapsed time than the non-geodesic method.
-		The results demonstrate the efficiency of the geodesic \gls{rcg} algorithm \ref{ag:rcg} on large-scale \gls{bd}-\gls{ris} design problems.
-
-		\begin{table}[!t]
-			\caption{Performance of \gls{d}-\gls{ris} and Fully-Connected \gls{bd}-\gls{ris} on \eqref{op:rate}}
-			\label{tb:complexity_bond}
-			\centering
-			\resizebox{\columnwidth}{!}{
-				\begin{tabular}{ccccccc}
-					\toprule
-					\multirow{3}{*}{\gls{ris} type} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
-													& Objective                             & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular}                             & Time [s]         & Objective        & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular} & Time [s] \\ \midrule
-					Diagonal                        & $\num{25.33}$                      & 2.06                                  & $\num{2.620e-2}$ & $\num{32.22}$ & 2.92      & 1.277    \\
-					Fully-connected BD              & $\num{26.10}$                      & 3.84                                  & $\num{2.719e-2}$ & $\num{36.58}$ & 3.03      & 0.806    \\ \bottomrule
-				\end{tabular}
-			}
-		\end{table}
-		Table \ref{tb:complexity_bond} compares the performance of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} on rate maximization problem \eqref{op:rate} using the \gls{ao} design in Section \ref{sc:rate_ao}, where $N_\mathrm{T}=N_\mathrm{R}=4$ and $P=\qty{20}{dB}$.
-		The statistics are averaged over \num{100} independent runs.
-		The fact that fully-connected \gls{bd}-\gls{ris} provides a higher achievable rate using slightly more outer iterations $I_\text{AO}$ than \gls{d}-\gls{ris} is consistent with our analysis.
-		Interestingly, \emph{the former still ends up with shorter elapsed time,} which seems to contradict the complexity analysis that $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris} and $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris}.
-		One possible reason is that \gls{bd}-\gls{ris} only involves 1 backtracking line search per iteration while \gls{d}-\gls{ris} requires $N_\mathrm{S}$ times.
-		Another reason is that the group-wise update of \gls{d}-\gls{ris} leads to slower convergence of inner iterations.
-		These results suggest that optimizing \gls{bd}-\gls{ris} may be less computational intensive than expected.
-	\end{subsection}
-
-	\begin{subsection}{Channel Singular Value Redistribution}
-		\begin{subsubsection}{Achievable Singular Value Region}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[$2 \times 32 \times 2$ (no direct)]{
-					\label{fg:singular_pareto_sx32_nd}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_singular_pareto_sx32_nd.tex}
-
-					}
-				}
-				\subfloat[$2 \times 32 \times 2$]{
-					\label{fg:singular_pareto_sx32}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_singular_pareto_sx32.tex}
-					}
-				}
-				\\
-				\subfloat[$2 \times 64 \times 2$]{
-					\label{fg:singular_pareto_sx64}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_singular_pareto_sx64.tex}
-					}
-				}
-				\subfloat[$2 \times 128 \times 2$]{
-					\label{fg:singular_pareto_sx128}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_singular_pareto_sx128.tex}
-					}
-				}
-				\caption{Pareto frontiers of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel reshaped by \gls{bd}-\gls{ris}.}
-				\label{fg:singular_pareto}
-			\end{figure}
-			Fig. \ref{fg:singular_pareto} illustrates the Pareto frontiers of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} aided by \gls{ris}.
-			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
-			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two spaces.
-			We observe that the smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
-			When the direct channel is significant, the shape of the singular value region depends heavily on the relative strength of the indirect channels, which is $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$ in this case.
-			Fig.
-\subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the point of direct channel.
-			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
-			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
-			It suggests the design flexibility from larger group size allows better alignment of multiple modes simultaneously.
-			% not only provides a better trade-off in channel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
-			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
-			In particular, Fig.
-\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable inter-connections between elements.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Analytical Bounds and Numerical Results}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[$4 \times 32 \times 4$ (rank-1)]{
-					\label{fg:singular_bound_rank1_sx32}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_singular_bound_rank1_sx32.tex}
-					}
-				}
-				\subfloat[$4 \times 64 \times 4$ (rank-1)]{
-					\label{fg:singular_bound_rank1_sx64}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_singular_bound_rank1_sx64.tex}
-					}
-				}
-				\\
-				\subfloat[$4 \times 128 \times 4$ (rank-2)]{
-					\label{fg:singular_bound_rank2_sx128}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_singular_bound_rank2_sx128.tex}
-					}
-				}
-				\subfloat[$4 \times 256 \times 4$ (rank-4)]{
-					\label{fg:singular_bound_rank4_sx256}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_singular_bound_rank4_sx256.tex}
-					}
-				}
-				\caption{
-					Achievable channel singular values: analytical bounds (lines) and numerical results (bars).
-					Baselines of bars denote the singular values of the direct channel.
-					Blue (resp.
-red) bars denote the lower (resp.
-upper) dynamic range of singular values obtained by solving \eqref{op:pareto} with $\rho_n/\rho_{n'} \to 0$ (resp.
-$\to \infty$), $\forall n, \ n' \ne n$.
-					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
-					`rank-$k$' refers to the rank of the forward channel.
-				}
-				\label{fg:singular_bound}
-			\end{figure}
-			We focus on achieving the analytical bounds in Proposition \ref{pp:rd} since many bounds in Proposition \ref{pp:nd} are provided with closed-form \gls{ris} solutions.
-			For a rank-$k$ forward channel, Fig.
-\ref{fg:singular_bound} compares the individual singular value bounds in Proposition \ref{pp:rd} and the numerical results obtained by solving problem \eqref{op:pareto} with proper weights.
-			When the \gls{ris} is in \gls{los} of the transmitter, Figs.
-\subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
-			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris} using a small $N_\mathrm{S}$.
-			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
-			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
-			Those observations align with Proposition \ref{pp:rd}.
-			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both backward and forward channels are full-rank.
-			This can be predicted from \eqref{eq:auxiliary_rd} where the singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
-			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scales with the rank of backward and forward channels.
-
-			\begin{figure}[!t]
-				\centering
-				\subfloat[$1 \times 256 \times 1$ (no direct)]{
-					\label{fg:power_bond_txrx1_nd}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_power_bond_txrx1_nd.tex}
-					}
-				}
-				\subfloat[$4 \times 256 \times 4$ (no direct)]{
-					\label{fg:power_bond_txrx4_nd}
-					\resizebox{!}{3.25cm}{
-						\input{../assets/simulation/pc_power_bond_txrx4_nd.tex}
-					}
-				}
-				\caption{
-					Average maximum channel power gain versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
-					`Cascaded' refers to the upper bound in \eqref{iq:power_nd}.
-				}
-				\label{fg:power_bond}
-			\end{figure}
-
-			Fig.
-\ref{fg:power_bond} compares the analytical bound on channel power gain in Corollary \ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
-			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:ris_nd_power_max} or via optimization approach \eqref{eq:ris_power}.
-			For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-			It comes purely from branch matching as discussed in Example \ref{eg:siso} and agrees with the asymptotic power scaling law derived in \cite[(30)]{Shen2020a}
-			Interestingly, Fig.
-\subref*{fg:power_bond_txrx4_nd} shows that this gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} and aligns with the expectation analysis \eqref{eq:power_nd_rayleigh}.
-			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
-		\end{subsubsection}
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rate Maximization}
-		\begin{figure}[!t]
-			\centering
-			\subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)]{
-				\label{fg:power_sx_txrx16_nd}
-				\resizebox{!}{3.15cm}{
-					\input{../assets/simulation/pc_power_sx_txrx16_nd.tex}
-				}
-			}
-			\subfloat[$16 \times N_\mathrm{S} \times 16$]{
-				\label{fg:power_sx_txrx16}
-				\resizebox{!}{3.15cm}{
-					\input{../assets/simulation/pc_power_sx_txrx16.tex}
-				}
-			}
-			\caption{
-				Average maximum channel power gain versus \gls{ris} configuration.
-				`Explicit' refers to the optimal solution \eqref{eq:ris_nd_power_max} when the direct channel is negligible.
-				`OP-left' and `OP-right' refer to the suboptimal solutions, when the direct channel is significant, by lossy transformation \eqref{op:procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
-			}
-			\label{fg:power_sx}
-		\end{figure}
-
-		We first focus on the channel power gain problem \eqref{op:power}.
-		Fig. \ref{fg:power_sx} shows the maximum channel power gain under different \gls{ris} configurations.
-		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is even larger when the direct channel is significant.
-		As shown in Figs.
-\subref*{fg:power_sx_txrx16_nd} and \subref*{fg:power_sx_txrx16}, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power gain as a 256-element \gls{d}-\gls{ris} when the direct channel is significant, but less so when it is negligible.
-		This is because the mode alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced when the modes of direct channel is taken into account.
-		We also notice that the suboptimal solutions \eqref{eq:ris_procrustes} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
-
-		\begin{figure}[!t]
-			\centering
-			\subfloat[$4 \times 128 \times 4$]{
-				\label{fg:rate_beamforming}
-				\resizebox{!}{3.25cm}{
-					\input{../assets/simulation/pc_rate_beamforming.tex}
-				}
-			}
-			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$]{
-				\label{fg:rate_txrx}
-				\resizebox{!}{3.25cm}{
-					\input{../assets/simulation/pc_rate_txrx.tex}
-				}
-			}
-			\\
-			\subfloat[$4 \times N_\mathrm{S} \times 4$]{
-				\label{fg:rate_sx}
-				\resizebox{!}{3.25cm}{
-					\input{../assets/simulation/pc_rate_sx.tex}
-				}
-			}
-			\subfloat[$4 \times 128 \times 4$]{
-				\label{fg:rate_kfactor}
-				\resizebox{!}{3.25cm}{
-					\input{../assets/simulation/pc_rate_kfactor.tex}
-				}
-			}
-			\caption{
-				Average achievable rate versus \gls{mimo} and \gls{ris} configurations.
-				The transmit power corresponds to a direct \gls{snr} of \num{-10} to \qty{30}{dB}.
-				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
-				`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
-			}
-			\label{fg:rate}
-		\end{figure}
-
-		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
-		At a transmit power $P = \qty{10}{dB}$, Fig.
-\subref*{fg:rate_beamforming} shows that introducing a 128-element \gls{d}-\gls{ris} to $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
-		A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section \ref{sc:rate_ao} and the low-complexity shaping-inspired solution in Section \ref{sc:rate_lc} narrows as $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
-		This implies that joint \gls{ris}-transceiver designs can be decoupled by first shaping the wireless channel and then optimizing the active beamformer, which simplifies the design substantially.
-		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}
-		increases with the number of transmit and receive antennas and scattering elements, especially at high \gls{snr}.
-		For $N_\mathrm{S}=128$ and $P = \qty{20}{dB}$,
-		the achievable rate ratio of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is \num{1.04}, \num{1.11}, and \num{1.13} for $N_\mathrm{T}=N_\mathrm{R}=1$, \num{4}, and \num{16}, respectively.
-		For $N_\mathrm{T}=N_\mathrm{R}=4$ and $P = \qty{20}{dB}$, this ratio amounts to \num{1.03}, \num{1.08}, and \num{1.13} for $N_\mathrm{S}=16$, \num{64}, and \num{256}, respectively.
-		Those observations align with the power gain results in Fig. \ref{fg:power_sx} and highlight the rate benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} in large-scale \gls{mimo} systems.
-		In the low power regime (\num{-20} to \qty{-10}{dB}), we also notice that the slope of the achievable rate of \gls{bd}-\gls{ris} is steeper than that of \gls{d}-\gls{ris}.
-		That is, \gls{bd}-\gls{ris} can help to activate more streams and achieve the asymptotic \gls{dof} at a low transmit \gls{snr}.
-		This is particularly visible in Fig. \subref*{fg:rate_sx} where the topmost curve is almost a linear function of the transmit power.
-		It is also expected from the shaping results in Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
-		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician K-factor increases and becomes indistinguishable in \gls{los} environment.
-		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
-
-		% \begin{subsubsection}{MIMO Interference Channel}
-		% 	\label{sc:simulation_wsr}
-		% 	\begin{figure}[!t]
-		% 		\centering
-		% 		\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
-		% 			\label{fg:ic_interference_sx}
-		% 			\resizebox{!}{3.15cm}{
-		% 				\input{../assets/simulation/ic_interference_sx.tex}
-		% 			}
-		% 		}
-		% 		\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
-		% 			\label{fg:ic_wsr_beamforming}
-		% 			\resizebox{!}{3.15cm}{
-		% 				\input{../assets/simulation/ic_wsr_beamforming.tex}
-		% 			}
-		% 		}
-		% 		\\
-		% 		\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
-		% 			\label{fg:ic_wsr_sx}
-		% 			\resizebox{!}{3.15cm}{
-		% 				\input{../assets/simulation/ic_wsr_sx.tex}
-		% 			}
-		% 		}
-		% 		\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
-		% 			\label{fg:ic_wsr_txrx}
-		% 			\resizebox{!}{3.15cm}{
-		% 				\input{../assets/simulation/ic_wsr_txrx.tex}
-		% 			}
-		% 		}
-		% 		\caption{
-		% 			Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
-		% 			`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
-		% 			`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
-		% 		}
-		% 	\end{figure}
-
-		% 	Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference by solving problem \eqref{op:interference}.
-		% 	In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
-		% 	The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.
-
-		% 	Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section \ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
-		% 	Unlike the point-to-point case, the latter is not as effective as the former.
-		% 	The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
-		% 	On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
-		% 	A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.
-
-		% 	Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
-		% 	Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
-		% 	The reasons have been discussed in the point-to-point case.
-		% \end{subsubsection}
-	\end{subsection}
-
-	\begin{subsection}{Practical Constraints}
-		\begin{subsubsection}{RIS Symmetry}
-			\label{sc:ris_symmetry}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[Power: $2 \times N_\mathrm{S} \times 2$]{
-					\label{fg:pc_power_symmetry}
-					\resizebox{!}{3.15cm}{
-						\input{../assets/simulation/pc_power_symmetry.tex}
-					}
-				}
-				\subfloat[Rate: $4 \times N_\mathrm{S} \times 4$]{
-					\label{fg:pc_rate_symmetry}
-					\resizebox{!}{3.15cm}{
-						\input{../assets/simulation/pc_rate_symmetry.tex}
-					}
-				}
-				\caption{
-					Impact of \gls{ris} symmetry on the power gain and achievable rate of \gls{mimo} point-to-point channel.
-				}
-			\end{figure}
-			Symmetric \gls{ris} satisfying $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$ are often considered in the literature due to hardware constraints.
-			This study aim to investigate the impact of \gls{ris} symmetry on the system performance.
-			\begin{remark}
-				All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry. In particular,
-				\begin{enumerate}[label=(\roman*)]
-					\item \emph{\gls{svd}-based (e.g., \eqref{eq:ris_nd_sv_indl}, \eqref{eq:ris_nd_power}, \eqref{eq:ris_nd_rate_max}, \eqref{eq:ris_power}, \eqref{eq:ris_procrustes}):} Those closed-form asymmetric solutions are constructed from the product of singular matrices.
-If symmetry is required, one can replace the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} and use unitary factor $\mathbf{Q}$ to construct the corresponding $\mathbf{\Theta}$.
-\label{it:takagi}
-					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
-\label{it:projection}
-				\end{enumerate}
-			\end{remark}
-
-			Figs.
-\ref{fg:pc_power_symmetry} and \ref{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
-			Here, `Asymmetric' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, `Enforced' refers to enforcing symmetry on `Asymmetric', `Legacy' refers to a straightforward extension of the \gls{siso} \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, `Takagi' refers to the modification \ref{it:takagi}, and `Projection' refers to the modification \ref{it:projection}.
-			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and scale with the number of scattering elements.
-			The two proposed modifications also outperform other candidates in both problems.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Channel Estimation Error}
-			\label{sc:estimation_error}
-			% \begin{figure}[!t]
-			% 	\centering
-			% 	\resizebox{!}{3.15cm}{
-			% 		\input{../assets/simulation/ic_wsr_pair.tex}
-			% 	}
-			% 	\caption{
-			% 		Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
-			% 	}
-			% 	\label{fg:ic_wsr_pair}
-			% \end{figure}
-
-			% Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
-			% Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
-			% \begin{equation*}
-			% 	\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
-			% \end{equation*}
-			% where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
-			% The \gls{wsr} is evaluated using the true channels.
-			% We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
-			% On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
-			% In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
-			% These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
-		\end{subsubsection}
-	\end{subsection}
-\end{section}
-
-\begin{section}{Conclusion}
-	This paper analyzes the channel shaping capability of a passive \gls{ris} in terms of singular value redistribution.
-	We focus on a \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than \gls{d}-\gls{ris}.
-	This translates to a wider dynamic range of and better trade-off between singular values, resulting in significant power and rate gains.
-	Analytical singular value bounds are derived under typical \gls{ris} deployment scenarios and the Pareto frontiers are characterized via an efficient \gls{rcg} method.
-	We also present two beamforming designs for rate maximization problem in \gls{mimo} point-to-point channel and interference channel, one for optimal performance and the other exploits channel shaping for lower complexity.
-	Extensive simulations show that the shaping advantage of \gls{bd}-\gls{ris} stems from its superior branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.
-
-	% It would be interesting to investigate the impact of channel shaping through \gls{ris} on other wireless applications such as sensing and far-field power transfer.
-	% One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
-	% Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
-	% Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward spaces simultaneously.
-	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
-	% into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
-	% even better channel shaping can be achieved by incorporating the \gls{ris} into the \gls{mimo} precoding and combining design.
-\end{section}
 
@@
 		is a special case of \eqref{iq:horn} with $(I, J, K) \in [N_\mathrm{S}]^3$.
-		The minimum\footnote{One may think to take the \emph{maximum} of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
-However, this is infeasible since the singular values will be reordered therein.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
+		The minimum\footnote{One may think to take the maximum of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
+This is infeasible since the singular values will be reordered.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
 		On the other hand, the set of lower bounds
@@
 \begin{section}{Acknowledgement}
-	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct some technical errors.
+	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct several technical errors.
 \end{section}

### 2025-02-25 manuscript/main.tex
:construction: Merge footnotes

@@
 \input{preamble}
+
+\externaldocument[~]{appendix}
 
@@
 \begin{abstract}
-	This paper investigates the limits to which a passive \gls{ris} can reshape a point-to-point \gls{mimo} in terms of singular values
-	% and power gain
-	and thus improve the rate performance.
-	% redistribute the singular values of a point-to-point \gls{mimo} channel for providing power and rate gains.
-	We depart from the conventional \gls{ris} with \gls{d} phase shift matrix and adopt a \gls{bd} model interconnecting elements for signal amplitude and phase manipulation.
-	This translates to superior branch matching and mode alignment capabilities in \gls{mimo}.
-	% featuring group-wise connections for enhanced branch matching and mode alignment capabilities.
-	Specifically, analytical singular values bounds are derived under popular \gls{ris} deployment scenarios
-	% the scenario of rank-deficient backward/forward channel or negligible direct channel, which
-	to showcase the shaping advantages of \gls{bd}-\gls{ris} in terms of dynamic range and \gls{dof}.
+	This paper investigates the limits to which a passive \gls{ris} can reshape a point-to-point \gls{mimo} in terms of singular values for improved wireless (e.g., rate and power) performance.
+	We depart from the \gls{d} scattering matrix and adopt a \gls{bd} model that exploits element-wise connections for signal amplitude and phase manipulation.
+	% , which translate to superior \gls{mimo} shaping capabilities.
+	Specifically, analytical bounds are derived under popular \gls{ris} deployment scenarios to showcase the shaping potentials of \gls{bd}-\gls{ris} on the channel \gls{dof}, singular value spread, power gain, and capacity.
 	A numerical optimization method is then proposed for a broader range of shaping problems and invoked to characterize the achievable singular value region.
 	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
-	Results show that compared to \gls{d}-\gls{ris}, \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate.
+	Results show that \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate.
 	Those benefits become more pronounced when the number of \gls{ris} elements or \gls{mimo} dimensions increase.
@@
 \begin{IEEEkeywords}
-	MIMO, RIS, channel shaping, rate maximization, singular value bounds, manifold optimization.
+	MIMO, RIS, channel shaping, rate maximization, singular value analysis, manifold optimization.
 \end{IEEEkeywords}
@@
 		\begin{itemize}
-			\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
+			\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and \gls{dof} \cite{Bafghi2022,Zheng2023,Chae2023}.
 Those are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to minor perturbations of the channel matrix;
@@
 		This simple architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal.
-		The idea was later generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}.
+		The idea was later generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components, which can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.
 		This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
@@
 	$\diag(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
-	$\sv(\cdot)$, $\ran(\cdot)$, and $\ker(\cdot)$ evaluate the singular values (in descending order), column space (range), and kernel of a matrix, respectively.
+	$\sv(\cdot)$, $\ran(\cdot)$, and $\ker(\cdot)$ evaluate the singular values (in descending order), range, and kernel of a matrix, respectively.
 	% $\sv(\cdot)$ extracts the singular values of a matrix as a non-ascending vector.
@@
 	$\conv(\cdot)$ returns the convex hull of arguments.
-	$\mathrm{vec}(\cdot)$ stacks the columns of a matrix sequentially into a vector.
+	$\mathrm{vec}(\cdot)$ stacks the columns of a matrix as a vector.
 	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
@@
 	$(\cdot)_{[x:y]}$ is a shortcut for $(\cdot)_x,(\cdot)_{x+1},\ldots,(\cdot)_y$.
-	$\odot$ denotes the element-wise (Hadamard) product.
+	$\odot$ denotes the Hadamard product.
 	$\mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
@@
 		The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a} such that $N_\mathrm{S} = \sum_{g=1}^G N_g$.
-		Without loss of generality we assume equal group size $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$ and no mutual coupling between elements.
-		For asymmetric \gls{bd}-\gls{ris}, the overall scattering matrix is block-diagonal with unitary blocks\footnote{We assume asymmetric network by default to establish a benchmark for passive \gls{ris}.
-Some symmetric solutions (i.e., $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$) will be discussed and their performance will be evaluated in Section~\ref{sc:simulation}.}
+		We assume equal group size $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$, no mutual coupling between elements, and asymmetric circuit components for reference.
+		% Some symmetric solutions (i.e., $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$) will be discussed and their performance will be evaluated in Section~\ref{sc:simulation}.
+		The overall scattering matrix is block-diagonal with unitary blocks
 		\begin{equation}
@@
 		where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary matrices and $\mathbf{X}_g$ is a permutation matrix.
-		Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via group $g$ and $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
-		The equivalent channel is thus
+		Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel induced by group $g$ and $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
+		The equivalent channel is
 		\begin{equation}
@@
 		\end{figure}
-		With an exhaustive grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$, Fig.~\ref{fg:shaping_potential} shows the achievable singular values of a specific channel realization
+		With an exhaustive grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$, Fig.~\ref{fg:shaping_potential} shows the achievable singular values of a specific channel instance
+		$
+			\mathbf{H}_\mathrm{B} =
+				\begin{bsmallmatrix}
+					-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
+					0.4131 + 0.2651 \jmath  & -0.1960 + 0.4650 \jmath
+				\end{bsmallmatrix}, \
+				\mathbf{H}_\mathrm{F} =
+				\begin{bsmallmatrix}
+					-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
+					0.0196 + 0.4011 \jmath  & -0.3170 - 0.2303 \jmath
+				\end{bsmallmatrix}.
+		$
 		% \begin{equation*}
-		% 	\mathbf{H}_\mathrm{B} =
+		% 	\begin{split}
+		% 		\mathbf{H}_\mathrm{B} & =
 		% 		\begin{bsmallmatrix}
@@
 		% 		\end{bsmallmatrix},
-		% 		\mathbf{H}_\mathrm{F} =
+		% 		\\
+		% 		\mathbf{H}_\mathrm{F} & =
 		% 		\begin{bsmallmatrix}
@@
 		% 		\end{bsmallmatrix}.
+		% 	\end{split}
 		% \end{equation*}
-		\begin{equation*}
-			\begin{split}
-				\mathbf{H}_\mathrm{B} & =
-				\begin{bsmallmatrix}
-					-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
-					0.4131 + 0.2651 \jmath  & -0.1960 + 0.4650 \jmath
-				\end{bsmallmatrix},
-				\\
-				\mathbf{H}_\mathrm{F} & =
-				\begin{bsmallmatrix}
-					-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
-					0.0196 + 0.4011 \jmath  & -0.3170 - 0.2303 \jmath
-				\end{bsmallmatrix}.
-			\end{split}
-		\end{equation*}
 		In this example, both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris}.
@@
 		\label{sc:shaping_analytical}
-		The main results of this subsection are presented in the following Propositions and Corollaries.
-		\begin{proposition}[Degrees of freedom]
+		% \footnote{Here \gls{dof} refers to the maximum number of streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\textnormal{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.
+It is closely related to radar \gls{dof} which refers to the number of independent measurements.}
+		\begin{definition}[\gls{dof}]
+			\gls{dof} refers to the maximum number of streams that can be transmitted in parallel over a \gls{mimo} channel in the asymptotic high-\gls{snr} regime
+			\begin{equation}
+				\textnormal{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho},
+			\end{equation}
+			where $\rho$ is the \gls{snr}.
+			% It is closely related to radar \gls{dof} which refers to the number of independent measurements.
+		\end{definition}
+
+		\begin{definition}[Negligible direct channel]
+			% A direct channel is considered negligible when the signal power received via the direct channel is negligible compared to the signal power received via the scattering of \gls{ris}
+			A direct channel is considered negligible when its contribution to the received signal is substantially weaker than that of the \gls{ris}-induced channels. Mathematically, this can be defined as
+			\begin{equation*}
+				\frac{\lVert \mathbf{H}_\mathrm{D} \rVert _\mathrm{F}^2}{\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2} < \epsilon,
+			\end{equation*}
+			where $\epsilon$ is a small positive threshold.
+			This can result from a very large number of \gls{ris} elements (as in Proposition~\ref{pp:rd}) or physical obstacles in the propagation path (as in Proposition~\ref{pp:nd}).
+			% A direct channel is considered negligible when the
+			% signal going through it is negligible compared to that through the scattering of \gls{ris}
+			% power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}.
+
+			% Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
+		\end{definition}
+
+		The main results of this subsection are summarized in the following Propositions and Corollaries.
+		\begin{proposition}[\gls{dof}]
 			\label{pp:dof}
-			\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof}\footnote{Here \gls{dof} refers to the maximum number of streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\textnormal{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}.
-It is closely related to radar \gls{dof} which refers to the number of independent measurements.} than \gls{d}-\gls{ris}.
+			\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
 		\end{proposition}
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:dof}.
+			Please refer to Appendix~\ref{~ap:dof} in the supplement.
 		\end{proof}
@@
 				\diag(1, 1, 0, 0).
-				% \begin{bsmallmatrix}
-				% 	1 & 0 & 0 & 0 \\
-				% 	0 & 1 & 0 & 0 \\
-				% 	0 & 0 & 0 & 0 \\
-				% 	0 & 0 & 0 & 0
-				% \end{bsmallmatrix}.
 			\end{equation*}
@@
 			\end{equation*}
-			and achieves a \gls{dof} of 1.
-			In contrast, fully-connected \gls{bd}-\gls{ris} $\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
+			with 1 \gls{dof}.
+			In contrast, a fully-connected \gls{bd}-\gls{ris} can fully align or misalign the kernel of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ using \eqref{~eq:ris_dof_max} or \eqref{~eq:ris_dof_min} in Appendix~\ref{~ap:dof}
+			\begin{equation*}
+				\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
 				\begin{bsmallmatrix}
@@
 					0 & 0 & 1 & 0
-			\end{bsmallmatrix}$ and $\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} =
+				\end{bsmallmatrix}, \quad
+				\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} =
 				\begin{bsmallmatrix}
@@
 					0 & -1 & 0 & 0
-			\end{bsmallmatrix}$ in \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min}
-			result in
+				\end{bsmallmatrix}.
+			\end{equation*}
+			Those correspond to
 			\begin{equation*}
@@
 			\end{equation*}
-			and achieve \gls{dof} of 2 and 0, respectively.
+			and a \gls{dof} of 2 and 0, respectively.
 		\end{example}
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:rank_deficient}.
+			Please refer to Appendix~\ref{~ap:rank_deficient} in the supplement.
 		\end{proof}
@@
 		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected in all cases.} while the last $k$ channel singular values can be suppressed to zero.
-		Proposition \ref{pp:rd} complements Proposition \ref{pp:dof} and Example \ref{eg:dof} by quantifying the dynamic range of extreme singular values.
-		A special case is Corollary \ref{co:los} for \gls{los} channel\footnote{A similar eigenvalue result has been derived for \gls{d}-\gls{ris} only \cite{Semmler2023}.}.
+		Proposition \ref{pp:rd} complements Proposition \ref{pp:dof} by quantifying the dynamic range of extreme singular values.
+		A special case of \gls{los} channel is presented below\footnote{A similar eigenvalue result has been derived for \gls{d}-\gls{ris} only \cite{Semmler2023}.}.
 
@@
 		We emphasize that Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
-		Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible\footnote{Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
-This can result from a very large number of \gls{ris} elements (as discussed in Proposition~\ref{pp:rd}) or physical obstacles in the propagation path (as discussed in Proposition~\ref{pp:nd}).}.
+		Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible.
 		For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes, and we will later show in Section \ref{sc:simulation} that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd}.
+			Please refer to Appendix~\ref{~ap:nd} in the supplement.
 		\end{proof}
@@
 		Its importance lies in that our initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
-		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over definition\footnote{This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.} $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
+		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over the definition $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
+		This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.
 		The results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd_sv_prod_tail}.
+			Please refer to Appendix~\ref{~ap:nd_sv_prod_tail} in the supplement.
 		\end{proof}
@@
 			\end{subequations}
-			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices\footnote{%
-				\label{fn:svd_non_uniqueness}%
-				We highlight the non-uniqueness of $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$.
-When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace.
-Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.} of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
 			and $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary permutation matrices of dimension $N_\mathrm{S}$ satisfying:
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd_sv_indl}.
+			Please refer to Appendix~\ref{~ap:nd_sv_indl} in the supplement.
 		\end{proof}
+
+		\begin{remark}
+			\label{rm:svd}
+			We emphasize that the singular matrices in the \gls{svd} are not uniquely defined.
+			When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace.
+Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.
+			Consequently, all \gls{svd}-based \gls{ris} solutions in this paper are inherently non-unique.
+		\end{remark}
 
@@
 below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp.
-oppositely), that is,\footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
+oppositely), that is,
+			% \footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$.
 This is a looser version of \eqref{iq:power_nd} and cannot take equalities unless the extreme singular values are of multiplicity $N$.}
@@
 			\end{equation}
-			whose upper\footnote{%
-				\label{fn:power_nd_max}%
-				The upper bound \eqref{eq:ris_nd_power_max} is reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.} and lower bounds are attained respectively at
+			whose upper and lower bounds are attained respectively at
 			\begin{subequations}
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd_power}.
+			Please refer to Appendix~\ref{~ap:nd_power} in the supplement.
 		\end{proof}
@@
 		We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
-		% TODO relay
+		The upper bound \eqref{eq:ris_nd_power_max} is also reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.
 		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the expectation of maximum channel power gain can be numerically evaluated as
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:nd_capacity}.
+			Please refer to Appendix~\ref{~ap:nd_capacity} in the supplement.
 		\end{proof}
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:shaping}.
+			Please refer to Appendix~\ref{~ap:shaping} in the supplement.
 		\end{proof}
@@
 		\begin{algorithm}[!t]
+			\footnotesize
 			\caption{Group-wise geodesic \gls{rcg}}
@@
 		where $\rho_n \ge 0$ is the weight associated with the $n$-th channel singular value.
-		Varying those weights help to characterize the Pareto frontier of singular values that encloses the achievable region.
-		While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication, detection probability for sensing, and harvestable energy for power transfer).
+		Varying those weights help to characterize the Pareto frontier that encloses the achievable singular value region.
+		While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication \cite{Clerckx2013}, detection probability for sensing \cite{Liu2022c}, and harvested power for power transfer \cite{Shen2021}).
 		Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd}.
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:rate}.
+			Please refer to Appendix~\ref{~ap:rate} in the supplement.
 		\end{proof}
@@
 Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
-		Inspired by \cite{Nie2017}, we propose a closed-form iterative solution that empirically converges to a stationary point of problem \eqref{op:power}.
+		Inspired by \cite{Nie2017}, we propose a closed-form iterative solution based on orthogonal projection.
 		The idea is to approximate the quadratic objective \eqref{ob:power} successively by Taylor expansion and solve each subproblem by group-wise \gls{svd}.
@@
 			\label{pp:power}
-			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point when $\mathbf{M}_g$ is rank-deficient due to the non-uniqueness of the orthonormal bases of kernels.}
+			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the orthogonal projection of
+			\begin{equation}
+				\label{eq:auxiliary_power}
+				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+			\end{equation}
+			onto the Stiefel manifold, given in the closed-form \cite{Manton2002}
+			% $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$ .
+			% sequence
+			% \footnote{However, \eqref{eq:ris_power} might not converge to a single solution point when $\mathbf{M}_g$ is rank-deficient due to the non-uniqueness of the orthonormal bases of kernels.}
 			\begin{equation}
 				\label{eq:ris_power}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+				\mathbf{\Theta}_g^{(r+1)} = \underset{\mathbf{X}_g \in \mathbb{U}^{L \times L}}{\arg\min} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)\mathsf{H}},
 			\end{equation}
@@
 			% leads to a convergence of the objective function \eqref{ob:power} towards a stationary point,\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point due to the non-uniqueness of \gls{svd}, especially when $\mathbf{M}_g$ is rank-deficient.}
-			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of\footnote{We notice that $\mathbf{\Theta}_g$ coincides with the orthogonal projection of $\mathbf{M}_g$ onto the Stiefel manifold $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g$.} % \cite{Manton2002}
-			\begin{equation}
-				\label{eq:auxiliary_power}
-				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-			\end{equation}
-			Besides, when \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
+			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of $\mathbf{M}_g^{(r)}$.
+			% However, \eqref{eq:ris_power} might not converge to a single solution due to the non-uniqueness of \gls{svd}, c.f. Remark \ref{rm:svd}.
+			When \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
 		\end{proposition}
@@
 		\begin{proof}
-			Please refer to Appendix~\ref{ap:power}.
+			Please refer to Appendix~\ref{~ap:power} in the supplement.
 		\end{proof}
@@
 		\begin{remark}
-			\label{re:power}
-			The sequence \eqref{eq:auxiliary_power} is constructed iteratively from its orthogonal projection.
-			Although a formal proof remains elusive, empirical evidence from simulation indicates that \eqref{eq:auxiliary_power} converge, and thus \eqref{eq:ris_power} converges to a stationary point, for extensively tested scenarios.
-			% We thus conjecture that the sequence \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
+			\label{rm:power}
+			While a rigorous proof remains intricate due to the non-uniqueness of \gls{svd},
+			there is strong empirical evidence from simulation result that
+			% empirical evidence from extensive simulation indicates that
+			\eqref{eq:auxiliary_power} converges and \eqref{eq:ris_power} provides an optimal solution for vastly tested scenarios.
 		\end{remark}
@@
 	% 		\begin{proof}
-	% 			Please refer to Appendix~\ref{ap:wsr}.
+	% 			Please refer to Appendix~\ref{~ap:wsr} in the supplement.
 	% 		\end{proof}
@@
 	% 		\begin{proof}
-	% 			Please refer to Appendix~\ref{ap:interference}.
+	% 			Please refer to Appendix~\ref{~ap:interference} in the supplement.
 	% 		\end{proof}
@@
 			Fig.
-\ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc are highlighted on the Pareto frontiers.
-			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
+\ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point,\footnote{For \gls{mimo} wireless power transfer with \gls{rf} combining, the maximum harvested power depends solely on the dominant channel singular value \cite{Shen2021}.} and rate-optimal arc are highlighted on the Pareto frontiers.
+			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization.
+			% , and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
 			As the \gls{snr} increases, the rate-optimal point proceeds on the arc from the east (favoring $\sigma_1(\mathbf{H})$) to the north (favoring $\sigma_2(\mathbf{H})$).
@@
 
-\begin{appendix}
-	\begin{subsection}{Proof of Proposition \ref{pp:dof}}
-		\label{ap:dof}
-		It suffices to consider the rank of the indirect channel.
-		Denote the \gls{svd} of the backward and forward channels as
-		\begin{equation*}
-			\mathbf{H}_\mathrm{B/F} = \begin{bmatrix}
-				\mathbf{U}_{\mathrm{B/F},1} & \mathbf{U}_{\mathrm{B/F},2}
-			\end{bmatrix}
-			\begin{bmatrix}
-				\mathbf{\Sigma}_{\mathrm{B/F},1} & \mathbf{0} \\
-				\mathbf{0}                     & \mathbf{0}
-			\end{bmatrix}
-			\begin{bmatrix}
-				\mathbf{V}_{\mathrm{B/F},1}^\mathsf{H} \\
-				\mathbf{V}_{\mathrm{B/F},2}^\mathsf{H}
-			\end{bmatrix},
-		\end{equation*}
-		where $\mathbf{U}_{\mathrm{B/F},1}$ and $\mathbf{V}_{\mathrm{B/F},1}$ are any left and right singular matrices of $\mathbf{H}_\mathrm{B/F}$ corresponding to non-zero singular values $\mathbf{\Sigma}_{\mathrm{B/F},1}$, and $\mathbf{U}_{\mathrm{B/F},2}$ and $\mathbf{V}_{\mathrm{B/F},2}$ are those corresponding to zero singular values.
-		The rank of the indirect channel is \cite[(16.5.10.b)]{Hogben2013}
-		\begin{equation*}
-			\begin{split}
-				\rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
-				& = \rank(\mathbf{H}_\mathrm{B}) - \dim \bigl(\ker(\mathbf{H}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H}) \cap \ran(\mathbf{H}_\mathrm{B}^\mathsf{H})\bigr) \\
-				& = \rank(\mathbf{H}_\mathrm{B}) - \dim \bigl(\ran(\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}) \cap \ran(\mathbf{V}_{\mathrm{B},1})\bigr) \\
-				& \triangleq r_\mathrm{B} - r_\mathrm{L}(\mathbf{\Theta}),
-			\end{split}
-		\end{equation*}
-		where we define $r_\mathrm{L}(\mathbf{\Theta}) \triangleq \dim \bigl(\ran(\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}) \cap \ran(\mathbf{V}_{\mathrm{B},1})\bigr)$ and $r_\mathrm{B/F} \triangleq \rank(\mathbf{H}_\mathrm{B/F})$.
-		Since $\mathbf{U}_{\mathrm{F},2} \in \mathbb{U}^{N_\mathrm{S} \times (N_\mathrm{S} - r_\mathrm{F})}$ and $\mathbf{V}_{\mathrm{B},1} \in \mathbb{U}^{N_\mathrm{S} \times r_\mathrm{B}}$, we have $\max(r_\mathrm{B} - r_\mathrm{F}, 0) \le r_\mathrm{L}(\mathbf{\Theta}) \le \min(N_\mathrm{S} - r_\mathrm{F}, r_\mathrm{B})$
-		and thus
-		\begin{equation}
-			\label{iq:rank_indirect}
-			\max(r_\mathrm{B} + r_\mathrm{F} - N_\mathrm{S}, 0) \le \rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \le \min(r_\mathrm{B}, r_\mathrm{F}).
-		\end{equation}
-		To attain the upper bound in \eqref{iq:rank_indirect}, the \gls{ris} needs to minimize $r_\mathrm{L}(\mathbf{\Theta})$ by aligning the ranges of $\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}$ and $\mathbf{V}_{\mathrm{B},2}$ as much as possible.
-		This is achieved by
-		\begin{equation}
-			\label{eq:ris_dof_max}
-			\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} = \mathbf{Q}_{\mathrm{B},2} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H},
-		\end{equation}
-		where $\mathbf{Q}_{\mathrm{B},2}$ and $\mathbf{Q}_{\mathrm{F},2}$ are the unitary matrices of the QR decomposition of $\mathbf{V}_{\mathrm{B},2}$ and $\mathbf{U}_{\mathrm{F},2}$, respectively.
-		Similarly, the lower bound in \eqref{iq:rank_indirect} is attained at
-		\begin{equation}
-			\label{eq:ris_dof_min}
-			\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} = \mathbf{Q}_{\mathrm{B},1} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H},
-		\end{equation}
-		where $\mathbf{Q}_{\mathrm{B},1}$ is the unitary matrix of the QR decomposition of $\mathbf{V}_{\mathrm{B},1}$.
-		While the \gls{dof}-optimal structures \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min} are always feasible for fully-connected \gls{bd}-\gls{ris}, they are generally infeasible for \gls{d}-\gls{ris} unless there exist some QR decomposition that diagonalize $\mathbf{Q}_{\mathrm{B},2} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H}$ and $\mathbf{Q}_{\mathrm{B},1} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H}$ simultaneously.
-		That is, \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{dof} of indirect channel, and thus equivalent channel, than \gls{d}-\gls{ris}.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pp:rd}}
-		\label{ap:rank_deficient}
-		We consider rank-$k$ forward channel and the proof follows similarly for rank-$k$ backward channel.
-		Let $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the forward channel.
-		The channel Gram matrix $\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} $ can be written as
-		\begin{equation*}
-			\begin{split}
-				\mathbf{G}
-				& = \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H}                                                         \\
-				& \quad + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H}       \\
-				& = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}                                                                                                                                                                                                               \\
-				& \quad + (\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F}) (\mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} + \mathbf{V}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{D}^\mathsf{H}) \\
-				& = \mathbf{Y} + \mathbf{Z} \mathbf{Z}^\mathsf{H},
-			\end{split}
-		\end{equation*}
-		where we define $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H} \in \mathbb{H}^{N_\mathrm{R} \times N_\mathrm{R}}$ and $\mathbf{Z} \triangleq \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{R} \times k}$.
-		That is to say, $\mathbf{G}$ can be expressed as a Hermitian matrix plus $k$ rank-1 perturbations.
-		According to the Cauchy interlacing formula \cite[Theorem 8.4.3]{Golub2013}, the $n$-th eigenvalue of $\mathbf{G}$ is bounded by
-		\begin{align}
-			\lambda_n(\mathbf{G}) & \le \lambda_{n-k}(\mathbf{Y}), &  & \text{if } n > k, \label{iq:ev_rd_max}          \\
-			\lambda_n(\mathbf{G}) & \ge \lambda_n(\mathbf{Y}),     &  & \text{if } n < N - k + 1 \label{iq:ev_rd_min}.
-		\end{align}
-		Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, taking the square roots of \eqref{iq:ev_rd_max} and \eqref{iq:ev_rd_min} gives \eqref{iq:sv_rd_max} and \eqref{iq:sv_rd_min}.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pp:nd}}
-		\label{ap:nd}
-		Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
-		The scattering matrix of fully-connected \gls{bd}-\gls{ris} can be decomposed as
-		\begin{equation}
-			\label{eq:ris_decompose}
-			\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{X} \mathbf{U}_\mathrm{F}^\mathsf{H},
-		\end{equation}
-		where $\mathbf{X} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ is a unitary matrix to be designed.
-		The equivalent channel is thus a function of $\mathbf{X}$
-		\begin{equation}
-			\label{eq:channel_nd}
-			\mathbf{H} = \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}.
-		\end{equation}
-		Since $\sv(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \sv(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
-		\begin{equation}
-			\label{eq:sv_factor}
-			\begin{split}
-				\sv(\mathbf{H}) & = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})                                                                     \\
-								& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})                                                                                                                            \\
-								& = \sv(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H}) \\
-								& = \sv(\mathbf{BF}),
-			\end{split}
-		\end{equation}
-		where $\bar{\mathbf{U}}_{\mathrm{B}} \in \mathbb{U}^{N_\mathrm{R} \times N_\mathrm{R}}$, $\bar{\mathbf{V}}_\mathrm{B}, \bar{\mathbf{U}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\bar{\mathbf{V}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{T} \times N_\mathrm{T}}$ can be designed arbitrarily.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Corollary \ref{co:nd_sv_prod_tail}}
-		\label{ap:nd_sv_prod_tail}
-		\eqref{iq:sv_nd_prod_largest} follows from \eqref{iq:horn} when $r = k$.
-		On the other hand, if we can prove
-		\begin{equation}
-			\label{eq:sv_prod_all_ext}
-			\prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
-		\end{equation}
-		then \eqref{iq:sv_nd_prod_smallest} follows from \eqref{iq:sv_nd_prod_largest} and the non-negativity of singular values.
-		To see \eqref{eq:sv_prod_all_ext}, we start from a stricter result
-		\begin{equation}
-			\label{eq:sv_product_all}
-			\prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
-		\end{equation}
-		which is provable by cases.
-		When $N_\mathrm{S} > N$, both sides of \eqref{eq:sv_product_all} become zero since $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}_\mathrm{B}) = \sigma_n(\mathbf{H}_\mathrm{F}) = 0$ for $n > N$.
-		When $N_\mathrm{S} \le N$, we have
-		\begin{equation*}
-			\begin{split}
-				\prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H})
-				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})             \\
-				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\hat{\mathbf{\Sigma}}_\mathrm{B} \mathbf{X} \hat{\mathbf{\Sigma}}_\mathrm{F}) \\
-				& = \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{B} \mathbf{X} \hat{\mathbf{\Sigma}}_\mathrm{F}\bigr)                               \\
-				& = \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{B}\bigr) \det(\mathbf{X}) \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{F}\bigr)         \\
-				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{\Sigma}_\mathrm{B}) \sigma_n(\mathbf{\Sigma}_\mathrm{F}),
-			\end{split}
-		\end{equation*}
-		where the first equality follows from \eqref{eq:sv_factor} and $\hat{\mathbf{\Sigma}}_\mathrm{B}, \hat{\mathbf{\Sigma}}_\mathrm{F}$ truncate $\mathbf{\Sigma}_\mathrm{B}, \mathbf{\Sigma}_\mathrm{F}$ to square matrices of dimension $N_\mathrm{S}$, respectively.
-		It is evident that \eqref{eq:sv_product_all} implies \eqref{eq:sv_prod_all_ext} and thus \eqref{iq:sv_nd_prod_smallest}.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Corollary \ref{co:nd_sv_indl}}
-		\label{ap:nd_sv_indl}
-		In \eqref{iq:sv_nd_indl}, the set of upper bounds
-		\begin{equation}
-			\label{iq:sv_nd_indl_set_max}
-			\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+1\bigr\}
-		\end{equation}
-		is a special case of \eqref{iq:horn} with $(I, J, K) \in [N_\mathrm{S}]^3$.
-		The minimum\footnote{One may think to take the maximum of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
-However, this is infeasible since the singular values will be reordered.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
-		On the other hand, the set of lower bounds
-		\begin{equation}
-			\label{iq:sv_nd_indl_set_min}
-			\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+N_\mathrm{S}\bigr\}
-		\end{equation}
-		can be induced by \eqref{iq:sv_nd_indl_set_max}, \eqref{eq:sv_product_all}, and the non-negativity of singular values.
-		The maximum of \eqref{iq:sv_nd_indl_set_min} is selected as the tightest lower bound in \eqref{iq:sv_nd_indl}.
-		Interested readers are also referred to \cite[(2.0.3)]{Zhang2005}.
-
-		To attain the upper bound, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ channel singular values.
-		It follows from \eqref{eq:ris_nd_sv_indl_max} that
-		\begin{equation*}
-			\begin{split}
-				\sv(\mathbf{H})
-				& = \sv(\mathbf{H}_\mathrm{B} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{F})                                                                                                                         \\
-				& = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \\
-				& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Sigma}_\mathrm{F}).
-			\end{split}
-		\end{equation*}
-		On the one hand, $\mathbf{P}_{ij}=1$ with $(i, j)$ satisfying \eqref{eq:idx_nd_sv_indl_max} ensures $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is a singular value of $\mathbf{H}$.
-		It is actually among the first $n$ since the number of pairs $(i',j')$ not majorized by $(i,j)$ is $n-1$.
-		On the other hand, \eqref{eq:perm_nd_sv_indl_max} ensures the first $(n-1)$-th singular values are no smaller than $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$.
-		Combining both facts, we claim the upper bound $\sigma_n(\mathbf{H}) = \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is attainable by \eqref{eq:ris_nd_sv_indl_max}.
-		The attainability of the lower bound can be proved similarly and the details are omitted.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Corollary \ref{co:nd_power}}
-		\label{ap:nd_power}
-		From \eqref{eq:ris_decompose} and \eqref{eq:channel_nd} we have
-		\begin{equation}
-			\begin{split}
-				\lVert \mathbf{H} \rVert _\mathrm{F}^2
-				& = \tr \bigl(\mathbf{V}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{U}_\mathrm{B}^\mathsf{H} \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}\bigr) \\
-				& = \tr \bigl(\mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \cdot \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H}\bigr)                                                                                                         \\
-				& \triangleq \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr),
-			\end{split}
-		\end{equation}
-		where $\mathbf{X} \triangleq \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, $\tilde{\mathbf{B}} \triangleq \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\tilde{\mathbf{F}} \triangleq \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$.
-		By Ruhe's trace inequality for positive semi-definite matrices \cite[(H.1.g) and (H.1.h)]{Marshall2010},
-		\begin{equation*}
-			\sum_{n=1}^N \lambda_n(\tilde{\mathbf{B}}) \lambda_{N_\mathrm{S}-n+1}(\tilde{\mathbf{F}}) \le \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr) \le \sum_{n=1}^N \lambda_n(\tilde{\mathbf{B}}) \lambda_n(\tilde{\mathbf{F}}),
-		\end{equation*}
-		which simplifies to \eqref{iq:power_nd}.
-		The upper bound is attained when $\mathbf{X}$ is chosen to match the singular values of $\tilde{\mathbf{F}}$ to those of $\tilde{\mathbf{B}}$ in similar order.
-		Apparently this occurs at $\mathbf{X} = \mathbf{I}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
-		On the other hand, the lower bound is attained when the singular values of $\tilde{\mathbf{F}}$ and $\tilde{\mathbf{B}}$ are matched in reverse order, namely $\mathbf{X} = \mathbf{J}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Corollary \ref{co:nd_capacity_snr_extreme}}
-		\label{ap:nd_capacity}
-		When perfect \gls{csi} is available at the transmitter, in the low-\gls{snr} regime, the capacity is achieved by dominant eigenmode transmission \cite[(5.26)]{Clerckx2013}
-		\begin{align*}
-			C_{\rho_\downarrow}
-			& = \log\bigl(1 + \rho \lambda_1(\mathbf{H}^\mathsf{H} \mathbf{H})\bigr)        \\
-			& = \log\bigl(1 + \rho \sigma_1^2(\mathbf{H})\bigr)                             \\
-			& \approx \rho \sigma_1^2(\mathbf{H})                                           \\
-			& \le \rho \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}),
-		\end{align*}
-		where the approximation is $\log(1 + x) \approx x$ for small $x$ and the inequality follows from \eqref{iq:sv_nd_prod_largest} with $k=1$.
-		In the high-\gls{snr} regime, the capacity is achieved by multiple eigenmode transmission with uniform power location \cite[(5.27)]{Clerckx2013}
-		\begin{align*}
-			C_{\rho_\uparrow}
-			& = \sum\nolimits_{n=1}^N \log\Bigl(1 + \frac{\rho}{N} \lambda_n(\mathbf{H}^\mathsf{H} \mathbf{H})\Bigr)                     \\
-			& \approx \sum\nolimits_{n=1}^N \log\Bigl(\frac{\rho}{N} \sigma_n^2(\mathbf{H})\Bigr)                                        \\
-			& = N \log \frac{\rho}{N} + \sum\nolimits_{n=1}^N \log \sigma_n^2(\mathbf{H})                                                \\
-			& = N \log \frac{\rho}{N} + \log \prod\nolimits_{n=1}^N \sigma_n^2(\mathbf{H})                                               \\
-			& \le N \log \frac{\rho}{N} + 2 \log \prod\nolimits_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
-		\end{align*}
-		where the approximation is $\log(1 + x) \approx \log(x)$ for large $x$ and the inequality follows from \eqref{iq:sv_nd_prod_largest} with $k=N$.
-
-		We now show \eqref{eq:ris_nd_rate_max} can achieve the upper bounds in \eqref{iq:capacity_nd_snr_low} and \eqref{iq:capacity_nd_snr_high} simultaneously.
-		On the one hand, \eqref{eq:ris_nd_rate_max} is a special case of \eqref{eq:ris_nd_sv_indl_max} with $\mathbf{P} = \mathbf{I}$, which satisfies \eqref{eq:idx_nd_sv_indl_max} and \eqref{eq:perm_nd_sv_indl_max} for $n=1$ and thus attain $\sigma_1(\mathbf{H}) = \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
-		On the other hand, since $\log(\cdot)$ is a monotonic function, we can prove similar to Appendix \ref{ap:nd_power} that $\sum_{n=1}^N \log \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \log \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})$ and the bound is tight at \eqref{eq:ris_nd_rate_max}.
-		The proof is complete.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pp:shaping}}
-		\label{ap:shaping}
-		The sub-differential of a symmetric gauge function of singular values of a matrix with respect to the matrix itself is given by \cite[Theorem 2]{Watson1992}
-		\begin{equation}
-			\partial_{\mathbf{H}^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \bigr\},
-		\end{equation}
-		where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
-		It implies
-		\begin{align*}
-			\partial f\bigl(\sv(\mathbf{H})\bigr)
-			& \ni \tr \bigl(\mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \partial \mathbf{H}^*\bigr) \\
-			& = \tr \bigl(\mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \mathbf{H}_{\mathrm{F},g}^*\bigr) \\
-			& = \tr \bigl(\mathbf{H}_{\mathrm{F},g}^* \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \bigr),
-		\end{align*}
-		and therefore $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ constitutes a sub-gradient of $f\bigl(\sv(\mathbf{H})\bigr)$ with respect to $\mathbf{\Theta}_g$.
-		The convex hull of those sub-gradients is the sub-differential \eqref{eq:shaping_subdiff}.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Lemma \ref{lm:rate}}
-		\label{ap:rate}
-		The differential of $R$ with respect to $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
-		\begin{align*}
-			\partial R
-			& = \frac{1}{\eta} \tr \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}                                                                      \\
-			& = \frac{1}{\eta} \tr \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\} \\
-			& = \frac{1}{\eta} \tr \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
-		\end{align*}
-		and the corresponding complex derivative is \eqref{eq:gradient_eucl_rate}.
-	\end{subsection}
-
-	\begin{subsection}{Proof of Proposition \ref{pp:power}}
-		\label{ap:power}
-		The differential of \eqref{ob:power} with respect to $\mathbf{\Theta}_g^*$ is
-		\begin{align*}
-			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
-			& = \tr\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr) \\
-			& = \tr\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
-		\end{align*}
-		and the corresponding complex derivative is
-		\begin{equation}
-			\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \triangleq \mathbf{M}_g,
-		\end{equation}
-		whose \gls{svd} is denoted as $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$.
-		The quadratic objective \eqref{ob:power} can be successively approximated by its first-order Taylor expansion, resulting in the subproblem
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_ris_taylor}}{\label{ob:power_ris_taylor}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		\end{maxi!}
-		whose optimal solution is
-		\begin{equation}
-			\label{eq:ris_power_taylor}
-			\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}, \quad \forall g.
-		\end{equation}
-		This is because $\Re \bigl\{\tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \tr(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \tr(\mathbf{\Sigma}_g)$ and the bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$.
-
-		Next, we prove that solving the affine approximation \eqref{op:power_ris_taylor} by \eqref{eq:ris_power_taylor} does not decrease \eqref{ob:power}.
-		Since $\tilde{\mathbf{\Theta}} = \diag(\tilde{\mathbf{\Theta}}_1, \ldots, \tilde{\mathbf{\Theta}}_G)$ is optimal for \eqref{op:power_ris_taylor}, we have
-		\begin{equation}
-			\label{iq:power_ris_taylor}
-			\begin{split}
-				2 \Re \bigl\{ & \sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
-				& + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\} \\
-				\ge 2 \Re \bigl\{ &\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
-				& + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}.
-			\end{split}
-		\end{equation}
-		Besides, $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ implies
-		\begin{equation}
-			\label{iq:auxiliary_nonnegative}
-			\begin{split}
-				& \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \\
-				& \quad + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \\
-				\ge & 2 \Re \bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\bigr\}.
-			\end{split}
-		\end{equation}
-		Adding \eqref{iq:power_ris_taylor} and \eqref{iq:auxiliary_nonnegative}, we have
-		\begin{equation}
-			\begin{split}
-				& 2 \Re \bigl\{\tr(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
-				\ge & 2 \Re \bigl\{\tr({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
-			\end{split}
-		\end{equation}
-		which suggests that \eqref{ob:power} is non-decreasing as the solution iterates over \eqref{eq:ris_power_taylor}.
-		Since \eqref{ob:power} is also bounded from above, the sequence of objective value converges.
-
-		Finally, we prove that any solution when \eqref{eq:auxiliary_power} converges, denoted by $\mathbf{\Theta}'$, is a stationary point of \eqref{op:power}.
-		The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
-		\begin{gather}
-			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_ris_optimal}\\
-			\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_ris_taylor_optimal}
-		\end{gather}
-		When \eqref{eq:auxiliary_power} converges, $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}' \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ and \eqref{eq:power_ris_taylor_optimal} reduces to \eqref{eq:power_ris_optimal}.
-		The proof is thus completed.
-	\end{subsection}
-
-	% \begin{subsection}{Proof of Lemma \ref{lm:wsr}}
-	% 	\label{ap:wsr}
-	% 	The differential of $f = \sum_{k=1}^K \rho_k R_k$ with respect to $\mathbf{\Theta}_g^*$ is
+% \begin{appendix}
+% 	\begin{subsection}{Proof of Proposition \ref{pp:dof}}
+% 		\label{ap:dof}
+% 		It suffices to consider the rank of the indirect channel.
+% 		Denote the \gls{svd} of the backward and forward channels as
+% 		\begin{equation*}
+% 			\mathbf{H}_\mathrm{B/F} = \begin{bmatrix}
+% 				\mathbf{U}_{\mathrm{B/F},1} & \mathbf{U}_{\mathrm{B/F},2}
+% 			\end{bmatrix}
+% 			\begin{bmatrix}
+% 				\mathbf{\Sigma}_{\mathrm{B/F},1} & \mathbf{0} \\
+% 				\mathbf{0}                     & \mathbf{0}
+% 			\end{bmatrix}
+% 			\begin{bmatrix}
+% 				\mathbf{V}_{\mathrm{B/F},1}^\mathsf{H} \\
+% 				\mathbf{V}_{\mathrm{B/F},2}^\mathsf{H}
+% 			\end{bmatrix},
+% 		\end{equation*}
+% 		where $\mathbf{U}_{\mathrm{B/F},1}$ and $\mathbf{V}_{\mathrm{B/F},1}$ are any left and right singular matrices of $\mathbf{H}_\mathrm{B/F}$ corresponding to non-zero singular values $\mathbf{\Sigma}_{\mathrm{B/F},1}$, and $\mathbf{U}_{\mathrm{B/F},2}$ and $\mathbf{V}_{\mathrm{B/F},2}$ are those corresponding to zero singular values.
+% 		The rank of the indirect channel is \cite[(16.5.10.b)]{Hogben2013}
+% 		\begin{equation*}
+% 			\begin{split}
+% 				\rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
+% 				& = \rank(\mathbf{H}_\mathrm{B}) - \dim \bigl(\ker(\mathbf{H}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H}) \cap \ran(\mathbf{H}_\mathrm{B}^\mathsf{H})\bigr) \\
+% 				& = \rank(\mathbf{H}_\mathrm{B}) - \dim \bigl(\ran(\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}) \cap \ran(\mathbf{V}_{\mathrm{B},1})\bigr) \\
+% 				& \triangleq r_\mathrm{B} - r_\mathrm{L}(\mathbf{\Theta}),
+% 			\end{split}
+% 		\end{equation*}
+% 		where we define $r_\mathrm{L}(\mathbf{\Theta}) \triangleq \dim \bigl(\ran(\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}) \cap \ran(\mathbf{V}_{\mathrm{B},1})\bigr)$ and $r_\mathrm{B/F} \triangleq \rank(\mathbf{H}_\mathrm{B/F})$.
+% 		Since $\mathbf{U}_{\mathrm{F},2} \in \mathbb{U}^{N_\mathrm{S} \times (N_\mathrm{S} - r_\mathrm{F})}$ and $\mathbf{V}_{\mathrm{B},1} \in \mathbb{U}^{N_\mathrm{S} \times r_\mathrm{B}}$, we have $\max(r_\mathrm{B} - r_\mathrm{F}, 0) \le r_\mathrm{L}(\mathbf{\Theta}) \le \min(N_\mathrm{S} - r_\mathrm{F}, r_\mathrm{B})$
+% 		and thus
+% 		\begin{equation}
+% 			\label{iq:rank_indirect}
+% 			\max(r_\mathrm{B} + r_\mathrm{F} - N_\mathrm{S}, 0) \le \rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \le \min(r_\mathrm{B}, r_\mathrm{F}).
+% 		\end{equation}
+% 		To attain the upper bound in \eqref{iq:rank_indirect}, the \gls{ris} needs to minimize $r_\mathrm{L}(\mathbf{\Theta})$ by aligning the ranges of $\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}$ and $\mathbf{V}_{\mathrm{B},2}$ as much as possible.
+% 		This is achieved by
+% 		\begin{equation}
+% 			\label{eq:ris_dof_max}
+% 			\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} = \mathbf{Q}_{\mathrm{B},2} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H},
+% 		\end{equation}
+% 		where $\mathbf{Q}_{\mathrm{B},2}$ and $\mathbf{Q}_{\mathrm{F},2}$ are the unitary matrices of the QR decomposition of $\mathbf{V}_{\mathrm{B},2}$ and $\mathbf{U}_{\mathrm{F},2}$, respectively.
+% 		Similarly, the lower bound in \eqref{iq:rank_indirect} is attained at
+% 		\begin{equation}
+% 			\label{eq:ris_dof_min}
+% 			\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} = \mathbf{Q}_{\mathrm{B},1} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H},
+% 		\end{equation}
+% 		where $\mathbf{Q}_{\mathrm{B},1}$ is the unitary matrix of the QR decomposition of $\mathbf{V}_{\mathrm{B},1}$.
+% 		While the \gls{dof}-optimal structures \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min} are always feasible for fully-connected \gls{bd}-\gls{ris}, they are generally infeasible for \gls{d}-\gls{ris} unless there exist some QR decomposition that diagonalize $\mathbf{Q}_{\mathrm{B},2} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H}$ and $\mathbf{Q}_{\mathrm{B},1} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H}$ simultaneously.
+% 		That is, \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{dof} of indirect channel, and thus equivalent channel, than \gls{d}-\gls{ris}.
+% 	\end{subsection}
+
+% 	\begin{subsection}{Proof of Proposition \ref{pp:rd}}
+% 		\label{ap:rank_deficient}
+% 		We consider rank-$k$ forward channel and the proof follows similarly for rank-$k$ backward channel.
+% 		Let $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the forward channel.
+% 		The channel Gram matrix $\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} $ can be written as
+% 		\begin{equation*}
+% 			\begin{split}
+% 				\mathbf{G}
+% 				& = \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H}                                                         \\
+% 				& \quad + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H}       \\
+% 				& = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}                                                                                                                                                                                                               \\
+% 				& \quad + (\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F}) (\mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} + \mathbf{V}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{D}^\mathsf{H}) \\
+% 				& = \mathbf{Y} + \mathbf{Z} \mathbf{Z}^\mathsf{H},
+% 			\end{split}
+% 		\end{equation*}
+% 		where we define $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H} \in \mathbb{H}^{N_\mathrm{R} \times N_\mathrm{R}}$ and $\mathbf{Z} \triangleq \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{R} \times k}$.
+% 		That is to say, $\mathbf{G}$ can be expressed as a Hermitian matrix plus $k$ rank-1 perturbations.
+% 		According to the Cauchy interlacing formula \cite[Theorem 8.4.3]{Golub2013}, the $n$-th eigenvalue of $\mathbf{G}$ is bounded by
+% 		\begin{align}
+% 			\lambda_n(\mathbf{G}) & \le \lambda_{n-k}(\mathbf{Y}), &  & \text{if } n > k, \label{iq:ev_rd_max}          \\
+% 			\lambda_n(\mathbf{G}) & \ge \lambda_n(\mathbf{Y}),     &  & \text{if } n < N - k + 1 \label{iq:ev_rd_min}.
+% 		\end{align}
+% 		Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, taking the square roots of \eqref{iq:ev_rd_max} and \eqref{iq:ev_rd_min} gives \eqref{iq:sv_rd_max} and \eqref{iq:sv_rd_min}.
+% 	\end{subsection}
+
+% 	\begin{subsection}{Proof of Proposition \ref{pp:nd}}
+% 		\label{ap:nd}
+% 		Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
+% 		The scattering matrix of fully-connected \gls{bd}-\gls{ris} can be decomposed as
+% 		\begin{equation}
+% 			\label{eq:ris_decompose}
+% 			\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{X} \mathbf{U}_\mathrm{F}^\mathsf{H},
+% 		\end{equation}
+% 		where $\mathbf{X} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ is a unitary matrix to be designed.
+% 		The equivalent channel is thus a function of $\mathbf{X}$
+% 		\begin{equation}
+% 			\label{eq:channel_nd}
+% 			\mathbf{H} = \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}.
+% 		\end{equation}
+% 		Since $\sv(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \sv(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
+% 		\begin{equation}
+% 			\label{eq:sv_factor}
+% 			\begin{split}
+% 				\sv(\mathbf{H}) & = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})                                                                     \\
+% 								& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})                                                                                                                            \\
+% 								& = \sv(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H}) \\
+% 								& = \sv(\mathbf{BF}),
+% 			\end{split}
+% 		\end{equation}
+% 		where $\bar{\mathbf{U}}_{\mathrm{B}} \in \mathbb{U}^{N_\mathrm{R} \times N_\mathrm{R}}$, $\bar{\mathbf{V}}_\mathrm{B}, \bar{\mathbf{U}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\bar{\mathbf{V}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{T} \times N_\mathrm{T}}$ can be designed arbitrarily.
+% 	\end{subsection}
+
+% 	\begin{subsection}{Proof of Corollary \ref{co:nd_sv_prod_tail}}
+% 		\label{ap:nd_sv_prod_tail}
+% 		\eqref{iq:sv_nd_prod_largest} follows from \eqref{iq:horn} when $r = k$.
+% 		On the other hand, if we can prove
+% 		\begin{equation}
+% 			\label{eq:sv_prod_all_ext}
+% 			\prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
+% 		\end{equation}
+% 		then \eqref{iq:sv_nd_prod_smallest} follows from \eqref{iq:sv_nd_prod_largest} and the non-negativity of singular values.
+% 		To see \eqref{eq:sv_prod_all_ext}, we start from a stricter result
+% 		\begin{equation}
+% 			\label{eq:sv_product_all}
+% 			\prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
+% 		\end{equation}
+% 		which is provable by cases.
+% 		When $N_\mathrm{S} > N$, both sides of \eqref{eq:sv_product_all} become zero since $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}_\mathrm{B}) = \sigma_n(\mathbf{H}_\mathrm{F}) = 0$ for $n > N$.
+% 		When $N_\mathrm{S} \le N$, we have
+% 		\begin{equation*}
+% 			\begin{split}
+% 				\prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H})
+% 				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})             \\
+% 				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\hat{\mathbf{\Sigma}}_\mathrm{B} \mathbf{X} \hat{\mathbf{\Sigma}}_\mathrm{F}) \\
+% 				& = \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{B} \mathbf{X} \hat{\mathbf{\Sigma}}_\mathrm{F}\bigr)                               \\
+% 				& = \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{B}\bigr) \det(\mathbf{X}) \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{F}\bigr)         \\
+% 				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{\Sigma}_\mathrm{B}) \sigma_n(\mathbf{\Sigma}_\mathrm{F}),
+% 			\end{split}
+% 		\end{equation*}
+% 		where the first equality follows from \eqref{eq:sv_factor} and $\hat{\mathbf{\Sigma}}_\mathrm{B}, \hat{\mathbf{\Sigma}}_\mathrm{F}$ truncate $\mathbf{\Sigma}_\mathrm{B}, \mathbf{\Sigma}_\mathrm{F}$ to square matrices of dimension $N_\mathrm{S}$, respectively.
+% 		It is evident that \eqref{eq:sv_product_all} implies \eqref{eq:sv_prod_all_ext} and thus \eqref{iq:sv_nd_prod_smallest}.
+% 	\end{subsection}
+
+% 	\begin{subsection}{Proof of Corollary \ref{co:nd_sv_indl}}
+% 		\label{ap:nd_sv_indl}
+% 		In \eqref{iq:sv_nd_indl}, the set of upper bounds
+% 		\begin{equation}
+% 			\label{iq:sv_nd_indl_set_max}
+% 			\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+1\bigr\}
+% 		\end{equation}
+% 		is a special case of \eqref{iq:horn} with $(I, J, K) \in [N_\mathrm{S}]^3$.
+% 		The minimum\footnote{One may think to take the maximum of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value.
+This is infeasible since the singular values will be reordered.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
+% 		On the other hand, the set of lower bounds
+% 		\begin{equation}
+% 			\label{iq:sv_nd_indl_set_min}
+% 			\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+N_\mathrm{S}\bigr\}
+% 		\end{equation}
+% 		can be induced by \eqref{iq:sv_nd_indl_set_max}, \eqref{eq:sv_product_all}, and the non-negativity of singular values.
+% 		The maximum of \eqref{iq:sv_nd_indl_set_min} is selected as the tightest lower bound in \eqref{iq:sv_nd_indl}.
+% 		Interested readers are also referred to \cite[(2.0.3)]{Zhang2005}.
+
+% 		To attain the upper bound, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ channel singular values.
+% 		It follows from \eqref{eq:ris_nd_sv_indl_max} that
+% 		\begin{equation*}
+% 			\begin{split}
+% 				\sv(\mathbf{H})
+% 				& = \sv(\mathbf{H}_\mathrm{B} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{F})                                                                                                                         \\
+% 				& = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \\
+% 				& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Sigma}_\mathrm{F}).
+% 			\end{split}
+% 		\end{equation*}
+% 		On the one hand, $\mathbf{P}_{ij}=1$ with $(i, j)$ satisfying \eqref{eq:idx_nd_sv_indl_max} ensures $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is a singular value of $\mathbf{H}$.
+% 		It is actually among the first $n$ since the number of pairs $(i',j')$ not majorized by $(i,j)$ is $n-1$.
+% 		On the other hand, \eqref{eq:perm_nd_sv_indl_max} ensures the first $(n-1)$-th singular values are no smaller than $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$.
+% 		Combining both facts, we claim the upper bound $\sigma_n(\mathbf{H}) = \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is attainable by \eqref{eq:ris_nd_sv_indl_max}.
+% 		The attainability of the lower bound can be proved similarly and the details are omitted.
+% 	\end{subsection}
+
+% 	\begin{subsection}{Proof of Corollary \ref{co:nd_power}}
+% 		\label{ap:nd_power}
+% 		From \eqref{eq:ris_decompose} and \eqref{eq:channel_nd} we have
+% 		\begin{equation}
+% 			\begin{split}
+% 				\lVert \mathbf{H} \rVert _\mathrm{F}^2
+% 				& = \tr \bigl(\mathbf{V}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{U}_\mathrm{B}^\mathsf{H} \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}\bigr) \\
+% 				& = \tr \bigl(\mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \cdot \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H}\bigr)                                                                                                         \\
+% 				& \triangleq \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr),
+% 			\end{split}
+% 		\end{equation}
+% 		where $\mathbf{X} \triangleq \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, $\tilde{\mathbf{B}} \triangleq \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\tilde{\mathbf{F}} \triangleq \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$.
+% 		By Ruhe's trace inequality for positive semi-definite matrices \cite[(H.1.g) and (H.1.h)]{Marshall2010},
+% 		\begin{equation*}
+% 			\sum_{n=1}^N \lambda_n(\tilde{\mathbf{B}}) \lambda_{N_\mathrm{S}-n+1}(\tilde{\mathbf{F}}) \le \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr) \le \sum_{n=1}^N \lambda_n(\tilde{\mathbf{B}}) \lambda_n(\tilde{\mathbf{F}}),
+% 		\end{equation*}
+% 		which simplifies to \eqref{iq:power_nd}.
+% 		The upper bound is attained when $\mathbf{X}$ is chosen to match the singular values of $\tilde{\mathbf{F}}$ to those of $\tilde{\mathbf{B}}$ in similar order.
+% 		Apparently this occurs at $\mathbf{X} = \mathbf{I}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
+% 		On the other hand, the lower bound is attained when the singular values of $\tilde{\mathbf{F}}$ and $\tilde{\mathbf{B}}$ are matched in reverse order, namely $\mathbf{X} = \mathbf{J}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
+% 	\end{subsection}
+
+% 	\begin{subsection}{Proof of Corollary \ref{co:nd_capacity_snr_extreme}}
+% 		\label{ap:nd_capacity}
+% 		When perfect \gls{csi} is available at the transmitter, in the low-\gls{snr} regime, the capacity is achieved by dominant eigenmode transmission \cite[(5.26)]{Clerckx2013}
 % 		\begin{align*}
-	% 		\partial f
-	% 		& = \sum_{k=1}^K \rho_k \tr \Bigl\{ \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \Bigl( \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \\
-	% 		& \quad + \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(k)} - \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \\
-	% 		& \quad \times \sum_{j \ne k} \Bigl(\mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \\
-	% 		& \quad + \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \Bigr) \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \Bigr) \mathbf{W}_k \Bigr\} \\
-	% 		& = \sum_{k=1}^K \rho_k \Bigl( \tr \Bigl\{ \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H}\Bigr\} \\
-	% 		& \quad + \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g \Bigr\} \\
-	% 		& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \\
-	% 		& \quad \quad \times \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
-	% 		& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \\
-	% 		& \quad \quad \times \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \Bigr\} \Bigr),
+% 			C_{\rho_\downarrow}
+% 			& = \log\bigl(1 + \rho \lambda_1(\mathbf{H}^\mathsf{H} \mathbf{H})\bigr)        \\
+% 			& = \log\bigl(1 + \rho \sigma_1^2(\mathbf{H})\bigr)                             \\
+% 			& \approx \rho \sigma_1^2(\mathbf{H})                                           \\
+% 			& \le \rho \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}),
 % 		\end{align*}
-	% 	and the corresponding complex derivative is \eqref{eq:gradient_eucl_wsr}.
+% 		where the approximation is $\log(1 + x) \approx x$ for small $x$ and the inequality follows from \eqref{iq:sv_nd_prod_largest} with $k=1$.
+% 		In the high-\gls{snr} regime, the capacity is achieved by multiple eigenmode transmission with uniform power location \cite[(5.27)]{Clerckx2013}
+% 		\begin{align*}
+% 			C_{\rho_\uparrow}
+% 			& = \sum\nolimits_{n=1}^N \log\Bigl(1 + \frac{\rho}{N} \lambda_n(\mathbf{H}^\mathsf{H} \mathbf{H})\Bigr)                     \\
+% 			& \approx \sum\nolimits_{n=1}^N \log\Bigl(\frac{\rho}{N} \sigma_n^2(\mathbf{H})\Bigr)                                        \\
+% 			& = N \log \frac{\rho}{N} + \sum\nolimits_{n=1}^N \log \sigma_n^2(\mathbf{H})                                                \\
+% 			& = N \log \frac{\rho}{N} + \log \prod\nolimits_{n=1}^N \sigma_n^2(\mathbf{H})                                               \\
+% 			& \le N \log \frac{\rho}{N} + 2 \log \prod\nolimits_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
+% 		\end{align*}
+% 		where the approximation is $\log(1 + x) \approx \log(x)$ for large $x$ and the inequality follows from \eqref{iq:sv_nd_prod_largest} with $k=N$.
+
+% 		We now show \eqref{eq:ris_nd_rate_max} can achieve the upper bounds in \eqref{iq:capacity_nd_snr_low} and \eqref{iq:capacity_nd_snr_high} simultaneously.
+% 		On the one hand, \eqref{eq:ris_nd_rate_max} is a special case of \eqref{eq:ris_nd_sv_indl_max} with $\mathbf{P} = \mathbf{I}$, which satisfies \eqref{eq:idx_nd_sv_indl_max} and \eqref{eq:perm_nd_sv_indl_max} for $n=1$ and thus attain $\sigma_1(\mathbf{H}) = \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
+% 		On the other hand, since $\log(\cdot)$ is a monotonic function, we can prove similar to Appendix \ref{ap:nd_power} that $\sum_{n=1}^N \log \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \log \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})$ and the bound is tight at \eqref{eq:ris_nd_rate_max}.
+% 		The proof is complete.
 % 	\end{subsection}
 
-	% \begin{subsection}{Proof of Proposition \ref{pp:interference}}
-	% 	\label{ap:interference}
-	% 	Minimizing \eqref{ob:interference} is equivalent to maximizing
+% 	\begin{subsection}{Proof of Proposition \ref{pp:shaping}}
+% 		\label{ap:shaping}
+% 		The sub-differential of a symmetric gauge function of singular values of a matrix with respect to the matrix itself is given by \cite[Theorem 2]{Watson1992}
+% 		\begin{equation}
+% 			\partial_{\mathbf{H}^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \bigr\},
+% 		\end{equation}
+% 		where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
+% 		It implies
 % 		\begin{align*}
-	% 		f(\mathbf{\Theta}) & = - I + \sum_g \beta_g^{(k)} \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \Bigr\} \\
-	% 		& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
-	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
-	% 		& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
-	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
-	% 		& \quad + \tr \Bigl\{ \sum_g \beta_g^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
-	% 		& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
-	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
-	% 		& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
-	% 		& \quad + \tr \Bigl\{ \sum_g \mathbf{B}_{g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\},
+% 			\partial f\bigl(\sv(\mathbf{H})\bigr)
+% 			& \ni \tr \bigl(\mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \partial \mathbf{H}^*\bigr) \\
+% 			& = \tr \bigl(\mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \mathbf{H}_{\mathrm{F},g}^*\bigr) \\
+% 			& = \tr \bigl(\mathbf{H}_{\mathrm{F},g}^* \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \bigr),
 % 		\end{align*}
-	% 	where $\mathbf{B}_{g}^{(k)} = \beta_g^{(k)} \mathbf{I} - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)}$ and the relaxation constant $\beta_g^{(k)}$ can be chosen arbitrarily.
-	% 	One can choose $\beta_g^{(k)} = \lambda_1(\mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)})$ to ensure the positive semi-definiteness of $\mathbf{B}_{g}^{(k)}$ and formulate a quadratic function to be maximized.
-	% 	The remaining proof is similar to Appendix \ref{ap:power} and omitted here.
+% 		and therefore $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ constitutes a sub-gradient of $f\bigl(\sv(\mathbf{H})\bigr)$ with respect to $\mathbf{\Theta}_g$.
+% 		The convex hull of those sub-gradients is the sub-differential \eqref{eq:shaping_subdiff}.
 % 	\end{subsection}
-\end{appendix}
-
-\begin{section}{Acknowledgement}
-	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct many technical errors.
-\end{section}
+
+% 	\begin{subsection}{Proof of Lemma \ref{lm:rate}}
+% 		\label{ap:rate}
+% 		The differential of $R$ with respect to $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
+% 		\begin{align*}
+% 			\partial R
+% 			& = \frac{1}{\eta} \tr \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}                                                                      \\
+% 			& = \frac{1}{\eta} \tr \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\} \\
+% 			& = \frac{1}{\eta} \tr \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
+% 		\end{align*}
+% 		and the corresponding complex derivative is \eqref{eq:gradient_eucl_rate}.
+% 	\end{subsection}
+
+% 	\begin{subsection}{Proof of Proposition \ref{pp:power}}
+% 		\label{ap:power}
+% 		The differential of \eqref{ob:power} with respect to $\mathbf{\Theta}_g^*$ is
+% 		\begin{align*}
+% 			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
+% 			& = \tr\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr) \\
+% 			& = \tr\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
+% 		\end{align*}
+% 		and the corresponding complex derivative is
+% 		\begin{equation}
+% 			\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \triangleq \mathbf{M}_g,
+% 		\end{equation}
+% 		whose \gls{svd} is denoted as $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$.
+% 		The quadratic objective \eqref{ob:power} can be successively approximated by its first-order Taylor expansion, resulting in the subproblem
+% 		\begin{maxi!}
+% 			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_ris_taylor}}{\label{ob:power_ris_taylor}}
+% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+% 		\end{maxi!}
+% 		whose optimal solution is
+% 		\begin{equation}
+% 			\label{eq:ris_power_taylor}
+% 			\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}, \quad \forall g.
+% 		\end{equation}
+% 		This is because $\Re \bigl\{\tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \tr(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \tr(\mathbf{\Sigma}_g)$ and the bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$.
+
+% 		Next, we prove that solving the affine approximation \eqref{op:power_ris_taylor} by \eqref{eq:ris_power_taylor} does not decrease \eqref{ob:power}.
+% 		Since $\tilde{\mathbf{\Theta}} = \diag(\tilde{\mathbf{\Theta}}_1, \ldots, \tilde{\mathbf{\Theta}}_G)$ is optimal for \eqref{op:power_ris_taylor}, we have
+% 		\begin{equation}
+% 			\label{iq:power_ris_taylor}
+% 			\begin{split}
+% 				2 \Re \bigl\{ & \sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
+% 				& + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\} \\
+% 				\ge 2 \Re \bigl\{ &\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
+% 				& + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}.
+% 			\end{split}
+% 		\end{equation}
+% 		Besides, $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ implies
+% 		\begin{equation}
+% 			\label{iq:auxiliary_nonnegative}
+% 			\begin{split}
+% 				& \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \\
+% 				& \quad + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \\
+% 				\ge & 2 \Re \bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\bigr\}.
+% 			\end{split}
+% 		\end{equation}
+% 		Adding \eqref{iq:power_ris_taylor} and \eqref{iq:auxiliary_nonnegative}, we have
+% 		\begin{equation}
+% 			\begin{split}
+% 				& 2 \Re \bigl\{\tr(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
+% 				\ge & 2 \Re \bigl\{\tr({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
+% 			\end{split}
+% 		\end{equation}
+% 		which suggests that \eqref{ob:power} is non-decreasing as the solution iterates over \eqref{eq:ris_power_taylor}.
+% 		Since \eqref{ob:power} is also bounded from above, the sequence of objective value converges.
+
+% 		Finally, we prove that any solution when \eqref{eq:auxiliary_power} converges, denoted by $\mathbf{\Theta}'$, is a stationary point of \eqref{op:power}.
+% 		The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
+% 		\begin{gather}
+% 			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_ris_optimal}\\
+% 			\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_ris_taylor_optimal}
+% 		\end{gather}
+% 		When \eqref{eq:auxiliary_power} converges, $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}' \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ and \eqref{eq:power_ris_taylor_optimal} reduces to \eqref{eq:power_ris_optimal}.
+% 		The proof is thus completed.
+% 	\end{subsection}
+
+% 	% \begin{subsection}{Proof of Lemma \ref{lm:wsr}}
+% 	% 	\label{ap:wsr}
+% 	% 	The differential of $f = \sum_{k=1}^K \rho_k R_k$ with respect to $\mathbf{\Theta}_g^*$ is
+% 	% 	\begin{align*}
+% 	% 		\partial f
+% 	% 		& = \sum_{k=1}^K \rho_k \tr \Bigl\{ \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \Bigl( \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \\
+% 	% 		& \quad + \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(k)} - \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \\
+% 	% 		& \quad \times \sum_{j \ne k} \Bigl(\mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \\
+% 	% 		& \quad + \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \Bigr) \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \Bigr) \mathbf{W}_k \Bigr\} \\
+% 	% 		& = \sum_{k=1}^K \rho_k \Bigl( \tr \Bigl\{ \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H}\Bigr\} \\
+% 	% 		& \quad + \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g \Bigr\} \\
+% 	% 		& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \\
+% 	% 		& \quad \quad \times \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+% 	% 		& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \\
+% 	% 		& \quad \quad \times \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \Bigr\} \Bigr),
+% 	% 	\end{align*}
+% 	% 	and the corresponding complex derivative is \eqref{eq:gradient_eucl_wsr}.
+% 	% \end{subsection}
+
+% 	% \begin{subsection}{Proof of Proposition \ref{pp:interference}}
+% 	% 	\label{ap:interference}
+% 	% 	Minimizing \eqref{ob:interference} is equivalent to maximizing
+% 	% 	\begin{align*}
+% 	% 		f(\mathbf{\Theta}) & = - I + \sum_g \beta_g^{(k)} \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \Bigr\} \\
+% 	% 		& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
+% 	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+% 	% 		& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
+% 	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
+% 	% 		& \quad + \tr \Bigl\{ \sum_g \beta_g^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
+% 	% 		& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
+% 	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
+% 	% 		& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
+% 	% 		& \quad + \tr \Bigl\{ \sum_g \mathbf{B}_{g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\},
+% 	% 	\end{align*}
+% 	% 	where $\mathbf{B}_{g}^{(k)} = \beta_g^{(k)} \mathbf{I} - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)}$ and the relaxation constant $\beta_g^{(k)}$ can be chosen arbitrarily.
+% 	% 	One can choose $\beta_g^{(k)} = \lambda_1(\mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)})$ to ensure the positive semi-definiteness of $\mathbf{B}_{g}^{(k)}$ and formulate a quadratic function to be maximized.
+% 	% 	The remaining proof is similar to Appendix \ref{ap:power} and omitted here.
+% 	% \end{subsection}
+% \end{appendix}
+
+% \begin{section}{Acknowledgement}
+% 	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct several technical errors.
+% \end{section}
 
